### 2018-06-01 express2018/part2.tex
Added 2nd part of the draft paper sources

%%%% -*- Mode: LaTeX -*-
%%
%% This is the draft of the 2nd part of EXPRESS/SOS 2018 paper, co-authored by
%% Prof. Davide Sangiorgi and Chun Tian.

\documentclass{eptcs} % required template (EPTCS) by EXPRESS/SOS 2018

%% Math symbol packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathrsfs}

\usepackage{stmaryrd}
\SetSymbolFont{stmry}{bold}{U}{stmry}{m}{n}
% \cupdot (the best one)
\newcommand{\cupdot}{\mathbin{\mathaccent\cdot\cup}}

\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{proposition}
\newtheorem{proposition}{Proposition}[section]

% HOL theorem embedding support
\usepackage{holindex}
\usepackage{alltt}
\include{tokens}

\usepackage[all,cmtip]{xy}

\begin{document}

\section{Formalization}

In the second half of this paper, we present a formalization of all new concepts and
theorems developed in the first part of this paper. The main purpose
is to convince the readers that, there's no flaw\footnote{Perheps this is the first
  time a frontier development in Concurrency Theory ships with its
  formalization in the same paper.} in those informal proofs. This work is based on a rather
complete formalization of CCS in HOL theorem prover
(HOL4), described in a MSc thesis \cite{Chun:2017} and now lives in
the official examples folder of HOL4 source
code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}.
The work is essentially a porting and extension of the early CCS
formalization by Monica Nesi \cite{Nesi} in HOL88.

We will not repeat all concepts and major theorems of CCS again in its
formalized ways, nor talk about the changes and improvements comparing
with previous CCS work including Nesi's. Instead, we just focus on our
targeting theorems. However, as the unique solution of (rooted)
contraction theorem stood at the end of a chain of results, it's
impossible to describe only their statements and formal proofs without
describing many dependent things first.  On the other side, it's very
hard to convince audience the novelty in a proof
engineering work, especially when there exists multiple formalizations
 in the same area. After all, the whole interactive theorem proving (ITP)
technique is just a translation of definitions and hand-made
proofs from their informal representations to their formal versions.

Unlike complicated large programs (e.g. operating systems) which
usually contain countless of bugs even after years of updates and
bugfixes, a huge prove engineering work can easily claim its
\emph{correctness} without concerning other aspects (performance,
quality of definitions, easiness of reading by human, etc.)
Yet still different formalizations (of the same theory) done by
different persons could be huge different, due to the great
flexibilities on choices making at the design of types, terms and
definitions. It's also quite common to break long original proofs into
small lemmas and reuse them in the proof of other relevant
theorems. For the same theorem, good and bad-killed proof engineers
(suppose they both finished the proof)
may result into very different proof steps of huge size
differences.\footnote{But it's not true that a shorter proof is always
better, and a shorted proof may not be executed faster if it heavily
depends on automatic proof searching tools such as Meson and Metis. On
the other side, longer proof without automatic proof searching can be
easier understood by students who are learning the theory being
formalized. Indeed, we have tried to follow the informal proof steps literally, and only used
automatic proof searching techniques on obvious small proof goals.}
Roughly speaking, there're relative ``good'' and ``bad'' designs and
considerations, but if they all \emph{correctly} formalized the same theory, few people
care about their differences, unless they want to extend existing work
to verify their new developments.

In the rest of this section, we're not going to repeat any proof steps
as they're essentially the same with the informal proofs. Instead, we
mostly focus on the key definitions, i.e. the formal
representation of various concepts, plus brief descriptions on
important stage theorem expressed in these definitions.

\subsection{Simplifications and Limitations}

We have only formally verified simplified forms of the unique
solution theorems introduced in the first part. This is to not only
save the formalization efforts, but also to make us focusing on the most
important part of the proof. The most important simplification is
that, we have only proved all unique solution theorems with only single-variable equations
(contractions).

But such a simplification doesn't hurt the rigorousness of our entire
work, as once the single-equation version of the theorem is
proven, the general case is just a routine
adaptation for paper proofs. \footnote{However, it's impossible to directly derive the
  multi-variable versions of unique solution theorems from their
  single-variable versions.} \footnote{Also, I don't know if there
  exists a higher-level general
  duality theorem such that some kind of results on single-variable CCS
  equations must also hold for multi-variable equation groups. --Chun.}
It's not easy to formalize multi-variable CCS equations with
introducing a large number of definitions and intermediate
results. It's easy, however, to directly use the semantics context to
represent single-variable equations without the need of formalizing
the concept of ``equation'' at all.

\subsubsection{Limitations}

There're two major limitations in this work. One is the class of CCS
processes, i.e. we're limited with Finitary CCS which has no infinite
sums or parallel compositions. The only important theorem in which
arbitrary infinite sums of CCS processes must be used, is the following
``coarsest congruence contained in weak bisimilarity'' theorem without
any limitations on the involved processes:
\begin{equation}
\forall p\; q.\; p \approx^c\! q \Longleftrightarrow \forall r.\; p+r \approx
q+r
\end{equation}
Milner's classical proof of above result needs to assume that $p$ and $q$ didn't
use up all available labels. The newer proof by van Glabbek requires a
special choice of $r$ which is not weak bisimilar with any process
transited from $p$ and $q$, and the actual chosen process may contain
arbitrary large sums of CCS processes. This goes beyond the
expressiveness of HOL, as result we followed the same proof ideas but
limited with finite state CCS only.

The other limitation is, even for single-variable equation, the
variable doesn't appear inside any constant.  For example, an equation like
$P \approx E\{P/X\}$ in which $E = A$ and $A \overset{\mathrm{def}}{=}
\tau.A + b.X$ is not supported, because the equation variable $X$
appears inside the definition of constant $A$. On the other side, if
$E = A + X$ with whatever definition of constant $A$ in which there's
no appearence of $X$, such equations are supported. This is not
exactly the same as \emph{pure} equations (no constants anywhere), but
essentially works in the same way. This limitation comes from the fact
that, our congruence definition doesn't consider constants at all.
And to fix the issue, we must prove the Proposition 4.12 in Milner's
book first:
\begin{proposition}
Let $\tilde{E}$ and $\tilde{F}$ contain variables $\tilde{X}$ at
most. Let
$\tilde{A}\overset{\mathrm{def}}{=}\tilde{E}\{\tilde{A}/\tilde{X}\},
\tilde{B}\overset{\mathrm{def}}{=}\tilde{E}\{\tilde{B}/\tilde{X}\}$
and $\tilde{E}\sim\tilde{F}$. Then $\tilde{A}\sim\tilde{B}$.
\end{proposition}
which has one of the longest proof in that book, depends on bisimulation upto
$\sim$ and lemmas on free variables appeared in CCS
processes. This complicated part is planed as the future work.

\subsection{CCS, Transitions and Bisimilarities}

In our formalization of CCS, the set of transition actions are not
defined by the union of all visiable actions (names and conames) and the invisible
action $\tau$. Instead, we define only visible names as a simple
algebraic datatype ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}`` in which the type parameter
$\beta$ can be any other type (thus we don't know anything about the
cardinality of the set of all visiable actions), and then use HOL's
\texttt{optionTheory} to further extend the type by one more
element, $\tau$. Having a dedicated type for all visiable actions is quite
convenient and make some statements shorter. (e.g. the restriction
operator can only take a set of visible actions)

The type of CCS process is defined by an algebraic datatype in HOL,
i.e. an inductive defined finite structure constructed by unary and
binary operators.\footnote{It seems possible to switch to co-algebraic
datatypes for the support of potential infinite sums. Indeed, we never
need to induct on CCS processes in any proof so far.} 
It's not easy to directly extend this datatype with new operators,
without hurting the existing proved results.\footnote{This is usually
  called \emph{deep embedding} when implementing a new logic in theorem
  provers. In case of CCS, \emph{shallow embedding} seems impossible.}
Relabeling operator is not necessary from the theoretical view, as
it's possible to use \emph{syntactic
  substitution} instead\footnote{c.f. Section 4.1.2. (page 168) of Robert Gorrieri's CCS book.}
However, it's quite hard to formalize syntactic substitution for CCS,
as it requires to prove many results on the free and bound names
first.

Without constants (or recursion operator), a CCS process cannot
represent infinite-state LTS and many deep results in CCS cease to
exist then. Therefore any serious CCS formalization
must contain the support of constants (or recursion operator. Nowadays
most CCS textbooks and papers use constants, but from the formal view
it's better (or only possible) to use the original form: the recursion
operator, because any CCS process must be presented as single, finite term in
theorem prover. In Milner's book, this CCS operator is called \texttt{fix},
as it essentially returns the fixpoint of a CCS equation. We use the
symbol \texttt{rec} instead and limit ourself to single-variable case,
as we want to extend to multi-variable recursion operator in the
future with the original name. So instead of saying a CCS process $A$
with constant definitions
$A \overset{\mathrm{def}}{=} \tau.A + b.B$ and $B
\overset{\mathrm{def}}{=} b.B$, we use $\mathbf{rec}\;A.\, (\tau.A +
b.(\mathbf{rec}\;B.\,(b.B)))$ instead.

The extra beauty of above recursion opeator is, if we imagine the
\texttt{rec} symbol as $\lambda$ in $\lambda$-expressions, i.e. $\lambda A.\, (\tau.A +
b.(\lambda B.\,(b.B)))$, then we can see both $A$ and $B$ are bound
variables in this expression. On the other side, it's easy to write
an extra constant $C$ inside previous process without a surrounding $\lambda C$, and it must
be a \emph{free variable} of that $\lambda$-expressions. If we go back to the constant-based CCS
syntax, this would mean a malformed CCS process because not all the
constants used in it are defined. Our point here is:
\begin{enumerate}
\item Under the recursion-based CCS syntax, all possible CCS terms
  constructed from the algebraic datatype are well-formed, and those
  free variables can be seen and used\footnote{However, in our
    formalization of unique solution of equations theorems, we focus
    on single-variable case and directly used $\lambda$-expression
    (typed: $CCS\rightarrow CCS$) as equation. The current discussion
    is mainly for the support of multi-variable equations in the future.} as equation variables.
\item All proved theorems about CCS naturally take CCS process with
  extra free variables, as they by themselves have no transition, just
  like $\mathrm{0}$. (this is a natural consequence derived from SOS rules)
\end{enumerate}

The transition of CCS processes is defined by an inductive
relation, literally the same as SOS rules appearing in CCS
textbooks.\footnote{There's an interesting finding here: we never need to use the induction
theorem for transition relation at all, after having proved almost all
notable results for CCS. In another word, the whole CCS formal theory
builds normally, even if the transition relation
is defined co-inductively (by the same set of SOS rules). A potential
need is the prove the set of ending process of transitions from any
process doesn't use any new labels, but so far this result is not
formalized yet. The question
is: do the largest fixpoint and smallest fixpoint \emph{coincide} for
a relation defined by SOS rules? (if not, what else do we have in the
co-inductive relation?)} The only notable SOS rule which is different
with their usual version in textbooks, is the recursion rule:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{E} (\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}) \HOLFreeVar{X} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}
\end{alltt}
which says, if we substitute all appearences of constant $X$ in $E$ to
$(\mathbf{rec}\; X E)$ and the resulting process has a transition to $E_1$
with action $u$, then $(\mathbf{rec}\; X E)$ has the same
transition.

\subsection{Semantic context, guardness and (pre)congruence}

The congruence (or substitutivity) of bisimilarity relations are
usually defined by a series of substitutivity theorems in most CCS
textbooks (c.f. Milners' and Gorrieri's). The concept of semantic context wasn't explicitly given in
Milner's book.\footnote{Milner says (p.\,84): ``.. congruence
  relation; that is, it is preserved by all algebraic contexts'', but
  he didn't further give a clear definition of algerbaic contexts.}
Later books made it explicitly, for exmaple, in Sangior's book\footnote{Introduction to Bisimulation and
  Coinduction},  a \emph{(semantic) context} is a process expression with a single occurrence of a hold
$[\cdot]$ in it, as a subexpression (c.f. p.99 of Sangiorgi's book).

In van Glabbek's paper\footnote{A characterisation of weak
  bisimulation congruence}), maybe for the first time the concept of
congruence is clearly defined in association with equivalence
relation:
\begin{definition}
An equivalence relation $\approx$ is a congruence for a set of
operators $L$ iff for every $n$-ary operator $f$ in $L$ one has
$g_1\approx h_1 \wedge \cdots \wedge g_n \approx h_n \Rightarrow
f(g_1,\ldots,g_n) \approx f(h_1,\ldots,h_n)$. This is the case iff for
every semantic context $C[\cdot]$ one has $g\approx h \Rightarrow
C[g]\approx C[h]$.
\end{definition}

van Glabbek further gave a way to construct congruence relations from
any existing equivalence relations:
\begin{definition}
\label{def:precc}
Given an equivalence relation $\sim$, its (pre)congruence closure,
notated as $[\sim]$ is defined by
\begin{equation}
g\,[\sim]\, h \mbox{ iff } C[g] \sim C[h] \mbox{ for every semantic
  context } C[\cdot].
\end{equation}
\end{definition}
And it's simple to prove that, for any equivation relation $\sim$,
$[\sim]$ is the coarsest congruence finer than $\sim$.

Here we have basically followed van Glabbek's approach. But the
restriction of single occurrence of the hole seems unnecessary: all
congruence relations in CCS hold also under semantic context with
multiple holes. Further more, a multi-hole semantic context $C$ can be
naturally used for representing an equation (or contraction), e.g. $P
\sim C[P]$.

It remains to find a suitable formal definition of semantic
context. There're multiple ways.\footnote{A literal approach is to
define another algebraic datatype which copies everything from the
existing CCS datatype, plus a dedicated symbol for that ``hole'', then
an inductively defined \texttt{replace} operator can be used for
replacing that hole with any CCS process, returning a normal CCS
datatype.} Here we have chosen to use $\lambda$-expressions (typed
$CCS\rightarrow CCS$) to represent a (multi-hole) semantic
context. The definition is inductive:\footnote{Due to symbol conflicts
  with $\lambda$-calculus, the prefix operator in CCS is represented
  as double-dot in HOL.}
\begin{alltt}
\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})
\end{alltt}

Under above definition, we can formally define the concept of
``precongruence'' and ``congruence'' in the following ways:
\begin{alltt}
\HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}. \HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})
\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLConst{precongruence} \HOLFreeVar{R}
\end{alltt}

A \emph{weak guarded} context is a context in which all holes appears
in the sub-expression of prefixed processes. We can easily define it
following the same idea:
\begin{alltt}
\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})
\end{alltt}
(Notice the differences between a weak guarded context and a normal
one: $\lambda t. t$ is not weakly guarded as the variable is directly
exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
guarded as long as $e[\cdot]$ is a semantic context, no necessary weakly guaded.)

By induction on the structure of $\lambda$-expressions, we can easily
prove that, a weakly guarded context is also a (normal) context, and the
composition of a (normal) context and a weakly guarded context is
still weakly guarded:
\begin{alltt}
WG_IS_CONTEXT:
\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \HOLFreeVar{e}
CONTEXT_WG_combin:
\HOLTokenTurnstile{} \HOLConst{CONTEXT} \HOLFreeVar{c} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLFreeVar{c} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{e})
\end{alltt}
It's a similar process to define strongly guarded context
(\texttt{SG}), sequential context (\texttt{SEQ}) and their
variants without direct sums (\texttt{GCONTEXT}, \texttt{WGS},
\texttt{GSEQ}). Some lemmas about their relationships have very long
(but trivial) formal proofs due to the combinatorial explosion of
inductions on their structures. For example, one such 
lemma says, for any semantic context $E$ which is both strongly guarded
and sequential (no direct sums) and another sequential context $H$ (no
direct sums), the composition $H \circ E$ is still both strongly
guarded and sequential (no direct sums):
\begin{alltt}
SG_GSEQ_combin:
\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{H}. \HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E})
\end{alltt}

\subsection{Milner's unique solution of equations theorems}

Once the representation issue of CCS equations is resolved, the actual
proofs of Milner's unique solution of equations theorems is not very
interesting from the view of theorem proving, although it's a 
precise proof engineering work producing quite long proofs.
Since we have chosen to use semantic context to represent
single-variable equations, an equation like $P \sim E\{P/X\}$ now
becomes $P \sim E[P]$, in which $E$ is a (multi-hole) semantic
context, and there's no need to say it ``contains at most the variable
$X$'' any more, as equation variable doesn't appear in $E$ at
all. Under these simplifications, the formal proof of Milner's unique
solution of equations theorem for $\sim$ is a literal mapping for informal
proofs based on bisimulation upto $\sim$, induction and case analysis
of weakly guarded contexts. Below is the formal version of Lemma 4.13
and Proposition 4.14 in Milner's book:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \HOLBoundVar{P\sp{\prime}}.
       \HOLFreeVar{E} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sp{\prime}}. \HOLConst{CONTEXT} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{P}) \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}. \HOLFreeVar{E} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{Q}
\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}. \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}
\end{alltt}

Milner's book only gives the unique solution of equations theorem of
observational congruence ($\approx^c$, Proposition 7.13):
\begin{alltt}
OBS_UNIQUE_SOLUTION:
\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}. \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
\end{alltt}
But its original proof is wrong and cannot be fixed even using the
alternative version of bisimulation upto $\approx$ (c.f. The problem
of ``Weak Bisimulation up to''). For this proof, we've made a direct
proof without using any bisimulation upto technique, which essentially
depends on the following relationship between observational congruence
and weak bisimulation (not bisimilarity):
\begin{alltt}
OBS_CONGR_BY_WEAK_BISIM:
\HOLTokenTurnstile{} \HOLConst{WEAK_BISIM} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u}.
            (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}. \HOLBoundVar{E\sp{\prime}} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}. \HOLBoundVar{E\sp{\prime}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}}
       \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{E\sp{\prime}}
\end{alltt}

There's actual a third version for weak
bisimilarity not explicitly mentioned in Milner's book, mostly because
it's even more restrictive: beside being strongly guarded and sequential, the
equation variable $X$ must not appear in any direct
sum:\footnote{Here, \texttt{GSEQ} means a sequential context without
  direct sums.}
\begin{alltt}
WEAK_UNIQUE_SOLUTION:
\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}. \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
\end{alltt}

\subsection{Unique solution of contractions}

The major difficultis in formalizing Sangiorgi's unique solution of
contractions theorem is to prove its main lemma (c.f. Lemma 3.9 of
main paper), in which the length of weak transitions are used for
induction. Introducing a special vesion of weak transition relation
with length would be an easier choice, but we have chosen to use trace
instead, so that in the future it's possible to extend the work with
trace equivalence included.

A trace is represented by the beginning and ending CCS processes, plus
a list of action it passes. Insteading of defining it directly, we
have first defined a new concept called Reflexive Transitive Closure with a
List (LRTC):
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{LRTC} \HOLFreeVar{R} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b} \HOLSymConst{\HOLTokenEquiv{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.
       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x}. \HOLBoundVar{P} \HOLBoundVar{x} [] \HOLBoundVar{x}) \HOLSymConst{\HOLTokenConj{}}
       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z}. \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLBoundVar{x} (\HOLBoundVar{h}\HOLSymConst{::}\HOLBoundVar{t}) \HOLBoundVar{z}) \HOLSymConst{\HOLTokenImp{}}
       \HOLBoundVar{P} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b}
\end{alltt}
For any labelled translation relation $R$, \HOLinline{\HOLConst{LRTC} \HOLFreeVar{R}} builds a new
relation accumulating all labels in the middle. Then the trace of CCS processes can be
defined by simply combining LRTC with the (strong) CCS transition
relation:
\begin{alltt}
\HOLConst{TRACE} \HOLSymConst{=} \HOLConst{LRTC} \HOLConst{TRANS}
\end{alltt}

If there's at most one visible action (label) in the list of actions of a trace,
then the trace is also a weak transition. We divided this observation
into two cases: no label and unique label. The definition of ``no
label'' in an action list is easy and clear:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{NO_LABEL} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}. \HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLFreeVar{L}
\end{alltt}
while the definition of ``unique label'' can be done in many ways, in
which we have chosen to use the version learnt from Robert Beers in
a private discussion which prevented counting or filtering in the list:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}}
   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{L\sb{\mathrm{1}}} \HOLBoundVar{L\sb{\mathrm{2}}}.
       (\HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} [\HOLFreeVar{u}] \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{=} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenConj{}}
       \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}. \HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDisj{}} \HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{L\sb{\mathrm{2}}}
\end{alltt}
It says, a label is unique in an action list iff it there's no other
labels in the rest part of the list.

The final relationship between traces and weak transitions is stated
and proved in the following lemma:
\begin{alltt}
WEAK_TRANS_AND_TRACE:
\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}}
   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{us}.
       \HOLConst{TRACE} \HOLFreeVar{E} \HOLBoundVar{us} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{NULL} \HOLBoundVar{us} \HOLSymConst{\HOLTokenConj{}} \HOLKeyword{if} \HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLKeyword{then} \HOLConst{NO_LABEL} \HOLBoundVar{us}
       \HOLKeyword{else} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLBoundVar{us}
\end{alltt}
(A weak transition $E\overset{u}{\rightarrow}E'$ is a trace with non
empty action list: 1) without any visible label, if $u = \tau$, or 2)
$u$ is the unique label in the list, if $u \neq \tau$.)

To finish the proof of Lemma 3.9 in Sangiorgi's paper, we used above
lemma to convert weak transitions to traces, which either keep its
length or become shorter after passing weak bisimilations, then we
used above lemma again to convert the traces back to weak transitions.

The proof of the final unique solution of contractions theorem is just
a literal transition of its informal proofs: (noticed that the weakly
guarded context is the version without direct sums)
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}. \HOLBoundVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
\end{alltt}

\subsection{Unique solution of rooted contractions}

The proof of Unique solution of rooted contractions theorem is the
same proof steps of Unique solution of contractions theorem plus the
application of \texttt{OBS_CONGR_BY_WEAK_BISIM} at the
beginning.\footnote{In the thesis work, the conclusion of this theorem
is weak bisimilarity, and the proof is exactly the same as Unique
solution of contractions theorem. Now we got a stronger conclusion
using observational congruence, and the previous version becomes a
trivial collorary of the current version.} The
two proofs are quite similar, mostly because the only property we need
from (rooted) contraction is its precongruence. Once we have proved
the precongruence of rooted contracion, we can naturally use the
normal version of weakly guarded expressions with direct sums included.

\begin{alltt}
UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS:
\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}. \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
\end{alltt}

\subsection{Coarsest (pre)congruence contained in $\approx$ (or $\succeq_{\mathrm{bis}}$)}

The ``coarsest congruence contained in weak bisimilarity ($\approx$)''
theorem in CCS is somehow special, as its current known proofs either
rely on quite restricted conditions, or have an extremely complicated proof
(c.f. van Glabbek's paper) in
which ordinal theory is required.  Actually even the relationship
between its name and statement is not well explained in many CCS
textbooks. But van Glabbek's paper has given the so far clearest
explainion, here we briefly repeat his arguments:

As we know weak bisimilarity ($\approx$) is not (real) congruence, as
it doesn't satisfy subsitutivity on direct sums (but if the CCS syntax
is non-standard, i.e. has only prefixed sums, $\approx$ is indeed a
congruence). The purpose is to find a coarsest congruence contained in
weak bisimilarity. (``coarsest'' means, any other congruence finer than it must be contained in it)
There're two ways to build a congruence from weak bisimilarity, one
way is the standard definition for observational congruence (rooted
weak bisimilarity) $\approx^c$ in CCS textbooks, but even it's proven to be a
congruence we don't know if it's coarsest one.  The other way is to
build a (pre)congruence closure (Def.\,\ref{def:precc}) directly upon
the original weak bisimilarity relation, we call the resulting
relation ``Weak bisimilarity congruence'' ($[\approx]$):
\begin{alltt}
\HOLConst{WEAK_CONGR} \HOLSymConst{=} \HOLConst{CC} \HOLConst{WEAK_EQUIV}
\HOLConst{CC} \HOLFreeVar{R} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}. \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}. \HOLConst{CONTEXT} \HOLBoundVar{c} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{c} \HOLBoundVar{g}) (\HOLBoundVar{c} \HOLBoundVar{h}))
\end{alltt}
It can be shown that any such (pre)congruence closure is automatically coarset.

Now it remains to prove that, the congrunce relation built by above
two quite different approaches actually coincide. To achive this goal,
we first noticed that, all other operators beside sums used in
semantic context doesn't matter, because they're already substituible
for weak bisimilarity. The only important operator is the sum
operator. To focus on this important operator, we can temporily
introduce another concept called \emph{sum equivalence}:
\begin{alltt}
\HOLConst{SUM_EQUIV} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}. \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLBoundVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{+} \HOLBoundVar{r})
\end{alltt}
It can be shown that, weak bisimilarity congruence implies this sum
equivalence. Thus if we can further prove that the sum
equivalence imples observational congrence, all the three relations
must coincide together, as shown in the following diagram:
\begin{displaymath}
\xymatrix{
{\textrm{Weak bisimilarity } (\approx)} & {\textrm{Sum
    equivalence } (\approx^+)} \ar@/^3ex/[ldd]^{\subseteq ?}\\
{\textrm{Weak bisim. congruence } ([\approx])}
\ar[u]^{\subseteq} \ar[ru]^{\subseteq} \\
{\textrm{Rooted bisimilarity } (\approx^c)} \ar[u]^{\subseteq}
}
\end{displaymath}
In another words, observational congruence is the coarsest congruence
contained in weak bisimilary if and only if
\begin{equation}
\forall p\; q.\; p \approx^c\! q \Longleftrightarrow \forall r.\; p+r \approx
q+r
\end{equation}

The classical assumption for proving above theorem requires that $p$
and $q$ do not use up all available visible actions,
i.e. $\mathrm{fn}(p) \cup \mathrm{fn}(q) \neq \mathscr{L}$. But it's
not easy to formalize and use such an assumption without a detailed
treatment on free and bound names (visible actions) of CCS
processes.\footnote{There're totally four such concepts: 1) free names
are all visible actions appearing in a CCS term without surrounding
$\nu$ (restriction) operator on the same action; 2) bound names are
the set of all actions ever used by $\nu$ (restriction) operator; 3)
free variables (or equation variables) are those variables without a
definition given by recursion
operator; 4) bound variables (process constants) are variables with
definitions given by recursion operator. All CCS results using these
concepts are not touched so far, although these four concepts are
successfully defined using HOL's set and list theories.} However, by
analyzing the proof steps, we found that, what's really required is to
not use up all available labels in those weak transitions directly
lead from $p$ and $q$. In another words, even they have used all
available labels, as long as their first weak transitions didn't, the
whole proof can still be finished.\footnote{Further more, $p$ and $q$
  can be considered separately: the proof can be finished as long as
  \emph{each} of them didn't use up all labels on first weak
  transition, while the union of these labels are all labels.}
We have formalized this property of
CCS process and call it ``free action'' property:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{a}. \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}}. \HOLSymConst{\HOLTokenNeg{}}(\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{a}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}})
\end{alltt}
With this property, the classical form of this theorem that we have
formally proved is:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r})
\end{alltt}

If we drop this classical assumption, then the proof becomes much
harder, as given a van Glabbek's paper. Beside, it requires that CCS
syntax must support infinite sums of processes, and this ``infinity''
will go to arbitrary ordinals. Unfortunately, this is beyond the
ability of HOL (or simple type theory). What we can prove by following
the same idea is the following version for finite state CCS, i.e. the
set of all reachable processes is finite:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r})
\end{alltt}

For contraction and rooted contraction, the situation (and proof
steps) is exactly the same:
\begin{displaymath}
\xymatrix{
{\textrm{Contraction } (\succeq_{\mathrm{bis}})} & {\textrm{Sum
    contraction } (\succeq_{\mathrm{bis}}^+)} \ar@/^3ex/[ldd]^{\subseteq ?}\\
{\textrm{Contraction precongruence } ([\succeq_{\mathrm{bis}}])}
\ar[u]^{\subseteq} \ar[ru]^{\subseteq} \\
{\textrm{Rooted contraction } (\succeq_{\mathrm{bis}}^c)} \ar[u]^{\subseteq}
}
\end{displaymath}

And we got two versions of theorem saying rooted contraction is the
coarsest precongruence of (bisimilarity) contraction:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r})
\HOLTokenTurnstile{} \HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r})
\end{alltt}

\end{document}

### 2018-06-04 express2018/part2.tex
Sync with part2.htex

@@
 
-In the second half of this paper, we present a formalization of all new concepts and
-theorems developed in the first part of this paper. The main purpose
-is to convince the readers that, there's no flaw\footnote{Perheps this is the first
+In the second half of this paper, we present a formalization of CCS
+including the new concepts and theorems proposed in the first half of
+this paper. The main purpose is to convince the readers that, there's no flaw\footnote{Perheps this is the first
   time a frontier development in Concurrency Theory ships with its
-  formalization in the same paper.} in those informal proofs. This work is based on a rather
-complete formalization of CCS in HOL theorem prover
-(HOL4), described in a MSc thesis \cite{Chun:2017} and now lives in
+  formalization in the same paper.} in the informal proofs. The formalization work is based on a formalization of CCS in HOL theorem prover
+(HOL4), described in second author's MSc thesis \cite{Chun:2017} and now lives in
 the official examples folder of HOL4 source
@@
 
-We will not repeat all concepts and major theorems of CCS again in its
-formalized ways, nor talk about the changes and improvements comparing
-with previous CCS work including Nesi's. Instead, we just focus on our
-targeting theorems. However, as the unique solution of (rooted)
-contraction theorem stood at the end of a chain of results, it's
-impossible to describe only their statements and formal proofs without
-describing many dependent things first.  On the other side, it's very
+We will not repeat all definitions and theorems of CCS again by their
+formalized versions, nor we talk about the changes and improvements
+comparing with previous CCS work by Nesi. Instead, we just focus on our
+targeting theorems. However, the unique solution of (rooted)
+contraction theorem stood at the end of a chain of and
+concepts and results, it's
+impossible to describe only the final statements and it formal proofs without
+describing all dependent concepts first.  On the other side, it's very
 hard to convince audience the novelty in a proof
@@
 Unlike complicated large programs (e.g. operating systems) which
-usually contain countless of bugs even after years of updates and
-bugfixes, a huge prove engineering work can easily claim its
+usually contain countless of bugs even after years of updates, a huge
+proof engineering work can easily claim its
 \emph{correctness} without concerning other aspects (performance,
@@
 Yet still different formalizations (of the same theory) done by
-different persons could be huge different, due to the great
-flexibilities on choices making at the design of types, terms and
-definitions. It's also quite common to break long original proofs into
-small lemmas and reuse them in the proof of other relevant
-theorems. For the same theorem, good and bad-killed proof engineers
-(suppose they both finished the proof)
-may result into very different proof steps of huge size
-differences.\footnote{But it's not true that a shorter proof is always
+different persons could be very different, due to the great
+flexibilities on choices made during the design of types, terms and
+definitions. It's also quite common to break the original long proofs to
+small pieces. For the same theorem, good and bad-killed proof engineers
+may result into very different proof steps with quite different
+lenths.\footnote{But it's not true that a shorter proof is always
 better, and a shorted proof may not be executed faster if it heavily

### 2018-06-04 express2018/part2.tex
Updates following Sangiorgi's suggestions

@@
   time a frontier development in Concurrency Theory ships with its
-  formalization in the same paper.} in the informal proofs. The formalization work is based on a formalization of CCS in HOL theorem prover
-(HOL4), described in second author's MSc thesis \cite{Chun:2017} and now lives in
-the official examples folder of HOL4 source
+  formalization in the same paper.} in the informal proofs. The
+formalization work is based on a formalization of CCS in HOL theorem
+prover (HOL4), described in second author's MSc thesis
+\cite{Chun:2017} and now lives in the official examples folder of HOL4 source
 code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}.
@@
 We will not repeat all definitions and theorems of CCS again by their
-formalized versions, nor we talk about the changes and improvements
-comparing with previous CCS work by Nesi. Instead, we just focus on our
-targeting theorems. However, the unique solution of (rooted)
-contraction theorem stood at the end of a chain of and
-concepts and results, it's
-impossible to describe only the final statements and it formal proofs without
-describing all dependent concepts first.  On the other side, it's very
-hard to convince audience the novelty in a proof
-engineering work, especially when there exists multiple formalizations
- in the same area. After all, the whole interactive theorem proving (ITP)
-technique is just a translation of definitions and hand-made
-proofs from their informal representations to their formal versions.
-
-Unlike complicated large programs (e.g. operating systems) which
-usually contain countless of bugs even after years of updates, a huge
-proof engineering work can easily claim its
-\emph{correctness} without concerning other aspects (performance,
-quality of definitions, easiness of reading by human, etc.)
-Yet still different formalizations (of the same theory) done by
-different persons could be very different, due to the great
-flexibilities on choices made during the design of types, terms and
-definitions. It's also quite common to break the original long proofs to
-small pieces. For the same theorem, good and bad-killed proof engineers
-may result into very different proof steps with quite different
-lenths.\footnote{But it's not true that a shorter proof is always
-better, and a shorted proof may not be executed faster if it heavily
-depends on automatic proof searching tools such as Meson and Metis. On
-the other side, longer proof without automatic proof searching can be
-easier understood by students who are learning the theory being
-formalized. Indeed, we have tried to follow the informal proof steps literally, and only used
-automatic proof searching techniques on obvious small proof goals.}
-Roughly speaking, there're relative ``good'' and ``bad'' designs and
-considerations, but if they all \emph{correctly} formalized the same theory, few people
-care about their differences, unless they want to extend existing work
-to verify their new developments.
-
-In the rest of this section, we're not going to repeat any proof steps
-as they're essentially the same with the informal proofs. Instead, we
-mostly focus on the key definitions, i.e. the formal
-representation of various concepts, plus brief descriptions on
-important stage theorem expressed in these definitions.
+formalized versions. Instead, we just focus on several highlights in
+this work, i.e.
+\begin{enumerate}
+\item The use of recursion operators in formalizing process constants
+  and variables;
+\item The formalization of semantics context in $\lambda$-expressions and the theory of
+  (pre)congruence for CCS;
+\item The definition and uses of trace in the proof of unique solution of
+  contractions theorem;
+\item The proof of hard version of ``coarsest congruence
+  contained in $\approx$'' theorem.
+\end{enumerate}
 
@@
 If we drop this classical assumption, then the proof becomes much
-harder, as given a van Glabbek's paper. Beside, it requires that CCS
-syntax must support infinite sums of processes, and this ``infinity''
-will go to arbitrary ordinals. Unfortunately, this is beyond the
-ability of HOL (or simple type theory). What we can prove by following
-the same idea is the following version for finite state CCS, i.e. the
-set of all reachable processes is finite:
+harder, as given a van Glabbek's paper. The most important
+intermediate result we have proved here, is the following lemma:
+\begin{alltt}
+\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
+        \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}} \HOLBoundVar{u}.
+\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenConj{}}
+        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{q\sp{\prime}} \HOLBoundVar{u}.
+\HOLFreeVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenImp{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
+\HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r}) \HOLSymConst{\HOLTokenImp{}}
+   \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q}
+\end{alltt}
+It roughly says, for any two processes $p$ and $q$, if we can find
+another stable (no $\tau$-transitions) process $k$ which is not weak bisimilar to any transition of
+$p$ and $q$, then the hard part of our main theorem is proved. In
+practice, once two processes were given, it's not hard to find
+such a process, but the arbitrariness of $p$ and $q$ made this result
+extremely hard to prove. The method given by van Glabbek requires a
+construction of arbitrarily non-bisimilar processes called ``Klop
+processes'':
+\begin{definition}{(Klop processes)}
+For each ordinal $\lambda$, and an arbitrary chosen non-$\tau$ action $a$,
+define a CCS process $k_\lambda$ as follows:
+\begin{enumerate}
+\item $k_0 = 0$,
+\item $k_{\lambda+1} = k_\lambda + a.k_\lambda$ and
+\item for $\lambda$ a limit ordinal, $k_\lambda = \sum_{\mu < \lambda}
+  k_\mu$, meaning that $k_\lambda$ is constructed from all graphs
+  $k_\mu$ for $\mu < \lambda$ by identifying their root.
+\end{enumerate}
+\end{definition}
+It's not hard to prove that, all $k_i$ are non-bisimilar (not only
+weakly but also strongly). The idea is, for any two processes, the union of sets of their all
+transitions cannot be arbitrarily large: it has to be limited by an
+ordinal number. But above contruction can be arbitrarily large, so
+there always exists a Klop process which can be used to satisfy above
+lemma (and finish the proof).
+
+However, this goes beyond HOL's expressivity to define above process, mostly
+because there's no way to express infinite ``sums'' in CCS
+datatype.\footnote{There're actually several ways to modify the
+  datatype to support infinite sums, but none of these infinity can be
+arbitrary. The full version of ordinal theory cannot be expressed in HOL.}
+What we can do is to eliminate the last branch with limiting
+ordinals, and define Klop processes only on finite cases:
+\begin{alltt}
+\HOLConst{KLOP} \HOLFreeVar{a} \HOLNumLit{0} \HOLSymConst{=} \HOLConst{nil}
+\HOLConst{KLOP} \HOLFreeVar{a} (\HOLConst{SUC} \HOLFreeVar{n}) \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLSymConst{+} \HOLConst{label} \HOLFreeVar{a}\HOLSymConst{..}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\hfill[KLOP_def]
+\end{alltt}
+But this means we much assume the two processes $p$ and $q$ are
+finite-state, i.e. their corresponding LTS graphs have only finite
+states. Choosing an element from a countable infinite set of processes
+to make sure it's not bisimiar with a given set of processes, this is
+essentially a pure set-theoretic problem, as formalized and proved in
+the following lemma:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenImp{}}
+   \HOLConst{FINITE} \HOLFreeVar{A} \HOLSymConst{\HOLTokenConj{}} \HOLConst{INFINITE} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y}.
+\HOLBoundVar{x} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{x} \HOLSymConst{\HOLTokenNotEqual{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y}) \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
+\HOLBoundVar{k} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n}.
+\HOLBoundVar{n} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{A} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{n} \HOLBoundVar{k}
+\end{alltt}
+
+With all these results, finally we can prove the ``coarsest congruence
+contained in $\approx$'' theorem for finite-state CCS:
 \begin{alltt}

### 2018-06-07 express2018/ccs.tex
DS

% \section{Background}
% \label{s:back}

\section{CCS}
\label{ss:ccs}

\finish{maybe use recursion in place of constants, so to be
  more faithful wrt the HOL formalisation
}

We assume  an infinite set  of \emph{names} $  a, b, \ldots $
 and   a  set  of
\emph{constant identifiers} (or simply \emph{constants}) 
 for writing recursive processes. 
The special symbol $\tau$ does not occur in the names and in the 
constants. 
The class   of the  CCS processes  is
built from the operators
of  parallel
composition,  sum,
 restriction, input and output prefix ???,  
and  constants:
$$ \begin{array}{ccl}
P  & := &    \outC a . P \midd \; a . P \midd \;  P_1 |  P_2 \; \midd  \;
P_1 + P_2 \; \midd % \; \mu . P\; \midd  \; 
  \res a P  \;  \midd \;   K  \;  \midd \; \nil  \\[\tkpS]
   \end{array}
 $$
Each constant $K$ has  a definition 
 $K \Defi P$.
We sometimes omit trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil $ .
The operational semantics is given by means of an LTS, and is
reported in Figure~\ref{f:LTSCCS} (the symmetric version  of the two rules for
parallel composition and the rule for sum  has been omitted).

 The \emph{immediate derivatives} of a
process $P$ are the elements of  the set $\{P' \st P \arr\mu P' \mbox{ for some $\mu$ }
\}$.   
We use $\ell$ to range over
 visible actions (i.e.,  inputs or outputs, excluding  $\tau$).
\begin{figure*}
\begin{center}
 $\displaystyle{   P \arr\mu   P' \over   P + Q   \arr\mu
P'  } $  $ \hb$   
%{{\sf par1}}:
 $\displaystyle{   P \arr\mu   P' \over   P | Q   \arr\mu
P' | Q } $  $ \hb$   
  $\; \;$  $\displaystyle{ P \arr{ a}P' \hk \hk  Q
\arr{\outC a }Q'  \over     P|  Q \arr{ \tau} P'
|  Q'  }$ 
\\
\hskip .6cm  
 $\displaystyle{  \over  \mu.  P    \arr\mu
P } $  $ \hb$   
\hskip .6cm  
$\displaystyle{ P \arr{\mu}P' \over
 \res a     P   \arr{\mu} \res a P'} $ $ \mu \neq a, \outC a$
$ \hb$ %  &
\hskip .5cm 
$\displaystyle{ P \arr{\mu}P' \over
 K   \arr{ \mu} P'  } $  if  $  K \Defi P$
\end{center}
%  \begin{center}
% \begin{tabular}{rlcrlcrl}
% %{{\sf sum}}:
% & $  \Sigma_{i\in I} \mu_i.   P_i 
% \arr{ \mu_i  }P_i$ & $ \hb$ &
% %{{\sf par1}}:
% & $\displaystyle{   P \arr\mu   P' \over   P | Q   \arr\mu
% P' | Q } $ & $ \hb$ &  
% % \multicolumn{5}{c}{
% %  {{\sf com1}}: 
% &  $\; \;$  $\displaystyle{ P \arr{ a}P' \hk \hk  Q
% \arr{\outC a }Q'  \over     P|  Q \arr{ \tau} P'
% |  Q'  }$ 
%  \\[\mysp]
% \multicolumn{8}{c}{ 
% %{{\sf res}}:  %&
% \hskip .4cm  
%  $\displaystyle{ P \arr{\mu}P' \over
%  \res a     P   \arr{\mu} \res a P'} $ $ \mu \neq a, \outC a$
% % & 
% $ \hb$ %  &
% \hskip .4cm 
% %{{\sf const}}: %& 
% \hskip .3cm 
% $\displaystyle{ P \arr{\mu}P' \over
%  K   \arr{ \mu} P'  } $  if  $  K \Defi P$
% }\end{tabular}
%  \end{center} 
\caption{The LTS for CCS}
\label{f:LTSCCS}
\end{figure*}

Some standard notations for transitions:  $\Longrightarrow $ is the 
reflexive and  transitive closure of $\arr\tau $, and 
$\Arr \mu $ is $\Longrightarrow \arr\mu \Longrightarrow $ (the
composition of the three relations).
Moreover,   
$ 
P \arcap \mu P'$ holds if $P \arr\mu P'$ or ($\mu =\tau$ and
$P=P'$); similarly 
$ 
P \Arcap \mu P'$ holds if $P \Arr\mu P'$ or ($\mu =\tau$ and
$P=P'$).
We write $P (\arr\mu)^n P'$ if $P$ can become $P'$ after performing
$n$ $\mu$-transitions. Finally, $P \arr\mu$ holds if there is $P'$
with $P \arr\mu P'$, and similarly for other forms of transitions.

\paragraph{Further notations}
Letters  $\R,\S$ range over relations.
We use infix notation for relations, e.g., 
$P \RR Q$ means that $(P,Q) \in \R$.
We use a tilde to denote a tuple, with countably many elements; thus
the tuple may also be infinite.
 All
notations  are  extended to tuples componentwise;
e.g., $\til P \RR \til Q$ means that $P_i \RR Q_i$, for  each  
component $i$  of the tuples $\til P$ and $\til Q$.
And $\ct{\til P}$ is the process obtained by replacing each hole
$\holei i$ of the  context $\qct$ with $P_i$.  
We write $
\ctx \R$ for the closure of a relation under contexts. Thus $P\: \ctx \R\: Q$
means that there are a context $\qct$ and tuples $\til P,\til Q$ with
$P =  \ct{\til P}, Q =  \ct{\til Q}$ and    $\til P \RR \til Q$.
We use  symbol 
$\DSdefi$ for abbreviations. For instance, $P \DSdefi G $, where
$G$ is some expression, means that  $P$ stands
for the  expression
$G$ (in contrast,  symbol $\Defi$ is used for the definition of
constants, whereas   $=$ is used for syntactic equality and for equations).
If $\leq$ is a preorder, then  $\geq$  is its inverse (and
conversely).

### 2018-06-07 express2018/intro.tex
DS

\section{Introduction}

A prominent proof method for bisimulation, put forward by Milner and widely used in his
 landmark  CCS book \cite{Mil89}
is
\emph{unique solution of equations}, whereby two tuples of processes are
componentwise bisimilar if they are solutions 
of the same system of equations.
This method  is important in verification techniques and tools
  based on 
algebraic      reasoning \cite{theoryAndPractice,RosUnder10,BaeBOOK}.

In the   \emph{weak} case (when  behavioural equivalences abstract from internal moves,
which practically is the most relevant case), however, 
Milner's proof method has severe syntactical limitations. 
To overcome such limitations, Sangiorgi proposes to replace
equations with  special inequations called
\emph{contractions} \cite{...}. Contraction is a preorder that, roughly, places some efficiency
constraints on processes.  
Uniqueness of the solutions 
 of a system of contractions
 is defined as with systems of
equations:  
any two solutions must be bisimilar.
The difference with equations is in the meaning of solution:
in the case of contractions
the solution is evaluated with respect to
the contraction preorder, rather than bisimilarity. 
With contractions, most syntactic limitations of the unique-solution theorem can be
removed.  One constraint that still remains in \cite{San...} is on occurrences of the sum operator, due to
the failure of substitutivity of contraction wrt such operator.

The purpose of this paper is twofold. 
On the one hand, we refine the contraction proof technique by moving to the 
\emph{rooted contraction}, that is, the largest congruence included in the contraction
preoder.  Using rooted contraction one obtains a unique-solution theorem that is valid for
\emph{rooted bisimilarity} (hence also for bisimilarity itself).  
On the other hand, we provide a  
 comprehensive formalization  of the core of the theory of CCS 
 in the HOL
theorem prover (HOL4). The formalisation  includes the theory of unique solution of equations and
contractions discussed in the present paper, but is not limited to it (partly because such
theorems rely on a number of more fundamental results):
indeed the formalisation encompasses the basic properties of strong and weak
bisimilarity (e.g. the fixed-point and substitutivity properties), 
their algebraic theory, 
 various
versions of ``bisimulation up to'' techniques (e.g., bisimulation up-to expansion),
the basic properties  of rooted bisimilarity. Considering the relationship between bisimilarity and rooted
bisimilarity, the formalisation includes the proof that the latter is the coarsest
congruence included in the former, for which two proofs are formalised: one as in Milner's
book,  requiring the hypothesis that  no processes can use all labels; the other without
such hypothesis, essentially formalising van Glabbek's paper ...
Similar theorems are proved for rooted contractions wrt the contraction preorder.

\finish{for Express, insist more on structured operational semantics,
  to fit the scope of the conference}

### 2018-06-07 express2018/contraction.tex
DS

\section{Contractions}
\label{s:mcontr}
The constraints on the unique-solution Theorem~\ref{t:Mil89} can be 
weakened if  we move from equations to inequations called
  \emph{contractions}.

  Intuitively,
  the bisimilarity contraction 
$\mcontrBIS$ 
 is  a preorder in which 
$P \mcontrBIS Q  $  holds  if $P \wb Q$ and, in addition, 
$Q$ has the \emph{possibility} of being at least as efficient as $P$ (as far as
$\tau$-actions performed). 
Process $Q$, however, may be nondeterministic and may have other ways
of doing the same work, and these could be  slow (i.e., involving
more $\tau$-steps than those performed by $P$).
Thus, in contrast with expansion,  we cannot really say that `$Q$ is more efficient than
$P$'.

\begin{definition}[bisimulation  contraction]
\label{d:BisCon}
A process relation ${\R}$ 
 is a {\em  bisimulation  contraction}  if, whenever
 $P\RR Q$, %for all $\mu$

\begin{enumerate}

\item   $P \arr\mu P'$ implies there is $Q'$ such that $Q \arcap \mu
  Q'$
 and $P' \RR Q'$;

\item 
    $Q \arr\mu Q'$   implies there is $P'$ such that $P \Arcap \mu
 P'$ and $P' 
\wb Q'$.
\end{enumerate}
\emph{Bisimilarity  contraction}, written $\mcontrBIS$, is the union
of all bisimulation contractions. 
\qed\end{definition}
% We say that $P$  {\emph{bisimilarly  contracts} $Q$, written
% $Q \mcontrBIS Q$.
% We write $\mexpaBIS$ for the inverse of $\mcontrBIS$.

In the first clause $Q$ is required to match $P$'s challenge
transition with at most one transition.
This makes sure that $Q$ is capable of mimicking $P$'s
work at least as efficiently as $P$. 
In contrast, the second clause of Definition~\ref{d:BisCon}, on the
challenges from $Q$, entirely ignores efficiency: it is the same
clause of  weak bisimulation~--- the final derivatives are even required
to be related  by $\wb$, rather than by $\R$.

Bisimilarity  contraction is coarser than 
 the expansion  relation 
$\contr$ of   Definition~\ref{d:expa}. Clause (1) is the same in the two
definitions. But in clause (2) expansion uses 
$P \Arr \mu P'$, rather than $P \Arcap \mu P'$; 
 moreover with
contraction the final derivatives are simply required to be bisimilar.
An expansion 
$P \contr Q$
tells us  that $Q$ is always at least as efficient as $P$, whereas  the
 contraction $P \mcontrBIS Q$  just says that $Q$ has the  possibility of
being at least as efficient as $P$.

% \iflong\newDS
% Note the use of $\wb$, in place of $\R$, in the second clause:
%  we are only interested to know that $Q$ may  mimic $P$'s
% more in an efficient manner (first clause); we do not care about
% efficiency
% on the
% challenges proposed by $Q$,   which are handled using ordinary
% bisimilarity.
% \fi

\begin{example}
\label{exa:contr}
{ We have %\mcontrBIS a + \tau^n . a $
 $ a \not  \mcontrBIS \tau. a$. However,
$a+ \tau . a \mcontrBIS a$, as well as its converse, 
$  a \mcontrBIS a +
\tau . a $. Indeed, if $P \wb Q$ then 
$  P  \mcontrBIS P +Q$. The last two relations do not hold with 
$\contr$, which explains the strictness of the inclusion
 ${\contr} \subseteq {\mcontrBIS}$. 
% The inclusion is strict: for instance
% $a+ \tau . a \mcontrBIS a$, where $\mcontrBIS$ cannot be replaced by
%  $\contr$. Also the converse of  $a+ \tau . a \mcontrBIS a$ holds, namely
% $  a \mcontrBIS a +
% \tau . a $. However, we have %\mcontrBIS a + \tau^n . a $
%  $ a \not  \mcontrBIS \tau. a$
\qed} \end{example}

% The substitutivity proofs for for expansion and bisimilarity carry
% over to contraction,

As  bisimilarity  and expansion, so 
contraction is preserved by all operators but sum.

### 2018-06-07 express2018/expansion.tex
DS

\subsection{Equivalences: bisimilarity and rooted bisimilarity}
\label{ss:BiEx}

The equivalences here are 
 \emph{weak}, in that they
abstract from the number of internal steps performed
\begin{definition}[bisimilarity]
\label{d:wb}
A process relation ${\R}$ 
 is a \emph{bisimulation} if, whenever
 $P\RR Q$, %for all $\mu$ 
we have:
\begin{enumerate}
\item 
    $P \arr\mu P'$   implies that there is $Q'$ such that $Q \Arcap
\mu Q'$ and $P' 
\RR Q'$;

\item the converse of (1)
 on the actions from $Q$.
%\item if $Q  \Ar\mu   Q'$, then there is $P'$ s.t.\ $P
%\Arcap\mu  P'$ and $P' 
%\RR Q'$.
\end{enumerate}  
 $P$ and $Q$ are \emph{bisimilar},
written $P \wb
 Q$, if $P \RR Q$ for some  bisimulation $\R$.  
\qed\end{definition} 
\finish{the definition of rooted bisimilarity }

We sometimes call bisimilarity \emph{weak} bisimilarity, to
distinguish it from \emph{strong bisimilarity}, $\sim$,
obtained by replacing in the above definition   the weak answer $
Q\Arcap\mu Q'$ with the strong  $Q \arr \mu Q'$.

The bisimulation proof method can be enhanced by means of \emph{up-to
  techniques}. One of the most useful auxiliary relations in up-to
techniques  is the \emph{expansion} relation  $\contr$ \cite{SaMi92}. This is an asymmetric version
of $\wb$ where $P \contr Q$  means that 
 $P \wb Q$,
but also that $Q$  achieves  the same as  $P$ 
with  no more work, i.e. with no more $\tau$ actions.
Intuitively, if $ P \contr Q$, we can think of $Q$ as being 
at least as fast as $P$
or, more generally, we can think that $P$  uses at least as many resources as $Q$.

\subsection{Preorders: expansion and contraction}

\begin{definition}[expansion]
\label{d:expa}
A process relation ${\R}$ 
 is an {\em  expansion} if, whenever
we have $P\RR Q$, %for all $\mu$

\begin{enumerate}

\item   $P \arr\mu P'$ implies that there is $Q'$ with $Q \arcap \mu
  Q'$
 and $P' \RR Q'$;

\item 
    $Q \arr\mu Q'$   implies that there is $P'$ with $P \Arr \mu
 P'$ and $P' 
\RR Q'$.

\end{enumerate}
 $P$  {\em expands } $Q$, written
$P  \contr Q$, 
if $P \RR Q$,  for some expansion $\R$. 
\qed\end{definition}

\finish{here the definition of contraction}

As bisimilarity, so expansion is preserved by all operators but sum.

### 2018-06-07 express2018/unique.tex
DS

\subsection{Systems of contractions}
\label{ss:SysContr}

A \emph{system of contractions} is defined as a system of equations,
except that the contraction symbol $\mcontr$ is used in the place of
the equality symbol $=$. Thus a system of contractions is a set 
$\{  X_i \mcontr E_i\}_{i\in I}$
where $I$ is an  indexing set and expressions
$E_i$  may contain the  \behavC\  variables 
$\{  X_i\}_{i\in I}$.

\begin{definition}
\label{d:uni_contra}
Given a  system of contractions 
$\{  X_i \mcontr E_i\}_{i\in I}$, 
 we say that:
\begin{itemize}
\item
 $\til P$ is a \emph{solution  for $\mcontrBIS$ of the 
 system of contractions} 
 if $\til P \mcontrBIS \til E [\til P]$;
\item 
the system  
has  \emph{a unique 
solution for $\asymp$}
if 
whenever 
 $\til P$ and $\til Q$ are both solutions  for  $\mcontrBIS$
 then $\til P \asymp \til Q$.
\qed\end{itemize}
\end{definition}

\begin{definition}
\label{d:guarded}
A system of contractions $\{  X_i \mcontr E_i\}_{i\in I}$
 is
\emph{weakly guarded}
if,  in each    $E_i$, each occurrence of
a \behavC\ variable is underneath a prefix.
\qed\end{definition}

\begin{lemma}
\label{l:uptocon}
Suppose $\til P$ and $\til Q$ are solutions  for $\wb$
 of a system of weakly-guarded
contractions.
For any context $\qct$, 
if  $\ct{\til P}\Arr{\mu}  R$,
 then 
there is a  context $\qctp$
such that $R \mcontrBIS \ctp{\til P}$ and  $\ct{\til Q} \Arcap{\mu}
 \wb \ctp{\til Q}$.
\end{lemma}

\begin{theorem}[unique solution of contractions for $\wb$]
\label{t:contra_bisimulation_u}
A system of weakly-guarded contractions
    has 
a unique solution 
 for $\wb$.
\end{theorem}

\finish{sopra: sum-free} 
\section{Rooted contraction and unique solution for rooted bisimilarity}
\label{ss:new}

\begin{definition}[rooted contraction]
\label{d:rcontra}
Two processes $P$ and $Q$ are in the rooted contraction, written 
 $P\rcontr Q$, 
if

\begin{enumerate}

\item   $P \arr\mu P'$ implies that there is $Q'$ with $Q \arr \mu
  Q'$
 and $P'\mcontrBIS Q'$;

\item 
    $Q \arr\mu Q'$   implies that there is $P'$ with $P \Arr \mu
 P'$ and $P' 
\mcontrBIS Q'$.

\end{enumerate}
\qed\end{definition}

\finish{the only difference: the hat missing in the first clause}

\begin{theorem}
\label{t:}
Relation $\rcontr$ is a precongruence in CCS. 
\end{theorem}

\finish{two proofs}

For the unique solution result a key lemma is the following one.

\begin{lemma}
\label{l:uptocon}
Suppose $\til P$ and $\til Q$ are solutions  for $\rcontr$ 
 of a system of weakly-guarded
contractions.
For any context $\qct$, 
if  $\ct{\til P}\Arr{\mu}  R$,
 then 
there is a  context $\qctp$
such that $R \mcontrBIS \ctp{\til P}$ and  $\ct{\til Q} \Arcap{\mu}
 \wb \ctp{\til Q}$.
\end{lemma}
\finish{sopra: si potrebbe togliere il hat, secondo me, e allora avremmo il risultato per
  rooted bisimilarity}

\begin{theorem}[unique solution of contractions for $\wb$]
\label{t:contra_bisimulation_u}
A system of weakly-guarded contractions
    has 
a unique solution 
 for $\wb$.
\end{theorem}

\finish{sopra: e' la stessa assertion dell'altro theorem, occorre differenziare}

### 2018-06-09 express2018/part2.tex
DS
Add a top-level TeX file (main)
Added (candidate) title and abstract

@@
 %% Prof. Davide Sangiorgi and Chun Tian.
-
-\documentclass{eptcs} % required template (EPTCS) by EXPRESS/SOS 2018
-
-%% Math symbol packages
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{mathrsfs}
-
-\usepackage{stmaryrd}
-\SetSymbolFont{stmry}{bold}{U}{stmry}{m}{n}
-% \cupdot (the best one)
-\newcommand{\cupdot}{\mathbin{\mathaccent\cdot\cup}}
-
-\usepackage{amsthm}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-\theoremstyle{proposition}
-\newtheorem{proposition}{Proposition}[section]
-
-% HOL theorem embedding support
-\usepackage{holindex}
-\usepackage{alltt}
-\include{tokens}
-
-\usepackage[all,cmtip]{xy}
-
-\begin{document}
 
@@
 \begin{definition}
-\label{def:precc}
 Given an equivalence relation $\sim$, its (pre)congruence closure,
@@
 congruence we don't know if it's coarsest one.  The other way is to
-build a (pre)congruence closure (Def.\,\ref{def:precc}) directly upon
+build a (pre)congruence closure (Def ??) directly upon
 the original weak bisimilarity relation, we call the resulting
@@
 \end{alltt}
-
-\end{document}

### 2018-06-11 express2018/ccs.tex
Cumulative updates (still not touching the 2nd part)

@@
 \finish{maybe use recursion in place of constants, so to be
-  more faithful wrt the HOL formalisation
-}
+  more faithful wrt the HOL formalization}
 
-We assume  an infinite set  of \emph{names} $  a, b, \ldots $
- and   a  set  of
-\emph{constant identifiers} (or simply \emph{constants}) 
- for writing recursive processes. 
+We assume  a possibly infinite set of \emph{input names} $a, b,
+\ldots$ and \emph{output names} $\outC a, \outC b, \ldots$,
+ and a set of \emph{constant identifiers} (or simply \emph{constants})
+ $A, B, \ldots$ for writing recursive processes. 
 The special symbol $\tau$ does not occur in the names and in the 
 constants. 
-The class   of the  CCS processes  is
-built from the operators
-of  parallel
-composition,  sum,
- restriction, input and output prefix ???,  
-and  constants:
-$$ \begin{array}{ccl}
-P  & := &    \outC a . P \midd \; a . P \midd \;  P_1 |  P_2 \; \midd  \;
+The class  of the CCS processes is inductively built from $\nil$ by the operators
+of parallel composition,  sum,
+ restriction, prefix, and constants:
+\begin{equation*}
+\begin{array}{ccl}
+P  & := &  \nil \; \midd \;  \mu . P \; \midd \;  P_1 |  P_2 \; \midd  \;
 P_1 + P_2 \; \midd % \; \mu . P\; \midd  \; 
-  \res a P  \;  \midd \;   K  \;  \midd \; \nil  \\[\tkpS]
+  (\res a\!)\, P  \;  \midd \;   K   %\\[\tkpS]
 \end{array}
- $$
+\end{equation*}
 Each constant $K$ has  a definition 
@@
 \\
+\vskip .1cm
 \hskip .6cm  
@@
 $\displaystyle{ P \arr{\mu}P' \over
- \res a     P   \arr{\mu} \res a P'} $ $ \mu \neq a, \outC a$
+ (\res a\!)\, P   \arr{\mu} (\res a\!)\, P'} $ $ \mu \neq a, \outC a$
 $ \hb$ %  &
@@
 %  \end{center} 
-\caption{The LTS for CCS}
+\caption{The LTS of CCS}
 \label{f:LTSCCS}

### 2018-06-11 express2018/expansion.tex
Cumulative updates (still not touching the 2nd part)

@@
  Q$, if $P \RR Q$ for some  bisimulation $\R$.  
-\qed\end{definition} 
+\end{definition}
+
+\begin{definition}{rooted bisimilarity}
+
+\end{definition}
 \finish{the definition of rooted bisimilarity }
 
-We sometimes call bisimilarity \emph{weak} bisimilarity, to
+We sometimes call bisimilarity as ``\emph{weak} bisimilarity'', to
 distinguish it from \emph{strong bisimilarity}, $\sim$,

### 2018-06-11 express2018/intro.tex
Added (candidate) title and abstract
Cumulative updates (still not touching the 2nd part)

@@
 A prominent proof method for bisimulation, put forward by Milner and widely used in his
- landmark  CCS book \cite{Mil89}
-is
+landmark CCS book \cite{Mil89} is the
 \emph{unique solution of equations}, whereby two tuples of processes are
@@
 This method  is important in verification techniques and tools
-  based on 
-algebraic      reasoning \cite{theoryAndPractice,RosUnder10,BaeBOOK}.
+based on algebraic reasoning \cite{theoryAndPractice,RosUnder10,BaeBOOK}.
 
@@
 equations with  special inequations called
-\emph{contractions} \cite{...}. Contraction is a preorder that, roughly, places some efficiency
-constraints on processes.  
-Uniqueness of the solutions 
- of a system of contractions
- is defined as with systems of
-equations:  
+\emph{contractions} \cite{sangiorgi2015equations}. Contraction is a
+preorder that, roughly, places some efficiency
+constraints on processes.  Uniqueness of the solutions of a system of contractions
+ is defined as with systems of equations:  
 any two solutions must be bisimilar.
@@
 With contractions, most syntactic limitations of the unique-solution theorem can be
-removed.  One constraint that still remains in \cite{San...} is on occurrences of the sum operator, due to
-the failure of substitutivity of contraction wrt such operator.
+removed.  One constraint that still remains in
+\cite{sangiorgi2015equations} is on occurrences of the sum operator,
+due to the failure of substitutivity of contraction w.r.t. such operator.
 
@@
 On the one hand, we refine the contraction proof technique by moving to the 
-\emph{rooted contraction}, that is, the largest congruence included in the contraction
-preoder.  Using rooted contraction one obtains a unique-solution theorem that is valid for
+\emph{rooted contraction} \cite{Tian:2017wrba}, that is, the coarsest (pre)congruence contained in the contraction
+preorder.  Using rooted contraction one obtains an unique-solution theorem that is valid for
 \emph{rooted bisimilarity} (hence also for bisimilarity itself).  
@@
  in the HOL
-theorem prover (HOL4). The formalisation  includes the theory of unique solution of equations and
+theorem prover (HOL4). The formalization  includes the proofs of
+Milner's 3 ``unique solution of equations'' theorems and
 contractions discussed in the present paper, but is not limited to it (partly because such
 theorems rely on a number of more fundamental results):
-indeed the formalisation encompasses the basic properties of strong and weak
+indeed the formalization encompasses the basic properties of strong and weak
 bisimilarity (e.g. the fixed-point and substitutivity properties), 
-their algebraic theory, 
- various
-versions of ``bisimulation up to'' techniques (e.g., bisimulation up-to expansion),
+their algebraic theory, various versions of ``bisimulation up to''
+techniques (e.g., bisimulation up-to expansion),
 the basic properties  of rooted bisimilarity. Considering the relationship between bisimilarity and rooted
-bisimilarity, the formalisation includes the proof that the latter is the coarsest
-congruence included in the former, for which two proofs are formalised: one as in Milner's
+bisimilarity, the formalization includes the proof that the latter is the coarsest
+congruence included in the former, for which two proofs are formalized: one as in Milner's
 book,  requiring the hypothesis that  no processes can use all labels; the other without
-such hypothesis, essentially formalising van Glabbek's paper ...
+such hypothesis, essentially formalising van Glabbek's paper \cite{vanGlabbeek:2005ur}.
 Similar theorems are proved for rooted contractions wrt the contraction preorder.
 
-\finish{for Express, insist more on structured operational semantics,
+\finish{for Express, insist more on Structural Operational Semantics,
   to fit the scope of the conference}

### 2018-06-11 express2018/expansion.tex
Fixed and added basic definitions.

@@
 \item 
-    $P \arr\mu P'$   implies that there is $Q'$ such that $Q \Arcap
-\mu Q'$ and $P' 
-\RR Q'$;
-
+    $P \arr\mu P'$   implies that there is $Q'$ such that $Q \Arcap \mu Q'$ and $P' \RR Q'$;
 \item the converse of (1)
@@
 
-\begin{definition}{rooted bisimilarity}
-
+\begin{definition}{(rooted bisimilarity)}
+Two processes $P$ and $Q$ are rooted bisimilar, denoted $P
+\approx^c Q$, if for all $\mu$ (including $\tau$):
+\begin{enumerate}
+ \item  $P \arr\mu P'$   implies that there is $Q'$ such that $Q
+   \Arr\mu Q'$ and $P' \approx Q'$;
+\item the converse of (1) on the actions from $Q$.
+\end{enumerate}
 \end{definition}
-\finish{the definition of rooted bisimilarity }
 
@@
 we have $P\RR Q$, %for all $\mu$ 
-
 \begin{enumerate}
-
 \item   $P \arr\mu P'$ implies that there is $Q'$ with $Q \arcap \mu
@@
  and $P' \RR Q'$;
-
 \item 
@@
 \RR Q'$.
+\end{enumerate}
+ $P$  {\em expands} $Q$, written
+$P  \expa Q$, 
+if $P \RR Q$,  for some expansion $\R$. 
+\end{definition}
 
+\begin{definition}[contraction]
+\label{d:expa}
+A process relation ${\R}$ is an {\em contraction} if, whenever
+we have $P\RR Q$, %for all $\mu$ 
+\begin{enumerate}
+\item $P \arr\mu P'$ implies that there is $Q'$ with $Q \arcap \mu Q'$
+ and $P' \RR Q'$;
+\item $Q \arr\mu Q'$   implies that there is $P'$ with $P \Arcap \mu
+ P'$ and $P' \wb Q'$.
 \end{enumerate}
- $P$  {\em expands } $Q$, written
+ $P$  {\em contracts} $Q$, written
 $P  \contr Q$, 
-if $P \RR Q$,  for some expansion $\R$. 
-\qed\end{definition}
+if $P \RR Q$,  for some contraction $\R$. 
+\end{definition}
 
-\finish{here the definition of contraction}
-
-As bisimilarity, so expansion is preserved by all operators but sum.
+As bisimilarity, expansion and contraction are preserved by all operators but sum.

### 2018-06-11 express2018/unique.tex
Fixed and added basic definitions.

@@
 \finish{sopra: sum-free}
-\section{Rooted contraction and unique solution for rooted bisimilarity}
+
+\section{Rooted contraction and unique solution theorem for rooted bisimilarity}
 \label{ss:new}
@@
 Two processes $P$ and $Q$ are in the rooted contraction, written 
- $P\rcontr Q$, 
-if
-
+ $P\rcontr Q$, if
 \begin{enumerate}
-
-\item   $P \arr\mu P'$ implies that there is $Q'$ with $Q \arr \mu
-  Q'$
+\item $P \arr\mu P'$ implies that there is $Q'$ with $Q \arr \mu Q'$
  and $P'\mcontrBIS Q'$;
-
-\item 
-    $Q \arr\mu Q'$   implies that there is $P'$ with $P \Arr \mu
- P'$ and $P' 
-\mcontrBIS Q'$.
-
+\item $Q \arr\mu Q'$   implies that there is $P'$ with $P \Arr \mu
+ P'$ and $P' \wb Q'$.
 \end{enumerate}
-\qed\end{definition}
-
-\finish{the only difference: the hat missing in the first clause}
+\end{definition}
 
 \begin{theorem}
-\label{t:}
+\label{t:rcontr-precongruence}
 Relation $\rcontr$ is a precongruence in CCS. 
@@
 \end{lemma}
-\finish{sopra: si potrebbe togliere il hat, secondo me, e allora avremmo il risultato per
-  rooted bisimilarity}
 

### 2018-06-11 express2018/equa.tex
Added missing equa.tex

\subsection{Systems of  equations}
\label{ss:SysEq}

Uniqueness of  solutions of equations \cite{Mil89} intuitively says that if  a context $\qct$ obeys
certain  conditions, 
then all processes $P$  that satisfy the equation $ P \wb \ct P$ are
bisimilar with each other.

We need variables to write equations. We  use
 capital
letters  $X,Y,Z$
 for  these variables and call them \emph{\behav\  variables}.
 The body of an equation is a CCS expression
possibly containing \behav\  variables. Thus such expressions, ranged
over by $E$, live in the CCS
grammar extended with \behav\  variables.
% , which we  call 
%  \emph{extended CCS}.

\begin{definition}
Assume that, for each $i$ of 
 a countable indexing set $I$, we have variables $X_i$, and expressions
$E_i$ possibly containing  such variables. 
Then 
$$\{  X_i = E_i\}_{i\in I}$$
is 
  a \emph{system of equations}. (There is one equation for each variable $X_i$.)
\qed\end{definition}

We write $E[\til P]$ for the expression resulting from $E$ by
replacing each variable $X_i$   with the process $P_i$, assuming
$\til P$ and $\til X$ have the same length. (This is syntactic
replacement, akin to the substitution of the holes of a context with 
 processes.) 
The components of $\til P$ need not be
 different from each other, as it must be for the variables $\til X$.
If the system has infinitely many equations,
the  tuples $\til P$ and $\til X$
 are infinite too.
\begin{definition}
Suppose  $\{  X_i = E_i\}_{i\in I}$ is a system of equations: 
\begin{itemize}
\item
 $\til P$ is a \emph{solution of the 
system of equations  for $\wb$} 
if for each $i$ it holds
that $P_i \wb E_i [\til P]$.

\item the  system has 
\emph{a unique solution for $\wb$}  if whenever 
 $\til P$ and $\til Q$ are both solutions for $\wb$, then $\til P \wb
 \til Q$. \qed
\end{itemize} 
 \end{definition}

Examples of systems with a  unique solution for $\wb$ are: 
\begin{enumerate}
\item
$ X = a. X$

\item 
$ X_1 = a.  X_2$, $ X_2 = b.  X_1$

\end{enumerate}

The unique solution of the system (1), modulo $\wb$,  is the constant $K \Defi a
. K$:  for any other solution $P$ we have $P \wb K$.
The unique solution of (2), modulo $\wb$, are the constants $K_1 , K_2$
with $K_1 \Defi a . K_2$ and $K_2 \Defi b. K_1$; again, for any other
pair of solutions $P_1,P_2$ we have $K_1 \wb P_1$ and $K_2 \wb P_2$.
Examples of systems that do not have a unique solution are: 
\begin{enumerate}
\item $X = X $

\item $X = \tau . X$
\item $X = a | X$

\end{enumerate} 
All processes are solutions of (1) and (2); examples of solutions for
(3) are $K$ and $K | b$, for $K \Defi a
. K$.

\begin{definition}
A system of equations 
$\{  X_i = E_i\}_{i\in I}$
 is 
\begin{itemize}
\item
\emph{guarded} if,  in each    $E_i$, each occurrence of
an \behav\  variable is underneath a visible prefix;

\item 
 \emph{sequential} if,  in each    $E_i$, each occurrence of
an \behav\  variable only appears  underneath prefixes and sums.
\qed\end{itemize}
 \end{definition}

In other words,  
if the system is sequential, then 
 for
every expression $E_i$, any subexpression of $E_i$ in which $X_j $ 
appears, apart from $X_j$ itself,  is a sum (of prefixed terms). 
For instance, 
\begin{itemize}
\item $X = \tau. X + \mu . \nil$ is sequential but not 
 guarded, because the guarding prefix for the variable
is not visible.

\item $X =  \ell . X | P$ is  guarded but not sequential.

\item $X =  \ell . X + \tau. \res a (a .\outC b | a.\nil)$, as well as 
$X = \tau . (a. X + \tau . b .X + \tau  )$
are both 
 guarded and sequential.
\end{itemize}

\begin{theorem}[unique solution of equations, \cite{Mil89}]
\label{t:Mil89}
A system of guarded and sequential equations
% $\{  X_i = E_i\}_{i\in I}$ 
   has 
a unique solution
 for $\wb$. \qed
\end{theorem}

The proof exploits an invariance property on immediate transitions for
guarded and sequential expressions, and then extracts a bisimulation
(up-to bisimilarity) out
of the solutions of the system.  
To see the  need of the
 sequentiality  condition, 
  consider
 the equation (from \cite{Mil89}) 
\[ X = \res a (a. X | \outC a) \]
where $X$ is guarded but not sequential. Any processes that does
not use  $a$
 is a solution.

### 2018-06-11 express2018/expansion.tex
Added missing equa.tex

@@
 A process relation ${\R}$ 
- is a \emph{bisimulation} if, whenever
+ is a (weak) \emph{bisimulation} if, whenever
  $P\RR Q$, %for all $\mu$ 
@@
 
-\begin{definition}{(rooted bisimilarity)}
-Two processes $P$ and $Q$ are rooted bisimilar, denoted $P
-\approx^c Q$, if for all $\mu$ (including $\tau$):
-\begin{enumerate}
- \item  $P \arr\mu P'$   implies that there is $Q'$ such that $Q
-   \Arr\mu Q'$ and $P' \approx Q'$;
-\item the converse of (1) on the actions from $Q$.
-\end{enumerate}
-\end{definition}
-
 We sometimes call bisimilarity as ``\emph{weak} bisimilarity'', to
@@
 
+Bisimilarity is not congruence w.r.t direct sums, one obvious way to
+fix the definition is to define another relation on top of it:
+\begin{definition}{(rooted bisimilarity)}
+Two processes $P$ and $Q$ are rooted bisimilar, denoted $P
+\approx^c Q$, if and only if for all $\mu$ (including $\tau$):
+\begin{enumerate}
+ \item  $P \arr\mu P'$ implies that there is $Q'$ such that $Q
+   \Arr\mu Q'$ and $P' \wb Q'$;
+\item the converse of (1) on the actions from $Q$.
+\end{enumerate}
+\end{definition}
+Besides reducing the rooted bisimiarity of two processes to
+the bisimilarities of their first-step transition ends, this definition also brings a proof technique for proving the
+rooted bisimiarity by constructing a bisimulation:
+\begin{lemma}{(Rooted bisimilarity by constructing a bisimulation)}
+\label{l:obs_congr_by_weak_bisim}
+Given a (weak) bisimulation $\RR$, if two processes $P$ and $Q$
+satisfies the following properties:
+\begin{enumerate}
+ \item  $P \arr\mu P'$ implies that there is $Q'$ such that $Q
+   \Arr\mu Q'$ and $P' \RR Q'$;
+\item the converse of (1) on the actions from $Q$.
+\end{enumerate}
+then $P$ and $Q$ are rooted bisimilar, i.e., $P \approx^c Q$.
+\end{lemma}
+
+\subsection{Preorders: expansion and contraction (??)}
+
 The bisimulation proof method can be enhanced by means of \emph{up-to
   techniques}. One of the most useful auxiliary relations in up-to
-techniques  is the \emph{expansion} relation  $\contr$ \cite{SaMi92}. This is an asymmetric version
-of $\wb$ where $P \contr Q$  means that 
+techniques  is the \emph{expansion} relation  $\expa$ \cite{SaMi92}. This is an asymmetric version
+of $\wb$ where $P \expa Q$  means that 
  $P \wb Q$,
@@
 with  no more work, i.e. with no more $\tau$ actions.
-Intuitively, if $ P \contr Q$, we can think of $Q$ as being 
+Intuitively, if $ P \expa Q$, we can think of $Q$ as being 
 at least as fast as $P$
 or, more generally, we can think that $P$  uses at least as many resources as $Q$.
-
-\subsection{Preorders: expansion and contraction}
 
@@
 
-\begin{definition}[contraction]
-\label{d:expa}
-A process relation ${\R}$ is an {\em contraction} if, whenever
-we have $P\RR Q$, %for all $\mu$ 
-\begin{enumerate}
-\item $P \arr\mu P'$ implies that there is $Q'$ with $Q \arcap \mu Q'$
- and $P' \RR Q'$;
-\item $Q \arr\mu Q'$   implies that there is $P'$ with $P \Arcap \mu
- P'$ and $P' \wb Q'$.
-\end{enumerate}
- $P$  {\em contracts} $Q$, written
-$P  \contr Q$, 
-if $P \RR Q$,  for some contraction $\R$. 
-\end{definition}
-
-As bisimilarity, expansion and contraction are preserved by all operators but sum.
+As bisimilarity, expansion is preserved by all operators but sum.

### 2018-06-11 express2018/part2.tex
Cumulative updates (still not touching the 2nd part)
Clean up, re-ordered part2 before adding new contents

@@
 including the new concepts and theorems proposed in the first half of
-this paper. The main purpose is to convince the readers that, there's no flaw\footnote{Perheps this is the first
-  time a frontier development in Concurrency Theory ships with its
-  formalization in the same paper.} in the informal proofs. The
+this paper. The main purpose is to convince the readers that, there's no flaw in the informal proofs. The
 formalization work is based on a formalization of CCS in HOL theorem
 prover (HOL4), described in second author's MSc thesis
-\cite{Chun:2017} and now lives in the official examples folder of HOL4 source
+\cite{Tian:2017wrba} and now lives in the official examples folder of HOL4 source
 code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}.
@@
 \begin{enumerate}
-\item The use of recursion operators in formalizing process constants
-  and variables;
 \item The formalization of semantics context in $\lambda$-expressions and the theory of
@@
   contractions theorem;
-\item The proof of hard version of ``coarsest congruence
+\item The proof of the hard version of ``coarsest congruence
   contained in $\approx$'' theorem.
@@
 
-\subsubsection{Limitations}
-
 There're two major limitations in this work. One is the class of CCS
 processes, i.e. we're limited with Finitary CCS which has no infinite
-sums or parallel compositions. The only important theorem in which
-arbitrary infinite sums of CCS processes must be used, is the following
-``coarsest congruence contained in weak bisimilarity'' theorem without
-any limitations on the involved processes:
-\begin{equation}
-\forall p\; q.\; p \approx^c\! q \Longleftrightarrow \forall r.\; p+r \approx
-q+r
-\end{equation}
-Milner's classical proof of above result needs to assume that $p$ and $q$ didn't
-use up all available labels. The newer proof by van Glabbek requires a
-special choice of $r$ which is not weak bisimilar with any process
-transited from $p$ and $q$, and the actual chosen process may contain
-arbitrary large sums of CCS processes. This goes beyond the
-expressiveness of HOL, as result we followed the same proof ideas but
-limited with finite state CCS only.
-
-The other limitation is, even for single-variable equation, the
-variable doesn't appear inside any constant.  For example, an equation like
-$P \approx E\{P/X\}$ in which $E = A$ and $A \overset{\mathrm{def}}{=}
-\tau.A + b.X$ is not supported, because the equation variable $X$
-appears inside the definition of constant $A$. On the other side, if
-$E = A + X$ with whatever definition of constant $A$ in which there's
-no appearence of $X$, such equations are supported. This is not
-exactly the same as \emph{pure} equations (no constants anywhere), but
-essentially works in the same way. This limitation comes from the fact
-that, our congruence definition doesn't consider constants at all.
-And to fix the issue, we must prove the Proposition 4.12 in Milner's
-book first:
-\begin{proposition}
-Let $\tilde{E}$ and $\tilde{F}$ contain variables $\tilde{X}$ at
-most. Let
-$\tilde{A}\overset{\mathrm{def}}{=}\tilde{E}\{\tilde{A}/\tilde{X}\},
-\tilde{B}\overset{\mathrm{def}}{=}\tilde{E}\{\tilde{B}/\tilde{X}\}$
-and $\tilde{E}\sim\tilde{F}$. Then $\tilde{A}\sim\tilde{B}$.
-\end{proposition}
-which has one of the longest proof in that book, depends on bisimulation upto
-$\sim$ and lemmas on free variables appeared in CCS
-processes. This complicated part is planed as the future work.
+sums or parallel compositions. The other limitation is, even for single-variable equation, the
+variable doesn't appear inside any constant.
 
@@
 transition.
-
-\subsection{Semantic context, guardness and (pre)congruence}
-
-The congruence (or substitutivity) of bisimilarity relations are
-usually defined by a series of substitutivity theorems in most CCS
-textbooks (c.f. Milners' and Gorrieri's). The concept of semantic context wasn't explicitly given in
-Milner's book.\footnote{Milner says (p.\,84): ``.. congruence
-  relation; that is, it is preserved by all algebraic contexts'', but
-  he didn't further give a clear definition of algerbaic contexts.}
-Later books made it explicitly, for exmaple, in Sangior's book\footnote{Introduction to Bisimulation and
-  Coinduction},  a \emph{(semantic) context} is a process expression with a single occurrence of a hold
-$[\cdot]$ in it, as a subexpression (c.f. p.99 of Sangiorgi's book).
-
-In van Glabbek's paper\footnote{A characterisation of weak
-  bisimulation congruence}), maybe for the first time the concept of
-congruence is clearly defined in association with equivalence
-relation:
-\begin{definition}
-An equivalence relation $\approx$ is a congruence for a set of
-operators $L$ iff for every $n$-ary operator $f$ in $L$ one has
-$g_1\approx h_1 \wedge \cdots \wedge g_n \approx h_n \Rightarrow
-f(g_1,\ldots,g_n) \approx f(h_1,\ldots,h_n)$. This is the case iff for
-every semantic context $C[\cdot]$ one has $g\approx h \Rightarrow
-C[g]\approx C[h]$.
-\end{definition}
-
-van Glabbek further gave a way to construct congruence relations from
-any existing equivalence relations:
-\begin{definition}
-Given an equivalence relation $\sim$, its (pre)congruence closure,
-notated as $[\sim]$ is defined by
-\begin{equation}
-g\,[\sim]\, h \mbox{ iff } C[g] \sim C[h] \mbox{ for every semantic
-  context } C[\cdot].
-\end{equation}
-\end{definition}
-And it's simple to prove that, for any equivation relation $\sim$,
-$[\sim]$ is the coarsest congruence finer than $\sim$.
-
-Here we have basically followed van Glabbek's approach. But the
-restriction of single occurrence of the hole seems unnecessary: all
-congruence relations in CCS hold also under semantic context with
-multiple holes. Further more, a multi-hole semantic context $C$ can be
-naturally used for representing an equation (or contraction), e.g. $P
-\sim C[P]$.
-
-It remains to find a suitable formal definition of semantic
-context. There're multiple ways.\footnote{A literal approach is to
-define another algebraic datatype which copies everything from the
-existing CCS datatype, plus a dedicated symbol for that ``hole'', then
-an inductively defined \texttt{replace} operator can be used for
-replacing that hole with any CCS process, returning a normal CCS
-datatype.} Here we have chosen to use $\lambda$-expressions (typed
-$CCS\rightarrow CCS$) to represent a (multi-hole) semantic
-context. The definition is inductive:\footnote{Due to symbol conflicts
-  with $\lambda$-calculus, the prefix operator in CCS is represented
-  as double-dot in HOL.}
-\begin{alltt}
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})
-\end{alltt}
-
-Under above definition, we can formally define the concept of
-``precongruence'' and ``congruence'' in the following ways:
-\begin{alltt}
-\HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
-\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})
-\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLConst{precongruence} \HOLFreeVar{R}
-\end{alltt}
-
-A \emph{weak guarded} context is a context in which all holes appears
-in the sub-expression of prefixed processes. We can easily define it
-following the same idea:
-\begin{alltt}
-\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})
-\end{alltt}
-(Notice the differences between a weak guarded context and a normal
-one: $\lambda t. t$ is not weakly guarded as the variable is directly
-exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
-guarded as long as $e[\cdot]$ is a semantic context, no necessary weakly guaded.)
-
-By induction on the structure of $\lambda$-expressions, we can easily
-prove that, a weakly guarded context is also a (normal) context, and the
-composition of a (normal) context and a weakly guarded context is
-still weakly guarded:
-\begin{alltt}
-WG_IS_CONTEXT:
-\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \HOLFreeVar{e}
-CONTEXT_WG_combin:
-\HOLTokenTurnstile{} \HOLConst{CONTEXT} \HOLFreeVar{c} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLFreeVar{c} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{e})
-\end{alltt}
-It's a similar process to define strongly guarded context
-(\texttt{SG}), sequential context (\texttt{SEQ}) and their
-variants without direct sums (\texttt{GCONTEXT}, \texttt{WGS},
-\texttt{GSEQ}). Some lemmas about their relationships have very long
-(but trivial) formal proofs due to the combinatorial explosion of
-inductions on their structures. For example, one such 
-lemma says, for any semantic context $E$ which is both strongly guarded
-and sequential (no direct sums) and another sequential context $H$ (no
-direct sums), the composition $H \circ E$ is still both strongly
-guarded and sequential (no direct sums):
-\begin{alltt}
-SG_GSEQ_combin:
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{H}.
-\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E})
-\end{alltt}
-
-\subsection{Milner's unique solution of equations theorems}
-
-Once the representation issue of CCS equations is resolved, the actual
-proofs of Milner's unique solution of equations theorems is not very
-interesting from the view of theorem proving, although it's a 
-precise proof engineering work producing quite long proofs.
-Since we have chosen to use semantic context to represent
-single-variable equations, an equation like $P \sim E\{P/X\}$ now
-becomes $P \sim E[P]$, in which $E$ is a (multi-hole) semantic
-context, and there's no need to say it ``contains at most the variable
-$X$'' any more, as equation variable doesn't appear in $E$ at
-all. Under these simplifications, the formal proof of Milner's unique
-solution of equations theorem for $\sim$ is a literal mapping for informal
-proofs based on bisimulation upto $\sim$, induction and case analysis
-of weakly guarded contexts. Below is the formal version of Lemma 4.13
-and Proposition 4.14 in Milner's book:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \HOLBoundVar{P\sp{\prime}}.
-       \HOLFreeVar{E} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sp{\prime}}.
-\HOLConst{CONTEXT} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{P}) \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
-\HOLFreeVar{E} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{Q}
-\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}
-\end{alltt}
-
-Milner's book only gives the unique solution of equations theorem of
-observational congruence ($\approx^c$, Proposition 7.13):
-\begin{alltt}
-OBS_UNIQUE_SOLUTION:
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
-\end{alltt}
-But its original proof is wrong and cannot be fixed even using the
-alternative version of bisimulation upto $\approx$ (c.f. The problem
-of ``Weak Bisimulation up to''). For this proof, we've made a direct
-proof without using any bisimulation upto technique, which essentially
-depends on the following relationship between observational congruence
-and weak bisimulation (not bisimilarity):
-\begin{alltt}
-OBS_CONGR_BY_WEAK_BISIM:
-\HOLTokenTurnstile{} \HOLConst{WEAK_BISIM} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u}.
-            (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLBoundVar{E\sp{\prime}} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLBoundVar{E\sp{\prime}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{E\sp{\prime}}
-\end{alltt}
-
-There's actual a third version for weak
-bisimilarity not explicitly mentioned in Milner's book, mostly because
-it's even more restrictive: beside being strongly guarded and sequential, the
-equation variable $X$ must not appear in any direct
-sum:\footnote{Here, \texttt{GSEQ} means a sequential context without
-  direct sums.}
-\begin{alltt}
-WEAK_UNIQUE_SOLUTION:
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
-\end{alltt}
-
-\subsection{Unique solution of contractions}
-
-The major difficultis in formalizing Sangiorgi's unique solution of
-contractions theorem is to prove its main lemma (c.f. Lemma 3.9 of
-main paper), in which the length of weak transitions are used for
-induction. Introducing a special vesion of weak transition relation
-with length would be an easier choice, but we have chosen to use trace
-instead, so that in the future it's possible to extend the work with
-trace equivalence included.
-
-A trace is represented by the beginning and ending CCS processes, plus
-a list of action it passes. Insteading of defining it directly, we
-have first defined a new concept called Reflexive Transitive Closure with a
-List (LRTC):
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{LRTC} \HOLFreeVar{R} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b} \HOLSymConst{\HOLTokenEquiv{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.
-       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x}. \HOLBoundVar{P} \HOLBoundVar{x} [] \HOLBoundVar{x}) \HOLSymConst{\HOLTokenConj{}}
-       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z}.
-\HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLBoundVar{x} (\HOLBoundVar{h}\HOLSymConst{::}\HOLBoundVar{t}) \HOLBoundVar{z}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLBoundVar{P} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b}
-\end{alltt}
-For any labelled translation relation $R$, \HOLinline{\HOLConst{LRTC} \HOLFreeVar{R}} builds a new
-relation accumulating all labels in the middle. Then the trace of CCS processes can be
-defined by simply combining LRTC with the (strong) CCS transition
-relation:
-\begin{alltt}
-\HOLConst{TRACE} \HOLSymConst{=} \HOLConst{LRTC} \HOLConst{TRANS}
-\end{alltt}
-
-If there's at most one visible action (label) in the list of actions of a trace,
-then the trace is also a weak transition. We divided this observation
-into two cases: no label and unique label. The definition of ``no
-label'' in an action list is easy and clear:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{NO_LABEL} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
-\HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLFreeVar{L}
-\end{alltt}
-while the definition of ``unique label'' can be done in many ways, in
-which we have chosen to use the version learnt from Robert Beers in
-a private discussion which prevented counting or filtering in the list:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}}
-   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{L\sb{\mathrm{1}}} \HOLBoundVar{L\sb{\mathrm{2}}}.
-       (\HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} [\HOLFreeVar{u}] \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{=} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenConj{}}
-       \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
-\HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDisj{}} \HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{L\sb{\mathrm{2}}}
-\end{alltt}
-It says, a label is unique in an action list iff it there's no other
-labels in the rest part of the list.
-
-The final relationship between traces and weak transitions is stated
-and proved in the following lemma:
-\begin{alltt}
-WEAK_TRANS_AND_TRACE:
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}}
-   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{us}.
-       \HOLConst{TRACE} \HOLFreeVar{E} \HOLBoundVar{us} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{NULL} \HOLBoundVar{us} \HOLSymConst{\HOLTokenConj{}} \HOLKeyword{if} \HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLKeyword{then} \HOLConst{NO_LABEL} \HOLBoundVar{us}
-       \HOLKeyword{else} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLBoundVar{us}
-\end{alltt}
-(A weak transition $E\overset{u}{\rightarrow}E'$ is a trace with non
-empty action list: 1) without any visible label, if $u = \tau$, or 2)
-$u$ is the unique label in the list, if $u \neq \tau$.)
-
-To finish the proof of Lemma 3.9 in Sangiorgi's paper, we used above
-lemma to convert weak transitions to traces, which either keep its
-length or become shorter after passing weak bisimilations, then we
-used above lemma again to convert the traces back to weak transitions.
-
-The proof of the final unique solution of contractions theorem is just
-a literal transition of its informal proofs: (noticed that the weakly
-guarded context is the version without direct sums)
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
-\end{alltt}
-
-\subsection{Unique solution of rooted contractions}
-
-The proof of Unique solution of rooted contractions theorem is the
-same proof steps of Unique solution of contractions theorem plus the
-application of \texttt{OBS_CONGR_BY_WEAK_BISIM} at the
-beginning.\footnote{In the thesis work, the conclusion of this theorem
-is weak bisimilarity, and the proof is exactly the same as Unique
-solution of contractions theorem. Now we got a stronger conclusion
-using observational congruence, and the previous version becomes a
-trivial collorary of the current version.} The
-two proofs are quite similar, mostly because the only property we need
-from (rooted) contraction is its precongruence. Once we have proved
-the precongruence of rooted contracion, we can naturally use the
-normal version of weakly guarded expressions with direct sums included.
-
-\begin{alltt}
-UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS:
-\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
-\end{alltt}
 
@@
 \end{alltt}
+
+\subsection{Semantic context, guardness and (pre)congruence}
+
+We need to find a suitable formal definition of semantic
+context. There're multiple ways. Here we have chosen to use $\lambda$-expressions (typed
+$CCS\rightarrow CCS$) to represent a (multi-hole) semantic
+context. The definition is inductive:
+\begin{alltt}
+\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
+\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
+\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
+\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})
+\end{alltt}
+
+Under above definition, we can formally define the concept of
+``precongruence'' and ``congruence'' in the following ways:
+\begin{alltt}
+\HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
+\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
+\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})
+\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLConst{precongruence} \HOLFreeVar{R}
+\end{alltt}
+
+A \emph{weak guarded} context is a context in which all holes appears
+in the sub-expression of prefixed processes. We can easily define it
+following the same idea:
+\begin{alltt}
+\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
+\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
+\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})
+\end{alltt}
+(Notice the differences between a weak guarded context and a normal
+one: $\lambda t. t$ is not weakly guarded as the variable is directly
+exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
+guarded as long as $e[\cdot]$ is a semantic context, no necessary weakly guaded.)
+
+It's a similar process to define strongly guarded context
+(\texttt{SG}), sequential context (\texttt{SEQ}) and their
+variants without direct sums (\texttt{GCONTEXT}, \texttt{WGS},
+\texttt{GSEQ}). Some lemmas about their relationships have very long
+(but trivial) formal proofs due to the combinatorial explosion of
+inductions on their structures. For example, one such 
+lemma says, for any semantic context $E$ which is both strongly guarded
+and sequential (no direct sums) and another sequential context $H$ (no
+direct sums), the composition $H \circ E$ is still both strongly
+guarded and sequential (no direct sums):
+\begin{alltt}
+SG_GSEQ_combin:
+\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{H}.
+\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E})
+\end{alltt}
+
+\subsection{Milner's ``unique solution of equations'' theorems}
+
+Once the representation issue of CCS equations is resolved, the actual
+proofs of Milner's unique solution of equations theorems is not very
+interesting from the view of theorem proving, although it's a 
+precise proof engineering work producing quite long proofs.
+Since we have chosen to use semantic context to represent
+single-variable equations, an equation like $P \sim E\{P/X\}$ now
+becomes $P \sim E[P]$, in which $E$ is a (multi-hole) semantic
+context, and there's no need to say it ``contains at most the variable
+$X$'' any more, as equation variable doesn't appear in $E$ at
+all. Under these simplifications, the formal proof of Milner's unique
+solution of equations theorem for $\sim$ is a literal mapping for informal
+proofs based on bisimulation upto $\sim$, induction and case analysis
+of weakly guarded contexts. Below is the formal version of Lemma 4.13
+and Proposition 4.14 in Milner's book:
+
+\begin{alltt}
+STRONG_UNIQUE_SOLUTION:
+\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
+\HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}
+\end{alltt}
+
+\begin{alltt}
+WEAK_UNIQUE_SOLUTION:
+\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
+\HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
+\end{alltt}
+
+\begin{alltt}
+OBS_UNIQUE_SOLUTION:
+\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
+\HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
+\end{alltt}
+
+\subsection{Unique solution of contractions}
+
+The major difficultis in formalizing Sangiorgi's unique solution of
+contractions theorem is to prove its main lemma (c.f. Lemma 3.9 of
+main paper), in which the length of weak transitions are used for
+induction. Introducing a special vesion of weak transition relation
+with length would be an easier choice, but we have chosen to use trace
+instead, so that in the future it's possible to extend the work with
+trace equivalence included.
+
+A trace is represented by the beginning and ending CCS processes, plus
+a list of action it passes. Insteading of defining it directly, we
+have first defined a new concept called Reflexive Transitive Closure with a
+List (LRTC):
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{LRTC} \HOLFreeVar{R} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b} \HOLSymConst{\HOLTokenEquiv{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.
+       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x}. \HOLBoundVar{P} \HOLBoundVar{x} [] \HOLBoundVar{x}) \HOLSymConst{\HOLTokenConj{}}
+       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z}.
+\HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLBoundVar{x} (\HOLBoundVar{h}\HOLSymConst{::}\HOLBoundVar{t}) \HOLBoundVar{z}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLBoundVar{P} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b}
+\end{alltt}
+For any labelled translation relation $R$, \HOLinline{\HOLConst{LRTC} \HOLFreeVar{R}} builds a new
+relation accumulating all labels in the middle. Then the trace of CCS processes can be
+defined by simply combining LRTC with the (strong) CCS transition
+relation:
+\begin{alltt}
+\HOLConst{TRACE} \HOLSymConst{=} \HOLConst{LRTC} \HOLConst{TRANS}
+\end{alltt}
+
+If there's at most one visible action (label) in the list of actions of a trace,
+then the trace is also a weak transition. We divided this observation
+into two cases: no label and unique label. The definition of ``no
+label'' in an action list is easy and clear:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{NO_LABEL} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
+\HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLFreeVar{L}
+\end{alltt}
+while the definition of ``unique label'' can be done in many ways, in
+which we have chosen to use the version learnt from Robert Beers in
+a private discussion which prevented counting or filtering in the list:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}}
+   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{L\sb{\mathrm{1}}} \HOLBoundVar{L\sb{\mathrm{2}}}.
+       (\HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} [\HOLFreeVar{u}] \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{=} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
+\HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDisj{}} \HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{L\sb{\mathrm{2}}}
+\end{alltt}
+It says, a label is unique in an action list iff it there's no other
+labels in the rest part of the list.
+
+The final relationship between traces and weak transitions is stated
+and proved in the following lemma:
+\begin{alltt}
+WEAK_TRANS_AND_TRACE:
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}}
+   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{us}.
+       \HOLConst{TRACE} \HOLFreeVar{E} \HOLBoundVar{us} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{NULL} \HOLBoundVar{us} \HOLSymConst{\HOLTokenConj{}} \HOLKeyword{if} \HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLKeyword{then} \HOLConst{NO_LABEL} \HOLBoundVar{us}
+       \HOLKeyword{else} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLBoundVar{us}
+\end{alltt}
+(A weak transition $E\overset{u}{\rightarrow}E'$ is a trace with non
+empty action list: 1) without any visible label, if $u = \tau$, or 2)
+$u$ is the unique label in the list, if $u \neq \tau$.)
+
+To finish the proof of Lemma 3.9 in Sangiorgi's paper, we used above
+lemma to convert weak transitions to traces, which either keep its
+length or become shorter after passing weak bisimilations, then we
+used above lemma again to convert the traces back to weak transitions.
+
+The proof of the final unique solution of contractions theorem is just
+a literal transition of its informal proofs: (noticed that the weakly
+guarded context is the version without direct sums)
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
+\HOLBoundVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
+\end{alltt}
+
+\subsection{Unique solution of rooted contractions}
+
+The proof of Unique solution of rooted contractions theorem is the
+same proof steps of Unique solution of contractions theorem plus the
+application of \texttt{OBS_CONGR_BY_WEAK_BISIM} at the
+beginning.\footnote{In the thesis work, the conclusion of this theorem
+is weak bisimilarity, and the proof is exactly the same as Unique
+solution of contractions theorem. Now we got a stronger conclusion
+using observational congruence, and the previous version becomes a
+trivial collorary of the current version.} The
+two proofs are quite similar, mostly because the only property we need
+from (rooted) contraction is its precongruence. Once we have proved
+the precongruence of rooted contracion, we can naturally use the
+normal version of weakly guarded expressions with direct sums included.
+
+\begin{alltt}
+UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS:
+\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
+\HOLBoundVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
+\end{alltt}

### 2018-06-11 express2018/formal.tex
Stage work on part2

--- 2018-06-11 express2018/part2.tex
@@
-%%%% -*- Mode: LaTeX -*-
-%%
-%% This is the draft of the 2nd part of EXPRESS/SOS 2018 paper, co-authored by
-%% Prof. Davide Sangiorgi and Chun Tian.
-
 \section{Formalization}
@@
 formalization work is based on a formalization of CCS in HOL theorem
-prover (HOL4), described in second author's MSc thesis
+prover (HOL4) \cite{slind2008brief}, described in second author's MSc thesis
 \cite{Tian:2017wrba} and now lives in the official examples folder of HOL4 source
@@
 formalization by Monica Nesi \cite{Nesi} in HOL88.
+
+Higher Order Logic (or ``HOL Logic'') \cite{hollogic} stands for simple-typed $\lambda$-calculus plus Hibert
+choice operator, axiom of infinity, and rank-1 polymorphim (type
+variables). HOL4 implemented this logic without any extension, while
+some other theorem provers in HOL family (e.g. Isabelle/HOL) has
+various extensions. The HOL Logic is considerability simpler than logic
+foundations in most other theorem provers, e.g. Coq. As a result,
+formal theories in HOL can be easily migrated (sometimes even
+automatically) into other theorem provers.
 
@@
 proven, the general case is just a routine
-adaptation for paper proofs. \footnote{However, it's impossible to directly derive the
-  multi-variable versions of unique solution theorems from their
-  single-variable versions.} \footnote{Also, I don't know if there
-  exists a higher-level general
-  duality theorem such that some kind of results on single-variable CCS
-  equations must also hold for multi-variable equation groups. --Chun.}
+adaptation for paper proofs.
 It's not easy to formalize multi-variable CCS equations with
@@
 
-There're two major limitations in this work. One is the class of CCS
-processes, i.e. we're limited with Finitary CCS which has no infinite
-sums or parallel compositions. The other limitation is, even for single-variable equation, the
-variable doesn't appear inside any constant.
-
-\subsection{CCS, Transitions and Bisimilarities}
-
-In our formalization of CCS, the set of transition actions are not
-defined by the union of all visiable actions (names and conames) and the invisible
-action $\tau$. Instead, we define only visible names as a simple
-algebraic datatype ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}`` in which the type parameter
-$\beta$ can be any other type (thus we don't know anything about the
-cardinality of the set of all visiable actions), and then use HOL's
-\texttt{optionTheory} to further extend the type by one more
-element, $\tau$. Having a dedicated type for all visiable actions is quite
-convenient and make some statements shorter. (e.g. the restriction
-operator can only take a set of visible actions)
-
-The type of CCS process is defined by an algebraic datatype in HOL,
-i.e. an inductive defined finite structure constructed by unary and
-binary operators.\footnote{It seems possible to switch to co-algebraic
-datatypes for the support of potential infinite sums. Indeed, we never
-need to induct on CCS processes in any proof so far.} 
-It's not easy to directly extend this datatype with new operators,
-without hurting the existing proved results.\footnote{This is usually
-  called \emph{deep embedding} when implementing a new logic in theorem
-  provers. In case of CCS, \emph{shallow embedding} seems impossible.}
-Relabeling operator is not necessary from the theoretical view, as
-it's possible to use \emph{syntactic
-  substitution} instead\footnote{c.f. Section 4.1.2. (page 168) of Robert Gorrieri's CCS book.}
-However, it's quite hard to formalize syntactic substitution for CCS,
-as it requires to prove many results on the free and bound names
-first.
-
-Without constants (or recursion operator), a CCS process cannot
-represent infinite-state LTS and many deep results in CCS cease to
-exist then. Therefore any serious CCS formalization
-must contain the support of constants (or recursion operator. Nowadays
-most CCS textbooks and papers use constants, but from the formal view
-it's better (or only possible) to use the original form: the recursion
-operator, because any CCS process must be presented as single, finite term in
-theorem prover. In Milner's book, this CCS operator is called \texttt{fix},
-as it essentially returns the fixpoint of a CCS equation. We use the
-symbol \texttt{rec} instead and limit ourself to single-variable case,
-as we want to extend to multi-variable recursion operator in the
-future with the original name. So instead of saying a CCS process $A$
-with constant definitions
-$A \overset{\mathrm{def}}{=} \tau.A + b.B$ and $B
-\overset{\mathrm{def}}{=} b.B$, we use $\mathbf{rec}\;A.\, (\tau.A +
-b.(\mathbf{rec}\;B.\,(b.B)))$ instead.
-
-The extra beauty of above recursion opeator is, if we imagine the
-\texttt{rec} symbol as $\lambda$ in $\lambda$-expressions, i.e. $\lambda A.\, (\tau.A +
-b.(\lambda B.\,(b.B)))$, then we can see both $A$ and $B$ are bound
-variables in this expression. On the other side, it's easy to write
-an extra constant $C$ inside previous process without a surrounding $\lambda C$, and it must
-be a \emph{free variable} of that $\lambda$-expressions. If we go back to the constant-based CCS
-syntax, this would mean a malformed CCS process because not all the
-constants used in it are defined. Our point here is:
-\begin{enumerate}
-\item Under the recursion-based CCS syntax, all possible CCS terms
-  constructed from the algebraic datatype are well-formed, and those
-  free variables can be seen and used\footnote{However, in our
-    formalization of unique solution of equations theorems, we focus
-    on single-variable case and directly used $\lambda$-expression
-    (typed: $CCS\rightarrow CCS$) as equation. The current discussion
-    is mainly for the support of multi-variable equations in the future.} as equation variables.
-\item All proved theorems about CCS naturally take CCS process with
-  extra free variables, as they by themselves have no transition, just
-  like $\mathrm{0}$. (this is a natural consequence derived from SOS rules)
-\end{enumerate}
-
-The transition of CCS processes is defined by an inductive
-relation, literally the same as SOS rules appearing in CCS
-textbooks.\footnote{There's an interesting finding here: we never need to use the induction
-theorem for transition relation at all, after having proved almost all
-notable results for CCS. In another word, the whole CCS formal theory
-builds normally, even if the transition relation
-is defined co-inductively (by the same set of SOS rules). A potential
-need is the prove the set of ending process of transitions from any
-process doesn't use any new labels, but so far this result is not
-formalized yet. The question
-is: do the largest fixpoint and smallest fixpoint \emph{coincide} for
-a relation defined by SOS rules? (if not, what else do we have in the
-co-inductive relation?)} The only notable SOS rule which is different
-with their usual version in textbooks, is the recursion rule:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{E} (\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}) \HOLFreeVar{X} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}
-\end{alltt}
-which says, if we substitute all appearences of constant $X$ in $E$ to
-$(\mathbf{rec}\; X E)$ and the resulting process has a transition to $E_1$
-with action $u$, then $(\mathbf{rec}\; X E)$ has the same
-transition.
-
-\subsection{Coarsest (pre)congruence contained in $\approx$ (or $\succeq_{\mathrm{bis}}$)}
-
-The ``coarsest congruence contained in weak bisimilarity ($\approx$)''
-theorem in CCS is somehow special, as its current known proofs either
-rely on quite restricted conditions, or have an extremely complicated proof
-(c.f. van Glabbek's paper) in
-which ordinal theory is required.  Actually even the relationship
-between its name and statement is not well explained in many CCS
-textbooks. But van Glabbek's paper has given the so far clearest
-explainion, here we briefly repeat his arguments:
-
-As we know weak bisimilarity ($\approx$) is not (real) congruence, as
-it doesn't satisfy subsitutivity on direct sums (but if the CCS syntax
-is non-standard, i.e. has only prefixed sums, $\approx$ is indeed a
-congruence). The purpose is to find a coarsest congruence contained in
-weak bisimilarity. (``coarsest'' means, any other congruence finer than it must be contained in it)
-There're two ways to build a congruence from weak bisimilarity, one
-way is the standard definition for observational congruence (rooted
-weak bisimilarity) $\approx^c$ in CCS textbooks, but even it's proven to be a
-congruence we don't know if it's coarsest one.  The other way is to
-build a (pre)congruence closure (Def ??) directly upon
-the original weak bisimilarity relation, we call the resulting
-relation ``Weak bisimilarity congruence'' ($[\approx]$):
-\begin{alltt}
-\HOLConst{WEAK_CONGR} \HOLSymConst{=} \HOLConst{CC} \HOLConst{WEAK_EQUIV}
-\HOLConst{CC} \HOLFreeVar{R} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}.
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}.
-\HOLConst{CONTEXT} \HOLBoundVar{c} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{c} \HOLBoundVar{g}) (\HOLBoundVar{c} \HOLBoundVar{h}))
-\end{alltt}
-It can be shown that any such (pre)congruence closure is automatically coarset.
-
-Now it remains to prove that, the congrunce relation built by above
-two quite different approaches actually coincide. To achive this goal,
-we first noticed that, all other operators beside sums used in
-semantic context doesn't matter, because they're already substituible
-for weak bisimilarity. The only important operator is the sum
-operator. To focus on this important operator, we can temporily
-introduce another concept called \emph{sum equivalence}:
-\begin{alltt}
-\HOLConst{SUM_EQUIV} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}.
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLBoundVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{+} \HOLBoundVar{r})
-\end{alltt}
-It can be shown that, weak bisimilarity congruence implies this sum
-equivalence. Thus if we can further prove that the sum
-equivalence imples observational congrence, all the three relations
-must coincide together, as shown in the following diagram:
-\begin{displaymath}
-\xymatrix{
-{\textrm{Weak bisimilarity } (\approx)} & {\textrm{Sum
-    equivalence } (\approx^+)} \ar@/^3ex/[ldd]^{\subseteq ?}\\
-{\textrm{Weak bisim. congruence } ([\approx])}
-\ar[u]^{\subseteq} \ar[ru]^{\subseteq} \\
-{\textrm{Rooted bisimilarity } (\approx^c)} \ar[u]^{\subseteq}
-}
-\end{displaymath}
-In another words, observational congruence is the coarsest congruence
-contained in weak bisimilary if and only if
-\begin{equation}
-\forall p\; q.\; p \approx^c\! q \Longleftrightarrow \forall r.\; p+r \approx
-q+r
-\end{equation}
-
-The classical assumption for proving above theorem requires that $p$
-and $q$ do not use up all available visible actions,
-i.e. $\mathrm{fn}(p) \cup \mathrm{fn}(q) \neq \mathscr{L}$. But it's
-not easy to formalize and use such an assumption without a detailed
-treatment on free and bound names (visible actions) of CCS
-processes.\footnote{There're totally four such concepts: 1) free names
-are all visible actions appearing in a CCS term without surrounding
-$\nu$ (restriction) operator on the same action; 2) bound names are
-the set of all actions ever used by $\nu$ (restriction) operator; 3)
-free variables (or equation variables) are those variables without a
-definition given by recursion
-operator; 4) bound variables (process constants) are variables with
-definitions given by recursion operator. All CCS results using these
-concepts are not touched so far, although these four concepts are
-successfully defined using HOL's set and list theories.} However, by
-analyzing the proof steps, we found that, what's really required is to
-not use up all available labels in those weak transitions directly
-lead from $p$ and $q$. In another words, even they have used all
-available labels, as long as their first weak transitions didn't, the
-whole proof can still be finished.\footnote{Further more, $p$ and $q$
-  can be considered separately: the proof can be finished as long as
-  \emph{each} of them didn't use up all labels on first weak
-  transition, while the union of these labels are all labels.}
-We have formalized this property of
-CCS process and call it ``free action'' property:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{a}.
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}}.
-\HOLSymConst{\HOLTokenNeg{}}(\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{a}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}})
-\end{alltt}
-With this property, the classical form of this theorem that we have
-formally proved is:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
-   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r})
-\end{alltt}
-
-If we drop this classical assumption, then the proof becomes much
-harder, as given a van Glabbek's paper. The most important
-intermediate result we have proved here, is the following lemma:
-\begin{alltt}
-\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
-        \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}} \HOLBoundVar{u}.
-\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenConj{}}
-        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{q\sp{\prime}} \HOLBoundVar{u}.
-\HOLFreeVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenImp{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r}) \HOLSymConst{\HOLTokenImp{}}
-   \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q}
-\end{alltt}
-It roughly says, for any two processes $p$ and $q$, if we can find
-another stable (no $\tau$-transitions) process $k$ which is not weak bisimilar to any transition of
-$p$ and $q$, then the hard part of our main theorem is proved. In
-practice, once two processes were given, it's not hard to find
-such a process, but the arbitrariness of $p$ and $q$ made this result
-extremely hard to prove. The method given by van Glabbek requires a
-construction of arbitrarily non-bisimilar processes called ``Klop
-processes'':
-\begin{definition}{(Klop processes)}
-For each ordinal $\lambda$, and an arbitrary chosen non-$\tau$ action $a$,
-define a CCS process $k_\lambda$ as follows:
-\begin{enumerate}
-\item $k_0 = 0$,
-\item $k_{\lambda+1} = k_\lambda + a.k_\lambda$ and
-\item for $\lambda$ a limit ordinal, $k_\lambda = \sum_{\mu < \lambda}
-  k_\mu$, meaning that $k_\lambda$ is constructed from all graphs
-  $k_\mu$ for $\mu < \lambda$ by identifying their root.
-\end{enumerate}
-\end{definition}
-It's not hard to prove that, all $k_i$ are non-bisimilar (not only
-weakly but also strongly). The idea is, for any two processes, the union of sets of their all
-transitions cannot be arbitrarily large: it has to be limited by an
-ordinal number. But above contruction can be arbitrarily large, so
-there always exists a Klop process which can be used to satisfy above
-lemma (and finish the proof).
-
-However, this goes beyond HOL's expressivity to define above process, mostly
-because there's no way to express infinite ``sums'' in CCS
-datatype.\footnote{There're actually several ways to modify the
-  datatype to support infinite sums, but none of these infinity can be
-arbitrary. The full version of ordinal theory cannot be expressed in HOL.}
-What we can do is to eliminate the last branch with limiting
-ordinals, and define Klop processes only on finite cases:
-\begin{alltt}
-\HOLConst{KLOP} \HOLFreeVar{a} \HOLNumLit{0} \HOLSymConst{=} \HOLConst{nil}
-\HOLConst{KLOP} \HOLFreeVar{a} (\HOLConst{SUC} \HOLFreeVar{n}) \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLSymConst{+} \HOLConst{label} \HOLFreeVar{a}\HOLSymConst{..}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\hfill[KLOP_def]
-\end{alltt}
-But this means we much assume the two processes $p$ and $q$ are
-finite-state, i.e. their corresponding LTS graphs have only finite
-states. Choosing an element from a countable infinite set of processes
-to make sure it's not bisimiar with a given set of processes, this is
-essentially a pure set-theoretic problem, as formalized and proved in
-the following lemma:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenImp{}}
-   \HOLConst{FINITE} \HOLFreeVar{A} \HOLSymConst{\HOLTokenConj{}} \HOLConst{INFINITE} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y}.
-\HOLBoundVar{x} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{x} \HOLSymConst{\HOLTokenNotEqual{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y}) \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
-\HOLBoundVar{k} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n}.
-\HOLBoundVar{n} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{A} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{n} \HOLBoundVar{k}
-\end{alltt}
-
-With all these results, finally we can prove the ``coarsest congruence
-contained in $\approx$'' theorem for finite-state CCS:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
-   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r})
-\end{alltt}
-
-For contraction and rooted contraction, the situation (and proof
-steps) is exactly the same:
-\begin{displaymath}
-\xymatrix{
-{\textrm{Contraction } (\succeq_{\mathrm{bis}})} & {\textrm{Sum
-    contraction } (\succeq_{\mathrm{bis}}^+)} \ar@/^3ex/[ldd]^{\subseteq ?}\\
-{\textrm{Contraction precongruence } ([\succeq_{\mathrm{bis}}])}
-\ar[u]^{\subseteq} \ar[ru]^{\subseteq} \\
-{\textrm{Rooted contraction } (\succeq_{\mathrm{bis}}^c)} \ar[u]^{\subseteq}
-}
-\end{displaymath}
-
-And we got two versions of theorem saying rooted contraction is the
-coarsest precongruence of (bisimilarity) contraction:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
-   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r})
-\HOLTokenTurnstile{} \HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
-   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r})
-\end{alltt}
-
-\subsection{Semantic context, guardness and (pre)congruence}
-
-We need to find a suitable formal definition of semantic
-context. There're multiple ways. Here we have chosen to use $\lambda$-expressions (typed
-$CCS\rightarrow CCS$) to represent a (multi-hole) semantic
-context. The definition is inductive:
-\begin{alltt}
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})
-\end{alltt}
-
-Under above definition, we can formally define the concept of
-``precongruence'' and ``congruence'' in the following ways:
-\begin{alltt}
-\HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
-\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})
-\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLConst{precongruence} \HOLFreeVar{R}
-\end{alltt}
-
-A \emph{weak guarded} context is a context in which all holes appears
-in the sub-expression of prefixed processes. We can easily define it
-following the same idea:
-\begin{alltt}
-\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})
-\end{alltt}
-(Notice the differences between a weak guarded context and a normal
-one: $\lambda t. t$ is not weakly guarded as the variable is directly
-exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
-guarded as long as $e[\cdot]$ is a semantic context, no necessary weakly guaded.)
-
-It's a similar process to define strongly guarded context
-(\texttt{SG}), sequential context (\texttt{SEQ}) and their
-variants without direct sums (\texttt{GCONTEXT}, \texttt{WGS},
-\texttt{GSEQ}). Some lemmas about their relationships have very long
-(but trivial) formal proofs due to the combinatorial explosion of
-inductions on their structures. For example, one such 
-lemma says, for any semantic context $E$ which is both strongly guarded
-and sequential (no direct sums) and another sequential context $H$ (no
-direct sums), the composition $H \circ E$ is still both strongly
-guarded and sequential (no direct sums):
-\begin{alltt}
-SG_GSEQ_combin:
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{H}.
-\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E})
-\end{alltt}
-
-\subsection{Milner's ``unique solution of equations'' theorems}
-
-Once the representation issue of CCS equations is resolved, the actual
-proofs of Milner's unique solution of equations theorems is not very
-interesting from the view of theorem proving, although it's a 
-precise proof engineering work producing quite long proofs.
-Since we have chosen to use semantic context to represent
-single-variable equations, an equation like $P \sim E\{P/X\}$ now
-becomes $P \sim E[P]$, in which $E$ is a (multi-hole) semantic
-context, and there's no need to say it ``contains at most the variable
-$X$'' any more, as equation variable doesn't appear in $E$ at
-all. Under these simplifications, the formal proof of Milner's unique
-solution of equations theorem for $\sim$ is a literal mapping for informal
-proofs based on bisimulation upto $\sim$, induction and case analysis
-of weakly guarded contexts. Below is the formal version of Lemma 4.13
-and Proposition 4.14 in Milner's book:
-
-\begin{alltt}
-STRONG_UNIQUE_SOLUTION:
-\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}
-\end{alltt}
-
-\begin{alltt}
-WEAK_UNIQUE_SOLUTION:
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
-\end{alltt}
-
-\begin{alltt}
-OBS_UNIQUE_SOLUTION:
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
-\end{alltt}
-
-\subsection{Unique solution of contractions}
-
-The major difficultis in formalizing Sangiorgi's unique solution of
-contractions theorem is to prove its main lemma (c.f. Lemma 3.9 of
-main paper), in which the length of weak transitions are used for
-induction. Introducing a special vesion of weak transition relation
-with length would be an easier choice, but we have chosen to use trace
-instead, so that in the future it's possible to extend the work with
-trace equivalence included.
-
-A trace is represented by the beginning and ending CCS processes, plus
-a list of action it passes. Insteading of defining it directly, we
-have first defined a new concept called Reflexive Transitive Closure with a
-List (LRTC):
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{LRTC} \HOLFreeVar{R} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b} \HOLSymConst{\HOLTokenEquiv{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.
-       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x}. \HOLBoundVar{P} \HOLBoundVar{x} [] \HOLBoundVar{x}) \HOLSymConst{\HOLTokenConj{}}
-       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z}.
-\HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLBoundVar{x} (\HOLBoundVar{h}\HOLSymConst{::}\HOLBoundVar{t}) \HOLBoundVar{z}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLBoundVar{P} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b}
-\end{alltt}
-For any labelled translation relation $R$, \HOLinline{\HOLConst{LRTC} \HOLFreeVar{R}} builds a new
-relation accumulating all labels in the middle. Then the trace of CCS processes can be
-defined by simply combining LRTC with the (strong) CCS transition
-relation:
-\begin{alltt}
-\HOLConst{TRACE} \HOLSymConst{=} \HOLConst{LRTC} \HOLConst{TRANS}
-\end{alltt}
-
-If there's at most one visible action (label) in the list of actions of a trace,
-then the trace is also a weak transition. We divided this observation
-into two cases: no label and unique label. The definition of ``no
-label'' in an action list is easy and clear:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{NO_LABEL} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
-\HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLFreeVar{L}
-\end{alltt}
-while the definition of ``unique label'' can be done in many ways, in
-which we have chosen to use the version learnt from Robert Beers in
-a private discussion which prevented counting or filtering in the list:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}}
-   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{L\sb{\mathrm{1}}} \HOLBoundVar{L\sb{\mathrm{2}}}.
-       (\HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} [\HOLFreeVar{u}] \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{=} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenConj{}}
-       \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
-\HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDisj{}} \HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{L\sb{\mathrm{2}}}
-\end{alltt}
-It says, a label is unique in an action list iff it there's no other
-labels in the rest part of the list.
-
-The final relationship between traces and weak transitions is stated
-and proved in the following lemma:
-\begin{alltt}
-WEAK_TRANS_AND_TRACE:
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}}
-   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{us}.
-       \HOLConst{TRACE} \HOLFreeVar{E} \HOLBoundVar{us} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{NULL} \HOLBoundVar{us} \HOLSymConst{\HOLTokenConj{}} \HOLKeyword{if} \HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLKeyword{then} \HOLConst{NO_LABEL} \HOLBoundVar{us}
-       \HOLKeyword{else} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLBoundVar{us}
-\end{alltt}
-(A weak transition $E\overset{u}{\rightarrow}E'$ is a trace with non
-empty action list: 1) without any visible label, if $u = \tau$, or 2)
-$u$ is the unique label in the list, if $u \neq \tau$.)
-
-To finish the proof of Lemma 3.9 in Sangiorgi's paper, we used above
-lemma to convert weak transitions to traces, which either keep its
-length or become shorter after passing weak bisimilations, then we
-used above lemma again to convert the traces back to weak transitions.
-
-The proof of the final unique solution of contractions theorem is just
-a literal transition of its informal proofs: (noticed that the weakly
-guarded context is the version without direct sums)
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
-\end{alltt}
-
-\subsection{Unique solution of rooted contractions}
-
-The proof of Unique solution of rooted contractions theorem is the
-same proof steps of Unique solution of contractions theorem plus the
-application of \texttt{OBS_CONGR_BY_WEAK_BISIM} at the
-beginning.\footnote{In the thesis work, the conclusion of this theorem
-is weak bisimilarity, and the proof is exactly the same as Unique
-solution of contractions theorem. Now we got a stronger conclusion
-using observational congruence, and the previous version becomes a
-trivial collorary of the current version.} The
-two proofs are quite similar, mostly because the only property we need
-from (rooted) contraction is its precongruence. Once we have proved
-the precongruence of rooted contracion, we can naturally use the
-normal version of weakly guarded expressions with direct sums included.
-
-\begin{alltt}
-UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS:
-\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
-\end{alltt}
+There're two major limitations in this work. One is due to HOL, we only support Finitary CCS, i.e.
+no infinite sum nor infinite parallel composition.
+The other limitation is, equation variables (or holes in semantics contexts)
+cannot appear inside recursion operator closure. However, these limitations do not
+cause any difference in the proof of main results represented in this paper.

### 2018-06-11 express2018/part2.tex
Stage work on part2

@@
 
-\section{Formalization}
-
-In the second half of this paper, we present a formalization of CCS
-including the new concepts and theorems proposed in the first half of
-this paper. The main purpose is to convince the readers that, there's no flaw in the informal proofs. The
-formalization work is based on a formalization of CCS in HOL theorem
-prover (HOL4), described in second author's MSc thesis
-\cite{Tian:2017wrba} and now lives in the official examples folder of HOL4 source
-code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}.
-The work is essentially a porting and extension of the early CCS
-formalization by Monica Nesi \cite{Nesi} in HOL88.
-
-We will not repeat all definitions and theorems of CCS again by their
-formalized versions. Instead, we just focus on several highlights in
-this work, i.e.
-\begin{enumerate}
-\item The formalization of semantics context in $\lambda$-expressions and the theory of
-  (pre)congruence for CCS;
-\item The definition and uses of trace in the proof of unique solution of
-  contractions theorem;
-\item The proof of the hard version of ``coarsest congruence
-  contained in $\approx$'' theorem.
-\end{enumerate}
-
-\subsection{Simplifications and Limitations}
-
-We have only formally verified simplified forms of the unique
-solution theorems introduced in the first part. This is to not only
-save the formalization efforts, but also to make us focusing on the most
-important part of the proof. The most important simplification is
-that, we have only proved all unique solution theorems with only single-variable equations
-(contractions).
-
-But such a simplification doesn't hurt the rigorousness of our entire
-work, as once the single-equation version of the theorem is
-proven, the general case is just a routine
-adaptation for paper proofs. \footnote{However, it's impossible to directly derive the
-  multi-variable versions of unique solution theorems from their
-  single-variable versions.} \footnote{Also, I don't know if there
-  exists a higher-level general
-  duality theorem such that some kind of results on single-variable CCS
-  equations must also hold for multi-variable equation groups. --Chun.}
-It's not easy to formalize multi-variable CCS equations with
-introducing a large number of definitions and intermediate
-results. It's easy, however, to directly use the semantics context to
-represent single-variable equations without the need of formalizing
-the concept of ``equation'' at all.
-
-There're two major limitations in this work. One is the class of CCS
-processes, i.e. we're limited with Finitary CCS which has no infinite
-sums or parallel compositions. The other limitation is, even for single-variable equation, the
-variable doesn't appear inside any constant.
-
 \subsection{CCS, Transitions and Bisimilarities}
 
-In our formalization of CCS, the set of transition actions are not
-defined by the union of all visiable actions (names and conames) and the invisible
-action $\tau$. Instead, we define only visible names as a simple
-algebraic datatype ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}`` in which the type parameter
-$\beta$ can be any other type (thus we don't know anything about the
-cardinality of the set of all visiable actions), and then use HOL's
-\texttt{optionTheory} to further extend the type by one more
-element, $\tau$. Having a dedicated type for all visiable actions is quite
-convenient and make some statements shorter. (e.g. the restriction
-operator can only take a set of visible actions)
+In the formalization of CCS, it's better to have two distinct
+types for actions: the type \HOLinline{\ensuremath{\beta} \HOLTyOp{Label}} ($\beta$ is a type variable.) for visible actions, divided by input
+and output actions:
+\begin{lstlisting}
+val _ = Datatype `Label = name 'b | coname 'b`;
+\end{lstlisting}
+and the type \HOLinline{\ensuremath{\beta} \HOLTyOp{Action}} as the
+union of all visible and invisible actions. The cardinality of all
+available types depends on the choice of type variable $\beta$.
 
-The type of CCS process is defined by an algebraic datatype in HOL,
-i.e. an inductive defined finite structure constructed by unary and
-binary operators.\footnote{It seems possible to switch to co-algebraic
-datatypes for the support of potential infinite sums. Indeed, we never
-need to induct on CCS processes in any proof so far.} 
-It's not easy to directly extend this datatype with new operators,
-without hurting the existing proved results.\footnote{This is usually
-  called \emph{deep embedding} when implementing a new logic in theorem
-  provers. In case of CCS, \emph{shallow embedding} seems impossible.}
-Relabeling operator is not necessary from the theoretical view, as
-it's possible to use \emph{syntactic
-  substitution} instead\footnote{c.f. Section 4.1.2. (page 168) of Robert Gorrieri's CCS book.}
-However, it's quite hard to formalize syntactic substitution for CCS,
-as it requires to prove many results on the free and bound names
-first.
+The core datatype ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'' is then defined as an inductive
+datatype in HOL, based on its Datatype package:
+\begin{lstlisting}
+val _ = Datatype `CCS = nil
+		      | var 'a
+		      | prefix ('b Action) CCS
+		      | sum CCS CCS
+		      | par CCS CCS
+		      | restr (('b Label) set) CCS
+		      | relab CCS ('b Relabeling)
+		      | rec 'a CCS`;
+\end{lstlisting}
 
-Without constants (or recursion operator), a CCS process cannot
-represent infinite-state LTS and many deep results in CCS cease to
-exist then. Therefore any serious CCS formalization
-must contain the support of constants (or recursion operator. Nowadays
-most CCS textbooks and papers use constants, but from the formal view
-it's better (or only possible) to use the original form: the recursion
-operator, because any CCS process must be presented as single, finite term in
-theorem prover. In Milner's book, this CCS operator is called \texttt{fix},
-as it essentially returns the fixpoint of a CCS equation. We use the
-symbol \texttt{rec} instead and limit ourself to single-variable case,
-as we want to extend to multi-variable recursion operator in the
-future with the original name. So instead of saying a CCS process $A$
-with constant definitions
-$A \overset{\mathrm{def}}{=} \tau.A + b.B$ and $B
-\overset{\mathrm{def}}{=} b.B$, we use $\mathbf{rec}\;A.\, (\tau.A +
-b.(\mathbf{rec}\;B.\,(b.B)))$ instead.
+We have added some minimal grammar support using HOL's powerful pretty printer, to represent CCS
+processes in more readable forms. Table \ref{tab:ccsoperator} has listed the notation of typical CCS processes and
+major operators supported by above definition. (Notice the use of
+recursition operator for representing process constants)
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{Operator} & \textbf{Notation} & \textbf{HOL} & \textbf{HOL
+  (alternative)}\\
+\hline
+nil & $\textbf{0}$ &  \HOLinline{\HOLConst{nil}} & \HOLinline{\HOLConst{nil}} \\
+Rrefix & $a.b.0$ & \texttt{prefix a (prefix b nil)} & \HOLinline{\HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{b}\HOLSymConst{..}\HOLConst{nil}} \\
+Sum & $p + q$ & \texttt{sum p q} & \HOLinline{\HOLFreeVar{p} \HOLSymConst{+} \HOLFreeVar{q}} \\
+Parallel & $p \,\mid\, q$ & \texttt{par p q} & \HOLinline{\HOLFreeVar{p} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{q}} \\
+Restriction & $(\nu\;L)\;p$ & \texttt{restr L p} & \HOLinline{\HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{p}} \\
+Constant & $A=a.A$ & \texttt{rec A (prefix a (var A))} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} (\HOLFreeVar{a}\HOLSymConst{..}\HOLConst{var} \HOLFreeVar{A})} \\
+\hline
+\end{tabular}
+\end{center}
+   \caption{Syntax of CCS operators}
+   \label{tab:ccsoperator}
+\end{table}
 
-The extra beauty of above recursion opeator is, if we imagine the
-\texttt{rec} symbol as $\lambda$ in $\lambda$-expressions, i.e. $\lambda A.\, (\tau.A +
-b.(\lambda B.\,(b.B)))$, then we can see both $A$ and $B$ are bound
-variables in this expression. On the other side, it's easy to write
-an extra constant $C$ inside previous process without a surrounding $\lambda C$, and it must
-be a \emph{free variable} of that $\lambda$-expressions. If we go back to the constant-based CCS
-syntax, this would mean a malformed CCS process because not all the
-constants used in it are defined. Our point here is:
-\begin{enumerate}
-\item Under the recursion-based CCS syntax, all possible CCS terms
-  constructed from the algebraic datatype are well-formed, and those
-  free variables can be seen and used\footnote{However, in our
-    formalization of unique solution of equations theorems, we focus
-    on single-variable case and directly used $\lambda$-expression
-    (typed: $CCS\rightarrow CCS$) as equation. The current discussion
-    is mainly for the support of multi-variable equations in the future.} as equation variables.
-\item All proved theorems about CCS naturally take CCS process with
-  extra free variables, as they by themselves have no transition, just
-  like $\mathrm{0}$. (this is a natural consequence derived from SOS rules)
-\end{enumerate}
-
-The transition of CCS processes is defined by an inductive
-relation, literally the same as SOS rules appearing in CCS
-textbooks.\footnote{There's an interesting finding here: we never need to use the induction
-theorem for transition relation at all, after having proved almost all
-notable results for CCS. In another word, the whole CCS formal theory
-builds normally, even if the transition relation
-is defined co-inductively (by the same set of SOS rules). A potential
-need is the prove the set of ending process of transitions from any
-process doesn't use any new labels, but so far this result is not
-formalized yet. The question
-is: do the largest fixpoint and smallest fixpoint \emph{coincide} for
-a relation defined by SOS rules? (if not, what else do we have in the
-co-inductive relation?)} The only notable SOS rule which is different
-with their usual version in textbooks, is the recursion rule:
+The transition semantics of CCS processes were defined by the following
+Structural Operational Semantics (SOS for short) rules in
+Fig.\;\ref{f:LTSCCS}, except that the transition rule for constants
+has been changed to recursion operator:
 \begin{alltt}
@@
 which says, if we substitute all appearences of constant $X$ in $E$ to
-$(\mathbf{rec}\; X E)$ and the resulting process has a transition to $E_1$
-with action $u$, then $(\mathbf{rec}\; X E)$ has the same
+$(\mathbf{rec}\; X\; E)$ and the resulting process has a transition to $E_1$
+with action $u$, then $(\mathbf{rec}\; X\; E)$ has the same
 transition.
@@
 
-The major difficultis in formalizing Sangiorgi's unique solution of
+The major difficulties in formalizing Sangiorgi's unique solution of
 contractions theorem is to prove its main lemma (c.f. Lemma 3.9 of

### 2018-06-12 express2018/part2.tex
Stage work on part2

@@
 
-\subsection{CCS, Transitions and Bisimilarities}
+\subsection{CCS and transitions based on SOS rules}
 
@@
 \hline
-\textbf{Operator} & \textbf{Notation} & \textbf{HOL} & \textbf{HOL
+\textbf{Operator} & \textbf{Notation} & \textbf{HOL term} & \textbf{HOL
   (alternative)}\\
@@
 nil & $\textbf{0}$ &  \HOLinline{\HOLConst{nil}} & \HOLinline{\HOLConst{nil}} \\
-Rrefix & $a.b.0$ & \texttt{prefix a (prefix b nil)} & \HOLinline{\HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{b}\HOLSymConst{..}\HOLConst{nil}} \\
+Prefix & $a.b.0$ & \texttt{prefix a (prefix b nil)} & \HOLinline{\HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{b}\HOLSymConst{..}\HOLConst{nil}} \\
 Sum & $p + q$ & \texttt{sum p q} & \HOLinline{\HOLFreeVar{p} \HOLSymConst{+} \HOLFreeVar{q}} \\
@@
 \end{center}
+\vspace{-1em}
    \caption{Syntax of CCS operators}
@@
 with action $u$, then $(\mathbf{rec}\; X\; E)$ has the same
-transition.
+transition. Other SOS rules have the following forms:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E}\hfill\texttt{[PREFIX]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{+} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[SUM1]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{+} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[SUM2]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sp{\prime}}\hfill\texttt{[PAR1]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[PAR2]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} (\HOLConst{COMPL} \HOLFreeVar{l})\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
+   \HOLFreeVar{E} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sb{\mathrm{2}}}\hfill\texttt{[PAR3]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} ((\HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}}) \HOLSymConst{\HOLTokenDisj{}} (\HOLFreeVar{u} \HOLSymConst{=} \HOLConst{label} \HOLFreeVar{l}) \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{E\sp{\prime}}\hfill\texttt{[RESTR]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{rf}\hfill\texttt{[RELABELING]}
+\end{alltt}
+Above rules work as \emph{axioms} in the theory of CCS, as they cannot be
+proved by more primitive theorems or axioms. From the view of theorem prover, these
+SOS rules are nothing but an \emph{inductive 
+  definition} on 3-ary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL4's function
+\texttt{Hol_reln}.\footnote{On the other side, above literal SOS rules are not
+the \emph{only} thing we got from \texttt{Hol_reln}, which also
+returns the fix-point theorem and induction principle for the
+relation, otherwise things like ``$\textbf{0}$ has no transition''
+cannot be proved at all.} The ultimate result here (before
+bisimilution gets involved), is an ML function taking a CCS process
+and returning a theorem indicating all its direct transitions.
+
+For instance, we know that the process $(a.0 | \bar{a}.0)$ have three
+possible transitions:
+\begin{enumerate}
+\item $(a.0 | \bar{a}.0) \overset{a}{\longrightarrow} (0 | \bar{a}.0)$;
+\item $(a.0 | \bar{a}.0) \overset{\bar{a}}{\longrightarrow} (a.0 | 0)$;
+\item $(a.0 | \bar{a}.0) \overset{\tau}{\longrightarrow} (0 | 0)$.
+\end{enumerate}
+To completely decide all possible transitions, if done manually, the
+following results must be proved:
+\begin{enumerate}
+\item there exists transitions from $(a.0 | \bar{a}.0)$ (optionally);
+\item each of above three transitions using SOS inference rules;
+\item there's no other transition beside the three existing ones.
+\end{enumerate}
+For large complex processes it's surprising hard to prove the
+non-existence of transitions. Instead, if we call the function \texttt{CCS\_TRANS\_CONV} with the
+root process:
+\begin{lstlisting}
+> CCS_TRANS_CONV
+	 ``par (prefix (label (name "a")) nil)
+	       (prefix (label (coname "a")) nil)``
+\end{lstlisting}
+we get the following theorem, which completely answers the question:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{In} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}}
+   ((\HOLFreeVar{u} \HOLSymConst{=} \HOLConst{In} \HOLStringLit{a}) \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil}) \HOLSymConst{\HOLTokenDisj{}}
+    (\HOLFreeVar{u} \HOLSymConst{=} \HOLConst{Out} \HOLStringLit{a}) \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{In} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil})) \HOLSymConst{\HOLTokenDisj{}}
+   (\HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}}) \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil})
+\end{alltt}
+
+\subsection{Bisimulation and Bisimilarity}
+
+It's well known that, bisimilarity is a coinductive
+relation. Historically, it can be defined in HOL without any special
+support, but now using HOL's
+coinductive relation module (\texttt{Hol_coreln}), it's much easier to
+get the equivalent definition with minimal efforts.
+
+First of all, we define the zero or more $\tau$-transition chains of
+CCS processes as a new relation called \texttt{EPS} ($\epsilon$),
+which is the RTC (reflexive transitive closure) of single-step $\tau$-transition:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{EPS} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
+\HOLBoundVar{E} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}})\HOLSymConst{\HOLTokenSupStar{}}\hfill{[EPS_def]}
+\end{alltt}
+Then we can define weak transition as a normal transition wrapped by
+two $\epsilon$-transitions:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+\HOLFreeVar{E} \HOLSymConst{\HOLTokenEPS} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenEPS} \HOLFreeVar{E\sp{\prime}}\hfill{[WEAK_TRANS]}
+\end{alltt}
+Now we're ready to present the formalized version of (weak)
+bisimulation relation as a predicate \texttt{WEAK_BISIM}:
+\begin{definition}{(Weak bisimulation)}
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{WEAK_BISIM} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenEquiv{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
+       \HOLFreeVar{Wbsm} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l}.
+            (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
+                 \HOLBoundVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}}
+                 \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
+\HOLBoundVar{E\sp{\prime}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
+            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
+                \HOLBoundVar{E\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
+                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
+\HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
+       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
+\HOLBoundVar{E} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
+\HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenEPS} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
+\HOLBoundVar{E\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
+\HOLBoundVar{E} \HOLSymConst{\HOLTokenEPS} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}\hfill{[WEAK_BISIM]}
+\end{alltt}
+\end{definition}
+
+There're two ways to define weak bisimulation equivalence in HOL4, one
+is to define it as the union of all weak bisimulations:
+\begin{definition}{(Alternative definition of weak equivalence)}
+For any two CCS processes $E$ and $E'$, they're \emph{weak
+  bisimulation equivalent} (or weak bisimilar) if and only if there's
+a weak bisimulation relation between $E$ and $E'$:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{Wbsm}.
+\HOLBoundVar{Wbsm} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WEAK_BISIM} \HOLBoundVar{Wbsm}\hfill{[WEAK_EQUIV]}
+\end{alltt}
+\end{definition}
+This was the definition used by Monica Nesi in Hol88 in which there was no
+direct support for defining co-inductive relations.  The new method we
+have used in this project, is to use HOL4's new co-inductive relation
+defining facility \texttt{Hol_coreln} to define weak bisimulation
+equivalence:
+\begin{lstlisting}
+val (WEAK_EQUIV_rules, WEAK_EQUIV_coind, WEAK_EQUIV_cases)
+  = Hol_coreln `
+    (!(E :('a, 'b) CCS) (E' :('a, 'b) CCS).
+       (!l.
+	 (!E1. TRANS E  (label l) E1 ==>
+	       (?E2. WEAK_TRANS E' (label l) E2 /\
+                 WEAK_EQUIV E1 E2)) /\
+	 (!E2. TRANS E' (label l) E2 ==>
+	       (?E1. WEAK_TRANS E  (label l) E1 /\
+                 WEAK_EQUIV E1 E2))) /\
+       (!E1. TRANS E  tau E1 ==>
+                 (?E2. EPS E' E2 /\ WEAK_EQUIV E1 E2)) /\
+       (!E2. TRANS E' tau E2 ==>
+                 (?E1. EPS E  E1 /\ WEAK_EQUIV E1 E2))
+      ==> WEAK_EQUIV E E')`;
+\end{lstlisting}
+The fixpoint theorem (\texttt{WEAK_EQUIV_cases}) returned by above
+\texttt{Hol_coreln} call, also named ``the property (*)'' \cite{Mil89}:
+\begin{proposition}{(The property (*) for weak bisimulation
+    equivalence)}
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLFreeVar{a\sb{\mathrm{0}}} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{a\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenEquiv{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l}.
+        (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
+\HOLFreeVar{a\sb{\mathrm{0}}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
+\HOLFreeVar{a\sb{\mathrm{1}}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
+        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
+\HOLFreeVar{a\sb{\mathrm{1}}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
+\HOLFreeVar{a\sb{\mathrm{0}}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
+\HOLFreeVar{a\sb{\mathrm{0}}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
+\HOLFreeVar{a\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenEPS} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
+\HOLFreeVar{a\sb{\mathrm{1}}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
+\HOLFreeVar{a\sb{\mathrm{0}}} \HOLSymConst{\HOLTokenEPS} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{E\sb{\mathrm{2}}}\hfill{[WEAK_PROPERTY_STAR]}
+\end{alltt}
+\end{proposition}
+It is widely used in proving many results regarding bisimilarities. The
+old way for proving this fundamental theorem is quite hard but now
+it's a natural consequence of co-inductive relation definitions.
 
@@
 
-\subsection{Milner's ``unique solution of equations'' theorems}
+% \subsection{Milner's ``unique solution of equations'' theorems}
 
-Once the representation issue of CCS equations is resolved, the actual
-proofs of Milner's unique solution of equations theorems is not very
-interesting from the view of theorem proving, although it's a 
-precise proof engineering work producing quite long proofs.
-Since we have chosen to use semantic context to represent
-single-variable equations, an equation like $P \sim E\{P/X\}$ now
-becomes $P \sim E[P]$, in which $E$ is a (multi-hole) semantic
-context, and there's no need to say it ``contains at most the variable
-$X$'' any more, as equation variable doesn't appear in $E$ at
-all. Under these simplifications, the formal proof of Milner's unique
-solution of equations theorem for $\sim$ is a literal mapping for informal
-proofs based on bisimulation upto $\sim$, induction and case analysis
-of weakly guarded contexts. Below is the formal version of Lemma 4.13
-and Proposition 4.14 in Milner's book:
+% Once the representation issue of CCS equations is resolved, the actual
+% proofs of Milner's unique solution of equations theorems is not very
+% interesting from the view of theorem proving, although it's a 
+% precise proof engineering work producing quite long proofs.
+% Since we have chosen to use semantic context to represent
+% single-variable equations, an equation like $P \sim E\{P/X\}$ now
+% becomes $P \sim E[P]$, in which $E$ is a (multi-hole) semantic
+% context, and there's no need to say it ``contains at most the variable
+% $X$'' any more, as equation variable doesn't appear in $E$ at
+% all. Under these simplifications, the formal proof of Milner's unique
+% solution of equations theorem for $\sim$ is a literal mapping for informal
+% proofs based on bisimulation upto $\sim$, induction and case analysis
+% of weakly guarded contexts. Below is the formal version of Lemma 4.13
+% and Proposition 4.14 in Milner's book:
 
-\begin{alltt}
-STRONG_UNIQUE_SOLUTION:
-\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
+% \begin{alltt}
+% STRONG_UNIQUE_SOLUTION:
+% \HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
 \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}
-\end{alltt}
+% \end{alltt}
 
-\begin{alltt}
-WEAK_UNIQUE_SOLUTION:
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
+% \begin{alltt}
+% WEAK_UNIQUE_SOLUTION:
+% \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
 \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
-\end{alltt}
+% \end{alltt}
 
-\begin{alltt}
-OBS_UNIQUE_SOLUTION:
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
+% \begin{alltt}
+% OBS_UNIQUE_SOLUTION:
+% \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
 \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
-\end{alltt}
+% \end{alltt}
 

### 2018-06-12 express2018/conclusions.tex
text

\section{Conclusions}

\finish{discuss multiple equations/contractions}

### 2018-06-12 express2018/related.tex
text

\section{Related work}

\finish{comments on Monica Nesi and others}

### 2018-06-12 express2018/sos.tex
text

--- 2018-06-12 express2018/part2.tex
@@
 \end{alltt}
-
-\subsection{Bisimulation and Bisimilarity}
-
-It's well known that, bisimilarity is a coinductive
-relation. Historically, it can be defined in HOL without any special
-support, but now using HOL's
-coinductive relation module (\texttt{Hol_coreln}), it's much easier to
-get the equivalent definition with minimal efforts.
-
-First of all, we define the zero or more $\tau$-transition chains of
-CCS processes as a new relation called \texttt{EPS} ($\epsilon$),
-which is the RTC (reflexive transitive closure) of single-step $\tau$-transition:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{EPS} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-\HOLBoundVar{E} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}})\HOLSymConst{\HOLTokenSupStar{}}\hfill{[EPS_def]}
-\end{alltt}
-Then we can define weak transition as a normal transition wrapped by
-two $\epsilon$-transitions:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLFreeVar{E} \HOLSymConst{\HOLTokenEPS} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenEPS} \HOLFreeVar{E\sp{\prime}}\hfill{[WEAK_TRANS]}
-\end{alltt}
-Now we're ready to present the formalized version of (weak)
-bisimulation relation as a predicate \texttt{WEAK_BISIM}:
-\begin{definition}{(Weak bisimulation)}
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{WEAK_BISIM} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenEquiv{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-       \HOLFreeVar{Wbsm} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l}.
-            (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-                 \HOLBoundVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}}
-                 \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLBoundVar{E\sp{\prime}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-                \HOLBoundVar{E\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
-                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLBoundVar{E} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenEPS} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLBoundVar{E\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLBoundVar{E} \HOLSymConst{\HOLTokenEPS} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}\hfill{[WEAK_BISIM]}
-\end{alltt}
-\end{definition}
-
-There're two ways to define weak bisimulation equivalence in HOL4, one
-is to define it as the union of all weak bisimulations:
-\begin{definition}{(Alternative definition of weak equivalence)}
-For any two CCS processes $E$ and $E'$, they're \emph{weak
-  bisimulation equivalent} (or weak bisimilar) if and only if there's
-a weak bisimulation relation between $E$ and $E'$:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{Wbsm}.
-\HOLBoundVar{Wbsm} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WEAK_BISIM} \HOLBoundVar{Wbsm}\hfill{[WEAK_EQUIV]}
-\end{alltt}
-\end{definition}
-This was the definition used by Monica Nesi in Hol88 in which there was no
-direct support for defining co-inductive relations.  The new method we
-have used in this project, is to use HOL4's new co-inductive relation
-defining facility \texttt{Hol_coreln} to define weak bisimulation
-equivalence:
-\begin{lstlisting}
-val (WEAK_EQUIV_rules, WEAK_EQUIV_coind, WEAK_EQUIV_cases)
-  = Hol_coreln `
-    (!(E :('a, 'b) CCS) (E' :('a, 'b) CCS).
-       (!l.
-	 (!E1. TRANS E  (label l) E1 ==>
-	       (?E2. WEAK_TRANS E' (label l) E2 /\
-                 WEAK_EQUIV E1 E2)) /\
-	 (!E2. TRANS E' (label l) E2 ==>
-	       (?E1. WEAK_TRANS E  (label l) E1 /\
-                 WEAK_EQUIV E1 E2))) /\
-       (!E1. TRANS E  tau E1 ==>
-                 (?E2. EPS E' E2 /\ WEAK_EQUIV E1 E2)) /\
-       (!E2. TRANS E' tau E2 ==>
-                 (?E1. EPS E  E1 /\ WEAK_EQUIV E1 E2))
-      ==> WEAK_EQUIV E E')`;
-\end{lstlisting}
-The fixpoint theorem (\texttt{WEAK_EQUIV_cases}) returned by above
-\texttt{Hol_coreln} call, also named ``the property (*)'' \cite{Mil89}:
-\begin{proposition}{(The property (*) for weak bisimulation
-    equivalence)}
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{a\sb{\mathrm{0}}} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{a\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenEquiv{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l}.
-        (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLFreeVar{a\sb{\mathrm{0}}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLFreeVar{a\sb{\mathrm{1}}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLFreeVar{a\sb{\mathrm{1}}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLFreeVar{a\sb{\mathrm{0}}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLFreeVar{a\sb{\mathrm{0}}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLFreeVar{a\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenEPS} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLFreeVar{a\sb{\mathrm{1}}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLFreeVar{a\sb{\mathrm{0}}} \HOLSymConst{\HOLTokenEPS} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{E\sb{\mathrm{2}}}\hfill{[WEAK_PROPERTY_STAR]}
-\end{alltt}
-\end{proposition}
-It is widely used in proving many results regarding bisimilarities. The
-old way for proving this fundamental theorem is quite hard but now
-it's a natural consequence of co-inductive relation definitions.
-
-\subsection{Coarsest (pre)congruence contained in $\approx$ (or $\succeq_{\mathrm{bis}}$)}
-
-The ``coarsest congruence contained in weak bisimilarity ($\approx$)''
-theorem in CCS is somehow special, as its current known proofs either
-rely on quite restricted conditions, or have an extremely complicated proof
-(c.f. van Glabbek's paper) in
-which ordinal theory is required.  Actually even the relationship
-between its name and statement is not well explained in many CCS
-textbooks. But van Glabbek's paper has given the so far clearest
-explainion, here we briefly repeat his arguments:
-
-As we know weak bisimilarity ($\approx$) is not (real) congruence, as
-it doesn't satisfy subsitutivity on direct sums (but if the CCS syntax
-is non-standard, i.e. has only prefixed sums, $\approx$ is indeed a
-congruence). The purpose is to find a coarsest congruence contained in
-weak bisimilarity. (``coarsest'' means, any other congruence finer than it must be contained in it)
-There're two ways to build a congruence from weak bisimilarity, one
-way is the standard definition for observational congruence (rooted
-weak bisimilarity) $\approx^c$ in CCS textbooks, but even it's proven to be a
-congruence we don't know if it's coarsest one.  The other way is to
-build a (pre)congruence closure (Def ??) directly upon
-the original weak bisimilarity relation, we call the resulting
-relation ``Weak bisimilarity congruence'' ($[\approx]$):
-\begin{alltt}
-\HOLConst{WEAK_CONGR} \HOLSymConst{=} \HOLConst{CC} \HOLConst{WEAK_EQUIV}
-\HOLConst{CC} \HOLFreeVar{R} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}.
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}.
-\HOLConst{CONTEXT} \HOLBoundVar{c} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{c} \HOLBoundVar{g}) (\HOLBoundVar{c} \HOLBoundVar{h}))
-\end{alltt}
-It can be shown that any such (pre)congruence closure is automatically coarset.
-
-Now it remains to prove that, the congrunce relation built by above
-two quite different approaches actually coincide. To achive this goal,
-we first noticed that, all other operators beside sums used in
-semantic context doesn't matter, because they're already substituible
-for weak bisimilarity. The only important operator is the sum
-operator. To focus on this important operator, we can temporily
-introduce another concept called \emph{sum equivalence}:
-\begin{alltt}
-\HOLConst{SUM_EQUIV} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}.
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLBoundVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{+} \HOLBoundVar{r})
-\end{alltt}
-It can be shown that, weak bisimilarity congruence implies this sum
-equivalence. Thus if we can further prove that the sum
-equivalence imples observational congrence, all the three relations
-must coincide together, as shown in the following diagram:
-\begin{displaymath}
-\xymatrix{
-{\textrm{Weak bisimilarity } (\approx)} & {\textrm{Sum
-    equivalence } (\approx^+)} \ar@/^3ex/[ldd]^{\subseteq ?}\\
-{\textrm{Weak bisim. congruence } ([\approx])}
-\ar[u]^{\subseteq} \ar[ru]^{\subseteq} \\
-{\textrm{Rooted bisimilarity } (\approx^c)} \ar[u]^{\subseteq}
-}
-\end{displaymath}
-In another words, observational congruence is the coarsest congruence
-contained in weak bisimilary if and only if
-\begin{equation}
-\forall p\; q.\; p \approx^c\! q \Longleftrightarrow \forall r.\; p+r \approx
-q+r
-\end{equation}
-
-The classical assumption for proving above theorem requires that $p$
-and $q$ do not use up all available visible actions,
-i.e. $\mathrm{fn}(p) \cup \mathrm{fn}(q) \neq \mathscr{L}$. But it's
-not easy to formalize and use such an assumption without a detailed
-treatment on free and bound names (visible actions) of CCS
-processes.\footnote{There're totally four such concepts: 1) free names
-are all visible actions appearing in a CCS term without surrounding
-$\nu$ (restriction) operator on the same action; 2) bound names are
-the set of all actions ever used by $\nu$ (restriction) operator; 3)
-free variables (or equation variables) are those variables without a
-definition given by recursion
-operator; 4) bound variables (process constants) are variables with
-definitions given by recursion operator. All CCS results using these
-concepts are not touched so far, although these four concepts are
-successfully defined using HOL's set and list theories.} However, by
-analyzing the proof steps, we found that, what's really required is to
-not use up all available labels in those weak transitions directly
-lead from $p$ and $q$. In another words, even they have used all
-available labels, as long as their first weak transitions didn't, the
-whole proof can still be finished.\footnote{Further more, $p$ and $q$
-  can be considered separately: the proof can be finished as long as
-  \emph{each} of them didn't use up all labels on first weak
-  transition, while the union of these labels are all labels.}
-We have formalized this property of
-CCS process and call it ``free action'' property:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{a}.
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}}.
-\HOLSymConst{\HOLTokenNeg{}}(\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{a}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}})
-\end{alltt}
-With this property, the classical form of this theorem that we have
-formally proved is:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
-   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r})
-\end{alltt}
-
-If we drop this classical assumption, then the proof becomes much
-harder, as given a van Glabbek's paper. The most important
-intermediate result we have proved here, is the following lemma:
-\begin{alltt}
-\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
-        \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}} \HOLBoundVar{u}.
-\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenConj{}}
-        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{q\sp{\prime}} \HOLBoundVar{u}.
-\HOLFreeVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenImp{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r}) \HOLSymConst{\HOLTokenImp{}}
-   \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q}
-\end{alltt}
-It roughly says, for any two processes $p$ and $q$, if we can find
-another stable (no $\tau$-transitions) process $k$ which is not weak bisimilar to any transition of
-$p$ and $q$, then the hard part of our main theorem is proved. In
-practice, once two processes were given, it's not hard to find
-such a process, but the arbitrariness of $p$ and $q$ made this result
-extremely hard to prove. The method given by van Glabbek requires a
-construction of arbitrarily non-bisimilar processes called ``Klop
-processes'':
-\begin{definition}{(Klop processes)}
-For each ordinal $\lambda$, and an arbitrary chosen non-$\tau$ action $a$,
-define a CCS process $k_\lambda$ as follows:
-\begin{enumerate}
-\item $k_0 = 0$,
-\item $k_{\lambda+1} = k_\lambda + a.k_\lambda$ and
-\item for $\lambda$ a limit ordinal, $k_\lambda = \sum_{\mu < \lambda}
-  k_\mu$, meaning that $k_\lambda$ is constructed from all graphs
-  $k_\mu$ for $\mu < \lambda$ by identifying their root.
-\end{enumerate}
-\end{definition}
-It's not hard to prove that, all $k_i$ are non-bisimilar (not only
-weakly but also strongly). The idea is, for any two processes, the union of sets of their all
-transitions cannot be arbitrarily large: it has to be limited by an
-ordinal number. But above contruction can be arbitrarily large, so
-there always exists a Klop process which can be used to satisfy above
-lemma (and finish the proof).
-
-However, this goes beyond HOL's expressivity to define above process, mostly
-because there's no way to express infinite ``sums'' in CCS
-datatype.\footnote{There're actually several ways to modify the
-  datatype to support infinite sums, but none of these infinity can be
-arbitrary. The full version of ordinal theory cannot be expressed in HOL.}
-What we can do is to eliminate the last branch with limiting
-ordinals, and define Klop processes only on finite cases:
-\begin{alltt}
-\HOLConst{KLOP} \HOLFreeVar{a} \HOLNumLit{0} \HOLSymConst{=} \HOLConst{nil}
-\HOLConst{KLOP} \HOLFreeVar{a} (\HOLConst{SUC} \HOLFreeVar{n}) \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLSymConst{+} \HOLConst{label} \HOLFreeVar{a}\HOLSymConst{..}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\hfill[KLOP_def]
-\end{alltt}
-But this means we much assume the two processes $p$ and $q$ are
-finite-state, i.e. their corresponding LTS graphs have only finite
-states. Choosing an element from a countable infinite set of processes
-to make sure it's not bisimiar with a given set of processes, this is
-essentially a pure set-theoretic problem, as formalized and proved in
-the following lemma:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenImp{}}
-   \HOLConst{FINITE} \HOLFreeVar{A} \HOLSymConst{\HOLTokenConj{}} \HOLConst{INFINITE} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y}.
-\HOLBoundVar{x} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{x} \HOLSymConst{\HOLTokenNotEqual{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y}) \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
-\HOLBoundVar{k} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n}.
-\HOLBoundVar{n} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{A} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{n} \HOLBoundVar{k}
-\end{alltt}
-
-With all these results, finally we can prove the ``coarsest congruence
-contained in $\approx$'' theorem for finite-state CCS:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
-   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r})
-\end{alltt}
-
-For contraction and rooted contraction, the situation (and proof
-steps) is exactly the same:
-\begin{displaymath}
-\xymatrix{
-{\textrm{Contraction } (\succeq_{\mathrm{bis}})} & {\textrm{Sum
-    contraction } (\succeq_{\mathrm{bis}}^+)} \ar@/^3ex/[ldd]^{\subseteq ?}\\
-{\textrm{Contraction precongruence } ([\succeq_{\mathrm{bis}}])}
-\ar[u]^{\subseteq} \ar[ru]^{\subseteq} \\
-{\textrm{Rooted contraction } (\succeq_{\mathrm{bis}}^c)} \ar[u]^{\subseteq}
-}
-\end{displaymath}
-
-And we got two versions of theorem saying rooted contraction is the
-coarsest precongruence of (bisimilarity) contraction:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
-   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r})
-\HOLTokenTurnstile{} \HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
-   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r})
-\end{alltt}
-
-\subsection{Semantic context, guardness and (pre)congruence}
-
-We need to find a suitable formal definition of semantic
-context. There're multiple ways. Here we have chosen to use $\lambda$-expressions (typed
-$CCS\rightarrow CCS$) to represent a (multi-hole) semantic
-context. The definition is inductive:
-\begin{alltt}
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})
-\end{alltt}
-
-Under above definition, we can formally define the concept of
-``precongruence'' and ``congruence'' in the following ways:
-\begin{alltt}
-\HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
-\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})
-\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLConst{precongruence} \HOLFreeVar{R}
-\end{alltt}
-
-A \emph{weak guarded} context is a context in which all holes appears
-in the sub-expression of prefixed processes. We can easily define it
-following the same idea:
-\begin{alltt}
-\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})
-\end{alltt}
-(Notice the differences between a weak guarded context and a normal
-one: $\lambda t. t$ is not weakly guarded as the variable is directly
-exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
-guarded as long as $e[\cdot]$ is a semantic context, no necessary weakly guaded.)
-
-It's a similar process to define strongly guarded context
-(\texttt{SG}), sequential context (\texttt{SEQ}) and their
-variants without direct sums (\texttt{GCONTEXT}, \texttt{WGS},
-\texttt{GSEQ}). Some lemmas about their relationships have very long
-(but trivial) formal proofs due to the combinatorial explosion of
-inductions on their structures. For example, one such 
-lemma says, for any semantic context $E$ which is both strongly guarded
-and sequential (no direct sums) and another sequential context $H$ (no
-direct sums), the composition $H \circ E$ is still both strongly
-guarded and sequential (no direct sums):
-\begin{alltt}
-SG_GSEQ_combin:
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{H}.
-\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E})
-\end{alltt}
-
-% \subsection{Milner's ``unique solution of equations'' theorems}
-
-% Once the representation issue of CCS equations is resolved, the actual
-% proofs of Milner's unique solution of equations theorems is not very
-% interesting from the view of theorem proving, although it's a 
-% precise proof engineering work producing quite long proofs.
-% Since we have chosen to use semantic context to represent
-% single-variable equations, an equation like $P \sim E\{P/X\}$ now
-% becomes $P \sim E[P]$, in which $E$ is a (multi-hole) semantic
-% context, and there's no need to say it ``contains at most the variable
-% $X$'' any more, as equation variable doesn't appear in $E$ at
-% all. Under these simplifications, the formal proof of Milner's unique
-% solution of equations theorem for $\sim$ is a literal mapping for informal
-% proofs based on bisimulation upto $\sim$, induction and case analysis
-% of weakly guarded contexts. Below is the formal version of Lemma 4.13
-% and Proposition 4.14 in Milner's book:
-
-% \begin{alltt}
-% STRONG_UNIQUE_SOLUTION:
-% \HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}
-% \end{alltt}
-
-% \begin{alltt}
-% WEAK_UNIQUE_SOLUTION:
-% \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
-% \end{alltt}
-
-% \begin{alltt}
-% OBS_UNIQUE_SOLUTION:
-% \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
-% \end{alltt}
-
-\subsection{Unique solution of contractions}
-
-The major difficulties in formalizing Sangiorgi's unique solution of
-contractions theorem is to prove its main lemma (c.f. Lemma 3.9 of
-main paper), in which the length of weak transitions are used for
-induction. Introducing a special vesion of weak transition relation
-with length would be an easier choice, but we have chosen to use trace
-instead, so that in the future it's possible to extend the work with
-trace equivalence included.
-
-A trace is represented by the beginning and ending CCS processes, plus
-a list of action it passes. Insteading of defining it directly, we
-have first defined a new concept called Reflexive Transitive Closure with a
-List (LRTC):
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{LRTC} \HOLFreeVar{R} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b} \HOLSymConst{\HOLTokenEquiv{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.
-       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x}. \HOLBoundVar{P} \HOLBoundVar{x} [] \HOLBoundVar{x}) \HOLSymConst{\HOLTokenConj{}}
-       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z}.
-\HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLBoundVar{x} (\HOLBoundVar{h}\HOLSymConst{::}\HOLBoundVar{t}) \HOLBoundVar{z}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLBoundVar{P} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b}
-\end{alltt}
-For any labelled translation relation $R$, \HOLinline{\HOLConst{LRTC} \HOLFreeVar{R}} builds a new
-relation accumulating all labels in the middle. Then the trace of CCS processes can be
-defined by simply combining LRTC with the (strong) CCS transition
-relation:
-\begin{alltt}
-\HOLConst{TRACE} \HOLSymConst{=} \HOLConst{LRTC} \HOLConst{TRANS}
-\end{alltt}
-
-If there's at most one visible action (label) in the list of actions of a trace,
-then the trace is also a weak transition. We divided this observation
-into two cases: no label and unique label. The definition of ``no
-label'' in an action list is easy and clear:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{NO_LABEL} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
-\HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLFreeVar{L}
-\end{alltt}
-while the definition of ``unique label'' can be done in many ways, in
-which we have chosen to use the version learnt from Robert Beers in
-a private discussion which prevented counting or filtering in the list:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}}
-   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{L\sb{\mathrm{1}}} \HOLBoundVar{L\sb{\mathrm{2}}}.
-       (\HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} [\HOLFreeVar{u}] \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{=} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenConj{}}
-       \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
-\HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDisj{}} \HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{L\sb{\mathrm{2}}}
-\end{alltt}
-It says, a label is unique in an action list iff it there's no other
-labels in the rest part of the list.
-
-The final relationship between traces and weak transitions is stated
-and proved in the following lemma:
-\begin{alltt}
-WEAK_TRANS_AND_TRACE:
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}}
-   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{us}.
-       \HOLConst{TRACE} \HOLFreeVar{E} \HOLBoundVar{us} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{NULL} \HOLBoundVar{us} \HOLSymConst{\HOLTokenConj{}} \HOLKeyword{if} \HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLKeyword{then} \HOLConst{NO_LABEL} \HOLBoundVar{us}
-       \HOLKeyword{else} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLBoundVar{us}
-\end{alltt}
-(A weak transition $E\overset{u}{\rightarrow}E'$ is a trace with non
-empty action list: 1) without any visible label, if $u = \tau$, or 2)
-$u$ is the unique label in the list, if $u \neq \tau$.)
-
-To finish the proof of Lemma 3.9 in Sangiorgi's paper, we used above
-lemma to convert weak transitions to traces, which either keep its
-length or become shorter after passing weak bisimilations, then we
-used above lemma again to convert the traces back to weak transitions.
-
-The proof of the final unique solution of contractions theorem is just
-a literal transition of its informal proofs: (noticed that the weakly
-guarded context is the version without direct sums)
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
-\end{alltt}
-
-\subsection{Unique solution of rooted contractions}
-
-The proof of Unique solution of rooted contractions theorem is the
-same proof steps of Unique solution of contractions theorem plus the
-application of \texttt{OBS_CONGR_BY_WEAK_BISIM} at the
-beginning.\footnote{In the thesis work, the conclusion of this theorem
-is weak bisimilarity, and the proof is exactly the same as Unique
-solution of contractions theorem. Now we got a stronger conclusion
-using observational congruence, and the previous version becomes a
-trivial collorary of the current version.} The
-two proofs are quite similar, mostly because the only property we need
-from (rooted) contraction is its precongruence. Once we have proved
-the precongruence of rooted contracion, we can naturally use the
-normal version of weakly guarded expressions with direct sums included.
-
-\begin{alltt}
-UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS:
-\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
-\end{alltt}

### 2018-06-12 express2018/formal.tex
text

@@
 
-In the second half of this paper, we present a formalization of CCS
+We highlight here a formalization of CCS
+in the HOL theorem
+prover (HOL4) \cite{slind2008brief},
 including the new concepts and theorems proposed in the first half of
-this paper. The main purpose is to convince the readers that, there's no flaw in the informal proofs. The
-formalization work is based on a formalization of CCS in HOL theorem
-prover (HOL4) \cite{slind2008brief}, described in second author's MSc thesis
-\cite{Tian:2017wrba} and now lives in the official examples folder of HOL4 source
+this paper.
+%  The main purpose is to convince the readers that, there's no flaw
+%  in the informal proofs. 
+The whole formalisation can be found 
+in \cite{Tian:2017wrba}  or in 
+ in the official example folder of HOL4 source
 code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}.
-The work is essentially a porting and extension of the early CCS
-formalization by Monica Nesi \cite{Nesi} in HOL88.
+\finish{i would say here how big is the formalisation, ie how many
+  lines of code} 
+%  This
+%  work is based on a formalization of CCS in HOL theorem
+% prover (HOL4) \cite{slind2008brief}, described in second author's MSc thesis
+% \cite{Tian:2017wrba} and now lives in the official examples folder of HOL4 source
+% code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}.
 
@@
 choice operator, axiom of infinity, and rank-1 polymorphim (type
-variables). HOL4 implemented this logic without any extension, while
-some other theorem provers in HOL family (e.g. Isabelle/HOL) has
-various extensions. The HOL Logic is considerability simpler than logic
-foundations in most other theorem provers, e.g. Coq. As a result,
+variables). HOL4 implemented this logic without any extension, in
+contrast
+with
+some other theorem provers of the  HOL family (e.g. Isabelle/HOL). 
+\finish{not having extensions above: sounds like a defect; what is the
+advantage? the portability explained in the next sentence?} 
+The HOL Logic has considerability simpler logic
+foundations than most other theorem provers, e.g. Coq. As a result,
 formal theories in HOL can be easily migrated (sometimes even
@@
 
+\finish{below: to be reformulated} 
 We will not repeat all definitions and theorems of CCS again by their
@@
 
-\subsection{Simplifications and Limitations}
+In contrast with the theorems in the first part of the paper, in the
+formalisation we consider only single equations/contractions. 
+This considerably simplifies the  reading of the HOL scripts. 
+The extension of the work to multiple equations/contractions is
+discussed in Section~\ref{s:}.
 
-We have only formally verified simplified forms of the unique
-solution theorems introduced in the first part. This is to not only
-save the formalization efforts, but also to make us focusing on the most
-important part of the proof. The most important simplification is
-that, we have only proved all unique solution theorems with only single-variable equations
-(contractions).
+% \subsection{Simplifications and Limitations}
 
-But such a simplification doesn't hurt the rigorousness of our entire
-work, as once the single-equation version of the theorem is
-proven, the general case is just a routine
-adaptation for paper proofs.
-It's not easy to formalize multi-variable CCS equations with
-introducing a large number of definitions and intermediate
-results. It's easy, however, to directly use the semantics context to
-represent single-variable equations without the need of formalizing
-the concept of ``equation'' at all.
+% We have only formally verified simplified forms of the unique
+% solution theorems introduced in the first part. This is to not only
+% save the formalization efforts, but also to make us focusing on the most
+% important part of the proof. The most important simplification is
+% that, we have only proved all unique solution theorems with only single-variable equations
+% (contractions).
 
-There're two major limitations in this work. One is due to HOL, we only support Finitary CCS, i.e.
-no infinite sum nor infinite parallel composition.
-The other limitation is, equation variables (or holes in semantics contexts)
-cannot appear inside recursion operator closure. However, these limitations do not
-cause any difference in the proof of main results represented in this paper.
+% But such a simplification doesn't hurt the rigorousness of our entire
+% work, as once the single-equation version of the theorem is
+% proven, the general case is just a routine
+% adaptation for paper proofs.
+% It's not easy to formalize multi-variable CCS equations with
+% introducing a large number of definitions and intermediate
+% results. It's easy, however, to directly use the semantics context to
+% represent single-variable equations without the need of formalizing
+% the concept of ``equation'' at all.
+
+% There're two major limitations in this work. One is due to HOL, we only support Finitary CCS, i.e.
+% no infinite sum nor infinite parallel composition.
+% The other limitation is, equation variables (or holes in semantics contexts)
+% cannot appear inside recursion operator closure. However, these limitations do not
+% cause any difference in the proof of main results represented in this paper.

### 2018-06-12 express2018/part2.tex
text

@@
-%%%% -*- Mode: LaTeX -*-
-%%
-%% This is the draft of the 2nd part of EXPRESS/SOS 2018 paper, co-authored by
-%% Prof. Davide Sangiorgi and Chun Tian.
-
-\subsection{CCS and transitions based on SOS rules}
-
-In the formalization of CCS, it's better to have two distinct
-types for actions: the type \HOLinline{\ensuremath{\beta} \HOLTyOp{Label}} ($\beta$ is a type variable.) for visible actions, divided by input
-and output actions:
-\begin{lstlisting}
-val _ = Datatype `Label = name 'b | coname 'b`;
-\end{lstlisting}
-and the type \HOLinline{\ensuremath{\beta} \HOLTyOp{Action}} as the
-union of all visible and invisible actions. The cardinality of all
-available types depends on the choice of type variable $\beta$.
-
-The core datatype ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'' is then defined as an inductive
-datatype in HOL, based on its Datatype package:
-\begin{lstlisting}
-val _ = Datatype `CCS = nil
-		      | var 'a
-		      | prefix ('b Action) CCS
-		      | sum CCS CCS
-		      | par CCS CCS
-		      | restr (('b Label) set) CCS
-		      | relab CCS ('b Relabeling)
-		      | rec 'a CCS`;
-\end{lstlisting}
-
-We have added some minimal grammar support using HOL's powerful pretty printer, to represent CCS
-processes in more readable forms. Table \ref{tab:ccsoperator} has listed the notation of typical CCS processes and
-major operators supported by above definition. (Notice the use of
-recursition operator for representing process constants)
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Operator} & \textbf{Notation} & \textbf{HOL term} & \textbf{HOL
-  (alternative)}\\
-\hline
-nil & $\textbf{0}$ &  \HOLinline{\HOLConst{nil}} & \HOLinline{\HOLConst{nil}} \\
-Prefix & $a.b.0$ & \texttt{prefix a (prefix b nil)} & \HOLinline{\HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{b}\HOLSymConst{..}\HOLConst{nil}} \\
-Sum & $p + q$ & \texttt{sum p q} & \HOLinline{\HOLFreeVar{p} \HOLSymConst{+} \HOLFreeVar{q}} \\
-Parallel & $p \,\mid\, q$ & \texttt{par p q} & \HOLinline{\HOLFreeVar{p} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{q}} \\
-Restriction & $(\nu\;L)\;p$ & \texttt{restr L p} & \HOLinline{\HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{p}} \\
-Constant & $A=a.A$ & \texttt{rec A (prefix a (var A))} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} (\HOLFreeVar{a}\HOLSymConst{..}\HOLConst{var} \HOLFreeVar{A})} \\
-\hline
-\end{tabular}
-\end{center}
-\vspace{-1em}
-   \caption{Syntax of CCS operators}
-   \label{tab:ccsoperator}
-\end{table}
-
-The transition semantics of CCS processes were defined by the following
-Structural Operational Semantics (SOS for short) rules in
-Fig.\;\ref{f:LTSCCS}, except that the transition rule for constants
-has been changed to recursion operator:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{E} (\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}) \HOLFreeVar{X} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}
-\end{alltt}
-which says, if we substitute all appearences of constant $X$ in $E$ to
-$(\mathbf{rec}\; X\; E)$ and the resulting process has a transition to $E_1$
-with action $u$, then $(\mathbf{rec}\; X\; E)$ has the same
-transition. Other SOS rules have the following forms:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E}\hfill\texttt{[PREFIX]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{+} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[SUM1]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{+} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[SUM2]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sp{\prime}}\hfill\texttt{[PAR1]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[PAR2]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} (\HOLConst{COMPL} \HOLFreeVar{l})\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
-   \HOLFreeVar{E} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sb{\mathrm{2}}}\hfill\texttt{[PAR3]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} ((\HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}}) \HOLSymConst{\HOLTokenDisj{}} (\HOLFreeVar{u} \HOLSymConst{=} \HOLConst{label} \HOLFreeVar{l}) \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{E\sp{\prime}}\hfill\texttt{[RESTR]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{rf}\hfill\texttt{[RELABELING]}
-\end{alltt}
-Above rules work as \emph{axioms} in the theory of CCS, as they cannot be
-proved by more primitive theorems or axioms. From the view of theorem prover, these
-SOS rules are nothing but an \emph{inductive 
-  definition} on 3-ary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL4's function
-\texttt{Hol_reln}.\footnote{On the other side, above literal SOS rules are not
-the \emph{only} thing we got from \texttt{Hol_reln}, which also
-returns the fix-point theorem and induction principle for the
-relation, otherwise things like ``$\textbf{0}$ has no transition''
-cannot be proved at all.} The ultimate result here (before
-bisimilution gets involved), is an ML function taking a CCS process
-and returning a theorem indicating all its direct transitions.
-
-For instance, we know that the process $(a.0 | \bar{a}.0)$ have three
-possible transitions:
-\begin{enumerate}
-\item $(a.0 | \bar{a}.0) \overset{a}{\longrightarrow} (0 | \bar{a}.0)$;
-\item $(a.0 | \bar{a}.0) \overset{\bar{a}}{\longrightarrow} (a.0 | 0)$;
-\item $(a.0 | \bar{a}.0) \overset{\tau}{\longrightarrow} (0 | 0)$.
-\end{enumerate}
-To completely decide all possible transitions, if done manually, the
-following results must be proved:
-\begin{enumerate}
-\item there exists transitions from $(a.0 | \bar{a}.0)$ (optionally);
-\item each of above three transitions using SOS inference rules;
-\item there's no other transition beside the three existing ones.
-\end{enumerate}
-For large complex processes it's surprising hard to prove the
-non-existence of transitions. Instead, if we call the function \texttt{CCS\_TRANS\_CONV} with the
-root process:
-\begin{lstlisting}
-> CCS_TRANS_CONV
-	 ``par (prefix (label (name "a")) nil)
-	       (prefix (label (coname "a")) nil)``
-\end{lstlisting}
-we get the following theorem, which completely answers the question:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{In} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}}
-   ((\HOLFreeVar{u} \HOLSymConst{=} \HOLConst{In} \HOLStringLit{a}) \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil}) \HOLSymConst{\HOLTokenDisj{}}
-    (\HOLFreeVar{u} \HOLSymConst{=} \HOLConst{Out} \HOLStringLit{a}) \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{In} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil})) \HOLSymConst{\HOLTokenDisj{}}
-   (\HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}}) \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil})
-\end{alltt}
-
 \subsection{Bisimulation and Bisimilarity}

### 2018-06-12 express2018/sos.tex
text

@@
 
-In the formalization of CCS, it's better to have two distinct
-types for actions: the type \HOLinline{\ensuremath{\beta} \HOLTyOp{Label}} ($\beta$ is a type variable.) for visible actions, divided by input
+In the formalization of CCS, 
+the type \HOLinline{\ensuremath{\beta} \HOLTyOp{Label}} ($\beta$ is a
+type variable) accounts for visible actions, divided into input
 and output actions:
@@
 \end{lstlisting}
-and the type \HOLinline{\ensuremath{\beta} \HOLTyOp{Action}} as the
-union of all visible and invisible actions. The cardinality of all
-available types depends on the choice of type variable $\beta$.
+Then
+the type \HOLinline{\ensuremath{\beta} \HOLTyOp{Action}} is the
+union of all visible and invisible actions. The cardinality of
+\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}} (and therefore of all
+CCS types built on top of it) 
+ depends on the choice of initial  type $\beta$.
+\finish{i have reformulated the sentence above; check it}
 
-The core datatype ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'' is then defined as an inductive
+The core datatype ``\HOLinline{(\ensuremath{\alpha},
+  \ensuremath{\beta}) \HOLTyOp{CCS}}'', accounting for the CCS syntax,  is then defined as an inductive
 datatype in HOL, based on its Datatype package:
+\finish{above: check the change i made. Also, explain what is $\alpha
+  $ (i suppose the set of  variables for recursion)} 
 \begin{lstlisting}
@@
 
-We have added some minimal grammar support using HOL's powerful pretty printer, to represent CCS
+We have added some  grammar support using HOL's powerful pretty printer, to represent CCS
 processes in more readable forms. Table \ref{tab:ccsoperator} has listed the notation of typical CCS processes and
-major operators supported by above definition. (Notice the use of
-recursition operator for representing process constants)
+major operators supported by above definition.
+
+\finish{explain what is ``HOL   (alternative)''. 
+Also: the table gives the impression that all recursion are guarded,
+ie, the body of the recursion begins with a prefix. I would instead
+put in the table the plain recursion rec A.P. Also, in the row for
+prefix, i would write plain prefix u.P}
+\finish{explain why restriction takes a set of names, rather than a
+  single name as in the  CCS syntax}
+
+%  (Notice the use of
+% recursition operator for representing process constants)
 \begin{table}[h]
@@
 \hline
-\textbf{Operator} & \textbf{Notation} & \textbf{HOL term} & \textbf{HOL
+\textbf{Operator} & \textbf{CCS Notation} & \textbf{HOL term} & \textbf{HOL
   (alternative)}\\
@@
 Restriction & $(\nu\;L)\;p$ & \texttt{restr L p} & \HOLinline{\HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{p}} \\
-Constant & $A=a.A$ & \texttt{rec A (prefix a (var A))} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} (\HOLFreeVar{a}\HOLSymConst{..}\HOLConst{var} \HOLFreeVar{A})} \\
+Recursion & $A=a.A$ & \texttt{rec A (prefix a (var A))} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} (\HOLFreeVar{a}\HOLSymConst{..}\HOLConst{var} \HOLFreeVar{A})} \\
 \hline
@@
 
-The transition semantics of CCS processes were defined by the following
-Structural Operational Semantics (SOS for short) rules in
-Fig.\;\ref{f:LTSCCS}, except that the transition rule for constants
-has been changed to recursion operator:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{E} (\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}) \HOLFreeVar{X} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}
-\end{alltt}
-which says, if we substitute all appearences of constant $X$ in $E$ to
-$(\mathbf{rec}\; X\; E)$ and the resulting process has a transition to $E_1$
-with action $u$, then $(\mathbf{rec}\; X\; E)$ has the same
-transition. Other SOS rules have the following forms:
+The transition semantics of CCS processes  follows
+the Structural Operational Semantics (SOS) rules in
+Figure~\ref{f:LTSCCS}:
 \begin{alltt}
@@
 \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{rf}\hfill\texttt{[RELABELING]}
+\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{E} (\HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{E}) \HOLFreeVar{A} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}
+\texttt{[RECURSION]}
 \end{alltt}
-Above rules work as \emph{axioms} in the theory of CCS, as they cannot be
-proved by more primitive theorems or axioms. From the view of theorem prover, these
-SOS rules are nothing but an \emph{inductive 
-  definition} on 3-ary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL4's function
-\texttt{Hol_reln}.\footnote{On the other side, above literal SOS rules are not
-the \emph{only} thing we got from \texttt{Hol_reln}, which also
-returns the fix-point theorem and induction principle for the
-relation, otherwise things like ``$\textbf{0}$ has no transition''
-cannot be proved at all.} The ultimate result here (before
-bisimilution gets involved), is an ML function taking a CCS process
+The rule 
+\texttt{[RECURSION]
+ says that if we substitute all appearences of variable $A$ in $E$ to
+$(\mathbf{rec}\; A\; E)$ and the resulting process has a transition to $E_1$
+with action $u$, then $(\mathbf{rec}\; A\; E)$ has the same
+transition.
+
+% Above rules work as \emph{axioms} in the theory of CCS, as they cannot be
+% proved by more primitive theorems or axioms.
+
+From the HOL  viewpoint, these
+SOS rules are \emph{inductive 
+  definitions} on the 3-ary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL4's function
+\texttt{Hol_reln}.\footnote{\texttt{Hol_reln} also
+gives us a fix-point theorem and induction principle for the
+relation, otherwise statements like ``$\textbf{0}$ has no transition''
+could not be proved.}
+
+\finish{the text below is important but there are various things that
+  are not clear: where does ML come from (we have not talked about ML
+  before and for a non-expert in HOL this is a mystery)? did you have
+  to define it? was it difficult or is there some HOL facility that helps? }
+
+The ultimate result here (before
+bisimilution gets involved), is an ML function
+\finish{is this the function \texttt{CCS\_TRANS\_CONV}}  mentioned
+later below? }
+  taking a CCS process
 and returning a theorem indicating all its direct transitions.

### 2018-06-12 express2018/sos.tex
text

@@
 \end{alltt}
+\finish{adjust last line above}
+
 The rule 
-\texttt{[RECURSION]
+\texttt{[RECURSION]}
  says that if we substitute all appearences of variable $A$ in $E$ to
@@
 bisimilution gets involved), is an ML function
-\finish{is this the function \texttt{CCS\_TRANS\_CONV}}  mentioned
+\finish{is this the function \texttt{CCS\_TRANS\_CONV}  mentioned
 later below? }

### 2018-06-12 express2018/part2.tex
text

@@
-\subsection{Bisimulation and Bisimilarity}
-
-It's well known that, bisimilarity is a coinductive
-relation. Historically, it can be defined in HOL without any special
-support, but now using HOL's
-coinductive relation module (\texttt{Hol_coreln}), it's much easier to
-get the equivalent definition with minimal efforts.
-
-First of all, we define the zero or more $\tau$-transition chains of
-CCS processes as a new relation called \texttt{EPS} ($\epsilon$),
-which is the RTC (reflexive transitive closure) of single-step $\tau$-transition:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{EPS} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-\HOLBoundVar{E} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}})\HOLSymConst{\HOLTokenSupStar{}}\hfill{[EPS_def]}
-\end{alltt}
-Then we can define weak transition as a normal transition wrapped by
-two $\epsilon$-transitions:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLFreeVar{E} \HOLSymConst{\HOLTokenEPS} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenEPS} \HOLFreeVar{E\sp{\prime}}\hfill{[WEAK_TRANS]}
-\end{alltt}
-Now we're ready to present the formalized version of (weak)
-bisimulation relation as a predicate \texttt{WEAK_BISIM}:
-\begin{definition}{(Weak bisimulation)}
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{WEAK_BISIM} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenEquiv{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-       \HOLFreeVar{Wbsm} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l}.
-            (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-                 \HOLBoundVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}}
-                 \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLBoundVar{E\sp{\prime}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-                \HOLBoundVar{E\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
-                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLBoundVar{E} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenEPS} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLBoundVar{E\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLBoundVar{E} \HOLSymConst{\HOLTokenEPS} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}\hfill{[WEAK_BISIM]}
-\end{alltt}
-\end{definition}
-
-There're two ways to define weak bisimulation equivalence in HOL4, one
-is to define it as the union of all weak bisimulations:
-\begin{definition}{(Alternative definition of weak equivalence)}
-For any two CCS processes $E$ and $E'$, they're \emph{weak
-  bisimulation equivalent} (or weak bisimilar) if and only if there's
-a weak bisimulation relation between $E$ and $E'$:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{Wbsm}.
-\HOLBoundVar{Wbsm} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WEAK_BISIM} \HOLBoundVar{Wbsm}\hfill{[WEAK_EQUIV]}
-\end{alltt}
-\end{definition}
-This was the definition used by Monica Nesi in Hol88 in which there was no
-direct support for defining co-inductive relations.  The new method we
-have used in this project, is to use HOL4's new co-inductive relation
-defining facility \texttt{Hol_coreln} to define weak bisimulation
-equivalence:
-\begin{lstlisting}
-val (WEAK_EQUIV_rules, WEAK_EQUIV_coind, WEAK_EQUIV_cases)
-  = Hol_coreln `
-    (!(E :('a, 'b) CCS) (E' :('a, 'b) CCS).
-       (!l.
-	 (!E1. TRANS E  (label l) E1 ==>
-	       (?E2. WEAK_TRANS E' (label l) E2 /\
-                 WEAK_EQUIV E1 E2)) /\
-	 (!E2. TRANS E' (label l) E2 ==>
-	       (?E1. WEAK_TRANS E  (label l) E1 /\
-                 WEAK_EQUIV E1 E2))) /\
-       (!E1. TRANS E  tau E1 ==>
-                 (?E2. EPS E' E2 /\ WEAK_EQUIV E1 E2)) /\
-       (!E2. TRANS E' tau E2 ==>
-                 (?E1. EPS E  E1 /\ WEAK_EQUIV E1 E2))
-      ==> WEAK_EQUIV E E')`;
-\end{lstlisting}
-The fixpoint theorem (\texttt{WEAK_EQUIV_cases}) returned by above
-\texttt{Hol_coreln} call, also named ``the property (*)'' \cite{Mil89}:
-\begin{proposition}{(The property (*) for weak bisimulation
-    equivalence)}
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{a\sb{\mathrm{0}}} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{a\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenEquiv{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l}.
-        (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLFreeVar{a\sb{\mathrm{0}}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLFreeVar{a\sb{\mathrm{1}}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLFreeVar{a\sb{\mathrm{1}}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLFreeVar{a\sb{\mathrm{0}}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLFreeVar{a\sb{\mathrm{0}}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLFreeVar{a\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenEPS} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLFreeVar{a\sb{\mathrm{1}}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLFreeVar{a\sb{\mathrm{0}}} \HOLSymConst{\HOLTokenEPS} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{E\sb{\mathrm{2}}}\hfill{[WEAK_PROPERTY_STAR]}
-\end{alltt}
-\end{proposition}
-It is widely used in proving many results regarding bisimilarities. The
-old way for proving this fundamental theorem is quite hard but now
-it's a natural consequence of co-inductive relation definitions.
-
 \subsection{Coarsest (pre)congruence contained in $\approx$ (or $\succeq_{\mathrm{bis}}$)}

### 2018-06-12 express2018/formal.tex
text
Fixed formal.tex and sos.tex (releasing locks on my side)

@@
 %  in the informal proofs. 
-The whole formalisation can be found 
+The whole formalization can be found 
 in \cite{Tian:2017wrba}  or in 
  in the official example folder of HOL4 source
-code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}.
-\finish{i would say here how big is the formalisation, ie how many
-  lines of code} 
+code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}. The
+work consists of about 20,000 lines of proof scripts in Standard ML.
 %  This
@@
 choice operator, axiom of infinity, and rank-1 polymorphim (type
-variables). HOL4 implemented this logic without any extension, in
-contrast
-with
-some other theorem provers of the  HOL family (e.g. Isabelle/HOL). 
-\finish{not having extensions above: sounds like a defect; what is the
-advantage? the portability explained in the next sentence?} 
+variables). HOL4 implemented the original HOL Logic, while
+some other theorem provers of the HOL family (e.g. Isabelle/HOL) added
+further extensions (they made the formal language more powerful,
+but they also bring the possibilities that the entire logic becomes inconsistent).
 The HOL Logic has considerability simpler logic
@@
 
-\finish{below: to be reformulated} 
+\finish{below: to be reformulated (by Davide) later} 
 We will not repeat all definitions and theorems of CCS again by their
@@
 In contrast with the theorems in the first part of the paper, in the
-formalisation we consider only single equations/contractions. 
+formalization we consider only single equations/contractions. 
 This considerably simplifies the  reading of the HOL scripts. 
 The extension of the work to multiple equations/contractions is
-discussed in Section~\ref{s:}.
+discussed in Section~\ref{s:}. \finish{to be finished}
 

### 2018-06-12 express2018/sos.tex
Fixed formal.tex and sos.tex (releasing locks on my side)

--- 2018-06-12 express2018/sos.tex
@@
 
-In the formalization of CCS, it's better to have two distinct
-types for actions: the type \HOLinline{\ensuremath{\beta} \HOLTyOp{Label}} ($\beta$ is a type variable.) for visible actions, divided by input
+In the formalization of CCS, 
+the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' ($\beta$ is a
+type variable) accounts for visible actions, divided into input
 and output actions:
@@
 \end{lstlisting}
-and the type \HOLinline{\ensuremath{\beta} \HOLTyOp{Action}} as the
-union of all visible and invisible actions. The cardinality of all
-available types depends on the choice of type variable $\beta$.
+Then
+the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
+union of all visible and invisible actions. The cardinality of
+``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' (and therefore of all
+CCS types built on top of it) 
+ depends on the choice of initial  type $\beta$.
 
-The core datatype ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'' is then defined as an inductive
-datatype in HOL, based on its Datatype package:
+The core datatype ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'', accounting for the CCS syntax, is then defined as an inductive
+datatype in HOL, based on its Datatype package: ($\alpha$ is the type
+variable for recursion variables) 
 \begin{lstlisting}
@@
 
-We have added some minimal grammar support using HOL's powerful pretty printer, to represent CCS
-processes in more readable forms. Table \ref{tab:ccsoperator} has listed the notation of typical CCS processes and
-major operators supported by above definition. (Notice the use of
-recursition operator for representing process constants)
+We have added some  grammar support using HOL's powerful pretty printer, to represent CCS
+processes in more readable forms (as shown in the ``HOL (abbrev.)''
+column in Table \ref{tab:ccsoperator}, the rest of table has listed the notation of typical CCS processes and
+major operators supported by above definition). For restriction
+operator, we chose to takes a set of names, rather than a
+  single name as in the  CCS syntax, to prevent the formalization
+  efforts on the equivalence of CCS processes with different order of
+  nested restrictions. Also, we don't assume that al recursion are
+  guarded, i.e. any term like \texttt{var X} must appear in \texttt{P} of \texttt{rec X P}.
+
+%  (Notice the use of
+% recursition operator for representing process constants)
 \begin{table}[h]
@@
 \hline
-\textbf{Operator} & \textbf{Notation} & \textbf{HOL term} & \textbf{HOL
-  (alternative)}\\
+\textbf{Operator} & \textbf{CCS Notation} & \textbf{HOL term} &
+                                                                \textbf{HOL (abbrev.)}\\
 \hline
 nil & $\textbf{0}$ & \HOLinline{\HOLConst{nil}} & \HOLinline{\HOLConst{nil}} \\
-Prefix & $a.b.0$ & \texttt{prefix a (prefix b nil)} & \HOLinline{\HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{b}\HOLSymConst{..}\HOLConst{nil}} \\
-Sum & $p + q$ & \texttt{sum p q} & \HOLinline{\HOLFreeVar{p} \HOLSymConst{+} \HOLFreeVar{q}} \\
-Parallel & $p \,\mid\, q$ & \texttt{par p q} & \HOLinline{\HOLFreeVar{p} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{q}} \\
-Restriction & $(\nu\;L)\;p$ & \texttt{restr L p} & \HOLinline{\HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{p}} \\
-Constant & $A=a.A$ & \texttt{rec A (prefix a (var A))} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} (\HOLFreeVar{a}\HOLSymConst{..}\HOLConst{var} \HOLFreeVar{A})} \\
+prefix & $u.P$ & \texttt{prefix u P} & \HOLinline{\HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{P}} \\
+sum & $P + Q$ & \texttt{sum P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{+} \HOLFreeVar{Q}} \\
+parallel & $P \,\mid\, Q$ & \texttt{par P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q}} \\
+restriction & $(\nu\;L)\;P$ & \texttt{restr L P} & \HOLinline{\HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{P}}
+  \\
+recursion & $A$ with $A\Defi P$ & \texttt{rec A P} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P}} \\
+input action & $a$ & \texttt{label (name a)} & \HOLinline{\HOLConst{In} \HOLFreeVar{a}} \\
+output action & $\outC a$ & \texttt{label (coname a)} & \HOLinline{\HOLConst{Out} \HOLFreeVar{a}} \\
 \hline
@@
 \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{rf}\hfill\texttt{[RELABELING]}
+\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{E} (\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}) \HOLFreeVar{X} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[REC]}
 \end{alltt}
-Above rules work as \emph{axioms} in the theory of CCS, as they cannot be
-proved by more primitive theorems or axioms. From the view of theorem prover, these
-SOS rules are nothing but an \emph{inductive 
-  definition} on 3-ary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL4's function
-\texttt{Hol_reln}.\footnote{On the other side, above literal SOS rules are not
-the \emph{only} thing we got from \texttt{Hol_reln}, which also
-returns the fix-point theorem and induction principle for the
-relation, otherwise things like ``$\textbf{0}$ has no transition''
-cannot be proved at all.} The ultimate result here (before
-bisimilution gets involved), is an ML function taking a CCS process
-and returning a theorem indicating all its direct transitions.
+
+Here the rule \texttt{[REC]} (Recursion)
+ says that if we substitute all appearences of variable $A$ in $E$ to
+$(\mathbf{rec}\; A\; E)$ and the resulting process has a transition to $E_1$
+with action $u$, then $(\mathbf{rec}\; A\; E)$ has the same
+transition. From the HOL  viewpoint, these
+SOS rules are \emph{inductive 
+  definitions} on the 3-ary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL4's
+\texttt{Hol_reln} function.\footnote{\texttt{Hol_reln} also
+gives us a fix-point theorem and induction principle for the
+relation, otherwise statements like ``$\textbf{0}$ has no transition''
+could not be proved.}
+
+HOL4 is written in Standard ML (or ML for abbreviation). This single language plays three roles here:
+\begin{enumerate}
+\item It serves as the underlying implementation language for the core HOL engine;
+\item It's used to implement tactics (and tacticals) for automatic theorem proving;
+\item It's used as the command language of the interactive HOL system.
+\end{enumerate}
+Besides, HOL4 users can write arbitrary applications which leverages
+the theorem proving facility. The ultimate result (initially done by Nesi)
+at this point, is a complex Standard ML function
+  taking a CCS process and returning a theorem indicating all its direct transitions.
 
 For instance, we know that the process $(a.0 | \bar{a}.0)$ have three
-possible transitions:
+possible transitions: $(a.0 | \bar{a}.0) \overset{a}{\longrightarrow}
+(0 | \bar{a}.0)$, $(a.0 | \bar{a}.0)
+\overset{\bar{a}}{\longrightarrow} (a.0 | 0)$ and $(a.0 | \bar{a}.0)
+\overset{\tau}{\longrightarrow} (0 | 0)$.
+To completely decide all possible transitions, if done manually, the
+following facts should be proved:
 \begin{enumerate}
-\item $(a.0 | \bar{a}.0) \overset{a}{\longrightarrow} (0 | \bar{a}.0)$;
-\item $(a.0 | \bar{a}.0) \overset{\bar{a}}{\longrightarrow} (a.0 | 0)$;
-\item $(a.0 | \bar{a}.0) \overset{\tau}{\longrightarrow} (0 | 0)$.
-\end{enumerate}
-To completely decide all possible transitions, if done manually, the
-following results must be proved:
-\begin{enumerate}
-\item there exists transitions from $(a.0 | \bar{a}.0)$ (optionally);
-\item each of above three transitions using SOS inference rules;
+\item there exists transitions from $(a.0 | \bar{a}.0)$ (optional);
+\item the correctness for each of the transitions by SOS rules;
 \item there's no other transition beside the three existing ones.
 \end{enumerate}
-For large complex processes it's surprising hard to prove the
-non-existence of transitions. Instead, if we call the function \texttt{CCS\_TRANS\_CONV} with the
-root process:
+For large complex processes it's surprisingly hard to manually prove the
+non-existence of transitions. Instead, if we call the ML function \texttt{CCS\_TRANS\_CONV} on the
+root process $(a.0 | \bar{a}.0)$:
 \begin{lstlisting}
@@
 \end{lstlisting}
-we get the following theorem, which completely answers the question:
+We immediately get the following theorem, which completely answers the question:
 \begin{alltt}

### 2018-06-12 express2018/unique.tex
I have to use labels without hypen and underscore (don't know why) to prevent strange LaTeX compilation errors.

@@
 \begin{definition}
-\label{d:uni_contra}
+\label{d:uniContra}
 Given a  system of contractions 
@@
 \begin{theorem}[unique solution of contractions for $\wb$]
-\label{t:contra_bisimulation_u}
+\label{t:contraBisimulationU}
 A system of weakly-guarded contractions
@@
 \begin{theorem}
-\label{t:rcontr-precongruence}
+\label{t:rcontrPrecongruence}
 Relation $\rcontr$ is a precongruence in CCS. 

### 2018-06-12 express2018/part2.tex
text

@@
-\subsection{Coarsest (pre)congruence contained in $\approx$ (or $\succeq_{\mathrm{bis}}$)}
-
-The ``coarsest congruence contained in weak bisimilarity ($\approx$)''
-theorem in CCS is somehow special, as its current known proofs either
-rely on quite restricted conditions, or have an extremely complicated proof
-(c.f. van Glabbek's paper) in
-which ordinal theory is required.  Actually even the relationship
-between its name and statement is not well explained in many CCS
-textbooks. But van Glabbek's paper has given the so far clearest
-explainion, here we briefly repeat his arguments:
-
-As we know weak bisimilarity ($\approx$) is not (real) congruence, as
-it doesn't satisfy subsitutivity on direct sums (but if the CCS syntax
-is non-standard, i.e. has only prefixed sums, $\approx$ is indeed a
-congruence). The purpose is to find a coarsest congruence contained in
-weak bisimilarity. (``coarsest'' means, any other congruence finer than it must be contained in it)
-There're two ways to build a congruence from weak bisimilarity, one
-way is the standard definition for observational congruence (rooted
-weak bisimilarity) $\approx^c$ in CCS textbooks, but even it's proven to be a
-congruence we don't know if it's coarsest one.  The other way is to
-build a (pre)congruence closure (Def ??) directly upon
-the original weak bisimilarity relation, we call the resulting
-relation ``Weak bisimilarity congruence'' ($[\approx]$):
-\begin{alltt}
-\HOLConst{WEAK_CONGR} \HOLSymConst{=} \HOLConst{CC} \HOLConst{WEAK_EQUIV}
-\HOLConst{CC} \HOLFreeVar{R} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}.
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}.
-\HOLConst{CONTEXT} \HOLBoundVar{c} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{c} \HOLBoundVar{g}) (\HOLBoundVar{c} \HOLBoundVar{h}))
-\end{alltt}
-It can be shown that any such (pre)congruence closure is automatically coarset.
-
-Now it remains to prove that, the congrunce relation built by above
-two quite different approaches actually coincide. To achive this goal,
-we first noticed that, all other operators beside sums used in
-semantic context doesn't matter, because they're already substituible
-for weak bisimilarity. The only important operator is the sum
-operator. To focus on this important operator, we can temporily
-introduce another concept called \emph{sum equivalence}:
-\begin{alltt}
-\HOLConst{SUM_EQUIV} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}.
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLBoundVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{+} \HOLBoundVar{r})
-\end{alltt}
-It can be shown that, weak bisimilarity congruence implies this sum
-equivalence. Thus if we can further prove that the sum
-equivalence imples observational congrence, all the three relations
-must coincide together, as shown in the following diagram:
-\begin{displaymath}
-\xymatrix{
-{\textrm{Weak bisimilarity } (\approx)} & {\textrm{Sum
-    equivalence } (\approx^+)} \ar@/^3ex/[ldd]^{\subseteq ?}\\
-{\textrm{Weak bisim. congruence } ([\approx])}
-\ar[u]^{\subseteq} \ar[ru]^{\subseteq} \\
-{\textrm{Rooted bisimilarity } (\approx^c)} \ar[u]^{\subseteq}
-}
-\end{displaymath}
-In another words, observational congruence is the coarsest congruence
-contained in weak bisimilary if and only if
-\begin{equation}
-\forall p\; q.\; p \approx^c\! q \Longleftrightarrow \forall r.\; p+r \approx
-q+r
-\end{equation}
-
-The classical assumption for proving above theorem requires that $p$
-and $q$ do not use up all available visible actions,
-i.e. $\mathrm{fn}(p) \cup \mathrm{fn}(q) \neq \mathscr{L}$. But it's
-not easy to formalize and use such an assumption without a detailed
-treatment on free and bound names (visible actions) of CCS
-processes.\footnote{There're totally four such concepts: 1) free names
-are all visible actions appearing in a CCS term without surrounding
-$\nu$ (restriction) operator on the same action; 2) bound names are
-the set of all actions ever used by $\nu$ (restriction) operator; 3)
-free variables (or equation variables) are those variables without a
-definition given by recursion
-operator; 4) bound variables (process constants) are variables with
-definitions given by recursion operator. All CCS results using these
-concepts are not touched so far, although these four concepts are
-successfully defined using HOL's set and list theories.} However, by
-analyzing the proof steps, we found that, what's really required is to
-not use up all available labels in those weak transitions directly
-lead from $p$ and $q$. In another words, even they have used all
-available labels, as long as their first weak transitions didn't, the
-whole proof can still be finished.\footnote{Further more, $p$ and $q$
-  can be considered separately: the proof can be finished as long as
-  \emph{each} of them didn't use up all labels on first weak
-  transition, while the union of these labels are all labels.}
-We have formalized this property of
-CCS process and call it ``free action'' property:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{a}.
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}}.
-\HOLSymConst{\HOLTokenNeg{}}(\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{a}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}})
-\end{alltt}
-With this property, the classical form of this theorem that we have
-formally proved is:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
-   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r})
-\end{alltt}
-
-If we drop this classical assumption, then the proof becomes much
-harder, as given a van Glabbek's paper. The most important
-intermediate result we have proved here, is the following lemma:
-\begin{alltt}
-\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
-        \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}} \HOLBoundVar{u}.
-\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenConj{}}
-        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{q\sp{\prime}} \HOLBoundVar{u}.
-\HOLFreeVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenImp{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r}) \HOLSymConst{\HOLTokenImp{}}
-   \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q}
-\end{alltt}
-It roughly says, for any two processes $p$ and $q$, if we can find
-another stable (no $\tau$-transitions) process $k$ which is not weak bisimilar to any transition of
-$p$ and $q$, then the hard part of our main theorem is proved. In
-practice, once two processes were given, it's not hard to find
-such a process, but the arbitrariness of $p$ and $q$ made this result
-extremely hard to prove. The method given by van Glabbek requires a
-construction of arbitrarily non-bisimilar processes called ``Klop
-processes'':
-\begin{definition}{(Klop processes)}
-For each ordinal $\lambda$, and an arbitrary chosen non-$\tau$ action $a$,
-define a CCS process $k_\lambda$ as follows:
-\begin{enumerate}
-\item $k_0 = 0$,
-\item $k_{\lambda+1} = k_\lambda + a.k_\lambda$ and
-\item for $\lambda$ a limit ordinal, $k_\lambda = \sum_{\mu < \lambda}
-  k_\mu$, meaning that $k_\lambda$ is constructed from all graphs
-  $k_\mu$ for $\mu < \lambda$ by identifying their root.
-\end{enumerate}
-\end{definition}
-It's not hard to prove that, all $k_i$ are non-bisimilar (not only
-weakly but also strongly). The idea is, for any two processes, the union of sets of their all
-transitions cannot be arbitrarily large: it has to be limited by an
-ordinal number. But above contruction can be arbitrarily large, so
-there always exists a Klop process which can be used to satisfy above
-lemma (and finish the proof).
-
-However, this goes beyond HOL's expressivity to define above process, mostly
-because there's no way to express infinite ``sums'' in CCS
-datatype.\footnote{There're actually several ways to modify the
-  datatype to support infinite sums, but none of these infinity can be
-arbitrary. The full version of ordinal theory cannot be expressed in HOL.}
-What we can do is to eliminate the last branch with limiting
-ordinals, and define Klop processes only on finite cases:
-\begin{alltt}
-\HOLConst{KLOP} \HOLFreeVar{a} \HOLNumLit{0} \HOLSymConst{=} \HOLConst{nil}
-\HOLConst{KLOP} \HOLFreeVar{a} (\HOLConst{SUC} \HOLFreeVar{n}) \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLSymConst{+} \HOLConst{label} \HOLFreeVar{a}\HOLSymConst{..}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\hfill[KLOP_def]
-\end{alltt}
-But this means we much assume the two processes $p$ and $q$ are
-finite-state, i.e. their corresponding LTS graphs have only finite
-states. Choosing an element from a countable infinite set of processes
-to make sure it's not bisimiar with a given set of processes, this is
-essentially a pure set-theoretic problem, as formalized and proved in
-the following lemma:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenImp{}}
-   \HOLConst{FINITE} \HOLFreeVar{A} \HOLSymConst{\HOLTokenConj{}} \HOLConst{INFINITE} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y}.
-\HOLBoundVar{x} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{x} \HOLSymConst{\HOLTokenNotEqual{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y}) \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
-\HOLBoundVar{k} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n}.
-\HOLBoundVar{n} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{A} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{n} \HOLBoundVar{k}
-\end{alltt}
-
-With all these results, finally we can prove the ``coarsest congruence
-contained in $\approx$'' theorem for finite-state CCS:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
-   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r})
-\end{alltt}
-
-For contraction and rooted contraction, the situation (and proof
-steps) is exactly the same:
-\begin{displaymath}
-\xymatrix{
-{\textrm{Contraction } (\succeq_{\mathrm{bis}})} & {\textrm{Sum
-    contraction } (\succeq_{\mathrm{bis}}^+)} \ar@/^3ex/[ldd]^{\subseteq ?}\\
-{\textrm{Contraction precongruence } ([\succeq_{\mathrm{bis}}])}
-\ar[u]^{\subseteq} \ar[ru]^{\subseteq} \\
-{\textrm{Rooted contraction } (\succeq_{\mathrm{bis}}^c)} \ar[u]^{\subseteq}
-}
-\end{displaymath}
-
-And we got two versions of theorem saying rooted contraction is the
-coarsest precongruence of (bisimilarity) contraction:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
-   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r})
-\HOLTokenTurnstile{} \HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
-   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{+} \HOLBoundVar{r} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{q} \HOLSymConst{+} \HOLBoundVar{r})
-\end{alltt}
-
 \subsection{Semantic context, guardness and (pre)congruence}

### 2018-06-12 express2018/conclusions.tex
text

@@
+\section{To do}
+
+\finish{explain that also up-to techniques for bisimilarity have been
+  formalised, including those making use of expansion. 
+Point out that an advantage of the formalisation is 
+that we can take advantage of results about different 
+equivalences/preorders that have similar proofs, even if the proofs
+themselves can be tedious and long. Examples are: ....
+There are only a few points in which the scripts have to be modified,
+and when the execution of the scripts succesfully terminate we have
+the guarantee that the proof is completed. Without theorem provers,
+the risk of overlooking or missing  small but important details is
+high. 
+} 
 \section{Conclusions}

### 2018-06-12 express2018/part2.tex
text

@@
-\subsection{Semantic context, guardness and (pre)congruence}
-
-We need to find a suitable formal definition of semantic
-context. There're multiple ways. Here we have chosen to use $\lambda$-expressions (typed
-$CCS\rightarrow CCS$) to represent a (multi-hole) semantic
-context. The definition is inductive:
-\begin{alltt}
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})
-\end{alltt}
-
-Under above definition, we can formally define the concept of
-``precongruence'' and ``congruence'' in the following ways:
-\begin{alltt}
-\HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
-\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})
-\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLConst{precongruence} \HOLFreeVar{R}
-\end{alltt}
-
-A \emph{weak guarded} context is a context in which all holes appears
-in the sub-expression of prefixed processes. We can easily define it
-following the same idea:
-\begin{alltt}
-\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})
-\end{alltt}
-(Notice the differences between a weak guarded context and a normal
-one: $\lambda t. t$ is not weakly guarded as the variable is directly
-exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
-guarded as long as $e[\cdot]$ is a semantic context, no necessary weakly guaded.)
-
-It's a similar process to define strongly guarded context
-(\texttt{SG}), sequential context (\texttt{SEQ}) and their
-variants without direct sums (\texttt{GCONTEXT}, \texttt{WGS},
-\texttt{GSEQ}). Some lemmas about their relationships have very long
-(but trivial) formal proofs due to the combinatorial explosion of
-inductions on their structures. For example, one such 
-lemma says, for any semantic context $E$ which is both strongly guarded
-and sequential (no direct sums) and another sequential context $H$ (no
-direct sums), the composition $H \circ E$ is still both strongly
-guarded and sequential (no direct sums):
-\begin{alltt}
-SG_GSEQ_combin:
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{H}.
-\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E})
-\end{alltt}
-
-% \subsection{Milner's ``unique solution of equations'' theorems}
-
-% Once the representation issue of CCS equations is resolved, the actual
-% proofs of Milner's unique solution of equations theorems is not very
-% interesting from the view of theorem proving, although it's a 
-% precise proof engineering work producing quite long proofs.
-% Since we have chosen to use semantic context to represent
-% single-variable equations, an equation like $P \sim E\{P/X\}$ now
-% becomes $P \sim E[P]$, in which $E$ is a (multi-hole) semantic
-% context, and there's no need to say it ``contains at most the variable
-% $X$'' any more, as equation variable doesn't appear in $E$ at
-% all. Under these simplifications, the formal proof of Milner's unique
-% solution of equations theorem for $\sim$ is a literal mapping for informal
-% proofs based on bisimulation upto $\sim$, induction and case analysis
-% of weakly guarded contexts. Below is the formal version of Lemma 4.13
-% and Proposition 4.14 in Milner's book:
-
-% \begin{alltt}
-% STRONG_UNIQUE_SOLUTION:
-% \HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}
-% \end{alltt}
-
-% \begin{alltt}
-% WEAK_UNIQUE_SOLUTION:
-% \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
-% \end{alltt}
-
-% \begin{alltt}
-% OBS_UNIQUE_SOLUTION:
-% \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
-% \end{alltt}
-
 \subsection{Unique solution of contractions}
 
-The major difficulties in formalizing Sangiorgi's unique solution of
-contractions theorem is to prove its main lemma (c.f. Lemma 3.9 of
-main paper), in which the length of weak transitions are used for
-induction. Introducing a special vesion of weak transition relation
-with length would be an easier choice, but we have chosen to use trace
-instead, so that in the future it's possible to extend the work with
-trace equivalence included.
+The major difficulties in the formalisation of the results about unique solution of
+contractions are in the proof of  Lemma \ref{...}; in particular, it
+uses an induction on the length of weak transitions. 
+For this, one could introduced a refined form of weak transition relation
+enriched with its length; we have however preferred to use 
+traces (one reason is to be able to extend the formalisation in the
+future so to handle also unique solution results for forms of  trace
+equivalence).
+% Introducing a special vesion of weak transition relation
+% with length would be an easier choice, but we have chosen to use trace
+% instead, so that in the future it's possible to extend the work with
+% trace equivalence included.
+
+\finish{since we do not do trace equivalence, the argument above seems
+weak. Are there other reasons?}
+
+We represent a trace by the initial process, the final derivative, and
+the
+list of actions performed. 
+To formalise this, 
+we first introduce 
+the Reflexive Transitive Closure with a
+List (LRTC);
 
@@
 List (LRTC):
+given a  labelled transition relation $R$, \HOLinline{\HOLConst{LRTC}
+  \HOLFreeVar{R}} builds 
+the possible traces derived from $R$.
 \begin{alltt}
@@
 \end{alltt}
-For any labelled translation relation $R$, \HOLinline{\HOLConst{LRTC} \HOLFreeVar{R}} builds a new
-relation accumulating all labels in the middle. Then the trace of CCS processes can be
-defined by simply combining LRTC with the (strong) CCS transition
+ Then the traces for the  CCS processes
+are obtained
+ by combining LRTC with the (strong) CCS transition
 relation:
@@
 \end{alltt}
+\finish{above: what is MEM? has it been explained before?} 
 while the definition of ``unique label'' can be done in many ways, in
@@
 \end{alltt}
+\finish{above: cannot you just use the \HOLConst{NO_LABEL} predicate
+  previously defined?}
+
 It says, a label is unique in an action list iff it there's no other
@@
 and proved in the following lemma:
+
+\finish{below: explain in $us$ what is $s$ } 
 \begin{alltt}
@@
 \end{alltt}
-(A weak transition $E\overset{u}{\rightarrow}E'$ is a trace with non
+(A weak transition $E\overset{u}{\rightarrow}E'$ 
+\finish{above: you mean $E\overset{u}{\Rightarrow}E'$?}  
+is a trace with non
 empty action list: 1) without any visible label, if $u = \tau$, or 2)
@@
 
-To finish the proof of Lemma 3.9 in Sangiorgi's paper, we used above
-lemma to convert weak transitions to traces, which either keep its
-length or become shorter after passing weak bisimilations, then we
-used above lemma again to convert the traces back to weak transitions.
+To finish the proof of Lemma~\ref{l:}, we use the  above
+result to freely switch between weak transitions and traces
+during the induction argument.
+% , which either keep its
+% length or become shorter after passing weak bisimilations, then we
+% used above lemma again to convert the traces back to weak transitions.
 
-The proof of the final unique solution of contractions theorem is just
-a literal transition of its informal proofs: (noticed that the weakly
+The statement of the  final unique solution of contractions theorem is
+the following (a  weakly
 guarded context is the version without direct sums)
+\finish{version of what?} 
 \begin{alltt}

### 2018-06-12 express2018/equa.tex
text

@@
 $\til P$ and $\til X$ have the same length. (This is syntactic
-replacement, akin to the substitution of the holes of a context with 
- processes.) 
-The components of $\til P$ need not be
- different from each other, as it must be for the variables $\til X$.
-If the system has infinitely many equations,
-the  tuples $\til P$ and $\til X$
- are infinite too.
+replacement.) 
+% The components of $\til P$ need not be
+%  different from each other, as it must be for the variables $\til X$.
+% If the system has infinitely many equations,
+% the  tuples $\til P$ and $\til X$
+%  are infinite too.
 \begin{definition}
@@
 
-Examples of systems with a  unique solution for $\wb$ are: 
-\begin{enumerate}
-\item
+% Examples of systems with a  unique solution for $\wb$ are: 
+% \begin{enumerate}
+% \item
+% $ X = a. X$
+
+% \item 
+% $ X_1 = a.  X_2$, $ X_2 = b.  X_1$
+
+% \end{enumerate}
+
+For instance, the solution of the equation 
 $ X = a. X$ 
+is  the process
+$R \defi \recu A . a A$, and   for any other solution $P$ we have $P \wb R$.
+In contrast, the equation 
+ $X = a|  X$ has solutions that may be quite different, namely any process capable of
+continuosly  performing $a$ action (but that could behave arbitrarily  on other actions).
 
-\item 
-$ X_1 = a.  X_2$, $ X_2 = b.  X_1$
+% The unique solution of the system (1), modulo $\wb$,  is the constant $K \Defi a
+% . K$:  for any other solution $P$ we have $P \wb K$.
+% The unique solution of (2), modulo $\wb$, are the constants $K_1 , K_2$
+% with $K_1 \Defi a . K_2$ and $K_2 \Defi b. K_1$; again, for any other
+% pair of solutions $P_1,P_2$ we have $K_1 \wb P_1$ and $K_2 \wb P_2$.
+% Examples of systems that do not have a unique solution are: 
+% \begin{enumerate}
+% \item $X = X $
 
-\end{enumerate}
+% \item $X = \tau . X$
+% \item $X = a | X$
 
-The unique solution of the system (1), modulo $\wb$,  is the constant $K \Defi a
-. K$:  for any other solution $P$ we have $P \wb K$.
-The unique solution of (2), modulo $\wb$, are the constants $K_1 , K_2$
-with $K_1 \Defi a . K_2$ and $K_2 \Defi b. K_1$; again, for any other
-pair of solutions $P_1,P_2$ we have $K_1 \wb P_1$ and $K_2 \wb P_2$.
-Examples of systems that do not have a unique solution are: 
-\begin{enumerate}
-\item $X = X $
-
-\item $X = \tau . X$
-\item $X = a | X$
-
-\end{enumerate} 
-All processes are solutions of (1) and (2); examples of solutions for
-(3) are $K$ and $K | b$, for $K \Defi a
-. K$.
+% \end{enumerate} 
+% All processes are solutions of (1) and (2); examples of solutions for
+% (3) are $K$ and $K | b$, for $K \Defi a
+% . K$.
 
@@
 
-In other words,  
-if the system is sequential, then 
- for
-every expression $E_i$, any subexpression of $E_i$ in which $X_j $ 
-appears, apart from $X_j$ itself,  is a sum (of prefixed terms). 
-For instance, 
-\begin{itemize}
-\item $X = \tau. X + \mu . \nil$ is sequential but not 
- guarded, because the guarding prefix for the variable
-is not visible.
+% In other words,  
+% if the system is sequential, then 
+%  for
+% every expression $E_i$, any subexpression of $E_i$ in which $X_j $ 
+% appears, apart from $X_j$ itself,  is a sum (of prefixed terms). 
+% For instance, 
+% \begin{itemize}
+% \item $X = \tau. X + \mu . \nil$ is sequential but not 
+%  guarded, because the guarding prefix for the variable
+% is not visible.
 
-\item $X =  \ell . X | P$ is  guarded but not sequential.
+% \item $X =  \ell . X | P$ is  guarded but not sequential.
 
-\item $X =  \ell . X + \tau. \res a (a .\outC b | a.\nil)$, as well as 
-$X = \tau . (a. X + \tau . b .X + \tau  )$
-are both 
- guarded and sequential.
-\end{itemize}
+% \item $X =  \ell . X + \tau. \res a (a .\outC b | a.\nil)$, as well as 
+% $X = \tau . (a. X + \tau . b .X + \tau  )$
+% are both 
+%  guarded and sequential.
+% \end{itemize}
 
@@
 
-The proof exploits an invariance property on immediate transitions for
-guarded and sequential expressions, and then extracts a bisimulation
-(up-to bisimilarity) out
-of the solutions of the system.  
+% The proof exploits an invariance property on immediate transitions for
+% guarded and sequential expressions, and then extracts a bisimulation
+% (up-to bisimilarity) out
+% of the solutions of the system.  
 To see the  need of the

### 2018-06-12 express2018/expansion.tex
I have to use labels without hypen and underscore (don't know why) to prevent strange LaTeX compilation errors.
text

@@
 fix the definition is to define another relation on top of it:
-\begin{definition}{(rooted bisimilarity)}
-Two processes $P$ and $Q$ are rooted bisimilar, denoted $P
-\approx^c Q$, if and only if for all $\mu$ (including $\tau$):
+\begin{definition}[rooted bisimilarity]
+Two processes $P$ and $Q$ are \emph{rooted bisimilar}, written $P
+\approx^c Q$, if we have:
 \begin{enumerate}
@@
 \end{definition}
-Besides reducing the rooted bisimiarity of two processes to
-the bisimilarities of their first-step transition ends, this definition also brings a proof technique for proving the
-rooted bisimiarity by constructing a bisimulation:
-\begin{lemma}{(Rooted bisimilarity by constructing a bisimulation)}
-\label{l:obs_congr_by_weak_bisim}
-Given a (weak) bisimulation $\RR$, if two processes $P$ and $Q$
-satisfies the following properties:
-\begin{enumerate}
- \item  $P \arr\mu P'$ implies that there is $Q'$ such that $Q
-   \Arr\mu Q'$ and $P' \RR Q'$;
-\item the converse of (1) on the actions from $Q$.
-\end{enumerate}
-then $P$ and $Q$ are rooted bisimilar, i.e., $P \approx^c Q$.
-\end{lemma}
+% Besides reducing the rooted bisimiarity of two processes to
+% the bisimilarities of their first-step transition ends, this definition also brings a proof technique for proving the
+% rooted bisimiarity by constructing a bisimulation:
+% \begin{lemma}{(Rooted bisimilarity by constructing a bisimulation)}
+% \label{l:obsCongrByWeakBisim}
+% Given a (weak) bisimulation $\RR$, if two processes $P$ and $Q$
+% satisfies the following properties:
+% \begin{enumerate}
+%  \item  $P \arr\mu P'$ implies that there is $Q'$ such that $Q
+%    \Arr\mu Q'$ and $P' \RR Q'$;
+% \item the converse of (1) on the actions from $Q$.
+% \end{enumerate}
+% then $P$ and $Q$ are rooted bisimilar, i.e., $P \approx^c Q$.
+% \end{lemma}
 

### 2018-06-12 express2018/unique.tex
text

@@
 a \behavC\ variable is underneath a prefix.
+
+The system use \emph{weakly-guarded sums} if 
+each $E_i$ only makes use of guarded sums.
 \qed\end{definition}
+
+\finish{introduce guarded sums, and contrast it with arbitrary sums}
 
@@
  of a system of weakly-guarded
-contractions.
+contractions that uses  weakly-guarded sums.
 For any context $\qct$, 
@@
 
+\finish{here a sketch of the proof (notably with the induction argument)}
+
 \begin{theorem}[unique solution of contractions for $\wb$]
@@
 A system of weakly-guarded contractions
-    has 
+ that uses  weakly-guarded sums    has 
 a unique solution 
@@
 \end{theorem}
-
-\finish{sopra: sum-free}
 

### 2018-06-12 express2018/ccs.tex
text

@@
 
-\finish{maybe use recursion in place of constants, so to be
-  more faithful wrt the HOL formalization}
-
-We assume  a possibly infinite set of \emph{input names} $a, b,
-\ldots$ and \emph{output names} $\outC a, \outC b, \ldots$,
- and a set of \emph{constant identifiers} (or simply \emph{constants})
- $A, B, \ldots$ for writing recursive processes. 
-The special symbol $\tau$ does not occur in the names and in the 
-constants. 
+We assume  a possibly infinite set of \emph{names} $a, b,
+\ldots$, that does not contain the special symbol $\tau$, and
+variables $A,B, \ldots$ used for writing recursive behaviours. 
 The class  of the CCS processes is inductively built from $\nil$ by the operators
-of parallel composition,  sum,
- restriction, prefix, and constants:
+of  prefixing, parallel composition,  sum,
+ restriction,  and recursion:
 \begin{equation*}
 \begin{array}{ccl}
+\mu  & := &  a \; \midd \;  \outC a  \; \midd \;  \tau \\
 P  & := &  \nil \; \midd \;  \mu . P \; \midd \;  P_1 |  P_2 \; \midd  \;
 P_1 + P_2 \; \midd % \; \mu . P\; \midd  \; 
-  (\res a\!)\, P  \;  \midd \;   K   %\\[\tkpS]
+  (\res a\!)\, P  \;  \midd \;   \recu A  P   %\\[\tkpS]
 \end{array}
 \end{equation*}
-Each constant $K$ has  a definition 
- $K \Defi P$.
-We sometimes omit trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil $ .
+%We sometimes omit trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil $ .
 The operational semantics is given by means of an LTS, and is
@@
 parallel composition and the rule for sum  has been omitted).
+A CCS expression \emph{uses weakly-guarded sums} if all occurrences of
+the sum  operator are of the form $\mu_1.P_1 + \mu_2.P_2 + \ldots
+\mu_n.P_n$, for some $n \geq 2$.
 
@@
 \hskip .5cm 
-$\displaystyle{ P \arr{\mu}P' \over
- K   \arr{ \mu} P'  } $  if  $  K \Defi P$
+$\displaystyle{ P \sub {\recu A P} A \arr{\mu}P' \over
+ \recu A P   \arr{ \mu} P'  } $
 \end{center}
-%  \begin{center}
-% \begin{tabular}{rlcrlcrl}
-% %{{\sf sum}}:
-% & $  \Sigma_{i\in I} \mu_i.   P_i 
-% \arr{ \mu_i  }P_i$ & $ \hb$ &
-% %{{\sf par1}}:
-% & $\displaystyle{   P \arr\mu   P' \over   P | Q   \arr\mu
-% P' | Q } $ & $ \hb$ &  
-% % \multicolumn{5}{c}{
-% %  {{\sf com1}}: 
-% &  $\; \;$  $\displaystyle{ P \arr{ a}P' \hk \hk  Q
-% \arr{\outC a }Q'  \over     P|  Q \arr{ \tau} P'
-% |  Q'  }$ 
-%  \\[\mysp]
-% \multicolumn{8}{c}{ 
-% %{{\sf res}}:  %&
-% \hskip .4cm  
-%  $\displaystyle{ P \arr{\mu}P' \over
-%  \res a     P   \arr{\mu} \res a P'} $ $ \mu \neq a, \outC a$
-% % & 
-% $ \hb$ %  &
-% \hskip .4cm 
-% %{{\sf const}}: %& 
-% \hskip .3cm 
-% $\displaystyle{ P \arr{\mu}P' \over
-%  K   \arr{ \mu} P'  } $  if  $  K \Defi P$
-% }\end{tabular}
-%  \end{center} 
 \caption{The LTS of CCS}
@@
 for the  expression
-$G$ (in contrast,  symbol $\Defi$ is used for the definition of
-constants, whereas   $=$ is used for syntactic equality and for equations).
+$G$.
 If $\leq$ is a preorder, then  $\geq$  is its inverse (and

### 2018-06-12 express2018/unique.tex
text

@@
 has  \emph{a unique 
-solution for $\asymp$}
+solution for $\approx$}
 if 
@@
  $\til P$ and $\til Q$ are both solutions  for  $\mcontrBIS$
- then $\til P \asymp \til Q$.
+ then $\til P \approx \til Q$.
 \qed\end{itemize}
@@
 
-\finish{introduce guarded sums, and contrast it with arbitrary sums}
-
 \begin{lemma}
@@
 contractions that uses  weakly-guarded sums.
-For any context $\qct$, 
+For any context $\qct$ that uses  weakly-guarded sums, 
 if  $\ct{\til P}\Arr{\mu}  R$,
  then 
-there is a  context $\qctp$
+there is a  context $\qctp$ that uses  weakly-guarded sums
 such that $R \mcontrBIS \ctp{\til P}$ and  $\ct{\til Q} \Arcap{\mu}
@@
 
-\finish{here a sketch of the proof (notably with the induction argument)}
+\begin{proof}{[Sketch]}
+Let $n$ be the length of the transition $\ct{\til P}\Arr\mu R$  (the
+number of `strong steps' of which it is composed), and  
+let $\ctpp {\til P}$ and $\ctpp {\til Q}$  be the processes obtained
+from  $\ct {\til P}$ and $\ct {\til Q}$ by unfolding the definitions
+of the contractions $n$ times. Thus in $\qctpp$ each hole is
+underneath at least $n$ prefixes, and cannot contribute to an action
+in the first $n$ transitions; moreover all the contexts use
+weakly-guarded sums.
+
+We have $\ct{\til P} \mcontrBIS \ctpp{\til P}$, and 
+$\ct{\til Q} \mcontrBIS \ctpp{\til Q}$, 
+ by the substitutivity  properties of $\mcontrBIS$ (we exploit here
+ the syntactic constraints on sums). Moreover,
+ since each hole of the  context $\qctpp$ is underneath at least $n$
+ prefixes, applying  
+the definition
+ of $ \mcontrBIS$ on the transition 
+ $\ct{\til P}\Arr{\mu}  R$, we infer the existence
+ of $\qctp$ such that 
+$
+\ctpp{\til P}\Arcap{\mu} \ctp{\til P} \mexpaBIS R
+$
+and 
+$
+\ctpp{\til Q}\Arcap{\mu}  \ctp{\til Q} 
+. $
+Finally, again applying the definition of $\mcontrBIS$ on 
+$\ct{\til Q} \mcontrBIS \ctpp{\til Q}$, 
+we derive 
+$
+\ct{\til Q}\Arcap{\mu}  \wb \ctp{\til Q} 
+.$
+\end{proof}
 
@@
 
-\section{Rooted contraction and unique solution theorem for rooted bisimilarity}
+\begin{proof}{[Sketch]}
+One shows that if $\til P$ and $\til Q$ are solutions for $\wb$ of a system of weakly-guarded
+contractions that uses weakly-guarded sums,  then the
+ relation 
+\[\R \DSdefi \{ 
+(R,S) \st R \wb \ct{\til P}, S \wb \ct{\til Q} \mbox{ for some context
+$\qct$} \} \, . 
+\]
+ is a bisimulation, exploiting 
+ Lemma~\ref{l:uptocon}.
+\end{proof}
+
+\section{Rooted contraction}
 \label{ss:new}
+
+The unique solution theorem of Section~\ref{ss:SysContr} require a
+constrained syntax for sums, due to the congruence and precongruence
+problems of bisimilarity and contraction with such operator. 
+We show here that the constraints can be
+removed by moving to the induced congruence and precongruence.
 
@@
 \label{d:rcontra}
-Two processes $P$ and $Q$ are in the rooted contraction, written 
+Two processes $P$ and $Q$ are in the \emph{rooted contraction}, written 
  $P\rcontr Q$, if
@@
 \label{t:rcontrPrecongruence}
-Relation $\rcontr$ is a precongruence in CCS. 
+Relation $\rcontr$ is a precongruence in CCS.  Indeed it is the
+largest precongruence contained in $\contr$.
 \end{theorem}
 
-\finish{two proofs}
+The proof of this result is along the lines of the analogous result
+for rooted bisimilarity with respect to bisimilarity.
 
-For the unique solution result a key lemma is the following one.
+For a system of contraction, the meaning of 
+`solution  for $\rcontr$' and of 
+ \emph{a unique 
+solution for $\rapprox$}
+is the expected one~--- just replace in Definition~\ref{d:uniContra}  the preorder 
+$\contr$ with $\rcontr$, and the equivalence 
+$\approx$ with $\rapprox$.
+
+For the rooted relations, the analogous of Lemma~\ref{l:uptocon} and of
+Theorem~\ref{t:contraBisimulationU} can now be stated without constraints on the sum
+operator.  
+The schema of the proofs is also the same; the substitutivity
+properties of 
+$\rcontr$ and $\rapprox$ allow us to avoid issues with the sum
+operator. Some care is needed in Theorem~\ref{t:rcontraBisimulationU}
+to make sure that the final result is about  
+$\rapprox$, rather than (the weaker) $\approx$.
 
 \begin{lemma}
-\label{l:uptocon}
+\label{l:ruptocon}
 Suppose $\til P$ and $\til Q$ are solutions  for $\rcontr$ 
@@
 
-\begin{theorem}[unique solution of contractions for $\wb$]
-\label{t:contraBisimulationU}
+\begin{theorem}[unique solution of contractions for $\rapprox$]
+\label{t:rcontraBisimulationU}
 A system of weakly-guarded contractions
@@
 a unique solution 
- for $\wb$.
+ for $\rapprox$.
 \end{theorem}
-
-\finish{sopra: e' la stessa assertion dell'altro theorem, occorre differenziare}

### 2018-06-12 express2018/part2.tex
htex files sync with checked .tex files

@@
 \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLBoundVar{x} (\HOLBoundVar{h}\HOLSymConst{::}\HOLBoundVar{t}) \HOLBoundVar{z}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLBoundVar{P} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b}
+       \HOLBoundVar{P} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b}\hfill{[LRTC_DEF]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{TRACE} \HOLSymConst{=} \HOLConst{LRTC} \HOLConst{TRANS}
+\HOLConst{TRACE} \HOLSymConst{=} \HOLConst{LRTC} \HOLConst{TRANS}\hfill{[TRACE_def]}
 \end{alltt}
@@
 \HOLTokenTurnstile{} \HOLConst{NO_LABEL} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
-\HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLFreeVar{L}
+\HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLFreeVar{L}\hfill{[NO_LABEL_def]}
 \end{alltt}
@@
        \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
-\HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDisj{}} \HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{L\sb{\mathrm{2}}}
+\HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDisj{}} \HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{L\sb{\mathrm{2}}}\hfill{UNIQUE_LABEL_def}
 \end{alltt}
@@
 \begin{alltt}
-WEAK_TRANS_AND_TRACE:
 \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}}
@@
        \HOLConst{TRACE} \HOLFreeVar{E} \HOLBoundVar{us} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{NULL} \HOLBoundVar{us} \HOLSymConst{\HOLTokenConj{}} \HOLKeyword{if} \HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLKeyword{then} \HOLConst{NO_LABEL} \HOLBoundVar{us}
-       \HOLKeyword{else} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLBoundVar{us}
+       \HOLKeyword{else} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLBoundVar{us}\hfill{[WEAK_TRANS_AND_TRACE]}
 \end{alltt}
@@
 The statement of the  final unique solution of contractions theorem is
-the following (a  weakly
-guarded context is the version without direct sums)
-\finish{version of what?} 
+the following (\texttt{WGS} is a weakly guarded context without direct sums)
 \begin{alltt}
+UNIQUE_SOLUTION_OF_CONTRACTIONS:
 \HOLTokenTurnstile{} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.

### 2018-06-12 express2018/sos.tex
formalization -> formalisation (following title)

@@
 
-In the formalization of CCS, 
+In the formalisation of CCS, 
 the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' ($\beta$ is a
@@
 operator, we chose to takes a set of names, rather than a
-  single name as in the  CCS syntax, to prevent the formalization
+  single name as in the  CCS syntax, to prevent the formalisation
   efforts on the equivalence of CCS processes with different order of

### 2018-06-12 express2018/context.tex
DS

\subsection{Semantic context, guardness and (pre)congruence}

\finish{i have no idea what a ``semantic'' context is. This is a
  strange terminology, as contexts are by definitions syntactic.
They just seem ordinary contexts to me (multi-hole)
}

We need to find a suitable formal definition of semantic
context. There're multiple ways. Here we have chosen to use $\lambda$-expressions (typed
$CCS\rightarrow CCS$) to represent a (multi-hole) semantic
context. The definition is inductive:
\begin{alltt}
\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})
\end{alltt}

Under above definition, we can formally define the concept of
``precongruence'' and ``congruence'' in the following ways:
\begin{alltt}
\HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}. \HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})
\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLConst{precongruence} \HOLFreeVar{R}
\end{alltt}

A \emph{weak guarded} context is a context in which all holes appears
in the sub-expression of prefixed processes. We can easily define it
following the same idea:
\begin{alltt}
\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})
\end{alltt}
(Notice the differences between a weak guarded context and a normal
one: $\lambda t. t$ is not weakly guarded as the variable is directly
exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
guarded as long as $e[\cdot]$ is a semantic context, no necessary weakly guaded.)

It's a similar process to define strongly guarded context
(\texttt{SG}), sequential context (\texttt{SEQ}) and their
variants without direct sums (\texttt{GCONTEXT}, \texttt{WGS},
\texttt{GSEQ}). Some lemmas about their relationships have very long
(but trivial) formal proofs due to the combinatorial explosion of
inductions on their structures. For example, one such 
lemma says, for any semantic context $E$ which is both strongly guarded
and sequential (no direct sums) and another sequential context $H$ (no
direct sums), the composition $H \circ E$ is still both strongly
guarded and sequential (no direct sums):
\begin{alltt}
SG_GSEQ_combin:
\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{H}. \HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E})
\end{alltt}

% \subsection{Milner's ``unique solution of equations'' theorems}

% Once the representation issue of CCS equations is resolved, the actual
% proofs of Milner's unique solution of equations theorems is not very
% interesting from the view of theorem proving, although it's a 
% precise proof engineering work producing quite long proofs.
% Since we have chosen to use semantic context to represent
% single-variable equations, an equation like $P \sim E\{P/X\}$ now
% becomes $P \sim E[P]$, in which $E$ is a (multi-hole) semantic
% context, and there's no need to say it ``contains at most the variable
% $X$'' any more, as equation variable doesn't appear in $E$ at
% all. Under these simplifications, the formal proof of Milner's unique
% solution of equations theorem for $\sim$ is a literal mapping for informal
% proofs based on bisimulation upto $\sim$, induction and case analysis
% of weakly guarded contexts. Below is the formal version of Lemma 4.13
% and Proposition 4.14 in Milner's book:

% \begin{alltt}
% STRONG_UNIQUE_SOLUTION:
% \HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}. \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}
% \end{alltt}

% \begin{alltt}
% WEAK_UNIQUE_SOLUTION:
% \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}. \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
% \end{alltt}

% \begin{alltt}
% OBS_UNIQUE_SOLUTION:
% \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}. \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
% \end{alltt}

### 2018-06-12 express2018/formal.tex

@@
-\section{Formalization}
+\section{Formalisation}
 
-We highlight here a formalization of CCS
+We highlight here a formalisation of CCS
 in the HOL theorem
@@
 %  in the informal proofs. 
-The whole formalization can be found 
+The whole formalisation can be found 
 in \cite{Tian:2017wrba}  or in 
@@
 %  This
-%  work is based on a formalization of CCS in HOL theorem
+%  work is based on a formalisation of CCS in HOL theorem
 % prover (HOL4) \cite{slind2008brief}, described in second author's MSc thesis
@@
 \begin{enumerate}
-\item The formalization of semantics context in $\lambda$-expressions and the theory of
+\item The formalisation of semantics context in $\lambda$-expressions and the theory of
   (pre)congruence for CCS;
@@
 In contrast with the theorems in the first part of the paper, in the
-formalization we consider only single equations/contractions. 
+formalisation we consider only single equations/contractions. 
 This considerably simplifies the  reading of the HOL scripts. 
@@
 % solution theorems introduced in the first part. This is to not only
-% save the formalization efforts, but also to make us focusing on the most
+% save the formalisation efforts, but also to make us focusing on the most
 % important part of the proof. The most important simplification is

### 2018-06-12 express2018/intro.tex

@@
 On the other hand, we provide a  
- comprehensive formalization  of the core of the theory of CCS 
+ comprehensive formalisation  of the core of the theory of CCS 
  in the HOL
-theorem prover (HOL4). The formalization  includes the proofs of
+theorem prover (HOL4). The formalisation  includes the proofs of
 Milner's 3 ``unique solution of equations'' theorems and
@@
 theorems rely on a number of more fundamental results):
-indeed the formalization encompasses the basic properties of strong and weak
+indeed the formalisation encompasses the basic properties of strong and weak
 bisimilarity (e.g. the fixed-point and substitutivity properties), 
@@
 the basic properties  of rooted bisimilarity. Considering the relationship between bisimilarity and rooted
-bisimilarity, the formalization includes the proof that the latter is the coarsest
+bisimilarity, the formalisation includes the proof that the latter is the coarsest
 congruence included in the former, for which two proofs are formalized: one as in Milner's

### 2018-06-12 express2018/context.tex
Sync with newly added context.tex (removed "semantic" words)

@@
-\subsection{Semantic context, guardness and (pre)congruence}
+%%%% -*- Mode: LaTeX -*-
+%%
+%% This is the draft of the 2nd part of EXPRESS/SOS 2018 paper, co-authored by
+%% Prof. Davide Sangiorgi and Chun Tian.
 
-\finish{i have no idea what a ``semantic'' context is. This is a
-  strange terminology, as contexts are by definitions syntactic.
-They just seem ordinary contexts to me (multi-hole)
-}
+\subsection{Context, guardness and (pre)congruence}
 
-We need to find a suitable formal definition of semantic
+We need to find a suitable formal definition of 
 context. There're multiple ways. Here we have chosen to use $\lambda$-expressions (typed
-$CCS\rightarrow CCS$) to represent a (multi-hole) semantic
+$CCS\rightarrow CCS$) to represent a (multi-hole) 
 context. The definition is inductive:
 \begin{alltt}
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})
+\HOLTokenTurnstile{} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{t}) \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
+\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{p})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
+\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
+\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLSymConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLBoundVar{e} \HOLBoundVar{t}))) \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
+\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})
+\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
+\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{p})) \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
+\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
+\HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLSymConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLBoundVar{e} \HOLBoundVar{t}))) \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
+\HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})
 \end{alltt}
@@
 exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
-guarded as long as $e[\cdot]$ is a semantic context, no necessary weakly guaded.)
+guarded as long as $e[\cdot]$ is a  context, no necessary weakly guaded.)
 
@@
 inductions on their structures. For example, one such 
-lemma says, for any semantic context $E$ which is both strongly guarded
+lemma says, for any  context $E$ which is both strongly guarded
 and sequential (no direct sums) and another sequential context $H$ (no
@@
 \begin{alltt}
-SG_GSEQ_combin:
 \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{H}.
-\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E})
+\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E})\hfill{[SG_GSEQ_combin]}
 \end{alltt}
@@
 % precise proof engineering work producing quite long proofs.
-% Since we have chosen to use semantic context to represent
+% Since we have chosen to use  context to represent
 % single-variable equations, an equation like $P \sim E\{P/X\}$ now
-% becomes $P \sim E[P]$, in which $E$ is a (multi-hole) semantic
+% becomes $P \sim E[P]$, in which $E$ is a (multi-hole) 
 % context, and there's no need to say it ``contains at most the variable
@@
 % STRONG_UNIQUE_SOLUTION:
-% \HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}
 % \end{alltt}
@@
 % WEAK_UNIQUE_SOLUTION:
-% \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
 % \end{alltt}
@@
 % OBS_UNIQUE_SOLUTION:
-% \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
 % \end{alltt}

### 2018-06-13 express2018/ccs.tex
text
DS

@@
 \ldots$, that does not contain the special symbol $\tau$, and
-variables $A,B, \ldots$ used for writing recursive behaviours. 
+a set of variables $A,B, \ldots$ for writing recursive behaviours. 
 The class  of the CCS processes is inductively built from $\nil$ by the operators
@@
 P_1 + P_2 \; \midd % \; \mu . P\; \midd  \; 
-  (\res a\!)\, P  \;  \midd \;   \recu A  P   %\\[\tkpS]
+  (\res a\!)\, P  \;  \midd \;   \recu A  P\;  \midd \; A   %\\[\tkpS]
 \end{array}
@@
 the sum  operator are of the form $\mu_1.P_1 + \mu_2.P_2 + \ldots
-\mu_n.P_n$, for some $n \geq 2$.
++ \mu_n.P_n$, for some $n \geq 2$.
 

### 2018-06-13 express2018/expansion.tex
text
htex files sync with checked .tex files
DS

@@
-\subsection{Equivalences: bisimilarity and rooted bisimilarity}
+\subsection{Bisimilarity, rooted bisimilarity,  and up-to techniques}
 \label{ss:BiEx}
 
-The equivalences here are 
+The equivalences we consider are  mainly
  \emph{weak}, in that they
@@
 
-We sometimes call bisimilarity as ``\emph{weak} bisimilarity'', to
+We sometimes call bisimilarity as ``\emph{weak}'', to
 distinguish it from \emph{strong bisimilarity}, $\sim$,
@@
 
-Bisimilarity is not congruence w.r.t direct sums, one obvious way to
-fix the definition is to define another relation on top of it:
+Bisimilarity is not preserved by the sum operator. 
+For this, Milner introduces \emph{observational congruence}, also called \emph{rooted
+  bisimilarity}.
 \begin{definition}[rooted bisimilarity]
+\label{d:rootedBisimilarity}
 Two processes $P$ and $Q$ are \emph{rooted bisimilar}, written $P
-\approx^c Q$, if we have:
+\rapprox Q$, if we have:
 \begin{enumerate}
@@
 
-\subsection{Preorders: expansion and contraction (??)}
+\begin{theorem}
+\label{t:rapproxCongruence}
+Relation $\rapprox$ is a congruence in CCS.  Indeed it is the
+largest congruence contained in $\approx$.
+\end{theorem}
 
@@
 As bisimilarity, expansion is preserved by all operators but sum.
+%An example of up-to technique involving expansion is

### 2018-06-13 express2018/unique.tex
DS

@@
 for rooted bisimilarity with respect to bisimilarity. 
+Similarly one can define and handle the rooted variant of the expansion preorder.
 
@@
 there is a  context $\qctp$
-such that $R \mcontrBIS \ctp{\til P}$ and  $\ct{\til Q} \Arcap{\mu}
+such that $R \mcontrBIS \ctp{\til P}$ and  $\ct{\til Q} \Arr{\mu}
  \wb \ctp{\til Q}$.

### 2018-06-13 express2018/context.tex
Stage fixes

@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{t}) \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{p})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
-\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{a}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
-\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLSymConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLBoundVar{e} \HOLBoundVar{t}))) \HOLSymConst{\HOLTokenConj{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
-\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})
+\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
+\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
+\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
+\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[CONTEXT_rules]}
 \end{alltt}
@@
 \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
-\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})
-\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLConst{precongruence} \HOLFreeVar{R}
+\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})\hfill{[precongruence_def]}
+\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLConst{precongruence} \HOLFreeVar{R}\hfill{[congruence_def]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
-\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{p})) \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
-\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{a}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
-\HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLSymConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLBoundVar{e} \HOLBoundVar{t}))) \HOLSymConst{\HOLTokenConj{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
-\HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})
+\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
+\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
+\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[WG_rules]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{H}.
-\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E})\hfill{[SG_GSEQ_combin]}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
+\HOLConst{SG} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{H}.
+\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLBoundVar{E})
 \end{alltt}

### 2018-06-13 express2018/formal.tex
Stage fixes

@@
 \begin{enumerate}
-\item The formalisation of semantics context in $\lambda$-expressions and the theory of
+\item The use of HOL's new coinductive relation package for defining bisimilarity;
+\item The formalisation of context by $\lambda$-expression and the theory of
   (pre)congruence for CCS;
@@
   contractions theorem;
-\item The proof of the hard version of ``coarsest congruence
-  contained in $\approx$'' theorem.
-\end{enumerate}
+\end{enumerate}\finish{TODO: need updates}
 
@@
 The extension of the work to multiple equations/contractions is
-discussed in Section~\ref{s:}. \finish{to be finished}
+discussed in Section~\ref{s:concl}.
 

### 2018-06-13 express2018/part2.tex
Stage fixes

@@
+%%%% -*- Mode: LaTeX -*-
+%%
+%% This is the draft of the 2nd part of EXPRESS/SOS 2018 paper, co-authored by
+%% Prof. Davide Sangiorgi and Chun Tian.
+
 \subsection{Unique solution of contractions}
@@
 The major difficulties in the formalisation of the results about unique solution of
-contractions are in the proof of  Lemma \ref{...}; in particular, it
+contractions are in the proof of lemma~\ref{l:ruptocon}; in particular, it
 uses an induction on the length of weak transitions. 
 For this, one could introduced a refined form of weak transition relation
-enriched with its length; we have however preferred to use 
-traces (one reason is to be able to extend the formalisation in the
-future so to handle also unique solution results for forms of  trace
-equivalence).
-% Introducing a special vesion of weak transition relation
-% with length would be an easier choice, but we have chosen to use trace
-% instead, so that in the future it's possible to extend the work with
-% trace equivalence included.
-
-\finish{since we do not do trace equivalence, the argument above seems
-weak. Are there other reasons?}
+enriched with its length, but such a non-standard relation finds no
+other uses beside proving our target theorem. Another way is to use 
+traces instead, as it shows more clearly all passing actions inside a
+trace, making formal reasoning easier.
 
 We represent a trace by the initial process, the final derivative, and
-the
-list of actions performed. 
+the list of actions performed. 
 To formalise this, 
@@
 into two cases: no label and unique label. The definition of ``no
-label'' in an action list is easy and clear:
+label'' in an action list is easy and clear (\texttt{MEM} is for
+testing if an element is \emph{member} of a list):
 \begin{alltt}
@@
 \end{alltt}
-\finish{above: what is MEM? has it been explained before?} 
 while the definition of ``unique label'' can be done in many ways, in
@@
    \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{L\sb{\mathrm{1}}} \HOLBoundVar{L\sb{\mathrm{2}}}.
-       (\HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} [\HOLFreeVar{u}] \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{=} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenConj{}}
-       \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
-\HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDisj{}} \HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{L\sb{\mathrm{2}}}\hfill{UNIQUE_LABEL_def}
+(\HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} [\HOLFreeVar{u}] \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{=} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{2}}}\hfill{UNIQUE_LABEL_def}
 \end{alltt}
-\finish{above: cannot you just use the \HOLConst{NO_LABEL} predicate
-  previously defined?}
-
 It says, a label is unique in an action list iff it there's no other
@@
 The final relationship between traces and weak transitions is stated
-and proved in the following lemma:
-
-\finish{below: explain in $us$ what is $s$ } 
+and proved in the following lemma: (here $us$ as single variable means
+a list of actions)
+\begin{lemma}
+A weak transition $E\overset{u}{\Rightarrow}E'$ is a just trace with non
+empty action list: 1) without any visible label, if $u = \tau$, or 2)
+$u$ is the unique label in the list, if $u \neq \tau$.
 \begin{alltt}
@@
 \end{alltt}
-(A weak transition $E\overset{u}{\rightarrow}E'$ 
-\finish{above: you mean $E\overset{u}{\Rightarrow}E'$?}  
-is a trace with non
-empty action list: 1) without any visible label, if $u = \tau$, or 2)
-$u$ is the unique label in the list, if $u \neq \tau$.)
+\end{lemma}
 
-To finish the proof of Lemma~\ref{l:}, we use the  above
+To finish the proof of Lemma~\ref{l:ruptocon}, we use the  above
 result to freely switch between weak transitions and traces
@@
 The statement of the  final unique solution of contractions theorem is
-the following (\texttt{WGS} is a weakly guarded context without direct sums)
+the following (\texttt{WGS} is a weakly guarded context without direct
+sums)
 \begin{alltt}

### 2018-06-13 express2018/context.tex
Minor fixes

@@
 exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
-guarded as long as $e[\cdot]$ is a  context, no necessary weakly guaded.)
+guarded as long as $e[\cdot]$ is a context, not necessary weakly guaded.)
 
@@
 \texttt{GSEQ}). Some lemmas about their relationships have very long
-(but trivial) formal proofs due to the combinatorial explosion of
-inductions on their structures. For example, one such 
+(but trivial) formal proofs due to multiple levels of
+inductions on context structures. For example, one such 
 lemma says, for any  context $E$ which is both strongly guarded

### 2018-06-13 express2018/contraction.tex
Added missing equa.tex
Minor fixes

@@
 \label{s:mcontr}
+
 The constraints on the unique-solution Theorem~\ref{t:Mil89} can be 
@@
 of all bisimulation contractions. 
-\qed\end{definition}
+\end{definition}
 % We say that $P$  {\emph{bisimilarly  contracts} $Q$, written
@@
  the expansion  relation 
-$\contr$ of   Definition~\ref{d:expa}. Clause (1) is the same in the two
+$\expa$ of Definition~\ref{d:expa}. Clause (1) is the same in the two
 definitions. But in clause (2) expansion uses 
@@
 \label{exa:contr}
-{ We have %\mcontrBIS a + \tau^n . a $
+We have %\mcontrBIS a + \tau^n . a $
  $ a \not  \mcontrBIS \tau. a$. However,
@@
 $  P  \mcontrBIS P +Q$. The last two relations do not hold with 
-$\contr$, which explains the strictness of the inclusion
- ${\contr} \subseteq {\mcontrBIS}$. 
+$\expa$, which explains the strictness of the inclusion
+ ${\expa} \subseteq {\mcontrBIS}$. 
 % The inclusion is strict: for instance
@@
 %  $ a \not  \mcontrBIS \tau. a$
-\qed} \end{example}
+\end{example}
 

### 2018-06-13 express2018/formal.tex
Minor fixes

@@
 code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}. The
-work consists of about 20,000 lines of proof scripts in Standard ML.
-%  This
-%  work is based on a formalisation of CCS in HOL theorem
-% prover (HOL4) \cite{slind2008brief}, described in second author's MSc thesis
-% \cite{Tian:2017wrba} and now lives in the official examples folder of HOL4 source
-% code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}.
+work consists of about 20,000 lines of proof scripts in Standard ML,
+derived from an early work \cite{Nesi:1992ve} by Monica Nesi in 1992-1995.
+
+HOL4 is written in Standard ML (or ML for abbreviation). This single language plays three roles here:
+\begin{enumerate}
+\item It serves as the underlying implementation language for the core HOL engine;
+\item It's used to implement tactics (and tacticals) for automatic theorem proving;
+\item It's used as the command language of the interactive HOL system.
+\end{enumerate}
+Besides, HOL4 users can write arbitrary applications which leverages
+the theorem proving facility.
 

### 2018-06-13 express2018/intro.tex
Minor fixes

@@
 theorem prover (HOL4). The formalisation  includes the proofs of
-Milner's 3 ``unique solution of equations'' theorems and
-contractions discussed in the present paper, but is not limited to it (partly because such
+``unique solution of (rooted) contractions'' theorems and
+(pre)congruence properties discussed in the present paper, but is not limited to it (partly because such
 theorems rely on a number of more fundamental results):
@@
 techniques (e.g., bisimulation up-to expansion),
-the basic properties  of rooted bisimilarity. Considering the relationship between bisimilarity and rooted
+some basic properties of rooted bisimilarity (including Hennessy Lemma
+and Deng Lemma).
+Considering the relationship between bisimilarity and rooted
 bisimilarity, the formalisation includes the proof that the latter is the coarsest

### 2018-06-13 express2018/part2.tex
Minor fixes

@@
    \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{L\sb{\mathrm{1}}} \HOLBoundVar{L\sb{\mathrm{2}}}.
-(\HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} [\HOLFreeVar{u}] \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{=} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{2}}}\hfill{UNIQUE_LABEL_def}
+(\HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} [\HOLFreeVar{u}] \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{=} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{2}}}\hfill{[UNIQUE_LABEL_def]}
 \end{alltt}
@@
 
-The proof of Unique solution of rooted contractions theorem is the
-same proof steps of Unique solution of contractions theorem plus the
-application of \texttt{OBS_CONGR_BY_WEAK_BISIM} at the
-beginning.\footnote{In the thesis work, the conclusion of this theorem
+The formal proof of ``unique solution of rooted contractions theorem''
+(Thm.\; \ref{t:rcontraBisimulationU}) has the
+same initial proof steps as Thm.\; ref{{t:contraBisimulationU}} plus a
+little more steps to handle the rooted bisimilarity at conclusion. (In the thesis work, the conclusion of this theorem
 is weak bisimilarity, and the proof is exactly the same as Unique
@@
 using observational congruence, and the previous version becomes a
-trivial collorary of the current version.} The
+trivial collorary of the current version.) The
 two proofs are quite similar, mostly because the only property we need

### 2018-06-13 express2018/sos.tex
DS
Minor fixes

@@
 
-HOL4 is written in Standard ML (or ML for abbreviation). This single language plays three roles here:
-\begin{enumerate}
-\item It serves as the underlying implementation language for the core HOL engine;
-\item It's used to implement tactics (and tacticals) for automatic theorem proving;
-\item It's used as the command language of the interactive HOL system.
-\end{enumerate}
-Besides, HOL4 users can write arbitrary applications which leverages
-the theorem proving facility. The ultimate result (initially done by Nesi)
+The ultimate result (initially done by Nesi)
 at this point, is a complex Standard ML function

### 2018-06-13 express2018/unique.tex
Minor fixes

@@
  then $\til P \approx \til Q$.
-\qed\end{itemize}
+\end{itemize}
 \end{definition}
@@
 each $E_i$ only makes use of guarded sums.
-\qed\end{definition}
+\end{definition}
 
@@
 We show here that the constraints can be
-removed by moving to the induced congruence and precongruence.
-
+removed by moving to the induced congruence and precongruence, so
+called ``rooted contraction'':
 \begin{definition}[rooted contraction]
@@
 
+The quick finding of rooted contraction was by help of
+theorem provers, and was based on two principles: 1) Its definition must NOT be recursive
+(or coinductive), instead it should mimic the definition of rooted bisimilarity
+($\approx^c$); 2) It must be built on top of the existing \emph{contracts}
+relation $\mcontrBIS$, which we believe it's the \emph{right} one (as
+it's complete). Multiple candicates were tested, and finally the above
+definition was proven to be a precongruence:
 \begin{theorem}
@@
 \end{theorem}  
-
 The proof of this result is along the lines of the analogous result
@@
 
-\begin{theorem}[unique solution of contractions for $\rapprox$]
+\begin{theorem}[Unique solution of contractions for $\rapprox$]
 \label{t:rcontraBisimulationU}

### 2018-06-13 express2018/intro.tex
DS

--- 2018-06-12 express2018/intro.tex
@@
 
-The purpose of this paper is twofold. 
-On the one hand, we refine the contraction proof technique by moving to the 
-\emph{rooted contraction} \cite{Tian:2017wrba}, that is, the coarsest (pre)congruence contained in the contraction
-preorder.  Using rooted contraction one obtains an unique-solution theorem that is valid for
-\emph{rooted bisimilarity} (hence also for bisimilarity itself).  
-On the other hand, we provide a  
+The main goal  of the work described in this paper is 
+a rather  
  comprehensive formalisation  of the core of the theory of CCS 
  in the HOL
-theorem prover (HOL4). The formalisation  includes the proofs of
-Milner's 3 ``unique solution of equations'' theorems and
-contractions discussed in the present paper, but is not limited to it (partly because such
-theorems rely on a number of more fundamental results):
+theorem prover (HOL4),  with a focus on the theory of unique solutions of contractions.
+The formalisation however is not confined to the theory of  unique solutions, but embraces 
+most of the 
+core of the theory of CCS \cite{Milner}
+(partly because the theory of unique solutions
+ relies on a number of more fundamental results):
 indeed the formalisation encompasses the basic properties of strong and weak
@@
 their algebraic theory, various versions of ``bisimulation up to''
-techniques (e.g., bisimulation up-to expansion),
-the basic properties  of rooted bisimilarity. Considering the relationship between bisimilarity and rooted
-bisimilarity, the formalisation includes the proof that the latter is the coarsest
-congruence included in the former, for which two proofs are formalized: one as in Milner's
+techniques (e.g., bisimulation up-to bisimilarity),
+the main properties  of the rooted bisimilarity (the congruence induced by weak
+bisimilarity, also called observation congruence). Concerning rooed bisimilarity, the formalisation
+includes Hennessy and Deng lemmas, and two proofs that rooted bisimilarity is the largest
+congruence included in bisimilarity:
+one as in Milner's
 book,  requiring the hypothesis that  no processes can use all labels; the other without
-such hypothesis, essentially formalising van Glabbek's paper \cite{vanGlabbeek:2005ur}.
-Similar theorems are proved for rooted contractions wrt the contraction preorder.
+such hypothesis, essentially formalising van Glabbek's paper \cite{vanGlabbeek:2005ur}
+(such proof however follows the structure of the ordinal numbers, which cannot be handled
+in HOL, and therefore it is restricted to finite-state processes ).
+Similar theorems are proved for the rooted contraction preorder.
 
-\finish{for Express, insist more on Structural Operational Semantics,
-  to fit the scope of the conference}
+In this respect,  the work is an extensive experiment with the use of the HOL theorem prover and its
+most recent developments, including a package  for expressing coinductive definitions.
+
+From the CCS theory viewpoint, the formalisation has offered us the possibility of 
+further refining the theory of unique solutions. 
+In particular, the existing theory  placed limitations on the body of the contractions due to the
+substitutivity problems of weak bisimilarity and other behavioural relations with respect
+to the sum operator.  
+We have thus refined the proof  technique based on contractions by moving to the 
+\emph{rooted contraction}, that is, the coarsest (pre)congruence contained in the contraction
+preorder.  Using rooted contraction one obtains a unique-solution theorem that is valid for
+\emph{rooted bisimilarity} (hence also for bisimilarity itself), and without syntactic
+constraints on the occurrences of sums.
+
+\finish{ I had to remove the reference \cite{Tian:2017wrba} here since it would further
+  weaken this paper. }
+
+Another advantage of the formalisation is 
+that we can take advantage of results about different 
+equivalences or preorders that share a similar  proof structure. 
+Examples are: the results that rooted bisimilarity and rooted contraction are,
+respectively, the coarsest congruence contained in weak bisimilarity 
+and the coarsest precongruence contained in the contraction  preorder; 
+the result about unique solution of equations for weak bisimilarity that uses the
+contraction preorder as an auxiliary relation, and other unique solution results (e.g., 
+the one for rooted in which
+the auxiliary relation is rooted contraction); various forms of enhancement of the bisimulation
+proof method (the `up-to' techniques).  
+In these cases, there are only a few places in which the HOL scripts have to be modified.
+Then the succesful termination of the scripts  gives us a guarantee that the proof is
+completed,  removing the risk 
+of overlooking or missing details as in hand-written proofs.
+
+% to describe
+% The purpose of this paper is twofold. 
+% On the one hand, 
+% On the other hand, we provide a  
+%  comprehensive formalisation  of the core of the theory of CCS 
+%  in the HOL
+% theorem prover (HOL4). The formalisation  includes the proofs of
+% Milner's 3 ``unique solution of equations'' theorems and
+% contractions discussed in the present paper, but is not limited to it (partly because such
+% theorems rely on a number of more fundamental results):
+% indeed the formalisation encompasses the basic properties of strong and weak
+% bisimilarity (e.g. the fixed-point and substitutivity properties), 
+% their algebraic theory, various versions of ``bisimulation up to''
+% techniques (e.g., bisimulation up-to expansion),
+% the basic properties  of rooted bisimilarity. 
+% Thus the work is an extensive experiment with the use of the HOL theorem provers and its
+% most recent developments, including a facility  for expressing coinductive definitions.
+
+% % Considering the relationship between bisimilarity and rooted
+% % bisimilarity, the formalisation includes the proof that the latter is the coarsest
+% % congruence included in the former, for which two proofs are formalized: one as in Milner's
+% % book,  requiring the hypothesis that  no processes can use all labels; the other without
+% % such hypothesis, essentially formalising van Glabbek's paper \cite{vanGlabbeek:2005ur}.
+% % Similar theorems are proved for rooted contractions wrt the contraction preorder.
+
+\paragraph{Structure of the paper}....

### 2018-06-13 express2018/conclusions.tex
Stage fixes
DS
finished "Related"; fixed "sos"; in-progress "conclusions" (the todo)

--- 2018-06-12 express2018/conclusions.tex
@@
-\section{Conclusions}
+\section{To Do}
+\label{s:todo}
 
 \finish{discuss multiple equations/contractions}
+
+The formalisation of multi-variable context (or expressions) and the version of
+``unique solutions'' theorems with multiple equations/contractions, is
+a relative hard problem. To the best of our knowledge, so far there's no formalization (in any kind of
+process calculi) touching these areas yet. However, we've made a few initial steps
+of this interesting problem.
+
+\section{Conclusions}
+\label{s:concl}

### 2018-06-13 express2018/related.tex
finished "Related"; fixed "sos"; in-progress "conclusions" (the todo)

@@
-\section{Related work}
+\section{Related formalisation work}
 
-\finish{comments on Monica Nesi and others}
+Monica Nesi formalized both pure CCS \cite{Nesi:1992ve} and value-passing CCS
+\cite{Nesi:2017wo} in old versions of HOL theorem prover.
+She was mainly focusing on writing decision procedures (ML functions) which
+automatically prove theorems showning bisimilarity of CCS processes,
+thus HOL interactive shell could be used in
+place of model checking tools like CWB
+\cite{cleaveland1993concurrency}. The author ported her work from
+HOL88 to latest HOL4, with small improvement, then added more concepts
+and theorems, with the total lines of proof scripts at least doubled.
+
+Beside Nesi, there're two other CCS formalisations. One
+is done in Isabelle/HOL (based on Nominal datatypes) in 2010, by Jesper Bengtson as part of his PhD
+thesis project \cite{bengtson2010formalising}, available in Isabelle's Archive of Formal
+Proofs (AFP)\footnote{\url{https://www.isa-afp.org/entries/CCS.html}}. He has formalized
+classic properties for strong/weak equivalence and observational
+congruence, however the CCS grammar doesn't include process constants
+(or recursion operators). And the proved theorems also look quite
+different with their forms in textbooks.
+The other formalisation is based on Coq, done by Solange
+Coupet-Grimal in 1995, which is part of the
+``coq-contribs'' archive (Coq's official user contributed code)
+\footnote{\url{https://github.com/coq-contribs/ccs}}. This is actually
+a formalisation of transition systems without any algebraic operator,
+and covers the very basic properties of strong/weak equivalence and observational
+congruence.

### 2018-06-13 express2018/context.tex
Stage work

--- 2018-06-12 express2018/context.tex
@@
 \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})
+\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})\hfill{[CONTEXT_rules]}
 \end{alltt}
@@
 \HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})
+\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})\hfill{[WG_rules]}
 \end{alltt}
@@
 \texttt{GSEQ}). Some lemmas about their relationships have very long
-(but trivial) formal proofs due to the combinatorial explosion of
-inductions on their structures. For example, one such 
-lemma says, for any  context $E$ which is both strongly guarded
-and sequential (no direct sums) and another sequential context $H$ (no
-direct sums), the composition $H \circ E$ is still both strongly
-guarded and sequential (no direct sums):
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{H}.
-\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLFreeVar{E})\hfill{[SG_GSEQ_combin]}
-\end{alltt}
+(but trivial) formal proofs due to multiple levels of
+inductions on context structures.%  For example, one such 
+% lemma says, for any  context $E$ which is both strongly guarded
+% and sequential (no direct sums) and another sequential context $H$ (no
+% direct sums), the composition $H \circ E$ is still both strongly
+% guarded and sequential (no direct sums):
+% \begin{alltt}
+% \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
+\HOLConst{SG} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{H}.
+\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLBoundVar{E})
+% \end{alltt}
 

### 2018-06-13 express2018/formal.tex
Stage work

@@
 
-\finish{below: to be reformulated (by Davide) later} 
-We will not repeat all definitions and theorems of CCS again by their
-formalized versions. Instead, we just focus on several highlights in
-this work, i.e.
-\begin{enumerate}
-\item The use of HOL's new coinductive relation package for defining bisimilarity;
-\item The formalisation of context by $\lambda$-expression and the theory of
-  (pre)congruence for CCS;
-\item The definition and uses of trace in the proof of unique solution of
-  contractions theorem;
-\end{enumerate}\finish{TODO: need updates}
+% \finish{below: to be reformulated (by Davide) later} 
+% We will not repeat all definitions and theorems of CCS again by their
+% formalized versions. Instead, we just focus on several highlights in
+% this work, i.e.
+% \begin{enumerate}
+% \item The use of HOL's new coinductive relation package for defining bisimilarity;
+% \item The formalisation of context by $\lambda$-expression and the theory of
+%   (pre)congruence for CCS;
+% \item The definition and uses of trace in the proof of unique solution of
+%   contractions theorem;
+% \end{enumerate}\finish{TODO: need updates}
 

### 2018-06-13 express2018/intro.tex
DS
Stage work

@@
 most of the 
-core of the theory of CCS \cite{Milner}
+core of the theory of CCS \cite{Mil89}
 (partly because the theory of unique solutions
@@
 most recent developments, including a package  for expressing coinductive definitions.
+The
+work consists of about 20,000 lines of proof scripts in Standard ML.
 

### 2018-06-13 express2018/part2.tex
Stage work

@@
 The formal proof of ``unique solution of rooted contractions theorem''
-(Thm.\; \ref{t:rcontraBisimulationU}) has the
-same initial proof steps as Thm.\; ref{{t:contraBisimulationU}} plus a
+(Theorem~\;\ref{t:rcontraBisimulationU}) has the
+same initial proof steps as Theorem~\;\ref{t:contraBisimulationU} plus a
 little more steps to handle the rooted bisimilarity at conclusion. (In the thesis work, the conclusion of this theorem

### 2018-06-13 express2018/related.tex
Stage work

@@
 
-Monica Nesi formalized both pure CCS \cite{Nesi:1992ve} and value-passing CCS
-\cite{Nesi:2017wo} in old versions of HOL theorem prover.
+Monica Nesi formalized both pure CCS \cite{Nesi:1992ve} and Value-Passing CCS
+\cite{Nesi:2017wo} in old versions of HOL theorem prover, but the
+related proof scripts were not publically available.\footnote{Part of
+ the formalization of pure CCS can be found at \url{https://github.com/binghe/informatica-public/tree/master/CCS2/CCS-Nesi}.}
 She was mainly focusing on writing decision procedures (ML functions) which
-automatically prove theorems showning bisimilarity of CCS processes,
-thus HOL interactive shell could be used in
-place of model checking tools like CWB
-\cite{cleaveland1993concurrency}. The author ported her work from
-HOL88 to latest HOL4, with small improvement, then added more concepts
-and theorems, with the total lines of proof scripts at least doubled.
+automatically prove theorems showning bisimilarity of CCS
+processes.\footnote{The work is ported (by the 2nd author) from
+HOL88 to latest HOL4, with small improvements on existing work, then
+added the theory of context and (pre)congruence, coarsest
+(pre)congruence contained in bisimilarity, bisimulation up to,
+expansion, contraction, and unique solution of
+equations/expansions/contractions et al, these additions have doubled
+the size of original work.}
 
-Beside Nesi, there're two other CCS formalisations. One
+Beside Nesi, there're three other CCS formalisations. One
 is done in Isabelle/HOL (based on Nominal datatypes) in 2010, by Jesper Bengtson as part of his PhD
@@
 and covers the very basic properties of strong/weak equivalence and observational
-congruence.
+congruence. The last one was done by Chaudhuri et
+al.\cite{chaudhuri2014formalization} using Abella, this work
+particularily focus on bisimulation up to techniques while the CCS
+type doesn't have restriction, recursion and relabelling operators.

### 2018-06-13 express2018/equa.tex
text
Stage work
A little more compression, release all locks except "bisim"
compression

@@
   a \emph{system of equations}. (There is one equation for each variable $X_i$.)
-\qed\end{definition}
+\end{definition}
 
@@
 if for each $i$ it holds
-that $P_i \wb E_i [\til P]$.
+that $P_i \wb E_i [\til P]$;
 
-\item the  system has 
-\emph{a unique solution for $\wb$}  if whenever 
+\item it %the  system
+ has \emph{a unique solution for $\wb$}  if whenever 
  $\til P$ and $\til Q$ are both solutions for $\wb$, then $\til P \wb
- \til Q$. \qed
+ \til Q$. 
 \end{itemize} 
@@
 is  the process
-$R \defi \recu A . a A$, and   for any other solution $P$ we have $P \wb R$.
+$R \DSdefi \recu A . a A$, and   for any other solution $P$ we have $P \wb R$.
 In contrast, the equation 
@@
 an \behav\  variable only appears  underneath prefixes and sums.
-\qed\end{itemize}
+\end{itemize}
  \end{definition}
@@
 a unique solution
- for $\wb$. \qed
+ for $\wb$.
 \end{theorem}
@@
   consider
- the equation (from \cite{Mil89}) 
-\[ X = \res a (a. X | \outC a) \]
+ the equation (from \cite{Mil89}) $X = \res a (a. X | \outC a)$
 where $X$ is guarded but not sequential. Any processes that does

### 2018-06-13 express2018/conclusions.tex
Stage work
The "almost final" version

--- 2018-06-12 express2018/conclusions.tex
@@
+% \section{To Do}
+% \label{s:todo}
+
+% \finish{discuss multiple equations/contractions}
+
+% The formalisation of multi-variable context (or expressions) and the version of
+% ``unique solutions'' theorems with multiple equations/contractions, is
+% a relative hard problem. To the best of our knowledge, so far there's no formalization (in any kind of
+% process calculi) touching these areas yet. However, we've made a few initial steps
+% of this interesting problem.
+
 \section{Conclusions}
+\label{s:concl}
 
-\finish{discuss multiple equations/contractions}
+We believe that, beside the discovery of the rooted contraction $\rcontr$
+with a more elegant unique solution theorem,
+our CCS formalisation in HOL4 has also
+provided a solid formal framework for future theoretical developments in
+Concurrency Theory, particularily for process algebras like CCS. It's
+easily understandable, with statements extremely close to the original
+textbook. The logic foundations of HOL makes the whole work (or individual
+parts) easily portable to other theorem provers.
+
+Further plan on the formalisation mainly includes: 1) the extension to
+multi-variable equation/contractions. 2) the support of recursion operators in
+CCS context and expressions.
+
+The second author would like to thank many people from HOL community
+for their help in the past two years: Michael Norrish, Thomas Tuerk, 
+Ramana Kumar, Konrad Slind, and Jeremy Dawson. The second half of this
+paper was written in memory of  Mike J. Gordon.

### 2018-06-13 express2018/contraction.tex
The "almost final" version

@@
  the expansion  relation 
-$\expa$ of Definition~\ref{d:expa}. Clause (1) is the same in the two
+$\expa$ \cite{sangiorgi2017equations, arun1992efficiency}
+%of Definition~\ref{d:expa}.
+Clause (1) is the same in the two
 definitions. But in clause (2) expansion uses 
@@
 An expansion 
-$P \contr Q$
+$P \expa Q$
 tells us  that $Q$ is always at least as efficient as $P$, whereas  the
@@
 
-As  bisimilarity  and expansion, so 
-contraction is preserved by all operators but sum.
+As  bisimilarity  and expansion, contraction is preserved by all operators but sum.

### 2018-06-13 express2018/expansion.tex
A little more compression, release all locks except "bisim"
The "almost final" version

@@
 
-The bisimulation proof method can be enhanced by means of \emph{up-to
-  techniques}. One of the most useful auxiliary relations in up-to
-techniques  is the \emph{expansion} relation  $\expa$ \cite{SaMi92}. This is an asymmetric version
-of $\wb$ where $P \expa Q$  means that 
- $P \wb Q$,
-but also that $Q$  achieves  the same as  $P$ 
-with  no more work, i.e. with no more $\tau$ actions.
-Intuitively, if $ P \expa Q$, we can think of $Q$ as being 
-at least as fast as $P$
-or, more generally, we can think that $P$  uses at least as many resources as $Q$.
+% \finish{Remove expansion here? --Chun}
+% The bisimulation proof method can be enhanced by means of \emph{up-to
+%   techniques}. One of the most useful auxiliary relations in up-to
+% techniques  is the \emph{expansion} relation  $\expa$ \cite{SaMi92}. This is an asymmetric version
+% of $\wb$ where $P \expa Q$  means that 
+%  $P \wb Q$,
+% but also that $Q$  achieves  the same as  $P$ 
+% with  no more work, i.e. with no more $\tau$ actions.
+% Intuitively, if $ P \expa Q$, we can think of $Q$ as being 
+% at least as fast as $P$
+% or, more generally, we can think that $P$  uses at least as many resources as $Q$.
 
-\begin{definition}[expansion]
-\label{d:expa}
-A process relation ${\R}$ 
- is an {\em  expansion} if, whenever
-we have $P\RR Q$, %for all $\mu$ 
-\begin{enumerate}
-\item   $P \arr\mu P'$ implies that there is $Q'$ with $Q \arcap \mu
-  Q'$
- and $P' \RR Q'$;
-\item 
-    $Q \arr\mu Q'$   implies that there is $P'$ with $P \Arr \mu
- P'$ and $P' 
-\RR Q'$.
-\end{enumerate}
- $P$  {\em expands} $Q$, written
-$P  \expa Q$, 
-if $P \RR Q$,  for some expansion $\R$. 
-\end{definition}
+% \begin{definition}[expansion]
+% \label{d:expa}
+% A process relation ${\R}$ 
+%  is an {\em  expansion} if, whenever
+% we have $P\RR Q$, %for all $\mu$ 
+% \begin{enumerate}
+% \item   $P \arr\mu P'$ implies that there is $Q'$ with $Q \arcap \mu
+%   Q'$
+%  and $P' \RR Q'$;
+% \item 
+%     $Q \arr\mu Q'$   implies that there is $P'$ with $P \Arr \mu
+%  P'$ and $P' 
+% \RR Q'$.
+% \end{enumerate}
+%  $P$  {\em expands} $Q$, written
+% $P  \expa Q$, 
+% if $P \RR Q$,  for some expansion $\R$. 
+% \end{definition}
 
-As bisimilarity, expansion is preserved by all operators but sum.
+% As bisimilarity, expansion is preserved by all operators but sum.
 %An example of up-to technique involving expansion is

### 2018-06-13 express2018/formal.tex
The "almost final" version

@@
 
-HOL4 is written in Standard ML (or ML for abbreviation). This single language plays three roles here:
+HOL4 is written in Standard ML (ML for abbreviation), which plays three roles here:
 \begin{enumerate}
 \item It serves as the underlying implementation language for the core HOL engine;
-\item It's used to implement tactics (and tacticals) for automatic theorem proving;
-\item It's used as the command language of the interactive HOL system.
+\item It's used to implement tactics (and tacticals) for writing proofs;
+\item It's used as the command language of the HOL interactive shell.
 \end{enumerate}
 Besides, HOL4 users can write arbitrary applications which leverages
-the theorem proving facility.
+the theorem proving facility. The HOL logic language, on the other
+side, is more close to Classic ML, in which the early HOL systems were built.
 

### 2018-06-13 express2018/part2.tex
The "almost final" version

--- 2018-06-13 express2018/part2.tex
@@
 % used above lemma again to convert the traces back to weak transitions.
-
-The statement of the final unique solution of contractions theorem is
-the following (\texttt{WGS} is a weakly guarded context without direct
+Below is the formally proved version of
+Theorem~\ref{t:contraBisimulationU}: (Here \texttt{WGS} stands for weakly guarded context without direct
 sums)
@@
 The formal proof of ``unique solution of rooted contractions theorem''
-(Thm.\; \ref{t:rcontraBisimulationU}) has the
-same initial proof steps as Thm.\; ref{{t:contraBisimulationU}} plus a
+(Theorem~\ref{t:rcontraBisimulationU}) has the
+same initial proof steps as Theorem~\ref{t:contraBisimulationU} plus a
 little more steps to handle the rooted bisimilarity at conclusion. (In the thesis work, the conclusion of this theorem
@@
 the precongruence of rooted contracion, we can naturally use the
-normal version of weakly guarded expressions with direct sums included.
-
+normal version of weakly guarded expressions with direct sums
+included. Below is the formally proved version of Theorem~\ref{t:rcontraBisimulationU}:
 \begin{alltt}

### 2018-06-13 express2018/related.tex
The "almost final" version

@@
 automatically prove theorems showning bisimilarity of CCS
-processes.\footnote{The work is ported (by the 2nd author) from
-HOL88 to latest HOL4, with small improvements on existing work, then
-added the theory of context and (pre)congruence, coarsest
-(pre)congruence contained in bisimilarity, bisimulation up to,
-expansion, contraction, and unique solution of
-equations/expansions/contractions et al, these additions have doubled
-the size of original work.}
+processes.%
+% \footnote{The work is ported (by the 2nd author) from
+% HOL88 to latest HOL4, with small improvements on existing work, then
+% added the theory of context and (pre)congruence, coarsest
+% (pre)congruence contained in bisimilarity, bisimulation up to,
+% expansion, contraction, and unique solution of
+% equations/expansions/contractions et al, these additions have doubled
+% the size of original work.}
 

### 2018-06-13 express2018/sos.tex
finished "Related"; fixed "sos"; in-progress "conclusions" (the todo)
The "almost final" version

@@
 
-\subsection{CCS and transitions based on SOS rules}
+\subsection{CCS and its transitions by SOS rules}
 
@@
   \\
-recursion & $A$ with $A\Defi P$ & \texttt{rec A P} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P}} \\
+recursion & $A$ with $A\Defi P$ & \texttt{rec A P} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P}}
+  \\
+\hline
 input action & $a$ & \texttt{label (name a)} & \HOLinline{\HOLConst{In} \HOLFreeVar{a}} \\
@@
   definitions} on the 3-ary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL4's
-\texttt{Hol_reln} function.\footnote{\texttt{Hol_reln} also
-gives us a fix-point theorem and induction principle for the
-relation, otherwise statements like ``$\textbf{0}$ has no transition''
-could not be proved.}
+\texttt{Hol_reln} function.
 
@@
   taking a CCS process and returning a theorem indicating all its direct transitions.
-
 For instance, we know that the process $(a.0 | \bar{a}.0)$ have three

### 2018-06-14 express2018/formal.tex
text

@@
 code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}. The
-work consists of about 20,000 lines of proof scripts in Standard ML,
-derived from an early work \cite{Nesi:1992ve} by Monica Nesi in 1992-1995.
+work consists of about 20,000 lines of proof scripts in Standard ML
+(and that follows the pioneering work by Nesi \cite{Nesi:1992ve}, in
+1992-1995).
 
@@
 \end{enumerate}
-Besides, HOL4 users can write arbitrary applications which leverages
-the theorem proving facility. The HOL logic language, on the other
+HOL4 users can write arbitrary applications which leverage
+the theorem proving facility. 
+\iflong
+The HOL logic language, on the other
  side, is more close to Classic ML, in which the early HOL systems were built.
+\DS{removed the sentence because  it did not
+  seem important} 
+\fi
 

### 2018-06-14 express2018/formal.tex
text

@@
 choice operator, axiom of infinity, and rank-1 polymorphim (type
-variables). HOL4 implemented the original HOL Logic, while
-some other theorem provers of the HOL family (e.g. Isabelle/HOL) added
-further extensions (they made the formal language more powerful,
-but they also bring the possibilities that the entire logic becomes inconsistent).
-The HOL Logic has considerability simpler logic
-foundations than most other theorem provers, e.g. Coq. As a result,
+variables). HOL4 implements the original HOL Logic, 
+in contrast with 
+ other theorem provers of the HOL family (e.g. Isabelle/HOL) that have
+made extensions
+%  (they made the formal language more powerful,
+% but they also bring the possibilities that the entire logic becomes
+% inconsistent). 
+Indeed the HOL Logic has considerability simpler logic
+foundations than most other theorem provers. %, e.g. Coq. 
+As a result,
 formal theories in HOL can be easily migrated (sometimes even
@@
 
-In contrast with the theorems in the first part of the paper, in the
+In the
 formalisation we consider only single equations/contractions. 
-This considerably simplifies the  reading of the HOL scripts. 
-The extension of the work to multiple equations/contractions is
-discussed in Section~\ref{s:concl}.
+This considerably simplifies the  reading of the HOL scripts (on 
+the extension  to multiple equations/contractions
+see also  Section~\ref{s:concl}).
 

### 2018-06-14 express2018/sos.tex
The "almost final" version
text

@@
 CCS types built on top of it) 
- depends on the choice of initial  type $\beta$.
+ depends on the choice of the initial  type $\beta$.
 
 The core datatype ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'', accounting for the CCS syntax, is then defined as an inductive
-datatype in HOL, based on its Datatype package: ($\alpha$ is the type
-variable for recursion variables) 
+datatype in HOL, based on its Datatype package ($\alpha$ is the type
+variable for recursion variables): 
 \begin{lstlisting}
@@
 
-We have added some  grammar support using HOL's powerful pretty printer, to represent CCS
-processes in more readable forms (as shown in the ``HOL (abbrev.)''
-column in Table \ref{tab:ccsoperator}, the rest of table has listed the notation of typical CCS processes and
-major operators supported by above definition). For restriction
-operator, we chose to takes a set of names, rather than a
-  single name as in the  CCS syntax, to prevent the formalisation
-  efforts on the equivalence of CCS processes with different order of
-  nested restrictions. Also, we don't assume that al recursion are
+We have added some  grammar support,
+ using HOL powerful `pretty printer', to represent CCS
+processes in more readable forms (see the `HOL (abbrev.)'
+column of Table \ref{tab:ccsoperator}; the table summarises 
+the main syntactic notations for CCS). For the restriction
+operator, we have chosen to allow a  set of names as a parameter, rather than a
+  single name as in the ordinary  CCS syntax; this simplifies 
+the manipulation of 
+ processes with different orders of
+  nested restrictions.
+ Also, we don't assume that al recursion are
   guarded, i.e. any term like \texttt{var X} must appear in \texttt{P} of \texttt{rec X P}.
+\finish{do not understand above}
 
@@
 \end{alltt}
-
-Here the rule \texttt{[REC]} (Recursion)
+\finish{notation above and below: all E' maybe should be P'} 
+The rule \texttt{[REC]} (Recursion)
  says that if we substitute all appearences of variable $A$ in $E$ to
@@
 \texttt{Hol_reln} function.
+\finish{explain what \texttt{Hol_reln} is}
 
-The ultimate result (initially done by Nesi)
-at this point, is a complex Standard ML function
+A useful function that we have defined, exploiting the interplay
+between HOL4 and Standard ML (and following an idea by Nesi \cite{...})
+ is a complex Standard ML function
   taking a CCS process and returning a theorem indicating all its direct transitions.
-For instance, we know that the process $(a.0 | \bar{a}.0)$ have three
+For instance, we know that the process $(a.0 | \bar{a}.0)$ has three
 possible transitions: $(a.0 | \bar{a}.0) \overset{a}{\longrightarrow}
@@
 \overset{\tau}{\longrightarrow} (0 | 0)$.
-To completely decide all possible transitions, if done manually, the
+To completely describe all possible transitions of a process, if done manually, the
 following facts should be proved:
 \begin{enumerate}
+\iflong
 \item there exists transitions from $(a.0 | \bar{a}.0)$ (optional);
+\fi
 \item the correctness for each of the transitions by SOS rules;
@@
 \end{enumerate}
-For large complex processes it's surprisingly hard to manually prove the
-non-existence of transitions. Instead, if we call the ML function \texttt{CCS\_TRANS\_CONV} on the
-root process $(a.0 | \bar{a}.0)$:
+For large complex processes it is surprisingly hard to manually prove the
+non-existence of transitions.  Hence the usefulness of appealing to 
+the new  function \texttt{CCS\_TRANS\_CONV}. 
+For instance the function
+called on the  process $(a.0 | \bar{a}.0)$ thus
 \begin{lstlisting}
-> CCS_TRANS_CONV
-	 ``par (prefix (label (name "a")) nil)
+> CCS_TRANS_CONV ``par (prefix (label (name "a")) nil)
                        (prefix (label (coname "a")) nil)``
 \end{lstlisting}
-We immediately get the following theorem, which completely answers the question:
+returns the following theorem, indeed describing all immediate
+transitions of the process:
 \begin{alltt}

### 2018-06-14 express2018/related.tex
Further mentioned pi-calculi formalization at Sweden

@@
 thesis project \cite{bengtson2010formalising}, available in Isabelle's Archive of Formal
-Proofs (AFP)\footnote{\url{https://www.isa-afp.org/entries/CCS.html}}. He has formalized
+Proofs (AFP) \footnote{\url{https://www.isa-afp.org/entries/CCS.html}}. He has formalized
 classic properties for strong/weak equivalence and observational
 congruence, however the CCS grammar doesn't include process constants
-(or recursion operators). And the proved theorems also look quite
-different with their forms in textbooks.
+(or recursion operators), and the proved theorems also look quite
+different with their forms in textbooks. On the other side, Jesper
+Bengtson and Joachim Parrow made great progress on pi-calculus formalization and
+proved that the algebraic axiomatization of bisimulation
+equivalence in the pi-calculus is sound and complete. \cite{bengtson2007completeness}
 The other formalisation is based on Coq, done by Solange
@@
 congruence. The last one was done by Chaudhuri et
-al.\cite{chaudhuri2014formalization} using Abella, this work
+al. \cite{chaudhuri2014formalization} using Abella, this work
 particularily focus on bisimulation up to techniques while the CCS

### 2018-06-14 express2018/sos.tex
Fixed remain issues in sos.tex

@@
   nested restrictions.
- Also, we don't assume that al recursion are
-  guarded, i.e. any term like \texttt{var X} must appear in \texttt{P} of \texttt{rec X P}.
-\finish{do not understand above}
+ Also, we don't assume that the uses of \texttt{var} are
+  guarded by \texttt{rec} of the same variable.
 
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E}\hfill\texttt{[PREFIX]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{+} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[SUM1]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{+} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[SUM2]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sp{\prime}}\hfill\texttt{[PAR1]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[PAR2]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} (\HOLConst{COMPL} \HOLFreeVar{l})\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
-   \HOLFreeVar{E} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sb{\mathrm{2}}}\hfill\texttt{[PAR3]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} ((\HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}}) \HOLSymConst{\HOLTokenDisj{}} (\HOLFreeVar{u} \HOLSymConst{=} \HOLConst{label} \HOLFreeVar{l}) \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{E\sp{\prime}}\hfill\texttt{[RESTR]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{rf}\hfill\texttt{[RELABELING]}
-\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{E} (\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}) \HOLFreeVar{X} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[REC]}
+\HOLTokenTurnstile{} \HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P}\hfill\texttt{[PREFIX]}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{+} \HOLFreeVar{Q} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[SUM1]}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{Q} \HOLSymConst{+} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[SUM2]}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q}\hfill\texttt{[PAR1]}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{Q} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{Q} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[PAR2]}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLTokenTransBegin\HOLConst{label} (\HOLConst{COMPL} \HOLFreeVar{l})\HOLTokenTransEnd \HOLFreeVar{Q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q\sp{\prime}}\hfill\texttt{[PAR3]}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{Q} \HOLSymConst{\HOLTokenConj{}} ((\HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}}) \HOLSymConst{\HOLTokenDisj{}} (\HOLFreeVar{u} \HOLSymConst{=} \HOLConst{label} \HOLFreeVar{l}) \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{Q}\hfill\texttt{[RESTR]}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLConst{relab} \HOLFreeVar{P} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{Q} \HOLFreeVar{rf}\hfill\texttt{[RELABELING]}
+\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{P} (\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{P}) \HOLFreeVar{X} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[REC]}
 \end{alltt}
-\finish{notation above and below: all E' maybe should be P'} 
+
 The rule \texttt{[REC]} (Recursion)
@@
   definitions} on the 3-ary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL4's
-\texttt{Hol_reln} function.
-\finish{explain what \texttt{Hol_reln} is}
+\texttt{Hol_reln} function (inductive relation package).
 
 A useful function that we have defined, exploiting the interplay
-between HOL4 and Standard ML (and following an idea by Nesi \cite{...})
+between HOL4 and Standard ML (and following an idea by Nesi \cite{Nesi:1992ve})
  is a complex Standard ML function

### 2018-06-14 express2018/related.tex
Make some more spaces

@@
 
-Beside Nesi, there're three other CCS formalisations. One
+Beside Nesi, there exist other CCS formalisations. One
 is done in Isabelle/HOL (based on Nominal datatypes) in 2010, by Jesper Bengtson as part of his PhD
@@
 (or recursion operators), and the proved theorems also look quite
-different with their forms in textbooks. On the other side, Jesper
-Bengtson and Joachim Parrow made great progress on pi-calculus formalization and
-proved that the algebraic axiomatization of bisimulation
-equivalence in the pi-calculus is sound and complete. \cite{bengtson2007completeness}
+different with their forms in textbooks.%
+%  On the other side, Jesper
+% Bengtson and Joachim Parrow made great progress on pi-calculus formalization and
+% proved that the algebraic axiomatization of bisimulation
+% equivalence in the pi-calculus is sound and complete. \cite{bengtson2007completeness}
 The other formalisation is based on Coq, done by Solange

### 2018-06-14 express2018/part2.tex
Other changes mainly in part2

@@
 The final relationship between traces and weak transitions is stated
-and proved in the following lemma: (here $us$ as single variable means
+and proved in the following lemma: (here $acts$ as a single variable means
 a list of actions)
 \begin{lemma}
-A weak transition $E\overset{u}{\Rightarrow}E'$ is a just trace with non
+A weak transition $P\overset{u}{\Rightarrow}P'$ is a just trace with non
 empty action list: 1) without any visible label, if $u = \tau$, or 2)
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}}
-   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{us}.
-       \HOLConst{TRACE} \HOLFreeVar{E} \HOLBoundVar{us} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{NULL} \HOLBoundVar{us} \HOLSymConst{\HOLTokenConj{}} \HOLKeyword{if} \HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLKeyword{then} \HOLConst{NO_LABEL} \HOLBoundVar{us}
-       \HOLKeyword{else} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLBoundVar{us}\hfill{[WEAK_TRANS_AND_TRACE]}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}}
+   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{acts}.
+       \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{acts} \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{NULL} \HOLBoundVar{acts} \HOLSymConst{\HOLTokenConj{}}
+       \HOLKeyword{if} \HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLKeyword{then} \HOLConst{NO_LABEL} \HOLBoundVar{acts} \HOLKeyword{else} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLBoundVar{acts}\hfill{[WEAK_TRANS_AND_TRACE]}
 \end{alltt}
@@
 
-To finish the proof of Lemma~\ref{l:ruptocon}, we use the  above
+To finish the proof of Lemma~\ref{l:ruptocon}, we have used the  above
 result to freely switch between weak transitions and traces
@@
 \begin{alltt}
-UNIQUE_SOLUTION_OF_CONTRACTIONS:
 \HOLTokenTurnstile{} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
 \HOLBoundVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
+\hfill{[UNIQUE_SOLUTION_OF_CONTRACTIONS]}
 \end{alltt}
@@
 same initial proof steps as Theorem~\ref{t:contraBisimulationU} plus a
-little more steps to handle the rooted bisimilarity at conclusion. (In the thesis work, the conclusion of this theorem
-is weak bisimilarity, and the proof is exactly the same as Unique
-solution of contractions theorem. Now we got a stronger conclusion
-using observational congruence, and the previous version becomes a
-trivial collorary of the current version.) The
+little more steps to handle the rooted bisimilarity at conclusion. The
 two proofs are quite similar, mostly because the only property we need
@@
 normal version of weakly guarded expressions with direct sums
-included. Below is the formally proved version of Theorem~\ref{t:rcontraBisimulationU}:
+included. Below is the formally verified version of
+Theorem~\ref{t:rcontraBisimulationU}:
 \begin{alltt}
-UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS:
 \HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
 \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
+\hfill{[UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS]}
 \end{alltt}
+
+See how similar it is with Milner's original ``unique solution of
+equations'' theorem for strong bisimilarity ($\sim$) in which the same
+weak guardness (\texttt{WG}) is required:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
+\HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}\hfill{[STRONG_UNIQUE_SOLUTION]}
+\end{alltt}
+
+Or our Theorem~\ref{t:rcontraBisimulationU} can be seen as a more
+applicable version of Milner's ``unique solution of
+equations'' theorem for rooted bisimilarity ($\rapprox$), which has more
+restrictions on equations:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
+\HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
+\hfill{[OBS_UNIQUE_SOLUTION]}
+\end{alltt}

### 2018-06-14 express2018/related.tex
Other changes mainly in part2

--- 2018-06-14 express2018/related.tex
@@
 She was mainly focusing on writing decision procedures (ML functions) which
-automatically prove theorems showning bisimilarity of CCS
+automatically prove theorems showing the bisimilarity of two given CCS
 processes.%
@@
 
-Beside Nesi, there're three other CCS formalisations. One
-is done in Isabelle/HOL (based on Nominal datatypes) in 2010, by Jesper Bengtson as part of his PhD
-thesis project \cite{bengtson2010formalising}, available in Isabelle's Archive of Formal
-Proofs (AFP) \footnote{\url{https://www.isa-afp.org/entries/CCS.html}}. He has formalized
-classic properties for strong/weak equivalence and observational
-congruence, however the CCS grammar doesn't include process constants
-(or recursion operators), and the proved theorems also look quite
-different with their forms in textbooks. On the other side, Jesper
-Bengtson and Joachim Parrow made great progress on pi-calculus formalization and
+Beside Nesi, there exist other CCS formalisations. Jesper Bengtson
+formalized CCS, $\pi$-calculi and $\psi$-calculi in his PhD
+thesis \cite{bengtson2010formalising} using Isabelle/HOL and its
+nominal logic. For CCS, he has formalized
+basic properties for strong/weak equivalence and observational
+congruence, however the CCS syntax doesn't have constants
+(or recursion operator), and the proved theorems also look quite
+different with their forms in textbooks.
+On the other side, Jesper
+Bengtson and Joachim Parrow made great progress on $\pi$-calculus formalization and
 proved that the algebraic axiomatization of bisimulation
-equivalence in the pi-calculus is sound and complete. \cite{bengtson2007completeness}
+equivalence in the $\pi$-calculi is sound and complete. \cite{bengtson2007completeness}
 The other formalisation is based on Coq, done by Solange

### 2018-06-14 express2018/context.tex
Other changes mainly in part2
text

@@
 
-We need to find a suitable formal definition of 
-context. There're multiple ways. Here we have chosen to use $\lambda$-expressions (typed
-$CCS\rightarrow CCS$) to represent a (multi-hole) 
-context. The definition is inductive:
+% We need to find a suitable formal definition of 
+% context. There're multiple ways. Here
+
+We have chosen to use $\lambda$-expressions (typed
+$CCS\rightarrow CCS$) to represent  (multi-hole) 
+contexts. The definition is inductive:
 \begin{alltt}
@@
 
-A \emph{weak guarded} context is a context in which all holes appears
-in the sub-expression of prefixed processes. We can easily define it
-following the same idea:
+\finish{
+The definintion of congruence  requires the relation to be an equivalence. This is correct.
+However the def of precongruence does not require the relation to be a preorder (ie. reflexive and transitive). Can it be added (only in the paper for now) ?
+}
+
+A \emph{weakly guarded} context is a context in which each hole is
+underneath a  prefix (where \texttt{WG} stands for weakly guarded):
 \begin{alltt}
@@
 \end{alltt}
-(Notice the differences between a weak guarded context and a normal
-one: $\lambda t. t$ is not weakly guarded as the variable is directly
-exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
-guarded as long as $e[\cdot]$ is a context, not necessary weakly guaded.)
+% (Notice the differences between a weak guarded context and a normal
+% one: $\lambda t. t$ is not weakly guarded as the variable is directly
+% exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
+% guarded as long as $e[\cdot]$ is a context, not necessary weakly guarded.)
 
-It's a similar process to define strongly guarded context
-(\texttt{SG}), sequential context (\texttt{SEQ}) and their
-variants without direct sums (\texttt{GCONTEXT}, \texttt{WGS},
+In the same manner we can  define \emph{strongly guarded contexts}
+(\texttt{SG}), sequential contexts (\texttt{SEQ}), and their
+variants without  sums (\texttt{GCONTEXT}, \texttt{WGS},
 \texttt{GSEQ}). Some lemmas about their relationships have very long
@@
 inductions on context structures.%  For example, one such
+
+\finish{above: not consistent with the terminology in
+  the first part; we should change part 1 to use  `strongly guarded'}
+\finish{also: in part 1 the theorems about unique solutions of plain
+  contractions say that sums can appear but only in their guarded
+  form; is this what is done in the formalisation? (this is a minor
+  point, we can adjust it later, since we do not show here the HOL definitions)}
+
 % lemma says, for any  context $E$ which is both strongly guarded

### 2018-06-14 express2018/context.tex
Unlock context

@@
 \begin{alltt}
-\HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
+\HOLTokenTurnstile{} \HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
+   \HOLConst{PreOrder} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}}
    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
-\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})\hfill{[precongruence_def]}
-\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLConst{precongruence} \HOLFreeVar{R}\hfill{[congruence_def]}
+\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})
+\HOLTokenTurnstile{} \HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
+   \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
+\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})
 \end{alltt}
-
-\finish{
-The definintion of congruence  requires the relation to be an equivalence. This is correct.
-However the def of precongruence does not require the relation to be a preorder (ie. reflexive and transitive). Can it be added (only in the paper for now) ?
-}
 
@@
 % guarded as long as $e[\cdot]$ is a context, not necessary weakly guarded.)
-
-In the same manner we can  define \emph{strongly guarded contexts}
-(\texttt{SG}), sequential contexts (\texttt{SEQ}), and their
-variants without  sums (\texttt{GCONTEXT}, \texttt{WGS},
-\texttt{GSEQ}). Some lemmas about their relationships have very long
-(but trivial) formal proofs due to multiple levels of
-inductions on context structures.%  For example, one such
-
-\finish{above: not consistent with the terminology in
-  the first part; we should change part 1 to use  `strongly guarded'}
-\finish{also: in part 1 the theorems about unique solutions of plain
-  contractions say that sums can appear but only in their guarded
-  form; is this what is done in the formalisation? (this is a minor
-  point, we can adjust it later, since we do not show here the HOL definitions)}
+A \emph{strongly guarded} (\texttt{SG}) context is a context in which
+ each hole is underneath a visible prefix:
+\begin{alltt}
+\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{e}.
+\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{label} \HOLBoundVar{l}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
+\HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
+\HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLSymConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLBoundVar{e} \HOLBoundVar{t}))) \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
+\HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})\hfill{[SG_rules]}
+\end{alltt}
+And a \emph{sequential} (\texttt{SEQ}) context is a context in which each hole is under prefix or sums:
+ \begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{t}) \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
+\HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{p})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
+\HOLConst{SEQ} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{SEQ} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})\hfill{[SEQ_rules]}
+\end{alltt}
+In the same manner, we can also define all
+variants of above concepts without \emph{direct} sums (\texttt{GCONTEXT}, \texttt{WGS} and
+\texttt{GSEQ}). A large amount of lemmas must be proved for their relationships and properties of compositions. These proofs all have long (and trivial) steps due to multiple levels of
+inductions on their structures.%  For example, one such
 
@@
 % \begin{alltt}
-% \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
-\HOLConst{SG} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{H}.
-\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} (\HOLBoundVar{H} \HOLSymConst{\HOLTokenCompose} \HOLBoundVar{E})
+
 % \end{alltt}

### 2018-06-14 express2018/part2.tex
text

@@
 
-The major difficulties in the formalisation of the results about unique solution of
-contractions are in the proof of lemma~\ref{l:ruptocon}; in particular, it
-uses an induction on the length of weak transitions. 
-For this, one could introduced a refined form of weak transition relation
-enriched with its length, but such a non-standard relation finds no
-other uses beside proving our target theorem. Another way is to use 
-traces instead, as it shows more clearly all passing actions inside a
-trace, making formal reasoning easier.
+A delicate point in the formalisation of the results about unique solution of
+contractions are the proof of lemma~\ref{l:ruptocon} and alike lemmas;
+in particular, there is
+ an induction on the length of weak transitions. 
+For this, rather than 
+ introducing a refined form of weak transition relation
+enriched with its length, 
+we found it more elegant  to  work with traces
+(a motivation for this is to set the ground for extensions of this
+formalisation work to trace equivalence in place of bisimilarity).
 
-We represent a trace by the initial process, the final derivative, and
-the list of actions performed. 
-To formalise this, 
-we first introduce 
-the Reflexive Transitive Closure with a
-List (LRTC);
+% but such a non-standard relation finds no
+% other uses beside proving our target theorem. Another way is to use 
+% traces instead, as it shows more clearly all passing actions inside a
+% trace, making formal reasoning easier.
 
-A trace is represented by the beginning and ending CCS processes, plus
-a list of action it passes. Insteading of defining it directly, we
-have first defined a new concept called Reflexive Transitive Closure with a
-List (LRTC):
-given a  labelled transition relation $R$, \HOLinline{\HOLConst{LRTC}
+% We represent a trace by the initial process, the final derivative, and
+% the list of actions performed. 
+% To formalise this, 
+% we first introduce 
+% the Reflexive Transitive Closure with a
+% List (LRTC);
+
+A trace is represented by the initial and final processes, plus
+a list of actions  so performed.
+For this, we first 
+ define the Reflexive Transitive Closure with a
+List (\texttt{LRTC}):
+given a  labelled transition relation \texttt{R}, 
+then
+\HOLinline{\HOLConst{LRTC}
   \HOLFreeVar{R}} builds 
-the possible traces derived from $R$.
+the possible traces derived from \texttt{R}:
 \begin{alltt}
@@
 \end{alltt}
- Then the traces for the  CCS processes
+The traces for a  CCS processes
 are obtained
- by combining LRTC with the (strong) CCS transition
-relation:
+ by combining \texttt{LRTC} with the  CCS transition
+relation  \texttt{TRANS}:
 \begin{alltt}
@@
 \end{alltt}
-
-If there's at most one visible action (label) in the list of actions of a trace,
-then the trace is also a weak transition. We divided this observation
-into two cases: no label and unique label. The definition of ``no
-label'' in an action list is easy and clear (\texttt{MEM} is for
-testing if an element is \emph{member} of a list):
+If there is at most one visible action (i.e., a label) 
+in the list of actions of a trace,
+then the trace  also represents a weak transition. Here 
+we distinguish two cases: no label and unique label. The definition of `no
+label' in an action list is easy (below \texttt{MEM} 
+tests if a given element is a member of a list):
 \begin{alltt}
@@
 \end{alltt}
-while the definition of ``unique label'' can be done in many ways, in
-which we have chosen to use the version learnt from Robert Beers in
-a private discussion which prevented counting or filtering in the list:
+The definition below of `unique label'
+%  can be done in many ways, in
+% which we have chosen to use the version learnt from Robert Beers in
+% a private discussion which 
+avoids counting or filtering in a list;
+it says that a label is unique in an action list iff it there is no other
+label in the remainder part of the list:
 \begin{alltt}
@@
 \end{alltt}
-It says, a label is unique in an action list iff it there's no other
-labels in the rest part of the list.
 
 The final relationship between traces and weak transitions is stated
-and proved in the following lemma: (here $acts$ as a single variable means
-a list of actions)
-\begin{lemma}
-A weak transition $P\overset{u}{\Rightarrow}P'$ is a just trace with non
-empty action list: 1) without any visible label, if $u = \tau$, or 2)
-$u$ is the unique label in the list, if $u \neq \tau$.
+and proved in the following theorem
+(where the  variable $acts$ stands for
+a list of actions); 
+it says that a
+ weak transition $P\overset{u}{\Rightarrow}P'$ is a  trace with a
+ non-empty 
+action list, i.e., either without any (visible) label if $u = \tau$, orelse 
+if $u \neq \tau$ then $u$ is the unique label in the list: 
+%\begin{lemma}
+% A weak transition $P\overset{u}{\Rightarrow}P'$ is a just trace with non
+% empty action list: 1) without any visible label, if $u = \tau$, or 2)
+% $u$ is the unique label in the list, if $u \neq \tau$.
 \begin{alltt}
@@
 \end{alltt}
-\end{lemma}
+%\end{lemma}
 
@@
 % used above lemma again to convert the traces back to weak transitions.
-Below is the formally proved version of
-Theorem~\ref{t:contraBisimulationU}: (Here \texttt{WGS} stands for weakly guarded context without direct
-sums)
+
+\finish{would not it have been good to actually see the formalisation of 
+lemma~\ref{l:ruptocon}? (also to see how trace are actually used in
+the induction)}
+
+Below is the formalisation of
+Theorem~\ref{t:contraBisimulationU} (where \texttt{WGS} stands for
+`weakly guarded context with weakly-guarded sums')
 \begin{alltt}
@@
 (Theorem~\ref{t:rcontraBisimulationU}) has the
-same initial proof steps as Theorem~\ref{t:contraBisimulationU} plus a
-little more steps to handle the rooted bisimilarity at conclusion. The
-two proofs are quite similar, mostly because the only property we need
-from (rooted) contraction is its precongruence. Once we have proved
-the precongruence of rooted contracion, we can naturally use the
-normal version of weakly guarded expressions with direct sums
-included. Below is the formally verified version of
+same initial proof steps as Theorem~\ref{t:contraBisimulationU}; 
+it then requires a
+few steps to handle  rooted bisimilarity in the conclusion. 
+At the end the
+two proofs are very similar, mostly because the only property we need
+from (rooted) contraction is its precongruence. 
+(Having proved
+the precongruence property for the rooted contracion, 
+we can use the
+plain version of weakly-guarded expressions with sums
+included.) Below is the formally verified version of
 Theorem~\ref{t:rcontraBisimulationU}:
@@
 
-See how similar it is with Milner's original ``unique solution of
-equations'' theorem for strong bisimilarity ($\sim$) in which the same
-weak guardness (\texttt{WG}) is required:
+Having no constraints on sums, the result is
+ similar with Milner's original `unique solution of
+equations' theorem for \emph{strong} bisimilarity ($\sim$)~--- 
+the same
+weakly guarded  condition (\texttt{WG}) is required:
 \begin{alltt}
@@
 
-Or our Theorem~\ref{t:rcontraBisimulationU} can be seen as a more
-applicable version of Milner's ``unique solution of
-equations'' theorem for rooted bisimilarity ($\rapprox$), which has more
-restrictions on equations:
+In contrast, Milner's `unique solution of
+equations' theorem for rooted bisimilarity ($\rapprox$)
+has more severe constraints: 
+% Or our Theorem~\ref{t:rcontraBisimulationU} can be seen as a more
+% applicable version of Milner's ``unique solution of
+% equations'' theorem for rooted bisimilarity ($\rapprox$), which has more
+% restrictions on equations:
 \begin{alltt}

### 2018-06-14 express2018/related.tex
text

--- 2018-06-14 express2018/related.tex
@@
 
-Monica Nesi formalized both pure CCS \cite{Nesi:1992ve} and Value-Passing CCS
-\cite{Nesi:2017wo} in old versions of HOL theorem prover, but the
-related proof scripts were not publically available.\footnote{Part of
- the formalization of pure CCS can be found at \url{https://github.com/binghe/informatica-public/tree/master/CCS2/CCS-Nesi}.}
-She was mainly focusing on writing decision procedures (ML functions) which
-automatically prove theorems showning bisimilarity of CCS
+The closest to our work is Monica Nesi's.
+She made the first formalisation of CCS, using
+early versions of the HOL theorem prover (HOL88)\footnote{Part of
+ the formalization of pure CCS can be found at \url{https://github.com/binghe/informatica-public/tree/master/CCS2/CCS-Nesi}.}.
+Nesi's  main focus has been 
+ decision procedures (as ML functions) for
+automatically proving bisimilarities between CCS
 processes.%
+Her work has been a basis for ours. However the differences are
+substantial, both because we have used the most recent version of HOL
+(e.g., including support for coinduction) and because of the size of
+the body of the CCS theory considered.
+
+\finish{above: is it fair?}
+
+% formalized both pure CCS \cite{Nesi:1992ve} and Value-Passing CCS
+% \cite{Nesi:2017wo} in old versions of HOL theorem prover, but the
+% related proof scripts were not publically available.
 % \footnote{The work is ported (by the 2nd author) from
@@
 
-Beside Nesi, there exist other CCS formalisations. One
-is done in Isabelle/HOL (based on Nominal datatypes) in 2010, by Jesper Bengtson as part of his PhD
-thesis project \cite{bengtson2010formalising}, available in Isabelle's Archive of Formal
-Proofs (AFP) \footnote{\url{https://www.isa-afp.org/entries/CCS.html}}. He has formalized
-classic properties for strong/weak equivalence and observational
-congruence, however the CCS grammar doesn't include process constants
-(or recursion operators), and the proved theorems also look quite
-different with their forms in textbooks.%
+%Beside Nesi, there exist other CCS formalisations. 
+Bengtson,  Parrow, and  Weber
+have made a substantial formalisation work 
+on CCS, $\pi$-calculi and $\psi$-calculi 
+into Isabelle/HOL and its
+nominal logic
+ \cite{bengtson2010formalising,bengtson2007completeness,DBLP:journals/jar/BengtsonPW16}. The main focus has been 
+ $\psi$-calculi and the handling  of name binders.
+The formalisations also  include
+ basic properties for strong and weak bisimilarities  such as
+ substitutivity and 
+ algebraic laws.
+% Jesper Bengtson's PhD thesis 
+%  \cite{bengtson2010formalising} looks  at 
+% formalizations of CCS, $\pi$-calculi and $\psi$-calculi
+% into Isabelle/HOL and its
+% nominal logic. For CCS, 
+% he has 
+%  formalized
+%  basic properties for strong/weak equivalence (congruence, basic
+%  algebraic laws), for a  and observational
+% congruence, however the CCS syntax doesn't have constants
+% (or recursion operator), using replication in place of recursion.
+% The formalisation effort has then been continued 
+%
 % On the other side, Jesper
-% Bengtson and Joachim Parrow made great progress on pi-calculus formalization and
+% Bengtson and Joachim Parrow made great progress on $\pi$-calculus
+% formalization and 
 % proved that the algebraic axiomatization of bisimulation
-% equivalence in the pi-calculus is sound and complete. \cite{bengtson2007completeness}
-The other formalisation is based on Coq, done by Solange
-Coupet-Grimal in 1995, which is part of the
-``coq-contribs'' archive (Coq's official user contributed code)
-\footnote{\url{https://github.com/coq-contribs/ccs}}. This is actually
-a formalisation of transition systems without any algebraic operator,
-and covers the very basic properties of strong/weak equivalence and observational
-congruence. The last one was done by Chaudhuri et
-al. \cite{chaudhuri2014formalization} using Abella, this work
-particularily focus on bisimulation up to techniques while the CCS
-type doesn't have restriction, recursion and relabelling operators.
+% equivalence in the $\pi$-calculi is sound and
+% complete. \cite{bengtson2007completeness} 
+Other formalisation of CCS or related calculi include: 
+ Solange
+Coupet-Grimal, in 
+1995, in Coq (this  is part of the
+``coq-contribs'' archive --- Coq's official user contributed
+code\footnote{\url{https://github.com/coq-contribs/ccs}})  which is
+actually
+a formalisation of transition systems (without an algebraic structure),
+and covers  basic properties of strong and weak bisimilarities;
+and  Chaudhuri et
+al.\   \cite{chaudhuri2014formalization}  in Abella, which
+ focuses on `bisimulation up-to' techniques for strong bisimilarity 
+for  CCS and $\pi$-calculus. Formalisations less related to ours
+include
+ Kahsai and Miculan  \cite{...} for the spi-calculus    in
+Nominal Isabelle; 
+  Hirschkoff  \cite{...} for the $\pi$-calculus    in Coq.
+
+% The other formalisation is based on Coq, done by Solange
+% Coupet-Grimal in 1995, which is part of the
+% ``coq-contribs'' archive (Coq's official user contributed code)
+% \footnote{\url{https://github.com/coq-contribs/ccs}}. This is actually
+% a formalisation of transition systems without any algebraic operator,
+% and covers the very basic properties of strong/weak equivalence and
+% observational 
+% congruence.
+
+\finish{make sure we mention the papers below}
+
+\begin{itemize}
+\item
+Bengtson, J., Parrow, J.: Formalising the pi-calculus using nominal logic. Logical Methods in Computer
+Science
+5
+(2) (2008)
+
+\item 
+  Hirschkoff, D.: A full formalisation of pi-calculus theory in the calculus of constructions. In: E.L. Gunter,
+A.P. Felty (eds.) Proceedings TPHOLs 97,
+LNCS, vol. 1275,  Springer (1997
+
+\item 
+Kahsai, T., Miculan, M.: Implementing spi calculus using nominal techniques. In: 
+ Proceedings CiE 2008,
+LNCS, vol. 5028, Springer (2008)
+\end{itemize}
+
+\finish{in the references, the citation below is not complete: 
+Kaustuv Chaudhuri, Matteo Cimini, Dale Miller:
+A Lightweight Formalization of the Metatheory of Bisimulation-Up-To. CPP 2015: 157-166}

### 2018-06-14 express2018/conclusions.tex
text

@@
 
-\section{Conclusions}
+\section{Conclusions and future work}
 \label{s:concl}
@@
 CCS context and expressions.
+\subsection*{Acknowledgements}
 
-The second author would like to thank many people from HOL community
-for their help in the past two years: Michael Norrish, Thomas Tuerk, 
-Ramana Kumar, Konrad Slind, and Jeremy Dawson. The second half of this
-paper was written in memory of  Mike J. Gordon.
+We would like to thank many people from the HOL community
+for their help in the past two years, in particular: 
+Michael Norrish, Thomas Tuerk, 
+Ramana Kumar, Konrad Slind, and Jeremy Dawson. 
+% The second half of this
+% paper was written in memory of  Mike J. Gordon.

### 2018-06-14 express2018/conclusions.tex
text

@@
 
-We believe that, beside the discovery of the rooted contraction $\rcontr$
-with a more elegant unique solution theorem,
-our CCS formalisation in HOL4 has also
-provided a solid formal framework for future theoretical developments in
-Concurrency Theory, particularily for process algebras like CCS. It's
-easily understandable, with statements extremely close to the original
-textbook. The logic foundations of HOL makes the whole work (or individual
+We have highlighted a formalisation of the theory of CCS in the 
+HOL4 theorem prover. The formalisation has focused on the theory of
+unique solution of equations and contractions. 
+The formalisation has also allowed us to further develop the theory,
+notably the basic properties of rooted contraction, and the unique
+solution theorem for it with respect to rooted bisimilarity. 
+The formalisation brings up and exploits similarities between results
+and proofs for different equivalences and preorders. 
+We think that the statements in the formalisation are easy to read and
+understand, as they remain very close  to  the ordinary  statements of
+the theory of CCS. 
+Moreover, 
+the logic foundations of HOL makes the whole work (or individual
 parts) easily portable to other theorem provers.
 
-Further plan on the formalisation mainly includes: 1) the extension to
-multi-variable equation/contractions. 2) the support of recursion operators in
-CCS context and expressions.
+As future work,  it would be worth extending the current work
+to multiple equations and contractions; and considering other equivalences
+and preorders, notably trace relations.  
+On another line, one could  
+examine the formalisation of  a different approach to unique
+solutions, by Durier et al.\ \cite{DurierHS17}, in which the use of contraction is
+replaced by semantic conditions on process transitions such as
+divergence.
+
+% Further plan on the formalisation mainly includes: 1) the extension to
+% multi-variable equation/contractions. 2) the support of recursion
+% operators in 
+% CCS context and expressions.
+
+% We believe that, beside the discovery of the rooted contraction $\rcontr$
+% with a more elegant unique solution theorem,
+% our CCS formalisation in HOL4 has also
+% provided a solid formal framework for future theoretical developments in
+% Concurrency Theory, particularily for process algebras like CCS. It's
+% easily understandable, with statements extremely close to the original
+% textbook. The logic foundations of HOL makes the whole work (or individual
+% parts) easily portable to other theorem provers.
+
 \subsection*{Acknowledgements}
@@
 We would like to thank many people from the HOL community
-for their help in the past two years, in particular: 
+for their help in the past two years, in particular 
 Michael Norrish, Thomas Tuerk, 
-Ramana Kumar, Konrad Slind, and Jeremy Dawson. 
+Ramana Kumar, Konrad Slind, Robert Beers, and Jeremy Dawson. 
 % The second half of this

### 2018-06-14 express2018/formal.tex
text

@@
 \section{Formalisation}
-
+\label{s:for}
 We highlight here a formalisation of CCS

### 2018-06-14 express2018/intro.tex
The "almost final" version
text

@@
 This method  is important in verification techniques and tools
-based on algebraic reasoning \cite{theoryAndPractice,RosUnder10,BaeBOOK}.
+based on algebraic reasoning \cite{theoryAndPractice,BaeBOOK}.
 
@@
 
-\finish{ I had to remove the reference \cite{Tian:2017wrba} here since it would further
-  weaken this paper. }
+% \finish{ I had to remove the reference \cite{Tian:2017wrba} here
+% since it would further 
+%   weaken this paper. }
 
@@
 
-\paragraph{Structure of the paper}....
+\paragraph{Structure of the paper} 
+Section~\ref{ss:ccs} presens basic background material on CCS,
+including its syntax, operational semantics, bisimilarity and rooted
+bisimilarity. Section~\ref{s:eq} discussed equations and contractions.
+ Section~\ref{ss:new} presents rooted contraction and the related
+ unique-solution result for rooted bisimilarity. Section~\ref{s:for}
+ highlight our formalisation in HOL4. Finally,  Section~\ref{s:rel} and
+ \ref{s:concl} discuss related work, conclusions,  and  a few
+ directions for future work.

### 2018-06-14 express2018/ccs.tex
text

@@
 + \mu_n.P_n$, for some $n \geq 2$. 
-
  The \emph{immediate derivatives} of a
@@
 \end{figure*}
-
 Some standard notations for transitions:  $\Longrightarrow $ is the 

### 2018-06-14 express2018/conclusions.tex
text

@@
 We have highlighted a formalisation of the theory of CCS in the 
-HOL4 theorem prover. The formalisation has focused on the theory of
+HOL4 theorem prover (for lack of space we have not discussed 
+the formalisation of some basic algebraic theory, of the basic
+properties of the expansion preorder,  and of a few
+ versions of `bisimulation up to'
+techniques such as  bisimulation up-to bisimilarity). 
+The formalisation has focused on the theory of
 unique solution of equations and contractions. 

### 2018-06-14 express2018/contraction.tex
Make some more spaces
Fixed cites
text

@@
-\section{Contractions}
+\subsection{Contractions}
 \label{s:mcontr}
@@
 Bisimilarity  contraction is coarser than 
- the expansion  relation 
-$\expa$ \cite{sangiorgi2017equations, arun1992efficiency}
-%of Definition~\ref{d:expa}.
+ the \emph{expansion  relation} 
+$\expa$ \cite{sangiorgi2015equations, arun1992efficiency}. This 
+is a
+preorder widely used in proof techniques for bisimilarity and that 
+intuitively refines bisimilarity by 
+ formalising the idea of `efficiency' between processes.
 Clause (1) is the same in the two
-definitions. But in clause (2) expansion uses 
+preorders. But in clause (2) expansion uses 
 $P \Arr \mu P'$, rather than $P \Arcap \mu P'$; 

### 2018-06-14 express2018/unique.tex
text

--- 2018-06-13 express2018/unique.tex
@@
 We show here that the constraints can be
-removed by moving to the induced congruence and precongruence.
-
+removed by moving to the induced congruence and precongruence, the
+latter 
+called \emph{rooted contraction}.
 \begin{definition}[rooted contraction]
@@
 
+The definition of rooted contraction adapts the definition of rooted
+bisimilarity on top of that of the  contraction preorder
+$\mcontrBIS$.
+
+% The quick finding of rooted contraction was by help of
+% theorem provers, and was based on two principles: 1) Its definition must NOT be recursive
+% (or coinductive), instead it should mimic the definition of rooted bisimilarity
+% ($\approx^c$); 2) It must be built on top of the existing \emph{contracts}
+% relation $\mcontrBIS$, which we believe it's the \emph{right} one (as
+% it's complete). Multiple candicates were tested, and finally the above
+% definition was proven to be a precongruence:
+
 \begin{theorem}

### 2018-06-14 express2018/formal.tex
text

@@
 \item It serves as the underlying implementation language for the core HOL engine;
-\item It's used to implement tactics (and tacticals) for writing proofs;
-\item It's used as the command language of the HOL interactive shell.
+\item it is used to implement tactics (and tacticals) for writing proofs;
+\item it is used as the command language of the HOL interactive shell.
 \end{enumerate}
@@
 choice operator, axiom of infinity, and rank-1 polymorphim (type
-variables). HOL4 implements the original HOL Logic, 
+variables). HOL4 implements the original HOL logics, 
 in contrast with 
  other theorem provers of the HOL family (e.g. Isabelle/HOL) that have
-made extensions
+made extensions.
 %  (they made the formal language more powerful,
@@
 formalisation we consider only single equations/contractions. 
-This considerably simplifies the  reading of the HOL scripts (on 
-the extension  to multiple equations/contractions
-see also  Section~\ref{s:concl}).
+This considerably simplifies the  reading of the HOL scripts.
+%  (on 
+% the extension  to multiple equations/contractions
+% see also  Section~\ref{s:concl}).
 

### 2018-06-14 express2018/sos.tex
text

@@
   nested restrictions.
- Also, we don't assume that the uses of \texttt{var} are
-  guarded by \texttt{rec} of the same variable.
+%  Also, we do not assume that the uses of \texttt{var} are
+%   guarded by \texttt{rec} of the same variable.
 
@@
 \fi
-\item the correctness for each of the transitions by SOS rules;
-\item there's no other transition beside the three existing ones.
+\item the correctness for each of the transitions;
+\item the non-existence of other transitions.
 \end{enumerate}
-For large complex processes it is surprisingly hard to manually prove the
+For large  processes it may be surprisingly hard to manually prove the
 non-existence of transitions.  Hence the usefulness of appealing to 
 the new  function \texttt{CCS\_TRANS\_CONV}. 
-For instance the function
-called on the  process $(a.0 | \bar{a}.0)$ thus
+For instance this function
+is called on the  process $(a.0 | \bar{a}.0)$ thus:
 \begin{lstlisting}
@@
 \end{lstlisting}
-returns the following theorem, indeed describing all immediate
+This returns the following theorem, indeed describing all immediate
 transitions of the process:

### 2018-06-14 express2018/intro.tex
Fixed part2

@@
 In these cases, there are only a few places in which the HOL scripts have to be modified.
-Then the succesful termination of the scripts  gives us a guarantee that the proof is
+Then the successful termination of the scripts  gives us a guarantee that the proof is
 completed,  removing the risk 

### 2018-06-14 express2018/part2.tex
Fixed part2

@@
 given a  labelled transition relation \texttt{R}, 
-then
-\HOLinline{\HOLConst{LRTC}
-  \HOLFreeVar{R}} builds 
+then \texttt{LRTC R}  builds 
 the possible traces derived from \texttt{R}:
@@
 
-To finish the proof of Lemma~\ref{l:ruptocon}, we have used the  above
-result to freely switch between weak transitions and traces
-during the induction argument.
-% , which either keep its
-% length or become shorter after passing weak bisimilations, then we
-% used above lemma again to convert the traces back to weak transitions.
+Now we show the formalized statements of Lemma~\ref{l:uptocon}, which
+is quite long:\vspace{-1em}
+\begin{alltt}
+\begin{small}
+\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E}.
+\HOLConst{WGS} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{E} \HOLFreeVar{Q}) \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{C}.
+       \HOLConst{GCONTEXT} \HOLBoundVar{C} \HOLSymConst{\HOLTokenImp{}}
+       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{R}.
+            \HOLBoundVar{C} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
+            \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
+                \HOLConst{GCONTEXT} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{C\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}}
+                (\HOLConst{WEAK_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} (\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}.
+\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{y})) (\HOLBoundVar{C} \HOLFreeVar{Q})
+                  (\HOLBoundVar{C\sp{\prime}} \HOLFreeVar{Q})) \HOLSymConst{\HOLTokenConj{}}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}.
+           \HOLBoundVar{C} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
+           \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
+               \HOLConst{GCONTEXT} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{C\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}}
+               (\HOLConst{WEAK_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{EPS}) (\HOLBoundVar{C} \HOLFreeVar{Q}) (\HOLBoundVar{C\sp{\prime}} \HOLFreeVar{Q})
+\end{small}
+\end{alltt}
+\vspace{-1em} Traces were involved in the proof of above lemma by using
+the following ``unfolding'' lemma:\vspace{-1em}
+\begin{alltt}
+\begin{small}
+\HOLTokenTurnstile{} \HOLConst{GCONTEXT} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{TRACE} ((\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}) \HOLFreeVar{P}) \HOLFreeVar{xs} \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+   \HOLConst{LENGTH} \HOLFreeVar{xs} \HOLSymConst{\HOLTokenLeq{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
+       \HOLConst{GCONTEXT} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{C\sp{\prime}} \HOLFreeVar{P}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLConst{TRACE} ((\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}) \HOLBoundVar{Q}) \HOLFreeVar{xs} (\HOLBoundVar{C\sp{\prime}} \HOLBoundVar{Q})
+\end{small}
+\end{alltt}
+It roughly says, for any context $C$ and weakly guarded expression
+$E$, if $C \circ E^n[P] \overset{xs}{\Longrightarrow} P'$ and the length
+of actions $xs \leqslant n$, then $P$ has the form of $C'[P]$, meaning
+it's not touched during the transitions. Without traces it is
+impossible to reason on the length of intermediate actions behind weak transitions.
 
-\finish{would not it have been good to actually see the formalisation of 
-lemma~\ref{l:ruptocon}? (also to see how trace are actually used in
-the induction)}
-
-Below is the formalisation of
-Theorem~\ref{t:contraBisimulationU} (where \texttt{WGS} stands for
+With all above work, finally we can formally prove
+Theorem~\ref{t:contraBisimulationU}: (here \texttt{WGS} stands for
 `weakly guarded context with weakly-guarded sums')
@@
 \HOLBoundVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
-\hfill{[UNIQUE_SOLUTION_OF_CONTRACTIONS]}
 \end{alltt}
@@
 \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
-\hfill{[UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS]}
 \end{alltt}
@@
 \HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}\hfill{[STRONG_UNIQUE_SOLUTION]}
+\HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}
 \end{alltt}
@@
 \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
-\hfill{[OBS_UNIQUE_SOLUTION]}
 \end{alltt}

### 2018-06-14 express2018/related.tex
text
Fixed part2

--- 2018-06-14 express2018/related.tex
@@
 Monica Nesi formalized both pure CCS \cite{Nesi:1992ve} and Value-Passing CCS
-\cite{Nesi:2017wo} in old versions of HOL theorem prover, but the
-related proof scripts were not publically available.\footnote{Part of
- the formalization of pure CCS can be found at \url{https://github.com/binghe/informatica-public/tree/master/CCS2/CCS-Nesi}.}
-She was mainly focusing on writing decision procedures (ML functions) which
-automatically prove theorems showning bisimilarity of CCS
-processes.%
-% \footnote{The work is ported (by the 2nd author) from
-% HOL88 to latest HOL4, with small improvements on existing work, then
-% added the theory of context and (pre)congruence, coarsest
-% (pre)congruence contained in bisimilarity, bisimulation up to,
-% expansion, contraction, and unique solution of
-% equations/expansions/contractions et al, these additions have doubled
-% the size of original work.}
+\cite{Nesi:2017wo} in old versions of HOL theorem prover.\footnote{Part of
+ the proof scripts for pure CCS now is available at \url{https://github.com/binghe/informatica-public/tree/master/CCS2/CCS-Nesi}.}.
+Nesi's main focus was on
+ decision procedures (as ML functions) for
+automatically proving bisimilarities between CCS
+processes. She stopped once all needed algebraic laws were proved. We
+first ported her pure CCS formalisation to HOL4 with many essential
+changes and then added new concepts and deep theorems. The total lines of
+proof scripts gets doubled for now.
 
-Beside Nesi, there exist other CCS formalisations. One
-is done in Isabelle/HOL (based on Nominal datatypes) in 2010, by Jesper Bengtson as part of his PhD
-thesis project \cite{bengtson2010formalising}, available in Isabelle's Archive of Formal
-Proofs (AFP) \footnote{\url{https://www.isa-afp.org/entries/CCS.html}}. He has formalized
-classic properties for strong/weak equivalence and observational
-congruence, however the CCS grammar doesn't include process constants
-(or recursion operators), and the proved theorems also look quite
-different with their forms in textbooks.%
+Bengtson,  Parrow and Weber
+have made a substantial formalisation work 
+on CCS, $\pi$-calculi
+\cite{bengtson2010formalising,bengtson2007formalising,bengtson2007completeness}
+and $\psi$-calculi 
+using Isabelle/HOL and its nominal datatype package, with main focus on the handling of name binders.
+% Jesper Bengtson's PhD thesis 
+%  \cite{bengtson2010formalising} looks  at 
+% formalizations of CCS, $\pi$-calculi and $\psi$-calculi
+% into Isabelle/HOL and its
+% nominal logic. For CCS, 
+% he has 
+%  formalized
+%  basic properties for strong/weak equivalence (congruence, basic
+%  algebraic laws), for a  and observational
+% congruence, however the CCS syntax doesn't have constants
+% (or recursion operator), using replication in place of recursion.
+% The formalisation effort has then been continued 
+%
 % On the other side, Jesper
-% Bengtson and Joachim Parrow made great progress on pi-calculus formalization and
+% Bengtson and Joachim Parrow made great progress on $\pi$-calculus
+% formalization and 
 % proved that the algebraic axiomatization of bisimulation
-% equivalence in the pi-calculus is sound and complete. \cite{bengtson2007completeness}
-The other formalisation is based on Coq, done by Solange
-Coupet-Grimal in 1995, which is part of the
-``coq-contribs'' archive (Coq's official user contributed code)
-\footnote{\url{https://github.com/coq-contribs/ccs}}. This is actually
-a formalisation of transition systems without any algebraic operator,
-and covers the very basic properties of strong/weak equivalence and observational
-congruence. The last one was done by Chaudhuri et
-al. \cite{chaudhuri2014formalization} using Abella, this work
-particularily focus on bisimulation up to techniques while the CCS
-type doesn't have restriction, recursion and relabelling operators.
+% equivalence in the $\pi$-calculi is sound and
+% complete. \cite{bengtson2007completeness} 
+Other formalisations in this area include the work of Solange
+Coupet-Grimal\footnote{\url{https://github.com/coq-contribs/ccs}} in Coq
+and Chaudhuri et al.\;\cite{chaudhuri2015lightweight} in Abella. The
+latter focuses on `bisimulation up-to' techniques for strong bisimilarity 
+for CCS and $\pi$-calculus.
+Formalisations less related to ours
+include Kahsai and Miculan \cite{kahsai2008implementing} for the spi
+calculus  in Isabelle, and Hirschkoff \cite{hirschkoff1997full} for the $\pi$-calculus in Coq.
+
+% The other formalisation is based on Coq, done by Solange
+% Coupet-Grimal in 1995, which is part of the
+% ``coq-contribs'' archive (Coq's official user contributed code)
+% \footnote{\url{https://github.com/coq-contribs/ccs}}. This is actually
+% a formalisation of transition systems without any algebraic operator,
+% and covers the very basic properties of strong/weak equivalence and
+% observational 
+% congruence.

### 2018-06-14 express2018/context.tex
Minor fixes

@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
-   \HOLConst{PreOrder} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}}
+\HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
 \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
-\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})
-\HOLTokenTurnstile{} \HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
-   \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}}
+\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{PreOrder} \HOLFreeVar{R}
+\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
 \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
-\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})
+    \HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{equivalence} \HOLFreeVar{R}
 \end{alltt}
 
-A \emph{weakly guarded} context is a context in which each hole is
-underneath a  prefix (where \texttt{WG} stands for weakly guarded):
+A \emph{weakly guarded} (\texttt{WG}) context is a context in which each hole is
+underneath a prefix:
 \begin{alltt}
@@
 \end{alltt}
+
 In the same manner, we can also define all

### 2018-06-14 express2018/part2.tex
Minor fixes

@@
 then \texttt{LRTC R}  builds 
-the possible traces derived from \texttt{R}:
+the trace relation derived from \texttt{R}:
 \begin{alltt}

### 2018-06-15 express2018/conclusions.tex
text
Fixed all spelling issues; adjusted page breaking; deleted some really unrelated references.

--- 2018-06-14 express2018/conclusions.tex
@@
 We have highlighted a formalisation of the theory of CCS in the 
-HOL4 theorem prover. The formalisation has focused on the theory of
+HOL4 theorem prover (for lack of space we have not discussed 
+the formalisation of some basic algebraic theory, of the basic
+properties of the expansion preorder,   and of a few
+ versions of `bisimulation up to'
+techniques). % such as  bisimulation up-to bisimilarity). 
+The formalisation has focused on the theory of
 unique solution of equations and contractions. 
-The formalisation has also allowed us to further develop the theory,
+It has also allowed us to further develop the theory,
 notably the basic properties of rooted contraction, and the unique
@@
 the theory of CCS. 
-Moreover, 
-the logic foundations of HOL makes the whole work (or individual
-parts) easily portable to other theorem provers.
+%Moreover, 
+%the logic foundations of HOL makes the whole work (or individual
+%parts) easily portable to other theorem provers.
 
@@
 and preorders, notably trace relations.  
-On another line, one could  
-examine the formalisation of  a different approach to unique
-solutions, by Durier et al.\ \cite{DurierHS17}, in which the use of contraction is
-replaced by semantic conditions on process transitions such as
-divergence.
+%On another line, one could  
+%examine the formalisation of  a different approach to unique
+%solutions, by Durier et al.\ \cite{DurierHS17}, in which the use of contraction is
+%replaced by semantic conditions on process transitions such as
+%divergence.
 
@@
 
-\subsection*{Acknowledgements}
+\paragraph{Acknowledgements}
 
-We would like to thank many people from the HOL community
-for their help in the past two years, in particular 
+We would like to thank many people from the HOL community:
 Michael Norrish, Thomas Tuerk, 
-Ramana Kumar, Konrad Slind, Robert Beers, and Jeremy Dawson. 
+Ramana Kumar, Konrad Slind, Jeremy Dawson, Robert Beers, etc.
 % The second half of this

### 2018-06-15 express2018/equa.tex
Unlock context
text
Fixed all spelling issues; adjusted page breaking; deleted some really unrelated references.

@@
+\section{Equations and contractions}
+\label{s:eq}
+
 \subsection{Systems of  equations}
@@
 bisimilar with each other.
-
 We need variables to write equations. We  use
@@
 is  the process
-$R \DSdefi \recu A . a A$, and   for any other solution $P$ we have $P \wb R$.
+$R \DSdefi \recu A { a. A}$, and   for any other solution $P$ we have $P \wb R$.
 In contrast, the equation 
  $X = a|  X$ has solutions that may be quite different, namely any process capable of
-continuosly  performing $a$ action (but that could behave arbitrarily  on other actions).
+continuously  performing $a$ action (but that could behave arbitrarily  on other actions).
 
@@
 \item
-\emph{guarded} if,  in each    $E_i$, each occurrence of
+\emph{(strongly) guarded} if,  in each    $E_i$, each occurrence of
 an \behav\  variable is underneath a visible prefix;

### 2018-06-15 express2018/formal.tex
Fixed all spelling issues; adjusted page breaking; deleted some really unrelated references.

@@
 Higher Order Logic (or ``HOL Logic'') \cite{hollogic} stands for simple-typed $\lambda$-calculus plus Hibert
-choice operator, axiom of infinity, and rank-1 polymorphim (type
+choice operator, axiom of infinity, and rank-1 polymorphism (type
 variables). HOL4 implements the original HOL logics, 
@@
 % inconsistent). 
-Indeed the HOL Logic has considerability simpler logic
+Indeed the HOL Logic has considerable simpler logic
 foundations than most other theorem provers. %, e.g. Coq. 

### 2018-06-15 express2018/intro.tex
Fixed all spelling issues; adjusted page breaking; deleted some really unrelated references.

@@
 This method  is important in verification techniques and tools
-based on algebraic reasoning \cite{theoryAndPractice,BaeBOOK}.
+based on algebraic reasoning \cite{BaeBOOK,theoryAndPractice}.
 
@@
 the main properties  of the rooted bisimilarity (the congruence induced by weak
-bisimilarity, also called observation congruence). Concerning rooed bisimilarity, the formalisation
+bisimilarity, also called observation congruence). Concerning rooted bisimilarity, the formalisation
 includes Hennessy and Deng lemmas, and two proofs that rooted bisimilarity is the largest
@@
 book,  requiring the hypothesis that  no processes can use all labels; the other without
-such hypothesis, essentially formalising van Glabbek's paper \cite{vanGlabbeek:2005ur}
+such hypothesis, essentially formalising van Glabbeek's paper \cite{vanGlabbeek:2005ur}
 (such proof however follows the structure of the ordinal numbers, which cannot be handled
@@
 \paragraph{Structure of the paper} 
-Section~\ref{ss:ccs} presens basic background material on CCS,
+Section~\ref{ss:ccs} presents basic background materials on CCS,
 including its syntax, operational semantics, bisimilarity and rooted

### 2018-06-15 express2018/part2.tex
Fixed all spelling issues; adjusted page breaking; deleted some really unrelated references.

@@
  non-empty 
-action list, i.e., either without any (visible) label if $u = \tau$, orelse 
+action list, i.e., either without any (visible) label if $u = \tau$, or else 
 if $u \neq \tau$ then $u$ is the unique label in the list: 
@@
 (Having proved
-the precongruence property for the rooted contracion, 
+the precongruence property for the rooted contraction, 
 we can use the

### 2018-06-15 express2018/related.tex
Fixed missing ref
Fixed all spelling issues; adjusted page breaking; deleted some really unrelated references.

@@
 \section{Related formalisation work}
+\label{s:rel}
 
-Monica Nesi formalized both pure CCS \cite{Nesi:1992ve} and Value-Passing CCS
-\cite{Nesi:2017wo} in old versions of HOL theorem prover.\footnote{Part of
- the proof scripts for pure CCS now is available at \url{https://github.com/binghe/informatica-public/tree/master/CCS2/CCS-Nesi}.}.
-Nesi's main focus was on
+Monica Nesi was the first in this area, she formalized both pure CCS \cite{Nesi:1992ve} and Value-Passing CCS
+\cite{Nesi:2017wo} in old versions of HOL theorem prover.
+%\footnote{Part of
+% the proof scripts for pure CCS now is available at \url{https://github.com/binghe/informatica-public/tree/master/CCS2/CCS-Nesi}.}.
+Her main focus was on
  decision procedures (as ML functions) for
 automatically proving bisimilarities between CCS
-processes. She stopped once all needed algebraic laws were proved. We
-first ported her pure CCS formalisation to HOL4 with many essential
-changes and then added new concepts and deep theorems. The total lines of
-proof scripts gets doubled for now.
+processes. We
+first ported her work pure CCS formalisation to HOL4 with essential
+changes and new contents.
 
@@
 on CCS, $\pi$-calculi
-\cite{bengtson2010formalising,bengtson2007formalising,bengtson2007completeness}
+\cite{bengtson2010formalising,bengtson2007completeness,bengtson2007formalising}
 and $\psi$-calculi 
@@
 for CCS and $\pi$-calculus.
-Formalisations less related to ours
-include Kahsai and Miculan \cite{kahsai2008implementing} for the spi
-calculus  in Isabelle, and Hirschkoff \cite{hirschkoff1997full} for the $\pi$-calculus in Coq.
-
-% The other formalisation is based on Coq, done by Solange
-% Coupet-Grimal in 1995, which is part of the
-% ``coq-contribs'' archive (Coq's official user contributed code)
-% \footnote{\url{https://github.com/coq-contribs/ccs}}. This is actually
-% a formalisation of transition systems without any algebraic operator,
-% and covers the very basic properties of strong/weak equivalence and
-% observational 
-% congruence.
+% Formalisations less related to ours
+% include Kahsai and Miculan \cite{kahsai2008implementing} for the spi
+% calculus  in Isabelle, and Hirschkoff \cite{hirschkoff1997full} for the $\pi$-calculus in Coq.

### 2018-06-15 express2018/sos.tex
Sync with sos.tex
Fixed all spelling issues; adjusted page breaking; deleted some really unrelated references.

@@
 processes in more readable forms (see the `HOL (abbrev.)'
-column of Table \ref{tab:ccsoperator}; the table summarises 
+column of Table \ref{tab:ccsoperator}; the table summarizes 
 the main syntactic notations for CCS). For the restriction
@@
 %  (Notice the use of
-% recursition operator for representing process constants)
+% recursion operator for representing process constants)
 \begin{table}[h]
@@
 The rule \texttt{[REC]} (Recursion)
- says that if we substitute all appearences of variable $A$ in $E$ to
+ says that if we substitute all appearances of variable $A$ in $E$ to
 $(\mathbf{rec}\; A\; E)$ and the resulting process has a transition to $E_1$

### 2018-06-15 express2018/unique.tex
Fixes in lemma 3.9 \ref{l:uptocon}

@@
 \label{l:uptocon}
-Suppose $\til P$ and $\til Q$ are solutions  for $\wb$
- of a system of weakly-guarded
-contractions that uses  weakly-guarded sums.
-For any context $\qct$ that uses  weakly-guarded sums, 
+Suppose $\til P$ and $\til Q$ are solutions  for $\mcontrBIS$
+ of a system of weakly-guarded contractions (no direct sums).
+For any context $\qct$ (no direct sums),
 if  $\ct{\til P}\Arr{\mu}  R$,
  then 
-there is a  context $\qctp$ that uses  weakly-guarded sums
+there is a context $\qctp$ (no direct sums)
 such that $R \mcontrBIS \ctp{\til P}$ and  $\ct{\til Q} \Arcap{\mu}

### 2018-06-15 express2018/formal.tex
Adjusted order of text in HOL introduction

@@
 
-HOL4 is written in Standard ML (ML for abbreviation), which plays three roles here:
-\begin{enumerate}
-\item It serves as the underlying implementation language for the core HOL engine;
-\item it is used to implement tactics (and tacticals) for writing proofs;
-\item it is used as the command language of the HOL interactive shell.
-\end{enumerate}
-HOL4 users can write arbitrary applications which leverage
-the theorem proving facility. 
-\iflong
-The HOL logic language, on the other
- side, is more close to Classic ML, in which the early HOL systems were built.
-\DS{removed the sentence because  it did not
-  seem important} 
-\fi
-
 Higher Order Logic (or ``HOL Logic'') \cite{hollogic} stands for simple-typed $\lambda$-calculus plus Hibert
@@
 
+HOL4 is written in Standard ML (ML for abbreviation), which plays three roles here:
+\begin{enumerate}
+\item It serves as the underlying implementation language for the core HOL engine;
+\item it is used to implement tactics (and tacticals) for writing proofs;
+\item it is used as the command language of the HOL interactive shell.
+\end{enumerate}
+Besides, HOL4 users usually write complex automatic
+verification tools (in the same language) by calling HOL's interactive theorem proving facilities.
+\iflong
+The HOL logic language, on the other
+ side, is more close to Classic ML, in which the early HOL systems were built.
+\DS{removed the sentence because  it did not
+  seem important} 
+\fi
+
 % \finish{below: to be reformulated (by Davide) later} 
@@
 
-In the
+In this
 formalisation we consider only single equations/contractions. 
-This considerably simplifies the  reading of the HOL scripts.
+This setup considerably simplified the required proof steps while still aligned with
+their informal proofs.
 %  (on 

### 2018-06-15 express2018/sos.tex
Adjusted order of text in HOL introduction

@@
 
-In the formalisation of CCS, 
+In our formalisation of CCS, 
 the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' ($\beta$ is a
@@
 \end{lstlisting}
-Then
-the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
+And the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
 union of all visible and invisible actions. The cardinality of

### 2018-06-15 express2018/part2.tex
Fixed typo in lemma explanations; english typo

@@
 $E$, if $C \circ E^n[P] \overset{xs}{\Longrightarrow} P'$ and the length
-of actions $xs \leqslant n$, then $P$ has the form of $C'[P]$, meaning
-it's not touched during the transitions. Without traces it is
+of actions $xs \leqslant n$, then $P'$ has the form of $C'[P]$, meaning
+$P$ is not touched during the transitions. Without using traces it is
 impossible to reason on the length of intermediate actions behind weak transitions.

### 2018-06-17 express2018/conclusions.tex
text

@@
 the theory of CCS. 
-%Moreover, 
-%the logic foundations of HOL makes the whole work (or individual
-%parts) easily portable to other theorem provers.
+Moreover, 
+the logic foundations of HOL makes the whole work (or individual
+parts) easily portable to other theorem provers.
 
@@
 and preorders, notably trace relations.  
-%On another line, one could  
-%examine the formalisation of  a different approach to unique
-%solutions, by Durier et al.\ \cite{DurierHS17}, in which the use of contraction is
-%replaced by semantic conditions on process transitions such as
-%divergence.
+On another line, one could  
+examine the formalisation of  a different approach to unique
+solutions, by Durier et al.\ \cite{DurierHS17}, in which the use of contraction is
+replaced by semantic conditions on process transitions such as
+divergence.
 
@@
 
-We would like to thank many people from the HOL community:
-Michael Norrish, Thomas Tuerk, 
-Ramana Kumar, Konrad Slind, Jeremy Dawson, Robert Beers, etc.
+We have benefitted from suggestions and comments 
+from several people from the HOL
+community, including Robert Beers, Jeremy Dawson,
+Ramana Kumar,
+Michael Norrish, 
+ Konrad Slind,
+Thomas Tuerk.
+
 % The second half of this

### 2018-06-17 express2018/context.tex
Fixed all spelling issues; adjusted page breaking; deleted some really unrelated references.
text

@@
 
-\subsection{Context, guardness and (pre)congruence}
+\subsection{Context, guardedness and (pre)congruence}
 
@@
 \end{alltt}
-
-Under above definition, we can formally define the concept of
-``precongruence'' and ``congruence'' in the following ways:
+We can then define
+`precongruence' and `congruence' thus:
 \begin{alltt}
@@
 In the same manner, we can also define all
-variants of above concepts without \emph{direct} sums (\texttt{GCONTEXT}, \texttt{WGS} and
-\texttt{GSEQ}). A large amount of lemmas must be proved for their relationships and properties of compositions. These proofs all have long (and trivial) steps due to multiple levels of
-inductions on their structures.%  For example, one such
+variants of above concepts with only weakly-guarded sums (\texttt{GCONTEXT}, \texttt{WGS} and
+\texttt{GSEQ}). Several lemmas have then to be proved for ther
+relationships among these kinds of contexts and properties about their
+compositions. These proofs are usually tedious but  long,  due to multiple levels of
+inductions on the structure of the contexts.%  For example, one such
 
@@
 % solution of equations theorem for $\sim$ is a literal mapping for informal
-% proofs based on bisimulation upto $\sim$, induction and case analysis
+% proofs based on bisimulation up to $\sim$, induction and case analysis
 % of weakly guarded contexts. Below is the formal version of Lemma 4.13

### 2018-06-17 express2018/contraction.tex
Fixed all spelling issues; adjusted page breaking; deleted some really unrelated references.
text

@@
 more $\tau$-steps than those performed by $P$).
-Thus, in contrast with expansion,  we cannot really say that `$Q$ is more efficient than
-$P$'.
+% Thus, in contrast with expansion,  we cannot really say that `$Q$ is more efficient than
+% $P$'.
 
@@
  the \emph{expansion  relation} 
-$\expa$ \cite{sangiorgi2015equations, arun1992efficiency}. This 
-is a
+$\expa$ \cite{sangiorgi2015equations} %, arun1992efficiency}.
+This is a
 preorder widely used in proof techniques for bisimilarity and that 

### 2018-06-17 express2018/equa.tex
text

@@
 Then 
-$$\{  X_i = E_i\}_{i\in I}$$
+$\{  X_i = E_i\}_{i\in I}$
 is 
@@
  $X = a|  X$ has solutions that may be quite different, namely any process capable of
-continuously  performing $a$ action (but that could behave arbitrarily  on other actions).
+continuously  performing $a$ actions (but that could behave arbitrarily  on other actions).
 

### 2018-06-17 express2018/expansion.tex
Make some more spaces
text

@@
-\subsection{Bisimilarity, rooted bisimilarity,  and up-to techniques}
+\subsection{Bisimilarity and  rooted bisimilarity}
 \label{ss:BiEx}
@@
 
-We sometimes call bisimilarity as ``\emph{weak}'', to
+We sometimes call bisimilarity `\emph{weak}', to
 distinguish it from \emph{strong bisimilarity}, $\sim$,
@@
 Q\Arcap\mu Q'$ with the strong  $Q \arr \mu Q'$.
-
 Bisimilarity is not preserved by the sum operator. 
@@
 \label{t:rapproxCongruence}
-Relation $\rapprox$ is a congruence in CCS.  Indeed it is the
+$\rapprox$ is a congruence in CCS. Indeed, it is the
 largest congruence contained in $\approx$.

### 2018-06-17 express2018/formal.tex
text

@@
 code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}. The
-work consists of about 20,000 lines of proof scripts in Standard ML
-(and that follows the pioneering work by Nesi \cite{Nesi:1992ve}, in
-1992-1995).
+work consists of about 20,000 lines of proof scripts in Standard ML;
+it develops
+some pioneering work by Nesi \cite{Nesi:1992ve}, in
+1992-1995.
 
-Higher Order Logic (or ``HOL Logic'') \cite{hollogic} stands for simple-typed $\lambda$-calculus plus Hibert
+Higher Order Logic (or ``HOL Logic'') \cite{hollogic} stands for simple-typed $\lambda$-calculus plus Hilbert
 choice operator, axiom of infinity, and rank-1 polymorphism (type
@@
 \end{enumerate}
-Besides, HOL4 users usually write complex automatic
-verification tools (in the same language) by calling HOL's interactive theorem proving facilities.
+Further, in the same language
+ HOL4 users can write complex automatic
+verification tools  by calling HOL's interactive theorem proving facilities.
 \iflong
@@
 formalisation we consider only single equations/contractions. 
-This setup considerably simplified the required proof steps while still aligned with
-their informal proofs.
+This  %considerably
+ simplifies the required proof steps in HOL   while enhancing the
+ reading of the scripts.
+%   still aligned with
+% their informal proofs.
 %  (on 

### 2018-06-17 express2018/intro.tex
text

@@
 Milner's proof method has severe syntactical limitations. 
-To overcome such limitations, Sangiorgi proposes to replace
-equations with  special inequations called
+A way for  overcoming such limitations is to replace 
+equations
+ with  special inequations called
 \emph{contractions} \cite{sangiorgi2015equations}. Contraction is a
 preorder that, roughly, places some efficiency
-constraints on processes.  Uniqueness of the solutions of a system of contractions
+constraints on processes.  Uniqueness of the solution of a system of contractions
  is defined as with systems of equations:  
 any two solutions must be bisimilar.
-The difference with equations is in the meaning of solution:
+The difference with equations is in the meaning of a solution:
 in the case of contractions
@@
 \cite{sangiorgi2015equations} is on occurrences of the sum operator,
-due to the failure of substitutivity of contraction w.r.t. such operator.
+due to the failure of the substitutivity of contraction for  such an operator.
 
@@
 bisimilarity (e.g. the fixed-point and substitutivity properties), 
-their algebraic theory, various versions of ``bisimulation up to''
+their basic algebraic theory, various versions of ``bisimulation up to''
 techniques (e.g., bisimulation up-to bisimilarity),
 the main properties  of the rooted bisimilarity (the congruence induced by weak
-bisimilarity, also called observation congruence). Concerning rooted bisimilarity, the formalisation
+bisimilarity, also called observation congruence), and of the expansion preorder (an
+efficiency-like refinement of bisimilarity). Concerning rooted bisimilarity, the formalisation
 includes Hennessy and Deng lemmas, and two proofs that rooted bisimilarity is the largest
@@
 such hypothesis, essentially formalising van Glabbeek's paper \cite{vanGlabbeek:2005ur}
-(such proof however follows the structure of the ordinal numbers, which cannot be handled
+(such a proof however follows the structure of the ordinal numbers, which cannot be handled
 in HOL, and therefore it is restricted to finite-state processes ).
 Similar theorems are proved for the rooted contraction preorder.
-
 In this respect,  the work is an extensive experiment with the use of the HOL theorem prover and its
@@
 to the sum operator.  
-We have thus refined the proof  technique based on contractions by moving to the 
+We have thus refined the proof  technique based on contractions by moving to  
 \emph{rooted contraction}, that is, the coarsest (pre)congruence contained in the contraction
-preorder.  Using rooted contraction one obtains a unique-solution theorem that is valid for
-\emph{rooted bisimilarity} (hence also for bisimilarity itself), and without syntactic
+preorder.  The resulting 
+ unique-solution theorem is valid for
+\emph{rooted bisimilarity} (hence also for bisimilarity itself), and places no 
 constraints on the occurrences of sums.
@@
 proof method (the `up-to' techniques).  
-In these cases, there are only a few places in which the HOL scripts have to be modified.
+In these cases,  moving between proofs there are only a few places in which the HOL scripts have to be modified.
 Then the successful termination of the scripts  gives us a guarantee that the proof is

### 2018-06-17 express2018/part2.tex
text

--- 2018-06-15 express2018/part2.tex
@@
 
-Now we show the formalized statements of Lemma~\ref{l:uptocon}, which
-is quite long:\vspace{-1em}
+We show the  formalized statement of Lemma~\ref{l:uptocon}:\vspace{-1em}
 \begin{alltt}
@@
 \end{alltt}
-\vspace{-1em} Traces were involved in the proof of above lemma by using
-the following ``unfolding'' lemma:\vspace{-1em}
+\vspace{-1em} Traces are introduced in the proof of above lemma via 
+the following `unfolding' lemma:\vspace{-1em}
 \begin{alltt}
@@
 \end{alltt}
-It roughly says, for any context $C$ and weakly guarded expression
-$E$, if $C \circ E^n[P] \overset{xs}{\Longrightarrow} P'$ and the length
-of actions $xs \leqslant n$, then $P$ has the form of $C'[P]$, meaning
-it's not touched during the transitions. Without traces it is
-impossible to reason on the length of intermediate actions behind weak transitions.
+It roughly says that, for any context $C$ and weakly guarded expression
+$E$, if $C [\, E^n[P]\,] \overset{xs}{\Longrightarrow} P'$ and the length
+of actions $xs \leqslant n$, then $P$ has the form of $C'[P]$ (meaning
+that $P$ is not touched during the transitions). Traces are necessary
+ to  reason about the length of intermediate actions in weak transitions.
 
 With all above work, finally we can formally prove
-Theorem~\ref{t:contraBisimulationU}: (here \texttt{WGS} stands for
-`weakly guarded context with weakly-guarded sums')
+Theorem~\ref{t:contraBisimulationU} (here \texttt{WGS} stands for
+`weakly guarded context with weakly-guarded sums'):
 \begin{alltt}
@@
 it then requires a
-few steps to handle  rooted bisimilarity in the conclusion. 
-At the end the
+few more steps to handle  rooted bisimilarity in the conclusion. 
+Overall  the
 two proofs are very similar, mostly because the only property we need
 from (rooted) contraction is its precongruence. 
-(Having proved
-the precongruence property for the rooted contraction, 
-we can use the
-plain version of weakly-guarded expressions with sums
-included.) Below is the formally verified version of
-Theorem~\ref{t:rcontraBisimulationU}:
+ Below is the formally verified version of
+Theorem~\ref{t:rcontraBisimulationU}
+(having proved
+the precongruence of rooted contraction, 
+we can use  weakly-guarded expressions,   without constraints on  sums;
+that is, \texttt{WG} in place of \texttt{WGS}):
 \begin{alltt}
@@
 \end{alltt}
-
-Having no constraints on sums, the result is
- similar with Milner's original `unique solution of
+Having removed the  constraints on sums, the result is
+ similar to Milner's original `unique solution of
 equations' theorem for \emph{strong} bisimilarity ($\sim$)~--- 

### 2018-06-17 express2018/related.tex
text

@@
 
-Monica Nesi was the first in this area, she formalized both pure CCS \cite{Nesi:1992ve} and Value-Passing CCS
-\cite{Nesi:2017wo} in old versions of HOL theorem prover.
+The closest of our work is Monica Nesi's \cite{Nesi:1992ve,Nesi:2017wo}. She has made
+the first formalization of CCS,  using early versions of the HOL theorem prover.
+% both pure CCS  and Value-Passing CCS
+%\cite{Nesi:2017wo} in old versions of HOL theorem prover.
 %\footnote{Part of
 % the proof scripts for pure CCS now is available at \url{https://github.com/binghe/informatica-public/tree/master/CCS2/CCS-Nesi}.}. 
-Her main focus was on
+Her main focus is  on
  decision procedures (as ML functions) for
 automatically proving bisimilarities between CCS
-processes. We
-first ported her work pure CCS formalisation to HOL4 with essential
-changes and new contents.
+processes.  Her work has been a basis for ours. However, the differences are substantial,
+both because we have used the most recent version of HOL, and because of the spectrum of
+the theory considered.
 
@@
 on CCS, $\pi$-calculi
-\cite{bengtson2010formalising,bengtson2007completeness,bengtson2007formalising}
 and $\psi$-calculi 
-using Isabelle/HOL and its nominal datatype package, with main focus on the handling of name binders.
+using Isabelle/HOL and its nominal datatype package, with main focus on the handling of
+name binders \cite{bengtson2010formalising,bengtson2007completeness,bengtson2007formalising}.
 % Jesper Bengtson's PhD thesis 

### 2018-06-17 express2018/sos.tex
text

@@
 \end{lstlisting}
-And the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
+The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
 union of all visible and invisible actions. The cardinality of
@@
 val _ = Datatype `CCS = nil
-		      | var 'a
+		      | var 'A
 		      | prefix ('b Action) CCS
@@
 		      | relab CCS ('b Relabeling)
-		      | rec 'a CCS`;
+		      | rec 'A CCS`;
 \end{lstlisting}
@@
   \\
-recursion & $A$ with $A\Defi P$ & \texttt{rec A P} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P}}
+recursion & $\recu A P$ & \texttt{rec A P} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P}}
   \\
@@
 \HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLConst{relab} \HOLFreeVar{P} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{Q} \HOLFreeVar{rf}\hfill\texttt{[RELABELING]}
-\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{P} (\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{P}) \HOLFreeVar{X} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[REC]}
+\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{P} (\HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P}) \HOLFreeVar{A} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[REC]}
 \end{alltt}
@@
 The rule \texttt{[REC]} (Recursion)
- says that if we substitute all appearances of variable $A$ in $E$ to
-$(\mathbf{rec}\; A\; E)$ and the resulting process has a transition to $E_1$
-with action $u$, then $(\mathbf{rec}\; A\; E)$ has the same
+ says that if we substitute all appearances of variable $A$ in $P$ to
+$(\mathbf{rec}\; A\; P)$ and the resulting process has a transition to $P'$
+with action $u$, then $(\mathbf{rec}\; A\; P)$ has the same
 transition. From the HOL  viewpoint, these

### 2018-06-17 express2018/unique.tex
text

--- 2018-06-14 express2018/unique.tex
@@
 \label{l:uptocon}
-Suppose $\til P$ and $\til Q$ are solutions  for $\wb$
- of a system of weakly-guarded
-contractions that uses  weakly-guarded sums.
-For any context $\qct$ that uses  weakly-guarded sums, 
+Suppose $\til P$ and $\til Q$ are solutions  for $\mcontrBIS$
+ of a system of weakly-guarded contractions that uses 
+weakly-guarded sums.
+For any context $\qct$  that uses 
+weakly-guarded sums,
 if  $\ct{\til P}\Arr{\mu}  R$,
  then 
-there is a  context $\qctp$ that uses  weakly-guarded sums
+there is a context $\qctp$  that uses 
+weakly-guarded sums
 such that $R \mcontrBIS \ctp{\til P}$ and  $\ct{\til Q} \Arcap{\mu}
@@
 
-The unique solution theorem of Section~\ref{ss:SysContr} require a
+The unique solution theorem of Section~\ref{ss:SysContr} requires a
 constrained syntax for sums, due to the congruence and precongruence
@@
 for rooted bisimilarity with respect to bisimilarity. 
-Similarly one can define and handle the rooted variant of the expansion preorder.
+%Similarly one can define and handle the rooted variant of the expansion preorder.
 

### 2018-06-17 express2018/part2.tex
text

@@
  to  reason about the length of intermediate actions in weak transitions.
+% =======
+% It roughly says, for any context $C$ and weakly guarded expression
+% $E$, if $C \circ E^n[P] \overset{xs}{\Longrightarrow} P'$ and the length
+% of actions $xs \leqslant n$, then $P'$ has the form of $C'[P]$, meaning
+% $P$ is not touched during the transitions. Without using traces it is
+% impossible to reason on the length of intermediate actions behind weak transitions.
+% >>>>>>> cc6dee720d90c66ca8c543bc3826fbc1f9c81686
 

### 2018-06-17 express2018/conclusions.tex
Minor changes

@@
 Michael Norrish, 
- Konrad Slind,
+Konrad Slind, and
 Thomas Tuerk.

### 2018-06-17 express2018/formal.tex
Minor changes

@@
 choice operator, axiom of infinity, and rank-1 polymorphism (type
-variables). HOL4 implements the original HOL logics, 
-in contrast with 
- other theorem provers of the HOL family (e.g. Isabelle/HOL) that have
-made extensions.
+variables). HOL4 implemented the original HOL Logic, 
+while some other theorem provers in HOL family (e.g. Isabelle/HOL) have
+certain extensions.
 %  (they made the formal language more powerful,
@@
 verification tools  by calling HOL's interactive theorem proving facilities.
-\iflong
-The HOL logic language, on the other
- side, is more close to Classic ML, in which the early HOL systems were built.
-\DS{removed the sentence because  it did not
-  seem important} 
-\fi
 

### 2018-06-17 express2018/part2.tex
Minor changes

--- 2018-06-17 express2018/part2.tex
@@
 \end{alltt}
+\vspace{-1em}
 It roughly says that, for any context $C$ and weakly guarded expression

### 2018-06-17 express2018/sos.tex
Minor changes

@@
 The core datatype ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'', accounting for the CCS syntax, is then defined as an inductive
-datatype in HOL, based on its Datatype package ($\alpha$ is the type
-variable for recursion variables):
+datatype in HOL, based on its Datatype package (here \texttt{'a} as $\alpha$
+is the type
+variable for recursion variables, \texttt{'b} as $\beta$ is the type
+variable for actions):
 \begin{lstlisting}
 val _ = Datatype `CCS = nil
-		      | var 'A
+		      | var 'a
 		      | prefix ('b Action) CCS
@@
 		      | relab CCS ('b Relabeling)
-		      | rec 'A CCS`;
+		      | rec 'a CCS`;
 \end{lstlisting}

### 2018-06-18 express2018/sos.tex
text

@@
 The core datatype ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'', accounting for the CCS syntax, is then defined as an inductive
-datatype in HOL, based on its Datatype package (here \texttt{'a} as $\alpha$
+datatype in HOL, based on its Datatype package (here \texttt{'a} 
 is the type
-variable for recursion variables, \texttt{'b} as $\beta$ is the type
-variable for actions):
+variable   $\alpha$ for recursion variables, \texttt{'b} is the type
+variable   $\beta$ for actions):
 \begin{lstlisting}

### 2018-07-22 express2018/contraction.tex
Fixed below example 3.6: "As bisimilarity .." #6
Fixed p.5 l.13: between [15] and "This" is missing a dot. #26 (also #5, I think)

@@
  the \emph{expansion relation} 
-$\expa$ \cite{sangiorgi2015equations} %, arun1992efficiency}.
+$\expa$ \cite{sangiorgi2015equations,arun1992efficiency}.
 This is a
@@
 
-As  bisimilarity  and expansion, contraction is preserved by all operators but sum.
+\hl{Like (weak)} bisimilarity and expansion, contraction is preserved by all operators but sum.

### 2018-07-22 express2018/ccs.tex
text
Fixed "sec 2: is relabelling in there or not? In the formalisation it appears to be" #4

@@
 We assume  a possibly infinite set of \emph{names} $a, b,
-\ldots$, that does not contain the special symbol $\tau$, and
+\ldots$, which does not contain the special symbol $\tau$, and
 a set of variables $A,B, \ldots$ for writing recursive behaviours. 
 The class  of the CCS processes is inductively built from $\nil$ by the operators
-of  prefixing, parallel composition,  sum,
- restriction,  and recursion:
+of  prefixing, parallel composition,  sum, restriction, recursion and \hl{relabeling}:
 \begin{equation*}
 \begin{array}{ccl}
-\mu  & := &  a \; \midd \;  \outC a  \; \midd \;  \tau \\
+\mu  & := &  \tau \hspace{.3pt} \; \midd \; a  \; \midd \;  \outC a  \\
 P  & := &  \nil \; \midd \;  \mu . P \; \midd \;  P_1 |  P_2 \; \midd  \;
 P_1 + P_2 \; \midd % \; \mu . P\; \midd  \; 
-  (\res a\!)\, P  \;  \midd \;   \recu A  P\;  \midd \; A   %\\[\tkpS]
+  (\res a\!)\, P  \;  \midd \;  A \; \midd \; \recu A  P
+\; \midd \; P\; [f]  % relabelling
 \end{array}
@@
 %We sometimes omit trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil $ .
-The operational semantics is given by means of an LTS, and is
-reported in Figure~\ref{f:LTSCCS} (the symmetric version  of the two rules for
-parallel composition and the rule for sum  has been omitted).
+The operational semantics of CCS is given by means of
+a Labeled Transition System (LTS), shown in Fig.~\ref{f:LTSCCS} (the symmetric version of the two rules for
+parallel composition and the rule for sum are omitted).
 A CCS expression \emph{uses weakly-guarded sums} if all occurrences of
@@
 \}$.   
-We use $\ell$ to range over
- visible actions (i.e.,  inputs or outputs, excluding  $\tau$).
+% We use $\ell$ to range over
+%  visible actions (i.e.,  inputs or outputs, excluding  $\tau$).
 \begin{figure*}
 \begin{center}
+\vskip .1cm
+ $\displaystyle{  \over  \mu.  P    \arr\mu
+P } $  $ \hb$   
+\hskip .5cm
  $\displaystyle{   P \arr\mu   P' \over   P + Q   \arr\mu
 P'  } $  $ \hb$   
-%{{\sf par1}}:
+\hskip .5cm
  $\displaystyle{   P \arr\mu   P' \over   P | Q   \arr\mu
 P' | Q } $  $ \hb$   
+\hskip .3cm
   $\; \;$  $\displaystyle{ P \arr{ a}P' \hk \hk  Q
@@
 \\
-\vskip .1cm
-\hskip .6cm  
- $\displaystyle{  \over  \mu.  P    \arr\mu
-P } $  $ \hb$   
-\hskip .6cm  
+\vspace{.2cm}
 $\displaystyle{ P \arr{\mu}P' \over
  (\res a\!)\, P   \arr{\mu} (\res a\!)\, P'} $ $ \mu \neq a, \outC a$
-$ \hb$ %  &
-\hskip .5cm 
+$ \hb$
+%
 $\displaystyle{ P \sub {\recu A P} A \arr{\mu}P' \over
  \recu A P   \arr{ \mu} P'  } $
+\hskip .5cm  
+$\displaystyle{ P \arr{\mu} P' \over
+ P \;[f] \arr{f(\mu)} P' \;[f]} $ $\forall a.\, f(\outC a) = \overline{f(a)}$
+$ \hb$ %  &
 \end{center}
-\caption{The LTS of CCS}
+\caption{\hl{Structural Operational Semantics} of CCS}
 \label{f:LTSCCS}
@@
 $P=P'$).
-We write $P (\arr\mu)^n P'$ if $P$ can become $P'$ after performing
+We write $P \:(\arr\mu)^n P'$ if $P$ can become $P'$ after performing
 $n$ $\mu$-transitions. Finally, $P \arr\mu$ holds if there is $P'$
@@
 \paragraph{Further notations}
-Letters  $\R,\S$ range over relations.
+Letters  $\R$, $\S$ range over relations.
 We use infix notation for relations, e.g., 

### 2018-07-22 express2018/unique.tex
Fixed p6, l-8: "a system of contraction*s*" #10

@@
 
-For a system of contraction, the meaning of 
-`solution  for $\rcontr$' and of 
+For a system of contractions, the meaning of 
+``solution for $\rcontr$'' and of 
  \emph{a unique 
 solution for $\rapprox$}
-is the expected one~--- just replace in Definition~\ref{d:uniContra}  the preorder 
+is the expected one---just replace in Definition~\ref{d:uniContra}  the preorder 
 $\contr$ with $\rcontr$, and the equivalence 

### 2018-07-22 express2018/unique.tex
Fixed def 4.1: "the rooted contraction" remove "the"? #8
Fixed 'right after, "The definition of rooted contraction (..)" I find this sentence unclear' #9

@@
 \label{d:rcontra}
-Two processes $P$ and $Q$ are in the \emph{rooted contraction}, written 
+Two processes $P$ and $Q$ are in \emph{rooted contraction}, written 
  $P\rcontr Q$, if
@@
 
-The definition of rooted contraction adapts the definition of rooted
-bisimilarity on top of that of the  contraction preorder
-$\mcontrBIS$.
+%Above definition adapts the definition of rooted
+%bisimilarity on top of that of the  contraction preorder
+%$\mcontrBIS$.  %% Reviewer said this sentance is unclear. I too think so.
 
-% The quick finding of rooted contraction was by help of
-% theorem provers, and was based on two principles: 1) Its definition must NOT be recursive
-% (or coinductive), instead it should mimic the definition of rooted bisimilarity
-% ($\approx^c$); 2) It must be built on top of the existing \emph{contracts}
-% relation $\mcontrBIS$, which we believe it's the \emph{right} one (as
-% it's complete). Multiple candicates were tested, and finally the above
-% definition was proven to be a precongruence:
+\hl{The discovery of this definition is with help of HOL theorem
+  prover and
+the following two principles:} 1) Its definition must not be recursive,
+instead it should resemble the definition of rooted bisimilarity
+$\approx^c$ in Def.~\ref{d:rootedBisimilarity};
+2) It must be built on top of existing \emph{contracts}
+relation $\mcontrBIS$, which we believe it's the \emph{right} one
+because of its completeness. \hl{Multiple candicates were quickly tested,
+finally only above definition is proven to be a precongruence, as the
+following theorem states:}
 

### 2018-07-22 express2018/related.tex
Fixed sec 6: Damien Pous also formalised up-to techniques and some ccs examples in Coq #23
Fixed 'It is not very clear which things are novel (comparing with Nesi)' #42

--- 2018-06-15 express2018/related.tex
@@
 
-Monica Nesi was the first in this area, she formalized both pure CCS \cite{Nesi:1992ve} and Value-Passing CCS
-\cite{Nesi:2017wo} in old versions of HOL theorem prover.
-%\footnote{Part of
-% the proof scripts for pure CCS now is available at \url{https://github.com/binghe/informatica-public/tree/master/CCS2/CCS-Nesi}.}.
-Her main focus was on
- decision procedures (as ML functions) for
-automatically proving bisimilarities between CCS
-processes. We
-first ported her work pure CCS formalisation to HOL4 with essential
-changes and new contents.
+\hl{Monica Nesi made the first CCS formalisations for both pure and
+value-passing CCS} \cite{Nesi:1992ve,Nesi:2017wo} using early versions of the HOL
+theorem prover.\footnote{Part of 
+ her scripts is at \url{https://github.com/binghe/informatica-public/tree/master/CCS2/CCS-Nesi}.}.
+Her main focus was on implementing decision procedures (as ML functions) for
+automatically proving bisimilarities of CCS
+processes, thus she stopped proving deeper theorems in Milner's book, once the congruence and algebraic laws of
+strong, weak and rooted bisimilarity were proved. \hl{\textbf{Her work is
+  the working basis for ours.} However, now the
+differences are substantial, especially in the way of defining
+bisimilarities. We have benefited from recent versions of HOL4, and our current
+formalisation has covered a much larger spectrum of the whole theory.}
 
@@
 on CCS, $\pi$-calculi
-\cite{bengtson2010formalising,bengtson2007completeness,bengtson2007formalising}
 and $\psi$-calculi 
-using Isabelle/HOL and its nominal datatype package, with main focus on the handling of name binders.
+using Isabelle/HOL and its \texttt{nominal} datatype package, with main focus on the handling of
+name binders \cite{bengtson2010formalising,bengtson2007completeness,bengtson2007formalising}.
 % Jesper Bengtson's PhD thesis 
@@
 for CCS and $\pi$-calculus.
+Damien Pous also formalised up-to techniques and some CCS examples in
+Coq. \cite{pous2007new}
 % Formalisations less related to ours

### 2018-07-22 express2018/formal.tex
Reworked HOL4 introduction

@@
 %  in the informal proofs. 
-The whole formalisation can be found 
-in \cite{Tian:2017wrba}  or in 
- in the official example folder of HOL4 source
-code\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL}}. The
-work consists of about 20,000 lines of proof scripts in Standard ML;
-it develops
-some pioneering work by Nesi \cite{Nesi:1992ve}, in
-1992-1995.
+The whole formalisation (apart from minor fixes and extensions in this
+paper)
+is described in \cite{Tian:2017wrba}, and the
+proof scripts are in HOL4 official examples\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL/tree/master/examples/CCS}}. The
+work consists of about 20,000 lines of proof scripts in Standard ML.
 
-Higher Order Logic (or ``HOL Logic'') \cite{hollogic} stands for simple-typed $\lambda$-calculus plus Hilbert
-choice operator, axiom of infinity, and rank-1 polymorphism (type
-variables). HOL4 implemented the original HOL Logic, 
+Higher Order Logic (or \emph{HOL Logic}) \cite{hollogic} is a variant of
+Church’s simple theory of types (STT) \cite{church1940formulation}
+\hl{(or \emph{simple-typed $\lambda$-calculus}),
+plus a higher order version of Hilbert's choice operator $\varepsilon$,
+Axiom of Infinity, and Rank-1 (prenex) polymorphism.}
+HOL4 has implemented the original HOL Logic, 
 while some other theorem provers in HOL family (e.g. Isabelle/HOL) have
@@
 % inconsistent). 
-Indeed the HOL Logic has considerable simpler logic
+Indeed the HOL Logic has considerable simpler logical
 foundations than most other theorem provers. %, e.g. Coq. 
 As a result,
-formal theories in HOL can be easily migrated (sometimes even
-automatically) into other theorem provers.
+formal theories built in HOL4 is relatively easier convincible and can
+be also easily migrated into other theorem provers,
+sometimes even automatically \cite{hurd2011opentheory}.
 
-HOL4 is written in Standard ML (ML for abbreviation), which plays three roles here:
+HOL4 is written in Standard ML, a single programming language who
+plays three different roles: (The situation is quite different in
+other systems like Coq\footnote{\hl{The Coq Proof Assistant.} \url{https://coq.inria.fr}}.)
 \begin{enumerate}
@@
 \end{enumerate}
-Further, in the same language
- HOL4 users can write complex automatic
+\hl{Moreover, using} the same language HOL4 users can write complex automatic
 verification tools by calling HOL's interactive theorem proving facilities.
@@
 
-In this
-formalisation we consider only single equations/contractions. 
-This  %considerably
- simplifies the required proof steps in HOL   while enhancing the
- reading of the scripts.
+\textbf{In this
+formalisation we consider only single-variable equations/contractions.}
+This considerably
+ simplifies the required proofs in HOL, enhances the readibility of
+ proof scripts, \hl{without loss of generality (for paper proofs, the
+ general case is just a routine
+ adaptation).}
 %   still aligned with

### 2018-07-22 express2018/related.tex
Fixed 'It is not very clear which things are novel (comparing with Nesi)' #42 (addition changes)

@@
 processes, thus she stopped proving deeper theorems in Milner's book, once the congruence and algebraic laws of
-strong, weak and rooted bisimilarity were proved. \hl{\textbf{Her work is
-  the working basis for ours.} However, now the
-differences are substantial, especially in the way of defining
-bisimilarities. We have benefited from recent versions of HOL4, and our current
-formalisation has covered a much larger spectrum of the whole theory.}
+strong, weak and rooted bisimilarity were proved. \hl{Her work is
+  the working basis of ours. However, the differences are substantial, especially in the way of defining
+bisimilarities. We greatly benefited from features and standard
+libraries in recent versions of HOL4, and our formalisation has
+covered a much larger spectrum of the whole theory.}
 

### 2018-07-22 express2018/conclusions.tex
Cut off guessing words in related work of Nesi

@@
 We think that the statements in the formalisation are easy to read and
-understand, as they remain very close  to  the ordinary  statements of
-the theory of CCS. 
-Moreover, 
-the logic foundations of HOL makes the whole work (or individual
-parts) easily portable to other theorem provers.
+understand, as they are very close to the orginal statements found in
+standard CCS textbooks \cite{Gorrieri:2015jt,Mil89}.
 
-As future work,  it would be worth extending the current work
-to multiple equations and contractions; and considering other equivalences
-and preorders, notably trace relations.  
-On another line, one could  
-examine the formalisation of  a different approach to unique
-solutions, by Durier et al.\ \cite{DurierHS17}, in which the use of contraction is
+For the future work, it would be worth extending the current work
+to multi-variable equations/contractions, with other equivalences
+and preorders considered, notably the trace-related relations.
+On the other side, one could examine the formalisation of a different approach to unique
+solutions, in which the use of contraction is
 replaced by semantic conditions on process transitions such as
-divergence.
+divergence. \cite{DurierHS17}
 

### 2018-07-22 express2018/related.tex
Cut off guessing words in related work of Nesi

@@
 theorem prover.\footnote{Part of 
- her scripts is at \url{https://github.com/binghe/informatica-public/tree/master/CCS2/CCS-Nesi}.}.
+ the proof scripts is at \url{https://github.com/binghe/informatica-public/tree/master/CCS2/CCS-Nesi}.}.
 Her main focus was on implementing decision procedures (as ML functions) for
 automatically proving bisimilarities of CCS
-processes, thus she stopped proving deeper theorems in Milner's book, once the congruence and algebraic laws of
-strong, weak and rooted bisimilarity were proved. \hl{Her work is
+processes. %, thus she stopped proving deeper theorems in Milner's
+           %book, once the congruence and algebraic laws of 
+%strong, weak and rooted bisimilarity were proved.
+\hl{Her work is
   the working basis of ours. However, the differences are substantial, especially in the way of defining

### 2018-07-23 express2018/intro.tex
Fixed l-2 above section 2: "highlight*s* our formalisation" #3
Added [sangiorgi2017] journal paper as main references, long version is more clear.

@@
  with  special inequations called
-\emph{contractions} \cite{sangiorgi2015equations}. Contraction is a
+\emph{contractions} \cite{sangiorgi2015equations,sangiorgi2017equations}. Contraction is a
 preorder that, roughly, places some efficiency
@@
 removed.  One constraint that still remains in
-\cite{sangiorgi2015equations} is on occurrences of the sum operator,
+\cite{sangiorgi2017equations}
+is on occurrences of the sum operator,
 due to the failure of the substitutivity of contraction for  such an operator.
 
-The main goal  of the work described in this paper is 
-a rather  
- comprehensive formalisation  of the core of the theory of CCS 
- in the HOL
+The main goal of the work described in this paper is a rather
+comprehensive formalisation  of the core of the theory of CCS in the HOL
 theorem prover (HOL4),  with a focus on the theory of unique solutions of contractions.
@@
  unique-solution result for rooted bisimilarity. Section~\ref{s:for}
- highlight our formalisation in HOL4. Finally,  Section~\ref{s:rel} and
+ \hl{highlights} our formalisation in HOL4. Finally,  Section~\ref{s:rel} and
  \ref{s:concl} discuss related work, conclusions,  and  a few

### 2018-07-23 express2018/equa.tex
Fixed p.4, “In contrast, ...”: #31

@@
 is  the process
-$R \DSdefi \recu A { a. A}$, and   for any other solution $P$ we have $P \wb R$.
+$R \DSdefi \recu A {\, (a. A)}$, and for any other solution $P$ we have $P \wb R$.
 In contrast, the equation 
- $X = a|  X$ has solutions that may be quite different, namely any process capable of
-continuously  performing $a$ actions (but that could behave arbitrarily  on other actions).
+ $X = a|  X$ has solutions that may be quite different, for instance,
+ $K$ and $K | b$, for $K \DSdefi \recu K {\, (a. K)}$. (Actually any process capable of
+continuously performing $a$ actions (while behaves arbitrarily on
+other actions) is a solution for $X = a|  X$.)
 

### 2018-07-23 express2018/equa.tex
Fixed p.4, Def. 3.3: #32

@@
 
-\begin{definition}
+\begin{definition}[guardedness of equations]
+\label{def:guardness}
 A system of equations 
@@
 \item
-\emph{(strongly) guarded} if,  in each    $E_i$, each occurrence of
-an \behav\  variable is underneath a visible prefix;
+\textbf{weakly guarded} if,  in each    $E_i$, each occurrence of
+an \behav\  variable is underneath a prefix;
 
 \item
- \emph{sequential} if,  in each    $E_i$, each occurrence of
-an \behav\  variable only appears  underneath prefixes and sums.
+\textbf{(strongly) guarded} if,  in each    $E_i$, each occurrence of
+an \behav\  variable is underneath a \textbf{visible} prefix;
+
+\item 
+ \textbf{sequential} if,  in each    $E_i$, each of its subexpressions with occurrence of
+an \behav\  variable, apart from the variable itself, is in forms of
+prefixes or sums.
 \end{itemize}

### 2018-07-23 express2018/ccs.tex
Fixed doubts on p.11, free_action property: #37 (L is defined now)
Make uses of "derivatives" and its weak, immediate variants

@@
 
-We assume  a possibly infinite set of \emph{names} $a, b,
-\ldots$, which does not contain the special symbol $\tau$, and
+We assume  a possibly infinite set of \emph{names} $\mathscr{L} = \{a, b,
+\ldots\}$, which does not contain the special symbol $\tau$, and
 a set of variables $A,B, \ldots$ for writing recursive behaviours. 
@@
 parallel composition and the rule for sum are omitted).
-A CCS expression \emph{uses weakly-guarded sums} if all occurrences of
+A CCS expression uses only \emph{weakly-guarded sums} if all occurrences of
 the sum operator are of the form $\mu_1.P_1 + \mu_2.P_2 + \ldots
@@
  The \emph{immediate derivatives} of a
-process $P$ are the elements of  the set $\{P' \st P \arr\mu P' \mbox{ for some $\mu$ }
-\}$.   
+process $P$ are the elements of the set $\{P' \st P \arr\mu P' \mbox{
+  for some $\mu$}\}$.
 % We use $\ell$ to range over

### 2018-07-23 express2018/intro.tex
Fixed 'p. 2, l.1: I don’t know the “Hennessy and Deng” lemmas; put a reference.' #30

@@
 theorem prover (HOL4),  with a focus on the theory of unique solutions of contractions.
-The formalisation however is not confined to the theory of  unique solutions, but embraces 
-most of the 
-core of the theory of CCS \cite{Mil89}
-(partly because the theory of unique solutions
- relies on a number of more fundamental results):
-indeed the formalisation encompasses the basic properties of strong and weak
-bisimilarity (e.g. the fixed-point and substitutivity properties), 
-their basic algebraic theory, various versions of ``bisimulation up to''
-techniques (e.g., bisimulation up-to bisimilarity),
-the main properties  of the rooted bisimilarity (the congruence induced by weak
-bisimilarity, also called observation congruence), and of the expansion preorder (an
-efficiency-like refinement of bisimilarity). Concerning rooted bisimilarity, the formalisation
-includes Hennessy and Deng lemmas, and two proofs that rooted bisimilarity is the largest
-congruence included in bisimilarity:
-one as in Milner's
-book,  requiring the hypothesis that  no processes can use all labels; the other without
-such hypothesis, essentially formalising van Glabbeek's paper \cite{vanGlabbeek:2005ur}
-(such a proof however follows the structure of the ordinal numbers, which cannot be handled
-in HOL, and therefore it is restricted to finite-state processes ).
+The formalisation, however, is not confined to the theory of unique
+solutions of equations, but embraces a significant portion the theory of CCS \cite{Mil89}
+(mostly because the theory of unique solutions relies on a large number of more fundamental results).
+Indeed the formalisation encompasses the basic properties of strong and weak
+bisimilarity (e.g. the fixed-point and substitutivity properties), the
+basic properties of
+rooted bisimilarity (the congruence induced by weak
+bisimilarity, also called observation congruence), and
+their algebraic laws. Further extensions (beyond Nesi
+\cite{Nesi:1992ve}) include four versions of ``bisimulation up to''
+techniques (e.g., bisimulation up-to bisimilarity), and of the
+expansion and contraction preorder (two
+efficiency-like refinements of weak bisimilarity). Concerning rooted bisimilarity, the formalisation
+includes Hennessy Lemma and Deng Lemma (Lemma 4.1 and 4.2 of
+\cite{Gorrieri:2015jt}),
+ and two long proofs saying the rooted bisimilarity is the largest (coarsest)
+ congruence contained in (weak) bisimilarity: one following Milner's
+ book \cite{Mil89}, with the hypothesis that no processes can use up
+ all labels;
+the other without such hypothesis, essentially formalising van Glabbeek's paper \cite{vanGlabbeek:2005ur}.
 Similar theorems are proved for the rooted contraction preorder.
@@
 most recent developments, including a package for expressing coinductive definitions.
-The
-work consists of about 20,000 lines of proof scripts in Standard ML.
+In total, the work consists of about 20,000 lines of proof scripts in Standard ML.
 
-From the CCS theory viewpoint, the formalisation has offered us the possibility of 
-further refining the theory of unique solutions. 
+From the viewpoint of CCS theory, the formalisation has offered us the possibility of 
+further refining the theory of unique solutions of equations.
 In particular, the existing theory placed limitations on the body of the contractions due to the
@@
 to the sum operator.
-We have thus refined the proof  technique based on contractions by moving to  
-\emph{rooted contraction}, that is, the coarsest (pre)congruence contained in the contraction
-preorder.  The resulting 
- unique-solution theorem is valid for
+We have thus refined the contraction-based proof technique, by moving to  
+\emph{rooted contraction}, that is, the coarsest precongruence contained in the contraction
+preorder. The resulting unique-solution theorem is now valid for
 \emph{rooted bisimilarity} (hence also for bisimilarity itself), and places no 

### 2018-07-23 express2018/intro.tex
Fixed 'p.1 l.5 in Introduction' #24

@@
 
-In the   \emph{weak} case (when  behavioural equivalences abstract from internal moves,
-which practically is the most relevant case), however, 
-Milner's proof method has severe syntactical limitations. 
-A way for  overcoming such limitations is to replace 
-equations
+In the versions of Milner's unique solution theorems for proving that all
+solutions are weakly (or rooted) bisimilar (in practice these are the most
+relevant cases), however,
+Milner's proof method has severe syntactical limitations, such that
+the equations must be ``guarded and sequential,'' that is, the
+variables of the equations may only be used underneath a visible
+prefix and preceed, in the syntax tree, only by the sum and prefix operators.
+One way of overcoming such limitations is to replace equations
  with special inequations called
@@
 preorder that, roughly, places some efficiency
-constraints on processes.  Uniqueness of the solution of a system of contractions
- is defined as with systems of equations:  
-any two solutions must be bisimilar.
+constraints on processes.  The uniqueness of solutions of a system of contractions
+is defined as with systems of equations: any two solutions must be bisimilar.
 The difference with equations is in the meaning of a solution:
-in the case of contractions
-the solution is evaluated with respect to
+in the case of contractions the solution is evaluated with respect to
 the contraction preorder, rather than bisimilarity. 
@@
 removed.  One constraint that still remains in
-\cite{sangiorgi2017equations}
-is on occurrences of the sum operator,
-due to the failure of the substitutivity of contraction for  such an operator.
+\cite{sangiorgi2017equations} (in which the issue is bypassed using a more
+restrictive CCS syntax)
+is the occurrences of direct sums, due to the failure of the
+substitutivity of contraction under direct sums.
 

### 2018-07-23 express2018/related.tex
Re-enable previous disabled related work due to space limits
Use new link for Nesi's old work.

@@
 value-passing CCS} \cite{Nesi:1992ve,Nesi:2017wo} using early versions of the HOL
-theorem prover.\footnote{Part of 
- the proof scripts is at \url{https://github.com/binghe/informatica-public/tree/master/CCS2/CCS-Nesi}.}.
+theorem prover.\footnote{Part of her old proof scripts is available at
+  \url{https://github.com/binghe/HOL-CCS/tree/master/CCS-Nesi}.}.
 Her main focus was on implementing decision procedures (as ML functions) for
@@
 Coq. \cite{pous2007new}
-% Formalisations less related to ours
-% include Kahsai and Miculan \cite{kahsai2008implementing} for the spi
-% calculus  in Isabelle, and Hirschkoff \cite{hirschkoff1997full} for the $\pi$-calculus in Coq.
+Formalisations less related to ours
+include Kahsai and Miculan \cite{kahsai2008implementing} for the spi
+calculus  in Isabelle, and Hirschkoff \cite{hirschkoff1997full} for the $\pi$-calculus in Coq.

### 2018-07-23 express2018/expansion.tex
Fixed 'Definitions 2.1 and 2.2: I think is clearer if you expand the second clause and explicitly write the converse of 1.' #25

@@
 abstract from the number of internal steps performed
-\begin{definition}[bisimilarity]
+\begin{definition}%[bisimilarity]
 \label{d:wb}
 A process relation ${\R}$ 
- is a (weak) \emph{bisimulation} if, whenever
+ is a \emph{bisimulation} if, whenever
  $P\RR Q$, %for all $\mu$ 
@@
 \begin{enumerate}
-\item 
-    $P \arr\mu P'$   implies that there is $Q'$ such that $Q \Arcap \mu Q'$ and $P' \RR Q'$;
-\item the converse of (1)
- on the actions from $Q$.
-%\item if $Q  \Ar\mu   Q'$, then there is $P'$ s.t.\ $P
-%\Arcap\mu  P'$ and $P' 
-%\RR Q'$.
+\item $P \arr\mu P'$ implies that there is $Q'$ such that $Q \Arcap \mu Q'$ and $P' \RR Q'$;\vspace{-4pt}
+\item $Q \arr\mu Q'$,implies that there is $P'$ such that $P \Arcap
+  \mu P'$ and $P' \RR Q'$.
+% (the converse of (1) on the actions from $Q$)
 \end{enumerate}  
- $P$ and $Q$ are \emph{bisimilar},
-written $P \wb
- Q$, if $P \RR Q$ for some  bisimulation $\R$.  
+ $P$ and $Q$ are \textbf{bisimilar},
+written as $P \wb Q$, if $P \RR Q$ for any bisimulation $\R$.  
 \end{definition}
 
-We sometimes call bisimilarity `\emph{weak}', to
-distinguish it from \emph{strong bisimilarity}, $\sim$,
+We sometimes call bisimilarity the \emph{weak} one, to
+distinguish it from \emph{strong bisimilarity} ($\sim$)
 obtained by replacing in the above definition   the weak answer $
 Q\Arcap\mu Q'$ with the strong  $Q \arr \mu Q'$.
-Bisimilarity is not preserved by the sum operator. 
-For this, Milner introduces \emph{observational congruence}, also called \emph{rooted
-  bisimilarity}.
-\begin{definition}[rooted bisimilarity]
+Bisimilarity (the weak one) is not preserved by the sum operator (except for
+guarded sums). For this, Milner introduces \emph{observational congruence}, also called \emph{rooted
+  bisimilarity} \cite{Gorrieri:2015jt,Sangiorgi:2011ut}:
+\begin{definition}%[rooted bisimilarity]
 \label{d:rootedBisimilarity}
@@
    \Arr\mu Q'$ and $P' \wb Q'$;
-\item the converse of (1) on the actions from $Q$.
+ \item  $Q \arr\mu Q'$ implies that there is $P'$ such that $P
+   \Arr\mu P'$ and $P' \wb Q'$. %the converse of (1) on the actions from $Q$.
 \end{enumerate}

### 2018-07-23 express2018/equa.tex
Use "coarsest" instead of "largest" for consistency

@@
 \begin{itemize}
-\item
-\textbf{weakly guarded} if,  in each    $E_i$, each occurrence of
+\item \emph{weakly guarded} if, in each $E_i$, each occurrence of
   an \behav\  variable is underneath a prefix;
 
-\item
-\textbf{(strongly) guarded} if,  in each    $E_i$, each occurrence of
+\item \emph{(strongly) guarded} if, in each $E_i$, each occurrence of
   an \behav\  variable is underneath a \textbf{visible} prefix;
 
-\item 
- \textbf{sequential} if,  in each    $E_i$, each of its subexpressions with occurrence of
+\item \emph{sequential} if, in each $E_i$, each of its subexpressions with occurrence of
   an \behav\  variable, apart from the variable itself, is in forms of

### 2018-07-23 express2018/conclusions.tex
More on future work

@@
 and preorders considered, notably the trace-related relations.
-On the other side, one could examine the formalisation of a different approach to unique
+On the other side, one could examine the formalisation of a different
+approach \cite{DurierHS17} to unique
 solutions, in which the use of contraction is
 replaced by semantic conditions on process transitions such as
-divergence. \cite{DurierHS17}
+divergence. \hl{The problem of formalising value-passing CCS in a
+more elegant way with minimal efforts (by exploiting the type variable
+of actions, for example) also deserves some thinking.}
 
@@
 Thomas Tuerk.
-
-% The second half of this
-% paper was written in memory of  Mike J. Gordon.
+%
+The second half of this
+paper was written in memory of Mike J. Gordon, the creator of HOL theorem prover.

### 2018-07-23 express2018/equa.tex
Clarify Milner's unique solution theorem for WEAK_EQUIV

@@
 In contrast, the equation 
- $X = a|  X$ has solutions that may be quite different, for instance,
+ $X = a|  X$ has solutions that may be quite different, \hl{for instance,
  $K$ and $K | b$, for $K \DSdefi \recu K {\, (a. K)}$. (Actually any process capable of
 continuously performing $a$ actions (while behaves arbitrarily on
-other actions) is a solution for $X = a|  X$.)
+other actions) is a solution for $X = a|  X$.)}
 
@@
 \label{t:Mil89}
-A system of guarded and sequential equations
-% $\{  X_i = E_i\}_{i\in I}$ 
-   has 
-a unique solution
- for $\wb$.
+A system of guarded and sequential equations (without direct sums)
+$\{  X_i = E_i\}_{i\in I}$ has a unique solution for $\wb$.
 \end{theorem}
@@
 % of the solutions of the system.  
-To see the  need of the
- sequentiality  condition, 
-  consider
+To see the  need of the sequentiality  condition, consider
  the equation (from \cite{Mil89}) $X = \res a (a. X | \outC a)$
-where $X$ is guarded but not sequential. Any processes that does
-not use  $a$
- is a solution.
+where $X$ is guarded but not sequential. Any \hl{process} who does not use $a$ is a solution.

### 2018-07-23 express2018/related.tex
Minor typesetting optimizations

@@
 value-passing CCS} \cite{Nesi:1992ve,Nesi:2017wo} using early versions of the HOL
-theorem prover.\footnote{Part of her old proof scripts is available at
+theorem prover.\footnote{Part of her old proof scripts is now available at
   \url{https://github.com/binghe/HOL-CCS/tree/master/CCS-Nesi}.}.

### 2018-07-23 express2018/unique.tex
Fixed proof of thm 3.10: "exploiting lemma 3.9": maybe explain a bit in a line or so. #7

@@
 \begin{itemize}
-\item
- $\til P$ is a \emph{solution  for $\mcontrBIS$ of the 
- system of contractions} 
- if $\til P \mcontrBIS \til E [\til P]$;
-\item 
-the system  
-has  \emph{a unique 
-solution for $\approx$}
-if 
-whenever 
- $\til P$ and $\til Q$ are both solutions  for  $\mcontrBIS$
- then $\til P \approx \til Q$.
+\item $\til P$ is a \emph{solution (for $\mcontrBIS$) of the 
+ system of contractions} if $\til P \mcontrBIS \til E [\til P]$;
+\item the system has \emph{a unique solution (for $\approx$)}
+if $\til P \approx \til Q$ whenever $\til P$ and $\til Q$ are both solutions.
 \end{itemize}
@@
 
-\begin{definition}
-\label{d:guarded}
-A system of contractions $\{  X_i \mcontr E_i\}_{i\in I}$
- is
-\emph{weakly guarded}
-if,  in each    $E_i$, each occurrence of
-a \behavC\ variable is underneath a prefix.
+The guardedness of contractions follows Def.~\ref{def:guardness} (for equations).
+% \begin{definition}
+% \label{d:guarded}
+% A system of contractions $\{  X_i \mcontr E_i\}_{i\in I}$
+%  is
+% \emph{weakly guarded}
+% if,  in each    $E_i$, each occurrence of
+% a \behavC\ variable is underneath a prefix.
 
-The system use \emph{weakly-guarded sums} if 
-each $E_i$ only makes use of guarded sums.
-\end{definition}
+% The system use \emph{weakly-guarded sums} if 
+% each $E_i$ only makes use of guarded sums.
+% \end{definition}
 
@@
 
-\begin{proof}{[Sketch]}
+\begin{proof}{(sketch from \cite{sangiorgi2017equations})}
 Let $n$ be the length of the transition $\ct{\til P}\Arr\mu R$  (the
@@
 underneath at least $n$ prefixes, and cannot contribute to an action
-in the first $n$ transitions; moreover all the contexts use
+in the first $n$ transitions; moreover all the contexts have only
 weakly-guarded sums.
@@
 A system of weakly-guarded contractions
- that uses  weakly-guarded sums    has 
-a unique solution 
- for $\wb$.
+having only weakly-guarded sums, has a unique solution for $\wb$.
 \end{theorem}
 
-\begin{proof}{[Sketch]}
-One shows that if $\til P$ and $\til Q$ are solutions for $\wb$ of a system of weakly-guarded
-contractions that uses weakly-guarded sums,  then the
- relation 
-\[\R \DSdefi \{ 
+\begin{proof}{(sketch from \cite{sangiorgi2017equations})}
+Suppose $\til P$ and $\til Q$ are two such solutions (for $\wb$) and consider
+the relation
+\begin{equation*}
+\R \DSdefi \{ 
 (R,S) \st R \wb \ct{\til P}, S \wb \ct{\til Q} \mbox{ for some context
-$\qct$} \} \, . 
-\]
- is a bisimulation, exploiting 
- Lemma~\ref{l:uptocon}.
+$\qct$ (having only weakly-guarded sums)} \} \enspace.
+\end{equation*}
+We show that $\R$ is a bisimulation. Suppose $R\ \R\ S$ vis the context
+$C$, and $R \arr{\mu} R'$. We have to find $S'$ with $S \Arcap{\mu}
+S'$ and $R'\ \R\ S'$. From $R \wb C[{\til P}]$, we derive $C[{\til P}]
+\Arcap{\mu} R'' \wb R'$ for some $R''$. By Lemma~\ref{l:uptocon},
+there is $C'$ with $R'' \mcontrBIS C'[{\til P}]$ and $C[{\til Q}]
+\Arcap{\mu} \wb C'[{\til Q}]$. Hence, by definition of $\wb$, there is
+also $S'$ with $S \Arcap{\mu} S' \wb C'[{\til Q}]$. This closes the
+proof, as we have $R' \wb C'[{\til P}]$ and $S' \wb C'[{\til Q}]$.
 \end{proof}
@@
 \label{t:rcontrPrecongruence}
-Relation $\rcontr$ is a precongruence in CCS.  Indeed it is the
-largest precongruence contained in $\contr$.
+$\rcontr$ is a precongruence in CCS, and it is the
+coarsest precongruence contained in $\contr$.
 \end{theorem}  
@@
 for rooted bisimilarity with respect to bisimilarity. 
-%Similarly one can define and handle the rooted variant of the expansion preorder.
+%Similarly one can define and handle the rooted variant of the
+%expansion preorder. (not sure)
 
@@
 solution for $\rapprox$}
-is the expected one---just replace in Definition~\ref{d:uniContra}  the preorder 
+is the expected one --- just replace in Definition~\ref{d:uniContra}  the preorder 
 $\contr$ with $\rcontr$, and the equivalence 
@@
 
-\begin{theorem}[Unique solution of contractions for $\rapprox$]
+\begin{theorem}[unique solution of contractions for $\rapprox$]
 \label{t:rcontraBisimulationU}
-A system of weakly-guarded contractions
-    has 
-a unique solution 
+A system of weakly-guarded contractions has a unique solution 
  for $\rapprox$.

### 2018-07-23 express2018/expansion.tex
Use "coarsest" instead of "largest" for consistency
Minor grammatical fixes

@@
 
-The equivalences we consider are  mainly
- \emph{weak}, in that they
-abstract from the number of internal steps performed
+The equivalences we consider are mainly the \emph{weak} ones, in that they
+abstract from the number of internal steps performed:
 \begin{definition}%[bisimilarity]
 \label{d:wb}
-A process relation ${\R}$ 
- is a \emph{bisimulation} if, whenever
+A process relation ${\R}$ is a \emph{bisimulation} if, whenever
  $P\RR Q$, %for all $\mu$ 
@@
 Bisimilarity (the weak one) is not preserved by the sum operator (except for
-guarded sums). For this, Milner introduces \emph{observational congruence}, also called \emph{rooted
+guarded sums). For this, Milner introduced \emph{observational congruence}, also called \emph{rooted
   bisimilarity} \cite{Gorrieri:2015jt,Sangiorgi:2011ut}:
@@
 \label{t:rapproxCongruence}
-$\rapprox$ is a congruence in CCS. Indeed, it is the
-largest congruence contained in $\approx$.
+$\rapprox$ is a congruence in CCS, and it is the
+coarsest congruence contained in $\approx$.
 \end{theorem}

### 2018-07-23 express2018/formal.tex
Minor grammatical fixes

@@
 is described in \cite{Tian:2017wrba}, and the
-proof scripts are in HOL4 official examples\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL/tree/master/examples/CCS}}. The
-work consists of about 20,000 lines of proof scripts in Standard ML.
+proof scripts are in HOL4 official
+examples\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL/tree/master/examples/CCS}}. The
+current work consists of about 20,000 lines of proof scripts in Standard ML.
 
@@
 
-\textbf{In this
+\emph{In this
 formalisation we consider only single-variable equations/contractions.}

### 2018-07-23 express2018/intro.tex
Slightly improved introduction with more benefits of theorem proving

@@
 most recent developments, including a package for expressing coinductive definitions.
-In total, the work consists of about 20,000 lines of proof scripts in Standard ML.
 
-From the viewpoint of CCS theory, the formalisation has offered us the possibility of 
-further refining the theory of unique solutions of equations.
-In particular, the existing theory placed limitations on the body of the contractions due to the
+From the view of CCS theory, this formalisation has offered us the possibility of
+further refining the theory of unique solutions of
+equations, as formally proving previous previously known results gives us a
+chance to see \emph{what's really needed} for establishing that results.
+In particular, the existing theory has placed limitations on the body of the contractions due to the
 substitutivity problems of weak bisimilarity and other behavioural relations with respect

### 2018-07-23 express2018/unique.tex
Fixed 'p.5 l.-1: If I'm not mistaken, instead of "C[Q]=>\approx C'[Q]" it should simply write "C[Q]\approx C'[Q]".' #28
Added proof sketch for Theorem 4.4 (the most important theoretical result)

@@
 such that $R \mcontrBIS \ctp{\til P}$ and $\ct{\til Q} \Arcap{\mu}
- \wb \ctp{\til Q}$.
+ \wb \ctp{\til Q}$.\footnote{There's no typo here: $\ct{\til Q} \Arcap{\mu} \wb \ctp{\til
+     Q}$ means $\exists {\til R}.\; \ct{\til Q} \Arcap{\mu} {\til R}
+   \wb \ctp{\til Q}$. Same as in Lemma~\ref{l:ruptocon}.}
 \end{lemma}
@@
 the relation
-\begin{equation*}
+\begin{equation}
+\label{eq:R}
 \R \DSdefi \{ 
@@
 $\qct$ (having only weakly-guarded sums)} \} \enspace.
-\end{equation*}
-We show that $\R$ is a bisimulation. Suppose $R\ \R\ S$ vis the context
-$C$, and $R \arr{\mu} R'$. We have to find $S'$ with $S \Arcap{\mu}
+\end{equation}
+We show that $\R$ is a bisimulation. \hl{Suppose $R\ \R\ S$ vis the context
+$C$}, and $R \arr{\mu} R'$. We have to find $S'$ with $S \Arcap{\mu}
 S'$ and $R'\ \R\ S'$. From $R \wb C[{\til P}]$, we derive $C[{\til P}]
@@
 removed by moving to the induced congruence and precongruence, the
-latter 
-called \emph{rooted contraction}.
-\begin{definition}[rooted contraction]
+latter called \emph{rooted contraction}:
+\begin{definition}
 \label{d:rcontra}
-Two processes $P$ and $Q$ are in \emph{rooted contraction}, written 
+Two processes $P$ and $Q$ are in \emph{rooted contraction}, written as
  $P\rcontr Q$, if
@@
   prover and
-the following two principles:} 1) Its definition must not be recursive,
+the following two principles:} (1) Its definition must not be recursive,
 instead it should resemble the definition of rooted bisimilarity
 $\approx^c$ in Def.~\ref{d:rootedBisimilarity};
-2) It must be built on top of existing \emph{contracts}
+(2) It must be built on top of existing \emph{contracts}
 relation $\mcontrBIS$, which we believe it's the \emph{right} one
@@
 finally only above definition is proven to be a precongruence, as the
-following theorem states:}
+following theorem states.} (The proof of this result is along the lines of the analogous result
+for rooted bisimilarity with respect to bisimilarity.)
 
@@
 \end{theorem}
-The proof of this result is along the lines of the analogous result
-for rooted bisimilarity with respect to bisimilarity. 
-%Similarly one can define and handle the rooted variant of the
-%expansion preorder. (not sure)
 
-For a system of contractions, the meaning of 
-``solution for $\rcontr$'' and of 
- \emph{a unique 
-solution for $\rapprox$}
+For a system of rooted contractions, the meaning of 
+``solution for $\rcontr$'' and of \emph{a unique solution for $\rapprox$}
 is the expected one --- just replace in Definition~\ref{d:uniContra}  the preorder 
@@
 $\approx$ with $\rapprox$.
-
-For the rooted relations, the analogous of Lemma~\ref{l:uptocon} and of
+%
+For this new relation, the analogous of Lemma~\ref{l:uptocon} and of
 Theorem~\ref{t:contraBisimulationU} can now be stated without constraints on the sum
 operator.
-The schema of the proofs is also the same; the substitutivity
-properties of 
-$\rcontr$ and $\rapprox$ allow us to avoid issues with the sum
-operator. Some care is needed in Theorem~\ref{t:rcontraBisimulationU}
-to make sure that the final result is about  
-$\rapprox$, rather than (the weaker) $\approx$.
+The schema of the proofs is almost the same, because all needed
+properties of $\rcontr$ in the proof is its precongruence, which is
+now true for unrestricted contexts using direct sums:
 
@@
 A system of weakly-guarded contractions has a unique solution 
- for $\rapprox$.
+ for $\rapprox$. (thus also for $\wb$)
 \end{theorem}
+
+\begin{proof}
+We first follow the same steps as in the proof of Theorem~\ref{t:contraBisimulationU} to show the relation $\R$ (now
+with $\rcontr$ and unrestrict context $C$) in (\ref{eq:R}) is bisimulation,
+exploting Lemma~\ref{l:ruptocon}. \hl{Then it remains to show that,} for
+any two process $P$ and $Q$ with action $\mu$, if $P \arr{\mu} P'$ then
+there is $Q'$ such that $Q \Arr{\mu} Q'$ (not $Q \Arcap{\mu} Q'$!) and
+$P'\ \R\ Q'$, and also for the converse direction, exploting Lemma
+4.13 of \cite{Mil89} \hl{(unexpected!)}. \hl{By definition of
+\emph{bisimulation} (not $\wb$!) and $\approx^c$, we actually proved $P
+\approx^c Q$ instead of $P \wb Q$.}
+\end{proof}

### 2018-07-23 express2018/formal.tex
Clarified 'Getting a glimpse of user involvement in proving the theorems mentioned in Section 5. Is HOL able to prove the theorems automatically, or is it an interactive process?' #43

@@
 HOL4 is written in Standard ML, a single programming language who
-plays three different roles: (The situation is quite different in
-other systems like Coq\footnote{\hl{The Coq Proof Assistant.} \url{https://coq.inria.fr}}.)
+plays three different roles:
+%(The situation is quite different in other systems like Coq\footnote{\hl{The Coq Proof Assistant.} \url{https://coq.inria.fr}}.)
 \begin{enumerate}
@@
 \hl{Moreover, using} the same language HOL4 users can write complex automatic
-verification tools by calling HOL's interactive theorem proving facilities.
+verification tools by calling HOL's interactive theorem proving
+facilities. \hl{(The formal proof of theorems in CCS theory
+is mostly done by an \emph{interactive process} closely following
+their informal proofs.)}
 

### 2018-07-23 express2018/conclusions.tex
Updated all generated TeX files

@@
 For the future work, it would be worth extending the current work
-to multi-variable equations/contractions, with other equivalences
-and preorders considered, notably the trace-related relations.
+to multi-variable equations/contractions. \hl{Preliminary work shows that,
+the key idea could be using unguarded constants as free variables
+(\texttt{FV}) and define guardness directly on type CCS (instead of CCS
+$\rightarrow$ CCS) then connect to previous context:}
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{weakly_guarded1} \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X}.
+\HOLBoundVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e}.
+\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{e} (\HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{=} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \HOLBoundVar{e}
+\end{alltt}
+
+Formalising other equivalences and preorders could also be considered,
+notably the trace equivalences.
 On the other side, one could examine the formalisation of a different

### 2018-07-23 express2018/context.tex
Minor changes
Updated all generated TeX files

@@
 
-We have chosen to use $\lambda$-expressions (typed
-$CCS\rightarrow CCS$) to represent  (multi-hole) 
-contexts. The definition is inductive:
+We have chosen to use $\lambda$-expressions (\hl{with the type}
+``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'')
+to represent \emph{multi-hole contexts}.
+%
+\hl{This choice has a significant advantage over \emph{one-hole
+contexts}, as each hole corresponds to one
+appearence of the \emph{same} variable in single-variable
+expressions (or equations). Thus \emph{contexts} can be directly used in
+formulating the unique solution of equations theorems in
+single-variable cases.} The precise definition is given inductively:
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{t}) \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{p})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
-\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{a}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
-\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLSymConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLBoundVar{e} \HOLBoundVar{t}))) \HOLSymConst{\HOLTokenConj{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
-\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})\hfill{[CONTEXT_rules]}
+\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
+\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
+\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
+\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[CONTEXT_rules]}
 \end{alltt}
-We can then define
-`precongruence' and `congruence' thus:
+
+A (pre)congruence is a relation of CCS processes defined on top of
+above multi-hole contexts. \hl{The only difference between congruence and
+precongruence is, the former must be an equivalence (reflexive,
+symmetric, transitive), while the latter can be just a preorder (reflexive, transitive)}:
+\begin{alltt}
+\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
+\HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}}
+\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
+\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})\hfill{[congruence_def]}
+\hfill{[precongruence_def]}
+\end{alltt}
+\vspace{-4ex}
 \begin{alltt}
 \HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
-\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{PreOrder} \HOLFreeVar{R}
-\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
-    \HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{equivalence} \HOLFreeVar{R}
+\HOLConst{PreOrder} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
+\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})
 \end{alltt}
 
-A \emph{weakly guarded} (\texttt{WG}) context is a context in which each hole is
+A context is \emph{weakly guarded} (\texttt{WG}) if each hole is
 underneath a prefix:
 \begin{alltt}
-\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
-\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{p})) \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
-\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{a}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
-\HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLSymConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLBoundVar{e} \HOLBoundVar{t}))) \HOLSymConst{\HOLTokenConj{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
-\HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})\hfill{[WG_rules]}
+\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
+\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
+\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[WG_rules]}
 \end{alltt}
@@
 % guarded as long as $e[\cdot]$ is a context, not necessary weakly guarded.)
-A \emph{strongly guarded} (\texttt{SG}) context is a context in which
- each hole is underneath a visible prefix:
+
+A context is \emph{(strongly) guarded} (\texttt{SG}) if each hole is underneath a \emph{visible} prefix:
 \begin{alltt}
-\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{e}.
-\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLConst{label} \HOLBoundVar{l}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
-\HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{a}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
-\HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLSymConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLBoundVar{e} \HOLBoundVar{t}))) \HOLSymConst{\HOLTokenConj{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
-\HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})\hfill{[SG_rules]}
-\end{alltt}
-And a \emph{sequential} (\texttt{SEQ}) context is a context in which each hole is under prefix or sums:
- \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{t}) \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
-\HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{p})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
-\HOLConst{SEQ} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{a}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{SEQ} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})\hfill{[SEQ_rules]}
+\HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
+\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{label} \HOLFreeVar{l}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{SG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{SG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
+\HOLConst{SG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[SG_rules]}
 \end{alltt}
 
-In the same manner, we can also define all
-variants of above concepts with only weakly-guarded sums (\texttt{GCONTEXT}, \texttt{WGS} and
-\texttt{GSEQ}). Several lemmas have then to be proved for ther
+A context is \emph{sequential} (\texttt{SEQ}) if each of its \emph{subcontexts} with
+a hole, apart from the hole itself, is in forms of prefixes or sums:
+(c.f. Def.~\ref{def:guardness} and p.101,157 of \cite{Mil89} for
+the informal definitions.)
+ \begin{alltt}
+\HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
+\HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
+\HOLConst{SEQ} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{SEQ} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})\hfill{[SEQ_rules]}
+\end{alltt}
+
+In the same manner, \hl{we can also define variants of contexts (\texttt{GCONTEXT}) and weakly guarded
+contexts (\texttt{WGS}) in which only guarded sums are allowed (i.e. direct sums are forbidden):}
+\begin{alltt}
+\HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
+\HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
+\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{a\sb{\mathrm{1}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{a\sb{\mathrm{2}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
+\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[GCONTEXT_rules]}
+\end{alltt}
+\begin{alltt}
+\HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
+\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{a\sb{\mathrm{1}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{a\sb{\mathrm{2}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{WGS} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{WGS} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
+\HOLConst{WGS} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[WGS_rules]}
+\end{alltt}
+
+\hl{Although weak bisimilarity is not compatible with an unrestricted
+variant of binary choice, it is compatible with weakly guarded
+sums. As a consequence, weak bisimilarity is indeed a ``congruence''
+if we have had another version of \texttt{congruence} w.r.t. above \texttt{GCONTEXT}.}
+%
+Many lemmas have then to be proved for their
 relationships among these kinds of contexts and properties about their

### 2018-07-23 express2018/part2.tex
Updated all generated TeX files

--- 2018-06-17 express2018/part2.tex
@@
 A delicate point in the formalisation of the results about unique solution of
-contractions are the proof of lemma~\ref{l:ruptocon} and alike lemmas;
+contractions are the proof of Lemma~\ref{l:ruptocon} and lemmas alike;
 in particular, there is
@@
 For this, we first 
- define the Reflexive Transitive Closure with a
-List (\texttt{LRTC}):
-given a  labelled transition relation \texttt{R}, 
-then \texttt{LRTC R}  builds 
-the trace relation derived from \texttt{R}:
+ define \hl{the concept of list-accumulating reflexive transitive closure
+ (\texttt{LRTC})}.
+Given a labelled transition relation \texttt{R}, \texttt{LRTC R} is
+a 3-ary relation representing the trace of transitions:
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{LRTC} \HOLFreeVar{R} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b} \HOLSymConst{\HOLTokenEquiv{}}
+\HOLConst{LRTC} \HOLFreeVar{R} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b} \HOLSymConst{\HOLTokenEquiv{}}
 \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.
@@
 \end{alltt}
-The traces for a  CCS processes
-are obtained
- by combining \texttt{LRTC} with the  CCS transition
-relation  \texttt{TRANS}:
+\hl{The trace relation for CCS can be then obtained
+ by composing \texttt{LRTC} with the (strong) transition
+relation \texttt{TRANS}}:
 \begin{alltt}
@@
 \end{alltt}
-If there is at most one visible action (i.e., a label) 
-in the list of actions of a trace,
-then the trace  also represents a weak transition. Here 
-we distinguish two cases: no label and unique label. The definition of `no
-label' in an action list is easy (below \texttt{MEM} 
-tests if a given element is a member of a list):
+
+\hl{Notice that if the list of actions is empty, that means that there is no transition and hence,}
+if there is at most one visible action (i.e. a label) in the list of actions,
+then the trace is also a weak transition. Here
+we must distinguish between two cases: no label and unique label (in
+the list of actions). The definition of ``no
+label'' in an action list is easy (here \texttt{MEM} tests if a given element is a member of a list):
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{NO_LABEL} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
+\HOLConst{NO_LABEL} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
 \HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLFreeVar{L}\hfill{[NO_LABEL_def]}
 \end{alltt}
-The definition below of `unique label'
-%  can be done in many ways, in
-% which we have chosen to use the version learnt from Robert Beers in
-% a private discussion which 
-avoids counting or filtering in a list;
-it says that a label is unique in an action list iff it there is no other
-label in the remainder part of the list:
+
+The definition of ``unique label'' \hl{can be done in many ways, the
+following definition (learnt from Robert Beers) has
+avoided any counting or filtering in the list.}
+It says that a label is unique in a list of actions if and only if there is no
+label in the rest of list:
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}}
+\HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}}
 \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{L\sb{\mathrm{1}}} \HOLBoundVar{L\sb{\mathrm{2}}}.
@@
 a list of actions); 
-it says that a
- weak transition $P\overset{u}{\Rightarrow}P'$ is a  trace with a
- non-empty 
-action list, i.e., either without any (visible) label if $u = \tau$, or else 
-if $u \neq \tau$ then $u$ is the unique label in the list: 
+it says, a weak transition $P\overset{u}{\Rightarrow}P'$ is also a
+trace $P\overset{acts}{\longrightarrow}P'$ with a
+ non-empty action list $acts$, in which either there is no label (for $u = \tau$), or 
+$u$ is the unique label (for $u \neq \tau$):
 %\begin{lemma}
@@
 
-We show the  formalized statement of Lemma~\ref{l:uptocon}:\vspace{-1em}
+Now the formalised version of Lemma~\ref{l:uptocon}:
+\hfill{\texttt{[UNIQUE_SOLUTION_OF_CONTRACTIONS_LEMMA]}\vspace{-1em}
 \begin{alltt}
@@
 \end{alltt}
-\vspace{-1em} Traces are introduced in the proof of above lemma via 
-the following `unfolding' lemma:\vspace{-1em}
+\vspace{-1em}
+Traces are actually used in the proof of above lemma via 
+the following ``unfolding lemma'':\vspace{-1em}
 \begin{alltt}
@@
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
-\HOLConst{TRACE} ((\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}) \HOLBoundVar{Q}) \HOLFreeVar{xs} (\HOLBoundVar{C\sp{\prime}} \HOLBoundVar{Q})
+\HOLConst{TRACE} ((\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}) \HOLBoundVar{Q}) \HOLFreeVar{xs} (\HOLBoundVar{C\sp{\prime}} \HOLBoundVar{Q})\hfill{[unfolding_lemma4]}
 \end{small}
 \end{alltt}
-It roughly says that, for any context $C$ and weakly guarded expression
+\vspace{-1em}
+It roughly says, for any context $C$ and weakly-guarded context
 $E$, if $C [\, E^n[P]\,] \overset{xs}{\Longrightarrow} P'$ and the length
 of actions $xs \leqslant n$, then $P$ has the form of $C'[P]$ (meaning
-that $P$ is not touched during the transitions). Traces are necessary
- to  reason about the length of intermediate actions in weak transitions.
-% =======
-% It roughly says, for any context $C$ and weakly guarded expression
-% $E$, if $C \circ E^n[P] \overset{xs}{\Longrightarrow} P'$ and the length
-% of actions $xs \leqslant n$, then $P'$ has the form of $C'[P]$, meaning
-% $P$ is not touched during the transitions. Without using traces it is
-% impossible to reason on the length of intermediate actions behind weak transitions.
-% >>>>>>> cc6dee720d90c66ca8c543bc3826fbc1f9c81686
+that $P$ is not touched during the transitions). Traces are used for
+reasoning about the \hl{number} of intermediate actions in weak
+transitions. For instance, from Def.~\ref{d:BisCon}, \hl{it is easy
+to see that, a weak transition either gets shorter
+or remains the same when passing into $\mcontrBIS$ from left to right}.
+\hl{This fact, among others, is crucial} in proving
+Lemma~\ref{l:uptocon}. We show only one such lemma, for the case of
+$\tau$-transitions passing into $\mcontrBIS$ (from left to right):
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{xs} \HOLBoundVar{P\sp{\prime}}.
+       \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{xs} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{xs\sp{\prime}} \HOLBoundVar{Q\sp{\prime}}.
+           \HOLConst{TRACE} \HOLFreeVar{Q} \HOLBoundVar{xs\sp{\prime}} \HOLBoundVar{Q\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{Q\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLBoundVar{xs\sp{\prime}} \HOLSymConst{\HOLTokenLeq{}} \HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenConj{}}
+           \HOLConst{NO_LABEL} \HOLBoundVar{xs\sp{\prime}}\hfill{[contracts_AND_TRACE_tau]}
+\end{alltt}
 
-With all above work, finally we can formally prove
-Theorem~\ref{t:contraBisimulationU} (here \texttt{WGS} stands for
-`weakly guarded context with weakly-guarded sums'):
+Finally, \hl{with all above work carefully done with patience,}
+ we have formally proved Theorem~\ref{t:contraBisimulationU}:
 \begin{alltt}
@@
 \HOLBoundVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
+\hfill{[UNIQUE_SOLUTION_OF_CONTRACTIONS]}
 \end{alltt}
+\vspace{-2ex}
 
@@
 \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
+\hfill{[UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS]}
 \end{alltt}
@@
 \HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}
+\HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}\hfill{[STRONG_UNIQUE_SOLUTION]}
 \end{alltt}
 
-In contrast, Milner's `unique solution of
-equations' theorem for rooted bisimilarity ($\rapprox$)
+In contrast, Milner's ``unique solution of
+equations'' theorem for rooted bisimilarity ($\rapprox$)
 has more severe constraints:
@@
 \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
+\hfill{[OBS_UNIQUE_SOLUTION]}
 \end{alltt}
+\vspace{-4ex}

### 2018-07-24 express2018/context.tex
Updated all generated TeX files

@@
 \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
 \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
@@
 
-A (pre)congruence is a relation of CCS processes defined on top of
-above multi-hole contexts. \hl{The only difference between congruence and
+A context is \emph{weakly guarded} (\texttt{WG}) if each hole is
+underneath a prefix:
+\begin{alltt}
+\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
+\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
+\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[WG_rules]}
+\end{alltt}
+% (Notice the differences between a weak guarded context and a normal
+% one: $\lambda t. t$ is not weakly guarded as the variable is directly
+% exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
+% guarded as long as $e[\cdot]$ is a context, not necessary weakly guarded.)
+
+A context is \emph{(strongly) guarded} (\texttt{SG}) if each hole is underneath a \emph{visible} prefix:
+\begin{alltt}
+\HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
+\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{label} \HOLFreeVar{l}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{SG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{SG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
+\HOLConst{SG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[SG_rules]}
+\end{alltt}
+
+A context is \emph{sequential} (\texttt{SEQ}) if each of its \emph{subcontexts} with
+a hole, apart from the hole itself, is in forms of prefixes or sums:
+(c.f. Def.~\ref{def:guardness} and p.101,157 of \cite{Mil89} for
+the informal definitions.)
+ \begin{alltt}
+\HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
+\HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
+\HOLConst{SEQ} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{SEQ} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})\hfill{[SEQ_rules]}
+\end{alltt}
+
+In the same manner, \hl{we can also define variants of contexts (\texttt{GCONTEXT}) and weakly guarded
+contexts (\texttt{WGS}) in which only guarded sums are allowed (i.e. direct sums are forbidden):}
+\begin{alltt}
+\HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
+\HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
+\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{a\sb{\mathrm{1}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{a\sb{\mathrm{2}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
+\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[GCONTEXT_rules]}
+\end{alltt}
+\begin{alltt}
+\HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
+\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
+\HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{a\sb{\mathrm{1}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{a\sb{\mathrm{2}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{WGS} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
+\HOLConst{WGS} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
+\HOLConst{WGS} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[WGS_rules]}
+\end{alltt}
+
+% Many lemmas have then to be proved for their
+% relationships among these kinds of contexts and properties about their
+% compositions. These proofs are usually tedious but  long,  due to multiple levels of
+% inductions on the structure of the contexts.
+
+A (pre)congruence is a relation on CCS processes defined on top of
+\texttt{CONTEXT}. \hl{The only difference between congruence and
 precongruence is, the former must be an equivalence (reflexive,
@@
 
-A context is \emph{weakly guarded} (\texttt{WG}) if each hole is
-underneath a prefix:
+\hl{For example, we can prove that, strong bisimilarity ($\sim$) and
+rooted bisimilarity ($\approx^c$) are both congruence by above
+definition: (the transitivity proof of rooted bisimilarity is actually not easy.)}
 \begin{alltt}
-\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[WG_rules]}
+\HOLTokenTurnstile{} \HOLConst{congruence} \HOLConst{STRONG_EQUIV}\hfill{[STRONG_EQUIV_congruence]}
+\HOLTokenTurnstile{} \HOLConst{congruence} \HOLConst{OBS_CONGR}\hfill{[OBS_CONGR_congruence]}
 \end{alltt}
-% (Notice the differences between a weak guarded context and a normal
-% one: $\lambda t. t$ is not weakly guarded as the variable is directly
-% exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
-% guarded as long as $e[\cdot]$ is a context, not necessary weakly guarded.)
+\hl{Weak bisimilarity ($\approx$) is \emph{not} congruence
+  w.r.t. \texttt{CONTEXT}. However, it is ``congruence''
+  w.r.t. \texttt{GCONTEXT} (or if the CCS syntax were defined with
+  only guarded sum operator, as in \cite{sangiorgi2015equations}) because $\approx$ is indeed preserved by 
+  weakly-guarded sums.}
 
-A context is \emph{(strongly) guarded} (\texttt{SG}) if each hole is underneath a \emph{visible} prefix:
-\begin{alltt}
-\HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{label} \HOLFreeVar{l}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{SG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{SG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{SG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[SG_rules]}
-\end{alltt}
-
-A context is \emph{sequential} (\texttt{SEQ}) if each of its \emph{subcontexts} with
-a hole, apart from the hole itself, is in forms of prefixes or sums:
-(c.f. Def.~\ref{def:guardness} and p.101,157 of \cite{Mil89} for
-the informal definitions.)
- \begin{alltt}
-\HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
-\HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{SEQ} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{SEQ} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})\hfill{[SEQ_rules]}
-\end{alltt}
-
-In the same manner, \hl{we can also define variants of contexts (\texttt{GCONTEXT}) and weakly guarded
-contexts (\texttt{WGS}) in which only guarded sums are allowed (i.e. direct sums are forbidden):}
-\begin{alltt}
-\HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
-\HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{a\sb{\mathrm{1}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{a\sb{\mathrm{2}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[GCONTEXT_rules]}
-\end{alltt}
-\begin{alltt}
-\HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{a\sb{\mathrm{1}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{+} \HOLFreeVar{a\sb{\mathrm{2}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WGS} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WGS} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{WGS} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[WGS_rules]}
-\end{alltt}
-
-\hl{Although weak bisimilarity is not compatible with an unrestricted
-variant of binary choice, it is compatible with weakly guarded
-sums. As a consequence, weak bisimilarity is indeed a ``congruence''
-if we have had another version of \texttt{congruence} w.r.t. above \texttt{GCONTEXT}.}
-%
-Many lemmas have then to be proved for their
-relationships among these kinds of contexts and properties about their
-compositions. These proofs are usually tedious but  long,  due to multiple levels of
-inductions on the structure of the contexts.%  For example, one such
-
-% lemma says, for any  context $E$ which is both strongly guarded
-% and sequential (no direct sums) and another sequential context $H$ (no
-% direct sums), the composition $H \circ E$ is still both strongly
-% guarded and sequential (no direct sums):
-% \begin{alltt}
-
-% \end{alltt}
-
-% \subsection{Milner's ``unique solution of equations'' theorems}
-
-% Once the representation issue of CCS equations is resolved, the actual
-% proofs of Milner's unique solution of equations theorems is not very
-% interesting from the view of theorem proving, although it's a 
-% precise proof engineering work producing quite long proofs.
-% Since we have chosen to use  context to represent
-% single-variable equations, an equation like $P \sim E\{P/X\}$ now
-% becomes $P \sim E[P]$, in which $E$ is a (multi-hole) 
-% context, and there's no need to say it ``contains at most the variable
-% $X$'' any more, as equation variable doesn't appear in $E$ at
-% all. Under these simplifications, the formal proof of Milner's unique
-% solution of equations theorem for $\sim$ is a literal mapping for informal
-% proofs based on bisimulation up to $\sim$, induction and case analysis
-% of weakly guarded contexts. Below is the formal version of Lemma 4.13
-% and Proposition 4.14 in Milner's book:
-
-% \begin{alltt}
-% STRONG_UNIQUE_SOLUTION:
-% \end{alltt}
-
-% \begin{alltt}
-% WEAK_UNIQUE_SOLUTION:
-% \end{alltt}
-
-% \begin{alltt}
-% OBS_UNIQUE_SOLUTION:
-% \end{alltt}
+% no space for WEAK_EQUIV_PRESD_BY_GUARDED_SUM

### 2018-07-24 express2018/sos.tex
Updated all generated TeX files

@@
 
-In our formalisation of CCS, 
-the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' ($\beta$ is a
-type variable) accounts for visible actions, divided into input
-and output actions:
+In our CCS formalisation, the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' (\texttt{'b} or
+$\beta$ is the type variable for actions) accounts for visible actions, divided into input
+and output actions, defined by HOL's Datatype package:
 \begin{lstlisting}
@@
 The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
-union of all visible and invisible actions. The cardinality of
+union of all visible actions, plus invisible action $\tau$ (now based on
+HOL's \texttt{option} theory). The cardinality of
 ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' (and therefore of all
 CCS types built on top of it)
- depends on the choice of the initial type $\beta$.
+ depends on the choice (or \emph{type-instantiation}) of $\beta$.
 
-The core datatype ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'', accounting for the CCS syntax, is then defined as an inductive
-datatype in HOL, based on its Datatype package (here \texttt{'a} 
-is the type
-variable   $\alpha$ for recursion variables, \texttt{'b} is the type
-variable   $\beta$ for actions):
+The type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'', accounting for the CCS
+syntax\footnote{\hl{The order of type variables $\alpha, \beta$ can be
+    arbitrary. But our choice is aligned with other CCS literals.
+$\mathrm{CCS}(h,k)$ is the CCS subcalculus which can use at most $h$ constants
+and $k$ actions.} \cite{gorrieri2017ccs} \hl{Thus, to formalize theorems on
+this kind of CCS subcalculus, it is enough to instantiate the type
+variables $\alpha, \beta$ with types having the corresponding cardinalities $h, k$.}}, is then defined inductively:
+(\texttt{'a} or $\alpha$ is the type variable for recursion variables,
+``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is \hl{the type of all relabeling functions,
+\mbox{\color{blue}{\texttt{`}}} is for backquotes of HOL terms}):
 \begin{lstlisting}
@@
 We have added some grammar support,
- using HOL powerful `pretty printer', to represent CCS
-processes in more readable forms (see the `HOL (abbrev.)'
-column of Table \ref{tab:ccsoperator}; the table summarizes 
-the main syntactic notations for CCS). For the restriction
+ using \hl{HOL's powerful pretty printer}, to represent CCS
+processes in more readable forms (c.f. the column \textbf{HOL (abbrev.)}
+in Table \ref{tab:ccsoperator}, \hl{which} summarizes 
+the main syntactic notations \hl{of} CCS). For the restriction
 operator, we have chosen to allow a  set of names as a parameter, rather than a
@@
 prefix & $u.P$ & \texttt{prefix u P} & \HOLinline{\HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{P}} \\
-sum & $P + Q$ & \texttt{sum P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{+} \HOLFreeVar{Q}} \\
+sum & $P + Q$ & \texttt{sum P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{Q}} \\
 parallel & $P \,\mid\, Q$ & \texttt{par P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q}} \\
@@
   \\
+relabeling & $P\;[r\!\!f]$ & \texttt{relab P rf} & \HOLinline{\HOLConst{relab} \HOLFreeVar{P} \HOLFreeVar{rf}}
+  \\
 \hline
+invisible action & $\tau$ & \texttt{tau} & \HOLinline{\HOLSymConst{\ensuremath{\tau}}} \\
 input action & $a$ & \texttt{label (name a)} & \HOLinline{\HOLConst{In} \HOLFreeVar{a}} \\
@@
 
-The transition semantics of CCS processes  follows
-the Structural Operational Semantics (SOS) rules in
-Figure~\ref{f:LTSCCS}:
+The transition semantics of CCS processes follows Structural
+Operational Semantics (SOS) in Fig.~\ref{f:LTSCCS}:
 \begin{alltt}
 \HOLTokenTurnstile{} \HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P}\hfill\texttt{[PREFIX]}
-\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{+} \HOLFreeVar{Q} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[SUM1]}
-\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{Q} \HOLSymConst{+} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[SUM2]}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{Q} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[SUM1]}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{Q} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[SUM2]}
 \HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q}\hfill\texttt{[PAR1]}
@@
 
-The rule \texttt{[REC]} (Recursion)
+The rule \texttt{REC} (Recursion)
  says that if we substitute all appearances of variable $A$ in $P$ to
@@
 SOS rules are \emph{inductive 
-  definitions} on the 3-ary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL4's
-\texttt{Hol_reln} function (inductive relation package).
+  definitions} on the 3-ary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL's
+\texttt{Hol_reln} function.
 
@@
  is a complex Standard ML function
-  taking a CCS process and returning a theorem indicating all its direct transitions.
+  taking a CCS process and returning a theorem indicating all its
+  direct transitions.\footnote{If the input process could yield
+    something infinite branching, due to the use of recursion or
+    relabeling operators, the program will loop forever without
+    outputing a theorem.}
 For instance, we know that the process $(a.0 | \bar{a}.0)$ has three
@@
 To completely describe all possible transitions of a process, if done manually, the
-following facts should be proved:
-\begin{enumerate}
-\iflong
-\item there exists transitions from $(a.0 | \bar{a}.0)$ (optional);
-\fi
-\item the correctness for each of the transitions;
-\item the non-existence of other transitions.
-\end{enumerate}
+following facts should be proved: (1) there exists transitions from
+$(a.0 | \bar{a}.0)$ (optional); (2) the correctness for each of the
+transitions; and (3) the non-existence of other transitions.
+
 For large processes it may be surprisingly hard to manually prove the
@@
 is called on the  process $(a.0 | \bar{a}.0)$ thus:
+\hl{(\mbox{\color{blue}{\texttt{``}}} is for double-backquotes of HOL
+  terms, \mbox{\color{blue}{\texttt{>}}} is HOL's prompt)}
 \begin{lstlisting}

### 2018-07-24 express2018/context.tex
Updated all generated TeX files

@@
 In the same manner, \hl{we can also define variants of contexts (\texttt{GCONTEXT}) and weakly guarded
-contexts (\texttt{WGS}) in which only guarded sums are allowed (i.e. direct sums are forbidden):}
+contexts (\texttt{WGS}) in which only guarded sums are allowed (i.e.~direct sums are forbidden):}
 \begin{alltt}

### 2018-07-24 express2018/part2.tex
Updated all generated TeX files

@@
 For this, we first 
- define \hl{the concept of list-accumulating reflexive transitive closure
+ define \hl{the concept of label-accumulated reflexive transitive closure
  (\texttt{LRTC})}.
-Given a labelled transition relation \texttt{R}, \texttt{LRTC R} is
-a 3-ary relation representing the trace of transitions:
+Given a labeled transition relation \texttt{R} on CCS, \texttt{LRTC R} is
+a label-accumulated relation representing the trace of transitions:
 \begin{alltt}
@@
 \hl{The trace relation for CCS can be then obtained
- by composing \texttt{LRTC} with the (strong) transition
-relation \texttt{TRANS}}:
+ by calling \texttt{LRTC} on the (strong, or single-step) labeled transition
+ relation \texttt{TRANS} ($\overset{\mu}{\rightarrow}$) defined by SOS rules}:
 \begin{alltt}
@@
 \hl{Notice that if the list of actions is empty, that means that there is no transition and hence,}
-if there is at most one visible action (i.e. a label) in the list of actions,
+if there is at most one visible action (i.e.~a label) in the list of actions,
 then the trace is also a weak transition. Here
@@
 \end{alltt}
+
 Having removed the  constraints on sums, the result is
@@
 equations' theorem for \emph{strong} bisimilarity ($\sim$)~--- 
-the same
-weakly guarded  condition (\texttt{WG}) is required:
+the same weakly guarded context (\texttt{WG}) is required:
 \begin{alltt}
@@
 \end{alltt}
-
 In contrast, Milner's ``unique solution of

### 2018-07-24 express2018/sos.tex
Updated all generated TeX files

@@
 \hline
+constant & $A$ & \texttt{var A} & \HOLinline{\HOLConst{var} \HOLFreeVar{A}} \\
 invisible action & $\tau$ & \texttt{tau} & \HOLinline{\HOLSymConst{\ensuremath{\tau}}} \\
@@
 \vspace{-1em}
-   \caption{Syntax of CCS operators}
+   \caption{Syntax of CCS operators, constant and actions}
    \label{tab:ccsoperator}

### 2018-07-24 express2018/unique.tex
Updated all generated TeX files

@@
 operator.
-The schema of the proofs is almost the same, because all needed
-properties of $\rcontr$ in the proof is its precongruence, which is
-now true for unrestricted contexts using direct sums:
-
+The schema of the proofs is almost identical, because all 
+properties of $\rcontr$ needed in this proof is its precongruence, which is
+indeed true on unrestricted contexts including direct sums:
 \begin{lemma}

### 2018-07-25 express2018/conclusions.tex
text

@@
 For the future work, it would be worth extending the current work
-to multi-variable equations/contractions. \hl{Preliminary work shows that,
-the key idea could be using unguarded constants as free variables
+to multi-variable equations/contractions. \hl{
+A the key aspect could be using unguarded constants as free variables
 (\texttt{FV}) and define guardness directly on type CCS (instead of CCS
-$\rightarrow$ CCS) then connect to previous context:}
+$\rightarrow$ CCS):}
 \begin{alltt}
@@
 Formalising other equivalences and preorders could also be considered,
-notably the trace equivalences.
-On the other side, one could examine the formalisation of a different
+notably the trace equivalences as well as 
+more refined calculi such as  value-passing CCS (e.g.,  exploiting the type variable
+of actions).}
+
+On another line, one could examine the formalisation of a different
 approach \cite{DurierHS17} to unique
@@
 replaced by semantic conditions on process transitions such as
-divergence. \hl{The problem of formalising value-passing CCS in a
-more elegant way with minimal efforts (by exploiting the type variable
-of actions, for example) also deserves some thinking.}
-
+divergence. 
 % Further plan on the formalisation mainly includes: 1) the extension to

### 2018-07-25 express2018/context.tex
text

--- 2018-07-23 express2018/context.tex
@@
 above multi-hole contexts. \hl{The only difference between congruence and
-precongruence is, the former must be an equivalence (reflexive,
+precongruence is that the former must be an equivalence (reflexive,
 symmetric, transitive), while the latter can be just a preorder (reflexive, transitive)}:
@@
 In the same manner, \hl{we can also define variants of contexts (\texttt{GCONTEXT}) and weakly guarded
-contexts (\texttt{WGS}) in which only guarded sums are allowed (i.e. direct sums are forbidden):}
+contexts (\texttt{WGS}) in which only guarded sums are allowed (i.e. arbitrary sums are forbidden):}
 \begin{alltt}
@@
 
-\hl{Although weak bisimilarity is not compatible with an unrestricted
-variant of binary choice, it is compatible with weakly guarded
-sums. As a consequence, weak bisimilarity is indeed a ``congruence''
-if we have had another version of \texttt{congruence} w.r.t. above \texttt{GCONTEXT}.}
+\hl{Although weak bisimilarity is not compatible with  aribtrary sums, it is compatible with weakly guarded
+sums. As a consequence, weak bisimilarity would  indeed be a ``congruence''
+if we have had a version of \texttt{congruence} referring to
+ \texttt{GCONTEXT}.}
 %

### 2018-07-25 express2018/part2.tex
text

--- 2018-07-23 express2018/part2.tex
@@
 
-\hl{Notice that if the list of actions is empty, that means that there is no transition and hence,}
-if there is at most one visible action (i.e. a label) in the list of actions,
+\hl{If the list of actions is empty,  there is no transition and hence,}
+if there is at most one visible action (i.e., a label) in the list of actions,
 then the trace is also a weak transition. Here
-we must distinguish between two cases: no label and unique label (in
+we have to distinguish two cases: no label and unique label (in
 the list of actions). The definition of ``no
@@
 The definition of ``unique label'' \hl{can be done in many ways, the
-following definition (learnt from Robert Beers) has
-avoided any counting or filtering in the list.}
+following definition\footnote{A suggestion from Robert Beers}
+avoids any counting or filtering in the list.}
 It says that a label is unique in a list of actions if and only if there is no
@@
 transitions. For instance, from Def.~\ref{d:BisCon}, \hl{it is easy
-to see that, a weak transition either gets shorter
-or remains the same when passing into $\mcontrBIS$ from left to right}.
-\hl{This fact, among others, is crucial} in proving
+to see that a weak transition either becomes shorter
+or remains the same when moving between $\mcontrBIS$-related processes}.
+\hl{This property is essential} in the  proof of
 Lemma~\ref{l:uptocon}. We show only one such lemma, for the case of
@@
 
-Finally, \hl{with all above work carefully done with patience,}
- we have formally proved Theorem~\ref{t:contraBisimulationU}:
+We can thus finally prove
+ Theorem~\ref{t:contraBisimulationU}:
 \begin{alltt}

### 2018-07-25 express2018/related.tex
Use "composition closure" (CC) instead of "context closure" (CC)
text

@@
 libraries in recent versions of HOL4, and our formalisation has
-covered a much larger spectrum of the whole theory.}
+covered a  larger spectrum of the  CCS theory.}
 

### 2018-07-25 express2018/sos.tex
text

--- 2018-07-24 express2018/sos.tex
@@
 The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
-union of all visible actions, plus invisible action $\tau$ (now based on
-HOL's \texttt{option} theory). The cardinality of
+union of all visible and invisible actions. The cardinality of
 ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' (and therefore of all
@@
 syntax\footnote{\hl{The order of type variables $\alpha, \beta$ can be
-    arbitrary. But our choice is aligned with other CCS literals.
+    arbitrary. Our choice is aligned with other CCS literals. Then
 $\mathrm{CCS}(h,k)$ is the CCS subcalculus which can use at most $h$ constants
-and $k$ actions.} \cite{gorrieri2017ccs} \hl{Thus, to formalize theorems on
-this kind of CCS subcalculus, it is enough to instantiate the type
+and $k$ actions.} \hl{Thus, to formalize theorems on such a 
+calculus, it is enough to instantiate the type
 variables $\alpha, \beta$ with types having the corresponding cardinalities $h, k$.}}, is then defined inductively:
@@
 ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is \hl{the type of all relabeling functions,
-\mbox{\color{blue}{\texttt{`}}} is for backquotes of HOL terms}):
+`\mbox{\color{blue}{\texttt{`}}}' is the backquote for HOL terms}):
 \begin{lstlisting}
@@
 prefix & $u.P$ & \texttt{prefix u P} & \HOLinline{\HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{P}} \\
-sum & $P + Q$ & \texttt{sum P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{Q}} \\
+sum & $P + Q$ & \texttt{sum P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{+} \HOLFreeVar{Q}} \\
 parallel & $P \,\mid\, Q$ & \texttt{par P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q}} \\
@@
 \HOLTokenTurnstile{} \HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P}\hfill\texttt{[PREFIX]}
-\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{Q} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[SUM1]}
-\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{Q} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[SUM2]}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{+} \HOLFreeVar{Q} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[SUM1]}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{Q} \HOLSymConst{+} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[SUM2]}
 \HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q}\hfill\texttt{[PAR1]}
@@
 
-The rule \texttt{REC} (Recursion)
+The rule \texttt{[REC]} (Recursion)
  says that if we substitute all appearances of variable $A$ in $P$ to
@@
 is called on the  process $(a.0 | \bar{a}.0)$ thus:
-\hl{(\mbox{\color{blue}{\texttt{``}}} is for double-backquotes of HOL
-  terms, \mbox{\color{blue}{\texttt{>}}} is HOL's prompt)}
+\hl{(`\mbox{\color{blue}{\texttt{``}}}' is the double-backquote for HOL terms)}
 \begin{lstlisting}

### 2018-07-25 express2018/unique.tex
text

--- 2018-07-23 express2018/unique.tex
@@
 
-\hl{The discovery of this definition is with help of HOL theorem
+\hl{The precise formulation of  this definition was guided by the HOL theorem
   prover and
-the following two principles:} (1) Its definition must not be recursive,
-instead it should resemble the definition of rooted bisimilarity
+the following two principles:} (1) the definition should not be recursive,
+along the lines of rooted bisimilarity
 $\approx^c$ in Def.~\ref{d:rootedBisimilarity};
-(2) It must be built on top of existing \emph{contracts}
-relation $\mcontrBIS$, which we believe it's the \emph{right} one
-because of its completeness. \hl{Multiple candicates were quickly tested,
-finally only above definition is proven to be a precongruence, as the
-following theorem states.} (The proof of this result is along the lines of the analogous result
-for rooted bisimilarity with respect to bisimilarity.)
+(2) the definition should  be built on top of existing \emph{contraction}
+relation $\mcontrBIS$ (because of its completeness). 
+\hl{A few other candicates were quickly tested and rejected, e.g.,
+  because of  precongruence issue.} The proof of the precongruence
+ result below is along the lines of the analogous result
+for rooted bisimilarity with respect to bisimilarity.
 
@@
 there is $Q'$ such that $Q \Arr{\mu} Q'$ (not $Q \Arcap{\mu} Q'$!) and
-$P'\ \R\ Q'$, and also for the converse direction, exploting Lemma
-4.13 of \cite{Mil89} \hl{(unexpected!)}. \hl{By definition of
+$P'\ \R\ Q'$, and also for the converse direction, 
+\hl{(surprisingly)}
+exploting Lemma
+4.13 of \cite{Mil89}. \hl{By definition of
 \emph{bisimulation} (not $\wb$!) and $\approx^c$, we actually proved $P

### 2018-07-25 express2018/conclusions.tex
Merged changes of 'conclusions.tex'

@@
-% \section{To Do}
-% \label{s:todo}
-
-% \finish{discuss multiple equations/contractions}
-
-% The formalisation of multi-variable context (or expressions) and the version of
-% ``unique solutions'' theorems with multiple equations/contractions, is
-% a relative hard problem. To the best of our knowledge, so far there's no formalization (in any kind of
-% process calculi) touching these areas yet. However, we've made a few initial steps
-% of this interesting problem.
+%%%% -*- Mode: LaTeX -*-
 
@@
 For the future work, it would be worth extending the current work
-to multi-variable equations/contractions. \hl{
-A the key aspect could be using unguarded constants as free variables
+to multi-variable equations/contractions. \hl{Preliminary work shows that,
+a key aspect could be using unguarded constants as free variables
 (\texttt{FV}) and define guardness directly on type CCS (instead of CCS
-$\rightarrow$ CCS):}
+$\rightarrow$ CCS) then connect to previous context:}
 \begin{alltt}
@@
 Formalising other equivalences and preorders could also be considered,
-notably the trace equivalences as well as 
-more refined calculi such as  value-passing CCS (e.g.,  exploiting the type variable
+notably the trace equivalences, \hl{as well as more refined process
+calculi such as value-passing CCS (e.g.~ exploiting the type variable
 of actions).}
-
-On another line, one could examine the formalisation of a different
+%
+On another research line, one could examine the formalisation of a different
 approach \cite{DurierHS17} to unique
@@
 divergence.
+
 % Further plan on the formalisation mainly includes: 1) the extension to
@@
 from several people from the HOL
-community, including Robert Beers, Jeremy Dawson,
+community, including (in alphabet order) Robert Beers, Jeremy Dawson,
 Ramana Kumar,

### 2018-07-25 express2018/part2.tex
Merged changes of 'part2.tex'

--- 2018-07-24 express2018/part2.tex
@@
 
-\hl{Notice that if the list of actions is empty, that means that there is no transition and hence,}
-if there is at most one visible action (i.e.~a label) in the list of actions,
+\hl{If the list of actions is empty, that means that there is no transition and hence,}
+if there is at most one visible action (i.e., a label) in the list of actions,
 then the trace is also a weak transition. Here
-we must distinguish between two cases: no label and unique label (in
+we have to distinguish between two cases: no label and unique label (in
 the list of actions). The definition of ``no
@@
 The definition of ``unique label'' \hl{can be done in many ways, the
-following definition (learnt from Robert Beers) has
-avoided any counting or filtering in the list.}
+following definition (a suggestion from Robert Beers)
+avoides any counting or filtering in the list.}
 It says that a label is unique in a list of actions if and only if there is no
@@
 transitions. For instance, from Def.~\ref{d:BisCon}, \hl{it is easy
-to see that, a weak transition either gets shorter
-or remains the same when passing into $\mcontrBIS$ from left to right}.
-\hl{This fact, among others, is crucial} in proving
+to see that, a weak transition either becomes shorter
+or remains the same when moving between $\mcontrBIS$-related processes}.
+\hl{This property is essential} in the proof of
 Lemma~\ref{l:uptocon}. We show only one such lemma, for the case of
@@
 
-Finally, \hl{with all above work carefully done with patience,}
- we have formally proved Theorem~\ref{t:contraBisimulationU}:
+\hl{With all above lemmas, we can thus finally prove Theorem~\ref{t:contraBisimulationU}:}
 \begin{alltt}
@@
 equations'' theorem for rooted bisimilarity ($\rapprox$)
-has more severe constraints:
+has more severe constraints (strongly guarded and sequential):
 % Or our Theorem~\ref{t:rcontraBisimulationU} can be seen as a more

### 2018-07-25 express2018/part2.tex
Merged changes of 'unique.tex'

@@
 equations'' theorem for rooted bisimilarity ($\rapprox$)
-has more severe constraints (strongly guarded and sequential):
+has more severe constraints (both strongly guarded and sequential):
 % Or our Theorem~\ref{t:rcontraBisimulationU} can be seen as a more

### 2018-07-25 express2018/unique.tex
Merged changes of 'unique.tex'

@@
 there is $Q'$ such that $Q \Arr{\mu} Q'$ (not $Q \Arcap{\mu} Q'$!) and
-$P'\ \R\ Q'$, and also for the converse direction, 
-\hl{(surprisingly)}
-exploting Lemma
-4.13 of \cite{Mil89}. \hl{By definition of
+$P'\ \R\ Q'$, and also for the converse direction, exploting Lemma
+4.13 of \cite{Mil89} \hl{(surprisingly)}. \hl{By definition of
 \emph{bisimulation} (not $\wb$!) and $\approx^c$, we actually proved $P

### 2018-07-25 express2018/sos.tex
Revert "text" (it's merged later, manually)
This reverts commit 6842460cc5279c6358bbeec6f6a342d085f0e9c7.

@@
 syntax\footnote{\hl{The order of type variables $\alpha, \beta$ can be
-    arbitrary. Our choice is aligned with other CCS literals. Then
+    arbitrary. But our choice is aligned with other CCS literals.
 $\mathrm{CCS}(h,k)$ is the CCS subcalculus which can use at most $h$ constants
-and $k$ actions.} \hl{Thus, to formalize theorems on such a 
-calculus, it is enough to instantiate the type
+and $k$ actions.} \cite{gorrieri2017ccs} \hl{Thus, to formalize theorems on
+this kind of CCS subcalculus, it is enough to instantiate the type
 variables $\alpha, \beta$ with types having the corresponding cardinalities $h, k$.}}, is then defined inductively:

### 2018-07-25 express2018/context.tex

--- 2018-07-24 express2018/context.tex
@@
 In the same manner, \hl{we can also define variants of contexts (\texttt{GCONTEXT}) and weakly guarded
-contexts (\texttt{WGS}) in which only guarded sums are allowed (i.e. direct sums are forbidden):}
+contexts (\texttt{WGS}) in which only guarded sums are allowed (i.e.~arbitrary sums are forbidden):}
 \begin{alltt}
@@
 \texttt{CONTEXT}. \hl{The only difference between congruence and
-precongruence is, the former must be an equivalence (reflexive,
+precongruence is that the former must be an equivalence (reflexive,
 symmetric, transitive), while the latter can be just a preorder (reflexive, transitive)}:
@@
 \end{alltt}
-\hl{Weak bisimilarity ($\approx$) is \emph{not} congruence
-  w.r.t. \texttt{CONTEXT}. However, it is ``congruence''
-  w.r.t. \texttt{GCONTEXT} (or if the CCS syntax were defined with
-  only guarded sum operator, as in \cite{sangiorgi2015equations}) because $\approx$ is indeed preserved by 
+
+\hl{Although weak bisimilarity ($\approx$) is \emph{not} congruence
+  with respect to~\texttt{CONTEXT}, it is indeed ``congruence''
+  with respect to~\texttt{GCONTEXT} (or if the CCS syntax were defined with
+  only guarded sum operator \cite{sangiorgi2015equations}) as weak
+  bisimilarity ($\approx$) is indeed preserved by 
   weakly-guarded sums.}

### 2018-07-25 express2018/related.tex

@@
 theorem prover.\footnote{Part of her old proof scripts is now available at
-  \url{https://github.com/binghe/HOL-CCS/tree/master/CCS-Nesi}.}.
-Her main focus was on implementing decision procedures (as ML functions) for
+  \url{https://github.com/binghe/HOL-CCS/tree/master/CCS-Nesi}.}
+Her main focus was on implementing decision procedures (as a ML
+program, e.g.~\cite{CLEAVELAND:1993dr}) for
 automatically proving bisimilarities of CCS
@@
 libraries in recent versions of HOL4, and our formalisation has
-covered a  larger spectrum of the  CCS theory.}
+covered a much larger spectrum of the (pure) CCS theory.}
 

### 2018-07-25 express2018/sos.tex

--- 2018-07-24 express2018/sos.tex
@@
 The type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'', accounting for the CCS
-syntax\footnote{\hl{The order of type variables $\alpha, \beta$ can be
-    arbitrary. But our choice is aligned with other CCS literals.
+syntax\footnote{\hl{The order of type variables $\alpha$ and $\beta$
+    is irrelevant. Our choice is aligned with other CCS literals.
 $\mathrm{CCS}(h,k)$ is the CCS subcalculus which can use at most $h$ constants
 and $k$ actions.} \cite{gorrieri2017ccs} \hl{Thus, to formalize theorems on
-this kind of CCS subcalculus, it is enough to instantiate the type
-variables $\alpha, \beta$ with types having the corresponding cardinalities $h, k$.}}, is then defined inductively:
+such a CCS subcalculus, the needed CCS type can be retrieved by instantiating the type
+variables $\alpha$ and $\beta$ in ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'' with types
+having the corresponding cardinalities $h$ and $k$. Monica Nesi goes
+too far by adding another type variable $\gamma$ for value-passing CCS \cite{Nesi:2017wo}.}}, is then defined inductively:
 (\texttt{'a} or $\alpha$ is the type variable for recursion variables,
@@
 with action $u$, then $(\mathbf{rec}\; A\; P)$ has the same
-transition. From the HOL  viewpoint, these
+transition. From HOL's viewpoint, these
 SOS rules are \emph{inductive 

### 2018-07-25 express2018/intro.tex
Added DOIs to all cited papers.

@@
 This method is important in verification techniques and tools
-based on algebraic reasoning \cite{BaeBOOK,theoryAndPractice}.
+based on algebraic reasoning \cite{RosUnder10,BaeBOOK,theoryAndPractice}.
 
@@
  all labels;
-the other without such hypothesis, essentially formalising van Glabbeek's paper \cite{vanGlabbeek:2005ur}.
+the other without such hypothesis, essentially formalising van Glabbeek's paper \cite{van2005characterisation}.
 Similar theorems are proved for the rooted contraction preorder.
@@
 the one for rooted in which
-the auxiliary relation is rooted contraction); various forms of enhancement of the bisimulation
-proof method (the `up-to' techniques).  
-In these cases,  moving between proofs there are only a few places in which the HOL scripts have to be modified.
+the auxiliary relation is rooted contraction); various forms of enhancements of the bisimulation
+proof method (the `up-to' techniques) \cite{Mil89,sangiorgi1992problem}.
+In these cases,  moving between proofs there are only a few places in
+which the HOL scripts have to be modified.
 Then the successful termination of the scripts  gives us a guarantee that the proof is
@@
 % % book,  requiring the hypothesis that  no processes can use all labels; the other without
-% % such hypothesis, essentially formalising van Glabbek's paper \cite{vanGlabbeek:2005ur}.
+% % such hypothesis, essentially formalising van Glabbek's paper \cite{van2005characterisation}.
 % % Similar theorems are proved for rooted contractions wrt the contraction preorder.

### 2018-07-25 express2018/related.tex
Added DOIs to all cited papers.

@@
 Her main focus was on implementing decision procedures (as a ML
-program, e.g.~\cite{CLEAVELAND:1993dr}) for
+program, e.g.~\cite{cleaveland1993concurrency}) for
 automatically proving bisimilarities of CCS
@@
 using Isabelle/HOL and its \texttt{nominal} datatype package, with main focus on the handling of
-name binders \cite{bengtson2010formalising,bengtson2007completeness,bengtson2007formalising}.
+name binders \cite{bengtson2010formalising,bengtson2007completeness,parrow2009formalising}.
 % Jesper Bengtson's PhD thesis 

### 2018-07-25 express2018/sos.tex
Last addition: name of example theorem.

@@
     (\HOLFreeVar{u} \HOLSymConst{=} \HOLConst{Out} \HOLStringLit{a}) \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{In} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil})) \HOLSymConst{\HOLTokenDisj{}}
-   (\HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}}) \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil})
+   (\HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}}) \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil})\hfill{[Example.ex_A]}
 \end{alltt}

### 2018-07-25 express2018/intro.tex
Added breakurl package (for PostScript->PDF workflow); completed Robin's name (at least the first appearence!)
More reasonable positions of some cites

@@
 
-A prominent proof method for bisimulation, put forward by Milner and widely used in his
+A prominent proof method for bisimulation, put forward by Robin Milner and widely used in his
 landmark CCS book \cite{Mil89} is the
@@
 This method is important in verification techniques and tools
-based on algebraic reasoning \cite{RosUnder10,BaeBOOK,theoryAndPractice}.
+based on algebraic reasoning \cite{BaeBOOK,theoryAndPractice,RosUnder10}.
 
@@
 \cite{Nesi:1992ve}) include four versions of ``bisimulation up to''
-techniques (e.g., bisimulation up-to bisimilarity), and of the
+techniques (e.g., bisimulation up-to bisimilarity) \cite{Mil89,sangiorgi1992problem}, and the
 expansion and contraction preorder (two
@@
 \cite{Gorrieri:2015jt}),
- and two long proofs saying the rooted bisimilarity is the largest (coarsest)
+ and two long proofs saying the rooted bisimilarity is the coarsest (largest)
  congruence contained in (weak) bisimilarity: one following Milner's
@@
 the auxiliary relation is rooted contraction); various forms of enhancements of the bisimulation
-proof method (the `up-to' techniques) \cite{Mil89,sangiorgi1992problem}.
+proof method (the `up-to' techniques).
 In these cases,  moving between proofs there are only a few places in

### 2018-07-25 express2018/part2.tex
Use a better sample theorem to show the power of TRACE

@@
 Lemma~\ref{l:uptocon}. We show only one such lemma, for the case of
-$\tau$-transitions passing into $\mcontrBIS$ (from left to right):
+non-$\tau$ weak transitions passing into $\mcontrBIS$ (from left to right):
 \begin{alltt}
 \HOLTokenTurnstile{} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{xs} \HOLBoundVar{P\sp{\prime}}.
-       \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{xs} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{xs} \HOLBoundVar{l} \HOLBoundVar{P\sp{\prime}}.
+       \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{xs} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{UNIQUE_LABEL} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{xs} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{xs\sp{\prime}} \HOLBoundVar{Q\sp{\prime}}.
-           \HOLConst{TRACE} \HOLFreeVar{Q} \HOLBoundVar{xs\sp{\prime}} \HOLBoundVar{Q\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{Q\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLBoundVar{xs\sp{\prime}} \HOLSymConst{\HOLTokenLeq{}} \HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenConj{}}
-           \HOLConst{NO_LABEL} \HOLBoundVar{xs\sp{\prime}}\hfill{[contracts_AND_TRACE_tau]}
+           \HOLConst{TRACE} \HOLFreeVar{Q} \HOLBoundVar{xs\sp{\prime}} \HOLBoundVar{Q\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLBoundVar{xs\sp{\prime}} \HOLSymConst{\HOLTokenLeq{}} \HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenConj{}}
+           \HOLConst{UNIQUE_LABEL} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{xs\sp{\prime}}\hfill{[contracts_AND_TRACE_label]}
 \end{alltt}

### 2018-07-25 express2018/unique.tex
Use a better sample theorem to show the power of TRACE

@@
 (R,S) \st R \wb \ct{\til P}, S \wb \ct{\til Q} \mbox{ for some context
-$\qct$ (having only weakly-guarded sums)} \} \enspace.
+$\qct$ (weakly-guarded sum only)} \} \enspace.
 \end{equation}
@@
 ``solution for $\rcontr$'' and of \emph{a unique solution for $\rapprox$}
-is the expected one --- just replace in Definition~\ref{d:uniContra}  the preorder 
+is the expected one --- just replace in Def.~\ref{d:uniContra}  the preorder 
 $\contr$ with $\rcontr$, and the equivalence 

### 2018-07-25 express2018/conclusions.tex
There're still typos (found by spellchecker), amazing...

@@
 We think that the statements in the formalisation are easy to read and
-understand, as they are very close to the orginal statements found in
+understand, as they are very close to the original statements found in
 standard CCS textbooks \cite{Gorrieri:2015jt,Mil89}.
@@
 a key aspect could be using unguarded constants as free variables
-(\texttt{FV}) and define guardness directly on type CCS (instead of CCS
+(\texttt{FV}) and define guardedness directly on type CCS (instead of CCS
 $\rightarrow$ CCS) then connect to previous context:}
@@
 % provided a solid formal framework for future theoretical developments in
-% Concurrency Theory, particularily for process algebras like CCS. It's
+% Concurrency Theory, particularly for process algebras like CCS. It's
 % easily understandable, with statements extremely close to the original
@@
 Konrad Slind, and
-Thomas Tuerk.
+Thomas T\"{u}rk.
 %

### 2018-07-25 express2018/context.tex
There're still typos (found by spellchecker), amazing...

@@
 contexts}, as each hole corresponds to one
-appearence of the \emph{same} variable in single-variable
+appearance of the \emph{same} variable in single-variable
 expressions (or equations). Thus \emph{contexts} can be directly used in

### 2018-07-25 express2018/formal.tex
There're still typos (found by spellchecker), amazing...

@@
 \hl{Moreover, using} the same language HOL4 users can write complex automatic
-verification tools by calling HOL's interactive theorem proving
-facilities. \hl{(The formal proof of theorems in CCS theory
-is mostly done by an \emph{interactive process} closely following
-their informal proofs.)}
+verification tools by calling HOL's theorem proving
+facilities. \hl{(The formal proofs of theorems in CCS theory
+are mostly done by an \emph{interactive process} closely following
+their informal proofs, with minimal automatic proof searching.)}
 
@@
 This considerably
- simplifies the required proofs in HOL, enhances the readibility of
+ simplifies the required proofs in HOL, enhances the readability of
  proof scripts, \hl{without loss of generality (for paper proofs, the

### 2018-07-25 express2018/intro.tex
There're still typos (found by spellchecker), amazing...

@@
 variables of the equations may only be used underneath a visible
-prefix and preceed, in the syntax tree, only by the sum and prefix operators.
+prefix and proceed, in the syntax tree, only by the sum and prefix operators.
 One way of overcoming such limitations is to replace equations

### 2018-07-25 express2018/part2.tex
There're still typos (found by spellchecker), amazing...

@@
 following definition (a suggestion from Robert Beers)
-avoides any counting or filtering in the list.}
+avoids any counting or filtering in the list.}
 It says that a label is unique in a list of actions if and only if there is no

### 2018-07-25 express2018/related.tex
There're still typos (found by spellchecker), amazing...

@@
 
-\hl{Monica Nesi made the first CCS formalisations for both pure and
+\hl{Monica Nesi did the first CCS formalisations for both pure and
 value-passing CCS} \cite{Nesi:1992ve,Nesi:2017wo} using early versions of the HOL

### 2018-07-25 express2018/sos.tex
There're still typos (found by spellchecker), amazing...

@@
 SOS rules are \emph{inductive 
-  definitions} on the 3-ary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL's
+  definitions} on the tenary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL's
 \texttt{Hol_reln} function.
@@
     relabeling operators, the program will loop forever without
-    outputing a theorem.}
+    outputting a theorem.}
 For instance, we know that the process $(a.0 | \bar{a}.0)$ has three

### 2018-07-25 express2018/unique.tex
There're still typos (found by spellchecker), amazing...

@@
 along the lines of rooted bisimilarity
-$\approx^c$ in Def.~\ref{d:rootedBisimilarity};
+$\rapprox$ in Def.~\ref{d:rootedBisimilarity};
 (2) the definition should  be built on top of existing \emph{contraction}
 relation $\mcontrBIS$ (because of its completeness). 
-\hl{A few other candicates were quickly tested and rejected, e.g.,
+\hl{A few other candidates were quickly tested and rejected, e.g.,
   because of  precongruence issue.} The proof of the precongruence

### 2018-07-25 express2018/ccs.tex
Use back "rf" as relabeling function in CCS syntax
Further wording fixes (bisimilarity definition was wrong!)

@@
 We assume  a possibly infinite set of \emph{names} $\mathscr{L} = \{a, b,
-\ldots\}$, which does not contain the special symbol $\tau$, and
-a set of variables $A,B, \ldots$ for writing recursive behaviours. 
-The class  of the CCS processes is inductively built from $\nil$ by the operators
-of  prefixing, parallel composition,  sum, restriction, recursion and \hl{relabeling}:
+\ldots\}$ forming input and output actions, plus a special invisible
+action $\tau$ not in $\mathscr{L}$, and a set of variables $A,B,
+\ldots$ for defining recursive behaviours.
+The class  of the CCS processes is inductively defined from $\nil$ by the operators
+of prefixing, parallel composition, sum (binary choice), restriction, recursion and \hl{relabeling}:
 \begin{equation*}
@@
   (\res a\!)\, P  \;  \midd \;  A \; \midd \; \recu A  P
-\; \midd \; P\; [f]  % relabelling
+\; \midd \; P\; [r\!\!f]  % relabelling
 \end{array}
@@
 The operational semantics of CCS is given by means of
-a Labeled Transition System (LTS), shown in Fig.~\ref{f:LTSCCS} (the symmetric version of the two rules for
+a Labeled Transition System (LTS), shown in Fig.~\ref{f:LTSCCS} as SOS
+rules (the symmetric version of the two rules for
 parallel composition and the rule for sum are omitted).
@@
 % We use $\ell$ to range over
-%  visible actions (i.e.,  inputs or outputs, excluding  $\tau$).
+%  visible actions (i.e.~inputs or outputs, excluding  $\tau$).
 \begin{figure*}
@@
 $\displaystyle{ P \arr{\mu} P' \over
- P \;[f] \arr{f(\mu)} P' \;[f]} $ $\forall a.\, f(\outC a) = \overline{f(a)}$
+ P \;[r\!\!f] \arr{r\!\!f(\mu)} P' \;[r\!\!f]} $ $\forall a.\, r\!\!f(\outC a) = \overline{r\!\!f(a)}$
 $ \hb$ %  &
@@
 \end{figure*}
-Some standard notations for transitions:  $\Longrightarrow $ is the 
-reflexive and  transitive closure of $\arr\tau $, and 
-$\Arr \mu $ is $\Longrightarrow \arr\mu \Longrightarrow $ (the
+Some standard notations for transitions:  $\Arr\epsilon$ is the 
+reflexive and transitive closure of $\arr\tau$, and 
+$\Arr \mu $ is $\Arr\epsilon \arr\mu \Arr\epsilon$ (the
 composition of the three relations).
@@
 \ctx \R$ for the closure of a relation under contexts. Thus $P\: \ctx \R\: Q$
-means that there are a context $\qct$ and tuples $\til P,\til Q$ with
+means that there are context $\qct$ and tuples $\til P,\til Q$ with
 $P =  \ct{\til P}, Q =  \ct{\til Q}$ and    $\til P \RR \til Q$.

### 2018-07-25 express2018/expansion.tex
Fixed spacing issues by "i.e. "
Further wording fixes (bisimilarity definition was wrong!)

@@
 
-The equivalences we consider are mainly the \emph{weak} ones, in that they
-abstract from the number of internal steps performed:
+The equivalences we consider here are mainly \emph{weak} ones, in that they
+abstract from the number of internal steps being performed:
 \begin{definition}%[bisimilarity]
@@
  $P$ and $Q$ are \textbf{bisimilar},
-written as $P \wb Q$, if $P \RR Q$ for any bisimulation $\R$.  
+written as $P \wb Q$, if $P \RR Q$ for some bisimulation $\R$.
 \end{definition}
@@
 We sometimes call bisimilarity the \emph{weak} one, to
-distinguish it from \emph{strong bisimilarity} ($\sim$)
+distinguish it from \emph{strong} bisimilarity ($\sim$),
 obtained by replacing in the above definition   the weak answer $
 Q\Arcap\mu Q'$ with the strong  $Q \arr \mu Q'$.
-Bisimilarity (the weak one) is not preserved by the sum operator (except for
+Weak bisimilarity is not preserved by the sum operator (except for
 guarded sums). For this, Milner introduced \emph{observational congruence}, also called \emph{rooted
@@
 % \end{enumerate}
-% then $P$ and $Q$ are rooted bisimilar, i.e., $P \approx^c Q$.
+% then $P$ and $Q$ are rooted bisimilar, i.e.~$P \approx^c Q$.
 % \end{lemma}
@@
 $\rapprox$ is a congruence in CCS, and it is the
-coarsest congruence contained in $\approx$.
+coarsest (i.e.~largest) congruence contained in $\approx$.
 \end{theorem}
@@
 % but also that $Q$  achieves  the same as  $P$ 
-% with  no more work, i.e. with no more $\tau$ actions.
+% with  no more work, i.e.~with no more $\tau$ actions.
 % Intuitively, if $ P \expa Q$, we can think of $Q$ as being 

### 2018-07-25 express2018/intro.tex
Further wording fixes (bisimilarity definition was wrong!)

@@
 further refining the theory of unique solutions of
-equations, as formally proving previous previously known results gives us a
-chance to see \emph{what's really needed} for establishing that results.
-In particular, the existing theory has placed limitations on the body of the contractions due to the
+equations, as formally proving a previously known result gives us a
+chance to see \emph{what's really needed} for establishing that result.
+In particular, the existing theory \cite{sangiorgi2017equations} has
+placed limitations on the body of the contractions due to the
 substitutivity problems of weak bisimilarity and other behavioural relations with respect
@@
 In these cases,  moving between proofs there are only a few places in
-which the HOL scripts have to be modified.
-Then the successful termination of the scripts  gives us a guarantee that the proof is
-completed,  removing the risk 
+which the HOL proof scripts have to be modified.
+Then the successful termination of the proof gives us a guarantee that the proof is
+complete and trustworthy, removing the risk 
 of overlooking or missing details as in hand-written proofs.

### 2018-07-25 express2018/part2.tex
Further wording fixes (bisimilarity definition was wrong!)

@@
 that is, \texttt{WG} in place of \texttt{WGS}):
+\vspace{-2ex}
 \begin{alltt}
+\hfill{[UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS]}
 \HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
 \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
-\hfill{[UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS]}
 \end{alltt}
@@
 \end{alltt}
+
 In contrast, Milner's ``unique solution of
 equations'' theorem for rooted bisimilarity ($\rapprox$)
-has more severe constraints (both strongly guarded and sequential):
+has more severe constraints (must be both strongly guarded and sequential):
 % Or our Theorem~\ref{t:rcontraBisimulationU} can be seen as a more
@@
 % restrictions on equations:
+\vspace{-2ex}
 \begin{alltt}
+\hfill{[OBS_UNIQUE_SOLUTION]}
 \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
 \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
-\hfill{[OBS_UNIQUE_SOLUTION]}
 \end{alltt}
-\vspace{-4ex}

### 2018-07-25 express2018/contraction.tex
Fixed p.5 l.22: instead of \subseteq write \subset or \subsetneq. #27
Minor typesetting optimizations
Make the definition of "contracts" consistent with bisimilarity definition.

--- 2018-06-17 express2018/contraction.tex
@@
 
-\begin{definition}[bisimulation  contraction]
+\begin{definition}%[bisimulation contraction]
 \label{d:BisCon}
@@
 \begin{enumerate}
-
 \item   $P \arr\mu P'$ implies there is $Q'$ such that $Q \arcap \mu
@@
 \end{enumerate}
-\emph{Bisimilarity  contraction}, written $\mcontrBIS$, is the union
-of all bisimulation contractions. 
+\emph{Bisimilarity  contraction}, written as $P \mcontrBIS Q$ ($P$
+\emph{contracts to} $Q$), if $P\ \R\ Q$ for some contraction $\R$.
 \end{definition}
@@
  the \emph{expansion relation} 
-$\expa$ \cite{sangiorgi2015equations} %, arun1992efficiency}.
+$\expa$ \cite{arun1992efficiency,sangiorgi2015equations}.
 This is a
@@
 $\expa$, which explains the strictness of the inclusion
- ${\expa} \subseteq {\mcontrBIS}$. 
+ ${\expa} \subset {\mcontrBIS}$. 
 % The inclusion is strict: for instance
@@
 
-As  bisimilarity  and expansion, contraction is preserved by all operators but sum.
+\hl{Like} (weak) bisimilarity and expansion, contraction is
+preserved by all operators but (direct) sum.

### 2018-07-25 express2018/contraction.tex
Replacing \emph{} inside \begin{defn} with \textbf{} to preserve the italic fonts.

@@
 A process relation ${\R}$ 
- is a {\em  bisimulation  contraction}  if, whenever
+ is a \textbf{(bisimulation) contraction} if, whenever
  $P\RR Q$, %for all $\mu$
@@
 \end{enumerate}
-\emph{Bisimilarity  contraction}, written as $P \mcontrBIS Q$ ($P$
-\emph{contracts to} $Q$), if $P\ \R\ Q$ for some contraction $\R$.
+\textbf{Bisimilarity contraction}, written as $P \mcontrBIS Q$ ($P$
+\textbf{contracts to} $Q$), if $P\ \R\ Q$ for some contraction $\R$.
 \end{definition}

### 2018-07-25 express2018/unique.tex
Replacing \emph{} inside \begin{defn} with \textbf{} to preserve the italic fonts.

@@
 We first follow the same steps as in the proof of Theorem~\ref{t:contraBisimulationU} to show the relation $\R$ (now
-with $\rcontr$ and unrestrict context $C$) in (\ref{eq:R}) is bisimulation,
+with $\rcontr$ and unrestricted context $C$) in (\ref{eq:R}) is bisimulation,
 exploting Lemma~\ref{l:ruptocon}. \hl{Then it remains to show that,} for

### 2018-07-25 express2018/expansion.tex
Replacing \emph{} inside \begin{defn} with \textbf{} to preserve the italic fonts. #2

@@
 \label{d:wb}
-A process relation ${\R}$ is a \emph{bisimulation} if, whenever
+A process relation ${\R}$ is a \textbf{bisimulation} if, whenever
  $P\RR Q$, %for all $\mu$ 
@@
 \label{d:rootedBisimilarity}
-Two processes $P$ and $Q$ are \emph{rooted bisimilar}, written $P
+Two processes $P$ and $Q$ are \textbf{rooted bisimilar}, written as $P
 \rapprox Q$, if we have:

### 2018-07-25 express2018/ccs.tex
Use \overline to indicate "output" actions briefly.

@@
 
-We assume  a possibly infinite set of \emph{names} $\mathscr{L} = \{a, b,
-\ldots\}$ forming input and output actions, plus a special invisible
-action $\tau$ not in $\mathscr{L}$, and a set of variables $A,B,
+We assume  a possibly infinite set of names $\mathscr{L} = \{a, b,
+\ldots\}$ forming input and $\overline{\mbox{output}}$ actions, plus a special invisible
+action $\tau \notin \mathscr{L}$, and a set of variables $A,B,
 \ldots$ for defining recursive behaviours.
-The class  of the CCS processes is inductively defined from $\nil$ by the operators
-of prefixing, parallel composition, sum (binary choice), restriction, recursion and \hl{relabeling}:
+Given a deadlock $\nil$, the class of CCS processes is then inductively defined from $\nil$ by the operators
+of prefixing, parallel composition, summation (binary choice), restriction, recursion and \hl{relabeling}:
 \begin{equation*}

### 2018-07-25 express2018/formal.tex
More precise description of multi-variable cases

@@
 
-HOL4 is written in Standard ML, a single programming language who
+HOL4 is written in Standard ML, a single programming language which
 plays three different roles:
@@
 This considerably
- simplifies the required proofs in HOL, enhances the readability of
- proof scripts, \hl{without loss of generality (for paper proofs, the
- general case is just a routine
- adaptation).}
+ simplifies the required proofs in HOL, also enhances the readability of
+ proof scripts \hl{without loss of generality. (For paper proofs, the
+ multi-variable case is just a routine adaptation.)}
 %   still aligned with

### 2018-07-26 express2018/conclusions.tex
Refined future work with a line explaining the new definition

@@
 
-We have highlighted a formalisation of the theory of CCS in the 
+In this paper, we have highlighted a formalisation of the theory of CCS in the 
 HOL4 theorem prover (for lack of space we have not discussed 
@@
 
-For the future work, it would be worth extending the current work
-to multi-variable equations/contractions. \hl{Preliminary work shows that,
-a key aspect could be using unguarded constants as free variables
-(\texttt{FV}) and define guardedness directly on type CCS (instead of CCS
-$\rightarrow$ CCS) then connect to previous context:}
+For the future work, it would be worth extending
+to multi-variable equations/contractions. \hl{A key aspect could be using unguarded constants as free variables
+(\texttt{FV}) and define guardedness directly on expressions of type CCS (instead of
+CCS $\rightarrow$ CCS), then link to contexts. For instance, an expression is weakly-guarded when each
+of its free variables, replaced by a hole, results in a weakly-guarded context.}
 \begin{alltt}
@@
 notably the trace equivalences, \hl{as well as more refined process
-calculi such as value-passing CCS (e.g.~ exploiting the type variable
+calculi such as value-passing CCS (e.g.~exploiting the type variable
 of actions).}
@@
 replaced by semantic conditions on process transitions such as
-divergence.
+divergence. We hope this work also inspires new formalisations on
+other process calculi.
 

### 2018-07-26 express2018/related.tex
Refined future work with a line explaining the new definition

@@
 value-passing CCS} \cite{Nesi:1992ve,Nesi:2017wo} using early versions of the HOL
-theorem prover.\footnote{Part of her old proof scripts is now available at
+theorem prover.\footnote{Part of this work can now be found at
   \url{https://github.com/binghe/HOL-CCS/tree/master/CCS-Nesi}.}
@@
 Bengtson,  Parrow and Weber
-have made a substantial formalisation work 
+made a substantial formalisation work 
 on CCS, $\pi$-calculi

### 2018-07-26 express2018/conclusions.tex
Grammatical fixes

@@
 to multi-variable equations/contractions. \hl{A key aspect could be using unguarded constants as free variables
-(\texttt{FV}) and define guardedness directly on expressions of type CCS (instead of
-CCS $\rightarrow$ CCS), then link to contexts. For instance, an expression is weakly-guarded when each
-of its free variables, replaced by a hole, results in a weakly-guarded context.}
+(\texttt{FV}) and defining guardedness directly on expressions of type CCS (instead of
+CCS $\rightarrow$ CCS), then linking to contexts. For instance, an expression is weakly-guarded when each
+of its free variables, replaced by a hole, results in a weakly-guarded context:}
 \begin{alltt}

### 2018-07-26 express2018/formal.tex
HOL traces its roots back to Edinburgh LCF by Robin Milner and others in 1972

@@
 
-Higher Order Logic (or \emph{HOL Logic}) \cite{hollogic} is a variant of
-Church’s simple theory of types (STT) \cite{church1940formulation}
-\hl{(or \emph{simple-typed $\lambda$-calculus}),
+Higher Order Logic (or \emph{HOL Logic}) \cite{hollogic}, which traces
+its roots back to
+\emph{Edinburgh LCF} by Robin Milner and others in 1972, is a variant of
+Church’s simple theory of types (STT) \cite{church1940formulation},
 plus a higher order version of Hilbert's choice operator $\varepsilon$,
-Axiom of Infinity, and Rank-1 (prenex) polymorphism.}
+Axiom of Infinity, and Rank-1 (prenex) polymorphism.
 HOL4 has implemented the original HOL Logic, 
@@
 foundations than most other theorem provers. %, e.g. Coq. 
-As a result,
-formal theories built in HOL4 is relatively easier convincible and can
-be also easily migrated into other theorem provers,
-sometimes even automatically \cite{hurd2011opentheory}.
+As a consequence,
+formal theories built in HOL is easily convincible and can
+also be easily ported to other proof systems,
+sometimes automatically \cite{hurd2011opentheory}.
 
@@
 \begin{enumerate}
-\item It serves as the underlying implementation language for the core HOL engine;
-\item it is used to implement tactics (and tacticals) for writing proofs;
+\item It serves as the underlying implementation language for the core HOL engine;\vspace{-1ex}
+\item it is used to implement tactics (and tacticals) for writing proofs;\vspace{-1ex}
 \item it is used as the command language of the HOL interactive shell.

### 2018-07-26 express2018/formal.tex
Added cite of Milner's LCF paper

@@
 Higher Order Logic (or \emph{HOL Logic}) \cite{hollogic}, which traces
-its roots back to
-\emph{Edinburgh LCF} by Robin Milner and others in 1972, is a variant of
+its roots back to \emph{LCF} \cite{milner1972logic} by Robin Milner in 1972, is a variant of
 Church’s simple theory of types (STT) \cite{church1940formulation},

### 2018-07-26 express2018/formal.tex
Fixed bibitem of LCF

--- 2018-07-26 express2018/formal.tex
@@
 Higher Order Logic (or \emph{HOL Logic}) \cite{hollogic}, which traces
-its roots back to
-\emph{Edinburgh LCF} by Robin Milner and others in 1972, is a variant of
+its roots back to LCF
+\cite{gordon1979edinburgh,milner1972logic} by Robin Milner and others since 1972, is a variant of
 Church’s simple theory of types (STT) \cite{church1940formulation},

### 2018-07-26 express2018/related.tex
Added two old pi-calculus formalisation as related work.

@@
 % complete. \cite{bengtson2007completeness} 
-Other formalisations in this area include the work of Solange
-Coupet-Grimal\footnote{\url{https://github.com/coq-contribs/ccs}} in Coq
-and Chaudhuri et al.\;\cite{chaudhuri2015lightweight} in Abella. The
-latter focuses on `bisimulation up-to' techniques for strong bisimilarity 
+Other formalisations in this area include the work of T. F. Melham
+\cite{melham1994mechanized} and O.A. Mohamed
+\cite{mohamed1995mechanizing} in HOL,
+the work of S. Coupet-Grimal\footnote{\url{https://github.com/coq-contribs/ccs}} in Coq
+and Chaudhuri et al.\;\cite{chaudhuri2015lightweight} in Abella
+, which
+focuses on `bisimulation up-to' techniques %for strong bisimilarity
 for CCS and $\pi$-calculus.

### 2018-07-26 express2018/related.tex
Final additions of related work. I think now this is enough.

@@
 
-Bengtson,  Parrow and Weber
-made a substantial formalisation work 
+Bengtson, Parrow and Weber did a substantial formalisation work
 on CCS, $\pi$-calculi
 and $\psi$-calculi 
-using Isabelle/HOL and its \texttt{nominal} datatype package, with main focus on the handling of
+using Isabelle/HOL and its \texttt{nominal} logic, with main focus on the handling of
 name binders \cite{bengtson2010formalising,bengtson2007completeness,parrow2009formalising}.
@@
 % complete. \cite{bengtson2007completeness} 
-Other formalisations in this area include the work of T. F. Melham
+Other formalisations in this area include the early work of T. F. Melham
 \cite{melham1994mechanized} and O.A. Mohamed
-\cite{mohamed1995mechanizing} in HOL,
-the work of S. Coupet-Grimal\footnote{\url{https://github.com/coq-contribs/ccs}} in Coq
-and Chaudhuri et al.\;\cite{chaudhuri2015lightweight} in Abella
-, which
+\cite{mohamed1995mechanizing} in HOL, Compton
+\cite{compton2005embedding} in Isabelle/HOL,
+Solange\footnote{\url{https://github.com/coq-contribs/ccs}} in Coq
+and Chaudhuri et al.\;\cite{chaudhuri2015lightweight} in Abella, the latter
 focuses on `bisimulation up-to' techniques %for strong bisimilarity
 for CCS and $\pi$-calculus.
-Damien Pous also formalised up-to techniques and some CCS examples in
-Coq. \cite{pous2007new}
+Damien Pous \cite{pous2007new} also formalised up-to techniques and some CCS examples in
+Coq.
 Formalisations less related to ours
 include Kahsai and Miculan \cite{kahsai2008implementing} for the spi
-calculus  in Isabelle, and Hirschkoff \cite{hirschkoff1997full} for the $\pi$-calculus in Coq.
+calculus in Isabelle/HOL, and Hirschkoff \cite{hirschkoff1997full} for the $\pi$-calculus in Coq.

### 2018-07-31 express2018/conclusions.tex
Slightly shrink the paper for arXiv.org

@@
 Formalising other equivalences and preorders could also be considered,
-notably the trace equivalences, \hl{as well as more refined process
-calculi such as value-passing CCS (e.g.~exploiting the type variable
-of actions).}
+notably the trace equivalences, as well as more refined process
+calculi such as value-passing CCS.
+% (e.g.~exploiting the type variable
+%of actions).}
 %
@@
 replaced by semantic conditions on process transitions such as
-divergence. We hope this work also inspires new formalisations on
-other process calculi.
+divergence. 
+%We hope this work also inspires new formalisations on other process calculi.
 

### 2018-11-06 ic-journal/contraction.tex
Duplicate the paper sources (no content changes), using Elsevier's LaTeX template (for submission/review)

--- 2018-07-25 express2018/contraction.tex
@@
 The constraints on the unique-solution Theorem~\ref{t:Mil89} can be 
-weakened if  we move from equations to inequations called
+weakened if we move from equations to a special kind of inequations called
   \emph{contractions}.
 
-  Intuitively,
-  the bisimilarity contraction 
-$\mcontrBIS$ 
- is  a preorder in which 
+Intuitively, the bisimilarity contraction $\mcontrBIS$ is a preorder in which 
 $P \mcontrBIS Q  $  holds  if $P \wb Q$ and, in addition, 
@@
 \item   $P \arr\mu P'$ implies there is $Q'$ such that $Q \arcap \mu
-  Q'$
- and $P' \RR Q'$;
-
-\item 
-    $Q \arr\mu Q'$   implies there is $P'$ such that $P \Arcap \mu
- P'$ and $P' 
-\wb Q'$.
+  Q'$ and $P' \RR Q'$;
+\item $Q \arr\mu Q'$   implies there is $P'$ such that $P \Arcap \mu
+ P'$ and $P' \wb Q'$\enspace.
 \end{enumerate}

### 2018-11-06 ic-journal/sos.tex
Duplicate the paper sources (no content changes), using Elsevier's LaTeX template (for submission/review)

--- 2018-07-25 express2018/sos.tex
@@
  says that if we substitute all appearances of variable $A$ in $P$ to
-$(\mathbf{rec}\; A\; P)$ and the resulting process has a transition to $P'$
-with action $u$, then $(\mathbf{rec}\; A\; P)$ has the same
+$(\recu A P)$ and the resulting process has a transition to $P'$
+with action $u$, then $(\recu A P)$ has the same
 transition. From HOL's viewpoint, these

### 2019-01-18 ic-journal/ccs.tex
Duplicate the paper sources (no content changes), using Elsevier's LaTeX template (for submission/review)
Minor typesetting fixes after changing the template
Removed all obsoleted highlights (\hl{...}) in previous review.

--- 2018-07-25 express2018/ccs.tex
@@
 Given a deadlock $\nil$, the class of CCS processes is then inductively defined from $\nil$ by the operators
-of prefixing, parallel composition, summation (binary choice), restriction, recursion and \hl{relabeling}:
+of prefixing, parallel composition, summation (binary choice), restriction, recursion and relabeling:
 \begin{equation*}
@@
   (\res a\!)\, P  \;  \midd \;  A \; \midd \; \recu A  P
-\; \midd \; P\; [r\!\!f]  % relabelling
+\; \midd \; P\; [r\!f]  % relabelling
 \end{array}
@@
 %  visible actions (i.e.~inputs or outputs, excluding  $\tau$).
-\begin{figure*}
+\begin{figure*}[t]
 \begin{center}
@@
 $\displaystyle{ P \arr{\mu} P' \over
- P \;[r\!\!f] \arr{r\!\!f(\mu)} P' \;[r\!\!f]} $ $\forall a.\, r\!\!f(\outC a) = \overline{r\!\!f(a)}$
+ P \;[r\!f] \arr{r\!f(\mu)} P' \;[r\!f]} $ $\forall a.\, r\!f(\outC a) = \overline{r\!f(a)}$
 $ \hb$ %  &
 \end{center}
-\caption{\hl{Structural Operational Semantics} of CCS}
+\caption{Structural Operational Semantics of CCS}
 \label{f:LTSCCS}
@@
 Moreover,   
-$ 
-P \arcap \mu P'$ holds if $P \arr\mu P'$ or ($\mu =\tau$ and
+$ P \arcap \mu P'$ holds if $P \arr\mu P'$ or ($\mu =\tau$ and
 $P=P'$); similarly 
-$ 
-P \Arcap \mu P'$ holds if $P \Arr\mu P'$ or ($\mu =\tau$ and
+$ P \Arcap \mu P'$ holds if $P \Arr\mu P'$ or ($\mu =\tau$ and
 $P=P'$).
@@
 $P =  \ct{\til P}, Q =  \ct{\til Q}$ and $\til P \RR \til Q$.
-We use  symbol 
-$\DSdefi$ for abbreviations. For instance, $P \DSdefi G $, where
-$G$ is some expression, means that  $P$ stands
-for the  expression
-$G$.
+We use the symbol $\DSdefi$ for abbreviations. For instance, $P \DSdefi G $, where
+$G$ is some expression, means that $P$ stands for the expression $G$.
 If $\leq$ is a preorder, then  $\geq$  is its inverse (and

### 2019-01-18 ic-journal/coarsest.tex
Removed all obsoleted highlights (\hl{...}) in previous review.

%%%% -*- Mode: LaTeX -*-
%%
%% This is the draft of the 2nd part of EXPRESS/SOS 2018 paper, co-authored by
%% Prof. Davide Sangiorgi and Chun Tian.

\subsection{Coarsest (pre)congruence contained in $\approx$ ($\succeq_{\mathrm{bis}}$)}
\label{s:coarsest}

% The ``coarsest congruence contained in weak bisimilarity ($\approx$)''
% theorem in CCS is somehow special, as its current known proofs either
% rely on quite restricted conditions, or have an extremely complicated proof
% (c.f. van Glabbeek's paper) in
% which ordinal theory is required.  Actually even the relationship
% between its name and statement is not well explained in many CCS
% textbooks. But van Glabbeek's paper has given the so far clearest
% explanation, here we briefly repeat his arguments:

As bisimilarity ($\approx$) is not congruence, for this reason rooted bisimilarity has been
introduced (Def.~\ref{d:rootedBisimilarity}).
In this subsection we discuss two proofs of an important result stating that
rooted bisimilarity is the coarsest congruence contained in
bisimilarity \cite{van2005characterisation,Gorrieri:2015jt,Mil89} (thus it
is the best one):
\begin{equation}
\label{eq:coarsest}
\forall p\ \ q.\ p\ \rapprox\ \! q\ \Longleftrightarrow\ ( \forall r.\ p\ +\
r\ \approx\ q\ +\ r )\enspace.
\end{equation}

% : Milner's proof \cite{Mil89}, that requires
% that no process can use all available names; and van Glabbeek's proof
% \cite{van2005characterisation}, that does not require additional assumptions.

Actually the coarsest congruence
contained in (weak) bisimilarity, namely the \emph{bisimilarity
  congruence} \cite{van2005characterisation}, can be constructed as
the \emph{composition closure} (\texttt{CC}) of (weak) bisimilarity:
\begin{alltt}
\HOLConst{WEAK_CONGR} \HOLSymConst{=} \HOLConst{CC} \HOLConst{WEAK_EQUIV}\hfill{[WEAK_CONGR]}
\HOLConst{CC} \HOLFreeVar{R} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}. \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}. \HOLConst{CONTEXT} \HOLBoundVar{c} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{c} \HOLBoundVar{g}) (\HOLBoundVar{c} \HOLBoundVar{h}))\hfill{[CC_def]}
\end{alltt}
Indeed, for any relation $R$ 
on CCS processes, the composition closure of $R$ is always finer (i.e.~smaller) than
$R$, no matter if $R$ is (pre)congruence or not\footnote{But if $R$ is
  equivalence (or preorder), the composition closure of $R$ must be congruence
  (or precongruence). Also there is no need to put $R\ g\ h$ in the antecedent of
\texttt{CC\_def}, as this is anyhow obtained from the trivial context $(\lambda x.\,x)$.}: (here $\subseteq_r$ stands for \emph{relational subset})
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}. \HOLConst{CC} \HOLBoundVar{R} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R}\hfill{[CC_is_finer]}
\end{alltt}
Furthermore, we prove that any (pre)congruence contained in $R$ (which
itself may not be) is contained in the composition closure of $R$
(hence the closure is the coarsest one):
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R} \HOLBoundVar{R\sp{\prime}}. \HOLConst{congruence} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLConst{CC} \HOLBoundVar{R}\hfill{[CC_is_coarsest]}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R} \HOLBoundVar{R\sp{\prime}}. \HOLConst{precongruence} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLConst{CC} \HOLBoundVar{R}\hfill{[CC_is_coarsest']}
\end{alltt}

Given the central role of the  
 sum operator, we also consider the closure of bisimilarity under such
 operator, called \emph{equivalence compatible with sums}
(\texttt{SUM_EQUIV}): %%, denoted by $\approx^+$: (not used this symbol)
\begin{alltt}
\HOLConst{SUM_EQUIV} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}. \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r})\hfill{[SUM_EQUIV]}
\end{alltt}

% it doesn't satisfy substitutivity on direct sums (but if the CCS syntax
% is non-standard, i.e.~has only prefixed sums, $\approx$ is indeed a
% congruence). The purpose is to find a coarsest congruence contained in
% weak bisimilarity. (``coarsest'' means, any other congruence finer than it must be contained in it)
% There're two ways to build a congruence from weak bisimilarity, one
% way is the standard definition for observational congruence (rooted
% weak bisimilarity) $\rapprox$ in CCS textbooks, but even it's proven to be a
% congruence we don't know if it's coarsest one.  The other way is to
% build a (pre)congruence closure (Def ??) directly upon
% the original weak bisimilarity relation, we call the resulting
% relation ``Weak bisimilarity congruence'' ($[\approx]$):
% \begin{alltt}
% \HOLConst{WEAK_CONGR} \HOLSymConst{=} \HOLConst{CC} \HOLConst{WEAK_EQUIV}
% \end{alltt}
% It can be shown that any such (pre)congruence closure is automatically coarsest.
%
% Now it remains to prove that, the congruence relation built by above
% two quite different approaches actually coincide. To achieve this goal,
% we first noticed that, all other operators beside sums used in
% semantic context doesn't matter, because they're already substitutable
% for weak bisimilarity. The only important operator is the sum
% operator. To focus on this important operator, we can temporally
% introduce another concept called \emph{sum equivalence}:
% \begin{alltt}
% \HOLConst{SUM_EQUIV} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}. \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r})
% \end{alltt}
Rooted bisimilarity $\rapprox$ (a congruence contained in
$\wb$), is now contained in \texttt{WEAK_CONGR},
which in turn is trivially contained in \texttt{SUM_EQUIV}, as shown
in Fig.~\ref{fig:relationship}. Thus, to prove (\ref{eq:coarsest}),
the crux is to prove that \texttt{SUM_EQUIV} implies
rooted bisimilarity ($\rapprox$), making all three relations
($\rapprox$, \texttt{WEAK_CONGR} and \texttt{SUM_EQUIV}) equivalent:
\begin{equation}
\label{equa:pq}
\forall p\ \ q.\ ( \forall r.\ p\ +\ r \;\approx\; q\ +\ r ) \
\Rightarrow\ p\ \rapprox\ \! q\enspace.
\end{equation}

\begin{figure}[ht]
\begin{displaymath}
\xymatrix@R=3ex{
{\textrm{Weak bisimilarity } (\approx)} & {\textrm{Equiv.
    compatible with sums (\texttt{SUM\_EQUIV})}} \ar@/^3ex/[ldd]^{\subseteq}\\
{\textrm{Bisimilarity congruence (\texttt{WEAK\_CONGR})}}
\ar[u]^{\subseteq} \ar[ru]^{\subseteq} \\
{\textrm{Rooted bisimilarity } (\rapprox)} \ar[u]^{\subseteq}
}
\end{displaymath}
\vspace{-2ex}
\caption{Relationship between the equivalences mentioned}
\label{fig:relationship}
\end{figure}

The standard argument \cite{Mil89} requires that $p$
and $q$ do not use up all available labels (i.e.~visible actions).
Formalising such an argument requires however 
a detailed treatment on free and bound names of CCS
processes (with the restriction operator being a binder), not done yet.
However, the proof of (\ref{equa:pq}) can be carried out 
% But it's
% not easy to formalize and use such an assumption without a detailed
% treatment on free and bound names (visible actions) of CCS
% processes.\footnote{There're totally four such concepts: 1) free names
% are all visible actions appearing in a CCS term without surrounding
% $\nu$ (restriction) operator on the same action; 2) bound names are
% the set of all actions ever used by $\nu$ (restriction) operator; 3)
% free variables (or equation variables) are those variables without a
% definition given by recursion
% operator; 4) bound variables (process constants) are variables with
% definitions given by recursion operator. All CCS results using these
% concepts are not touched so far, although these four concepts are
% successfully defined using HOL's set and list theories.} However, by
just assuming that all immediate \emph{weak} derivatives of
 $p$ and $q$ do not use up all available labels.
% analyzing the proof steps, we found that, what's really required is to
% not use up all available labels in those weak transitions directly
% lead from $p$ and $q$. In another words, even they have used all
% available labels, as long as their first weak transitions didn't, the
% whole proof can still be finished.\footnote{Further more, $p$ and $q$
%   can be considered separately: the proof can be finished as long as
%   \emph{each} of them didn't use up all labels on first weak
%   transition, while the union of these labels are all labels.}
We have formalised this property and
 called it the \emph{free action} property:
\begin{alltt}
\HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{a}. \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}}. \HOLSymConst{\HOLTokenNeg{}}(\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{a}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}})\hfill{[free_action_def]}
\end{alltt}
%
With this property, the actual formalisation of (\ref{equa:pq}) says:
%\begin{theorem}{(Coarsest congruence contained in $\wb$)}
\vspace{-2ex}
\begin{alltt}
\hfill{[COARSEST_CONGR_RL]}
\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}) \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q}
\end{alltt}
%\end{theorem}

With an almost identical proof, rooted contraction
($\rcontr$) is also the coarsest
precongruence contained in bisimilarity contraction ($\mcontrBIS$)
(the other direction of (\ref{eq:coarsest}) is trivial):
%\begin{theorem}{(Coarsest precongruence contained in $\contr$)}
\vspace{-2ex}
\begin{alltt}
\hfill{[COARSEST_PRECONGR_RL]}
\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}) \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{q}
\end{alltt}
%\end{theorem}

The formal proofs of above two results precisely follow Milner
\cite{Mil89}. If only $p$ (or $q$) has free actions while the other uses up all available
labels, the classic assumption $\mathrm{fn}(p) \cup
\mathrm{fn}(q) \neq \mathscr{L}$ (here $\mathrm{fn}$ stands for \emph{free
  names}) does not hold, and the proof cannot be completed. Our
assumption is a bit \emph{weaker}
in the sense that, $p$ and $q$ do not really need to have the
\emph{same} free action (also, $a$ and $\outC a$ are
\emph{different} actions).

There exists a different, more complex proof of (\ref{eq:coarsest}),
given by van Glabbeek \cite{van2005characterisation}, which does not
require any additional assumption.
The core lemma says, for
any two processes $p$ and $q$, if there exists a \emph{stable} (i.e.~$\tau$-free)
 process $k$ which is not bisimilar with any derivative of $p$ and
 $q$, then \texttt{SUM_EQUIV} indeed implies rooted bisimilarity ($\rapprox$):
\begin{alltt}
\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
        \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}} \HOLBoundVar{u}. \HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenConj{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{q\sp{\prime}} \HOLBoundVar{u}. \HOLFreeVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenImp{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}) \HOLSymConst{\HOLTokenImp{}}
   \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q}\hfill{[PROP3_COMMON]}
\end{alltt}
\begin{alltt}
\HOLConst{STABLE} \HOLFreeVar{p} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{p\sp{\prime}}. \HOLFreeVar{p} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{u} \HOLSymConst{\HOLTokenNotEqual{}} \HOLSymConst{\ensuremath{\tau}}\hfill{[STABLE]}
\end{alltt}
To actually get this process $k$, the proof relies on arbitrary infinite sum of 
processes and uses transfinite induction to obtain
an arbitrary large sequence of processes (firstly introduced by Jan
Willem Klop \cite{van2005characterisation})
 that are all pairwise non-bisimilar.
We have partially formalised
this proof, because the typed logic
implemented in various HOL systems (including Isabelle/HOL) is not
strong enough to define a type for all possible ordinal values
\cite{norrish2013ordinals}, thus
we have replaced transfinite induction with plain induction. As a
consequence, the final
result is about a restricted class of processes (which we have taken
to be the finite-state processes). This proof uses extensively HOL's
\texttt{pred_set} theory \cite{melham1992hol} and has an interesting mix
of CCS and pure mathematics in it. (c.f. \cite{Tian:2017wrba} for
more details.)

### 2019-01-18 ic-journal/conclusions.tex
Removed all obsoleted highlights (\hl{...}) in previous review.

--- 2018-07-31 express2018/conclusions.tex
@@
 For the future work, it would be worth extending
-to multi-variable equations/contractions. \hl{A key aspect could be using unguarded constants as free variables
+to multi-variable equations/contractions. A key aspect could be using unguarded constants as free variables
 (\texttt{FV}) and defining guardedness directly on expressions of type CCS (instead of
 CCS $\rightarrow$ CCS), then linking to contexts. For instance, an expression is weakly-guarded when each
-of its free variables, replaced by a hole, results in a weakly-guarded context:}
+of its free variables, replaced by a hole, results in a weakly-guarded context:
 \begin{alltt}
@@
 The second half of this
-paper was written in memory of Mike J. Gordon, the creator of HOL theorem prover.
+paper was written in memory of Michael J.~C.~Gordon, the creator of HOL theorem prover.

### 2019-01-18 ic-journal/context.tex
Removed all obsoleted highlights (\hl{...}) in previous review.

--- 2018-07-25 express2018/context.tex
@@
 
-We have chosen to use $\lambda$-expressions (\hl{with the type}
+We have chosen to use $\lambda$-expressions (with the type
 ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'')
@@
 %
-\hl{This choice has a significant advantage over \emph{one-hole
+This choice has a significant advantage over \emph{one-hole
 contexts}, as each hole corresponds to one
@@
 formulating the unique solution of equations theorems in
-single-variable cases.} The precise definition is given inductively:
+single-variable cases. The precise definition is given inductively:
 \begin{alltt}
@@
 
-In the same manner, \hl{we can also define variants of contexts (\texttt{GCONTEXT}) and weakly guarded
-contexts (\texttt{WGS}) in which only guarded sums are allowed (i.e.~arbitrary sums are forbidden):}
+In the same manner, we can also define variants of contexts (\texttt{GCONTEXT}) and weakly guarded
+contexts (\texttt{WGS}) in which only guarded sums are allowed (i.e.~arbitrary sums are forbidden):
 \begin{alltt}
@@
 A (pre)congruence is a relation on CCS processes defined on top of
-\texttt{CONTEXT}. \hl{The only difference between congruence and
+\texttt{CONTEXT}. The only difference between congruence and
 precongruence is that the former must be an equivalence (reflexive,
-symmetric, transitive), while the latter can be just a preorder (reflexive, transitive)}:
+symmetric, transitive), while the latter can be just a preorder (reflexive, transitive):
 \begin{alltt}
@@
 
-\hl{For example, we can prove that, strong bisimilarity ($\sim$) and
+For example, we can prove that, strong bisimilarity ($\sim$) and
 rooted bisimilarity ($\approx^c$) are both congruence by above
-definition: (the transitivity proof of rooted bisimilarity is actually not easy.)}
+definition: (the transitivity proof of rooted bisimilarity is actually not easy.)
 \begin{alltt}
@@
 
-\hl{Although weak bisimilarity ($\approx$) is \emph{not} congruence
+Although weak bisimilarity ($\approx$) is \emph{not} congruence
   with respect to~\texttt{CONTEXT}, it is indeed ``congruence''
@@
   bisimilarity ($\approx$) is indeed preserved by 
-  weakly-guarded sums.}
+  weakly-guarded sums.
 

### 2019-01-18 ic-journal/formal.tex
Removed all obsoleted highlights (\hl{...}) in previous review.

--- 2018-07-26 express2018/formal.tex
@@
 \end{enumerate}
-\hl{Moreover, using} the same language HOL4 users can write complex automatic
+Moreover, using the same language HOL4 users can write complex automatic
 verification tools by calling HOL's theorem proving
-facilities. \hl{(The formal proofs of theorems in CCS theory
+facilities. (The formal proofs of theorems in CCS theory
 are mostly done by an \emph{interactive process} closely following
-their informal proofs, with minimal automatic proof searching.)}
+their informal proofs, with minimal automatic proof searching.)
 
@@
  simplifies the required proofs in HOL, also enhances the readability of
- proof scripts \hl{without loss of generality. (For paper proofs, the
- multi-variable case is just a routine adaptation.)}
+ proof scripts without loss of generality. (For paper proofs, the
+ multi-variable case is just a routine adaptation.)
 %   still aligned with

### 2019-01-18 ic-journal/part2.tex
Removed all obsoleted highlights (\hl{...}) in previous review.

--- 2018-07-25 express2018/part2.tex
@@
 For this, we first 
- define \hl{the concept of label-accumulated reflexive transitive closure
- (\texttt{LRTC})}.
+ define the concept of label-accumulated reflexive transitive closure
+ (\texttt{LRTC}).
 Given a labeled transition relation \texttt{R} on CCS, \texttt{LRTC R} is
@@
 \end{alltt}
-\hl{The trace relation for CCS can be then obtained
+The trace relation for CCS can be then obtained
  by calling \texttt{LRTC} on the (strong, or single-step) labeled transition
- relation \texttt{TRANS} ($\overset{\mu}{\rightarrow}$) defined by SOS rules}:
+ relation \texttt{TRANS} ($\overset{\mu}{\rightarrow}$) defined by SOS rules:
 \begin{alltt}
@@
 
-\hl{If the list of actions is empty, that means that there is no transition and hence,}
+If the list of actions is empty, that means that there is no transition and hence,
 if there is at most one visible action (i.e., a label) in the list of actions,
@@
 
-The definition of ``unique label'' \hl{can be done in many ways, the
+The definition of ``unique label'' can be done in many ways, the
 following definition (a suggestion from Robert Beers)
-avoids any counting or filtering in the list.}
+avoids any counting or filtering in the list.
 It says that a label is unique in a list of actions if and only if there is no
@@
 \end{alltt}
-\vspace{-1em}
+
 It roughly says, for any context $C$ and weakly-guarded context
@@
 that $P$ is not touched during the transitions). Traces are used for
-reasoning about the \hl{number} of intermediate actions in weak
-transitions. For instance, from Def.~\ref{d:BisCon}, \hl{it is easy
+reasoning about the number of intermediate actions in weak
+transitions. For instance, from Def.~\ref{d:BisCon}, it is easy
 to see that, a weak transition either becomes shorter
-or remains the same when moving between $\mcontrBIS$-related processes}.
-\hl{This property is essential} in the proof of
+or remains the same when moving between $\mcontrBIS$-related processes.
+This property is essential in the proof of
 Lemma~\ref{l:uptocon}. We show only one such lemma, for the case of
@@
 
-\hl{With all above lemmas, we can thus finally prove Theorem~\ref{t:contraBisimulationU}:}
+With all above lemmas, we can thus finally prove Theorem~\ref{t:contraBisimulationU}:
 \begin{alltt}
@@
 \end{alltt}
-\vspace{-2ex}
 
@@
 that is, \texttt{WG} in place of \texttt{WGS}):
-\vspace{-2ex}
+
 \begin{alltt}
@@
 % restrictions on equations:
-\vspace{-2ex}
+
 \begin{alltt}

### 2019-01-18 ic-journal/related.tex
Duplicate the paper sources (no content changes), using Elsevier's LaTeX template (for submission/review)
Removed all obsoleted highlights (\hl{...}) in previous review.

--- 2018-07-26 express2018/related.tex
@@
-\section{Related formalisation work}
+\section{Related work on formalisation}
 \label{s:rel}
 
-\hl{Monica Nesi did the first CCS formalisations for both pure and
-value-passing CCS} \cite{Nesi:1992ve,Nesi:2017wo} using early versions of the HOL
+Monica Nesi did the first CCS formalisations for both pure and
+value-passing CCS \cite{Nesi:1992ve,Nesi:2017wo} using early versions of the HOL
 theorem prover.\footnote{Part of this work can now be found at
@@
 %strong, weak and rooted bisimilarity were proved.
-\hl{Her work is
+Her work is
   the working basis of ours. However, the differences are substantial, especially in the way of defining
@@
 libraries in recent versions of HOL4, and our formalisation has
-covered a much larger spectrum of the (pure) CCS theory.}
+covered a much larger spectrum of the (pure) CCS theory.
 

### 2019-01-18 ic-journal/sos.tex
Removed all obsoleted highlights (\hl{...}) in previous review.

@@
 \end{lstlisting}
-The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
+The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label} \HOLTyOp{option}}'' is the
 union of all visible actions, plus invisible action $\tau$ (now based on
 HOL's \texttt{option} theory). The cardinality of
-``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' (and therefore of all
+``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label} \HOLTyOp{option}}'' (and therefore of all
 CCS types built on top of it)
@@
 The type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'', accounting for the CCS
-syntax\footnote{\hl{The order of type variables $\alpha$ and $\beta$
+syntax\footnote{The order of type variables $\alpha$ and $\beta$
     is irrelevant. Our choice is aligned with other CCS literals.
 $\mathrm{CCS}(h,k)$ is the CCS subcalculus which can use at most $h$ constants
-and $k$ actions.} \cite{gorrieri2017ccs} \hl{Thus, to formalize theorems on
+and $k$ actions. \cite{gorrieri2017ccs} Thus, to formalize theorems on
 such a CCS subcalculus, the needed CCS type can be retrieved by instantiating the type
@@
 having the corresponding cardinalities $h$ and $k$. Monica Nesi goes
-too far by adding another type variable $\gamma$ for value-passing CCS \cite{Nesi:2017wo}.}}, is then defined inductively:
+too far by adding another type variable $\gamma$ for value-passing CCS \cite{Nesi:2017wo}.}, is then defined inductively:
 (\texttt{'a} or $\alpha$ is the type variable for recursion variables,
-``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is \hl{the type of all relabeling functions,
-\mbox{\color{blue}{\texttt{`}}} is for backquotes of HOL terms}):
+``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling functions,
+\mbox{\color{blue}{\texttt{`}}} is for backquotes of HOL terms):
 \begin{lstlisting}
@@
 We have added some grammar support,
- using \hl{HOL's powerful pretty printer}, to represent CCS
+ using HOL's powerful pretty printer, to represent CCS
 processes in more readable forms (c.f. the column \textbf{HOL (abbrev.)}
-in Table \ref{tab:ccsoperator}, \hl{which} summarizes 
-the main syntactic notations \hl{of} CCS). For the restriction
+in Table \ref{tab:ccsoperator}, which summarizes 
+the main syntactic notations of CCS). For the restriction
 operator, we have chosen to allow a  set of names as a parameter, rather than a
@@
 parallel & $P \,\mid\, Q$ & \texttt{par P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q}} \\
-restriction & $(\nu\;L)\;P$ & \texttt{restr L P} & \HOLinline{\HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{P}}
-  \\
-recursion & $\recu A P$ & \texttt{rec A P} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P}}
-  \\
-relabeling & $P\;[r\!\!f]$ & \texttt{relab P rf} & \HOLinline{\HOLConst{relab} \HOLFreeVar{P} \HOLFreeVar{rf}}
-  \\
+restriction & $(\nu\;L)\;P$ & \texttt{restr L P} & \HOLinline{\HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{P}}  \\
+recursion & $\recu A P$ & \texttt{rec A P} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P}}  \\
+relabeling & $P\;[r\!f]$ & \texttt{relab P rf} & \HOLinline{\HOLConst{relab} \HOLFreeVar{P} \HOLFreeVar{rf}}  \\
 \hline
@@
 \end{center}
-\vspace{-1em}
+%\vspace{-1em}
    \caption{Syntax of CCS operators, constant and actions}
@@
 SOS rules are \emph{inductive 
-  definitions} on the tenary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL's
+  definitions} on the tenary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Label} \HOLTyOp{option} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL's
 \texttt{Hol_reln} function.
@@
 is called on the  process $(a.0 | \bar{a}.0)$ thus:
-\hl{(\mbox{\color{blue}{\texttt{``}}} is for double-backquotes of HOL
-  terms, \mbox{\color{blue}{\texttt{>}}} is HOL's prompt)}
+(\mbox{\color{blue}{\texttt{``}}} is for double-backquotes of HOL
+  terms, \mbox{\color{blue}{\texttt{>}}} is HOL's prompt)
 \begin{lstlisting}

### 2019-01-18 ic-journal/unique.tex
Duplicate the paper sources (no content changes), using Elsevier's LaTeX template (for submission/review)
Removed all obsoleted highlights (\hl{...}) in previous review.

--- 2018-07-25 express2018/unique.tex
@@
 \end{equation}
-We show that $\R$ is a bisimulation. \hl{Suppose $R\ \R\ S$ vis the context
-$C$}, and $R \arr{\mu} R'$. We have to find $S'$ with $S \Arcap{\mu}
+We show that $\R$ is a bisimulation. Suppose $R\ \R\ S$ vis the context
+$C$, and $R \arr{\mu} R'$. We have to find $S'$ with $S \Arcap{\mu}
 S'$ and $R'\ \R\ S'$. From $R \wb C[{\til P}]$, we derive $C[{\til P}]
@@
 
-\section{Rooted contraction}
+\subsection{Rooted contraction}
 \label{ss:new}
@@
 \item $Q \arr\mu Q'$   implies that there is $P'$ with $P \Arr \mu
- P'$ and $P' \wb Q'$.
+ P'$ and $P' \wb Q'$\enspace.
 \end{enumerate}
@@
 
-\hl{The precise formulation of  this definition was guided by the HOL theorem
+The precise formulation of  this definition was guided by the HOL theorem
   prover and
-the following two principles:} (1) the definition should not be recursive,
+the following two principles: (1) the definition should not be recursive,
 along the lines of rooted bisimilarity
@@
 relation $\mcontrBIS$ (because of its completeness). 
-\hl{A few other candidates were quickly tested and rejected, e.g.,
-  because of  precongruence issue.} The proof of the precongruence
+A few other candidates were quickly tested and rejected, e.g.,
+  because of  precongruence issue. The proof of the precongruence
  result below is along the lines of the analogous result
@@
 with $\rcontr$ and unrestricted context $C$) in (\ref{eq:R}) is bisimulation,
-exploting Lemma~\ref{l:ruptocon}. \hl{Then it remains to show that,} for
+exploting Lemma~\ref{l:ruptocon}. Then it remains to show that, for
 any two process $P$ and $Q$ with action $\mu$, if $P \arr{\mu} P'$ then
@@
 $P'\ \R\ Q'$, and also for the converse direction, exploting Lemma
-4.13 of \cite{Mil89} \hl{(surprisingly)}. \hl{By definition of
+4.13 of \cite{Mil89} (surprisingly). By definition of
 \emph{bisimulation} (not $\wb$!) and $\approx^c$, we actually proved $P
-\approx^c Q$ instead of $P \wb Q$.}
+\approx^c Q$ instead of $P \wb Q$.
 \end{proof}

### 2019-01-21 ic-journal/equa.tex
Removed all obsoleted highlights (\hl{...}) in previous review.
Marked additions

--- 2018-07-23 express2018/equa.tex
@@
 \label{t:Mil89}
-A system of guarded and sequential equations
-% $\{  X_i = E_i\}_{i\in I}$ 
-   has 
-a unique solution
- for $\wb$.
+A system of guarded and sequential equations (without direct sums)
+$\{  X_i = E_i\}_{i\in I}$ has \hl{an} unique solution for $\wb$.
 \end{theorem}
@@
 % of the solutions of the system.  
-To see the  need of the
- sequentiality  condition, 
-  consider
+To see the  need of the sequentiality  condition, consider
  the equation (from \cite{Mil89}) $X = \res a (a. X | \outC a)$
-where $X$ is guarded but not sequential. Any processes that does
-not use  $a$
- is a solution.
+where $X$ is guarded but not sequential. Any process that does not use $a$ is a solution.
+
+% next file: contraction.tex

### 2019-01-21 ic-journal/formal.tex
Marked additions

@@
 \begin{enumerate}
-\item It serves as the underlying implementation language for the core HOL engine;\vspace{-1ex}
-\item it is used to implement tactics (and tacticals) for writing proofs;\vspace{-1ex}
+\item It serves as the underlying implementation language for the core HOL engine;
+\item it is used to implement tactics (and tacticals) for writing proofs;
 \item it is used as the command language of the HOL interactive shell.
@@
 % cause any difference in the proof of main results represented in this paper.
+
+% next file: sos.htex

### 2019-01-21 ic-journal/intro.tex
Removed all obsoleted highlights (\hl{...}) in previous review.
Marked additions

--- 2018-07-25 express2018/intro.tex
@@
 With contractions, most syntactic limitations of the unique-solution theorem can be
-removed.  One constraint that still remains in
+\hl{eliminated}.  One constraint that still remains in
 \cite{sangiorgi2017equations} (in which the issue is bypassed using a more
@@
 
-Another advantage of the formalisation is 
+Another \hl{benefit} of the formalisation is 
 that we can take advantage of results about different 
@@
  unique-solution result for rooted bisimilarity. Section~\ref{s:for}
- \hl{highlights} our formalisation in HOL4. Finally,  Section~\ref{s:rel} and
+ highlights our formalisation in HOL4. Finally,  Section~\ref{s:rel} and
  \ref{s:concl} discuss related work, conclusions,  and  a few
  directions for future work.
+
+ % next file: ccs.tex

### 2019-01-21 ic-journal/sos.tex
Marked additions

@@
 \end{lstlisting}
-The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label} \HOLTyOp{option}}'' is the
+The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
 union of all visible actions, plus invisible action $\tau$ (now based on
 HOL's \texttt{option} theory). The cardinality of
-``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label} \HOLTyOp{option}}'' (and therefore of all
+``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' (and therefore of all
 CCS types built on top of it)
@@
 having the corresponding cardinalities $h$ and $k$. Monica Nesi goes
-too far by adding another type variable $\gamma$ for value-passing CCS \cite{Nesi:2017wo}.}, is then defined inductively:
+too far by adding another type variable $\gamma$ for value-passing CCS
+\cite{Nesi:2017wo}.}, is then defined inductively:
 (\texttt{'a} or $\alpha$ is the type variable for recursion variables,
@@
 SOS rules are \emph{inductive 
-  definitions} on the tenary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Label} \HOLTyOp{option} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL's
+  definitions} on the tenary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL's
 \texttt{Hol_reln} function.
@@
 \end{alltt}
+
+% next file: bisim.htex

### 2019-01-21 ic-journal/unique.tex
Marked additions

@@
 constrained syntax for sums, due to the congruence and precongruence
-problems of bisimilarity and contraction with such operator. 
+problems of bisimilarity and contraction with \hl{direct sums}. 
 We show here that the constraints can be
-removed by moving to the induced congruence and precongruence, the
+\hl{eliminated} by moving to the induced congruence and precongruence, the
 latter called \emph{rooted contraction}:
@@
 \end{proof}
+
+% next file: formal.tex

### 2019-01-25 ic-journal/sos.tex
Stage work on IC journal version

@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{In} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}}
-   ((\HOLFreeVar{u} \HOLSymConst{=} \HOLConst{In} \HOLStringLit{a}) \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil}) \HOLSymConst{\HOLTokenDisj{}}
-    (\HOLFreeVar{u} \HOLSymConst{=} \HOLConst{Out} \HOLStringLit{a}) \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{In} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil})) \HOLSymConst{\HOLTokenDisj{}}
-   (\HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}}) \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil})\hfill{[Example.ex_A]}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{E}.
+       \HOLConst{In} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}}
+       ((\HOLBoundVar{u} \HOLSymConst{=} \HOLConst{In} \HOLStringLit{a}) \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{E} \HOLSymConst{=} \HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil}) \HOLSymConst{\HOLTokenDisj{}}
+        (\HOLBoundVar{u} \HOLSymConst{=} \HOLConst{Out} \HOLStringLit{a}) \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{E} \HOLSymConst{=} \HOLConst{In} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil})) \HOLSymConst{\HOLTokenDisj{}}
+       (\HOLBoundVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}}) \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{E} \HOLSymConst{=} \HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil})\hfill{[Example.ex_A]}
 \end{alltt}

### 2019-01-27 ic-journal/expansion.tex
Duplicate the paper sources (no content changes), using Elsevier's LaTeX template (for submission/review)
Marked additions
Synchronized with latest version in HOL example

--- 2018-07-25 express2018/expansion.tex
@@
 \begin{enumerate}
-\item $P \arr\mu P'$ implies that there is $Q'$ such that $Q \Arcap \mu Q'$ and $P' \RR Q'$;\vspace{-4pt}
+\item $P \arr\mu P'$ implies that there is $Q'$ such that $Q \Arcap \mu Q'$ and $P' \RR Q'$;
 \item $Q \arr\mu Q'$,implies that there is $P'$ such that $P \Arcap
-  \mu P'$ and $P' \RR Q'$.
+  \mu P'$ and $P' \RR Q'$\enspace.
 % (the converse of (1) on the actions from $Q$)
@@
  \item  $Q \arr\mu Q'$ implies that there is $P'$ such that $P
-   \Arr\mu P'$ and $P' \wb Q'$. %the converse of (1) on the actions from $Q$.
+   \Arr\mu P'$ and $P' \wb Q'$\enspace.
+%the converse of (1) on the actions from $Q$.
 \end{enumerate}
@@
 $\rapprox$ is a congruence in CCS, and it is the
-coarsest (i.e.~largest) congruence contained in $\approx$.
+coarsest congruence contained in $\approx$.
 \end{theorem}
@@
 % As bisimilarity, expansion is preserved by all operators but sum.
-%An example of up-to technique involving expansion is
+% An example of up-to technique involving expansion is
+
+% next file: equa.tex

### 2019-01-27 ic-journal/intro.tex
Revisited abstract and introduction.

@@
 A prominent proof method for bisimulation, put forward by Robin Milner and widely used in his
-landmark CCS book \cite{Mil89} is the
+landmark CCS book \cite{Mil89}, is the
 \emph{unique solution of equations}, whereby two tuples of processes are
@@
 
-In the versions of Milner's unique solution theorems for proving that all
+In the versions of Milner's unique-solution theorems for proving that all
 solutions are weakly (or rooted) bisimilar (in practice these are the most
@@
 Milner's proof method has severe syntactical limitations, such that
-the equations must be ``guarded and sequential,'' that is, the
+the equations must be ``(strongly) guarded and sequential,'' that is, the
 variables of the equations may only be used underneath a visible
@@
 The main goal of the work described in this paper is a rather
-comprehensive formalisation of the core of the theory of CCS in the HOL
-theorem prover (HOL4),  with a focus on the theory of unique solutions of contractions.
+comprehensive formalisation of the core theory of CCS in the HOL
+theorem prover (HOL4),  with a focus on the theory of unique solutions
+of \hl{equations and} contractions.
 The formalisation, however, is not confined to the theory of unique
-solutions of equations, but embraces a significant portion the theory of CCS \cite{Mil89}
-(mostly because the theory of unique solutions relies on a large number of more fundamental results).
+solutions of equations \hl{(and contractions)}, but embraces a
+significant portion the theory of CCS \cite{Mil89}, mostly because the
+theory of unique solutions relies on a large number of more fundamental results.
 Indeed the formalisation encompasses the basic properties of strong and weak
@@
 \cite{Gorrieri:2015jt}),
- and two long proofs saying the rooted bisimilarity is the coarsest (largest)
+ and two long proofs saying \hl{that} the rooted bisimilarity is the coarsest (largest)
  congruence contained in (weak) bisimilarity: one following Milner's
@@
 Similar theorems are proved for the rooted contraction preorder.
-In this respect, the work is an extensive experiment with the use of the HOL theorem prover and its
-most recent developments, including a package for expressing coinductive definitions.
+In this respect, the work is an extensive experiment with the use of the HOL theorem prover with its
+recent developments, including a package for coinductive definitions.
 
 From the view of CCS theory, this formalisation has offered us the possibility of
-further refining the theory of unique solutions of
-equations, as formally proving a previously known result gives us a
+further refining the theory of unique solutions of \hl{contractions}, as
+formally proving a previously known result gives us the
 chance to see \emph{what's really needed} for establishing that result.
@@
 
-% \finish{ I had to remove the reference \cite{Tian:2017wrba} here
-% since it would further 
-%   weaken this paper. }
-
 Another \hl{benefit} of the formalisation is 
 that we can take advantage of results about different 
-equivalences or preorders that share a similar proof structure. 
+equivalences and preorders that share similar proof structures. 
 Examples are: the results that rooted bisimilarity and rooted contraction are,
@@
 Then the successful termination of the proof gives us a guarantee that the proof is
-complete and trustworthy, removing the risk 
-of overlooking or missing details as in hand-written proofs.
-
-% to describe
-% The purpose of this paper is twofold. 
-% On the one hand, 
-% On the other hand, we provide a  
-%  comprehensive formalisation  of the core of the theory of CCS 
-%  in the HOL
-% theorem prover (HOL4). The formalisation  includes the proofs of
-% Milner's 3 ``unique solution of equations'' theorems and
-% contractions discussed in the present paper, but is not limited to it (partly because such
-% theorems rely on a number of more fundamental results):
-% indeed the formalisation encompasses the basic properties of strong and weak
-% bisimilarity (e.g. the fixed-point and substitutivity properties), 
-% their algebraic theory, various versions of ``bisimulation up to''
-% techniques (e.g., bisimulation up-to expansion),
-% the basic properties  of rooted bisimilarity. 
-% Thus the work is an extensive experiment with the use of the HOL theorem provers and its
-% most recent developments, including a facility  for expressing coinductive definitions.
-
-% % Considering the relationship between bisimilarity and rooted
-% % bisimilarity, the formalisation includes the proof that the latter is the coarsest
-% % congruence included in the former, for which two proofs are formalized: one as in Milner's
-% % book,  requiring the hypothesis that  no processes can use all labels; the other without
-% % such hypothesis, essentially formalising van Glabbek's paper \cite{van2005characterisation}.
-% % Similar theorems are proved for rooted contractions wrt the contraction preorder.
+complete and trustworthy, \hl{eliminating} the risks 
+of overlooking or missing details as in \hl{\emph{paper-and-pencil} proofs}.
 
 \paragraph{Structure of the paper}
+
 Section~\ref{ss:ccs} presents basic background materials on CCS,
 including its syntax, operational semantics, bisimilarity and rooted
-bisimilarity. Section~\ref{s:eq} discussed equations and contractions.
+bisimilarity.
+%
+Section~\ref{s:eq} discussed equations and contractions.
+%
 Section~\ref{ss:new} presents rooted contraction and the related
- unique-solution result for rooted bisimilarity. Section~\ref{s:for}
- highlights our formalisation in HOL4. Finally,  Section~\ref{s:rel} and
- \ref{s:concl} discuss related work, conclusions,  and  a few
- directions for future work.
+unique-solution result for rooted bisimilarity.
+%
+Section~\ref{s:for} highlights our formalisation in HOL4.
+%
+Finally,  Section~\ref{s:rel} and \ref{s:concl} discuss related work,
+conclusions, and a few directions for future work.
 
- % next file: ccs.tex
+%%% next file: ccs.tex

### 2019-01-27 ic-journal/ccs.tex
Marked additions
Revisited first part

@@
 \ldots\}$ forming input and $\overline{\mbox{output}}$ actions, plus a special invisible
-action $\tau \notin \mathscr{L}$, and a set of variables $A,B,
-\ldots$ for defining recursive behaviours.
+action $\tau \notin \mathscr{L}$, and a set of variables $A, B,
+\ldots$ for defining recursive behaviours \hl{of CCS processes}.
 Given a deadlock $\nil$, the class of CCS processes is then inductively defined from $\nil$ by the operators
@@
 \end{equation*}
-%We sometimes omit trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil $ .
-The operational semantics of CCS is given by means of
-a Labeled Transition System (LTS), shown in Fig.~\ref{f:LTSCCS} as SOS
+\hl{We sometimes omit the trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil$.}
+The operational semantics of CCS is then given by means of
+a Labeled Transition System (LTS), shown in Fig.~\ref{f:LTSCCS} as
+some \hl{Structural Operational Semantics (SOS)}
 rules (the symmetric version of the two rules for
@@
   for some $\mu$}\}$.
-% We use $\ell$ to range over
-%  visible actions (i.e.~inputs or outputs, excluding  $\tau$).
+ \hl{We use $\ell$ to range over
+  visible actions (i.e.~inputs or outputs, excluding  $\tau$).}
 \begin{figure*}[t]
@@
 \paragraph{Further notations}
-Letters  $\R$, $\S$ range over relations.
+\hl{Let} letters $\R$, $\S$ range over relations \hl{of CCS processes}.
 We use infix notation for relations, e.g., 
 $P \RR Q$ means that $(P,Q) \in \R$.
-We use a tilde to denote a tuple, with countably many elements; thus
-the tuple may also be infinite.
- All
-notations  are  extended to tuples componentwise;
+We use a tilde \hl{like $\til P$} to denote a tuple \hl{(of processes)}, with
+countably many elements; thus the tuple may also be infinite.
+All notations are extended to tuples componentwise,
 e.g., $\til P \RR \til Q$ means that $P_i \RR Q_i$, for each  
@@
 conversely).
+
+% next file: expansion.tex

### 2019-01-27 ic-journal/contraction.tex
Removed all obsoleted highlights (\hl{...}) in previous review.
Marked additions
Revisited first part

@@
 
-The constraints on the unique-solution Theorem~\ref{t:Mil89} can be 
+The constraints \hl{on equations (which must be both guarded and
+sequential)} in Theorem~\ref{t:Mil89} can be
 weakened if we move from equations to a special kind of inequations called
@@
 $P \mcontrBIS Q  $  holds  if $P \wb Q$ and, in addition, 
-$Q$ has the \emph{possibility} of being at least as efficient as $P$ (as far as
-$\tau$-actions performed). 
+$Q$ \emph{has the possibility of being at least as efficient as $P$} (as far as
+$\tau$-actions \hl{are} performed). 
 Process $Q$, however, may be nondeterministic and may have other ways
-of doing the same work, and these could be  slow (i.e., involving
+of doing the same work, and those could be slow (i.e., involving
 more $\tau$-steps than those performed by $P$).
@@
 \end{enumerate}
-\textbf{Bisimilarity contraction}, written as $P \mcontrBIS Q$ ($P$
+\emph{Bisimilarity contraction}, written as $P \mcontrBIS Q$ ($P$
 \textbf{contracts to} $Q$), if $P\ \R\ Q$ for some contraction $\R$.
@@
 intuitively refines bisimilarity by 
- formalising the idea of `efficiency' between processes.
+ formalising the idea of \emph{efficiency} between processes.
 Clause (1) is the same in the two
@@
 
-\hl{Like} (weak) bisimilarity and expansion, contraction is
+Like (weak) bisimilarity and expansion, contraction is
 preserved by all operators but (direct) sum.
+
+% next file: unique.tex

### 2019-01-27 ic-journal/equa.tex
Revisited first part

@@
 bisimilar with each other.
-We need variables to write equations. We  use
- capital
-letters  $X,Y,Z$
+We need variables to write equations. We use capital letters $X,Y,Z$
 for these variables and call them \emph{\behav\  variables}.
@@
 possibly containing \behav\  variables. Thus such expressions, ranged
-over by $E$, live in the CCS
-grammar extended with \behav\  variables.
+over by $E$, live in the CCS grammar extended with \behav\  variables.
 % , which we  call 
@@
 
-\begin{definition}
+\begin{definition}[\hl{System of equations}]
 Assume that, for each $i$ of 
@@
 replacing each variable $X_i$   with the process $P_i$, assuming
-$\til P$ and $\til X$ have the same length. (This is syntactic
+$\til P$ and $\til X$ have the same length. (This is a syntactic
 replacement.) 
-% The components of $\til P$ need not be
-%  different from each other, as it must be for the variables $\til X$.
-% If the system has infinitely many equations,
-% the  tuples $\til P$ and $\til X$
-%  are infinite too.
-\begin{definition}
+\hl{The components of $\til P$ need not be
+different from each other, as it must be for the variables $\til X$.
+If the system has infinitely many equations,
+the  tuples $\til P$ and $\til X$
+are infinite too.}
+\begin{definition}[\hl{Unique solution of equations}]
 Suppose  $\{  X_i = E_i\}_{i\in I}$ is a system of equations: 
@@
 
-\item it %the  system
+\item It %the  system
  has \emph{a unique solution for $\wb$}  if whenever 
@@
 
-% Examples of systems with a  unique solution for $\wb$ are: 
-% \begin{enumerate}
-% \item
-% $ X = a. X$
+ \begin{example}
+\hl{Examples of systems with an unique solution for $\wb$ are:}
+\begin{enumerate}[(1)]
+\item $X = a. X$;
+\item $X_1 = a.  X_2,\qquad X_2 = b.  X_1$\enspace.
+\end{enumerate}
+\end{example}
+The unique solution of (1), modulo $\wb$, is the
+constant $K \Defi a. K$:
+for any other solution $P$ we have $P \wb K$.
+The unique solution of (2), modulo $\wb$, are the constants $K_1 , K_2$
+with $K_1 \Defi a . K_2$ and $K_2 \Defi b. K_1$; again, for any other
+pair of solutions $P_1,P_2$ we have $K_1 \wb P_1$ and $K_2 \wb P_2$.
 
-% \item 
-% $ X_1 = a.  X_2$, $ X_2 = b.  X_1$
+\begin{example}
+\hl{Examples of systems that do not have unique solutions are:}
+\begin{enumerate}[(1)]
+\item $X = X$;
+\item $X = \tau . X$;
+\item $X = a | X$\enspace.
+\end{enumerate}
+\end{example}
+All processes are solutions of (1) and (2);
+In contrast, the equation (3) has solutions that may be quite different, for instance,
+ $K$ and $K | b$, for $K \DSdefi \recu K {\, (a. K)}$. (Actually any process capable of
+continuously performing $a$ actions while behaves arbitrarily on
+other actions is a solution for $X = a|  X$.)
 
-% \end{enumerate}
-
-For instance, the solution of the equation 
-$ X = a. X$ 
-is  the process
-$R \DSdefi \recu A {\, (a. A)}$, and for any other solution $P$ we have $P \wb R$.
-In contrast, the equation 
- $X = a|  X$ has solutions that may be quite different, for instance,
- $K$ and $K | b$, for $K \DSdefi \recu K {\, (a. K)}$. (Actually any process capable of
-continuously performing $a$ actions (while behaves arbitrarily on
-other actions) is a solution for $X = a|  X$.)
-
-% The unique solution of the system (1), modulo $\wb$,  is the constant $K \Defi a
-% . K$:  for any other solution $P$ we have $P \wb K$.
-% The unique solution of (2), modulo $\wb$, are the constants $K_1 , K_2$
-% with $K_1 \Defi a . K_2$ and $K_2 \Defi b. K_1$; again, for any other
-% pair of solutions $P_1,P_2$ we have $K_1 \wb P_1$ and $K_2 \wb P_2$.
-% Examples of systems that do not have a unique solution are: 
-% \begin{enumerate}
-% \item $X = X $
-
-% \item $X = \tau . X$
-% \item $X = a | X$
-
-% \end{enumerate} 
-% All processes are solutions of (1) and (2); examples of solutions for
-% (3) are $K$ and $K | b$, for $K \Defi a
-% . K$.
-
-\begin{definition}[guardedness of equations]
+\begin{definition}[Guardedness of equations]
 \label{def:guardness}
@@
 
-% In other words,  
-% if the system is sequential, then 
-%  for
-% every expression $E_i$, any subexpression of $E_i$ in which $X_j $ 
-% appears, apart from $X_j$ itself,  is a sum (of prefixed terms). 
-% For instance, 
-% \begin{itemize}
-% \item $X = \tau. X + \mu . \nil$ is sequential but not 
-%  guarded, because the guarding prefix for the variable
-% is not visible.
+\hl{In other words,
+ if the system is sequential, then  for
+ every expression $E_i$, any subexpression of $E_i$ in which $X_j $ 
+ appears, apart from $X_j$ itself,  is a sum (of prefixed terms).}
+ For instance, 
+ \begin{itemize}
+ \item $X = \tau. X + \mu . \nil$ is sequential but not 
+  guarded, because the guarding prefix for the variable is not visible.
 
-% \item $X =  \ell . X | P$ is  guarded but not sequential.
+ \item $X =  \ell . X | P$ is guarded but not sequential, because of
+   the use of parallel composition.
 
-% \item $X =  \ell . X + \tau. \res a (a .\outC b | a.\nil)$, as well as 
-% $X = \tau . (a. X + \tau . b .X + \tau  )$
-% are both 
-%  guarded and sequential.
-% \end{itemize}
+ \item $X =  \ell . X + \tau. \res a (a .\outC b | a.\nil)$, as well as 
+ $X = \tau . (a. X + \tau . b .X + \tau  )$
+are both guarded and sequential.
+\end{itemize}
 
-\begin{theorem}[unique solution of equations, \cite{Mil89}]
+\begin{theorem}[Unique solution of equations \cite{Mil89}]
 \label{t:Mil89}

### 2019-01-27 ic-journal/expansion.tex
Revisited first part

@@
 A process relation ${\R}$ is a \textbf{bisimulation} if, whenever
- $P\RR Q$, %for all $\mu$ 
-we have:
+ $P\RR Q$, \hl{for all $\mu$} we have:
 \begin{enumerate}
@@
   \mu P'$ and $P' \RR Q'$\enspace.
-% (the converse of (1) on the actions from $Q$)
 \end{enumerate}  
@@
 Two processes $P$ and $Q$ are \textbf{rooted bisimilar}, written as $P
-\rapprox Q$, if we have:
+\rapprox Q$, if \hl{for all $\mu$} we have:
 \begin{enumerate}
@@
    \Arr\mu P'$ and $P' \wb Q'$\enspace.
-%the converse of (1) on the actions from $Q$.
 \end{enumerate}
@@
 
+\hl{TODO: put some words here?}
+
 \begin{theorem}
@@
 $\rapprox$ is a congruence in CCS, and it is the
-coarsest congruence contained in $\approx$.
+coarsest congruence contained in $\approx$ \cite{van2005characterisation}:
+\begin{equation}
+\forall p\;q.\,p \rapprox q \Longleftrightarrow (\forall r.\, p + r \approx q +r)\enspace.
+\end{equation}
 \end{theorem}

### 2019-01-28 ic-journal/contraction.tex
Stage fixes

@@
 
-% \iflong\newDS
-% Note the use of $\wb$, in place of $\R$, in the second clause:
-%  we are only interested to know that $Q$ may  mimic $P$'s
-% more in an efficient manner (first clause); we do not care about
-% efficiency
-% on the
-% challenges proposed by $Q$,   which are handled using ordinary
-% bisimilarity.
-% \fi
+Note the use of $\wb$, in place of $\R$, in the second clause:
+we are only interested to know that $Q$ may  mimic $P$'s
+more in an efficient manner (first clause); we do not care about
+efficiency on the challenges proposed by $Q$, which are handled using ordinary
+bisimilarity.
 
@@
  ${\expa} \subset {\mcontrBIS}$. 
-% The inclusion is strict: for instance
-% $a+ \tau . a \mcontrBIS a$, where $\mcontrBIS$ cannot be replaced by
-%  $\contr$. Also the converse of  $a+ \tau . a \mcontrBIS a$ holds, namely
-% $  a \mcontrBIS a +
-% \tau . a $. However, we have %\mcontrBIS a + \tau^n . a $
-%  $ a \not  \mcontrBIS \tau. a$
+The inclusion is strict: for instance
+$a+ \tau . a \mcontrBIS a$, where $\mcontrBIS$ cannot be replaced by
+$\contr$. Also the converse of  $a+ \tau . a \mcontrBIS a$ holds, namely
+$  a \mcontrBIS a +
+\tau . a $. However, we have %\mcontrBIS a + \tau^n . a $
+$ a \not  \mcontrBIS \tau. a$
 \end{example}
 
-% The substitutivity proofs for for expansion and bisimilarity carry
-% over to contraction,
-
-Like (weak) bisimilarity and expansion, contraction is
+The substitutivity proofs for for expansion and bisimilarity carry
+over to contraction. Like (weak) bisimilarity and expansion, contraction is
 preserved by all operators but (direct) sum.

### 2019-01-28 ic-journal/formal.tex
Stage fixes

@@
 \label{s:for}
+
 We highlight here a formalisation of CCS
@@
 
-Higher Order Logic (or \emph{HOL Logic}) \cite{hollogic}, which traces
+Higher Order Logic (HOL) \cite{hollogic} traces
 its roots back to LCF
-\cite{gordon1979edinburgh,milner1972logic} by Robin Milner and others since 1972, is a variant of
+\cite{gordon1979edinburgh,milner1972logic} by Robin Milner and others
+since 1972, it is a variant of
 Church’s simple theory of types (STT) \cite{church1940formulation},

### 2019-01-28 ic-journal/unique.tex
Stage fixes

@@
 
-The unique solution theorem of Section~\ref{ss:SysContr} requires a
+The unique-solution theorem \ref{t:contraBisimulationU} of Section~\ref{ss:SysContr} requires a
 constrained syntax for sums, due to the congruence and precongruence
@@
 \begin{proof}
-We first follow the same steps as in the proof of Theorem~\ref{t:contraBisimulationU} to show the relation $\R$ (now
+We first follow the same steps as in the proof of
+Theorem~\ref{t:contraBisimulationU} to show the relation $\R$ (now
 with $\rcontr$ and unrestricted context $C$) in (\ref{eq:R}) is bisimulation,

### 2019-01-30 ic-journal/ccs.tex
Stage fixes
Stage work

@@
 action $\tau \notin \mathscr{L}$, and a set of variables $A, B,
-\ldots$ for defining recursive behaviours \hl{of CCS processes}.
+\ldots$ for defining recursive behaviours.
 Given a deadlock $\nil$, the class of CCS processes is then inductively defined from $\nil$ by the operators
@@
 \begin{equation*}
-\begin{array}{ccl}
-\mu  & := &  \tau \hspace{.3pt} \; \midd \; a  \; \midd \;  \outC a  \\
-P  & := &  \nil \; \midd \;  \mu . P \; \midd \;  P_1 |  P_2 \; \midd  \;
+\begin{array}{cccl}
+\mu  & := & \tau\!\!\!\! & \midd \; a  \; \midd \;  \outC a  \\
+P  & := & \nil\!\!\!\! & \midd \;  \mu . P \; \midd \;  P_1 |  P_2 \; \midd  \;
 P_1 + P_2 \; \midd % \; \mu . P\; \midd  \; 
@@
 $P \RR Q$ means that $(P,Q) \in \R$.
-We use a tilde \hl{like $\til P$} to denote a tuple \hl{(of processes)}, with
-countably many elements; thus the tuple may also be infinite.
+We use tilded letters \hl{like $\til P$} to denote tuples \hl{(of processes)} with
+countably many elements; thus the tuple may also be infinite \hl{(??)}.
 All notations are extended to tuples componentwise,

### 2019-01-30 ic-journal/intro.tex
Stage work

@@
 
-In the versions of Milner's unique-solution theorems for proving that all
+\hl{In Milner's versions of unique-solution theorems} for proving that all
 solutions are weakly (or rooted) bisimilar (in practice these are the most
-relevant cases), however,
-Milner's proof method has severe syntactical limitations, such that
-the equations must be ``(strongly) guarded and sequential,'' that is, the
+relevant cases), however, the proof method has severe syntactical limitations:
+the equations must be \emph{(strongly) guarded and sequential}. That is, the
 variables of the equations may only be used underneath a visible
 prefix and proceed, in the syntax tree, only by the sum and prefix operators.
-One way of overcoming such limitations is to replace equations
+One way of overcoming such limitations is to replace the equations
  with special inequations called
@@
 constraints on processes.  The uniqueness of solutions of a system of contractions
-is defined as with systems of equations: any two solutions must be bisimilar.
+is defined as with systems of equations: any two solutions must be \hl{(componentwise)} bisimilar.
 The difference with equations is in the meaning of a solution:
@@
 formally proving a previously known result gives us the
-chance to see \emph{what's really needed} for establishing that result.
+chance to see \emph{what is really needed} for establishing that result.
 In particular, the existing theory \cite{sangiorgi2017equations} has
@@
 %
-Section~\ref{s:eq} discussed equations and contractions.
+Section~\ref{s:eq} discusses equations and contractions.
 %

### 2019-01-30 ic-journal/ccs.tex
Stage work

@@
 \ldots$ for defining recursive behaviours.
-Given a deadlock $\nil$, the class of CCS processes is then inductively defined from $\nil$ by the operators
+Given a deadlock $\nil$, the class of CCS processes is inductively defined from $\nil$ by the operators
 of prefixing, parallel composition, summation (binary choice), restriction, recursion and relabeling:
@@
 a Labeled Transition System (LTS), shown in Fig.~\ref{f:LTSCCS} as
-some \hl{Structural Operational Semantics (SOS)}
+\hl{Structural Operational Semantics (SOS)}
 rules (the symmetric version of the two rules for
 parallel composition and the rule for sum are omitted).
-A CCS expression uses only \emph{weakly-guarded sums} if all occurrences of
+A CCS expression uses only \emph{weakly\hl{ }guarded sums} if all occurrences of
 the sum operator are of the form $\mu_1.P_1 + \mu_2.P_2 + \ldots
@@
 \paragraph{Further notations}
-\hl{Let} letters $\R$, $\S$ range over relations \hl{of CCS processes}.
-We use infix notation for relations, e.g., 
-$P \RR Q$ means that $(P,Q) \in \R$.
-We use tilded letters \hl{like $\til P$} to denote tuples \hl{(of processes)} with
-countably many elements; thus the tuple may also be infinite \hl{(??)}.
+\hl{Let variables} $\R$, $\S$ range over binary relations%
+\footnote{We use infix notation for relations, e.g., 
+$P \RR Q$ means that $(P,Q) \in \R$.} of CCS processes.
+We use tilded letters \hl{like $\til P$} to denote tuples \hl{of processes} with
+countably many elements; (Thus the tuple may also be infinite.)
 All notations are extended to tuples componentwise,

### 2019-01-30 ic-journal/contraction.tex
Stage work

@@
 A process relation ${\R}$ 
- is a \textbf{(bisimulation) contraction} if, whenever
- $P\RR Q$, %for all $\mu$
-
+ is a \textbf{contraction} if, whenever
+ $P\RR Q$, for all $\mu$
 \begin{enumerate}
@@
 \end{definition}
-% We say that $P$  {\emph{bisimilarly  contracts} $Q$, written
-% $Q \mcontrBIS Q$.
-% We write $\mexpaBIS$ for the inverse of $\mcontrBIS$.
 
@@
 Bisimilarity contraction is coarser than 
- the \emph{expansion relation} 
-$\expa$ \cite{arun1992efficiency,sangiorgi2015equations}.
-This is a
-preorder widely used in proof techniques for bisimilarity and that 
+ the \emph{expansion relation} $\expa$.
+This is a preorder widely used in proof techniques for bisimilarity and that 
 intuitively refines bisimilarity by 
@@
 over to contraction. Like (weak) bisimilarity and expansion, contraction is
-preserved by all operators but (direct) sum.
+preserved by all operators but (direct) sums.
 
-% next file: unique.tex
+% next file: equa.tex

### 2019-01-30 ic-journal/equa.tex
Stage work

@@
-\section{Equations and contractions}
+\section{Systems of equations and contractions}
 \label{s:eq}
@@
 possibly containing \behav\  variables. Thus such expressions, ranged
-over by $E$, live in the CCS grammar extended with \behav\  variables.
-% , which we  call 
-%  \emph{extended CCS}.
+over $E$, live in the CCS grammar extended with \behav\ variables
+, which we  call \emph{extended CCS}.
 
@@
 $E_i$ possibly containing  such variables. 
-Then 
-$\{  X_i = E_i\}_{i\in I}$
-is 
+Then $\{X_i = E_i\}_{i\in I}$ is 
 a \emph{system of equations}. (There is one equation for each variable $X_i$.)
@@
 A system of guarded and sequential equations (without direct sums)
-$\{  X_i = E_i\}_{i\in I}$ has \hl{an} unique solution for $\wb$.
+$\{X_i = E_i\}_{i\in I}$ has \hl{an} unique solution for $\wb$.
 \end{theorem}
 
-% The proof exploits an invariance property on immediate transitions for
-% guarded and sequential expressions, and then extracts a bisimulation
-% (up-to bisimilarity) out
-% of the solutions of the system.  
+The proof exploits an invariance property on immediate transitions for
+guarded and sequential expressions, and then extracts a bisimulation
+(up-to bisimilarity) out
+of the solutions of the system.
 To see the  need of the sequentiality condition, consider
@@
 
-% next file: contraction.tex
+% next file: unique.tex

### 2019-01-30 ic-journal/expansion.tex
Stage work

--- 2019-01-27 ic-journal/expansion.tex
@@
 A process relation ${\R}$ is a \textbf{bisimulation} if, whenever
- $P\RR Q$, %for all $\mu$ 
-we have:
+ $P\RR Q$, \hl{for all $\mu\in \mathscr{L}\cup\{\tau\}$} we have:
 \begin{enumerate}
@@
   \mu P'$ and $P' \RR Q'$\enspace.
-% (the converse of (1) on the actions from $Q$)
 \end{enumerate}
@@
 Two processes $P$ and $Q$ are \textbf{rooted bisimilar}, written as $P
-\rapprox Q$, if we have:
+\rapprox Q$, iff \hl{for all $\mu\in \mathscr{L}\cup\{\tau\}$}
 \begin{enumerate}
@@
 $\rapprox$ is a congruence in CCS, and it is the
-coarsest congruence contained in $\approx$.
+coarsest congruence contained in $\approx$ \cite{van2005characterisation}.
 \end{theorem}
 
-% \finish{Remove expansion here? --Chun}
-% The bisimulation proof method can be enhanced by means of \emph{up-to
-%   techniques}. One of the most useful auxiliary relations in up-to
-% techniques  is the \emph{expansion} relation  $\expa$ \cite{SaMi92}. This is an asymmetric version
-% of $\wb$ where $P \expa Q$  means that 
-%  $P \wb Q$,
-% but also that $Q$  achieves  the same as  $P$ 
-% with  no more work, i.e.~with no more $\tau$ actions.
-% Intuitively, if $ P \expa Q$, we can think of $Q$ as being 
-% at least as fast as $P$
-% or, more generally, we can think that $P$  uses at least as many resources as $Q$.
+\subsection{Expansions}
+\label{s:expa}
 
-% \begin{definition}[expansion]
-% \label{d:expa}
-% A process relation ${\R}$ 
-%  is an {\em  expansion} if, whenever
-% we have $P\RR Q$, %for all $\mu$ 
-% \begin{enumerate}
-% \item   $P \arr\mu P'$ implies that there is $Q'$ with $Q \arcap \mu
-%   Q'$
-%  and $P' \RR Q'$;
-% \item 
-%     $Q \arr\mu Q'$   implies that there is $P'$ with $P \Arr \mu
-%  P'$ and $P' 
-% \RR Q'$.
-% \end{enumerate}
-%  $P$  {\em expands} $Q$, written
-% $P  \expa Q$, 
-% if $P \RR Q$,  for some expansion $\R$. 
-% \end{definition}
+\hl{The bisimulation proof method can be enhanced by means of \emph{up-to
+techniques}. One of the most useful auxiliary relations in up-to
+techniques is the \emph{expansion} relation} $\expa$ \cite{arun1992efficiency,sangiorgi2015equations}.
+This is an asymmetric version
+of $\wb$ where $P \expa Q$ means that $P \wb Q$,
+but also that $Q$ achieves the same as $P$
+with no more work, i.e.~with no more $\tau$ actions.
+Intuitively, if $P \expa Q$, we can think of $Q$ as being
+at least as fast as $P$
+or, more generally, we can think that $P$ uses at least as many resources as $Q$.
+\begin{definition}%[expansion]
+\label{d:expa}
+A process relation ${\R}$
+  is an \textbf{expansion} if, whenever
+we have $P\RR Q$, for all $\mu$
+ \begin{enumerate}
+ \item   $P \arr\mu P'$ implies that there is $Q'$ with $Q \arcap \mu
+   Q'$
+  and $P' \RR Q'$;
+ \item
+     $Q \arr\mu Q'$   implies that there is $P'$ with $P \Arr \mu
+  P'$ and $P'
+ \RR Q'$.
+ \end{enumerate}
+  $P$  {\em expands} $Q$, written as
+ $P  \expa Q$,
+ if $P \RR Q$ for some expansion $\R$.
+ \end{definition}
 
-% As bisimilarity, expansion is preserved by all operators but sum.
-% An example of up-to technique involving expansion is
+Same as bisimilarity, the expansion preorder is preserved by all operators but (direct) sums.
 
-% next file: equa.tex
+% next file: contraction.tex

### 2019-01-30 ic-journal/intro.tex
Stage work

@@
 Indeed the formalisation encompasses the basic properties of strong and weak
-bisimilarity (e.g. the fixed-point and substitutivity properties), the
+bisimilarity (e.g.~the fixed-point and substitutivity properties), the
 basic properties of
@@
 \cite{Nesi:1992ve}) include four versions of ``bisimulation up to''
-techniques (e.g., bisimulation up-to bisimilarity) \cite{Mil89,sangiorgi1992problem}, and the
+techniques (e.g.~bisimulation up-to bisimilarity) \cite{Mil89,sangiorgi1992problem}, and the
 expansion and contraction preorder (two
@@
 the result about unique solution of equations for weak bisimilarity that uses the
-contraction preorder as an auxiliary relation, and other unique solution results (e.g., 
+contraction preorder as an auxiliary relation, and other unique solution results (e.g.~%
 the one for rooted in which
@@
 bisimilarity.
-%
 Section~\ref{s:eq} discusses equations and contractions.
-%
 Section~\ref{ss:new} presents rooted contraction and the related
 unique-solution result for rooted bisimilarity.
-%
 Section~\ref{s:for} highlights our formalisation in HOL4.
-%
 Finally,  Section~\ref{s:rel} and \ref{s:concl} discuss related work,

### 2019-01-30 ic-journal/expansion.tex
Stage work

@@
 \end{definition}
-% Besides reducing the rooted bisimiarity of two processes to
-% the bisimilarities of their first-step transition ends, this definition also brings a proof technique for proving the
-% rooted bisimiarity by constructing a bisimulation:
-% \begin{lemma}{(Rooted bisimilarity by constructing a bisimulation)}
-% \label{l:obsCongrByWeakBisim}
-% Given a (weak) bisimulation $\RR$, if two processes $P$ and $Q$
-% satisfies the following properties:
-% \begin{enumerate}
-%  \item  $P \arr\mu P'$ implies that there is $Q'$ such that $Q
-%    \Arr\mu Q'$ and $P' \RR Q'$;
-% \item the converse of (1) on the actions from $Q$.
-% \end{enumerate}
-% then $P$ and $Q$ are rooted bisimilar, i.e.~$P \approx^c Q$.
-% \end{lemma}
+
+Besides reducing the rooted bisimiarity of two processes to
+the bisimilarities of their first-step transition ends, above definition also brings a proof technique for proving the rooted bisimiarity by constructing a bisimulation:
+\begin{lemma}{(Rooted bisimilarity by constructing a bisimulation)}
+\label{l:obsCongrByWeakBisim}
+Given a (weak) bisimulation $\RR$, if two processes $P$ and $Q$
+satisfies the following properties:
+\begin{enumerate}
+\item $P \arr\mu P'$ implies that there is $Q'$ such that $Q
+   \Arr\mu Q'$ and $P' \RR Q'$;
+\item the converse of (1) on the actions from $Q$.
+\end{enumerate}
+then $P$ and $Q$ are rooted bisimilar, i.e.~$P \approx^c Q$.
+\end{lemma}
 

### 2019-01-30 ic-journal/formal.tex
Stage work

@@
-\section{Formalisation}
+\section{The formalisation}
 \label{s:for}
@@
 examples\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL/tree/master/examples/CCS}}. The
-current work consists of about 20,000 lines of proof scripts in Standard ML.
+current work consists of about 20,000 lines of proof scripts.
 
@@
 
-\emph{In this
+\textbf{In this
 formalisation we consider only single-variable equations/contractions.}
@@
  simplifies the required proofs in HOL, also enhances the readability of
- proof scripts without loss of generality. (For paper proofs, the
- multi-variable case is just a routine adaptation.)
-%   still aligned with
-% their informal proofs.
-%  (on 
-% the extension  to multiple equations/contractions
-% see also  Section~\ref{s:concl}).
+ proof scripts without loss of generality. For the informal pencil-and-paper proofs, the
+ multi-variable case is just a routine adaptation, \hl{while the elegant formalisation
+   of multi-variable equations is quite a challenge.} In Section~\ref{s:concl} some ideas
+ are discussed.
 

### 2019-01-30 ic-journal/sos.tex
Stage work

@@
 
-\subsection{CCS and its transitions by SOS rules}
+\subsection{CCS processes and their transitions}
 
@@
 CCS types built on top of it)
- depends on the choice (or \emph{type-instantiation}) of $\beta$.
+ depends on the choice (or \emph{type-instantiation}) of \hl{type variable} $\beta$.
 
@@
 syntax\footnote{The order of type variables $\alpha$ and $\beta$
-    is irrelevant. Our choice is aligned with other CCS literals.
+    is arbitrary. Our choice is aligned with other CCS literals.
 $\mathrm{CCS}(h,k)$ is the CCS subcalculus which can use at most $h$ constants
@@
  using HOL's powerful pretty printer, to represent CCS
-processes in more readable forms (c.f. the column \textbf{HOL (abbrev.)}
-in Table \ref{tab:ccsoperator}, which summarizes 
+processes in more readable forms (c.f. the column ``HOL (abbrev.)''
+of Table \ref{tab:ccsoperator}, which summarizes 
 the main syntactic notations of CCS). For the restriction
@@
 
-The rule \texttt{REC} (Recursion)
+The last rule \texttt{REC} (Recursion)
  says that if we substitute all appearances of variable $A$ in $P$ to
@@
 with action $u$, then $(\recu A P)$ has the same
-transition. From HOL's viewpoint, these
+transition. In its definition, \texttt{CCS_Subst} is a recursive substutiion function
+with the following long definition:
+\begin{alltt}
+\HOLConst{CCS_Subst} \HOLConst{nil} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{=} \HOLConst{nil}
+\HOLConst{CCS_Subst} (\HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{E}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{=} \HOLFreeVar{u}\HOLSymConst{..}\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
+\HOLConst{CCS_Subst} (\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E\sb{\mathrm{2}}}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{=}
+\HOLConst{CCS_Subst} \HOLFreeVar{E\sb{\mathrm{1}}} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_Subst} \HOLFreeVar{E\sb{\mathrm{2}}} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
+\HOLConst{CCS_Subst} (\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sb{\mathrm{2}}}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{=}
+\HOLConst{CCS_Subst} \HOLFreeVar{E\sb{\mathrm{1}}} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{CCS_Subst} \HOLFreeVar{E\sb{\mathrm{2}}} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
+\HOLConst{CCS_Subst} (\HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{E}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{=} \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X})
+\HOLConst{CCS_Subst} (\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{f}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{=} \HOLConst{relab} (\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}) \HOLFreeVar{f}
+\HOLConst{CCS_Subst} (\HOLConst{var} \HOLFreeVar{Y}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{=} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E\sp{\prime}} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}
+\HOLConst{CCS_Subst} (\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{=}
+\HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} (\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X})\hfill{[CCS_Subst_def]}
+\end{alltt}
+
+From HOL's viewpoint, these
 SOS rules are \emph{inductive 
@@
 
-A useful function that we have defined, exploiting the interplay
-between HOL4 and Standard ML (and following an idea by Nesi \cite{Nesi:1992ve})
+A useful \hl{facility} exploiting the interplay
+between HOL4 and Standard ML (that follows an idea by Nesi \cite{Nesi:1992ve})
  is a complex Standard ML function
-  taking a CCS process and returning a theorem indicating all its
-  direct transitions.\footnote{If the input process could yield
-    something infinite branching, due to the use of recursion or
-    relabeling operators, the program will loop forever without
-    outputting a theorem.}
+  taking a CCS process and returning a theorem indicating all
+  direct transitions of the process.\footnote{If the input process could yield
+    something infinite branching (i.e.~divergent), due to the use of recursion or
+    relabeling operators, the program will loop forever without giving the output.
+  \hl{Checking if any given process is divergent, is beyond the scope of current work.}}
 For instance, we know that the process $(a.0 | \bar{a}.0)$ has three

### 2019-01-30 ic-journal/unique.tex
Stage work

--- 2019-01-21 ic-journal/unique.tex
@@
 A \emph{system of contractions} is defined as a system of equations,
-except that the contraction symbol $\mcontr$ is used in the place of
+except that the contraction symbol $\mcontrBIS$ is used in the place of
 the equality symbol $=$. Thus a system of contractions is a set 
-$\{  X_i \mcontr E_i\}_{i\in I}$
+$\{  X_i \mcontrBIS E_i\}_{i\in I}$
 where $I$ is an  indexing set and expressions
@@
 Given a system of contractions 
-$\{  X_i \mcontr E_i\}_{i\in I}$, 
+$\{  X_i \mcontrBIS E_i\}_{i\in I}$, 
  we say that:
@@
  system of contractions} if $\til P \mcontrBIS \til E [\til P]$;
-\item the system has \emph{a unique solution (for $\approx$)}
+\item The system has \emph{a unique solution (for $\approx$)}
 if $\til P \approx \til Q$ whenever $\til P$ and $\til Q$ are both solutions.
@@
 The guardedness of contractions follows Def.~\ref{def:guardness} (for equations).
-% \begin{definition}
-% \label{d:guarded}
-% A system of contractions $\{  X_i \mcontr E_i\}_{i\in I}$
-%  is
-% \emph{weakly guarded}
-% if,  in each    $E_i$, each occurrence of
-% a \behavC\ variable is underneath a prefix.
-
-% The system use \emph{weakly-guarded sums} if 
-% each $E_i$ only makes use of guarded sums.
-% \end{definition}
 
@@
 
-The unique solution theorem of Section~\ref{ss:SysContr} requires a
+The unique-solution Theorem \ref{t:contraBisimulationU} requires a
 constrained syntax for sums, due to the congruence and precongruence
@@
 \label{d:rcontra}
-Two processes $P$ and $Q$ are in \emph{rooted contraction}, written as
- $P\rcontr Q$, if
+Two processes $P$ and $Q$ are in \textbf{rooted contraction}, written as
+ $P\rcontr Q$, if for all $\mu$
 \begin{enumerate}
@@
 
-The precise formulation of  this definition was guided by the HOL theorem
-  prover and
-the following two principles: (1) the definition should not be recursive,
+\hl{The discovery of above definition was guided by the HOL theorem
+  prover keeping in mind}
+the following two principles: (1) its definition should not be recursive,
 along the lines of rooted bisimilarity
 $\rapprox$ in Def.~\ref{d:rootedBisimilarity};
-(2) the definition should  be built on top of existing \emph{contraction}
+(2) its definition should be built on top of the existing \emph{contraction}
 relation $\mcontrBIS$ (because of its completeness). 
-A few other candidates were quickly tested and rejected, e.g.,
-  because of  precongruence issue. The proof of the precongruence
- result below is along the lines of the analogous result
+A few other candidates were quickly tested and rejected,
+whenever the precongruence proof attempts failed. \hl{The successful
+proof of the precongruence result of $\rcontr$} is along the lines of the analogous result
 for rooted bisimilarity with respect to bisimilarity.
@@
 4.13 of \cite{Mil89} (surprisingly). By definition of
-\emph{bisimulation} (not $\wb$!) and $\approx^c$, we actually proved $P
+\emph{bisimulation} and $\approx^c$, we actually proved $P
 \approx^c Q$ instead of $P \wb Q$.

### 2019-01-30 ic-journal/context.tex
Marked additions
Stage work

@@
 
-For example, we can prove that, strong bisimilarity ($\sim$) and
-rooted bisimilarity ($\approx^c$) are both congruence by above
-definition: (the transitivity proof of rooted bisimilarity is actually not easy.)
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{congruence} \HOLConst{STRONG_EQUIV}\hfill{[STRONG_EQUIV_congruence]}
-\HOLTokenTurnstile{} \HOLConst{congruence} \HOLConst{OBS_CONGR}\hfill{[OBS_CONGR_congruence]}
-\end{alltt}
-
-Although weak bisimilarity ($\approx$) is \emph{not} congruence
-  with respect to~\texttt{CONTEXT}, it is indeed ``congruence''
-  with respect to~\texttt{GCONTEXT} (or if the CCS syntax were defined with
-  only guarded sum operator \cite{sangiorgi2015equations}) as weak
-  bisimilarity ($\approx$) is indeed preserved by 
-  weakly-guarded sums.
-
-% no space for WEAK_EQUIV_PRESD_BY_GUARDED_SUM
+% next file: coarsest.htex

### 2019-01-31 ic-journal/coarsest.tex
Marked additions
Stage work (coarsest congr, ver.2)

@@
 % (c.f. van Glabbeek's paper) in
-% which ordinal theory is required.  Actually even the relationship
+% which the theory of ordinals is required.  Actually even the relationship
 % between its name and statement is not well explained in many CCS
@@
   (or precongruence). Also there is no need to put $R\ g\ h$ in the antecedent of
-\texttt{CC\_def}, as this is anyhow obtained from the trivial context $(\lambda x.\,x)$.}: (here $\subseteq_r$ stands for \emph{relational subset})
+  \texttt{CC\_def}, as this is anyhow obtained from the trivial context $(\lambda x.\,x)$.}:
+(here $\subseteq_r$ stands for \emph{relational subset})
 \begin{alltt}
@@
 precongruence contained in bisimilarity contraction ($\mcontrBIS$)
-(the other direction of (\ref{eq:coarsest}) is trivial):
+(the other direction is trivial):
 %\begin{theorem}{(Coarsest precongruence contained in $\contr$)}
@@
 implemented in various HOL systems (including Isabelle/HOL) is not
-strong enough to define a type for all possible ordinal values
+strong enough to define a type for all possible ordinals
 \cite{norrish2013ordinals}, thus
@@
 result is about a restricted class of processes (which we have taken
-to be the finite-state processes). This proof uses extensively HOL's
-\texttt{pred_set} theory \cite{melham1992hol} and has an interesting mix
-of CCS and pure mathematics in it. (c.f. \cite{Tian:2017wrba} for
-more details.)
+to be the finite-state processes).
+
+\subsection{Arbitrary many non-bisimilar processes}
+
+The assumption in previous \texttt{PROP3_COMMON} requires the
+existence of a special CCS process, which is not weak equivalence to
+any sub-process leading from the two root processes by weak
+transitions. On worst cases, there may be infinite such
+sub-processes\footnote{Even the CCS is finite branching, that's
+  because after a weak transition, the end process may have an
+  infinite $\tau$-chain, and with each $\tau$-transition added into
+  the weak transition, the new end process is still a valid weak
+  transition, thus lead to infinite number of weak transitions.} Thus
+there's no essential differences to consider all states in the
+process group instead.
+
+Then it's natural to ask if there are infinite
+equivalence classes of CCS processes. If so, then it should be 
+possible to choose one which is not equivalent with all the (finite) states in the
+graphs of the two given processes. It turns out that, after Jan Willem
+Klop, it's possible to construct such processes, in which each of them forms a new
+equivalence class, we call them ``Klop processes'' in this paper:
+\begin{definition}[Klop processes]
+For each ordinal $\lambda$, and an arbitrary chosen non-$\tau$ action $a$,
+define a CCS process $k_\lambda$ as follows:
+\begin{itemize}
+\item $k_0 = 0$,
+\item $k_{\lambda+1} = k_\lambda + a.k_\lambda$ and
+\item for $\lambda$ a limit ordinal, $k_\lambda = \sum_{\mu < \lambda}
+  k_\mu$, meaning that $k_\lambda$ is constructed from all graphs
+  $k_\mu$ for $\mu < \lambda$ by identifying their root.
+\end{itemize}
+\end{definition}
+
+If both processes $p$ and $q$ are finite-state CCS processes, that is,
+the number of reachable states from $p$ and $q$ are both finite. And
+in this case, the following limited version of Klop processes can be
+defined as a recursive function (on natural numbers) in HOL4:
+\begin{definition}{(Klop processes as recursive function on natural numbers)}
+\begin{alltt}
+\HOLConst{KLOP} \HOLFreeVar{a} \HOLNumLit{0} \HOLSymConst{=} \HOLConst{nil}
+\HOLConst{KLOP} \HOLFreeVar{a} (\HOLConst{SUC} \HOLFreeVar{n}) \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLSymConst{\ensuremath{+}} \HOLConst{label} \HOLFreeVar{a}\HOLSymConst{..}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\hfill[KLOP_def]
+\end{alltt}
+\end{definition}
+
+By induction on the definition of Klop processes and SOS inference
+rules ($\mathrm{Sum}_1$) and ($\mathrm{Sum}_2$), we can easily prove
+the following properties of Klop functions:
+\begin{proposition}{(Properties of Klop functions and processes)}
+\begin{enumerate}
+\item All Klop processes are stable:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{STABLE} (\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n})\hfill[KLOP_PROP0]
+\end{alltt}
+\item All transitions of a Klop process must lead to another smaller Klop
+  process, and any smaller Klop process must be a possible transition
+  of a larger Klop process:
+\begin{alltt}
+\hfill[KLOP_PROP1]
+\HOLTokenTurnstile{} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{a}\HOLTokenTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{m}.
+\HOLBoundVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLBoundVar{m})
+\end{alltt}
+\item The weak transition version of above property:
+\begin{alltt}
+\hfill[KLOP_PROP1']
+\HOLTokenTurnstile{} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLTokenWeakTransBegin\HOLConst{label} \HOLFreeVar{a}\HOLTokenWeakTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{m}.
+\HOLBoundVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLBoundVar{m})
+\end{alltt}
+\item All Klop processes are distinct according to strong equivalence:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLFreeVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{m} \HOLSymConst{\HOLTokenStrongEQ} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n})\hfill[KLOP_PROP2]
+\end{alltt}
+\item All Klop processes are distinct according to weak equivalence:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLFreeVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{m} \HOLSymConst{\HOLTokenWeakEQ} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n})\hfill[KLOP_PROP2']
+\end{alltt}
+\item Klop functions are one-one:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{ONE_ONE} (\HOLConst{KLOP} \HOLFreeVar{a})\hfill{KLOP_ONE_ONE}
+\end{alltt}
+\end{enumerate}
+\end{proposition}
+
+Once we have a recursive function defined on all natural numbers $0, 1,
+\ldots$, we can map them into a set containing all these Klop processes,
+and the set is countable infinite. On the other side, the number of
+all states coming from
+two finite-state CCS processes $p$ and $q$ is finite. Choosing from an
+infinite set for an element distinct with any subprocess leading from
+$p$ and $q$, is always possible.  This result is purely mathematical,
+completely falling into basic set theory:
+\begin{lemma}
+Given an equivalence relation $R$ defined on a type, and two sets $A, B$
+of elements in this type, $A$ is finite, $B$ is infinite, and all elements
+in $B$ are not equivalent, then there exists an element $k$ in $B$
+which is not equivalent with any element in $A$:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenImp{}}
+   \HOLConst{FINITE} \HOLFreeVar{A} \HOLSymConst{\HOLTokenConj{}} \HOLConst{INFINITE} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y}.
+\HOLBoundVar{x} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{x} \HOLSymConst{\HOLTokenNotEqual{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y}) \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
+\HOLBoundVar{k} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n}.
+\HOLBoundVar{n} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{A} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{n} \HOLBoundVar{k}\hfill[INFINITE_EXISTS_LEMMA]
+\end{alltt}
+\end{lemma}
+\begin{proof}
+  We built an explicit mapping $f$ from $A$ to $B$\footnote{There're
+    multiple ways to prove this lemma, a simpler proof is to make a
+    reverse mapping from $B$ to the power set of $A$ (or further use
+    the Axiom of Choice (AC) to make a mapping from $B$ to $A$), then
+    the non-injectivity of this mapping will contradict the fact that
+    all elements in the infinite set are distinct. Our proof doesn't
+    need AC, and it relies on very simple truths about sets.}, for all
+  $x \in A$, $y = f(x)$ if $y \in B$ and $y$ is equivalent with
+  $x$. But it's possible that no element in $B$ is equivalent with
+  $x$, and in this case we just choose an arbitrary element as
+  $f(x)$. Such a mapping is to make sure the range of $f$ always fall
+  into $B$.
+
+  Now we can map $A$ to a subset of $B$, say $B_0$, and the
+  cardinality of $B_0$ must be equal or smaller than the cardinality
+  of $A$, thus finite. Now we choose an element $k$ from the rest part
+  of $B$, this element is the desire one, because for any element
+  $x \in A$, if it's equivalent with $k$, consider two cases for
+  $y = f(x) \in B_0$:
+  \begin{enumerate}
+  \item $y$ is equivalent with $x$. In this case by transitivity of
+    $R$, we have two distinct elements $y$ and $k$, one in $B_0$, the
+    other in $B\setminus B_0$, they're equivalent. This violates the
+    assumption that all elements in $B$ are distinct.
+  \item $y$ is arbitrary chosen because there's no equivalent element
+    for $x$ in $B$. But we already know one: $k$.
+  \end{enumerate}
+  Thus there's no element $x$ (in $A$) which is equivalent with $k$.
+\end{proof}
+
+To reason about finite-state CCS, we also need to define the concept
+of ``finite-state'':
+\begin{definition}{(Definitions related to finite-state CCS)}
+\begin{enumerate}
+\item Define \emph{reachable} as the RTC of a relation, which
+  indicates the existence of a transition between two processes:
+\begin{alltt}
+\HOLConst{Reach} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
+\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{u}.
+\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}})\HOLSymConst{\HOLTokenSupStar{}}\hfill[Reach_def]
+\end{alltt}
+\item The ``nodes'' of a process is the set of all processes reachable
+  from it:
+\begin{alltt}
+\HOLConst{NODES} \HOLFreeVar{p} \HOLSymConst{=} \HOLTokenLeftbrace{}\HOLBoundVar{q} \HOLTokenBar{} \HOLConst{Reach} \HOLFreeVar{p} \HOLBoundVar{q}\HOLTokenRightbrace{}\hfill[NODES_def]
+\end{alltt}
+\item A process is finite-state if the set of nodes is finite:
+\begin{alltt}
+\HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{FINITE} (\HOLConst{NODES} \HOLFreeVar{p})\hfill[finite_state_def]
+\end{alltt}
+\end{enumerate}
+\end{definition}
+
+Among many properties of above definitions, we mainly rely on the
+following ``obvious'' property on weak transitions:
+\begin{proposition}
+If $p$ weakly transit to $q$, then $q$ must be in the node set of $p$:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{q} \HOLSymConst{\HOLTokenIn{}} \HOLConst{NODES} \HOLFreeVar{p}\hfill[WEAK_TRANS_IN_NODES]
+\end{alltt}
+\end{proposition}
+
+Using all above results, now we can easily prove the following finite
+version of ``Klop lemma'':
+\begin{lemma}{(Klop lemma, the finite version)}
+\label{lem:klop-lemma-finite}
+For any two finite-state CCS $p$ and $q$, there exists another process $k$, which
+is not weak equivalent with any sub-process weakly transited from $p$
+and $q$:
+\begin{alltt}
+KLOP_LEMMA_FINITE:
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}.
+       \HOLConst{finite_state} \HOLBoundVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLBoundVar{q} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
+           \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}} \HOLBoundVar{u}.
+\HOLBoundVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenConj{}}
+           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{q\sp{\prime}} \HOLBoundVar{u}.
+\HOLBoundVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})
+\end{alltt}
+\end{lemma}
+
+Combining above lemma with \texttt{PROP3_COMMON} and \texttt{COARSEST_CONGR_RL},
+we can easily prove the following theorem for finite-state CCS:
+\begin{theorem}{(Coarsest congruence contained in $\approx$ for
+    finite-state CCS)}
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
+   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
+\HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r})\hfill[COARSEST_CONGR_FINITE]
+\end{alltt}
+\end{theorem}
+
+% next file: part2.htex

### 2019-01-31 ic-journal/context.tex
Stage work (coarsest congr, ver.2)

@@
 \end{alltt}
-% (Notice the differences between a weak guarded context and a normal
-% one: $\lambda t. t$ is not weakly guarded as the variable is directly
-% exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
-% guarded as long as $e[\cdot]$ is a context, not necessary weakly guarded.)
+(Notice the differences between a weak guarded context and a normal
+one: $\lambda t. t$ is not weakly guarded as the variable is directly
+exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
+guarded as long as $e[\cdot]$ is a context, not necessary weakly guarded.)
 
@@
 
-% Many lemmas have then to be proved for their
-% relationships among these kinds of contexts and properties about their
-% compositions. These proofs are usually tedious but  long,  due to multiple levels of
-% inductions on the structure of the contexts.
+Many lemmas have then to be proved for their
+ relationships among these kinds of contexts and properties about their
+ compositions. These proofs are usually tedious but long,  due to multiple levels of
+ inductions on the structure of the contexts.
 

### 2019-01-31 ic-journal/part2.tex
Marked additions
Synchronized with latest version in HOL example
Done draft IC journal version

@@
 %% Prof. Davide Sangiorgi and Chun Tian.
+
+\subsection{Unique solution of equations}
+
+\paragraph{For strong bisimularity}
+\hl{Based on results of ``bisimulation up to $\sim$'', we have first proved the following
+non-trivial lemma. It states in effect that if $X$ is weakly guarded
+in $E$, then the ``first move'' of $E$ is independent of the agent
+substituted for $X$:}
+\begin{lemma}[Lemma 3.13 of \cite{Mil89}]
+If the variable $X$ are weakly guarded in $E$, and
+$E\{P/X\}\overset{\alpha}{\rightarrow} P'$, then $P'$ takes the form
+$E'\{P/X\}$ (for some expression $E'$), and moreover, for any $Q$,
+$E\{Q/X\}\overset{\alpha}{\rightarrow} E'\{Q/X\}$:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \HOLBoundVar{P\sp{\prime}}.
+       \HOLFreeVar{E} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sp{\prime}}.
+\HOLConst{CONTEXT} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{P}) \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLFreeVar{E} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{Q}\hfill{[STRONG_UNIQUE_SOLUTION_LEMMA]}
+\end{alltt}
+\end{lemma}
+
+We're now ready to prove the following, the main proposition above the
+``unique solution of equations'':
+\begin{theorem}[Proposition 3.14 of \cite{Mil89}]
+Let the expression $E$ contains at most the variable $X$, and let $X$ be weakly
+guarded in $E$, then
+\begin{equation}
+\text{If } P \sim E\{P/X\} \text{ and } Q \sim E\{Q/X\} \text{ then }
+P \sim Q.
+\end{equation}
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
+\HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}\hfill{[STRONG_UNIQUE_SOLUTION]}
+\end{alltt}
+\end{theorem}
+In above proof, we have identified 14 major sub-goals, dividing into 7
+groups, in which each pairs are symmetric (thus having similar proof
+steps). The proof of this last theorem consists of 500 lines (each
+line usually have 2 or 3 HOL tactics, to make the proof not too long
+in lines).
+
+\paragraph{For weak bisimilarity}
+Actually Milner's book contains only two ``unique solutions of
+equations'' theorems, one for strong equivalence, the other for
+observational congruence (with a wrong proof).   But there's indeed a
+version for weak equivalence which shares a large portion of proof
+steps with the case for ``observation congruence''.  The problem is, since weak
+equivalence is not congruence, to make correct statement of this
+theorem, we must slightly modify the concept of sequential expresses
+with further restrictions: no direct sums (or only guarded sums).
+The ``unique solution of equations'' theorem for weak equivalence
+requires more restrictions on the expression, namely, strong guardness.
+Now we're ready to state and prove the following lemma:
+\begin{lemma}
+If the variable $X$ are (strongly) guarded and sequential in $G$, and
+$G\{P/X\}\overset{\alpha}{\rightarrow} P'$, then $P'$ takes the form
+$H\{P/X\}$ (for some expression $H$), and for any $Q$,
+$G\{Q/X\}\overset{\alpha}{\rightarrow} H\{Q/X\}$. Moreover $H$ is
+sequential, and if $\alpha = \tau$ then $H$ is also guarded.
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{G} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{G} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \HOLBoundVar{P\sp{\prime}}.
+       \HOLFreeVar{G} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}.
+           \HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} ((\HOLBoundVar{a} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}) \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{H} \HOLBoundVar{P}) \HOLSymConst{\HOLTokenConj{}}
+           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}\hfill{[WEAK_UNIQUE_SOLUTION_LEMMA]}
+\end{alltt}
+\end{lemma}
+
+Once above lemma is proved, it's just one small step toward the target theorem:
+\begin{theorem}{(Unique solution of equations for weak equivalence)}
+Let $E$ be guarded and sequential expressions, and let $P \wb
+E\{P/X\}$,
+$Q \wb E\{Q/X\}$. Then $P \wb Q$.
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
+\HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}\hfill{[WEAK_UNIQUE_SOLUTION]}
+\end{alltt}
+\end{theorem}
+
+\paragraph{For rooted bisimilarity}
+For ``unique solutions of
+equations'' theorem of rooted bisimilarity, we have used a whole new technique, i.e. the
+following lemma:
+\begin{lemma}
+To prove two processes $E$ and $E'$ are observational congruence, it's
+enough to construct a bisimulation with additional observational
+transition properties:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{WEAK_BISIM} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
+       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u}.
+            (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
+\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
+\HOLBoundVar{E\sp{\prime}} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
+            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
+\HOLBoundVar{E\sp{\prime}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
+\HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{E\sp{\prime}}\hfill{[OBS_CONGR_BY_WEAK_BISIM]}
+\end{alltt}
+\end{lemma}
+
+This lemma can be easily proved by definition of observational
+congruence and weak equivalence, however it's never mentioned in
+Milner's book. Actually we think it's impossible to prove the
+corresponding ``unique solutions'' theorem without this result.
+What we have proved is the following one. Notice that, we didn't use
+any ``bisimulation up-to'' techniques, because they're not applicable
+once above theorem \texttt{OBS_CONGR_BY_WEAK_BISIM} is used. Instead
+we have directly constructed a bisimulation to finish the proof.
+\begin{lemma}
+If the variable $X$ are (strongly) guarded and sequential in $G$, and
+$G\{P/X\}\overset{\alpha}{\rightarrow} P'$, then $P'$ takes the form
+$H\{P/X\}$ (for some expression $H$), and for any $Q$,
+$G\{Q/X\}\overset{\alpha}{\rightarrow} H\{Q/X\}$. Moreover $H$ is
+sequential, and if $\alpha = \tau$ then $H$ is also guarded.
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{G} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{G} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \HOLBoundVar{P\sp{\prime}}.
+       \HOLFreeVar{G} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}.
+           \HOLConst{SEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} ((\HOLBoundVar{a} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}) \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{H} \HOLBoundVar{P}) \HOLSymConst{\HOLTokenConj{}}
+           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}\hfill{[OBS_UNIQUE_SOLUTION_LEMMA]}
+\end{alltt}
+\end{lemma}
+
+\begin{theorem}{(Unique solution of equations for observational congruence)}
+Let $E$ be guarded and sequential expressions, and let $P \rapprox
+E\{P/X\}$,
+$Q \rapprox E\{Q/X\}$. Then $P \rapprox Q$.
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
+\HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}\hfill{[OBS_UNIQUE_SOLUTION]}
+\end{alltt}
+\end{theorem}
 
@@
 that is, \texttt{WG} in place of \texttt{WGS}):
-
 \begin{alltt}
@@
 equations' theorem for \emph{strong} bisimilarity ($\sim$)~--- 
-the same weakly guarded context (\texttt{WG}) is required:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}\hfill{[STRONG_UNIQUE_SOLUTION]}
-\end{alltt}
-
+the same weakly guarded context (\texttt{WG}) is required.
 In contrast, Milner's ``unique solution of
@@
 has more severe constraints (must be both strongly guarded and sequential):
-% Or our Theorem~\ref{t:rcontraBisimulationU} can be seen as a more
-% applicable version of Milner's ``unique solution of
-% equations'' theorem for rooted bisimilarity ($\rapprox$), which has more
-% restrictions on equations:
+The Theorem~\ref{t:rcontraBisimulationU} \hl{can also be seen as a more
+applicable version of Milner's ``unique solution of
+equations'' theorem for rooted bisimilarity ($\rapprox$), which has more
+restrictions on equations.}
 
-\begin{alltt}
-\hfill{[OBS_UNIQUE_SOLUTION]}
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
-\end{alltt}
+% next file: related.tex

### 2019-01-31 ic-journal/related.tex
Marked additions
Done draft IC journal version

@@
 and $\psi$-calculi 
-using Isabelle/HOL and its \texttt{nominal} logic, with main focus on the handling of
-name binders \cite{bengtson2010formalising,bengtson2007completeness,parrow2009formalising}.
+using Isabelle/HOL and its nominal logic, with the main focus on the handling of
+name binders \cite{bengtson2007completeness,parrow2009formalising}.
 % Jesper Bengtson's PhD thesis 
@@
 and Chaudhuri et al.\;\cite{chaudhuri2015lightweight} in Abella, the latter
-focuses on `bisimulation up-to' techniques %for strong bisimilarity
+focuses on `bisimulation up-to' techniques (for strong bisimilarity)
 for CCS and $\pi$-calculus.
@@
 calculus in Isabelle/HOL, and Hirschkoff \cite{hirschkoff1997full} for the $\pi$-calculus in Coq.
+
+% next file: conclusions.htex

### 2019-02-03 ic-journal/ccs.tex
text

@@
  \hl{We use $\ell$ to range over
-  visible actions (i.e.~inputs or outputs, excluding  $\tau$).}
+  visible actions (i.e.~inputs or outputs, excluding  $\tau$)}
+ \DS{and $\alpha, \mu$  to range over all actions.}
 \begin{figure*}[t]
@@
 \paragraph{Further notations}
-\hl{Let variables} $\R$, $\S$ range over binary relations%
-\footnote{We use infix notation for relations, e.g., 
-$P \RR Q$ means that $(P,Q) \in \R$.} of CCS processes.
-We use tilded letters \hl{like $\til P$} to denote tuples \hl{of processes} with
-countably many elements; (Thus the tuple may also be infinite.)
+\DS{We let $\R$, $\S$ range over binary relations, sometimes using 
+ infix notation for them; e.g., 
+$P \RR Q$ means that $(P,Q) \in \R$.}
+We use \DS{a tilde, as in  $\til P$, to denote tuples of processes with
+countably many elements (thus the tuple may also be infinite.}
 All notations are extended to tuples componentwise,

### 2019-02-03 ic-journal/coarsest.tex
text

@@
 
-As bisimilarity ($\approx$) is not congruence, for this reason rooted bisimilarity has been
+\DS{
+%As bisimilarity ($\approx$) is not congruence, for this reason rooted bisimilarity has been
 introduced (Def.~\ref{d:rootedBisimilarity}).
@@
 rooted bisimilarity is the coarsest congruence contained in
-bisimilarity \cite{van2005characterisation,Gorrieri:2015jt,Mil89} (thus it
-is the best one):
+bisimilarity \cite{van2005characterisation,Gorrieri:2015jt,Mil89}:
+}
 \begin{equation}
@@
 
-The formal proofs of above two results precisely follow Milner
-\cite{Mil89}. If only $p$ (or $q$) has free actions while the other uses up all available
-labels, the classic assumption $\mathrm{fn}(p) \cup
+\DS{
+The formal proofs  of the above two results  follow Milner's proof
+\cite{Mil89}. If only $p$ (or $q$) has free actions while the other uses all available
+labels, the assumption $\mathrm{fn}(p) \cup
 \mathrm{fn}(q) \neq \mathscr{L}$ (here $\mathrm{fn}$ stands for \emph{free
   names}) does not hold, and the proof cannot be completed. Our
-assumption is a bit \emph{weaker}
-in the sense that, $p$ and $q$ do not really need to have the
-\emph{same} free action (also, $a$ and $\outC a$ are
-\emph{different} actions).
+assumption is \emph{weaker}
+in the sense that $p$ and $q$ need not have the
+\emph{same} free actions (note that $a$ and its complementary  $\outC a$ are
+considered \emph{different} as actions).}
 
@@
 \end{alltt}
-To actually get this process $k$, the proof relies on arbitrary infinite sum of 
+\DS{To construct this process $k$,}
+ the proof relies on arbitrary infinite sum of 
 processes and uses transfinite induction to obtain
@@
 \subsection{Arbitrary many non-bisimilar processes}
-
-The assumption in previous \texttt{PROP3_COMMON} requires the
-existence of a special CCS process, which is not weak equivalence to
-any sub-process leading from the two root processes by weak
-transitions. On worst cases, there may be infinite such
-sub-processes\footnote{Even the CCS is finite branching, that's
-  because after a weak transition, the end process may have an
-  infinite $\tau$-chain, and with each $\tau$-transition added into
-  the weak transition, the new end process is still a valid weak
-  transition, thus lead to infinite number of weak transitions.} Thus
-there's no essential differences to consider all states in the
-process group instead.
-
-Then it's natural to ask if there are infinite
-equivalence classes of CCS processes. If so, then it should be 
-possible to choose one which is not equivalent with all the (finite) states in the
-graphs of the two given processes. It turns out that, after Jan Willem
-Klop, it's possible to construct such processes, in which each of them forms a new
-equivalence class, we call them ``Klop processes'' in this paper:
+\DS{
+The assumption in the  previous \texttt{PROP3_COMMON} requires the
+existence of a special CCS process, which is not weak bisimilar to
+any sub-process emanating from the two root processes by weak
+transitions. In the worst case, there may be infinite such
+sub-processes (even on finitely branching processes).
+We can however consider  the equivalence classes of CCS processes 
+modulo weak bisimilarity.
+If there are infinitely many of them, 
+then it should be 
+possible to choose one  that is distinct from all the (finitely many) states in the
+graphs of the two given processes.  
+This can be done following a contruction originally given by 
+ Jan Willem
+Klop \cite{CITATION???}.
+ We call  ``Klop processes''  the processes in this construction:}
 \begin{definition}[Klop processes]
@@
 \end{definition}
-
-If both processes $p$ and $q$ are finite-state CCS processes, that is,
-the number of reachable states from $p$ and $q$ are both finite. And
-in this case, the following limited version of Klop processes can be
-defined as a recursive function (on natural numbers) in HOL4:
+\DS{When processes are finite-state, that is,
+the number of  states in which a process may evolve by performing
+transitions is finite, 
+we can use  the following subset of Klop processes, 
+defined as a recursive function (on natural numbers) in HOL4:}
 \begin{definition}{(Klop processes as recursive function on natural numbers)}
@@
 By induction on the definition of Klop processes and SOS inference
-rules ($\mathrm{Sum}_1$) and ($\mathrm{Sum}_2$), we can easily prove
+rules ($\mathrm{Sum}_1$) and ($\mathrm{Sum}_2$), we can  prove
 the following properties of Klop functions:
@@
 \end{alltt}
-\item All transitions of a Klop process must lead to another smaller Klop
-  process, and any smaller Klop process must be a possible transition
-  of a larger Klop process:
+\item  \DS{Any transition from a Klop process leads to a smaller Klop
+  process, and conversely:}
 \begin{alltt}
@@
 \end{alltt}
-\item The weak transition version of above property:
+\item The weak transition version of the above property:
 \begin{alltt}
@@
 \end{proposition}
-
-Once we have a recursive function defined on all natural numbers $0, 1,
-\ldots$, we can map them into a set containing all these Klop processes,
-and the set is countable infinite. On the other side, the number of
-all states coming from
-two finite-state CCS processes $p$ and $q$ is finite. Choosing from an
-infinite set for an element distinct with any subprocess leading from
-$p$ and $q$, is always possible.  This result is purely mathematical,
-completely falling into basic set theory:
+\DS{Having
+ a recursive function  on all natural numbers,
+  we can map these into a set containing  all Klop processes. 
+We can therefore 
+choose a number that is mapped onto a Klop process
+that is distinct (i.e., not bisimilar)  from 
+any  of the derivatives of two  given 
+two finite-state CCS processes $p$ and $q$
+(by definition, the number of such derivatives is finite).
+This is done by 
+appealing to a   basic   set-theory result.
+}
+% (processes 
+% all states coming from
+% two finite-state CCS processes $p$ and $q$ is finite. Choosing from an
+% infinite set for an element distinct with any subprocess leading from
+% $p$ and $q$, is always possible.  This result is purely mathematical,
+% completely falling into basic set theory:
 \begin{lemma}
@@
 \end{lemma}
-\begin{proof}
-  We built an explicit mapping $f$ from $A$ to $B$\footnote{There're
-    multiple ways to prove this lemma, a simpler proof is to make a
-    reverse mapping from $B$ to the power set of $A$ (or further use
-    the Axiom of Choice (AC) to make a mapping from $B$ to $A$), then
-    the non-injectivity of this mapping will contradict the fact that
-    all elements in the infinite set are distinct. Our proof doesn't
-    need AC, and it relies on very simple truths about sets.}, for all
-  $x \in A$, $y = f(x)$ if $y \in B$ and $y$ is equivalent with
-  $x$. But it's possible that no element in $B$ is equivalent with
-  $x$, and in this case we just choose an arbitrary element as
-  $f(x)$. Such a mapping is to make sure the range of $f$ always fall
-  into $B$.
+% \begin{proof}
+%   We built an explicit mapping $f$ from $A$ to $B$\footnote{There're
+%     multiple ways to prove this lemma, a simpler proof is to make a
+%     reverse mapping from $B$ to the power set of $A$ (or further use
+%     the Axiom of Choice (AC) to make a mapping from $B$ to $A$), then
+%     the non-injectivity of this mapping will contradict the fact that
+%     all elements in the infinite set are distinct. Our proof doesn't
+%     need AC, and it relies on very simple truths about sets.}, for all
+%   $x \in A$, $y = f(x)$ if $y \in B$ and $y$ is equivalent with
+%   $x$. But it's possible that no element in $B$ is equivalent with
+%   $x$, and in this case we just choose an arbitrary element as
+%   $f(x)$. Such a mapping is to make sure the range of $f$ always fall
+%   into $B$.
 
-  Now we can map $A$ to a subset of $B$, say $B_0$, and the
-  cardinality of $B_0$ must be equal or smaller than the cardinality
-  of $A$, thus finite. Now we choose an element $k$ from the rest part
-  of $B$, this element is the desire one, because for any element
-  $x \in A$, if it's equivalent with $k$, consider two cases for
-  $y = f(x) \in B_0$:
-  \begin{enumerate}
-  \item $y$ is equivalent with $x$. In this case by transitivity of
-    $R$, we have two distinct elements $y$ and $k$, one in $B_0$, the
-    other in $B\setminus B_0$, they're equivalent. This violates the
-    assumption that all elements in $B$ are distinct.
-  \item $y$ is arbitrary chosen because there's no equivalent element
-    for $x$ in $B$. But we already know one: $k$.
-  \end{enumerate}
-  Thus there's no element $x$ (in $A$) which is equivalent with $k$.
-\end{proof}
+%   Now we can map $A$ to a subset of $B$, say $B_0$, and the
+%   cardinality of $B_0$ must be equal or smaller than the cardinality
+%   of $A$, thus finite. Now we choose an element $k$ from the rest part
+%   of $B$, this element is the desire one, because for any element
+%   $x \in A$, if it's equivalent with $k$, consider two cases for
+%   $y = f(x) \in B_0$:
+%   \begin{enumerate}
+%   \item $y$ is equivalent with $x$. In this case by transitivity of
+%     $R$, we have two distinct elements $y$ and $k$, one in $B_0$, the
+%     other in $B\setminus B_0$, they're equivalent. This violates the
+%     assumption that all elements in $B$ are distinct.
+%   \item $y$ is arbitrary chosen because there's no equivalent element
+%     for $x$ in $B$. But we already know one: $k$.
+%   \end{enumerate}
+%   Thus there's no element $x$ (in $A$) which is equivalent with $k$.
+% \end{proof}
 
@@
 \begin{proposition}
-If $p$ weakly transit to $q$, then $q$ must be in the node set of $p$:
+\DS{If $p$ has a  weak transition onto $q$,} then $q$ must be in the node set of $p$:
 \begin{alltt}
@@
 
-Using all above results, now we can easily prove the following finite
+Using all the above results, now we can easily prove the following finite
 version of ``Klop lemma'':
-\begin{lemma}{(Klop lemma, the finite version)}
+\begin{lemma}{(Klop lemma,  finite version)}
 \label{lem:klop-lemma-finite}
-For any two finite-state CCS $p$ and $q$, there exists another process $k$, which
-is not weak equivalent with any sub-process weakly transited from $p$
-and $q$:
+\DS{For any two finite-state CCS $p$ and $q$, there exists another process $k$, which
+is not weak equivalent to any derivative  of $p$
+and $q$ (i.e., processes reachable from $p$ and $q$ by means of transitions):}
 \begin{alltt}
@@
 
-Combining above lemma with \texttt{PROP3_COMMON} and \texttt{COARSEST_CONGR_RL},
-we can easily prove the following theorem for finite-state CCS:
+Combining the above lemma with \texttt{PROP3_COMMON} and \texttt{COARSEST_CONGR_RL},
+we can  prove the following theorem for finite-state CCS:
 \begin{theorem}{(Coarsest congruence contained in $\approx$ for

### 2019-02-03 ic-journal/contraction.tex
text

--- 2019-01-27 ic-journal/contraction.tex
@@
 
-The constraints \hl{on equations (which must be both guarded and
-sequential)} in Theorem~\ref{t:Mil89} can be
+The constraints on the unique-solution Theorem~\ref{t:Mil89} can be 
 weakened if we move from equations to a special kind of inequations called
@@
 $P \mcontrBIS Q  $  holds  if $P \wb Q$ and, in addition, 
-$Q$ \emph{has the possibility of being at least as efficient as $P$} (as far as
-$\tau$-actions \hl{are} performed). 
+$Q$ has the \emph{possibility} of being at least as efficient as $P$ (as far as
+$\tau$-actions performed). 
 Process $Q$, however, may be nondeterministic and may have other ways
-of doing the same work, and those could be slow (i.e., involving
+of doing the same work, and these could be  slow (i.e., involving
 more $\tau$-steps than those performed by $P$).
@@
 A process relation ${\R}$ 
- is a \textbf{(bisimulation) contraction} if, whenever
+ is a \emph{(bisimulation) contraction} if, whenever
  $P\RR Q$, %for all $\mu$
@@
 \emph{Bisimilarity contraction}, written as $P \mcontrBIS Q$ ($P$
-\textbf{contracts to} $Q$), if $P\ \R\ Q$ for some contraction $\R$.
+\emph{contracts to} $Q$), if $P\ \R\ Q$ for some contraction $\R$.
 \end{definition}
@@
 intuitively refines bisimilarity by 
- formalising the idea of \emph{efficiency} between processes.
+ formalising the idea of `efficiency' between processes.
 Clause (1) is the same in the two
@@
 % \fi
+
+\begin{definition}%[expansion]
+\label{d:expa}
+A process relation ${\R}$
+  is an \emph{expansion} if, whenever
+we have $P\RR Q$, for all $\mu$
+ \begin{enumerate}
+ \item   $P \arr\mu P'$ implies that there is $Q'$ with $Q \arcap \mu
+   Q'$
+  and $P' \RR Q'$;
+ \item
+     $Q \arr\mu Q'$   implies that there is $P'$ with $P \Arr \mu
+  P'$ and $P'
+ \RR Q'$.
+ \end{enumerate}
+  $P$  {\em expands} $Q$, written as
+ $P  \expa Q$,
+ if $P \RR Q$ for some expansion $\R$.
+ \end{definition}
+
+As bisimilarity, so the expansion preorder is preserved by all operators but  sums.
 
@@
 
-Like (weak) bisimilarity and expansion, contraction is
+\hl{Like} (weak) bisimilarity and expansion, contraction is
 preserved by all operators but (direct) sum.
-
-% next file: unique.tex

### 2019-02-03 ic-journal/equa.tex
text

--- 2019-01-21 ic-journal/equa.tex
@@
 \item \emph{(strongly) guarded} if, in each $E_i$, each occurrence of
-  an \behav\  variable is underneath a \textbf{visible} prefix;
+  an \behav\  variable is underneath a \emph{visible} prefix;
 
@@
 A system of guarded and sequential equations (without direct sums)
-$\{  X_i = E_i\}_{i\in I}$ has \hl{an} unique solution for $\wb$.
+$\{  X_i = E_i\}_{i\in I}$ has a unique solution for $\wb$.
 \end{theorem}
@@
  the equation (from \cite{Mil89}) $X = \res a (a. X | \outC a)$
-where $X$ is guarded but not sequential. Any process that does not use $a$ is a solution.
-
-% next file: contraction.tex
+where $X$ is guarded but not sequential. Any \hl{process that} does not use $a$ is a solution.

### 2019-02-03 ic-journal/expansion.tex
text

@@
 \label{d:wb}
-A process relation ${\R}$ is a \textbf{bisimulation} if, whenever
- $P\RR Q$, \hl{for all $\mu\in \mathscr{L}\cup\{\tau\}$} we have:
+A process relation ${\R}$ is a \emph{bisimulation} if, whenever
+ $P\RR Q$, \DS{for all $\mu$} we have:
 \begin{enumerate}
@@
 \end{enumerate}
- $P$ and $Q$ are \textbf{bisimilar},
+ $P$ and $Q$ are \emph{bisimilar},
 written as $P \wb Q$, if $P \RR Q$ for some bisimulation $\R$.
@@
 \label{d:rootedBisimilarity}
-Two processes $P$ and $Q$ are \textbf{rooted bisimilar}, written as $P
-\rapprox Q$, iff \hl{for all $\mu\in \mathscr{L}\cup\{\tau\}$}
+Two processes $P$ and $Q$ are \emph{rooted bisimilar}, written as $P
+\rapprox Q$, if
+\DS{for all $\mu$}:
+%  \hl{for all $\mu\in \mathscr{L}\cup\{\tau\}$}
 \begin{enumerate}
@@
 Besides reducing the rooted bisimiarity of two processes to
-the bisimilarities of their first-step transition ends, above definition also brings a proof technique for proving the rooted bisimiarity by constructing a bisimulation:
-\begin{lemma}{(Rooted bisimilarity by constructing a bisimulation)}
+the bisimilarities of their  \DS{immediate derivatives}, the
+above definition also brings up a proof technique \DS{for proving  rooted
+bisimiarity results  by constructing a bisimulation.}
+\begin{lemma}%{(Rooted bisimilarity by constructing a bisimulation)}
 \label{l:obsCongrByWeakBisim}
@@
 \end{theorem}
-
-\subsection{Expansions}
-\label{s:expa}
-
-\hl{The bisimulation proof method can be enhanced by means of \emph{up-to
-techniques}. One of the most useful auxiliary relations in up-to
-techniques is the \emph{expansion} relation} $\expa$ \cite{arun1992efficiency,sangiorgi2015equations}.
-This is an asymmetric version
-of $\wb$ where $P \expa Q$ means that $P \wb Q$,
-but also that $Q$ achieves the same as $P$
-with no more work, i.e.~with no more $\tau$ actions.
-Intuitively, if $P \expa Q$, we can think of $Q$ as being
-at least as fast as $P$
-or, more generally, we can think that $P$ uses at least as many resources as $Q$.
-\begin{definition}%[expansion]
-\label{d:expa}
-A process relation ${\R}$
-  is an \textbf{expansion} if, whenever
-we have $P\RR Q$, for all $\mu$
- \begin{enumerate}
- \item   $P \arr\mu P'$ implies that there is $Q'$ with $Q \arcap \mu
-   Q'$
-  and $P' \RR Q'$;
- \item
-     $Q \arr\mu Q'$   implies that there is $P'$ with $P \Arr \mu
-  P'$ and $P'
- \RR Q'$.
- \end{enumerate}
-  $P$  {\em expands} $Q$, written as
- $P  \expa Q$,
- if $P \RR Q$ for some expansion $\R$.
- \end{definition}
-
-Same as bisimilarity, the expansion preorder is preserved by all operators but (direct) sums.
-
-% next file: contraction.tex

### 2019-02-03 ic-journal/formal.tex
text

@@
 
-\textbf{In this
+\emph{In this
 formalisation we consider only single-variable equations/contractions.}
 This considerably
- simplifies the required proofs in HOL, also enhances the readability of
- proof scripts without loss of generality. For the informal pencil-and-paper proofs, the
- multi-variable case is just a routine adaptation, \hl{while the elegant formalisation
-   of multi-variable equations is quite a challenge.} In Section~\ref{s:concl} some ideas
- are discussed.
+ simplifies the required proofs in HOL, and  enhances the readability of
+ proof scripts without loss of generality. For the  pencil-and-paper proofs, the
+ multi-variable case is just a routine adaptation, \DS{while the   formalisation
+ is not (this is also discussed  in Section~\ref{s:concl}).}
 

### 2019-02-03 ic-journal/intro.tex
text

@@
 
-\hl{In Milner's versions of unique-solution theorems} for proving that all
-solutions are weakly (or rooted) bisimilar (in practice these are the most
-relevant cases), however, the proof method has severe syntactical limitations:
+\DS{
+In Milner's versions of the unique-solution theorems for weak
+equivalences,
+ the  method has severe syntactical limitations:}
 the equations must be \emph{(strongly) guarded and sequential}. That is, the
@@
 With contractions, most syntactic limitations of the unique-solution theorem can be
-\hl{eliminated}.  One constraint that still remains in
+removed.  One constraint that still remains in
 \cite{sangiorgi2017equations} (in which the issue is bypassed using a more
@@
 The formalisation, however, is not confined to the theory of unique
-solutions of equations \hl{(and contractions)}, but embraces a
+\DS{solutions}, but embraces a
 significant portion the theory of CCS \cite{Mil89}, mostly because the
@@
 \cite{Gorrieri:2015jt}),
- and two long proofs saying \hl{that} the rooted bisimilarity is the coarsest (largest)
+ and two long proofs saying \hl{that}  rooted bisimilarity is the coarsest (largest)
  congruence contained in (weak) bisimilarity: one following Milner's

### 2019-02-03 ic-journal/part2.tex
text

@@
 
-\paragraph{For strong bisimularity}
-\hl{Based on results of ``bisimulation up to $\sim$'', we have first proved the following
-non-trivial lemma. It states in effect that if $X$ is weakly guarded
+\paragraph{Sstrong bisimularity}
+\DS{Based on results about ``bisimulation up to $\sim$'', we have first proved the following
+ lemma. It states  that if $X$ is weakly guarded
 in $E$, then the ``first move'' of $E$ is independent of the agent
@@
 
-We're now ready to prove the following, the main proposition above the
-``unique solution of equations'':
+% We are now ready to prove the following, the main proposition above the
+% ``unique solution of equations'':
 \begin{theorem}[Proposition 3.14 of \cite{Mil89}]
-Let the expression $E$ contains at most the variable $X$, and let $X$ be weakly
-guarded in $E$, then
+\DS{Suppose the expression $E$ contains at most the variable $X$, and let $X$ be weakly
+guarded in $E$.}
 \begin{equation}
@@
 \end{theorem}
-In above proof, we have identified 14 major sub-goals, dividing into 7
-groups, in which each pairs are symmetric (thus having similar proof
+\DS{In above proof, we have identified 14 major sub-goals, dividing them into 7
+groups, in which each pair is symmetric (thus having similar proof
 steps). The proof of this last theorem consists of 500 lines (each
-line usually have 2 or 3 HOL tactics, to make the proof not too long
-in lines).
+line usually has 2 or 3 HOL tactics, to make the proof not too long
+in lines). }
 
-\paragraph{For weak bisimilarity}
-Actually Milner's book contains only two ``unique solutions of
+\paragraph{Weak bisimilarity}
+\DS{Milner's book  \cite{CITATION???}
+contains only two ``unique solutions of
 equations'' theorems, one for strong equivalence, the other for
-observational congruence (with a wrong proof).   But there's indeed a
-version for weak equivalence which shares a large portion of proof
-steps with the case for ``observation congruence''.  The problem is, since weak
-equivalence is not congruence, to make correct statement of this
-theorem, we must slightly modify the concept of sequential expresses
-with further restrictions: no direct sums (or only guarded sums).
-The ``unique solution of equations'' theorem for weak equivalence
-requires more restrictions on the expression, namely, strong guardness.
-Now we're ready to state and prove the following lemma:
+observational congruence.   There is however a
+version  of the result for weak bisimilarity that shares a large portion of proof
+steps with that case for observational congruence.  
+As  weak bisimilarity 
+ is not congruence, we have to be more restrictive on the syntax for
+ the equation, using strong guardedness. }
+% to make correct statement of this
+% theorem, we must slightly modify the concept of sequential expresses
+% with further restrictions: no direct sums (or only guarded sums).
+% The ``unique solution of equations'' theorem for weak equivalence
+% requires more restrictions on the expression, namely, .
+% Now we're ready to state and prove the following lemma:
 \begin{lemma}
-If the variable $X$ are (strongly) guarded and sequential in $G$, and
+If the variable $X$ is strongly guarded and sequential in $G$, and
 $G\{P/X\}\overset{\alpha}{\rightarrow} P'$, then $P'$ takes the form
-$H\{P/X\}$ (for some expression $H$), and for any $Q$,
+$H\{P/X\}$, for some expression $H$, and for any $Q$, we have
 $G\{Q/X\}\overset{\alpha}{\rightarrow} H\{Q/X\}$. Moreover $H$ is
@@
 
-Once above lemma is proved, it's just one small step toward the target theorem:
+\DS{We can then derive the target theorem.}
 \begin{theorem}{(Unique solution of equations for weak equivalence)}
@@
 
-\paragraph{For rooted bisimilarity}
-For ``unique solutions of
-equations'' theorem of rooted bisimilarity, we have used a whole new technique, i.e. the
-following lemma:
+\paragraph{Rooted bisimilarity}
+\DS{For the ``unique solutions of
+equations'' theorem of rooted bisimilarity, we have used a new technique, i.e., the
+following lemma.   It is   assertion 
+ \texttt{OBS_CONGR_BY_WEAK_BISIM} mentioned in
+ Section~\ref{ss:bb}, corresponding to
+ Lemma~\ref{l:obsCongrByWeakBisim}; we only report the text for  \texttt{OBS_CONGR_BY_WEAK_BISIM}.}
+
 \begin{lemma}
-To prove two processes $E$ and $E'$ are observational congruence, it's
-enough to construct a bisimulation with additional observational
-transition properties:
+% To prove two processes $E$ and $E'$  observationally congruent, it is
+% sufficient enough to construct a bisimulation with additional observational
+% transition properties:
 \begin{alltt}
@@
 \end{lemma}
-
-This lemma can be easily proved by definition of observational
-congruence and weak equivalence, however it's never mentioned in
-Milner's book. Actually we think it's impossible to prove the
-corresponding ``unique solutions'' theorem without this result.
-What we have proved is the following one. Notice that, we didn't use
-any ``bisimulation up-to'' techniques, because they're not applicable
-once above theorem \texttt{OBS_CONGR_BY_WEAK_BISIM} is used. Instead
-we have directly constructed a bisimulation to finish the proof.
+\DS{
+This lemma
+plays a key role in 
+the
+corresponding `unique solutions' theorem, in connection with the
+following result. 
+In this part, we have not 
+used 
+ ``bisimulation up-to'' techniques. Using
+ the  above \texttt{OBS_CONGR_BY_WEAK_BISIM},
+ we  directly construct the appropriate bisimulation relations.
+}
 \begin{lemma}
-If the variable $X$ are (strongly) guarded and sequential in $G$, and
+If the variable $X$ is strongly guarded and sequential in $G$, and
 $G\{P/X\}\overset{\alpha}{\rightarrow} P'$, then $P'$ takes the form
-$H\{P/X\}$ (for some expression $H$), and for any $Q$,
+$H\{P/X\}$, for some  $H$, and for any $Q$, we also have 
 $G\{Q/X\}\overset{\alpha}{\rightarrow} H\{Q/X\}$. Moreover $H$ is
@@
 
+\DS{
 Having removed the  constraints on sums, the result is
@@
 equations'' theorem for rooted bisimilarity ($\rapprox$)
-has more severe constraints (must be both strongly guarded and sequential):
-The Theorem~\ref{t:rcontraBisimulationU} \hl{can also be seen as a more
-applicable version of Milner's ``unique solution of
-equations'' theorem for rooted bisimilarity ($\rapprox$), which has more
-restrictions on equations.}
-
+has more rigid constraints, as the variables must be both strongly guarded and sequential.
+%  Theorem~\ref{t:rcontraBisimulationU} \hl{can also be seen as a more
+% applicable version of Milner's ``unique solution of
+% equations'' theorem for rooted bisimilarity ($\rapprox$), which has more
+% restrictions on equations.}
+}
 % next file: related.tex

### 2019-02-03 ic-journal/sos.tex
text

@@
 
-A useful \hl{facility} exploiting the interplay
+A useful facility exploiting the interplay
 between HOL4 and Standard ML (that follows an idea by Nesi \cite{Nesi:1992ve})
@@
   taking a CCS process and returning a theorem indicating all
-  direct transitions of the process.\footnote{If the input process could yield
-    something infinite branching (i.e.~divergent), due to the use of recursion or
-    relabeling operators, the program will loop forever without giving the output.
-  \hl{Checking if any given process is divergent, is beyond the scope of current work.}}
+  direct transitions of the process.\footnote{If the input process were
+ infinite branching, due to the use of recursion or
+    relabeling operators, the program will loop forever.}
 For instance, we know that the process $(a.0 | \bar{a}.0)$ has three

### 2019-02-03 ic-journal/old_expansion.tex
text

\subsection{Expansions}
\label{s:expa}

\hl{The bisimulation proof method can be enhanced by means of \emph{up-to
techniques}. One of the most useful auxiliary relations in up-to
techniques is the \emph{expansion} relation} $\expa$ \cite{arun1992efficiency,sangiorgi2015equations}.
This is an asymmetric version
of $\wb$ where $P \expa Q$ means that $P \wb Q$,
but also that $Q$ achieves the same as $P$
with no more work, i.e.~with no more $\tau$ actions.
Intuitively, if $P \expa Q$, we can think of $Q$ as being
at least as fast as $P$
or, more generally, we can think that $P$ uses at least as many resources as $Q$.
\begin{definition}%[expansion]
\label{d:expa}
A process relation ${\R}$
  is an \textbf{expansion} if, whenever
we have $P\RR Q$, for all $\mu$
 \begin{enumerate}
 \item   $P \arr\mu P'$ implies that there is $Q'$ with $Q \arcap \mu
   Q'$
  and $P' \RR Q'$;
 \item
     $Q \arr\mu Q'$   implies that there is $P'$ with $P \Arr \mu
  P'$ and $P'
 \RR Q'$.
 \end{enumerate}
  $P$  {\em expands} $Q$, written as
 $P  \expa Q$,
 if $P \RR Q$ for some expansion $\R$.
 \end{definition}

Same as bisimilarity, the expansion preorder is preserved by all operators but (direct) sums.

% next file: contraction.tex

### 2019-02-07 ic-journal/ccs.tex
Synchronized htex with tex files; clear all highlights

--- 2019-01-30 ic-journal/ccs.tex
@@
 \end{equation*}
-\hl{We sometimes omit the trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil$.}
+We sometimes omit the trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil$.
 The operational semantics of CCS is then given by means of
 a Labeled Transition System (LTS), shown in Fig.~\ref{f:LTSCCS} as
-\hl{Structural Operational Semantics (SOS)}
+Structural Operational Semantics (SOS)
 rules (the symmetric version of the two rules for
 parallel composition and the rule for sum are omitted).
-A CCS expression uses only \emph{weakly\hl{ }guarded sums} if all occurrences of
+A CCS expression uses only \emph{weakly guarded sums} if all occurrences of
 the sum operator are of the form $\mu_1.P_1 + \mu_2.P_2 + \ldots
@@
   for some $\mu$}\}$.
- \hl{We use $\ell$ to range over
-  visible actions (i.e.~inputs or outputs, excluding  $\tau$).}
+We use $\ell$ to range over
+visible actions (i.e.~inputs or outputs, excluding  $\tau$)
+and $\alpha, \mu$  to range over all actions.
 \begin{figure*}[t]
@@
 \paragraph{Further notations}
-\hl{Let variables} $\R$, $\S$ range over binary relations%
-\footnote{We use infix notation for relations, e.g., 
-$P \RR Q$ means that $(P,Q) \in \R$.} of CCS processes.
-We use tilded letters \hl{like $\til P$} to denote tuples \hl{of processes} with
-countably many elements; (Thus the tuple may also be infinite.)
+We let $\R$, $\S$ range over binary relations, sometimes using 
+ infix notation for them; e.g., 
+$P \RR Q$ means that $(P,Q) \in \R$.
+We use a tilde, as in  $\til P$, to denote tuples of processes with
+countably many elements (thus the tuple may also be infinite.)
 All notations are extended to tuples componentwise,

### 2019-02-07 ic-journal/coarsest.tex
Synchronized htex with tex files; clear all highlights

@@
 
-\DS{
 %As bisimilarity ($\approx$) is not congruence, for this reason rooted bisimilarity has been
@@
 bisimilarity \cite{van2005characterisation,Gorrieri:2015jt,Mil89}:
-}
 \begin{equation}
@@
 %\begin{theorem}{(Coarsest congruence contained in $\wb$)}
-\vspace{-2ex}
 \begin{alltt}
-\hfill{[COARSEST_CONGR_RL]}
 \HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}) \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q}
+\HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}) \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q}\hfill{[COARSEST_CONGR_RL]}
 \end{alltt}
@@
 
-\DS{
 The formal proofs  of the above two results  follow Milner's proof
@@
 \emph{same} free actions (note that $a$ and its complementary  $\outC a$ are
-considered \emph{different} as actions).}
+considered \emph{different} as actions).
 
@@
 \end{alltt}
-\DS{To construct this process $k$,}
+To construct this process $k$,
  the proof relies on arbitrary infinite sum of 
@@
 \subsection{Arbitrary many non-bisimilar processes}
-\DS{
+
 The assumption in the  previous \texttt{PROP3_COMMON} requires the
@@
 This can be done following a contruction originally given by 
- Jan Willem
-Klop \cite{CITATION???}.
- We call  ``Klop processes''  the processes in this construction:}
+ Jan Willem Klop \cite{van2005characterisation}.
+ We call  ``Klop processes''  the processes in this construction:
 \begin{definition}[Klop processes]
@@
 \end{definition}
-\DS{When processes are finite-state, that is,
+When processes are finite-state, that is,
 the number of  states in which a process may evolve by performing
@@
 we can use  the following subset of Klop processes, 
-defined as a recursive function (on natural numbers) in HOL4:}
+defined as a recursive function (on natural numbers) in HOL4:
 \begin{definition}{(Klop processes as recursive function on natural numbers)}
@@
 \HOLConst{KLOP} \HOLFreeVar{a} \HOLNumLit{0} \HOLSymConst{=} \HOLConst{nil}
-\HOLConst{KLOP} \HOLFreeVar{a} (\HOLConst{SUC} \HOLFreeVar{n}) \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLSymConst{\ensuremath{+}} \HOLConst{label} \HOLFreeVar{a}\HOLSymConst{..}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\hfill[KLOP_def]
+\HOLConst{KLOP} \HOLFreeVar{a} (\HOLConst{SUC} \HOLFreeVar{n}) \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLSymConst{\ensuremath{+}} \HOLConst{label} \HOLFreeVar{a}\HOLSymConst{..}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\hfill{[KLOP_def]}
 \end{alltt}
@@
 \end{alltt}
-\item  \DS{Any transition from a Klop process leads to a smaller Klop
-  process, and conversely:}
+\item Any transition from a Klop process leads to a smaller Klop
+  process, and conversely:
 \begin{alltt}
-\hfill[KLOP_PROP1]
 \HOLTokenTurnstile{} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{a}\HOLTokenTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{m}.
-\HOLBoundVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLBoundVar{m})
+\HOLBoundVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLBoundVar{m})\hfill{[KLOP_PROP1]}
 \end{alltt}
@@
 \begin{alltt}
-\hfill[KLOP_PROP1']
 \HOLTokenTurnstile{} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLTokenWeakTransBegin\HOLConst{label} \HOLFreeVar{a}\HOLTokenWeakTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{m}.
-\HOLBoundVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLBoundVar{m})
+\HOLBoundVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLBoundVar{m})\hfill{[KLOP_PROP1']}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{m} \HOLSymConst{\HOLTokenStrongEQ} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n})\hfill[KLOP_PROP2]
+\HOLTokenTurnstile{} \HOLFreeVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{m} \HOLSymConst{\HOLTokenStrongEQ} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n})\hfill{[KLOP_PROP2]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{m} \HOLSymConst{\HOLTokenWeakEQ} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n})\hfill[KLOP_PROP2']
+\HOLTokenTurnstile{} \HOLFreeVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{m} \HOLSymConst{\HOLTokenWeakEQ} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n})\hfill{[KLOP_PROP2']}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{ONE_ONE} (\HOLConst{KLOP} \HOLFreeVar{a})\hfill{KLOP_ONE_ONE}
+\HOLTokenTurnstile{} \HOLConst{ONE_ONE} (\HOLConst{KLOP} \HOLFreeVar{a})\hfill{[KLOP_ONE_ONE]}
 \end{alltt}
@@
 \end{proposition}
-\DS{Having
+Having
  a recursive function  on all natural numbers,
@@
 appealing to a basic set-theory result.
-}
+
 % (processes 
@@
 \begin{proposition}
-\DS{If $p$ has a  weak transition onto $q$,} then $q$ must be in the node set of $p$:
+If $p$ has a weak transition onto $q$, then $q$ must be in the node set of $p$:
 \begin{alltt}
@@
 \label{lem:klop-lemma-finite}
-\DS{For any two finite-state CCS $p$ and $q$, there exists another process $k$, which
+For any two finite-state CCS $p$ and $q$, there exists another process $k$, which
 is not weak equivalent to any derivative  of $p$
-and $q$ (i.e., processes reachable from $p$ and $q$ by means of transitions):}
+and $q$ (i.e., processes reachable from $p$ and $q$ by means of transitions):
 \begin{alltt}
-KLOP_LEMMA_FINITE:
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}.
@@
            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{q\sp{\prime}} \HOLBoundVar{u}.
-\HOLBoundVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})
+\HOLBoundVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})\hfill{[KLOP_LEMMA_FINITE]}
 \end{alltt}

### 2019-02-07 ic-journal/equa.tex
Synchronized htex with tex files; clear all highlights

@@
 In contrast, the equation 
- $X = a|  X$ has solutions that may be quite different, \hl{for instance,
+ $X = a|  X$ has solutions that may be quite different, for instance,
  $K$ and $K | b$, for $K \DSdefi \recu K {\, (a. K)}$. (Actually any process capable of
 continuously performing $a$ actions (while behaves arbitrarily on
-other actions) is a solution for $X = a|  X$.)}
+other actions) is a solution for $X = a|  X$.)
 
@@
  the equation (from \cite{Mil89}) $X = \res a (a. X | \outC a)$
-where $X$ is guarded but not sequential. Any \hl{process that} does not use $a$ is a solution.
+where $X$ is guarded but not sequential. Any process that does not use $a$ is a solution.

### 2019-02-07 ic-journal/expansion.tex
Synchronized htex with tex files; clear all highlights

@@
 A process relation ${\R}$ is a \emph{bisimulation} if, whenever
- $P\RR Q$, \DS{for all $\mu$} we have:
+ $P\RR Q$, for all $\mu$ we have:
 \begin{enumerate}
@@
 \rapprox Q$, if
-\DS{for all $\mu$}:
-%  \hl{for all $\mu\in \mathscr{L}\cup\{\tau\}$}
+for all $\mu$:
+%  for all $\mu\in \mathscr{L}\cup\{\tau\}$
 \begin{enumerate}
@@
 Besides reducing the rooted bisimiarity of two processes to
-the bisimilarities of their  \DS{immediate derivatives}, the
-above definition also brings up a proof technique \DS{for proving  rooted
-bisimiarity results  by constructing a bisimulation.}
+the bisimilarities of their immediate derivatives, the
+above definition also brings up a proof technique for proving  rooted
+bisimiarity results  by constructing a bisimulation.
 \begin{lemma}%{(Rooted bisimilarity by constructing a bisimulation)}

### 2019-02-07 ic-journal/formal.tex
Synchronized htex with tex files; clear all highlights

@@
 plays three different roles:
-%(The situation is quite different in other systems like Coq\footnote{\hl{The Coq Proof Assistant.} \url{https://coq.inria.fr}}.)
+%(The situation is quite different in other systems like
+%Coq\footnote{The Coq Proof Assistant. \url{https://coq.inria.fr}}).
 \begin{enumerate}
@@
  proof scripts without loss of generality. For the  pencil-and-paper proofs, the
- multi-variable case is just a routine adaptation, \DS{while the   formalisation
- is not (this is also discussed  in Section~\ref{s:concl}).}
+ multi-variable case is just a routine adaptation, while the   formalisation
+ is not (this is also discussed in Section~\ref{s:concl}).
 

### 2019-02-07 ic-journal/intro.tex
Synchronized htex with tex files; clear all highlights

@@
 
-\DS{
 In Milner's versions of the unique-solution theorems for weak
 equivalences,
- the  method has severe syntactical limitations:}
+ the  method has severe syntactical limitations:
 the equations must be \emph{(strongly) guarded and sequential}. That is, the
@@
 constraints on processes.  The uniqueness of solutions of a system of contractions
-is defined as with systems of equations: any two solutions must be \hl{(componentwise)} bisimilar.
+is defined as with systems of equations: any two solutions must be (componentwise) bisimilar.
 The difference with equations is in the meaning of a solution:
@@
 theorem prover (HOL4),  with a focus on the theory of unique solutions
-of \hl{equations and} contractions.
+of equations and contractions.
 The formalisation, however, is not confined to the theory of unique
-\DS{solutions}, but embraces a
+solutions, but embraces a
 significant portion the theory of CCS \cite{Mil89}, mostly because the
@@
 \cite{Gorrieri:2015jt}),
- and two long proofs saying \hl{that}  rooted bisimilarity is the coarsest (largest)
+ and two long proofs saying that  rooted bisimilarity is the coarsest (largest)
  congruence contained in (weak) bisimilarity: one following Milner's
@@
 From the view of CCS theory, this formalisation has offered us the possibility of
-further refining the theory of unique solutions of \hl{contractions}, as
+further refining the theory of unique solutions of contractions, as
 formally proving a previously known result gives us the
@@
 
-Another \hl{benefit} of the formalisation is 
+Another benefit of the formalisation is 
 that we can take advantage of results about different 
@@
 Then the successful termination of the proof gives us a guarantee that the proof is
-complete and trustworthy, \hl{eliminating} the risks 
-of overlooking or missing details as in \hl{\emph{paper-and-pencil} proofs}.
+complete and trustworthy, eliminating the risks 
+of overlooking or missing details as in \emph{paper-and-pencil} proofs.
 

### 2019-02-07 ic-journal/part2.tex
Synchronized htex with tex files; clear all highlights

@@
 \paragraph{Sstrong bisimularity}
-\DS{Based on results about ``bisimulation up to $\sim$'', we have first proved the following
+Based on results about ``bisimulation up to $\sim$'', we have first proved the following
  lemma. It states  that if $X$ is weakly guarded
 in $E$, then the ``first move'' of $E$ is independent of the agent
-substituted for $X$:}
+substituted for $X$:
 \begin{lemma}[Lemma 3.13 of \cite{Mil89}]
@@
 \begin{alltt}
+\hfill{[STRONG_UNIQUE_SOLUTION_LEMMA]}
 \HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}}
@@
 \HOLConst{CONTEXT} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{P}) \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
-\HOLFreeVar{E} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{Q}\hfill{[STRONG_UNIQUE_SOLUTION_LEMMA]}
+\HOLFreeVar{E} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{Q}
 \end{alltt}
@@
 \begin{theorem}[Proposition 3.14 of \cite{Mil89}]
-\DS{Suppose the expression $E$ contains at most the variable $X$, and let $X$ be weakly
-guarded in $E$.}
+Suppose the expression $E$ contains at most the variable $X$, and let $X$ be weakly
+guarded in $E$.
 \begin{equation}
@@
 \end{theorem}
-\DS{In above proof, we have identified 14 major sub-goals, dividing them into 7
+In above proof, we have identified 14 major sub-goals, dividing them into 7
 groups, in which each pair is symmetric (thus having similar proof
@@
 line usually has 2 or 3 HOL tactics, to make the proof not too long
-in lines). }
+in lines).
 
 \paragraph{Weak bisimilarity}
-\DS{Milner's book  \cite{CITATION???}
-contains only two ``unique solutions of
+Milner's book \cite{Mil89} contains only two ``unique solutions of
 equations'' theorems, one for strong equivalence, the other for
@@
  is not congruence, we have to be more restrictive on the syntax for
- the equation, using strong guardedness. }
+ the equation, using strong guardedness.
 % to make correct statement of this
@@
 
-\DS{We can then derive the target theorem.}
+We can then derive the target theorem:
 \begin{theorem}{(Unique solution of equations for weak equivalence)}
@@
 \paragraph{Rooted bisimilarity}
-\DS{For the ``unique solutions of
+For the ``unique solutions of
 equations'' theorem of rooted bisimilarity, we have used a new technique, i.e., the
@@
  Section~\ref{ss:bb}, corresponding to
- Lemma~\ref{l:obsCongrByWeakBisim}; we only report the text for  \texttt{OBS_CONGR_BY_WEAK_BISIM}.}
+ Lemma~\ref{l:obsCongrByWeakBisim}; we only report the text for  \texttt{OBS_CONGR_BY_WEAK_BISIM}.
 
@@
 \end{lemma}
-\DS{
-This lemma
-plays a key role in 
-the
+
+This lemma plays a key role in the
 corresponding `unique solutions' theorem, in connection with the
@@
  we  directly construct the appropriate bisimulation relations.
-}
 \begin{lemma}
@@
 
-\DS{
 Having removed the  constraints on sums, the result is
@@
 has more rigid constraints, as the variables must be both strongly guarded and sequential.
-%  Theorem~\ref{t:rcontraBisimulationU} \hl{can also be seen as a more
+%  Theorem~\ref{t:rcontraBisimulationU} can also be seen as a more
 % applicable version of Milner's ``unique solution of
 % equations'' theorem for rooted bisimilarity ($\rapprox$), which has more
-% restrictions on equations.}
-}
+% restrictions on equations.
 % next file: related.tex

### 2019-02-07 ic-journal/sos.tex
Synchronized htex with tex files; clear all highlights

@@
 CCS types built on top of it)
- depends on the choice (or \emph{type-instantiation}) of \hl{type variable} $\beta$.
+ depends on the choice (or \emph{type-instantiation}) of type variable $\beta$.
 

### 2019-02-07 ic-journal/unique.tex
Synchronized htex with tex files; clear all highlights

--- 2019-01-21 ic-journal/unique.tex
@@
 constrained syntax for sums, due to the congruence and precongruence
-problems of bisimilarity and contraction with \hl{direct sums}. 
+problems of bisimilarity and contraction with such operator. 
 We show here that the constraints can be
-\hl{eliminated} by moving to the induced congruence and precongruence, the
+removed by moving to the induced congruence and precongruence, the
 latter called \emph{rooted contraction}:
@@
 $P'\ \R\ Q'$, and also for the converse direction, exploting Lemma
-4.13 of \cite{Mil89} (surprisingly). By definition of
+4.13 of \cite{Mil89} (TODO). By definition of
 \emph{bisimulation} (not $\wb$!) and $\approx^c$, we actually proved $P
@@
 \end{proof}
-
-% next file: formal.tex

### 2019-02-08 ic-journal/part2.tex
Enriched the proof of Theorem 3.14

@@
 \subsection{Unique solution of equations}
+\label{ss:part2}
 
-\paragraph{Sstrong bisimularity}
+\paragraph{Strong bisimularity}
 Based on results about ``bisimulation up to $\sim$'', we have first proved the following
@@
 \begin{lemma}[Lemma 3.13 of \cite{Mil89}]
+\label{lem:313}
 If the variable $X$ are weakly guarded in $E$, and

### 2019-02-08 ic-journal/unique.tex
Enriched the proof of Theorem 3.14

@@
 \end{lemma}
+The proof of Lemma~\ref{l:ruptocon} is exactly the same as of
+Lemma~\ref{l:uptocon}, because all we need from $\mcontrBIS$ and
+$\rcontr$ is their precongruences (in the sense of different
+definitions of contexts). Also notice that, the conclusion of
+Lemma~\ref{l:ruptocon} still uses $\mcontrBIS$, because $\rcontr$ does
+not hold.
 
-\begin{theorem}[unique solution of contractions for $\rapprox$]
+\begin{theorem}[Unique solution of contractions for $\rapprox$]
 \label{t:rcontraBisimulationU}
 A system of weakly-guarded contractions has a unique solution 
- for $\rapprox$. (thus also for $\wb$)
+ for $\rapprox$ (thus also for $\wb$).
 \end{theorem}
@@
 \begin{proof}
-We first follow the same steps as in the proof of Theorem~\ref{t:contraBisimulationU} to show the relation $\R$ (now
-with $\rcontr$ and unrestricted context $C$) in (\ref{eq:R}) is bisimulation,
-exploting Lemma~\ref{l:ruptocon}. Then it remains to show that, for
+\hl{Suppose $\til P$ and $\til Q$ are two such solutions: $\til P \rcontr
+C[{\til P}]$ and $\til Q \rcontr C[{\til Q}]$ (thus also $\til P \wb
+C[{\til P}]$ and $\til Q \wb C[{\til Q}]$).} We first follow the same steps as in the proof of
+Theorem~\ref{t:contraBisimulationU} to show that the following
+relation is bisimulation: (instead of using Lemma~\ref{l:uptocon}, now we need to use
+Lemma~\ref{l:ruptocon})
+\begin{equation}
+\label{eq:R2}
+\R \DSdefi \{ 
+(R,S) \st R \wb \ct{\til P}, S \wb \ct{\til Q} \mbox{ for some context
+$\qct$} \} \enspace.
+\end{equation}
+
+\hl{So far we have only proved $\til P$ and $\til Q$ are bisimilar,
+  $\til P \wb \til Q$, since obviously $(\til P,\til Q)
+\in \R$. But actually they are even rooted bisimilar.} To further prove
+$\til P \rapprox \til Q$, we can leverage
+Lemma~\ref{l:obsCongrByWeakBisim}. Thus it remains to show that, for 
 any two process $P$ and $Q$ with action $\mu$, if $P \arr{\mu} P'$ then
-there is $Q'$ such that $Q \Arr{\mu} Q'$ (not $Q \Arcap{\mu} Q'$!) and
-$P'\ \R\ Q'$, and also for the converse direction, exploting Lemma
-4.13 of \cite{Mil89} (TODO). By definition of
-\emph{bisimulation} (not $\wb$!) and $\approx^c$, we actually proved $P
-\approx^c Q$ instead of $P \wb Q$.
+there is $Q'$ such that $Q \Arr{\mu} Q'$ (not $Q \Arcap{\mu} Q'$) and
+$P'\ \R\ Q'$ (also for the converse direction).  The prove for this
+part is routine, just at certain steps we have to use
+Lemma~\ref{lem:313} in Section~\ref{ss:part2}, the
+one for proving Milner's ``unique solution of equations for $\sim$'',
+quite unexpected.
 \end{proof}

### 2019-02-08 ic-journal/coarsest.tex
text

@@
 %As bisimilarity ($\approx$) is not congruence, for this reason rooted bisimilarity has been
-introduced (Def.~\ref{d:rootedBisimilarity}).
-In this subsection we discuss two proofs of an important result stating that
+%introduced (Def.~\ref{d:rootedBisimilarity}).
+In this subsection we discuss two proofs of \DDS{the fundamental  result} stating that
 rooted bisimilarity is the coarsest congruence contained in
@@
 
-Actually the coarsest congruence
-contained in (weak) bisimilarity, namely the \emph{bisimilarity
-  congruence} \cite{van2005characterisation}, can be constructed as
+\DDS{The coarsest congruence
+contained in (weak) bisimilarity, namely  \emph{bisimilarity
+  congruence}, is}
 the \emph{composition closure} (\texttt{CC}) of (weak) bisimilarity:
@@
 \end{alltt}
-Indeed, for any relation $R$ 
-on CCS processes, the composition closure of $R$ is always finer (i.e.~smaller) than
-$R$, no matter if $R$ is (pre)congruence or not\footnote{But if $R$ is
-  equivalence (or preorder), the composition closure of $R$ must be congruence
-  (or precongruence). Also there is no need to put $R\ g\ h$ in the antecedent of
-  \texttt{CC\_def}, as this is anyhow obtained from the trivial context $(\lambda x.\,x)$.}:
+ (We need not  put $R\ g\ h$ in the antecedent of
+  \texttt{CC\_def}, as this is anyhow obtained from the trivial context $(\lambda x.\,x)$.)
+\DDS{For any relation $R$ 
+on CCS processes, the composition closure of $R$ is always at least as
+fine as }
+$R$
 (here $\subseteq_r$ stands for \emph{relational subset})
@@
 rooted bisimilarity ($\rapprox$), making all three relations
-($\rapprox$, \texttt{WEAK_CONGR} and \texttt{SUM_EQUIV}) equivalent:
+($\rapprox$, \texttt{WEAK_CONGR} and \texttt{SUM_EQUIV}) coincide:
 \begin{equation}
@@
 The standard argument \cite{Mil89} requires that $p$
-and $q$ do not use up all available labels (i.e.~visible actions).
-Formalising such an argument requires however 
+and $q$ do not use up available labels (i.e.~visible actions).
+Formalising such an argument requires  
 a detailed treatment on free and bound names of CCS
-processes (with the restriction operator being a binder), not done yet.
+processes (with the restriction operator being a binder).
 However, the proof of (\ref{equa:pq}) can be carried out 
@@
 just assuming that all immediate \emph{weak} derivatives of
- $p$ and $q$ do not use up all available labels.
+ $p$ and $q$ do not use  all available labels.
 % analyzing the proof steps, we found that, what's really required is to
@@
 ($\rcontr$) is also the coarsest
-precongruence contained in bisimilarity contraction ($\mcontrBIS$)
+precongruence contained in the bisimilarity contraction ($\mcontrBIS$)
 (the other direction is trivial):
@@
 
-The formal proofs  of the above two results  follow Milner's proof
-\cite{Mil89}. If only $p$ (or $q$) has free actions while the other uses all available
-labels, the assumption $\mathrm{fn}(p) \cup
-\mathrm{fn}(q) \neq \mathscr{L}$ (here $\mathrm{fn}$ stands for \emph{free
-  names}) does not hold, and the proof cannot be completed. Our
-assumption is \emph{weaker}
-in the sense that $p$ and $q$ need not have the
-\emph{same} free actions (note that $a$ and its complementary  $\outC a$ are
-considered \emph{different} as actions).
+\DDS{The formal proofs  of the above two results  follow Milner's proof
+\cite{Mil89}. The assumption is Milner's result 
+requires  $\mathrm{fn}(p) \cup
+\mathrm{fn}(q) \neq \mathscr{L}$ (where $\mathrm{fn}$ stands for \emph{free
+  names}), and is therefore strictly stronger than the assumption in
+our result above, where we only look at immediate weak
+derivatives $p$ and $q$, requiring that there is at least one action
+that never appears as a label; moreover such an action need not be
+the same for $p$ and for $q$
+%  If only $p$ (or $q$) has free actions while the other uses all available
+% labels, the assumption $\mathrm{fn}(p) \cup
+% \mathrm{fn}(q) \neq \mathscr{L}$ (here $\mathrm{fn}$ stands for \emph{free
+%   names}) does not hold, and the proof cannot be completed. Our
+% assumption is \emph{weaker}
+% in the sense that $p$ and $q$ need not have the
+% \emph{same} free actions 
+(and where an action $a$ and its complementary  $\outC a$ are
+considered \emph{different} actions).}
 
-There exists a different, more complex proof of (\ref{eq:coarsest}),
+There exists a different, more complex, proof of (\ref{eq:coarsest}),
 given by van Glabbeek \cite{van2005characterisation}, which does not
@@
 To construct this process $k$,
- the proof relies on arbitrary infinite sum of 
+ the proof relies on arbitrary infinite sums of 
 processes and uses transfinite induction to obtain
@@
 to be the finite-state processes).
+\DDS{The proof, in the section below, uses extensively HOL's
+\texttt{pred_set} theory \cite{melham1992hol}, with a mix
+of CCS and pure mathematics.}
 
@@
 The assumption in the  previous \texttt{PROP3_COMMON} requires the
-existence of a special CCS process, which is not weak bisimilar to
+existence of a special CCS process, which is not weakly bisimilar to
 any sub-process emanating from the two root processes by weak
@@
 modulo weak bisimilarity.
-If there are infinitely many of them, 
-then it should be 
+If there are infinitely many of such classes, 
+then it will be 
 possible to choose one  that is distinct from all the (finitely many) states in the
 graphs of the two given processes.  
-This can be done following a contruction originally given by 
- Jan Willem Klop \cite{van2005characterisation}.
+\DDS{This can be done following Klop's contruction \cite{van2005characterisation}.}
  We call  ``Klop processes''  the processes in this construction:
@@
 
-By induction on the definition of Klop processes and SOS inference
+By induction on the definition of Klop processes,  and using the SOS inference
 rules ($\mathrm{Sum}_1$) and ($\mathrm{Sum}_2$), we can  prove
@@
 \begin{enumerate}
-\item All Klop processes are stable:
+\item (All Klop processes are stable)
 \begin{alltt}
@@
 \end{alltt}
-\item Any transition from a Klop process leads to a smaller Klop
-  process, and conversely:
+\item (Any transition from a Klop process leads to a smaller Klop
+  process, and conversely)
 \begin{alltt}
@@
 \end{alltt}
-\item The weak transition version of the above property:
+\item (The weak version of the previous property)
 \begin{alltt}
@@
 \end{alltt}
-\item All Klop processes are distinct according to strong equivalence:
+\item (All Klop processes are distinct according to strong   bisimilarity)
 \begin{alltt}
@@
 \end{alltt}
-\item All Klop processes are distinct according to weak equivalence:
+\item (All Klop processes are distinct according to weak bisimilarity)
 \begin{alltt}
@@
 \end{alltt}
-\item Klop functions are one-one:
+\item (Klop functions are one-one)
 \begin{alltt}
@@
 Given an equivalence relation $R$ defined on a type, and two sets $A, B$
-of elements in this type, $A$ is finite, $B$ is infinite, and all elements
-in $B$ are not equivalent, then there exists an element $k$ in $B$
-which is not equivalent with any element in $A$:
+of elements in this type, 
+\DDS{if $A$ is finite, $B$ is infinite, and all elements
+in $B$ belong to distinct equivalence classes,} then there exists an element $k$ in $B$
+which is not equivalent to any element in $A$:
 \begin{alltt}
@@
 Among many properties of above definitions, we mainly rely on the
-following ``obvious'' property on weak transitions:
+following (trivial) property for weak transitions:
 \begin{proposition}
@@
 
-Using all the above results, now we can easily prove the following finite
+Using all the above results, now we can  prove the following finite
 version of ``Klop lemma'':
@@
 \label{lem:klop-lemma-finite}
-For any two finite-state CCS $p$ and $q$, there exists another process $k$, which
-is not weak equivalent to any derivative  of $p$
-and $q$ (i.e., processes reachable from $p$ and $q$ by means of transitions):
+\DDS{For any two finite-state CCS $p$ and $q$, there is another process
+$k$, which is not weakly bisimilar 
+with
+ any weak derivative  of $p$
+and $q$ (i.e., any process reachable from $p $ or $q$ by means of transitions):}
 \begin{alltt}

### 2019-02-08 ic-journal/conclusions.tex
text

@@
 In this paper, we have highlighted a formalisation of the theory of CCS in the 
-HOL4 theorem prover (for lack of space we have not discussed 
-the formalisation of some basic algebraic theory, of the basic
-properties of the expansion preorder,   and of a few
- versions of `bisimulation up to'
-techniques). % such as  bisimulation up-to bisimilarity). 
-The formalisation has focused on the theory of
-unique solution of equations and contractions. 
-It has also allowed us to further develop the theory,
+HOL4 theorem prover.
+%  (for lack of space we have not discussed 
+% the formalisation of some basic algebraic theory, of the basic
+% properties of the expansion preorder,   and of a few
+%  versions of `bisimulation up to'
+% techniques). %
+%such as  bisimulation up-to bisimilarity). 
+\DDS{The formalisation supports  4 methods for establishing (strong and weak) bisimilarity
+results: 
+\begin{enumerate}
+\item
+ constructing a bisimulation (the standard bisimulation proof
+method);
+\item constructing a `bisimulation up-to'; 
+\item employing algebraic laws;
+\item defining a system of equations or contractions
+(i.e., the `unique-solution' method)
+\end{enumerate}
+ }
+
+The formalisation has actually focused on the theory of
+unique solution of equations and contractions. It    
+ has also allowed us to further develop the theory,
 notably the basic properties of rooted contraction, and the unique
@@
 The formalisation brings up and exploits similarities between results
-and proofs for different equivalences and preorders. 
+and proofs for different equivalences and preorders. \DS{Indeed we have
+considered several `unique-solution' results (for various equivalences
+and preorders); they share many parts of the proofs, but present a few
+delicate and subtle differences in a few points. In a paper-pencil
+proof, checking all details would be long and error-prune, since one
+is tempted to overlook  details that tend to repeat themselves. 
+A theorem-prover formalisation is in this respect  helpful and reassuring.}
 We think that the statements in the formalisation are easy to read and
-understand, as they are very close to the original statements found in
+understand, as they are  close to the original statements found in
 standard CCS textbooks \cite{Gorrieri:2015jt,Mil89}.
@@
 %
-The second half of this
-paper was written in memory of Michael J.~C.~Gordon, the creator of HOL theorem prover.
+\DDS{The 
+paper was written in memory of Michael J.~C.~Gordon, the creator of the HOL theorem prover.}

### 2019-02-08 ic-journal/context.tex
text

@@
 
-Many lemmas have then to be proved for their
+Many lemmas have then to be proved for the
  relationships among these kinds of contexts and properties about their
@@
 \texttt{CONTEXT}. The only difference between congruence and
-precongruence is that the former must be an equivalence (reflexive,
-symmetric, transitive), while the latter can be just a preorder (reflexive, transitive):
+precongruence is that the former  is an equivalence (reflexive,
+symmetric, transitive), while the latter can  just be  a preorder (reflexive, transitive):
 \begin{alltt}

### 2019-02-08 ic-journal/formal.tex
text

@@
  proof scripts without loss of generality. For the  pencil-and-paper proofs, the
- multi-variable case is just a routine adaptation, while the   formalisation
+ multi-variable case is just a routine adaptation, while the \DDS{theorem-prover}   formalisation
  is not (this is also discussed in Section~\ref{s:concl}).

### 2019-02-08 ic-journal/part2.tex
text

@@
 steps). The proof of this last theorem consists of 500 lines (each
-line usually has 2 or 3 HOL tactics, to make the proof not too long
-in lines).
+line usually has 2 or 3 HOL tactics, to make the proof shorter).
 
@@
 We can then derive the target theorem:
-\begin{theorem}{(Unique solution of equations for weak equivalence)}
+\begin{theorem}{(Unique solution of equations for weak bisimilarity)}
 Let $E$ be guarded and sequential expressions, and let $P \wb
@@
 For the ``unique solutions of
-equations'' theorem of rooted bisimilarity, we have used a new technique, i.e., the
+equations'' theorem of rooted bisimilarity, we use a different
+technique, represented by the
 following lemma.   It is   assertion 
  \texttt{OBS_CONGR_BY_WEAK_BISIM} mentioned in
- Section~\ref{ss:bb}, corresponding to
+ Section~\ref{ss:bb}, and corresponds to
  Lemma~\ref{l:obsCongrByWeakBisim}; we only report the text for  \texttt{OBS_CONGR_BY_WEAK_BISIM}.

### 2019-02-08 ic-journal/sos.tex
text

@@
     is arbitrary. Our choice is aligned with other CCS literals.
-$\mathrm{CCS}(h,k)$ is the CCS subcalculus which can use at most $h$ constants
-and $k$ actions. \cite{gorrieri2017ccs} Thus, to formalize theorems on
-such a CCS subcalculus, the needed CCS type can be retrieved by instantiating the type
+$\mathrm{CCS}(h,k)$ is the CCS subcalculus that can use at most $h$ constants
+and $k$ actions \cite{gorrieri2017ccs}. Thus, to formalize theorems on
+such a calculus, the needed CCS type can be retrieved by instantiating the type
 variables $\alpha$ and $\beta$ in ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'' with types
 having the corresponding cardinalities $h$ and $k$. Monica Nesi goes
-too far by adding another type variable $\gamma$ for value-passing CCS
+farther, by adding another type variable $\gamma$ for value-passing CCS
 \cite{Nesi:2017wo}.}, is then defined inductively:

### 2019-02-08 ic-journal/unique.tex
text

--- 2019-02-07 ic-journal/unique.tex
@@
 $\contr$ with $\rcontr$, and the equivalence 
-$\approx$ with $\rapprox$.
+$\approx$ with $\rapprox$ \DDS{ (note that  with $\rapprox$ one considers
+solutions with respect to  $\rcontr$).}
 %
@@
 \end{lemma}
+The proof of Lemma~\ref{l:ruptocon} is exactly the same as of
+Lemma~\ref{l:uptocon}, because all we need from $\mcontrBIS$ and
+$\rcontr$ is their precongruences (in the sense of different
+definitions of contexts). Also notice that, the conclusion of
+Lemma~\ref{l:ruptocon} still uses $\mcontrBIS$, because $\rcontr$ does
+not hold.
 
-\begin{theorem}[unique solution of contractions for $\rapprox$]
+\begin{theorem}[Unique solution of contractions for $\rapprox$]
 \label{t:rcontraBisimulationU}
 A system of weakly-guarded contractions has a unique solution 
- for $\rapprox$. (thus also for $\wb$)
+ for $\rapprox$. % (thus also for $\wb$).
 \end{theorem}
@@
 \begin{proof}
-We first follow the same steps as in the proof of Theorem~\ref{t:contraBisimulationU} to show the relation $\R$ (now
-with $\rcontr$ and unrestricted context $C$) in (\ref{eq:R}) is bisimulation,
-exploting Lemma~\ref{l:ruptocon}. Then it remains to show that, for
-any two process $P$ and $Q$ with action $\mu$, if $P \arr{\mu} P'$ then
-there is $Q'$ such that $Q \Arr{\mu} Q'$ (not $Q \Arcap{\mu} Q'$!) and
-$P'\ \R\ Q'$, and also for the converse direction, exploting Lemma
-4.13 of \cite{Mil89} (TODO). By definition of
-\emph{bisimulation} (not $\wb$!) and $\approx^c$, we actually proved $P
-\approx^c Q$ instead of $P \wb Q$.
+\hl{Suppose $\til P$ and $\til Q$ are two such solutions: $\til P \rcontr
+C[{\til P}]$ and $\til Q \rcontr C[{\til Q}]$ (thus also $\til P \wb
+C[{\til P}]$ and $\til Q \wb C[{\til Q}]$).} We first follow the same steps as in the proof of
+Theorem~\ref{t:contraBisimulationU} to show that the following
+relation is bisimulation 
+\DDS{ (using 
+Lemma~\ref{l:ruptocon}
+in place of  Lemma~\ref{l:uptocon}):}
+\begin{equation}
+\label{eq:R2}
+\R \DSdefi \{ 
+(R,S) \st R \wb \ct{\til P}, S \wb \ct{\til Q} \mbox{ for some context
+$\qct$} \} \enspace.
+\end{equation}
+\DDS{The property that $\R$ is a bisimulation  proves  $\til P$ and $\til Q$ bisimilar, i.e.,
+  $\til P \wb \til Q$.  To further prove
+$\til P \rapprox \til Q$, we  appeal to
+Lemma~\ref{l:obsCongrByWeakBisim}. Thus it remains to show that, for 
+any two process $P$ and $Q$ and action $\mu$, if $P \arr{\mu} P'$ then
+there is $Q'$ such that $Q \Arr{\mu} Q'$  and
+$P'\ \R\ Q'$ (and  the converse direction).  The prove for this
+part is routine,  using 
+Lemma 3.13 of \cite{Mil89},  reported as 
+Lemma~\ref{lem:313} in Section~\ref{ss:part2} (the lemma is  also needed 
+in  Milner's  proof of ``unique solution of equations for $\sim$'').}
 \end{proof}

### 2019-02-09 ic-journal/coarsest.tex
Sync htex with tex files, clear all DS and DDS blocks

@@
 %introduced (Def.~\ref{d:rootedBisimilarity}).
-In this subsection we discuss two proofs of \DDS{the fundamental  result} stating that
+In this subsection we discuss two proofs of the fundamental result stating that
 rooted bisimilarity is the coarsest congruence contained in
@@
 
-\DDS{The coarsest congruence
+The coarsest congruence
 contained in (weak) bisimilarity, namely \emph{bisimilarity
-  congruence}, is}
+  congruence}, is
 the \emph{composition closure} (\texttt{CC}) of (weak) bisimilarity:
@@
   \texttt{CC\_def}, as this is anyhow obtained from the trivial context $(\lambda x.\,x)$.)
-\DDS{For any relation $R$ 
+For any relation $R$ 
 on CCS processes, the composition closure of $R$ is always at least as
-fine as }
-$R$
+fine as $R$
 (here $\subseteq_r$ stands for \emph{relational subset})
@@
 
-\DDS{The formal proofs  of the above two results  follow Milner's proof
+The formal proofs  of the above two results  follow Milner's proof
 \cite{Mil89}. The assumption is Milner's result 
@@
 (and where an action $a$ and its complementary  $\outC a$ are
-considered \emph{different} actions).}
+considered \emph{different} actions).
 
@@
 to be the finite-state processes).
-\DDS{The proof, in the section below, uses extensively HOL's
+The proof, in the section below, uses extensively HOL's
 \texttt{pred_set} theory \cite{melham1992hol}, with a mix
-of CCS and pure mathematics.}
+of CCS and pure mathematics.
 
@@
 graphs of the two given processes.  
-\DDS{This can be done following Klop's contruction \cite{van2005characterisation}.}
+This can be done following Klop's contruction \cite{van2005characterisation}.
  We call  ``Klop processes''  the processes in this construction:
@@
 of elements in this type, 
-\DDS{if $A$ is finite, $B$ is infinite, and all elements
-in $B$ belong to distinct equivalence classes,} then there exists an element $k$ in $B$
+if $A$ is finite, $B$ is infinite, and all elements
+in $B$ belong to distinct equivalence classes, then there exists an element $k$ in $B$
 which is not equivalent to any element in $A$:
@@
 \label{lem:klop-lemma-finite}
-\DDS{For any two finite-state CCS $p$ and $q$, there is another process
+For any two finite-state CCS $p$ and $q$, there is another process
 $k$, which is not weakly bisimilar 
@@
  any weak derivative  of $p$
-and $q$ (i.e., any process reachable from $p $ or $q$ by means of transitions):}
+and $q$ (i.e., any process reachable from $p $ or $q$ by means of transitions):
 \begin{alltt}

### 2019-02-09 ic-journal/conclusions.tex
Sync htex with tex files, clear all DS and DDS blocks

@@
 %such as  bisimulation up-to bisimilarity). 
-\DDS{The formalisation supports  4 methods for establishing (strong and weak) bisimilarity
+The formalisation supports 4 methods for establishing (strong and weak) bisimilarity
 results: 
@@
 \end{enumerate}
- }
 
@@
 The formalisation brings up and exploits similarities between results
-and proofs for different equivalences and preorders. \DS{Indeed we have
+and proofs for different equivalences and preorders. Indeed we have
 considered several `unique-solution' results (for various equivalences
@@
 is tempted to overlook  details that tend to repeat themselves. 
-A theorem-prover formalisation is in this respect  helpful and reassuring.}
+A theorem-prover formalisation is in this respect  helpful and reassuring.
 We think that the statements in the formalisation are easy to read and
@@
 %
-\DDS{The 
-paper was written in memory of Michael J.~C.~Gordon, the creator of the HOL theorem prover.}
+The 
+paper was written in memory of Michael J.~C.~Gordon, the creator of the HOL theorem prover.

### 2019-02-09 ic-journal/unique.tex
Final fixes

@@
 $\contr$ with $\rcontr$, and the equivalence 
-$\approx$ with $\rapprox$ \DDS{ (note that  with $\rapprox$ one considers
-solutions with respect to  $\rcontr$).}
+$\approx$ with $\rapprox$ (note that with $\rapprox$ one considers
+solutions with respect to  $\rcontr$).
 %
@@
 \begin{proof}
-\hl{Suppose $\til P$ and $\til Q$ are two such solutions: $\til P \rcontr
+Suppose $\til P$ and $\til Q$ are two such solutions: $\til P \rcontr
 C[{\til P}]$ and $\til Q \rcontr C[{\til Q}]$ (thus also $\til P \wb
-C[{\til P}]$ and $\til Q \wb C[{\til Q}]$).} We first follow the same steps as in the proof of
+C[{\til P}]$ and $\til Q \wb C[{\til Q}]$). We first follow the same steps as in the proof of
 Theorem~\ref{t:contraBisimulationU} to show that the following
 relation is bisimulation 
-\DDS{ (using 
+(using 
 Lemma~\ref{l:ruptocon}
-in place of  Lemma~\ref{l:uptocon}):}
+in place of  Lemma~\ref{l:uptocon}):
 \begin{equation}
@@
 \end{equation}
-\DDS{The property that $\R$ is a bisimulation  proves  $\til P$ and $\til Q$ bisimilar, i.e.,
+The property that $\R$ is a bisimulation  proves  $\til P$ and $\til Q$ bisimilar, i.e.,
   $\til P \wb \til Q$.  To further prove
@@
 Lemma~\ref{lem:313} in Section~\ref{ss:part2} (the lemma is  also needed 
-in  Milner's  proof of ``unique solution of equations for $\sim$'').}
+in  Milner's  proof of ``unique solution of equations for $\sim$'').
 \end{proof}

### 2019-03-06 ic-journal/formal.tex
Clean up the rest DDS macros; disable line numbers

--- 2019-02-07 ic-journal/formal.tex
@@
  proof scripts without loss of generality. For the  pencil-and-paper proofs, the
- multi-variable case is just a routine adaptation, while the   formalisation
+ multi-variable case is just a routine adaptation, while the
+ formalisation in theorem prover % \DDS{}
  is not (this is also discussed in Section~\ref{s:concl}).

### 2019-08-06 ic-journal/response-letter.tex
Added response-leter.tex filled with original reviews (from reviews.txt)

\begin{center}
\textbf{
{\small Changes for Submission 1 to SI:EXPRESS/SOS'18}\\[5mm]
{\large Unique Solutions of Contractions, CCS, and their HOL
  Formalisation
}}
\end{center}

\section*{Responses to Review 1 (accept - minor revision)}

\subsection*{Meta comments}

\begin{enumerate}
\item \begin{quote}
    This paper describes a HOL formalisation of several notions in
    process theory: CCS and various kinds of bisimilarity, and in
    particular the unique-solutions technique. The latter was
    introduced by Milner, and recently revisited and refined by the
    second author.
  \end{quote}

\item \begin{quote}
    In general, these kinds of results are error-prone, especially
    those related to weak bisimilarity: there are multiple known
    mistakes in the literature. Therefore, formalisation is a
    worthwile effort. Moreover, the formalisation itself is quite
    readable. The paper itself documents this formalisation and is,
    for the most part, clear.
  \end{quote}

\item \begin{quote}
    The paper is an extended version of an EXPRESS/SOS paper. The
    extension consists of a more detailed report of the proofs -
    perhaps this is enough.
  \end{quote}

\item \begin{quote}
    I was disappointed though that multi-variable contexts are still
    not treated (I reviewed the EXPRESS/SOS paper as well and
    complained about that then). This means the current formalisation
    does *not* fully formalise the unique-solution method. The journal
    version would have been ideal to solve this issue. It is briefly
    discussed in the conclusion, but in fact, the first author's
    master thesis argues that it is possible: "With these new devices,
    it’s possible to formalize all “unique solution of equations”
    theorems with multi-variable equations, without touching existing
    formalization framework.". The current discussion should at the
    very least explain this (is the master thesis wrong? is this too
    hard, or too much work?), but hopefully it can just be done
    properly so that the paper fully covers the correctness of the
    unique-solution method. 
  \end{quote}

\item \begin{quote}
    overall the paper can use a bit of spell-checking and proofreading (e.g. there are some initials in the margin)
  \end{quote}

\end{enumerate}

\subsection*{Detailed comments}

\begin{enumerate}
\item \begin{quote}
    L45: "about unique solution*s*"
  \end{quote}

\item \begin{quote}
    L84 "the weak one" rephrase
  \end{quote}

\item \begin{quote}
    L91 "bisimiarity"
  \end{quote}

\item \begin{quote}
    proof of thm 3.10: could there be some kind of picture to help? also, the "Hence," in the one-to-last line refers only to the property right before it, right? (about $C[\tilde{Q}]$)
  \end{quote}

\item \begin{quote}
    L209: "their precongruences" precongruence closure?
  \end{quote}

\item \begin{quote}
    L216 "using Lemma 3.13 ... Section 4.9" perhaps just repeat the lemma before the theorem, as it's a bit hard to read Lemma 4.14 at this stage 
  \end{quote}

\item \begin{quote}
    L224: full stop and new sentence after "1972"
  \end{quote}

\item \begin{quote}
    L227 "considerable" -> "considerably"
  \end{quote}

\item \begin{quote}
    L228 "formal theories built in HOL is easily convincible" questionable grammar
  \end{quote}

\item \begin{quote}
    L238 how is this without loss of generality?
  \end{quote}

\item \begin{quote}
    L245 maybe more clear to just give the definition of $\beta$ Action 
  \end{quote}

\item \begin{quote}
    L250,300: perhaps explain what these (double) backquotes signify or just remove the sentence
  \end{quote}

\item \begin{quote}
    L277 "substutiion"
  \end{quote}

\item \begin{quote}
    L280 (around): put some of these equalities on a single line? enough space
  \end{quote}

\item \begin{quote}
    L316 and later, e.g. 323: is "p" a closed ccs term?
  \end{quote}

\item \begin{quote}
    L361 "Many lemmas ... contexts" this is a bit vague
  \end{quote}

\item \begin{quote}
    L374 "An highlight"
  \end{quote}

\item \begin{quote}
    L378 "is a" => "are"
  \end{quote}

\item \begin{quote}
    L385 "With *the* above"
  \end{quote}

\item \begin{quote}
    L386 "the definition" of what? (bisimilarity, but say that)
  \end{quote}

\item \begin{quote}
    L394 "since *the* Kananaskis-11 release"
  \end{quote}

\item \begin{quote}
    L396 "we call *the* Hol_coreln"
  \end{quote}

\item \begin{quote}
    L410 $E$ and $E'$ missing
  \end{quote}

\item \begin{quote}
    L436 "is defined upon weak transition" grammar
  \end{quote}

\item \begin{quote}
    L505 this is good: it is missing for strong bisimilarity, should
    be added there too (the two definitions are now not explicitly
    related)
  \end{quote}

\item \begin{quote}
    L580 "a contraction" ?
  \end{quote}

\item \begin{quote}
    section 4.6 header: "the formalisation of bisimulation up to
    bisimilarity", i would say; also since you're not using
    compatible/respectful functions
  \end{quote}

\item \begin{quote}
    L599 PRQ not so pretty spacing. perhaps mention around here that
    naive weak bisimulation up to weak bisimilarity is unsound?
  \end{quote}

\item \begin{quote}
    L655 (around here): i'd say in the text above it that this is a
    different bisimulation game, not a different up-to technique
  \end{quote}

\item \begin{quote}
    L708 " closure of bisimilarity under such operator" not sure whether this is gramatically correct
  \end{quote}

\item \begin{quote}
    figure 2: I'm a bit confused since the other implication is missing. 
  \end{quote}

\item \begin{quote}
    Overall, in section 4.7, it seems the claim in the beginning is
    only proved under certain hypotheses: the "free-action" property,
    or in the Glabbeek proof, finite processes. This is all very much
    hidden: and it should be said up-front what we are going to prove
    exactly under which assumptions.
  \end{quote}

\item \begin{quote}
    L740 "this proof" which? 
  \end{quote}

\item \begin{quote}
    The beginning of section 4.8 is really confusing: what are "the
    two root processes"? What are we going to prove in this section,
    and why, what is the aim here? Again, under which assumptions are
    we going to work?
  \end{quote}

\item \begin{quote}
    L820 "bisimularity"
  \end{quote}

\item \begin{quote}
    Lemma 4.14 is nicely introduced, Thm 4.15 not. 
  \end{quote}

\item \begin{quote}
    L898 full stop \& new sentence after "many ways"
  \end{quote}

\item \begin{quote}
    L990-995 aren't some of the textbook proofs even wrong? (e.g. [2]
    in the proof for unique solutions makes use of weak bisimulation
    up to weak bisimilarity, if i remember correctly) - one could
    perhaps say this, it makes the point even stronger
  \end{quote}

\end{enumerate}

\section*{Responses to Review 2 (accept - minor revision)}

\subsection*{Meta comments}

\begin{enumerate}
\item \begin{quote}
    This paper presents a formalisation in HOL of the core classical
    theory of CCS, with a particular focus on unique (modulo a proper
    equivalence) solutions of equations, and of the more recent theory
    of contractions developed by one of the authors.
  \end{quote}

\item \begin{quote}
    The focus is on weak semantics, which is well-known to be quite
    delicate, which makes the results of the paper relevant and
    interesting.
  \end{quote}

\item \begin{quote}
    Notably, the HOL formalisation has allowed the authors to refine
    the theory of unique solutions of contractions. In detail, the
    authors rely on rooted contractions and prove that a system of
    weakly guarded contractions has a unique solution modulo rooted
    weak bisimilarity. Interestingly, no constraint on occurrences of
    summations is required.

    I found this work elegant and interesting, I propose acceptance with minor review.
  \end{quote}

\end{enumerate}

\subsection*{Detailed comments}

\begin{enumerate}

\item \begin{quote}
    There are some typos. E.g., several times I read “bisimiarity” (the “l” is missed).
  \end{quote}

\item \begin{quote}
    There are side remarks that should be removed.
  \end{quote}

\item \begin{quote}
    The two sentences immediately before and after Example 3.7 are equivalent.
  \end{quote}

\item \begin{quote}
    The notion of “substitutivity property” should be introduced, now it’s used but not explained.
  \end{quote}

\item \begin{quote}
    I strongly believe that Section 4 is accessible only to people
    already familiar with HOL syntax. I suggest the authors to give
    some more details. Some examples.
  \end{quote}

\item \begin{quote}
    You assume the reader knows what Hol_reln is, but this not always the case. 
Then, you define the congruence in terms of the equivalence, but is
the equivalence already defined somewhere?
  \end{quote}

\item \begin{quote}
    The argument at lines 387-389 is clear only after the lines 394-427 have been read.
  \end{quote}

\item \begin{quote}
    At lines 577 you write that proving properties for contraction is
    in general harder than proving properties for expansion. Could you
    explain why?
  \end{quote}
\end{enumerate}

\section*{Responses to Review 3 (accept - major revision)}

\subsection*{Meta comments}

\begin{enumerate}
\item \begin{quote}
    This paper presents a HOL formalisation of part of the theory of
    CCS. It formalises the syntax and operational semantics of CCS,
    strong and weak bisimilarity, and several well-known auxiliary
    techniques for establishing that CCS processes are bisimilar.
  \end{quote}

\item \begin{quote}
    The most notable contribution seems to be the formalisation (and
    modest extension) of results already obtained by the second author
    in an ACM TOCL paper (ref. [7]) pertaining regarding the
    uniqueness of solutions of contractions. The main addition with
    respect to the EXPRESS/SOS 2018 publication of the authors with
    the same title (ref. [1]), seems to be a HOL formalisation of the
    proof that rooted weak bisimilarity is the coarsest congruence
    contained in weak bisimilarity, and that rooted contraction is the
    coarsest precongruence contained in contraction. The HOL proof
    scripts are publicly available through a GitHub repository.
  \end{quote}

\item \begin{quote}
    The scientific contribution of the paper is, in my opinion,
    modest, at least in its current form. With the exception of the
    extension of the results in [7] to rooted contractions, the paper
    seems to merely consist of reformulations in HOL of well-known
    definitions and theorems with, here and there, some superficial
    comments about the proof scripts needed to prove the results
    (e.g., the coinduction package available for HOL simplifies the
    formalisation).
  \end{quote}

\item \begin{quote}
    Putting it bluntly, the current message of the paper seems to be
    that there are HOL proof scripts available in a GitHub
    repository. Perhaps there is something interesting and general to
    learn from this particular HOL formalisation, either about HOL or
    about CCS, but then this should be explained in much more detail.
  \end{quote}

\item \begin{quote}
    It does not help that the paper has many typos and ungrammatical
    sentences. Also, the article explains too little about HOL for a
    reader without prior exposure to HOL to fully appreciate the
    contents of Section 4 and, in particular, understand the
    meta-remarks about the formalisation.
  \end{quote}

\item \begin{quote}
    I do find it very useful that the theory of CCS is formalised in
    HOL, so that others can benefit from it when doing
    computer-assisted proofs of results pertaining to CCS, or about
    CCS processes. I think this is important work, and researchers
    should get due credit for this. Currently, the value is really in
    the availability of the HOL proof scripts, and not so much in the
    article they wrote about it.
  \end{quote}

\item \begin{quote}
    In conclusion, on the positive side, I think the authors did some
    important work formalising part of the theory of CCS in HOL, and
    on the negative side I have doubts about the scientific value of
    the article they wrote about it. I am therefore reluctant to
    support publication in Information and Computation at this stage.
  \end{quote}

\item \begin{quote}
    I am therefore reluctant to support publication in Information and
    Computation at this stage. I suggest to ask the authors for a
    major revision in which they make the paper accessible for readers
    not familiar with HOL, comment in more detail on the HOL proof
    scripts and what can be learned from them, and take into account
    the detailed comments below.
  \end{quote}
\end{enumerate}

\subsection*{Line-based comments}

\begin{enumerate}
\item \begin{quote}
    Abstract:
    There should be a remark that this is about weak bisimilarity. In
    general 'bisimilarity' is strong bisimilarity.
  \end{quote}

\item \begin{quote}
    L18: Remove the word 'rather'
  \end{quote}

\item \begin{quote}
    L28: Hennessy Lemma -> Hennessy's Lemma
  \end{quote}

\item \begin{quote}
    L28: Deng Lemma -> Deng's lemma
  \end{quote}

\item \begin{quote}
    L28: Remove the word 'long'
  \end{quote}

\item \begin{quote}
    L28: proofs -> theorems
  \end{quote}

\item \begin{quote}
    L32: Add the word 'also' after 'the work is'
  \end{quote}

\item \begin{quote}
    L34: From the view of -> From the point of view of
  \end{quote}

\item \begin{quote}
    L35: Regarding the sentence "as formally proving a previously known result gives us the chance to see
    what is really needed for establishing that result."
    Either omit this sentence or explain what technical insights one
    gains by doing this work
  \end{quote}

\item \begin{quote}
    L43-48: This sentence is difficult to read and could be split into multiple sentences.
  \end{quote}

\item \begin{quote}
    L55-60: Remove "Given a deadlock 0"
  \end{quote}

\item \begin{quote}
    L58: the trailing 0 -> a trailing 0
  \end{quote}

\item \begin{quote}
    L59: "shown in Fig. 1" is placed after "a Labeled Transition
    System", causing the belief that Figure 1 contains an LTS. 
    But there is no LTS. Figure 1 contains the SOS of CCS.

    Semantics: The relabeling rule is not explained anywhere.

    Semantics: The constraint on the relabeling functions does not belong to the inference rule, but should be formulated as a restriction on the syntax.
  \end{quote}

\item \begin{quote}
    L74: Add the word 'a' between 'are' and 'context'.
    Contexts: Does an i-holed context have exactly one hole $[]_i$ for each i? This question is not answered anywhere in the text.
    In the formalisation you only use contexts with one kind of hole []. This definition can be changed to only
    use one hole as well, with a clear indication that this hole can occur multiple times.
  \end{quote}

\item \begin{quote}
    L82: Remove the comma after $Q'$
Definition 2.2: Superscript $c$ is already used for contextual closure.
    Does $\approx^c$ stand for the contextual closure of $\approx$, or is it something else?
    Since contextual closure is not used anywhere in the paper, it is best to remove it.
    Otherwise you need different notation for rooted bisimilarity.
  \end{quote}

\item \begin{quote}
    L91: What does 'reducing' mean?
  \end{quote}

\item \begin{quote}
    L91: bisimiarity -> bisimilarity
  \end{quote}

\item \begin{quote}
    L92: bisimiarity -> bisimilarity
  \end{quote}

\item \begin{quote}
    L92: Add a colon after 'results'
  \end{quote}

\item \begin{quote}
    L118: Why is the word 'actions' in bold font? It says 'ds' in the margin, what does that mean?
  \end{quote}

\item \begin{quote}
Definition 3.3: The definition of ‘sequential’ is awkward.  Moreover
this definition calls for some examples since the definitions can be
very confusing.
  \end{quote}

\item \begin{quote}
Theorem 3.4: What are direct sums?
  \end{quote}

\item \begin{quote}
    L.127: I think it would be clearer to give two concrete solutions
    rather than saying that any process not using a is a solution.
  \end{quote}

\item \begin{quote}
    L138: "Bisimilarity contraction ... some contraction R". This is not a grammatically correct sentence.
  \end{quote}

\item \begin{quote}
    L142: ".. are even required". The word 'even' suggests that this
    is a stronger requirement, but it is in fact weaker.
  \end{quote}

\item \begin{quote}
    L143: Add the words "that is" after 'preorder'.
  \end{quote}

\item \begin{quote}
    L144: remove ‘that’
  \end{quote}

\item \begin{quote}
    L153: "As bisimilarity .. but sums." This is not a grammatically correct sentence.
  \end{quote}

\item \begin{quote}
    Example 3.7: this example shows strictness of the inclusion. But
    the sentence before the example suggests that this is going to
    show that the preorder is not preserved by sums.
  \end{quote}

\item \begin{quote}
    L157: Doesn’t this statement deserve a proof?
  \end{quote}

\item \begin{quote}
    L163: $P >= E[P]$ is spelled out earlier in Definition 3.2. Maybe spell out this one as well.
  \end{quote}

\item \begin{quote}
    L165: If you define the notion of guardedness in Definition 3.3 on
    expressions first, and only thereafter extend it to systems of
    equations, then you could here simply reuse the definition on
    expressions to get a definition of the notion for systems of
    contractions. The advantage is that you are precise rather than
    suggestive.
  \end{quote}

\item \begin{quote}
    L169: "The number of strong steps of which is is composed". Note
    that there is not a unique sequence; in fact, there may be many
    ways to reach R from $C[\tilde{P}]$ with a weak $\mu$-trace.
  \end{quote}

\item \begin{quote}
    L176: What does "applying the definition of $>=_{bis}$" mean?
    Footnote: Why not just spell out this definition instead of making a remark about it?  It would make the conclusion of the proof somewhat easier to digest. If you decide to keep the footnote, change $\tilde{R}$ to $R'$. The notation $\tilde{R}$ is used for tuples.
  \end{quote}

\item \begin{quote}
    L181: vis ?
  \end{quote}

\item \begin{quote}
    L184: closes -> completes
  \end{quote}

\item \begin{quote}
    L194: ‘the definition should not be recursive’?
  \end{quote}

\item \begin{quote}
    Definition 3.11: Similar to the remark about Definition 2.2.
  \end{quote}

\item \begin{quote}
    Proof of Theorem 3.14: Why do you use context $C$ instead of tuples of expressions $\tilde{E}$?
    If this is the case because you only use contexts with one kind of hole, then you should use the letter
    E instead of C.
    If $\tilde{P}$ is a solution then $P_i >=^c E_i[\tilde{P}]$ for all i, but this quantification over i is missing.
  \end{quote}

\item \begin{quote}
    L215: The prove -> The proof
  \end{quote}

\item \begin{quote}
    General: the word 'Logic' in "HOL Logic" is redundant.
  \end{quote}

\item \begin{quote}
    L223-225: Perhaps you want to reformulate this long sentence. It is hard to read.
  \end{quote}

\item \begin{quote}
    L227: considerable -> considerably
  \end{quote}

\item \begin{quote}
    L228: is -> are
  \end{quote}

\item \begin{quote}
    L228: what does convincible mean here?
  \end{quote}

\item \begin{quote}
    L230: single?
  \end{quote}

\item \begin{quote}
    L235: The sentence between parentheses is an important remark and
    should not be between parentheses.
  \end{quote}

\item \begin{quote}
    L238: without loss of generality?
  \end{quote}

\item \begin{quote}
    L239: similar to the comment about line 118, theorem-prover is
    bold and 'ds' is in the margin.
  \end{quote}

\item \begin{quote}
    L245: now based on HOL’s option theory?
  \end{quote}

\item \begin{quote}
    L249: What are ‘backquotes’?
  \end{quote}

\item \begin{quote}
    Footnote 3: What are CCS literals?
  \end{quote}

\item \begin{quote}
    L265: What does the turnstile mean? I would expect that structural
    operational rules are axioms of the theory, but the turnstile
    suggests to me that they are theorems.
  \end{quote}

\item \begin{quote}
    L275: we substitute rec A. P for all occurrences of the variable A in P.
  \end{quote}

\item \begin{quote}
    L279: substutiion -> substitution
  \end{quote}

\item \begin{quote}
    L289: these -> the, on the tenary -> of the ternary
  \end{quote}

\item \begin{quote}
    General: in the lines 293-300 the trailing deadlock 0 is given,
    while in the preliminaries you stated that it would be omitted. If
    you decide to keep the deadlock, it should also be in bold font.
  \end{quote}

\item \begin{quote}
    L296: I don’t understand fact (1).
  \end{quote}

\item \begin{quote}
    L299: ‘Hence ... CCS_TRANS_CONV’ is not a grammatically correct sentence; there is a verb missing.
  \end{quote}

\item \begin{quote}
    L316: Explain what is p.
  \end{quote}

\item \begin{quote}
    Footnote 4: Do you mean ‘unguarded recursion’? How can relabelling operators cause infinite branching?
  \end{quote}

\item \begin{quote}
    L362: tedious but long -> tedious and long
  \end{quote}

\item \begin{quote}
    L374: An highlight -> A highlight
  \end{quote}

\item \begin{quote}
    L378: relations on CCS process -> relation on CCS processes
  \end{quote}

\item \begin{quote}
    Footnote 5: Add the word 'respectively' between 'quantifiers' and 'in'.
  \end{quote}

\item \begin{quote}
    Footnote 6: Regarding the last sentence between parentheses. What do you mean by this?
  \end{quote}

\item \begin{quote}
    General: The same trick of applying the coinduction package to the
    definition of bisimulation is repeated twice.
  \end{quote}

\item \begin{quote}
    General: In the sections about the HOL formalisation you refer to
    weak bisimulation instead of bisimulation.    
  \end{quote}

\item \begin{quote}
    L461: I think there is no need to include those 3
    theorems. Wouldn’t it suffice to write that similar theorems are
    returned as for \texttt{STRONG\_EQUIV}?
  \end{quote}

\item \begin{quote}
    L496-503: A similar remark can be made for \texttt{STRONG\_EQUIV}. Why do you put it here?
  \end{quote}

\item \begin{quote}
    L523,524: Similar to the comment about line L28
  \end{quote}

\item \begin{quote}
    L545: What does this statement mean?
  \end{quote}

\item \begin{quote}
    Up-to techniques: You mention four up-to techniques for weak
    bisimilarity and each of them are not powerful enough to prove the
    unique solution theorems. Why are they not powerful enough?
  \end{quote}

\item \begin{quote}
    L580: ‘Surprisingly’ To me this is not really surprising. Why do you find it surprising?
  \end{quote}

\item \begin{quote}
    L606-619: I really see no added value in repeating Def. 4.2 in HOL syntax.
  \end{quote}

\item \begin{quote}
    Def. 4.4: Shouldn’t there be double arrows? (twice)
  \end{quote}

\item \begin{quote}
    L700: This paragraph starts with a sentence in parentheses, which is not very desirable.
    Moreover this sentence does not seem to be connected to the next sentence.
  \end{quote}

\item \begin{quote}
    L701: Sentence does not end with a period.
  \end{quote}

\item \begin{quote}
    L704: What do you mean by "which itself may not be"?
  \end{quote}

\item \begin{quote}
    Figure 2: The $\subseteq$ from \texttt{SUM\_EQUIV} to Rooted
    bisimilarity makes the figure confusing; put a $\supseteq$
  \end{quote}

\item \begin{quote}
    L723: is -> in
  \end{quote}

\item \begin{quote}
    L723-L727: This sentence should be split into multiple sentences.
  \end{quote}

\item \begin{quote}
    L744-745: pure mathematics?
  \end{quote}

\item \begin{quote}
    L746: Arbitrary -> Arbitrarily
  \end{quote}

\item \begin{quote}
    L749: "infinite such sub-processes" this construction does not seem right and could be avoided.
  \end{quote}

\item \begin{quote}
    L754: non-$\tau$ action $a$ -> $a\neq\tau$
  \end{quote}

\item \begin{quote}
    L766: "By induction on the definition", don't you mean by induction on natural numbers?
  \end{quote}

\item \begin{quote}
    L823: are -> is
  \end{quote}

\item \begin{quote}
    L831: `In above proof’ Which proof are your referring too? I only see a theorem.
  \end{quote}

\item \begin{quote}
    L837: Add the word 'a' between 'not' and 'congruence'
  \end{quote}

\item \begin{quote}
    L837: why do you also need the condition of sequentiality?
  \end{quote}

\item \begin{quote}
    L991: error-prune -> error-prone, ’since one is tempted to overlook details’?
  \end{quote}

\item \begin{quote}
    L1001: the trace equivalences -> trace-based equivalences
  \end{quote}

\item \begin{quote}
    L1006: in alphabetic order
  \end{quote}

\item \begin{quote}
    L1040: hol4 -> HOL4
  \end{quote}

\end{enumerate}

\section*{Other changes}

\begin{enumerate}
\item TODO
\end{enumerate}

### 2019-08-08 ic-journal/response-letter.tex
Enriched bisimulationTheory

@@
 
+  We have added "(weak)" before "bisimilarity", in the first line of abstract.
+
 \item \begin{quote}
@@
 
+  We have rephrased it into multiple sentences.
+
 \item \begin{quote}
@@
     But there is no LTS. Figure 1 contains the SOS of CCS.
+  \end{quote}
 
+  We have rephrased it, saying Fig.1 represents an LTS expressed in SOS rules.
+
+\item \begin{quote}
     Semantics: The relabeling rule is not explained anywhere.
+  \end{quote}
 
+\item \begin{quote}
     Semantics: The constraint on the relabeling functions does not belong to the inference rule, but should be formulated as a restriction on the syntax.
@@
     L74: Add the word 'a' between 'are' and 'context'.
-    Contexts: Does an i-holed context have exactly one hole $[]_i$ for each i? This question is not answered anywhere in the text.
-    In the formalisation you only use contexts with one kind of hole []. This definition can be changed to only
+  \end{quote}
+
+\item \begin{quote}
+  Contexts: Does an $i$-holed context have exactly one hole $[]_i$ for
+  each $i$? This question is not answered anywhere in the text.
+
+  In the formalisation you only use contexts with one kind of hole $[]$. This definition can be changed to only
   use one hole as well, with a clear indication that this hole can occur multiple times.
@@
     L82: Remove the comma after $Q'$
+  \end{quote}
+
+\item \begin{quote}
     Definition 2.2: Superscript $c$ is already used for contextual closure.
@@
 
+In this section, we listed other changes. All line numbers are based
+on the original review version of this paper.
+
 \begin{enumerate}

### 2019-08-08 ic-journal/ccs.tex
Enriched bisimulationTheory

@@
 The operational semantics of CCS is then given by means of
-a Labeled Transition System (LTS), shown in Fig.~\ref{f:LTSCCS} as
-Structural Operational Semantics (SOS)
-rules (the symmetric version of the two rules for
-parallel composition and the rule for sum are omitted).
+a Labeled Transition System (LTS) \hl{expressed in Structural Operational
+Semantics (SOS) rules}, shown in Fig.~\ref{f:LTSCCS}.
+The symmetric version of the two \hl{SOS} rules for
+parallel composition and the rule for sum are omitted.
 A CCS expression uses only \emph{weakly guarded sums} if all occurrences of

### 2019-08-08 ic-journal/intro.tex
Enriched bisimulationTheory

@@
 equivalences and preorders that share similar proof structures.
-Examples are: the results that rooted bisimilarity and rooted contraction are,
-respectively, the coarsest congruence contained in weak bisimilarity 
-and the coarsest precongruence contained in the contraction preorder; 
-the result about unique solution of equations for weak bisimilarity that uses the
-contraction preorder as an auxiliary relation, and other unique solution results (e.g.~%
-the one for rooted in which
-the auxiliary relation is rooted contraction); various forms of enhancements of the bisimulation
-proof method (the `up-to' techniques).
+%
+% Examples are: the results that rooted bisimilarity and rooted contraction are,
+% respectively, the coarsest congruence contained in weak bisimilarity 
+% and the coarsest precongruence contained in the contraction preorder; 
+% the result about unique solution of equations for weak bisimilarity that uses the
+% contraction preorder as an auxiliary relation, and other unique solution results (e.g.~%
+% the one for rooted in which
+% the auxiliary relation is rooted contraction); various forms of enhancements of the bisimulation
+% proof method (the `up-to' techniques).
+%
+% rephrased: (TODO: still hard to read --Chun)
+\hl{Such structural simililarities can be found, for instance, in the
+following cases: the proofs that rooted bisimilarity and rooted
+contraction are, respectively, the coarsest congruence contained in
+weak bisimilarity and the coarsest precongruence contained in the
+contraction preorder; the proofs about unique solution of equations
+for weak bisimilarity that uses the contraction preorder as an
+auxiliary relation, and other unique solution results (e.g. the one
+for rooted in which the auxiliary relation is rooted contraction); the
+proofs about various forms of enhancements of the bisimulation proof
+method (the `up-to' techniques).}
+%
 In these cases, moving between proofs there are only a few places in

### 2019-08-20 paper/HOLMultivariate.tex
Added MultivariateTheory into TeX generations

\newcommand{\HOLMultivariateDate}{20 Agosto 2019}
\newcommand{\HOLMultivariateTime}{13:05}
\begin{SaveVerbatim}{HOLMultivariateDefinitionsCCSXXequationXXdef}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es}.
       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenEquiv{}}
       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{E}. \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs}) \HOLBoundVar{Es}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateDefinitionsCCSXXequationXXdef}{\UseVerbatim{HOLMultivariateDefinitionsCCSXXequationXXdef}}
\begin{SaveVerbatim}{HOLMultivariateDefinitionsCCSXXsolutionXXdef}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{R} \HOLBoundVar{Ps}.
       \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{R} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenEquiv{}}
       \HOLConst{LIST_REL} \HOLBoundVar{R} \HOLBoundVar{Ps} (\HOLConst{MAP} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps})) \HOLBoundVar{Es})
\end{SaveVerbatim}
\newcommand{\HOLMultivariateDefinitionsCCSXXsolutionXXdef}{\UseVerbatim{HOLMultivariateDefinitionsCCSXXsolutionXXdef}}
\begin{SaveVerbatim}{HOLMultivariateDefinitionsCCSXXSUBSTXXdef}
\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map}. \HOLConst{CCS_Subst} \HOLConst{nil} \HOLBoundVar{map} \HOLSymConst{=} \HOLConst{nil}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{u} \HOLBoundVar{E}. \HOLConst{CCS_Subst} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLBoundVar{map} \HOLSymConst{=} \HOLBoundVar{u}\HOLSymConst{..}\HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{map}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
        \HOLConst{CCS_Subst} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLBoundVar{map} \HOLSymConst{=}
        \HOLConst{CCS_Subst} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{map} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_Subst} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLBoundVar{map}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
        \HOLConst{CCS_Subst} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLBoundVar{map} \HOLSymConst{=}
        \HOLConst{CCS_Subst} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{map} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{CCS_Subst} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLBoundVar{map}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{L} \HOLBoundVar{E}. \HOLConst{CCS_Subst} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLBoundVar{map} \HOLSymConst{=} \HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{map})) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{E} \HOLBoundVar{rf}.
        \HOLConst{CCS_Subst} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLBoundVar{map} \HOLSymConst{=} \HOLConst{relab} (\HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{map}) \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{X}.
        \HOLConst{CCS_Subst} (\HOLConst{var} \HOLBoundVar{X}) \HOLBoundVar{map} \HOLSymConst{=}
        \HOLKeyword{if} \HOLConst{MEM} \HOLBoundVar{X} (\HOLConst{MAP} \HOLConst{FST} \HOLBoundVar{map}) \HOLKeyword{then} \HOLConst{THE} (\HOLConst{ALOOKUP} \HOLBoundVar{map} \HOLBoundVar{X})
        \HOLKeyword{else} \HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{X} \HOLBoundVar{E}.
       \HOLConst{CCS_Subst} (\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLBoundVar{map} \HOLSymConst{=}
       \HOLKeyword{if} \HOLConst{MEM} \HOLBoundVar{X} (\HOLConst{MAP} \HOLConst{FST} \HOLBoundVar{map}) \HOLKeyword{then} \HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}
       \HOLKeyword{else} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{map})
\end{SaveVerbatim}
\newcommand{\HOLMultivariateDefinitionsCCSXXSUBSTXXdef}{\UseVerbatim{HOLMultivariateDefinitionsCCSXXSUBSTXXdef}}
\begin{SaveVerbatim}{HOLMultivariateDefinitionscontextXXdef}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}.
       \HOLConst{context} \HOLBoundVar{Xs} \HOLSymConst{=}
       (\HOLTokenLambda{}\HOLBoundVar{E}.
            \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
            \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{t} \HOLBoundVar{X})) \HOLBoundVar{Xs})
\end{SaveVerbatim}
\newcommand{\HOLMultivariateDefinitionscontextXXdef}{\UseVerbatim{HOLMultivariateDefinitionscontextXXdef}}
\begin{SaveVerbatim}{HOLMultivariateDefinitionsfromListXXdef}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps}. (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{=} \HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})
\end{SaveVerbatim}
\newcommand{\HOLMultivariateDefinitionsfromListXXdef}{\UseVerbatim{HOLMultivariateDefinitionsfromListXXdef}}
\begin{SaveVerbatim}{HOLMultivariateDefinitionsweaklyXXguardedXXdef}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}.
       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLSymConst{=}
       (\HOLTokenLambda{}\HOLBoundVar{E}.
            \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
            \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{t} \HOLBoundVar{X})) \HOLBoundVar{Xs})
\end{SaveVerbatim}
\newcommand{\HOLMultivariateDefinitionsweaklyXXguardedXXdef}{\UseVerbatim{HOLMultivariateDefinitionsweaklyXXguardedXXdef}}
\newcommand{\HOLMultivariateDefinitions}{
\HOLDfnTag{Multivariate}{CCS_equation_def}\HOLMultivariateDefinitionsCCSXXequationXXdef
\HOLDfnTag{Multivariate}{CCS_solution_def}\HOLMultivariateDefinitionsCCSXXsolutionXXdef
\HOLDfnTag{Multivariate}{CCS_SUBST_def}\HOLMultivariateDefinitionsCCSXXSUBSTXXdef
\HOLDfnTag{Multivariate}{context_def}\HOLMultivariateDefinitionscontextXXdef
\HOLDfnTag{Multivariate}{fromList_def}\HOLMultivariateDefinitionsfromListXXdef
\HOLDfnTag{Multivariate}{weakly_guarded_def}\HOLMultivariateDefinitionsweaklyXXguardedXXdef
}
\begin{SaveVerbatim}{HOLMultivariateTheoremsALOOKUPXXfromList}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{n}.
       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{n} \HOLSymConst{\HOLTokenLt{}} \HOLConst{LENGTH} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}}
       (\HOLConst{THE} (\HOLConst{ALOOKUP} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) (\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs})) \HOLSymConst{=} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps})
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsALOOKUPXXfromList}{\UseVerbatim{HOLMultivariateTheoremsALOOKUPXXfromList}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSubstXXalt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}. \HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{X} \HOLSymConst{=} \HOLConst{CCS_Subst} \HOLBoundVar{E} [(\HOLBoundVar{X}\HOLSymConst{,}\HOLBoundVar{E\sp{\prime}})]
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsCCSXXSubstXXalt}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSubstXXalt}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXELIM}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}.
       \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps}.
           (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}} (\HOLConst{CCS_Subst} \HOLBoundVar{E} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{=} \HOLBoundVar{E})
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXELIM}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXELIM}}
\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXpar}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
       \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremscontextXXpar}{\UseVerbatim{HOLMultivariateTheoremscontextXXpar}}
\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXparXXrule}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}})
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremscontextXXparXXrule}{\UseVerbatim{HOLMultivariateTheoremscontextXXparXXrule}}
\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXprefix}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}. \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremscontextXXprefix}{\UseVerbatim{HOLMultivariateTheoremscontextXXprefix}}
\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXprefixXXrule}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}. \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E})
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremscontextXXprefixXXrule}{\UseVerbatim{HOLMultivariateTheoremscontextXXprefixXXrule}}
\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrec}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
       \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
       \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremscontextXXrec}{\UseVerbatim{HOLMultivariateTheoremscontextXXrec}}
\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrelab}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}. \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremscontextXXrelab}{\UseVerbatim{HOLMultivariateTheoremscontextXXrelab}}
\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrelabXXrule}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}. \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf})
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremscontextXXrelabXXrule}{\UseVerbatim{HOLMultivariateTheoremscontextXXrelabXXrule}}
\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrestr}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}. \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremscontextXXrestr}{\UseVerbatim{HOLMultivariateTheoremscontextXXrestr}}
\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrestrXXrule}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}. \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E})
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremscontextXXrestrXXrule}{\UseVerbatim{HOLMultivariateTheoremscontextXXrestrXXrule}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsEVERYXXweaklyXXguarded}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es}.
       \HOLConst{EVERY} (\HOLConst{weakly_guarded} \HOLBoundVar{Xs}) \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{X}. \HOLConst{MEM} \HOLBoundVar{E} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{t} \HOLBoundVar{X})
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsEVERYXXweaklyXXguarded}{\UseVerbatim{HOLMultivariateTheoremsEVERYXXweaklyXXguarded}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsINXXfromList}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{Xs} \HOLBoundVar{Ps}.
       (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
       (\HOLConst{MEM} \HOLBoundVar{X} (\HOLConst{MAP} \HOLConst{FST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps})) \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs})
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsINXXfromList}{\UseVerbatim{HOLMultivariateTheoremsINXXfromList}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsstrongXXuniqueXXsolution}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es}.
       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLConst{weakly_guarded} \HOLBoundVar{Xs}) \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{Qs}.
           \HOLBoundVar{Ps} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{STRONG_EQUIV} \HOLSymConst{\HOLTokenConj{}}
           \HOLBoundVar{Qs} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{STRONG_EQUIV} \HOLSymConst{\HOLTokenImp{}}
           \HOLConst{STRONG_EQUIV} \HOLBoundVar{Ps} \HOLBoundVar{Qs}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsstrongXXuniqueXXsolution}{\UseVerbatim{HOLMultivariateTheoremsstrongXXuniqueXXsolution}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsstrongXXuniqueXXsolutionXXlemma}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}.
       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps}.
           (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{P\sp{\prime}}.
               \HOLConst{CCS_Subst} \HOLBoundVar{E} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
               \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sp{\prime}}.
                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
                   (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLConst{CCS_Subst} \HOLBoundVar{E\sp{\prime}} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps})) \HOLSymConst{\HOLTokenConj{}}
                   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
                       (\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
                       \HOLConst{CCS_Subst} \HOLBoundVar{E} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs})
                       \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd
                       \HOLConst{CCS_Subst} \HOLBoundVar{E\sp{\prime}} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs})
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsstrongXXuniqueXXsolutionXXlemma}{\UseVerbatim{HOLMultivariateTheoremsstrongXXuniqueXXsolutionXXlemma}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractions}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es}.
       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLConst{weakly_guarded} \HOLBoundVar{Xs}) \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{Qs}.
           \HOLBoundVar{Ps} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLSymConst{\HOLTokenConj{}}
           \HOLBoundVar{Qs} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLSymConst{\HOLTokenImp{}}
           \HOLConst{WEAK_EQUIV} \HOLBoundVar{Ps} \HOLBoundVar{Qs}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractions}{\UseVerbatim{HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractions}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractionsXXlemma}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{Qs}.
       (\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{Es}.
            \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLConst{weakly_guarded} \HOLBoundVar{Xs}) \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
            \HOLBoundVar{Ps} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLSymConst{\HOLTokenConj{}}
            \HOLBoundVar{Qs} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts}) \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{C}.
           \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenImp{}}
           (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{R}.
                \HOLConst{CCS_Subst} \HOLBoundVar{C} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenImp{} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
                    \HOLBoundVar{R} \HOLConst{contracts} \HOLConst{CCS_Subst} \HOLBoundVar{C\sp{\prime}} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{\HOLTokenConj{}}
                    (\HOLConst{WEAK_EQUIV} \HOLConst{O} (\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}. \HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenImp{} \HOLBoundVar{y}))
                      (\HOLConst{CCS_Subst} \HOLBoundVar{C} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}))
                      (\HOLConst{CCS_Subst} \HOLBoundVar{C\sp{\prime}} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}))) \HOLSymConst{\HOLTokenConj{}}
           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}.
               \HOLConst{CCS_Subst} \HOLBoundVar{C} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLTokenWeakTransBegin\HOLConst{\ensuremath{\tau}}\HOLTokenImp{} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
               \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
                   \HOLBoundVar{R} \HOLConst{contracts} \HOLConst{CCS_Subst} \HOLBoundVar{C\sp{\prime}} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{\HOLTokenConj{}}
                   (\HOLConst{WEAK_EQUIV} \HOLConst{O} \HOLConst{EPS}) (\HOLConst{CCS_Subst} \HOLBoundVar{C} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}))
                     (\HOLConst{CCS_Subst} \HOLBoundVar{C\sp{\prime}} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}))
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractionsXXlemma}{\UseVerbatim{HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractionsXXlemma}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsuniqueXXsolutionXXofXXrootedXXcontractions}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es}.
       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLConst{weakly_guarded} \HOLBoundVar{Xs}) \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{Qs}.
           \HOLBoundVar{Ps} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLSymConst{\HOLTokenConj{}}
           \HOLBoundVar{Qs} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLSymConst{\HOLTokenImp{}}
           \HOLConst{OBS_CONGR} \HOLBoundVar{Ps} \HOLBoundVar{Qs}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsuniqueXXsolutionXXofXXrootedXXcontractions}{\UseVerbatim{HOLMultivariateTheoremsuniqueXXsolutionXXofXXrootedXXcontractions}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXimpXXcontext}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}. \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXimpXXcontext}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXimpXXcontext}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXpar}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}}
       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXpar}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXpar}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXprefix}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}. \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXprefix}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXprefix}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrec}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrec}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrec}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrelab}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrelab}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrelab}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrestr}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}. \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrestr}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrestr}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXsum}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}}
       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXsum}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXsum}}
\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXvar}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y}. \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{var} \HOLBoundVar{Y}) \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs}
\end{SaveVerbatim}
\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXvar}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXvar}}
\newcommand{\HOLMultivariateTheorems}{
\HOLThmTag{Multivariate}{ALOOKUP_fromList}\HOLMultivariateTheoremsALOOKUPXXfromList
\HOLThmTag{Multivariate}{CCS_Subst_alt}\HOLMultivariateTheoremsCCSXXSubstXXalt
\HOLThmTag{Multivariate}{CCS_SUBST_ELIM}\HOLMultivariateTheoremsCCSXXSUBSTXXELIM
\HOLThmTag{Multivariate}{context_par}\HOLMultivariateTheoremscontextXXpar
\HOLThmTag{Multivariate}{context_par_rule}\HOLMultivariateTheoremscontextXXparXXrule
\HOLThmTag{Multivariate}{context_prefix}\HOLMultivariateTheoremscontextXXprefix
\HOLThmTag{Multivariate}{context_prefix_rule}\HOLMultivariateTheoremscontextXXprefixXXrule
\HOLThmTag{Multivariate}{context_rec}\HOLMultivariateTheoremscontextXXrec
\HOLThmTag{Multivariate}{context_relab}\HOLMultivariateTheoremscontextXXrelab
\HOLThmTag{Multivariate}{context_relab_rule}\HOLMultivariateTheoremscontextXXrelabXXrule
\HOLThmTag{Multivariate}{context_restr}\HOLMultivariateTheoremscontextXXrestr
\HOLThmTag{Multivariate}{context_restr_rule}\HOLMultivariateTheoremscontextXXrestrXXrule
\HOLThmTag{Multivariate}{EVERY_weakly_guarded}\HOLMultivariateTheoremsEVERYXXweaklyXXguarded
\HOLThmTag{Multivariate}{IN_fromList}\HOLMultivariateTheoremsINXXfromList
\HOLThmTag{Multivariate}{strong_unique_solution}\HOLMultivariateTheoremsstrongXXuniqueXXsolution
\HOLThmTag{Multivariate}{strong_unique_solution_lemma}\HOLMultivariateTheoremsstrongXXuniqueXXsolutionXXlemma
\HOLThmTag{Multivariate}{unique_solution_of_obs_contractions}\HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractions
\HOLThmTag{Multivariate}{unique_solution_of_obs_contractions_lemma}\HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractionsXXlemma
\HOLThmTag{Multivariate}{unique_solution_of_rooted_contractions}\HOLMultivariateTheoremsuniqueXXsolutionXXofXXrootedXXcontractions
\HOLThmTag{Multivariate}{weakly_guarded_imp_context}\HOLMultivariateTheoremsweaklyXXguardedXXimpXXcontext
\HOLThmTag{Multivariate}{weakly_guarded_par}\HOLMultivariateTheoremsweaklyXXguardedXXpar
\HOLThmTag{Multivariate}{weakly_guarded_prefix}\HOLMultivariateTheoremsweaklyXXguardedXXprefix
\HOLThmTag{Multivariate}{weakly_guarded_rec}\HOLMultivariateTheoremsweaklyXXguardedXXrec
\HOLThmTag{Multivariate}{weakly_guarded_relab}\HOLMultivariateTheoremsweaklyXXguardedXXrelab
\HOLThmTag{Multivariate}{weakly_guarded_restr}\HOLMultivariateTheoremsweaklyXXguardedXXrestr
\HOLThmTag{Multivariate}{weakly_guarded_sum}\HOLMultivariateTheoremsweaklyXXguardedXXsum
\HOLThmTag{Multivariate}{weakly_guarded_var}\HOLMultivariateTheoremsweaklyXXguardedXXvar
}

### 2019-09-03 ic-journal/coarsest.tex
Updated all generated files

@@
 \begin{alltt}
-\HOLConst{WEAK_CONGR} \HOLSymConst{=} \HOLConst{CC} \HOLConst{WEAK_EQUIV}\hfill{[WEAK_CONGR]}
-\HOLConst{CC} \HOLFreeVar{R} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}.
+\HOLConst{WEAK_CONGR} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{CC} \HOLConst{WEAK_EQUIV}\hfill{[WEAK_CONGR]}
+\HOLConst{CC} \HOLFreeVar{R} \HOLSymConst{\HOLTokenDefEquality{}} (\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}.
 \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}.
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R} \HOLBoundVar{R\sp{\prime}}.
-\HOLConst{precongruence} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLConst{CC} \HOLBoundVar{R}\hfill{[CC_is_coarsest']}
+\HOLConst{precongruence} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLConst{CC} \HOLBoundVar{R}\hfill{[PCC_is_coarsest]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{SUM_EQUIV} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}.
+\HOLConst{SUM_EQUIV} \HOLSymConst{\HOLTokenDefEquality{}} (\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}.
 \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
@@
 % \begin{alltt}
-% \HOLConst{WEAK_CONGR} \HOLSymConst{=} \HOLConst{CC} \HOLConst{WEAK_EQUIV}
+% \HOLConst{WEAK_CONGR} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{CC} \HOLConst{WEAK_EQUIV}
 % \end{alltt}
@@
 % \begin{alltt}
-% \HOLConst{SUM_EQUIV} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}.
+% \HOLConst{SUM_EQUIV} \HOLSymConst{\HOLTokenDefEquality{}} (\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}.
 \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
@@
 \begin{alltt}
-\HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{a}.
+\HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{a}.
 \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}}.
-\HOLSymConst{\HOLTokenNeg{}}(\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{a}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}})\hfill{[free_action_def]}
+\HOLSymConst{\HOLTokenNeg{}}(\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{a}\HOLTokenImp{} \HOLBoundVar{p\sp{\prime}})\hfill{[free_action_def]}
 \end{alltt}
@@
         \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}} \HOLBoundVar{u}.
-\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenConj{}}
+\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenImp{} \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenConj{}}
         \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{q\sp{\prime}} \HOLBoundVar{u}.
-\HOLFreeVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenImp{}}
+\HOLFreeVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenImp{} \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenImp{}}
    (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
@@
 \begin{alltt}
-\HOLConst{STABLE} \HOLFreeVar{p} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{p\sp{\prime}}.
+\HOLConst{STABLE} \HOLFreeVar{p} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{p\sp{\prime}}.
 \HOLFreeVar{p} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{u} \HOLSymConst{\HOLTokenNotEqual{}} \HOLSymConst{\ensuremath{\tau}}\hfill{[STABLE]}
@@
 \begin{alltt}
-\HOLConst{KLOP} \HOLFreeVar{a} \HOLNumLit{0} \HOLSymConst{=} \HOLConst{nil}
-\HOLConst{KLOP} \HOLFreeVar{a} (\HOLConst{SUC} \HOLFreeVar{n}) \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLSymConst{\ensuremath{+}} \HOLConst{label} \HOLFreeVar{a}\HOLSymConst{..}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\hfill{[KLOP_def]}
+\HOLConst{KLOP} \HOLFreeVar{a} \HOLNumLit{0} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{nil}
+\HOLConst{KLOP} \HOLFreeVar{a} (\HOLConst{SUC} \HOLFreeVar{n}) \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLSymConst{\ensuremath{+}} \HOLConst{label} \HOLFreeVar{a}\HOLSymConst{..}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\hfill{[KLOP_def]}
 \end{alltt}
@@
 \HOLTokenTurnstile{} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{a}\HOLTokenTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{m}.
-\HOLBoundVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLBoundVar{m})\hfill{[KLOP_PROP1]}
+\HOLBoundVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLBoundVar{m}\hfill{[KLOP_PROP1]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLTokenWeakTransBegin\HOLConst{label} \HOLFreeVar{a}\HOLTokenWeakTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{m}.
-\HOLBoundVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{E} \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLBoundVar{m})\hfill{[KLOP_PROP1']}
+\HOLTokenTurnstile{} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLTokenWeakTransBegin\HOLConst{label} \HOLFreeVar{a}\HOLTokenImp{} \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{m}.
+\HOLBoundVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLBoundVar{m}\hfill{[KLOP_PROP1']}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{Reach} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
+\HOLConst{Reach} \HOLSymConst{\HOLTokenDefEquality{}} (\HOLTokenLambda{}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
 \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{u}.
@@
 \begin{alltt}
-\HOLConst{NODES} \HOLFreeVar{p} \HOLSymConst{=} \HOLTokenLeftbrace{}\HOLBoundVar{q} \HOLTokenBar{} \HOLConst{Reach} \HOLFreeVar{p} \HOLBoundVar{q}\HOLTokenRightbrace{}\hfill[NODES_def]
+\HOLConst{NODES} \HOLFreeVar{p} \HOLSymConst{\HOLTokenDefEquality{}} \HOLTokenLeftbrace{}\HOLBoundVar{q} \HOLTokenBar{} \HOLConst{Reach} \HOLFreeVar{p} \HOLBoundVar{q}\HOLTokenRightbrace{}\hfill[NODES_def]
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{FINITE} (\HOLConst{NODES} \HOLFreeVar{p})\hfill[finite_state_def]
+\HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{FINITE} (\HOLConst{NODES} \HOLFreeVar{p})\hfill[finite_state_def]
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{q} \HOLSymConst{\HOLTokenIn{}} \HOLConst{NODES} \HOLFreeVar{p}\hfill[WEAK_TRANS_IN_NODES]
+\HOLTokenTurnstile{} \HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenImp{} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{q} \HOLSymConst{\HOLTokenIn{}} \HOLConst{NODES} \HOLFreeVar{p}\hfill[WEAK_TRANS_IN_NODES]
 \end{alltt}
@@
            \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}} \HOLBoundVar{u}.
-\HOLBoundVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenConj{}}
+\HOLBoundVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenImp{} \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenConj{}}
            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{q\sp{\prime}} \HOLBoundVar{u}.
-\HOLBoundVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})\hfill{[KLOP_LEMMA_FINITE]}
+\HOLBoundVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenImp{} \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})\hfill{[KLOP_LEMMA_FINITE]}
 \end{alltt}

### 2019-09-03 ic-journal/conclusions.tex
Final fixes
Updated all generated files

@@
 
-For the future work, it would be worth extending
-to multi-variable equations/contractions. A key aspect could be using unguarded constants as free variables
-(\texttt{FV}) and defining guardedness directly on expressions of type CCS (instead of
-CCS $\rightarrow$ CCS), then linking to contexts. For instance, an expression is weakly-guarded when each
-of its free variables, replaced by a hole, results in a weakly-guarded context:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{weakly_guarded1} \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X}.
-\HOLBoundVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e}.
-\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{e} (\HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{=} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \HOLBoundVar{e}
-\end{alltt}
-
 Formalising other equivalences and preorders could also be considered,

### 2019-09-03 ic-journal/context.tex
Updated all generated files

@@
 \begin{alltt}
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[CONTEXT_rules]}
+\HOLTokenTurnstile{} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{t}) \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
+\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{p})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
+\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
+\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLSymConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLBoundVar{e} \HOLBoundVar{t}))) \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
+\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})\hfill{[CONTEXT_rules]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[WG_rules]}
+\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
+\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{p})) \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
+\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
+\HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLSymConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLBoundVar{e} \HOLBoundVar{t}))) \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
+\HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})\hfill{[WG_rules]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{label} \HOLFreeVar{l}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{SG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{SG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{SG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[SG_rules]}
+\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{e}.
+\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{label} \HOLBoundVar{l}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
+\HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
+\HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLSymConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLBoundVar{e} \HOLBoundVar{t}))) \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
+\HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})\hfill{[SG_rules]}
 \end{alltt}
@@
  \begin{alltt}
-\HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
-\HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{SEQ} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{SEQ} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})\hfill{[SEQ_rules]}
+\HOLTokenTurnstile{} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{t}) \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
+\HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{p})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
+\HOLConst{SEQ} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{SEQ} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})\hfill{[SEQ_rules]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
-\HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{a\sb{\mathrm{1}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{a\sb{\mathrm{2}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[GCONTEXT_rules]}
+\HOLTokenTurnstile{} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{t}) \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
+\HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{p})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
+\HOLConst{GCONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a\sb{\mathrm{1}}} \HOLBoundVar{a\sb{\mathrm{2}}} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+        \HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
+        \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a\sb{\mathrm{1}}}\HOLSymConst{..}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{a\sb{\mathrm{2}}}\HOLSymConst{..}\HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+        \HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
+\HOLConst{GCONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLSymConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLBoundVar{e} \HOLBoundVar{t}))) \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
+\HOLConst{GCONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})\hfill{[GCONTEXT_rules]}
 \end{alltt}
 \begin{alltt}
-\HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{a\sb{\mathrm{1}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{a\sb{\mathrm{2}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WGS} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WGS} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{WGS} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[WGS_rules]}
+\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
+\HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{p})) \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
+\HOLConst{GCONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{..}\HOLBoundVar{e} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a\sb{\mathrm{1}}} \HOLBoundVar{a\sb{\mathrm{2}}} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+        \HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
+        \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a\sb{\mathrm{1}}}\HOLSymConst{..}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{a\sb{\mathrm{2}}}\HOLSymConst{..}\HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{WGS} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
+\HOLConst{WGS} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLSymConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLBoundVar{e} \HOLBoundVar{t}))) \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
+\HOLConst{WGS} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} (\HOLBoundVar{e} \HOLBoundVar{t}) \HOLBoundVar{rf})\hfill{[WGS_rules]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
+\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenDefEquality{}}
   \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}}
@@
 \begin{alltt}
-\HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
-\HOLConst{PreOrder} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
+\HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenDefEquality{}}
+  \HOLConst{PreOrder} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}}
+  \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
 \HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})

### 2019-09-03 ic-journal/part2.tex
Final fixes
Updated all generated files

@@
        \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sp{\prime}}.
-\HOLConst{CONTEXT} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{P}) \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLConst{CONTEXT} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
 \HOLFreeVar{E} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{Q}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLBoundVar{Q}\hfill{[STRONG_UNIQUE_SOLUTION]}
+\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{Q}\hfill{[STRONG_UNIQUE_SOLUTION]}
 \end{alltt}
@@
        \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}.
-           \HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} ((\HOLBoundVar{a} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}) \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{H} \HOLBoundVar{P}) \HOLSymConst{\HOLTokenConj{}}
+           \HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{a} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}) \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}}
            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
@@
 \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLBoundVar{E\sp{\prime}} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
+\HOLBoundVar{E\sp{\prime}} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenImp{} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
             \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
 \HOLBoundVar{E\sp{\prime}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}}
+\HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenImp{} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}}
        \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{E\sp{\prime}}\hfill{[OBS_CONGR_BY_WEAK_BISIM]}
@@
        \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}.
-           \HOLConst{SEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} ((\HOLBoundVar{a} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}) \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{H} \HOLBoundVar{P}) \HOLSymConst{\HOLTokenConj{}}
-           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLConst{SEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{a} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}) \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
 \HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}\hfill{[OBS_UNIQUE_SOLUTION_LEMMA]}
@@
 \begin{alltt}
-\HOLConst{LRTC} \HOLFreeVar{R} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b} \HOLSymConst{\HOLTokenEquiv{}}
+\HOLConst{LRTC} \HOLFreeVar{R} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b} \HOLSymConst{\HOLTokenDefEquality{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.
@@
 \begin{alltt}
-\HOLConst{TRACE} \HOLSymConst{=} \HOLConst{LRTC} \HOLConst{TRANS}\hfill{[TRACE_def]}
+\HOLConst{TRACE} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{LRTC} \HOLConst{TRANS}\hfill{[TRACE_def]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{NO_LABEL} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
+\HOLConst{NO_LABEL} \HOLFreeVar{L} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
 \HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLFreeVar{L}\hfill{[NO_LABEL_def]}
@@
 \begin{alltt}
-\HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}}
+\HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLSymConst{\HOLTokenDefEquality{}}
   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{L\sb{\mathrm{1}}} \HOLBoundVar{L\sb{\mathrm{2}}}.
-(\HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} [\HOLFreeVar{u}] \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{=} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{2}}}\hfill{[UNIQUE_LABEL_def]}
+\HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} [\HOLFreeVar{u}] \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{=} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{2}}}\hfill{[UNIQUE_LABEL_def]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenImp{} \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}}
    \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{acts}.
@@
        (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{R}.
-            \HOLBoundVar{C} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
+            \HOLBoundVar{C} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenImp{} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
             \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
@@
                 (\HOLConst{WEAK_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} (\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}.
-\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{y})) (\HOLBoundVar{C} \HOLFreeVar{Q})
+\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenImp{} \HOLBoundVar{y})) (\HOLBoundVar{C} \HOLFreeVar{Q})
                   (\HOLBoundVar{C\sp{\prime}} \HOLFreeVar{Q})) \HOLSymConst{\HOLTokenConj{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}.
-           \HOLBoundVar{C} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
+           \HOLBoundVar{C} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenImp{} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
            \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
@@
    \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-       \HOLConst{GCONTEXT} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{C\sp{\prime}} \HOLFreeVar{P}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{GCONTEXT} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{C\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
@@
 \begin{alltt}
-\hfill{[UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS]}
 \HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
 \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
+\hfill{[UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS]}
 \end{alltt}

### 2019-09-03 ic-journal/sos.tex
Updated all generated files

@@
 restriction & $(\nu\;L)\;P$ & \texttt{restr L P} & \HOLinline{\HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{P}}  \\
-recursion & $\recu A P$ & \texttt{rec A P} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P}}  \\
+recursion & $\recu A P$ & \texttt{rec A P} & \HOLinline{\HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{A} \HOLFreeVar{P}}  \\
 relabeling & $P\;[r\!f]$ & \texttt{relab P rf} & \HOLinline{\HOLConst{relab} \HOLFreeVar{P} \HOLFreeVar{rf}}  \\
@@
 \HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLTokenTransBegin\HOLConst{label} (\HOLConst{COMPL} \HOLFreeVar{l})\HOLTokenTransEnd \HOLFreeVar{Q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q\sp{\prime}}\hfill\texttt{[PAR3]}
-\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{Q} \HOLSymConst{\HOLTokenConj{}} ((\HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}}) \HOLSymConst{\HOLTokenDisj{}} (\HOLFreeVar{u} \HOLSymConst{=} \HOLConst{label} \HOLFreeVar{l}) \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenImp{}}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{Q} \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{=} \HOLConst{label} \HOLFreeVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenImp{}}
    \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{Q}\hfill\texttt{[RESTR]}
 \HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLConst{relab} \HOLFreeVar{P} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{Q} \HOLFreeVar{rf}\hfill\texttt{[RELABELING]}
-\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{P} (\HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P}) \HOLFreeVar{A} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[REC]}
+\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{P} (\HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{A} \HOLFreeVar{P}) \HOLFreeVar{A} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{A} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[REC]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{CCS_Subst} \HOLConst{nil} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{=} \HOLConst{nil}
-\HOLConst{CCS_Subst} (\HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{E}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{=} \HOLFreeVar{u}\HOLSymConst{..}\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
-\HOLConst{CCS_Subst} (\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E\sb{\mathrm{2}}}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{=}
+\HOLConst{CCS_Subst} \HOLConst{nil} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{nil}
+\HOLConst{CCS_Subst} (\HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{E}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLFreeVar{u}\HOLSymConst{..}\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
+\HOLConst{CCS_Subst} (\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E\sb{\mathrm{2}}}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}}
   \HOLConst{CCS_Subst} \HOLFreeVar{E\sb{\mathrm{1}}} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_Subst} \HOLFreeVar{E\sb{\mathrm{2}}} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
-\HOLConst{CCS_Subst} (\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sb{\mathrm{2}}}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{=}
+\HOLConst{CCS_Subst} (\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sb{\mathrm{2}}}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}}
   \HOLConst{CCS_Subst} \HOLFreeVar{E\sb{\mathrm{1}}} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{CCS_Subst} \HOLFreeVar{E\sb{\mathrm{2}}} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
-\HOLConst{CCS_Subst} (\HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{E}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{=} \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X})
-\HOLConst{CCS_Subst} (\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{f}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{=} \HOLConst{relab} (\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}) \HOLFreeVar{f}
-\HOLConst{CCS_Subst} (\HOLConst{var} \HOLFreeVar{Y}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{=} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E\sp{\prime}} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}
-\HOLConst{CCS_Subst} (\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{=}
-\HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} (\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X})\hfill{[CCS_Subst_def]}
+\HOLConst{CCS_Subst} (\HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{E}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X})
+\HOLConst{CCS_Subst} (\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{f}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{relab} (\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}) \HOLFreeVar{f}
+\HOLConst{CCS_Subst} (\HOLConst{var} \HOLFreeVar{Y}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E\sp{\prime}} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}
+\HOLConst{CCS_Subst} (\HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{Y} \HOLFreeVar{E}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}}
+  \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{Y} (\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X})\hfill{[CCS_Subst_def]}
 \end{alltt}
@@
        \HOLConst{In} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}}
-       ((\HOLBoundVar{u} \HOLSymConst{=} \HOLConst{In} \HOLStringLit{a}) \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{E} \HOLSymConst{=} \HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil}) \HOLSymConst{\HOLTokenDisj{}}
-        (\HOLBoundVar{u} \HOLSymConst{=} \HOLConst{Out} \HOLStringLit{a}) \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{E} \HOLSymConst{=} \HOLConst{In} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil})) \HOLSymConst{\HOLTokenDisj{}}
-       (\HOLBoundVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}}) \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{E} \HOLSymConst{=} \HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil})\hfill{[Example.ex_A]}
+       (\HOLBoundVar{u} \HOLSymConst{=} \HOLConst{In} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLSymConst{\HOLTokenDisj{}}
+        \HOLBoundVar{u} \HOLSymConst{=} \HOLConst{Out} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{In} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil}) \HOLSymConst{\HOLTokenDisj{}}
+       \HOLBoundVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil}\hfill{[Example.ex_A]}
 \end{alltt}

### 2019-09-03 paper/HOLMultivariate.tex
Updated all generated files

@@
-\newcommand{\HOLMultivariateDate}{20 Agosto 2019}
-\newcommand{\HOLMultivariateTime}{13:05}
+\newcommand{\HOLMultivariateDate}{03 Settembre 2019}
+\newcommand{\HOLMultivariateTime}{10:42}
 \begin{SaveVerbatim}{HOLMultivariateDefinitionsCCSXXequationXXdef}
@@
        \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{E}. \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs}) \HOLBoundVar{Es}
+       \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{FV} \HOLBoundVar{e} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs}) \HOLBoundVar{Es}
 \end{SaveVerbatim}
@@
        \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{R} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenEquiv{}}
+       \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}.
+\HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{e}) (\HOLConst{set} \HOLBoundVar{Xs})) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
        \HOLConst{LIST_REL} \HOLBoundVar{R} \HOLBoundVar{Ps} (\HOLConst{MAP} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps})) \HOLBoundVar{Es})
@@
 \begin{SaveVerbatim}{HOLMultivariateDefinitionsCCSXXSUBSTXXdef}
-\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map}. \HOLConst{CCS_Subst} \HOLConst{nil} \HOLBoundVar{map} \HOLSymConst{=} \HOLConst{nil}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{u} \HOLBoundVar{E}.
-\HOLConst{CCS_Subst} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLBoundVar{map} \HOLSymConst{=} \HOLBoundVar{u}\HOLSymConst{..}\HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{map}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{CCS_Subst} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLBoundVar{map} \HOLSymConst{=}
-        \HOLConst{CCS_Subst} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{map} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_Subst} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLBoundVar{map}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{CCS_Subst} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLBoundVar{map} \HOLSymConst{=}
-        \HOLConst{CCS_Subst} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{map} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{CCS_Subst} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLBoundVar{map}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{L} \HOLBoundVar{E}.
-\HOLConst{CCS_Subst} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLBoundVar{map} \HOLSymConst{=} \HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{map})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{E} \HOLBoundVar{rf}.
-        \HOLConst{CCS_Subst} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLBoundVar{map} \HOLSymConst{=} \HOLConst{relab} (\HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{map}) \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{X}.
-        \HOLConst{CCS_Subst} (\HOLConst{var} \HOLBoundVar{X}) \HOLBoundVar{map} \HOLSymConst{=}
-        \HOLKeyword{if} \HOLConst{MEM} \HOLBoundVar{X} (\HOLConst{MAP} \HOLConst{FST} \HOLBoundVar{map}) \HOLKeyword{then} \HOLConst{THE} (\HOLConst{ALOOKUP} \HOLBoundVar{map} \HOLBoundVar{X})
-        \HOLKeyword{else} \HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{\HOLTokenConj{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{map} \HOLBoundVar{X} \HOLBoundVar{E}.
-       \HOLConst{CCS_Subst} (\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLBoundVar{map} \HOLSymConst{=}
-       \HOLKeyword{if} \HOLConst{MEM} \HOLBoundVar{X} (\HOLConst{MAP} \HOLConst{FST} \HOLBoundVar{map}) \HOLKeyword{then} \HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}
-       \HOLKeyword{else} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{map})
+\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLConst{nil} \HOLSymConst{=} \HOLConst{nil}) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{u} \HOLBoundVar{E}.
+\HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{=} \HOLBoundVar{u}\HOLSymConst{..}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{=}
+        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{=}
+        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{L} \HOLBoundVar{E}.
+\HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{=} \HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E} \HOLBoundVar{rf}.
+        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{=} \HOLConst{relab} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}) \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{X}.
+        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{=}
+        \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLBoundVar{fm} \HOLConst{'} \HOLBoundVar{X} \HOLKeyword{else} \HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{X} \HOLBoundVar{E}.
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLSymConst{=}
+       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\HOLTokenBackslash{}\HOLTokenBackslash{}} \HOLBoundVar{X}) \HOLBoundVar{E})
+       \HOLKeyword{else} \HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps}.
-(\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{=} \HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})
+(\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{=} \HOLConst{FEMPTY} \HOLSymConst{|++} \HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})
 \end{SaveVerbatim}
@@
 }
-\begin{SaveVerbatim}{HOLMultivariateTheoremsALOOKUPXXfromList}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{n}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{n} \HOLSymConst{\HOLTokenLt{}} \HOLConst{LENGTH} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}}
-       (\HOLConst{THE} (\HOLConst{ALOOKUP} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) (\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs})) \HOLSymConst{=} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps})
+\begin{SaveVerbatim}{HOLMultivariateTheoremsBVXXSUBSETXXBIGUNION}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{BV} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}}
+       \HOLConst{BV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{BV} (\HOLConst{set} \HOLBoundVar{Ps}))
 \end{SaveVerbatim}
-\newcommand{\HOLMultivariateTheoremsALOOKUPXXfromList}{\UseVerbatim{HOLMultivariateTheoremsALOOKUPXXfromList}}
-\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSubstXXalt}
+\newcommand{\HOLMultivariateTheoremsBVXXSUBSETXXBIGUNION}{\UseVerbatim{HOLMultivariateTheoremsBVXXSUBSETXXBIGUNION}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXsolutionXXlength}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{R} \HOLBoundVar{Ps}.
+       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{R} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenImp{}}
+       (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXsolutionXXlength}{\UseVerbatim{HOLMultivariateTheoremsCCSXXsolutionXXlength}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXelim}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
+       \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXelim}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXelim}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXelimYY}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{fm}.
+\HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{FDOM} \HOLBoundVar{fm}) \HOLSymConst{\HOLTokenImp{}} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXelimYY}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXelimYY}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXFEMPTY}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}. \HOLConst{CCS_SUBST} \HOLConst{FEMPTY} \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXFEMPTY}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXFEMPTY}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXFOLDR}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{EVERY} (\HOLTokenLambda{}(\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{p}).
+\HOLConst{FV} \HOLBoundVar{p} \HOLConst{\HOLTokenSubset{}} \HOLTokenLeftbrace{}\HOLBoundVar{x}\HOLTokenRightbrace{}) (\HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLSymConst{=}
+        \HOLConst{FOLDR} (\HOLTokenLambda{}(\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}) \HOLBoundVar{e}.
+\HOLConst{CCS_Subst} \HOLBoundVar{e} \HOLBoundVar{y} \HOLBoundVar{x}) \HOLBoundVar{E} (\HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})))
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXFOLDR}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXFOLDR}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXISXXPROC}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{IS_PROC} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXISXXPROC}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXISXXPROC}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXnested}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{Es} \HOLBoundVar{C}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{C}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Es}) \HOLBoundVar{C}) \HOLSymConst{=}
+        \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLConst{MAP} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps})) \HOLBoundVar{Es}) \HOLBoundVar{C})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXnested}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXnested}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXnil}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLConst{nil} \HOLSymConst{=} \HOLConst{nil}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXnil}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXnil}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXpar}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{=}
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXpar}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXpar}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXprefix}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{u} \HOLBoundVar{E}.
+\HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{=} \HOLBoundVar{u}\HOLSymConst{..}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXprefix}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXprefix}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXPROC}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{P}.
+       (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{P}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{IS_PROC} \HOLBoundVar{P} \HOLSymConst{\HOLTokenImp{}}
+       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{P} \HOLSymConst{=} \HOLBoundVar{P})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXPROC}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXPROC}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXrec}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{X} \HOLBoundVar{E}.
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLSymConst{=}
+       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\HOLTokenBackslash{}\HOLTokenBackslash{}} \HOLBoundVar{X}) \HOLBoundVar{E})
+       \HOLKeyword{else} \HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXrec}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXrec}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXreduce}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{Xs} \HOLBoundVar{P} \HOLBoundVar{Ps}.
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLBoundVar{X} \HOLConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLBoundVar{e}) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
+           \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs})) \HOLSymConst{\HOLTokenConj{}}
+           (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E\sp{\prime}}) \HOLSymConst{\HOLTokenImp{}}
+           (\HOLConst{CCS_SUBST} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{CCS_Subst} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{P} \HOLBoundVar{X})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXreduce}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXreduce}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXrelab}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E} \HOLBoundVar{rf}.
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{=} \HOLConst{relab} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}) \HOLBoundVar{rf}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXrelab}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXrelab}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXrestr}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{L} \HOLBoundVar{E}.
+\HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{=} \HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXrestr}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXrestr}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXself}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{Xs}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLConst{MAP} \HOLConst{var} \HOLBoundVar{Xs}) \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXself}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXself}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXSING}
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-\HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{X} \HOLSymConst{=} \HOLConst{CCS_Subst} \HOLBoundVar{E} [(\HOLBoundVar{X}\HOLSymConst{,}\HOLBoundVar{E\sp{\prime}})]
+\HOLConst{CCS_SUBST} (\HOLConst{FEMPTY} \HOLSymConst{|+} (\HOLBoundVar{X}\HOLSymConst{,}\HOLBoundVar{E\sp{\prime}})) \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{X}
 \end{SaveVerbatim}
-\newcommand{\HOLMultivariateTheoremsCCSXXSubstXXalt}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSubstXXalt}}
-\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXELIM}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}.
-       \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps}.
-           (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}} (\HOLConst{CCS_Subst} \HOLBoundVar{E} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{=} \HOLBoundVar{E})
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXSING}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXSING}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXsum}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{=}
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}
 \end{SaveVerbatim}
-\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXELIM}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXELIM}}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXsum}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXsum}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXvar}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{X}.
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{=}
+       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLBoundVar{fm} \HOLConst{'} \HOLBoundVar{X} \HOLKeyword{else} \HOLConst{var} \HOLBoundVar{X}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXvar}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXvar}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXbackwardXXrules}
+\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
+\HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
+\HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
+\HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
+       \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremscontextXXbackwardXXrules}{\UseVerbatim{HOLMultivariateTheoremscontextXXbackwardXXrules}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXcombin}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{C}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLConst{context} \HOLBoundVar{Xs}) \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Es}) \HOLBoundVar{C})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremscontextXXcombin}{\UseVerbatim{HOLMultivariateTheoremscontextXXcombin}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXnil}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}. \HOLConst{context} \HOLBoundVar{Xs} \HOLConst{nil}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremscontextXXnil}{\UseVerbatim{HOLMultivariateTheoremscontextXXnil}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXpar}
@@
 \newcommand{\HOLMultivariateTheoremscontextXXpar}{\UseVerbatim{HOLMultivariateTheoremscontextXXpar}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXparXXrewrite}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+       \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremscontextXXparXXrewrite}{\UseVerbatim{HOLMultivariateTheoremscontextXXparXXrewrite}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXparXXrule}
@@
 \newcommand{\HOLMultivariateTheoremscontextXXprefix}{\UseVerbatim{HOLMultivariateTheoremscontextXXprefix}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXprefixXXrewrite}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
+\HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremscontextXXprefixXXrewrite}{\UseVerbatim{HOLMultivariateTheoremscontextXXprefixXXrewrite}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXprefixXXrule}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
+       \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs})
 \end{SaveVerbatim}
@@
 \newcommand{\HOLMultivariateTheoremscontextXXrelab}{\UseVerbatim{HOLMultivariateTheoremscontextXXrelab}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrelabXXrewrite}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
+\HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremscontextXXrelabXXrewrite}{\UseVerbatim{HOLMultivariateTheoremscontextXXrelabXXrewrite}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrelabXXrule}
@@
 \newcommand{\HOLMultivariateTheoremscontextXXrestr}{\UseVerbatim{HOLMultivariateTheoremscontextXXrestr}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrestrXXrewrite}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
+\HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremscontextXXrestrXXrewrite}{\UseVerbatim{HOLMultivariateTheoremscontextXXrestrXXrewrite}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrestrXXrule}
@@
 \newcommand{\HOLMultivariateTheoremscontextXXrestrXXrule}{\UseVerbatim{HOLMultivariateTheoremscontextXXrestrXXrule}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrules}
+\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}.
+\HOLConst{context} \HOLBoundVar{Xs} \HOLConst{nil}) \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y}.
+\HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{var} \HOLBoundVar{Y})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E})) \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremscontextXXrules}{\UseVerbatim{HOLMultivariateTheoremscontextXXrules}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXsum}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+       \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremscontextXXsum}{\UseVerbatim{HOLMultivariateTheoremscontextXXsum}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXsumXXrewrite}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+       \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremscontextXXsumXXrewrite}{\UseVerbatim{HOLMultivariateTheoremscontextXXsumXXrewrite}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXsumXXrule}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremscontextXXsumXXrule}{\UseVerbatim{HOLMultivariateTheoremscontextXXsumXXrule}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXvar}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y}. \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{var} \HOLBoundVar{Y})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremscontextXXvar}{\UseVerbatim{HOLMultivariateTheoremscontextXXvar}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsDISJOINTXXBVXXCCSXXSUBST}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{e}) (\HOLConst{set} \HOLBoundVar{Xs})) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{DISJOINT} (\HOLConst{BV} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E})) (\HOLConst{set} \HOLBoundVar{Xs})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsDISJOINTXXBVXXCCSXXSUBST}{\UseVerbatim{HOLMultivariateTheoremsDISJOINTXXBVXXCCSXXSUBST}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsdisjointXXimpXXcontext}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}.
+       \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsdisjointXXimpXXcontext}{\UseVerbatim{HOLMultivariateTheoremsdisjointXXimpXXcontext}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsdisjointXXimpXXweaklyXXguarded}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}.
+       \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsdisjointXXimpXXweaklyXXguarded}{\UseVerbatim{HOLMultivariateTheoremsdisjointXXimpXXweaklyXXguarded}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsEVERYXXweaklyXXguarded}
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es}.
-       \HOLConst{EVERY} (\HOLConst{weakly_guarded} \HOLBoundVar{Xs}) \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{X}.
@@
 \newcommand{\HOLMultivariateTheoremsEVERYXXweaklyXXguarded}{\UseVerbatim{HOLMultivariateTheoremsEVERYXXweaklyXXguarded}}
-\begin{SaveVerbatim}{HOLMultivariateTheoremsINXXfromList}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{Xs} \HOLBoundVar{Ps}.
-       (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       (\HOLConst{MEM} \HOLBoundVar{X} (\HOLConst{MAP} \HOLConst{FST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps})) \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs})
+\begin{SaveVerbatim}{HOLMultivariateTheoremsFDOMXXfromList}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps}.
+(\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}} (\HOLConst{FDOM} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{=} \HOLConst{set} \HOLBoundVar{Xs})
 \end{SaveVerbatim}
-\newcommand{\HOLMultivariateTheoremsINXXfromList}{\UseVerbatim{HOLMultivariateTheoremsINXXfromList}}
+\newcommand{\HOLMultivariateTheoremsFDOMXXfromList}{\UseVerbatim{HOLMultivariateTheoremsFDOMXXfromList}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsfromListXXEMPTY}
+\HOLTokenTurnstile{} ([] \HOLSymConst{\HOLTokenMapto{}} []) \HOLSymConst{=} \HOLConst{FEMPTY}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsfromListXXEMPTY}{\UseVerbatim{HOLMultivariateTheoremsfromListXXEMPTY}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsfromListXXFAPPLYXXEL}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{n}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{n} \HOLSymConst{\HOLTokenLt{}} \HOLConst{LENGTH} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}}
+       ((\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLConst{'} (\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs}) \HOLSymConst{=} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsfromListXXFAPPLYXXEL}{\UseVerbatim{HOLMultivariateTheoremsfromListXXFAPPLYXXEL}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsfromListXXFAPPLYXXELYY}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{P} \HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{n}.
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLBoundVar{n} \HOLSymConst{\HOLTokenLt{}} \HOLConst{LENGTH} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}}
+       ((\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}) \HOLConst{'} (\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs}) \HOLSymConst{=} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsfromListXXFAPPLYXXELYY}{\UseVerbatim{HOLMultivariateTheoremsfromListXXFAPPLYXXELYY}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsfromListXXFAPPLYXXHD}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{Xs} \HOLBoundVar{P} \HOLBoundVar{Ps} \HOLBoundVar{n}.
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       ((\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}) \HOLConst{'} \HOLBoundVar{X} \HOLSymConst{=} \HOLBoundVar{P})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsfromListXXFAPPLYXXHD}{\UseVerbatim{HOLMultivariateTheoremsfromListXXFAPPLYXXHD}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsfromListXXHD}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{xs} \HOLBoundVar{y} \HOLBoundVar{ys}.
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{x} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{ys}) \HOLSymConst{\HOLTokenImp{}}
+       ((\HOLBoundVar{x}\HOLSymConst{::}\HOLBoundVar{xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{y}\HOLSymConst{::}\HOLBoundVar{ys}) \HOLSymConst{=} (\HOLBoundVar{xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{ys}) \HOLSymConst{|+} (\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}))
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsfromListXXHD}{\UseVerbatim{HOLMultivariateTheoremsfromListXXHD}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsFVXXSUBSETXXBIGUNION}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{FV} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}}
+       \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{FV} (\HOLConst{set} \HOLBoundVar{Ps}))
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsFVXXSUBSETXXBIGUNION}{\UseVerbatim{HOLMultivariateTheoremsFVXXSUBSETXXBIGUNION}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsFVXXSUBSETXXBIGUNIONXXPRO}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{FV} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}}
+       \HOLConst{FV} \HOLBoundVar{E} \HOLConst{DIFF} \HOLConst{set} \HOLBoundVar{Xs} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{FV} (\HOLConst{set} \HOLBoundVar{Ps}))
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsFVXXSUBSETXXBIGUNIONXXPRO}{\UseVerbatim{HOLMultivariateTheoremsFVXXSUBSETXXBIGUNIONXXPRO}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsLISTXXRELXXequivalence}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}. \HOLConst{equivalence} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \HOLConst{equivalence} (\HOLConst{LIST_REL} \HOLBoundVar{R})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsLISTXXRELXXequivalence}{\UseVerbatim{HOLMultivariateTheoremsLISTXXRELXXequivalence}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsOBSXXCONGRXXsubstXXcontext}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{Qs}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{OBS_CONGR} \HOLBoundVar{Ps} \HOLBoundVar{Qs} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
+           \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}}
+           \HOLConst{OBS_CONGR} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E})
+             (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsOBSXXCONGRXXsubstXXcontext}{\UseVerbatim{HOLMultivariateTheoremsOBSXXCONGRXXsubstXXcontext}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsOBSXXcontractsXXreflexive}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps}. \HOLConst{OBS_contracts} \HOLBoundVar{Ps} \HOLBoundVar{Ps}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsOBSXXcontractsXXreflexive}{\UseVerbatim{HOLMultivariateTheoremsOBSXXcontractsXXreflexive}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsOBSXXcontractsXXsubstXXcontext}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{Qs}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{OBS_contracts} \HOLBoundVar{Ps} \HOLBoundVar{Qs} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
+           \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}}
+           \HOLConst{OBS_contracts} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E})
+             (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsOBSXXcontractsXXsubstXXcontext}{\UseVerbatim{HOLMultivariateTheoremsOBSXXcontractsXXsubstXXcontext}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsOBSXXcontractsXXtransitive}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{Qs} \HOLBoundVar{Rs}.
+       \HOLConst{OBS_contracts} \HOLBoundVar{Ps} \HOLBoundVar{Qs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{OBS_contracts} \HOLBoundVar{Qs} \HOLBoundVar{Rs} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{OBS_contracts} \HOLBoundVar{Ps} \HOLBoundVar{Rs}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsOBSXXcontractsXXtransitive}{\UseVerbatim{HOLMultivariateTheoremsOBSXXcontractsXXtransitive}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsSTRONGXXEQUIVXXsubstXXcontext}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{Qs}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{STRONG_EQUIV} \HOLBoundVar{Ps} \HOLBoundVar{Qs} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
+           \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}}
+           \HOLConst{STRONG_EQUIV} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E})
+             (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsSTRONGXXEQUIVXXsubstXXcontext}{\UseVerbatim{HOLMultivariateTheoremsSTRONGXXEQUIVXXsubstXXcontext}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsstrongXXuniqueXXsolution}
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es}.
-       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLConst{weakly_guarded} \HOLBoundVar{Xs}) \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{Qs}.
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps}.
@@
            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{P\sp{\prime}}.
-               \HOLConst{CCS_Subst} \HOLBoundVar{E} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+               \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sp{\prime}}.
-                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
-                   (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLConst{CCS_Subst} \HOLBoundVar{E\sp{\prime}} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps})) \HOLSymConst{\HOLTokenConj{}}
+                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLBoundVar{E\sp{\prime}} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}}
+                   (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E\sp{\prime}}) \HOLSymConst{\HOLTokenConj{}}
                    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
                        (\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-                       \HOLConst{CCS_Subst} \HOLBoundVar{E} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs})
+                       \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E}
                        \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd
-                       \HOLConst{CCS_Subst} \HOLBoundVar{E\sp{\prime}} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs})
+                       \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E\sp{\prime}}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es}.
-       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLConst{weakly_guarded} \HOLBoundVar{Xs}) \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{Qs}.
@@
 \newcommand{\HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractions}{\UseVerbatim{HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractions}}
-\begin{SaveVerbatim}{HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractionsXXlemma}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{Qs}.
-       (\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{Es}.
-            \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLConst{weakly_guarded} \HOLBoundVar{Xs}) \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
-            \HOLBoundVar{Ps} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLSymConst{\HOLTokenConj{}}
-            \HOLBoundVar{Qs} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{C}.
-           \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenImp{}}
-           (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{R}.
-                \HOLConst{CCS_Subst} \HOLBoundVar{C} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenImp{} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
-                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
-                    \HOLBoundVar{R} \HOLConst{contracts} \HOLConst{CCS_Subst} \HOLBoundVar{C\sp{\prime}} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{\HOLTokenConj{}}
-                    (\HOLConst{WEAK_EQUIV} \HOLConst{O} (\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}.
-\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenImp{} \HOLBoundVar{y}))
-                      (\HOLConst{CCS_Subst} \HOLBoundVar{C} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}))
-                      (\HOLConst{CCS_Subst} \HOLBoundVar{C\sp{\prime}} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}))) \HOLSymConst{\HOLTokenConj{}}
-           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}.
-               \HOLConst{CCS_Subst} \HOLBoundVar{C} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLTokenWeakTransBegin\HOLConst{\ensuremath{\tau}}\HOLTokenImp{} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
-               \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
-                   \HOLBoundVar{R} \HOLConst{contracts} \HOLConst{CCS_Subst} \HOLBoundVar{C\sp{\prime}} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{\HOLTokenConj{}}
-                   (\HOLConst{WEAK_EQUIV} \HOLConst{O} \HOLConst{EPS}) (\HOLConst{CCS_Subst} \HOLBoundVar{C} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}))
-                     (\HOLConst{CCS_Subst} \HOLBoundVar{C\sp{\prime}} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}))
-\end{SaveVerbatim}
-\newcommand{\HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractionsXXlemma}{\UseVerbatim{HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractionsXXlemma}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsuniqueXXsolutionXXofXXrootedXXcontractions}
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es}.
-       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLConst{weakly_guarded} \HOLBoundVar{Xs}) \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{Qs}.
@@
 \newcommand{\HOLMultivariateTheoremsuniqueXXsolutionXXofXXrootedXXcontractions}{\UseVerbatim{HOLMultivariateTheoremsuniqueXXsolutionXXofXXrootedXXcontractions}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsuniqueXXsolutionXXofXXrootedXXcontractionsXXlemma}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps} \HOLBoundVar{Qs}.
+       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLBoundVar{Qs} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{C}.
+           \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenImp{}}
+           (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{R}.
+                \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenImp{} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
+                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
+                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+                    \HOLBoundVar{R} \HOLConst{contracts} \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+                    (\HOLConst{WEAK_EQUIV} \HOLConst{O} (\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}.
+\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenImp{} \HOLBoundVar{y}))
+                      (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C})
+                      (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C\sp{\prime}})) \HOLSymConst{\HOLTokenConj{}}
+           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}.
+               \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{\ensuremath{\tau}}\HOLTokenImp{} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
+               \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
+                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+                   \HOLBoundVar{R} \HOLConst{contracts} \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+                   (\HOLConst{WEAK_EQUIV} \HOLConst{O} \HOLConst{EPS}) (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C})
+                     (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C\sp{\prime}})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsuniqueXXsolutionXXofXXrootedXXcontractionsXXlemma}{\UseVerbatim{HOLMultivariateTheoremsuniqueXXsolutionXXofXXrootedXXcontractionsXXlemma}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsUSCXXunfoldingXXlemmaOne}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{E} \HOLBoundVar{C\sb{\mathrm{0}}} \HOLBoundVar{Ps}.
+       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLConst{context} \HOLBoundVar{Xs}) \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}}
+       (\HOLBoundVar{E} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}.
+\HOLConst{MAP} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ys})) \HOLBoundVar{Es})) \HOLSymConst{\HOLTokenConj{}}
+       (\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}.
+\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ys}) \HOLFreeVar{C})) \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n}.
+\HOLConst{OBS_contracts} (\HOLBoundVar{C\sb{\mathrm{0}}} \HOLBoundVar{Ps}) ((\HOLBoundVar{C\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}) \HOLBoundVar{Ps})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsUSCXXunfoldingXXlemmaOne}{\UseVerbatim{HOLMultivariateTheoremsUSCXXunfoldingXXlemmaOne}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsUSCXXunfoldingXXlemmaTwo}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
+           \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}}
+           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{u} \HOLBoundVar{P\sp{\prime}}.
+               (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+               \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{e}) (\HOLConst{set} \HOLBoundVar{Xs})) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+               \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+               \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
+                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+                   (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C\sp{\prime}}) \HOLSymConst{\HOLTokenConj{}}
+                   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
+                       (\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+                       \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E}
+                       \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd
+                       \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C\sp{\prime}}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsUSCXXunfoldingXXlemmaTwo}{\UseVerbatim{HOLMultivariateTheoremsUSCXXunfoldingXXlemmaTwo}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsUSCXXunfoldingXXlemmaThree}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{C} \HOLBoundVar{E}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}}
+       (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       (\HOLBoundVar{E} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}.
+\HOLConst{MAP} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ys})) \HOLBoundVar{Es})) \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{x} \HOLBoundVar{P\sp{\prime}}.
+           (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+           \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{e}) (\HOLConst{set} \HOLBoundVar{Xs})) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+           \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{E} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+           \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
+               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C\sp{\prime}}) \HOLSymConst{\HOLTokenConj{}}
+               \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
+                   (\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+                   \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{E} \HOLBoundVar{Qs}) \HOLBoundVar{C}
+                   \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd
+                   \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C\sp{\prime}}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsUSCXXunfoldingXXlemmaThree}{\UseVerbatim{HOLMultivariateTheoremsUSCXXunfoldingXXlemmaThree}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsUSCXXunfoldingXXlemmaFour}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{C} \HOLBoundVar{E} \HOLBoundVar{C\sb{\mathrm{0}}}.
+       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}}
+       (\HOLBoundVar{E} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}.
+\HOLConst{MAP} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ys})) \HOLBoundVar{Es})) \HOLSymConst{\HOLTokenConj{}}
+       (\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}.
+\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ys}) \HOLBoundVar{C})) \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n} \HOLBoundVar{xs} \HOLBoundVar{Ps} \HOLBoundVar{P\sp{\prime}}.
+           (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+           \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{e}) (\HOLConst{set} \HOLBoundVar{Xs})) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+           \HOLConst{TRACE} ((\HOLBoundVar{C\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}) \HOLBoundVar{Ps}) \HOLBoundVar{xs} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenLeq{}} \HOLBoundVar{n} \HOLSymConst{\HOLTokenImp{}}
+           \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime\prime}}.
+               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C\sp{\prime\prime}}) \HOLSymConst{\HOLTokenConj{}}
+               \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
+                   (\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+                   \HOLConst{TRACE} ((\HOLBoundVar{C\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}) \HOLBoundVar{Qs}) \HOLBoundVar{xs}
+                     (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C\sp{\prime\prime}})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsUSCXXunfoldingXXlemmaFour}{\UseVerbatim{HOLMultivariateTheoremsUSCXXunfoldingXXlemmaFour}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXbackwardXXrules}
+\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y}.
+\HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{var} \HOLBoundVar{Y}) \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
+\HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}}
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}}
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
+\HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXbackwardXXrules}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXbackwardXXrules}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXcombin}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{C}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Es}) \HOLBoundVar{C})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXcombin}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXcombin}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXimpXXcontext}
@@
 \newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXimpXXcontext}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXimpXXcontext}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXnil}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}. \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLConst{nil}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXnil}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXnil}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXpar}
@@
 \newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXpar}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXpar}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXparXXrewrite}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenEquiv{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXparXXrewrite}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXparXXrewrite}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXparXXrule}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXparXXrule}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXparXXrule}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXprefix}
@@
 \newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXprefix}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXprefix}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXprefixXXrule}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXprefixXXrule}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXprefixXXrule}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrec}
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrec}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrec}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrecYY}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
@@
 \end{SaveVerbatim}
-\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrec}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrec}}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrecYY}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrecYY}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrecXXrule}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{Y} \HOLBoundVar{E})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrecXXrule}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrecXXrule}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrelab}
@@
 \newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrelab}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrelab}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrelabXXrewrite}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrelabXXrewrite}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrelabXXrewrite}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrelabXXrule}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrelabXXrule}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrelabXXrule}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrestr}
@@
 \newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrestr}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrestr}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrestrXXrewrite}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
+\HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrestrXXrewrite}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrestrXXrewrite}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrestrXXrule}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
+\HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrestrXXrule}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrestrXXrule}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrules}
+\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}. \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLConst{nil}) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y}.
+\HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{var} \HOLBoundVar{Y})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
+\HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E})) \HOLSymConst{\HOLTokenConj{}}
+   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf})) \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{Y} \HOLBoundVar{E})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrules}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrules}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXsum}
@@
 \newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXsum}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXsum}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXsumXXrewrite}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenEquiv{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXsumXXrewrite}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXsumXXrewrite}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXsumXXrule}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXsumXXrule}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXsumXXrule}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXvar}
@@
 \newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXvar}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXvar}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXvarXXrule}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y}.
+\HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{var} \HOLBoundVar{Y})
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXvarXXrule}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXvarXXrule}}
 \newcommand{\HOLMultivariateTheorems}{
-\HOLThmTag{Multivariate}{ALOOKUP_fromList}\HOLMultivariateTheoremsALOOKUPXXfromList
-\HOLThmTag{Multivariate}{CCS_Subst_alt}\HOLMultivariateTheoremsCCSXXSubstXXalt
-\HOLThmTag{Multivariate}{CCS_SUBST_ELIM}\HOLMultivariateTheoremsCCSXXSUBSTXXELIM
+\HOLThmTag{Multivariate}{BV_SUBSET_BIGUNION}\HOLMultivariateTheoremsBVXXSUBSETXXBIGUNION
+\HOLThmTag{Multivariate}{CCS_solution_length}\HOLMultivariateTheoremsCCSXXsolutionXXlength
+\HOLThmTag{Multivariate}{CCS_SUBST_elim}\HOLMultivariateTheoremsCCSXXSUBSTXXelim
+\HOLThmTag{Multivariate}{CCS_SUBST_elim'}\HOLMultivariateTheoremsCCSXXSUBSTXXelimYY
+\HOLThmTag{Multivariate}{CCS_SUBST_FEMPTY}\HOLMultivariateTheoremsCCSXXSUBSTXXFEMPTY
+\HOLThmTag{Multivariate}{CCS_SUBST_FOLDR}\HOLMultivariateTheoremsCCSXXSUBSTXXFOLDR
+\HOLThmTag{Multivariate}{CCS_SUBST_IS_PROC}\HOLMultivariateTheoremsCCSXXSUBSTXXISXXPROC
+\HOLThmTag{Multivariate}{CCS_SUBST_nested}\HOLMultivariateTheoremsCCSXXSUBSTXXnested
+\HOLThmTag{Multivariate}{CCS_SUBST_nil}\HOLMultivariateTheoremsCCSXXSUBSTXXnil
+\HOLThmTag{Multivariate}{CCS_SUBST_par}\HOLMultivariateTheoremsCCSXXSUBSTXXpar
+\HOLThmTag{Multivariate}{CCS_SUBST_prefix}\HOLMultivariateTheoremsCCSXXSUBSTXXprefix
+\HOLThmTag{Multivariate}{CCS_SUBST_PROC}\HOLMultivariateTheoremsCCSXXSUBSTXXPROC
+\HOLThmTag{Multivariate}{CCS_SUBST_rec}\HOLMultivariateTheoremsCCSXXSUBSTXXrec
+\HOLThmTag{Multivariate}{CCS_SUBST_reduce}\HOLMultivariateTheoremsCCSXXSUBSTXXreduce
+\HOLThmTag{Multivariate}{CCS_SUBST_relab}\HOLMultivariateTheoremsCCSXXSUBSTXXrelab
+\HOLThmTag{Multivariate}{CCS_SUBST_restr}\HOLMultivariateTheoremsCCSXXSUBSTXXrestr
+\HOLThmTag{Multivariate}{CCS_SUBST_self}\HOLMultivariateTheoremsCCSXXSUBSTXXself
+\HOLThmTag{Multivariate}{CCS_SUBST_SING}\HOLMultivariateTheoremsCCSXXSUBSTXXSING
+\HOLThmTag{Multivariate}{CCS_SUBST_sum}\HOLMultivariateTheoremsCCSXXSUBSTXXsum
+\HOLThmTag{Multivariate}{CCS_SUBST_var}\HOLMultivariateTheoremsCCSXXSUBSTXXvar
+\HOLThmTag{Multivariate}{context_backward_rules}\HOLMultivariateTheoremscontextXXbackwardXXrules
+\HOLThmTag{Multivariate}{context_combin}\HOLMultivariateTheoremscontextXXcombin
+\HOLThmTag{Multivariate}{context_nil}\HOLMultivariateTheoremscontextXXnil
 \HOLThmTag{Multivariate}{context_par}\HOLMultivariateTheoremscontextXXpar
+\HOLThmTag{Multivariate}{context_par_rewrite}\HOLMultivariateTheoremscontextXXparXXrewrite
 \HOLThmTag{Multivariate}{context_par_rule}\HOLMultivariateTheoremscontextXXparXXrule
 \HOLThmTag{Multivariate}{context_prefix}\HOLMultivariateTheoremscontextXXprefix
+\HOLThmTag{Multivariate}{context_prefix_rewrite}\HOLMultivariateTheoremscontextXXprefixXXrewrite
 \HOLThmTag{Multivariate}{context_prefix_rule}\HOLMultivariateTheoremscontextXXprefixXXrule
@@
 \HOLThmTag{Multivariate}{context_relab}\HOLMultivariateTheoremscontextXXrelab
+\HOLThmTag{Multivariate}{context_relab_rewrite}\HOLMultivariateTheoremscontextXXrelabXXrewrite
 \HOLThmTag{Multivariate}{context_relab_rule}\HOLMultivariateTheoremscontextXXrelabXXrule
 \HOLThmTag{Multivariate}{context_restr}\HOLMultivariateTheoremscontextXXrestr
+\HOLThmTag{Multivariate}{context_restr_rewrite}\HOLMultivariateTheoremscontextXXrestrXXrewrite
 \HOLThmTag{Multivariate}{context_restr_rule}\HOLMultivariateTheoremscontextXXrestrXXrule
+\HOLThmTag{Multivariate}{context_rules}\HOLMultivariateTheoremscontextXXrules
+\HOLThmTag{Multivariate}{context_sum}\HOLMultivariateTheoremscontextXXsum
+\HOLThmTag{Multivariate}{context_sum_rewrite}\HOLMultivariateTheoremscontextXXsumXXrewrite
+\HOLThmTag{Multivariate}{context_sum_rule}\HOLMultivariateTheoremscontextXXsumXXrule
+\HOLThmTag{Multivariate}{context_var}\HOLMultivariateTheoremscontextXXvar
+\HOLThmTag{Multivariate}{DISJOINT_BV_CCS_SUBST}\HOLMultivariateTheoremsDISJOINTXXBVXXCCSXXSUBST
+\HOLThmTag{Multivariate}{disjoint_imp_context}\HOLMultivariateTheoremsdisjointXXimpXXcontext
+\HOLThmTag{Multivariate}{disjoint_imp_weakly_guarded}\HOLMultivariateTheoremsdisjointXXimpXXweaklyXXguarded
 \HOLThmTag{Multivariate}{EVERY_weakly_guarded}\HOLMultivariateTheoremsEVERYXXweaklyXXguarded
-\HOLThmTag{Multivariate}{IN_fromList}\HOLMultivariateTheoremsINXXfromList
+\HOLThmTag{Multivariate}{FDOM_fromList}\HOLMultivariateTheoremsFDOMXXfromList
+\HOLThmTag{Multivariate}{fromList_EMPTY}\HOLMultivariateTheoremsfromListXXEMPTY
+\HOLThmTag{Multivariate}{fromList_FAPPLY_EL}\HOLMultivariateTheoremsfromListXXFAPPLYXXEL
+\HOLThmTag{Multivariate}{fromList_FAPPLY_EL'}\HOLMultivariateTheoremsfromListXXFAPPLYXXELYY
+\HOLThmTag{Multivariate}{fromList_FAPPLY_HD}\HOLMultivariateTheoremsfromListXXFAPPLYXXHD
+\HOLThmTag{Multivariate}{fromList_HD}\HOLMultivariateTheoremsfromListXXHD
+\HOLThmTag{Multivariate}{FV_SUBSET_BIGUNION}\HOLMultivariateTheoremsFVXXSUBSETXXBIGUNION
+\HOLThmTag{Multivariate}{FV_SUBSET_BIGUNION_PRO}\HOLMultivariateTheoremsFVXXSUBSETXXBIGUNIONXXPRO
+\HOLThmTag{Multivariate}{LIST_REL_equivalence}\HOLMultivariateTheoremsLISTXXRELXXequivalence
+\HOLThmTag{Multivariate}{OBS_CONGR_subst_context}\HOLMultivariateTheoremsOBSXXCONGRXXsubstXXcontext
+\HOLThmTag{Multivariate}{OBS_contracts_reflexive}\HOLMultivariateTheoremsOBSXXcontractsXXreflexive
+\HOLThmTag{Multivariate}{OBS_contracts_subst_context}\HOLMultivariateTheoremsOBSXXcontractsXXsubstXXcontext
+\HOLThmTag{Multivariate}{OBS_contracts_transitive}\HOLMultivariateTheoremsOBSXXcontractsXXtransitive
+\HOLThmTag{Multivariate}{STRONG_EQUIV_subst_context}\HOLMultivariateTheoremsSTRONGXXEQUIVXXsubstXXcontext
 \HOLThmTag{Multivariate}{strong_unique_solution}\HOLMultivariateTheoremsstrongXXuniqueXXsolution
@@
 \HOLThmTag{Multivariate}{unique_solution_of_obs_contractions}\HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractions
-\HOLThmTag{Multivariate}{unique_solution_of_obs_contractions_lemma}\HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractionsXXlemma
 \HOLThmTag{Multivariate}{unique_solution_of_rooted_contractions}\HOLMultivariateTheoremsuniqueXXsolutionXXofXXrootedXXcontractions
+\HOLThmTag{Multivariate}{unique_solution_of_rooted_contractions_lemma}\HOLMultivariateTheoremsuniqueXXsolutionXXofXXrootedXXcontractionsXXlemma
+\HOLThmTag{Multivariate}{USC_unfolding_lemma1}\HOLMultivariateTheoremsUSCXXunfoldingXXlemmaOne
+\HOLThmTag{Multivariate}{USC_unfolding_lemma2}\HOLMultivariateTheoremsUSCXXunfoldingXXlemmaTwo
+\HOLThmTag{Multivariate}{USC_unfolding_lemma3}\HOLMultivariateTheoremsUSCXXunfoldingXXlemmaThree
+\HOLThmTag{Multivariate}{USC_unfolding_lemma4}\HOLMultivariateTheoremsUSCXXunfoldingXXlemmaFour
+\HOLThmTag{Multivariate}{weakly_guarded_backward_rules}\HOLMultivariateTheoremsweaklyXXguardedXXbackwardXXrules
+\HOLThmTag{Multivariate}{weakly_guarded_combin}\HOLMultivariateTheoremsweaklyXXguardedXXcombin
 \HOLThmTag{Multivariate}{weakly_guarded_imp_context}\HOLMultivariateTheoremsweaklyXXguardedXXimpXXcontext
+\HOLThmTag{Multivariate}{weakly_guarded_nil}\HOLMultivariateTheoremsweaklyXXguardedXXnil
 \HOLThmTag{Multivariate}{weakly_guarded_par}\HOLMultivariateTheoremsweaklyXXguardedXXpar
+\HOLThmTag{Multivariate}{weakly_guarded_par_rewrite}\HOLMultivariateTheoremsweaklyXXguardedXXparXXrewrite
+\HOLThmTag{Multivariate}{weakly_guarded_par_rule}\HOLMultivariateTheoremsweaklyXXguardedXXparXXrule
 \HOLThmTag{Multivariate}{weakly_guarded_prefix}\HOLMultivariateTheoremsweaklyXXguardedXXprefix
+\HOLThmTag{Multivariate}{weakly_guarded_prefix_rule}\HOLMultivariateTheoremsweaklyXXguardedXXprefixXXrule
 \HOLThmTag{Multivariate}{weakly_guarded_rec}\HOLMultivariateTheoremsweaklyXXguardedXXrec
+\HOLThmTag{Multivariate}{weakly_guarded_rec'}\HOLMultivariateTheoremsweaklyXXguardedXXrecYY
+\HOLThmTag{Multivariate}{weakly_guarded_rec_rule}\HOLMultivariateTheoremsweaklyXXguardedXXrecXXrule
 \HOLThmTag{Multivariate}{weakly_guarded_relab}\HOLMultivariateTheoremsweaklyXXguardedXXrelab
+\HOLThmTag{Multivariate}{weakly_guarded_relab_rewrite}\HOLMultivariateTheoremsweaklyXXguardedXXrelabXXrewrite
+\HOLThmTag{Multivariate}{weakly_guarded_relab_rule}\HOLMultivariateTheoremsweaklyXXguardedXXrelabXXrule
 \HOLThmTag{Multivariate}{weakly_guarded_restr}\HOLMultivariateTheoremsweaklyXXguardedXXrestr
+\HOLThmTag{Multivariate}{weakly_guarded_restr_rewrite}\HOLMultivariateTheoremsweaklyXXguardedXXrestrXXrewrite
+\HOLThmTag{Multivariate}{weakly_guarded_restr_rule}\HOLMultivariateTheoremsweaklyXXguardedXXrestrXXrule
+\HOLThmTag{Multivariate}{weakly_guarded_rules}\HOLMultivariateTheoremsweaklyXXguardedXXrules
 \HOLThmTag{Multivariate}{weakly_guarded_sum}\HOLMultivariateTheoremsweaklyXXguardedXXsum
+\HOLThmTag{Multivariate}{weakly_guarded_sum_rewrite}\HOLMultivariateTheoremsweaklyXXguardedXXsumXXrewrite
+\HOLThmTag{Multivariate}{weakly_guarded_sum_rule}\HOLMultivariateTheoremsweaklyXXguardedXXsumXXrule
 \HOLThmTag{Multivariate}{weakly_guarded_var}\HOLMultivariateTheoremsweaklyXXguardedXXvar
+\HOLThmTag{Multivariate}{weakly_guarded_var_rule}\HOLMultivariateTheoremsweaklyXXguardedXXvarXXrule
 }

### 2019-09-03 ic-journal/sos.tex
cancelled renaming of quantifiers from E -> P/Q as now they're talking about equations too.

@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P}\hfill\texttt{[PREFIX]}
-\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{Q} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[SUM1]}
-\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{Q} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[SUM2]}
-\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q}\hfill\texttt{[PAR1]}
-\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{Q} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{Q} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[PAR2]}
-\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLTokenTransBegin\HOLConst{label} (\HOLConst{COMPL} \HOLFreeVar{l})\HOLTokenTransEnd \HOLFreeVar{Q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q\sp{\prime}}\hfill\texttt{[PAR3]}
-\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{Q} \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{=} \HOLConst{label} \HOLFreeVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{Q}\hfill\texttt{[RESTR]}
-\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLConst{relab} \HOLFreeVar{P} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{Q} \HOLFreeVar{rf}\hfill\texttt{[RELABELING]}
-\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{P} (\HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{A} \HOLFreeVar{P}) \HOLFreeVar{A} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{A} \HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{P\sp{\prime}}\hfill\texttt{[REC]}
+\HOLTokenTurnstile{} \HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E}\hfill\texttt{[PREFIX]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[SUM1]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[SUM2]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sp{\prime}}\hfill\texttt{[PAR1]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[PAR2]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} (\HOLConst{COMPL} \HOLFreeVar{l})\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
+   \HOLFreeVar{E} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sb{\mathrm{2}}}\hfill\texttt{[PAR3]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{=} \HOLConst{label} \HOLFreeVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{E\sp{\prime}}\hfill\texttt{[RESTR]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{rf}\hfill\texttt{[RELABELING]}
+\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{E} (\HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{X} \HOLFreeVar{E}) \HOLFreeVar{X} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[REC]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{CCS_Subst} \HOLConst{nil} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{nil}
+\HOLConst{CCS_Subst} \HOLConst{nil} \HOLFreeVar{E} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{nil}
 \HOLConst{CCS_Subst} (\HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{E}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLFreeVar{u}\HOLSymConst{..}\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
@@
 \HOLConst{CCS_Subst} (\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{f}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{relab} (\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}) \HOLFreeVar{f}
-\HOLConst{CCS_Subst} (\HOLConst{var} \HOLFreeVar{Y}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E\sp{\prime}} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}
+\HOLConst{CCS_Subst} (\HOLConst{var} \HOLFreeVar{Y}) \HOLFreeVar{E} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}
 \HOLConst{CCS_Subst} (\HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{Y} \HOLFreeVar{E}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}}

### 2019-09-03 paper/HOLMultivariate.tex
Fixed TRANS_IMP_NO_NIL (CCSTheory)
Updated generated TeX code (stable now)

@@
 \newcommand{\HOLMultivariateDate}{03 Settembre 2019}
-\newcommand{\HOLMultivariateTime}{10:42}
+\newcommand{\HOLMultivariateTime}{14:31}
 \begin{SaveVerbatim}{HOLMultivariateDefinitionsCCSXXequationXXdef}
@@
 \begin{SaveVerbatim}{HOLMultivariateDefinitionsCCSXXsolutionXXdef}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{R} \HOLBoundVar{Ps}.
-       \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{R} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenEquiv{}}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps}.
+       \HOLConst{CCS_solution} \HOLBoundVar{R} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenEquiv{}}
        \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}.
@@
    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{X} \HOLBoundVar{E}.
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLSymConst{=}
-       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\HOLTokenBackslash{}\HOLTokenBackslash{}} \HOLBoundVar{X}) \HOLBoundVar{E})
-       \HOLKeyword{else} \HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLSymConst{=}
+       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\HOLTokenBackslash{}\HOLTokenBackslash{}} \HOLBoundVar{X}) \HOLBoundVar{E})
+       \HOLKeyword{else} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{R} \HOLBoundVar{Ps}.
-       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{R} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CCS_solution} \HOLBoundVar{R} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenImp{}}
        (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs})
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{X} \HOLBoundVar{E}.
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLSymConst{=}
-       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\HOLTokenBackslash{}\HOLTokenBackslash{}} \HOLBoundVar{X}) \HOLBoundVar{E})
-       \HOLKeyword{else} \HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLSymConst{=}
+       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\HOLTokenBackslash{}\HOLTokenBackslash{}} \HOLBoundVar{X}) \HOLBoundVar{E})
+       \HOLKeyword{else} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})
 \end{SaveVerbatim}
@@
    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
        \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs})
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
        \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs})
@@
 \newcommand{\HOLMultivariateTheoremsSTRONGXXEQUIVXXsubstXXcontext}{\UseVerbatim{HOLMultivariateTheoremsSTRONGXXEQUIVXXsubstXXcontext}}
-\begin{SaveVerbatim}{HOLMultivariateTheoremsstrongXXuniqueXXsolution}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es}.
-       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{Qs}.
-           \HOLBoundVar{Ps} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{STRONG_EQUIV} \HOLSymConst{\HOLTokenConj{}}
-           \HOLBoundVar{Qs} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{STRONG_EQUIV} \HOLSymConst{\HOLTokenImp{}}
-           \HOLConst{STRONG_EQUIV} \HOLBoundVar{Ps} \HOLBoundVar{Qs}
-\end{SaveVerbatim}
-\newcommand{\HOLMultivariateTheoremsstrongXXuniqueXXsolution}{\UseVerbatim{HOLMultivariateTheoremsstrongXXuniqueXXsolution}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsstrongXXuniqueXXsolutionXXlemma}
@@
 \newcommand{\HOLMultivariateTheoremsstrongXXuniqueXXsolutionXXlemma}{\UseVerbatim{HOLMultivariateTheoremsstrongXXuniqueXXsolutionXXlemma}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsstrongXXuniqueXXsolutionXXthm}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps} \HOLBoundVar{Qs}.
+       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       \HOLBoundVar{Ps} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{STRONG_EQUIV} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       \HOLBoundVar{Qs} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{STRONG_EQUIV} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{STRONG_EQUIV} \HOLBoundVar{Ps} \HOLBoundVar{Qs}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsstrongXXuniqueXXsolutionXXthm}{\UseVerbatim{HOLMultivariateTheoremsstrongXXuniqueXXsolutionXXthm}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractions}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es}.
-       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{Qs}.
-           \HOLBoundVar{Ps} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLSymConst{\HOLTokenConj{}}
-           \HOLBoundVar{Qs} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLSymConst{\HOLTokenImp{}}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps} \HOLBoundVar{Qs}.
+       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       \HOLBoundVar{Ps} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       \HOLBoundVar{Qs} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
        \HOLConst{WEAK_EQUIV} \HOLBoundVar{Ps} \HOLBoundVar{Qs}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsuniqueXXsolutionXXofXXrootedXXcontractions}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es}.
-       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{Qs}.
-           \HOLBoundVar{Ps} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLSymConst{\HOLTokenConj{}}
-           \HOLBoundVar{Qs} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLSymConst{\HOLTokenImp{}}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps} \HOLBoundVar{Qs}.
+       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       \HOLBoundVar{Ps} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       \HOLBoundVar{Qs} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
        \HOLConst{OBS_CONGR} \HOLBoundVar{Ps} \HOLBoundVar{Qs}
@@
        \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLBoundVar{Qs} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Qs} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{C}.
@@
            (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{R}.
-                \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenImp{} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
+                \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
                 \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
@@
                     (\HOLConst{WEAK_EQUIV} \HOLConst{O} (\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}.
-\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenImp{} \HOLBoundVar{y}))
+\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{y}))
                       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C})
@@
            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}.
-               \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{\ensuremath{\tau}}\HOLTokenImp{} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
+               \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
@@
        \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLConst{context} \HOLBoundVar{Xs}) \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}}
        (\HOLBoundVar{E} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}.
@@
    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs})
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs})
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
@@
        \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{Y} \HOLBoundVar{E})
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E})
 \end{SaveVerbatim}
@@
 \HOLThmTag{Multivariate}{STRONG_EQUIV_subst_context}\HOLMultivariateTheoremsSTRONGXXEQUIVXXsubstXXcontext
-\HOLThmTag{Multivariate}{strong_unique_solution}\HOLMultivariateTheoremsstrongXXuniqueXXsolution
 \HOLThmTag{Multivariate}{strong_unique_solution_lemma}\HOLMultivariateTheoremsstrongXXuniqueXXsolutionXXlemma
+\HOLThmTag{Multivariate}{strong_unique_solution_thm}\HOLMultivariateTheoremsstrongXXuniqueXXsolutionXXthm
 \HOLThmTag{Multivariate}{unique_solution_of_obs_contractions}\HOLMultivariateTheoremsuniqueXXsolutionXXofXXobsXXcontractions

### 2019-09-03 ic-journal/multivariate.tex
Added multivariate.[h]tex

%%%% -*- Mode: LaTeX -*-

\section{Multivariate extensions}

(\hl{This section is new.})

\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{CCS_equation} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{STRONG_EQUIV} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLFreeVar{Qs} \HOLSymConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{STRONG_EQUIV} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenImp{}}
   \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{Qs}\hfill{[strong_unique_solution_thm]}
\end{alltt}

\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{CCS_equation} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLFreeVar{Qs} \HOLSymConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenImp{}}
   \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Qs}\hfill{[unique_solution_of_rooted_contractions]}
\end{alltt}

### 2019-09-03 ic-journal/related.tex
Added multivariate.[h]tex

@@
 name binders \cite{bengtson2007completeness,parrow2009formalising}.
-% Jesper Bengtson's PhD thesis 
-%  \cite{bengtson2010formalising} looks  at 
-% formalizations of CCS, $\pi$-calculi and $\psi$-calculi
-% into Isabelle/HOL and its
-% nominal logic. For CCS, 
-% he has 
-%  formalized
-%  basic properties for strong/weak equivalence (congruence, basic
-%  algebraic laws), for a  and observational
-% congruence, however the CCS syntax doesn't have constants
-% (or recursion operator), using replication in place of recursion.
+\hl{Jesper Bengtson's PhD thesis}~\cite{bengtson2010formalising}
+contains more details about this work. For CCS, 
+he has formalized basic properties for strong/weak equivalence (congruence, basic
+ algebraic laws), for a  and observational
+congruence, however the CCS syntax doesn't have constants
+(or recursion operator), using replication in place of recursion.
 % The formalisation effort has then been continued 
@@
 % complete. \cite{bengtson2007completeness} 
-Other formalisations in this area include the early work of T. F. Melham
-\cite{melham1994mechanized} and O.A. Mohamed
+Other formalisations in this area include the early work of T.F.~Melham
+\cite{melham1994mechanized} and O.A.~Mohamed
 \cite{mohamed1995mechanizing} in HOL, Compton

### 2019-09-03 ic-journal/sos.tex
Added multivariate.[h]tex

@@
 restriction & $(\nu\;L)\;P$ & \texttt{restr L P} & \HOLinline{\HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{P}}  \\
-recursion & $\recu A P$ & \texttt{rec A P} & \HOLinline{\HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{A} \HOLFreeVar{P}}  \\
+recursion & $\recu A P$ & \texttt{rec A P} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P}}  \\
 relabeling & $P\;[r\!f]$ & \texttt{relab P rf} & \HOLinline{\HOLConst{relab} \HOLFreeVar{P} \HOLFreeVar{rf}}  \\
@@
 \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{rf}\hfill\texttt{[RELABELING]}
-\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{E} (\HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{X} \HOLFreeVar{E}) \HOLFreeVar{X} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[REC]}
+\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{E} (\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}) \HOLFreeVar{X} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[REC]}
 \end{alltt}
@@
 \HOLConst{CCS_Subst} (\HOLConst{var} \HOLFreeVar{Y}) \HOLFreeVar{E} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}
-\HOLConst{CCS_Subst} (\HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{Y} \HOLFreeVar{E}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}}
-  \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLSymConst{\ensuremath{\mu}} \HOLFreeVar{Y} (\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X})\hfill{[CCS_Subst_def]}
+\HOLConst{CCS_Subst} (\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}}
+  \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} (\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X})\hfill{[CCS_Subst_def]}
 \end{alltt}

### 2019-09-04 ic-journal/formal.tex
The new substitution syntax (learnt from HOL's lambda example)

@@
 in the HOL theorem
-prover (HOL4) \cite{slind2008brief},
+prover (HOL4) \cite{Melham:1993vl,slind2008brief},
 including the new concepts and theorems proposed in the first half of

### 2019-09-04 ic-journal/sos.tex
The new substitution syntax (learnt from HOL's lambda example)

@@
 \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{rf}\hfill\texttt{[RELABELING]}
-\HOLTokenTurnstile{} \HOLConst{CCS_Subst} \HOLFreeVar{E} (\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}) \HOLFreeVar{X} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[REC]}
+\HOLTokenTurnstile{} [\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}/\HOLFreeVar{X}] \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[REC]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{CCS_Subst} \HOLConst{nil} \HOLFreeVar{E} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{nil}
-\HOLConst{CCS_Subst} (\HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{E}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLFreeVar{u}\HOLSymConst{..}\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
-\HOLConst{CCS_Subst} (\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E\sb{\mathrm{2}}}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}}
-  \HOLConst{CCS_Subst} \HOLFreeVar{E\sb{\mathrm{1}}} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_Subst} \HOLFreeVar{E\sb{\mathrm{2}}} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
-\HOLConst{CCS_Subst} (\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sb{\mathrm{2}}}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}}
-  \HOLConst{CCS_Subst} \HOLFreeVar{E\sb{\mathrm{1}}} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{CCS_Subst} \HOLFreeVar{E\sb{\mathrm{2}}} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
-\HOLConst{CCS_Subst} (\HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{E}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X})
-\HOLConst{CCS_Subst} (\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{f}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{relab} (\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}) \HOLFreeVar{f}
-\HOLConst{CCS_Subst} (\HOLConst{var} \HOLFreeVar{Y}) \HOLFreeVar{E} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}
-\HOLConst{CCS_Subst} (\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}) \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X} \HOLSymConst{\HOLTokenDefEquality{}}
-  \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} (\HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X})\hfill{[CCS_Subst_def]}
+[\HOLFreeVar{E}/\HOLFreeVar{X}] \HOLConst{nil} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{nil}
+[\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] (\HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{E}) \HOLSymConst{\HOLTokenDefEquality{}} \HOLFreeVar{u}\HOLSymConst{..}[\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] \HOLFreeVar{E}
+[\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] (\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenDefEquality{}} [\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} [\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] \HOLFreeVar{E\sb{\mathrm{2}}}
+[\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] (\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenDefEquality{}} [\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} [\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] \HOLFreeVar{E\sb{\mathrm{2}}}
+[\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] (\HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} ([\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] \HOLFreeVar{E})
+[\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] (\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{f}) \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{relab} ([\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] \HOLFreeVar{E}) \HOLFreeVar{f}
+[\HOLFreeVar{E}/\HOLFreeVar{X}] (\HOLConst{var} \HOLFreeVar{Y}) \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}
+[\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] (\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} ([\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] \HOLFreeVar{E})\hfill{[CCS_Subst_def]}
 \end{alltt}

### 2019-09-04 paper/HOLMultivariate.tex
The new substitution syntax (learnt from HOL's lambda example)

@@
-\newcommand{\HOLMultivariateDate}{03 Settembre 2019}
-\newcommand{\HOLMultivariateTime}{14:31}
+\newcommand{\HOLMultivariateDate}{04 Settembre 2019}
+\newcommand{\HOLMultivariateTime}{10:49}
 \begin{SaveVerbatim}{HOLMultivariateDefinitionsCCSXXequationXXdef}
@@
 \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{e}) (\HOLConst{set} \HOLBoundVar{Xs})) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{LIST_REL} \HOLBoundVar{R} \HOLBoundVar{Ps} (\HOLConst{MAP} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps})) \HOLBoundVar{Es})
+       \HOLConst{LIST_REL} \HOLBoundVar{R} \HOLBoundVar{Ps} (\HOLConst{MAP} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{Es})
 \end{SaveVerbatim}
@@
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLSymConst{=}
-       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\HOLTokenBackslash{}\HOLTokenBackslash{}} \HOLBoundVar{X}) \HOLBoundVar{E})
+       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\ensuremath{\setminus}} \HOLBoundVar{X}) \HOLBoundVar{E})
        \HOLKeyword{else} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})
@@
             \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
-            \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{X}.
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{t} \HOLBoundVar{X})) \HOLBoundVar{Xs})
+            \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. [\HOLBoundVar{t}/\HOLBoundVar{X}] \HOLBoundVar{E})) \HOLBoundVar{Xs})
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps}.
-(\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{=} \HOLConst{FEMPTY} \HOLSymConst{|++} \HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})
+\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{FEMPTY} \HOLSymConst{|++} \HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})
 \end{SaveVerbatim}
@@
             \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
-            \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{X}.
-\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{t} \HOLBoundVar{X})) \HOLBoundVar{Xs})
+            \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. [\HOLBoundVar{t}/\HOLBoundVar{X}] \HOLBoundVar{E})) \HOLBoundVar{Xs})
 \end{SaveVerbatim}
@@
        \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{BV} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}}
-       \HOLConst{BV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{BV} (\HOLConst{set} \HOLBoundVar{Ps}))
+       \HOLConst{BV} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{BV} (\HOLConst{set} \HOLBoundVar{Ps}))
 \end{SaveVerbatim}
@@
        \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})
+       ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})
 \end{SaveVerbatim}
@@
        \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLSymConst{=}
-        \HOLConst{FOLDR} (\HOLTokenLambda{}(\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}) \HOLBoundVar{e}.
-\HOLConst{CCS_Subst} \HOLBoundVar{e} \HOLBoundVar{y} \HOLBoundVar{x}) \HOLBoundVar{E} (\HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})))
+       ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{FOLDR} (\HOLTokenLambda{}(\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}) \HOLBoundVar{e}.
+[\HOLBoundVar{y}/\HOLBoundVar{x}] \HOLBoundVar{e}) \HOLBoundVar{E} (\HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})))
 \end{SaveVerbatim}
@@
        \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{IS_PROC} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E})
+       \HOLConst{IS_PROC} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E})
 \end{SaveVerbatim}
@@
        (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{C}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Es}) \HOLBoundVar{C}) \HOLSymConst{=}
-        \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLConst{MAP} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps})) \HOLBoundVar{Es}) \HOLBoundVar{C})
+       ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] ([\HOLBoundVar{Es}/\HOLBoundVar{Xs}] \HOLBoundVar{C}) \HOLSymConst{=} [\HOLConst{MAP} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{Es}/\HOLBoundVar{Xs}] \HOLBoundVar{C})
 \end{SaveVerbatim}
@@
        \HOLConst{IS_PROC} \HOLBoundVar{P} \HOLSymConst{\HOLTokenImp{}}
-       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{P} \HOLSymConst{=} \HOLBoundVar{P})
+       ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{P} \HOLSymConst{=} \HOLBoundVar{P})
 \end{SaveVerbatim}
@@
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-           \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs})) \HOLSymConst{\HOLTokenConj{}}
-           (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E\sp{\prime}}) \HOLSymConst{\HOLTokenImp{}}
-           (\HOLConst{CCS_SUBST} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{CCS_Subst} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{P} \HOLBoundVar{X})
+           \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs})) \HOLSymConst{\HOLTokenConj{}} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E\sp{\prime}}) \HOLSymConst{\HOLTokenImp{}}
+           ([\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}/\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} [\HOLBoundVar{P}/\HOLBoundVar{X}] \HOLBoundVar{E\sp{\prime}})
 \end{SaveVerbatim}
@@
        \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLConst{MAP} \HOLConst{var} \HOLBoundVar{Xs}) \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})
+       ([\HOLConst{MAP} \HOLConst{var} \HOLBoundVar{Xs}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-\HOLConst{CCS_SUBST} (\HOLConst{FEMPTY} \HOLSymConst{|+} (\HOLBoundVar{X}\HOLSymConst{,}\HOLBoundVar{E\sp{\prime}})) \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{X}
+\HOLConst{CCS_SUBST} (\HOLConst{FEMPTY} \HOLSymConst{|+} (\HOLBoundVar{X}\HOLSymConst{,}\HOLBoundVar{E\sp{\prime}})) \HOLBoundVar{E} \HOLSymConst{=} [\HOLBoundVar{E\sp{\prime}}/\HOLBoundVar{X}] \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
        (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Es}) \HOLBoundVar{C})
+       \HOLConst{context} \HOLBoundVar{Xs} ([\HOLBoundVar{Es}/\HOLBoundVar{Xs}] \HOLBoundVar{C})
 \end{SaveVerbatim}
@@
        \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{DISJOINT} (\HOLConst{BV} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E})) (\HOLConst{set} \HOLBoundVar{Xs})
+       \HOLConst{DISJOINT} (\HOLConst{BV} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E})) (\HOLConst{set} \HOLBoundVar{Xs})
 \end{SaveVerbatim}
@@
 \HOLConst{MEM} \HOLBoundVar{E} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLConst{CCS_Subst} \HOLBoundVar{E} \HOLBoundVar{t} \HOLBoundVar{X})
+[\HOLBoundVar{t}/\HOLBoundVar{X}] \HOLBoundVar{E})
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps}.
-(\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}} (\HOLConst{FDOM} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLSymConst{=} \HOLConst{set} \HOLBoundVar{Xs})
+       (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       (\HOLConst{FDOM} (\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps}) \HOLSymConst{=} \HOLConst{set} \HOLBoundVar{Xs})
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsfromListXXEMPTY}
-\HOLTokenTurnstile{} ([] \HOLSymConst{\HOLTokenMapto{}} []) \HOLSymConst{=} \HOLConst{FEMPTY}
+\HOLTokenTurnstile{} \HOLConst{fromList} [] [] \HOLSymConst{=} \HOLConst{FEMPTY}
 \end{SaveVerbatim}
@@
        \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{n} \HOLSymConst{\HOLTokenLt{}} \HOLConst{LENGTH} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}}
-       ((\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLConst{'} (\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs}) \HOLSymConst{=} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps})
+       (\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLConst{'} (\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs}) \HOLSymConst{=} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps})
 \end{SaveVerbatim}
@@
        \HOLBoundVar{n} \HOLSymConst{\HOLTokenLt{}} \HOLConst{LENGTH} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}}
-       ((\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}) \HOLConst{'} (\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs}) \HOLSymConst{=} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps})
+       (\HOLConst{fromList} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}) (\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}) \HOLConst{'} (\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs}) \HOLSymConst{=} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps})
 \end{SaveVerbatim}
@@
        \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       ((\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}) \HOLConst{'} \HOLBoundVar{X} \HOLSymConst{=} \HOLBoundVar{P})
+       (\HOLConst{fromList} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}) (\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}) \HOLConst{'} \HOLBoundVar{X} \HOLSymConst{=} \HOLBoundVar{P})
 \end{SaveVerbatim}
@@
        \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{x} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{ys}) \HOLSymConst{\HOLTokenImp{}}
-       ((\HOLBoundVar{x}\HOLSymConst{::}\HOLBoundVar{xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{y}\HOLSymConst{::}\HOLBoundVar{ys}) \HOLSymConst{=} (\HOLBoundVar{xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{ys}) \HOLSymConst{|+} (\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}))
+       (\HOLConst{fromList} (\HOLBoundVar{x}\HOLSymConst{::}\HOLBoundVar{xs}) (\HOLBoundVar{y}\HOLSymConst{::}\HOLBoundVar{ys}) \HOLSymConst{=} \HOLConst{fromList} \HOLBoundVar{xs} \HOLBoundVar{ys} \HOLSymConst{|+} (\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}))
 \end{SaveVerbatim}
@@
        \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{FV} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}}
-       \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{FV} (\HOLConst{set} \HOLBoundVar{Ps}))
+       \HOLConst{FV} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{FV} (\HOLConst{set} \HOLBoundVar{Ps}))
 \end{SaveVerbatim}
@@
        \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{FV} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}}
+       \HOLConst{FV} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}}
        \HOLConst{FV} \HOLBoundVar{E} \HOLConst{DIFF} \HOLConst{set} \HOLBoundVar{Xs} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{FV} (\HOLConst{set} \HOLBoundVar{Ps}))
@@
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
-           \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}}
-           \HOLConst{OBS_CONGR} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E})
-             (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E})
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{OBS_CONGR} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E})
 \end{SaveVerbatim}
@@
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
-           \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}}
-           \HOLConst{OBS_contracts} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E})
-             (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E})
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{OBS_contracts} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E})
 \end{SaveVerbatim}
@@
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
-           \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}}
-           \HOLConst{STRONG_EQUIV} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E})
-             (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E})
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{STRONG_EQUIV} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E})
 \end{SaveVerbatim}
@@
            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{P\sp{\prime}}.
-               \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+               [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sp{\prime}}.
                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLBoundVar{E\sp{\prime}} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}}
-                   (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E\sp{\prime}}) \HOLSymConst{\HOLTokenConj{}}
+                   (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E\sp{\prime}}) \HOLSymConst{\HOLTokenConj{}}
                    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
                        (\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-                       \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E}
-                       \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd
-                       \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E\sp{\prime}}
+                       [\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd [\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E\sp{\prime}}
 \end{SaveVerbatim}
@@
            (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{R}.
-                \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
+                [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
                 \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
-                    \HOLBoundVar{R} \HOLConst{contracts} \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLConst{contracts} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
                     (\HOLConst{WEAK_EQUIV} \HOLConst{O} (\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}.
 \HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{y}))
-                      (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C})
-                      (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C\sp{\prime}})) \HOLSymConst{\HOLTokenConj{}}
+                      ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}})) \HOLSymConst{\HOLTokenConj{}}
            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}.
-               \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
+               [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
-                   \HOLBoundVar{R} \HOLConst{contracts} \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
-                   (\HOLConst{WEAK_EQUIV} \HOLConst{O} \HOLConst{EPS}) (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C})
-                     (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C\sp{\prime}})
+                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLConst{contracts} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+                   (\HOLConst{WEAK_EQUIV} \HOLConst{O} \HOLConst{EPS}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}})
 \end{SaveVerbatim}
@@
        (\HOLBoundVar{E} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}.
-\HOLConst{MAP} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ys})) \HOLBoundVar{Es})) \HOLSymConst{\HOLTokenConj{}}
-       (\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}.
-\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ys}) \HOLFreeVar{C})) \HOLSymConst{\HOLTokenImp{}}
+\HOLConst{MAP} [\HOLBoundVar{Ys}/\HOLBoundVar{Xs}] \HOLBoundVar{Es})) \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}.
+[\HOLBoundVar{Ys}/\HOLBoundVar{Xs}] \HOLFreeVar{C})) \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n}.
@@
                \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{e}) (\HOLConst{set} \HOLBoundVar{Xs})) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-               \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+               [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
-                   (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C\sp{\prime}}) \HOLSymConst{\HOLTokenConj{}}
+                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}}) \HOLSymConst{\HOLTokenConj{}}
                    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
                        (\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-                       \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{E}
-                       \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd
-                       \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C\sp{\prime}}
+                       [\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd [\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}}
 \end{SaveVerbatim}
@@
        (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
-       (\HOLBoundVar{E} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}.
-\HOLConst{MAP} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ys})) \HOLBoundVar{Es})) \HOLSymConst{\HOLTokenImp{}}
+       (\HOLBoundVar{E} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}. \HOLConst{MAP} [\HOLBoundVar{Ys}/\HOLBoundVar{Xs}] \HOLBoundVar{Es})) \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{x} \HOLBoundVar{P\sp{\prime}}.
@@
            \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{e}) (\HOLConst{set} \HOLBoundVar{Xs})) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-           \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{E} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+           [\HOLBoundVar{E} \HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
            \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C\sp{\prime}}) \HOLSymConst{\HOLTokenConj{}}
+               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}}) \HOLSymConst{\HOLTokenConj{}}
                \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
                    (\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-                   \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{E} \HOLBoundVar{Qs}) \HOLBoundVar{C}
-                   \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd
-                   \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C\sp{\prime}}
+                   [\HOLBoundVar{E} \HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd [\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}}
 \end{SaveVerbatim}
@@
        \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}}
-       (\HOLBoundVar{E} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}.
-\HOLConst{MAP} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ys})) \HOLBoundVar{Es})) \HOLSymConst{\HOLTokenConj{}}
-       (\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}.
-\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ys}) \HOLBoundVar{C})) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{E} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}.
+\HOLConst{MAP} [\HOLBoundVar{Ys}/\HOLBoundVar{Xs}] \HOLBoundVar{Es})) \HOLSymConst{\HOLTokenConj{}}
+       (\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}. [\HOLBoundVar{Ys}/\HOLBoundVar{Xs}] \HOLBoundVar{C})) \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n} \HOLBoundVar{xs} \HOLBoundVar{Ps} \HOLBoundVar{P\sp{\prime}}.
@@
            \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime\prime}}.
-               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C\sp{\prime\prime}}) \HOLSymConst{\HOLTokenConj{}}
+               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime\prime}}) \HOLSymConst{\HOLTokenConj{}}
                \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
                    (\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-                   \HOLConst{TRACE} ((\HOLBoundVar{C\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}) \HOLBoundVar{Qs}) \HOLBoundVar{xs}
-                     (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Qs}) \HOLBoundVar{C\sp{\prime\prime}})
+                   \HOLConst{TRACE} ((\HOLBoundVar{C\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}) \HOLBoundVar{Qs}) \HOLBoundVar{xs} ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime\prime}})
 \end{SaveVerbatim}
@@
        (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Es}) \HOLBoundVar{C})
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} ([\HOLBoundVar{Es}/\HOLBoundVar{Xs}] \HOLBoundVar{C})
 \end{SaveVerbatim}

### 2019-09-04 ic-journal/response-letter.tex
Improved TeX output of "nil" (final changes on HOL side)

@@
 \end{center}
+
+Dear Chairs and Reviewers,
+
+\vskip 10pt
+\noindent
+
+thank you for conditionally accepting our paper and for the fruitful
+comments. We took all of them into consideration, and thoroughly
+addressed each of them in the revised version. We believe that after
+this revision, the quality of the paper has been significantly
+improved.
+
+In the following, we discuss the changes to the paper and provide a
+point-by-point reply to the issues that have been raised.
+\ \\
+
+Best regards,
+\begin{flushright}
+  Chun Tian and Davide Sangiorgi \\
+  September 13, 2019
+\end{flushright}
+
+\vspace{1cm}
 

### 2019-09-04 ic-journal/coarsest.tex
cancelled renaming of quantifiers from E -> P/Q as now they're talking about equations too.
Improved TeX output of "nil" (final changes on HOL side)

@@
 \HOLConst{WEAK_CONGR} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{CC} \HOLConst{WEAK_EQUIV}\hfill{[WEAK_CONGR]}
-\HOLConst{CC} \HOLFreeVar{R} \HOLSymConst{\HOLTokenDefEquality{}} (\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}.
+\HOLConst{CC} \HOLFreeVar{R} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}.
 \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}.
-\HOLConst{CONTEXT} \HOLBoundVar{c} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{c} \HOLBoundVar{g}) (\HOLBoundVar{c} \HOLBoundVar{h}))\hfill{[CC_def]}
+\HOLConst{CONTEXT} \HOLBoundVar{c} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \ensuremath{(}\HOLBoundVar{c} \HOLBoundVar{g}\ensuremath{)} \ensuremath{(}\HOLBoundVar{c} \HOLBoundVar{h}\ensuremath{)}\ensuremath{)}\hfill{[CC_def]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{SUM_EQUIV} \HOLSymConst{\HOLTokenDefEquality{}} (\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}.
+\HOLConst{SUM_EQUIV} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}.
 \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r})\hfill{[SUM_EQUIV]}
+\HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)}\hfill{[SUM_EQUIV]}
 \end{alltt}
@@
 % \begin{alltt}
-% \HOLConst{SUM_EQUIV} \HOLSymConst{\HOLTokenDefEquality{}} (\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}.
+% \HOLConst{SUM_EQUIV} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}.
 \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r})
+\HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)}
 % \end{alltt}
@@
 \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}}.
-\HOLSymConst{\HOLTokenNeg{}}(\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{a}\HOLTokenImp{} \HOLBoundVar{p\sp{\prime}})\hfill{[free_action_def]}
+\HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{a}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}}\ensuremath{)}\hfill{[free_action_def]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}) \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q}\hfill{[COARSEST_CONGR_RL]}
+\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
+\HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q}\hfill{[COARSEST_CONGR_RL]}
 \end{alltt}
@@
 \hfill{[COARSEST_PRECONGR_RL]}
-\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}) \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{q}
+\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
+\HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{q}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
-        \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}} \HOLBoundVar{u}.
-\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenImp{} \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenConj{}}
+\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
+        \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}} \HOLBoundVar{u}.
+\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
         \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{q\sp{\prime}} \HOLBoundVar{u}.
-\HOLFreeVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenImp{} \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenImp{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}) \HOLSymConst{\HOLTokenImp{}}
+\HOLFreeVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
+\HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
    \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q}\hfill{[PROP3_COMMON]}
@@
 \begin{alltt}
-\HOLConst{KLOP} \HOLFreeVar{a} \HOLNumLit{0} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{nil}
-\HOLConst{KLOP} \HOLFreeVar{a} (\HOLConst{SUC} \HOLFreeVar{n}) \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLSymConst{\ensuremath{+}} \HOLConst{label} \HOLFreeVar{a}\HOLSymConst{..}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\hfill{[KLOP_def]}
+\HOLConst{KLOP} \HOLFreeVar{a} \HOLNumLit{0} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{\ensuremath{\mathbf{0}}}
+\HOLConst{KLOP} \HOLFreeVar{a} \ensuremath{(}\HOLConst{SUC} \HOLFreeVar{n}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLSymConst{\ensuremath{+}} \HOLConst{label} \HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\hfill{[KLOP_def]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{STABLE} (\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n})\hfill[KLOP_PROP0]
+\HOLTokenTurnstile{} \HOLConst{STABLE} \ensuremath{(}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\ensuremath{)}\hfill[KLOP_PROP0]
 \end{alltt}
@@
 \HOLTokenTurnstile{} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{a}\HOLTokenTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{m}.
-\HOLBoundVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLBoundVar{m}\hfill{[KLOP_PROP1]}
+\HOLBoundVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{KLOP} \HOLFreeVar{a} \HOLBoundVar{m}\hfill{[KLOP_PROP1]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLTokenWeakTransBegin\HOLConst{label} \HOLFreeVar{a}\HOLTokenImp{} \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{m}.
-\HOLBoundVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{=} \HOLConst{KLOP} \HOLFreeVar{a} \HOLBoundVar{m}\hfill{[KLOP_PROP1']}
+\HOLTokenTurnstile{} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLTokenWeakTransBegin\HOLConst{label} \HOLFreeVar{a}\HOLTokenWeakTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{m}.
+\HOLBoundVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{KLOP} \HOLFreeVar{a} \HOLBoundVar{m}\hfill{[KLOP_PROP1']}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{m} \HOLSymConst{\HOLTokenStrongEQ} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n})\hfill{[KLOP_PROP2]}
+\HOLTokenTurnstile{} \HOLFreeVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{m} \HOLSymConst{\HOLTokenStrongEQ} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\ensuremath{)}\hfill{[KLOP_PROP2]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{m} \HOLSymConst{\HOLTokenWeakEQ} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n})\hfill{[KLOP_PROP2']}
+\HOLTokenTurnstile{} \HOLFreeVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{m} \HOLSymConst{\HOLTokenWeakEQ} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\ensuremath{)}\hfill{[KLOP_PROP2']}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{ONE_ONE} (\HOLConst{KLOP} \HOLFreeVar{a})\hfill{[KLOP_ONE_ONE]}
+\HOLTokenTurnstile{} \HOLConst{ONE_ONE} \ensuremath{(}\HOLConst{KLOP} \HOLFreeVar{a}\ensuremath{)}\hfill{[KLOP_ONE_ONE]}
 \end{alltt}
@@
 \HOLTokenTurnstile{} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenImp{}}
-   \HOLConst{FINITE} \HOLFreeVar{A} \HOLSymConst{\HOLTokenConj{}} \HOLConst{INFINITE} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y}.
-\HOLBoundVar{x} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{x} \HOLSymConst{\HOLTokenNotEqual{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y}) \HOLSymConst{\HOLTokenImp{}}
+   \HOLConst{FINITE} \HOLFreeVar{A} \HOLSymConst{\HOLTokenConj{}} \HOLConst{INFINITE} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y}.
+\HOLBoundVar{x} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{x} \HOLSymConst{\HOLTokenNotEqual{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
    \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
@@
 \begin{alltt}
-\HOLConst{Reach} \HOLSymConst{\HOLTokenDefEquality{}} (\HOLTokenLambda{}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
+\HOLConst{Reach} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
 \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{u}.
-\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}})\HOLSymConst{\HOLTokenSupStar{}}\hfill[Reach_def]
+\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}}\ensuremath{)}\HOLSymConst{\HOLTokenSupStar{}}\hfill[Reach_def]
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{FINITE} (\HOLConst{NODES} \HOLFreeVar{p})\hfill[finite_state_def]
+\HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{FINITE} \ensuremath{(}\HOLConst{NODES} \HOLFreeVar{p}\ensuremath{)}\hfill[finite_state_def]
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenImp{} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{q} \HOLSymConst{\HOLTokenIn{}} \HOLConst{NODES} \HOLFreeVar{p}\hfill[WEAK_TRANS_IN_NODES]
+\HOLTokenTurnstile{} \HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{q} \HOLSymConst{\HOLTokenIn{}} \HOLConst{NODES} \HOLFreeVar{p}\hfill[WEAK_TRANS_IN_NODES]
 \end{alltt}
@@
        \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
-           \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}} \HOLBoundVar{u}.
-\HOLBoundVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenImp{} \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})) \HOLSymConst{\HOLTokenConj{}}
+           \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}} \HOLBoundVar{u}.
+\HOLBoundVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{q\sp{\prime}} \HOLBoundVar{u}.
-\HOLBoundVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenImp{} \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}(\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k})\hfill{[KLOP_LEMMA_FINITE]}
+\HOLBoundVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\hfill{[KLOP_LEMMA_FINITE]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}}
-   (\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r})\hfill[COARSEST_CONGR_FINITE]
+\HOLTokenTurnstile{} \HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
+\HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)}\hfill[COARSEST_CONGR_FINITE]
 \end{alltt}

### 2019-09-04 ic-journal/context.tex
The new substitution syntax (learnt from HOL's lambda example)
Improved TeX output of "nil" (final changes on HOL side)

--- 2019-02-08 ic-journal/context.tex
@@
 We have chosen to use $\lambda$-expressions (with the type
-``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'')
+``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
 to represent \emph{multi-hole contexts}.
@@
 \begin{alltt}
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
-\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[CONTEXT_rules]}
+\HOLTokenTurnstile{} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{t}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
+\HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
+\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
+\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
+\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)}\hfill{[CONTEXT_rules]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{WG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[WG_rules]}
+\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
+\HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
+\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
+\HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
+\HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)}\hfill{[WG_rules]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{label} \HOLFreeVar{l}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{SG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{SG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{SG} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[SG_rules]}
+\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
+\HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{e}.
+\HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{label} \HOLBoundVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
+\HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
+\HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
+\HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)}\hfill{[SG_rules]}
 \end{alltt}
@@
  \begin{alltt}
-\HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
-\HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{SEQ} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{SEQ} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})\hfill{[SEQ_rules]}
+\HOLTokenTurnstile{} \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{t}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
+\HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
+\HOLConst{SEQ} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{SEQ} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\hfill{[SEQ_rules]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
-\HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{a\sb{\mathrm{1}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{a\sb{\mathrm{2}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[GCONTEXT_rules]}
+\HOLTokenTurnstile{} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{t}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
+\HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
+\HOLConst{GCONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a\sb{\mathrm{1}}} \HOLBoundVar{a\sb{\mathrm{2}}} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+        \HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a\sb{\mathrm{1}}}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{a\sb{\mathrm{2}}}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
+\HOLConst{GCONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
+\HOLConst{GCONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)}\hfill{[GCONTEXT_rules]}
 \end{alltt}
 \begin{alltt}
-\HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
-\HOLConst{GCONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
-\HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{a\sb{\mathrm{1}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{a\sb{\mathrm{2}}}\HOLSymConst{..}\HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WGS} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
-\HOLConst{WGS} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
-\HOLConst{WGS} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[WGS_rules]}
+\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}.
+\HOLConst{WGS} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}.
+\HOLConst{GCONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a\sb{\mathrm{1}}} \HOLBoundVar{a\sb{\mathrm{2}}} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a\sb{\mathrm{1}}}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{a\sb{\mathrm{2}}}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
+\HOLConst{WGS} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
+\HOLConst{WGS} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}.
+\HOLConst{WGS} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLConst{relab} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)}\hfill{[WGS_rules]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
-\HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}}
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
-\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})\hfill{[congruence_def]}
-\hfill{[precongruence_def]}
-\end{alltt}
-\vspace{-4ex}
-\begin{alltt}
-\HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenEquiv{}}
+\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenDefEquality{}}
+  \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
+\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \ensuremath{(}\HOLBoundVar{ctx} \HOLBoundVar{x}\ensuremath{)} \ensuremath{(}\HOLBoundVar{ctx} \HOLBoundVar{y}\ensuremath{)}\hfill{[congruence]}
+
+\HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenDefEquality{}}
   \HOLConst{PreOrder} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
-\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} (\HOLBoundVar{ctx} \HOLBoundVar{x}) (\HOLBoundVar{ctx} \HOLBoundVar{y})
+\HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \ensuremath{(}\HOLBoundVar{ctx} \HOLBoundVar{x}\ensuremath{)} \ensuremath{(}\HOLBoundVar{ctx} \HOLBoundVar{y}\ensuremath{)}\hfill{[precongruence]}
 \end{alltt}

### 2019-09-04 ic-journal/part2.tex
cancelled renaming of quantifiers from E -> P/Q as now they're talking about equations too.
Added multivariate.[h]tex
Improved TeX output of "nil" (final changes on HOL side)

@@
    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \HOLBoundVar{P\sp{\prime}}.
-       \HOLFreeVar{E} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sp{\prime}}.
-\HOLConst{CONTEXT} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLFreeVar{E} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sp{\prime}}.
+\HOLConst{CONTEXT} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
 \HOLFreeVar{E} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{Q}
@@
        \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}.
-           \HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{a} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}) \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}}
-           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
 \HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}\hfill{[WEAK_UNIQUE_SOLUTION_LEMMA]}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}\hfill{[WEAK_UNIQUE_SOLUTION]}
+\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{Q}\hfill{[WEAK_UNIQUE_SOLUTION]}
 \end{alltt}
@@
    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u}.
-            (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u}.
+            \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
 \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLBoundVar{E\sp{\prime}} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenImp{} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
+\HOLBoundVar{E\sp{\prime}} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
             \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
 \HOLBoundVar{E\sp{\prime}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenImp{} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}}
+\HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
        \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{E\sp{\prime}}\hfill{[OBS_CONGR_BY_WEAK_BISIM]}
@@
        \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}.
-\HOLConst{SEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{a} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}) \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLConst{SEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
 \HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}\hfill{[OBS_UNIQUE_SOLUTION_LEMMA]}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}\hfill{[OBS_UNIQUE_SOLUTION]}
+\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Q}\hfill{[OBS_UNIQUE_SOLUTION]}
 \end{alltt}
@@
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.
-      (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x}. \HOLBoundVar{P} \HOLBoundVar{x} [] \HOLBoundVar{x}) \HOLSymConst{\HOLTokenConj{}}
-      (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z}.
-\HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLBoundVar{x} (\HOLBoundVar{h}\HOLSymConst{::}\HOLBoundVar{t}) \HOLBoundVar{z}) \HOLSymConst{\HOLTokenImp{}}
+      \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x}.
+\HOLBoundVar{P} \HOLBoundVar{x} \ensuremath{[}\ensuremath{]} \HOLBoundVar{x}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z}.
+\HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLBoundVar{x} \ensuremath{(}\HOLBoundVar{h}\HOLSymConst{::}\HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{z}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \HOLBoundVar{P} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b}\hfill{[LRTC_DEF]}
@@
 \HOLConst{NO_LABEL} \HOLFreeVar{L} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
-\HOLConst{MEM} (\HOLConst{label} \HOLBoundVar{l}) \HOLFreeVar{L}\hfill{[NO_LABEL_def]}
+\HOLConst{MEM} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \HOLFreeVar{L}\hfill{[NO_LABEL_def]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLSymConst{\HOLTokenDefEquality{}}
-  \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{L\sb{\mathrm{1}}} \HOLBoundVar{L\sb{\mathrm{2}}}.
-\HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} [\HOLFreeVar{u}] \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{=} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{2}}}\hfill{[UNIQUE_LABEL_def]}
+\HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{L\sb{\mathrm{1}}} \HOLBoundVar{L\sb{\mathrm{2}}}.
+\HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} \ensuremath{[}\HOLFreeVar{u}\ensuremath{]} \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{2}}}\hfill{[UNIQUE_LABEL_def]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenImp{} \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}}
    \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{acts}.
        \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{acts} \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{NULL} \HOLBoundVar{acts} \HOLSymConst{\HOLTokenConj{}}
-       \HOLKeyword{if} \HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLKeyword{then} \HOLConst{NO_LABEL} \HOLBoundVar{acts} \HOLKeyword{else} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLBoundVar{acts}\hfill{[WEAK_TRANS_AND_TRACE]}
+       \HOLKeyword{if} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLKeyword{then} \HOLConst{NO_LABEL} \HOLBoundVar{acts} \HOLKeyword{else} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLBoundVar{acts}\hfill{[WEAK_TRANS_AND_TRACE]}
 \end{alltt}
@@
 \begin{small}
-\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E}.
-\HOLConst{WGS} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{E} \HOLFreeVar{Q}) \HOLSymConst{\HOLTokenImp{}}
+\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E}.
+\HOLConst{WGS} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{E} \HOLFreeVar{Q}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{C}.
        \HOLConst{GCONTEXT} \HOLBoundVar{C} \HOLSymConst{\HOLTokenImp{}}
-       (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{R}.
-            \HOLBoundVar{C} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenImp{} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{R}.
+            \HOLBoundVar{C} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
             \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
                 \HOLConst{GCONTEXT} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{C\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}}
-                (\HOLConst{WEAK_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} (\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}.
-\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenImp{} \HOLBoundVar{y})) (\HOLBoundVar{C} \HOLFreeVar{Q})
-                  (\HOLBoundVar{C\sp{\prime}} \HOLFreeVar{Q})) \HOLSymConst{\HOLTokenConj{}}
+                \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}.
+\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{y}\ensuremath{)}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C} \HOLFreeVar{Q}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C\sp{\prime}} \HOLFreeVar{Q}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}.
-           \HOLBoundVar{C} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenImp{} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
+           \HOLBoundVar{C} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
            \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-               \HOLConst{GCONTEXT} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{C\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}}
-               (\HOLConst{WEAK_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{EPS}) (\HOLBoundVar{C} \HOLFreeVar{Q}) (\HOLBoundVar{C\sp{\prime}} \HOLFreeVar{Q})
+\HOLConst{GCONTEXT} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{C\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{EPS}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C} \HOLFreeVar{Q}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C\sp{\prime}} \HOLFreeVar{Q}\ensuremath{)}
 \end{small}
@@
 \begin{small}
-\HOLTokenTurnstile{} \HOLConst{GCONTEXT} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{TRACE} ((\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}) \HOLFreeVar{P}) \HOLFreeVar{xs} \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
-   \HOLConst{LENGTH} \HOLFreeVar{xs} \HOLSymConst{\HOLTokenLeq{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}}
+\HOLTokenTurnstile{} \HOLConst{GCONTEXT} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}\ensuremath{)} \HOLFreeVar{P}\ensuremath{)} \HOLFreeVar{xs} \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{xs} \HOLSymConst{\HOLTokenLeq{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}}
    \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-       \HOLConst{GCONTEXT} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P\sp{\prime}} \HOLSymConst{=} \HOLBoundVar{C\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}}
-       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
-\HOLConst{TRACE} ((\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}) \HOLBoundVar{Q}) \HOLFreeVar{xs} (\HOLBoundVar{C\sp{\prime}} \HOLBoundVar{Q})\hfill{[unfolding_lemma4]}
+\HOLConst{GCONTEXT} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{C\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}\ensuremath{)} \HOLBoundVar{Q}\ensuremath{)} \HOLFreeVar{xs} \ensuremath{(}\HOLBoundVar{C\sp{\prime}} \HOLBoundVar{Q}\ensuremath{)}\hfill{[unfolding_lemma4]}
 \end{small}
@@
    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{xs} \HOLBoundVar{l} \HOLBoundVar{P\sp{\prime}}.
-       \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{xs} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{UNIQUE_LABEL} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{xs} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{xs} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{UNIQUE_LABEL} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{xs\sp{\prime}} \HOLBoundVar{Q\sp{\prime}}.
            \HOLConst{TRACE} \HOLFreeVar{Q} \HOLBoundVar{xs\sp{\prime}} \HOLBoundVar{Q\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLBoundVar{xs\sp{\prime}} \HOLSymConst{\HOLTokenLeq{}} \HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenConj{}}
-           \HOLConst{UNIQUE_LABEL} (\HOLConst{label} \HOLBoundVar{l}) \HOLBoundVar{xs\sp{\prime}}\hfill{[contracts_AND_TRACE_label]}
+           \HOLConst{UNIQUE_LABEL} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \HOLBoundVar{xs\sp{\prime}}\hfill{[contracts_AND_TRACE_label]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}
+\HOLTokenTurnstile{} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{Q}
 \hfill{[UNIQUE_SOLUTION_OF_CONTRACTIONS]}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}.
-\HOLBoundVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{Q}
+\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Q}
 \hfill{[UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS]}

### 2019-09-04 ic-journal/sos.tex
Improved TeX output of "nil" (final changes on HOL side)

@@
 
-The type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'', accounting for the CCS
+The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'', accounting for the CCS
 syntax\footnote{The order of type variables $\alpha$ and $\beta$
@@
 such a calculus, the needed CCS type can be retrieved by instantiating the type
-variables $\alpha$ and $\beta$ in ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'' with types
+variables $\alpha$ and $\beta$ in ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' with types
 having the corresponding cardinalities $h$ and $k$. Monica Nesi goes
@@
 \hline
-\textbf{Operator} & \textbf{CCS Notation} & \textbf{HOL term} &
-                                                                \textbf{HOL (abbrev.)}\\
+\textbf{Operator} & \textbf{CCS notation} & \textbf{HOL term} &
+                                                                \textbf{\TeX{} output} \\
 \hline
-nil & $\textbf{0}$ & \HOLinline{\HOLConst{nil}} & \HOLinline{\HOLConst{nil}} \\
-prefix & $u.P$ & \texttt{prefix u P} & \HOLinline{\HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{P}} \\
+nil & $\textbf{0}$ & \texttt{nil} & \HOLinline{\HOLConst{\ensuremath{\mathbf{0}}}} \\
+prefix & $u.P$ & \texttt{prefix u P} & \HOLinline{\HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{P}} \\
 sum & $P + Q$ & \texttt{sum P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{Q}} \\
-parallel & $P \,\mid\, Q$ & \texttt{par P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{Q}} \\
-restriction & $(\nu\;L)\;P$ & \texttt{restr L P} & \HOLinline{\HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{P}}  \\
+parallel & $P \,\mid\, Q$ & \texttt{par P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{Q}} \\
+restriction & $(\nu\;L)\;P$ & \texttt{restr L P} & \HOLinline{\ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{P}}  \\
 recursion & $\recu A P$ & \texttt{rec A P} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P}}  \\
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E}\hfill\texttt{[PREFIX]}
+\HOLTokenTurnstile{} \HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E}\hfill\texttt{[PREFIX]}
 \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[SUM1]}
 \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[SUM2]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sp{\prime}}\hfill\texttt{[PAR1]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[PAR2]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} (\HOLConst{COMPL} \HOLFreeVar{l})\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
-   \HOLFreeVar{E} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sb{\mathrm{2}}}\hfill\texttt{[PAR3]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLFreeVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{=} \HOLConst{label} \HOLFreeVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{E\sp{\prime}}\hfill\texttt{[RESTR]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sp{\prime}}\hfill\texttt{[PAR1]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[PAR2]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLFreeVar{l}\ensuremath{)}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sb{\mathrm{2}}}\hfill\texttt{[PAR3]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLFreeVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+   \ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E\sp{\prime}}\hfill\texttt{[RESTR]}
 \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{rf}\hfill\texttt{[RELABELING]}
-\HOLTokenTurnstile{} [\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}/\HOLFreeVar{X}] \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[REC]}
+\HOLTokenTurnstile{} \ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[REC]}
 \end{alltt}
@@
 \begin{alltt}
-[\HOLFreeVar{E}/\HOLFreeVar{X}] \HOLConst{nil} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{nil}
-[\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] (\HOLFreeVar{u}\HOLSymConst{..}\HOLFreeVar{E}) \HOLSymConst{\HOLTokenDefEquality{}} \HOLFreeVar{u}\HOLSymConst{..}[\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] \HOLFreeVar{E}
-[\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] (\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenDefEquality{}} [\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} [\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] \HOLFreeVar{E\sb{\mathrm{2}}}
-[\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] (\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenDefEquality{}} [\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} [\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] \HOLFreeVar{E\sb{\mathrm{2}}}
-[\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] (\HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} ([\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] \HOLFreeVar{E})
-[\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] (\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{f}) \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{relab} ([\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] \HOLFreeVar{E}) \HOLFreeVar{f}
-[\HOLFreeVar{E}/\HOLFreeVar{X}] (\HOLConst{var} \HOLFreeVar{Y}) \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}
-[\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] (\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{=} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} ([\HOLFreeVar{E\sp{\prime}}/\HOLFreeVar{X}] \HOLFreeVar{E})\hfill{[CCS_Subst_def]}
+\ensuremath{[}\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{\ensuremath{\mathbf{0}}}
+\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}
+\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E\sb{\mathrm{2}}}
+\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E\sb{\mathrm{2}}}
+\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}
+\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{relab} \ensuremath{(}\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLFreeVar{rf}
+\ensuremath{[}\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{var} \HOLFreeVar{Y}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}
+\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} \ensuremath{(}\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\hfill{[CCS_Subst_def]}
 \end{alltt}
@@
 SOS rules are \emph{inductive 
-  definitions} on the tenary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL's
+  definitions} on the tenary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL's
 \texttt{Hol_reln} function.
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{E}.
-       \HOLConst{In} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}}
-       (\HOLBoundVar{u} \HOLSymConst{=} \HOLConst{In} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLSymConst{\HOLTokenDisj{}}
-        \HOLBoundVar{u} \HOLSymConst{=} \HOLConst{Out} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{In} \HOLStringLit{a}\HOLSymConst{..}\HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil}) \HOLSymConst{\HOLTokenDisj{}}
-       \HOLBoundVar{u} \HOLSymConst{=} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{nil} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{nil}\hfill{[Example.ex_A]}
+       \HOLConst{In} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}}
+       \ensuremath{(}\HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{In} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\HOLTokenDisj{}} \HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{Out} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{In} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
+       \HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}\hfill{[Example.ex_A]}
 \end{alltt}

### 2019-09-04 paper/HOLMultivariate.tex
Improved TeX output of "nil" (final changes on HOL side)

@@
 \newcommand{\HOLMultivariateDate}{04 Settembre 2019}
-\newcommand{\HOLMultivariateTime}{10:49}
+\newcommand{\HOLMultivariateTime}{13:47}
 \begin{SaveVerbatim}{HOLMultivariateDefinitionsCCSXXequationXXdef}
@@
        \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenEquiv{}}
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{FV} \HOLBoundVar{e} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs}) \HOLBoundVar{Es}
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{FV} \HOLBoundVar{e} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLBoundVar{Es}
 \end{SaveVerbatim}
@@
        \HOLConst{CCS_solution} \HOLBoundVar{R} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenEquiv{}}
-       \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}.
-\HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{e}) (\HOLConst{set} \HOLBoundVar{Xs})) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{LIST_REL} \HOLBoundVar{R} \HOLBoundVar{Ps} (\HOLConst{MAP} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{Es})
+       \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
+\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{LIST_REL} \HOLBoundVar{R} \HOLBoundVar{Ps} \ensuremath{(}\HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateDefinitionsCCSXXSUBSTXXdef}
-\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLConst{nil} \HOLSymConst{=} \HOLConst{nil}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{u} \HOLBoundVar{E}.
-\HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{=} \HOLBoundVar{u}\HOLSymConst{..}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{=}
-        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{=}
-        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{L} \HOLBoundVar{E}.
-\HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{=} \HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E} \HOLBoundVar{rf}.
-        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{=} \HOLConst{relab} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}) \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{X}.
-        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{=}
-        \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLBoundVar{fm} \HOLConst{'} \HOLBoundVar{X} \HOLKeyword{else} \HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{\HOLTokenConj{}}
+\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm}.
+\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{u} \HOLBoundVar{E}.
+\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
+        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
+        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{L} \HOLBoundVar{E}.
+\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLConst{nu} \HOLBoundVar{L} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{nu} \HOLBoundVar{L} \ensuremath{(}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E} \HOLBoundVar{rf}.
+        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{relab} \ensuremath{(}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{X}.
+        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLConst{var} \HOLBoundVar{X}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
+        \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLBoundVar{fm} \HOLConst{'} \HOLBoundVar{X} \HOLKeyword{else} \HOLConst{var} \HOLBoundVar{X}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{X} \HOLBoundVar{E}.
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLSymConst{=}
-       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\ensuremath{\setminus}} \HOLBoundVar{X}) \HOLBoundVar{E})
-       \HOLKeyword{else} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
+       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLBoundVar{X} \ensuremath{(}\HOLConst{CCS_SUBST} \ensuremath{(}\HOLBoundVar{fm} \HOLSymConst{\ensuremath{\setminus}} \HOLBoundVar{X}\ensuremath{)} \HOLBoundVar{E}\ensuremath{)}
+       \HOLKeyword{else} \HOLConst{rec} \HOLBoundVar{X} \ensuremath{(}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}.
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLSymConst{=}
-       (\HOLTokenLambda{}\HOLBoundVar{E}.
-            \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
-            \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. [\HOLBoundVar{t}/\HOLBoundVar{X}] \HOLBoundVar{E})) \HOLBoundVar{Xs})
+       \HOLConst{context} \HOLBoundVar{Xs} \HOLSymConst{\ensuremath{=}}
+       \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}.
+            \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+            \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
+\HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Xs}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps}.
-\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{FEMPTY} \HOLSymConst{|++} \HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})
+\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{FEMPTY} \HOLSymConst{|++} \HOLConst{ZIP} \ensuremath{(}\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLSymConst{=}
-       (\HOLTokenLambda{}\HOLBoundVar{E}.
-            \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
-            \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. [\HOLBoundVar{t}/\HOLBoundVar{X}] \HOLBoundVar{E})) \HOLBoundVar{Xs})
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLSymConst{\ensuremath{=}}
+       \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}.
+            \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+            \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
+\HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Xs}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{BV} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{BV} (\HOLConst{set} \HOLBoundVar{Ps}))
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{BV} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}
 \end{SaveVerbatim}
@@
        \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CCS_solution} \HOLBoundVar{R} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenImp{}}
-       (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs})
+       \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
-       \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})
+       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{fm}.
-\HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{FDOM} \HOLBoundVar{fm}) \HOLSymConst{\HOLTokenImp{}} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})
+\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{FDOM} \HOLBoundVar{fm}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXFEMPTY}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}. \HOLConst{CCS_SUBST} \HOLConst{FEMPTY} \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}. \HOLConst{CCS_SUBST} \HOLConst{FEMPTY} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{EVERY} (\HOLTokenLambda{}(\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{p}).
-\HOLConst{FV} \HOLBoundVar{p} \HOLConst{\HOLTokenSubset{}} \HOLTokenLeftbrace{}\HOLBoundVar{x}\HOLTokenRightbrace{}) (\HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})) \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{FOLDR} (\HOLTokenLambda{}(\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}) \HOLBoundVar{e}.
-[\HOLBoundVar{y}/\HOLBoundVar{x}] \HOLBoundVar{e}) \HOLBoundVar{E} (\HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})))
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{p}\ensuremath{)}.
+\HOLConst{FV} \HOLBoundVar{p} \HOLConst{\HOLTokenSubset{}} \HOLTokenLeftbrace{}\HOLBoundVar{x}\HOLTokenRightbrace{}\ensuremath{)} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{FOLDR} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}\ensuremath{)} \HOLBoundVar{e}.
+\ensuremath{[}\HOLBoundVar{y}\ensuremath{/}\HOLBoundVar{x}\ensuremath{]} \HOLBoundVar{e}\ensuremath{)} \HOLBoundVar{E} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{IS_PROC} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E})
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{IS_PROC} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{Es} \HOLBoundVar{C}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
-       (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{C}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] ([\HOLBoundVar{Es}/\HOLBoundVar{Xs}] \HOLBoundVar{C}) \HOLSymConst{=} [\HOLConst{MAP} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{Es}/\HOLBoundVar{Xs}] \HOLBoundVar{C})
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Es}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXnil}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLConst{nil} \HOLSymConst{=} \HOLConst{nil}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm}.
+\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{=}
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{u} \HOLBoundVar{E}.
-\HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{=} \HOLBoundVar{u}\HOLSymConst{..}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}
+\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{P}.
-       (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{P}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{P}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \HOLConst{IS_PROC} \HOLBoundVar{P} \HOLSymConst{\HOLTokenImp{}}
-       ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{P} \HOLSymConst{=} \HOLBoundVar{P})
+       \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{P} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{P}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{X} \HOLBoundVar{E}.
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLSymConst{=}
-       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\ensuremath{\setminus}} \HOLBoundVar{X}) \HOLBoundVar{E})
-       \HOLKeyword{else} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
+       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLBoundVar{X} \ensuremath{(}\HOLConst{CCS_SUBST} \ensuremath{(}\HOLBoundVar{fm} \HOLSymConst{\ensuremath{\setminus}} \HOLBoundVar{X}\ensuremath{)} \HOLBoundVar{E}\ensuremath{)}
+       \HOLKeyword{else} \HOLConst{rec} \HOLBoundVar{X} \ensuremath{(}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{Xs} \HOLBoundVar{P} \HOLBoundVar{Ps}.
-       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLBoundVar{X} \HOLConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLBoundVar{e}) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
+\HOLBoundVar{X} \HOLConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLBoundVar{e}\ensuremath{)} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-           \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs})) \HOLSymConst{\HOLTokenConj{}} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E\sp{\prime}}) \HOLSymConst{\HOLTokenImp{}}
-           ([\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}/\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} [\HOLBoundVar{P}/\HOLBoundVar{X}] \HOLBoundVar{E\sp{\prime}})
+           \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \ensuremath{(}\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+           \ensuremath{(}\ensuremath{[}\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{P}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E} \HOLBoundVar{rf}.
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{=} \HOLConst{relab} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}) \HOLBoundVar{rf}
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{relab} \ensuremath{(}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{rf}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{L} \HOLBoundVar{E}.
-\HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{=} \HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})
+\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLConst{nu} \HOLBoundVar{L} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{nu} \HOLBoundVar{L} \ensuremath{(}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{Xs}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       ([\HOLConst{MAP} \HOLConst{var} \HOLBoundVar{Xs}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \ensuremath{(}\ensuremath{[}\HOLConst{MAP} \HOLConst{var} \HOLBoundVar{Xs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-\HOLConst{CCS_SUBST} (\HOLConst{FEMPTY} \HOLSymConst{|+} (\HOLBoundVar{X}\HOLSymConst{,}\HOLBoundVar{E\sp{\prime}})) \HOLBoundVar{E} \HOLSymConst{=} [\HOLBoundVar{E\sp{\prime}}/\HOLBoundVar{X}] \HOLBoundVar{E}
+\HOLConst{CCS_SUBST} \ensuremath{(}\HOLConst{FEMPTY} \HOLSymConst{|+} \ensuremath{(}\HOLBoundVar{X}\HOLSymConst{,}\HOLBoundVar{E\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{E\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{=}
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{X}.
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{=}
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLConst{var} \HOLBoundVar{X}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
        \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLBoundVar{fm} \HOLConst{'} \HOLBoundVar{X} \HOLKeyword{else} \HOLConst{var} \HOLBoundVar{X}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXbackwardXXrules}
-\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
-\HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}}
+\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
+\HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
+\HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{nu} \HOLBoundVar{L} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
+\HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs})
+       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{C}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLConst{context} \HOLBoundVar{Xs}) \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
-       (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{context} \HOLBoundVar{Xs} ([\HOLBoundVar{Es}/\HOLBoundVar{Xs}] \HOLBoundVar{C})
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLConst{context} \HOLBoundVar{Xs}\ensuremath{)} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Es}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXnil}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}. \HOLConst{context} \HOLBoundVar{Xs} \HOLConst{nil}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}. \HOLConst{context} \HOLBoundVar{Xs} \HOLConst{\ensuremath{\mathbf{0}}}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}})
+       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E})
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs})
+       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
-\HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
-\HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
-\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf})
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{nu} \HOLBoundVar{L} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{nu} \HOLBoundVar{L} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E})
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{nu} \HOLBoundVar{L} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrules}
-\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}.
-\HOLConst{context} \HOLBoundVar{Xs} \HOLConst{nil}) \HOLSymConst{\HOLTokenConj{}} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y}.
-\HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{var} \HOLBoundVar{Y})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E})) \HOLSymConst{\HOLTokenConj{}}
+\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}.
+\HOLConst{context} \HOLBoundVar{Xs} \HOLConst{\ensuremath{\mathbf{0}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y}.
+\HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{var} \HOLBoundVar{Y}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{nu} \HOLBoundVar{L} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
-\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf})
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}})
+       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXvar}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y}. \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{var} \HOLBoundVar{Y})
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y}. \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{var} \HOLBoundVar{Y}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{e}) (\HOLConst{set} \HOLBoundVar{Xs})) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{DISJOINT} (\HOLConst{BV} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E})) (\HOLConst{set} \HOLBoundVar{Xs})
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
+\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}.
-       \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
        \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}.
-       \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
@@
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{X}.
-\HOLConst{MEM} \HOLBoundVar{E} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}.
-[\HOLBoundVar{t}/\HOLBoundVar{X}] \HOLBoundVar{E})
+\HOLConst{MEM} \HOLBoundVar{E} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps}.
-       (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       (\HOLConst{FDOM} (\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps}) \HOLSymConst{=} \HOLConst{set} \HOLBoundVar{Xs})
+       \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \ensuremath{(}\HOLConst{FDOM} \ensuremath{(}\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsfromListXXEMPTY}
-\HOLTokenTurnstile{} \HOLConst{fromList} [] [] \HOLSymConst{=} \HOLConst{FEMPTY}
+\HOLTokenTurnstile{} \HOLConst{fromList} \ensuremath{[}\ensuremath{]} \ensuremath{[}\ensuremath{]} \HOLSymConst{\ensuremath{=}} \HOLConst{FEMPTY}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{n}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{n} \HOLSymConst{\HOLTokenLt{}} \HOLConst{LENGTH} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}}
-       (\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLConst{'} (\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs}) \HOLSymConst{=} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps})
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{n} \HOLSymConst{\HOLTokenLt{}} \HOLConst{LENGTH} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}}
+       \ensuremath{(}\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLConst{'} \ensuremath{(}\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{P} \HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{n}.
-       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \HOLBoundVar{n} \HOLSymConst{\HOLTokenLt{}} \HOLConst{LENGTH} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}}
-       (\HOLConst{fromList} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}) (\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}) \HOLConst{'} (\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs}) \HOLSymConst{=} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps})
+       \ensuremath{(}\HOLConst{fromList} \ensuremath{(}\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}\ensuremath{)} \ensuremath{(}\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}\ensuremath{)} \HOLConst{'} \ensuremath{(}\HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{EL} \HOLBoundVar{n} \HOLBoundVar{Ps}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{Xs} \HOLBoundVar{P} \HOLBoundVar{Ps} \HOLBoundVar{n}.
-       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       (\HOLConst{fromList} (\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}) (\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}) \HOLConst{'} \HOLBoundVar{X} \HOLSymConst{=} \HOLBoundVar{P})
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \ensuremath{(}\HOLConst{fromList} \ensuremath{(}\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}\ensuremath{)} \ensuremath{(}\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}\ensuremath{)} \HOLConst{'} \HOLBoundVar{X} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{P}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{xs} \HOLBoundVar{y} \HOLBoundVar{ys}.
-       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{x} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{ys}) \HOLSymConst{\HOLTokenImp{}}
-       (\HOLConst{fromList} (\HOLBoundVar{x}\HOLSymConst{::}\HOLBoundVar{xs}) (\HOLBoundVar{y}\HOLSymConst{::}\HOLBoundVar{ys}) \HOLSymConst{=} \HOLConst{fromList} \HOLBoundVar{xs} \HOLBoundVar{ys} \HOLSymConst{|+} (\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}))
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{x} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{ys}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \ensuremath{(}\HOLConst{fromList} \ensuremath{(}\HOLBoundVar{x}\HOLSymConst{::}\HOLBoundVar{xs}\ensuremath{)} \ensuremath{(}\HOLBoundVar{y}\HOLSymConst{::}\HOLBoundVar{ys}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{fromList} \HOLBoundVar{xs} \HOLBoundVar{ys} \HOLSymConst{|+} \ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}\ensuremath{)}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{FV} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{FV} (\HOLConst{set} \HOLBoundVar{Ps}))
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{FV} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{FV} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}}
-       \HOLConst{FV} \HOLBoundVar{E} \HOLConst{DIFF} \HOLConst{set} \HOLBoundVar{Xs} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{FV} (\HOLConst{set} \HOLBoundVar{Ps}))
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLConst{\HOLTokenSubset{}}
+       \HOLConst{FV} \HOLBoundVar{E} \HOLConst{DIFF} \HOLConst{set} \HOLBoundVar{Xs} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{FV} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsLISTXXRELXXequivalence}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}. \HOLConst{equivalence} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \HOLConst{equivalence} (\HOLConst{LIST_REL} \HOLBoundVar{R})
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}.
+\HOLConst{equivalence} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \HOLConst{equivalence} \ensuremath{(}\HOLConst{LIST_REL} \HOLBoundVar{R}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{Qs}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \HOLConst{OBS_CONGR} \HOLBoundVar{Ps} \HOLBoundVar{Qs} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{OBS_CONGR} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E})
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{OBS_CONGR} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{Qs}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \HOLConst{OBS_contracts} \HOLBoundVar{Ps} \HOLBoundVar{Qs} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{OBS_contracts} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E})
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{OBS_contracts} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{Qs}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \HOLConst{STRONG_EQUIV} \HOLBoundVar{Ps} \HOLBoundVar{Qs} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{STRONG_EQUIV} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E})
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{STRONG_EQUIV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps}.
-           (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
+           \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{P\sp{\prime}}.
-               [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+               \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sp{\prime}}.
                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLBoundVar{E\sp{\prime}} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}}
-                   (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E\sp{\prime}}) \HOLSymConst{\HOLTokenConj{}}
+                   \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
                    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
-                       (\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-                       [\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd [\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E\sp{\prime}}
+                       \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+                       \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}
 \end{SaveVerbatim}
@@
            \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenImp{}}
-           (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{R}.
-                [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
+           \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{R}.
+                \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
                 \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLConst{contracts} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
-                    (\HOLConst{WEAK_EQUIV} \HOLConst{O} (\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}.
-\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{y}))
-                      ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}})) \HOLSymConst{\HOLTokenConj{}}
+                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLConst{contracts} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+                    \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLConst{O} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}.
+\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{y}\ensuremath{)}\ensuremath{)}
+                      \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}.
-               [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
+               \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLConst{contracts} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
-                   (\HOLConst{WEAK_EQUIV} \HOLConst{O} \HOLConst{EPS}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C}) ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}})
+                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLConst{contracts} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+                   \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLConst{O} \HOLConst{EPS}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{E} \HOLBoundVar{C\sb{\mathrm{0}}} \HOLBoundVar{Ps}.
-       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLConst{context} \HOLBoundVar{Xs}) \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLConst{context} \HOLBoundVar{Xs}\ensuremath{)} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
        \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}}
-       (\HOLBoundVar{E} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}.
-\HOLConst{MAP} [\HOLBoundVar{Ys}/\HOLBoundVar{Xs}] \HOLBoundVar{Es})) \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}.
-[\HOLBoundVar{Ys}/\HOLBoundVar{Xs}] \HOLFreeVar{C})) \HOLSymConst{\HOLTokenImp{}}
+       \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
+\HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
+\ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n}.
-\HOLConst{OBS_contracts} (\HOLBoundVar{C\sb{\mathrm{0}}} \HOLBoundVar{Ps}) ((\HOLBoundVar{C\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}) \HOLBoundVar{Ps})
+\HOLConst{OBS_contracts} \ensuremath{(}\HOLBoundVar{C\sb{\mathrm{0}}} \HOLBoundVar{Ps}\ensuremath{)} \ensuremath{(}\ensuremath{(}\HOLBoundVar{C\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}\ensuremath{)} \HOLBoundVar{Ps}\ensuremath{)}
 \end{SaveVerbatim}
@@
            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{u} \HOLBoundVar{P\sp{\prime}}.
-               (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-               \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{e}) (\HOLConst{set} \HOLBoundVar{Xs})) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-               [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+               \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+               \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
+\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+               \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}}) \HOLSymConst{\HOLTokenConj{}}
+                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
                    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
-                       (\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-                       [\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd [\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}}
+                       \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+                       \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}
 \end{SaveVerbatim}
@@
        \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}}
-       (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
-       (\HOLBoundVar{E} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}. \HOLConst{MAP} [\HOLBoundVar{Ys}/\HOLBoundVar{Xs}] \HOLBoundVar{Es})) \HOLSymConst{\HOLTokenImp{}}
+       \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
+\HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{x} \HOLBoundVar{P\sp{\prime}}.
-           (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-           \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{e}) (\HOLConst{set} \HOLBoundVar{Xs})) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-           [\HOLBoundVar{E} \HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+           \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+           \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
+\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+           \ensuremath{[}\HOLBoundVar{E} \HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
            \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}}) \HOLSymConst{\HOLTokenConj{}}
+               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
                \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
-                   (\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-                   [\HOLBoundVar{E} \HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd [\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime}}
+                   \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+                   \ensuremath{[}\HOLBoundVar{E} \HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}
 \end{SaveVerbatim}
@@
        \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{E} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}.
-\HOLConst{MAP} [\HOLBoundVar{Ys}/\HOLBoundVar{Xs}] \HOLBoundVar{Es})) \HOLSymConst{\HOLTokenConj{}}
-       (\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{=} (\HOLTokenLambda{}\HOLBoundVar{Ys}. [\HOLBoundVar{Ys}/\HOLBoundVar{Xs}] \HOLBoundVar{C})) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
+\HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
+\ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n} \HOLBoundVar{xs} \HOLBoundVar{Ps} \HOLBoundVar{P\sp{\prime}}.
-           (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-           \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{e}) (\HOLConst{set} \HOLBoundVar{Xs})) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-           \HOLConst{TRACE} ((\HOLBoundVar{C\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}) \HOLBoundVar{Ps}) \HOLBoundVar{xs} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenLeq{}} \HOLBoundVar{n} \HOLSymConst{\HOLTokenImp{}}
+           \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+           \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
+\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+           \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLBoundVar{C\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}\ensuremath{)} \HOLBoundVar{Ps}\ensuremath{)} \HOLBoundVar{xs} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenLeq{}} \HOLBoundVar{n} \HOLSymConst{\HOLTokenImp{}}
            \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime\prime}}.
-               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime\prime}} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{P\sp{\prime}} \HOLSymConst{=} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime\prime}}) \HOLSymConst{\HOLTokenConj{}}
+               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
                \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
-                   (\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-                   \HOLConst{TRACE} ((\HOLBoundVar{C\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}) \HOLBoundVar{Qs}) \HOLBoundVar{xs} ([\HOLBoundVar{Qs}/\HOLBoundVar{Xs}] \HOLBoundVar{C\sp{\prime\prime}})
+                   \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+                   \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLBoundVar{C\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}\ensuremath{)} \HOLBoundVar{Qs}\ensuremath{)} \HOLBoundVar{xs} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime\prime}}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXbackwardXXrules}
-\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y}.
-\HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{var} \HOLBoundVar{Y}) \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
-\HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}}
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}}
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
-\HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}}
+\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y}.
+\HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{var} \HOLBoundVar{Y}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
+\HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
+\HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{nu} \HOLBoundVar{L} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs})
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
 \end{SaveVerbatim}
@@
        \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
-       (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} ([\HOLBoundVar{Es}/\HOLBoundVar{Xs}] \HOLBoundVar{C})
+       \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Es}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXnil}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}. \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLConst{nil}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}. \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLConst{\ensuremath{\mathbf{0}}}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenEquiv{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}}
        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
@@
        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}})
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
-\HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E})
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs})
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E})
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf})
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
-\HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{nu} \HOLBoundVar{L} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
-\HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{nu} \HOLBoundVar{L} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
-\HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E})
+\HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{nu} \HOLBoundVar{L} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrules}
-\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}. \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLConst{nil}) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y}.
-\HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{var} \HOLBoundVar{Y})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}.
+\HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLConst{\ensuremath{\mathbf{0}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y}.
+\HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{var} \HOLBoundVar{Y}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{u} \HOLBoundVar{E}.
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
         \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
         \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
-\HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E})) \HOLSymConst{\HOLTokenConj{}}
-   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf})) \HOLSymConst{\HOLTokenConj{}}
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
+\HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{nu} \HOLBoundVar{L} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E})
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenEquiv{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}}
        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
@@
        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}})
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y}.
-\HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{var} \HOLBoundVar{Y}) \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs}
+\HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{var} \HOLBoundVar{Y}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y}.
-\HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{var} \HOLBoundVar{Y})
+\HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{var} \HOLBoundVar{Y}\ensuremath{)}
 \end{SaveVerbatim}

### 2019-09-04 ic-journal/response-letter.tex
Stage fixes with highlights

@@
 \begin{enumerate}
-\item \begin{quote}
-    This paper describes a HOL formalisation of several notions in
-    process theory: CCS and various kinds of bisimilarity, and in
-    particular the unique-solutions technique. The latter was
-    introduced by Milner, and recently revisited and refined by the
-    second author.
-  \end{quote}
+% \item \begin{quote}
+%     This paper describes a HOL formalisation of several notions in
+%     process theory: CCS and various kinds of bisimilarity, and in
+%     particular the unique-solutions technique. The latter was
+%     introduced by Milner, and recently revisited and refined by the
+%     second author.
+%   \end{quote}
 
-\item \begin{quote}
-    In general, these kinds of results are error-prone, especially
-    those related to weak bisimilarity: there are multiple known
-    mistakes in the literature. Therefore, formalisation is a
-    worthwile effort. Moreover, the formalisation itself is quite
-    readable. The paper itself documents this formalisation and is,
-    for the most part, clear.
-  \end{quote}
+% \item \begin{quote}
+%     In general, these kinds of results are error-prone, especially
+%     those related to weak bisimilarity: there are multiple known
+%     mistakes in the literature. Therefore, formalisation is a
+%     worthwile effort. Moreover, the formalisation itself is quite
+%     readable. The paper itself documents this formalisation and is,
+%     for the most part, clear.
+%   \end{quote}
 
-\item \begin{quote}
-    The paper is an extended version of an EXPRESS/SOS paper. The
-    extension consists of a more detailed report of the proofs -
-    perhaps this is enough.
-  \end{quote}
+% \item \begin{quote}
+%     The paper is an extended version of an EXPRESS/SOS paper. The
+%     extension consists of a more detailed report of the proofs -
+%     perhaps this is enough.
+%   \end{quote}
 
@@
 
+  Now we have additionally formalised the multivariate (i.e. multi-variable)
+  version of the \emph{unique solution of rooted contractions theorem}
+  (Theorem~\ref{t:rcontraBisimulationU}) and \emph{Milner's strong
+  unique-solution theorem} (Prop.~4.14 (2)
+  of~\citep[p.~103]{Mil89}), together with a detailed discussion on
+  multivariate contexts, weakly-guarded equations and multivariate
+  variable substitutions. This work consists of 4,000 lines of new
+  proof scripts, and it is indeed based on the existing framework in
+  the sense that, we do not need to change the CCS datatype definition
+  and any SOS rule. (c.f. Section~\ref{sec:multivariate} for more details.)
+
 \item \begin{quote}
@@
 
+  \hl{TODO}: I don't understand this comment. Is the referee indicating
+  that our uses of ``solutions'' wasn't accurate because we didn't
+  formalize their multivariate case?
+
 \item \begin{quote}
@@
 
+  Rephrased: ``We sometimes call the bisimulation and bisimilarity defined above
+the \emph{weak} bisimulation (and weak bisimilarity), ...''
+
 \item \begin{quote}
@@
   \end{quote}
+
+  We have fixed this typo (totally two instances in the paper, also in L92).
 

### 2019-09-04 ic-journal/expansion.tex
Enriched the proof of Theorem 3.14
Stage fixes with highlights

@@
 
-We sometimes call bisimilarity the \emph{weak} one, to
-distinguish it from \emph{strong} bisimilarity ($\sim$),
-obtained by replacing in the above definition   the weak answer $
-Q\Arcap\mu Q'$ with the strong  $Q \arr \mu Q'$.
+\hl{We sometimes call the bisimulation and bisimilarity defined above
+the \emph{weak} bisimulation (and weak bisimilarity), to
+distinguish it from the \emph{strong} bisimulation and strong bisimilarity} ($\sim$),
+obtained by replacing the weak transition $Q\Arcap\mu Q'$ in the above
+definition with the strong transition $Q \arr \mu Q'$ (same for the
+other case).
 Weak bisimilarity is not preserved by the sum operator (except for
@@
 
-Besides reducing the rooted bisimiarity of two processes to
+Besides reducing the rooted \hl{bisimilarity} of two processes to
 the bisimilarities of their immediate derivatives, the
 above definition also brings up a proof technique for proving rooted
-bisimiarity results  by constructing a bisimulation.
-\begin{lemma}%{(Rooted bisimilarity by constructing a bisimulation)}
+\hl{bisimilarity} results by constructing a bisimulation.
+\begin{lemma}[Rooted bisimilarity by bisimulation]
 \label{l:obsCongrByWeakBisim}
@@
    \Arr\mu Q'$ and $P' \RR Q'$;
-\item the converse of (1) on the actions from $Q$.
+\item $Q \arr\mu Q'$ \hl{implies that there is} $P'$ such that $P
+   \Arr\mu P'$ and $P' \RR Q'$.
 \end{enumerate}
-then $P$ and $Q$ are rooted bisimilar, i.e.~$P \approx^c Q$.
+\hl{Then} $P$ and $Q$ are rooted bisimilar, i.e.~$P \approx^c Q$.
 \end{lemma}

### 2019-09-04 ic-journal/sos.tex
Stage fixes with highlights

@@
 \hline
-\textbf{Operator} & \textbf{CCS notation} & \textbf{HOL term} &
+\hl{\textbf{CCS concept}} & \hl{\textbf{Notation}} & \textbf{HOL term} &
                                                                 \textbf{\TeX{} output} \\
 \hline
-nil & $\textbf{0}$ & \texttt{nil} & \HOLinline{\HOLConst{\ensuremath{\mathbf{0}}}} \\
+\hl{deadlock} & $\textbf{0}$ & \texttt{nil} & \HOLinline{\HOLConst{\ensuremath{\mathbf{0}}}} \\
 prefix & $u.P$ & \texttt{prefix u P} & \HOLinline{\HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{P}} \\
@@
 \hline
-constant & $A$ & \texttt{var A} & \HOLinline{\HOLConst{var} \HOLFreeVar{A}} \\
+\hl{variable} & $A$ & \texttt{var A} & \HOLinline{\HOLConst{var} \HOLFreeVar{A}} \\
 invisible action & $\tau$ & \texttt{tau} & \HOLinline{\HOLSymConst{\ensuremath{\tau}}} \\

### 2019-09-04 ic-journal/sos.tex
Enriched Table 1 + TeX outputs of "In/Out"

@@
  using HOL's powerful pretty printer, to represent CCS
-processes in more readable forms (c.f. the column ``HOL (abbrev.)''
+processes in more readable forms (c.f. the column \hl{``\TeX{} output''}
 of Table \ref{tab:ccsoperator}, which summarizes
@@
 \begin{center}
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|}
 \hline
 \hl{\textbf{CCS concept}} & \hl{\textbf{Notation}} & \textbf{HOL term} &
-                                                                \textbf{\TeX{} output} \\
+                                             \textbf{HOL abbrev.} & \hl{\textbf{\TeX{} output}} \\
 \hline
-\hl{deadlock} & $\textbf{0}$ & \texttt{nil} & \HOLinline{\HOLConst{\ensuremath{\mathbf{0}}}} \\
-prefix & $u.P$ & \texttt{prefix u P} & \HOLinline{\HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{P}} \\
-sum & $P + Q$ & \texttt{sum P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{Q}} \\
-parallel & $P \,\mid\, Q$ & \texttt{par P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{Q}} \\
-restriction & $(\nu\;L)\;P$ & \texttt{restr L P} & \HOLinline{\ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{P}}  \\
-recursion & $\recu A P$ & \texttt{rec A P} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P}}  \\
-relabeling & $P\;[r\!f]$ & \texttt{relab P rf} & \HOLinline{\HOLConst{relab} \HOLFreeVar{P} \HOLFreeVar{rf}}  \\
+\hl{deadlock} & $\textbf{0}$ & \texttt{nil} & \texttt{nil} & \HOLinline{\HOLConst{\ensuremath{\mathbf{0}}}} \\
+prefix & $\mu.P$ & \texttt{prefix u P} & \texttt{u..P} & \HOLinline{\HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{P}} \\
+\hl{summation} & $P + Q$ & \texttt{sum P Q} & \texttt{P + Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{Q}} \\
+parallel \hl{composition} & $P \,\mid\, Q$ & \texttt{par P Q} & \texttt{P || Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{Q}} \\
+restriction & $(\nu{}L)\;P$ & \texttt{restr L P} & \texttt{(nu L) P} & \HOLinline{\ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{P}}  \\
+recursion & $\recu A P$ & \texttt{rec A P} & \texttt{rec A P} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P}}  \\
+relabeling & $P\;[r\!f]$ & \texttt{relab P rf} &\texttt{relab P rf} & \HOLinline{\HOLConst{relab} \HOLFreeVar{P} \HOLFreeVar{rf}}  \\
+\hl{constant/variable} & $A$ & \texttt{var A} &\texttt{var A} & \HOLinline{\HOLConst{var} \HOLFreeVar{A}} \\
+invisible action & $\tau$ & \texttt{tau} & \texttt{tau} & \HOLinline{\HOLSymConst{\ensuremath{\tau}}} \\
+input action & $a$ & \texttt{label (name a)} &\texttt{In(a)} & \HOLinline{\HOLConst{\HOLTokenInputAct} \HOLFreeVar{a}} \\
+output action & $\outC a$ & \texttt{label (coname a)} & \texttt{Out(a)} & \HOLinline{\HOLConst{\HOLTokenOutputAct} \HOLFreeVar{a}} \\
 \hline
-\hl{variable} & $A$ & \texttt{var A} & \HOLinline{\HOLConst{var} \HOLFreeVar{A}} \\
-invisible action & $\tau$ & \texttt{tau} & \HOLinline{\HOLSymConst{\ensuremath{\tau}}} \\
-input action & $a$ & \texttt{label (name a)} & \HOLinline{\HOLConst{In} \HOLFreeVar{a}} \\
-output action & $\outC a$ & \texttt{label (coname a)} & \HOLinline{\HOLConst{Out} \HOLFreeVar{a}} \\
+\hl{variable substitution} & $E\{E'/X\}$ & \texttt{CCS_Subst E E' X} &
+                                           \texttt{[E'/X]  E} & \HOLinline{\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}} \\
+\hl{transition} & $P\overset{\mu}{\longrightarrow}Q$
+                       & \texttt{TRANS P u Q} & \texttt{P ---u-> Q} & \HOLinline{\HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{Q}} \\
+\hl{weak transition} & $P\overset{\mu}{\Longrightarrow}Q$
+                       & \texttt{WEAK\_TRANS P u Q} & \texttt{P ==u=> Q} & \HOLinline{\HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{Q}} \\
+\hl{$\epsilon$--transition} & $P\overset{\epsilon}{\Longrightarrow}Q$
+                       & \texttt{EPS P Q} & \texttt{EPS P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\HOLTokenEPS} \HOLFreeVar{Q}} \\
 \hline
@@
 \end{center}
-%\vspace{-1em}
-   \caption{Syntax of CCS operators, constant and actions}
+   \caption{Syntax of \hl{various CCS concepts in HOL}}
    \label{tab:ccsoperator}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{E}.
-       \HOLConst{In} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}}
-       \ensuremath{(}\HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{In} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{Out} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\HOLTokenDisj{}} \HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{Out} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{In} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
+       \HOLConst{\HOLTokenInputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}}
+       \ensuremath{(}\HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\HOLTokenDisj{}} \HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
        \HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}\hfill{[Example.ex_A]}

### 2019-09-05 ic-journal/sos.tex
Fixed proofs of Theorem 3.10 and 3.14 with pictures added

@@
 \hl{constant/variable} & $A$ & \texttt{var A} &\texttt{var A} & \HOLinline{\HOLConst{var} \HOLFreeVar{A}} \\
+\hline
 invisible action & $\tau$ & \texttt{tau} & \texttt{tau} & \HOLinline{\HOLSymConst{\ensuremath{\tau}}} \\
@@
 \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[PAR2]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLFreeVar{l}\ensuremath{)}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sb{\mathrm{2}}}\hfill\texttt{[PAR3]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLFreeVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-   \ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E\sp{\prime}}\hfill\texttt{[RESTR]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{rf}\hfill\texttt{[RELABELING]}
-\HOLTokenTurnstile{} \ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[REC]}
 \end{alltt}
+
+\begin{equation}
+\infer[\HOLRuleName{PAR3}]{\HOLinline{\HOLFreeVar{E} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sb{\mathrm{2}}}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}}&\HOLinline{\HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLFreeVar{l}\ensuremath{)}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{2}}}}}
+\end{equation}
+
+\begin{equation}
+\infer[\HOLRuleName{RESTR}]{\HOLinline{\ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E\sp{\prime}}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}}}&\HOLinline{\HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLFreeVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}}}
+\end{equation}
+
+\begin{equation}
+\infer[\HOLRuleName{RELABELING}]{\HOLinline{\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{rf}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}}}}
+\end{equation}
+
+\begin{equation}
+\infer[\HOLRuleName{REC}]{\HOLinline{\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}}}{\HOLinline{\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}}}
+\end{equation}
 
@@
 with action $u$, then $(\recu A P)$ has the same
-transition. In its definition, \texttt{CCS_Subst} is a recursive substutiion function
+transition. In its definition, \texttt{CCS_Subst} is a recursive \hl{substitution} function
 with the following long definition:
 \begin{alltt}
-\ensuremath{[}\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{\ensuremath{\mathbf{0}}}
+    \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{\ensuremath{\mathbf{0}}}
     \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}
@@
     \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{relab} \ensuremath{(}\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLFreeVar{rf}
-\ensuremath{[}\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{var} \HOLFreeVar{Y}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}
+    \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{var} \HOLFreeVar{Y}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E\sp{\prime}} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}
     \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} \ensuremath{(}\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\hfill{[CCS_Subst_def]}

### 2019-09-05 ic-journal/unique.tex
Fixed proofs of Theorem 3.10 and 3.14 with pictures added

@@
  \wb \ctp{\til Q}$.\footnote{There's no typo here: $\ct{\til Q} \Arcap{\mu} \wb \ctp{\til
-     Q}$ means $\exists {\til R}.\; \ct{\til Q} \Arcap{\mu} {\til R}
+     Q}$ means $\exists Q'.\; \ct{\til Q} \Arcap{\mu} Q'
    \wb \ctp{\til Q}$. Same as in Lemma~\ref{l:ruptocon}.}
@@
 
-\begin{theorem}[unique solution of contractions for $\wb$]
-\label{t:contraBisimulationU}
-A system of weakly-guarded contractions
-having only weakly-guarded sums, has a unique solution for $\wb$.
+\begin{theorem}[unique solution of contractions~\cite{sangiorgi2017equations}] % for $\wb$
+\label{t:contraBisimulationU} % Thm 3.10
+%A system of weakly-guarded contractions
+%having only weakly-guarded sums, has a unique solution for $\wb$.
+\hl{Let the expressions $E_i$ ($i \in I$) contain at most the
+  variables $X_i$ ($i \in I$), and let each $X_j$ ($j\in I$) be weakly
+  guarded in each $E_i$. For any two groups of CCS processes $P_i$ and
+  $Q_i$ ($i \in I$), if $\til P \mcontrBIS \til E\{\til P/\til X\}$ and
+    $\til Q \mcontrBIS \til E\{\til Q/\til X\}$ then $\til P \wb \til Q$.}
 \end{theorem}
 
-\begin{proof}{(sketch from \cite{sangiorgi2017equations})}
-Suppose $\til P$ and $\til Q$ are two such solutions (for $\wb$) and consider
-the relation
-\begin{equation}
-\label{eq:R}
-\R \DSdefi \{ 
-(R,S) \st R \wb \ct{\til P}, S \wb \ct{\til Q} \mbox{ for some context
+\begin{proof}
+\hl{We want to prove $P_i \wb Q_i$ ($i \in I$) by considering} the following relation
+\begin{equation*}
+%\label{eq:R}
+\R \DSdefi \{(R,S) \st R \wb \ct{\til P}, S \wb \ct{\til Q} \mbox{~for some context
 $\qct$ (weakly-guarded sum only)} \} \enspace.
-\end{equation}
-We show that $\R$ is a bisimulation. Suppose $R\ \R\ S$ vis the context
-$C$, and $R \arr{\mu} R'$. We have to find $S'$ with $S \Arcap{\mu}
-S'$ and $R'\ \R\ S'$. From $R \wb C[{\til P}]$, we derive $C[{\til P}]
-\Arcap{\mu} R'' \wb R'$ for some $R''$. By Lemma~\ref{l:uptocon},
-there is $C'$ with $R'' \mcontrBIS C'[{\til P}]$ and $C[{\til Q}]
-\Arcap{\mu} \wb C'[{\til Q}]$. Hence, by definition of $\wb$, there is
-also $S'$ with $S \Arcap{\mu} S' \wb C'[{\til Q}]$. This closes the
-proof, as we have $R' \wb C'[{\til P}]$ and $S' \wb C'[{\til Q}]$.
+\end{equation*}
+
+\hl{Obviously we have $(P_i,Q_i) \in \R$ (by taking $C \equiv E_i$, and
+the fact that $\mcontrBIS$ implies $\wb$). It remains to}
+show that $\R$ is a bisimulation. Suppose \hl{$(R, S) \in \R$ via} a context
+$C$. \hl{For any $R'$ such that $R \arr{\mu} R'$, we have to find a} $S'$ with $S \Arcap{\mu}
+S'$ and $(R', S' \in \R$. From $R \wb C[{\til P}]$, we derive $C[{\til P}]
+\Arcap{\mu} R'' \wb R'$ for some $R''$. Then by Lemma~\ref{l:uptocon},
+there exists $C'$ with $R'' \mcontrBIS C'[{\til P}]$ and $C[{\til Q}]
+\Arcap{\mu} S'' \wb C'[{\til Q}]$ for some $S''$. \hl{From $S \wb C[{\til
+  Q}]$ and $C[{\til Q}] \Arcap{\mu} S''$, by induction and definition of $\wb$, it is not
+hard to see that,}
+there exists also $S'$ with $S \Arcap{\mu} S'$. This closes the
+proof, as we have $R' \wb C'[{\til P}]$ and $S' \wb C'[{\til Q}]$ \hl{by
+transitivity of $\wb$ and the fact that $\mcontrBIS$ implies $\wb$.
+(The other side from $S$ follows in the same manner.)}
+c.f. Fig.~\ref{fig:310} \hl{for a visual illustration.}
 \end{proof}
+
+\begin{figure}[ht]
+\begin{displaymath}
+  \xymatrix{
+    {C[{\til P}]} \ar@{.}[r]^{\wb} \ar@{=>}[d]^{\widehat{\mu}} & {R} \ar@{-}[r]
+    \ar@{->}[d]^{\mu} & {\R} \ar@{-}[r] & {S} \ar@{.}[r]^{\wb}
+    \ar@{=>}[d]^{\widehat{\mu}} & {C[{\til Q}]} \ar@{=>}[d]^{\widehat{\mu}} \\
+    {R''} \ar@{.}[d]_{\mcontrBIS} \ar@{.}[r]^{\wb} & {R'} \ar@{-}[r]
+    \ar@{.}[ld]^{\wb} & {\R} \ar@{-}[r] & {S'} \ar@{.}[r]^{\wb} \ar@{.}[rd]_{\wb}
+    & {S''} \ar@{.}[d]^{\wb} \\
+    {C'[{\til P}]} & {} & {} & {} & {C'[{\til Q}]}
+  }
+\end{displaymath}
+\caption{Proof illustration of Theorem~\ref{t:contraBisimulationU}
+  (showing $\R$ is a bisimulation)}
+\label{fig:310}
+\end{figure}
 
@@
 
-\begin{theorem}[Unique solution of contractions for $\rapprox$]
+\begin{theorem}[Unique solution of \hl{rooted} contractions]
 \label{t:rcontraBisimulationU}
-A system of weakly-guarded contractions has a unique solution 
- for $\rapprox$. % (thus also for $\wb$).
+%A system of weakly-guarded contractions has a unique solution for $\rapprox$. 
+% (thus also for $\wb$).
+\hl{Let the expressions $E_i$ ($i \in I$) contain at most the
+  variables $X_i$ ($i \in I$), and let each $X_j$ ($j\in I$) be weakly
+  guarded in each $E_i$. For any two groups of CCS processes $P_i$ and
+  $Q_i$ ($i \in I$), if $\til P \rcontr \til E\{\til P/\til X\}$ and
+    $\til Q \rcontr \til E\{\til Q/\til X\}$ then $\til P \rapprox \til Q$.}
 \end{theorem}
@@
 \begin{proof}
-Suppose $\til P$ and $\til Q$ are two such solutions: $\til P \rcontr
-C[{\til P}]$ and $\til Q \rcontr C[{\til Q}]$ (thus also $\til P \wb
-C[{\til P}]$ and $\til Q \wb C[{\til Q}]$). We first follow the same steps as in the proof of
-Theorem~\ref{t:contraBisimulationU} to show that the following
-relation is bisimulation 
-(using 
-Lemma~\ref{l:ruptocon}
-in place of  Lemma~\ref{l:uptocon}):
-\begin{equation}
-\label{eq:R2}
-\R \DSdefi \{ 
-(R,S) \st R \wb \ct{\til P}, S \wb \ct{\til Q} \mbox{ for some context
+\hl{We want to prove $P_i \rapprox Q_i$ ($i \in I$) by considering}
+the following relation
+\begin{equation*}
+\R \DSdefi \{(R,S) \st R \wb \ct{\til P}, S \wb \ct{\til Q} \mbox{~for some context
 $\qct$} \} \enspace.
-\end{equation}
-The property that $\R$ is a bisimulation  proves  $\til P$ and $\til Q$ bisimilar, i.e.,
-  $\til P \wb \til Q$.  To further prove
-$\til P \rapprox \til Q$, we  appeal to
-Lemma~\ref{l:obsCongrByWeakBisim}. Thus it remains to show that, for 
-any two process $P$ and $Q$ and action $\mu$, if $P \arr{\mu} P'$ then
-there is $Q'$ such that $Q \Arr{\mu} Q'$  and
-$P'\ \R\ Q'$ (and  the converse direction).  The prove for this
-part is routine,  using 
-Lemma 3.13 of \cite{Mil89},  reported as 
-Lemma~\ref{lem:313} in Section~\ref{ss:part2} (the lemma is  also needed 
-in  Milner's  proof of ``unique solution of equations for $\sim$'').
+\end{equation*}
+
+Following the same steps in the proof of
+Theorem~\ref{t:contraBisimulationU}
+(using Lemma~\ref{l:ruptocon}
+in place of Lemma~\ref{l:uptocon}), \hl{we can prove that $(P_i, Q_i)
+\in\R$ and $\R$ is indeed a bisimulation. But this only shows $P_i \wb Q_i$.}
+%
+To further show $P_i \rapprox Q_i$, we appeal to
+Lemma~\ref{l:obsCongrByWeakBisim}: \hl{for any $P'$ such that $P_i \arr{\mu} P'$, we have to
+  find a $Q'$ with $Q_i \Arr{\mu} Q'$ and $(R',S') \in \R$.
+%
+From $P_i \rcontr E_i[{\til P}]$, by definition of $\rcontr$ we derive $E_i[{\til P}] \arr{\mu}
+P''$ for some $P''$.} Then by Lemma 3.13 of~\citep[p.~102]{Mil89}
+(c.f. also Lemma~\ref{lem:313} in Section~\ref{ss:part2}) \hl{there exists
+a context
+$C$ with $P'' = C[{\til P}]$ and $E_i[{\til Q}] \arr{\mu} C[{\til Q}]$.
+From $Q_i \rcontr E_i[{\til Q}]$ and $E_i[{\til Q}] \arr{\mu} C[{\til
+  Q}]$, by definition of $\rcontr$ we have $Q_i \Arr{\mu} Q'$ for some
+$Q'$ and $Q' \wb C[{\til Q}]$. This closes the proof, as we have
+$P' \wb C[{\til P}]$ (by the fact that $\mcontrBIS$ implies $\wb$) and
+$Q' \wb C[{\til Q}]$. (The other side from $Q_i$ follows in the same manner.)}
+c.f. Fig.~\ref{fig:314} \hl{for a visual illustration.}
 \end{proof}
+
+\begin{figure}[ht]
+\begin{displaymath}
+  \xymatrix{
+    {E_i[{\til P}]} \ar@{.}[r]^{\preceq^{\mathrm{c}}_{\mathrm{bis}}} \ar@{->}[d]^{\mu} & {P_i} \ar@{-}[r]
+    \ar@{->}[d]^{\mu} & {\R} \ar@{-}[r] & {Q_i} \ar@{.}[r]^{\rcontr}
+    \ar@{=>}[d]^{\mu} & {E_i[{\til Q}]} \ar@{->}[d]^{\mu} \\
+    {C[{\til P}] = P''} \ar@{.}[r]^{\qquad\preceq_{\mathrm{bis}}} & {P'} \ar@{-}[r] & {\R} \ar@{-}[r] & {Q'} \ar@{.}[r]^{\wb} 
+    & {C[{\til Q}]} \\
+  }
+\end{displaymath}
+\caption{Proof illustration of Theorem~\ref{t:rcontraBisimulationU}
+  (showing $P_i \rapprox Q_i$)}
+\label{fig:314}
+\end{figure}

### 2019-09-05 ic-journal/response-letter.tex
Fixed proofs of Theorem 3.10 and 3.14 with pictures added
Stage work fixing paper

@@
 
+  We have rephrased this proof (also the theorem statements) with a
+  picture (Fig.~\ref{fig:310} illustrating the proof. The "Hence" part
+  actually used a property of $\wb$ that can be easily proven by induction
+  on each $\tau$-transition in a weak transition.
+
 \item \begin{quote}
@@
   \end{quote}
+
+  Rephrased: ``... because all we need from $\mcontrBIS$ (or
+$\rcontr$) is their substitutivity properties (as precongruences)
+w.r.t the corresponding definitions of contexts.''
 
@@
 
+  We have recalled Lemma 3.13 of \cite{Mil89} as
+  Lemma~\ref{lem:milner313} right before Theorem 3.13, which now becomes Theorem~\ref{t:rcontraBisimulationU}).
+
 \item \begin{quote}
@@
   \end{quote}
+  Done.
 
@@
 
+  Now we used the following sentence: ``As a consequence, theories and proofs verified in HOL are relatively more
+  convincible to non-experts.''
+
 \item \begin{quote}
@@
   \end{quote}
+
+  Sentence eliminated as now we have formalized the multivariate
+  version of unique-solution theorems. The ``without loss of
+  generality'' part is actually true, in the sense that, all steps of
+  informal proofs do appears in the uni-variate formal proofs. The
+  additional difficulities of the formal multivariate proof is discussed in Section~\ref{sec:multivariate}.
 
@@
 
+  The original HOL definition of the type Action is now given.
+
 \item \begin{quote}
@@
   \end{quote}
+  Sentences removed. In HOL, single and double backquotes are
+  delimitator between ``inner'' (logic) and ``outer'' (proof)
+  languages but this is not quite relevant to the present paper.
+  After new HOL releases (k13) most uses of backquotes in  definitions can be eliminated.
 
@@
   \end{quote}
+  Fixed.
 
@@
   \end{quote}
+  Now we have removed most less-interesting cases and explained in
+  details the two interesting cases (recursion operator and (free) variables).
 
@@
 
+  Rephrased: ``Many lemmas about above concepts (\texttt{CONTEXT}, \texttt{WG},
+  \texttt{SEQ}, etc.)''
+
 \item \begin{quote}
@@
   \end{quote}
+  Fixed. Now we say ``One highlight...''.
 

### 2019-09-05 ic-journal/context.tex
Stage work fixing paper

@@
 
-Many lemmas have then to be proved for the
+\hl{Many lemmas about above concepts} (\HOLinline{\HOLConst{CONTEXT}}, \HOLinline{\HOLConst{WG}},
+\HOLinline{\HOLConst{SEQ}}, etc.) have then to be proven for the
  relationships among these kinds of contexts and properties about their
- compositions. These proofs are usually tedious but long,  due to multiple levels of
+ compositions. These proofs are usually tedious and long,  due to multiple levels of
  inductions on the structure of the contexts.

### 2019-09-05 ic-journal/formal.tex
Stage work fixing paper

@@
 \cite{gordon1979edinburgh,milner1972logic} by Robin Milner and others
-since 1972, it is a variant of
-Church’s simple theory of types (STT) \cite{church1940formulation},
+since \hl{1972. It} is a variant of
+Church’s Simple Theory of Types (STT)~\cite{church1940formulation},
 plus a higher order version of Hilbert's choice operator $\varepsilon$,
 Axiom of Infinity, and Rank-1 (prenex) polymorphism.
-HOL4 has implemented the original HOL Logic, 
+HOL4 has implemented the original HOL, 
 while some other theorem provers in HOL family (e.g. Isabelle/HOL) have
@@
 % inconsistent). 
-Indeed the HOL Logic has considerable simpler logical
+Indeed the HOL has \hl{considerably} simpler logical
 foundations than most other theorem provers. %, e.g. Coq. 
-As a consequence,
-formal theories built in HOL is easily convincible and can
-also be easily ported to other proof systems,
-sometimes automatically \cite{hurd2011opentheory}.
+\hl{As a consequence, theories and proofs verified in HOL are relatively more
+convincible to non-experts.}
 
@@
 
-\emph{In this
-formalisation we consider only single-variable equations/contractions.}
-This considerably
- simplifies the required proofs in HOL, and  enhances the readability of
- proof scripts without loss of generality. For the  pencil-and-paper proofs, the
- multi-variable case is just a routine adaptation, while the
- formalisation in theorem prover % \DDS{}
- is not (this is also discussed in Section~\ref{s:concl}).
+%% [Chun]: cancelled this part as now we have multivariate formal proofs!
+% \emph{In this
+% formalisation we consider only single-variable equations/contractions.}
+% This considerably
+%  simplifies the required proofs in HOL, and  enhances the readability of
+%  proof scripts without loss of generality. For the  pencil-and-paper proofs, the
+%  multi-variable case is just a routine adaptation, while the
+%  formalisation in theorem prover % \DDS{}
+%  is not (this is also discussed in Section~\ref{s:concl}).
 

### 2019-09-05 ic-journal/sos.tex
Stage work fixing paper

@@
 \begin{lstlisting}
-val _ = Datatype `Label = name 'b | coname 'b`;
+Datatype: Label = name 'b | coname 'b
+End
 \end{lstlisting}
 The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
-union of all visible actions, plus invisible action $\tau$ (now based on
-HOL's \texttt{option} theory). The cardinality of
+union of all visible actions, plus invisible action $\tau$. It's
+defined as an abbreviation of HOL's core type ``\HOLinline{\ensuremath{\alpha} \HOLTyOp{option}}'' instantiated
+with the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'':
+\begin{lstlisting}
+Type Action[pp] = ``:'b Label option``;
+\end{lstlisting}
+The cardinality of
 ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' (and therefore of all
@@
 (\texttt{'a} or $\alpha$ is the type variable for recursion variables,
-``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling functions,
-\mbox{\color{blue}{\texttt{`}}} is for backquotes of HOL terms):
+``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling functions):
 \begin{lstlisting}
-val _ = Datatype `CCS = nil
+Datatype: CCS = nil
               | var 'a
@@
               | relab CCS ('b Relabeling)
-		      | rec 'a CCS`;
+              | rec 'a CCS
+End
 \end{lstlisting}
@@
 with action $u$, then $(\recu A P)$ has the same
-transition. In its definition, \texttt{CCS_Subst} is a recursive \hl{substitution} function
-with the following long definition:
+transition. Here, ``\HOLinline{\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}}'' is \hl{an abbreviation}
+of ``\HOLinline{\HOLConst{CCS_Subst} \HOLFreeVar{E} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{)} \HOLFreeVar{X}}'', where \HOLinline{\HOLConst{CCS_Subst}} is a
+recursive function substituting all appearences of a free variable
+into another CCS term.
+For most CCS operators \HOLinline{\HOLConst{CCS_Subst}} just recursively goes into a deeper
+level without changing anything, e.g.
 \begin{alltt}
-    \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{\ensuremath{\mathbf{0}}}
-    \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}
-    \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E\sb{\mathrm{2}}}
-    \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E\sb{\mathrm{2}}}
-    \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}
-    \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{relab} \ensuremath{(}\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLFreeVar{rf}
-    \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{var} \HOLFreeVar{Y}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E\sp{\prime}} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}
-    \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} \ensuremath{(}\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\hfill{[CCS_Subst_def]}
+\HOLTokenTurnstile{} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E\sb{\mathrm{2}}}\hfill{[CCS_Subst_sum]}
 \end{alltt}
+The only two insteresting cases are for the recursion operator and
+recursion variables:
+\begin{alltt}
+\HOLTokenTurnstile{} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} \ensuremath{(}\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\hfill{[CCS_Subst_rec]}
+\HOLTokenTurnstile{} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{var} \HOLFreeVar{Y}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E\sp{\prime}} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}\hfill{[CCS_Subst_var]}
+\end{alltt}
+\hl{Intuitively, the variable substitutions only happens on \emph{free}
+variables: the variable $Y$ in} ``\HOLinline{\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}}'' \hl{is
+considered \emph{bound} and the substitution process ignores it if $Y$ is
+being substituted. The actual substitution happens in case of}
+``\HOLinline{\HOLConst{var} \HOLFreeVar{Y}}'' if $Y$ is being substituted (and if \HOLinline{\HOLConst{CCS_Subst}}
+can actually reach it).
 
@@
 is called on the  process $(a.0 | \bar{a}.0)$ thus:
-(\mbox{\color{blue}{\texttt{``}}} is for double-backquotes of HOL
-  terms, \mbox{\color{blue}{\texttt{>}}} is HOL's prompt)
 \begin{lstlisting}

### 2019-09-05 ic-journal/unique.tex
Stage work fixing paper

@@
 
-% The system use \emph{weakly-guarded sums} if 
+% The system use \emph{guarded sums} if 
 % each $E_i$ only makes use of guarded sums.
@@
  of a system of weakly-guarded contractions that uses 
-weakly-guarded sums.
+guarded sums.
 For any context $\qct$  that uses 
-weakly-guarded sums,
-if  $\ct{\til P}\Arr{\mu}  R$,
- then 
-there is a context $\qctp$  that uses 
-weakly-guarded sums
-such that $R \mcontrBIS \ctp{\til P}$ and $\ct{\til Q} \Arcap{\mu}
- \wb \ctp{\til Q}$.\footnote{There's no typo here: $\ct{\til Q} \Arcap{\mu} \wb \ctp{\til
-     Q}$ means $\exists Q'.\; \ct{\til Q} \Arcap{\mu} Q'
-   \wb \ctp{\til Q}$. Same as in Lemma~\ref{l:ruptocon}.}
+guarded sums,
+if  $\ct{\til P}\Arr{\mu}  R$, then there is a context $\qctp$  that uses 
+guarded sums
+such that $R \mcontrBIS \ctp{\til P}$ and $\ct{\til Q} \Arcap{\mu} R'
+ \wb \ctp{\til Q}$ \hl{for some $R'$}.
 \end{lemma}
@@
 underneath at least $n$ prefixes, and cannot contribute to an action
-in the first $n$ transitions; moreover all the contexts have only
-weakly-guarded sums.
+in the first $n$ transitions; moreover all the contexts use guarded sums.
 
@@
  since each hole of the  context $\qctpp$ is underneath at least $n$
- prefixes, applying  
-the definition
+ prefixes, applying the definition
  of $ \mcontrBIS$ on the transition 
@@
  of $\qctp$ such that 
-$
-\ctpp{\til P}\Arcap{\mu} \ctp{\til P} \mexpaBIS R
-$
+$\ctpp{\til P}\Arcap{\mu} \ctp{\til P} \mexpaBIS R$
 and 
-$
-\ctpp{\til Q}\Arcap{\mu}  \ctp{\til Q} 
-. $
+$\ctpp{\til Q}\Arcap{\mu}  \ctp{\til Q}$.
 Finally, again applying the definition of $\mcontrBIS$ on 
@@
 we derive 
-$
-\ct{\til Q}\Arcap{\mu}  \wb \ctp{\til Q} 
-.$
+$\ct{\til Q}\Arcap{\mu} R' \wb \ctp{\til Q}$ \hl{for some $R'$}.
 \end{proof}
@@
 %A system of weakly-guarded contractions
-%having only weakly-guarded sums, has a unique solution for $\wb$.
+%having only guarded sums, has a unique solution for $\wb$.
 \hl{Let the expressions $E_i$ ($i \in I$) contain at most the
@@
 \R \DSdefi \{(R,S) \st R \wb \ct{\til P}, S \wb \ct{\til Q} \mbox{~for some context
-$\qct$ (weakly-guarded sum only)} \} \enspace.
+$\qct$ (\hl{with only guarded sums})} \} \enspace.
 \end{equation*}
@@
 $C$. \hl{For any $R'$ such that $R \arr{\mu} R'$, we have to find a} $S'$ with $S \Arcap{\mu}
-S'$ and $(R', S' \in \R$. From $R \wb C[{\til P}]$, we derive $C[{\til P}]
+S'$ and $(R', S') \in \R$. From $R \wb C[{\til P}]$, we derive $C[{\til P}]
 \Arcap{\mu} R'' \wb R'$ for some $R''$. Then by Lemma~\ref{l:uptocon},
@@
 there is a  context $\qctp$
-such that $R \mcontrBIS \ctp{\til P}$ and  $\ct{\til Q} \Arr{\mu}
- \wb \ctp{\til Q}$.
+such that $R \mcontrBIS \ctp{\til P}$ and  $\ct{\til Q} \Arr{\mu} R'
+ \wb \ctp{\til Q}$ \hl{for some $R'$}.
 \end{lemma}
 The proof of Lemma~\ref{l:ruptocon} is exactly the same as of
-Lemma~\ref{l:uptocon}, because all we need from $\mcontrBIS$ and
-$\rcontr$ is their precongruences (in the sense of different
-definitions of contexts). Also notice that, the conclusion of
-Lemma~\ref{l:ruptocon} still uses $\mcontrBIS$, because $\rcontr$ does
+Lemma~\ref{l:uptocon}, \hl{because all we need from $\mcontrBIS$ (or
+$\rcontr$) is their substitutivity properties (as precongruences)
+w.r.t the corresponding definitions of contexts.}
+Notice also that, the conclusion of
+Lemma~\ref{l:ruptocon} still uses $\mcontrBIS$, as $\rcontr$ does
 not hold.
+
+\hl{The next lemma is actually Lemma 3.13} of~\citep[p.~102]{Mil89}, \hl{which
+was designed to prove Milner's strong unique-solution theorem} (Prop.~3.14 of
+\citep[p.~103]{Mil89}).
+\begin{lemma}
+  \label{lem:milner313}
+  If the variables ${\til X}$ are weakly guarded in $E$, and $E\{\til
+  P/\til X\} \arr{\alpha} P'$, then $P'$ takes the form $E'\{\til
+  P/\til X\}$ (for some expression $E'$), and moreover, for any ${\til Q}$,
+  $E\{\til Q/\til X\} \arr{\alpha} E'\{\til Q/\til X\}$.
+\end{lemma}
 
@@
 From $P_i \rcontr E_i[{\til P}]$, by definition of $\rcontr$ we derive $E_i[{\til P}] \arr{\mu}
-P''$ for some $P''$.} Then by Lemma 3.13 of~\citep[p.~102]{Mil89}
-(c.f. also Lemma~\ref{lem:313} in Section~\ref{ss:part2}) \hl{there exists
-a context
-$C$ with $P'' = C[{\til P}]$ and $E_i[{\til Q}] \arr{\mu} C[{\til Q}]$.
-From $Q_i \rcontr E_i[{\til Q}]$ and $E_i[{\til Q}] \arr{\mu} C[{\til
+P''$ for some $P''$.} Then by Lemma~\ref{lem:milner313} there exists a context
+$E'$ with $P'' = E'[{\til P}]$ and $E_i[{\til Q}] \arr{\mu} E'[{\til Q}]$.
+%
+From $Q_i \rcontr E_i[{\til Q}]$ and $E_i[{\til Q}] \arr{\mu} E'[{\til
   Q}]$, by definition of $\rcontr$ we have $Q_i \Arr{\mu} Q'$ for some
-$Q'$ and $Q' \wb C[{\til Q}]$. This closes the proof, as we have
+$Q'$ and $Q' \wb E'[{\til Q}]$. This closes the proof, as we have
 $P' \wb C[{\til P}]$ (by the fact that $\mcontrBIS$ implies $\wb$) and
-$Q' \wb C[{\til Q}]$. (The other side from $Q_i$ follows in the same manner.)}
+$Q' \wb C[{\til Q}]$. (The other side from $Q_i$ follows in the same manner.)
 c.f. Fig.~\ref{fig:314} \hl{for a visual illustration.}
@@
     \ar@{=>}[d]^{\mu} & {E_i[{\til Q}]} \ar@{->}[d]^{\mu} \\
-    {C[{\til P}] = P''} \ar@{.}[r]^{\qquad\preceq_{\mathrm{bis}}} & {P'} \ar@{-}[r] & {\R} \ar@{-}[r] & {Q'} \ar@{.}[r]^{\wb} 
-    & {C[{\til Q}]} \\
+    {P'' = E'[{\til P}]} \ar@{.}[r]^{\qquad\preceq_{\mathrm{bis}}} & {P'} \ar@{-}[r] & {\R} \ar@{-}[r] & {Q'} \ar@{.}[r]^{\wb} 
+    & {E'[{\til Q}]} \\
   }

### 2019-09-05 ic-journal/response-letter.tex
Stage work revising the IC paper

@@
   \end{quote}
-
-  \hl{TODO}: I don't understand this comment. Is the referee indicating
-  that our uses of ``solutions'' wasn't accurate because we didn't
-  formalize their multivariate case?
+  Fixed.
 
@@
   \end{quote}
+  Fixed. ``... what kind of binary relations on CCS process are (strong) bisimulations.''
 
@@
   \end{quote}
+  Fixed (``the definition of (strong) bisimilarity``).
 
@@
   \end{quote}
+  All formal theorems and definitions are generated from HOL4.
+  By default, all theorems are fully specialised, removing outermost
+  universal quantifiers. For certain important theorems like this one,
+  now we have disabled the specialization showing outermost
+  universal quantifiers.
 
@@
   \end{quote}
+
+  Rephrased: ``The definition of weak bisimulation is based on weak
+  and $\epsilon$--transitions:''
 
@@
   \end{quote}
+TODO (remove the duplicated part of weak bisimulation, mergin into the
+strong case).
 
@@
   \end{quote}
+  This is no big problem here, as we are talking about any relation
+  (which is a contraction) is not in general a bisimulation. However
+  we have removed the word ``a'', having just: ``contraction does not imply weak bisimulation, ...''
 
@@
   \end{quote}
+  Fixed PRQ; Mentioned ``naive weak bisimulation up to weak
+  bisimilarity is unsound'' right before the definition of ``weak
+  bisimilation up to.''
 
@@
   \end{quote}
+  Thanks. We have added ``we actually used a different bisimulation game defined below''.
 
@@
   \end{quote}
+  Rephrased: `` we also consider the relation closure of bisimilarity
+  w.r.t. summation...''
 
@@
   \end{quote}
+
+  TODO: not understood this comment.
 
@@
 
+  TODO
+
 \item \begin{quote}
@@
   \end{quote}
+
+  ``this proof (Theorem~\ref{thm:coarsestfiniteState} in next
+  section)``.
 
@@
   \end{quote}
+
+  TODO
 
@@
 
+  Fixed (all raised by other reviewers).
+
 \item \begin{quote}
@@
 
+  Two of them, removed.
+
 \item \begin{quote}
@@
   \end{quote}
+
+  We have removed the one before Example 3.7.
 
@@
   \end{quote}
+
+  TODO (merge strong and weak cases0
 
@@
   \end{quote}
+
+  We added a few more words right after: ``this is mostly due to the surprising fact
+that, contraction does not imply weak bisimulation (while expansion
+indeed implies weak bisimulation) ''.
+
 \end{enumerate}

### 2019-09-05 ic-journal/coarsest.tex
Stage work revising the IC paper

@@
 \end{alltt}
- (We need not  put $R\ g\ h$ in the antecedent of
-  \texttt{CC\_def}, as this is anyhow obtained from the trivial context $(\lambda x.\,x)$.)
-For any relation $R$ 
+We do not need to put $R\ g\ h$ in the antecedent of
+  \texttt{CC\_def}, as this is anyhow obtained from the trivial context $(\lambda x.\,x)$.
+For any \hl{binary} relation $R$ 
 on CCS processes, the composition closure of $R$ is always at least as
@@
 Given the central role of the  
- sum operator, we also consider the closure of bisimilarity under such
- operator, called \emph{equivalence compatible with sums}
+ summation, we also consider the relation closure of bisimilarity
+ w.r.t. summation, called \emph{equivalence compatible with summation}
 (\texttt{SUM_EQUIV}): %%, denoted by $\approx^+$: (not used this symbol)
@@
 \begin{displaymath}
-\xymatrix@R=3ex{
+\xymatrix{
 {\textrm{Weak bisimilarity } (\approx)} & {\textrm{Equiv.
-    compatible with sums (\texttt{SUM\_EQUIV})}} \ar@/^3ex/[ldd]^{\subseteq}\\
+    compatible with summation (\texttt{SUM\_EQUIV})}}
+\ar@/^3ex/[ldd]^{\supseteq\; ?}\\
 {\textrm{Bisimilarity congruence (\texttt{WEAK\_CONGR})}}
@@
 \end{displaymath}
-\vspace{-2ex}
-\caption{Relationship between the equivalences mentioned}
+\caption{Relationships between several equivalences and $\wb$}
 \label{fig:relationship}
@@
  that are all pairwise non-bisimilar.
-We have partially formalised
-this proof, because the typed logic
+We have only partially formalised
+this proof (Theorem~\ref{thm:coarsestfiniteState} in next section), because ``the typed logic
 implemented in various HOL systems (including Isabelle/HOL) is not
-strong enough to define a type for all possible ordinals
-\cite{norrish2013ordinals}, thus
-we have replaced transfinite induction with plain induction. As a
-consequence, the final
-result is about a restricted class of processes (which we have taken
-to be the finite-state processes).
-The proof, in the section below, uses extensively HOL's
-\texttt{pred_set} theory \cite{melham1992hol}, with a mix
-of CCS and pure mathematics.
+strong enough to define a type for all possible
+ordinals''~\cite{norrish2013ordinals}.
+\hl{As a consequence, the final result is only for finite-state
+  CCS---a very restricted class.}
 
@@
     finite-state CCS)}
+  \label{thm:coarsestfiniteState}
 \begin{alltt}

### 2019-09-05 ic-journal/contraction.tex
Synchronized htex with tex files; clear all highlights
Stage work revising the IC paper

@@
-\subsection{Contractions}
+\subsection{Expansions and Contractions}
 \label{s:mcontr}
@@
 challenges from $Q$, entirely ignores efficiency: it is the same
-clause of  weak bisimulation~--- the final derivatives are even required
+clause of  weak bisimulation~---the final derivatives are even required
 to be related  by $\wb$, rather than by $\R$.
@@
 Bisimilarity  contraction is coarser than 
- the \emph{expansion relation} 
-$\expa$ \cite{arun1992efficiency,sangiorgi2015equations}.
+ the \emph{expansion relation} $\expa$~\cite{arun1992efficiency,sangiorgi2015equations}.
 This is a
@@
 
-As bisimilarity, so the expansion preorder is preserved by all operators but  sums.
-
 \begin{example}
@@
 
-\hl{Like} (weak) bisimilarity and expansion, contraction is
-preserved by all operators but (direct) sum.
+Like the case of (weak) bisimilarity, the expansion and contraction
+preorders are preserved by all CCS operators but the summation.

### 2019-09-05 ic-journal/intro.tex
Stage work revising the IC paper

@@
 % and the coarsest precongruence contained in the contraction preorder; 
-% the result about unique solution of equations for weak bisimilarity that uses the
+% the result about unique solution(s) of equations for weak bisimilarity that uses the
 % contraction preorder as an auxiliary relation, and other unique solution results (e.g.~%
@@
 weak bisimilarity and the coarsest precongruence contained in the
-contraction preorder; the proofs about unique solution of equations
+contraction preorder; the proofs about unique solution(s) of equations
 for weak bisimilarity that uses the contraction preorder as an

### 2019-09-05 ic-journal/part2.tex
Stage work revising the IC paper

@@
 
-\paragraph{Strong bisimularity}
+\paragraph{Strong bisimilarity}
 Based on results about ``bisimulation up to $\sim$'', we have first proved the following
@@
 
-The definition of ``unique label'' can be done in many ways, the
+The definition of ``unique label'' can be done in many \hl{ways. The}
 following definition (a suggestion from Robert Beers)

### 2019-09-05 ic-journal/sos.tex
Stage work revising the IC paper

@@
 The transition semantics of CCS processes follows Structural
-Operational Semantics (SOS) in Fig.~\ref{f:LTSCCS}:
+Operational Semantics (SOS) in Fig.~\ref{f:LTSCCS}:\footnote{All
+  formal theorems and definitions (their \TeX{} code) in this paper
+  are generated directly from HOL4. By default, all theorems are fully
+  specialised, removing outermost universal quantifiers.}
 \begin{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{E}.
-       \HOLConst{\HOLTokenInputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}}
-       \ensuremath{(}\HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\HOLTokenDisj{}} \HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
-       \HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}\hfill{[Example.ex_A]}
+\HOLTokenTurnstile{} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}}
+   \ensuremath{(}\HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
+   \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}\hfill{[Example.ex_A]}
 \end{alltt}

### 2019-09-08 ic-journal/response-letter.tex
Merged all revise suggestions from Sangiorgi

@@
 \begin{enumerate}
-% \item \begin{quote}
-%     This paper describes a HOL formalisation of several notions in
-%     process theory: CCS and various kinds of bisimilarity, and in
-%     particular the unique-solutions technique. The latter was
-%     introduced by Milner, and recently revisited and refined by the
-%     second author.
-%   \end{quote}
-
-% \item \begin{quote}
-%     In general, these kinds of results are error-prone, especially
-%     those related to weak bisimilarity: there are multiple known
-%     mistakes in the literature. Therefore, formalisation is a
-%     worthwile effort. Moreover, the formalisation itself is quite
-%     readable. The paper itself documents this formalisation and is,
-%     for the most part, clear.
-%   \end{quote}
-
-% \item \begin{quote}
-%     The paper is an extended version of an EXPRESS/SOS paper. The
-%     extension consists of a more detailed report of the proofs -
-%     perhaps this is enough.
-%   \end{quote}
+\item \begin{quote}
+    This paper describes a HOL formalisation of several notions in
+    process theory: CCS and various kinds of bisimilarity, and in
+    particular the unique-solutions technique. The latter was
+    introduced by Milner, and recently revisited and refined by the
+    second author.
+  \end{quote}
+
+\item \begin{quote}
+    In general, these kinds of results are error-prone, especially
+    those related to weak bisimilarity: there are multiple known
+    mistakes in the literature. Therefore, formalisation is a
+    worthwile effort. Moreover, the formalisation itself is quite
+    readable. The paper itself documents this formalisation and is,
+    for the most part, clear.
+  \end{quote}
+
+\item \begin{quote}
+    The paper is an extended version of an EXPRESS/SOS paper. The
+    extension consists of a more detailed report of the proofs -
+    perhaps this is enough.
+  \end{quote}
 
@@
   \end{quote}
-
   We have added "(weak)" before "bisimilarity", in the first line of abstract.
@@
   \end{quote}
+  Removed.
 
@@
 
+  Our formal proof of the classical result of ``$\rapprox$ is the
+  coarsest congruence contained in $\wb$'' is one such example, where
+  the formal theorem we obtained has slightly weaker antecedents under
+  the same proof idea. Anyway, we have omitted the sentence here.
+
 \item \begin{quote}
@@
   \end{quote}
+  We have moved the side condition to the main text where we explain
+  the syntax. (TODO)
 
@@
   \end{quote}
+  Done. (``... there exists a context ...'')
 
@@
 \end{quote}
+TODO
 
@@
   \end{quote}
+  TODO
 
@@
   \end{quote}
+We have rephrased the sentence: ``The above definition brings up a
+proof technique for proving rooted bisimilarity results, starting from
+a given bisimulation.''
 
@@
   \end{quote}
+  We have corrected it. It's an internal comment.
 
@@
 \end{quote}
+We have added some examples, and used Milner's original definition of sequentiality.
 
@@
 \end{quote}
+Rephrased: ``with guarded sums only''. We have removed all usages of
+``direct sym''.
 
@@
   \end{quote}
+  Done. Two examples are $\nil$ and $b.\nil$.
 
@@
   \end{quote}
+  We have rephrased the sentence.
 
@@
   \end{quote}
+  We have replaced it with ``indeed''.
 
@@
   \end{quote}
+
+  We have removed the sentence, including this statement with the
+  statement after the example.
 
@@
 
+  Having removed the sentence above now this should be ok. We have
+  also rephrased the sentence following the Example 3.7.
+
 \item \begin{quote}
@@
   \end{quote}
+  We have added a reference which contains this proof. Additionally,
+  this proof will be discussed later in a formalized version.
 
@@
   \end{quote}
+
+  Done.
 
@@
   \end{quote}
+
+  We have replaced ``the transition'' with ``a transition''.
 
@@
 
+  It should be ``via''.
+
 \item \begin{quote}
@@
   \end{quote}
+  We have completely re-worked this proof.
 
@@
   \end{quote}
+  Fixed during re-work of the proof of Theorem 3.14.
 
@@
   \end{quote}
+  Removed ``Logic'' from ``HOL Logic''.
 
@@
   \end{quote}
+  The long sentence is spilited.
 
@@
   \end{quote}
+  Changed to: ``the \emph{same} (programming language)''
 
@@
   \end{quote}
+  Removed parentheses.
 
@@
   \end{quote}
+  We have eliminated this sentence as now we have done the
+  multivariate formalizations.
 
@@
   \end{quote}
+  \texttt{option} is the name of the HOL formal theory.
 
@@
   \end{quote}
+  We have eliminated most uses of backquotes using HOL's new syntax.
 
@@
   \end{quote}
+  Sorry, it should be ``literature''.
 
@@
   \end{quote}
+  We have made them all in bold fonts.
 
@@
   \end{quote}
+We have re-phrased this part: ``(1) there exist indeed three
+  transitions mentioned above; (2) there exists no other
+  transition.''
 
@@
   \end{quote}
+  We have rephrased this sentence.
 
@@
   \end{quote}
+  We have removed the part ``due to the use of ...''. Infinite
+  branching is indeed possible, no matter what's the reason.
 
@@
   \end{quote}
+  Rephrased to ``One highlight...''
 
@@
   \end{quote}
+  By default, all theorems (their \TeX code) exported from HOL are
+  fully specialised, removing outermost universal quantifiers. We have
+  moved this sentence to an earlier footnote on the first such exported theorem.
 
@@
   \end{quote}
+  We have rephrased this sentence. Basically we meant, for whatever
+  algebraic law of strong bisimilarity, there're also versions for
+  weak and rooted bisimilarity.
 
@@
 
+  We have repharsed this part, moving the citation
+  \cite{sangiorgi1992problem} (which explains the reason) right before
+  the first sentence.
+
 \item \begin{quote}
@@
   \end{quote}
+  Actually this is indeed surprising. We have rephrased this sentence:
+  ``this is mostly due to the surprising fact
+  that, although the contraction preorder is contained in weak
+bisimilarity, contraction does not imply weak bisimulation (while
+expansion does so)''.
 
@@
   \end{quote}
+  We have removed the HOL version.
 
@@
   \end{quote}
+  Yes. We have fixed the definition.
 
@@
   \end{quote}
+  We have added a colon at the end.
 
@@
   \end{quote}
+  We have rephrased the sentence: ``(which needs not to be itself a (pre)congruence)''.
 
@@
   \end{quote}
+  We have removed this sentence.
 
@@
   \end{quote}
+  We have rephrased the sentence: ``There could be infinitely many such sub-processes, even on finitely
+  branching processes.''
 
@@
   \end{quote}
+  We have rephrased the sentence: ``Following the inductive structure
+  of the definition of Klop processes,...''
 
@@
   \end{quote}
+  Fixed as: ``In the proof of the above theorem''.
 
@@
   \end{quote}
+  TODO.
 
@@
   \end{quote}
+  Fixed bibtex item.
 

### 2019-09-08 ic-journal/ccs.tex
Stage fixes with highlights
Merged all revise suggestions from Sangiorgi

@@
 \ldots$ for defining recursive behaviours.
-Given a deadlock $\nil$, the class of CCS processes is inductively defined from $\nil$ by the operators
-of prefixing, parallel composition, summation (binary choice), restriction, recursion and relabeling:
+The class of CCS processes is inductively
+defined from $\nil$ \hl{(deadlock)} by the operators
+of prefixing, parallel composition, summation (binary choice),
+restriction, relabeling and recursion:
 \begin{equation*}
@@
 P  & := & \nil\!\!\!\! & \midd \;  \mu . P \; \midd \;  P_1 |  P_2 \; \midd  \;
-P_1 + P_2 \; \midd % \; \mu . P\; \midd  \; 
-  (\res a\!)\, P  \;  \midd \;  A \; \midd \; \recu A  P
+P_1 + P_2 \; \midd 
+(\res a\!)\, P
 \; \midd \; P\; [r\!f]  % relabelling
+\;  \midd \;  A \; \midd \; \recu A  P
 \end{array}
 \end{equation*}
-We sometimes omit the trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil$.
+We sometimes omit a trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil$.
 The operational semantics of CCS is then given by means of
@@
 $\displaystyle{ P \arr{\mu} P' \over
- P \;[r\!f] \arr{r\!f(\mu)} P' \;[r\!f]} $ $\forall a.\, r\!f(\outC a) = \overline{r\!f(a)}$
+ P \;[r\!f] \arr{r\!f(\mu)} P' \;[r\!f]} $
 $ \hb$ %  &
@@
 $\holei i$ of the  context $\qct$ with $P_i$.  
-We write $
-\ctx \R$ for the closure of a relation under contexts. Thus $P\: \ctx \R\: Q$
-means that there are context $\qct$ and tuples $\til P,\til Q$ with
+We write $\ctx \R$ for the closure of a relation under contexts.
+Thus $P\: \ctx \R\: Q$
+means that there \hl{exists a} context $\qct$ and tuples $\til P,\til Q$ with
 $P =  \ct{\til P}, Q =  \ct{\til Q}$ and $\til P \RR \til Q$.
@@
 
-% next file: expansion.tex
+% next file: expansion.tex (bisimilarity and rooted bisimilarity, actually)

### 2019-09-08 ic-journal/coarsest.tex
Merged all revise suggestions from Sangiorgi

@@
   \texttt{CC\_def}, as this is anyhow obtained from the trivial context $(\lambda x.\,x)$.
-For any \hl{binary} relation $R$ 
+\hl{The next result shows that, for any binary} relation $R$ 
 on CCS processes, the composition closure of $R$ is always at least as
-fine as $R$
-(here $\subseteq_r$ stands for \emph{relational subset})
+fine as $R$\hl{:} ($\subseteq_r$ stands for \emph{relational subset}.)
 \begin{alltt}
@@
 \end{alltt}
-Furthermore, we prove that any (pre)congruence contained in $R$ (which
-itself may not be) is contained in the composition closure of $R$
+Furthermore, we prove that any (pre)congruence contained in $R$
+\hl{(which needs not to be itself a (pre)congruence)}
+is contained in the composition closure of $R$
 (hence the closure is the coarsest one):
@@
 
-The formal proofs  of the above two results  follow Milner's proof
-\cite{Mil89}. The assumption is Milner's result 
+The formal proofs  of the above two results follow Milner's proof~\cite{Mil89}.
+The assumption \hl{in} Milner's result 
 requires $\mathrm{fn}(p) \cup
@@
   names}), and is therefore strictly stronger than the assumption in
-our result above, where we only look at immediate weak
-derivatives $p$ and $q$, requiring that there is at least one action
-that never appears as a label; moreover such an action need not be
-the same for $p$ and for $q$
-%  If only $p$ (or $q$) has free actions while the other uses all available
-% labels, the assumption $\mathrm{fn}(p) \cup
-% \mathrm{fn}(q) \neq \mathscr{L}$ (here $\mathrm{fn}$ stands for \emph{free
-%   names}) does not hold, and the proof cannot be completed. Our
-% assumption is \emph{weaker}
-% in the sense that $p$ and $q$ need not have the
-% \emph{same} free actions 
-(and where an action $a$ and its complementary  $\outC a$ are
-considered \emph{different} actions).
+our result above. \hl{Indeed, in out result we} only look at immediate weak
+derivatives for $p$ and $q$, \hl{and only requires that there is an input
+or output action}
+that never appears as a label. \hl{Furthermore, such an action need
+not to be the same for $p$ and for $q$,
+as an action $a$ and its complementary $\outC a$ are
+considered as \emph{different} actions.}
 
@@
 
-\subsection{Arbitrary many non-bisimilar processes}
+\subsection{Arbitrarily many non-bisimilar processes}
+\label{ss:arbitrarily}
 
@@
 any sub-process emanating from the two root processes by weak
-transitions. In the worst case, there may be infinite such
-sub-processes (even on finitely branching processes).
-We can however consider  the equivalence classes of CCS processes 
+transitions.
+\hl{There could be infinitely many such sub-processes, even on finitely
+branching processes.}
+We can, however, consider the equivalence classes of CCS processes
 modulo weak bisimilarity.
@@
 
-By induction on the definition of Klop processes,  and using the SOS inference
-rules ($\mathrm{Sum}_1$) and ($\mathrm{Sum}_2$), we can  prove
+\hl{Following the inductive structure of the definition of Klop processes,}
+  and using the SOS rules
+  ($\mathrm{Sum}_1$) and ($\mathrm{Sum}_2$), we proved
 the following properties of Klop functions:

### 2019-09-08 ic-journal/contraction.tex
Merged all revise suggestions from Sangiorgi

@@
 \end{enumerate}
-\emph{Bisimilarity contraction}, written as $P \mcontrBIS Q$ ($P$
-\emph{contracts to} $Q$), if $P\ \R\ Q$ for some contraction $\R$.
+\hl{Two processes $P$ and $Q$ are in the \emph{bisimilarity
+    contraction}}, written as $P \mcontrBIS Q$ ($P$ \emph{contracts to} $Q$),
+if $P\ \R\ Q$ for some contraction $\R$.
+\hl{Sometimes we write $\mexpaBIS$ for the inverse of $\mcontrBIS$.}
 \end{definition}
-% We say that $P$  {\emph{bisimilarly  contracts} $Q$, written
-% $Q \mcontrBIS Q$.
-% We write $\mexpaBIS$ for the inverse of $\mcontrBIS$.
 
@@
 challenges from $Q$, entirely ignores efficiency: it is the same
-clause of  weak bisimulation~---the final derivatives are even required
+clause of  weak bisimulation~---the final derivatives are \hl{indeed} required
 to be related  by $\wb$, rather than by $\R$.
@@
 the \emph{expansion relation} $\expa$~\cite{arun1992efficiency,sangiorgi2015equations}.
-This is a
-preorder widely used in proof techniques for bisimilarity and that 
+This is a preorder \hl{that is} widely used in proof techniques for bisimilarity and
 intuitively refines bisimilarity by 
@@
  \begin{enumerate}
- \item   $P \arr\mu P'$ implies that there is $Q'$ with $Q \arcap \mu
-   Q'$
+ \item   $P \arr\mu P'$ implies that there is $Q'$ with $Q \arcap \mu  Q'$
   and $P' \RR Q'$;
- \item
-     $Q \arr\mu Q'$   implies that there is $P'$ with $P \Arr \mu
-  P'$ and $P'
- \RR Q'$.
+ \item $Q \arr\mu Q'$   implies that there is $P'$ with $P \Arr \mu P'$ and $P' \RR Q'$.
  \end{enumerate}
-  $P$  {\em expands} $Q$, written as
- $P  \expa Q$,
+\hl{Two processes $P$ and $Q$ are in the \emph{bisimilarity
+    expansion}}, written as $P \expa Q$ ($P$ \emph{expands} $Q$),
  if $P \RR Q$ for some expansion $\R$.
@@
 
-% The substitutivity proofs for for expansion and bisimilarity carry
-% over to contraction,
-
-Like the case of (weak) bisimilarity, the expansion and contraction
-preorders are preserved by all CCS operators but the summation.
+\hl{In the same way as bisimilarity, both the expansion and the
+contraction preorders are preserved by all CCS operators except the
+summation. The proofs are similar, see e.g.}~\cite{sangiorgi2017equations}.

### 2019-09-08 ic-journal/equa.tex
text
Clean up the rest DDS macros; disable line numbers
Merged all revise suggestions from Sangiorgi

@@
 
-\begin{definition}
+\begin{definition} % Def 3.1
 Assume that, for each $i$ of 
@@
  $K$ and $K | b$, for $K \DSdefi \recu K {\, (a. K)}$. (Actually any process capable of
-continuously performing $a$ actions (while behaves arbitrarily on
-other actions) is a solution for $X = a|  X$.)
+continuously performing \hl{$a$--actions} is a solution \hl{of} $X = a  |  X$.)
 
@@
 \item \emph{(strongly) guarded} if, in each $E_i$, each occurrence of
-  an \behav\  variable is underneath a \emph{visible} prefix;
+  an equation variable is underneath a \emph{visible} prefix;
 
-\item \emph{sequential} if, in each $E_i$, each of its subexpressions with occurrence of
-  an \behav\  variable, apart from the variable itself, is in forms of
-  prefixes or sums.
+\item \emph{sequential} if, in each $E_i$, each \hl{occurrence of an
+    equation variable only appears underneath prefixes and sums.}
 \end{itemize}
@@
 
-% In other words,  
-% if the system is sequential, then 
-%  for
-% every expression $E_i$, any subexpression of $E_i$ in which $X_j $ 
-% appears, apart from $X_j$ itself,  is a sum (of prefixed terms). 
-% For instance, 
-% \begin{itemize}
-% \item $X = \tau. X + \mu . \nil$ is sequential but not 
-%  guarded, because the guarding prefix for the variable
-% is not visible.
+\hl{In other words, if the system is sequential, then for
+every expression $E_i$, any subexpression of $E_i$ in which $X_j $
+appears, apart from $X_j$ itself, is a sum (of prefixed terms).
+For instance,}
+\begin{itemize}
+\item $X = \tau. X + \mu . \nil$ is sequential but not 
+ guarded, because the guarding prefix for the variable
+is not visible.
 
-% \item $X =  \ell . X | P$ is  guarded but not sequential.
+\item $X =  \ell . X | P$ is guarded but not sequential.
 
-% \item $X =  \ell . X + \tau. \res a (a .\outC b | a.\nil)$, as well as 
-% $X = \tau . (a. X + \tau . b .X + \tau  )$
-% are both 
-%  guarded and sequential.
-% \end{itemize}
+\item $X =  \ell . X + \tau. \res a (a .\outC b | a.\nil)$, as well as
+$X = \tau . (a. X + \tau . b .X + \tau  )$ are both guarded and sequential.
+\end{itemize}
 
@@
 \label{t:Mil89}
-A system of guarded and sequential equations (without direct sums)
-$\{  X_i = E_i\}_{i\in I}$ has a unique solution for $\wb$.
+A system of guarded and sequential equations (\hl{with guarded sums only})
+$\{  X_i = E_i\}_{i\in I}$ has an unique solution for $\wb$.
 \end{theorem}
 
-% The proof exploits an invariance property on immediate transitions for
-% guarded and sequential expressions, and then extracts a bisimulation
-% (up-to bisimilarity) out
-% of the solutions of the system.  
+\hl{The proof exploits an invariance property on immediate transitions for
+guarded and sequential expressions, and then extracts a bisimulation
+(up to bisimilarity) out
+of the solutions of the system.  }
 To see the need of the sequentiality  condition, consider
  the equation (from \cite{Mil89}) $X = \res a (a. X | \outC a)$
-where $X$ is guarded but not sequential. Any process that does not use $a$ is a solution.
+where $X$ is guarded but not sequential. Any process that does not use
+$a$ is a solution\hl{, e.g. $\nil$ and $b.\nil$.}
+
+%% next file: contraction.tex

### 2019-09-08 ic-journal/expansion.tex
Merged all revise suggestions from Sangiorgi

@@
 A process relation ${\R}$ is a \emph{bisimulation} if, whenever
- $P\RR Q$, for all $\mu$ we have:
+ $P\RR Q$\hl{,} % for all $\mu$ we have:
 \begin{enumerate}
@@
 \item $Q \arr\mu Q'$,implies that there is $P'$ such that $P \Arcap
-  \mu P'$ and $P' \RR Q'$\enspace.
+  \mu P'$ and $P' \RR Q'$\hl{;}
 \end{enumerate}
@@
 Two processes $P$ and $Q$ are \emph{rooted bisimilar}, written as $P
-\rapprox Q$, if
-for all $\mu$:
+\rapprox Q$, \hl{if} % for all $\mu$:
 %  for all $\mu\in \mathscr{L}\cup\{\tau\}$
@@
 
-Besides reducing the rooted \hl{bisimilarity} of two processes to
-the bisimilarities of their immediate derivatives, the
-above definition also brings up a proof technique for proving rooted
-\hl{bisimilarity} results by constructing a bisimulation.
+\hl{The above definition brings up a proof technique for proving rooted
+bisimilarity results, starting from a given bisimulation.}
 \begin{lemma}[Rooted bisimilarity by bisimulation]
@@
 Given a (weak) bisimulation $\RR$, if two processes $P$ and $Q$
-satisfies the following properties:
+\hl{satisfy} the following properties \hl{(but not necessary $P\;\R\;Q$)}:
 \begin{enumerate}
@@
 \end{theorem}
+
+%% next file: equa.tex

### 2019-09-08 ic-journal/intro.tex
Merged all revise suggestions from Sangiorgi

@@
 
-The main goal of the work described in this paper is a rather
+The main goal of the work described in this paper is a %rather
 comprehensive formalisation of the core theory of CCS in the HOL
@@
 solutions, but embraces a
-significant portion the theory of CCS \cite{Mil89}, mostly because the
+significant portion the theory of CCS~\cite{Mil89}, mostly because the
 theory of unique solutions relies on a large number of more fundamental results.
@@
 efficiency-like refinements of weak bisimilarity). Concerning rooted bisimilarity, the formalisation
-includes Hennessy Lemma and Deng Lemma (Lemma 4.1 and 4.2 of
-\cite{Gorrieri:2015jt}),
- and two long proofs saying that  rooted bisimilarity is the coarsest (largest)
- congruence contained in (weak) bisimilarity: one following Milner's
- book \cite{Mil89}, with the hypothesis that no processes can use up
+includes \hl{Hennessy's Lemma} and \hl{Deng's Lemma},
+ and two \hl{theorems} saying that rooted bisimilarity is the coarsest (largest)
+ congruence contained in weak bisimilarity ($\wb$): one following Milner's
+ book~\cite{Mil89}, with the hypothesis that no processes can use up
  all labels;
-the other without such hypothesis, essentially formalising van Glabbeek's paper \cite{van2005characterisation}.
+the other without such hypothesis, essentially formalising van Glabbeek's paper~\cite{van2005characterisation}.
 Similar theorems are proved for the rooted contraction preorder.
-In this respect, the work is an extensive experiment with the use of the HOL theorem prover with its
-recent developments, including a package for coinductive definitions.
+In this respect, the work is \hl{also} an extensive experiment \hl{using} the HOL theorem prover with its
+recent developments, including \hl{its coinductive relation-defining package}.
 
-From the view of CCS theory, this formalisation has offered us the possibility of
-further refining the theory of unique solutions of contractions, as
-formally proving a previously known result gives us the
-chance to see \emph{what is really needed} for establishing that result.
-In particular, the existing theory \cite{sangiorgi2017equations} has
+From the \hl{point of} view of CCS theory, this formalisation has offered us the possibility of
+further refining the theory of unique solutions of contractions.
+In particular, the existing \hl{theorem}~\cite{sangiorgi2017equations} has
 placed limitations on the body of the contractions due to the

### 2019-09-08 ic-journal/part2.tex
Merged all revise suggestions from Sangiorgi

@@
 substituted for $X$:
-\begin{lemma}[Lemma 3.13 of \cite{Mil89}]
+\begin{lemma}[Lemma 3.13 of \cite{Mil89}, the univariate version]
 \label{lem:313}
-If the variable $X$ are weakly guarded in $E$, and
+If the variable $X$ is weakly guarded in $E$, and
 $E\{P/X\}\overset{\alpha}{\rightarrow} P'$, then $P'$ takes the form
@@
 \end{theorem}
-In above proof, we have identified 14 major sub-goals, dividing them into 7
+In \hl{the proof of the above theorem}, we have identified 14 major sub-goals, dividing them into 7
 groups, in which each pair is symmetric (thus having similar proof
@@
 As  weak bisimilarity 
- is not congruence, we have to be more restrictive on the syntax for
+ is not \hl{a} congruence, we have to be more restrictive on the syntax for
  the equation, using strong guardedness.

### 2019-09-08 ic-journal/sos.tex
Merged all revise suggestions from Sangiorgi

@@
 union of all visible actions, plus invisible action $\tau$. It's
-defined as an abbreviation of HOL's core type ``\HOLinline{\ensuremath{\alpha} \HOLTyOp{option}}'' instantiated
+defined as an abbreviation of HOL's core type ``\HOLinline{\ensuremath{\alpha} \HOLTyOp{option}}''%
+\footnote{\url{https://hol-theorem-prover.org/kananaskis-13-helpdocs/help/src-sml/htmlsigs/optionTheory.html}} instantiated
 with the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'':
@@
 syntax\footnote{The order of type variables $\alpha$ and $\beta$
-    is arbitrary. Our choice is aligned with other CCS literals.
-$\mathrm{CCS}(h,k)$ is the CCS subcalculus that can use at most $h$ constants
-and $k$ actions \cite{gorrieri2017ccs}. Thus, to formalize theorems on
-such a calculus, the needed CCS type can be retrieved by instantiating the type
+    is arbitrary. Our choice is aligned with other \hl{literature.
+For instance,} $\mathrm{CCS}(h,k)$ is the CCS subcalculus that can use at most $h$ constants
+and $k$ actions~\cite{gorrieri2017ccs}. To formalize theorems on
+such $\mathrm{CCS}(h,k)$, the required CCS type can be retrieved by instantiating the type
 variables $\alpha$ and $\beta$ in ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' with types
-having the corresponding cardinalities $h$ and $k$. Monica Nesi goes
-farther, by adding another type variable $\gamma$ for value-passing CCS
-\cite{Nesi:2017wo}.}, is then defined inductively:
+having the corresponding cardinalities $h$ and $k$.}, is then defined inductively:
 (\texttt{'a} or $\alpha$ is the type variable for recursion variables,
@@
  using HOL's powerful pretty printer, to represent CCS
-processes in more readable forms (c.f. the column \hl{``\TeX{} output''}
+processes in more readable forms (c.f. the column \hl{``\TeX{} outputs''}
 of Table \ref{tab:ccsoperator}, which summarizes
@@
 \hl{\textbf{CCS concept}} & \hl{\textbf{Notation}} & \textbf{HOL term} &
-                                             \textbf{HOL abbrev.} & \hl{\textbf{\TeX{} output}} \\
+                                             \textbf{HOL abbrev.} & \hl{\textbf{\TeX{} outputs}} \\
 \hline
@@
 The last rule \texttt{REC} (Recursion)
- says that if we substitute all appearances of variable $A$ in $P$ to
+ says that if we substitute all \hl{occurrences of the} variable $A$ in $P$ to
 $(\recu A P)$ and the resulting process has a transition to $P'$
@@
 
-From HOL's viewpoint, these
-SOS rules are \emph{inductive
-  definitions} on the tenary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL's
+From \hl{the point of view of HOL4, SOS rules are actually} \emph{inductive
+  definitions} \hl{of the ternary} relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL's
 \texttt{Hol_reln} function.
@@
   taking a CCS process and returning a theorem indicating all
-  direct transitions of the process.\footnote{If the input process were
- infinite branching, due to the use of recursion or
-    relabeling operators, the program will loop forever.}
-For instance, we know that the process $(a.0 | \bar{a}.0)$ has three
-possible transitions: $(a.0 | \bar{a}.0) \overset{a}{\longrightarrow}
-(0 | \bar{a}.0)$, $(a.0 | \bar{a}.0)
-\overset{\bar{a}}{\longrightarrow} (a.0 | 0)$ and $(a.0 | \bar{a}.0)
-\overset{\tau}{\longrightarrow} (0 | 0)$.
+  direct transitions of the process.\footnote{If the input process \hl{are
+ infinite branching, the function will not terminate}.}
+For instance, we know that the process $(a.\nil | \bar{a}.\nil)$ has three
+possible transitions: $(a.\nil | \bar{a}.\nil) \overset{a}{\longrightarrow}
+(\nil | \bar{a}.\nil)$, $(a.\nil | \bar{a}.\nil)
+\overset{\bar{a}}{\longrightarrow} (a.\nil | \nil)$ and $(a.\nil | \bar{a}.\nil)
+\overset{\tau}{\longrightarrow} (\nil | \nil)$.
 To completely describe all possible transitions of a process, if done manually, the
-following facts should be proved: (1) there exists transitions from
-$(a.0 | \bar{a}.0)$ (optional); (2) the correctness for each of the
-transitions; and (3) the non-existence of other transitions.
+following two facts must be proved: \hl{(1) there exist indeed three
+  transitions mentioned above; (2) there exists no other
+  transition. The first part can be easily proved by SOS rules, while
+  the second part can only be proved by \texttt{TRANS\_cases}. (TODO)}
 
-For large processes it may be surprisingly hard to manually prove the
-non-existence of transitions.  Hence the usefulness of appealing to
-the new  function \texttt{CCS\_TRANS\_CONV}.
-For instance this function
-is called on the  process $(a.0 | \bar{a}.0)$ thus:
-\begin{lstlisting}
-> CCS_TRANS_CONV ``par (prefix (label (name "a")) nil)
-                       (prefix (label (coname "a")) nil)``
-\end{lstlisting}
-This returns the following theorem, indeed describing all immediate
-transitions of the process:
+For large CCS processes it is surprisingly \hl{tedious} to manually derive
+all the possible transitions and prove the non-existence of others,
+\hl{which shows the usefulness of appealing to an ML function
+\texttt{CCS\_TRANS\_CONV} who is designed to automate the whole process.
+For instance, calling it on $(a.\nil | \bar{a}.\nil)$ the function returns the
+following theorem which describes all the transitions (just one-step) of the process:}
 \begin{alltt}
@@
    \ensuremath{(}\HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
-   \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}\hfill{[Example.ex_A]}
+   \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}
 \end{alltt}

### 2019-09-08 ic-journal/unique.tex
Merged all revise suggestions from Sangiorgi

@@
 \item $\til P$ is a \emph{solution (for $\mcontrBIS$) of the 
- system of contractions} if $\til P \mcontrBIS \til E [\til P]$;
-\item the system has \emph{a unique solution (for $\approx$)}
+ system of contractions} if \hl{for each $i$ it holds that $P_i \mcontrBIS E_i [\til P]$};
+\item \hl{The} system has \emph{a unique solution (for $\approx$)}
 if $\til P \approx \til Q$ whenever $\til P$ and $\til Q$ are both solutions.
@@
 \begin{proof}{(sketch from \cite{sangiorgi2017equations})}
-Let $n$ be the length of the transition $\ct{\til P}\Arr\mu R$  (the
-number of `strong steps' of which it is composed), and  
+  Let $n$ be the length \hl{(the number of one-step transitions)} of
+\hl{a} transition $\ct{\til P}\Arr\mu R$, and
 let $\ctpp {\til P}$ and $\ctpp {\til Q}$  be the processes obtained
@@
 \begin{proof}
-\hl{We want to prove $P_i \wb Q_i$ ($i \in I$) by considering} the following relation
+\hl{We want to prove $P_i \wb Q_i$ (for each $i \in I$) by considering} the following relation
 \begin{equation*}
@@
 hard to see that,}
-there exists also $S'$ with $S \Arcap{\mu} S'$. This closes the
+there exists also $S'$ with $S \Arcap{\mu} S'$. This \hl{completes} the
 proof, as we have $R' \wb C'[{\til P}]$ and $S' \wb C'[{\til Q}]$ \hl{by
@@
 \begin{proof}
-\hl{We want to prove $P_i \rapprox Q_i$ ($i \in I$) by considering}
+\hl{We want to prove $P_i \rapprox Q_i$ (for each $i \in I$) by considering}
 the following relation
@@
   Q}]$, by definition of $\rcontr$ we have $Q_i \Arr{\mu} Q'$ for some
-$Q'$ and $Q' \wb E'[{\til Q}]$. This closes the proof, as we have
+$Q'$ and $Q' \wb E'[{\til Q}]$. This \hl{completes} the proof, as we have
 $P' \wb C[{\til P}]$ (by the fact that $\mcontrBIS$ implies $\wb$) and

### 2019-09-09 ic-journal/ccs.tex
Stage work revising the paper (2nd round)

@@
 
+\hl{Here we beliefly recall the core theory of CCS, up to the unique solution of
+equation and contractions, with a focus on the syntactic differences with
+other literature.}
 We assume a possibly infinite set of names $\mathscr{L} = \{a, b,
-\ldots\}$ forming input and $\overline{\mbox{output}}$ actions, plus a special invisible
-action $\tau \notin \mathscr{L}$, and a set of variables $A, B,
-\ldots$ for defining recursive behaviours.
-The class of CCS processes is inductively
-defined from $\nil$ \hl{(deadlock)} by the operators
-of prefixing, parallel composition, summation (binary choice),
-restriction, relabeling and recursion:
+\ldots\}$ forming input and $\overline{\mbox{output}}$ labels (actions), plus a special invisible
+action $\tau \notin \mathscr{L}$, and \hl{another possibly infinite
+  set of agent} variables $A, B,
+\ldots \in \mathscr{X}$.
+The class of CCS processes is then inductively
+defined from $\nil$ \hl{(deadlock) and agent variables} by the operators
+of \emph{prefixing} (.), \emph{parallel composition} ($|$),
+\emph{summation}
+(or \emph{binary choice}, $+$),
+\emph{restriction} ($\nu$), \emph{relabeling} ($[\cdot]$) and
+\emph{recursion} ($\texttt{rec}$):
 \begin{equation*}
@@
 P_1 + P_2 \; \midd 
-(\res a\!)\, P
-\; \midd \; P\; [r\!f]  % relabelling
+(\res L)\, P
+\; \midd \; P\; [\mathit{rf}]  % relabelling
 \;  \midd \;  A \; \midd \; \recu A  P
@@
 \end{equation*}
-We sometimes omit a trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil$.
-The operational semantics of CCS is then given by means of
+\hl{Notice the (minor) differences with other CCS literature regarding the above definition:}
+\begin{enumerate}
+  \item Some literature adopts possibly infinite sums over an index
+    set ($\sum_{i\in I} P_i$) while we only consider binary (thus
+    finite) sums, which is less expressive.
+  \item Our restriction operator takes a set of (input) labels $L
+    \subseteq \mathscr{L}$, while some CCS literature only restricts
+    one label (for each restriction operator);
+  \item Our relabeling operator takes a relabeling function
+    $\mathit{rf} \colon \mathscr{L} \cup \overline{\mathscr{L}} \cup
+    \{\tau\} \rightarrow \mathscr{L} \cup \overline{\mathscr{L}} \cup
+    \{\tau\}$, which
+    is capable to handle multiple actions including $\tau$. A valid
+    relabeling function $\mathit{rf}$ must satisfy $\mathit{rf}(\tau) =
+    \tau$ and $\forall l\in\mathscr{L} \cup \overline{\mathscr{L}}.\, \mathit{rf}(\overline{l}) =
+    \overline{\mathit{rf}(l)}$ (with $\bar{\bar l} = l$ for all $l \in
+    \mathscr{L}$); Same expressiveness
+    with single-label relabeling.
+  \item The recursion operator $\texttt{rec}$ has the same expressiveness with
+    \emph{process constants} adopted in some literature. For instance, a
+    CCS process $a.C$ with the constant $C \DSdefi b.C$ can be
+    expressed as $a.(\texttt{rec}\, C. (b.C))$.
+\end{enumerate}
+Besides, we sometimes omit \hl{the} trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil$.
+\hl{A CCS process $P$ may \emph{derive} to another one, say $P'$, under
+  an action $\mu$, denoted by $P \arr{\mu} P'$.}
+The \hl{transitional semantics} of CCS processes is given by means of
 a Labeled Transition System (LTS) \hl{expressed in Structural Operational
-Semantics (SOS) rules}, shown in Fig.~\ref{f:LTSCCS}.
-The symmetric version of the two \hl{SOS} rules for
-parallel composition and the rule for sum are omitted.
-A CCS expression uses only \emph{weakly guarded sums} if all occurrences of
-the sum operator are of the form $\mu_1.P_1 + \mu_2.P_2 + \ldots
-+ \mu_n.P_n$, for some $n \geq 2$.
+Semantics (SOS) rules} shown in Fig.~\ref{f:LTSCCS}.
+(The symmetric versions of the \hl{SOS} rules for
+parallel composition and binary choice are omitted.)
+A CCS processes uses only \emph{guarded sums} if all occurrences of
+sums are in the form $a.P + b.Q$. \hl{(Otherwise we may call the sum
+a \emph{direct} one, e.g. $P + Q$ if either $P$ or $Q$ are not in the
+form of prefixes.)}
  The \emph{immediate derivatives} of a
-process $P$ are the elements of the set $\{P' \st P \arr\mu P' \mbox{
+process $P$ are elements of the set $\{P' \st P \arr\mu P' \mbox{
   for some $\mu$}\}$.
@@
 $\displaystyle{ P \arr{\mu}P' \over
- (\res a\!)\, P   \arr{\mu} (\res a\!)\, P'} $ $ \mu \neq a, \outC a$
+ (\res L\!)\, P \arr{\mu} (\res L\!)\, P'} $ $ \mu, \outC\mu \not\in L$
 $ \hb$
@@
 \end{figure*}
+
 Some standard notations for transitions: $\Arr\epsilon$ is the 
@@
 Moreover,   
-$ P \arcap \mu P'$ holds if $P \arr\mu P'$ or ($\mu =\tau$ and
-$P=P'$); similarly 
-$ P \Arcap \mu P'$ holds if $P \Arr\mu P'$ or ($\mu =\tau$ and
-$P=P'$).
+$P \arcap \mu P'$ holds if $P \arr\mu P'$ or $\mu =\tau \wedge P = P'$; similarly 
+$P \Arcap \mu P'$ holds if $P \Arr\mu P'$ or $\mu =\tau \wedge P = P'$).
 We write $P \:(\arr\mu)^n P'$ if $P$ can become $P'$ after performing
@@
  infix notation for them; e.g., 
-$P \RR Q$ means that $(P,Q) \in \R$.
+$P \,\R\, Q$ means $(P,Q) \in \R$.
 We use a tilde, as in  $\til P$, to denote tuples of processes with
@@
 All notations are extended to tuples componentwise,
-e.g., $\til P \RR \til Q$ means that $P_i \RR Q_i$, for each  
-component $i$ of the tuples $\til P$ and $\til Q$.
-And $\ct{\til P}$ is the process obtained by replacing each hole
-$\holei i$ of the  context $\qct$ with $P_i$.  
-We write $\ctx \R$ for the closure of a relation under contexts.
-Thus $P\: \ctx \R\: Q$
-means that there \hl{exists a} context $\qct$ and tuples $\til P,\til Q$ with
-$P =  \ct{\til P}, Q =  \ct{\til Q}$ and $\til P \RR \til Q$.
+e.g., $\til P \,\R\, \til Q$ means $P_i \,\R\, Q_i$ for each  
+index $i$ of the tuples $\til P$ and $\til Q$.
 We use the symbol $\DSdefi$ for abbreviations. For instance, $P \DSdefi G $, where
@@
 
+% \paragraph{CCS contexts and equations}
+% And $\ct{\til P}$ is the process obtained by replacing each hole
+% $\holei i$ of the  context $\qct$ with $P_i$.  
+% We write $\ctx \R$ for the closure of a relation under contexts.
+% Thus $P\: \ctx \R\: Q$
+% means that there \hl{exists a} context $\qct$ and tuples $\til P,\til Q$ with
+% $P =  \ct{\til P}, Q =  \ct{\til Q}$ and $\til P \RR \til Q$.
+
 % next file: expansion.tex (bisimilarity and rooted bisimilarity, actually)

### 2019-09-09 ic-journal/equa.tex
Stage work revising the paper (2nd round)

@@
 \label{s:eq}
+
+\hl{In the CCS syntax given in previous section, there is the syntactic
+possibility that an agent variable $A$ occurs
+outside the recursion operator of the same variable (or, equivalently, a
+process constant $C$ is used but undefined). We say such a variable is
+\emph{free}, while those variables wrapped by their recursions are
+\emph{bound}.}
+\hl{A CCS \emph{tem} (or \emph{expression}, i.e. those with valid syntax)
+without any free variable is called a CCS \emph{process}.}
+\hl{For instance, the variable $X$ is free in $a.X + \recu Y (b.Y)$, while $Y$
+is bound. There is also the syntactic possibility that the same
+variable $X$ is
+both free and bound, e.g. in $a.X + \recu X (b.X)$.
+This does not cause any ambiguity, but sometimes leads to more
+complex proofs.} (c.f. Section~\ref{sec:multivariate} for more details.)
+
+\hl{In this paper (and the formalisation work), we reuse the free agent
+variables as \emph{equation variables}. This eliminates the need of
+another type for CCS equations, and we can also reuse the existing
+variable substitution operation} (c.f. SOS rule for the Recursion in
+Fig.~\ref{f:LTSCCS}) \hl{for the substitution of equation variables.
+For example, the result of substituting equation variable $X$ to $\nil$ in $a.X +
+\recu X (b.X)$, denoted by $(a.X + \recu X (b.X)) \sub {\nil} X$, is
+$a.\nil + \recu X (b.X)$ with the part $\recu X (b.X)$
+untouched. Multivariate substitutions are written in the same syntax,
+e.g. $E \sub {\til P} {\til X}$. Whenever $\til X$ is clear from the
+context, we may also write $E[\til P]$ instead of $E \sub {\til P} {\til
+  X}$. ($E[P]$ for $E \sub P X$ in the case of a single variable $X$.)}
+
+\hl{In fact, free agent variables have the same transitional behavior
+as the deadlock $\nil$ if we strictly follow the existing SOS rules, as there is
+no SOS rule for them at all. In fact, most CCS theorems still hold if
+the involved CCS terms contain free variables. (The most notable
+exceptions are all versions of unique solution of equations/contracts,
+where all solutions must be \emph{pure} processes (without free variables).)}
 
@@
 
-Uniqueness of  solutions of equations \cite{Mil89} intuitively says that if  a context $\qct$ obeys
-certain  conditions, 
-then all processes $P$  that satisfy the equation $ P \wb \ct P$ are
+Milner's ``unique solution of equations'' theorems~\cite{Mil89} intuitively
+say that, if a context $C$ \hl{(i.e., a CCS expression with possibly
+free variables)} obeys certain conditions,
+then all processes $P$ that satisfy the equation $P \wb \ct P$ are
 bisimilar with each other.
-We need variables to write equations. We  use
- capital
-letters  $X,Y,Z$
- for  these variables and call them \emph{\behav\  variables}.
- The body of an equation is a CCS expression
-possibly containing \behav\  variables. Thus such expressions, ranged
-over by $E$, live in the CCS
-grammar extended with \behav\  variables.
-% , which we  call 
-%  \emph{extended CCS}.
+
+% TODO
 

### 2019-09-09 ic-journal/expansion.tex
Stage work revising the paper (2nd round)

@@
 \label{d:wb}
-A process relation ${\R}$ is a \emph{bisimulation} if, whenever
+A process relation ${\R}$ is a \hl{(weak)} \emph{bisimulation} if, whenever
  $P\RR Q$\hl{,} % for all $\mu$ we have:
@@
 \end{enumerate}
- $P$ and $Q$ are \emph{bisimilar},
+ $P$ and $Q$ are \hl{(weakly)} \emph{bisimilar},
 written as $P \wb Q$, if $P \RR Q$ for some bisimulation $\R$.
@@
 
-\hl{We sometimes call the bisimulation and bisimilarity defined above
-the \emph{weak} bisimulation (and weak bisimilarity), to
-distinguish it from the \emph{strong} bisimulation and strong bisimilarity} ($\sim$),
-obtained by replacing the weak transition $Q\Arcap\mu Q'$ in the above
-definition with the strong transition $Q \arr \mu Q'$ (same for the
-other case).
+\hl{The \emph{strong} bisimulation and strong bisimilarity} ($\sim$)
+can be obtained by replacing the weak transition $Q\Arcap\mu Q'$ in the above
+definition with normal transitions $Q \arr \mu Q'$ (similar for the other case).
 Weak bisimilarity is not preserved by the sum operator (except for
-guarded sums). For this, Milner introduced \emph{observational congruence}, also called \emph{rooted
-  bisimilarity} \cite{Gorrieri:2015jt,Sangiorgi:2011ut}:
+guarded sums), \hl{i.e. from $P_1 \wb Q_1$ and $P_2 \wb Q_2$ one
+  cannot obtain $P_1 + P_2 \wb Q_1 + Q_2$.}
+For this, Milner introduced the concept of \emph{observational congruence}, also called \emph{rooted
+  bisimilarity}~\cite{Gorrieri:2015jt,Sangiorgi:2011ut}:
 \begin{definition}%[rooted bisimilarity]
@@
 
-\hl{The above definition brings up a proof technique for proving rooted
-bisimilarity results, starting from a given bisimulation.}
+\hl{The above definition also brings up a proof technique for proving rooted
+bisimilarity from a given bisimulation. The next
+lemma is usually not mentioned in CCS literature but plays an
+important role in proving some key results in this paper:}
 \begin{lemma}[Rooted bisimilarity by bisimulation]
@@
 
+\hl{One basic property of rooted bisimiarity is that, it is (like $\sim$)
+a congruence (thus also an equivalence relation)
+w.r.t.~all CCS operators except for the Recursion and is the
+coarsest congruence contained in bisimilarity:}
+(c.f. Section~\ref{s:coarsest} for more details)
 \begin{theorem}
@@
 $\rapprox$ is a congruence in CCS, and it is the
-coarsest congruence contained in $\approx$ \cite{van2005characterisation}.
+coarsest congruence contained in $\wb$.
 \end{theorem}

### 2019-09-09 ic-journal/intro.tex
Stage work revising the paper (2nd round)

@@
 A prominent proof method for bisimulation, put forward by Robin Milner and widely used in his
-landmark CCS book \cite{Mil89}, is the
+landmark CCS book~\cite{Mil89}, is the
 \emph{unique solution of equations}, whereby two tuples of processes are
-componentwise bisimilar if they are solutions 
-of the same system of equations.
+componentwise bisimilar if they are solutions of the same system of equations.
 This method is important in verification techniques and tools
-based on algebraic reasoning \cite{BaeBOOK,theoryAndPractice,RosUnder10}.
+based on algebraic reasoning~\cite{BaeBOOK,theoryAndPractice,RosUnder10}.
 
-In Milner's versions of the unique-solution theorems for weak
-equivalences,
- the  method has severe syntactical limitations:
-the equations must be \emph{(strongly) guarded and sequential}. That is, the
-variables of the equations may only be used underneath a visible
-prefix and proceed, in the syntax tree, only by the sum and prefix operators.
-One way of overcoming such limitations is to replace the equations
+\hl{Milner's unique-solution theorem for weak bisimilarity, however,
+has severe syntactic limitations:}
+the equations must be both \emph{(strongly) guarded} and \emph{sequential}. That is,
+variables of the equations \hl{can only occur underneath visible prefixes and summations.}
+One way \hl{to overcome} such limitations is to replace the equations
 with special inequations called
-\emph{contractions} \cite{sangiorgi2015equations,sangiorgi2017equations}. Contraction is a
-preorder that, roughly, places some efficiency
-constraints on processes.  The uniqueness of solutions of a system of contractions
-is defined as with systems of equations: any two solutions must be (componentwise) bisimilar.
-The difference with equations is in the meaning of a solution:
+\emph{contractions}~\cite{sangiorgi2015equations,sangiorgi2017equations}. Contraction is a
+preorder that, roughly, places some efficiency constraints on processes.
+\hl{The unique solution of contractions is defined as with equations:}
+any two solutions must be componentwise bisimilar.
+The difference \hl{from} equations is \hl{at} the meaning of a solution:
 in the case of contractions the solution is evaluated with respect to
 the contraction preorder, rather than bisimilarity. 
-With contractions, most syntactic limitations of the unique-solution theorem can be
-removed.  One constraint that still remains in
-\cite{sangiorgi2017equations} (in which the issue is bypassed using a more
+With contractions, most syntactic limitations of the unique-solution theorem \hl{are
+eliminated}. One constraint that still remains
+in~\cite{sangiorgi2017equations}
+(where the issue is bypassed using a more
 restrictive CCS syntax)
-is the occurrences of direct sums, due to the failure of the
-substitutivity of contraction under direct sums.
+is the occurrences of \emph{direct} sums (e.g.~$P + Q$) due to
+the \hl{non-substitutivity of the contraction preorder in this case}.
 
-The main goal of the work described in this paper is a %rather
-comprehensive formalisation of the core theory of CCS in the HOL
-theorem prover (HOL4),  with a focus on the theory of unique solutions
-of equations and contractions.
-The formalisation, however, is not confined to the theory of unique
-solutions, but embraces a
-significant portion the theory of CCS~\cite{Mil89}, mostly because the
-theory of unique solutions relies on a large number of more fundamental results.
-Indeed the formalisation encompasses the basic properties of strong and weak
-bisimilarity (e.g.~the fixed-point and substitutivity properties), the
-basic properties of
-rooted bisimilarity (the congruence induced by weak
-bisimilarity, also called observation congruence), and
-their algebraic laws. Further extensions (beyond Nesi
-\cite{Nesi:1992ve}) include four versions of ``bisimulation up to''
-techniques (e.g.~bisimulation up-to bisimilarity) \cite{Mil89,sangiorgi1992problem}, and the
-expansion and contraction preorder (two
-efficiency-like refinements of weak bisimilarity). Concerning rooted bisimilarity, the formalisation
+The work \hl{behind} this paper is a
+comprehensive formalisation of Milner's Calculus of Communicating
+Systems (CCS) in the HOL theorem prover (HOL4),
+with a focus towards the theory of unique solutions of equations and contractions.
+\hl{Almost all results in Milner's CCS book}~\cite{Mil89} are covered, since
+the unique-solution theorems rely on a large number of fundamental results.
+Indeed the formalisation encompasses all basic properties of strong and weak
+\hl{bisimilarities} (e.g.~the fixed-point and substitutivity properties), the
+basic properties of rooted bisimilarity and their algebraic laws.
+Further extensions include several versions of ``bisimulation up to''
+techniques, the expansion and contraction preorder.
+Concerning rooted bisimilarity, the formalisation
 includes \hl{Hennessy's Lemma} and \hl{Deng's Lemma},
  and two \hl{theorems} saying that rooted bisimilarity is the coarsest (largest)
- congruence contained in weak bisimilarity ($\wb$): one following Milner's
- book~\cite{Mil89}, with the hypothesis that no processes can use up
- all labels;
-the other without such hypothesis, essentially formalising van Glabbeek's paper~\cite{van2005characterisation}.
-Similar theorems are proved for the rooted contraction preorder.
+ congruence contained in weak bisimilarity ($\wb$): one is classical
+ with the hypothesis that no process uses up all labels;
+the other without such hypothesis, essentially formalised van Glabbeek's proof~\cite{van2005characterisation}.
+Similar results are also proved for the rooted contraction preorder.
 In this respect, the work is \hl{also} an extensive experiment \hl{using} the HOL theorem prover with its
@@
 further refining the theory of unique solutions of contractions.
-In particular, the existing \hl{theorem}~\cite{sangiorgi2017equations} has
+In particular, Sangiorgi's result~\cite{sangiorgi2017equations} has
 placed limitations on the body of the contractions due to the
@@
 to the sum operator.
-We have thus refined the contraction-based proof technique, by moving to  
+\hl{In this paper, the contraction-based proof technique is further
+refined by moving from the contraction preorder} to
 \emph{rooted contraction}, that is, the coarsest precongruence contained in the contraction
@@
 equivalences and preorders that share similar proof structures.
-%
-% Examples are: the results that rooted bisimilarity and rooted contraction are,
-% respectively, the coarsest congruence contained in weak bisimilarity 
-% and the coarsest precongruence contained in the contraction preorder; 
-% the result about unique solution(s) of equations for weak bisimilarity that uses the
-% contraction preorder as an auxiliary relation, and other unique solution results (e.g.~%
-% the one for rooted in which
-% the auxiliary relation is rooted contraction); various forms of enhancements of the bisimulation
-% proof method (the `up-to' techniques).
-%
 % rephrased: (TODO: still hard to read --Chun)
@@
 
+\hl{The univariate versions of unique-solution theorems use
+$\lambda$-functions to present univariate CCS equations,
+while the multivariate versions require a
+careful and detailed formalisation of CCS equations with equation
+variables and multivariate variable substitutions.
+In contrast to most literature, we have adopted the same
+type for both CCS equations and processes: those undefined constants
+in CCS terms are treated as equation (free) variables, and a CCS
+\emph{process} is a CCS term without equation variables. As a result,
+most CCS results except the unique-solution theorems are valid for
+both CCS processes and equations.} (c.f. Section~\ref{sec:multivariate}
+for more deails.)
+
 \paragraph{Structure of the paper}
@@
 Section~\ref{s:for} highlights our formalisation in HOL4.
+In Section~\ref{sec:multivariate}, \hl{we describe the formalisation of
+multivariate versions of unique-solution theorems.}
 Finally,  Section~\ref{s:rel} and \ref{s:concl} discuss related work,

### 2019-09-09 ic-journal/equa.tex
Done revising equa.tex

@@
 context, we may also write $E[\til P]$ instead of $E \sub {\til P} {\til
-  X}$. ($E[P]$ for $E \sub P X$ in the case of a single variable $X$.)}
+  X}$. (and $E[P]$ for $E \sub P X$ if there is a single equation variable $X$.)}
 
 \hl{In fact, free agent variables have the same transitional behavior
-as the deadlock $\nil$ if we strictly follow the existing SOS rules, as there is
-no SOS rule for them at all. In fact, most CCS theorems still hold if
+as the deadlock $\nil$ according to the SOS rules, as there is
+no rule for their transitions at all. In fact, most CCS theorems still hold if
 the involved CCS terms contain free variables. (The most notable
 exceptions are all versions of unique solution of equations/contracts,
-where all solutions must be \emph{pure} processes (without free variables).)}
+where all solutions must be \emph{pure} processes (i.e. no free variable).)}
 
@@
 say that, if a context $C$ \hl{(i.e., a CCS expression with possibly
-free variables)} obeys certain conditions,
+free variables)}\footnote{\hl{Rigorously speaking, under our setting
+(i.e.~reusing free agent variables as equation variables) not all
+valid CCS expressions
+are valid contexts: those where free variables occur inside
+recusion operators must be all excluded. For instace, $\recu X (a.X +
+b.Y)$ is not a valid context with the variable $Y$. This special requirement
+is perfectly aligned with CCS literature using process constants, as any
+equation variable cannot occur inside the definition of any
+constant. In fact, all versions of ``unique solution of
+equations/contractions'' theorems do not hold if equation variables
+are allowed to occur inside any recursion operator.}} obeys certain conditions,
 then all processes $P$ that satisfy the equation $P \wb \ct P$ are
@@
 
-% TODO
-
-\begin{definition} % Def 3.1
+\begin{definition}[equations] % Def 3.1
 Assume that, for each $i$ of 
  a countable indexing set $I$, we have variables $X_i$, and expressions
-$E_i$ possibly containing  such variables. 
-Then 
-$\{  X_i = E_i\}_{i\in I}$
-is 
-  a \emph{system of equations}. (There is one equation for each variable $X_i$.)
+$E_i$ containing variables up to $\til X$. Then 
+$\{ X_i = E_i\}_{i\in I}$ is 
+  a \emph{system of equations}. (There is one equation $E_i$ for each variable $X_i$.)
 \end{definition}
 
-We write $E[\til P]$ for the expression resulting from $E$ by
-replacing each variable $X_i$   with the process $P_i$, assuming
-$\til P$ and $\til X$ have the same length. (This is syntactic
-replacement.) 
-% The components of $\til P$ need not be
-%  different from each other, as it must be for the variables $\til X$.
-% If the system has infinitely many equations,
-% the  tuples $\til P$ and $\til X$
-%  are infinite too.
-\begin{definition}
+The components of $\til P$ need not be
+different from each other, as it must be for the variables $\til X$.
+If the system has infinitely many equations, the  tuples $\til P$ and $\til X$ are infinite too.
+
+\begin{definition}[solutions and unique solutions]
 Suppose $\{ X_i = E_i\}_{i\in I}$ is a system of equations: 
@@
 \item
- $\til P$ is a \emph{solution of the 
-system of equations  for $\wb$} 
-if for each $i$ it holds
-that $P_i \wb E_i [\til P]$;
-
-\item it %the  system
- has \emph{a unique solution for $\wb$}  if whenever 
- $\til P$ and $\til Q$ are both solutions for $\wb$, then $\til P \wb
- \til Q$. 
+ $\til P$ is a \emph{solution of the system of equations (for $\wb$)} 
+if for each $i$ it holds that $P_i \wb E_i [\til P]$;
+\item The system has \emph{a unique solution for $\wb$}  if whenever 
+ $\til P$ and $\til Q$ are both solutions \hl{it holds that} $\til P \wb \til Q$. 
 \end{itemize} 
  \end{definition}
+\hl{Similarily, the \emph{(unique) solution of a system of equations for $\sim$}
+(or for $\rapprox$) can be obtained by replacing all occurrences of $\wb$
+in above definition with $\sim$ and $rapprox$, respectively.}
 
-% Examples of systems with a  unique solution for $\wb$ are: 
-% \begin{enumerate}
-% \item
-% $ X = a. X$
-
-% \item 
-% $ X_1 = a.  X_2$, $ X_2 = b.  X_1$
-
-% \end{enumerate}
-
-For instance, the solution of the equation 
-$ X = a. X$ 
+For instance, the solution of the equation $X = a. X$ 
 is the process
@@
  $K$ and $K | b$, for $K \DSdefi \recu K {\, (a. K)}$. (Actually any process capable of
-continuously performing \hl{$a$--actions} is a solution \hl{of} $X = a  |  X$.)
+continuously performing \hl{$a$--actions} is a solution \hl{of} $X = a|  X$.)
 
+%
 % The unique solution of the system (1), modulo $\wb$,  is the constant $K \Defi a
@@
 % pair of solutions $P_1,P_2$ we have $K_1 \wb P_1$ and $K_2 \wb P_2$.
-% Examples of systems that do not have a unique solution are: 
-% \begin{enumerate}
-% \item $X = X $
-
-% \item $X = \tau . X$
-% \item $X = a | X$
-
-% \end{enumerate} 
-% All processes are solutions of (1) and (2); examples of solutions for
-% (3) are $K$ and $K | b$, for $K \Defi a
-% . K$.
+%
+Examples of systems that do not have unique solutions are: $X = X$, $X
+= \tau . X$ and $X = a | X$.
 
@@
 \label{def:guardness}
-A system of equations 
-$\{  X_i = E_i\}_{i\in I}$
- is 
+A system of equations $\{ X_i = E_i\}_{i\in I}$ is 
 \begin{itemize}
 \item \emph{weakly guarded} if, in each $E_i$, each occurrence of
-  an \behav\  variable is underneath a prefix;
+  each $X_i$ is underneath a prefix;
 
 \item \emph{(strongly) guarded} if, in each $E_i$, each occurrence of
-  an equation variable is underneath a \emph{visible} prefix;
+  each $X_i$ is underneath a \emph{visible} prefix;
 
-\item \emph{sequential} if, in each $E_i$, each \hl{occurrence of an
-    equation variable only appears underneath prefixes and sums.}
+\item \emph{sequential} if, in each $E_i$, each
+  \hl{occurrence of each $X_i$ is only underneath prefixes and sums.}
 \end{itemize}
@@
 
-\hl{In other words, if the system is sequential, then for
-every expression $E_i$, any subexpression of $E_i$ in which $X_j $
-appears, apart from $X_j$ itself, is a sum (of prefixed terms).
+\hl{In other words, if a system of equations is sequential, then for
+each context $E_i$, any subcontext of $E_i$ in which $X_j $
+appears, apart from $X_j$ itself, is a sum of prefixed expressions.
 For instance,}
@@
  guarded, because the guarding prefix for the variable
-is not visible.
-
-\item $X =  \ell . X | P$ is guarded but not sequential.
-
+is not visible;
+\item $X =  \ell . X | P$ is guarded but not sequential;
 \item $X =  \ell . X + \tau. \res a (a .\outC b | a.\nil)$, as well as
@@
 
-\begin{theorem}[unique solution of equations, \cite{Mil89}]
-\label{t:Mil89}
-A system of guarded and sequential equations (\hl{with guarded sums only})
-$\{  X_i = E_i\}_{i\in I}$ has an unique solution for $\wb$.
+\hl{Milner has totally three versions of ``unique solution of equations''
+theorems, for $\sim$, $\wb$ and $\rapprox$, respectively, but only the
+following two versions are explicitly mentioned} in~\cite{Mil89}:
+\begin{theorem}[unique solution of equations for $\sim$]
+\label{t:Mil89s1}
+Let $E_i$ be weakly guarded with free variables $\subseteq \til X$,
+and let ${\til P} \sim {\til E}\{\til P /\til X\}$,
+  ${\til Q} \sim {\til E}\{\til Q /\til X\}$. Then ${\til P} \sim {\til Q}$.
 \end{theorem}
 
-\hl{The proof exploits an invariance property on immediate transitions for
+\begin{theorem}[unique solution of equations for $\rapprox$]
+\label{t:Mil89s3}
+Let $E_i$ be guarded and sequential with free
+variables $\subseteq \til X$, and let ${\til P} \rapprox {\til E}\{\til P /\til X\}$,
+  ${\til Q} \rapprox {\til E}\{\til Q /\til X\}$. Then ${\til P} \rapprox {\til Q}$.
+\end{theorem}
+
+The version for $\wb$, due to the non-substitutivity of $\wb$, further requires
+that all sums where equation variables appear are guarded sums:
+\begin{theorem}[unique solution of equations for $\wb$]
+\label{t:Mil89}
+Let $E_i$ be guarded (and with guarded sums) and sequential with free
+variables $\subseteq \til X$, and let ${\til P} \wb {\til E}\{\til P /\til X\}$,
+  ${\til Q} \wb {\til E}\{\til Q /\til X\}$. Then ${\til P} \wb {\til Q}$.
+\end{theorem}
+
+The proof of Theorem~\ref{t:Mil89} exploits an invariance property on immediate transitions for
 guarded and sequential expressions, and then extracts a bisimulation
 (up to bisimilarity) out
-of the solutions of the system.  }
+of the solutions of the system.
 To see the need of the sequentiality  condition, consider

### 2019-09-09 ic-journal/response-letter.tex
Finished revising the first past

@@
 
-  TODO
+  We meant the definition should not be \emph{coinductive}, just like the
+  case of $\rapprox$. Notice that, this is just an informal idea when searching for
+  a possible definiton of rooted contraction, and the definition we
+  found at last is indeed not coinductive (nor recursive).
 
@@
   \end{quote}
-  TODO
+  You meant removing also the comma (period) here? But it's different
+  here: the definition ends at clause (2), an end period is added with
+  an ``enspace'' distance.
 

### 2019-09-09 ic-journal/contraction.tex
Finished revising the first past

@@
 
-The constraints on the unique-solution Theorem~\ref{t:Mil89} can be 
+Milner's ``unique solution of equations'' theorem for $\wb$
+(Theorem~\ref{t:Mil89})
+\hl{brings a new proof technique for proving (weak) bisimilarities. However, it has
+severe limitations: the equations must be guarded and sequential (plus
+all sums where equation variables appear must be guarded sums).
+This greatly limits the usefulness of the technique, since
+the occurrences of other operators above the variables, such as parallel
+composition and restriction, in general cannot be removed.}
+The constraints of Theorem~\ref{t:Mil89}, however, can be greatly
 weakened if we move from equations to a special kind of inequations called
@@
 
-Intuitively, the bisimilarity contraction $\mcontrBIS$ is a preorder in which 
-$P \mcontrBIS Q  $  holds  if $P \wb Q$ and, in addition, 
-$Q$ has the \emph{possibility} of being at least as efficient as $P$ (as far as
-$\tau$-actions performed). 
-Process $Q$, however, may be nondeterministic and may have other ways
+Intuitively, the bisimilarity contraction $\mcontrBIS$ is a preorder
+such that, $P \mcontrBIS Q$ holds if $P \wb Q$ and, in addition, 
+$Q$ \emph{has the possibility of being at least as efficient as $P$} (as far as
+$\tau$-actions are performed).
+Process $Q$, however, may be non-deterministic and may have other ways
 of doing the same work, and these could be slow (i.e., involving
-more $\tau$-steps than those performed by $P$).
+more $\tau$-\hl{actions} than those performed by $P$).
 % Thus, in contrast with expansion,  we cannot really say that `$Q$ is more efficient than
@@
 
-\begin{definition}%[bisimulation contraction]
+\begin{definition}[contraction]
 \label{d:BisCon}
@@
 transition with at most one transition.
-This makes sure that $Q$ is capable of mimicking $P$'s
-work at least as efficiently as $P$. 
+This makes sure that $Q$ is capable of mimicking % verb: mimic
+$P$'s work at least as efficiently as $P$. 
 In contrast, the second clause of Definition~\ref{d:BisCon}, on the
@@
 Bisimilarity contraction is coarser than 
-the \emph{expansion relation} $\expa$~\cite{arun1992efficiency,sangiorgi2015equations}.
-This is a preorder \hl{that is} widely used in proof techniques for bisimilarity and
-intuitively refines bisimilarity by 
-formalising the idea of `efficiency' between processes.
-Clause (1) is the same in the two
-preorders. But in clause (2) expansion uses 
-$P \Arr \mu P'$, rather than $P \Arcap \mu P'$; 
- moreover with
-contraction the final derivatives are simply required to be bisimilar.
-An expansion 
-$P \expa Q$
-tells us  that $Q$ is always at least as efficient as $P$, whereas  the
- contraction $P \mcontrBIS Q$  just says that $Q$ has the possibility of
-being at least as efficient as $P$.
-
-% \iflong\newDS
-% Note the use of $\wb$, in place of $\R$, in the second clause:
-%  we are only interested to know that $Q$ may  mimic $P$'s
-% more in an efficient manner (first clause); we do not care about
-% efficiency
-% on the
-% challenges proposed by $Q$,   which are handled using ordinary
-% bisimilarity.
-% \fi
-
+the \emph{expansion relation}
+$\expa$~\cite{arun1992efficiency,sangiorgi2015equations}:
 \begin{definition}%[expansion]
@@
  \end{definition}
+The expansion preorder is widely used in proof techniques for bisimilarity and
+intuitively refines bisimilarity by 
+formalising the idea of ``efficiency'' between processes.
+Clause (1) is the same in the \hl{both}
+preorders, while in clause (2) expansion uses 
+$P \Arr \mu P'$, rather than $P \Arcap \mu P'$; 
+moreover in clause (2) of Def.~\ref{d:BisCon} the final derivatives
+are simply required to be bisimilar ($P' \wb Q'$).
+\hl{Intuitively, $P \expa Q$ holds if $P\wb Q$ and, in addition, \emph{$Q$
+  is always at least as efficient as $P$}.}
 
@@
 summation. The proofs are similar, see e.g.}~\cite{sangiorgi2017equations}.
+
+% next file: unique.tex

### 2019-09-09 ic-journal/equa.tex
Finished revising the first past

@@
 \begin{definition}[equations] % Def 3.1
+  \label{def:equation}
 Assume that, for each $i$ of 
@@
 \begin{definition}[solutions and unique solutions]
+  \label{def:solution}
 Suppose $\{ X_i = E_i\}_{i\in I}$ is a system of equations: 
@@
 theorems, for $\sim$, $\wb$ and $\rapprox$, respectively, but only the
-following two versions are explicitly mentioned} in~\cite{Mil89}:
+following two versions are explicitly mentioned} in~\citep[p.~103, 158]{Mil89}:
 \begin{theorem}[unique solution of equations for $\sim$]
 \label{t:Mil89s1}
-Let $E_i$ be weakly guarded with free variables $\subseteq \til X$,
+Let $E_i$ be weakly guarded with free variables up to $\til X$,
 and let ${\til P} \sim {\til E}\{\til P /\til X\}$,
@@
 Let $E_i$ be guarded and sequential with free
-variables $\subseteq \til X$, and let ${\til P} \rapprox {\til E}\{\til P /\til X\}$,
+variables up to $\til X$, and let ${\til P} \rapprox {\til E}\{\til P /\til X\}$,
   ${\til Q} \rapprox {\til E}\{\til Q /\til X\}$. Then ${\til P} \rapprox {\til Q}$.
@@
 
-The version for $\wb$, due to the non-substitutivity of $\wb$, further requires
-that all sums where equation variables appear are guarded sums:
+\hl{The version of Milner's unique-solution theorem for $\wb$ further requires
+that all sums where equation variables appear are guarded
+sums}\footnote{But if the CCS syntax were defined with only guarded
+  sums, i.e., $\sum_{i\in I} \mu_i.P_i$ as
+  in~\cite{sangiorgi2015equations}, this addition
+  requirement disappears automatically, and we can even say $\wb$ is indeed a
+  congruence.}:
 \begin{theorem}[unique solution of equations for $\wb$]
 \label{t:Mil89}
-Let $E_i$ be guarded (and with guarded sums) and sequential with free
-variables $\subseteq \til X$, and let ${\til P} \wb {\til E}\{\til P /\til X\}$,
+Let $E_i$ be guarded (with guarded sums only) and sequential with free
+variables up to $\til X$, and let ${\til P} \wb {\til E}\{\til P /\til X\}$,
   ${\til Q} \wb {\til E}\{\til Q /\til X\}$. Then ${\til P} \wb {\til Q}$.
@@
 
-The proof of Theorem~\ref{t:Mil89} exploits an invariance property on immediate transitions for
-guarded and sequential expressions, and then extracts a bisimulation
+The proof of \hl{the last theorem above} exploits an invariance
+property on immediate \hl{derivations}
+of guarded and sequential expressions, and then extracts a bisimulation
 (up to bisimilarity) out
@@
 
+\hl{For more details of above three theorems,} c.f. Section~\ref{ss:part2}
+for their formalised versions (the univariate case) and
+Section~\ref{sec:multivariate} for the multivariate case
+(Theorem~\ref{t:Mil89s1} only).
+
 %% next file: contraction.tex

### 2019-09-09 ic-journal/unique.tex
Finished revising the first past

@@
 except that the contraction symbol $\mcontr$ is used in the place of
-the equality symbol $=$. Thus a system of contractions is a set 
-$\{  X_i \mcontr E_i\}_{i\in I}$
-where $I$ is an  indexing set and expressions
-$E_i$  may contain the  \behavC\  variables 
-$\{  X_i\}_{i\in I}$.
+$=$ in Def.~\ref{def:equation}. Thus a system of contractions is a set 
+$\{  X_i \mcontr E_i\}_{i\in I}$ where $I$ is an indexing set and each
+$E_i$  contains variables up to $\til X$.
 
-\begin{definition}
-\label{d:uniContra}
-Given a system of contractions 
-$\{  X_i \mcontr E_i\}_{i\in I}$, 
- we say that:
-\begin{itemize}
-\item $\til P$ is a \emph{solution (for $\mcontrBIS$) of the 
- system of contractions} if \hl{for each $i$ it holds that $P_i \mcontrBIS E_i [\til P]$};
-\item \hl{The} system has \emph{a unique solution (for $\approx$)}
-if $\til P \approx \til Q$ whenever $\til P$ and $\til Q$ are both solutions.
-\end{itemize}
-\end{definition}
-
-The guardedness of contractions follows Def.~\ref{def:guardness} (for equations).
-% \begin{definition}
-% \label{d:guarded}
-% A system of contractions $\{  X_i \mcontr E_i\}_{i\in I}$
-%  is
-% \emph{weakly guarded}
-% if,  in each    $E_i$, each occurrence of
-% a \behavC\ variable is underneath a prefix.
-
-% The system use \emph{guarded sums} if 
-% each $E_i$ only makes use of guarded sums.
-% \end{definition}
+\hl{Now we recall (with the proof) Sangiorgi's ``unique solution of
+contractions'' theorem}~\cite{sangiorgi2017equations},
+which greatly weakened the requirements of Milner's result
+(Theorem~\ref{t:Mil89}).
 
@@
 guarded sums.
-For any context $\qct$  that uses 
-guarded sums,
+For any context $\qct$  that uses guarded sums,
 if $\ct{\til P}\Arr{\mu}  R$, then there is a context $\qctp$  that uses 
@@
 
-\begin{proof}{(sketch from \cite{sangiorgi2017equations})}
+\begin{proof}{(sketch from~\cite{sangiorgi2017equations})}
   Let $n$ be the length \hl{(the number of one-step transitions)} of
@@
 
-\begin{theorem}[unique solution of contractions~\cite{sangiorgi2017equations}] % for $\wb$
-\label{t:contraBisimulationU} % Thm 3.10
-%A system of weakly-guarded contractions
-%having only guarded sums, has a unique solution for $\wb$.
-\hl{Let the expressions $E_i$ ($i \in I$) contain at most the
-  variables $X_i$ ($i \in I$), and let each $X_j$ ($j\in I$) be weakly
-  guarded in each $E_i$. For any two groups of CCS processes $P_i$ and
-  $Q_i$ ($i \in I$), if $\til P \mcontrBIS \til E\{\til P/\til X\}$ and
-    $\til Q \mcontrBIS \til E\{\til Q/\til X\}$ then $\til P \wb \til Q$.}
+\begin{theorem}[unique solution of contractions~\cite{sangiorgi2017equations}]
+\label{t:contraBisimulationU} % was: Thm 3.10
+\hl{Let $E_i$ be weakly guarded (and with guarded sums only) with free
+variables up to $\til X$, and let $\til P \mcontrBIS \til E\{\til P/\til X\}$,
+    $\til Q \mcontrBIS \til E\{\til Q/\til X\}$. Then $\til P \wb \til Q$.}
 \end{theorem}
@@
 \begin{equation*}
-%\label{eq:R}
 \R \DSdefi \{(R,S) \st R \wb \ct{\til P}, S \wb \ct{\til Q} \mbox{~for some context
@@
 
-The unique solution theorem of Section~\ref{ss:SysContr} requires a
-constrained syntax for sums, due to the congruence and precongruence
-problems of bisimilarity and contraction with such operator. 
-We show here that the constraints can be
-removed by moving to the induced congruence and precongruence, the
-latter called \emph{rooted contraction}:
+Theorem~\ref{t:contraBisimulationU} brings a new proof technique for
+bisimilarity, which is much less restrictive than Milner's
+Theorem~\ref{t:Mil89} (but with the additional costs of checking $\mcontrBIS$
+in addition to $\wb$).
+However, comparing with Milner's Theorem~\ref{t:Mil89s1}, \hl{there is
+still one more limit: the involved CCS contexts must only
+use guarded sums. The is mainly due to the fact that $\wb$ is not a
+ (real) congruence and also $\mcontrBIS$ is not a (real) precongruence.
+Inspired by rooted bisimilarity, to completely eliminate the restriction
+on guarded sums, we have extended the idea of contractions by moving
+to \emph{rooted contractions}:}
+
 \begin{definition}
@@
 
-%Above definition adapts the definition of rooted
-%bisimilarity on top of that of the  contraction preorder
-%$\mcontrBIS$.  %% Reviewer said this sentance is unclear. I too think so.
-
-The precise formulation of  this definition was guided by the HOL theorem
-prover and
-the following two principles: (1) the definition should not be recursive,
-along the lines of rooted bisimilarity
-$\rapprox$ in Def.~\ref{d:rootedBisimilarity};
+\hl{The above definition was found with the help of interactive theorem proving.}
+First of all, the following two principles were adopted when searching
+for a possible definition: (1) the definition should not be \hl{coinductive},
+along the lines of rooted bisimilarity $\rapprox$ (Def.~\ref{d:rootedBisimilarity});
 (2) the definition should be built on top of existing \emph{contraction}
-relation $\mcontrBIS$ (because of its completeness). 
-A few other candidates were quickly tested and rejected, e.g.,
-  because of  precongruence issue. The proof of the precongruence
- result below is along the lines of the analogous result
-for rooted bisimilarity with respect to bisimilarity.
+relation $\mcontrBIS$.
+\hl{Then several candidates were quickly checked (using very similar
+  proof steps): the key is to prove its transitivity, and whenever the
+  proof attempts failed we tried to fix the definition. Eventually the
+  above definition was found and shown to be a precongruence, i.e. it
+  is preserved by all CCS operators except the Recursion, same as in
+  the cases of $\sim$ and $\rapprox$.}
+\hl{Furthermore, we needed to show that, the definition being found is the
+best possible one, by showing that it is the coarsest precongruence
+contains in $\mcontrBIS$, and the proof succeeded and is very similar
+with the same result for $\rapprox$} (c.f.~Section~\ref{s:coarsest} for
+more details).
 
@@
 \label{t:rcontrPrecongruence}
-$\rcontr$ is a precongruence in CCS, and it is the
-coarsest precongruence contained in $\contr$.
+$\rcontr$ is a precongruence in CCS, and it is the coarsest
+precongruence contained in $\mcontrBIS$.
 \end{theorem}
 
-For a system of rooted contractions, the meaning of 
-``solution for $\rcontr$'' and of \emph{a unique solution for $\rapprox$}
-is the expected one --- just replace in Def.~\ref{d:uniContra}  the preorder 
-$\contr$ with $\rcontr$, and the equivalence 
-$\approx$ with $\rapprox$ (note that with $\rapprox$ one considers
-solutions with respect to  $\rcontr$).
-%
 For this new relation, the analogous of Lemma~\ref{l:uptocon} and of
-Theorem~\ref{t:contraBisimulationU} can now be stated without constraints on the sum
-operator.
+Theorem~\ref{t:contraBisimulationU} can now be stated without
+constraints on the sum operator.
 The schema of the proofs is almost identical, because all 
@@
 Suppose $\til P$ and $\til Q$ are solutions  for $\rcontr$ 
- of a system of weakly-guarded
-contractions.
+ of a system of weakly-guarded contractions.
 For any context $\qct$, 
 if  $\ct{\til P}\Arr{\mu}  R$,
- then 
-there is a  context $\qctp$
+ then there is a context $\qctp$
 such that $R \mcontrBIS \ctp{\til P}$ and  $\ct{\til Q} \Arr{\mu} R'
@@
 \end{lemma}
-The proof of Lemma~\ref{l:ruptocon} is exactly the same as of
-Lemma~\ref{l:uptocon}, \hl{because all we need from $\mcontrBIS$ (or
-$\rcontr$) is their substitutivity properties (as precongruences)
-w.r.t the corresponding definitions of contexts.}
-Notice also that, the conclusion of
-Lemma~\ref{l:ruptocon} still uses $\mcontrBIS$, as $\rcontr$ does
-not hold.
+% The proof of Lemma~\ref{l:ruptocon} is exactly the same as of
+% Lemma~\ref{l:uptocon}, \hl{because all we need from $\mcontrBIS$ (or
+% $\rcontr$) is their substitutivity properties (as precongruences)
+% w.r.t the corresponding definitions of contexts.}
+% Notice also that, the conclusion of
+% Lemma~\ref{l:ruptocon} still uses $\mcontrBIS$, as $\rcontr$ does
+% not hold.
 
 \hl{The next lemma is actually Lemma 3.13} of~\citep[p.~102]{Mil89}, \hl{which
-was designed to prove Milner's strong unique-solution theorem} (Prop.~3.14 of
-\citep[p.~103]{Mil89}).
+was designed to prove Milner's ``unique solution of equations for
+$\sim$''} (Theorem~\ref{t:Mil89s1}):
 \begin{lemma}
@@
 \label{t:rcontraBisimulationU}
-%A system of weakly-guarded contractions has a unique solution for $\rapprox$. 
-% (thus also for $\wb$).
-\hl{Let the expressions $E_i$ ($i \in I$) contain at most the
-  variables $X_i$ ($i \in I$), and let each $X_j$ ($j\in I$) be weakly
-  guarded in each $E_i$. For any two groups of CCS processes $P_i$ and
-  $Q_i$ ($i \in I$), if $\til P \rcontr \til E\{\til P/\til X\}$ and
-    $\til Q \rcontr \til E\{\til Q/\til X\}$ then $\til P \rapprox \til Q$.}
+\hl{Let $E_i$ be weakly guarded with free variables up to $\til X$,
+and let $\til P \rcontr \til E\{\til P/\til X\}$,
+    $\til Q \rcontr \til E\{\til Q/\til X\}$. Then $\til P \rapprox \til Q$.}
 \end{theorem}

### 2019-09-10 ic-journal/multivariate.tex
Stage fixes with highlights
Stage work on 2nd part

@@
 
-\section{Multivariate extensions}
+\section{The multivariate formalisation}
+\label{sec:multivariate}
 
-(\hl{This section is new.})
+In this section, the formalisation of the multivariate (general)
+cases of Milner's ``unique solution of equations (for $\sim$)''
+(Theorem~\ref{t:Mil89s1}) and our ``unique solution of rooted
+contractions'' (Theorem~\ref{t:rcontraBisimulationU}) is
+described. This work is entirely new after~\cite{EPTCS276.10}.
+We choose these two theorems because they both depend on the same
+concept of ``weakly guarded contexts'', and Lemma~\ref{lem:milner313}.
+This further extension is accumulative and is completely based on the
+existing formal framework in the sense that, neither the CCS datatype nor
+the SOS rules need to be changed.
+
+The central problem of the multivariate formalisation is the
+representation of CCS equations and equation variables. Regarding
+a system of equations $\{X_i = E_i\}_{i\in I}$ as in
+Def.~\ref{def:equation},
+modern literature (after Milner) usually consider $X_i$ as
+\emph{process variables (or equation variables)}~\citep[p.~102]{Gorrieri:2015jt}
+\emph{outside} of the CCS syntax, and treat $E_i$ as an \emph{open} expression
+built with CCS operators which may contain some occurrences of $X_i$.
+For a formal point of view, this means we either need to define a
+whole new datatype (with extra equation variables) in which each CCS
+opeartor must be duplicated, or we should added equation variables as a
+new primitive element (e.g.~\texttt{Var X}) beside the recursion
+variables (e.g.~\texttt{var X}), then the substitution of equation
+variables in $E_i\{\til P/\til X\}$ would be simply the \emph{syntactic substitution} of
+each occurrence of $X_i$ in $E_i$ with the corresponding $P_i$. Notice that, in
+either case the \emph{disjointness} between equation variables and recursion
+variables (i.e. constants) is obvious and syntactically
+guaranteed. However, neither solution is elegant: dealing with another CCS-like type makes the
+whole formalisation work ugly and we loose the (possibly valuable) bisimilarity concepts and
+transitional semantics of CCS expressions; on the other hand,
+modifying the CCS datatype to just support the formalisation of
+unique-solution theorems is also not acceptable.
+
+Following the beginning of Section~\ref{s:eq},
+
+\subsection{Free and bound variables}
+
+\cite{milner1990operational}
+The following cases are interesting:
+
+\begin{center}
+\begin{tabular}{|l|l|}
+\hline
+\HOLConst{FV} \ensuremath{(}\HOLConst{var} \HOLFreeVar{X}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLTokenLeftbrace{}\HOLFreeVar{X}\HOLTokenRightbrace{} & \HOLConst{FV} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{p}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{FV} \HOLFreeVar{p} \HOLConst{DELETE} \HOLFreeVar{X} \\
+\HOLConst{BV} \ensuremath{(}\HOLConst{var} \HOLFreeVar{X}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\HOLTokenEmpty{}} & \HOLConst{BV} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{p}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLFreeVar{X} \HOLConst{INSERT} \HOLConst{BV} \HOLFreeVar{p} \\
+\hline
+\end{tabular}
+\end{center}
+
+\begin{small}
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u}.
+\HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sp{\prime}}.
+\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sp{\prime}}.
+\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sp{\prime}}.
+\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sp{\prime}}.
+\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\HOLBoundVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{1}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{l} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{E\sb{\mathrm{2}}}.
+            \HOLBoundVar{P} \HOLBoundVar{E} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \HOLBoundVar{E\sp{\prime}} \ensuremath{(}\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLBoundVar{l}\ensuremath{)}\ensuremath{)} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLSymConst{\ensuremath{\tau}} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{l} \HOLBoundVar{L}.
+            \HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLBoundVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \HOLBoundVar{E\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{rf}.
+\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)} \ensuremath{(}\HOLConst{relabel} \HOLBoundVar{rf} \HOLBoundVar{u}\ensuremath{)} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{rf}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{X} \HOLBoundVar{E\sb{\mathrm{1}}}.
+\HOLBoundVar{P} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a\sb{\mathrm{0}}} \HOLBoundVar{a\sb{\mathrm{1}}} \HOLBoundVar{a\sb{\mathrm{2}}}.
+\HOLBoundVar{a\sb{\mathrm{0}}} \HOLTokenTransBegin\HOLBoundVar{a\sb{\mathrm{1}}}\HOLTokenTransEnd \HOLBoundVar{a\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLBoundVar{a\sb{\mathrm{0}}} \HOLBoundVar{a\sb{\mathrm{1}}} \HOLBoundVar{a\sb{\mathrm{2}}}
+\end{alltt}
+\end{small}
 
 \begin{alltt}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{BV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLFreeVar{E}
+
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}
+\end{alltt}
+
+\begin{alltt}
+   \HOLConst{IS_PROC} \HOLFreeVar{P} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{FV} \HOLFreeVar{P} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\HOLTokenEmpty{}}
+
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{IS_PROC} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{IS_PROC} \HOLFreeVar{E\sp{\prime}}
+\end{alltt}
+
+\subsection{Multivariate substitutions}
+
+\begin{alltt}
+   \HOLConst{CCS_SUBST} \HOLFreeVar{fm} \ensuremath{(}\HOLConst{var} \HOLFreeVar{X}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLFreeVar{fm} \HOLKeyword{then} \HOLFreeVar{fm} \HOLConst{'} \HOLFreeVar{X} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{X}
+
+   \HOLConst{CCS_SUBST} \HOLFreeVar{fm} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}}
+     \HOLKeyword{if} \HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLFreeVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{X} \ensuremath{(}\HOLConst{CCS_SUBST} \ensuremath{(}\HOLFreeVar{fm} \HOLSymConst{\ensuremath{\setminus}} \HOLFreeVar{X}\ensuremath{)} \HOLFreeVar{E}\ensuremath{)}
+     \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{X} \ensuremath{(}\HOLConst{CCS_SUBST} \HOLFreeVar{fm} \HOLFreeVar{E}\ensuremath{)}
+\end{alltt}
+
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{CCS_SUBST} \ensuremath{(}\HOLConst{FEMPTY} \HOLSymConst{|+} \ensuremath{(}\HOLFreeVar{X}\HOLSymConst{,}\HOLFreeVar{E\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
+
+\HOLTokenTurnstile{} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{E}
+
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLFreeVar{X} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}}
+   \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
+\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLBoundVar{e}\ensuremath{)} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
+       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \ensuremath{(}\HOLFreeVar{X}\HOLSymConst{::}\HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+       \ensuremath{[}\HOLFreeVar{P}\HOLSymConst{::}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{X}\HOLSymConst{::}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLFreeVar{P}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}
+
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}}
+   \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{p}\ensuremath{)}.
+\HOLConst{FV} \HOLBoundVar{p} \HOLSymConst{\HOLTokenSubset{}} \HOLTokenLeftbrace{}\HOLBoundVar{x}\HOLTokenRightbrace{}\ensuremath{)} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLFreeVar{Xs}\HOLSymConst{,}\HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+   \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{FOLDR} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}\ensuremath{)} \HOLBoundVar{e}.
+\ensuremath{[}\HOLBoundVar{y}\ensuremath{/}\HOLBoundVar{x}\ensuremath{]} \HOLBoundVar{e}\ensuremath{)} \HOLFreeVar{E} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLFreeVar{Xs}\HOLSymConst{,}\HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
+
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLConst{MAP} \HOLConst{var} \HOLFreeVar{Xs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{E}
+
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}}
+   \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{C}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+   \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLConst{MAP} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}
+
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+   \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{BV} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
+
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+   \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DIFF} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{FV} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
+\end{alltt}
+
+\subsection{Multivariate (weakly-guarded) contexts}
+
+\begin{alltt}
+   \HOLConst{context} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenDefEquality{}}
+     \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}.
+\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
+\HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Xs}\ensuremath{)}
+
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLConst{context} \HOLFreeVar{Xs}\ensuremath{)} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
+   \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
+   \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)}
+
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{Qs} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
+\HOLConst{context} \HOLFreeVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\HOLTokenStrongEQ} \ensuremath{[}\HOLFreeVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E}
+
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Qs} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
+\HOLConst{context} \HOLFreeVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \ensuremath{[}\HOLFreeVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E}
+
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{Qs} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
+\HOLConst{context} \HOLFreeVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsContracts} \ensuremath{[}\HOLFreeVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E}
+\end{alltt}
+
+\begin{alltt}
+   \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenDefEquality{}}
+     \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}.
+\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
+\HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Xs}\ensuremath{)}
+
+\HOLTokenTurnstile{} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{E}
+
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
+   \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
+   \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)}
+\end{alltt}
+
+\subsection{Multivariate equations and solutions}
+
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{CCS_equation} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenEquiv{}}
+   \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
+\HOLConst{FV} \HOLBoundVar{e} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLFreeVar{Es}
+
+\HOLTokenTurnstile{} \HOLConst{CCS_solution} \HOLFreeVar{R} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenEquiv{}}
+   \HOLConst{ALL_PROC} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
+\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenConj{}}
+   \HOLConst{LIST_REL} \HOLFreeVar{R} \HOLFreeVar{Ps} \ensuremath{(}\HOLConst{MAP} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{Es}\ensuremath{)}
+\end{alltt}
+
+\subsection{Unique solution of equations for $\sim$ (the multivariate version)}
+
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps}.
+       \HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{P\sp{\prime}}.
+           \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+           \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sp{\prime}}.
+               \HOLConst{context} \HOLFreeVar{Xs} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+               \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
+\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}
+
 \HOLTokenTurnstile{} \HOLConst{CCS_equation} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
@@
 \end{alltt}
+
+\subsection{Unique solution of rooted contractions (the multivariate version)}
 

### 2019-09-10 ic-journal/multivariate.tex
Stage work on multivariate section.

@@
 contractions'' (Theorem~\ref{t:rcontraBisimulationU}) is
-described. This work is entirely new after~\cite{EPTCS276.10}.
+described.
 We choose these two theorems because they both depend on the same
 concept of ``weakly guarded contexts'', and Lemma~\ref{lem:milner313}.
-This further extension is accumulative and is completely based on the
+This work is entirely new after~\cite{EPTCS276.10}.
+It is accumulative, completely based on the
 existing formal framework in the sense that, neither the CCS datatype nor
@@
 The central problem of the multivariate formalisation is the
-representation of CCS equations and equation variables. Regarding
-a system of equations $\{X_i = E_i\}_{i\in I}$ as in
-Def.~\ref{def:equation},
-modern literature (after Milner) usually consider $X_i$ as
-\emph{process variables (or equation variables)}~\citep[p.~102]{Gorrieri:2015jt}
+representation of CCS equations (expressions, contexts).
+Recall the univariate formalisation, $\lambda$-functions (of type
+$CCS\rightarrow CCS$) are used to represent univariate CCS
+equations, and variable substitutions are simply done by
+calling $\lambda$-functions on the target CCS terms.
+This idea cannot be extended to the multivariate case, as
+we don't have a fixed number of variables to deal with.
+
+Modern literature (i.e.~after Milner) usually consider the $X_i$ of
+a system of equations $\{X_i = E_i\}_{i\in I}$ (c.f. Def.~\ref{def:equation}) as an
+\emph{equation variable (or process variable)}~\citep[p.~102]{Gorrieri:2015jt}
 \emph{outside} of the CCS syntax, and treat $E_i$ as an \emph{open} expression
@@
 whole new datatype (with extra equation variables) in which each CCS
-opeartor must be duplicated, or we should added equation variables as a
-new primitive element (e.g.~\texttt{Var X}) beside the recursion
-variables (e.g.~\texttt{var X}), then the substitution of equation
+opeartor must be duplicated, or we should add equation variables as a
+new primitive (e.g.~\texttt{Var X}) in the existing CCS type, beside the recursion
+variables (e.g.~\texttt{var X}). Then the substitution of equation
 variables in $E_i\{\til P/\til X\}$ would be simply the \emph{syntactic substitution} of
@@
 
-Following the beginning of Section~\ref{s:eq},
+In this project, we have chosen to adopt Milner's original approach,
+which is also the most elegant way: reusing \emph{free} recursion variables
+(i.e. undefined constants) as equation variables, then the variable
+substitution function used in SOS rules [\texttt{REC}] can be also
+used for substituting eqaution variables.
+However, this approach brings us great difficulities in proving many
+fundamental lemmas, mostly due to the variable capture issues between
+equation variables and recursion variables. We believe all these
+issues are solvable.
 
@@
 
-\cite{milner1990operational}
-The following cases are interesting:
+Recall the beginning of Section~\ref{s:eq},
+the CCS syntax leaves the syntactic possibility that an
+agent variable $A$ occurs outside the recursion operator of the same
+variable. In Milner's original book chapter~\cite{milner1990operational}, the
+variables which occur in Recursion (such as $X$ in $\recu X E$) are
+called \emph{bound} variables, while those which occur unbound are called
+\emph{free} variables. We denote the set of all bound variables of a
+given CCS term $E$ as \HOLinline{\HOLConst{BV} \HOLFreeVar{E}}, and the set of all free
+variables as \HOLinline{\HOLConst{FV} \HOLFreeVar{E}}. In HOL, both \HOLinline{\HOLConst{BV}} and \HOLinline{\HOLConst{FV}} have the
+type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}''.
+Milner didn't give their definitions
+explicitly, however,
 

### 2019-09-11 ic-journal/multivariate.tex
Stage work on multivariate section

@@
 opeartor must be duplicated, or we should add equation variables as a
-new primitive (e.g.~\texttt{Var X}) in the existing CCS type, beside the recursion
-variables (e.g.~\texttt{var X}). Then the substitution of equation
+new primitive (e.g.~\texttt{Var X}) in the existing CCS type beside
+the agent variables (e.g.~\texttt{var X}). Then the substitution of equation
 variables in $E_i\{\til P/\til X\}$ would be simply the \emph{syntactic substitution} of
 each occurrence of $X_i$ in $E_i$ with the corresponding $P_i$. Notice that, in
-either case the \emph{disjointness} between equation variables and recursion
-variables (i.e. constants) is obvious and syntactically
+either case the \emph{disjointness} between equation variables and
+agent variables (or constants) is obvious and syntactically
 guaranteed. However, neither solution is elegant: dealing with another CCS-like type makes the
@@
 In this project, we have chosen to adopt Milner's original approach,
-which is also the most elegant way: reusing \emph{free} recursion variables
+which is also the most elegant way: reusing \emph{free} agent variables
 (i.e. undefined constants) as equation variables, then the variable
@@
 fundamental lemmas, mostly due to the variable capture issues between
-equation variables and recursion variables. We believe all these
-issues are solvable.
+equation variables and agent variables.
 
@@
 \emph{free} variables. We denote the set of all bound variables of a
-given CCS term $E$ as \HOLinline{\HOLConst{BV} \HOLFreeVar{E}}, and the set of all free
-variables as \HOLinline{\HOLConst{FV} \HOLFreeVar{E}}. In HOL, both \HOLinline{\HOLConst{BV}} and \HOLinline{\HOLConst{FV}} have the
-type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}''.
-Milner didn't give their definitions
-explicitly, however,
-
+given CCS term $E$ as $\bv{E}$ (or \HOLinline{\HOLConst{BV}\\\;\HOLFreeVar{E}} in HOL), and the set of all free
+variables as $\fv{E}$ (or \HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}} in HOL). Both \HOLinline{\HOLConst{BV}} and \HOLinline{\HOLConst{FV}} have the
+type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}'', i.e.
+functions taking CCS terms returning sets of
+variables (of type \HOLinline{\ensuremath{\alpha}}).
+Milner didn't give their definitions explicitly. However, one can
+imagine that, for most CCS operators they just pass into
+subterms without collecting anything (and $\nil$ gives $\emptyset$).
+The only interesting cases are Recursion and agent variables, shown below: (Here \texttt{DELETE}
+and \texttt{INSERT} are set-theoretic operators of HOL's
+\texttt{pred_set} theory.)
 \begin{center}
@@
 \end{center}
+Furthermore, we say $E$ is a process, denoted by \HOLinline{\HOLConst{IS_PROC} \HOLFreeVar{E}}, if
+it contains no free variables, i.e. $\fv{E} = \emptyset$:
+\begin{alltt}
+   \HOLConst{IS_PROC} \HOLFreeVar{E} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\HOLTokenEmpty{}}
+\end{alltt}
 
-\begin{small}
+Notice that, for any CCS expression, the set of free and bound
+variables may not be disjoint, e.g. $X + \recu X E$.
+More importantly, when going
+from a CCS expression to its sub-expressions, the set of free
+variables may increase, while the set of bound variables always
+decrease. For instance, $\fv{\recu X (\mu.X)} = \emptyset$, while
+$\fv{\mu.X} = \{X\}$. This property of $\fv{\cdot}$ brings greatly
+difficulities when doing proofs on CCS transitions. As an evidence,
+we prove the following fundamental result about $\fv{\cdot}$:
+
+\begin{proposition}
+\label{prop:transFV}
+The derivatives of a process are themselves processes, i.e.
+if $E \arr{\mu} E'$ and $\fv{E} = \emptyset$, then $\fv{E'} =
+\emptyset$. Or, formally:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}}.
+\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{IS_PROC} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{IS_PROC} \HOLBoundVar{E\sp{\prime}}\hfill{[TRANS_PROC]}
+\end{alltt}
+\end{proposition}
+
+\begin{proof}
+Milner said it can be proven by ``an easy action
+induction''~\cite{milner1990operational}. However this is not true at all.
+%
+To see things more clearly, we try to prove a stronger result,
+i.e. the set of free variables decreases through derivations:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}}.
+\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E}\hfill{[TRANS_FV]}
+\end{alltt}
+
+From HOL's viewpoint, the so-called ``action induction'' is actually a higher-order matching
+based on the following induction principle generated
+together with SOS rules:
 \begin{alltt}
@@
        \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{l} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-            \HOLBoundVar{P} \HOLBoundVar{E} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \HOLBoundVar{E\sp{\prime}} \ensuremath{(}\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLBoundVar{l}\ensuremath{)}\ensuremath{)} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLSymConst{\ensuremath{\tau}} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+            \HOLBoundVar{P} \HOLBoundVar{E} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \HOLBoundVar{E\sp{\prime}} \ensuremath{(}\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLBoundVar{l}\ensuremath{)}\ensuremath{)} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
+            \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLSymConst{\ensuremath{\tau}} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{l} \HOLBoundVar{L}.
-            \HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLBoundVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \HOLBoundVar{E\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+            \HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLBoundVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+            \HOLBoundVar{P} \ensuremath{(}\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \HOLBoundVar{E\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{rf}.
@@
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a\sb{\mathrm{0}}} \HOLBoundVar{a\sb{\mathrm{1}}} \HOLBoundVar{a\sb{\mathrm{2}}}.
-\HOLBoundVar{a\sb{\mathrm{0}}} \HOLTokenTransBegin\HOLBoundVar{a\sb{\mathrm{1}}}\HOLTokenTransEnd \HOLBoundVar{a\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLBoundVar{a\sb{\mathrm{0}}} \HOLBoundVar{a\sb{\mathrm{1}}} \HOLBoundVar{a\sb{\mathrm{2}}}
+\HOLBoundVar{a\sb{\mathrm{0}}} \HOLTokenTransBegin\HOLBoundVar{a\sb{\mathrm{1}}}\HOLTokenTransEnd \HOLBoundVar{a\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLBoundVar{a\sb{\mathrm{0}}} \HOLBoundVar{a\sb{\mathrm{1}}} \HOLBoundVar{a\sb{\mathrm{2}}}\hfill{[TRANS_IND]}
 \end{alltt}
-\end{small}
+In the above long theorem, the outermost universal quantifier $P$ is a
+proposition about transition arguments $E$, $\mu$ and $E'$, and in
+this case $P(E, \mu, E')$ is actually $\fv{E'} \subseteq \fv{E}$. By Modus
+Ponens, the original proof goal can be reduced to several conjunct
+subgoals, each corresponding to one SOS rule. For instance, in one
+subgoal we are asked to prove that $\fv{E_1} \subseteq \fv{E} \Longrightarrow
+\fv{E_1} \subseteq \fv{E' + E}$, and this obviously holds, as $\fv{E}
+\subseteq \fv{E' + E} = \fv{E'} \cup \fv{E}$. Eventually we have only
+the following subgoal left: (the term above the line is the goal,
+those below the line are assumptions)
+\begin{alltt}
+        \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}
+   ------------------------------------
+    0.
+\HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+\end{alltt}
+Notice that, \HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLConst{DELETE}\\\;\HOLFreeVar{X}} comes from \HOLinline{\HOLConst{FV}\\\;\ensuremath{(}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{)}}, so
+the current goal is exactly the consequence of action induction on the
+SOS rule \texttt{REC}. Milner ever (correctly)
+said~\cite{milner1990operational} that,
+\begin{quote}
+  ``We shall often need to prove properties with the logical form `if
+  $E \arr{\alpha} E'$ then ...', ... but this is \emph{infeasible in
+    general} because, with (either) Recursion rule, an action for an
+  expression is inferred from an action of a `larger' expression.''
+\end{quote}
+Here the problem is, we know nothing about
+\HOLinline{\HOLConst{FV}\\\;\ensuremath{(}\ensuremath{[}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\HOLFreeVar{E}\ensuremath{)}}.
+To further proceed, we need to prove
+some other (easier) lemmas. First, the next lemma can be easily proven
+by doing induction on $E$ and basic set-theoretic facts:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
+\HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{E\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{FV} \HOLBoundVar{E\sp{\prime}}\hfill{[FV_SUBSET]}
+\end{alltt}
+Then, if we took $E' = \recu X E$ in the above lemma, we get
+\HOLinline{\HOLConst{FV}\\\;\ensuremath{(}\ensuremath{[}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\HOLSymConst{\HOLTokenSubset{}}\\\;\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}\\\;\HOLConst{FV}\\\;\ensuremath{(}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{)}} $=$ \HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLConst{DELETE}\\\;\HOLFreeVar{X}\ensuremath{)}} $=$
+\HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}}, i.e.
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E}.
+\HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E}\hfill{[FV_SUBSET_REC]}
+\end{alltt}
+Now we can enrich the assumptions of the current proof goal with above
+lemma and also conclude that \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} (by
+the transitivity of $\subseteq$):
+\begin{alltt}
+        \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}
+   ------------------------------------
+    0.
+\HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+    1.
+\HOLinline{\HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
+    2.  \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
+\end{alltt}
+Here, knowing \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} we cannot prove \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}.
+However, if we knew \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, then \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\ensuremath{=}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, and
+\HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}, the proof completes.
+Thus it remains to prove that
+\begin{alltt}
+        \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}
+   ------------------------------------
+    0.
+\HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+    1.
+\HOLinline{\HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
+    2.  \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
+\end{alltt}
+Now we try proof by contradiction (\emph{reductio ad absurdum}): if
+\HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, by assumption 0 we have \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}:
+\begin{alltt}
+        F
+   ------------------------------------
+    0.
+\HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+    1.
+\HOLinline{\HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
+    2.  \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
+    3.  \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}
+    4.
+\HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+\end{alltt}
+But this is impossible, because all free occurrences of $X$ in $E$ now become
+bound in the form of $\recu X E$. In fact, the following lemma can be
+easily proven by induction on $E$:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
+\HOLBoundVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\hfill{[NOTIN_FV_lemma]}
+\end{alltt}
+Adding the above lemma (taking $E' = E$) into the assumption list immediately causes
+a contradiction with assumption 4, thus the whole proof completes
+here. The (first) author cannot see any essentially easier proof of
+this proposition. (Without this result, the proof of Milner's ``unique solution of
+equations'' theorem (for $\sim$) cannot complete.)
+\end{proof}
 
+Comparing with the above long proof, the proof of a  similar result on
+bound variables is much easier:
+\begin{proposition}
+\label{prop:transBV}
+if $E \arr{\mu} E'$ then $\bv{E'} \subseteq \bv{E}$, or formally:
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{BV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLFreeVar{E}
-
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}}.
+\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{BV} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E}\hfill{[TRANS_BV]}
 \end{alltt}
-
+\end{proposition}
+\begin{proof}
+Following the proof of Prop.~\ref{prop:transFV}, we do action
+induction on $E \arr{\mu} E'$ and simplify all subgoals by set-theoretic
+facts. The only subgoal left is:
 \begin{alltt}
-   \HOLConst{IS_PROC} \HOLFreeVar{P} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{FV} \HOLFreeVar{P} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\HOLTokenEmpty{}}
-
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{IS_PROC} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{IS_PROC} \HOLFreeVar{E\sp{\prime}}
+        \HOLinline{\HOLConst{BV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLFreeVar{X} \HOLConst{INSERT} \HOLConst{BV} \HOLFreeVar{E}}
+   ------------------------------------
+    0.
+\HOLinline{\HOLConst{BV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
 \end{alltt}
+Notice the difference with the proof of Prop.~\ref{prop:transFV}: now
+we have \texttt{INSERT} in place of \texttt{DELETE}. Then, we directly
+use the assumption and the transitivity of $\subseteq$ and try to
+prove the following goal instead:
+\begin{alltt}
+        \HOLinline{\HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLFreeVar{X} \HOLConst{INSERT} \HOLConst{BV} \HOLFreeVar{E}}
+   ------------------------------------
+    0.
+\HOLinline{\HOLConst{BV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+\end{alltt}
+But this is an easy goal, due to the following lemma which can be
+easily proven by induction on $E$:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
+\HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{E\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{BV} \HOLBoundVar{E\sp{\prime}}\hfill{[BV_SUBSET]}
+\end{alltt}
+Taking $E ' = \recu X E$ in the above lemma, we have
+    \HOLinline{\HOLConst{BV}\\\;\ensuremath{(}\ensuremath{[}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\HOLSymConst{\HOLTokenSubset{}}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}\\\;\HOLConst{BV}\\\;\ensuremath{(}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{)}},
+    the right side equals to \HOLinline{\HOLConst{BV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}\\\;\ensuremath{(}\HOLFreeVar{X}\\\;\HOLConst{INSERT}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}} $=$
+    \HOLinline{\HOLFreeVar{X}\\\;\HOLConst{INSERT}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}}. The proof easily completes.
+\end{proof}
 

### 2019-09-11 ic-journal/multivariate.tex
Stage work on multivariate section

@@
 concept of ``weakly guarded contexts'', and Lemma~\ref{lem:milner313}.
-This work is entirely new after~\cite{EPTCS276.10}.
+\hl{This work is entirely new} after~\cite{EPTCS276.10}.
 It is accumulative, completely based on the
@@
 \begin{alltt}
-   \HOLConst{IS_PROC} \HOLFreeVar{E} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\HOLTokenEmpty{}}
+   \HOLConst{IS_PROC} \HOLFreeVar{E} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\HOLTokenEmpty{}}\hfill{[IS_PROC_def]}
 \end{alltt}
@@
 
-From HOL's viewpoint, the so-called ``action induction'' is actually a higher-order matching
-based on the following induction principle generated
-together with SOS rules:
+From HOL's viewpoint, the so-called ``action induction'' is actually a higher-order \hl{application}
+of the following \emph{induction principle} generated together with SOS
+rules: (which essentially says \HOLinline{\HOLConst{TRANS}} is the smallest relation
+satisfying SOS rules. This is the \emph{first} time we need the inductive
+nature of CCS derivations.)
 \begin{alltt}
@@
 \end{alltt}
-In the above long theorem, the outermost universal quantifier $P$ is a
-proposition about transition arguments $E$, $\mu$ and $E'$, and in
-this case $P(E, \mu, E')$ is actually $\fv{E'} \subseteq \fv{E}$. By Modus
-Ponens, the original proof goal can be reduced to several conjunct
-subgoals, each corresponding to one SOS rule. For instance, in one
-subgoal we are asked to prove that $\fv{E_1} \subseteq \fv{E} \Longrightarrow
-\fv{E_1} \subseteq \fv{E' + E}$, and this obviously holds, as $\fv{E}
+The above long theorem has the form \HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\HOLBoundVar{E\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\HOLBoundVar{E\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLBoundVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\HOLBoundVar{E\sp{\prime}}} (with $a_0, a_1, a_2$ renamed), where the
+outermost universal quantifier $P$ is a higher-order
+proposition (about $E$, $\mu$ and $E'$), and $X$ is another higher-order
+proposition about $P$.
+What we are trying to prove is actually in the form of
+\HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\HOLBoundVar{E\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\HOLBoundVar{E\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLFreeVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\HOLBoundVar{E\sp{\prime}}}, where
+\HOLinline{\HOLFreeVar{P}\\\;\HOLSymConst{\ensuremath{=}}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\HOLBoundVar{E\sp{\prime}}.\\\;\HOLConst{FV}\\\;\HOLBoundVar{E\sp{\prime}}\\\;\HOLSymConst{\HOLTokenSubset{}}\\\;\HOLConst{FV}\\\;\HOLBoundVar{E}\ensuremath{)}}.
+Thus, if we can prove
+$X$ under this specific $P$, by Modus Ponens (MP) the original proof completes.
+\hl{\emph{This is the whole idea of action induction.}}
+Now the original goal can be reduced to several conjunct
+subgoals, each corresponding to one SOS rule. For instance, in
+a subgoal about Summation we are asked to prove
+$\fv{E_1} \subseteq \fv{E} \Longrightarrow
+\fv{E_1} \subseteq \fv{E' + E}$, but this obviously holds: $\fv{E}
 \subseteq \fv{E' + E} = \fv{E'} \cup \fv{E}$. Eventually we have only
-the following subgoal left: (the term above the line is the goal,
+the following goal left: (the term above the dash line is the goal,
 those below the line are assumptions)
@@
 \end{alltt}
-Notice that, \HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLConst{DELETE}\\\;\HOLFreeVar{X}} comes from \HOLinline{\HOLConst{FV}\\\;\ensuremath{(}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{)}}, so
-the current goal is exactly the consequence of action induction on the
-SOS rule \texttt{REC}. Milner ever (correctly)
-said~\cite{milner1990operational} that,
-\begin{quote}
-  ``We shall often need to prove properties with the logical form `if
-  $E \arr{\alpha} E'$ then ...', ... but this is \emph{infeasible in
-    general} because, with (either) Recursion rule, an action for an
-  expression is inferred from an action of a `larger' expression.''
-\end{quote}
+Notice that, \HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLConst{DELETE}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{=}}\\\;\HOLConst{FV}\\\;\ensuremath{(}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{)}}, so
+this is indeed the consequence of action induction on the Recursion.
 Here the problem is, we know nothing about
@@
 \HOLinline{\HOLConst{FV}\\\;\ensuremath{(}\ensuremath{[}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\HOLSymConst{\HOLTokenSubset{}}\\\;\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}\\\;\HOLConst{FV}\\\;\ensuremath{(}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{)}} $=$ \HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLConst{DELETE}\\\;\HOLFreeVar{X}\ensuremath{)}} $=$
-\HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}}, i.e.
+\HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}}, i.e. the following lemma:
 \begin{alltt}
@@
 Now we can enrich the assumptions of the current proof goal with above
-lemma and also conclude that \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} (by
-the transitivity of $\subseteq$):
+lemma, then obtain \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} by
+from the transitivity of $\subseteq$:
 \begin{alltt}
@@
 \end{alltt}
-Here, knowing \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} we cannot prove \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}.
+Knowing \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} we cannot prove \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}.
 However, if we knew \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, then \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\ensuremath{=}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, and
-\HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}, the proof completes.
-Thus it remains to prove that
+\HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}, no matter if \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E}} or not, and the proof
+completes. Thus it remains to prove that
 \begin{alltt}
@@
 Now we try proof by contradiction (\emph{reductio ad absurdum}): if
-\HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, by assumption 0 we have \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}:
+the goal does not hold, i.e.
+\HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, then by assumption 0 we have \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}:
 \begin{alltt}
@@
 Adding the above lemma (taking $E' = E$) into the assumption list immediately causes
-a contradiction with assumption 4, thus the whole proof completes
-here. The (first) author cannot see any essentially easier proof of
-this proposition. (Without this result, the proof of Milner's ``unique solution of
-equations'' theorem (for $\sim$) cannot complete.)
+a contradiction with assumption 4, and the proof finally completes.
 \end{proof}
 
-Comparing with the above long proof, the proof of a  similar result on
-bound variables is much easier:
+Without the above result, the proof of Milner's ``unique solution of
+equations'' theorem (for $\sim$) cannot complete. Comparing with the
+above proof, the proof of the similar result for bound variables is much easier:
 \begin{proposition}
@@
 
+There are two ways to represent (and actually do) the multivariate
+substitution of $E\{\til P/\til X\}$ which substitutes each possibly
+occurrences of free variables $X_i$ in $E$ with the corresponding
+$P_i$: (1) repeatedly applying the existing univariate
+\HOLinline{\HOLConst{CCS_Subst}}; (2) defining a new multivariate substitution
+function. In any case, we (reasonably) assume that all $X_i$ are
+distinct with each other.
+
 \begin{alltt}
@@
 
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLFreeVar{X} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}}
-   \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
-\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLBoundVar{e}\ensuremath{)} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \ensuremath{(}\HOLFreeVar{X}\HOLSymConst{::}\HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-       \ensuremath{[}\HOLFreeVar{P}\HOLSymConst{::}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{X}\HOLSymConst{::}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLFreeVar{P}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLConst{MAP} \HOLConst{var} \HOLFreeVar{Xs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{E}
 
@@
 \ensuremath{[}\HOLBoundVar{y}\ensuremath{/}\HOLBoundVar{x}\ensuremath{]} \HOLBoundVar{e}\ensuremath{)} \HOLFreeVar{E} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLFreeVar{Xs}\HOLSymConst{,}\HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
-
-\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLConst{MAP} \HOLConst{var} \HOLFreeVar{Xs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{E}
 

### 2019-09-12 ic-journal/multivariate.tex
Stage work on multivariate section

@@
 of the following \emph{induction principle} generated together with SOS
-rules: (which essentially says \HOLinline{\HOLConst{TRANS}} is the smallest relation
-satisfying SOS rules. This is the \emph{first} time we need the inductive
-nature of CCS derivations.)
+rules: (which essentially says \hl{that} \HOLinline{\HOLConst{TRANS}} is the smallest relation
+satisfying SOS rules.)
 \begin{alltt}
@@
 subgoals, each corresponding to one SOS rule. For instance, in
-a subgoal about Summation we are asked to prove
+\hl{the subgoal for \texttt{SUM1} we need to prove}
 $\fv{E_1} \subseteq \fv{E} \Longrightarrow
-\fv{E_1} \subseteq \fv{E' + E}$, but this obviously holds: $\fv{E}
-\subseteq \fv{E' + E} = \fv{E'} \cup \fv{E}$. Eventually we have only
+\fv{E_1} \subseteq \fv{E + E'}$, but this obviously holds: $\fv{E}
+\subseteq \fv{E + E'} = \fv{E} \cup \fv{E'}$. Eventually we have only
 the following goal left: (the term above the dash line is the goal,
@@
 occurrences of free variables $X_i$ in $E$ with the corresponding
-$P_i$: (1) repeatedly applying the existing univariate
+$P_i$: (1) iterately applying the existing univariate
 \HOLinline{\HOLConst{CCS_Subst}}; (2) defining a new multivariate substitution
 function. In any case, we (reasonably) assume that all $X_i$ are
-distinct with each other.
+distinct with each other. On the other hand, there is the syntactic
+possibility that $\til P$ again contains variables from $\til X$, thus
+different orders of iterated substitutions may lead to different results.
+In fact, there are all kinds of issues with
+substitutions and applying them to term-like structures. To obtain the
+maximal flexibility with mimimal efforts, we defined
+a multivariate version of \HOLinline{\HOLConst{CCS_Subst}}
+called \HOLinline{\HOLConst{CCS_SUBST}} based HOL's \texttt{finite\_map} theory~\cite{holdesc}.
 
+A finite map of type \HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{\beta}} is like a function of type
+\HOLinline{\ensuremath{\alpha} \HOLTokenTransEnd \ensuremath{\beta}} having only finitely many elements in its
+domain. In HOL, an empty finite map is denoted as \HOLinline{\HOLConst{FEMPTY}}.
+If \HOLinline{\HOLFreeVar{fm}} is a finite map, its domain (as a set of keys) is denoted as
+\HOLinline{\HOLConst{FDOM} \HOLFreeVar{fm}}. Applying \HOLinline{\HOLFreeVar{fm}} on a certain key, say $k$, is denoted
+by \HOLinline{\HOLFreeVar{fm} \HOLConst{'} \HOLFreeVar{k}}.
+
+The function \HOLinline{\HOLConst{CCS_SUBST}} takes a finite
+map \HOLinline{\HOLFreeVar{fm}} of type \HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}} and a CCS expression,
+then it returns another CCS expression in which
+all occurrences of variables in the \HOLinline{\HOLFreeVar{fm}}'s domain are substituted with
+the corresponding value in \HOLinline{\HOLFreeVar{fm}}. Such a finite map can be built from
+the list of variables \HOLinline{\HOLFreeVar{Xs}} and the corresponding targets
+\HOLinline{\HOLFreeVar{Ps}} (of the same length) by a helper function \HOLinline{\HOLConst{fromList}} (whose details are
+not interesting and omitted here), while
+\HOLinline{\HOLConst{CCS_SUBST}\\\;\ensuremath{(}\HOLConst{fromList}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Ps}\ensuremath{)}\\\;\HOLFreeVar{E}} is
+abbreviated as \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}.
+The substitution process is
+variable-parallel thus order-independent. For most CCS operators it
+just recursively call itself on subterms of current input. The only
+interesting cases are at agent variables and recursion operators:
 \begin{alltt}
-   \HOLConst{CCS_SUBST} \HOLFreeVar{fm} \ensuremath{(}\HOLConst{var} \HOLFreeVar{X}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLFreeVar{fm} \HOLKeyword{then} \HOLFreeVar{fm} \HOLConst{'} \HOLFreeVar{X} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{X}
+   \HOLConst{CCS_SUBST} \HOLFreeVar{fm} \ensuremath{(}\HOLConst{var} \HOLFreeVar{X}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLFreeVar{fm} \HOLKeyword{then} \HOLFreeVar{fm} \HOLConst{'} \HOLFreeVar{X} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{X}\hfill{[CCS_SUBST_var]}
 
@@
      \HOLKeyword{if} \HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLFreeVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{X} \ensuremath{(}\HOLConst{CCS_SUBST} \ensuremath{(}\HOLFreeVar{fm} \HOLSymConst{\ensuremath{\setminus}} \HOLFreeVar{X}\ensuremath{)} \HOLFreeVar{E}\ensuremath{)}
-     \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{X} \ensuremath{(}\HOLConst{CCS_SUBST} \HOLFreeVar{fm} \HOLFreeVar{E}\ensuremath{)}
+     \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{X} \ensuremath{(}\HOLConst{CCS_SUBST} \HOLFreeVar{fm} \HOLFreeVar{E}\ensuremath{)}\hfill{[CCS_SUBST_rec]}
 \end{alltt}
+Notice that, the variable substitution only happens on free
+variables. In the case of $\recu X E$: if $X$ (a bound variable) is in
+the domain of \HOLinline{\HOLFreeVar{fm}}, \HOLinline{\HOLConst{CCS_SUBST}} must further does the
+substitution on $E$ using a reduce map with $X$, so that all
+occurences of agent variable $X$ in $E$ are correctly bypassed. On the
+other hand, since \HOLinline{\HOLConst{CCS_SUBST}} only walks each subterm
+once, even \HOLinline{\HOLFreeVar{Ps}} contains free variables, these variables will
+not be further substituted. Thus the process is indeed
+order-independent. Below we give some key lemmas about \HOLinline{\HOLConst{CCS_SUBST}}.
 
+\begin{lemma}
+  If there is only one single variable $X$ in the map (with the target
+  expression $E'$), then \HOLinline{\HOLConst{CCS_SUBST}} behaves exactly the
+  same as (the univariate) \HOLinline{\HOLConst{CCS_Subst}}:
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{CCS_SUBST} \ensuremath{(}\HOLConst{FEMPTY} \HOLSymConst{|+} \ensuremath{(}\HOLFreeVar{X}\HOLSymConst{,}\HOLFreeVar{E\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
+\HOLTokenTurnstile{} \HOLConst{CCS_SUBST} \ensuremath{(}\HOLConst{FEMPTY} \HOLSymConst{|+} \ensuremath{(}\HOLFreeVar{X}\HOLSymConst{,}\HOLFreeVar{E\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}\hfill{[CCS_SUBST_SING]}
+\end{alltt}
+\end{lemma}
 
-\HOLTokenTurnstile{} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{E}
+\begin{lemma}
+If the free variables of $E$ is disjoint with \HOLinline{\HOLFreeVar{Xs}}, a
+substitution of \HOLinline{\HOLFreeVar{Xs}} in $E$ does not change $E$:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{E}\hfill{[CCS_SUBST_elim]}
+\end{alltt}
+\end{lemma}
 
-\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLConst{MAP} \HOLConst{var} \HOLFreeVar{Xs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{E}
+\begin{lemma}
+Substituting each free variable $X$ in $E$ to \HOLinline{\HOLConst{var}\\\;\HOLFreeVar{X}} (itself)
+does not change $E$:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLConst{MAP} \HOLConst{var} \HOLFreeVar{Xs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{E}\hfill{[CCS_SUBST_self]}
+\end{alltt}
+\end{lemma}
 
-\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}}
-   \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{p}\ensuremath{)}.
-\HOLConst{FV} \HOLBoundVar{p} \HOLSymConst{\HOLTokenSubset{}} \HOLTokenLeftbrace{}\HOLBoundVar{x}\HOLTokenRightbrace{}\ensuremath{)} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLFreeVar{Xs}\HOLSymConst{,}\HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-   \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{FOLDR} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}\ensuremath{)} \HOLBoundVar{e}.
-\ensuremath{[}\HOLBoundVar{y}\ensuremath{/}\HOLBoundVar{x}\ensuremath{]} \HOLBoundVar{e}\ensuremath{)} \HOLFreeVar{E} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLFreeVar{Xs}\HOLSymConst{,}\HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
-
+The next lemma plays an important role. It essentially swaps the order of two substitutions:
+\begin{lemma}
+Under certain conditions, two nested substitutions can be
+converted into a single substitution where the targets are substituted first:
+\begin{alltt}
 \HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}}
    \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{C}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-   \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLConst{MAP} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}
+   \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLConst{MAP} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\hfill{[CCS_SUBST_nested]}
+\end{alltt}
+\end{lemma}
 
+Finally, the following two lemmas precisely estimate the free and
+bound variables of a substituted term:
+\begin{lemma}
+The bound variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}} have
+at most the union of all bound variables from $E$ and \HOLinline{\HOLFreeVar{Ps}}.
+\begin{alltt}
 \HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
    \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{BV} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
+\end{alltt}
+\end{lemma}
 
+\begin{lemma}
+The free variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}} have
+at most the union of all free variables from $E$ and \HOLinline{\HOLFreeVar{Ps}}
+removing \HOLinline{\HOLFreeVar{Xs}}.
+\begin{alltt}
 \HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
@@
 \end{alltt}
+\end{lemma}
+
+It is worth noting that, in some of the above lemmas, the condition
+\HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}} (the disjointness between bound variables of $E$ and
+ substitution variables) is not necessary but makes some proofs
+ easier.
 

### 2019-09-12 ic-journal/multivariate.tex
Stage work on multivariate section

@@
 
-\section{The multivariate formalisation}
+\section{The \multivariate formalisation}
 \label{sec:multivariate}
 
-In this section, the formalisation of the multivariate (general)
+In this section, the formalisation of the \multivariate (general)
 cases of Milner's ``unique solution of equations (for $\sim$)''
@@
 
-The central problem of the multivariate formalisation is the
+The central problem of the \multivariate formalisation is the
 representation of CCS equations (expressions, contexts).
@@
 calling $\lambda$-functions on the target CCS terms.
-This idea cannot be extended to the multivariate case, as
+This idea cannot be extended to the \multivariate case, as
 we don't have a fixed number of variables to deal with.
@@
 
-\subsection{Multivariate substitutions}
+\subsection{\Multivariate substitutions}
 
-There are two ways to represent (and actually do) the multivariate
+There are two ways to represent (and actually do) the \multivariate
 substitution of $E\{\til P/\til X\}$ which substitutes each possibly
@@
 $P_i$: (1) iterately applying the existing univariate
-\HOLinline{\HOLConst{CCS_Subst}}; (2) defining a new multivariate substitution
+\HOLinline{\HOLConst{CCS_Subst}}; (2) defining a new \multivariate substitution
 function. In any case, we (reasonably) assume that all $X_i$ are
@@
 maximal flexibility with mimimal efforts, we defined
-a multivariate version of \HOLinline{\HOLConst{CCS_Subst}}
+a \multivariate version of \HOLinline{\HOLConst{CCS_Subst}}
 called \HOLinline{\HOLConst{CCS_SUBST}} based HOL's \texttt{finite\_map} theory~\cite{holdesc}.
@@
 not be further substituted. Thus the process is indeed
-order-independent. Below we give some key lemmas about \HOLinline{\HOLConst{CCS_SUBST}}.
+order-independent. Below we present some key lemmas about
+\HOLinline{\HOLConst{CCS_SUBST}} \emph{without proofs}:
 
-\begin{lemma}
+\begin{lemma}[\texttt{CCS_SUBST_SING}]
   If there is only one single variable $X$ in the map (with the target
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{CCS_SUBST} \ensuremath{(}\HOLConst{FEMPTY} \HOLSymConst{|+} \ensuremath{(}\HOLFreeVar{X}\HOLSymConst{,}\HOLFreeVar{E\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}\hfill{[CCS_SUBST_SING]}
+\HOLTokenTurnstile{} \HOLConst{CCS_SUBST} \ensuremath{(}\HOLConst{FEMPTY} \HOLSymConst{|+} \ensuremath{(}\HOLFreeVar{X}\HOLSymConst{,}\HOLFreeVar{E\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
 \end{alltt}
@@
 
-\begin{lemma}
+\begin{lemma}[\texttt{CCS_SUBST_elim}]
 If the free variables of $E$ is disjoint with \HOLinline{\HOLFreeVar{Xs}}, a
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{E}\hfill{[CCS_SUBST_elim]}
+\HOLTokenTurnstile{} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{E}
 \end{alltt}
@@
 
-\begin{lemma}
+\begin{lemma}[\texttt{CCS_SUBST_self}]
 Substituting each free variable $X$ in $E$ to \HOLinline{\HOLConst{var}\\\;\HOLFreeVar{X}} (itself)
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLConst{MAP} \HOLConst{var} \HOLFreeVar{Xs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{E}\hfill{[CCS_SUBST_self]}
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLConst{MAP} \HOLConst{var} \HOLFreeVar{Xs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{E}
 \end{alltt}
@@
 The next lemma plays an important role. It essentially swaps the order of two substitutions:
-\begin{lemma}
+\begin{lemma}[\texttt{CCS_SUBST_nested}]
 Under certain conditions, two nested substitutions can be
@@
    \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{C}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-   \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLConst{MAP} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\hfill{[CCS_SUBST_nested]}
+   \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLConst{MAP} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}
 \end{alltt}
@@
 bound variables of a substituted term:
-\begin{lemma}
+\begin{lemma}[\texttt{BV_SUBSET_BIGUNION}]
 The bound variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}} have
@@
 
-\begin{lemma}
+\begin{lemma}[\texttt{FV_SUBSET_BIGUNION_PRO}]
 The free variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}} have
@@
 
-It is worth noting that, in some of the above lemmas, the condition
-\HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}} (the disjointness between bound variables of $E$ and
- substitution variables) is not necessary but makes some proofs
- easier.
+It is worth noting that, in the above lemmas, the condition
+\HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}} (the bound
+variables of $E$ and the free substitution variables are disjoint) is
+not necessary but makes some proofs (much) easier. As these lemmas are
+used in the rest work, these disjointness conditions eventually
+are propagated everywhere. (We believe that they can be
+all eliminated in the future.)
 
-\subsection{Multivariate (weakly-guarded) contexts}
+\subsection{\Multivariate (weakly-guarded) contexts}
+
+Recall in Section~\ref{ss:context}, univariate contexts and their
+guarded companions are defined as predicates over $\lambda$-expressions
+of type $CCS\rightarrow CCS$. These predicates, such as
+\HOLinline{\HOLConst{CONTEXT}}
+(contexts/expressions), \HOLinline{\HOLConst{WG}} (weak-guarded contexts),
+\HOLinline{\HOLConst{SG}} (strongly-guarded contexts) and \HOLinline{\HOLConst{SEQ}} (sequential
+contexts), are all defined inductively, i.e.~they are built from some ``holes''
+in a bottom-up way.
+For instance, \HOLinline{\HOLConst{WG}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\\\;\HOLSymConst{\ensuremath{\mid}}\\\;\HOLFreeVar{P}\ensuremath{)}}
+holds because \HOLinline{\HOLConst{WG}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\ensuremath{)}} holds on the ground,
+and for any agent variable $X$, we have (by $\beta$-reduction)
+\HOLinline{\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{P}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{var}\\\;\HOLFreeVar{X}\ensuremath{)}\\\;\HOLSymConst{\ensuremath{=}}\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{P}} (or ``$l.X + P$'' in textbook
+notation) is weakly guarded (c.f.~Def.~\ref{def:guardness}).
+
+It is possible to inductively assert multivariate contexts and their
+guarded variants, but this is not easy as we need to carefully exclude the cases where
+free variables occur inside any recusion operator (c.f. the footnote
+at the beginning of Section~\ref{ss:SysEq}. A more elegant (and less
+error-prone) solution is to define \multivariate contexts (and variants) upon the
+existing \univariate definitions. This is indeed our choice.
+
+For instance, to see the weak guardedness of $a.X + b.X + c.Y$, it is
+natural to focus on each (free) variable: if we substitute each
+occurrence of just one variable, say $X$, with a ``hole'' and see the
+resulting term as a $\lambda$-function, then all $\lambda$-functions
+derived from the original expression in this way must satisfy
+\HOLinline{\HOLConst{WG}}:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var} \HOLFreeVar{Y}\ensuremath{)}
+\HOLTokenTurnstile{} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var} \HOLFreeVar{X} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var} \HOLFreeVar{X} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\ensuremath{)}
+\end{alltt}
+Notice that, \HOLinline{\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{Y}\\\;\HOLSymConst{\ensuremath{=}}\\\;\ensuremath{[}\HOLFreeVar{t}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\ensuremath{(}\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{Y}\ensuremath{)}}.
+This idea leads to the following definitions:
+\begin{alltt}
+   \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLSymConst{\HOLTokenDefEquality{}}
+     \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
+\HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Xs}
+
+   \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLSymConst{\HOLTokenDefEquality{}}
+     \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
+\HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Xs}
+\end{alltt}
 
 \begin{alltt}
-   \HOLConst{context} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenDefEquality{}}
-     \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}.
-\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
-\HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Xs}\ensuremath{)}
-
 \HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLConst{context} \HOLFreeVar{Xs}\ensuremath{)} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
@@
 \begin{alltt}
-   \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenDefEquality{}}
-     \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}.
-\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
-\HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Xs}\ensuremath{)}
-
-\HOLTokenTurnstile{} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{E}
 
@@
 
-\subsection{Multivariate equations and solutions}
+\subsection{\Multivariate equations and solutions}
 
@@
 
-\subsection{Unique solution of equations for $\sim$ (the multivariate version)}
+\subsection{Unique solution of equations for $\sim$ (the \multivariate version)}
 
@@
 
-\subsection{Unique solution of rooted contractions (the multivariate version)}
+\subsection{Unique solution of rooted contractions (the \multivariate version)}
 

### 2019-09-13 paper/HOLMultivariate.tex
Enriched Table 1 + TeX outputs of "In/Out"
Updated CCS references
Updated generated theories
Separate FV and BV definitions
Updated generated TeX

@@
-\newcommand{\HOLMultivariateDate}{04 Settembre 2019}
-\newcommand{\HOLMultivariateTime}{13:47}
+\newcommand{\HOLMultivariateDate}{13 Settembre 2019}
+\newcommand{\HOLMultivariateTime}{10:02}
 \begin{SaveVerbatim}{HOLMultivariateDefinitionsCCSXXequationXXdef}
@@
 \begin{SaveVerbatim}{HOLMultivariateDefinitionscontextXXdef}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}.
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLSymConst{\ensuremath{=}}
-       \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}.
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}.
+       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}}
        \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
@@
 \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Xs}\ensuremath{)}
+\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Xs}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateDefinitionsweaklyXXguardedXXdef}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLSymConst{\ensuremath{=}}
-       \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}.
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}}
        \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
@@
 \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Xs}\ensuremath{)}
+\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Xs}
 \end{SaveVerbatim}
@@
        \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{p}\ensuremath{)}.
-\HOLConst{FV} \HOLBoundVar{p} \HOLConst{\HOLTokenSubset{}} \HOLTokenLeftbrace{}\HOLBoundVar{x}\HOLTokenRightbrace{}\ensuremath{)} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+\HOLConst{FV} \HOLBoundVar{p} \HOLConst{\HOLTokenSubset{}} \HOLTokenLeftbrace{}\HOLBoundVar{x}\HOLTokenRightbrace{}\ensuremath{)} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
        \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{FOLDR} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}\ensuremath{)} \HOLBoundVar{e}.
@@
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-           \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \ensuremath{(}\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-           \ensuremath{(}\ensuremath{[}\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{P}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}\ensuremath{)}
+\ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\ensuremath{[}\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{P}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{Xs}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \ensuremath{(}\ensuremath{[}\HOLConst{MAP} \HOLConst{var} \HOLBoundVar{Xs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E}\ensuremath{)}
+\HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\ensuremath{[}\HOLConst{MAP} \HOLConst{var} \HOLBoundVar{Xs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
+\HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
+\HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
 \end{SaveVerbatim}
 \newcommand{\HOLMultivariateTheoremscontextXXrec}{\UseVerbatim{HOLMultivariateTheoremscontextXXrec}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrecYY}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
+       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremscontextXXrecYY}{\UseVerbatim{HOLMultivariateTheoremscontextXXrecYY}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrelab}
@@
 \newcommand{\HOLMultivariateTheoremsFDOMXXfromList}{\UseVerbatim{HOLMultivariateTheoremsFDOMXXfromList}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsfromListXXDOMSUBXXNOTXXINXXDOM}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{Xs} \HOLBoundVar{Ps}.
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \ensuremath{(}\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{\setminus}} \HOLBoundVar{X} \HOLSymConst{\ensuremath{=}} \HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps}\ensuremath{)}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsfromListXXDOMSUBXXNOTXXINXXDOM}{\UseVerbatim{HOLMultivariateTheoremsfromListXXDOMSUBXXNOTXXINXXDOM}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsfromListXXEMPTY}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsfromListXXHD}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{xs} \HOLBoundVar{y} \HOLBoundVar{ys}.
-       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{x} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{ys}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \ensuremath{(}\HOLConst{fromList} \ensuremath{(}\HOLBoundVar{x}\HOLSymConst{::}\HOLBoundVar{xs}\ensuremath{)} \ensuremath{(}\HOLBoundVar{y}\HOLSymConst{::}\HOLBoundVar{ys}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{fromList} \HOLBoundVar{xs} \HOLBoundVar{ys} \HOLSymConst{|+} \ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}\ensuremath{)}\ensuremath{)}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{Xs} \HOLBoundVar{P} \HOLBoundVar{Ps}.
+       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \ensuremath{(}\HOLConst{fromList} \ensuremath{(}\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}\ensuremath{)} \ensuremath{(}\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLSymConst{|+} \ensuremath{(}\HOLBoundVar{X}\HOLSymConst{,}\HOLBoundVar{P}\ensuremath{)}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLThmTag{Multivariate}{context_rec}\HOLMultivariateTheoremscontextXXrec
+\HOLThmTag{Multivariate}{context_rec'}\HOLMultivariateTheoremscontextXXrecYY
 \HOLThmTag{Multivariate}{context_relab}\HOLMultivariateTheoremscontextXXrelab
@@
 \HOLThmTag{Multivariate}{FDOM_fromList}\HOLMultivariateTheoremsFDOMXXfromList
+\HOLThmTag{Multivariate}{fromList_DOMSUB_NOT_IN_DOM}\HOLMultivariateTheoremsfromListXXDOMSUBXXNOTXXINXXDOM
 \HOLThmTag{Multivariate}{fromList_EMPTY}\HOLMultivariateTheoremsfromListXXEMPTY

### 2019-09-13 ic-journal/formal.tex
Added HOL basis

@@
+%%%% -*- Mode: LaTeX; -*-
+
+\newcommand\fun{{\to}}
+\newcommand\prd{{\times}}
+\newcommand{\ty}[1]{\textsl{#1}}
+\newcommand\conj{\ \wedge\ }
+\newcommand\disj{\ \vee\ }
+\newcommand\imp{ \Rightarrow }
+\newcommand\eqv{\ \equiv\ }
+\newcommand\vbar{\mid}
+\newcommand\turn{\ \vdash\ } % FIXME: "\ " resultgs in extra space
+\newcommand\hilbert{\varepsilon}
+\newcommand{\uquant}[1]{\forall #1.\ }
+\newcommand{\equant}[1]{\exists #1.\ }
+\newcommand{\hquant}[1]{\hilbert #1.\ }
+\newcommand{\iquant}[1]{\exists ! #1.\ }
+\newcommand{\lquant}[1]{\lambda #1.\ }
+\newcommand{\ml}[1]{\mbox{{\def\_{\char'137}\texttt{#1}}}}
+\newcommand{\con}[1]{\mathrm{#1}}
+
+\newcommand\bool{\ty{bool}}
+\newcommand\num{\ty{num}}
+\newcommand\ind{\ty{ind}}
+\newcommand\lst{\ty{list}}
+
+\providecommand{\T}{\con{T}}
+\renewcommand{\T}{\con{T}}
+\newcommand\F{\con{F}}
+\newcommand\OneOne{\con{One\_One}}
+\newcommand\OntoSubset{\con{Onto\_Subset}}
+\newcommand\Onto{\con{Onto}}
+\newcommand\TyDef{\con{Type\_Definition}}
+
 \section{The formalisation}
@@
 
-We highlight here a formalisation of CCS
-in the HOL theorem
-prover (HOL4) \cite{Melham:1993vl,slind2008brief},
-including the new concepts and theorems proposed in the first half of
-this paper.
+We highlight here a formalisation of CCS in the HOL theorem prover
+(HOL4)~\cite{Melham:1993vl,slind2008brief}, \hl{with a focus towards the
+theory (and formal proofs) of the unique solution of
+equations/contractions theorems} mentioned in Section~\ref{s:eq} and
+\ref{s:mcontr}.
 %  The main purpose is to convince the readers that, there's no flaw
 %  in the informal proofs. 
-The whole formalisation (apart from minor fixes and extensions in this
-paper)
-is described in \cite{Tian:2017wrba}, and the
-proof scripts are in HOL4 official
-examples\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL/tree/master/examples/CCS}}. The
-current work consists of about 20,000 lines of proof scripts.
+\hl{The univariate versions of these theorems, apart from minor fixes and
+extensions in this paper, was already described in}
+\cite{Tian:2017wrba}. The multivariate proofs and the related results
+are new, and will be described in Section~\ref{sec:multivariate}.
+All proof scripts are available as part of HOL's official
+examples\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL/tree/master/examples/CCS}}.
+The work so far consists of about 24,000 lines (1MB) of code in total,
+in which about 5,000 lines were derived from the early work of Monica
+Nesi~\cite{Nesi:1992ve} on HOL88, with major modifications.
 
-Higher Order Logic (HOL) \cite{hollogic} traces
+Higher Order Logic (HOL)~\cite{hollogic} traces
 its roots back to LCF
@@
 \hl{As a consequence, theories and proofs verified in HOL are relatively more
-convincible to non-experts.}
+convincible to non-experts who are not familar with more advanced
+dependent type theories.}
 
-HOL4 is written in Standard ML, a single programming language which
+HOL4 is implemented in Standard ML, the same programming language who
 plays three different roles:
-%(The situation is quite different in other systems like
-%Coq\footnote{The Coq Proof Assistant. \url{https://coq.inria.fr}}).
 \begin{enumerate}
-\item It serves as the underlying implementation language for the core HOL engine;
-\item it is used to implement tactics (and tacticals) for writing proofs;
-\item it is used as the command language of the HOL interactive shell.
+\item the underlying implementation language for the core HOL engine;
+\item \hl{the language in which proof tactics are implemented;}
+\item \hl{the interface (outer) language of the HOL proof scripts and
+  interactive shell.}
 \end{enumerate}
@@
 verification tools by calling HOL's theorem proving
-facilities. (The formal proofs of theorems in CCS theory
+facilities. The formal proofs of theorems in CCS theory
 are mostly done by an \emph{interactive process} closely following
-their informal proofs, with minimal automatic proof searching.)
+their informal proofs, with minimal automatic proof searching.
 
-% \finish{below: to be reformulated (by Davide) later} 
-% We will not repeat all definitions and theorems of CCS again by their
-% formalized versions. Instead, we just focus on several highlights in
-% this work, i.e.
-% \begin{enumerate}
-% \item The use of HOL's new coinductive relation package for defining bisimilarity;
-% \item The formalisation of context by $\lambda$-expression and the theory of
-%   (pre)congruence for CCS;
-% \item The definition and uses of trace in the proof of unique solution of
-%   contractions theorem;
-% \end{enumerate}\finish{TODO: need updates}
+\subsection{Higher Order Logic}
 
-%% [Chun]: cancelled this part as now we have multivariate formal proofs!
-% \emph{In this
-% formalisation we consider only single-variable equations/contractions.}
-% This considerably
-%  simplifies the required proofs in HOL, and  enhances the readability of
-%  proof scripts without loss of generality. For the  pencil-and-paper proofs, the
-%  multi-variable case is just a routine adaptation, while the
-%  formalisation in theorem prover % \DDS{}
-%  is not (this is also discussed in Section~\ref{s:concl}).
+HOL is a formal system of typed logical terms. The types are expressions that denote sets (in the
+universe $\mathcal{U}$). HOL's type system is much simpler than those
+based on dependent types and other type theories. There are four kinds of types in the HOL
+logic, as illustrated in Fig. \ref{fig:hol-types} for its BNF
+grammar. Noticed that, in HOL the standard atomic types \emph{bool} and \emph{ind}
+ denote, respectively, the distinguished two-element set 2 and the
+distinguished infinite set $I$.
 
-% \subsection{Simplifications and Limitations}
+\newlength{\ttX}
+\settowidth{\ttX}{\tt X}
+\newcommand{\tyvar}{\setlength{\unitlength}{\ttX}\begin{picture}(1,6)
+\put(.5,0){\makebox(0,0)[b]{\footnotesize type variables}}
+\put(0,1.5){\vector(0,1){4.5}}
+\end{picture}}
+\newcommand{\tyatom}{\setlength{\unitlength}{\ttX}\begin{picture}(1,6)
+\put(.5,2.3){\makebox(0,0)[b]{\footnotesize atomic types}}
+\put(.5,3.3){\vector(0,1){2.6}}
+\end{picture}}
+\newcommand{\funty}{\setlength{\unitlength}{\ttX}\begin{picture}(1,6)
+\put(.5,1.5){\makebox(0,0)[b]{\footnotesize function types}}
+\put(.5,0){\makebox(0,0)[b]{\footnotesize (domain $\sigma_1$, codomain $\sigma_2$)}}
+\put(1,2.5){\vector(0,1){3.5}}
+\end{picture}}
+\newcommand{\cmpty}{\setlength{\unitlength}{\ttX}\begin{picture}(1,6)
+\put(2,3.3){\makebox(0,0)[b]{\footnotesize compound types}}
+\put(1.9,4.5){\vector(0,1){1.5}}
+\end{picture}}
 
-% We have only formally verified simplified forms of the unique
-% solution theorems introduced in the first part. This is to not only
-% save the formalisation efforts, but also to make us focusing on the most
-% important part of the proof. The most important simplification is
-% that, we have only proved all unique solution theorems with only single-variable equations
-% (contractions).
+\begin{figure}[h]
+\begin{equation*}
+\sigma\quad ::=\quad {\mathord{\mathop{\alpha}\limits_{\tyvar}}}
+        \quad\mid\quad{\mathord{\mathop{c}\limits_{\tyatom}}}
+        \quad\mid\quad\underbrace{(\sigma_1, \ldots , \sigma_n){op}}_{\cmpty}
+        \quad\mid\quad\underbrace{\sigma_1\fun\sigma_2}_{\funty}
+\end{equation*}
+   \caption{HOL's type grammar}
+   \label{fig:hol-types}
+\end{figure}
 
-% But such a simplification doesn't hurt the rigorousness of our entire
-% work, as once the single-equation version of the theorem is
-% proven, the general case is just a routine
-% adaptation for paper proofs.
-% It's not easy to formalize multi-variable CCS equations with
-% introducing a large number of definitions and intermediate
-% results. It's easy, however, to directly use the semantics context to
-% represent single-variable equations without the need of formalizing
-% the concept of ``equation'' at all.
+The terms of the HOL logic are expressions that denote elements of the
+sets denoted by types. There're four kinds of terms in the HOL
+logic. There can be described approximately by the BNF grammar in
+Fig. \ref{fig:hol-terms}.
 
-% There're two major limitations in this work. One is due to HOL, we only support Finitary CCS, i.e.
-% no infinite sum nor infinite parallel composition.
-% The other limitation is, equation variables (or holes in semantics contexts)
-% cannot appear inside recursion operator closure. However, these limitations do not
-% cause any difference in the proof of main results represented in this paper.
+\settowidth{\ttX}{\tt X}
+\newcommand{\var}{\setlength{\unitlength}{\ttX}\begin{picture}(1,6)
+\put(.5,0){\makebox(0,0)[b]{\footnotesize variables}}
+\put(0,1.5){\vector(0,1){4.5}}
+\end{picture}}
+\newcommand{\const}{\setlength{\unitlength}{\ttX}\begin{picture}(1,6)
+\put(.5,2.3){\makebox(0,0)[b]{\footnotesize constants}}
+\put(.5,3.5){\vector(0,1){2.4}}
+\end{picture}}
+\newcommand{\app}{\setlength{\unitlength}{\ttX}\begin{picture}(1,6)
+\put(.5,1.5){\makebox(0,0)[b]{\footnotesize function applications}}
+\put(.5,0){\makebox(0,0)[b]{\footnotesize (function $t$, argument $t'$)}}
+\put(0.5,2.5){\vector(0,1){3.5}}
+\end{picture}}
+\newcommand{\abs}{\setlength{\unitlength}{\ttX}\begin{picture}(1,6)
+\put(1,3.3){\makebox(0,0)[b]{\footnotesize $\lambda$-abstractions}}
+\put(0.7,4.5){\vector(0,1){1.5}}
+\end{picture}}
+
+\begin{figure}[h]
+\begin{equation*}
+t \quad ::=\quad {\mathord{\mathop{x}\limits_{\var}}}
+        \quad\mid\quad{\mathord{\mathop{c}\limits_{\const}}}
+        \quad\mid\quad\underbrace{t\ t'}_{\app}
+        \quad\mid\quad\underbrace{\lambda x .\ t}_{\abs}
+\end{equation*}
+   \caption{HOL's term grammar}
+   \label{fig:hol-terms}
+ \end{figure}
+
+The deductive system of the HOL is specified by eight primitive
+derivation rules: (c.f.~\cite{hollogic} for more details.)
+\begin{enumerate}
+\item Assumption introduction (\texttt{ASSUME});
+\item Reflexivity (\texttt{REFL});
+\item $\beta$-conversion (\texttt{BETA\_CONV});
+\item Substitution (\texttt{SUBST});
+\item Abstraction (\texttt{ABS});
+\item Type instantiation (\texttt{INST\_TYPE});
+\item Discharging an assumption (\texttt{DISCH});
+\item Modus Ponens (\texttt{MP}).
+\end{enumerate}
+All proofs are eventually reduced to applications of the above rules,
+which also give the semantics of two foundamental
+logical connectives, the equality ($=$) and implication
+($\Rightarrow$). The rest logical connectives and first-order
+quantifiers, including the logical true (\HOLinline{\HOLConst{T}}) and false (\HOLinline{\HOLConst{F}}), are
+further defined as $\lambda$-functions: (one rarely needs to care
+things at this level, however.)
+\begin{equation*}
+\begin{array}{l}
+\turn \T       =  ((\lquant{x_{\ty{bool}}}x) =
+               (\lquant{x_{\ty{bool}}}x))    \\
+\turn \forall  =  \lquant{P_{\alpha\fun\ty{bool}}} P =
+                    (\lquant{x}\T ) \\
+\turn \exists  =  \lquant{P_{\alpha\fun\ty{bool}}} P({\hilbert}\, P) \\
+\turn \F  =  \uquant{b_{\ty{bool}}} b  \\
+\turn \neg    =  \lquant{b} b \imp \F \\
+\turn {\wedge}  =  \lquant{b_1\ b_2}\uquant{b} (b_1\imp (b_2 \imp b)) \imp b \\
+\turn {\vee}  =  \lquant{b_1\ b_2}\uquant{b} (b_1 \imp b)\imp ((b_2 \imp b) \imp b) \\
+\turn \OneOne  =  \lquant{f_{\alpha \fun\beta}}\uquant{x_1\ x_2}
+                    (f\ x_1 = f\ x_2)  \imp (x_1 = x_2) \\
+\turn \Onto  =  \lquant{f_{\alpha\fun\beta}}
+                  \uquant{y}\equant{x} y = f\ x \\
+\turn \TyDef  =  \lambda P_{\alpha\fun\ty{bool}}\
+                  rep_{\beta\fun\alpha}.\;
+                  \OneOne\ rep \ \wedge{}\  (\uquant{x}P x = (\equant{y} x = rep\ y))
+\end{array}
+\end{equation*}
+It deserves to mention that, the last logical constant above,
+$\TyDef$, can be used to define new HOL types as bijections of
+subsets of existing types. (c.f.~\cite{Melham:1989dk} for more details.)
+HOL's \texttt{Datatype} package~\cite{Melham:1991, holdesc} automates
+this tedious process, and can be used to define needed types in CCS.
+
+Finally, the whole HOL \emph{standard} theory is based on the
+following four axioms, from which the almost\footnote{HOL is strictly
+  weaker than ZFC (the Zermelo-Frankel set theory with the
+Axiom of Choice), thus not all theorems valid in ZFC can be formalised
+in HOL. (c.f.~\cite{hollogic} for more details.)} entire mathematics
+can be formalised:
+\begin{equation*}
+\begin{array}{@{}l@{\qquad}l}
+\mbox{\texttt{BOOL\_CASES\_AX}} &\vdash \uquant{b} (b = \T ) \vee (b = \F )\\
+\mbox{\texttt{ETA\_AX}} &
+\vdash \uquant{f_{\alpha\fun\beta}}(\lquant{x}f\ x) = f\\
+\mbox{\texttt{SELECT\_AX}} &
+\vdash \uquant{P_{\alpha\fun\ty{bool}}\ x} P\ x \imp P({\hilbert}\ P)\\
+\mbox{\texttt{INFINITY\_AX}}&
+\vdash \equant{f_{\ind\fun \ind}} \OneOne \ f \conj \neg(\Onto \ f)\\
+\end{array}
+\end{equation*}
+
+Notice that, usually the above four axioms are the only axioms allowed
+in conventional formalisation projects in HOL: adding new axioms may
+either break the logic consistencies or make the whole work less
+convincible. The theorem prover (in general) guarantees that,
+without adding new axioms, if both the definitions and the statements
+of theorems are correct, then any proof which successfully completes must
+be correct.
 

### 2019-09-13 ic-journal/multivariate.tex
Added HOL basis

@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLConst{MAP} \HOLConst{var} \HOLFreeVar{Xs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{E}
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLConst{MAP} \HOLConst{var} \HOLFreeVar{Xs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{E}
 \end{alltt}
@@
 The free variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}} have
-at most the union of all free variables from $E$ and \HOLinline{\HOLFreeVar{Ps}}
-removing \HOLinline{\HOLFreeVar{Xs}}.
+at most the union of all free variables from $E$ and \HOLinline{\HOLFreeVar{Ps}},
+excluding \HOLinline{\HOLFreeVar{Xs}}.
 \begin{alltt}

### 2019-09-13 ic-journal/sos.tex
Stage work on 2nd part
Added HOL basis

@@
 
-\subsection{CCS processes and their transitions}
+\subsection{CCS: the formal theory}
 
-In our CCS formalisation, the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' (\texttt{'b} or
-$\beta$ is the type variable for actions) accounts for visible actions, divided into input
-and output actions, defined by HOL's Datatype package:
+\hl{The CCS formalisation starts with type definitions for action,
+relabeling and the CCS term itself. We use} the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' (\texttt{'b} or
+$\beta$ is \hl{a type variable}) for all visible actions. The
+cardinality and the exact elements depend on the type variable $\beta$
+supplied by the end user.
+\hl{All actions are} divided into input and \hl{$\overline{\text{output}}$ ones.}
+This type is defined by HOL's \texttt{Datatype} package in the
+following syntax:
 \begin{lstlisting}
@@
 \end{lstlisting}
+\hl{For instance, if the type $\beta$ is instantiated by the type
+\texttt{string}, then HOL terms} \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
+\HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input action $a$ and output
+action $\overline{\text{b}}$, respectively.
 The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
-union of all visible actions, plus invisible action $\tau$. It's
-defined as an abbreviation of HOL's core type ``\HOLinline{\ensuremath{\alpha} \HOLTyOp{option}}''%
-\footnote{\url{https://hol-theorem-prover.org/kananaskis-13-helpdocs/help/src-sml/htmlsigs/optionTheory.html}} instantiated
-with the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'':
-\begin{lstlisting}
-Type Action[pp] = ``:'b Label option``;
-\end{lstlisting}
-The cardinality of
-``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' (and therefore of all
-CCS types built on top of it)
- depends on the choice (or \emph{type-instantiation}) of type variable $\beta$.
+union of all visible actions, plus the invisible action $\tau$
+(\texttt{tau}). For instace, the input action $a$ and output
+action $\overline{\text{b}}$ of type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}''
+are denoted by \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLStringLit{a}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLStringLit{b}\ensuremath{)}}, respectively.
 
 The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'', accounting for the CCS
-syntax\footnote{The order of type variables $\alpha$ and $\beta$
+expressions, where \texttt{'a} (or $\alpha$) is the type variable\footnote{The order of type variables $\alpha$ and $\beta$
     is arbitrary. Our choice is aligned with other \hl{literature.
@@
 variables $\alpha$ and $\beta$ in ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' with types
-having the corresponding cardinalities $h$ and $k$.}, is then defined inductively:
-(\texttt{'a} or $\alpha$ is the type variable for recursion variables,
-``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling functions):
+having the corresponding cardinalities $h$ and $k$.} for
+agent variables, is then defined inductively:\footnote{``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling functions. They (and
+  related operations) are not discussed in this paper.}
 \begin{lstlisting}
@@
 \end{lstlisting}
+The above definitions allow us to use terms like \texttt{nil} and
+\texttt{sum P Q} in HOL. Their correspondences with conventional CCS notations
+in the literature, are given in Table~\ref{tab:ccsoperator}, \hl{where
+most CCS operators have also the more readable abbreviation forms,
+either for end user or for \TeX{} outputs.}\footnote{All
+  formal theorems and definitions in this paper
+  are generated from HOL4. Also, by default, all theorems are fully
+  specialised, removing outermost universal quantifiers.}
 
-We have added some grammar support,
- using HOL's powerful pretty printer, to represent CCS
-processes in more readable forms (c.f. the column \hl{``\TeX{} outputs''}
-of Table \ref{tab:ccsoperator}, which summarizes
-the main syntactic notations of CCS). For the restriction
-operator, we have chosen to allow a  set of names as a parameter, rather than a
-  single name as in the ordinary  CCS syntax; this simplifies
-the manipulation of
- processes with different orders of
-  nested restrictions.
-% Also, we do not assume that the uses of \texttt{var} are
-%  guarded by \texttt{rec} of the same variable.
-
-%  (Notice the use of
-% recursion operator for representing process constants)
 \begin{table}[h]
@@
 \end{center}
-   \caption{Syntax of \hl{various CCS concepts in HOL}}
+   \caption{Syntax of \hl{some CCS concepts in HOL}}
    \label{tab:ccsoperator}
@@
 
-The transition semantics of CCS processes follows Structural
-Operational Semantics (SOS) in Fig.~\ref{f:LTSCCS}:\footnote{All
-  formal theorems and definitions (their \TeX{} code) in this paper
-  are generated directly from HOL4. By default, all theorems are fully
-  specialised, removing outermost universal quantifiers.}
+The transition semantics of CCS processes strictly follows the SOS rules given
+in Fig.~\ref{f:LTSCCS}. However, they are not axioms, but the
+consequence of an \emph{inductive relation} definition of
+\HOLinline{\HOLConst{TRANS}} by HOL's \texttt{HOL_reln} function~\cite{holdesc} for more details.
+A successful invocation of the definitional principle returns three
+important theorems (\emph{rules}, \emph{ind} and \emph{cases}):
+\begin{itemize}
+  \item \hl{\emph{rules} is a conjunction of implications that will be the
+    same as the input term. In fact, the following formal versions of SOS rules are
+    extracted from the \emph{rules} theorem:}
 \begin{alltt}
@@
 \end{alltt}
+\begin{equation*}
+\infer[\HOLRuleName{PAR3}]{\HOLinline{\HOLFreeVar{E} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sb{\mathrm{2}}}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}}&\HOLinline{\HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLFreeVar{l}\ensuremath{)}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{2}}}}}
+\end{equation*}
+\begin{equation*}
+\infer[\HOLRuleName{RESTR}]{\HOLinline{\ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E\sp{\prime}}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}}}&\HOLinline{\HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLFreeVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}}}
+\end{equation*}
+\begin{equation*}
+\infer[\HOLRuleName{RELABELING}]{\HOLinline{\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{rf}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}}}}
+\end{equation*}
+\begin{equation*}
+\infer[\HOLRuleName{REC}]{\HOLinline{\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}}}{\HOLinline{\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}}}
+\end{equation*}
+\item \hl{\emph{ind} is the induction principle for the
+  relation.} (c.f.~Section~\ref{sec:multivariate} for the exact form
+  and its application.)
+\item \hl{\emph{cases} is the so-called `cases' or `inversion' theorem for
+  the relations, and is used to decompose an element in the relation into the possible ways of
+  obtaining it by the rules. For instance, it leads to the following
+  theorem:}
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime\prime}} \HOLSymConst{\HOLTokenEquiv{}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime\prime}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime\prime}}\hfill{[TRANS_SUM_EQ]}
+\end{alltt}
+\end{itemize}
 
-\begin{equation}
-\infer[\HOLRuleName{PAR3}]{\HOLinline{\HOLFreeVar{E} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sb{\mathrm{2}}}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}}&\HOLinline{\HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLFreeVar{l}\ensuremath{)}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{2}}}}}
-\end{equation}
-
-\begin{equation}
-\infer[\HOLRuleName{RESTR}]{\HOLinline{\ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E\sp{\prime}}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}}}&\HOLinline{\HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLFreeVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}}}
-\end{equation}
-
-\begin{equation}
-\infer[\HOLRuleName{RELABELING}]{\HOLinline{\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{rf}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}}}}
-\end{equation}
-
-\begin{equation}
-\infer[\HOLRuleName{REC}]{\HOLinline{\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}}}{\HOLinline{\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}}}
-\end{equation}
-
-The last rule \texttt{REC} (Recursion)
+The last SOS rule \texttt{REC} (Recursion)
  says that if we substitute all \hl{occurrences of the} variable $A$ in $P$ to

### 2019-09-13 ic-journal/multivariate.tex
Updated multivariate substitution theorem list

@@
 
-\begin{lemma}[\texttt{CCS_SUBST_SING}]
-  If there is only one single variable $X$ in the map (with the target
-  expression $E'$), then \HOLinline{\HOLConst{CCS_SUBST}} behaves exactly the
-  same as (the univariate) \HOLinline{\HOLConst{CCS_Subst}}:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{CCS_SUBST} \ensuremath{(}\HOLConst{FEMPTY} \HOLSymConst{|+} \ensuremath{(}\HOLFreeVar{X}\HOLSymConst{,}\HOLFreeVar{E\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
-\end{alltt}
-\end{lemma}
-
 \begin{lemma}[\texttt{CCS_SUBST_elim}]
@@
    \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLConst{MAP} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}
+\end{alltt}
+\end{lemma}
+
+The next three lemmas show the relative correctness of \texttt{CCS\_SUBST}
+w.r.t. \texttt{CCS\_Subst}:
+\begin{lemma}[\texttt{CCS_SUBST_SING}]
+  If there is only one single variable $X$ in the map (with the target
+  expression $E'$), then \HOLinline{\HOLConst{CCS_SUBST}} behaves exactly the
+  same as (the univariate) \HOLinline{\HOLConst{CCS_Subst}}:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{CCS_SUBST} \ensuremath{(}\HOLConst{FEMPTY} \HOLSymConst{|+} \ensuremath{(}\HOLFreeVar{X}\HOLSymConst{,}\HOLFreeVar{E\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
+\end{alltt}
+\end{lemma}
+
+\begin{lemma}[\texttt{CCS_SUBST_reduce}]
+Under certain conditions (to get rid of substitution orders), a \multivariate substitution of variables
+\HOLinline{\HOLFreeVar{X}\HOLSymConst{::}\HOLFreeVar{Xs}} can be reduced to a \multivariate substitution of
+variables \HOLinline{\HOLFreeVar{Xs}} and an \univariate substitution of $X$:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLFreeVar{X} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}}
+   \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
+\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLBoundVar{e}\ensuremath{)} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
+\ensuremath{[}\HOLFreeVar{P}\HOLSymConst{::}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{X}\HOLSymConst{::}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLFreeVar{P}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}
+\end{alltt}
+\end{lemma}
+
+\begin{lemma}[\texttt{CCS_SUBST_FOLDR}]
+Under certain conditions (to get rid of substitution orders), a
+\multivariate substitution can be reduced to repeated applications
+of \univariate substitutions of each variable:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}}
+   \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{p}\ensuremath{)}.
+\HOLConst{FV} \HOLBoundVar{p} \HOLSymConst{\HOLTokenSubset{}} \HOLTokenLeftbrace{}\HOLBoundVar{x}\HOLTokenRightbrace{}\ensuremath{)} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLFreeVar{Xs}\HOLSymConst{,}\HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+   \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{FOLDR} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}\ensuremath{)} \HOLBoundVar{e}.
+\ensuremath{[}\HOLBoundVar{y}\ensuremath{/}\HOLBoundVar{x}\ensuremath{]} \HOLBoundVar{e}\ensuremath{)} \HOLFreeVar{E} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLFreeVar{Xs}\HOLSymConst{,}\HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
 \end{alltt}
@@
 \begin{alltt}
-   \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLSymConst{\HOLTokenDefEquality{}}
-     \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
+   \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
 \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
@@
 
-   \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLSymConst{\HOLTokenDefEquality{}}
-     \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
+   \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
 \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
@@
    \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
-\HOLConst{FV} \HOLBoundVar{e} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLFreeVar{Es}
+\HOLConst{FV} \HOLBoundVar{e} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
+   \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
+\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Es}
 
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
+\HOLTokenTurnstile{} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps}.
@@
            \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sp{\prime}}.
-               \HOLConst{context} \HOLFreeVar{Xs} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+               \HOLConst{context} \HOLFreeVar{Xs} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+               \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
                \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.

### 2019-09-14 ic-journal/ccs.tex
text

@@
 
-\hl{Here we beliefly recall the core theory of CCS, up to the unique solution of
-equation and contractions, with a focus on the syntactic differences with
-other literature.}
+\hlD{Here we recall the core theory of CCS.}
 We assume a possibly infinite set of names $\mathscr{L} = \{a, b,
-\ldots\}$ forming input and $\overline{\mbox{output}}$ labels (actions), plus a special invisible
+\ldots\}$ \hlD{yielding} input and $\overline{\mbox{output}}$ labels (actions), plus a special invisible
 action $\tau \notin \mathscr{L}$, and \hl{another possibly infinite
@@
 \end{equation*}
-\hl{Notice the (minor) differences with other CCS literature regarding the above definition:}
-\begin{enumerate}
-  \item Some literature adopts possibly infinite sums over an index
-    set ($\sum_{i\in I} P_i$) while we only consider binary (thus
-    finite) sums, which is less expressive.
-  \item Our restriction operator takes a set of (input) labels $L
-    \subseteq \mathscr{L}$, while some CCS literature only restricts
-    one label (for each restriction operator);
-  \item Our relabeling operator takes a relabeling function
+\hlD{In our presentation of CCS, 
+the restriction operator takes a set of  labels $L
+    \subseteq \mathscr{L}$, rather than a single one.  
+The relabeling operator takes a relabeling function
     $\mathit{rf} \colon \mathscr{L} \cup \overline{\mathscr{L}} \cup
     \{\tau\} \rightarrow \mathscr{L} \cup \overline{\mathscr{L}} \cup
-    \{\tau\}$, which
-    is capable to handle multiple actions including $\tau$. A valid
-    relabeling function $\mathit{rf}$ must satisfy $\mathit{rf}(\tau) =
+    \{\tau\}$, that can  handle multiple actions including $\tau$. A valid
+    relabeling function $\mathit{rf}$ must however 
+satisfy $\mathit{rf}(\tau) =
     \tau$ and $\forall l\in\mathscr{L} \cup \overline{\mathscr{L}}.\, \mathit{rf}(\overline{l}) =
     \overline{\mathit{rf}(l)}$ (with $\bar{\bar l} = l$ for all $l \in
-    \mathscr{L}$); Same expressiveness
-    with single-label relabeling.
-  \item The recursion operator $\texttt{rec}$ has the same expressiveness with
-    \emph{process constants} adopted in some literature. For instance, a
-    CCS process $a.C$ with the constant $C \DSdefi b.C$ can be
-    expressed as $a.(\texttt{rec}\, C. (b.C))$.
-\end{enumerate}
-Besides, we sometimes omit \hl{the} trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil$.
-\hl{A CCS process $P$ may \emph{derive} to another one, say $P'$, under
-  an action $\mu$, denoted by $P \arr{\mu} P'$.}
-The \hl{transitional semantics} of CCS processes is given by means of
+    \mathscr{L}$).}
+% \hl{Notice the (minor) differences with other CCS literature
+% regarding the above definition:} 
+% \begin{enumerate}
+%   \item Some literature adopts possibly infinite sums over an index
+%     set ($\sum_{i\in I} P_i$) while we only consider binary (thus
+%     finite) sums, which is less expressive.
+%   \item Our restriction operator takes a set of (input) labels $L
+%     \subseteq \mathscr{L}$, while some CCS literature only restricts
+%     one label (for each restriction operator);
+%   \item Our relabeling operator takes a relabeling function
+%     $\mathit{rf} \colon \mathscr{L} \cup \overline{\mathscr{L}} \cup
+%     \{\tau\} \rightarrow \mathscr{L} \cup \overline{\mathscr{L}} \cup
+%     \{\tau\}$, which
+%     is capable to handle multiple actions including $\tau$. A valid
+%     relabeling function $\mathit{rf}$ must satisfy $\mathit{rf}(\tau) =
+%     \tau$ and $\forall l\in\mathscr{L} \cup
+%     \overline{\mathscr{L}}.\, \mathit{rf}(\overline{l}) = 
+%     \overline{\mathit{rf}(l)}$ (with $\bar{\bar l} = l$ for all $l \in
+%     \mathscr{L}$); Same expressiveness
+%     with single-label relabeling.
+%   \item The recursion operator $\texttt{rec}$ has the same
+%   expressiveness with  
+%     \emph{process constants} adopted in some literature. For instance, a
+%     CCS process $a.C$ with the constant $C \DSdefi b.C$ can be
+%     expressed as $a.(\texttt{rec}\, C. (b.C))$.
+% \end{enumerate}
+We sometimes omit \hlD{a} trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil$.
+\hl{A CCS process $P$ may \hlD{evolve} to another one, say $P'$, under
+  an action $\mu$, written by $P \arr{\mu} P'$.}
+The \hlD{transition semantics} of CCS processes is given by means of
 a Labeled Transition System (LTS) \hl{expressed in Structural Operational
@@
 A CCS processes uses only \emph{guarded sums} if all occurrences of
-sums are in the form $a.P + b.Q$. \hl{(Otherwise we may call the sum
-a \emph{direct} one, e.g. $P + Q$ if either $P$ or $Q$ are not in the
-form of prefixes.)}
+sums are in the form $a.P + b.Q$. 
+% \hl{(Otherwise we may call the sum
+% a \emph{direct} one, e.g. $P + Q$ if either $P$ or $Q$ are not in the
+% form of prefixes.)}
  The \emph{immediate derivatives} of a

### 2019-09-14 ic-journal/equa.tex
Stage work on 2nd part
text

@@
 
-\hl{In the CCS syntax given in previous section, there is the syntactic
+\hl{In the CCS syntax, 
+a recursion $\recu A  P$ acts as a binder for $A$ in the body $P$. 
+This gives rise, in the expected manner, to the notions of 
+\emph{free} and \emph{bound} recursion variables in a CCS expression.
+
+ given in previous section, there is the syntactic
 possibility that an agent variable $A$ occurs
@@
 both free and bound, e.g. in $a.X + \recu X (b.X)$.
-This does not cause any ambiguity, but sometimes leads to more
+This setting does not cause any ambiguity, but sometimes leads to more
 complex proofs.} (c.f. Section~\ref{sec:multivariate} for more details.)

### 2019-09-14 ic-journal/expansion.tex
text

@@
 
-\hl{The \emph{strong} bisimulation and strong bisimilarity} ($\sim$)
+\hlD{\emph{Strong} bisimulation and strong bisimilarity} ($\sim$)
 can be obtained by replacing the weak transition $Q\Arcap\mu Q'$ in the above
@@
 Weak bisimilarity is not preserved by the sum operator (except for
-guarded sums), \hl{i.e. from $P_1 \wb Q_1$ and $P_2 \wb Q_2$ one
-  cannot obtain $P_1 + P_2 \wb Q_1 + Q_2$.}
+guarded sums), \hlD{i.e.\  $P_1 \wb Q_1$ and $P_2 \wb Q_2$  does not imply
+ $P_1 + P_2 \wb Q_1 + Q_2$.}
 For this, Milner introduced the concept of \emph{observational congruence}, also called \emph{rooted
@@
 
-\hl{The above definition also brings up a proof technique for proving rooted
+\hlD{The above definition also brings up a proof technique for proving rooted
 bisimilarity from a given bisimulation. The next
-lemma is usually not mentioned in CCS literature but plays an
+lemma plays an
 important role in proving some key results in this paper:}
@@
 \label{l:obsCongrByWeakBisim}
-Given a (weak) bisimulation $\RR$, if two processes $P$ and $Q$
-\hl{satisfy} the following properties \hl{(but not necessary $P\;\R\;Q$)}:
+\hlD{Given a (weak) bisimulation $\RR$, suppose two processes $P$ and $Q$
+satisfy the following properties}:
 \begin{enumerate}
@@
 
-\hl{One basic property of rooted bisimiarity is that, it is (like $\sim$)
-a congruence (thus also an equivalence relation)
-w.r.t.~all CCS operators except for the Recursion and is the
-coarsest congruence contained in bisimilarity:}
-(c.f. Section~\ref{s:coarsest} for more details)
+\hlD{One basic property of rooted bisimiarity is congruence,
+indeed
+ the
+coarsest congruence contained in bisimilarity
+(c.f., Section~\ref{s:coarsest} for more details): }
 \begin{theorem}

### 2019-09-14 ic-journal/intro.tex
text

@@
 any two solutions must be componentwise bisimilar.
-The difference \hl{from} equations is \hl{at} the meaning of a solution:
+The difference \hl{from} equations is \hlD{in} the meaning of a solution:
 in the case of contractions the solution is evaluated with respect to
@@
 restrictive CCS syntax)
-is the occurrences of \emph{direct} sums (e.g.~$P + Q$) due to
+is the occurrences of %\emph{direct} 
+\hlD{sums} (e.g.~$P + Q$) due to
 the \hl{non-substitutivity of the contraction preorder in this case}.
 
-The work \hl{behind} this paper is a
+ \hlD{This paper presents}  a
 comprehensive formalisation of Milner's Calculus of Communicating
@@
 with a focus towards the theory of unique solutions of equations and contractions.
-\hl{Almost all results in Milner's CCS book}~\cite{Mil89} are covered, since
+\hlD{Many results in Milner's CCS book}~\cite{Mil89} are covered, since
 the unique-solution theorems rely on a large number of fundamental results.
@@
 
-From the \hl{point of} view of CCS theory, this formalisation has offered us the possibility of
+From the \hl{point of} view of the CCS theory, this formalisation has offered us the possibility of
 further refining the theory of unique solutions of contractions.
-In particular, Sangiorgi's result~\cite{sangiorgi2017equations} has
-placed limitations on the body of the contractions due to the
+In particular, \hlD{the existing result~\cite{sangiorgi2017equations} has
+ limitations} on the body of the contractions due to the
 substitutivity problems of weak bisimilarity and other behavioural relations with respect
@@
 \emph{rooted bisimilarity} (hence also for bisimilarity itself), and places no 
-constraints on the occurrences of sums.
+\hlD{constraints on the use the sum operator}.
 
@@
 %
-In these cases, moving between proofs there are only a few places in
+In these cases, when moving between proofs there are only a few places in
 which the HOL proof scripts have to be modified.
@@
 
-\hl{The univariate versions of unique-solution theorems use
-$\lambda$-functions to present univariate CCS equations,
+\finish{below: ``In contrast to most literature,...'' we need to
+  support this with references}
+
+\hlD{We first consider the case of a single equation (or contraction),
+that we call the univariate case, then consider the multivariate
+  case, where  more than one equation
+  (or contraction) is possible.
+The univariate  theorems use
+$\lambda$-functions to present  CCS equations,
 while the multivariate versions require a
-careful and detailed formalisation of CCS equations with equation
-variables and multivariate variable substitutions.
+more careful and delicate treatment of 
+expressions with several 
+variables and substitutions acting on them.
 In contrast to most literature, we have adopted the same
 type for both CCS equations and processes: those undefined constants
-in CCS terms are treated as equation (free) variables, and a CCS
-\emph{process} is a CCS term without equation variables. As a result,
-most CCS results except the unique-solution theorems are valid for
-both CCS processes and equations.} (c.f. Section~\ref{sec:multivariate}
-for more deails.)
+in CCS terms are treated as  (free) equation variables, and a CCS
+\emph{process} is a CCS term without equation variables. 
+This allows us a smoother move from the univariate case to the multivariate
+one. See Section~\ref{sec:multivariate}
+for  deails.}
 
@@
 unique-solution result for rooted bisimilarity.
-Section~\ref{s:for} highlights our formalisation in HOL4.
-In Section~\ref{sec:multivariate}, \hl{we describe the formalisation of
-multivariate versions of unique-solution theorems.}
+Section~\ref{s:for} highlights our formalisation in HOL4 \hlDfor the
+univariate case.}
+\hlD{Section~\ref{sec:multivariate} describes the move to the
+  multivariate case}. 
 Finally,  Section~\ref{s:rel} and \ref{s:concl} discuss related work,

### 2019-09-14 ic-journal/context.tex
Stage work on multivariate section
text

@@
 \subsection{Context, guardedness and (pre)congruence}
+\label{ss:context}
 
@@
 
+Both strong bisimilarity ($\sim$) and
+rooted bisimilarity ($\approx^c$) are congruence:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{congruence} \HOLConst{STRONG_EQUIV}\hfill{[STRONG_EQUIV_congruence]}
+\HOLTokenTurnstile{} \HOLConst{congruence} \HOLConst{OBS_CONGR}\hfill{[OBS_CONGR_congruence]}
+\end{alltt}
+
+Although weak bisimilarity ($\approx$) is \emph{not} a congruence
+  with respect to~\texttt{CONTEXT}, it is indeed substitutive
+  with respect to~\texttt{GCONTEXT} 
+% (or if the CCS syntax were defined with
+%   only guarded sum operator \cite{sangiorgi2015equations}) 
+as $\approx$ is indeed preserved by guarded sums.
+
+Also,
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{precongruence} \HOLConst{OBS_contracts}\hfill{[OBS_contracts_precongruence]}
+\end{alltt}
+
 % next file: coarsest.htex

### 2019-09-14 ic-journal/sos.tex
text

@@
 
-From \hl{the point of view of HOL4, SOS rules are actually} \emph{inductive
-  definitions} \hl{of the ternary} relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL's
-\texttt{Hol_reln} function.
-
 A useful facility exploiting the interplay
@@
   transitions mentioned above; (2) there exists no other
-  transition. The first part can be easily proved by SOS rules, while
-  the second part can only be proved by \texttt{TRANS\_cases}. (TODO)}
-
-For large CCS processes it is surprisingly \hl{tedious} to manually derive
+  transition.} For large CCS processes it is surprisingly \hl{tedious} to manually derive
 all the possible transitions and prove the non-existence of others,

### 2019-09-14 ic-journal/contraction.tex
text

@@
 (Theorem~\ref{t:Mil89})
-\hl{brings a new proof technique for proving (weak) bisimilarities. However, it has
-severe limitations: the equations must be guarded and sequential (plus
+\hlD{brings a new proof technique for proving (weak) bisimilarities. However, it has
+ limitations: the equations must be guarded and sequential (moreover
 all sums where equation variables appear must be guarded sums).
-This greatly limits the usefulness of the technique, since
+This limits the usefulness of the technique, since
 the occurrences of other operators above the variables, such as parallel
 composition and restriction, in general cannot be removed.}
-The constraints of Theorem~\ref{t:Mil89}, however, can be greatly
+The constraints of Theorem~\ref{t:Mil89}, however, can be 
 weakened if we move from equations to a special kind of inequations called

### 2019-09-14 ic-journal/equa.tex
text

@@
 
-\hl{In the CCS syntax, 
+\hlD{In the CCS syntax, 
 a recursion $\recu A  P$ acts as a binder for $A$ in the body $P$. 
@@
 \emph{free} and \emph{bound} recursion variables in a CCS expression. 
+For instance,  $X$ is free in $a.X + \recu Y (b.Y)$ while $Y$
+is bound; 
+in $a.X + \recu X (b.X)$,
+ $X$ is
+both free and bound.
+%  given in previous section, there is the syntactic
+% possibility that an agent variable $A$ occurs
+% outside the recursion operator of the same variable (or, equivalently, a
+% process constant $C$ is used but undefined). We say such a variable is
+% \emph{free}, while those variables wrapped by their recursions are
+% \emph{bound}.}
+A tem
+without free variables  is a  \emph{process}.}
+% This setting does not cause any ambiguity, but sometimes leads to more
+% complex proofs.} (c.f. Section~\ref{sec:multivariate} for more details.)
 
- given in previous section, there is the syntactic
-possibility that an agent variable $A$ occurs
-outside the recursion operator of the same variable (or, equivalently, a
-process constant $C$ is used but undefined). We say such a variable is
-\emph{free}, while those variables wrapped by their recursions are
-\emph{bound}.}
-\hl{A CCS \emph{tem} (or \emph{expression}, i.e. those with valid syntax)
-without any free variable is called a CCS \emph{process}.}
-\hl{For instance, the variable $X$ is free in $a.X + \recu Y (b.Y)$, while $Y$
-is bound. There is also the syntactic possibility that the same
-variable $X$ is
-both free and bound, e.g. in $a.X + \recu X (b.X)$.
-This setting does not cause any ambiguity, but sometimes leads to more
-complex proofs.} (c.f. Section~\ref{sec:multivariate} for more details.)
-
-\hl{In this paper (and the formalisation work), we reuse the free agent
-variables as \emph{equation variables}. This eliminates the need of
-another type for CCS equations, and we can also reuse the existing
+\hlD{In this paper (and the formalisation work), we use the agent
+variables also as \emph{equation variables}. This eliminates the need of
+another type for  equations, and we can reuse the existing
 variable substitution operation} (c.f. SOS rule for the Recursion in
-Fig.~\ref{f:LTSCCS}) \hl{for the substitution of equation variables.
-For example, the result of substituting equation variable $X$ to $\nil$ in $a.X +
-\recu X (b.X)$, denoted by $(a.X + \recu X (b.X)) \sub {\nil} X$, is
-$a.\nil + \recu X (b.X)$ with the part $\recu X (b.X)$
-untouched. Multivariate substitutions are written in the same syntax,
+Fig.~\ref{f:LTSCCS}) \hlD{for the substitution of equation variables.
+For example, the result of substituting variable $X$ with $\nil$ in $a.X +
+\recu X (b.X)$,  written $(a.X + \recu X (b.X)) \sub {\nil} X$, is
+$a.\nil + \recu X (b.X)$ (with the part $\recu X (b.X)$
+untouched). Multivariate substitutions are written in the same syntax,
 e.g. $E \sub {\til P} {\til X}$. Whenever $\til X$ is clear from the
 context, we may also write $E[\til P]$ instead of $E \sub {\til P} {\til
-  X}$. (and $E[P]$ for $E \sub P X$ if there is a single equation variable $X$.)}
+  X}$ (and $E[P]$ for $E \sub P X$ if there is a single equation variable $X$.)}
 
-\hl{In fact, free agent variables have the same transitional behavior
-as the deadlock $\nil$ according to the SOS rules, as there is
-no rule for their transitions at all. In fact, most CCS theorems still hold if
-the involved CCS terms contain free variables. (The most notable
-exceptions are all versions of unique solution of equations/contracts,
-where all solutions must be \emph{pure} processes (i.e. no free variable).)}
+% \hl{In fact, free agent variables have the same transitional behavior
+% as the deadlock $\nil$ according to the SOS rules, as there is
+% no rule for their transitions at all. In fact, most CCS theorems still hold if
+% the involved CCS terms contain free variables. (The most notable
+% exceptions are all versions of unique solution of equations/contracts,
+% where all solutions must be \emph{pure} processes (i.e. no free variable).)}
 
@@
 \label{ss:SysEq}
-
-Milner's ``unique solution of equations'' theorems~\cite{Mil89} intuitively
-say that, if a context $C$ \hl{(i.e., a CCS expression with possibly
-free variables)}\footnote{\hl{Rigorously speaking, under our setting
-(i.e.~reusing free agent variables as equation variables) not all
-valid CCS expressions
-are valid contexts: those where free variables occur inside
-recusion operators must be all excluded. For instace, $\recu X (a.X +
-b.Y)$ is not a valid context with the variable $Y$. This special requirement
-is perfectly aligned with CCS literature using process constants, as any
-equation variable cannot occur inside the definition of any
-constant. In fact, all versions of ``unique solution of
-equations/contractions'' theorems do not hold if equation variables
-are allowed to occur inside any recursion operator.}} obeys certain conditions,
+\hlD{When discussing equations it is standard to talk about `context'. This is a 
+ a CCS expression  possibly containing  free variables that, however, may not occur within
+the body of recursive definitions. 
+Milner's ``unique solution of equations'' }  theorems~\cite{Mil89} intuitively
+\hlD{say that, if a context $C$
+%  \hl{(i.e., a CCS expression with possibly
+% free variables)}\footnote{\hl{Rigorously speaking, under our setting
+% (i.e.~reusing free agent variables as equation variables) not all
+% valid CCS expressions
+% are valid contexts: those where free variables occur inside
+% recusion operators must be all excluded. For instace, $\recu X (a.X +
+% b.Y)$ is not a valid context with the variable $Y$. This special requirement
+% is perfectly aligned with CCS literature using process constants, as any
+% equation variable cannot occur inside the definition of any
+% constant. In fact, all versions of ``unique solution of
+% equations/contractions'' theorems do not hold if equation variables
+% are allowed to occur inside any recursion operator.}} 
+obeys certain conditions,
 then all processes $P$ that satisfy the equation $P \wb \ct P$ are
 bisimilar with each other.
+}
 
@@
  a countable indexing set $I$, we have variables $X_i$, and expressions
-$E_i$ containing variables up to $\til X$. Then 
+$E_i$ \hlD{possibly containing such variables $\cup_i \{ X_i\}$}. Then 
 $\{ X_i = E_i\}_{i\in I}$ is 
@@
 \item The system has \emph{a unique solution for $\wb$}  if whenever 
- $\til P$ and $\til Q$ are both solutions \hl{it holds that} $\til P \wb \til Q$. 
+ $\til P$ and $\til Q$ are both solutions \hlD{then} $\til P \wb \til Q$. 
 \end{itemize} 
@@
 (or for $\rapprox$) can be obtained by replacing all occurrences of $\wb$
-in above definition with $\sim$ and $rapprox$, respectively.}
+in above definition with $\sim$ and $\rapprox$, respectively.}
 
@@
 
-\item \emph{(strongly) guarded} if, in each $E_i$, each occurrence of
+\item \hlD{\emph{guarded}} if, in each $E_i$, each occurrence of
   each $X_i$ is underneath a \emph{visible} prefix;
+
+\finish{i have removed 
+``(strongly)''}
 
@@
 
-\hl{In other words, if a system of equations is sequential, then for
-each context $E_i$, any subcontext of $E_i$ in which $X_j $
+\hlD{In other words, if a system of equations is sequential, then for
+each  $E_i$, any subexpression of $E_i$ in which $X_j $
 appears, apart from $X_j$ itself, is a sum of prefixed expressions.
@@
 
-\hl{Milner has totally three versions of ``unique solution of equations''
-theorems, for $\sim$, $\wb$ and $\rapprox$, respectively, but only the
+\hlD{Milner has  three versions of  ``unique solution of equations''
+theorems, for $\sim$, $\wb$ and $\rapprox$, respectively, though only the
 following two versions are explicitly mentioned} in~\citep[p.~103, 158]{Mil89}:
@@
 \label{t:Mil89s1}
-Let $E_i$ be weakly guarded with free variables up to $\til X$,
+Let $E_i$ be weakly guarded with free variables in $\til X$,
 and let ${\til P} \sim {\til E}\{\til P /\til X\}$,
@@
 
-\hl{The version of Milner's unique-solution theorem for $\wb$ further requires
-that all sums where equation variables appear are guarded
-sums}\footnote{But if the CCS syntax were defined with only guarded
-  sums, i.e., $\sum_{i\in I} \mu_i.P_i$ as
-  in~\cite{sangiorgi2015equations}, this addition
-  requirement disappears automatically, and we can even say $\wb$ is indeed a
-  congruence.}:
+\hlD{The version of Milner's unique-solution theorem for $\wb$ further requires
+that all sums are guarded}:
+% \footnote{But if the CCS syntax were defined with only guarded
+%   sums, i.e., $\sum_{i\in I} \mu_i.P_i$ as
+%   in~\cite{sangiorgi2015equations}, this addition
+%   requirement disappears automatically, and we can even say $\wb$ is indeed a
+%   congruence.}:
 \begin{theorem}[unique solution of equations for $\wb$]
 \label{t:Mil89}
-Let $E_i$ be guarded (with guarded sums only) and sequential with free
+Let $E_i$ be \hlD{guarded}  and sequential with free
 variables up to $\til X$, and let ${\til P} \wb {\til E}\{\til P /\til X\}$,
@@
 
-The proof of \hl{the last theorem above} exploits an invariance
-property on immediate \hl{derivations}
+\finish{below and elsewhere: the correct terminology is ``derivative'', instead of ``derivation''}
+
+The proof of \hlD{the  theorem above} exploits an invariance
+property on immediate \hlD{derivatives}
 of guarded and sequential expressions, and then extracts a bisimulation
@@
 
-\hl{For more details of above three theorems,} c.f. Section~\ref{ss:part2}
-for their formalised versions (the univariate case) and
-Section~\ref{sec:multivariate} for the multivariate case
-(Theorem~\ref{t:Mil89s1} only).
+\hlD{For more details of above three theorems,} see Section~\ref{ss:part2}
+for the univariate case and
+Section~\ref{sec:multivariate} for the multivariate case.
+%(Theorem~\ref{t:Mil89s1} only).
 

### 2019-09-14 ic-journal/expansion.tex
text

@@
 Weak bisimilarity is not preserved by the sum operator (except for
-guarded sums), \hlD{i.e.\  $P_1 \wb Q_1$ and $P_2 \wb Q_2$  does not imply
- $P_1 + P_2 \wb Q_1 + Q_2$.}
+guarded sums), i.e.\  $P_1 \wb Q_1$ and $P_2 \wb Q_2$  \hlD{does not imply}
+ $P_1 + P_2 \wb Q_1 + Q_2$.
 For this, Milner introduced the concept of \emph{observational congruence}, also called \emph{rooted
@@
  the
-coarsest congruence contained in bisimilarity
-(c.f., Section~\ref{s:coarsest} for more details): }
+coarsest congruence contained in bisimilarity}
+(c.f., Section~\ref{s:coarsest} \hlD{for more details): }
 \begin{theorem}

### 2019-09-14 ic-journal/formal.tex
Moved context.htex after bisim.htex and before part2.htex (unique-solution theorems)
text

@@
 %  in the informal proofs. 
-\hl{The univariate versions of these theorems, apart from minor fixes and
-extensions in this paper, was already described in}
-\cite{Tian:2017wrba}. The multivariate proofs and the related results
-are new, and will be described in Section~\ref{sec:multivariate}.
+% \hl{The univariate versions of these theorems, apart from minor fixes and
+% extensions in this paper, was already described in}
+% \cite{Tian:2017wrba}. The multivariate proofs and the related results
+% are new, and will be described in Section~\ref{sec:multivariate}.
 All proof scripts are available as part of HOL's official
@@
 foundations than most other theorem provers. %, e.g. Coq. 
-\hl{As a consequence, theories and proofs verified in HOL are relatively more
-convincible to non-experts who are not familar with more advanced
+\hl{As a consequence, theories and proofs verified in HOL are easier to understand
+ to people who are not familar with more advanced
 dependent type theories.}
@@
 \item \hl{the language in which proof tactics are implemented;}
-\item \hl{the interface (outer) language of the HOL proof scripts and
+\item \hl{the interface  language of the HOL proof scripts and
   interactive shell.}
@@
 \begin{array}{@{}l@{\qquad}l}
-\mbox{\texttt{BOOL\_CASES\_AX}} &\vdash \uquant{b} (b = \T ) \vee (b = \F )\\
+\mbox{\texttt{BOOL\_CASES\_AX}} &\vdash \uquant{b} (b = \T )\ \vee \ (b = \F )\\
 \mbox{\texttt{ETA\_AX}} &

### 2019-09-14 ic-journal/intro.tex
text

@@
 further refining the theory of unique solutions of contractions.
-In particular, \hlD{the existing result~\cite{sangiorgi2017equations} has
- limitations} on the body of the contractions due to the
+In particular, \hlD{the existing result}~\cite{sangiorgi2017equations} \hlD{has  limitations} on the body of the contractions due to the
 substitutivity problems of weak bisimilarity and other behavioural relations with respect
@@
 This allows us a smoother move from the univariate case to the multivariate
-one. See Section~\ref{sec:multivariate}
-for  deails.}
+one. See} Section~\ref{sec:multivariate} for  details.
 
@@
 unique-solution result for rooted bisimilarity.
-Section~\ref{s:for} highlights our formalisation in HOL4 \hlDfor the
+Section~\ref{s:for} highlights our formalisation in HOL4 \hlD{for the
 univariate case.}
-\hlD{Section~\ref{sec:multivariate} describes the move to the
+Section~\ref{sec:multivariate} \hlD{describes the move to the
   multivariate case}. 

### 2019-09-14 ic-journal/sos.tex
text

@@
 expressions, where \texttt{'a} (or $\alpha$) is the type variable\footnote{The order of type variables $\alpha$ and $\beta$
-    is arbitrary. Our choice is aligned with other \hl{literature.
+    is arbitrary. Our choice is aligned with  the \hl{literature.
 For instance,} $\mathrm{CCS}(h,k)$ is the CCS subcalculus that can use at most $h$ constants
@@
 \hline
-\hl{deadlock} & $\textbf{0}$ & \texttt{nil} & \texttt{nil} & \HOLinline{\HOLConst{\ensuremath{\mathbf{0}}}} \\
+\hlD{nil} & $\textbf{0}$ & \texttt{nil} & \texttt{nil} & \HOLinline{\HOLConst{\ensuremath{\mathbf{0}}}} \\
 prefix & $\mu.P$ & \texttt{prefix u P} & \texttt{u..P} & \HOLinline{\HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{P}} \\
@@
 \end{equation*}
-\item \hl{\emph{ind} is the induction principle for the
-  relation.} (c.f.~Section~\ref{sec:multivariate} for the exact form
-  and its application.)
+\item \hlD{\emph{ind} is the induction principle for the
+  relation} (see Section~\ref{sec:multivariate} for the exact form
+  and its application).
 \item \hl{\emph{cases} is the so-called `cases' or `inversion' theorem for
@@
 transition. Here, ``\HOLinline{\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}}'' is \hl{an abbreviation}
-of ``\HOLinline{\HOLConst{CCS_Subst} \HOLFreeVar{E} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{)} \HOLFreeVar{X}}'', where \HOLinline{\HOLConst{CCS_Subst}} is a
+for ``\HOLinline{\HOLConst{CCS_Subst} \HOLFreeVar{E} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{)} \HOLFreeVar{X}}'', where \HOLinline{\HOLConst{CCS_Subst}} is a
 recursive function substituting all appearences of a free variable
@@
 \end{alltt}
-\hl{Intuitively, the variable substitutions only happens on \emph{free}
-variables: the variable $Y$ in} ``\HOLinline{\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}}'' \hl{is
-considered \emph{bound} and the substitution process ignores it if $Y$ is
-being substituted. The actual substitution happens in case of}
-``\HOLinline{\HOLConst{var} \HOLFreeVar{Y}}'' if $Y$ is being substituted (and if \HOLinline{\HOLConst{CCS_Subst}}
-can actually reach it).
+\hlD{The variable substitutions only affects free
+variables: the variable $Y$ in} ``\HOLinline{\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}}'' \hlD{is
+bound and therefore the substitution ignores it. }
+% The actual substitution happens in case of}
+% ``\HOLinline{\HOLConst{var} \HOLFreeVar{Y}}'' if $Y$ is being substituted (and if
+\HOLinline{\HOLConst{CCS_Subst}} 
+% can actually reach it).
 
@@
 To completely describe all possible transitions of a process, if done manually, the
-following two facts must be proved: \hl{(1) there exist indeed three
-  transitions mentioned above; (2) there exists no other
-  transition.} For large CCS processes it is surprisingly \hl{tedious} to manually derive
-all the possible transitions and prove the non-existence of others,
-\hl{which shows the usefulness of appealing to an ML function
-\texttt{CCS\_TRANS\_CONV} who is designed to automate the whole process.
+following two facts must be proved: \hl{(1) there are indeed the three
+  transitions mentioned above; (2) there are no other
+  transitions.} For large CCS processes it is surprisingly \hl{tedious} to manually derive
+all the possible transitions and prove the non-existence of others.
+\hlD{This shows the usefulness of appealing to an ML function
+\texttt{CCS\_TRANS\_CONV} that is designed to automate the whole process.
 For instance, calling it on $(a.\nil | \bar{a}.\nil)$ the function returns the

### 2019-09-14 ic-journal/unique.tex
text

@@
 
-\hl{Now we recall (with the proof) Sangiorgi's ``unique solution of
+\hlD{Now we recall the ``unique solution of
 contractions'' theorem}~\cite{sangiorgi2017equations},
-which greatly weakened the requirements of Milner's result
+\hlD{which weakens} the requirements of Milner's result
 (Theorem~\ref{t:Mil89}).
@@
 \hl{Let $E_i$ be weakly guarded (and with guarded sums only) with free
-variables up to $\til X$, and let $\til P \mcontrBIS \til E\{\til P/\til X\}$,
+variables in $\til X$, and let $\til P \mcontrBIS \til E\{\til P/\til X\}$,
     $\til Q \mcontrBIS \til E\{\til Q/\til X\}$. Then $\til P \wb \til Q$.}
@@
 \begin{proof}
-\hl{We want to prove $P_i \wb Q_i$ (for each $i \in I$) by considering} the following relation
+\hlD{We  prove $P_i \wb Q_i$ (for each $i \in I$) by considering} the following relation
 \begin{equation*}
@@
 \end{equation*}
+\finish{below: what is $\equiv$?}
 
@@
 \Arcap{\mu} S'' \wb C'[{\til Q}]$ for some $S''$. \hl{From $S \wb C[{\til
-  Q}]$ and $C[{\til Q}] \Arcap{\mu} S''$, by induction and definition of $\wb$, it is not
-hard to see that,}
-there exists also $S'$ with $S \Arcap{\mu} S'$. This \hl{completes} the
+  Q}]$ and $C[{\til Q}] \Arcap{\mu} S''$, by induction and definition of $\wb$, we find
+ $S'$} with $S \Arcap{\mu} S'$. This \hl{completes} the
 proof, as we have $R' \wb C'[{\til P}]$ and $S' \wb C'[{\til Q}]$ \hl{by
@@
 (The other side from $S$ follows in the same manner.)}
-c.f. Fig.~\ref{fig:310} \hl{for a visual illustration.}
+\hlD{See} Fig.~\ref{fig:310} \hl{for a visual illustration.}
 \end{proof}
@@
 in addition to $\wb$).
-However, comparing with Milner's Theorem~\ref{t:Mil89s1}, \hl{there is
-still one more limit: the involved CCS contexts must only
+However, comparing with Milner's Theorem~\ref{t:Mil89s1}, \hlD{there is
+a constraint: the involved CCS expression may only
 use guarded sums. The is mainly due to the fact that $\wb$ is not a
- (real) congruence and also $\mcontrBIS$ is not a (real) precongruence.
-Inspired by rooted bisimilarity, to completely eliminate the restriction
+ congruence and also $\mcontrBIS$ is not a  precongruence.
+Inspired by rooted bisimilarity, to  eliminate the restriction
 on guarded sums, we have extended the idea of contractions by moving
@@
 \hl{The above definition was found with the help of interactive theorem proving.}
-First of all, the following two principles were adopted when searching
-for a possible definition: (1) the definition should not be \hl{coinductive},
-along the lines of rooted bisimilarity $\rapprox$ (Def.~\ref{d:rootedBisimilarity});
-(2) the definition should be built on top of existing \emph{contraction}
+\hlD{The following two principles were adopted when searching
+for a possible definition: (1) the definition should not be coinductive,
+along the lines of rooted bisimilarity} $\rapprox$ (Def.~\ref{d:rootedBisimilarity});
+(2) the definition should be built on top of  the existing \emph{contraction}
 relation $\mcontrBIS$.
-\hl{Then several candidates were quickly checked (using very similar
-  proof steps): the key is to prove its transitivity, and whenever the
-  proof attempts failed we tried to fix the definition. Eventually the
-  above definition was found and shown to be a precongruence, i.e. it
-  is preserved by all CCS operators except the Recursion, same as in
-  the cases of $\sim$ and $\rapprox$.}
-\hl{Furthermore, we needed to show that, the definition being found is the
-best possible one, by showing that it is the coarsest precongruence
-contains in $\mcontrBIS$, and the proof succeeded and is very similar
-with the same result for $\rapprox$} (c.f.~Section~\ref{s:coarsest} for
-more details).
+% \hl{Then several candidates were quickly checked (using very similar
+%   proof steps): the key is to prove its transitivity, and whenever the
+%   proof attempts failed we tried to fix the definition. Eventually the
+%   above definition was found and shown to be a precongruence, i.e. it
+%   is preserved by all CCS operators except the Recursion, same as in
+%   the cases of $\sim$ and $\rapprox$.}
+\hlD{Furthermore, we needed to show that the definition found is the
+best possible one, by showing that it yields the coarsest precongruence
+contains in $\mcontrBIS$; the proof is similar
+to  the analogous result for $\rapprox$}. \hlD{See} Section~\ref{s:coarsest} for
+more details.
 
@@
 
-\hl{The next lemma is actually Lemma 3.13} of~\citep[p.~102]{Mil89}, \hl{which
-was designed to prove Milner's ``unique solution of equations for
-$\sim$''} (Theorem~\ref{t:Mil89s1}):
+\hl{The next lemma is actually Lemma 3.13} of~\citep[p.~102]{Mil89}, \hlD{and
+is needed} to prove Milner's ``unique solution of equations for
+$\sim$'' (Theorem~\ref{t:Mil89s1}):
 \begin{lemma}
@@
 \label{t:rcontraBisimulationU}
-\hl{Let $E_i$ be weakly guarded with free variables up to $\til X$,
+\hl{Let $E_i$ be weakly guarded with free variables in $\til X$,
 and let $\til P \rcontr \til E\{\til P/\til X\}$,
@@
 \begin{proof}
-\hl{We want to prove $P_i \rapprox Q_i$ (for each $i \in I$) by considering}
+\hl{We  prove $P_i \rapprox Q_i$ (for each $i \in I$) by considering}
 the following relation
@@
 $Q' \wb C[{\til Q}]$. (The other side from $Q_i$ follows in the same manner.)
-c.f. Fig.~\ref{fig:314} \hl{for a visual illustration.}
+\hlD{See} Fig.~\ref{fig:314}.
 \end{proof}

### 2019-09-14 ic-journal/multivariate.tex

@@
 order-independent. Below we present some key lemmas about
-\HOLinline{\HOLConst{CCS_SUBST}} \emph{without proofs}:
+\HOLinline{\HOLConst{CCS_SUBST}} \emph{without proofs}: \footnote{Hereafter,
+  some new logical constants from HOL's \texttt{pred_set}
+and \texttt{list} theories are used (c.f.~\cite{holdesc} for more
+details.): \HOLinline{\HOLConst{DISJOINT}} denotes set disjointness;
+``\HOLinline{\HOLConst{set}\\\;\HOLFreeVar{Xs}}'' is the set converted from the list \HOLinline{\HOLFreeVar{Xs}};
+\HOLinline{\HOLConst{ALL_DISTINCT}} says
+all elements of a list are distinct with each other; \HOLinline{\HOLConst{MAP}} is
+the mapping function from one list to another; \HOLinline{\HOLConst{EVERY}} means
+each element of a list satisfies a predicate; \HOLinline{\HOLConst{ZIP}} creates a
+new list from two lists of the same length, and each element of the new list is a pair of
+elements, each from one of the old lists.}
 
@@
 If the free variables of $E$ is disjoint with \HOLinline{\HOLFreeVar{Xs}}, a
-substitution of \HOLinline{\HOLFreeVar{Xs}} in $E$ does not change $E$:
+substitution of \HOLinline{\HOLFreeVar{Xs}} in $E$ does not change
+$E$:
 \begin{alltt}
@@
 
-The next three lemmas show the relative correctness of \texttt{CCS\_SUBST}
-w.r.t. \texttt{CCS\_Subst}:
-\begin{lemma}[\texttt{CCS_SUBST_SING}]
+The next three lemmas show the relative correctness of \texttt{CCS_SUBST}
+with respect to \texttt{CCS_Subst}:
+\begin{lemma}[\texttt{CCS_SUBST_sing}]
   If there is only one single variable $X$ in the map (with the target
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{CCS_SUBST} \ensuremath{(}\HOLConst{FEMPTY} \HOLSymConst{|+} \ensuremath{(}\HOLFreeVar{X}\HOLSymConst{,}\HOLFreeVar{E\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{CCS_Subst} \HOLFreeVar{E} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{X}
+\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{]}\ensuremath{/}\ensuremath{[}\HOLFreeVar{X}\ensuremath{]}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}
 \end{alltt}
@@
 Under certain conditions (to get rid of substitution orders), a
-\multivariate substitution can be reduced to repeated applications
-of \univariate substitutions of each variable:
+\multivariate substitution can be reduced to a sequence of
+of \univariate substitutions:
 \begin{alltt}
@@
 Notice that, \HOLinline{\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{Y}\\\;\HOLSymConst{\ensuremath{=}}\\\;\ensuremath{[}\HOLFreeVar{t}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\ensuremath{(}\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{Y}\ensuremath{)}}.
-This idea leads to the following definitions:
+This above idea leads to the
+following definitions of CCS contexts and weakly-guarded contexts:
 \begin{alltt}
@@
 \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Xs}
+\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Xs}\hfill{[context_def]}
 
@@
 \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Xs}
+\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Xs}\hfill{[weakly_guarded_def]}
 \end{alltt}
+Notice that,
 

### 2019-09-14 ic-journal/multivariate.tex
Stage work of the multivariate section (done Section 5.3)

@@
 order-independent. Below we present some key lemmas about
-\HOLinline{\HOLConst{CCS_SUBST}} \emph{without proofs}: \footnote{Hereafter,
+\HOLinline{\HOLConst{CCS_SUBST}} without proofs:\footnote{Hereafter,
   some new logical constants from HOL's \texttt{pred_set}
@@
 If the free variables of $E$ is disjoint with \HOLinline{\HOLFreeVar{Xs}}, a
-substitution of \HOLinline{\HOLFreeVar{Xs}} in $E$ does not change
-$E$:
+substitution of \HOLinline{\HOLFreeVar{Xs}} in $E$ does not change $E$:
 \begin{alltt}
@@
 
-\subsection{\Multivariate (weakly-guarded) contexts}
+\subsection{\Multivariate (weakly guarded) contexts}
 
@@
 \HOLinline{\HOLConst{CONTEXT}}
-(contexts/expressions), \HOLinline{\HOLConst{WG}} (weak-guarded contexts),
-\HOLinline{\HOLConst{SG}} (strongly-guarded contexts) and \HOLinline{\HOLConst{SEQ}} (sequential
+(contexts/expressions), \HOLinline{\HOLConst{WG}} (weak guarded contexts),
+\HOLinline{\HOLConst{SG}} (strongly guarded contexts) and \HOLinline{\HOLConst{SEQ}} (sequential
 contexts), are all defined inductively, i.e.~they are built from some ``holes''
@@
 This above idea leads to the
-following definitions of CCS contexts and weakly-guarded contexts:
+following definitions of CCS contexts and weakly guarded contexts:
 \begin{alltt}
@@
 \end{alltt}
-Notice that,
+Notice that, the above definitions take an extra list of variables \HOLinline{\HOLFreeVar{Xs}} and
+assert the CCS expression \HOLinline{\HOLFreeVar{E}} with respect to this list. This
+allows us to formalise the concepts of contexts and guardedness
+independently of \HOLinline{\HOLConst{FV}}.
+Then \HOLinline{\HOLConst{weakly_guarded}\\\;\ensuremath{(}\HOLConst{SET_TO_LIST}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\ensuremath{)}\\\;\HOLFreeVar{E}} can
+be used assert that $E$ is weakly guarded w.r.t.~all its free
+variables.\footnote{Here \HOLinline{\HOLConst{SET_TO_LIST}} converts a finite set
+  to a list of the same elements. It turns out that, we never need this, because
+  in all unique-solution theorems a list of variables \HOLinline{\HOLFreeVar{Xs}} is fixed and
+  then all equations are required to contain free variables up to
+  \HOLinline{\HOLFreeVar{Xs}}. Thus our choices in these definitions are optimal.}
+(The strong guardedness and sequentiality can also be defined similarily
+when needed, using
+their \univariate companions (\texttt{SG} and \texttt{SEQ}).)
 
+The most important property of contexts are that, strong bisimilarity
+and other (pre)congruence relations are preserved by contexts, e.g.
+\begin{lemma}[\texttt{STRONG_EQUIV_subst_context}]
+If two tuples of processes $\til P$ and $\til Q$ are strongly
+bisimilar\footnote{Hereafter, HOL terms like \HOLinline{\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenStrongEQ}\\\;\HOLFreeVar{Qs}}
+  means that, two list of CCS processes are componentwise
+  (strongly) bisimilar. The same notation $\sim$ has been overloaded.}
+for any context $E$ with the possible occurrences of variables $\til
+X$ (same length as $\til P$ and $\til Q$), $E\{\til P/\til X\}$ and
+$E\{\til Q/\til X\}$ are also strongly bisimilar:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{Qs} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
+\HOLConst{context} \HOLFreeVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\HOLTokenStrongEQ} \ensuremath{[}\HOLFreeVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E}
+\end{alltt}
+\end{lemma}
+The similar properties also hold if $\sim$ is replaced with rooted
+bisimilarity ($\rapprox$) or rooted contraction ($\rcontr$). (It does
+not hold for weak bisimilarity $\wb$ and the contraction preorder $\mcontrBIS$.)
+
+Another important property of contexts is their composability: if we
+substitute some free variables in a context for some other contexts, the
+resulting term is still a context (w.r.t.~the same set of variables):
 \begin{alltt}
@@
    \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
-   \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)}
-
-\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{Qs} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
-\HOLConst{context} \HOLFreeVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\HOLTokenStrongEQ} \ensuremath{[}\HOLFreeVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E}
-
-\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Qs} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
-\HOLConst{context} \HOLFreeVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \ensuremath{[}\HOLFreeVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E}
-
-\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{Qs} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
-\HOLConst{context} \HOLFreeVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsContracts} \ensuremath{[}\HOLFreeVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E}
+   \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)}\hfill{[context_combin]}
 \end{alltt}
 
+Not every expression fit with CCS syntax is a context: any free
+variable in concern must not occur inside any recusion operator
+(c.f. the footnote at the beginning of Section~\ref{ss:SysEq}). In the
+extreme case, if the set of free variables of an expression, say $E$,
+is disjoint with a list of variables $\til X$, then this expression is
+for sure a context:
 \begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{E}\hfill{[disjoint_imp_context]}
+\end{alltt}
+On the other hand, for any context (w.r.t.~$\til X$) of the form $\recu Y E$, we can
+conclude that, the set of free variables of $E$ excluding $Y$, is
+disjoint with $\til X$, i.e.
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{Y}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\hfill{[context_rec]}
+\end{alltt}
+Notice that, the above result is the best possible one. We cannot
+conclude \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}}, because $Y$ as a bound
+variable of $\recu Y E$ may be also a free variable in $\til X$. We
+also cannot conclude \HOLinline{\HOLConst{context}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{E}}, because in $\recu Y E$
+it is possible that the bound variable $Y$ occurs inside another
+recursion operator, then in $E$ it now becomes free. (See $\recu Y
+(\recu Z (a.Y + b.Z) + c.Y)$ for such an example.)
 
+For weakly-guarded contexts (which are also normal contexts), beside
+their regular properties (i.e. weak
+guardedness) as in the \univariate case (\HOLinline{\HOLConst{WG}}), we also need
+their composability w.r.t.~\multivariate contexts: if we
+substitute some free variables in a context $C$ for some weakly-guarded
+contexts, the resulting term is weakly-guarded (w.r.t.~the same set of variables):
+\begin{alltt}
 \HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
    \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
-   \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)}
+   \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)}\hfill{[weakly_guarded_combin]}
 \end{alltt}
@@
 \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Es}
-
 \HOLTokenTurnstile{} \HOLConst{CCS_solution} \HOLFreeVar{R} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenEquiv{}}

### 2019-09-14 ic-journal/coarsest.tex
text

@@
   names}), and is therefore strictly stronger than the assumption in
-our result above. \hl{Indeed, in out result we} only look at immediate weak
+our result above. \hl{Indeed, in our result we} only look at immediate weak
 derivatives for $p$ and $q$, \hl{and only requires that there is an input
@@
 ordinals''~\cite{norrish2013ordinals}.
-\hl{As a consequence, the final result is only for finite-state
-  CCS---a very restricted class.}
+\hlD{As a consequence, the final result is only for finite-state
+  CCS~--- a  restricted class.}
 

### 2019-09-14 ic-journal/conclusions.tex
text

@@
 delicate and subtle differences in a few points. In a paper-pencil
-proof, checking all details would be long and error-prune, since one
-is tempted to overlook  details that tend to repeat themselves. 
+proof, checking all details would be long and \hl{error-prone},
+\hl{especially in cases in which proofs are similar to each other or
+  when there are a long case analysis to be carried out.}
 A theorem-prover formalisation is in this respect  helpful and reassuring.
@@
 Formalising other equivalences and preorders could also be considered,
-notably the trace equivalences, as well as more refined process
+notably the \hl{trace-based} equivalences, as well as more refined process
 calculi such as value-passing CCS.
@@
 We have  benefitted from suggestions and comments 
-from several people from the HOL
-community, including (in alphabet order) Robert Beers, Jeremy Dawson,
+from  the \hl{anonymous reviewers} and several people from the HOL
+community, including (in \hl{alphabetic} order) Robert Beers, Jeremy Dawson,
 Ramana Kumar,
@@
 %
-The 
-paper was written in memory of Michael J.~C.~Gordon, the creator of the HOL theorem prover.
+The paper was written in memory of Michael J.~C.~Gordon, the creator of the HOL theorem prover.

### 2019-09-14 ic-journal/multivariate.tex
text

--- 2019-09-13 ic-journal/multivariate.tex
@@
 
-In this section, the formalisation of the \multivariate (general)
+In this section,  \hlD{we discuss the formalisation of the general}  \multivariate
 cases of Milner's ``unique solution of equations (for $\sim$)''
 (Theorem~\ref{t:Mil89s1}) and our ``unique solution of rooted
-contractions'' (Theorem~\ref{t:rcontraBisimulationU}) is
-described.
-We choose these two theorems because they both depend on the same
+contractions'' (Theorem~\ref{t:rcontraBisimulationU}).
+We chose these two theorems because they both depend on the same
 concept of ``weakly guarded contexts'', and Lemma~\ref{lem:milner313}.
-\hl{This work is entirely new} after~\cite{EPTCS276.10}.
-It is accumulative, completely based on the
-existing formal framework in the sense that, neither the CCS datatype nor
-the SOS rules need to be changed.
+%\hl{This work is entirely new} after~\cite{EPTCS276.10}.
+\hlD{The work is an extension of the univariate case
+ in the sense that neither the CCS datatype nor
+the SOS rules need to be changed.}
 
@@
 representation of CCS equations (expressions, contexts).
-Recall the univariate formalisation, $\lambda$-functions (of type
+\hlD{In the} univariate formalisation, $\lambda$-functions (of type
 $CCS\rightarrow CCS$) are used to represent univariate CCS
-equations, and variable substitutions are simply done by
-calling $\lambda$-functions on the target CCS terms.
+\hlD{equations, and variable substitutions are simply 
+calls to $\lambda$-functions on the target CCS terms.}
 This idea cannot be extended to the \multivariate case, as
-we don't have a fixed number of variables to deal with.
+we do not have a fixed number of variables to deal with.
 
-Modern literature (i.e.~after Milner) usually consider the $X_i$ of
-a system of equations $\{X_i = E_i\}_{i\in I}$ (c.f. Def.~\ref{def:equation}) as an
-\emph{equation variable (or process variable)}~\citep[p.~102]{Gorrieri:2015jt}
-\emph{outside} of the CCS syntax, and treat $E_i$ as an \emph{open} expression
-built with CCS operators which may contain some occurrences of $X_i$.
-For a formal point of view, this means we either need to define a
+In the  literature the variables  $X_i$ of
+a system of equations $\{X_i = E_i\}_{i\in I}$ are usually considered as
+\emph{equation variables}
+\emph{outside} of the CCS syntax; then an equation body  $E_i$  is an \emph{open} expression
+built with CCS operators plus the equation variables.
+\hlD{For a formal point of view, this means we either need to define a
 whole new datatype (with extra equation variables) in which each CCS
-opeartor must be duplicated, or we should add equation variables as a
-new primitive (e.g.~\texttt{Var X}) in the existing CCS type beside
-the agent variables (e.g.~\texttt{var X}). Then the substitution of equation
-variables in $E_i\{\til P/\til X\}$ would be simply the \emph{syntactic substitution} of
-each occurrence of $X_i$ in $E_i$ with the corresponding $P_i$. Notice that, in
-either case the \emph{disjointness} between equation variables and
-agent variables (or constants) is obvious and syntactically
-guaranteed. However, neither solution is elegant: dealing with another CCS-like type makes the
-whole formalisation work ugly and we loose the (possibly valuable) bisimilarity concepts and
-transitional semantics of CCS expressions; on the other hand,
-modifying the CCS datatype to just support the formalisation of
-unique-solution theorems is also not acceptable.
+opeartor must be duplicated, or we have to  add equation variables as a
+new primitive (e.g.~\texttt{Var X}) to the existing CCS type (besides
+the agent variables such as  \texttt{var X}).
+ Then the substitution of equation
+variables in $E_i\{\til P/\til X\}$ would be the \emph{syntactic substitution} of
+each occurrence of $X_i$ in $E_i$ with the corresponding $P_i$. In
+either cases the \emph{disjointness} between equation variables and
+agent variables is syntactically
+guaranteed. Both solutions are rather combersome, and require a non-trivial modification
+of the formalisation of the univariate case. }
 
-In this project, we have chosen to adopt Milner's original approach,
-which is also the most elegant way: reusing \emph{free} agent variables
-(i.e. undefined constants) as equation variables, then the variable
+% : dealing with another CCS-like type makes the
+% whole formalisation work ugly and we loose the (possibly valuable) bisimilarity concepts and
+% transitional semantics of CCS expressions; on the other hand,
+% modifying the CCS datatype to just support the formalisation of
+% unique-solution theorems is also not acceptable.
+
+\hlD{In this project, we have  followed} Milner~\cite{Mil89}, thus using the same alphabet for
+both agent variables and equation variables. 
+\hlD{This has allowed a large reuse of the univariate formalisation. For instance, 
+the variable
 substitution function used in SOS rules [\texttt{REC}] can be also
 used for substituting eqaution variables.
-However, this approach brings us great difficulities in proving many
+However, a lot of care is needed in 
+in the proofs of  many
 fundamental lemmas, mostly due to the variable capture issues between
 equation variables and agent variables.
+}
+
+% which is also the most elegant way: reusing \emph{free} agent variables
+% (i.e. undefined constants) as equation variables, then the variable
+% substitution function used in SOS rules [\texttt{REC}] can be also
+% used for substituting eqaution variables.
+% However, this approach brings us great difficulities in proving many
+% fundamental lemmas, mostly due to the variable capture issues between
+% equation variables and agent variables.
 
 \subsection{Free and bound variables}
+
+\finish{too many changes below to highlight them}
 
@@
 called \emph{bound} variables, while those which occur unbound are called
-\emph{free} variables. We denote the set of all bound variables of a
-given CCS term $E$ as $\bv{E}$ (or \HOLinline{\HOLConst{BV}\\\;\HOLFreeVar{E}} in HOL), and the set of all free
+\emph{free} variables.
+
+We denote the set of all bound variables of a
+given CCS term $E$ (we recall that these are variables that are bound in a recursion
+subexpression of $E$) as $\bv{E}$ (or \HOLinline{\HOLConst{BV}\\\;\HOLFreeVar{E}} in HOL), and the set of  free
 variables as $\fv{E}$ (or \HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}} in HOL). Both \HOLinline{\HOLConst{BV}} and \HOLinline{\HOLConst{FV}} have the
@@
 variables (of type \HOLinline{\ensuremath{\alpha}}).
-Milner didn't give their definitions explicitly. However, one can
-imagine that, for most CCS operators they just pass into
-subterms without collecting anything (and $\nil$ gives $\emptyset$).
-The only interesting cases are Recursion and agent variables, shown below: (Here \texttt{DELETE}
+% Milner didn't give their definitions explicitly. However, one can
+% imagine that, for most CCS operators they just pass into
+% subterms without collecting anything (and $\nil$ gives $\emptyset$).
+For their definition the interesting cases are those of 
+recursion and agent variables, shown below  (here \texttt{DELETE}
 and \texttt{INSERT} are set-theoretic operators of HOL's
-\texttt{pred_set} theory.)
+\texttt{pred_set} theory):
 \begin{center}
@@
 \end{center}
-Furthermore, we say $E$ is a process, denoted by \HOLinline{\HOLConst{IS_PROC} \HOLFreeVar{E}}, if
-it contains no free variables, i.e. $\fv{E} = \emptyset$:
+Furthermore, $E$ is a process, written \HOLinline{\HOLConst{IS_PROC} \HOLFreeVar{E}}, if
+it does not  contains free variables, i.e. $\fv{E} = \emptyset$:
 \begin{alltt}
@@
 
-Notice that, for any CCS expression, the set of free and bound
-variables may not be disjoint, e.g. $X + \recu X E$.
+Note that, in CCS expression, the set of free and bound
+variables need not be disjoint, e.g.\ in  $X + \recu X E$.
 More importantly, when going
 from a CCS expression to its sub-expressions, the set of free
-variables may increase, while the set of bound variables always
+variables may increase, while the set of bound variables may
 decrease. For instance, $\fv{\recu X (\mu.X)} = \emptyset$, while
-$\fv{\mu.X} = \{X\}$. This property of $\fv{\cdot}$ brings greatly
-difficulities when doing proofs on CCS transitions. As an evidence,
+$\fv{\mu.X} = \{X\}$. This property of $\fv{\cdot}$ brings some
+difficulities when doing proofs about CCS transitions. As an evidence,
 we prove the following fundamental result about $\fv{\cdot}$:
@@
 \begin{proof}
-Milner said it can be proven by ``an easy action
-induction''~\cite{milner1990operational}. However this is not true at all.
-%
-To see things more clearly, we try to prove a stronger result,
-i.e. the set of free variables decreases through derivations:
+% Milner said it can be proven by ``an easy action
+% induction''~\cite{milner1990operational}. However this is not true at all.
+% %
+%To see things more clearly, 
+We  prove a stronger result,
+i.e.,  the set of free variables decreases through derivations:
 \begin{alltt}
@@
 of the following \emph{induction principle} generated together with SOS
-rules: (which essentially says \hl{that} \HOLinline{\HOLConst{TRANS}} is the smallest relation
-satisfying SOS rules.)
+rules (which essentially says \hl{that} \HOLinline{\HOLConst{TRANS}} is the smallest relation
+satisfying SOS rules):
 \begin{alltt}
@@
 $X$ under this specific $P$, by Modus Ponens (MP) the original proof completes.
-\hl{\emph{This is the whole idea of action induction.}}
+This is the essence of action induction.
 Now the original goal can be reduced to several conjunct
@@
 $\fv{E_1} \subseteq \fv{E} \Longrightarrow
-\fv{E_1} \subseteq \fv{E + E'}$, but this obviously holds: $\fv{E}
+\fv{E_1} \subseteq \fv{E + E'}$, which holds as $\fv{E}
 \subseteq \fv{E + E'} = \fv{E} \cup \fv{E'}$. Eventually we have only
@@
 this is indeed the consequence of action induction on the Recursion.
-Here the problem is, we know nothing about
+Here the problem is that we know nothing about
 \HOLinline{\HOLConst{FV}\\\;\ensuremath{(}\ensuremath{[}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\HOLFreeVar{E}\ensuremath{)}}.
 To further proceed, we need to prove
-some other (easier) lemmas. First, the next lemma can be easily proven
-by doing induction on $E$ and basic set-theoretic facts:
+some other (easier) lemmas. First, the next lemma can be  proven
+by  induction on $E$ and a few basic set-theoretic facts:
 \begin{alltt}
@@
 \end{alltt}
-Then, if we took $E' = \recu X E$ in the above lemma, we get
+Now, if we take $E' = \recu X E$ in the above lemma, we get
 \HOLinline{\HOLConst{FV}\\\;\ensuremath{(}\ensuremath{[}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\HOLSymConst{\HOLTokenSubset{}}\\\;\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}\\\;\HOLConst{FV}\\\;\ensuremath{(}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{)}} $=$ \HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLConst{DELETE}\\\;\HOLFreeVar{X}\ensuremath{)}} $=$
@@
 \end{alltt}
-Now we can enrich the assumptions of the current proof goal with above
-lemma, then obtain \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} by
+Thus we can enrich the assumptions of the current proof goal with above
+lemma, and obtain \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} 
 from the transitivity of $\subseteq$:
@@
 \end{alltt}
-Now we try proof by contradiction (\emph{reductio ad absurdum}): if
+Now we try the  proof by contradiction (\emph{reductio ad absurdum}): if
 the goal does not hold, i.e.
@@
 bound in the form of $\recu X E$. In fact, the following lemma can be
-easily proven by induction on $E$:
+ proven by induction on $E$:
 \begin{alltt}
@@
 Without the above result, the proof of Milner's ``unique solution of
-equations'' theorem (for $\sim$) cannot complete. Comparing with the
-above proof, the proof of the similar result for bound variables is much easier:
+equations'' theorem (for $\sim$) cannot complete. Compared with the
+above proof, the proof of the similar result for bound variables is easier:
 \begin{proposition}
@@
 \end{alltt}
-Notice the difference with the proof of Prop.~\ref{prop:transFV}: now
+Note the difference with the proof of Prop.~\ref{prop:transFV}: now
 we have \texttt{INSERT} in place of \texttt{DELETE}. Then, we directly
@@
 \end{alltt}
-But this is an easy goal, due to the following lemma which can be
-easily proven by induction on $E$:
+This is an easy goal, due to the following lemma which is
+ proved by induction on $E$:
 \begin{alltt}
@@
     the right side equals to \HOLinline{\HOLConst{BV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}\\\;\ensuremath{(}\HOLFreeVar{X}\\\;\HOLConst{INSERT}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}} $=$
-    \HOLinline{\HOLFreeVar{X}\\\;\HOLConst{INSERT}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}}. The proof easily completes.
+    \HOLinline{\HOLFreeVar{X}\\\;\HOLConst{INSERT}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}}. Thus
+the    proof can 
+ be completed.
 \end{proof}
@@
 
-There are two ways to represent (and actually do) the \multivariate
+There are two ways to represent  the \multivariate
 substitution of $E\{\til P/\til X\}$ which substitutes each possibly
@@
 \HOLinline{\HOLConst{CCS_Subst}}; (2) defining a new \multivariate substitution
-function. In any case, we (reasonably) assume that all $X_i$ are
-distinct with each other. On the other hand, there is the syntactic
-possibility that $\til P$ again contains variables from $\til X$, thus
+function.
+% In any case, we (reasonably) assume that all $X_i$ are
+%distinct with each other. 
+Note that  there is the
+possibility that $\til P$   syntactically  again contains variables from $\til X$, thus
 different orders of iterated substitutions may lead to different results.
-In fact, there are all kinds of issues with
-substitutions and applying them to term-like structures. To obtain the
-maximal flexibility with mimimal efforts, we defined
+% In fact, there are all kinds of issues with
+% substitutions and applying them to term-like structures. 
+To obtain the
+maximal flexibility with a reduced effort, we defined
 a \multivariate version of \HOLinline{\HOLConst{CCS_Subst}}
@@
 map \HOLinline{\HOLFreeVar{fm}} of type \HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}} and a CCS expression,
-then it returns another CCS expression in which
+and then returns another CCS expression in which
 all occurrences of variables in the \HOLinline{\HOLFreeVar{fm}}'s domain are substituted with
@@
 variable-parallel thus order-independent. For most CCS operators it
-just recursively call itself on subterms of current input. The only
-interesting cases are at agent variables and recursion operators:
+just recursively calls itself on subterms. The only
+interesting cases are at agent variables and recursion:
 \begin{alltt}
@@
 \end{alltt}
-Notice that, the variable substitution only happens on free
+Note that the variable substitution only occurs on free
 variables. In the case of $\recu X E$: if $X$ (a bound variable) is in
-the domain of \HOLinline{\HOLFreeVar{fm}}, \HOLinline{\HOLConst{CCS_SUBST}} must further does the
-substitution on $E$ using a reduce map with $X$, so that all
-occurences of agent variable $X$ in $E$ are correctly bypassed. On the
-other hand, since \HOLinline{\HOLConst{CCS_SUBST}} only walks each subterm
-once, even \HOLinline{\HOLFreeVar{Ps}} contains free variables, these variables will
-not be further substituted. Thus the process is indeed
-order-independent. Below we present some key lemmas about
-\HOLinline{\HOLConst{CCS_SUBST}} \emph{without proofs}:
+the domain of \HOLinline{\HOLFreeVar{fm}}, \HOLinline{\HOLConst{CCS_SUBST}} must continue the
+substitution on $E$ using a reduced map~--- without $X$~--- so that all
+occurences of $X$ in $E$ are correctly bypassed. Since
+ since \HOLinline{\HOLConst{CCS_SUBST}} only runs
+once on each  subterm, the possible free variables in  \HOLinline{\HOLFreeVar{Ps}} are never
+ substituted. 
+% Thus the process is indeed
+% order-independent. 
+Below we present some key lemmas about
+\HOLinline{\HOLConst{CCS_SUBST}}, omitting the  proofs:
 
 \begin{lemma}[\texttt{CCS_SUBST_elim}]
-If the free variables of $E$ is disjoint with \HOLinline{\HOLFreeVar{Xs}}, a
+If the set of  free variables of $E$ is disjoint from \HOLinline{\HOLFreeVar{Xs}}, a
 substitution of \HOLinline{\HOLFreeVar{Xs}} in $E$ does not change $E$:
@@
 \begin{lemma}[\texttt{BV_SUBSET_BIGUNION}]
-The bound variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}} have
+The bound variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}} contains
 at most the union of all bound variables from $E$ and \HOLinline{\HOLFreeVar{Ps}}.
@@
 \begin{lemma}[\texttt{FV_SUBSET_BIGUNION_PRO}]
-The free variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}} have
+The free variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}} contain
 at most the union of all free variables from $E$ and \HOLinline{\HOLFreeVar{Ps}},
@@
 
-It is worth noting that, in the above lemmas, the condition
+In the above lemmas, the condition
 \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}} (the bound
 variables of $E$ and the free substitution variables are disjoint) is
-not necessary but makes some proofs (much) easier. As these lemmas are
-used in the rest work, these disjointness conditions eventually
-are propagated everywhere. (We believe that they can be
-all eliminated in the future.)
+not necessary but makes some proofs (much) easier. 
+As these lemmas are
+used in the rest work, such disjointness conditions 
+are propagated everywhere. 
+% (We believe that they can be
+% all eliminated in the future.)
 
@@
 \HOLinline{\HOLConst{SG}} (strongly-guarded contexts) and \HOLinline{\HOLConst{SEQ}} (sequential
-contexts), are all defined inductively, i.e.~they are built from some ``holes''
-in a bottom-up way.
+contexts), are all defined inductively, i.e.~they are built bottom-up starting from some ``holes''.
 For instance, \HOLinline{\HOLConst{WG}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\\\;\HOLSymConst{\ensuremath{\mid}}\\\;\HOLFreeVar{P}\ensuremath{)}}
-holds because \HOLinline{\HOLConst{WG}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\ensuremath{)}} holds on the ground,
+holds because
+\HOLinline{\HOLConst{WG}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\ensuremath{)}}
+holds on the ground,
+\finish{what does it mean ``on the ground''?} 
 and for any agent variable $X$, we have (by $\beta$-reduction)
@@
 It is possible to inductively assert multivariate contexts and their
-guarded variants, but this is not easy as we need to carefully exclude the cases where
-free variables occur inside any recusion operator (c.f. the footnote
-at the beginning of Section~\ref{ss:SysEq}. A more elegant (and less
-error-prone) solution is to define \multivariate contexts (and variants) upon the
-existing \univariate definitions. This is indeed our choice.
-
+guarded variants, but care is needed as  we need to exclude the cases where
+free variables occur inside a recusion operator. A more elegant
+ solution is to define \multivariate contexts (and variants) upon the
+existing \univariate definitions, which is the approach we have followed.
 For instance, to see the weak guardedness of $a.X + b.X + c.Y$, it is
@@
 resulting term as a $\lambda$-function, then all $\lambda$-functions
-derived from the original expression in this way must satisfy
+derived from the original expression  must satisfy
 \HOLinline{\HOLConst{WG}}:

### 2019-09-14 ic-journal/related.tex
text

@@
 %strong, weak and rooted bisimilarity were proved.
-Her work is
-  the working basis of ours. However, the differences are substantial, especially in the way of defining
+\hlD{Her work has been a
+ basis for ours.} However, the differences are substantial, especially in the way of defining
 bisimilarities. We greatly benefited from features and standard
@@
 name binders \cite{bengtson2007completeness,parrow2009formalising}.
-\hl{Jesper Bengtson's PhD thesis}~\cite{bengtson2010formalising}
-contains more details about this work. For CCS, 
+\hl{Details are found in   Bengtson's PhD thesis}~\cite{bengtson2010formalising}. For CCS, 
 he has formalized basic properties for strong/weak equivalence (congruence, basic
- algebraic laws), for a  and observational
-congruence, however the CCS syntax doesn't have constants
-(or recursion operator), using replication in place of recursion.
+ algebraic laws); \hlD{however the CCS syntax doesn't have constants
+(or recursion operator), using replication in place of recursion.}
 % The formalisation effort has then been continued 

### 2019-09-14 ic-journal/conclusions.tex
Merged changes in conclusions.tex

@@
 proof, checking all details would be long and \hl{error-prone},
-\hl{especially in cases in which proofs are similar to each other or
-  when there are a long case analysis to be carried out.}
+\hl{especially in cases where the proofs are similar to each other or
+  when there are long case analyses to be carried out.}
 A theorem-prover formalisation is in this respect  helpful and reassuring.

### 2019-09-14 ic-journal/multivariate.tex
Merged changes in multivariate.tex (with minor fixes)

@@
 representation of CCS equations (expressions, contexts).
-\hlD{In the} univariate formalisation, $\lambda$-functions (of type
+\hlD{In the} \univariate formalisation, $\lambda$-functions (of type
 $CCS\rightarrow CCS$) are used to represent univariate CCS
@@
 
-\finish{too many changes below to highlight them}
-
 Recall the beginning of Section~\ref{s:eq},
@@
 Furthermore, $E$ is a process, written \HOLinline{\HOLConst{IS_PROC} \HOLFreeVar{E}}, if
-it does not  contains free variables, i.e. $\fv{E} = \emptyset$:
+\hl{it does not contain any free variable}, i.e. $\fv{E} = \emptyset$:
 \begin{alltt}
    \HOLConst{IS_PROC} \HOLFreeVar{E} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\HOLTokenEmpty{}}\hfill{[IS_PROC_def]}
+\end{alltt}
+And a list of CCS processes can be asserted by \HOLinline{\HOLConst{ALL_PROC}} defined upon \HOLinline{\HOLConst{IS_PROC}}:
+\begin{alltt}
+   \HOLTokenTurnstile{} \HOLConst{ALL_PROC} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{EVERY} \HOLConst{IS_PROC} \HOLFreeVar{Es}\hfill{[ALL_PROC_def]}
 \end{alltt}
@@
 from a CCS expression to its sub-expressions, the set of free
-variables may increase, while the set of bound variables may
-decrease. For instance, $\fv{\recu X (\mu.X)} = \emptyset$, while
+variables may increase, while the set of bound variables \hl{either
+remains the same or decreases}. For instance, $\fv{\recu X (\mu.X)} = \emptyset$, while
 $\fv{\mu.X} = \{X\}$. This property of $\fv{\cdot}$ brings some
@@
 Thus we can enrich the assumptions of the current proof goal with above
-lemma, and obtain \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} 
-from the transitivity of $\subseteq$:
+lemma, and obtain \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} by the transitivity of $\subseteq$:
 \begin{alltt}
@@
 Knowing \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} we cannot prove \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}.
-However, if we knew \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, then \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\ensuremath{=}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, and
+However, if we knew \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, then \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\ensuremath{=}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, and \hl{then}
 \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}, no matter if \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E}} or not, and the proof
@@
 substitution on $E$ using a reduced map~--- without $X$~--- so that all
-occurences of $X$ in $E$ are correctly bypassed. Since
- since \HOLinline{\HOLConst{CCS_SUBST}} only runs
+occurences of $X$ in $E$ are correctly bypassed.
+\hl{Since} \HOLinline{\HOLConst{CCS_SUBST}} only runs
 once on each subterm, the possible free variables in  \HOLinline{\HOLFreeVar{Ps}} are never
@@
 Below we present some key lemmas about
-\HOLinline{\HOLConst{CCS_SUBST}}, omitting the  proofs:
+\HOLinline{\HOLConst{CCS_SUBST}}, omitting the proofs:\footnote{Hereafter,
+  some new logical constants from HOL's \texttt{pred_set}
+and \texttt{list} theories are used (c.f.~\cite{holdesc} for more
+details.): \HOLinline{\HOLConst{DISJOINT}} denotes set disjointness;
+``\HOLinline{\HOLConst{set}\\\;\HOLFreeVar{Xs}}'' is the set converted from the list \HOLinline{\HOLFreeVar{Xs}};
+\HOLinline{\HOLConst{ALL_DISTINCT}} says
+all elements of a list are distinct with each other; \HOLinline{\HOLConst{MAP}} is
+the mapping function from one list to another; \HOLinline{\HOLConst{EVERY}} means
+each element of a list satisfies a predicate; \HOLinline{\HOLConst{ZIP}} creates a
+new list from two lists of the same length, and each element of the new list is a pair of
+elements, each from one of the old lists.}
 
 \begin{lemma}[\texttt{CCS_SUBST_elim}]
-If the set of  free variables of $E$ is disjoint from \HOLinline{\HOLFreeVar{Xs}}, a
+If the free variables of $E$ is disjoint with \HOLinline{\HOLFreeVar{Xs}}, a
 substitution of \HOLinline{\HOLFreeVar{Xs}} in $E$ does not change $E$:
@@
 \begin{lemma}[\texttt{CCS_SUBST_self}]
-Substituting each free variable $X$ in $E$ to \HOLinline{\HOLConst{var}\\\;\HOLFreeVar{X}} (itself)
-does not change $E$:
+  Substituting each free variable $X$ % of \HOLinline{\HOLFreeVar{Xs}}
+  in $E$ to \HOLinline{\HOLConst{var}\\\;\HOLFreeVar{X}} (itself) does not change $E$:
 \begin{alltt}
@@
 \begin{lemma}[\texttt{CCS_SUBST_nested}]
-Under certain conditions, two nested substitutions can be
+Under certain conditions \hl{(to get rid of substitution orders)}, two nested substitutions can be
 converted into a single substitution where the targets are substituted first:
@@
 The next three lemmas show the relative correctness of \texttt{CCS\_SUBST}
-w.r.t. \texttt{CCS\_Subst}:
-\begin{lemma}[\texttt{CCS_SUBST_SING}]
+w.r.t.~\texttt{CCS\_Subst}:
+\begin{lemma}[\texttt{CCS_SUBST_sing}]
   If there is only one single variable $X$ in the map (with the target
@@
 \begin{lemma}[\texttt{BV_SUBSET_BIGUNION}]
-The bound variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}} contains
+The bound variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}} have
 at most the union of all bound variables from $E$ and \HOLinline{\HOLFreeVar{Ps}}.
@@
 \begin{lemma}[\texttt{FV_SUBSET_BIGUNION_PRO}]
-The free variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}} contain
+The free variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}} have
 at most the union of all free variables from $E$ and \HOLinline{\HOLFreeVar{Ps}},
@@
 \HOLinline{\HOLConst{CONTEXT}}
-(contexts/expressions), \HOLinline{\HOLConst{WG}} (weak-guarded contexts),
-\HOLinline{\HOLConst{SG}} (strongly-guarded contexts) and \HOLinline{\HOLConst{SEQ}} (sequential
-contexts), are all defined inductively, i.e.~they are built bottom-up starting from some ``holes''.
-For instance, \HOLinline{\HOLConst{WG}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\\\;\HOLSymConst{\ensuremath{\mid}}\\\;\HOLFreeVar{P}\ensuremath{)}}
-holds because
-\HOLinline{\HOLConst{WG}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\ensuremath{)}}
-holds on the ground,
-\finish{what does it mean ``on the ground''?} 
-and for any agent variable $X$, we have (by $\beta$-reduction)
+(contexts/expressions), \HOLinline{\HOLConst{WG}} (weak guarded contexts),
+\HOLinline{\HOLConst{SG}} (strongly guarded contexts) and \HOLinline{\HOLConst{SEQ}} (sequential
+contexts), are all defined inductively, i.e.~they are built from some ``holes''
+in a bottom-up way.
+For instance, \HOLinline{\HOLConst{WG}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\\\;\HOLSymConst{\ensuremath{\mid}}\\\;\HOLFreeVar{P}\ensuremath{)}}
+holds because \HOLinline{\HOLConst{WG}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\ensuremath{)}}
+holds \hl{as a base case of the inductive definition of} \HOLinline{\HOLConst{WG}}:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a}.
+\HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\ensuremath{)}\hfill{[WG1]}
+\end{alltt}
+\hl{For} any agent variable $X$, we have \hl{by $\beta$-reduction:}
 \HOLinline{\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{P}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{var}\\\;\HOLFreeVar{X}\ensuremath{)}\\\;\HOLSymConst{\ensuremath{=}}\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{P}} (or ``$l.X + P$'' in textbook
@@
 existing \univariate definitions, which is the approach we have followed.
-For instance, to see the weak guardedness of $a.X + b.X + c.Y$, it is
+For \hl{example}, to see the weak guardedness of $a.X + b.X + c.Y$, it is
 natural to focus on each (free) variable: if we substitute each
 occurrence of just one variable, say $X$, with a ``hole'' and see the
-resulting term as a $\lambda$-function, then all $\lambda$-functions
-derived from the original expression  must satisfy
-\HOLinline{\HOLConst{WG}}:
+resulting term as a $\lambda$-function, then all such $\lambda$-functions
+must satisfy \HOLinline{\HOLConst{WG}}, i.e.~the following results hold:
 \begin{alltt}
@@
 \end{alltt}
-Notice that, \HOLinline{\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{Y}\\\;\HOLSymConst{\ensuremath{=}}\\\;\ensuremath{[}\HOLFreeVar{t}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\ensuremath{(}\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{Y}\ensuremath{)}}.
+Also note that \HOLinline{\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{Y}\\\;\HOLSymConst{\ensuremath{=}}\\\;\ensuremath{[}\HOLFreeVar{t}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\ensuremath{(}\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{Y}\ensuremath{)}}
+can be expressed as a \univariate \hl{substitution of the original term.}
 This idea leads to the following definitions:
@@
 \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Xs}
+\ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Xs}\hfill{[weakly_guarded_def]}
 \end{alltt}
+Notice that, the above definitions take an extra list of variables \HOLinline{\HOLFreeVar{Xs}} and
+assert the CCS expression \HOLinline{\HOLFreeVar{E}} with respect to this list. This
+allows us to formalise the concepts of contexts and guardedness
+independently of \HOLinline{\HOLConst{FV}}.
+Then \HOLinline{\HOLConst{weakly_guarded}\\\;\ensuremath{(}\HOLConst{SET_TO_LIST}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\ensuremath{)}\\\;\HOLFreeVar{E}} can
+be used assert that $E$ is weakly guarded w.r.t.~all its free
+variables.\footnote{Here \HOLinline{\HOLConst{SET_TO_LIST}} converts a finite set
+  to a list of the same elements. It turns out that, we never need this, because
+  in all unique-solution theorems a list of variables \HOLinline{\HOLFreeVar{Xs}} is fixed and
+  then all equations are required to contain free variables up to
+  \HOLinline{\HOLFreeVar{Xs}}. Thus our choices in these definitions are optimal.}
+(The strong guardedness and sequentiality can also be defined similarily
+when needed, using
+their \univariate companions (\texttt{SG} and \texttt{SEQ}).)
 
+The most important property of contexts are that, strong bisimilarity
+and other (pre)congruence relations are preserved by contexts, e.g.
+\begin{lemma}[\texttt{STRONG_EQUIV_subst_context}]
+If two tuples of processes $\til P$ and $\til Q$ are strongly
+bisimilar\footnote{Hereafter, HOL terms like \HOLinline{\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenStrongEQ}\\\;\HOLFreeVar{Qs}}
+  means that, two list of CCS processes are componentwise
+  (strongly) bisimilar. The same notation $\sim$ has been overloaded.}
+for any context $E$ with the possible occurrences of variables $\til
+X$ (same length as $\til P$ and $\til Q$), $E\{\til P/\til X\}$ and
+$E\{\til Q/\til X\}$ are also strongly bisimilar:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{Qs} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
+\HOLConst{context} \HOLFreeVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\HOLTokenStrongEQ} \ensuremath{[}\HOLFreeVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E}
+\end{alltt}
+\end{lemma}
+The similar properties also hold if $\sim$ is replaced with rooted
+bisimilarity ($\rapprox$) or rooted contraction ($\rcontr$). (It does
+not hold for weak bisimilarity $\wb$ and the contraction preorder $\mcontrBIS$.)
+
+Another important property of contexts is their composability: if we
+substitute some free variables in a context for some other contexts, the
+resulting term is still a context (w.r.t.~the same set of variables):
 \begin{alltt}
@@
 
+With the formal definitions of \multivariate substitution and
+\multivariate (weakly-guarded) contexts, now we are ready to formally
+define \multivariate CCS equations/contractions and their (unique)
+solutions. Consider a system of equation $\{X_i = E_i\}_{i\in I}$
+(Def.~\ref{def:equation}), or its expanded form (here we suppose $I = [1,n]
+\in \mathbb{N}$, i.e.~a finite list):
+\begin{equation*}
+  \begin{cases}
+    &X_1 = E_1[\til X] \\
+    &X_2 = E_2[\til X] \\
+    & \vdots \\
+    &X_n = E_n[\til X]
+  \end{cases}
+\end{equation*}
+Consider its two essential ingredients:
+\begin{itemize}
+\item $\til X = (X_1, X_2, \ldots, X_n)$: a list of equation variables;
+\item $\til E = (E_1, E_2, \ldots, E_n)$: a list of CCS contexts 
+  with possible occurrences of free variables in $\til X$.
+\end{itemize}
+Obviously the two lists must have the same length. The all
+distinctness of $\til X$ is not really necessary but is very
+reasonable. Furthermore, we should assume $\til E$ does not contain
+any other free variables not in $\til X$, as Milner's unique-solution
+theorems also require the same condition.\footnote{One may think that,
+  if all other (i.e.~not in $\til X$) free variables in $\til E$ have
+  the same functionalities as $\nil$ as they are not to be
+  substituted, then all versions of unique-solution
+  theorems should still hold. However this is not the case for at
+  least Milner's Theorem~\ref{t:Mil89s1} as we shall explain.}
+
+In this project, the only optional restriction we added here is that, for each
+$E_i$ the set of its bound variables must be \emph{disjoint} with $\til
+X$. This restriction is actually aligned with literature based on
+process constants as one should never use the same name for equation
+variables and constants. However, we believe this restriction can be
+removed in the future.~\footnote{Essentially, this restriction is due
+  to the proof difficulties in some early lemmas about \multivariate
+  substitutions where \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}}
+  unnecessarily appears in the antecedents. Removing it requires a
+  more complex proof but is indeed possible. (We have succeeded in
+  fixing many such lemmas.) Once all these lemmas are
+fixed, the final unique-solution theorems also do not need this
+disjointness restriction.} Putting all together, below is the fomal
+definition of \multivariate CCS equation:
 \begin{alltt}
    \HOLTokenTurnstile{} \HOLConst{CCS_equation} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenEquiv{}}
-   \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
+      \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}}
+      \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
 \HOLConst{FV} \HOLBoundVar{e} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
-\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Es}
+\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Es}\hfill{[CCS_equation_def]}
+\end{alltt}
 
+Now consider (formally) what is a solution $\til P$ of CCS equation. First of
+all, the definition should be parametrized on a binary CCS
+relation $\R$ such as $\sim$ and $\rcontr$, so that the single definition
+could be used for the solution of all kind of CCS
+equations/contractions. Then, of course ${\til P} \ \R\  {\til E}\{\til
+P/\til X\}$ must hold, i.e.
+\begin{equation*}
+  \begin{cases}
+    &P_1 \ \R\ E_1\{\til P/\til X\} \\
+    &P_2 \ \R\ E_2\{\til P/\til X\} \\
+    & \vdots \\
+    &P_n \ \R\ E_n\{\til P/\til X\}
+  \end{cases}
+\end{equation*}
+Furthermore, each $P_i$ should be pure process, i.e. having no free
+variable. This is usually implicitly assumed in the literature but is
+actually a \emph{must} to complete some unique-solution proofs.
+At last, like the case of CCS equations, we must assume that, the
+set of bound variables (i.e. process constants) must be disjoint with
+$\til X$. (This disjointness requirement is optional but makes many proofs much
+easier, and it can be removed in the future.) Putting all together,
+below is the formal definition of a solution of \multivariate CCS
+equations:\footnote{If $R$ is a binary relation of CCS processes,
+  \HOLinline{\HOLConst{LIST_REL}\\\;\HOLFreeVar{R}} is the same binary relation but for lists of
+  CCS processes. Furthermore, \HOLinline{\HOLConst{LIST_REL}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{A}\\\;\HOLFreeVar{B}} implicitly
+  implies that the two lists $A$ and $B$ have the same length.}
+\begin{alltt}
    \HOLTokenTurnstile{} \HOLConst{CCS_solution} \HOLFreeVar{R} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenEquiv{}}
@@
 \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-   \HOLConst{LIST_REL} \HOLFreeVar{R} \HOLFreeVar{Ps} \ensuremath{(}\HOLConst{MAP} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{Es}\ensuremath{)}
+      \HOLConst{LIST_REL} \HOLFreeVar{R} \HOLFreeVar{Ps} \ensuremath{(}\HOLConst{MAP} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{Es}\ensuremath{)}\hfill{[CCS_solution_def]}
 \end{alltt}

### 2019-09-15 ic-journal/formal.tex
Minor changes.

@@
 
-HOL is a formal system of typed logical terms. The types are expressions that denote sets (in the
+\hl{HOL is a formal system of typed logical terms. The types are expressions that denote sets (in the
 universe $\mathcal{U}$). HOL's type system is much simpler than those
-based on dependent types and other type theories. There are four kinds of types in the HOL
+based on dependent types and other type theories.} There are four kinds of types in the HOL
 logic, as illustrated in Fig. \ref{fig:hol-types} for its BNF
@@
 of theorems are correct, then any proof which successfully completes must
-be correct.
+be correct. \hl{This is also the case here: SOS rules of CCS are
+\emph{not} axioms but consequences of an inductive relation.}
 

### 2019-09-15 ic-journal/intro.tex
Minor changes.

@@
 
-\finish{below: ``In contrast to most literature,...'' we need to
-  support this with references}
+We first consider the case of a single equation (or contraction),
+that we call the \univariate case, then consider the \multivariate
+  case, where  more than one equation
+  (or contraction) \hl{with multiple equation variables is considered.}
+The \univariate theorems use
+$\lambda$-functions to present CCS equations,
+while the \multivariate versions require a
+more careful and delicate treatment of CCS
+expressions with \hl{multiple} variables and substitutions acting on them.
 
-\hlD{We first consider the case of a single equation (or contraction),
-that we call the univariate case, then consider the multivariate
-  case, where  more than one equation
-  (or contraction) is possible.
-The univariate  theorems use
-$\lambda$-functions to present  CCS equations,
-while the multivariate versions require a
-more careful and delicate treatment of 
-expressions with several 
-variables and substitutions acting on them.
-In contrast to most literature, we have adopted the same
+\hl{In contrast to modern literature, e.g.}~\cite{Gorrieri:2015jt},
+\hl{we have followed Milner's original approach}~\cite{milner1990operational} and adopted the same
 type for both CCS equations and processes: those undefined constants
@@
 \emph{process} is a CCS term without equation variables. 
-This allows us a smoother move from the univariate case to the multivariate
-one. See} Section~\ref{sec:multivariate} for  details.
+This allows us a smoother move from the \univariate case to the \multivariate
+one. See Section~\ref{sec:multivariate} for  details.
 
@@
 unique-solution result for rooted bisimilarity.
-Section~\ref{s:for} highlights our formalisation in HOL4 \hlD{for the
-univariate case.}
-Section~\ref{sec:multivariate} \hlD{describes the move to the
-  multivariate case}. 
+Section~\ref{s:for} highlights our formalisation in HOL4 for the
+\univariate case.
+Section~\ref{sec:multivariate} describes the \hl{extension} to the
+  \multivariate case.
 Finally,  Section~\ref{s:rel} and \ref{s:concl} discuss related work,

### 2019-09-15 ic-journal/multivariate.tex
Minor changes.

@@
 
-In this section,  \hlD{we discuss the formalisation of the general}  \multivariate
+In this section,  \hlD{we discuss the formalisation of the} \multivariate
 cases of Milner's ``unique solution of equations (for $\sim$)''
@@
 contractions'' (Theorem~\ref{t:rcontraBisimulationU}).
+\hlC{This formalisation only supports finitely many
+  equations/contractions and equation variables.\footnote{The original theorems
+hold for even (uncountably) infinite equations and equation variables.}}
 We chose these two theorems because they both depend on the same
 concept of ``weakly guarded contexts'', and Lemma~\ref{lem:milner313}.
-%\hl{This work is entirely new} after~\cite{EPTCS276.10}.
-\hlD{The work is an extension of the univariate case
+\hlD{The work is an extension of the univariate case}~\cite{EPTCS276.10}
  in the sense that neither the CCS datatype nor
-the SOS rules need to be changed.}
+the SOS rules need to be changed.
 
@@
 variables in $E_i\{\til P/\til X\}$ would be the \emph{syntactic substitution} of
-each occurrence of $X_i$ in $E_i$ with the corresponding $P_i$. In
-either cases the \emph{disjointness} between equation variables and
+each occurrence of $X_i$ in $E_i$ with the corresponding $P_i$.
+In either cases the \emph{disjointness} between equation variables and
 agent variables is syntactically
@@
 
-\hlD{In this project, we have  followed} Milner~\cite{Mil89}, thus using the same alphabet for
-both agent variables and equation variables. 
-\hlD{This has allowed a large reuse of the univariate formalisation. For instance, 
+\hlD{In this project, we have followed} Milner~\cite{Mil89}, using the
+same alphabet for both agent variables and equation variables.
+This has allowed a large reuse of the \univariate formalisation. \hl{For instance, 
 the variable
@@
 used for substituting eqaution variables.
-However, a lot of care is needed in 
-in the proofs of  many
+However, a lot of care is needed in the proofs of many
 fundamental lemmas, mostly due to the variable capture issues between
-equation variables and agent variables.
-}
+equation variables and agent variables.}
 
@@
 \begin{proof}
-% Milner said it can be proven by ``an easy action
-% induction''~\cite{milner1990operational}. However this is not true at all.
-% %
-%To see things more clearly, 
 We  prove a stronger result,
@@
 
+\hlC{Milner said it can be proved by ``an easy action
+induction''}~\cite{milner1990operational}.
 From HOL's viewpoint, the so-called ``action induction'' is actually a higher-order \hl{application}

### 2019-09-15 ic-journal/part2.tex
Minor changes.

@@
 substituted for $X$:
-\begin{lemma}[Lemma 3.13 of \cite{Mil89}, the univariate version]
+\begin{lemma}[\texttt{STRONG_UNIQUE_SOLUTION_LEMMA} (Lemma 3.13 of \cite{Mil89}, the univariate version)]
 \label{lem:313}
@@
 \begin{alltt}
-\hfill{[STRONG_UNIQUE_SOLUTION_LEMMA]}
 \HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}}
@@
 % ``unique solution of equations'':
-\begin{theorem}[Proposition 3.14 of \cite{Mil89}]
+\begin{theorem}[\texttt{STRONG_UNIQUE_SOLUTION} (Proposition 3.14 of~\cite{Mil89})]
 Suppose the expression $E$ contains at most the variable $X$, and let $X$ be weakly
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{Q}\hfill{[STRONG_UNIQUE_SOLUTION]}
+\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{Q}
 \end{alltt}
@@
 \paragraph{Weak bisimilarity}
-Milner's book \cite{Mil89} contains only two ``unique solutions of
+Milner's book~\cite{Mil89} contains only two ``unique solutions of
 equations'' theorems, one for strong equivalence, the other for
@@
 % Now we're ready to state and prove the following lemma:
-\begin{lemma}
+\begin{lemma}[\texttt{WEAK_UNIQUE_SOLUTION_LEMMA}]
 If the variable $X$ is strongly guarded and sequential in $G$, and
@@
 \HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
-\HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}\hfill{[WEAK_UNIQUE_SOLUTION_LEMMA]}
+\HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}
 \end{alltt}
@@
 We can then derive the target theorem:
-\begin{theorem}{(Unique solution of equations for weak bisimilarity)}
+\begin{theorem}[\texttt{WEAK_UNIQUE_SOLUTION}]
 Let $E$ be guarded and sequential expressions, and let $P \wb
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{Q}\hfill{[WEAK_UNIQUE_SOLUTION]}
+\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{Q}
 \end{alltt}
@@
 
-\begin{lemma}
+\begin{lemma}[\texttt{OBS_CONGR_BY_WEAK_BISIM}]
 % To prove two processes $E$ and $E'$  observationally congruent, it is
@@
 \HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{E\sp{\prime}}\hfill{[OBS_CONGR_BY_WEAK_BISIM]}
+       \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{E\sp{\prime}}
 \end{alltt}
@@
  we  directly construct the appropriate bisimulation relations.
-\begin{lemma}
+\begin{lemma}[\texttt{OBS_UNIQUE_SOLUTION_LEMMA}]
 If the variable $X$ is strongly guarded and sequential in $G$, and
@@
 \HOLConst{SEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
-\HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}\hfill{[OBS_UNIQUE_SOLUTION_LEMMA]}
+\HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}
 \end{alltt}
@@
 
-\begin{theorem}{(Unique solution of equations for observational congruence)}
+\begin{theorem}[\texttt{OBS_UNIQUE_SOLUTION}]
 Let $E$ be guarded and sequential expressions, and let $P \rapprox
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Q}\hfill{[OBS_UNIQUE_SOLUTION]}
+\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Q}
 \end{alltt}
@@
      \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.
-      \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x}.
-\HOLBoundVar{P} \HOLBoundVar{x} \ensuremath{[}\ensuremath{]} \HOLBoundVar{x}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z}.
+         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x}. \HOLBoundVar{P} \HOLBoundVar{x} \ensuremath{[}\ensuremath{]} \HOLBoundVar{x}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z}.
 \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLBoundVar{x} \ensuremath{(}\HOLBoundVar{h}\HOLSymConst{::}\HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{z}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
@@
 \begin{alltt}
-\HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{L\sb{\mathrm{1}}} \HOLBoundVar{L\sb{\mathrm{2}}}.
+   \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLSymConst{\HOLTokenDefEquality{}}
+     \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{L\sb{\mathrm{1}}} \HOLBoundVar{L\sb{\mathrm{2}}}.
 \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} \ensuremath{[}\HOLFreeVar{u}\ensuremath{]} \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{2}}}\hfill{[UNIQUE_LABEL_def]}
@@
 
-Now the formalised version of Lemma~\ref{l:uptocon}:
-\hfill{\texttt{[UNIQUE_SOLUTION_OF_CONTRACTIONS_LEMMA]}\vspace{-1em}
+Now the formal version of Lemma~\ref{l:uptocon} (\texttt{UNIQUE_SOLUTION_OF_CONTRACTIONS_LEMMA}):
 \begin{alltt}
-\begin{small}
 \HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E}.
@@
 \HOLConst{GCONTEXT} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{C\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{EPS}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C} \HOLFreeVar{Q}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C\sp{\prime}} \HOLFreeVar{Q}\ensuremath{)}
-\end{small}
 \end{alltt}
-\vspace{-1em}
+
 Traces are actually used in the proof of above lemma via 
-the following ``unfolding lemma'':\vspace{-1em}
+the following lemma (\texttt{unfolding_lemma4}):
 \begin{alltt}
-\begin{small}
 \HOLTokenTurnstile{} \HOLConst{GCONTEXT} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}\ensuremath{)} \HOLFreeVar{P}\ensuremath{)} \HOLFreeVar{xs} \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{xs} \HOLSymConst{\HOLTokenLeq{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}}
@@
 \HOLConst{GCONTEXT} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{C\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
-\HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}\ensuremath{)} \HOLBoundVar{Q}\ensuremath{)} \HOLFreeVar{xs} \ensuremath{(}\HOLBoundVar{C\sp{\prime}} \HOLBoundVar{Q}\ensuremath{)}\hfill{[unfolding_lemma4]}
-\end{small}
+\HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}\ensuremath{)} \HOLBoundVar{Q}\ensuremath{)} \HOLFreeVar{xs} \ensuremath{(}\HOLBoundVar{C\sp{\prime}} \HOLBoundVar{Q}\ensuremath{)}
 \end{alltt}
-
-It roughly says, for any context $C$ and weakly-guarded context
+which roughly says, for any context $C$ and weakly-guarded context
 $E$, if $C [\, E^n[P]\,] \overset{xs}{\Longrightarrow} P'$ and the length
-of actions $xs \leqslant n$, then $P$ has the form of $C'[P]$ (meaning
-that $P$ is not touched during the transitions). Traces are used for
-reasoning about the number of intermediate actions in weak
+of actions $xs \leqslant n$, then \hl{$P'$} has the form of $C'[P]$.
+Traces are used \hl{in} reasoning about the number of intermediate actions in weak
 transitions. For instance, from Def.~\ref{d:BisCon}, it is easy
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{Q}
-\hfill{[UNIQUE_SOLUTION_OF_CONTRACTIONS]}
+\HOLTokenTurnstile{} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{Q}\hfill{[UNIQUE_SOLUTION_OF_CONTRACTIONS]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Q}
-\hfill{[UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS]}
+\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Q}\hfill{[UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS]}
 \end{alltt}

### 2019-09-15 ic-journal/related.tex
Minor changes.

@@
 %strong, weak and rooted bisimilarity were proved.
-\hlD{Her work has been a
- basis for ours.} However, the differences are substantial, especially in the way of defining
-bisimilarities. We greatly benefited from features and standard
+\hlD{Her work has been a basis for} ours~\cite{Tian:2017wrba}.
+However, the differences are substantial, especially in the way of defining
+bisimilarities. We greatly benefited from \hl{new} features and standard
 libraries in recent versions of HOL4, and our formalisation has

### 2019-09-15 ic-journal/sos.tex
Minor changes.

@@
 having the corresponding cardinalities $h$ and $k$.} for
-agent variables, is then defined inductively:\footnote{``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling functions. They (and
+agent variables, is then defined inductively:\footnote{\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}} is the type of all relabeling functions. They (and
   related operations) are not discussed in this paper.}
@@
 consequence of an \emph{inductive relation} definition of
-\HOLinline{\HOLConst{TRANS}} by HOL's \texttt{HOL_reln} function~\cite{holdesc} for more details.
+\HOLinline{\HOLConst{TRANS}} by HOL's \texttt{HOL_reln} function.~(c.f.~\citep[p.~219]{holdesc} for more details.)
 A successful invocation of the definitional principle returns three
@@
 \end{alltt}
-The only two insteresting cases are for the recursion operator and
-recursion variables:
+The only two insteresting cases are \hlC{at agent variables and recursion:}
 \begin{alltt}
+\HOLTokenTurnstile{} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{var} \HOLFreeVar{Y}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E\sp{\prime}} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}\hfill{[CCS_Subst_var]}
 \HOLTokenTurnstile{} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} \ensuremath{(}\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\hfill{[CCS_Subst_rec]}
-\HOLTokenTurnstile{} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{var} \HOLFreeVar{Y}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E\sp{\prime}} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}\hfill{[CCS_Subst_var]}
 \end{alltt}

### 2019-09-15 ic-journal/multivariate.tex
Minor updates (contraction)
Closed Section 5.

@@
 Thus, if we can prove
-$X$ under this specific $P$, by Modus Ponens (MP) the original proof completes.
+$X$ under this specific $P$, by Modus Ponens (MP) the original proof
+\hl{would have completed.}
 This is the essence of action induction.
@@
 \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}, no matter if \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E}} or not, and the proof
-completes. Thus it remains to prove that
+\hl{would have completed.} Thus it remains to show that
 \begin{alltt}
@@
 \end{alltt}
+Notice that, in HOL, \HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}\\\;\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenEquiv{}}\\\;\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenIn{}}\\\;\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}.
+The form in right side suggest that,
+\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}} is actually a set containing all
+solutions (of \HOLinline{\HOLConst{CCS_equation}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}). \hlC{Then the unique-solution
+theorems can be understood as: any two (syntactically different) elements
+in the set are bisimilar.}
 
-\subsection{Unique solution of equations for $\sim$ (the \multivariate version)}
+\subsection{Unique solution of equations/contractions (the \multivariate version)}
 
+With all above new devices (\multivariate contexts and substitutions),
+the \multivariate case of Lemma~\ref{lem:milner313} is formalised
+below:
 \begin{alltt}
@@
 \HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}
+\end{alltt}
+Notice that, while Milner did not pointed out explicitly, the involved
+weakly guarded context $E$ must contain free variables up to $\til
+X$~--- the same requirement as in Theorem~\ref{t:Mil89s1}, which
+otherwise does not complete. Besides, we further required that, the
+bound variables of $E$ must be disjoint with $\til X$.
 
+The \multivariate version of Theorem~\ref{t:Mil89s1} is formalised
+below:
+\begin{alltt}
 \HOLTokenTurnstile{} \HOLConst{CCS_equation} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
@@
 
-\subsection{Unique solution of rooted contractions (the \multivariate version)}
-
+And the \multivariate version of Theorem~\ref{t:rcontraBisimulationU}:
 \begin{alltt}
@@
 \end{alltt}
+
+Compared with their formal proofs in the \univariate case, although each
+step related to \multivariate substitutions is more difficult than
+the \univariate case, the entire proofs still follow the same outlines,
+and many proof scripts can be directly copied from their \univariate version.

### 2019-09-15 ic-journal/coarsest.tex
Minor fixes, closing the paper

@@
 With this property, the actual formalisation of (\ref{equa:pq}) says:
-%\begin{theorem}{(Coarsest congruence contained in $\wb$)}
+\begin{theorem}[\texttt{COARSEST_CONGR_RL}]
+  Under the free actions assumption, $\rapprox$ is coarsest congruence contained in $\wb$.
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q}\hfill{[COARSEST_CONGR_RL]}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}.
+\HOLConst{free_action} \HOLBoundVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLBoundVar{q} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
+\HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{q}
 \end{alltt}
-%\end{theorem}
+\end{theorem}
 
@@
 (the other direction is trivial):
-%\begin{theorem}{(Coarsest precongruence contained in $\contr$)}
-\vspace{-2ex}
+\begin{theorem}[\texttt{COARSEST_PRECONGR_RL}]
+  Under the free actions assumption, $\mcontrBIS$ is the coarsest precongruence contained in $\contr$.
 \begin{alltt}
-\hfill{[COARSEST_PRECONGR_RL]}
-\HOLTokenTurnstile{} \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{q}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}.
+\HOLConst{free_action} \HOLBoundVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free_action} \HOLBoundVar{q} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
+\HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{p} \HOLSymConst{\HOLTokenObsContracts} \HOLBoundVar{q}
 \end{alltt}
-%\end{theorem}
+\end{theorem}
 
@@
  process $k$ which is not bisimilar with any derivative of $p$ and
- $q$, then \texttt{SUM_EQUIV} indeed implies rooted bisimilarity ($\rapprox$):
+ $q$, then \texttt{SUM_EQUIV} indeed implies rooted bisimilarity
+ ($\rapprox$): (c.f.~\cite{Tian:2017wrba} for more details of the proof)
 \begin{alltt}
@@
 Combining the above lemma with \texttt{PROP3_COMMON} and \texttt{COARSEST_CONGR_RL},
-we can  prove the following theorem for finite-state CCS:
-\begin{theorem}{(Coarsest congruence contained in $\approx$ for
-    finite-state CCS)}
+we can prove the following theorem:
+\begin{theorem}[\texttt{COARSEST_CONGR_FINITE}]
     \label{thm:coarsestfiniteState}
+    For finite-state CCS, $\wb$ is the coarsest congruence contained in $\approx$:
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)}\hfill[COARSEST_CONGR_FINITE]
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}.
+\HOLConst{finite_state} \HOLBoundVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLBoundVar{q} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLBoundVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
+\HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)}
 \end{alltt}

### 2019-09-15 ic-journal/equa.tex
Minor fixes, closing the paper

@@
 variable substitution operation} (c.f. SOS rule for the Recursion in
-Fig.~\ref{f:LTSCCS}) \hlD{for the substitution of equation variables.
+Fig.~\ref{f:LTSCCS}) for the substitution of equation variables.
 For example, the result of substituting variable $X$ with $\nil$ in $a.X +
@@
 $a.\nil + \recu X (b.X)$ (with the part $\recu X (b.X)$
-untouched). Multivariate substitutions are written in the same syntax,
+untouched). \Multivariate substitutions are written in the same syntax,
 e.g. $E \sub {\til P} {\til X}$. Whenever $\til X$ is clear from the
 context, we may also write $E[\til P]$ instead of $E \sub {\til P} {\til
-  X}$ (and $E[P]$ for $E \sub P X$ if there is a single equation variable $X$.)}
+  X}$ (and $E[P]$ for $E \sub P X$ if there is a single equation variable $X$.)
 
@@
 \hlD{For more details of above three theorems,} see Section~\ref{ss:part2}
-for the univariate case and
-Section~\ref{sec:multivariate} for the multivariate case.
-%(Theorem~\ref{t:Mil89s1} only).
+for the \univariate case and
+Section~\ref{sec:multivariate} for the \multivariate case.
 

### 2019-09-15 ic-journal/multivariate.tex
Minor fixes, closing the paper

@@
 concept of ``weakly guarded contexts'', and Lemma~\ref{lem:milner313}.
-\hlD{The work is an extension of the univariate case}~\cite{EPTCS276.10}
+The work is an extension of the \univariate case~\cite{EPTCS276.10}
  in the sense that neither the CCS datatype nor
@@
 \hlD{In the} \univariate formalisation, $\lambda$-functions (of type
-$CCS\rightarrow CCS$) are used to represent univariate CCS
+$CCS\rightarrow CCS$) are used to represent \univariate CCS
 \hlD{equations, and variable substitutions are simply 
@@
 built with CCS operators plus the equation variables.
-\hlD{For a formal point of view, this means we either need to define a
+For a formal point of view, this means we either need to define a
 whole new datatype (with extra equation variables) in which each CCS
@@
 guaranteed. Both solutions are rather combersome, and require a non-trivial modification
-of the formalisation of the univariate case. }
+of the formalisation of the \univariate case.
 
@@
 \begin{alltt}
-   \HOLTokenTurnstile{} \HOLConst{ALL_PROC} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{EVERY} \HOLConst{IS_PROC} \HOLFreeVar{Es}\hfill{[ALL_PROC_def]}
+   \HOLConst{ALL_PROC} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{EVERY} \HOLConst{IS_PROC} \HOLFreeVar{Es}\hfill{[ALL_PROC_def]}
 \end{alltt}
@@
 occurrences of free variables $X_i$ in $E$ with the corresponding
-$P_i$: (1) iterately applying the existing univariate
+$P_i$: (1) iterately applying the existing \univariate
 \HOLinline{\HOLConst{CCS_Subst}}; (2) defining a new \multivariate substitution
@@
   expression $E'$), then \HOLinline{\HOLConst{CCS_SUBST}} behaves exactly the
-  same as (the univariate) \HOLinline{\HOLConst{CCS_Subst}}:
+  same as (the \univariate) \HOLinline{\HOLConst{CCS_Subst}}:
 \begin{alltt}
@@
 
-Recall in Section~\ref{ss:context}, univariate contexts and their
+Recall in Section~\ref{ss:context}, \univariate contexts and their
 guarded companions are defined as predicates over $\lambda$-expressions
@@
 
-It is possible to inductively assert multivariate contexts and their
+It is possible to inductively assert \multivariate contexts and their
 guarded variants, but care is needed as  we need to exclude the cases where

### 2019-09-15 ic-journal/part2.tex
Minor fixes, closing the paper

@@
 
-\paragraph{Strong bisimilarity}
+\subsubsection{Strong bisimilarity}
+
 Based on results about ``bisimulation up to $\sim$'', we have first proved the following
@@
 substituted for $X$:
-\begin{lemma}[\texttt{STRONG_UNIQUE_SOLUTION_LEMMA} (Lemma 3.13 of \cite{Mil89}, the univariate version)]
+\begin{lemma}[\texttt{STRONG_UNIQUE_SOLUTION_LEMMA} (Lemma 3.13 of~\cite{Mil89}, \univariate version)]
 \label{lem:313}
@@
 
-\paragraph{Weak bisimilarity}
+\subsubsection{Weak bisimilarity}
+
 Milner's book~\cite{Mil89} contains only two ``unique solutions of
@@
 
-\paragraph{Rooted bisimilarity}
+\subsubsection{Rooted bisimilarity}
+
 For the ``unique solutions of

### 2019-09-15 ic-journal/response-letter.tex
text
Removed STRONG_EQUIV defining process (as it's the same with WEAK_EQUIV), answering referee's related issues
Only two TODOs left.

@@
 comments. We took all of them into consideration, and thoroughly
-addressed each of them in the revised version. We believe that after
+addressed each of them in the revised version. Beside, we have done
+a further formalisation of the general, multivariable case of two
+unique-solution theorems as the referee have suggested. This work
+consists of another 4,000 lines of proof scripts and a whole new
+Section 5 in the paper. We believe that after
 this revision, the quality of the paper has been significantly
-improved.
+improved and has reached a whole new technical level.
 
@@
   \end{quote}
-TODO (remove the duplicated part of weak bisimulation, mergin into the
-strong case).
+  We have removed the duplicated part and only kept the part for weak bisimulation.
 
@@
   \end{quote}
-
-  TODO: not understood this comment.
+  We fixed one minor issue in Fig.~2: from \texttt{SUM_EQUIV} to
+  $\rapprox$ the label $\subseteq$ should be $\supseteq$. The main
+  message of Fig.~2 is to show the equivalences of three involved
+  relations by making a loop of implications.
 
@@
 
-  TODO
+  We have rephrased the beginning part, putting the free-action
+  hypothesis as early as possible.
 
@@
 
-  TODO
+  We have re-organized this section, putting the target theorem and
+  its limitations at first.
 
@@
 
-  TODO
+  We have explained slightly more on the proof details of Thm 4.15.
 
@@
 
-  TODO
+  Thanks for reminding this. We have added this argument into the conclusion.
 
@@
 
-  TODO
+  We have added some HOL background and linked further details to its official book.
 
@@
 
-  TODO
+  We have further explains what exact \texttt{Hol_reln} does and returns.
 
@@
 
-  TODO (merge strong and weak cases0
+  We have merged the strong and weak cases together.
 
@@
 
-  TODO
+  In this project, relabeling is not discussed besides their presense
+  in CCS syntax. In particular, relabeling doesn't show any speciality
+  in the proofs of unique-solution theorems.  We have added a footnote to clarify this.
 
@@
   We have moved the side condition to the main text where we explain
-  the syntax. (TODO)
+  the syntax.
 
@@
 \end{quote}
-TODO
+
+We have completely rewritten this part, now we adope free variables
+and unified CCS expressions for both processes and equations.
+ Thus the hole is not needed here. (It's formal defined later and used
+ to formalize the univariate version of unique-solution theorems.
 
@@
 Rephrased: ``with guarded sums only''. We have removed all usages of
-``direct sym''.
+``direct sum''.
 
@@
 
-  TODO
+  We have merged these definitions together as much as possible.
 
@@
   \end{quote}
-  TODO
+  We have further explained it.
 
@@
   \end{quote}
-  TODO
+  We have clarified that, SOS rules are NOT axioms, because it's
+  generally not allowed to define new axioms. SOS rules are actually
+  some theorems added by the inductive relation \texttt{TRANS} as a
+  conservative extension of the logic.
 
@@
   \end{quote}
-  TODO
+  We have removed the defining process of strong bisimulation, left
+  only the part for weak bisimulation.
 
@@
   \end{quote}
-  TODO
+  In the first part of the paper, strong bisimulation rarely appears
+  as the focus is on weak bisimulation. But in the formalisation
+  sections we also formalised Milner's unique-solution theorem for
+  strong bisimilarity and many statements must distinguish between
+  strong/weak bisimilarities. Thus we use more ``weak bisimulation''
+  to make it more clear. This is not in conflict with anything.
 
@@
   \end{quote}
-  TODO
+  Same as above.
 
@@
   \end{quote}
-  TODO.
+  We have added an example to show its necessity.
 
@@
 \end{enumerate}
-
-\section*{Other changes}
-
-In this section, we listed other changes. All line numbers are based
-on the original review version of this paper.
-
-\begin{enumerate}
-\item TODO
-\end{enumerate}

### 2019-09-15 ic-journal/coarsest.tex
Only two TODOs left.

@@
 
-% The ``coarsest congruence contained in weak bisimilarity ($\approx$)''
-% theorem in CCS is somehow special, as its current known proofs either
-% rely on quite restricted conditions, or have an extremely complicated proof
-% (c.f. van Glabbeek's paper) in
-% which the theory of ordinals is required.  Actually even the relationship
-% between its name and statement is not well explained in many CCS
-% textbooks. But van Glabbeek's paper has given the so far clearest
-% explanation, here we briefly repeat his arguments:
-
-%As bisimilarity ($\approx$) is not congruence, for this reason rooted bisimilarity has been
-%introduced (Def.~\ref{d:rootedBisimilarity}).
-In this subsection we discuss two proofs of the fundamental result stating that
-rooted bisimilarity is the coarsest congruence contained in
-bisimilarity \cite{van2005characterisation,Gorrieri:2015jt,Mil89}:
+In this section we give a proof of the second part of
+Theorem~\ref{t:rapproxCongruence}, i.e. $\rapprox$ is the coarsest
+congruence contained in $\wb$. \hl{This theorem is of special interests to
+us, because within our framework it seems impossible to prove it
+without any limitation.} The general form of this theorem can be
+expressed informally as below~\cite{van2005characterisation,Gorrieri:2015jt,Mil89}:
+\begin{proposition}
+\label{prop:coarsest}
 \begin{equation}
-\label{eq:coarsest}
 \forall p\ \ q.\ p\ \rapprox\ \! q\ \Longleftrightarrow\ ( \forall r.\ p\ +\
@@
 \end{equation}
+\end{proposition}
 
-% : Milner's proof \cite{Mil89}, that requires
-% that no process can use all available names; and van Glabbeek's proof
-% \cite{van2005characterisation}, that does not require additional assumptions.
+However, we are only interested in the proposition from right to left,
+as from left to right it holds trivially by the substitutivity of
+$\rapprox$ of summation and that fact that $\rapprox$ implies $\wb$:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}.
+\HOLBoundVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{q} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
+\HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\hfill{[COARSEST_CONGR_LR]}
+\end{alltt}
+
+The standard argument~\cite{Mil89} requires that $p$
+and $q$ do not use up available labels (i.e.~visible actions).
+Formalising such an argument requires  
+a detailed treatment on free and bound names of CCS
+processes (with the restriction operator being a binder).
+However, in this project we do not discuss on free and bound names
+(also called ``sorts'') of CCS processes. Instead, we
+assume that all immediate \emph{weak} derivatives of
+ $p$ and $q$ do not use all available action names. We call it
+ the \emph{free action} property:
+\begin{alltt}
+   \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{a}.
+\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}}.
+\HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{a}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}}\ensuremath{)}\hfill{[free_action_def]}
+\end{alltt}
+
+Below we show how Proposition~\ref{prop:coarsest} is connected with
+the statement in Theorem~\ref{t:rapproxCongruence}, and prove it under
+the free action assumptions.
 
@@
 which in turn is trivially contained in \texttt{SUM_EQUIV}, as shown
-in Fig.~\ref{fig:relationship}. Thus, to prove (\ref{eq:coarsest}),
+in Fig.~\ref{fig:relationship}. Thus, to prove (\ref{prop:coarsest}),
 the crux is to prove that \texttt{SUM_EQUIV} implies
@@
 \forall p\ \ q.\ ( \forall r.\ p\ +\ r \;\approx\; q\ +\ r ) \
-\Rightarrow\ p\ \rapprox\ \! q\enspace.
+\Longrightarrow\ p\ \rapprox\ \! q\enspace.
 \end{equation}
@@
 
-The standard argument \cite{Mil89} requires that $p$
-and $q$ do not use up available labels (i.e.~visible actions).
-Formalising such an argument requires  
-a detailed treatment on free and bound names of CCS
-processes (with the restriction operator being a binder).
-However, the proof of (\ref{equa:pq}) can be carried out 
-% But it's
-% not easy to formalize and use such an assumption without a detailed
-% treatment on free and bound names (visible actions) of CCS
-% processes.\footnote{There're totally four such concepts: 1) free names
-% are all visible actions appearing in a CCS term without surrounding
-% $\nu$ (restriction) operator on the same action; 2) bound names are
-% the set of all actions ever used by $\nu$ (restriction) operator; 3)
-% free variables (or equation variables) are those variables without a
-% definition given by recursion
-% operator; 4) bound variables (process constants) are variables with
-% definitions given by recursion operator. All CCS results using these
-% concepts are not touched so far, although these four concepts are
-% successfully defined using HOL's set and list theories.} However, by
-just assuming that all immediate \emph{weak} derivatives of
- $p$ and $q$ do not use  all available labels.
-% analyzing the proof steps, we found that, what's really required is to
-% not use up all available labels in those weak transitions directly
-% lead from $p$ and $q$. In another words, even they have used all
-% available labels, as long as their first weak transitions didn't, the
-% whole proof can still be finished.\footnote{Further more, $p$ and $q$
-%   can be considered separately: the proof can be finished as long as
-%   \emph{each} of them didn't use up all labels on first weak
-%   transition, while the union of these labels are all labels.}
-We have formalised this property and
- called it the \emph{free action} property:
-\begin{alltt}
-   \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{a}.
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}}.
-\HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{a}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}}\ensuremath{)}\hfill{[free_action_def]}
-\end{alltt}
-%
-With this property, the actual formalisation of (\ref{equa:pq}) says:
+Under the free action assumptions, the actual formalisation of (\ref{equa:pq}) says:
 \begin{theorem}[\texttt{COARSEST_CONGR_RL}]
@@
 
-There exists a different, more complex, proof of (\ref{eq:coarsest}),
-given by van Glabbeek \cite{van2005characterisation}, which does not
-require any additional assumption.
+\subsection{Arbitrarily many non-bisimilar processes}
+\label{ss:arbitrarily}
+
+In this section, we give another more complex proof of the second part
+of Theorem~\ref{t:rapproxCongruence}, but only for finite-state CCS:
+\begin{theorem}[\texttt{COARSEST_CONGR_FINITE}]
+    \label{thm:coarsestfiniteState}
+    For finite-state CCS, $\wb$ is the coarsest congruence contained in $\approx$:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}.
+\HOLConst{finite_state} \HOLBoundVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLBoundVar{q} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLBoundVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
+\HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)}
+\end{alltt}
+\end{theorem}
+
+The proof of above theorem was given by Rob van Glabbeek
+\cite{van2005characterisation}, which originally applies to all CCS processes.
 The core lemma says, for
@@
 \end{alltt}
-To construct this process $k$,
+
+To \hl{actually} construct this process $k$,
  the proof relies on arbitrary infinite sums of 
@@
   CCS~--- a  restricted class.}
-
-\subsection{Arbitrarily many non-bisimilar processes}
-\label{ss:arbitrarily}
 
@@
 Combining the above lemma with \texttt{PROP3_COMMON} and \texttt{COARSEST_CONGR_RL},
-we can prove the following theorem:
-\begin{theorem}[\texttt{COARSEST_CONGR_FINITE}]
-    \label{thm:coarsestfiniteState}
-    For finite-state CCS, $\wb$ is the coarsest congruence contained in $\approx$:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}.
-\HOLConst{finite_state} \HOLBoundVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLBoundVar{q} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLBoundVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)}
-\end{alltt}
-\end{theorem}
+we can prove the theorem \texttt{COARSEST_CONGR_FINITE}.
 

### 2019-09-15 ic-journal/part2.tex
Only two TODOs left.

@@
 
-% We are now ready to prove the following, the main proposition above the
-% ``unique solution of equations'':
+Then, by a structural induction on weakly-guarded context
+(\texttt{WG}), we have proved Milner's strong unique-solution theorem
+in the \univariate case (c.f.~Section~\ref{sec:multivariate} for the
+\multivariate case). The formal proof basically follows the outline of its
+informal version. It is tedious due to large amounts of case analysis
+on different CCS operators.
+
 \begin{theorem}[\texttt{STRONG_UNIQUE_SOLUTION} (Proposition 3.14 of~\cite{Mil89})]
@@
 \end{theorem}
-In \hl{the proof of the above theorem}, we have identified 14 major sub-goals, dividing them into 7
-groups, in which each pair is symmetric (thus having similar proof
-steps). The proof of this last theorem consists of 500 lines (each
-line usually has 2 or 3 HOL tactics, to make the proof shorter).
 

### 2019-09-15 ic-journal/conclusions.tex
Updated generated TeX files

@@
   when there are long case analyses to be carried out.}
-A theorem-prover formalisation is in this respect  helpful and reassuring.
-We think that the statements in the formalisation are easy to read and
-understand, as they are  close to the original statements found in
-standard CCS textbooks \cite{Gorrieri:2015jt,Mil89}.
+Some of the textbook proofs are even wrong, e.g. Milner's
+proof of the unique-solution theorem for $wb$
+(Theorem~\ref{t:Mil89s3}).
+For some other textbook proofs, even they are correct, sometimes they actually
+do not need all information from the antecedents, which can be further
+weakened. This kind of improvements can be easily found during the
+formalisation work.
+For our CCS formalisation, we believe that all the definitions and
+theorem statements are easy to read and
+understand, as they are very close to their original statements in
+textbooks~\cite{Gorrieri:2015jt,Mil89}.
 

### 2019-09-15 ic-journal/response-letter.tex
Literally handled ALL review issues. DONE.

@@
   \end{quote}
-  TODO
+  We have removed the definition of ``context closure'' since it's not
+  (explicitly) used in the paper.  Then $\rapprox$ is a standard
+  notation for rooted bisimilarity following
+  Gorrieri~\cite{Gorrieri:2015jt}, in which the superscript $c$ should be
+  understood as a separate function or operator.
 
@@
   \end{quote}
-  TODO
+  We have explained it in the paper. In this case there is no hole in the context.
 

### 2019-09-15 ic-journal/conclusions.tex
Literally handled ALL review issues. DONE.

@@
 
-In this paper, we have highlighted a formalisation of the theory of CCS in the 
-HOL4 theorem prover.
-%  (for lack of space we have not discussed 
-% the formalisation of some basic algebraic theory, of the basic
-% properties of the expansion preorder,   and of a few
-%  versions of `bisimulation up to'
-% techniques). %
-%such as  bisimulation up-to bisimilarity). 
-The formalisation supports 4 methods for establishing (strong and weak) bisimilarity
-results: 
+In this paper, beside the introduction of rooted contraction and its
+unique solution theorems as a theoretical extension
+of~\cite{sangiorgi2017equations},
+we highlighted a comprehensive formalisation of the theory of CCS in the 
+HOL4 theorem prover. In particular, the formalisation supports four
+methods for establishing (strong and weak) bisimilarities:
 \begin{enumerate}
-\item
- constructing a bisimulation (the standard bisimulation proof
+\item constructing a bisimulation (the standard bisimulation proof
 method);
@@
 \item employing algebraic laws;
-\item defining a system of equations or contractions
+\item constructing a system of equations or contractions
 (i.e., the `unique-solution' method)
@@
 The formalisation has actually focused on the theory of
-unique solution of equations and contractions. It    
- has also allowed us to further develop the theory,
+unique solution of equations and contractions, both \univariate and
+\multivariate cases. It    
+ has allowed us to further develop the theory,
 notably the basic properties of rooted contraction, and the unique
@@
   when there are long case analyses to be carried out.}
-Some of the textbook proofs are even wrong, e.g. Milner's
-proof of the unique-solution theorem for $wb$
-(Theorem~\ref{t:Mil89s3}).
+\hl{Some of the textbook proofs were even wrong and the correct version is
+known but not available in the literature. This is the case of Milner's
+proof of the unique-solution theorem for $wb$}
+(Theorem~\ref{t:Mil89s3}). \hl{Now we have fully verified formal proofs for
+people who can read them.}
 For some other textbook proofs, even they are correct, sometimes they actually
@@
 
-Formalising other equivalences and preorders could also be considered,
+For the future work, formalising other equivalences and preorders could also be considered,
 notably the \hl{trace-based} equivalences, as well as more refined process
@@
 divergence.
-%We hope this work also inspires new formalisations on other process calculi.
-
-% Further plan on the formalisation mainly includes: 1) the extension to
-% multi-variable equation/contractions. 2) the support of recursion
-% operators in 
-% CCS context and expressions.
+%
+Finally, the disjointness between free and bound variables in the current
+\multivariate formalisation is certainly a limitation that can be
+removed in the future. If needed, extending the current work to
+infinite number of equations and variables is also feasible.
 

### 2019-09-15 ic-journal/context.tex
text
Minor fixes, closing the paper
Literally handled ALL review issues. DONE.

@@
 \end{alltt}
+Notice in above inductive definitions, for any CCS term $p$,
+\HOLinline{\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{p}} is a valid context. In this case there is no
+hole in the context. On the other hand, if any CCS term with recursion
+could be a context, the recursion must be a subterm of this $p$.
 
@@
 
-\hl{Many lemmas about above concepts} (\HOLinline{\HOLConst{CONTEXT}}, \HOLinline{\HOLConst{WG}},
+\hlD{Many lemmas about the  above concepts} (\HOLinline{\HOLConst{CONTEXT}}, \HOLinline{\HOLConst{WG}},
 \HOLinline{\HOLConst{SEQ}}, etc.) have then to be proven for the
@@
 
-Also,
+Rooted contraction, on the other hand, is a precongruence:
 \begin{alltt}

### 2019-09-15 ic-journal/response-letter.tex
text

--- 2019-09-09 ic-journal/response-letter.tex
@@
+\newcommand{\Mark}{{\underline{\tt R:} }}
+
 \begin{center}
@@
 
-Dear Chairs and Reviewers,
-
 \vskip 10pt
@@
 
-thank you for conditionally accepting our paper and for the fruitful
-comments. We took all of them into consideration, and thoroughly
-addressed each of them in the revised version. We believe that after
-this revision, the quality of the paper has been significantly
-improved.
+We would like to thank the reviewers for many useful
+comments and suggestions. We believe we have taken all of them into consideration, as best
+as we could.
+
+The main addition, here again following the recommendations of the reviewers 
+has been the extension of the our central theorems 
+to the multivariable case (ie., moving from ``unique solution theorems'' for a single
+equations, or contractions,  to multi-equations  or multi-contractions). 
+ This has been a significant effort (also because a few alternative ways to make the
+ extension had to be examined). At the end, this work 
+consists of another 4,000 lines of proof scripts and a whole new
+Section 5 in the paper.
 
@@
 point-by-point reply to the issues that have been raised.
+
+Our answers are marked  with an `` \Mark''  at the beginning.
+
+\finish{add some kind of mark, like above, so that our answers are clearly seen} 
 \ \\
@@
 
-  Now we have additionally formalised the multivariate (i.e. multi-variable)
-  version of the \emph{unique solution of rooted contractions theorem}
+\Mark  As indicated  above,  we have make the extension to the multivariate (i.e. multi-variable)
+  versions of two core theorems:  the \emph{unique solution of rooted contractions theorem}
   (Theorem~\ref{t:rcontraBisimulationU}) and \emph{Milner's strong
   unique-solution theorem} (Prop.~4.14 (2)
-  of~\citep[p.~103]{Mil89}), together with a detailed discussion on
-  multivariate contexts, weakly-guarded equations and multivariate
-  variable substitutions. This work consists of 4,000 lines of new
-  proof scripts, and it is indeed based on the existing framework in
-  the sense that, we do not need to change the CCS datatype definition
-  and any SOS rule. (c.f. Section~\ref{sec:multivariate} for more details.)
+  of~\citep[p.~103]{Mil89}), and added a whole new section to  discuss the main issues
+  faced in the  extension (having to do, eg, with 
+  multivariable  contexts, weakly-guarded equations and multivariable substitutions). 
+The extension  is indeed based on the existing framework in
+  the sense that, we do not  change the CCS datatype definition
+  and the  SOS rules
 
@@
 
-  Rephrased: ``We sometimes call the bisimulation and bisimilarity defined above
-the \emph{weak} bisimulation (and weak bisimilarity), ...''
+Done.
 
@@
 
-  We have fixed this typo (totally two instances in the paper, also in L92).
+Fixed.
 
@@
   We have rephrased this proof (also the theorem statements) with a
-  picture (Fig.~\ref{fig:310} illustrating the proof. The "Hence" part
-  actually used a property of $\wb$ that can be easily proven by induction
-  on each $\tau$-transition in a weak transition.
+  picture (Fig.~\ref{fig:310} illustrating the proof. 
+% The "Hence" part
+%   actually used a property of $\wb$ that can be easily proven by induction
+%   on each $\tau$-transition in a weak transition.
 
@@
 
-  Rephrased: ``... because all we need from $\mcontrBIS$ (or
-$\rcontr$) is their substitutivity properties (as precongruences)
-w.r.t the corresponding definitions of contexts.''
+  Rephrased.
+
+% : ``... because all we need from $\mcontrBIS$ (or
+% $\rcontr$) is their substitutivity properties (as precongruences)
+% w.r.t the corresponding definitions of contexts.''
 
@@
 
-  Now we used the following sentence: ``As a consequence, theories and proofs verified in HOL are relatively more
-  convincible to non-experts.''
-
+We have rephrased the sentence.
+%   Now we used the following sentence: ``As a consequence, theories and proofs verified in HOL are relatively more
+%   convincible to non-experts.''
 \item \begin{quote}
@@
   Sentence eliminated as now we have formalized the multivariate
-  version of unique-solution theorems. The ``without loss of
-  generality'' part is actually true, in the sense that, all steps of
-  informal proofs do appears in the uni-variate formal proofs. The
-  additional difficulities of the formal multivariate proof is discussed in Section~\ref{sec:multivariate}.
+  version of the unique-solution theorems. The ``without loss of
+  generality'' intended to point out  that all steps of
+  informal proofs do appear in the univariate formal proofs. The
+  additional difficulities for the formal multivariate proof are discussed in Section~\ref{sec:multivariate}.
 
@@
   delimitator between ``inner'' (logic) and ``outer'' (proof)
-  languages but this is not quite relevant to the present paper.
+  languages but this is not really  relevant for the present paper.
   After new HOL releases (k13) most uses of backquotes in  definitions can be eliminated.
@@
 
-  Rephrased: ``Many lemmas about above concepts (\texttt{CONTEXT}, \texttt{WG},
-  \texttt{SEQ}, etc.)''
+We have rephrased
+% : ``Many lemmas about above concepts (\texttt{CONTEXT}, \texttt{WG},
+%   \texttt{SEQ}, etc.)''
 
@@
   \end{quote}
-  Fixed. Now we say ``One highlight...''.
+  Fixed.  %Now we say ``One highlight...''.
 
@@
   \end{quote}
-  Fixed. ``... what kind of binary relations on CCS process are (strong) bisimulations.''
+  Fixed.  
+%``... what kind of binary relations on CCS process are (strong) bisimulations.''
 
@@
 
-  Rephrased: ``The definition of weak bisimulation is based on weak
+We have rephrased: ``The definition of weak bisimulation is based on weak
   and $\epsilon$--transitions:''
@@
   \end{quote}
-  This is no big problem here, as we are talking about any relation
-  (which is a contraction) is not in general a bisimulation. However
-  we have removed the word ``a'', having just: ``contraction does not imply weak bisimulation, ...''
+We have rephrased this
 
@@
   \end{quote}
-  Fixed PRQ; Mentioned ``naive weak bisimulation up to weak
+  Fixed ( we  mention that the ``naive weak bisimulation up to weak
   bisimilarity is unsound'' right before the definition of ``weak
-  bisimilation up to.''
+  bisimilation up to.'')
 
@@
   \end{quote}
-  Thanks. We have added ``we actually used a different bisimulation game defined below''.
-
+  Thanks. We have rephrased it 
+%added ``we actually used a different bisimulation game defined below''.
 \item \begin{quote}
@@
   \end{quote}
-  Rephrased: `` we also consider the relation closure of bisimilarity
-  w.r.t. summation...''
+  Rephrased
+% : `` we also consider the relation closure of bisimilarity
+%   w.r.t. summation...''
 
@@
   \end{quote}
-
-  TODO: not understood this comment.
+  We fixed one minor issue in Fig.~2 (from \texttt{SUM_EQUIV} to
+  $\rapprox$ the label $\subseteq$ should be $\supseteq$). The main
+  message of Fig.~2 is to show the equivalences of three involved
+  relations by making a loop of implications.
 
@@
 
-  TODO
+  We have re-organized this section, putting the target theorem and
+  its limitations  first.
 
@@
 
-  TODO
+  We have add some explanation on the proof details of Thm 4.15.
 
@@
 
-  Fixed (all raised by other reviewers).
+  Fixed % (all raised by other reviewers).
 
@@
 
-  Two of them, removed.
+Done.  % Two of them, removed.
 
@@
 
-  TODO
+  We have added some HOL background and links to further details about its official documentation.
 
@@
 
-  TODO
+  We have  further explained what  \texttt{Hol_reln} does and returns.
 
@@
 
-  TODO (merge strong and weak cases0
+  We have merged the strong and weak cases.
 
@@
 
-  We added a few more words right after: ``this is mostly due to the surprising fact
+  We added some explanations, including this sentence:
+ ``this is mostly due to the (surprising) fact
  that, contraction does not imply weak bisimulation (while expansion
@@
   \end{quote}
-  Removed.
+Done.
 
@@
 
-  Our formal proof of the classical result of ``$\rapprox$ is the
+  Our formal proof of the standard  result  ``$\rapprox$ is the
   coarsest congruence contained in $\wb$'' is one such example, where
   the formal theorem we obtained has slightly weaker antecedents under
-  the same proof idea. Anyway, we have omitted the sentence here.
+  the same proof idea. We have however now omitted the sentence.
 
@@
 
-  We have rephrased it, saying Fig.1 represents an LTS expressed in SOS rules.
+  We have rephrased it (pointing out that Fig.1 represents an LTS expressed in SOS rules).
 
@@
 
-  TODO
+  In this project, relabeling is not discussed besides their presense
+  in CCS syntax. In particular, relabeling doesn't bring in any delicate issues
+  in the proofs of unique-solution theorems.  We have added a footnote to clarify this.
+
+\finish{is the footnote still there? anyway, i do not like footnotes. One could just say
+  two words on the rule for relabelling (maybe we do say it already?)}
 
@@
   \end{quote}
-  Done. (``... there exists a context ...'')
+  Done.
 
@@
 \end{quote}
-TODO
+
+We have completely rewritten this part, now we adopt free variables
+and unified CCS expressions for both processes and equations.
+We have then explained the meaning of context in relation to this 
+(having multiequations now we have to deal also with contexts with multiple holes)
 
@@
   \end{quote}
-  TODO
+  We have removed the definition of ``context closure'' since it's not
+  (explicitly) used in the paper.  Then $\rapprox$ is a standard
+  notation for rooted bisimilarity (eg  Gorrieri~\cite{Gorrieri:2015jt})
 
@@
   \end{quote}
-We have rephrased the sentence: ``The above definition brings up a
-proof technique for proving rooted bisimilarity results, starting from
-a given bisimulation.''
+We have rephrased the sentence.
+
+\finish{above: check, i think i rewrote it}
 
@@
   \end{quote}
-  We have corrected it. It's an internal comment.
+  We have corrected it.
 
@@
   \end{quote}
-  Done. Two examples are $\nil$ and $b.\nil$.
+  Done. (Two examples are $\nil$ and $b.\nil$.)
 
@@
 
-  TODO
+  We have merged these definitions as best as we could
 
@@
 
-  It should be ``via''.
+Corrected.
 
@@
   a possible definiton of rooted contraction, and the definition we
-  found at last is indeed not coinductive (nor recursive).
+  found at last is indeed not coinductive
 
@@
   \end{quote}
-  You meant removing also the comma (period) here? But it's different
-  here: the definition ends at clause (2), an end period is added with
-  an ``enspace'' distance.
+
+We have tried to clarify this.
+  % You meant removing also the comma (period) here? But it's different
+  % here: the definition ends at clause (2), an end period is added with
+  % an ``enspace'' distance.
 
@@
   \end{quote}
-  We have completely re-worked this proof.
+  We have  re-worked this proof.
 
@@
   \end{quote}
-  We have eliminated this sentence as now we have done the
+  We have eliminated this sentence as now we have  the
   multivariate formalizations.
@@
   \end{quote}
-  Sorry, it should be ``literature''.
+Corrected.
 
@@
   \end{quote}
-  TODO
+  We have tried to  clarify this. 
+(SOS rules are  not axioms, because it's
+  generally not allowed to define new axioms. SOS rules are actually
+ theorems added by the inductive relation \texttt{TRANS} as a
+  conservative extension of the logic.)
 
@@
   \end{quote}
-  We have removed the part ``due to the use of ...''. Infinite
-  branching is indeed possible, no matter what's the reason.
+  We have removed the part ``due to the use of ...''. 
+% Infinite
+%   branching is indeed possible, no matter what's the reason.
 
@@
 
+\finish{check above, after my modifications}
+
 \item \begin{quote}
@@
   \end{quote}
-  TODO
+  We have removed the one for strong bisimulation, leaving
+  only the part for weak bisimulation.
 
@@
   \end{quote}
-  TODO
+  In the first part of the paper, strong bisimulation rarely appears
+  as the focus is on weak bisimulation. But in the formalisation
+  sections we also formalised Milner's unique-solution theorem for
+  strong bisimilarity and many statements must distinguish between
+  strong/weak bisimilarities. Thus we often use ``weak bisimulation''
+  to make it  clearer.
 
@@
   \end{quote}
-  TODO
+As pointed out above, we have  only maintained 
+ the part for weak bisimulation.
 
@@
   \end{quote}
-  We have rephrased this sentence. Basically we meant, for whatever
-  algebraic law of strong bisimilarity, there're also versions for
-  weak and rooted bisimilarity.
+  We have rephrased this sentence. (Basically we meant that
+any  algebraic law for strong bisimilarity can be stated also for
+  weak and rooted bisimilarity.)
 
@@
 
-  We have repharsed this part, moving the citation
-  \cite{sangiorgi1992problem} (which explains the reason) right before
-  the first sentence.
+  We have repharsed this part.
+% , moving the citation
+%   \cite{sangiorgi1992problem} (which explains the reason) right before
+%   the first sentence.
 
@@
   \end{quote}
-  Actually this is indeed surprising. We have rephrased this sentence:
-  ``this is mostly due to the surprising fact
-  that, although the contraction preorder is contained in weak
-bisimilarity, contraction does not imply weak bisimulation (while
-expansion does so)''.
+ We have rephrased this sentence:
+%   ``this is mostly due to the (surprising) fact
+%   that, although the contraction preorder is contained in weak
+% bisimilarity, contraction does not imply weak bisimulation (while
+% expansion does so)''.
 
@@
   \end{quote}
-  We have rephrased the sentence: ``There could be infinitely many such sub-processes, even on finitely
-  branching processes.''
+  We have rephrased the sentence: 
+% ``There could be infinitely many such sub-processes, even on finitely
+%   branching processes.''
 
@@
   \end{quote}
-  TODO.
+  We have added an example to show its need.
 

### 2019-09-15 ic-journal/response-letter.tex
Final fixes; disabled highlights

@@
 
-Our answers are marked  with an `` \Mark''  at the beginning.
-
-\finish{add some kind of mark, like above, so that our answers are clearly seen} 
+Our answers are marked  with a `` \Mark''  at the beginning.
+
 \ \\
@@
   \end{quote}
+  \Mark
   Fixed.
@@
   \end{quote}
+  \Mark
 
@@
   \end{quote}
-
+  \Mark
 Fixed.
@@
 
+  \Mark
   We have rephrased this proof (also the theorem statements) with a
@@
 
+  \Mark
   Rephrased.
@@
 
+  \Mark
   We have recalled Lemma 3.13 of \cite{Mil89} as
@@
   \end{quote}
+  \Mark
   Done.
@@
 
+  \Mark
 We have rephrased the sentence.
@@
 
+  \Mark
   Sentence eliminated as now we have formalized the multivariate
@@
 
+  \Mark
   The original HOL definition of the type Action is now given.
@@
   \end{quote}
+
+  \Mark
   Sentences removed. In HOL, single and double backquotes are
@@
   \end{quote}
+  \Mark
   Now we have removed most less-interesting cases and explained in
@@
 
+  \Mark
+  Yes, we have further explained this.
+
 \item \begin{quote}
@@
 
+  \Mark
  We have rephrased
@@
   \end{quote}
+   \Mark
  Fixed.  %Now we say ``One highlight...''.
@@
   \end{quote}
+  \Mark
   Fixed.  
@@
   \end{quote}
+  \Mark
   Fixed (``the definition of (strong) bisimilarity``).
@@
   \end{quote}
+  \Mark
   All formal theorems and definitions are generated from HOL4.
@@
 
+  \Mark
  We have rephrased: ``The definition of weak bisimulation is based on weak
@@
   \end{quote}
+  \Mark
   We have removed the duplicated part and only kept the part for weak bisimulation.
@@
   \end{quote}
+  \Mark
  We have rephrased this
@@
   \end{quote}
-  Fixed ( we  mention that the ``naive weak bisimulation up to weak
+  \Mark
+  Fixed (we mention that the ``naive weak bisimulation up to weak
   bisimilarity is unsound'' right before the definition of ``weak
@@
   \end{quote}
+  \Mark
   Thanks. We have rephrased it 
@@
   \end{quote}
+  \Mark
   Rephrased
@@
   \end{quote}
+  \Mark
   We fixed one minor issue in Fig.~2 (from \texttt{SUM_EQUIV} to
@@
 
+  \Mark
   We have rephrased the beginning part, putting the free-action
@@
 
+  \Mark
   ``this proof (Theorem~\ref{thm:coarsestfiniteState} in next
@@
 
+  \Mark
   We have re-organized this section, putting the target theorem and
@@
 
+  \Mark
   We have add some explanation on the proof details of Thm 4.15.
@@
 
+  \Mark
   Thanks for reminding this. We have added this argument into the conclusion.
@@
 
+  \Mark
   Fixed % (all raised by other reviewers).
@@
 
+  \Mark
  Done.  % Two of them, removed.
@@
 
+   \Mark
  We have removed the one before Example 3.7.
@@
   \end{quote}
+   \Mark
+  We have rephrased it as ``precongruence property'' which is indeed
+  introduced and further explained in Section 4.
 
@@
 
+  \Mark
   We have added some HOL background and links to further details about its official documentation.
@@
 
+  \Mark
   We have  further explained what  \texttt{Hol_reln} does and returns.
@@
 
+  \Mark
   We have merged the strong and weak cases.
@@
 
+  \Mark
   We added some explanations, including this sentence:
@@
   \end{quote}
+  \Mark
   We have added "(weak)" before "bisimilarity", in the first line of abstract.
@@
   \end{quote}
+  \Mark
  Done.
@@
   \end{quote}
+   \Mark
  Done.
@@
 
+  \Mark
   Our formal proof of the standard  result  ``$\rapprox$ is the
@@
 
+  \Mark
   We have rephrased it into multiple sentences.
@@
 
+  \Mark
   We have rephrased it (pointing out that Fig.1 represents an LTS expressed in SOS rules).
@@
 
+  \Mark
   In this project, relabeling is not discussed besides their presense
   in CCS syntax. In particular, relabeling doesn't bring in any delicate issues
-  in the proofs of unique-solution theorems.  We have added a footnote to clarify this.
-
-\finish{is the footnote still there? anyway, i do not like footnotes. One could just say
-  two words on the rule for relabelling (maybe we do say it already?)}
+  in the proofs of unique-solution theorems.  We have clarified this
+  right before the CCS datatype definition.
 
@@
   \end{quote}
+  \Mark
   We have moved the side condition to the main text where we explain
@@
 
+  \Mark
  We have completely rewritten this part, now we adopt free variables
@@
   \end{quote}
+  \Mark
   We have removed the definition of ``context closure'' since it's not
@@
   \end{quote}
+  \Mark
  We have rephrased the sentence.
 
-\finish{above: check, i think i rewrote it}
-
 \item \begin{quote}
@@
   \end{quote}
+   \Mark
  Fixed.
@@
   \end{quote}
+  \Mark
+  We have rephrased texts around here, the original sentence has disappeared.
 
@@
   \end{quote}
+  \Mark
   We have corrected it.
@@
 \end{quote}
+  \Mark
  We have added some examples, and used Milner's original definition of sequentiality.
@@
 \end{quote}
+  \Mark
  Rephrased: ``with guarded sums only''. We have removed all usages of
@@
   \end{quote}
+   \Mark
  Done. (Two examples are $\nil$ and $b.\nil$.)
@@
   \end{quote}
+  \Mark
   We have rephrased the sentence.
@@
   \end{quote}
+  \Mark
   We have replaced it with ``indeed''.
@@
 
+  \Mark
   We have removed the sentence, including this statement with the
@@
 
+  \Mark
   Having removed the sentence above now this should be ok. We have
@@
   \end{quote}
+  \Mark
   We have added a reference which contains this proof. Additionally,
@@
 
+  \Mark
   Done.
@@
 
+  \Mark
   We have merged these definitions as best as we could
@@
 
+  \Mark
   We have replaced ``the transition'' with ``a transition''.
@@
 
+  \Mark
  Corrected.
@@
 
+  \Mark
   We meant the definition should not be \emph{coinductive}, just like the
@@
 
+  \Mark
  We have tried to clarify this.
@@
   \end{quote}
+   \Mark
  We have  re-worked this proof.
@@
   \end{quote}
+  \Mark
   Fixed during re-work of the proof of Theorem 3.14.
@@
   \end{quote}
+  \Mark
   Removed ``Logic'' from ``HOL Logic''.
@@
   \end{quote}
+  \Mark
   The long sentence is spilited.
@@
   \end{quote}
+  \Mark
   We have further explained it.
@@
   \end{quote}
+  \Mark
   Changed to: ``the \emph{same} (programming language)''
@@
   \end{quote}
+  \Mark
   Removed parentheses.
@@
   \end{quote}
+  \Mark
   We have eliminated this sentence as now we have  the
@@
   \end{quote}
-  \texttt{option} is the name of the HOL formal theory.
+  \Mark
+  \texttt{option} is the name of the HOL formal theory. (Then we have
+  removed this mention completely)
 
@@
   \end{quote}
+  \Mark
   We have eliminated most uses of backquotes using HOL's new syntax.
@@
   \end{quote}
+  \Mark
  Corrected.
@@
   \end{quote}
+   \Mark
  We have tried to  clarify this. 
@@
   \end{quote}
+  \Mark
   We have made them all in bold fonts.
@@
   \end{quote}
+  \Mark
  We have re-phrased this part: ``(1) there exist indeed three
@@
   \end{quote}
+   \Mark
  We have rephrased this sentence.
@@
   \end{quote}
+  \Mark
   We have explained it in the paper. In this case there is no hole in the context.
@@
   \end{quote}
+  \Mark
   We have removed the part ``due to the use of ...''. 
@@
   \end{quote}
+  \Mark
   Rephrased to ``One highlight...''
@@
   \end{quote}
+  \Mark
   By default, all theorems (their \TeX code) exported from HOL are
   fully specialised, removing outermost universal quantifiers. We have
-  moved this sentence to an earlier footnote on the first such exported theorem.
-
-\finish{check above, after my modifications}
+  moved this sentence to Section~\ref{ss:formalCCS} between parentheses.
 
@@
   \end{quote}
+  \Mark
   We have removed the one for strong bisimulation, leaving
@@
   \end{quote}
+  \Mark
   In the first part of the paper, strong bisimulation rarely appears
@@
   \end{quote}
+  \Mark
  As pointed out above, we have  only maintained 
@@
   \end{quote}
+   \Mark
  Same as above.
@@
   \end{quote}
+  \Mark
   We have rephrased this sentence. (Basically we meant that
@@
 
+  \Mark
   We have repharsed this part.
@@
   \end{quote}
+  \Mark
  We have rephrased this sentence:
@@
   \end{quote}
+  \Mark
   We have removed the HOL version.
@@
   \end{quote}
+  \Mark
   Yes. We have fixed the definition.
@@
   \end{quote}
+  \Mark
   We have added a colon at the end.
@@
   \end{quote}
+  \Mark
   We have rephrased the sentence: ``(which needs not to be itself a (pre)congruence)''.
@@
   \end{quote}
+  \Mark
   We have removed this sentence.
@@
   \end{quote}
+  \Mark
   We have rephrased the sentence: 
@@
   \end{quote}
+  \Mark
+  Fixed.
 
@@
   \end{quote}
+  \Mark
   We have rephrased the sentence: ``Following the inductive structure
@@
   \end{quote}
+  \Mark
   Fixed as: ``In the proof of the above theorem''.
@@
   \end{quote}
+  \Mark
   We have added an example to show its need.
@@
   \end{quote}
+  \Mark
   Fixed bibtex item.

### 2019-09-15 ic-journal/ccs.tex
text
Literally handled ALL review issues. DONE.
Final fixes; disabled highlights

@@
 
-\hlD{Here we recall the core theory of CCS.}
+\hl{Here we recall the core theory of CCS.}
 We assume a possibly infinite set of names $\mathscr{L} = \{a, b,
-\ldots\}$ \hlD{yielding} input and $\overline{\mbox{output}}$ labels (actions), plus a special invisible
+\ldots\}$ \hl{yielding} input and $\overline{\mbox{output}}$ labels (actions), plus a special invisible
 action $\tau \notin \mathscr{L}$, and \hl{another possibly infinite
@@
 The class of CCS processes is then inductively
-defined from $\nil$ \hl{(deadlock) and agent variables} by the operators
+defined from $\nil$ \hl{(the terminated process)} and agent variables by the operators
 of \emph{prefixing} (.), \emph{parallel composition} ($|$),
@@
 \end{equation*}
-\hlD{In our presentation of CCS, 
+\hl{In our presentation of CCS, 
 the restriction operator takes a set of  labels $L
@@
 % \end{enumerate}
-We sometimes omit \hlD{a} trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil$.
-\hl{A CCS process $P$ may \hlD{evolve} to another one, say $P'$, under
-  an action $\mu$, written by $P \arr{\mu} P'$.}
-The \hlD{transition semantics} of CCS processes is given by means of
+We sometimes omit \hl{a} trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil$.
+A CCS process $P$ may \hl{evolve} to another one, say $P'$, under
+  an action $\mu$, written by $P \arr{\mu} P'$.
+The \hl{transition semantics} of CCS processes is given by means of
 a Labeled Transition System (LTS) \hl{expressed in Structural Operational
@@
 
-% \paragraph{CCS contexts and equations}
-% And $\ct{\til P}$ is the process obtained by replacing each hole
-% $\holei i$ of the  context $\qct$ with $P_i$.  
-% We write $\ctx \R$ for the closure of a relation under contexts.
-% Thus $P\: \ctx \R\: Q$
-% means that there \hl{exists a} context $\qct$ and tuples $\til P,\til Q$ with
-% $P =  \ct{\til P}, Q =  \ct{\til Q}$ and $\til P \RR \til Q$.
-
 % next file: expansion.tex (bisimilarity and rooted bisimilarity, actually)

### 2019-09-15 ic-journal/coarsest.tex
Final fixes; disabled highlights

@@
 ordinals''~\cite{norrish2013ordinals}.
-\hlD{As a consequence, the final result is only for finite-state
-  CCS~--- a  restricted class.}
+As a consequence, the final result is only for finite-state
+  CCS~--- a  restricted class.
 
@@
 \begin{definition}[Klop processes]
-For each ordinal $\lambda$, and an arbitrary chosen non-$\tau$ action $a$,
+For each ordinal $\lambda$, and an arbitrary chosen action $a \neq \tau$,
 define a CCS process $k_\lambda$ as follows:

### 2019-09-15 ic-journal/context.tex
Final fixes; disabled highlights

@@
 
-A context is \emph{(strongly) guarded} (\texttt{SG}) if each hole is underneath a \emph{visible} prefix:
+A context is \emph{guarded} (\texttt{SG}) if each hole is underneath a \emph{visible} prefix:
 \begin{alltt}
@@
 
-\hlD{Many lemmas about the  above concepts} (\HOLinline{\HOLConst{CONTEXT}}, \HOLinline{\HOLConst{WG}},
-\HOLinline{\HOLConst{SEQ}}, etc.) have then to be proven for the
+Many lemmas about the above concepts (\HOLinline{\HOLConst{CONTEXT}}, \HOLinline{\HOLConst{WG}},
+\HOLinline{\HOLConst{SEQ}}, etc.) have to be proved for the
  relationships among these kinds of contexts and properties about their

### 2019-09-15 ic-journal/contraction.tex
Final fixes; disabled highlights

@@
 (Theorem~\ref{t:Mil89})
-\hlD{brings a new proof technique for proving (weak) bisimilarities. However, it has
+brings a new proof technique for proving (weak) bisimilarities. However, it has
  limitations: the equations must be guarded and sequential (moreover
@@
 the occurrences of other operators above the variables, such as parallel
-composition and restriction, in general cannot be removed.}
+composition and restriction, in general cannot be removed.
 The constraints of Theorem~\ref{t:Mil89}, however, can be 

### 2019-09-15 ic-journal/equa.tex
Final fixes; disabled highlights

@@
 
-\hlD{In the CCS syntax, 
+\hl{In the CCS syntax, 
 a recursion $\recu A  P$ acts as a binder for $A$ in the body $P$. 
@@
 
-\hlD{In this paper (and the formalisation work), we use the agent
+\hl{In this paper (and the formalisation work), we use the agent
 variables also as \emph{equation variables}. This eliminates the need of
@@
 \label{ss:SysEq}
-\hlD{When discussing equations it is standard to talk about `context'. This is a 
+\hl{When discussing equations it is standard to talk about `context'. This is a 
  a CCS expression  possibly containing  free variables that, however, may not occur within
@@
 Milner's ``unique solution of equations'' }  theorems~\cite{Mil89} intuitively
-\hlD{say that, if a context $C$
+\hl{say that, if a context $C$
 %  \hl{(i.e., a CCS expression with possibly
@@
  a countable indexing set $I$, we have variables $X_i$, and expressions
-$E_i$ \hlD{possibly containing such variables $\cup_i \{ X_i\}$}. Then 
+$E_i$ \hl{possibly containing such variables $\cup_i \{ X_i\}$}. Then 
 $\{ X_i = E_i\}_{i\in I}$ is 
@@
 \item The system has \emph{a unique solution for $\wb$}  if whenever 
- $\til P$ and $\til Q$ are both solutions \hlD{then} $\til P \wb \til Q$. 
+ $\til P$ and $\til Q$ are both solutions \hl{then} $\til P \wb \til Q$. 
 \end{itemize} 
@@
 
-\item \hlD{\emph{guarded}} if, in each $E_i$, each occurrence of
+\item \hl{\emph{guarded}} if, in each $E_i$, each occurrence of
   each $X_i$ is underneath a \emph{visible} prefix;
-
-\finish{i have removed 
-``(strongly)''}
 
@@
 
-\hlD{In other words, if a system of equations is sequential, then for
+\hl{In other words, if a system of equations is sequential, then for
 each  $E_i$, any subexpression of $E_i$ in which $X_j $
@@
 
-\hlD{Milner has  three versions of  ``unique solution of equations''
+\hl{Milner has  three versions of  ``unique solution of equations''
 theorems, for $\sim$, $\wb$ and $\rapprox$, respectively, though only the
@@
 
-\hlD{The version of Milner's unique-solution theorem for $\wb$ further requires
+\hl{The version of Milner's unique-solution theorem for $\wb$ further requires
 that all sums are guarded}:
@@
 \label{t:Mil89}
-Let $E_i$ be \hlD{guarded}  and sequential with free
+Let $E_i$ be \hl{guarded}  and sequential with free
 variables up to $\til X$, and let ${\til P} \wb {\til E}\{\til P /\til X\}$,
@@
 
-\finish{below and elsewhere: the correct terminology is ``derivative'', instead of ``derivation''}
-
-The proof of \hlD{the  theorem above} exploits an invariance
-property on immediate \hlD{derivatives}
+The proof of the theorem above exploits an invariance
+property on immediate derivatives
 of guarded and sequential expressions, and then extracts a bisimulation
@@
 where $X$ is guarded but not sequential. Any process that does not use
-$a$ is a solution\hl{, e.g. $\nil$ and $b.\nil$.}
+$a$ is a solution, e.g. $\nil$ and $b.\nil$.
 
-\hlD{For more details of above three theorems,} see Section~\ref{ss:part2}
+For more details of above three theorems, see Section~\ref{ss:part2}
 for the \univariate case and

### 2019-09-15 ic-journal/expansion.tex
Final fixes; disabled highlights

@@
 
-\hlD{\emph{Strong} bisimulation and strong bisimilarity} ($\sim$)
+\hl{\emph{Strong} bisimulation and strong bisimilarity} ($\sim$)
 can be obtained by replacing the weak transition $Q\Arcap\mu Q'$ in the above
@@
 Weak bisimilarity is not preserved by the sum operator (except for
-guarded sums), i.e.\  $P_1 \wb Q_1$ and $P_2 \wb Q_2$  \hlD{does not imply}
+guarded sums), i.e.\  $P_1 \wb Q_1$ and $P_2 \wb Q_2$  \hl{does not imply}
  $P_1 + P_2 \wb Q_1 + Q_2$.
@@
 
-\hlD{The above definition also brings up a proof technique for proving rooted
+\hl{The above definition also brings up a proof technique for proving rooted
 bisimilarity from a given bisimulation. The next
@@
 \label{l:obsCongrByWeakBisim}
-\hlD{Given a (weak) bisimulation $\RR$, suppose two processes $P$ and $Q$
+\hl{Given a (weak) bisimulation $\RR$, suppose two processes $P$ and $Q$
 satisfy the following properties}:
@@
 
-\hlD{One basic property of rooted bisimiarity is congruence,
-indeed
- the
-coarsest congruence contained in bisimilarity}
-(c.f., Section~\ref{s:coarsest} \hlD{for more details): }
+One basic property of rooted bisimiarity is congruence,
+indeed the coarsest congruence contained in bisimilarity
+(c.f. Section~\ref{s:coarsest} for more details):
 \begin{theorem}

### 2019-09-15 ic-journal/intro.tex
Final fixes; disabled highlights

@@
 has severe syntactic limitations:}
-the equations must be both \emph{(strongly) guarded} and \emph{sequential}. That is,
+the equations must be both \emph{guarded} and \emph{sequential}. That is,
 variables of the equations \hl{can only occur underneath visible prefixes and summations.}
@@
 any two solutions must be componentwise bisimilar.
-The difference \hl{from} equations is \hlD{in} the meaning of a solution:
+The difference \hl{from} equations is \hl{in} the meaning of a solution:
 in the case of contractions the solution is evaluated with respect to
@@
 is the occurrences of %\emph{direct} 
-\hlD{sums} (e.g.~$P + Q$) due to
+\hl{sums} (e.g.~$P + Q$) due to
 the \hl{non-substitutivity of the contraction preorder in this case}.
 
- \hlD{This paper presents}  a
+ \hl{This paper presents}  a
 comprehensive formalisation of Milner's Calculus of Communicating
@@
 with a focus towards the theory of unique solutions of equations and contractions.
-\hlD{Many results in Milner's CCS book}~\cite{Mil89} are covered, since
+\hl{Many results in Milner's CCS book}~\cite{Mil89} are covered, since
 the unique-solution theorems rely on a large number of fundamental results.
@@
 Concerning rooted bisimilarity, the formalisation
-includes \hl{Hennessy's Lemma} and \hl{Deng's Lemma},
- and two \hl{theorems} saying that rooted bisimilarity is the coarsest (largest)
+includes Hennessy's Lemma and Deng's Lemma,
+ and two theorems saying that rooted bisimilarity is the coarsest (largest)
  congruence contained in weak bisimilarity ($\wb$): one is classical
@@
 Similar results are also proved for the rooted contraction preorder.
-In this respect, the work is \hl{also} an extensive experiment \hl{using} the HOL theorem prover with its
-recent developments, including \hl{its coinductive relation-defining package}.
+In this respect, the work is also an extensive experiment using the HOL theorem prover with its
+recent developments, including its coinduction defining package.
 
-From the \hl{point of} view of the CCS theory, this formalisation has offered us the possibility of
+From the point of view of the CCS theory, this formalisation has offered us the possibility of
 further refining the theory of unique solutions of contractions.
-In particular, \hlD{the existing result}~\cite{sangiorgi2017equations} \hlD{has  limitations} on the body of the contractions due to the
+In particular, the existing result~\cite{sangiorgi2017equations} has limitations on the body of the contractions due to the
 substitutivity problems of weak bisimilarity and other behavioural relations with respect
 to the sum operator.
-\hl{In this paper, the contraction-based proof technique is further
-refined by moving from the contraction preorder} to
+In this paper, the contraction-based proof technique is further
+refined by moving from the contraction preorder to
 \emph{rooted contraction}, that is, the coarsest precongruence contained in the contraction
@@
 \emph{rooted bisimilarity} (hence also for bisimilarity itself), and places no 
-\hlD{constraints on the use the sum operator}.
+\hl{constraints on the use the sum operator}.
 
@@
 equivalences and preorders that share similar proof structures.
-% rephrased: (TODO: still hard to read --Chun)
-\hl{Such structural simililarities can be found, for instance, in the
+Such structural simililarities can be found, for instance, in the
 following cases: the proofs that rooted bisimilarity and rooted
@@
 proofs about various forms of enhancements of the bisimulation proof
-method (the `up-to' techniques).}
+method (the `up-to' techniques).
 %
@@
 more careful and delicate treatment of CCS
-expressions with \hl{multiple} variables and substitutions acting on them.
+expressions with multiple variables and substitutions acting on them.
 
-\hl{In contrast to modern literature, e.g.}~\cite{Gorrieri:2015jt},
-\hl{we have followed Milner's original approach}~\cite{milner1990operational} and adopted the same
+In contrast to modern literature, e.g.~\cite{Gorrieri:2015jt},
+we have followed Milner's original approach~\cite{milner1990operational} and adopted the same
 type for both CCS equations and processes: those undefined constants

### 2019-09-15 ic-journal/multivariate.tex
Literally handled ALL review issues. DONE.
Final fixes; disabled highlights

@@
 
-In this section,  \hlD{we discuss the formalisation of the} \multivariate
+In this section,  \hl{we discuss the formalisation of the} \multivariate
 cases of Milner's ``unique solution of equations (for $\sim$)''
@@
 contractions'' (Theorem~\ref{t:rcontraBisimulationU}).
-\hlC{This formalisation only supports finitely many
+\hl{This formalisation only supports finitely many
   equations/contractions and equation variables.\footnote{The original theorems
@@
 representation of CCS equations (expressions, contexts).
-\hlD{In the} \univariate formalisation, $\lambda$-functions (of type
+\hl{In the} \univariate formalisation, $\lambda$-functions (of type
 $CCS\rightarrow CCS$) are used to represent \univariate CCS
-\hlD{equations, and variable substitutions are simply 
+\hl{equations, and variable substitutions are simply 
 calls to $\lambda$-functions on the target CCS terms.}
@@
 
-\hlD{In this project, we have followed} Milner~\cite{Mil89}, using the
+\hl{In this project, we have followed} Milner~\cite{Mil89}, using the
 same alphabet for both agent variables and equation variables.
@@
 We  prove a stronger result,
-i.e.,  the set of free variables decreases through derivations:
+i.e.,  the set of free variables decreases through derivatives:
 \begin{alltt}
@@
 
-\hlC{Milner said it can be proved by ``an easy action
+\hl{Milner said it can be proved by ``an easy action
 induction''}~\cite{milner1990operational}.
@@
 (contexts/expressions), \HOLinline{\HOLConst{WG}} (weak guarded contexts),
-\HOLinline{\HOLConst{SG}} (strongly guarded contexts) and \HOLinline{\HOLConst{SEQ}} (sequential
+\HOLinline{\HOLConst{SG}} (guarded contexts) and \HOLinline{\HOLConst{SEQ}} (sequential
 contexts), are all defined inductively, i.e.~they are built from some ``holes''
@@
   \HOLinline{\HOLFreeVar{Xs}}. Thus our choices in these definitions are optimal.}
-(The strong guardedness and sequentiality can also be defined similarily
+(The guardedness and sequentiality can also be defined similarily
 when needed, using
@@
     &X_2 = E_2[\til X] \\
-    & \vdots \\
+    & \cdots \\
     &X_n = E_n[\til X]
@@
     &P_2 \ \R\ E_2\{\til P/\til X\} \\
-    & \vdots \\
+    & \cdots \\
     &P_n \ \R\ E_n\{\til P/\til X\}
@@
 \HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}} is actually a set containing all
-solutions (of \HOLinline{\HOLConst{CCS_equation}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}). \hlC{Then the unique-solution
+solutions (of \HOLinline{\HOLConst{CCS_equation}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}). Then the unique-solution
 theorems can be understood as: any two (syntactically different) elements
-in the set are bisimilar.}
+in the set are bisimilar.
 

### 2019-09-15 ic-journal/part2.tex
Updated generated TeX files
Final fixes; disabled highlights

@@
 \multivariate case). The formal proof basically follows the outline of its
-informal version. It is tedious due to large amounts of case analysis
-on different CCS operators.
+informal version. It is tedious due to large amounts of case analyses
+on each CCS operator.
 
@@
 \begin{lemma}[\texttt{WEAK_UNIQUE_SOLUTION_LEMMA}]
-If the variable $X$ is strongly guarded and sequential in $G$, and
+If the variable $X$ is guarded and sequential in $G$, and
 $G\{P/X\}\overset{\alpha}{\rightarrow} P'$, then $P'$ takes the form
@@
 \begin{lemma}[\texttt{OBS_UNIQUE_SOLUTION_LEMMA}]
-If the variable $X$ is strongly guarded and sequential in $G$, and
+If the variable $X$ is guarded and sequential in $G$, and
 $G\{P/X\}\overset{\alpha}{\rightarrow} P'$, then $P'$ takes the form
@@
 equations'' theorem for rooted bisimilarity ($\rapprox$)
-has more rigid constraints, as the variables must be both strongly guarded and sequential.
+has more rigid constraints, as the variables must be both guarded and sequential.
 %  Theorem~\ref{t:rcontraBisimulationU} can also be seen as a more

### 2019-09-15 ic-journal/related.tex
Final fixes; disabled highlights

@@
 program, e.g.~\cite{cleaveland1993concurrency}) for
-automatically proving bisimilarities of CCS
-processes. %, thus she stopped proving deeper theorems in Milner's
-           %book, once the congruence and algebraic laws of 
-%strong, weak and rooted bisimilarity were proved.
-\hlD{Her work has been a basis for} ours~\cite{Tian:2017wrba}.
+automatically proving bisimilarities of CCS processes.
+Her work has been a basis for ours~\cite{Tian:2017wrba}.
 However, the differences are substantial, especially in the way of defining
@@
 name binders \cite{bengtson2007completeness,parrow2009formalising}.
-\hl{Details are found in   Bengtson's PhD thesis}~\cite{bengtson2010formalising}. For CCS, 
+More details can be found in Bengtson's PhD thesis~\cite{bengtson2010formalising}. For CCS, 
 he has formalized basic properties for strong/weak equivalence (congruence, basic
- algebraic laws); \hlD{however the CCS syntax doesn't have constants
+ algebraic laws); \hl{however the CCS syntax doesn't have constants
 (or recursion operator), using replication in place of recursion.}

### 2019-09-15 ic-journal/sos.tex
Final fixes; disabled highlights

@@
 \subsection{CCS: the formal theory}
+\label{ss:formalCCS}
 
@@
 having the corresponding cardinalities $h$ and $k$.} for
-agent variables, is then defined inductively:\footnote{\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}} is the type of all relabeling functions. They (and
-  related operations) are not discussed in this paper.}
+agent variables, is then defined inductively: (\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}} is the type of all relabeling functions. They (and
+  related operations) are not discussed in this paper.)
 \begin{lstlisting}
@@
 most CCS operators have also the more readable abbreviation forms,
-either for end user or for \TeX{} outputs.}\footnote{All
+either for end user or for \TeX{} outputs.} (All
   formal theorems and definitions in this paper
   are generated from HOL4. Also, by default, all theorems are fully
-  specialised, removing outermost universal quantifiers.}
+  specialised, removing outermost universal quantifiers.)
 
@@
 \hline
-\hl{\textbf{CCS concept}} & \hl{\textbf{Notation}} & \textbf{HOL term} &
+\textbf{CCS concept} & \textbf{Notation} & \textbf{HOL term} &
                                              \textbf{HOL abbrev.} & \hl{\textbf{\TeX{} outputs}} \\
 \hline
-\hlD{nil} & $\textbf{0}$ & \texttt{nil} & \texttt{nil} & \HOLinline{\HOLConst{\ensuremath{\mathbf{0}}}} \\
+nil & $\textbf{0}$ & \texttt{nil} & \texttt{nil} & \HOLinline{\HOLConst{\ensuremath{\mathbf{0}}}} \\
 prefix & $\mu.P$ & \texttt{prefix u P} & \texttt{u..P} & \HOLinline{\HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{P}} \\
@@
 \end{equation*}
-\item \hlD{\emph{ind} is the induction principle for the
+\item \hl{\emph{ind} is the induction principle for the
   relation} (see Section~\ref{sec:multivariate} for the exact form
@@
 \end{alltt}
-The only two insteresting cases are \hlC{at agent variables and recursion:}
+The only two insteresting cases are at agent variables and recursion:
 \begin{alltt}
@@
 \end{alltt}
-\hlD{The variable substitutions only affects free
-variables: the variable $Y$ in} ``\HOLinline{\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}}'' \hlD{is
+\hl{The variable substitutions only affects free
+variables: the variable $Y$ in} ``\HOLinline{\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}}'' \hl{is
 bound and therefore the substitution ignores it. }
@@
 all the possible transitions and prove the non-existence of others.
-\hlD{This shows the usefulness of appealing to an ML function
+\hl{This shows the usefulness of appealing to an ML function
 \texttt{CCS\_TRANS\_CONV} that is designed to automate the whole process.

### 2019-09-15 ic-journal/unique.tex
Final fixes; disabled highlights

@@
 
-\hlD{Now we recall the ``unique solution of
+\hl{Now we recall the ``unique solution of
 contractions'' theorem}~\cite{sangiorgi2017equations},
-\hlD{which weakens} the requirements of Milner's result
+\hl{which weakens} the requirements of Milner's result
 (Theorem~\ref{t:Mil89}).
@@
 $\ct{\til Q} \mcontrBIS \ctpp{\til Q}$, 
- by the substitutivity  properties of $\mcontrBIS$ (we exploit here
+ from the precongruence property of $\mcontrBIS$ (we exploit here
  the syntactic constraints on sums). Moreover,
@@
 \begin{proof}
-\hlD{We  prove $P_i \wb Q_i$ (for each $i \in I$) by considering} the following relation
+\hl{We  prove $P_i \wb Q_i$ (for each $i \in I$) by considering} the following relation
 \begin{equation*}
@@
 \end{equation*}
-\finish{below: what is $\equiv$?}
 
-\hl{Obviously we have $(P_i,Q_i) \in \R$ (by taking $C \equiv E_i$, and
-the fact that $\mcontrBIS$ implies $\wb$). It remains to}
+Obviously we have $(P_i,Q_i) \in \R$ (by taking $C = E_i$, and
+the fact that $\mcontrBIS$ implies $\wb$). It remains to
 show that $\R$ is a bisimulation. Suppose \hl{$(R, S) \in \R$ via} a context
@@
 (The other side from $S$ follows in the same manner.)}
-\hlD{See} Fig.~\ref{fig:310} \hl{for a visual illustration.}
+See Fig.~\ref{fig:310} for a visual illustration.
 \end{proof}
@@
 in addition to $\wb$).
-However, comparing with Milner's Theorem~\ref{t:Mil89s1}, \hlD{there is
+However, comparing with Milner's Theorem~\ref{t:Mil89s1}, \hl{there is
 a constraint: the involved CCS expression may only
@@
 \hl{The above definition was found with the help of interactive theorem proving.}
-\hlD{The following two principles were adopted when searching
+\hl{The following two principles were adopted when searching
 for a possible definition: (1) the definition should not be coinductive,
@@
 %   the cases of $\sim$ and $\rapprox$.}
-\hlD{Furthermore, we needed to show that the definition found is the
+\hl{Furthermore, we needed to show that the definition found is the
 best possible one, by showing that it yields the coarsest precongruence
 contains in $\mcontrBIS$; the proof is similar
-to  the analogous result for $\rapprox$}. \hlD{See} Section~\ref{s:coarsest} for
+to  the analogous result for $\rapprox$}. \hl{See} Section~\ref{s:coarsest} for
 more details.
@@
 
-\hl{The next lemma is actually Lemma 3.13} of~\citep[p.~102]{Mil89}, \hlD{and
-is needed} to prove Milner's ``unique solution of equations for
+The next lemma is actually Lemma 3.13 of~\citep[p.~102]{Mil89}, and
+is needed to prove Milner's ``unique solution of equations for
 $\sim$'' (Theorem~\ref{t:Mil89s1}):
@@
 $Q' \wb C[{\til Q}]$. (The other side from $Q_i$ follows in the same manner.)
-\hlD{See} Fig.~\ref{fig:314}.
+See Fig.~\ref{fig:314} for a visual illustration.
 \end{proof}

### 2019-09-15 paper/HOLMultivariate.tex
Updated generated TeX theories

@@
-\newcommand{\HOLMultivariateDate}{13 Settembre 2019}
-\newcommand{\HOLMultivariateTime}{10:02}
+\newcommand{\HOLMultivariateDate}{15 Settembre 2019}
+\newcommand{\HOLMultivariateTime}{21:28}
 \begin{SaveVerbatim}{HOLMultivariateDefinitionsCCSXXequationXXdef}
@@
        \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{FV} \HOLBoundVar{e} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLBoundVar{Es}
+       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
+\HOLConst{FV} \HOLBoundVar{e} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
+\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Es}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}.
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}}
-       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
+\HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
 \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}}
-       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
 \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
@@
 \newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXFOLDR}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXFOLDR}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXFOLDRYY}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{E}.
+       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{FEVERY} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{p}\ensuremath{)}.
+\HOLConst{FV} \HOLBoundVar{p} \HOLConst{\HOLTokenSubset{}} \HOLTokenLeftbrace{}\HOLBoundVar{x}\HOLTokenRightbrace{}\ensuremath{)} \ensuremath{(}\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{FOLDR} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}\ensuremath{)} \HOLBoundVar{e}.
+\ensuremath{[}\HOLBoundVar{y}\ensuremath{/}\HOLBoundVar{x}\ensuremath{]} \HOLBoundVar{e}\ensuremath{)} \HOLBoundVar{E} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}\ensuremath{)}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXFOLDRYY}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXFOLDRYY}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXISXXPROC}
@@
 \HOLBoundVar{X} \HOLConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLBoundVar{e}\ensuremath{)} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-\ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\ensuremath{[}\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{P}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}\ensuremath{)}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
+\ensuremath{[}\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{P}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXself}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXself}}
+\begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXsing}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
+\ensuremath{[}\ensuremath{[}\HOLBoundVar{E\sp{\prime}}\ensuremath{]}\ensuremath{/}\ensuremath{[}\HOLBoundVar{X}\ensuremath{]}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{E\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}
+\end{SaveVerbatim}
+\newcommand{\HOLMultivariateTheoremsCCSXXSUBSTXXsing}{\UseVerbatim{HOLMultivariateTheoremsCCSXXSUBSTXXsing}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXSING}
@@
    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
+       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E} \HOLConst{DELETE} \HOLBoundVar{Y}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-\HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
+       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E} \HOLConst{DELETE} \HOLBoundVar{Y}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
 \end{SaveVerbatim}
 \newcommand{\HOLMultivariateTheoremscontextXXrec}{\UseVerbatim{HOLMultivariateTheoremscontextXXrec}}
-\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrecYY}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
-\end{SaveVerbatim}
-\newcommand{\HOLMultivariateTheoremscontextXXrecYY}{\UseVerbatim{HOLMultivariateTheoremscontextXXrecYY}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrelab}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}.
-       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}.
-       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
+\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps}.
@@
                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLBoundVar{E\sp{\prime}} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}}
+                   \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
                    \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
@@
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{C}.
-           \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenImp{}}
+           \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
            \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{R}.
@@
                 \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLConst{contracts} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+                    \HOLBoundVar{R} \HOLConst{contracts} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
                     \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLConst{O} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}.
@@
                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLConst{contracts} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+                   \HOLBoundVar{R} \HOLConst{contracts} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
                    \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLConst{O} \HOLConst{EPS}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}\ensuremath{)}
@@
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
-           \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}}
+           \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{u} \HOLBoundVar{P\sp{\prime}}.
@@
                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+                   \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
                    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
@@
        \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}}
-       \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
+\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
        \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
@@
            \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+               \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
                \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
@@
        \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
-\HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \ensuremath{(}\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
+       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
+\HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
 \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
@@
            \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime\prime}}.
-               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C\sp{\prime\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+               \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
                \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
@@
        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
+       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E} \HOLConst{DELETE} \HOLBoundVar{Y}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
 \end{SaveVerbatim}
@@
        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
+       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E} \HOLConst{DELETE} \HOLBoundVar{Y}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
 \end{SaveVerbatim}
 \newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrec}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrec}}
-\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrecYY}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E}
-\end{SaveVerbatim}
-\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrecYY}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrecYY}}
-\begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrecXXrule}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)}
-\end{SaveVerbatim}
-\newcommand{\HOLMultivariateTheoremsweaklyXXguardedXXrecXXrule}{\UseVerbatim{HOLMultivariateTheoremsweaklyXXguardedXXrecXXrule}}
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXrelab}
@@
 \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{nu} \HOLBoundVar{L} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}.
-       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E} \HOLBoundVar{rf}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLThmTag{Multivariate}{CCS_SUBST_FOLDR}\HOLMultivariateTheoremsCCSXXSUBSTXXFOLDR
+\HOLThmTag{Multivariate}{CCS_SUBST_FOLDR'}\HOLMultivariateTheoremsCCSXXSUBSTXXFOLDRYY
 \HOLThmTag{Multivariate}{CCS_SUBST_IS_PROC}\HOLMultivariateTheoremsCCSXXSUBSTXXISXXPROC
@@
 \HOLThmTag{Multivariate}{CCS_SUBST_self}\HOLMultivariateTheoremsCCSXXSUBSTXXself
+\HOLThmTag{Multivariate}{CCS_SUBST_sing}\HOLMultivariateTheoremsCCSXXSUBSTXXsing
 \HOLThmTag{Multivariate}{CCS_SUBST_SING}\HOLMultivariateTheoremsCCSXXSUBSTXXSING
@@
 \HOLThmTag{Multivariate}{context_rec}\HOLMultivariateTheoremscontextXXrec
-\HOLThmTag{Multivariate}{context_rec'}\HOLMultivariateTheoremscontextXXrecYY
 \HOLThmTag{Multivariate}{context_relab}\HOLMultivariateTheoremscontextXXrelab
@@
 \HOLThmTag{Multivariate}{weakly_guarded_rec}\HOLMultivariateTheoremsweaklyXXguardedXXrec
-\HOLThmTag{Multivariate}{weakly_guarded_rec'}\HOLMultivariateTheoremsweaklyXXguardedXXrecYY
-\HOLThmTag{Multivariate}{weakly_guarded_rec_rule}\HOLMultivariateTheoremsweaklyXXguardedXXrecXXrule
 \HOLThmTag{Multivariate}{weakly_guarded_relab}\HOLMultivariateTheoremsweaklyXXguardedXXrelab

### 2019-09-16 ic-journal/ccs.tex
Removed all reviewed highlights in the first part of the paper; re-enable highlights

@@
 
-\hl{Here we recall the core theory of CCS.}
+Here we recall the core theory of CCS.
 We assume a possibly infinite set of names $\mathscr{L} = \{a, b,
-\ldots\}$ \hl{yielding} input and $\overline{\mbox{output}}$ labels (actions), plus a special invisible
-action $\tau \notin \mathscr{L}$, and \hl{another possibly infinite
-  set of agent} variables $A, B,
-\ldots \in \mathscr{X}$.
-The class of CCS processes is then inductively
-defined from $\nil$ \hl{(the terminated process)} and agent variables by the operators
+\ldots\}$ yielding input and $\overline{\mbox{output}}$ labels (actions), plus a special invisible
+action $\tau \notin \mathscr{L}$, and another possibly infinite
+set of agent variables $A, B, \ldots \in \mathscr{X}$.
+The class of \hl{all} CCS \hl{terms (or expressions)} is then inductively
+defined from $\nil$ (the terminated process) and agent variables by the operators
 of \emph{prefixing} (.), \emph{parallel composition} ($|$),
@@
 \end{equation*}
-\hl{In our presentation of CCS, 
-the restriction operator takes a set of  labels $L
+In our presentation of CCS, the restriction operator takes a set of labels $L
   \subseteq \mathscr{L}$, rather than a single one.  
@@
     \overline{\mathit{rf}(l)}$ (with $\bar{\bar l} = l$ for all $l \in
-    \mathscr{L}$).}
-% \hl{Notice the (minor) differences with other CCS literature
-% regarding the above definition:} 
-% \begin{enumerate}
-%   \item Some literature adopts possibly infinite sums over an index
-%     set ($\sum_{i\in I} P_i$) while we only consider binary (thus
-%     finite) sums, which is less expressive.
-%   \item Our restriction operator takes a set of (input) labels $L
-%     \subseteq \mathscr{L}$, while some CCS literature only restricts
-%     one label (for each restriction operator);
-%   \item Our relabeling operator takes a relabeling function
-%     $\mathit{rf} \colon \mathscr{L} \cup \overline{\mathscr{L}} \cup
-%     \{\tau\} \rightarrow \mathscr{L} \cup \overline{\mathscr{L}} \cup
-%     \{\tau\}$, which
-%     is capable to handle multiple actions including $\tau$. A valid
-%     relabeling function $\mathit{rf}$ must satisfy $\mathit{rf}(\tau) =
-%     \tau$ and $\forall l\in\mathscr{L} \cup
-%     \overline{\mathscr{L}}.\, \mathit{rf}(\overline{l}) = 
-%     \overline{\mathit{rf}(l)}$ (with $\bar{\bar l} = l$ for all $l \in
-%     \mathscr{L}$); Same expressiveness
-%     with single-label relabeling.
-%   \item The recursion operator $\texttt{rec}$ has the same
-%   expressiveness with  
-%     \emph{process constants} adopted in some literature. For instance, a
-%     CCS process $a.C$ with the constant $C \DSdefi b.C$ can be
-%     expressed as $a.(\texttt{rec}\, C. (b.C))$.
-% \end{enumerate}
-We sometimes omit \hl{a} trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil$.
-A CCS process $P$ may \hl{evolve} to another one, say $P'$, under
+    \mathscr{L}$).
+We sometimes omit a trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil$.
+A CCS process $P$ may evolve to another one, say $P'$, under
   an action $\mu$, written by $P \arr{\mu} P'$.
-The \hl{transition semantics} of CCS processes is given by means of
-a Labeled Transition System (LTS) \hl{expressed in Structural Operational
-Semantics (SOS) rules} shown in Fig.~\ref{f:LTSCCS}.
-(The symmetric versions of the \hl{SOS} rules for
+The transition semantics of CCS processes is given by means of
+a Labeled Transition System (LTS) expressed in Structural Operational
+Semantics (SOS) rules shown in Fig.~\ref{f:LTSCCS}.
+(The symmetric versions of the SOS rules for
 parallel composition and binary choice are omitted.)
@@
 sums are in the form $a.P + b.Q$. 
-% \hl{(Otherwise we may call the sum
-% a \emph{direct} one, e.g. $P + Q$ if either $P$ or $Q$ are not in the
-% form of prefixes.)}
 The \emph{immediate derivatives} of a
-process $P$ are elements of the set $\{P' \st P \arr\mu P' \mbox{
-  for some $\mu$}\}$.
-We use $\ell$ to range over
-visible actions (i.e.~inputs or outputs, excluding  $\tau$)
+process $P$ are elements of the set $\{P' \st P \arr\mu P' \mbox{for some $\mu$}\}$.
+We use $\ell$ to range over visible actions (i.e.~inputs or outputs, excluding  $\tau$)
 and $\alpha, \mu$  to range over all actions.

### 2019-09-16 ic-journal/contraction.tex
Removed all reviewed highlights in the first part of the paper; re-enable highlights

@@
 of doing the same work, and these could be slow (i.e., involving
-more $\tau$-\hl{actions} than those performed by $P$).
+more $\tau$-actions than those performed by $P$).
 % Thus, in contrast with expansion,  we cannot really say that `$Q$ is more efficient than
@@
 \end{enumerate}
-\hl{Two processes $P$ and $Q$ are in the \emph{bisimilarity
-    contraction}}, written as $P \mcontrBIS Q$ ($P$ \emph{contracts to} $Q$),
+Two processes $P$ and $Q$ are in the \emph{bisimilarity
+contraction}, written as $P \mcontrBIS Q$ ($P$ \emph{contracts to} $Q$),
 if $P\ \R\ Q$ for some contraction $\R$.
-\hl{Sometimes we write $\mexpaBIS$ for the inverse of $\mcontrBIS$.}
+Sometimes we write $\mexpaBIS$ for the inverse of $\mcontrBIS$.
 \end{definition}
@@
 challenges from $Q$, entirely ignores efficiency: it is the same
-clause of  weak bisimulation~---the final derivatives are \hl{indeed} required
+clause of  weak bisimulation~---the final derivatives are indeed required
 to be related  by $\wb$, rather than by $\R$.
@@
  \end{enumerate}
-\hl{Two processes $P$ and $Q$ are in the \emph{bisimilarity
-    expansion}}, written as $P \expa Q$ ($P$ \emph{expands} $Q$),
+Two processes $P$ and $Q$ are in the \emph{bisimilarity
+  expansion}, written as $P \expa Q$ ($P$ \emph{expands} $Q$),
  if $P \RR Q$ for some expansion $\R$.
@@
 formalising the idea of ``efficiency'' between processes.
-Clause (1) is the same in the \hl{both}
-preorders, while in clause (2) expansion uses 
+Clause (1) is the same in the both preorders, while in clause (2) expansion uses 
 $P \Arr \mu P'$, rather than $P \Arcap \mu P'$; 
@@
 are simply required to be bisimilar ($P' \wb Q'$).
-\hl{Intuitively, $P \expa Q$ holds if $P\wb Q$ and, in addition, \emph{$Q$
-  is always at least as efficient as $P$}.}
+Intuitively, $P \expa Q$ holds if $P\wb Q$ and, in addition, \emph{$Q$
+  is always at least as efficient as $P$}.
 
@@
 
-\hl{In the same way as bisimilarity, both the expansion and the
+In the same way as bisimilarity, both the expansion and the
 contraction preorders are preserved by all CCS operators except the
-summation. The proofs are similar, see e.g.}~\cite{sangiorgi2017equations}.
+summation. The proofs are similar, see e.g.~\cite{sangiorgi2017equations}.
 

### 2019-09-16 ic-journal/equa.tex
Removed all reviewed highlights in the first part of the paper; re-enable highlights

@@
 
-\hl{In the CCS syntax, 
+In the CCS syntax, 
 a recursion $\recu A  P$ acts as a binder for $A$ in the body $P$. 
@@
 For instance,  $X$ is free in $a.X + \recu Y (b.Y)$ while $Y$
-is bound; 
-in $a.X + \recu X (b.X)$,
- $X$ is
-both free and bound.
-%  given in previous section, there is the syntactic
-% possibility that an agent variable $A$ occurs
-% outside the recursion operator of the same variable (or, equivalently, a
-% process constant $C$ is used but undefined). We say such a variable is
-% \emph{free}, while those variables wrapped by their recursions are
-% \emph{bound}.}
-A tem
-without free variables  is a  \emph{process}.}
+is bound; in $a.X + \recu X (b.X)$, $X$ is both free and bound.
+A \hl{term} without free variables is a \emph{process}.
 % This setting does not cause any ambiguity, but sometimes leads to more
@@
 
-\hl{In this paper (and the formalisation work), we use the agent
+In this paper (and the formalisation work), we use the agent
 variables also as \emph{equation variables}. This eliminates the need of
 another type for  equations, and we can reuse the existing
-variable substitution operation} (c.f. SOS rule for the Recursion in
+variable substitution operation (c.f. SOS rule for the Recursion in
 Fig.~\ref{f:LTSCCS}) for the substitution of equation variables.
@@
 
-% \hl{In fact, free agent variables have the same transitional behavior
+% In fact, free agent variables have the same transitional behavior
 % as the deadlock $\nil$ according to the SOS rules, as there is
@@
 % exceptions are all versions of unique solution of equations/contracts,
-% where all solutions must be \emph{pure} processes (i.e. no free variable).)}
+% where all solutions must be \emph{pure} processes (i.e. no free variable).)
 
@@
 \label{ss:SysEq}
-\hl{When discussing equations it is standard to talk about `context'. This is a 
+When discussing equations it is standard to talk about `context'. This is a 
  a CCS expression  possibly containing  free variables that, however, may not occur within
 the body of recursive definitions. 
-Milner's ``unique solution of equations'' }  theorems~\cite{Mil89} intuitively
-\hl{say that, if a context $C$
+Milner's ``unique solution of equations'' theorems~\cite{Mil89} intuitively
+say that, if a context $C$
 %  \hl{(i.e., a CCS expression with possibly
@@
 bisimilar with each other.
-}
 
@@
  a countable indexing set $I$, we have variables $X_i$, and expressions
-$E_i$ \hl{possibly containing such variables $\cup_i \{ X_i\}$}. Then 
+$E_i$ possibly containing such variables $\cup_i \{ X_i\}$. Then 
 $\{ X_i = E_i\}_{i\in I}$ is 
@@
 \item The system has \emph{a unique solution for $\wb$}  if whenever 
- $\til P$ and $\til Q$ are both solutions \hl{then} $\til P \wb \til Q$. 
+ $\til P$ and $\til Q$ are both solutions then $\til P \wb \til Q$. 
 \end{itemize} 
  \end{definition}
-\hl{Similarily, the \emph{(unique) solution of a system of equations for $\sim$}
+Similarily, the \emph{(unique) solution of a system of equations for $\sim$}
 (or for $\rapprox$) can be obtained by replacing all occurrences of $\wb$
-in above definition with $\sim$ and $\rapprox$, respectively.}
+in above definition with $\sim$ and $\rapprox$, respectively.
 
@@
  $K$ and $K | b$, for $K \DSdefi \recu K {\, (a. K)}$. (Actually any process capable of
-continuously performing \hl{$a$--actions} is a solution \hl{of} $X = a|  X$.)
+continuously performing $a$--actions is a solution of $X = a|  X$.)
 
@@
 
-\item \hl{\emph{guarded}} if, in each $E_i$, each occurrence of
+\item \emph{guarded} if, in each $E_i$, each occurrence of
   each $X_i$ is underneath a \emph{visible} prefix;
@@
 \item \emph{sequential} if, in each $E_i$, each
-  \hl{occurrence of each $X_i$ is only underneath prefixes and sums.}
+  occurrence of each $X_i$ is only underneath prefixes and sums.
 \end{itemize}
@@
 
-\hl{In other words, if a system of equations is sequential, then for
+In other words, if a system of equations is sequential, then for
 each  $E_i$, any subexpression of $E_i$ in which $X_j $
 appears, apart from $X_j$ itself, is a sum of prefixed expressions.
-For instance,}
+For instance,
 \begin{itemize}
@@
 
-\hl{Milner has  three versions of  ``unique solution of equations''
+Milner has  three versions of  ``unique solution of equations''
 theorems, for $\sim$, $\wb$ and $\rapprox$, respectively, though only the
-following two versions are explicitly mentioned} in~\citep[p.~103, 158]{Mil89}:
+following two versions are explicitly mentioned in~\citep[p.~103, 158]{Mil89}:
 \begin{theorem}[unique solution of equations for $\sim$]
@@
 
-\hl{The version of Milner's unique-solution theorem for $\wb$ further requires
-that all sums are guarded}:
+The version of Milner's unique-solution theorem for $\wb$ further requires
+that all sums are guarded:
 % \footnote{But if the CCS syntax were defined with only guarded
@@
 \label{t:Mil89}
-Let $E_i$ be \hl{guarded}  and sequential with free
+Let $E_i$ be guarded and sequential with free
 variables up to $\til X$, and let ${\til P} \wb {\til E}\{\til P /\til X\}$,

### 2019-09-16 ic-journal/expansion.tex
Removed all reviewed highlights in the first part of the paper; re-enable highlights

@@
 \label{d:wb}
-A process relation ${\R}$ is a \hl{(weak)} \emph{bisimulation} if, whenever
- $P\RR Q$\hl{,} % for all $\mu$ we have:
+A process relation ${\R}$ is a (weak) \emph{bisimulation} if, whenever
+ $P\RR Q$, % for all $\mu$ we have:
 \begin{enumerate}
@@
 \item $Q \arr\mu Q'$,implies that there is $P'$ such that $P \Arcap
-  \mu P'$ and $P' \RR Q'$\hl{;}
+  \mu P'$ and $P' \RR Q'$;
 \end{enumerate}
- $P$ and $Q$ are \hl{(weakly)} \emph{bisimilar},
+ $P$ and $Q$ are (weakly) \emph{bisimilar},
 written as $P \wb Q$, if $P \RR Q$ for some bisimulation $\R$.
@@
 
-\hl{\emph{Strong} bisimulation and strong bisimilarity} ($\sim$)
+\emph{Strong} bisimulation and strong bisimilarity ($\sim$)
 can be obtained by replacing the weak transition $Q\Arcap\mu Q'$ in the above
@@
 Weak bisimilarity is not preserved by the sum operator (except for
-guarded sums), i.e.\  $P_1 \wb Q_1$ and $P_2 \wb Q_2$  \hl{does not imply}
+guarded sums), i.e.\  $P_1 \wb Q_1$ and $P_2 \wb Q_2$  \hl{do} not imply
  $P_1 + P_2 \wb Q_1 + Q_2$.
@@
 Two processes $P$ and $Q$ are \emph{rooted bisimilar}, written as $P
-\rapprox Q$, \hl{if} % for all $\mu$:
+\rapprox Q$, if % for all $\mu$:
 %  for all $\mu\in \mathscr{L}\cup\{\tau\}$
@@
 
-\hl{The above definition also brings up a proof technique for proving rooted
+The above definition also brings up a proof technique for proving rooted
 bisimilarity from a given bisimulation. The next
 lemma plays an
-important role in proving some key results in this paper:}
+important role in proving some key results in this paper:
 \begin{lemma}[Rooted bisimilarity by bisimulation]
 \label{l:obsCongrByWeakBisim}
-\hl{Given a (weak) bisimulation $\RR$, suppose two processes $P$ and $Q$
-satisfy the following properties}:
+Given a (weak) bisimulation $\RR$, suppose two processes $P$ and $Q$
+satisfy the following properties:
 \begin{enumerate}
@@
    \Arr\mu Q'$ and $P' \RR Q'$;
-\item $Q \arr\mu Q'$ \hl{implies that there is} $P'$ such that $P
+\item $Q \arr\mu Q'$ implies that there is $P'$ such that $P
    \Arr\mu P'$ and $P' \RR Q'$.
 \end{enumerate}
-\hl{Then} $P$ and $Q$ are rooted bisimilar, i.e.~$P \approx^c Q$.
+Then $P$ and $Q$ are rooted bisimilar, i.e.~$P \approx^c Q$.
 \end{lemma}
@@
 indeed the coarsest congruence contained in bisimilarity
-(c.f. Section~\ref{s:coarsest} for more details):
+(c.f. Section~\ref{s:coarsest} and \hl{\mbox{Section~\ref{ss:context}}} for more details):
 \begin{theorem}

### 2019-09-16 ic-journal/intro.tex
Removed all reviewed highlights in the first part of the paper; re-enable highlights

@@
 
-\hl{Milner's unique-solution theorem for weak bisimilarity, however,
-has severe syntactic limitations:}
+Milner's unique-solution theorem for weak bisimilarity, however,
+has severe syntactic limitations:
 the equations must be both \emph{guarded} and \emph{sequential}. That is,
-variables of the equations \hl{can only occur underneath visible prefixes and summations.}
-One way \hl{to overcome} such limitations is to replace the equations
+variables of the equations can only occur underneath visible prefixes and summations.
+One way to overcome such limitations is to replace the equations
 with special inequations called
@@
 preorder that, roughly, places some efficiency constraints on processes.
-\hl{The unique solution of contractions is defined as with equations:}
+The unique solution of contractions is defined as with equations:
 any two solutions must be componentwise bisimilar.
-The difference \hl{from} equations is \hl{in} the meaning of a solution:
+The difference from equations is in the meaning of a solution:
 in the case of contractions the solution is evaluated with respect to
 the contraction preorder, rather than bisimilarity. 
-With contractions, most syntactic limitations of the unique-solution theorem \hl{are
-eliminated}. One constraint that still remains
+With contractions, most syntactic limitations of the unique-solution theorem are
+eliminated. One constraint that still remains
 in~\cite{sangiorgi2017equations}
@@
 restrictive CCS syntax)
-is the occurrences of %\emph{direct} 
-\hl{sums} (e.g.~$P + Q$) due to
-the \hl{non-substitutivity of the contraction preorder in this case}.
+is the occurrences of sums (e.g.~$P + Q$) due to
+the non-substitutivity of the contraction preorder in this case.
 
- \hl{This paper presents}  a
-comprehensive formalisation of Milner's Calculus of Communicating
+This paper presents a comprehensive formalisation of Milner's Calculus of Communicating
 Systems (CCS) in the HOL theorem prover (HOL4),
 with a focus towards the theory of unique solutions of equations and contractions.
-\hl{Many results in Milner's CCS book}~\cite{Mil89} are covered, since
+Many results in Milner's CCS book~\cite{Mil89} are covered, since
 the unique-solution theorems rely on a large number of fundamental results.
 Indeed the formalisation encompasses all basic properties of strong and weak
-\hl{bisimilarities} (e.g.~the fixed-point and substitutivity properties), the
+bisimilarities (e.g.~the fixed-point and substitutivity properties), the
 basic properties of rooted bisimilarity and their algebraic laws.
@@
 \emph{rooted bisimilarity} (hence also for bisimilarity itself), and places no 
-\hl{constraints on the use the sum operator}.
+constraints on the use the sum operator.
 
@@
   case, where  more than one equation
-  (or contraction) \hl{with multiple equation variables is considered.}
+  (or contraction) with multiple equation variables is considered.
 The \univariate theorems use
@@
 unique-solution result for rooted bisimilarity.
-Section~\ref{s:for} highlights our formalisation in HOL4 for the
-\univariate case.
-Section~\ref{sec:multivariate} describes the \hl{extension} to the
-  \multivariate case.
+Section~\ref{s:for} highlights our formalisation in HOL4 for the \univariate case.
+Section~\ref{sec:multivariate} describes the \hl{extension} to the \multivariate case.
 Finally,  Section~\ref{s:rel} and \ref{s:concl} discuss related work,

### 2019-09-16 ic-journal/multivariate.tex
Removed all reviewed highlights in the first part of the paper; re-enable highlights

@@
 
-In this section,  \hl{we discuss the formalisation of the} \multivariate
+In this section,  we discuss the formalisation of the \multivariate
 cases of Milner's ``unique solution of equations (for $\sim$)''
@@
 \hl{This formalisation only supports finitely many
-  equations/contractions and equation variables.\footnote{The original theorems
+  equations/contractions and equation variables.}\footnote{\hl{The original theorems
 hold for even (uncountably) infinite equations and equation variables.}}
@@
 representation of CCS equations (expressions, contexts).
-\hl{In the} \univariate formalisation, $\lambda$-functions (of type
+In the \univariate formalisation, $\lambda$-functions (of type
 $CCS\rightarrow CCS$) are used to represent \univariate CCS
-\hl{equations, and variable substitutions are simply 
-calls to $\lambda$-functions on the target CCS terms.}
+equations, and variable substitutions are simply 
+calls to $\lambda$-functions on the target CCS terms.
 This idea cannot be extended to the \multivariate case, as
@@
 
-% : dealing with another CCS-like type makes the
-% whole formalisation work ugly and we loose the (possibly valuable) bisimilarity concepts and
-% transitional semantics of CCS expressions; on the other hand,
-% modifying the CCS datatype to just support the formalisation of
-% unique-solution theorems is also not acceptable.
-
-\hl{In this project, we have followed} Milner~\cite{Mil89}, using the
+In this project, we have followed Milner~\cite{Mil89}, using the
 same alphabet for both agent variables and equation variables.
-This has allowed a large reuse of the \univariate formalisation. \hl{For instance, 
-the variable
-substitution function used in SOS rules [\texttt{REC}] can be also
+This has allowed a large reuse of the \univariate formalisation.
+For instance, the variable
+substitution function used in SOS rules \texttt{REC} can be also
 used for substituting eqaution variables.
@@
 fundamental lemmas, mostly due to the variable capture issues between
-equation variables and agent variables.}
+equation variables and agent variables.
 
@@
 Furthermore, $E$ is a process, written \HOLinline{\HOLConst{IS_PROC} \HOLFreeVar{E}}, if
-\hl{it does not contain any free variable}, i.e. $\fv{E} = \emptyset$:
+it does not contain any free variable, i.e. $\fv{E} = \emptyset$:
 \begin{alltt}
@@
 from a CCS expression to its sub-expressions, the set of free
-variables may increase, while the set of bound variables \hl{either
-remains the same or decreases}. For instance, $\fv{\recu X (\mu.X)} = \emptyset$, while
+variables may increase, while the set of bound variables either
+remains the same or decreases. For instance, $\fv{\recu X (\mu.X)} = \emptyset$, while
 $\fv{\mu.X} = \{X\}$. This property of $\fv{\cdot}$ brings some
 difficulities when doing proofs about CCS transitions. As an evidence,
-we prove the following fundamental result about $\fv{\cdot}$:
+we prove the following fundamental result about $\fv{\cdot}$\hl{\mbox{~\citep[p.~1209]{milner1990operational}}}:
 
@@
 
-\hl{Milner said it can be proved by ``an easy action
-induction''}~\cite{milner1990operational}.
-From HOL's viewpoint, the so-called ``action induction'' is actually a higher-order \hl{application}
+\hl{Milner said it can be proven by ``an easy action induction''.}
+From HOL's viewpoint, the so-called ``action induction'' is actually a higher-order application
 of the following \emph{induction principle} generated together with SOS
-rules (which essentially says \hl{that} \HOLinline{\HOLConst{TRANS}} is the smallest relation
+rules (which essentially says that \HOLinline{\HOLConst{TRANS}} is the smallest relation
 satisfying SOS rules):
@@
 $X$ under this specific $P$, by Modus Ponens (MP) the original proof
-\hl{would have completed.}
+would have completed.
 This is the essence of action induction.
@@
 subgoals, each corresponding to one SOS rule. For instance, in
-\hl{the subgoal for \texttt{SUM1} we need to prove}
+the subgoal for \texttt{SUM1} we need to prove
 $\fv{E_1} \subseteq \fv{E} \Longrightarrow
@@
 Knowing \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} we cannot prove \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}.
-However, if we knew \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, then \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\ensuremath{=}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, and \hl{then}
+However, if we knew \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, then \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\ensuremath{=}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, and then
 \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}, no matter if \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E}} or not, and the proof
-\hl{would have completed.} Thus it remains to show that
+would have completed. Thus it remains to show that
 \begin{alltt}
@@
 occurences of $X$ in $E$ are correctly bypassed.
-\hl{Since} \HOLinline{\HOLConst{CCS_SUBST}} only runs
+Since \HOLinline{\HOLConst{CCS_SUBST}} only runs
 once on each subterm, the possible free variables in  \HOLinline{\HOLFreeVar{Ps}} are never
@@
 \begin{lemma}[\texttt{CCS_SUBST_nested}]
-Under certain conditions \hl{(to get rid of substitution orders)}, two nested substitutions can be
+Under certain conditions (to get rid of substitution orders), two nested substitutions can be
 converted into a single substitution where the targets are substituted first:
@@
 holds because \HOLinline{\HOLConst{WG}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\ensuremath{)}}
-holds \hl{as a base case of the inductive definition of} \HOLinline{\HOLConst{WG}}:
+holds as a base case of the inductive definition of \HOLinline{\HOLConst{WG}}:
 \begin{alltt}
@@
 \end{alltt}
-\hl{For} any agent variable $X$, we have \hl{by $\beta$-reduction:}
+For any agent variable $X$, we have by $\beta$-reduction:
 \HOLinline{\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{P}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{var}\\\;\HOLFreeVar{X}\ensuremath{)}\\\;\HOLSymConst{\ensuremath{=}}\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{P}} (or ``$l.X + P$'' in textbook
@@
 existing \univariate definitions, which is the approach we have followed.
-For \hl{example}, to see the weak guardedness of $a.X + b.X + c.Y$, it is
+For example, to see the weak guardedness of $a.X + b.X + c.Y$, it is
 natural to focus on each (free) variable: if we substitute each
@@
 Also note that \HOLinline{\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{Y}\\\;\HOLSymConst{\ensuremath{=}}\\\;\ensuremath{[}\HOLFreeVar{t}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\ensuremath{(}\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{Y}\ensuremath{)}}
-can be expressed as a \univariate \hl{substitution of the original term.}
+can be expressed as a \univariate substitution of the original term.
 This idea leads to the following definitions:

### 2019-09-16 ic-journal/unique.tex
Removed all reviewed highlights in the first part of the paper; re-enable highlights

@@
 
-\hl{Now we recall the ``unique solution of
-contractions'' theorem}~\cite{sangiorgi2017equations},
-\hl{which weakens} the requirements of Milner's result
+Now we recall the ``unique solution of
+contractions'' theorem~\cite{sangiorgi2017equations},
+which weakens the requirements of Milner's result
 (Theorem~\ref{t:Mil89}).
@@
 such that $R \mcontrBIS \ctp{\til P}$ and $\ct{\til Q} \Arcap{\mu} R'
- \wb \ctp{\til Q}$ \hl{for some $R'$}.
+ \wb \ctp{\til Q}$ for some $R'$.
 \end{lemma}
@@
 \begin{proof}{(sketch from~\cite{sangiorgi2017equations})}
-  Let $n$ be the length \hl{(the number of one-step transitions)} of
-\hl{a} transition $\ct{\til P}\Arr\mu R$, and
+  Let $n$ be the length (the number of one-step transitions) of
+a transition $\ct{\til P}\Arr\mu R$, and
 let $\ctpp {\til P}$ and $\ctpp {\til Q}$  be the processes obtained
@@
 we derive 
-$\ct{\til Q}\Arcap{\mu} R' \wb \ctp{\til Q}$ \hl{for some $R'$}.
+$\ct{\til Q}\Arcap{\mu} R' \wb \ctp{\til Q}$ for some $R'$.
 \end{proof}
@@
 \label{t:contraBisimulationU} % was: Thm 3.10
-\hl{Let $E_i$ be weakly guarded (and with guarded sums only) with free
+Let $E_i$ be weakly guarded (and with guarded sums only) with free
 variables in $\til X$, and let $\til P \mcontrBIS \til E\{\til P/\til X\}$,
-    $\til Q \mcontrBIS \til E\{\til Q/\til X\}$. Then $\til P \wb \til Q$.}
+    $\til Q \mcontrBIS \til E\{\til Q/\til X\}$. Then $\til P \wb \til Q$.
 \end{theorem}
@@
 \begin{proof}
-\hl{We  prove $P_i \wb Q_i$ (for each $i \in I$) by considering} the following relation
+We  prove $P_i \wb Q_i$ (for each $i \in I$) by considering the following relation
 \begin{equation*}
 \R \DSdefi \{(R,S) \st R \wb \ct{\til P}, S \wb \ct{\til Q} \mbox{~for some context
-$\qct$ (\hl{with only guarded sums})} \} \enspace.
+$\qct$ (with only guarded sums)} \} \enspace.
 \end{equation*}
@@
 the fact that $\mcontrBIS$ implies $\wb$). It remains to
-show that $\R$ is a bisimulation. Suppose \hl{$(R, S) \in \R$ via} a context
-$C$. \hl{For any $R'$ such that $R \arr{\mu} R'$, we have to find a} $S'$ with $S \Arcap{\mu}
+show that $\R$ is a bisimulation. Suppose $(R, S) \in \R$ via a context
+$C$. For any $R'$ such that $R \arr{\mu} R'$, we have to find \hl{an} $S'$ with $S \Arcap{\mu}
 S'$ and $(R', S') \in \R$. From $R \wb C[{\til P}]$, we derive $C[{\til P}]
@@
 there exists $C'$ with $R'' \mcontrBIS C'[{\til P}]$ and $C[{\til Q}]
-\Arcap{\mu} S'' \wb C'[{\til Q}]$ for some $S''$. \hl{From $S \wb C[{\til
+\Arcap{\mu} S'' \wb C'[{\til Q}]$ for some $S''$. From $S \wb C[{\til
   Q}]$ and $C[{\til Q}] \Arcap{\mu} S''$, by induction and definition of $\wb$, we find
- $S'$} with $S \Arcap{\mu} S'$. This \hl{completes} the
-proof, as we have $R' \wb C'[{\til P}]$ and $S' \wb C'[{\til Q}]$ \hl{by
+ $S'$ with $S \Arcap{\mu} S'$. This completes the
+proof, as we have $R' \wb C'[{\til P}]$ and $S' \wb C'[{\til Q}]$ by
 transitivity of $\wb$ and the fact that $\mcontrBIS$ implies $\wb$.
-(The other side from $S$ follows in the same manner.)}
+(The other side from $S$ follows in the same manner.)
 See Fig.~\ref{fig:310} for a visual illustration.
@@
 in addition to $\wb$).
-However, comparing with Milner's Theorem~\ref{t:Mil89s1}, \hl{there is
+However, comparing with Milner's Theorem~\ref{t:Mil89s1}, there is
 a constraint: the involved CCS expression may only
@@
 on guarded sums, we have extended the idea of contractions by moving
-to \emph{rooted contractions}:}
+to \emph{rooted contractions}:
 
@@
 
-\hl{The above definition was found with the help of interactive theorem proving.}
-\hl{The following two principles were adopted when searching
+The above definition was found with the help of interactive theorem proving.
+The following two principles were adopted when searching
 for a possible definition: (1) the definition should not be coinductive,
-along the lines of rooted bisimilarity} $\rapprox$ (Def.~\ref{d:rootedBisimilarity});
+along the lines of rooted bisimilarity $\rapprox$ (Def.~\ref{d:rootedBisimilarity});
 (2) the definition should be built on top of  the existing \emph{contraction}
 relation $\mcontrBIS$.
-% \hl{Then several candidates were quickly checked (using very similar
-%   proof steps): the key is to prove its transitivity, and whenever the
-%   proof attempts failed we tried to fix the definition. Eventually the
-%   above definition was found and shown to be a precongruence, i.e. it
-%   is preserved by all CCS operators except the Recursion, same as in
-%   the cases of $\sim$ and $\rapprox$.}
-\hl{Furthermore, we needed to show that the definition found is the
+Furthermore, we needed to show that the \hl{found} definition is the
 best possible one, by showing that it yields the coarsest precongruence
-contains in $\mcontrBIS$; the proof is similar
-to  the analogous result for $\rapprox$}. \hl{See} Section~\ref{s:coarsest} for
+contains in $\mcontrBIS$; the proof is similar \hl{with}
+the analogous result for $\rapprox$. See Section~\ref{s:coarsest} for
 more details.
@@
 such that $R \mcontrBIS \ctp{\til P}$ and  $\ct{\til Q} \Arr{\mu} R'
- \wb \ctp{\til Q}$ \hl{for some $R'$}.
+ \wb \ctp{\til Q}$ for some $R'$.
 \end{lemma}
-% The proof of Lemma~\ref{l:ruptocon} is exactly the same as of
-% Lemma~\ref{l:uptocon}, \hl{because all we need from $\mcontrBIS$ (or
-% $\rcontr$) is their substitutivity properties (as precongruences)
-% w.r.t the corresponding definitions of contexts.}
-% Notice also that, the conclusion of
-% Lemma~\ref{l:ruptocon} still uses $\mcontrBIS$, as $\rcontr$ does
-% not hold.
 
@@
 
-\begin{theorem}[Unique solution of \hl{rooted} contractions]
+\begin{theorem}[Unique solution of rooted contractions]
 \label{t:rcontraBisimulationU}
-\hl{Let $E_i$ be weakly guarded with free variables in $\til X$,
+Let $E_i$ be weakly guarded with free variables in $\til X$,
 and let $\til P \rcontr \til E\{\til P/\til X\}$,
-    $\til Q \rcontr \til E\{\til Q/\til X\}$. Then $\til P \rapprox \til Q$.}
+    $\til Q \rcontr \til E\{\til Q/\til X\}$. Then $\til P \rapprox \til Q$.
 \end{theorem}
@@
 \begin{proof}
-\hl{We  prove $P_i \rapprox Q_i$ (for each $i \in I$) by considering}
+We  prove $P_i \rapprox Q_i$ (for each $i \in I$) by considering
 the following relation
@@
 (using Lemma~\ref{l:ruptocon}
-in place of Lemma~\ref{l:uptocon}), \hl{we can prove that $(P_i, Q_i)
-\in\R$ and $\R$ is indeed a bisimulation. But this only shows $P_i \wb Q_i$.}
+in place of Lemma~\ref{l:uptocon}), we can prove that $(P_i, Q_i)
+\in\R$ and $\R$ is indeed a bisimulation. But this only shows $P_i \wb Q_i$.
 %
 To further show $P_i \rapprox Q_i$, we appeal to
-Lemma~\ref{l:obsCongrByWeakBisim}: \hl{for any $P'$ such that $P_i \arr{\mu} P'$, we have to
+Lemma~\ref{l:obsCongrByWeakBisim}: for any $P'$ such that $P_i \arr{\mu} P'$, we have to
   find a $Q'$ with $Q_i \Arr{\mu} Q'$ and $(R',S') \in \R$.
@@
 From $P_i \rcontr E_i[{\til P}]$, by definition of $\rcontr$ we derive $E_i[{\til P}] \arr{\mu}
-P''$ for some $P''$.} Then by Lemma~\ref{lem:milner313} there exists a context
+P''$ for some $P''$. Then by Lemma~\ref{lem:milner313} there exists a context
 $E'$ with $P'' = E'[{\til P}]$ and $E_i[{\til Q}] \arr{\mu} E'[{\til Q}]$.
@@
   Q}]$, by definition of $\rcontr$ we have $Q_i \Arr{\mu} Q'$ for some
-$Q'$ and $Q' \wb E'[{\til Q}]$. This \hl{completes} the proof, as we have
+$Q'$ and $Q' \wb E'[{\til Q}]$. This completes the proof, as we have
 $P' \wb C[{\til P}]$ (by the fact that $\mcontrBIS$ implies $\wb$) and
@@
 \end{figure}
+
+% next file: formal.htex

### 2019-09-17 ic-journal/coarsest.tex
Cleanup old highlights in coarsest.htex

@@
   \texttt{CC\_def}, as this is anyhow obtained from the trivial context $(\lambda x.\,x)$.
-\hl{The next result shows that, for any binary} relation $R$ 
+The next result shows that, for any binary relation $R$ 
 on CCS processes, the composition closure of $R$ is always at least as
-fine as $R$\hl{:} ($\subseteq_r$ stands for \emph{relational subset}.)
+fine as $R$: ($\subseteq_r$ stands for \emph{relational subset}.)
 \begin{alltt}
@@
 Furthermore, we prove that any (pre)congruence contained in $R$
-\hl{(which needs not to be itself a (pre)congruence)}
+(which needs not to be itself a (pre)congruence)
 is contained in the composition closure of $R$
@@
 The formal proofs  of the above two results follow Milner's proof~\cite{Mil89}.
-The assumption \hl{in} Milner's result 
+The assumption in Milner's result 
 requires $\mathrm{fn}(p) \cup
@@
   names}), and is therefore strictly stronger than the assumption in
-our result above. \hl{Indeed, in our result we} only look at immediate weak
-derivatives for $p$ and $q$, \hl{and only requires that there is an input
-or output action}
-that never appears as a label. \hl{Furthermore, such an action need
+our result above. Indeed, in our result we only look at immediate weak
+derivatives for $p$ and $q$, and only requires that there is an input
+or output action
+that never appears as a label. Furthermore, such an action need
 not to be the same for $p$ and for $q$,
 as an action $a$ and its complementary $\outC a$ are
-considered as \emph{different} actions.}
+considered as \emph{different} actions.
 
@@
 
-To \hl{actually} construct this process $k$,
+To actually construct this process $k$,
  the proof relies on arbitrary infinite sums of 
@@
 transitions.
-\hl{There could be infinitely many such sub-processes, even on finitely
-branching processes.}
+There could be infinitely many such sub-processes, even on finitely
+branching processes.
 We can, however, consider the equivalence classes of CCS processes
@@
 
-\hl{Following the inductive structure of the definition of Klop processes,}
+Following the inductive structure of the definition of Klop processes,
   and using the SOS rules

### 2019-09-17 ic-journal/coarsest.tex
Fixed some minor issues in coarsest and bisim.htex

@@
 expressed informally as below~\cite{van2005characterisation,Gorrieri:2015jt,Mil89}:
-\begin{proposition}
+\begin{proposition}[\hl{$\rapprox$ is the coarsest congruence contained in $\wb$}]
 \label{prop:coarsest}
@@
 \begin{alltt}
-   \HOLConst{WEAK_CONGR} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{CC} \HOLConst{WEAK_EQUIV}\hfill{[WEAK_CONGR]}
    \HOLConst{CC} \HOLFreeVar{R} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}.
@@
 \HOLConst{CONTEXT} \HOLBoundVar{c} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \ensuremath{(}\HOLBoundVar{c} \HOLBoundVar{g}\ensuremath{)} \ensuremath{(}\HOLBoundVar{c} \HOLBoundVar{h}\ensuremath{)}\ensuremath{)}\hfill{[CC_def]}
+   \HOLConst{WEAK_CONGR} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{CC} \HOLConst{WEAK_EQUIV}\hfill{[WEAK_CONGR]}
 \end{alltt}
-We do not need to put $R\ g\ h$ in the antecedent of
+We do not need to put $R\ g\ h$ \hl{into} the antecedents of
   \texttt{CC\_def}, as this is anyhow obtained from the trivial context $(\lambda x.\,x)$.
@@
 \end{alltt}
-Furthermore, we prove that any (pre)congruence contained in $R$
-(which needs not to be itself a (pre)congruence)
+Furthermore, we prove that any (pre)congruence contained in $R$, \hl{who
+itself} needs not to be a (pre)congruence,
 is contained in the composition closure of $R$
-(hence the closure is the coarsest one):
+(hence the \hl{composition} closure is the coarsest one):
 \begin{alltt}
@@
 which in turn is trivially contained in \texttt{SUM_EQUIV}, as shown
-in Fig.~\ref{fig:relationship}. Thus, to prove (\ref{prop:coarsest}),
+in Fig.~\ref{fig:relationship}. Thus, to prove \hl{Prop.}~\ref{prop:coarsest},
 the crux is to prove that \texttt{SUM_EQUIV} implies
@@
 
-Under the free action assumptions, the actual formalisation of (\ref{equa:pq}) says:
+\hl{The} actual formalisation of (\ref{equa:pq}) says:
 \begin{theorem}[\texttt{COARSEST_CONGR_RL}]

### 2019-11-18 ic-journal/response-letter2.tex
Fixed the critical typo in Definition 4.6; added a new covering letter

\newcommand{\Mark}{{\underline{\tt R:} }}

\begin{center}
\textbf{
{\small Changes for Submission 1 to SI:EXPRESS/SOS'18 (2nd Round)}\\[5mm]
{\large Unique Solutions of Contractions, CCS, and their HOL
  Formalisation
}}
\end{center}

\vskip 10pt
\noindent

(TODO)
% We would like to thank the reviewers for many useful
% comments and suggestions. We believe we have taken all of them into consideration, as best
% as we could.

% The main addition, here again following the recommendations of the reviewers 
% has been the extension of the our central theorems 
% to the multivariable case (ie., moving from ``unique solution theorems'' for a single
% equations, or contractions,  to multi-equations  or multi-contractions). 
%  This has been a significant effort (also because a few alternative ways to make the
%  extension had to be examined). At the end, this work 
% consists of another 4,000 lines of proof scripts and a whole new
% Section 5 in the paper.

In the following, we discuss the changes to the paper and provide a
point-by-point reply to the issues that have been raised.

Our answers are marked  with a `` \Mark''  at the beginning.

\ \\

Best regards,
\begin{flushright}
  Chun Tian and Davide Sangiorgi \\
  (TODO) December 22, 2019
\end{flushright}

\vspace{1cm}

\section*{Responses to Review 1}

\subsection*{Meta comments}

\begin{enumerate}

\item \begin{quote}
    The multivariable case has been added. This is great: it makes the result stronger, and adds a real improvement over the conference version. 
  \end{quote}
  \Mark
  Thanks.

\item \begin{quote}
Overall the authors did address the minor comments. But the paper
still contains quite a few grammatical and other minor mistakes, also
in the newly added text. Below are a couple that I found just browsing
again through the paper; but this is certainly inexhaustive and the
authors should do some more careful proofreading.
\end{quote}
\Mark
(TODO) We have done a more careful proofreading and fixed all
grammatically wrong sentences in the paper.

\item \begin{quote}
    In fact, one of the corrections appears to have introduced a new
    bug: Theorem 4.7 in the new version is wrong; I guess Def. 4.6
    should be about weak transitions. In the original submission,
    there was verbatim copied proof code, which was however
    correct. But as it stands now, it suffers from the famous problem
    with weak bisimulation up-to found by the second author (one can
    simply use the same counterexample $\{(\tau. a , 0)\}$).
  \end{quote}
  \Mark
  This is an embarassing typo. The two $\arr{\mu}$ in
  Definition 4.6 should be $\Arr{\mu}$ instead. Our actual formalization is
  correct. Below is the fixed part of Definition 4.6:
\begin{enumerate}
\item Whenever $P \Arr{\mu} P'$ then, for some $Q'$, $Q \Arcap{\mu} Q'$ and $P' \wb \S \wb Q'$,
\item Whenever $Q \Arr{\mu} Q'$ then, for some $P'$, $P \Arcap{\mu} P'$ and $P' \wb \S \wb Q'$.
\end{enumerate}

\end{enumerate}

\subsection*{Detailed comments}

### 2019-11-18 ic-journal/response-letter2.tex
Fixed the blue "rec" keywords

@@
 \subsection*{Detailed comments}
+
+\begin{enumerate}
+  \item \begin{quote}
+25 "essentially formalised" => "essentially formalising" ? something is grammatically off with this sentence
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+47 ", then consider" => ". Then we consider" or something like that
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+311 "break the logic consistencies" break the logical consistency?
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+337 "rec" is blue
+\end{quote}
+  \Mark Fixed. The ``rec'' was wrongly identified as the keyword of ML
+  languages in the \LaTeX{} verbatim package that we used.
+
+  \item \begin{quote}
+323 and around: why is "a" in italics and $\bar{b}$ not?
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+sec 4.2: I'm now totally lost on the meaning of $(\alpha, \beta) CCS$.
+First $\beta$ is a label, then an action, and then there is some mystifying text between brackets (l328) about how this is not explained.
+*Please* just explain clearly what $\alpha$ and $\beta$ mean in $(\alpha, \beta) CCS$.
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+370 spurious \texttt{CCS_Subst} on line 370
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+530 "for the contraction" the contraction what? the game? functional? or remove "the"
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+555 "an “up-to” techniques." => "“up-to” techniques."
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+566 "the resulting ``weak bisimulation up``" correct; also the `` at the right should be ''
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+597 "not powerful *enough* to prove" 
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+600 perhaps point out that this is (almost) 
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+608 "This theorem is of special interests to us, because within our framework it seems impossible to prove it without any limitation" interests => interest; also, I do not really understand this sentence (which limitation?)
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+965 "Recall *from* the beginning of Section 3 *that*"
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+985 Is there anything fundamentally interesting going on in the proof? Otherwise perhaps remove it or replace by a high-level description?
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+1066 "the proof cannot complete" ?
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+1075 "substitutes each possibly occurrences" "substitues each possible occurence"
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+page 30: some the text in these lemma's is essentially (informal) explanation, with the HOL code giving the formal statements.
+Perhaps move the text out of the lemma environment?
+This will also make it look better, as it's now a full page of lemma's.
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+1149: "Recall *that* in"
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+1160: So the idea is that, whenever we replace a variable by a hole and view the other variables as constants, this is a single variable context - right?
+Perhaps this (expressed in line 960) can be emphasised again around here (but not entirely sure).
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+1165: "used *to* assert"
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+1169 add colon after e.g.
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+1171 add "then" after the comma 
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+1175 "The similar properties" => "Similar properties"
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+1182 "Not every expression fit with CCS syntax " ?
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+1210 "optional restriction" ?
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+1219 "that, the set" remove comma; also "must be disjoint" => "is disjoint"
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+1241 "while Milner did not pointed out explicitly," grammar
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+1293 " for people who can read them" sounds a bit strange; also the last sentence of the paragraph suggest most people could
+\end{quote}
+  \Mark
+
+  \item \begin{quote}
+1293-1294 "For some other textbook proofs (..) formalisation work." perhaps give a pointer to an instance where this was the case?
+\end{quote}
+  \Mark
+
+\end{enumerate}

### 2019-11-18 ic-journal/formal.tex
Minor fixes, closing the paper
Final fixes; disabled highlights
Clean up some old (confirmed) highlights

--- 2019-09-14 ic-journal/formal.tex
@@
 We highlight here a formalisation of CCS in the HOL theorem prover
-(HOL4)~\cite{Melham:1993vl,slind2008brief}, \hl{with a focus towards the
+(HOL4)~\cite{Melham:1993vl,slind2008brief}, with a focus towards the
 theory (and formal proofs) of the unique solution of
-equations/contractions theorems} mentioned in Section~\ref{s:eq} and
+equations/contractions theorems mentioned in Section~\ref{s:eq} and
 \ref{s:mcontr}.
-%  The main purpose is to convince the readers that, there's no flaw
-%  in the informal proofs. 
-% \hl{The univariate versions of these theorems, apart from minor fixes and
-% extensions in this paper, was already described in}
-% \cite{Tian:2017wrba}. The multivariate proofs and the related results
-% are new, and will be described in Section~\ref{sec:multivariate}.
 All proof scripts are available as part of HOL's official
@@
 \cite{gordon1979edinburgh,milner1972logic} by Robin Milner and others
-since \hl{1972. It} is a variant of
+since 1972. It is a variant of
 Church’s Simple Theory of Types (STT)~\cite{church1940formulation},
@@
 % inconsistent). 
-Indeed the HOL has \hl{considerably} simpler logical
+Indeed the HOL has considerably simpler logical
 foundations than most other theorem provers. %, e.g. Coq. 
-\hl{As a consequence, theories and proofs verified in HOL are easier to understand
+As a consequence, theories and proofs verified in HOL are easier to understand
  to people who are not familar with more advanced
-dependent type theories.}
+dependent type theories.
 
@@
 \begin{enumerate}
-\item the underlying implementation language for the core HOL engine;
-\item \hl{the language in which proof tactics are implemented;}
-\item \hl{the interface  language of the HOL proof scripts and
-  interactive shell.}
+\item \hl{The} underlying implementation language for the core HOL engine;
+\item \hl{The} language in which proof tactics are implemented;
+\item \hl{The} interface language of the HOL proof scripts and interactive shell.
 \end{enumerate}
@@
 The deductive system of the HOL is specified by eight primitive
-derivation rules: (c.f.~\cite{hollogic} for more details.)
+derivative rules: (c.f.~\cite{hollogic} for more details.)
 \begin{enumerate}
@@
 of theorems are correct, then any proof which successfully completes must
-be correct.
+be correct. This is also the case here: SOS rules of CCS are
+\emph{not} axioms but consequences of the inductive relation\hl{, the
+  CCS transition $\rightarrow$}.
 

### 2019-11-18 ic-journal/intro.tex
Clean up some old (confirmed) highlights

@@
  with the hypothesis that no process uses up all labels;
-the other without such hypothesis, essentially formalised van Glabbeek's proof~\cite{van2005characterisation}.
+the other without such hypothesis, essentially \hl{formalising} van Glabbeek's proof~\cite{van2005characterisation}.
 Similar results are also proved for the rooted contraction preorder.
@@
 
-We first consider the case of a single equation (or contraction),
-that we call the \univariate case, then consider the \multivariate
-  case, where  more than one equation
+We first consider the case of a single equation (or contraction)
+that we call the \emph{\univariate case}. \hl{Then we} consider
+the \emph{\multivariate case}, where more than one equation
   (or contraction) with multiple equation variables is considered.
-The \univariate theorems use
+The \univariate versions \hl{of unique-solution theorems} use
 $\lambda$-functions to present CCS equations,

### 2019-11-18 ic-journal/sos.tex
Clean up some old (confirmed) highlights

@@
 
-\hl{The CCS formalisation starts with type definitions for action,
-relabeling and the CCS term itself. We use} the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' (\texttt{'b} or
-$\beta$ is \hl{a type variable}) for all visible actions. The
+The CCS formalisation starts with type definitions for action,
+relabeling and the CCS term itself. We use the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' (\texttt{'b} or
+$\beta$ is a \emph{type variable}) for all visible actions. The
 cardinality and the exact elements depend on the type variable $\beta$
 supplied by the end user.
-\hl{All actions are} divided into input and \hl{$\overline{\text{output}}$ ones.}
+All actions are divided into input and $\overline{\text{output}}$ ones.
 This type is defined by HOL's \texttt{Datatype} package in the
@@
 \end{lstlisting}
-\hl{For instance, if the type $\beta$ is instantiated by the type
-\texttt{string}, then HOL terms} \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
+For instance, if the type $\beta$ is instantiated by the type
+\texttt{string}, then HOL terms \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
 \HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input action $a$ and output
@@
 expressions, where \texttt{'a} (or $\alpha$) is the type variable\footnote{The order of type variables $\alpha$ and $\beta$
-    is arbitrary. Our choice is aligned with  the \hl{literature.
-For instance,} $\mathrm{CCS}(h,k)$ is the CCS subcalculus that can use at most $h$ constants
+    is arbitrary. Our choice is aligned with  the literature.
+For instance, $\mathrm{CCS}(h,k)$ is the CCS subcalculus that can use at most $h$ constants
 and $k$ actions~\cite{gorrieri2017ccs}. To formalize theorems on
@@
 \texttt{sum P Q} in HOL. Their correspondences with conventional CCS notations
-in the literature, are given in Table~\ref{tab:ccsoperator}, \hl{where
+in the literature, are given in Table~\ref{tab:ccsoperator}, where
 most CCS operators have also the more readable abbreviation forms,
-either for end user or for \TeX{} outputs.} (All
+either for end user or for \TeX{} outputs. (All
   formal theorems and definitions in this paper
@@
 \textbf{CCS concept} & \textbf{Notation} & \textbf{HOL term} &
-                                             \textbf{HOL abbrev.} & \hl{\textbf{\TeX{} outputs}} \\
+                                             \textbf{HOL abbrev.} & \textbf{\TeX{} outputs} \\
 \hline
@@
 prefix & $\mu.P$ & \texttt{prefix u P} & \texttt{u..P} & \HOLinline{\HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{P}} \\
-\hl{summation} & $P + Q$ & \texttt{sum P Q} & \texttt{P + Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{Q}} \\
-parallel \hl{composition} & $P \,\mid\, Q$ & \texttt{par P Q} & \texttt{P || Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{Q}} \\
+summation & $P + Q$ & \texttt{sum P Q} & \texttt{P + Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{Q}} \\
+parallel composition & $P \,\mid\, Q$ & \texttt{par P Q} & \texttt{P || Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{Q}} \\
 restriction & $(\nu{}L)\;P$ & \texttt{restr L P} & \texttt{(nu L) P} & \HOLinline{\ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{P}}  \\
@@
 relabeling & $P\;[r\!f]$ & \texttt{relab P rf} &\texttt{relab P rf} & \HOLinline{\HOLConst{relab} \HOLFreeVar{P} \HOLFreeVar{rf}}  \\
-\hl{constant/variable} & $A$ & \texttt{var A} &\texttt{var A} & \HOLinline{\HOLConst{var} \HOLFreeVar{A}} \\
+constant/variable & $A$ & \texttt{var A} &\texttt{var A} & \HOLinline{\HOLConst{var} \HOLFreeVar{A}} \\
 \hline
@@
 \hline
-\hl{variable substitution} & $E\{E'/X\}$ & \texttt{CCS_Subst E E' X} &
+variable substitution & $E\{E'/X\}$ & \texttt{CCS_Subst E E' X} &
                                            \texttt{[E'/X]  E} & \HOLinline{\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}} \\
-\hl{transition} & $P\overset{\mu}{\longrightarrow}Q$
+transition & $P\overset{\mu}{\longrightarrow}Q$
                        & \texttt{TRANS P u Q} & \texttt{P ---u-> Q} & \HOLinline{\HOLFreeVar{P} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{Q}} \\
-\hl{weak transition} & $P\overset{\mu}{\Longrightarrow}Q$
+weak transition & $P\overset{\mu}{\Longrightarrow}Q$
                        & \texttt{WEAK\_TRANS P u Q} & \texttt{P ==u=> Q} & \HOLinline{\HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{Q}} \\
-\hl{$\epsilon$--transition} & $P\overset{\epsilon}{\Longrightarrow}Q$
+$\epsilon$--transition & $P\overset{\epsilon}{\Longrightarrow}Q$
                        & \texttt{EPS P Q} & \texttt{EPS P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\HOLTokenEPS} \HOLFreeVar{Q}} \\
@@
 \end{center}
-   \caption{Syntax of \hl{some CCS concepts in HOL}}
+   \caption{Syntax of some CCS concepts in HOL}
    \label{tab:ccsoperator}
@@
 \begin{itemize}
-  \item \hl{\emph{rules} is a conjunction of implications that will be the
+  \item \emph{rules} is a conjunction of implications that will be the
     same as the input term. In fact, the following formal versions of SOS rules are
-    extracted from the \emph{rules} theorem:}
+    extracted from the \emph{rules} theorem:
 \begin{alltt}
@@
 \end{equation*}
-\item \hl{\emph{ind} is the induction principle for the
-  relation} (see Section~\ref{sec:multivariate} for the exact form
-  and its application).
-\item \hl{\emph{cases} is the so-called `cases' or `inversion' theorem for
+\item \emph{ind} is the induction principle for the relation
+  (see Section~\ref{sec:multivariate} for the exact form and its application).
+\item \emph{cases} is the so-called `cases' or `inversion' theorem for
   the relations, and is used to decompose an element in the relation into the possible ways of
   obtaining it by the rules. For instance, it leads to the following
-  theorem:}
+  theorem:
 \begin{alltt}
@@
 The last SOS rule \texttt{REC} (Recursion)
- says that if we substitute all \hl{occurrences of the} variable $A$ in $P$ to
+ says that if we substitute all occurrences of the variable $A$ in $P$ to
 $(\recu A P)$ and the resulting process has a transition to $P'$
 with action $u$, then $(\recu A P)$ has the same
-transition. Here, ``\HOLinline{\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}}'' is \hl{an abbreviation}
+transition. Here, ``\HOLinline{\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}}'' is an abbreviation
 for ``\HOLinline{\HOLConst{CCS_Subst} \HOLFreeVar{E} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{)} \HOLFreeVar{X}}'', where \HOLinline{\HOLConst{CCS_Subst}} is a
@@
 \end{alltt}
-\hl{The variable substitutions only affects free
-variables: the variable $Y$ in} ``\HOLinline{\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}}'' \hl{is
-bound and therefore the substitution ignores it. }
+The variable substitutions only affects free
+variables: the variable $Y$ in ``\HOLinline{\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}}'' is
+bound and therefore the substitution ignores it.
 % The actual substitution happens in case of}
-% ``\HOLinline{\HOLConst{var} \HOLFreeVar{Y}}'' if $Y$ is being substituted (and if
-\HOLinline{\HOLConst{CCS_Subst}} 
+% ``\HOLinline{\HOLConst{var} \HOLFreeVar{Y}}'' if $Y$ is being
+% substituted (and if \HOLinline{\HOLConst{CCS_Subst}}
 % can actually reach it).
@@
   taking a CCS process and returning a theorem indicating all
-  direct transitions of the process.\footnote{If the input process \hl{are
- infinite branching, the function will not terminate}.}
+  direct transitions of the process.\footnote{If the input process are
+ infinite branching, the function will not terminate}.
 For instance, we know that the process $(a.\nil | \bar{a}.\nil)$ has three
@@
 To completely describe all possible transitions of a process, if done manually, the
-following two facts must be proved: \hl{(1) there are indeed the three
+following two facts must be proved: (1) there are indeed the three
   transitions mentioned above; (2) there are no other
-  transitions.} For large CCS processes it is surprisingly \hl{tedious} to manually derive
+  transitions. For large CCS processes it is surprisingly tedious to manually derive
 all the possible transitions and prove the non-existence of others.
-\hl{This shows the usefulness of appealing to an ML function
+This shows the usefulness of appealing to an ML function
 \texttt{CCS\_TRANS\_CONV} that is designed to automate the whole process.
 For instance, calling it on $(a.\nil | \bar{a}.\nil)$ the function returns the
-following theorem which describes all the transitions (just one-step) of the process:}
+following theorem which describes all the transitions (just one-step) of the process:
 \begin{alltt}

### 2019-11-19 ic-journal/formal.tex
More fixes of reviewer's issues

@@
 in conventional formalisation projects in HOL: adding new axioms may
-either break the logic consistencies or make the whole work less
-convincible. The theorem prover (in general) guarantees that,
+either break the logic \hl{consistency} or make the whole
+\hl{formalisation} work less
+convincible. \hl{In general,} the theorem prover guarantees that,
 without adding new axioms, if both the definitions and the statements
-of theorems are correct, then any proof which successfully completes must
-be correct. This is also the case here: SOS rules of CCS are
-\emph{not} axioms but consequences of the inductive relation\hl{, the
-  CCS transition $\rightarrow$}.
+of theorems \hl{were} correct, then the \hl{proofs of these theorems} must
+be \hl{also} correct.
+% This last sentence doesn't have a good link with the previous context,
+% disabled. --Chun
+%
+%% This is also the case here: SOS rules of CCS are
+%% \emph{not} axioms but consequences of the inductive relation\hl{, the
+%% CCS transition $\rightarrow$}.
 

### 2019-11-19 ic-journal/sos.tex
More fixes of reviewer's issues

@@
 \HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input action $a$ and output
-action $\overline{\text{b}}$, respectively.
+action \hl{$\overline{b}$}, respectively.
 The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
@@
 (\texttt{tau}). For instace, the input action $a$ and output
-action $\overline{\text{b}}$ of type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}''
+action \hl{$\overline{b}$} of type \hl{\mbox{``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''}}
 are denoted by \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLStringLit{a}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLStringLit{b}\ensuremath{)}}, respectively.
@@
 variable substitution & $E\{E'/X\}$ & \texttt{CCS_Subst E E' X} &
-                                           \texttt{[E'/X]  E} & \HOLinline{\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}} \\
+                                           \texttt{[E'/X]  E} & \HOLinline{\ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}} \\
 transition & $P\overset{\mu}{\longrightarrow}Q$
@@
 \HOLTokenTurnstile{} \HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E}\hfill\texttt{[PREFIX]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[SUM1]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[SUM2]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sp{\prime}}\hfill\texttt{[PAR1]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sb{\mathrm{1}}}\hfill\texttt{[PAR2]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}\hfill\texttt{[SUM1]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}\hfill\texttt{[SUM2]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sp{\prime}}\hfill\texttt{[PAR1]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}\hfill\texttt{[PAR2]}
 \end{alltt}
 \begin{equation*}
-\infer[\HOLRuleName{PAR3}]{\HOLinline{\HOLFreeVar{E} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E\sb{\mathrm{2}}}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}}&\HOLinline{\HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLFreeVar{l}\ensuremath{)}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{2}}}}}
+\infer[\HOLRuleName{PAR3}]{\HOLinline{\HOLFreeVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}}&\HOLinline{\ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLFreeVar{l}\ensuremath{)}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}}}
 \end{equation*}
 \begin{equation*}
-\infer[\HOLRuleName{RESTR}]{\HOLinline{\ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E\sp{\prime}}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}}}&\HOLinline{\HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLFreeVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}}}
+\infer[\HOLRuleName{RESTR}]{\HOLinline{\ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \ensuremath{\HOLFreeVar{E}\sp{\prime}}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime}}}&\HOLinline{\HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLFreeVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}}}
 \end{equation*}
 \begin{equation*}
-\infer[\HOLRuleName{RELABELING}]{\HOLinline{\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \HOLFreeVar{E\sp{\prime}} \HOLFreeVar{rf}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime}}}}
+\infer[\HOLRuleName{RELABELING}]{\HOLinline{\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLFreeVar{rf}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime}}}}
 \end{equation*}
 \begin{equation*}
-\infer[\HOLRuleName{REC}]{\HOLinline{\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}}}{\HOLinline{\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sb{\mathrm{1}}}}}
+\infer[\HOLRuleName{REC}]{\HOLinline{\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}}}{\HOLinline{\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}}}
 \end{equation*}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime\prime}} \HOLSymConst{\HOLTokenEquiv{}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime\prime}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{E\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E\sp{\prime\prime}}\hfill{[TRANS_SUM_EQ]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime\prime}} \HOLSymConst{\HOLTokenEquiv{}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime\prime}} \HOLSymConst{\HOLTokenDisj{}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime\prime}}\hfill{[TRANS_SUM_EQ]}
 \end{alltt}
@@
 with action $u$, then $(\recu A P)$ has the same
-transition. Here, ``\HOLinline{\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}}'' is an abbreviation
-for ``\HOLinline{\HOLConst{CCS_Subst} \HOLFreeVar{E} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{)} \HOLFreeVar{X}}'', where \HOLinline{\HOLConst{CCS_Subst}} is a
-recursive function substituting all appearences of a free variable
-into another CCS term.
+transition. Here, ``\HOLinline{\ensuremath{[}\HOLConst{rec}\;\;\HOLFreeVar{X}\;\;\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\;\;\HOLFreeVar{E}}'' is an abbreviation
+for ``\HOLinline{\HOLConst{CCS_Subst}\;\;\HOLFreeVar{E}\;\;\ensuremath{(}\HOLConst{rec}\;\;\HOLFreeVar{X}\;\;\HOLFreeVar{E}\ensuremath{)}\;\;\HOLFreeVar{X}}'', where \HOLinline{\HOLConst{CCS_Subst}} is a
+recursive function substituting all appearences of a free variable \hl{with} another CCS term.
 For most CCS operators \HOLinline{\HOLConst{CCS_Subst}} just recursively goes into a deeper
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E\sb{\mathrm{2}}}\hfill{[CCS_Subst_sum]}
+\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}\hfill{[CCS_Subst_sum]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{var} \HOLFreeVar{Y}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLFreeVar{E\sp{\prime}} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}\hfill{[CCS_Subst_var]}
-\HOLTokenTurnstile{} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} \ensuremath{(}\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\hfill{[CCS_Subst_rec]}
+\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{var} \HOLFreeVar{Y}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}\hfill{[CCS_Subst_var]}
+\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} \ensuremath{(}\ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\hfill{[CCS_Subst_rec]}
 \end{alltt}
 The variable substitutions only affects free
-variables: the variable $Y$ in ``\HOLinline{\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}}'' is
+variables: the variable $Y$ in ``\HOLinline{\HOLConst{rec}\!\;\HOLFreeVar{Y}\!\;\HOLFreeVar{E}}'' is
 bound and therefore the substitution ignores it.
-% The actual substitution happens in case of}
+% The actual substitution happens in case of
 % ``\HOLinline{\HOLConst{var} \HOLFreeVar{Y}}'' if $Y$ is being
-% substituted (and if \HOLinline{\HOLConst{CCS_Subst}}
-% can actually reach it).
+% substituted (and if \HOLinline{\HOLConst{CCS_Subst}} can actually reach it).
 
@@
 between HOL4 and Standard ML (that follows an idea by Nesi \cite{Nesi:1992ve})
- is a complex Standard ML function
-  taking a CCS process and returning a theorem indicating all
-  direct transitions of the process.\footnote{If the input process are
- infinite branching, the function will not terminate}.
+ is a \hl{recursive} ML function \hl{which takes} a CCS process and \hl{returns} a theorem indicating all
+  direct transitions of the process. \hl{(If the input process is
+ infinite branching, the function will not terminate.)}
 For instance, we know that the process $(a.\nil | \bar{a}.\nil)$ has three

### 2019-11-19 ic-journal/sos.tex
Cumulative fixes

@@
 The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'', accounting for the CCS
-expressions, where \texttt{'a} (or $\alpha$) is the type variable\footnote{The order of type variables $\alpha$ and $\beta$
-    is arbitrary. Our choice is aligned with  the literature.
+expressions, where \texttt{'a} (or $\alpha$) is the type
+variable\footnote{The order \hl{between} type variables $\alpha$ and $\beta$
+    \hl{can be} arbitrary. Our choice is aligned with the literature.
 For instance, $\mathrm{CCS}(h,k)$ is the CCS subcalculus that can use at most $h$ constants
@@
 having the corresponding cardinalities $h$ and $k$.} for
-agent variables, is then defined inductively: (\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}} is the type of all relabeling functions. They (and
-  related operations) are not discussed in this paper.)
+agent variables, is then defined inductively: (``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling
+  functions. \hl{Relabeling is formalised but is not to be} discussed in this paper.)
 \begin{lstlisting}
@@
 consequence of an \emph{inductive relation} definition of
-\HOLinline{\HOLConst{TRANS}} by HOL's \texttt{HOL_reln} function.~(c.f.~\citep[p.~219]{holdesc} for more details.)
+\HOLinline{\HOLConst{TRANS}} by HOL's \texttt{HOL_reln} function.~(\hl{See}~\citep[p.~219]{holdesc} for more details.)
 A successful invocation of the definitional principle returns three
@@
 A useful facility exploiting the interplay
-between HOL4 and Standard ML (that follows an idea by Nesi \cite{Nesi:1992ve})
+between HOL4 and Standard ML (that follows an idea \hl{of} Nesi~\cite{Nesi:1992ve})
  is a \hl{recursive} ML function \hl{which takes} a CCS process and \hl{returns} a theorem indicating all
@@
 For instance, we know that the process $(a.\nil | \bar{a}.\nil)$ has three
-possible transitions: $(a.\nil | \bar{a}.\nil) \overset{a}{\longrightarrow}
+possible \hl{(one-step)} transitions: $(a.\nil | \bar{a}.\nil) \overset{a}{\longrightarrow}
 (\nil | \bar{a}.\nil)$, $(a.\nil | \bar{a}.\nil)
@@
 \overset{\tau}{\longrightarrow} (\nil | \nil)$.
-To completely describe all possible transitions of a process, if done manually, the
+To completely describe all possible transitions of \hl{the} process, if done manually, the
 following two facts must be proved: (1) there are indeed the three
-  transitions mentioned above; (2) there are no other
-  transitions. For large CCS processes it is surprisingly tedious to manually derive
+  transitions mentioned above; (2) there \hl{is} no other
+  \hl{transition}. For large CCS processes it is surprisingly tedious to manually derive
 all the possible transitions and prove the non-existence of others.
@@
 \texttt{CCS\_TRANS\_CONV} that is designed to automate the whole process.
-For instance, calling it on $(a.\nil | \bar{a}.\nil)$ the function returns the
-following theorem which describes all the transitions (just one-step) of the process:
+For instance, \hl{taking the input} $(a.\nil | \bar{a}.\nil)$ the function returns the
+following theorem which describes all \hl{its one-step} transitions:
 \begin{alltt}

### 2019-11-20 ic-journal/response-letter2.tex
Clean up some old (confirmed) highlights
More fixes of reviewer's issues
Cumulative fixes
Cumulative fixes with highlights

@@
 \item \begin{quote}
-    The multivariable case has been added. This is great: it makes the result stronger, and adds a real improvement over the conference version. 
+    ``The multivariable case has been added. This is great: it makes the result stronger, and adds a real improvement over the conference version.''
   \end{quote}
   \Mark
-  Thanks.
+  Thanks for your suggestion (on doing this) in the previous
+  review. This extra formalisation work also closed an open question
+  (on how to naturally/elegantly formalise the multivariate case of
+  the unique-solution theorems) that the first author failed to
+  resolve in his master thesis work. There exists several CCS
+  formalisations as we mentioned in the related work (Section 6) but
+  our formalisation is the only one which covers the unique-solution
+  theorems, either in the univariable or multivariable cases.
 
 \item \begin{quote}
-Overall the authors did address the minor comments. But the paper
+``Overall the authors did address the minor comments. But the paper
 still contains quite a few grammatical and other minor mistakes, also
@@
 again through the paper; but this is certainly inexhaustive and the
-authors should do some more careful proofreading.
+authors should do some more careful proofreading.''
 \end{quote}
@@
 \item \begin{quote}
-    In fact, one of the corrections appears to have introduced a new
-    bug: Theorem 4.7 in the new version is wrong; I guess Def. 4.6
+    ``In fact, one of the corrections appears to have introduced a new
+    bug: Theorem 4.7 in the new version is wrong; I guess Def.~4.6
     should be about weak transitions. In the original submission,
@@
     with weak bisimulation up-to found by the second author (one can
-    simply use the same counterexample $\{(\tau. a , 0)\}$).
+    simply use the same counterexample $\{(\tau. a , 0)\}$).''
   \end{quote}
   \Mark
-  This is an embarassing typo. The two $\arr{\mu}$ in
-  Definition 4.6 should be $\Arr{\mu}$ instead. Our actual formalization is
-  correct. Below is the fixed part of Definition 4.6:
+  This is an embarassing typo when we were trying to make the paper
+  more compact. The two $\arr{\mu}$ in
+  Definition 4.6 should be $\Arr{\mu}$ instead. Our formalization
+  (ever shown as verbatim generated code in the previous version) is
+  however correct, because otherwise. Below is the fixed part of Definition 4.6:
 \begin{enumerate}
@@
 \end{enumerate}
+We also put the HOL definition back, to show the correspondence between the informal and formal definitions.
 
@@
 \end{quote}
-  \Mark
+  \Mark We have changed ``formalised'' (a wrong use of the past tense) to ``formalising''.
 
@@
 \end{quote}
-  \Mark
+  \Mark Fixed.
 
@@
 \end{quote}
-  \Mark
+  \Mark Fixed. This is a typesetting mistake.
 
@@
 \end{quote}
-  \Mark
+  \Mark (TODO)
 
@@
 \end{quote}
-  \Mark
+  \Mark Removed.
 
@@
 \end{quote}
-  \Mark
+  \Mark Removed ``the'' and re-organized the whole sentence.
 
@@
 \end{quote}
-  \Mark
+  \Mark Fixed and re-organized the whole sentence.
 
@@
 \end{quote}
-  \Mark
+  \Mark Fixed, thanks.
 
@@
 \end{quote}
-  \Mark
+  \Mark We have renamed the concept to ``bisimulation up to $\wb$ with weak arrows''.
 
@@
 \end{quote}
-  \Mark
+  \Mark We have fixed and re-organized this sentence adding an example
+  of such limitations (due to Milner).
 
@@
 \end{quote}
-  \Mark
+  \Mark Milner said it can be proven by ``an easy action induction''.
+             It is actually not that easy, and we take this chance to
+             illustrate how to apply ``action induction'' in HOL.
+             (TODO) The proof is now shortened, according to the
+             latest updates in the HOL formalisation.
 
   \item \begin{quote}
-1066 "the proof cannot complete" ?
+1066 (should be 1056) "the proof cannot complete" ?
 \end{quote}
-  \Mark
+  \Mark We wanted to say ``Proposition 5.1 is essential in the proofs of all unique-solution
+theorems (multivariable vesions).''
 

### 2019-11-20 ic-journal/coarsest.tex
Cumulative fixes with highlights

@@
 Theorem~\ref{t:rapproxCongruence}, i.e. $\rapprox$ is the coarsest
-congruence contained in $\wb$. \hl{This theorem is of special interests to
-us, because within our framework it seems impossible to prove it
-without any limitation.} The general form of this theorem can be
+congruence contained in $\wb$. This theorem is of special \hl{interest} to
+us, because under our \hl{CCS syntax (with only binary summations)} it seems impossible to prove it
+without any \hl{antecedent such as ``the involved processes do not
+  use up all available labels''}. The general form of this theorem can be
 expressed informally as below~\cite{van2005characterisation,Gorrieri:2015jt,Mil89}:
-\begin{proposition}[\hl{$\rapprox$ is the coarsest congruence contained in $\wb$}]
+\begin{proposition}
 \label{prop:coarsest}
+  \hl{Rooted bisimilarity ($\rapprox$) is the coarsest congruence
+    contained in weak bisimilarity ($\wb$):}
   \begin{equation}
+    \label{eq:coarsest}
 \forall p\ \ q.\ p\ \rapprox\ \! q\ \Longleftrightarrow\ ( \forall r.\ p\ +\
@@
 \end{proposition}
-
-However, we are only interested in the proposition from right to left,
-as from left to right it holds trivially by the substitutivity of
-$\rapprox$ of summation and that fact that $\rapprox$ implies $\wb$:
+From left to right (\ref{eq:coarsest}) trivially holds, due to the substitutivity of
+$\rapprox$ \hl{for} summation and \hl{the fact that} $\rapprox$ implies $\wb$:
 \begin{alltt}
@@
 \end{alltt}
-
+Thus we are only interested in (\ref{eq:coarsest}) from right to left.
+%
 The standard argument~\cite{Mil89} requires that $p$
-and $q$ do not use up available labels (i.e.~visible actions).
-Formalising such an argument requires  
-a detailed treatment on free and bound names of CCS
+and $q$ do not use up \hl{all} available labels (i.e.~visible actions).
+Formalising this \hl{result, however,} requires a detailed treatment on free and bound names of CCS
 processes (with the restriction operator being a binder).
-However, in this project we do not discuss on free and bound names
-(also called ``sorts'') of CCS processes. Instead, we
-assume that all immediate \emph{weak} derivatives of
- $p$ and $q$ do not use all available action names. We call it
+\hl{In} this project we do not discuss free and bound names (also
+called ``sorts'') of CCS processes. Instead, we
+assume \hl{a weaker condition} that all immediate \emph{weak} derivatives of
+ $p$ and $q$ do not use all available \hl{labels}. We \hl{might} call it
  the \emph{free action} property:
 \begin{alltt}
-   \HOLConst{free_action} \HOLFreeVar{p} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{a}.
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}}.
-\HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{a}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}}\ensuremath{)}\hfill{[free_action_def]}
+   \HOLConst{free_action} \HOLFreeVar{p} \HOLTokenDefEquality{} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{a}.
+\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{p}\sp{\prime}}.
+\HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{a}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{p}\sp{\prime}}\ensuremath{)}\hfill{[free_action_def]}
 \end{alltt}
 
-Below we show how Proposition~\ref{prop:coarsest} is connected with
+Below we show how \hl{Prop.}~\ref{prop:coarsest} is connected with
 the statement in Theorem~\ref{t:rapproxCongruence}, and prove it under
 the free action assumptions.
-
+%
 The coarsest congruence
@@
 \begin{alltt}
-   \HOLConst{CC} \HOLFreeVar{R} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}.
+   \HOLConst{CC} \HOLFreeVar{R} \HOLTokenDefEquality{} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}.
 \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}.
 \HOLConst{CONTEXT} \HOLBoundVar{c} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \ensuremath{(}\HOLBoundVar{c} \HOLBoundVar{g}\ensuremath{)} \ensuremath{(}\HOLBoundVar{c} \HOLBoundVar{h}\ensuremath{)}\ensuremath{)}\hfill{[CC_def]}
-   \HOLConst{WEAK_CONGR} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{CC} \HOLConst{WEAK_EQUIV}\hfill{[WEAK_CONGR]}
+   \HOLConst{WEAK_CONGR} \HOLTokenDefEquality{} \HOLConst{CC} \HOLConst{WEAK_EQUIV}\hfill{[WEAK_CONGR]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R} \HOLBoundVar{R\sp{\prime}}.
-\HOLConst{congruence} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLConst{CC} \HOLBoundVar{R}\hfill{[CC_is_coarsest]}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R} \HOLBoundVar{R\sp{\prime}}.
-\HOLConst{precongruence} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLConst{CC} \HOLBoundVar{R}\hfill{[PCC_is_coarsest]}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R} \ensuremath{\HOLBoundVar{R}\sp{\prime}}.
+\HOLConst{congruence} \ensuremath{\HOLBoundVar{R}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{R}\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \ensuremath{\HOLBoundVar{R}\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLConst{CC} \HOLBoundVar{R}\hfill{[CC_is_coarsest]}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R} \ensuremath{\HOLBoundVar{R}\sp{\prime}}.
+\HOLConst{precongruence} \ensuremath{\HOLBoundVar{R}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{R}\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \ensuremath{\HOLBoundVar{R}\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLConst{CC} \HOLBoundVar{R}\hfill{[PCC_is_coarsest]}
 \end{alltt}
@@
 \begin{alltt}
-   \HOLConst{SUM_EQUIV} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}.
+   \HOLConst{SUM_EQUIV} \HOLTokenDefEquality{} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}.
 \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
@@
 % \begin{alltt}
-% \HOLConst{WEAK_CONGR} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{CC} \HOLConst{WEAK_EQUIV}
+% \HOLConst{WEAK_CONGR} \HOLTokenDefEquality{} \HOLConst{CC} \HOLConst{WEAK_EQUIV}
 % \end{alltt}
@@
 % \begin{alltt}
-% \HOLConst{SUM_EQUIV} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}.
+% \HOLConst{SUM_EQUIV} \HOLTokenDefEquality{} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}.
 \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
@@
 
-The proof of above theorem was given by Rob van Glabbeek
-\cite{van2005characterisation}, which originally applies to all CCS processes.
+The formal proof follows van
+Glabbeek~\cite{van2005characterisation}.
 The core lemma says, for
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
-        \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}} \HOLBoundVar{u}.
-\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{q\sp{\prime}} \HOLBoundVar{u}.
-\HOLFreeVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}.
+       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
+            \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{p}\sp{\prime}} \HOLBoundVar{u}.
+\HOLBoundVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{p}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\ensuremath{\HOLBoundVar{p}\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+            \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{q}\sp{\prime}} \HOLBoundVar{u}.
+\HOLBoundVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{q}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\ensuremath{\HOLBoundVar{q}\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
        \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-   \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q}\hfill{[PROP3_COMMON]}
+\HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLBoundVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{q}\hfill{[PROP3_COMMON]}
 \end{alltt}
 \begin{alltt}
-   \HOLConst{STABLE} \HOLFreeVar{p} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{p\sp{\prime}}.
-\HOLFreeVar{p} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{u} \HOLSymConst{\HOLTokenNotEqual{}} \HOLSymConst{\ensuremath{\tau}}\hfill{[STABLE]}
+   \HOLConst{STABLE} \HOLFreeVar{p} \HOLTokenDefEquality{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \ensuremath{\HOLBoundVar{p}\sp{\prime}}.
+\HOLFreeVar{p} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{p}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{u} \HOLSymConst{\HOLTokenNotEqual{}} \HOLSymConst{\ensuremath{\tau}}\hfill{[STABLE]}
 \end{alltt}
@@
 As a consequence, the final result is only for finite-state
-  CCS~--- a  restricted class.
+CCS~--- a  restricted class.\footnote{\hl{van Glabbeek's
+  original proof applies to all CCS processes, but it
+  requires the CCS syntax to support arbitrary large summations based
+  on ordinals, and it relies on the fact that, there always exists an
+  ordinal large than the cardinality of any given set. This is beyond
+  the capacity of HOL.}}
 
-The assumption in the previous \texttt{PROP3_COMMON} requires the
+The assumption in \texttt{PROP3_COMMON} requires the
 existence of a special CCS process, which is not weakly bisimilar to
@@
 This can be done following Klop's contruction \cite{van2005characterisation}.
- We call  ``Klop processes''  the processes in this construction:
+ We call  the processes in this construction \hl{the ``Klop processes''}:
 \begin{definition}[Klop processes]
@@
 \begin{alltt}
-   \HOLConst{KLOP} \HOLFreeVar{a} \HOLNumLit{0} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{\ensuremath{\mathbf{0}}}
-   \HOLConst{KLOP} \HOLFreeVar{a} \ensuremath{(}\HOLConst{SUC} \HOLFreeVar{n}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLSymConst{\ensuremath{+}} \HOLConst{label} \HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\hfill{[KLOP_def]}
+   \HOLConst{KLOP} \HOLFreeVar{a} \HOLNumLit{0} \HOLTokenDefEquality{} \HOLConst{\ensuremath{\mathbf{0}}}
+   \HOLConst{KLOP} \HOLFreeVar{a} \ensuremath{(}\HOLConst{SUC} \HOLFreeVar{n}\ensuremath{)} \HOLTokenDefEquality{} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLSymConst{\ensuremath{+}} \HOLConst{label} \HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\hfill{[KLOP_def]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{Reach} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
+\HOLConst{Reach} \HOLTokenDefEquality{} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
 \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{u}.
-\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}}\ensuremath{)}\HOLSymConst{\HOLTokenSupStar{}}\hfill[Reach_def]
+\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)}\HOLSymConst{\HOLTokenSupStar{}}\hfill[Reach_def]
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{NODES} \HOLFreeVar{p} \HOLSymConst{\HOLTokenDefEquality{}} \HOLTokenLeftbrace{}\HOLBoundVar{q} \HOLTokenBar{} \HOLConst{Reach} \HOLFreeVar{p} \HOLBoundVar{q}\HOLTokenRightbrace{}\hfill[NODES_def]
+\HOLConst{NODES} \HOLFreeVar{p} \HOLTokenDefEquality{} \HOLTokenLeftbrace{}\HOLBoundVar{q} \HOLTokenBar{} \HOLConst{Reach} \HOLFreeVar{p} \HOLBoundVar{q}\HOLTokenRightbrace{}\hfill[NODES_def]
 \end{alltt}
@@
 \begin{alltt}
-\HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{FINITE} \ensuremath{(}\HOLConst{NODES} \HOLFreeVar{p}\ensuremath{)}\hfill[finite_state_def]
+\HOLConst{finite_state} \HOLFreeVar{p} \HOLTokenDefEquality{} \HOLConst{FINITE} \ensuremath{(}\HOLConst{NODES} \HOLFreeVar{p}\ensuremath{)}\hfill[finite_state_def]
 \end{alltt}
@@
        \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
-           \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}} \HOLBoundVar{u}.
-\HOLBoundVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{q\sp{\prime}} \HOLBoundVar{u}.
-\HOLBoundVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\hfill{[KLOP_LEMMA_FINITE]}
+           \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{p}\sp{\prime}} \HOLBoundVar{u}.
+\HOLBoundVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{p}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\ensuremath{\HOLBoundVar{p}\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+           \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{q}\sp{\prime}} \HOLBoundVar{u}.
+\HOLBoundVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{q}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\ensuremath{\HOLBoundVar{q}\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\hfill{[KLOP_LEMMA_FINITE]}
 \end{alltt}

### 2019-11-20 ic-journal/equa.tex
Cumulative fixes with highlights

@@
 For instance,  $X$ is free in $a.X + \recu Y (b.Y)$ while $Y$
-is bound; in $a.X + \recu X (b.X)$, $X$ is both free and bound.
-A \hl{term} without free variables is a \emph{process}.
+is bound; \hl{And} in $a.X + \recu X (b.X)$, $X$ is both free and bound.
+A \hl{term} without free variables is \hl{called} a \emph{process}.
 % This setting does not cause any ambiguity, but sometimes leads to more

### 2019-11-20 ic-journal/multivariate.tex
Cumulative fixes with highlights

@@
 
-Recall the beginning of Section~\ref{s:eq},
-the CCS syntax leaves the syntactic possibility that an
+Recall \hl{from} the beginning of Section~\ref{s:eq} \hl{that},
+CCS syntax leaves the syntactic possibility that an
 agent variable $A$ occurs outside the recursion operator of the same
@@
 \hline
-\HOLConst{FV} \ensuremath{(}\HOLConst{var} \HOLFreeVar{X}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLTokenLeftbrace{}\HOLFreeVar{X}\HOLTokenRightbrace{} & \HOLConst{FV} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{p}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{FV} \HOLFreeVar{p} \HOLConst{DELETE} \HOLFreeVar{X} \\
-\HOLConst{BV} \ensuremath{(}\HOLConst{var} \HOLFreeVar{X}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\HOLTokenEmpty{}} & \HOLConst{BV} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{p}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLFreeVar{X} \HOLConst{INSERT} \HOLConst{BV} \HOLFreeVar{p} \\
+\HOLConst{FV} \ensuremath{(}\HOLConst{var} \HOLFreeVar{X}\ensuremath{)} \HOLTokenDefEquality{} \HOLTokenLeftbrace{}\HOLFreeVar{X}\HOLTokenRightbrace{} & \HOLConst{FV} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{p}\ensuremath{)} \HOLTokenDefEquality{} \HOLConst{FV} \HOLFreeVar{p} \HOLConst{DELETE} \HOLFreeVar{X} \\
+\HOLConst{BV} \ensuremath{(}\HOLConst{var} \HOLFreeVar{X}\ensuremath{)} \HOLTokenDefEquality{} \HOLSymConst{\HOLTokenEmpty{}} & \HOLConst{BV} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{p}\ensuremath{)} \HOLTokenDefEquality{} \HOLFreeVar{X} \HOLConst{INSERT} \HOLConst{BV} \HOLFreeVar{p} \\
 \hline
@@
 \begin{alltt}
-   \HOLConst{IS_PROC} \HOLFreeVar{E} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\HOLTokenEmpty{}}\hfill{[IS_PROC_def]}
+   \HOLConst{IS_PROC} \HOLFreeVar{E} \HOLTokenDefEquality{} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\HOLTokenEmpty{}}\hfill{[IS_PROC_def]}
 \end{alltt}
@@
 \begin{alltt}
-   \HOLConst{ALL_PROC} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{EVERY} \HOLConst{IS_PROC} \HOLFreeVar{Es}\hfill{[ALL_PROC_def]}
+   \HOLConst{ALL_PROC} \HOLFreeVar{Es} \HOLTokenDefEquality{} \HOLConst{EVERY} \HOLConst{IS_PROC} \HOLFreeVar{Es}\hfill{[ALL_PROC_def]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}}.
-\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{IS_PROC} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{IS_PROC} \HOLBoundVar{E\sp{\prime}}\hfill{[TRANS_PROC]}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{IS_PROC} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{IS_PROC} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\hfill{[TRANS_PROC]}
 \end{alltt}
@@
 \begin{proof}
-We prove a stronger result,
-i.e.,  the set of free variables decreases through derivatives:
+We \hl{actually proved} a stronger result \hl{saying} the set of free
+variables \hl{in any CCS process} decreases through its derivatives:
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}}.
-\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E}\hfill{[TRANS_FV]}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E}\hfill{[TRANS_FV]}
 \end{alltt}
@@
 \hl{Milner said it can be proven by ``an easy action induction''.}
-From HOL's viewpoint, the so-called ``action induction'' is actually a higher-order application
+\hl{It is actually not that easy, and we take this chance to
+  illustrate how to apply ``action induction'' (in HOL), which} is actually a higher-order application
 of the following \emph{induction principle} generated together with SOS
@@
        \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u}.
-\HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sp{\prime}}.
-\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sp{\prime}}.
-\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sp{\prime}}.
-\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sp{\prime}}.
-\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\HOLBoundVar{E\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{1}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{l} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-            \HOLBoundVar{P} \HOLBoundVar{E} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \HOLBoundVar{E\sp{\prime}} \ensuremath{(}\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLBoundVar{l}\ensuremath{)}\ensuremath{)} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
-            \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLSymConst{\ensuremath{\tau}} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{l} \HOLBoundVar{L}.
-            \HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLBoundVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-            \HOLBoundVar{P} \ensuremath{(}\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \HOLBoundVar{E\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{rf}.
-\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)} \ensuremath{(}\HOLConst{relabel} \HOLBoundVar{rf} \HOLBoundVar{u}\ensuremath{)} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{rf}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{X} \HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLBoundVar{P} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \HOLBoundVar{E\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a\sb{\mathrm{0}}} \HOLBoundVar{a\sb{\mathrm{1}}} \HOLBoundVar{a\sb{\mathrm{2}}}.
-\HOLBoundVar{a\sb{\mathrm{0}}} \HOLTokenTransBegin\HOLBoundVar{a\sb{\mathrm{1}}}\HOLTokenTransEnd \HOLBoundVar{a\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLBoundVar{a\sb{\mathrm{0}}} \HOLBoundVar{a\sb{\mathrm{1}}} \HOLBoundVar{a\sb{\mathrm{2}}}\hfill{[TRANS_IND]}
+\HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{l} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+            \HOLBoundVar{P} \HOLBoundVar{E} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \ensuremath{(}\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLBoundVar{l}\ensuremath{)}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
+            \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \HOLSymConst{\ensuremath{\tau}} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{l} \HOLBoundVar{L}.
+            \HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLBoundVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+            \HOLBoundVar{P} \ensuremath{(}\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{rf}.
+\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)} \ensuremath{(}\HOLConst{relabel} \HOLBoundVar{rf} \HOLBoundVar{u}\ensuremath{)} \ensuremath{(}\HOLConst{relab} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{rf}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{X} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}.
+\HOLBoundVar{P} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}.
+\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\hfill{[TRANS_IND]}
 \end{alltt}
-The above long theorem has the form \HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\HOLBoundVar{E\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\HOLBoundVar{E\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLBoundVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\HOLBoundVar{E\sp{\prime}}} (with $a_0, a_1, a_2$ renamed), where the
+The above long theorem has the form \HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLBoundVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}} (with $a_0, a_1, a_2$ renamed), where the
 outermost universal quantifier $P$ is a higher-order
@@
 What we are trying to prove is actually in the form of
-\HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\HOLBoundVar{E\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\HOLBoundVar{E\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLFreeVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\HOLBoundVar{E\sp{\prime}}}, where
-\HOLinline{\HOLFreeVar{P}\\\;\HOLSymConst{\ensuremath{=}}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\HOLBoundVar{E\sp{\prime}}.\\\;\HOLConst{FV}\\\;\HOLBoundVar{E\sp{\prime}}\\\;\HOLSymConst{\HOLTokenSubset{}}\\\;\HOLConst{FV}\\\;\HOLBoundVar{E}\ensuremath{)}}.
+\HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLFreeVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}}, where
+\HOLinline{\HOLFreeVar{P}\\\;\HOLSymConst{\ensuremath{=}}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLConst{FV}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenSubset{}}\\\;\HOLConst{FV}\\\;\HOLBoundVar{E}\ensuremath{)}}.
 Thus, if we can prove
@@
 \begin{alltt}
-        \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}
+        \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}
    ------------------------------------
     0.
-\HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-\HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{E\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{FV} \HOLBoundVar{E\sp{\prime}}\hfill{[FV_SUBSET]}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\HOLConst{FV} \ensuremath{(}\ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\hfill{[FV_SUBSET]}
 \end{alltt}
@@
 Thus we can enrich the assumptions of the current proof goal with above
-lemma, and obtain \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} by the transitivity of $\subseteq$:
+lemma, and obtain \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} by the transitivity of $\subseteq$:
 \begin{alltt}
-        \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}
+        \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}
    ------------------------------------
     0.
-\HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
     1.
 \HOLinline{\HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
-    2.  \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
+    2.  \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
 \end{alltt}
-Knowing \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} we cannot prove \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}.
-However, if we knew \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, then \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\ensuremath{=}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, and then
-\HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}, no matter if \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E}} or not, and the proof
+Knowing \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} we cannot prove \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}.
+However, if we knew \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}}}, then \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\ensuremath{=}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}}}, and then
+\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}, no matter if \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E}} or not, and the proof
 would have completed. Thus it remains to show that
 \begin{alltt}
-        \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}
+        \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}}}
    ------------------------------------
     0.
-\HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
     1.
 \HOLinline{\HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
-    2.  \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
+    2.  \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
 \end{alltt}
@@
 the goal does not hold, i.e.
-\HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}, then by assumption 0 we have \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}:
+\HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}}}, then by assumption 0 we have \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}:
 \begin{alltt}
@@
     0.
-\HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
     1.
 \HOLinline{\HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
-    2.  \HOLinline{\HOLConst{FV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
-    3.  \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E\sp{\prime}}}
+    2.  \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
+    3.  \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}}}
     4.
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-\HOLBoundVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\hfill{[NOTIN_FV_lemma]}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\HOLBoundVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLBoundVar{X} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\hfill{[NOTIN_FV_lemma]}
 \end{alltt}
@@
 
-Without the above result, the proof of Milner's ``unique solution of
-equations'' theorem (for $\sim$) cannot complete. Compared with the
-above proof, the proof of the similar result for bound variables is easier:
+Proposition~\ref{prop:transFV} \hl{is essential in the proofs of the
+  multivariable versions of all unique-solution
+  theorems.
+In comparison with} the above proof, the proof of the similar
+result for bound variables is \hl{much} easier:
 \begin{proposition}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{E\sp{\prime}}.
-\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{BV} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E}\hfill{[TRANS_BV]}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E}\hfill{[TRANS_BV]}
 \end{alltt}
@@
 \begin{alltt}
-        \HOLinline{\HOLConst{BV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLFreeVar{X} \HOLConst{INSERT} \HOLConst{BV} \HOLFreeVar{E}}
+        \HOLinline{\HOLConst{BV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLFreeVar{X} \HOLConst{INSERT} \HOLConst{BV} \HOLFreeVar{E}}
    ------------------------------------
     0.
-\HOLinline{\HOLConst{BV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+\HOLinline{\HOLConst{BV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
 \end{alltt}
@@
     0.
-\HOLinline{\HOLConst{BV} \HOLFreeVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+\HOLinline{\HOLConst{BV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-\HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{E\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{BV} \HOLBoundVar{E\sp{\prime}}\hfill{[BV_SUBSET]}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\HOLConst{BV} \ensuremath{(}\ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\hfill{[BV_SUBSET]}
 \end{alltt}
@@
 \begin{alltt}
-   \HOLConst{CCS_SUBST} \HOLFreeVar{fm} \ensuremath{(}\HOLConst{var} \HOLFreeVar{X}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}} \HOLKeyword{if} \HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLFreeVar{fm} \HOLKeyword{then} \HOLFreeVar{fm} \HOLConst{'} \HOLFreeVar{X} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{X}\hfill{[CCS_SUBST_var]}
+   \HOLConst{CCS_SUBST} \HOLFreeVar{fm} \ensuremath{(}\HOLConst{var} \HOLFreeVar{X}\ensuremath{)} \HOLTokenDefEquality{} \HOLKeyword{if} \HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLFreeVar{fm} \HOLKeyword{then} \HOLFreeVar{fm} \HOLConst{'} \HOLFreeVar{X} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{X}\hfill{[CCS_SUBST_var]}
 
-   \HOLConst{CCS_SUBST} \HOLFreeVar{fm} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenDefEquality{}}
+   \HOLConst{CCS_SUBST} \HOLFreeVar{fm} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{)} \HOLTokenDefEquality{}
      \HOLKeyword{if} \HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLFreeVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{X} \ensuremath{(}\HOLConst{CCS_SUBST} \ensuremath{(}\HOLFreeVar{fm} \HOLSymConst{\ensuremath{\setminus}} \HOLFreeVar{X}\ensuremath{)} \HOLFreeVar{E}\ensuremath{)}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{]}\ensuremath{/}\ensuremath{[}\HOLFreeVar{X}\ensuremath{]}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLFreeVar{E\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}
+\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{]}\ensuremath{/}\ensuremath{[}\HOLFreeVar{X}\ensuremath{]}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}
 \end{alltt}
@@
 \begin{alltt}
-   \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
+   \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLTokenDefEquality{} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
 \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
@@
 
-   \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
+   \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLTokenDefEquality{} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}.
 \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
@@
        \HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{P\sp{\prime}}.
-           \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-           \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sp{\prime}}.
-               \HOLConst{context} \HOLFreeVar{Xs} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-               \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
+           \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+           \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+               \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+               \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
                \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
-\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}
+\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime}}
 \end{alltt}

### 2019-11-20 ic-journal/part2.tex
Cumulative fixes with highlights

@@
 \HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \HOLBoundVar{P\sp{\prime}}.
-\HOLFreeVar{E} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sp{\prime}}.
-\HOLConst{CONTEXT} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
-\HOLFreeVar{E} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{E\sp{\prime}} \HOLBoundVar{Q}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
+\HOLFreeVar{E} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\HOLConst{CONTEXT} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLFreeVar{E} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{Q}
 \end{alltt}
@@
 \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{G} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{G} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \HOLBoundVar{P\sp{\prime}}.
-       \HOLFreeVar{G} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
+       \HOLFreeVar{G} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}.
-\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
 \HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}
@@
 \HOLTokenTurnstile{} \HOLConst{WEAK_BISIM} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
        \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u}.
-            \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLBoundVar{E\sp{\prime}} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E\sb{\mathrm{2}}}.
-\HOLBoundVar{E\sp{\prime}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sb{\mathrm{1}}}.
-\HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{E\sp{\prime}}
+            \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}.
+\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+\ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+            \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+\ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}.
+\HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \ensuremath{\HOLBoundVar{E}\sp{\prime}}
 \end{alltt}
@@
 \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{G} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{G} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \HOLBoundVar{P\sp{\prime}}.
-       \HOLFreeVar{G} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
+       \HOLFreeVar{G} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}.
-\HOLConst{SEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLConst{SEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
 \HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}
@@
 \begin{alltt}
-   \HOLConst{LRTC} \HOLFreeVar{R} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b} \HOLSymConst{\HOLTokenDefEquality{}}
+   \HOLConst{LRTC} \HOLFreeVar{R} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b} \HOLTokenDefEquality{}
      \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.
@@
 \begin{alltt}
-   \HOLConst{TRACE} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{LRTC} \HOLConst{TRANS}\hfill{[TRACE_def]}
+   \HOLConst{TRACE} \HOLTokenDefEquality{} \HOLConst{LRTC} \HOLConst{TRANS}\hfill{[TRACE_def]}
 \end{alltt}
@@
 \begin{alltt}
-   \HOLConst{NO_LABEL} \HOLFreeVar{L} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
+   \HOLConst{NO_LABEL} \HOLFreeVar{L} \HOLTokenDefEquality{} \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}.
 \HOLConst{MEM} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \HOLFreeVar{L}\hfill{[NO_LABEL_def]}
@@
 \begin{alltt}
-   \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLSymConst{\HOLTokenDefEquality{}}
-     \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{L\sb{\mathrm{1}}} \HOLBoundVar{L\sb{\mathrm{2}}}.
-\HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} \ensuremath{[}\HOLFreeVar{u}\ensuremath{]} \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{2}}}\hfill{[UNIQUE_LABEL_def]}
+   \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLTokenDefEquality{}
+     \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{L}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{L}\sb{\mathrm{2}}}.
+\ensuremath{\HOLBoundVar{L}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} \ensuremath{[}\HOLFreeVar{u}\ensuremath{]} \HOLSymConst{\HOLTokenDoublePlus} \ensuremath{\HOLBoundVar{L}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \ensuremath{\HOLBoundVar{L}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \ensuremath{\HOLBoundVar{L}\sb{\mathrm{2}}}\hfill{[UNIQUE_LABEL_def]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLFreeVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}}
    \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{acts}.
-       \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{acts} \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{NULL} \HOLBoundVar{acts} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{acts} \ensuremath{\HOLFreeVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{NULL} \HOLBoundVar{acts} \HOLSymConst{\HOLTokenConj{}}
        \HOLKeyword{if} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLKeyword{then} \HOLConst{NO_LABEL} \HOLBoundVar{acts} \HOLKeyword{else} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLBoundVar{acts}\hfill{[WEAK_TRANS_AND_TRACE]}
@@
             \HOLBoundVar{C} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
-            \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-                \HOLConst{GCONTEXT} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{C\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}}
+            \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}.
+                \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenContracts{}} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}}
                 \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}.
-\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{y}\ensuremath{)}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C} \HOLFreeVar{Q}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C\sp{\prime}} \HOLFreeVar{Q}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{y}\ensuremath{)}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C} \HOLFreeVar{Q}\ensuremath{)} \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLFreeVar{Q}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}.
            \HOLBoundVar{C} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
-           \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-\HOLConst{GCONTEXT} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{C\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{EPS}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C} \HOLFreeVar{Q}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C\sp{\prime}} \HOLFreeVar{Q}\ensuremath{)}
+           \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}.
+\HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenContracts{}} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{EPS}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C} \HOLFreeVar{Q}\ensuremath{)} \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLFreeVar{Q}\ensuremath{)}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{GCONTEXT} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}\ensuremath{)} \HOLFreeVar{P}\ensuremath{)} \HOLFreeVar{xs} \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{xs} \HOLSymConst{\HOLTokenLeq{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-\HOLConst{GCONTEXT} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{C\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
-\HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}\ensuremath{)} \HOLBoundVar{Q}\ensuremath{)} \HOLFreeVar{xs} \ensuremath{(}\HOLBoundVar{C\sp{\prime}} \HOLBoundVar{Q}\ensuremath{)}
+\HOLTokenTurnstile{} \HOLConst{GCONTEXT} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}\ensuremath{)} \HOLFreeVar{P}\ensuremath{)} \HOLFreeVar{xs} \ensuremath{\HOLFreeVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{xs} \HOLSymConst{\HOLTokenLeq{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}.
+\HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLFreeVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}\ensuremath{)} \HOLBoundVar{Q}\ensuremath{)} \HOLFreeVar{xs} \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLBoundVar{Q}\ensuremath{)}
 \end{alltt}
@@
 \HOLTokenTurnstile{} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{xs} \HOLBoundVar{l} \HOLBoundVar{P\sp{\prime}}.
-       \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{xs} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{UNIQUE_LABEL} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{xs\sp{\prime}} \HOLBoundVar{Q\sp{\prime}}.
-           \HOLConst{TRACE} \HOLFreeVar{Q} \HOLBoundVar{xs\sp{\prime}} \HOLBoundVar{Q\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLBoundVar{xs\sp{\prime}} \HOLSymConst{\HOLTokenLeq{}} \HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenConj{}}
-           \HOLConst{UNIQUE_LABEL} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \HOLBoundVar{xs\sp{\prime}}\hfill{[contracts_AND_TRACE_label]}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{xs} \HOLBoundVar{l} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
+       \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{xs} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{UNIQUE_LABEL} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{xs}\sp{\prime}} \ensuremath{\HOLBoundVar{Q}\sp{\prime}}.
+           \HOLConst{TRACE} \HOLFreeVar{Q} \ensuremath{\HOLBoundVar{xs}\sp{\prime}} \ensuremath{\HOLBoundVar{Q}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \ensuremath{\HOLBoundVar{xs}\sp{\prime}} \HOLSymConst{\HOLTokenLeq{}} \HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenConj{}}
+           \HOLConst{UNIQUE_LABEL} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \ensuremath{\HOLBoundVar{xs}\sp{\prime}}\hfill{[contracts_AND_TRACE_label]}
 \end{alltt}

### 2019-11-21 ic-journal/multivariate.tex
Cumulative fixes

@@
 There are two ways to represent  the \multivariate
-substitution of $E\{\til P/\til X\}$ which substitutes each possibly
-occurrences of free variables $X_i$ in $E$ with the corresponding
+substitution of $E\{\til P/\til X\}$ which substitutes each \hl{possible
+occurrence} of free variables $X_i$ in $E$ with the corresponding
 $P_i$: (1) iterately applying the existing \univariate
@@
 
-Recall in Section~\ref{ss:context}, \univariate contexts and their
+Recall \hl{that} in Section~\ref{ss:context}, \univariate contexts and their
 guarded companions are defined as predicates over $\lambda$-expressions

### 2019-11-24 ic-journal/ccs.tex
Cumulative fixes based on discussions on three questions

@@
 
-\section{CCS}
+\section{Calculus of Communicating Systems (CCS)}
 \label{ss:ccs}
@@
 action $\tau \notin \mathscr{L}$, and another possibly infinite
-set of agent variables $A, B, \ldots \in \mathscr{X}$.
+set of agent variables \hl{$\mathscr{X} = \{X, Y, \ldots\}$}.
 The class of \hl{all} CCS \hl{terms (or expressions)} is then inductively
@@
 \; \midd \; P\; [\mathit{rf}]  % relabelling
-\;  \midd \;  A \; \midd \; \recu A  P
+\;  \midd \;  X \; \midd \; \recu X P
 \end{array}
@@
 %
-$\displaystyle{ P \sub {\recu A P} A \arr{\mu}P' \over
- \recu A P   \arr{ \mu} P'  } $
+$\displaystyle{ P \sub {\recu X P} X \arr{\mu}P' \over
+ \recu X P \arr{\mu} P'} $
 \hskip .5cm  
@@
 We let $\R$, $\S$ range over binary relations, sometimes using 
- infix notation for them; e.g., 
-$P \,\R\, Q$ means $(P,Q) \in \R$.
+ infix notation for them, \hl{e.g.} $P \,\R\, Q$ means $(P,Q) \in \R$.
 We use a tilde, as in  $\til P$, to denote tuples of processes with
-countably many elements (thus the tuple may also be infinite.)
-All notations are extended to tuples componentwise,
-e.g., $\til P \,\R\, \til Q$ means $P_i \,\R\, Q_i$ for each  
-index $i$ of the tuples $\til P$ and $\til Q$.
-We use the symbol $\DSdefi$ for abbreviations. For instance, $P \DSdefi G $, where
+countably many \hl{elements.}
+All \hl{relation} notations can be extended to tuples componentwise,
+e.g., $\til P \,\R\, \til Q$ means $P_i \,\R\, Q_i$ for each index $i$ of the tuples $\til P$ and $\til Q$.
+We use $\DSdefi$ to \hl{define} abbreviations. For instance, $P \DSdefi G $, where
 $G$ is some expression, means that $P$ stands for the expression $G$.

### 2019-11-24 ic-journal/expansion.tex
Cumulative fixes based on discussions on three questions

@@
 Weak bisimilarity is not preserved by the sum operator (except for
-guarded sums), i.e.\  $P_1 \wb Q_1$ and $P_2 \wb Q_2$  \hl{do} not imply
+guarded sums), i.e.~$P_1 \wb Q_1$ and $P_2 \wb Q_2$  \hl{do} not imply
  $P_1 + P_2 \wb Q_1 + Q_2$.
@@
 \end{definition}
-
+% This new sentence maintains a link with Definition 2.1
+\hl{It can be proved that, $P_1 \rapprox Q_1 \wedge P_2 \rapprox Q_2 \Longrightarrow
+P_1 + P_2 \rapprox Q_1 + Q_2$.}
 The above definition also brings up a proof technique for proving rooted
@@
 indeed the coarsest congruence contained in bisimilarity
-(c.f. Section~\ref{s:coarsest} and \hl{\mbox{Section~\ref{ss:context}}} for more details):
+(See Section~\ref{s:coarsest} and \hl{\mbox{Section~\ref{ss:context}}} for more details):
 \begin{theorem}

### 2019-11-24 ic-journal/formal.tex
Cumulative fixes with highlights
Cumulative fixes based on discussions on three questions

@@
 
-\subsection{Higher Order Logic}
+\subsection{Higher Order Logic (HOL)}
 
@@
 
-The terms of the HOL logic are expressions that denote elements of the
+The terms of the HOL logic are expressions \hl{which} denote elements of the
 sets denoted by types. There're four kinds of terms in the HOL
-logic. There can be described approximately by the BNF grammar in
-Fig. \ref{fig:hol-terms}.
+logic. \hl{They} can be described (in simplified forms) by the BNF grammar in
+Fig.~\ref{fig:hol-terms}. (See~\ref{hollogic} for a complete description.)
 
@@
 The deductive system of the HOL is specified by eight primitive
-derivative rules: (c.f.~\cite{hollogic} for more details.)
+derivative rules: (See~\cite{hollogic} for more details.)
 \begin{enumerate}
@@
 $\TyDef$, can be used to define new HOL types as bijections of
-subsets of existing types. (c.f.~\cite{Melham:1989dk} for more details.)
+subsets of existing types~\cite{Melham:1989dk}.
 HOL's \texttt{Datatype} package~\cite{Melham:1991, holdesc} automates
-this tedious process, and can be used to define needed types in CCS.
+this tedious process, and can be used for \hl{defining types needed for} CCS.
 
@@
 Notice that, usually the above four axioms are the only axioms allowed
-in conventional formalisation projects in HOL: adding new axioms may
-either break the logic \hl{consistency} or make the whole
-\hl{formalisation} work less
-convincible. \hl{In general,} the theorem prover guarantees that,
+in conventional formalisation projects in HOL: adding new axioms
+\hl{manually}, may break the logic \hl{consistency}.
+\hl{In general,} the theorem prover guarantees that,
 without adding new axioms, if both the definitions and the statements
-of theorems \hl{were} correct, then the \hl{proofs of these theorems} must
+of theorems are correct, then the \hl{proofs of these theorems} must
 be \hl{also} correct.

### 2019-11-24 ic-journal/sos.tex
Cumulative fixes based on discussions on three questions

@@
 The CCS formalisation starts with type definitions for action,
-relabeling and the CCS term itself. We use the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' (\texttt{'b} or
-$\beta$ is a \emph{type variable}) for all visible actions. The
-cardinality and the exact elements depend on the type variable $\beta$
-supplied by the end user.
-All actions are divided into input and $\overline{\text{output}}$ ones.
-This type is defined by HOL's \texttt{Datatype} package in the
+relabeling and the CCS term itself. We use the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}''
+for all labels (i.e. visible actions), where the type variable $\beta$ corresponds
+to $\mathscr{L}$ (the set of names for labels) used at the beginning
+of Section~\ref{ss:ccs}. The
+cardinality and the exact elements of this type depend on the type variable $\beta$
+instantiated by the end user \hl{or further formalisations built upon the
+present one.}
+All \hl{labels} are divided into input and $\overline{\text{output}}$ ones.
+The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is defined by HOL's \texttt{Datatype} package in the
 following syntax:
@@
 \end{lstlisting}
-For instance, if the type $\beta$ is instantiated by the type
-\texttt{string}, then HOL terms \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
+For instance, if the type $\beta$ is instantiated by \texttt{string}
+(the type of all strings), then HOL terms \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
 \HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input action $a$ and output
@@
 The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'', accounting for the CCS
-expressions, where \texttt{'a} (or $\alpha$) is the type
-variable\footnote{The order \hl{between} type variables $\alpha$ and $\beta$
+expressions, has two type variables \hl{$\alpha$ and $\beta$ corresponding%
+\footnote{The order \hl{between} type variables $\alpha$ and $\beta$
     \hl{can be} arbitrary. Our choice is aligned with the literature.
@@
 variables $\alpha$ and $\beta$ in ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' with types
-having the corresponding cardinalities $h$ and $k$.} for
-agent variables, is then defined inductively: (``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling
+having the corresponding cardinalities $h$ and $k$.}
+to $\mathscr{X}$ (the set of agent variables) and $\mathscr{L}$ (the
+set of names used for labels), respectively, used at the beginning of} Section~\ref{ss:ccs}.
+%
+The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' \hl{is defined inductively by HOL's \texttt{Datatype} package:}
+(Here ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling
   functions. \hl{Relabeling is formalised but is not to be} discussed in this paper.)

### 2019-11-25 ic-journal/ccs.tex
text

@@
 We assume a possibly infinite set of names $\mathscr{L} = \{a, b,
-\ldots\}$ yielding input and $\overline{\mbox{output}}$ labels (actions), plus a special invisible
+\ldots\}$ yielding input and output labels (actions), plus a special invisible
 action $\tau \notin \mathscr{L}$, and another possibly infinite
@@
 $P \arcap \mu P'$ holds if $P \arr\mu P'$ or $\mu =\tau \wedge P = P'$; similarly 
-$P \Arcap \mu P'$ holds if $P \Arr\mu P'$ or $\mu =\tau \wedge P = P'$).
+$P \Arcap \mu P'$ holds if ($P \Arr\mu P'$ or $\mu =\tau \wedge P = P'$).
 We write $P \:(\arr\mu)^n P'$ if $P$ can become $P'$ after performing
@@
  infix notation for them, \hl{e.g.} $P \,\R\, Q$ means $(P,Q) \in \R$.
-We use a tilde, as in  $\til P$, to denote tuples of processes with
-countably many \hl{elements.}
+We use a tilde, as in  $\til P$, to denote (finite) tuples of elements. 
+% We use a tilde, as in  $\til P$, to denote tuples of processes with
+% countably many \hl{elements.}
 All \hl{relation} notations can be extended to tuples componentwise,

### 2019-11-25 ic-journal/contraction.tex
Cumulative fixes with highlights
text

@@
 Intuitively, the bisimilarity contraction $\mcontrBIS$ is a preorder
-such that, $P \mcontrBIS Q$ holds if $P \wb Q$ and, in addition, 
+where $P \mcontrBIS Q$ holds if $P \wb Q$ and, in addition, 
 $Q$ \emph{has the possibility of being at least as efficient as $P$} (as far as
@@
 challenges from $Q$, entirely ignores efficiency: it is the same
-clause of  weak bisimulation~---the final derivatives are indeed required
+clause of  weak bisimulation~--- the final derivatives are indeed required
 to be related  by $\wb$, rather than by $\R$.
@@
 $\expa$~\cite{arun1992efficiency,sangiorgi2015equations}:
-\begin{definition}%[expansion]
+\begin{definition}[expansion]
 \label{d:expa}

### 2019-11-25 ic-journal/equa.tex
text

@@
 another type for  equations, and we can reuse the existing
-variable substitution operation (c.f. SOS rule for the Recursion in
+variable substitution operation (c.f.\ the   SOS rule for the Recursion in
 Fig.~\ref{f:LTSCCS}) for the substitution of equation variables.
@@
 context, we may also write $E[\til P]$ instead of $E \sub {\til P} {\til
-  X}$ (and $E[P]$ for $E \sub P X$ if there is a single equation variable $X$.)
+  X}$ (and $E[P]$ for $E \sub P X$ if there is a single equation
+variable $X$).
 
@@
 different from each other, as it must be for the variables $\til X$.
-If the system has infinitely many equations, the  tuples $\til P$ and $\til X$ are infinite too.
+% If the system has infinitely many equations, the  tuples $\til P$
+% and $\til X$ are infinite too.
 
@@
 Let $E_i$ be guarded and sequential with free
-variables up to $\til X$, and let ${\til P} \rapprox {\til E}\{\til P /\til X\}$,
+variables in $\til X$, and let ${\til P} \rapprox {\til E}\{\til P /\til X\}$,
   ${\til Q} \rapprox {\til E}\{\til Q /\til X\}$. Then ${\til P} \rapprox {\til Q}$.
@@
 Let $E_i$ be guarded and sequential with free
-variables up to $\til X$, and let ${\til P} \wb {\til E}\{\til P /\til X\}$,
+variables in $\til X$, and let ${\til P} \wb {\til E}\{\til P /\til X\}$,
   ${\til Q} \wb {\til E}\{\til Q /\til X\}$. Then ${\til P} \wb {\til Q}$.

### 2019-11-25 ic-journal/expansion.tex
text

@@
 \emph{Strong} bisimulation and strong bisimilarity ($\sim$)
-can be obtained by replacing the weak transition $Q\Arcap\mu Q'$ in the above
-definition with normal transitions $Q \arr \mu Q'$ (similar for the other case).
+can be obtained by replacing the weak transition $Q\Arcap\mu Q'$ in 
+clause (1) 
+ with the transition $Q \arr \mu Q'$ (and similarly for the other clause).
 Weak bisimilarity is not preserved by the sum operator (except for
@@
 One basic property of rooted bisimiarity is congruence,
-indeed the coarsest congruence contained in bisimilarity
+indeed it is  the coarsest congruence contained in bisimilarity
 (See Section~\ref{s:coarsest} and \hl{\mbox{Section~\ref{ss:context}}} for more details):

### 2019-11-25 ic-journal/formal.tex
text

@@
 HOL4 has implemented the original HOL, 
-while some other theorem provers in HOL family (e.g. Isabelle/HOL) have
+while some other theorem provers in the HOL family (e.g. Isabelle/HOL) have
 certain extensions.
@@
 % inconsistent). 
-Indeed the HOL has considerably simpler logical
+Indeed HOL has considerably simpler logical
 foundations than most other theorem provers. %, e.g. Coq. 
@@
 
-HOL4 is implemented in Standard ML, the same programming language who
+HOL4 is implemented in Standard ML, and
+ the same programming language
 plays three different roles:
@@
 verification tools by calling HOL's theorem proving
-facilities. The formal proofs of theorems in CCS theory
-are mostly done by an \emph{interactive process} closely following
-their informal proofs, with minimal automatic proof searching.
+facilities. The formal proofs of the CCS theorems that we have carried
+out 
+are mostly done in a manner that closely follows
+their paper proofs, with minimal automatic proof searching.
 
@@
 HOL is a formal system of typed logical terms. The types are expressions that denote sets (in the
-universe $\mathcal{U}$). HOL's type system is much simpler than those
+universe $\mathcal{U}$). HOL type system is much simpler than those
 based on dependent types and other type theories. There are four kinds of types in the HOL
 logic, as illustrated in Fig. \ref{fig:hol-types} for its BNF
-grammar. Noticed that, in HOL the standard atomic types \emph{bool} and \emph{ind}
+grammar. In HOL, the standard atomic types \emph{bool} and \emph{ind}
  denote, respectively, the distinguished two-element set 2 and the
@@
 The terms of the HOL logic are expressions \hl{which} denote elements of the
-sets denoted by types. There're four kinds of terms in the HOL
+sets denoted by types. There are four kinds of terms in the HOL
 logic. \hl{They} can be described (in simplified forms) by the BNF grammar in
-Fig.~\ref{fig:hol-terms}. (See~\ref{hollogic} for a complete description.)
+Fig.~\ref{fig:hol-terms}; see~\ref{hollogic} for a complete description.
 
@@
 
-The deductive system of the HOL is specified by eight primitive
-derivative rules: (See~\cite{hollogic} for more details.)
+The deductive system of HOL is specified by eight primitive
+derivative rules~\cite{hollogic}:
 \begin{enumerate}
@@
 which also give the semantics of two foundamental
-logical connectives, the equality ($=$) and implication
-($\Rightarrow$). The rest logical connectives and first-order
+logical connectives,  equality ($=$) and implication
+($\Rightarrow$). The remaining logical connectives and first-order
 quantifiers, including the logical true (\HOLinline{\HOLConst{T}}) and false (\HOLinline{\HOLConst{F}}), are
-further defined as $\lambda$-functions: (one rarely needs to care
-things at this level, however.)
+further defined as $\lambda$-functions: 
+% (one rarely needs to care
+% things at this level, however.)
 \begin{equation*}
@@
 \end{equation*}
-It deserves to mention that, the last logical constant above,
+The last logical constant,
 $\TyDef$, can be used to define new HOL types as bijections of
 subsets of existing types~\cite{Melham:1989dk}.
-HOL's \texttt{Datatype} package~\cite{Melham:1991, holdesc} automates
-this tedious process, and can be used for \hl{defining types needed for} CCS.
+HOL \texttt{Datatype} package~\cite{Melham:1991, holdesc} automates
+this tedious process, and can be used for \hl{defining the 
+types needed for} CCS.
 
 Finally, the whole HOL \emph{standard} theory is based on the
-following four axioms, from which the almost\footnote{HOL is strictly
+following four axioms:\footnote{HOL is strictly
   weaker than ZFC (the Zermelo-Frankel set theory with the
 Axiom of Choice), thus not all theorems valid in ZFC can be formalised
-in HOL. (c.f.~\cite{hollogic} for more details.)} entire mathematics
-can be formalised:
+in HOL. (c.f.~\cite{hollogic} for more details.)}
 \begin{equation*}
@@
 
-Notice that, usually the above four axioms are the only axioms allowed
+Usually the above four axioms are the only axioms allowed
 in conventional formalisation projects in HOL: adding new axioms
-\hl{manually}, may break the logic \hl{consistency}.
+\hl{manually}, may break logical \hl{consistency}.
 \hl{In general,} the theorem prover guarantees that,
 without adding new axioms, if both the definitions and the statements
-of theorems are correct, then the \hl{proofs of these theorems} must
-be \hl{also} correct.
+of theorems are correct, then the \hl{proofs of these theorems} is
+ \hl{also} correct.
 % This last sentence doesn't have a good link with the previous context,

### 2019-11-25 ic-journal/intro.tex
text

@@
 the equations must be both \emph{guarded} and \emph{sequential}. That is,
-variables of the equations can only occur underneath visible prefixes and summations.
+the variables of the equations can only occur underneath visible prefixes and summations.
 One way to overcome such limitations is to replace the equations
@@
  with the hypothesis that no process uses up all labels;
-the other without such hypothesis, essentially \hl{formalising} van Glabbeek's proof~\cite{van2005characterisation}.
+the other one is 
+without such hypothesis, essentially \hl{formalising} van Glabbeek's proof~\cite{van2005characterisation}.
 Similar results are also proved for the rooted contraction preorder.
 In this respect, the work is also an extensive experiment using the HOL theorem prover with its
-recent developments, including its coinduction defining package.
+recent developments, including its coinduction package.
 
@@
 further refining the theory of unique solutions of contractions.
-In particular, the existing result~\cite{sangiorgi2017equations} has limitations on the body of the contractions due to the
+In particular,  existing results~\cite{sangiorgi2017equations} have limitations on the body of the contractions due to the
 substitutivity problems of weak bisimilarity and other behavioural relations with respect
@@
 contraction preorder; the proofs about unique solution(s) of equations
-for weak bisimilarity that uses the contraction preorder as an
+for weak bisimilarity that use the contraction preorder as an
 auxiliary relation, and other unique solution results (e.g. the one
-for rooted in which the auxiliary relation is rooted contraction); the
+for rooted bisimilarity 
+ in which the auxiliary relation is rooted contraction); the
 proofs about various forms of enhancements of the bisimulation proof
@@
 which the HOL proof scripts have to be modified.
-Then the successful termination of the proof gives us a guarantee that the proof is
-complete and trustworthy, eliminating the risks 
+Then the successful termination of a proof gives us the
+ guarantee that the proof is
+sound and complete, eliminating the risks 
 of overlooking or missing details as in \emph{paper-and-pencil} proofs.
@@
 more careful and delicate treatment of CCS
-expressions with multiple variables and substitutions acting on them.
+expressions, with multiple variables and substitutions acting on them.
 
-In contrast to modern literature, e.g.~\cite{Gorrieri:2015jt},
+In contrast to literature  such as~\cite{Gorrieri:2015jt},
 we have followed Milner's original approach~\cite{milner1990operational} and adopted the same

### 2019-11-25 ic-journal/sos.tex
text

@@
 The CCS formalisation starts with type definitions for action,
-relabeling and the CCS term itself. We use the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}''
+relabeling and then the  processes. We use the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}''
 for all labels (i.e. visible actions), where the type variable $\beta$ corresponds
@@
 present one.}
-All \hl{labels} are divided into input and $\overline{\text{output}}$ ones.
+All \hl{labels} are divided into input and output ones.
 The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is defined by HOL's \texttt{Datatype} package in the
@@
 and $k$ actions~\cite{gorrieri2017ccs}. To formalize theorems on
-such $\mathrm{CCS}(h,k)$, the required CCS type can be retrieved by instantiating the type
+ $\mathrm{CCS}(h,k)$, the required CCS type can be retrieved by instantiating the type
 variables $\alpha$ and $\beta$ in ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' with types
@@
 to $\mathscr{X}$ (the set of agent variables) and $\mathscr{L}$ (the
-set of names used for labels), respectively, used at the beginning of} Section~\ref{ss:ccs}.
+set of names used for labels), respectively}.
 %
-The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' \hl{is defined inductively by HOL's \texttt{Datatype} package:}
-(Here ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling
-  functions. \hl{Relabeling is formalised but is not to be} discussed in this paper.)
+The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' \hl{is defined inductively by HOL \texttt{Datatype} package}
+(here ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling
+  functions;   \hl{we have also formalised relabeling, though we will
+    not discuss it}):
 \begin{lstlisting}
@@
 \texttt{sum P Q} in HOL. Their correspondences with conventional CCS notations
-in the literature, are given in Table~\ref{tab:ccsoperator}, where
+in the literature are given in Table~\ref{tab:ccsoperator}, where
 most CCS operators have also the more readable abbreviation forms,
@@
 consequence of an \emph{inductive relation} definition of
-\HOLinline{\HOLConst{TRANS}} by HOL's \texttt{HOL_reln} function.~(\hl{See}~\citep[p.~219]{holdesc} for more details.)
+\HOLinline{\HOLConst{TRANS}} by HOL \texttt{HOL_reln} function 
+(\hl{see}~\citep[p.~219]{holdesc} for more details).
 A successful invocation of the definitional principle returns three
@@
 \end{alltt}
-The only two insteresting cases are at agent variables and recursion:
+The only two insteresting cases are those for  agent variables and recursion:
 \begin{alltt}
@@
   \hl{transition}. For large CCS processes it is surprisingly tedious to manually derive
-all the possible transitions and prove the non-existence of others.
+all the possible transitions and prove the non-existence of other transitions.
 This shows the usefulness of appealing to an ML function

### 2019-11-25 ic-journal/unique.tex
text

@@
 $\{  X_i \mcontr E_i\}_{i\in I}$ where $I$ is an indexing set and each
-$E_i$  contains variables up to $\til X$.
+$E_i$  contains variables in $\til X$.
 
@@
 Theorem~\ref{t:contraBisimulationU} brings a new proof technique for
-bisimilarity, which is much less restrictive than Milner's
+bisimilarity, which is  less restrictive than Milner's
 Theorem~\ref{t:Mil89} (but with the additional costs of checking $\mcontrBIS$
 in addition to $\wb$).
-However, comparing with Milner's Theorem~\ref{t:Mil89s1}, there is
+However, comparing with Milner's Theorem~\ref{t:Mil89s1}, there remains
 a constraint: the involved CCS expression may only
-use guarded sums. The is mainly due to the fact that $\wb$ is not a
+use guarded sums. This is mainly due to the fact that $\wb$ is not a
  congruence and also $\mcontrBIS$ is not a  precongruence.
 Inspired by rooted bisimilarity, to  eliminate the restriction
-on guarded sums, we have extended the idea of contractions by moving
+on guarded sums we refine the idea of contractions by moving
 to \emph{rooted contractions}:

### 2019-11-26 paper/HOLMultivariate.tex
Re-generated theories (I take the lock back and sync all changes from .tex to .htex)

@@
-\newcommand{\HOLMultivariateDate}{15 Settembre 2019}
-\newcommand{\HOLMultivariateTime}{21:28}
+\newcommand{\HOLMultivariateDate}{19 Novembre 2019}
+\newcommand{\HOLMultivariateTime}{10:23}
 \begin{SaveVerbatim}{HOLMultivariateDefinitionsCCSXXequationXXdef}
@@
 \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
-        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
-        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
+        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
+        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{L} \HOLBoundVar{E}.
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXpar}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXsing}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-\ensuremath{[}\ensuremath{[}\HOLBoundVar{E\sp{\prime}}\ensuremath{]}\ensuremath{/}\ensuremath{[}\HOLBoundVar{X}\ensuremath{]}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{E\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\ensuremath{[}\ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{]}\ensuremath{/}\ensuremath{[}\HOLBoundVar{X}\ensuremath{]}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXSING}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
-\HOLConst{CCS_SUBST} \ensuremath{(}\HOLConst{FEMPTY} \HOLSymConst{|+} \ensuremath{(}\HOLBoundVar{X}\HOLSymConst{,}\HOLBoundVar{E\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{E\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\HOLConst{CCS_SUBST} \ensuremath{(}\HOLConst{FEMPTY} \HOLSymConst{|+} \ensuremath{(}\HOLBoundVar{X}\HOLSymConst{,}\ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXsum}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
+       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+        \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+        \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXpar}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXparXXrewrite}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXparXXrule}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+        \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+        \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXsum}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXsumXXrewrite}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXsumXXrule}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+       \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)}
 \end{SaveVerbatim}
@@
            \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{P\sp{\prime}}.
-               \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-               \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E\sp{\prime}}.
-                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLBoundVar{E\sp{\prime}} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}}
-                   \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-                   \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
+               \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+               \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+                   \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}}
+                   \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+                   \ensuremath{(}\ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
                    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
                        \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-                       \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}
+                       \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime}}
 \end{SaveVerbatim}
@@
                 \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
-                \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-                    \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-                    \HOLBoundVar{R} \HOLConst{contracts} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+                \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}.
+                    \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{C}\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+                    \HOLBoundVar{R} \HOLConst{contracts} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
                     \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLConst{O} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}.
 \HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{y}\ensuremath{)}\ensuremath{)}
-                      \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+                      \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}.
                \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
-               \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-                   \HOLBoundVar{R} \HOLConst{contracts} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
-                   \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLConst{O} \HOLConst{EPS}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}\ensuremath{)}
+               \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}.
+                   \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{C}\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+                   \HOLBoundVar{R} \HOLConst{contracts} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+                   \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLConst{O} \HOLConst{EPS}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime}}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsUSCXXunfoldingXXlemmaOne}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{E} \HOLBoundVar{C\sb{\mathrm{0}}} \HOLBoundVar{Ps}.
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{C}\sb{\mathrm{0}}} \HOLBoundVar{Ps}.
        \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLConst{context} \HOLBoundVar{Xs}\ensuremath{)} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
@@
        \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
-\HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
+\HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
 \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n}.
-\HOLConst{OBS_contracts} \ensuremath{(}\HOLBoundVar{C\sb{\mathrm{0}}} \HOLBoundVar{Ps}\ensuremath{)} \ensuremath{(}\ensuremath{(}\HOLBoundVar{C\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}\ensuremath{)} \HOLBoundVar{Ps}\ensuremath{)}
+\HOLConst{OBS_contracts} \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sb{\mathrm{0}}} \HOLBoundVar{Ps}\ensuremath{)} \ensuremath{(}\ensuremath{(}\ensuremath{\HOLBoundVar{C}\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}\ensuremath{)} \HOLBoundVar{Ps}\ensuremath{)}
 \end{SaveVerbatim}
@@
            \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{u} \HOLBoundVar{P\sp{\prime}}.
+           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
                \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
@@
 \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-               \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-               \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-                   \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-                   \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+               \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+               \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}.
+                   \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{C}\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+                   \ensuremath{(}\ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
                    \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
                        \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-                       \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}
+                       \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime}}
 \end{SaveVerbatim}
@@
 \HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{x} \HOLBoundVar{P\sp{\prime}}.
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{x} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
            \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
@@
 \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-           \ensuremath{[}\HOLBoundVar{E} \HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-           \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime}}.
-               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-               \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+           \ensuremath{[}\HOLBoundVar{E} \HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+           \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}.
+               \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{C}\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+               \ensuremath{(}\ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
                \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
                    \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-                   \ensuremath{[}\HOLBoundVar{E} \HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime}}
+                   \ensuremath{[}\HOLBoundVar{E} \HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime}}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsUSCXXunfoldingXXlemmaFour}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{C} \HOLBoundVar{E} \HOLBoundVar{C\sb{\mathrm{0}}}.
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{C} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{C}\sb{\mathrm{0}}}.
        \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
@@
        \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
-\HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{C\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
+\HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
 \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n} \HOLBoundVar{xs} \HOLBoundVar{Ps} \HOLBoundVar{P\sp{\prime}}.
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n} \HOLBoundVar{xs} \HOLBoundVar{Ps} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
            \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
@@
 \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-           \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLBoundVar{C\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}\ensuremath{)} \HOLBoundVar{Ps}\ensuremath{)} \HOLBoundVar{xs} \HOLBoundVar{P\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenLeq{}} \HOLBoundVar{n} \HOLSymConst{\HOLTokenImp{}}
-           \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{C\sp{\prime\prime}}.
-               \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C\sp{\prime\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C\sp{\prime\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-               \ensuremath{(}\HOLBoundVar{P\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+           \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\ensuremath{\HOLBoundVar{C}\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}\ensuremath{)} \HOLBoundVar{Ps}\ensuremath{)} \HOLBoundVar{xs} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenLeq{}} \HOLBoundVar{n} \HOLSymConst{\HOLTokenImp{}}
+           \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime\prime}}.
+               \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{C}\sp{\prime\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{C}\sp{\prime\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+               \ensuremath{(}\ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
                \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
                    \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-                   \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLBoundVar{C\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}\ensuremath{)} \HOLBoundVar{Qs}\ensuremath{)} \HOLBoundVar{xs} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C\sp{\prime\prime}}\ensuremath{)}
+                   \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\ensuremath{\HOLBoundVar{C}\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}\ensuremath{)} \HOLBoundVar{Qs}\ensuremath{)} \HOLBoundVar{xs} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime\prime}}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXpar}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXparXXrewrite}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXparXXrule}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
-        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
+        \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{L} \HOLBoundVar{E}.
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXsum}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXsumXXrewrite}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenEquiv{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsweaklyXXguardedXXsumXXrule}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
+       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)}
 \end{SaveVerbatim}

### 2019-11-26 ic-journal/coarsest.tex
It is recommended that "cf." be used only to suggest a comparison, and the word "see" be used to point to a source of information.
https://en.wikipedia.org/wiki/List_of_Latin_abbreviations

@@
  $q$, then \texttt{SUM_EQUIV} indeed implies rooted bisimilarity
- ($\rapprox$): (c.f.~\cite{Tian:2017wrba} for more details of the proof)
+ ($\rapprox$): (see~\cite{Tian:2017wrba} for more details of the proof)
 \begin{alltt}

### 2019-11-26 ic-journal/conclusions.tex
It is recommended that "cf." be used only to suggest a comparison, and the word "see" be used to point to a source of information.
https://en.wikipedia.org/wiki/List_of_Latin_abbreviations

@@
 delicate and subtle differences in a few points. In a paper-pencil
-proof, checking all details would be long and \hl{error-prone},
-\hl{especially in cases where the proofs are similar to each other or
-  when there are long case analyses to be carried out.}
-\hl{Some of the textbook proofs were even wrong and the correct version is
+proof, checking all details would be long and error-prone,
+especially in cases where the proofs are similar to each other or
+  when there are long case analyses to be carried out.
+Some of the textbook proofs were even wrong and the correct version is
 known but not available in the literature. This is the case of Milner's
-proof of the unique-solution theorem for $wb$}
-(Theorem~\ref{t:Mil89s3}). \hl{Now we have fully verified formal proofs for
-people who can read them.}
+proof of the unique-solution theorem for $wb$
+(Theorem~\ref{t:Mil89s3}). Now we have fully verified formal proofs for
+people who can read them.
 For some other textbook proofs, even they are correct, sometimes they actually
@@
 For the future work, formalising other equivalences and preorders could also be considered,
-notably the \hl{trace-based} equivalences, as well as more refined process
+notably the trace-based equivalences, as well as more refined process
 calculi such as value-passing CCS.
-% (e.g.~exploiting the type variable
-%of actions).}
 %
 On another research line, one could examine the formalisation of a different
-approach \cite{DurierHS17} to unique
+approach~\cite{DurierHS17} to unique
 solutions, in which the use of contraction is

### 2019-11-26 ic-journal/context.tex
Removed all reviewed highlights in the first part of the paper; re-enable highlights
Cumulative fixes with highlights
It is recommended that "cf." be used only to suggest a comparison, and the word "see" be used to point to a source of information.
https://en.wikipedia.org/wiki/List_of_Latin_abbreviations

@@
 \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}.
+\HOLConst{CONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}.
+\HOLConst{CONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
@@
 \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}.
+\HOLConst{WG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}.
+\HOLConst{WG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
@@
 \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}.
+\HOLConst{SG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}.
+\HOLConst{SG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
@@
 a hole, apart from the hole itself, is in forms of prefixes or sums:
-(c.f. Def.~\ref{def:guardness} and p.101,157 of \cite{Mil89} for
+(See Def.~\ref{def:guardness} and \citep[p.~101, 157]{Mil89} for
 the informal definitions.)
@@
 \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{SEQ} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\hfill{[SEQ_rules]}
+   \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}.
+\HOLConst{SEQ} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\hfill{[SEQ_rules]}
 \end{alltt}
@@
 \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a\sb{\mathrm{1}}} \HOLBoundVar{a\sb{\mathrm{2}}} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-        \HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{a\sb{\mathrm{1}}}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{a\sb{\mathrm{2}}}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}.
+        \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}.
+\HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
@@
 \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a\sb{\mathrm{1}}} \HOLBoundVar{a\sb{\mathrm{2}}} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{a\sb{\mathrm{1}}}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{a\sb{\mathrm{2}}}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.
-\HOLConst{WGS} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
-\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}.
+\HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}.
+\HOLConst{WGS} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.
+\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}.
@@
 \begin{alltt}
-\HOLConst{congruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenDefEquality{}}
+   \HOLConst{congruence} \HOLFreeVar{R} \HOLTokenDefEquality{}
      \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.
@@
 
-\HOLConst{precongruence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenDefEquality{}}
+   \HOLConst{precongruence} \HOLFreeVar{R} \HOLTokenDefEquality{}
      \HOLConst{PreOrder} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}.

### 2019-11-26 ic-journal/equa.tex
It is recommended that "cf." be used only to suggest a comparison, and the word "see" be used to point to a source of information.
https://en.wikipedia.org/wiki/List_of_Latin_abbreviations

@@
 % This setting does not cause any ambiguity, but sometimes leads to more
-% complex proofs.} (c.f. Section~\ref{sec:multivariate} for more details.)
+% complex proofs.} (see Section~\ref{sec:multivariate} for more details.)
 
@@
 another type for  equations, and we can reuse the existing
-variable substitution operation (c.f.\ the   SOS rule for the Recursion in
+variable substitution operation (cf.~the SOS rule for the Recursion in
 Fig.~\ref{f:LTSCCS}) for the substitution of equation variables.

### 2019-11-26 ic-journal/multivariate.tex
It is recommended that "cf." be used only to suggest a comparison, and the word "see" be used to point to a source of information.
https://en.wikipedia.org/wiki/List_of_Latin_abbreviations

@@
 This is an easy goal, due to the following lemma which is
- proved by induction on $E$:
+ proved by \hl{doing} induction on $E$:
 \begin{alltt}
@@
   some new logical constants from HOL's \texttt{pred_set}
-and \texttt{list} theories are used (c.f.~\cite{holdesc} for more
+and \texttt{list} theories are used (see~\cite{holdesc} for more
 details.): \HOLinline{\HOLConst{DISJOINT}} denotes set disjointness;
@@
 \HOLinline{\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{P}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{var}\\\;\HOLFreeVar{X}\ensuremath{)}\\\;\HOLSymConst{\ensuremath{=}}\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{P}} (or ``$l.X + P$'' in textbook
-notation) is weakly guarded (c.f.~Def.~\ref{def:guardness}).
+notation) is weakly guarded (cf.~Def.~\ref{def:guardness}).
 
@@
 variable in concern must not occur inside any recusion operator
-(c.f. the footnote at the beginning of Section~\ref{ss:SysEq}). In the
+(cf.~the footnote at the beginning of Section~\ref{ss:SysEq}). In the
 extreme case, if the set of free variables of an expression, say $E$,

### 2019-11-26 ic-journal/part2.tex
It is recommended that "cf." be used only to suggest a comparison, and the word "see" be used to point to a source of information.
https://en.wikipedia.org/wiki/List_of_Latin_abbreviations

@@
 (\texttt{WG}), we have proved Milner's strong unique-solution theorem
-in the \univariate case (c.f.~Section~\ref{sec:multivariate} for the
+in the \univariate case (cf.~Section~\ref{sec:multivariate} for the
 \multivariate case). The formal proof basically follows the outline of its

### 2019-11-26 ic-journal/part2.tex
Re-ordered Milner's 3 unique-solution theorems in Section 4.10. First we give the two theorems in Mil89, then the case of weak bisimilarity (not explicit in the book). This looks more fluent.

@@
 
-\subsubsection{Strong bisimilarity}
+\subsubsection{The case of strong bisimilarity}
 
@@
 
-\subsubsection{Weak bisimilarity}
-
-Milner's book~\cite{Mil89} contains only two ``unique solutions of
-equations'' theorems, one for strong equivalence, the other for
-observational congruence.   There is however a
-version  of the result for weak bisimilarity that shares a large portion of proof
-steps with that case for observational congruence.  
-As  weak bisimilarity 
- is not \hl{a} congruence, we have to be more restrictive on the syntax for
- the equation, using strong guardedness.
-% to make correct statement of this
-% theorem, we must slightly modify the concept of sequential expresses
-% with further restrictions: no direct sums (or only guarded sums).
-% The ``unique solution of equations'' theorem for weak equivalence
-% requires more restrictions on the expression, namely, .
-% Now we're ready to state and prove the following lemma:
-\begin{lemma}[\texttt{WEAK_UNIQUE_SOLUTION_LEMMA}]
-If the variable $X$ is guarded and sequential in $G$, and
-$G\{P/X\}\overset{\alpha}{\rightarrow} P'$, then $P'$ takes the form
-$H\{P/X\}$, for some expression $H$, and for any $Q$, we have
-$G\{Q/X\}\overset{\alpha}{\rightarrow} H\{Q/X\}$. Moreover $H$ is
-sequential, and if $\alpha = \tau$ then $H$ is also guarded.
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{G} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{G} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
-       \HOLFreeVar{G} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}.
-\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
-\HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}
-\end{alltt}
-\end{lemma}
-
-We can then derive the target theorem:
-\begin{theorem}[\texttt{WEAK_UNIQUE_SOLUTION}]
-Let $E$ be guarded and sequential expressions, and let $P \wb
-E\{P/X\}$,
-$Q \wb E\{Q/X\}$. Then $P \wb Q$.
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{Q}
-\end{alltt}
-\end{theorem}
-
-\subsubsection{Rooted bisimilarity}
+\subsubsection{The case of rooted bisimilarity}
 
@@
 \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Q}
+\end{alltt}
+\end{theorem}
+
+\subsubsection{The case of weak bisimilarity}
+
+Milner~\cite{Mil89} \emph{only mentioned} two ``unique solution of
+equations'' theorems, one for strong equivalence, the other for
+rooted bisimilarity.   There is, however, \hl{another
+version for} weak bisimilarity that shares a large portion of proof
+steps with the case \hl{of} rooted bisimilarity.
+As weak bisimilarity is not \hl{a} congruence, we have to be more restrictive
+on the syntax \hl{of} the equation, using strong guardedness.
+
+\begin{lemma}[\texttt{WEAK_UNIQUE_SOLUTION_LEMMA}]
+If the variable $X$ is guarded and sequential in $G$, and
+$G\{P/X\}\overset{\alpha}{\rightarrow} P'$, then $P'$ takes the form
+$H\{P/X\}$, for some expression $H$, and for any $Q$, we have
+$G\{Q/X\}\overset{\alpha}{\rightarrow} H\{Q/X\}$. Moreover $H$ is
+sequential, and if $\alpha = \tau$ then $H$ is also guarded.
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{G} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{G} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
+       \HOLFreeVar{G} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}.
+\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}
+\end{alltt}
+\end{lemma}
+
+We can then derive the target theorem:
+\begin{theorem}[\texttt{WEAK_UNIQUE_SOLUTION}]
+Let $E$ be guarded and sequential expressions, and let $P \wb
+E\{P/X\}$,
+$Q \wb E\{Q/X\}$. Then $P \wb Q$.
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{Q}
 \end{alltt}

### 2019-11-26 ic-journal/coarsest.tex
Prop. -> Proposition

@@
 
-Below we show how \hl{Prop.}~\ref{prop:coarsest} is connected with
+Below we show how Proposition~\ref{prop:coarsest} is connected with
 the statement in Theorem~\ref{t:rapproxCongruence}, and prove it under
@@
 which in turn is trivially contained in \texttt{SUM_EQUIV}, as shown
-in Fig.~\ref{fig:relationship}. Thus, to prove \hl{Prop.}~\ref{prop:coarsest},
+in Fig.~\ref{fig:relationship}. Thus, to prove Proposition~\ref{prop:coarsest},
 the crux is to prove that \texttt{SUM_EQUIV} implies

### 2019-11-26 ic-journal/multivariate.tex
Prop. -> Proposition

@@
 \begin{proof}
-Following the proof of Prop.~\ref{prop:transFV}, we do action
+Following the proof of Proposition~\ref{prop:transFV}, we do action
 induction on $E \arr{\mu} E'$ and simplify all subgoals by set-theoretic
@@
 \end{alltt}
-Note the difference with the proof of Prop.~\ref{prop:transFV}: now
+Note the difference with the proof of Proposition~\ref{prop:transFV}: now
 we have \texttt{INSERT} in place of \texttt{DELETE}. Then, we directly

### 2019-11-26 ic-journal/response-letter2.tex
Cumulative fixes
text

--- 2019-11-18 ic-journal/response-letter2.tex
@@
 (TODO)
-% We would like to thank the reviewers for many useful
-% comments and suggestions. We believe we have taken all of them into consideration, as best
-% as we could.
+
+Once more, we would like to thank the reviewers for many useful
+ comments and suggestions. %We believe we have taken all of them into consideration.
+We believe we have taken into account all 
+the points raised; we only comment below the most
+important ones.
+
+% , as best
+%  as we could.  The extension to 
+% the multivariable case (ie., moving from ``unique solution theorems'' for a single
+% equations, or contractions,  to multi-equations  or multi-contractions), 
+% has been a significant effort (eg,   additional 4,000 lines of proof scripts) but a
+% worthwhile one. Thanks the reviewers for pushing us to do  that.
 
@@
 
-In the following, we discuss the changes to the paper and provide a
-point-by-point reply to the issues that have been raised.
+% In the following, we discuss the changes to the paper and provide a
+% point-by-point reply to the issues that have been raised.
 
@@
 
-\vspace{1cm}
+% \vspace{1cm}
 
-\section*{Responses to Review 1}
+% \section*{Responses to Review 1}
 
-\subsection*{Meta comments}
+% \subsection*{Meta comments}
 
-\begin{enumerate}
+\begin{itemize}
+
+% \item \begin{quote}
+%     ``The multivariable case has been added. This is great: it makes
+%     the result stronger, and adds a real improvement over the
+%     conference version.'' 
+%   \end{quote}
+%   \Mark
+%   Thanks for your suggestion (on doing this) in the previous
+%   review. This extra formalisation work also closed an open question
+%   (on how to naturally/elegantly formalise the multivariate case of
+%   the unique-solution theorems) that the first author failed to
+%   resolve in his master thesis work. There exists several CCS
+%   formalisations as we mentioned in the related work (Section 6) but
+%   our formalisation is the only one which covers the unique-solution
+%   theorems, either in the univariable or multivariable cases.
 
 \item \begin{quote}
-    The multivariable case has been added. This is great: it makes the result stronger, and adds a real improvement over the conference version. 
-  \end{quote}
-  \Mark
-  Thanks.
-
-\item \begin{quote}
-Overall the authors did address the minor comments. But the paper
+``Overall the authors did address the minor comments. But the paper
 still contains quite a few grammatical and other minor mistakes, also
@@
 again through the paper; but this is certainly inexhaustive and the
-authors should do some more careful proofreading.
+authors should do some more careful proofreading.''
 \end{quote}
 \Mark
-(TODO) We have done a more careful proofreading and fixed all
-grammatically wrong sentences in the paper.
+ We have done a  careful proofreading,   amending all 
+grammatical problems we found, and also trying to improve the
+presentation in a number of sentences.
 
 \item \begin{quote}
-    In fact, one of the corrections appears to have introduced a new
-    bug: Theorem 4.7 in the new version is wrong; I guess Def. 4.6
+    ``In fact, one of the corrections appears to have introduced a new
+    bug: Theorem 4.7 in the new version is wrong; I guess Def.~4.6
     should be about weak transitions. In the original submission,
@@
     with weak bisimulation up-to found by the second author (one can
-    simply use the same counterexample $\{(\tau. a , 0)\}$).
+    simply use the same counterexample $\{(\tau. a , 0)\}$).''
   \end{quote}
   \Mark
-  This is an embarassing typo. The two $\arr{\mu}$ in
-  Definition 4.6 should be $\Arr{\mu}$ instead. Our actual formalization is
-  correct. Below is the fixed part of Definition 4.6:
-\begin{enumerate}
-\item Whenever $P \Arr{\mu} P'$ then, for some $Q'$, $Q \Arcap{\mu} Q'$ and $P' \wb \S \wb Q'$,
-\item Whenever $Q \Arr{\mu} Q'$ then, for some $P'$, $P \Arcap{\mu} P'$ and $P' \wb \S \wb Q'$.
-\end{enumerate}
+  This was a (embarassing) typo; we have corrected it. 
+%  when we were trying to make the paper
+%   more compact. The two $\arr{\mu}$ in
+%   Definition 4.6 should be $\Arr{\mu}$ instead. Our formalization
+%   (ever shown as verbatim generated code in the previous version) is
+%   however correct, because otherwise. Below is the fixed part of Definition 4.6:
+% \begin{enumerate}
+% \item Whenever $P \Arr{\mu} P'$ then, for some $Q'$, $Q \Arcap{\mu} Q'$ and $P' \wb \S \wb Q'$,
+% \item Whenever $Q \Arr{\mu} Q'$ then, for some $P'$, $P \Arcap{\mu} P'$ and $P' \wb \S \wb Q'$.
+% \end{enumerate}
+We also put the HOL definition back, to show the correspondence between the informal and formal definitions.
 
-\end{enumerate}
+% \end{enumerate}
 
-\subsection*{Detailed comments}
+% % \subsection*{Detailed comments}
 
-\begin{enumerate}
-  \item \begin{quote}
-25 "essentially formalised" => "essentially formalising" ? something is grammatically off with this sentence
-\end{quote}
-  \Mark
+%  We believe we have taken into account all 
+%  the points raised the reviewer; we only comment below the most
+%  important ones.
 
-  \item \begin{quote}
-47 ", then consider" => ". Then we consider" or something like that
-\end{quote}
-  \Mark
+% \begin{enumerate}
+%   \item \begin{quote}
+% 25 "essentially formalised" => "essentially formalising" ? something is grammatically off with this sentence
+% \end{quote}
+%   \Mark We have changed ``formalised'' (a wrong use of the past tense) to ``formalising''.
 
-  \item \begin{quote}
-311 "break the logic consistencies" break the logical consistency?
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 47 ", then consider" => ". Then we consider" or something like that
+% \end{quote}
+%   \Mark Fixed.
 
-  \item \begin{quote}
-337 "rec" is blue
-\end{quote}
-  \Mark Fixed. The ``rec'' was wrongly identified as the keyword of ML
-  languages in the \LaTeX{} verbatim package that we used.
+%   \item \begin{quote}
+% 311 "break the logic consistencies" break the logical consistency?
+% \end{quote}
+%   \Mark Fixed.
 
-  \item \begin{quote}
-323 and around: why is "a" in italics and $\bar{b}$ not?
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 337 "rec" is blue
+% \end{quote}
+%   \Mark Fixed. The ``rec'' was wrongly identified as the keyword of ML
+%   languages in the \LaTeX{} verbatim package that we used.
+
+%   \item \begin{quote}
+% 323 and around: why is "a" in italics and $\bar{b}$ not?
+% \end{quote}
+%   \Mark Fixed. This is a typesetting mistake.
 
@@
 \end{quote}
-  \Mark
+  \Mark We have reformulated a few sentences explaining this. 
+In particular, with reference to 
+the CCS syntax in Section~\ref{ss:ccs}, 
+alpha and beta represent, respectively, the 
+the set of agent variables 
+and %$\mathscr{L}$ (
+the
+set of names (the CCS syntax being parametric with respect to these sets)
 
-  \item \begin{quote}
-370 spurious \texttt{CCS_Subst} on line 370
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 370 spurious \texttt{CCS_Subst} on line 370
+% \end{quote}
+%   \Mark Removed.
 
-  \item \begin{quote}
-530 "for the contraction" the contraction what? the game? functional? or remove "the"
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 530 "for the contraction" the contraction what? the game? functional? or remove "the"
+% \end{quote}
+%   \Mark Removed ``the'' and re-organized the whole sentence.
 
-  \item \begin{quote}
-555 "an “up-to” techniques." => "“up-to” techniques."
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 555 "an “up-to” techniques." => "“up-to” techniques."
+% \end{quote}
+%   \Mark Fixed and re-organized the whole sentence.
 
-  \item \begin{quote}
-566 "the resulting ``weak bisimulation up``" correct; also the `` at the right should be ''
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 566 "the resulting ``weak bisimulation up``" correct; also the `` at the right should be ''
+% \end{quote}
+%   \Mark Fixed.
 
-  \item \begin{quote}
-597 "not powerful *enough* to prove" 
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 597 "not powerful *enough* to prove" 
+% \end{quote}
+%   \Mark Fixed, thanks.
 
-  \item \begin{quote}
-600 perhaps point out that this is (almost) 
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 600 perhaps point out that this is (almost) 
+% \end{quote}
+%   \Mark We have renamed the concept to ``bisimulation up to $\wb$ with weak arrows''.
 
@@
 \end{quote}
-  \Mark
+  \Mark We have reformulated the sentence. 
+%  fixed and re-organized this sentence adding an example
+%   of such limitations (due to Milner).
 
-  \item \begin{quote}
-965 "Recall *from* the beginning of Section 3 *that*"
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 965 "Recall *from* the beginning of Section 3 *that*"
+% \end{quote}
+%   \Mark Fixed, thanks.
 
@@
   \Mark 
+We have reformulated, trying to highlight its (possible) interest.
+% Milner said it can be proven by ``an easy action induction''.
+%              It is actually not that easy, and we take this chance to
+%              illustrate how to apply ``action induction'' in HOL.
+%              (TODO) 
+The proof has also been now shortened, according to the
+             latest updates in the HOL formalisation.
 
-  \item \begin{quote}
-1066 "the proof cannot complete" ?
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 1066 (should be 1056) "the proof cannot complete" ?
+% \end{quote}
+%   \Mark We wanted to say ``Proposition 5.1 is essential in the proofs of all unique-solution
+% theorems (multivariable vesions).''
 
-  \item \begin{quote}
-1075 "substitutes each possibly occurrences" "substitues each possible occurence"
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 1075 "substitutes each possibly occurrences" "substitues each possible occurence"
+% \end{quote}
+%   \Mark Fixed.
 
@@
 
-  \item \begin{quote}
-1149: "Recall *that* in"
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 1149: "Recall *that* in"
+% \end{quote}
+%   \Mark Fixed.
 
@@
 
-\end{enumerate}
+\end{itemize}

### 2019-11-26 ic-journal/ccs.tex
text

@@
 Here we recall the core theory of CCS.
-We assume a possibly infinite set of names $\mathscr{L} = \{a, b,
-\ldots\}$ yielding input and output labels (actions), plus a special invisible
+We assume a possibly infinite set of \emph{names} $\mathscr{L} = \{a, b,
+\ldots\}$ yielding \emph{input} and \emph{output labels} (or \emph{actions}), plus a special invisible
 action $\tau \notin \mathscr{L}$, and another possibly infinite
-set of agent variables \hl{$\mathscr{X} = \{X, Y, \ldots\}$}.
-The class of \hl{all} CCS \hl{terms (or expressions)} is then inductively
+set of \emph{agent variables} \hl{$\mathscr{X} = \{X, Y, \ldots\}$}.
+The class of  CCS \hl{terms} is then inductively
 defined from $\nil$ (the terminated process) and agent variables by the operators

### 2019-11-26 ic-journal/coarsest.tex
text

--- 2019-11-26 ic-journal/coarsest.tex
@@
 Theorem~\ref{t:rapproxCongruence}, i.e. $\rapprox$ is the coarsest
-congruence contained in $\wb$. This theorem is of special \hl{interest} to
-us, because under our \hl{CCS syntax (with only binary summations)} it seems impossible to prove it
-without any \hl{antecedent such as ``the involved processes do not
-  use up all available labels''}. The general form of this theorem can be
-expressed informally as below~\cite{van2005characterisation,Gorrieri:2015jt,Mil89}:
+congruence contained in $\wb$.
+The formalisation of this theorem presents some 
+delicate aspects; for instance, 
+with   our CCS syntax
+(with only binary sums)
+we have to add  an hypothesis about 
+ \hl{the involved processes  not
+  using all available labels}.
+% This theorem is of special \hl{interest} to us, because under our
+% \hl{CCS syntax (with only binary summations)} it seems impossible to
+% prove it without any \hl{antecedent such as ``the involved processes
+%   do not use up all available labels''}.
+The general form of the theorem is thus~\cite{van2005characterisation,Gorrieri:2015jt,Mil89}:
 \begin{proposition}
@@
 The standard argument~\cite{Mil89} requires that $p$
-and $q$ do not use up \hl{all} available labels (i.e.~visible actions).
-Formalising this \hl{result, however,} requires a detailed treatment on free and bound names of CCS
-processes (with the restriction operator being a binder).
-\hl{In} this project we do not discuss free and bound names (also
-called ``sorts'') of CCS processes. Instead, we
-assume \hl{a weaker condition} that all immediate \emph{weak} derivatives of
- $p$ and $q$ do not use all available \hl{labels}. We \hl{might} call it
+and $q$ do not use \hl{all} available labels (i.e.~visible actions).
+Formalising this \hl{result, however,} requires a detailed treatment of free and bound names of CCS
+processes (with the restriction operator acting as a binder).
+\hl{In} our formalisation, in contrast, 
+%  we do not discuss free and bound names (also
+% called ``sorts'') of CCS processes. Instead, 
+we 
+assume \hl{the weaker condition} that all immediate \emph{weak} derivatives of
+ $p$ and $q$ do not use all available \hl{labels}. We  call this
  the \emph{free action} property:
@@
 on CCS processes, the composition closure of $R$ is always at least as
-fine as $R$: ($\subseteq_r$ stands for \emph{relational subset}.)
+fine as $R$ ($\subseteq_r$ stands for \emph{relational subset}):
 \begin{alltt}
@@
 \end{alltt}
-Furthermore, we prove that any (pre)congruence contained in $R$, \hl{who
+Furthermore, we prove that any (pre)congruence contained in $R$, \hl{that
 itself} needs not to be a (pre)congruence,
@@
 
-Given the central role of the  
+Given the central role of  
  summation, we also consider the relation closure of bisimilarity
@@
 % \end{alltt}
-Rooted bisimilarity $\rapprox$ (a congruence contained in
-$\wb$), is now contained in \texttt{WEAK_CONGR},
+Rooted bisimilarity $\rapprox$ (as a congruence contained in
+$\wb$) is now contained in \texttt{WEAK_CONGR},
 which in turn is trivially contained in \texttt{SUM_EQUIV}, as shown
@@
 
-\hl{The} actual formalisation of (\ref{equa:pq}) says:
+\hl{The}  formalisation of (\ref{equa:pq}) says:
 \begin{theorem}[\texttt{COARSEST_CONGR_RL}]
@@
 ($\rcontr$) is also the coarsest
-precongruence contained in the bisimilarity contraction ($\mcontrBIS$)
-(the other direction is trivial):
+precongruence contained in the bisimilarity contraction ($\mcontrBIS$):
 \begin{theorem}[\texttt{COARSEST_PRECONGR_RL}]
@@
 our result above. Indeed, in our result we only look at immediate weak
-derivatives for $p$ and $q$, and only requires that there is an input
+derivatives for $p$ and $q$, and only require that there is an input
 or output action
@@
 not to be the same for $p$ and for $q$,
-as an action $a$ and its complementary $\outC a$ are
-considered as \emph{different} actions.
+and an action $a$ and its complementary $\outC a$ are
+considered {different} actions.
 
@@
 In this section, we give another more complex proof of the second part
-of Theorem~\ref{t:rapproxCongruence}, but only for finite-state CCS:
+of Theorem~\ref{t:rapproxCongruence}, but only for finite-state CCS.
 \begin{theorem}[\texttt{COARSEST_CONGR_FINITE}]
@@
 Glabbeek~\cite{van2005characterisation}.
-The core lemma says, for
+The core lemma says that for
 any two processes $p$ and $q$, if there exists a \emph{stable} (i.e.~$\tau$-free)
@@
  $q$, then \texttt{SUM_EQUIV} indeed implies rooted bisimilarity
- ($\rapprox$): (see~\cite{Tian:2017wrba} for more details of the proof)
+ ($\rapprox$) (c.f.~\cite{Tian:2017wrba} for more details of the proof):
 \begin{alltt}
@@
 We have only partially formalised
-this proof (Theorem~\ref{thm:coarsestfiniteState} in next section), because ``the typed logic
+this proof (Theorem~\ref{thm:coarsestfiniteState} in next section),
+because
+the typed logic
 implemented in various HOL systems (including Isabelle/HOL) is not
 strong enough to define a type for all possible
-ordinals''~\cite{norrish2013ordinals}.
+ordinals~\cite{norrish2013ordinals}.
 As a consequence, the final result is only for finite-state
-CCS~--- a  restricted class.\footnote{\hl{van Glabbeek's
-  original proof applies to all CCS processes, but it
+CCS.\footnote{\hl{van Glabbeek's
+  original proof applies to all CCS processes; however,  it
   requires the CCS syntax to support arbitrary large summations based
-  on ordinals, and it relies on the fact that, there always exists an
-  ordinal large than the cardinality of any given set. This is beyond
-  the capacity of HOL.}}
+  on ordinals, and relies on the existence  of an
+  ordinal larger than the cardinality of any given set. This is beyond
+  the possibilities of HOL.}}
 
@@
 \item for $\lambda$ a limit ordinal, $k_\lambda = \sum_{\mu < \lambda}
-  k_\mu$, meaning that $k_\lambda$ is constructed from all graphs
-  $k_\mu$ for $\mu < \lambda$ by identifying their root.
+  k_\mu$ (meaning that $k_\lambda$ is constructed from all graphs
+  $k_\mu$ for $\mu < \lambda$ by identifying their root).
 \end{itemize}
@@
   and using the SOS rules
-  ($\mathrm{Sum}_1$) and ($\mathrm{Sum}_2$), we proved
+  ($\mathrm{Sum}_1$) and ($\mathrm{Sum}_2$), we have proved
 the following properties of Klop functions:
@@
 any  of the derivatives of two  given 
-two finite-state CCS processes $p$ and $q$
+ finite-state CCS processes $p$ and $q$
 (by definition, the number of such derivatives is finite).
@@
 \begin{enumerate}
-\item Define \emph{reachable} as the RTC of a relation, which
+\item Define \emph{reachable} as the RTC (reflexive and transitive
+  closure)
+ of a relation, which
   indicates the existence of a transition between two processes:
@@
 \end{definition}
-
-Among many properties of above definitions, we mainly rely on the
-following (trivial) property for weak transitions:
+We rely
+on  various 
+ properties of the above definitions, such as the following one:
 \begin{proposition}

### 2019-11-26 ic-journal/conclusions.tex
text

--- 2019-09-15 ic-journal/conclusions.tex
@@
 
-In this paper, beside the introduction of rooted contraction and its
-unique solution theorems as a theoretical extension
-of~\cite{sangiorgi2017equations},
-we highlighted a comprehensive formalisation of the theory of CCS in the 
+In this paper, besides  introducing rooted contraction and its
+unique solution theorems,
+we have carried out a comprehensive formalisation of the theory of CCS in the 
 HOL4 theorem prover. In particular, the formalisation supports four
@@
 
-The formalisation has actually focused on the theory of
-unique solution of equations and contractions, both \univariate and
-\multivariate cases. It    
+The formalisation has focused on the theory of
+unique solution of equations and contractions, both in the  \univariate and
+in the \multivariate cases. It    
  has allowed us to further develop the theory,
@@
   when there are long case analyses to be carried out.}
-\hl{Some of the textbook proofs were even wrong and the correct version is
-known but not available in the literature. This is the case of Milner's
-proof of the unique-solution theorem for $wb$}
-(Theorem~\ref{t:Mil89s3}). \hl{Now we have fully verified formal proofs for
-people who can read them.}
-For some other textbook proofs, even they are correct, sometimes they actually
-do not need all information from the antecedents, which can be further
-weakened. This kind of improvements can be easily found during the
-formalisation work.
-For our CCS formalisation, we believe that all the definitions and
-theorem statements are easy to read and
-understand, as they are very close to their original statements in
-textbooks~\cite{Gorrieri:2015jt,Mil89}.
+% \hl{Some of the textbook proofs were even wrong and the correct version is
+% known but not available in the literature. This is the case of Milner's
+% proof of the unique-solution theorem for $wb$}
+% (Theorem~\ref{t:Mil89s3}). \hl{Now we have fully verified formal proofs for
+% people who can read them.}
+% For some other textbook proofs, even they are correct, sometimes they actually
+% do not need all information from the antecedents, which can be further
+% weakened. This kind of improvements can be easily found during the
+% formalisation work.
+%For our CCS formalisation, 
+We believe that the formalisation of  all definitions and
+theorems are easy to read and
+understand, as they are close to their original statement in
+textbooks.
 
-For the future work, formalising other equivalences and preorders could also be considered,
-notably the \hl{trace-based} equivalences, as well as more refined process
+For  future work, formalising other equivalences and preorders could also be considered,
+notably  \hl{trace-based} equivalences, as well as more refined process
 calculi such as value-passing CCS.
@@
 %
-On another research line, one could examine the formalisation of a different
-approach \cite{DurierHS17} to unique
+A different and possibly challenging  research line is
+ the formalisation of a different
+approach \cite{DurierHS17,DurierHS18} to unique
 solutions, in which the use of contraction is
@@
 %
-Finally, the disjointness between free and bound variables in the current
-\multivariate formalisation is certainly a limitation that can be
-removed in the future. If needed, extending the current work to
-infinite number of equations and variables is also feasible.
+% Finally, the disjointness between free and bound variables in the current
+% \multivariate formalisation is certainly a limitation that can be
+% removed in the future. If needed, extending the current work to
+% infinite number of equations and variables is also feasible.
 
@@
 from  the \hl{anonymous reviewers} and several people from the HOL
-community, including (in \hl{alphabetic} order) Robert Beers, Jeremy Dawson,
+community, including (in \hl{alphabetical} order) Robert Beers, Jeremy Dawson,
 Ramana Kumar,
@@
 %
+Sangiorgi has been  supported by 
+ MIUR-PRIN project `Analysis of
+Program Analyses' (ASPRA, ID 201784YSZ5$\_$004), and by the 
+European Research
+Council (ERC) Grant DLV-818616 DIAPASoN.
 The paper was written in memory of Michael J.~C.~Gordon, the creator of the HOL theorem prover.

### 2019-11-26 ic-journal/context.tex
text

@@
 \end{alltt}
-Notice in above inductive definitions, for any CCS term $p$,
-\HOLinline{\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{p}} is a valid context. In this case there is no
-hole in the context. On the other hand, if any CCS term with recursion
-could be a context, the recursion must be a subterm of this $p$.
+In above inductive definitions, for any CCS term $p$,
+\HOLinline{\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{p}} is a
+valid context, with  no
+hole. 
+% On the other hand, if any CCS term with recursion
+% could be a context, the recursion must be a subterm of this $p$.
 
@@
 \end{alltt}
-(Notice the differences between a weak guarded context and a normal
-one: $\lambda t. t$ is not weakly guarded as the variable is directly
-exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
+(Notice the differences between a weakly guarded context and an
+ordinary
+context: $\lambda t. t$ is not weakly guarded as the variable is directly
+exposed, without any prefixed action. And $\lambda t. a.e[t]$ is weakly
 guarded as long as $e[\cdot]$ is a context, not necessary weakly guarded.)
@@
 a hole, apart from the hole itself, is in forms of prefixes or sums:
-(See Def.~\ref{def:guardness} and \citep[p.~101, 157]{Mil89} for
+(c.f. Def.~\ref{def:guardness} and p.101,157 of \cite{Mil89} for
 the informal definitions.)
@@
 
-Many lemmas about the above concepts (\HOLinline{\HOLConst{CONTEXT}}, \HOLinline{\HOLConst{WG}},
-\HOLinline{\HOLConst{SEQ}}, etc.) have to be proved for the
- relationships among these kinds of contexts and properties about their
- compositions. These proofs are usually tedious and long,  due to multiple levels of
+In our work, several 
+ lemmas about the above concepts (\HOLinline{\HOLConst{CONTEXT}}, \HOLinline{\HOLConst{WG}},
+\HOLinline{\HOLConst{SEQ}}, etc.)  were needed 
+to capture properties about
+ the
+ relationships among these kinds of contexts and their
+ composition. These proofs are usually tedious and long,  due to multiple levels of
  inductions on the structure of the contexts.
@@
 \texttt{CONTEXT}. The only difference between congruence and
-precongruence is that the former  is an equivalence (reflexive,
-symmetric, transitive), while the latter can  just be  a preorder (reflexive, transitive):
+precongruence is that the former  is an equivalence, while
+ the latter can  just be  a preorder:
 \begin{alltt}
@@
 Both strong bisimilarity ($\sim$) and
-rooted bisimilarity ($\approx^c$) are congruence:
+rooted bisimilarity ($\approx^c$) are congruence relations:
 \begin{alltt}
@@
 as $\approx$ is indeed preserved by guarded sums.
-
 Rooted contraction, on the other hand, is a precongruence:

### 2019-11-26 ic-journal/equa.tex
text

--- 2019-11-25 ic-journal/equa.tex
@@
 For instance,  $X$ is free in $a.X + \recu Y (b.Y)$ while $Y$
-is bound; \hl{And} in $a.X + \recu X (b.X)$, $X$ is both free and bound.
-A \hl{term} without free variables is \hl{called} a \emph{process}.
+is bound; whereas 
+$X$ is both free and bound 
+ in $a.X + \recu X (b.X)$.
+A \hl{term} without free variables is  a \emph{process}.
 % This setting does not cause any ambiguity, but sometimes leads to more

### 2019-11-26 ic-journal/expansion.tex
text

@@
 % This new sentence maintains a link with Definition 2.1
-\hl{It can be proved that, $P_1 \rapprox Q_1 \wedge P_2 \rapprox Q_2 \Longrightarrow
-P_1 + P_2 \rapprox Q_1 + Q_2$.}
+Relation $\rapprox$ is indeed preserved by the sum operator.
+% \hl{It can be proved that $P_1 \rapprox Q_1 \wedge P_2 \rapprox Q_2 \Longrightarrow
+% P_1 + P_2 \rapprox Q_1 + Q_2$.}
 The above definition also brings up a proof technique for proving rooted
@@
 indeed it is  the coarsest congruence contained in bisimilarity
-(See Section~\ref{s:coarsest} and \hl{\mbox{Section~\ref{ss:context}}} for more details):
+(see Section~\ref{s:coarsest} and \hl{\mbox{Section~\ref{ss:context}}} for more details):
 \begin{theorem}

### 2019-11-26 ic-journal/formal.tex
It is recommended that "cf." be used only to suggest a comparison, and the word "see" be used to point to a source of information.
https://en.wikipedia.org/wiki/List_of_Latin_abbreviations
text

@@
 
-The terms of the HOL logic are expressions \hl{which} denote elements of the
-sets denoted by types. There are four kinds of terms in the HOL
+The terms of the HOL logic represent elements of the
+sets denoted by the types. There are four kinds of terms in the HOL
 logic. \hl{They} can be described (in simplified forms) by the BNF grammar in
-Fig.~\ref{fig:hol-terms}; see~\ref{hollogic} for a complete description.
+Fig.~\ref{fig:hol-terms}; see~\cite{hollogic} for a complete description.
 
@@
 types needed for} CCS.
-
 Finally, the whole HOL \emph{standard} theory is based on the
@@
 \hl{manually}, may break logical \hl{consistency}.
-\hl{In general,} the theorem prover guarantees that,
-without adding new axioms, if both the definitions and the statements
-of theorems are correct, then the \hl{proofs of these theorems} is
- \hl{also} correct.
+% \hl{In general,} the theorem prover guarantees that,
+% without adding new axioms, if both the definitions and the statements
+% of theorems are correct, then the \hl{proofs of these theorems} is
+%  \hl{also} correct.
 % This last sentence doesn't have a good link with the previous context,

### 2019-11-26 ic-journal/intro.tex
text

@@
   (or contraction) with multiple equation variables is considered.
-The \univariate versions \hl{of unique-solution theorems} use
+The \univariate versions the \hl{of unique-solution theorems} use
 $\lambda$-functions to present CCS equations,

### 2019-11-26 ic-journal/multivariate.tex
text

--- 2019-11-21 ic-journal/multivariate.tex
@@
 contractions'' (Theorem~\ref{t:rcontraBisimulationU}).
-\hl{This formalisation only supports finitely many
+\hl{This formalisation  supports finitely many
   equations/contractions and equation variables.}\footnote{\hl{The original theorems
-hold for even (uncountably) infinite equations and equation variables.}}
-We chose these two theorems because they both depend on the same
-concept of ``weakly guarded contexts'', and Lemma~\ref{lem:milner313}.
-The work is an extension of the \univariate case~\cite{EPTCS276.10}
+hold for even  infinitely-many equations and equation variables.}}
+We chose these two theorems because of their relevance and 
+because they well illustrate the effort needed for the \multivariate case. 
+% Both theorems depend on the same
+% concept of ``weakly guarded contexts'', and Lemma~\ref{lem:milner313}.
+The work is an extension of the \univariate case %~\cite{EPTCS276.10}
  in the sense that neither the CCS datatype nor
@@
 a system of equations $\{X_i = E_i\}_{i\in I}$ are usually considered as
-\emph{equation variables}
+equation variables
 \emph{outside} of the CCS syntax; then an equation body  $E_i$  is an \emph{open} expression
@@
 whole new datatype (with extra equation variables) in which each CCS
-opeartor must be duplicated, or we have to  add equation variables as a
+operator must be duplicated, or we have to  add equation variables as a
 new primitive (e.g.~\texttt{Var X}) to the existing CCS type (besides
@@
 substitution function used in SOS rules \texttt{REC} can be also
-used for substituting eqaution variables.
+used for substituting equation variables.
 However, a lot of care is needed in the proofs of many
@@
 
-Recall \hl{from} the beginning of Section~\ref{s:eq} \hl{that},
-CCS syntax leaves the syntactic possibility that an
-agent variable $A$ occurs outside the recursion operator of the same
-variable. In Milner's original book chapter~\cite{milner1990operational}, the
-variables which occur in Recursion (such as $X$ in $\recu X E$) are
-called \emph{bound} variables, while those which occur unbound are called
-\emph{free} variables.
+As mentioned at
+ the beginning of Section~\ref{s:eq},  
+ an
+agent variable may  occur outside the recursion in which it is bound;
+i.e., a variable can appear both  \emph{bound} and \emph{free} in a term. 
+% In Milner's original book chapter~\cite{milner1990operational}, the
+% variables which occur in Recursion (such as $X$ in $\recu X E$) are
+% called \emph{bound} variables, while those which occur unbound are called
+% \emph{free} variables.
 
-We denote the set of all bound variables of a
-given CCS term $E$ (we recall that these are variables that are bound in a recursion
+We denote the set of bound variables of a
+given CCS term $E$ (the variables that are bound in a recursion
 subexpression of $E$) as $\bv{E}$ (or \HOLinline{\HOLConst{BV}\\\;\HOLFreeVar{E}} in HOL), and the set of  free
 variables as $\fv{E}$ (or \HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}} in HOL). Both \HOLinline{\HOLConst{BV}} and \HOLinline{\HOLConst{FV}} have the
-type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}'', i.e.
-functions taking CCS terms returning sets of
+type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha},
+  \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd
+  \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}'',
+i.e. functions taking CCS terms and returning sets of
 variables (of type \HOLinline{\ensuremath{\alpha}}).
@@
 
-Note that, in CCS expression, the set of free and bound
-variables need not be disjoint, e.g.\ in  $X + \recu X E$.
+The set of free and bound
+variables of a term need not be disjoint, e.g.\ in  $X + \recu X E$.
 More importantly, when going
@@
 if $E \arr{\mu} E'$ and $\fv{E} = \emptyset$, then $\fv{E'} =
-\emptyset$. Or, formally:
+\emptyset$. Formally:
 \begin{alltt}
@@
 \begin{proof}
-We \hl{actually proved} a stronger result \hl{saying} the set of free
-variables \hl{in any CCS process} decreases through its derivatives:
+We \hl{actually prove} a stronger result,  \hl{asserting} that the set of free
+variables \hl{in a CCS process} may decrease through its derivatives:
 \begin{alltt}
@@
 
-\hl{Milner said it can be proven by ``an easy action induction''.}
-\hl{It is actually not that easy, and we take this chance to
-  illustrate how to apply ``action induction'' (in HOL), which} is actually a higher-order application
-of the following \emph{induction principle} generated together with SOS
-rules (which essentially says that \HOLinline{\HOLConst{TRANS}} is the smallest relation
-satisfying SOS rules):
+In textbooks such as \cite{Mil89} the proof of the above property is 
+commented as  ``an easy action induction''.
+In HOL, the proof 
+ is actually non-trivial:
+ ``action induction''  becomes a form of  higher-order application
+of the following \emph{induction principle}, generated together with the SOS
+rules (and that essentially says that \HOLinline{\HOLConst{TRANS}} is the smallest relation
+satisfying the SOS rules):
 \begin{alltt}
@@
 $X$ under this specific $P$, by Modus Ponens (MP) the original proof
-would have completed.
-This is the essence of action induction.
-Now the original goal can be reduced to several conjunct
+is completed.
+%This is the essence of action induction.
+Now, the  goal can be reduced to several conjunct
 subgoals, each corresponding to one SOS rule. For instance, in
@@
 \subseteq \fv{E + E'} = \fv{E} \cup \fv{E'}$. Eventually we have only
-the following goal left: (the term above the dash line is the goal,
-those below the line are assumptions)
+the following goal left (the term above the dash line is the goal,
+those below the line are assumptions):
 \begin{alltt}
@@
 \end{alltt}
-Notice that, \HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLConst{DELETE}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{=}}\\\;\HOLConst{FV}\\\;\ensuremath{(}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{)}}, so
+Note that \HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLConst{DELETE}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{=}}\\\;\HOLConst{FV}\\\;\ensuremath{(}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{)}}, so
 this is indeed the consequence of action induction on the Recursion.
@@
 \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}, no matter if \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E}} or not, and the proof
-would have completed. Thus it remains to show that
+would be complete. Thus it remains to show that
 \begin{alltt}
@@
   theorems.
-In comparison with} the above proof, the proof of the similar
-result for bound variables is \hl{much} easier:
+In comparison with} the above proof, the proof of the analogous
+result for bound variables is  easier:
 \begin{proposition}
@@
     the right side equals to \HOLinline{\HOLConst{BV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}\\\;\ensuremath{(}\HOLFreeVar{X}\\\;\HOLConst{INSERT}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}} $=$
-    \HOLinline{\HOLFreeVar{X}\\\;\HOLConst{INSERT}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}}. Thus
-the    proof can 
- be completed.
+    \HOLinline{\HOLFreeVar{X}\\\;\HOLConst{INSERT}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}}. This
+completes
+the    proof.
 \end{proof}
@@
 There are two ways to represent  the \multivariate
-substitution of $E\{\til P/\til X\}$ which substitutes each \hl{possible
-occurrence} of free variables $X_i$ in $E$ with the corresponding
+substitution  $E\{\til P/\til X\}$, that replaces each \hl{free occurrence}
+of  variables $X_i$ in $E$ with the corresponding
 $P_i$: (1) iterately applying the existing \univariate
@@
 map \HOLinline{\HOLFreeVar{fm}} of type \HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}} and a CCS expression,
-and then returns another CCS expression in which
-all occurrences of variables in the \HOLinline{\HOLFreeVar{fm}}'s domain are substituted with
+and returns another CCS expression in which
+all occurrences of variables in \HOLinline{\HOLFreeVar{fm}} domain are substituted with
 the corresponding value in \HOLinline{\HOLFreeVar{fm}}. Such a finite map can be built from
 the list of variables \HOLinline{\HOLFreeVar{Xs}} and the corresponding targets
-\HOLinline{\HOLFreeVar{Ps}} (of the same length) by a helper function \HOLinline{\HOLConst{fromList}} (whose details are
-not interesting and omitted here), while
+\HOLinline{\HOLFreeVar{Ps}}  by a helper function \HOLinline{\HOLConst{fromList}} (whose details 
+are omitted here), while
 \HOLinline{\HOLConst{CCS_SUBST}\\\;\ensuremath{(}\HOLConst{fromList}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Ps}\ensuremath{)}\\\;\HOLFreeVar{E}} is
 abbreviated as \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}.
-The substitution process is
-variable-parallel thus order-independent. For most CCS operators it
+The substitution mechanism is
+ order-independent. For most CCS operators it
 just recursively calls itself on subterms. The only
@@
 \end{alltt}
-Note that the variable substitution only occurs on free
+Variable substitution only occurs on free
 variables. In the case of $\recu X E$: if $X$ (a bound variable) is in
@@
 ``\HOLinline{\HOLConst{set}\\\;\HOLFreeVar{Xs}}'' is the set converted from the list \HOLinline{\HOLFreeVar{Xs}};
-\HOLinline{\HOLConst{ALL_DISTINCT}} says
-all elements of a list are distinct with each other; \HOLinline{\HOLConst{MAP}} is
+\HOLinline{\HOLConst{ALL_DISTINCT}} says that
+the elements of a list are all distinct; \HOLinline{\HOLConst{MAP}} is
 the mapping function from one list to another; \HOLinline{\HOLConst{EVERY}} means
@@
 new list from two lists of the same length, and each element of the new list is a pair of
-elements, each from one of the old lists.}
+elements from  the given lists.}
 
@@
   Substituting each free variable $X$ % of \HOLinline{\HOLFreeVar{Xs}}
-  in $E$ to \HOLinline{\HOLConst{var}\\\;\HOLFreeVar{X}} (itself) does not change $E$:
+  in $E$ with \HOLinline{\HOLConst{var}\\\;\HOLFreeVar{X}} (itself) does not change $E$:
 \begin{alltt}
@@
 \begin{lemma}[\texttt{BV_SUBSET_BIGUNION}]
-The bound variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}} have
-at most the union of all bound variables from $E$ and \HOLinline{\HOLFreeVar{Ps}}.
+The bound variables of
+\HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}
+are contained in  the union of the bound variables from $E$ and \HOLinline{\HOLFreeVar{Ps}}.
 \begin{alltt}
@@
 \begin{lemma}[\texttt{FV_SUBSET_BIGUNION_PRO}]
-The free variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}} have
-at most the union of all free variables from $E$ and \HOLinline{\HOLFreeVar{Ps}},
+The free variables of
+\HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}
+are contained in the  union of the free variables in $E$ and \HOLinline{\HOLFreeVar{Ps}},
 excluding \HOLinline{\HOLFreeVar{Xs}}.
@@
 variables of $E$ and the free substitution variables are disjoint) is
-not necessary but makes some proofs (much) easier. 
+not necessary but makes some proofs  easier. 
 As these lemmas are
@@
 
-Recall \hl{that} in Section~\ref{ss:context}, \univariate contexts and their
+As mentioned in 
+ Section~\ref{ss:context}, \univariate contexts and their
 guarded companions are defined as predicates over $\lambda$-expressions
@@
 \HOLinline{\HOLConst{SG}} (guarded contexts) and \HOLinline{\HOLConst{SEQ}} (sequential
-contexts), are all defined inductively, i.e.~they are built from some ``holes''
+contexts), are  defined inductively, i.e.~they are built from some ``holes''
 in a bottom-up way.
@@
 \HOLinline{\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{P}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{var}\\\;\HOLFreeVar{X}\ensuremath{)}\\\;\HOLSymConst{\ensuremath{=}}\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{P}} (or ``$l.X + P$'' in textbook
-notation) is weakly guarded (c.f.~Def.~\ref{def:guardness}).
+notation), and the expression  is weakly guarded (Def.~\ref{def:guardness}).
 
@@
 \end{alltt}
-Also note that \HOLinline{\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{Y}\\\;\HOLSymConst{\ensuremath{=}}\\\;\ensuremath{[}\HOLFreeVar{t}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\ensuremath{(}\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{Y}\ensuremath{)}}
+Note that \HOLinline{\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{Y}\\\;\HOLSymConst{\ensuremath{=}}\\\;\ensuremath{[}\HOLFreeVar{t}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\ensuremath{(}\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{Y}\ensuremath{)}}
 can be expressed as a \univariate substitution of the original term.
@@
 \end{alltt}
-Notice that, the above definitions take an extra list of variables \HOLinline{\HOLFreeVar{Xs}} and
+The above definitions take an extra list of variables \HOLinline{\HOLFreeVar{Xs}} and
 assert the CCS expression \HOLinline{\HOLFreeVar{E}} with respect to this list. This
@@
 variables.\footnote{Here \HOLinline{\HOLConst{SET_TO_LIST}} converts a finite set
-  to a list of the same elements. It turns out that, we never need this, because
+  to a list of the same elements. It turns out that we never need this, because
   in all unique-solution theorems a list of variables \HOLinline{\HOLFreeVar{Xs}} is fixed and
-  then all equations are required to contain free variables up to
-  \HOLinline{\HOLFreeVar{Xs}}. Thus our choices in these definitions are optimal.}
-(The guardedness and sequentiality can also be defined similarily
-when needed, using
+  then all equations are required to contain free variables in
+  \HOLinline{\HOLFreeVar{Xs}}.}
+(Guardedness and sequentiality can also be defined similarily, using
 their \univariate companions (\texttt{SG} and \texttt{SEQ}).)
 
-The most important property of contexts are that, strong bisimilarity
+The most important property of contexts are that strong bisimilarity
 and other (pre)congruence relations are preserved by contexts, e.g.
@@
 If two tuples of processes $\til P$ and $\til Q$ are strongly
-bisimilar\footnote{Hereafter, HOL terms like \HOLinline{\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenStrongEQ}\\\;\HOLFreeVar{Qs}}
-  means that, two list of CCS processes are componentwise
-  (strongly) bisimilar. The same notation $\sim$ has been overloaded.}
-for any context $E$ with the possible occurrences of variables $\til
-X$ (same length as $\til P$ and $\til Q$), $E\{\til P/\til X\}$ and
-$E\{\til Q/\til X\}$ are also strongly bisimilar:
+bisimilar\footnote{A HOL term like \HOLinline{\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenStrongEQ}\\\;\HOLFreeVar{Qs}}
+  means that two lists of CCS processes are componentwise
+  (strongly) bisimilar. %The same notation $\sim$ has been overloaded.
+}, then 
+for any context $E$
+% with the possible occurrences of variables $\til X$ 
+%(same length as $\til P$ and $\til Q$),
+also  $E\{\til P/\til X\}$ and
+$E\{\til Q/\til X\}$ are  strongly bisimilar:
 \begin{alltt}
@@
 
-Not every expression fit with CCS syntax is a context: any free
-variable in concern must not occur inside any recusion operator
-(c.f. the footnote at the beginning of Section~\ref{ss:SysEq}). In the
-extreme case, if the set of free variables of an expression, say $E$,
-is disjoint with a list of variables $\til X$, then this expression is
-for sure a context:
+Not every  expression from the CCS syntax is a context, as 
+context variable may not within a recusion. Trivially,
+ if the set of free variables of an expression
+is disjoint from a list of variables, then the expression is
+ a context:
 \begin{alltt}
@@
 \end{alltt}
-On the other hand, for any context (w.r.t.~$\til X$) of the form $\recu Y E$, we can
-conclude that, the set of free variables of $E$ excluding $Y$, is
-disjoint with $\til X$, i.e.
+On the other hand, for any context (w.r.t.~$\til X$) of the form $\recu Y E$, 
+ the set of free variables of $E$ excluding $Y$ is
+disjoint from $\til X$, i.e.
 \begin{alltt}
@@
 \end{alltt}
-Notice that, the above result is the best possible one. We cannot
-conclude \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}}, because $Y$ as a bound
-variable of $\recu Y E$ may be also a free variable in $\til X$. We
+In the above result we cannot
+conclude \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}}, because $Y$, as a bound
+variable of $\recu Y E$, may  also be  a free variable in $\til X$. We
 also cannot conclude \HOLinline{\HOLConst{context}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{E}}, because in $\recu Y E$
 it is possible that the bound variable $Y$ occurs inside another
-recursion operator, then in $E$ it now becomes free. (See $\recu Y
-(\recu Z (a.Y + b.Z) + c.Y)$ for such an example.)
+recursion operator, and  then it is a free variable for $E$ (as in $\recu Y
+(\recu Z (a.Y + b.Z) + c.Y)$).
 
@@
 substitute some free variables in a context $C$ for some weakly-guarded
-contexts, the resulting term is weakly-guarded (w.r.t.~the same set of variables):
+contexts the resulting term is weakly-guarded (w.r.t.~the same set of variables):
 \begin{alltt}
@@
 \end{itemize}
-Obviously the two lists must have the same length. The all
-distinctness of $\til X$ is not really necessary but is very
-reasonable. Furthermore, we should assume $\til E$ does not contain
-any other free variables not in $\til X$, as Milner's unique-solution
-theorems also require the same condition.\footnote{One may think that,
-  if all other (i.e.~not in $\til X$) free variables in $\til E$ have
-  the same functionalities as $\nil$ as they are not to be
-  substituted, then all versions of unique-solution
-  theorems should still hold. However this is not the case for at
-  least Milner's Theorem~\ref{t:Mil89s1} as we shall explain.}
-
-In this project, the only optional restriction we added here is that, for each
-$E_i$ the set of its bound variables must be \emph{disjoint} with $\til
-X$. This restriction is actually aligned with literature based on
-process constants as one should never use the same name for equation
-variables and constants. However, we believe this restriction can be
-removed in the future.~\footnote{Essentially, this restriction is due
-  to the proof difficulties in some early lemmas about \multivariate
+Obviously the two lists must have the same length. 
+% The all
+% distinctness of $\til X$ is not really necessary but is very
+% reasonable. 
+Furthermore, we should assume that $\til E$ does not contain
+ free variables not in $\til X$.
+% , as Milner's unique-solution
+% theorems also require the same condition.
+% \footnote{One may think that,
+%   if all other (i.e.~not in $\til X$) free variables in $\til E$ have
+%   the same functionalities as $\nil$ as they are not to be
+%   substituted, then all versions of unique-solution
+%   theorems should still hold. However this is not the case for at
+%   least Milner's Theorem~\ref{t:Mil89s1} as we shall explain.}
+The only optional condition we  have added is that, for each
+$E_i$, the set of its bound variables must be \emph{disjoint} from $\til
+X$. % This restriction is actually aligned with literature based on
+% process constants as one should never use the same name for equation
+% variables and constants. However, we believe this restriction can be
+% removed in the future.~
+\footnote{Essentially, this condition is due
+  to  some early lemmas about \multivariate
   substitutions where \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}}
-  unnecessarily appears in the antecedents. Removing it requires a
-  more complex proof but is indeed possible. (We have succeeded in
-  fixing many such lemmas.) Once all these lemmas are
-fixed, the final unique-solution theorems also do not need this
-disjointness restriction.} Putting all together, below is the fomal
+ appears in the antecedents. Removing this would require 
+  more complex proofs. 
+% (We have succeeded in
+%   fixing many such lemmas.) Once all these lemmas are
+% fixed, the final unique-solution theorems also do not need this
+% disjointness restriction.
+} 
+Putting all together, below is the fomal
 definition of \multivariate CCS equation:
@@
 
-Now consider (formally) what is a solution $\til P$ of CCS equation. First of
+Now consider (formally) what is a solution $\til P$ of CCS equations. First of
 all, the definition should be parametrized on a binary CCS
 relation $\R$ such as $\sim$ and $\rcontr$, so that the single definition
-could be used for the solution of all kind of CCS
+could be used for the solution of all kinds of CCS
 equations/contractions. Then, of course ${\til P} \ \R\  {\til E}\{\til
@@
 \end{equation*}
-Furthermore, each $P_i$ should be pure process, i.e. having no free
-variable. This is usually implicitly assumed in the literature but is
-actually a \emph{must} to complete some unique-solution proofs.
-At last, like the case of CCS equations, we must assume that, the
-set of bound variables (i.e. process constants) must be disjoint with
-$\til X$. (This disjointness requirement is optional but makes many proofs much
-easier, and it can be removed in the future.) Putting all together,
+Furthermore, each $P_i$ should be a pure process, i.e. having no free
+variable. 
+% This is usually implicitly assumed in the literature but is
+% actually a \emph{must} to complete some unique-solution proofs.
+Finally, 
+%like the case of CCS equations, we must assume that, 
+the
+set of bound variables %(i.e. process constants) 
+must be disjoint from
+$\til X$ (this disjointness requirement is optional but makes many proofs 
+easier). Putting all together,
 below is the formal definition of a solution of \multivariate CCS
@@
   \HOLinline{\HOLConst{LIST_REL}\\\;\HOLFreeVar{R}} is the same binary relation but for lists of
-  CCS processes. Furthermore, \HOLinline{\HOLConst{LIST_REL}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{A}\\\;\HOLFreeVar{B}} implicitly
+  CCS processes. Furthermore, \HOLinline{\HOLConst{LIST_REL}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{A}\\\;\HOLFreeVar{B}} 
   implies that the two lists $A$ and $B$ have the same length.}
@@
 \end{alltt}
-Notice that, in HOL, \HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}\\\;\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenEquiv{}}\\\;\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenIn{}}\\\;\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}.
-The form in right side suggest that,
+Note that, in HOL,
+\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}\\\;\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenEquiv{}}\\\;\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenIn{}}\\\;\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}.
+The form in the  right-hand side suggests that
 \HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}} is actually a set containing all
 solutions (of \HOLinline{\HOLConst{CCS_equation}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}). Then the unique-solution
-theorems can be understood as: any two (syntactically different) elements
+theorems can be understood thus: any two (syntactically different) elements
 in the set are bisimilar.
@@
 
-With all above new devices (\multivariate contexts and substitutions),
+With the above machinery about \multivariate contexts and substitutions,
 the \multivariate case of Lemma~\ref{lem:milner313} is formalised
@@
 \end{alltt}
-Notice that, while Milner did not pointed out explicitly, the involved
-weakly guarded context $E$ must contain free variables up to $\til
-X$~--- the same requirement as in Theorem~\ref{t:Mil89s1}, which
-otherwise does not complete. Besides, we further required that, the
-bound variables of $E$ must be disjoint with $\til X$.
+% Notice that, while Milner did not pointed out explicitly, the involved
+% weakly guarded context $E$ must contain free variables up to $\til
+% X$~--- the same requirement as in Theorem~\ref{t:Mil89s1}, which
+% otherwise does not complete. Besides, we further required that, the
+% bound variables of $E$ must be disjoint with $\til X$.
 
 The \multivariate version of Theorem~\ref{t:Mil89s1} is formalised
-below:
+thus:
 \begin{alltt}
@@
 step related to \multivariate substitutions is more difficult than
-the \univariate case, the entire proofs still follow the same outlines,
+the \univariate case, the entire proofs still follow the same outline,
 and many proof scripts can be directly copied from their \univariate version.

### 2019-11-26 ic-journal/part2.tex
text

--- 2019-11-20 ic-journal/part2.tex
@@
 version  of the result for weak bisimilarity that shares a large portion of proof
-steps with that case for observational congruence.  
+steps with the proof for observational congruence.  
 As  weak bisimilarity 
@@
 $G\{Q/X\}\overset{\alpha}{\rightarrow} H\{Q/X\}$. Moreover $H$ is
-sequential, and if $\alpha = \tau$ then $H$ is also guarded.
+sequential, and if $\alpha = \tau$, then $H$ is also guarded.
 \begin{alltt}
@@
 we found it more elegant  to  work with traces
-(a motivation for this is to set the ground for extensions of this
+(a further motivation  is to set the ground for extensions of this
 formalisation work to trace equivalence in place of bisimilarity).
@@
 
-If the list of actions is empty, that means that there is no transition and hence,
+If the list of actions is empty,  there is no transition and hence,
 if there is at most one visible action (i.e., a label) in the list of actions,
@@
 a list of actions); 
-it says, a weak transition $P\overset{u}{\Rightarrow}P'$ is also a
+it says that a weak transition $P\overset{u}{\Rightarrow}P'$ is also a
 trace $P\overset{acts}{\longrightarrow}P'$ with a
@@
 \end{alltt}
-which roughly says, for any context $C$ and weakly-guarded context
+which roughly says that for any context $C$ and weakly-guarded context
 $E$, if $C [\, E^n[P]\,] \overset{xs}{\Longrightarrow} P'$ and the length
@@
 transitions. For instance, from Def.~\ref{d:BisCon}, it is easy
-to see that, a weak transition either becomes shorter
+to see that a weak transition either becomes shorter
 or remains the same when moving between $\mcontrBIS$-related processes.
@@
 Lemma~\ref{l:uptocon}. We show only one such lemma, for the case of
-non-$\tau$ weak transitions passing into $\mcontrBIS$ (from left to right):
+visible weak transitions:
+% passing into $\mcontrBIS$ (from left to right):
 \begin{alltt}

### 2019-11-26 ic-journal/related.tex
text

@@
 libraries in recent versions of HOL4, and our formalisation has
-covered a much larger spectrum of the (pure) CCS theory.
+covered a  larger spectrum of the (pure) CCS theory.
 
@@
 he has formalized basic properties for strong/weak equivalence (congruence, basic
- algebraic laws); \hl{however the CCS syntax doesn't have constants
-(or recursion operator), using replication in place of recursion.}
+ algebraic laws); \hl{the CCS syntax does not have constants
+or recursion, using instead replication.}
 % The formalisation effort has then been continued 

### 2019-11-26 ic-journal/sos.tex
text

@@
 cardinality and the exact elements of this type depend on the type variable $\beta$
-instantiated by the end user \hl{or further formalisations built upon the
-present one.}
+instantiated by the end user.
+%  \hl{or further formalisations built upon the
+% present one.} 
 All \hl{labels} are divided into input and output ones.
@@
 \end{lstlisting}
-For instance, if the type $\beta$ is instantiated by \texttt{string}
-(the type of all strings), then HOL terms \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
+Intuitively, with reference to the CCS terminology reported in
+Section~\ref{ss:ccs}, $\beta$ represents the set of \emph{names}, and
+\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}} turns names into
+\emph{input
+and output actions}. 
+For instance, if the type $\beta$ is instantiated to \texttt{string}
+(the type of all strings), then the HOL terms \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
 \HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input action $a$ and output
@@
 The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'', accounting for the CCS
-expressions, has two type variables \hl{$\alpha$ and $\beta$ corresponding%
-\footnote{The order \hl{between} type variables $\alpha$ and $\beta$
-    \hl{can be} arbitrary. Our choice is aligned with the literature.
-For instance, $\mathrm{CCS}(h,k)$ is the CCS subcalculus that can use at most $h$ constants
-and $k$ actions~\cite{gorrieri2017ccs}. To formalize theorems on
- $\mathrm{CCS}(h,k)$, the required CCS type can be retrieved by instantiating the type
-variables $\alpha$ and $\beta$ in ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' with types
-having the corresponding cardinalities $h$ and $k$.}
-to $\mathscr{X}$ (the set of agent variables) and $\mathscr{L}$ (the
-set of names used for labels), respectively}.
+expressions, has two type variables $\alpha$ and $\beta$
+  corresponding
 %
-The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' \hl{is defined inductively by HOL \texttt{Datatype} package}
+% \footnote{The order \hl{between} type variables $\alpha$ and $\beta$
+%     \hl{can be} arbitrary. Our choice is aligned with the literature.
+% For instance, $\mathrm{CCS}(h,k)$ is the CCS subcalculus that can use at most $h$ constants
+% and $k$ actions~\cite{gorrieri2017ccs}. To formalize theorems on
+%  $\mathrm{CCS}(h,k)$, the required CCS type can be retrieved by instantiating the type
+% variables $\alpha$ and $\beta$ in ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' with types
+% having the corresponding cardinalities $h$ and $k$.}
+to  %$\mathscr{X}$ (
+the set of agent variables %) 
+and %$\mathscr{L}$ (
+the
+set of names % used for labels), 
+respectively (indeed the CCS syntax in Section~\ref{ss:ccs} is parametric
+with respect to the choice of these two sets).
+%
+The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha},
+  \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' \hl{is defined
+  inductively by the  HOL \texttt{Datatype} package}
 (here ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling
-  functions;   \hl{we have also formalised relabeling, though we will
-    not discuss it}):
+  functions;   \hl{we have also formalised relabeling, though it is not
+ discussed below}):
 \begin{lstlisting}
@@
 between HOL4 and Standard ML (that follows an idea \hl{of} Nesi~\cite{Nesi:1992ve})
- is a \hl{recursive} ML function \hl{which takes} a CCS process and \hl{returns} a theorem indicating all
-  direct transitions of the process. \hl{(If the input process is
- infinite branching, the function will not terminate.)}
+ is a \hl{recursive} ML function \hl{that takes} a CCS process and \hl{returns} a theorem indicating all
+  direct transitions of the process \hl{(if the input process is
+ infinitely branching, the function will not terminate).}
 For instance, we know that the process $(a.\nil | \bar{a}.\nil)$ has three
@@
 \overset{\tau}{\longrightarrow} (\nil | \nil)$.
-To completely describe all possible transitions of \hl{the} process, if done manually, the
-following two facts must be proved: (1) there are indeed the three
+To completely describe all possible transitions of \hl{the} process manually, the
+following two facts should be proved: (1) there are indeed the three
   transitions mentioned above; (2) there \hl{is} no other

### 2019-11-26 ic-journal/unique.tex
text

@@
 relation $\mcontrBIS$.
-Furthermore, we needed to show that the \hl{found} definition is the
-best possible one, by showing that it yields the coarsest precongruence
-contains in $\mcontrBIS$; the proof is similar \hl{with}
+Furthermore, we needed to show that the  definition \hl{found} 
+does indeed yields the coarsest precongruence
+contains in $\mcontrBIS$; the proof is similar \hl{to}
 the analogous result for $\rapprox$. See Section~\ref{s:coarsest} for

### 2019-11-27 ic-journal/part2.tex
Manually merged and synced changes in part2.tex

@@
 
-\subsubsection{Weak bisimilarity}
-
-Milner's book~\cite{Mil89} contains only two ``unique solutions of
-equations'' theorems, one for strong equivalence, the other for
-observational congruence.   There is however a
-version  of the result for weak bisimilarity that shares a large portion of proof
-steps with the proof for observational congruence.  
-As  weak bisimilarity 
- is not \hl{a} congruence, we have to be more restrictive on the syntax for
- the equation, using strong guardedness.
-% to make correct statement of this
-% theorem, we must slightly modify the concept of sequential expresses
-% with further restrictions: no direct sums (or only guarded sums).
-% The ``unique solution of equations'' theorem for weak equivalence
-% requires more restrictions on the expression, namely, .
-% Now we're ready to state and prove the following lemma:
-\begin{lemma}[\texttt{WEAK_UNIQUE_SOLUTION_LEMMA}]
-If the variable $X$ is guarded and sequential in $G$, and
-$G\{P/X\}\overset{\alpha}{\rightarrow} P'$, then $P'$ takes the form
-$H\{P/X\}$, for some expression $H$, and for any $Q$, we have
-$G\{Q/X\}\overset{\alpha}{\rightarrow} H\{Q/X\}$. Moreover $H$ is
-sequential, and if $\alpha = \tau$, then $H$ is also guarded.
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{G} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{G} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
-       \HOLFreeVar{G} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}.
-\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
-\HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}
-\end{alltt}
-\end{lemma}
-
-We can then derive the target theorem:
-\begin{theorem}[\texttt{WEAK_UNIQUE_SOLUTION}]
-Let $E$ be guarded and sequential expressions, and let $P \wb
-E\{P/X\}$,
-$Q \wb E\{Q/X\}$. Then $P \wb Q$.
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{Q}
-\end{alltt}
-\end{theorem}
-
-\subsubsection{Rooted bisimilarity}
+\subsubsection{The case of rooted bisimilarity}
 
@@
 \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Q}
+\end{alltt}
+\end{theorem}
+
+\subsubsection{The case of weak bisimilarity}
+
+Milner~\cite{Mil89} \emph{only mentioned} two ``unique solution of
+equations'' theorems, one for strong equivalence, the other for
+rooted bisimilarity.   There is, however, another
+version for weak bisimilarity that shares a large portion of proof
+steps with the proof for \hl{rooted bisimilarity.}
+As weak bisimilarity is not a congruence, we have to be more restrictive
+on the syntax of the equation, using strong guardedness.
+
+\begin{lemma}[\texttt{WEAK_UNIQUE_SOLUTION_LEMMA}]
+If the variable $X$ is guarded and sequential in $G$, and
+$G\{P/X\}\overset{\alpha}{\rightarrow} P'$, then $P'$ takes the form
+$H\{P/X\}$, for some expression $H$, and for any $Q$, we have
+$G\{Q/X\}\overset{\alpha}{\rightarrow} H\{Q/X\}$. Moreover $H$ is
+sequential, and if $\alpha = \tau$ then $H$ is also guarded.
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{G} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{G} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
+       \HOLFreeVar{G} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}.
+\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}
+\end{alltt}
+\end{lemma}
+
+We can then derive the target theorem:
+\begin{theorem}[\texttt{WEAK_UNIQUE_SOLUTION}]
+Let $E$ be guarded and sequential expressions, and let $P \wb
+E\{P/X\}$,
+$Q \wb E\{Q/X\}$. Then $P \wb Q$.
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{Q}
 \end{alltt}
@@
 
-The definition of ``unique label'' can be done in many \hl{ways. The}
+The definition of ``unique label'' can be done in many ways. The
 following definition (a suggestion from Robert Beers)
@@
 $E$, if $C [\, E^n[P]\,] \overset{xs}{\Longrightarrow} P'$ and the length
-of actions $xs \leqslant n$, then \hl{$P'$} has the form of $C'[P]$.
-Traces are used \hl{in} reasoning about the number of intermediate actions in weak
+of actions $xs \leqslant n$, then $P'$ has the form of $C'[P]$.
+Traces are used in reasoning about the number of intermediate actions in weak
 transitions. For instance, from Def.~\ref{d:BisCon}, it is easy
-to see that a weak transition either becomes shorter
+to see that, a weak transition either becomes shorter
 or remains the same when moving between $\mcontrBIS$-related processes.
@@
 visible weak transitions:
-% passing into $\mcontrBIS$ (from left to right):
+%passing into $\mcontrBIS$ (from left to right):
 \begin{alltt}

### 2019-11-27 ic-journal/response-letter2.tex
Synchronized all changes from .tex files

@@
 \noindent
-
-(TODO)
 
@@
 the CCS syntax in Section~\ref{ss:ccs}, 
-alpha and beta represent, respectively, the 
+$\alpha$ and $\beta$ represent, respectively,
 the set of agent variables 
-and %$\mathscr{L}$ (
-the
-set of names (the CCS syntax being parametric with respect to these sets)
+and the set of names (the CCS syntax being parametric with respect to these sets).
 

### 2019-11-27 ic-journal/coarsest.tex
Synchronized all changes from .tex files

@@
 delicate aspects; for instance, 
-with   our CCS syntax
-(with only binary sums)
+with our CCS syntax (\hl{which has} only binary sums)
 we have to add an hypothesis about
- \hl{the involved processes  not
-  using all available labels}.
-% This theorem is of special \hl{interest} to us, because under our
-% \hl{CCS syntax (with only binary summations)} it seems impossible to
-% prove it without any \hl{antecedent such as ``the involved processes
-%   do not use up all available labels''}.
+ the involved processes not using all available labels.
 The general form of the theorem is thus~\cite{van2005characterisation,Gorrieri:2015jt,Mil89}:
@@
 \label{prop:coarsest}
-  \hl{Rooted bisimilarity ($\rapprox$) is the coarsest congruence
-    contained in weak bisimilarity ($\wb$):}
+  Rooted bisimilarity ($\rapprox$) is the coarsest congruence
+    contained in weak bisimilarity ($\wb$):
   \begin{equation}
@@
 From left to right (\ref{eq:coarsest}) trivially holds, due to the substitutivity of
-$\rapprox$ \hl{for} summation and \hl{the fact that} $\rapprox$ implies $\wb$:
+$\rapprox$ for summation and the fact that $\rapprox$ implies $\wb$:
 \begin{alltt}
@@
 The standard argument~\cite{Mil89} requires that $p$
-and $q$ do not use \hl{all} available labels (i.e.~visible actions).
-Formalising this \hl{result, however,} requires a detailed treatment of free and bound names of CCS
+and $q$ do not use all available labels (i.e.~visible actions).
+Formalising this result, however, requires a detailed treatment of free and bound names of CCS
 processes (with the restriction operator acting as a binder).
-\hl{In} our formalisation, in contrast, 
-%  we do not discuss free and bound names (also
-% called ``sorts'') of CCS processes. Instead, 
-we 
-assume \hl{the weaker condition} that all immediate \emph{weak} derivatives of
- $p$ and $q$ do not use all available \hl{labels}. We  call this
+In our formalisation, in contrast,
+we assume \hl{a} weaker condition that all immediate \emph{weak} derivatives of
+ $p$ and $q$ do not use all available labels. We call this
  the \emph{free action} property:
@@
 \end{alltt}
-We do not need to put $R\ g\ h$ \hl{into} the antecedents of
+We do not need to put $R\ g\ h$ into the antecedents of
   \texttt{CC\_def}, as this is anyhow obtained from the trivial context $(\lambda x.\,x)$.
@@
 \end{alltt}
-Furthermore, we prove that any (pre)congruence contained in $R$, \hl{that
-itself} needs not to be a (pre)congruence,
+Furthermore, we prove that any (pre)congruence contained in $R$,
+that itself needs not to be a (pre)congruence,
 is contained in the composition closure of $R$
-(hence the \hl{composition} closure is the coarsest one):
+(hence the composition closure is the coarsest one):
 \begin{alltt}
@@
 
-\hl{The}  formalisation of (\ref{equa:pq}) says:
+The formalisation of (\ref{equa:pq}) says:
 \begin{theorem}[\texttt{COARSEST_CONGR_RL}]
@@
 our result above. Indeed, in our result we only look at immediate weak
-derivatives for $p$ and $q$, and only require that there is an input
+derivatives for $p$ and $q$, and only requires that there is an input
 or output action
@@
 and an action $a$ and its complementary $\outC a$ are
-considered {different} actions.
+considered different actions.
 
@@
  $q$, then \texttt{SUM_EQUIV} indeed implies rooted bisimilarity
- ($\rapprox$) (c.f.~\cite{Tian:2017wrba} for more details of the proof):
+ ($\rapprox$) (see~\cite{Tian:2017wrba} for more details of the proof):
 \begin{alltt}
@@
 As a consequence, the final result is only for finite-state
-CCS.\footnote{\hl{van Glabbeek's
+CCS.\footnote{van Glabbeek's
   original proof applies to all CCS processes; however,  it
@@
   ordinal larger than the cardinality of any given set. This is beyond
-  the possibilities of HOL.}}
+  the possibilities of HOL.}
 
@@
 This can be done following Klop's contruction \cite{van2005characterisation}.
- We call  the processes in this construction \hl{the ``Klop processes''}:
+ We call  the processes in this construction the ``Klop processes'':
 \begin{definition}[Klop processes]
@@
 \item Define \emph{reachable} as the RTC (reflexive and transitive
-  closure)
- of a relation, which
+  closure) of a relation, which
   indicates the existence of a transition between two processes:
@@
 \end{definition}
-We rely
-on  various 
+We rely on various 
  properties of the above definitions, such as the following one:

### 2019-11-27 ic-journal/conclusions.tex
Fixed some merge conflicts
Synchronized all changes from .tex files

@@
 and proofs for different equivalences and preorders. Indeed we have
-considered several `unique-solution' results (for various equivalences
+considered several ``unique-solution'' results (for various equivalences
 and preorders); they share many parts of the proofs, but present a few
 delicate and subtle differences in a few points. In a paper-pencil
-proof, checking all details would be long and \hl{error-prone},
-\hl{especially in cases where the proofs are similar to each other or
-  when there are long case analyses to be carried out.}
+proof, checking all details would be long and error-prone,
+especially in cases where the proofs are similar to each other or
+  when there are long case analyses to be carried out.
 % \hl{Some of the textbook proofs were even wrong and the correct version is
@@
 theorems are easy to read and
-understand, as they are close to their original statement in
+to understand, as they are close to their original statement in
 textbooks.
@@
 For future work, formalising other equivalences and preorders could also be considered,
-notably  \hl{trace-based} equivalences, as well as more refined process
+notably trace-based equivalences, as well as more refined process
 calculi such as value-passing CCS.
-% (e.g.~exploiting the type variable
-%of actions).}
 %
@@
  the formalisation of a different
-approach \cite{DurierHS17,DurierHS18} to unique
+approach~\cite{DurierHS17,DurierHS18} to unique
 solutions, in which the use of contraction is
@@
 We have  benefitted from suggestions and comments 
-from  the \hl{anonymous reviewers} and several people from the HOL
-community, including (in \hl{alphabetical} order) Robert Beers, Jeremy Dawson,
+from  the anonymous reviewers and several people from the HOL
+community, including (in alphabetical order) Robert Beers, Jeremy Dawson,
 Ramana Kumar,
@@
 Council (ERC) Grant DLV-818616 DIAPASoN.
+%
 The paper was written in memory of Michael J.~C.~Gordon, the creator of the HOL theorem prover.

### 2019-11-27 ic-journal/context.tex
Synchronized all changes from .tex files

--- 2019-11-26 ic-journal/context.tex
@@
 In above inductive definitions, for any CCS term $p$,
-\HOLinline{\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{p}} is a
-valid context, with  no
-hole. 
-% On the other hand, if any CCS term with recursion
-% could be a context, the recursion must be a subterm of this $p$.
+\HOLinline{\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{p}} is a valid context with no hole.
 
-A context is \emph{weakly guarded} (\texttt{WG}) if each hole is
+A context is \emph{weakly guarded} (\HOLinline{\HOLConst{WG}}) if each hole is
 underneath a prefix:
@@
 context: $\lambda t. t$ is not weakly guarded as the variable is directly
-exposed, without any prefixed action. And $\lambda t. a.e[t]$ is weakly
+exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
 guarded as long as $e[\cdot]$ is a context, not necessary weakly guarded.)
 
-A context is \emph{guarded} (\texttt{SG}) if each hole is underneath a \emph{visible} prefix:
+A context is \emph{guarded} (\HOLinline{\HOLConst{SG}}) if each hole is underneath a \emph{visible} prefix:
 \begin{alltt}
@@
 
-A context is \emph{sequential} (\texttt{SEQ}) if each of its \emph{subcontexts} with
+A context is \emph{sequential} (\HOLinline{\HOLConst{SEQ}}) if each of its \emph{subcontexts} with
 a hole, apart from the hole itself, is in forms of prefixes or sums:
-(c.f. Def.~\ref{def:guardness} and p.101,157 of \cite{Mil89} for
+(See Def.~\ref{def:guardness} and \citep[p.~101, 157]{Mil89} for
 the informal definitions.)
@@
 
-In the same manner, we can also define variants of contexts (\texttt{GCONTEXT}) and weakly guarded
-contexts (\texttt{WGS}) in which only guarded sums are allowed (i.e.~arbitrary sums are forbidden):
+In the same manner, we can also define variants of contexts (\HOLinline{\HOLConst{GCONTEXT}}) and weakly guarded
+contexts (\HOLinline{\HOLConst{WGS}}) in which only guarded sums are allowed (i.e.~arbitrary sums are forbidden):
 \begin{alltt}
@@
 
-In our work, several 
+\hl{Several}
 lemmas about the above concepts (\HOLinline{\HOLConst{CONTEXT}}, \HOLinline{\HOLConst{WG}},
-\HOLinline{\HOLConst{SEQ}}, etc.)  were needed 
-to capture properties about
- the
- relationships among these kinds of contexts and their
- composition. These proofs are usually tedious and long,  due to multiple levels of
+\HOLinline{\HOLConst{SEQ}}, etc.) \hl{are needed for capturing} properties about
+ the relationships among these kinds of contexts and their
+ compositions. These proofs are usually tedious and long,  due to multiple levels of
  inductions on the structure of the contexts.
@@
 A (pre)congruence is a relation on CCS processes defined on top of
-\texttt{CONTEXT}. The only difference between congruence and
-precongruence is that the former  is an equivalence, while
- the latter can  just be  a preorder:
+\HOLinline{\HOLConst{CONTEXT}}. The only difference between congruence and
+precongruence is that the former is an equivalence,
+while the latter can just be a preorder:
 \begin{alltt}
@@
 Although weak bisimilarity ($\approx$) is \emph{not} a congruence
-  with respect to~\texttt{CONTEXT}, it is indeed substitutive
-  with respect to~\texttt{GCONTEXT} 
+  with respect to~\HOLinline{\HOLConst{CONTEXT}}, it is indeed substitutive
+  with respect to~\HOLinline{\HOLConst{GCONTEXT}} 
 % (or if the CCS syntax were defined with
@@
 as $\approx$ is indeed preserved by guarded sums.
+%
 Rooted contraction, on the other hand, is a precongruence:

### 2019-11-27 ic-journal/formal.tex
Synchronized all changes from .tex files

@@
 \begin{enumerate}
-\item \hl{The} underlying implementation language for the core HOL engine;
-\item \hl{The} language in which proof tactics are implemented;
-\item \hl{The} interface language of the HOL proof scripts and interactive shell.
+\item The underlying implementation language for the core HOL engine;
+\item The language in which proof tactics are implemented;
+\item The interface language of the HOL proof scripts and interactive shell.
 \end{enumerate}
@@
 sets denoted by the types. There are four kinds of terms in the HOL
-logic. \hl{They} can be described (in simplified forms) by the BNF grammar in
+logic. They can be described (in simplified forms) by the BNF grammar in
 Fig.~\ref{fig:hol-terms}; see~\cite{hollogic} for a complete description.
@@
 HOL \texttt{Datatype} package~\cite{Melham:1991, holdesc} automates
-this tedious process, and can be used for \hl{defining the 
-types needed for} CCS.
+this tedious process, and can be used for defining the 
+types needed for CCS.
+%
 Finally, the whole HOL \emph{standard} theory is based on the
@@
 Axiom of Choice), thus not all theorems valid in ZFC can be formalised
-in HOL. (c.f.~\cite{hollogic} for more details.)}
+in HOL. (See~\cite{hollogic} for more details.)}
 \begin{equation*}
@@
 in conventional formalisation projects in HOL: adding new axioms
-\hl{manually}, may break logical \hl{consistency}.
-% \hl{In general,} the theorem prover guarantees that,
-% without adding new axioms, if both the definitions and the statements
-% of theorems are correct, then the \hl{proofs of these theorems} is
-%  \hl{also} correct.
-% This last sentence doesn't have a good link with the previous context,
-% disabled. --Chun
-%
-%% This is also the case here: SOS rules of CCS are
-%% \emph{not} axioms but consequences of the inductive relation\hl{, the
-%% CCS transition $\rightarrow$}.
+manually, may break logical consistency.
 

### 2019-11-27 ic-journal/intro.tex
Synchronized all changes from .tex files

--- 2019-11-25 ic-journal/intro.tex
@@
   (or contraction) with multiple equation variables is considered.
-The \univariate versions \hl{of unique-solution theorems} use
+The \univariate versions \hl{of the} unique-solution theorems use
 $\lambda$-functions to present CCS equations,

### 2019-11-27 ic-journal/multivariate.tex
Synchronized all changes from .tex files

@@
 contractions'' (Theorem~\ref{t:rcontraBisimulationU}).
-\hl{This formalisation  supports finitely many
-  equations/contractions and equation variables.}\footnote{\hl{The original theorems
-hold for even  infinitely-many equations and equation variables.}}
+This formalisation  supports finitely many
+  equations/contractions and equation variables.\footnote{The original theorems
+hold for even  infinitely-many equations and equation variables.}
 We chose these two theorems because of their relevance and 
@@
 
-As mentioned at
- the beginning of Section~\ref{s:eq},  
- an
-agent variable may  occur outside the recursion in which it is bound;
+As mentioned at the beginning of Section~\ref{s:eq},
+ an agent variable may occur outside the recursion in which it is bound;
 i.e., a variable can appear both \emph{bound} and \emph{free} in a term.
-% In Milner's original book chapter~\cite{milner1990operational}, the
-% variables which occur in Recursion (such as $X$ in $\recu X E$) are
-% called \emph{bound} variables, while those which occur unbound are called
-% \emph{free} variables.
 
@@
 variables as $\fv{E}$ (or \HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}} in HOL). Both \HOLinline{\HOLConst{BV}} and \HOLinline{\HOLConst{FV}} have the
-type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha},
-  \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd
-  \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}'',
-i.e. functions taking CCS terms and returning sets of
+type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}'', i.e.
+functions taking CCS terms and returning sets of
 variables (of type \HOLinline{\ensuremath{\alpha}}).
@@
 The set of free and bound
-variables of a term need not be disjoint, e.g.\ in  $X + \recu X E$.
+variables of a term need not be disjoint, e.g.~in $X + \recu X E$.
 More importantly, when going
@@
 \begin{proof}
-We \hl{actually prove} a stronger result,  \hl{asserting} that the set of free
-variables \hl{in a CCS process} may decrease through its derivatives:
+We actually prove a stronger result, asserting that the set of free
+variables in a CCS process may decrease through its derivatives:
 \begin{alltt}
@@
 
-In textbooks such as \cite{Mil89} the proof of the above property is 
+In textbooks such as~\cite{Mil89}, the proof of the above property is 
 commented as  ``an easy action induction''.
-In HOL, the proof 
- is actually non-trivial:
- ``action induction''  becomes a form of  higher-order application
+\hl{The actual proof in HOL is not that trivial}:
+ ``action induction'' (or \emph{transition induction}) becomes a form of higher-order application
 of the following \emph{induction principle}, generated together with the SOS
@@
 is completed.
-%This is the essence of action induction.
 Now, the goal can be reduced to several conjunct
@@
 
-Proposition~\ref{prop:transFV} \hl{is essential in the proofs of the
+Proposition~\ref{prop:transFV} is essential in the proofs of the
   multivariable versions of all unique-solution
   theorems.
-In comparison with} the above proof, the proof of the analogous
+In comparison with the above proof, the proof of the analogous
 result for bound variables is easier:
@@
     the right side equals to \HOLinline{\HOLConst{BV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}\\\;\ensuremath{(}\HOLFreeVar{X}\\\;\HOLConst{INSERT}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}} $=$
-    \HOLinline{\HOLFreeVar{X}\\\;\HOLConst{INSERT}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}}. This
-completes
-the    proof.
+    \HOLinline{\HOLFreeVar{X}\\\;\HOLConst{INSERT}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}}.
+This completes the proof.
 \end{proof}
@@
 There are two ways to represent the \multivariate
-substitution  $E\{\til P/\til X\}$, that replaces each \hl{free occurrence}
-of  variables $X_i$ in $E$ with the corresponding
+substitution $E\{\til P/\til X\}$, that replaces each \hl{free
+occurrence} of variables $X_i$ in $E$ with the corresponding
 $P_i$: (1) iterately applying the existing \univariate
@@
 the list of variables \HOLinline{\HOLFreeVar{Xs}} and the corresponding targets
-\HOLinline{\HOLFreeVar{Ps}}  by a helper function \HOLinline{\HOLConst{fromList}} (whose details 
-are omitted here), while
+\HOLinline{\HOLFreeVar{Ps}} by a helper function \HOLinline{\HOLConst{fromList}} (whose details are
+omitted here), while
 \HOLinline{\HOLConst{CCS_SUBST}\\\;\ensuremath{(}\HOLConst{fromList}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Ps}\ensuremath{)}\\\;\HOLFreeVar{E}} is
 abbreviated as \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}.
-The substitution mechanism is
- order-independent. For most CCS operators it
+The substitution mechanism is order-independent. For most CCS operators it
 just recursively calls itself on subterms. The only
@@
 \begin{lemma}[\texttt{BV_SUBSET_BIGUNION}]
-The bound variables of
-\HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}
-are contained in  the union of the bound variables from $E$ and \HOLinline{\HOLFreeVar{Ps}}.
+The bound variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}
+are contained in the union of the bound variables in $E$ and \HOLinline{\HOLFreeVar{Ps}}.
 \begin{alltt}
@@
 \begin{lemma}[\texttt{FV_SUBSET_BIGUNION_PRO}]
-The free variables of
-\HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}
+The free variables of \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}
 are contained in the union of the free variables in $E$ and \HOLinline{\HOLFreeVar{Ps}},
@@
 variables.\footnote{Here \HOLinline{\HOLConst{SET_TO_LIST}} converts a finite set
-  to a list of the same elements. It turns out that we never need this, because
+  to a list of the same elements. It turns out that, we never need this, because
   in all unique-solution theorems a list of variables \HOLinline{\HOLFreeVar{Xs}} is fixed and
@@
 (Guardedness and sequentiality can also be defined similarily, using
-their \univariate companions (\texttt{SG} and \texttt{SEQ}).)
+their \univariate companions \HOLinline{\HOLConst{SG}} and \HOLinline{\HOLConst{SEQ}}.)
 
-The most important property of contexts are that strong bisimilarity
+The most important property of contexts are that, strong bisimilarity
 and other (pre)congruence relations are preserved by contexts, e.g.
@@
   means that two lists of CCS processes are componentwise
-  (strongly) bisimilar. %The same notation $\sim$ has been overloaded.
-}, then 
+  (strongly) bisimilar.}, then
 for any context $E$
 % with the possible occurrences of variables $\til X$
-%(same length as $\til P$ and $\til Q$),
+% (same length as $\til P$ and $\til Q$),
 also $E\{\til P/\til X\}$ and
@@
  if the set of free variables of an expression
-is disjoint from a list of variables, then the expression is
- a context:
+is disjoint from a list of variables, then the expression is a context:
 \begin{alltt}
@@
 In the above result we cannot
-conclude \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}}, because $Y$, as a bound
-variable of $\recu Y E$, may  also be  a free variable in $\til X$. We
+conclude \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}}, because $Y$ as a bound
+variable of $\recu Y E$ may also be a free variable in $\til X$. We
 also cannot conclude \HOLinline{\HOLConst{context}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{E}}, because in $\recu Y E$
@@
 The only optional condition we have added is that, for each
-$E_i$, the set of its bound variables must be \emph{disjoint} from $\til
-X$. % This restriction is actually aligned with literature based on
+$E_i$, the set of its bound variables must be \emph{disjoint} from $\til X$.
+% This restriction is actually aligned with literature based on
 % process constants as one should never use the same name for equation
@@
 %like the case of CCS equations, we must assume that, 
-the
-set of bound variables %(i.e. process constants) 
+the set of bound variables %(i.e. process constants) 
 must be disjoint from
@@
   \HOLinline{\HOLConst{LIST_REL}\\\;\HOLFreeVar{R}} is the same binary relation but for lists of
-  CCS processes. Furthermore, \HOLinline{\HOLConst{LIST_REL}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{A}\\\;\HOLFreeVar{B}} 
+  CCS processes. Furthermore, \HOLinline{\HOLConst{LIST_REL}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{A}\\\;\HOLFreeVar{B}} implicitly
   implies that the two lists $A$ and $B$ have the same length.}
@@
 \end{alltt}
-Note that, in HOL,
-\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}\\\;\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenEquiv{}}\\\;\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenIn{}}\\\;\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}.
-The form in the  right-hand side suggests that
+Note that, in HOL, \HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}\\\;\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenEquiv{}}\\\;\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenIn{}}\\\;\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}.
+The form in the right-hand side suggests that,
 \HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}} is actually a set containing all
@@
 
-The \multivariate version of Theorem~\ref{t:Mil89s1} is formalised
-thus:
+The \multivariate version of Theorem~\ref{t:Mil89s1} is formalised thus:
 \begin{alltt}

### 2019-11-27 ic-journal/sos.tex
Synchronized all changes from .tex files

@@
 instantiated by the end user.
-%  \hl{or further formalisations built upon the
-% present one.} 
-All \hl{labels} are divided into input and output ones.
+All labels are divided into input and output ones.
 The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is defined by HOL's \texttt{Datatype} package in the
@@
 \HOLinline{\ensuremath{\beta} \HOLTyOp{Label}} turns names into
-\emph{input
-and output actions}. 
+\emph{input and output actions}.
 For instance, if the type $\beta$ is instantiated to \texttt{string}
@@
 \HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input action $a$ and output
-action \hl{$\overline{b}$}, respectively.
+action $\overline{b}$, respectively.
 The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
@@
 (\texttt{tau}). For instace, the input action $a$ and output
-action \hl{$\overline{b}$} of type \hl{\mbox{``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''}}
+action $\overline{b}$ of type ``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''
 are denoted by \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLStringLit{a}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLStringLit{b}\ensuremath{)}}, respectively.
@@
 The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'', accounting for the CCS
-expressions, has two type variables $\alpha$ and $\beta$
-  corresponding
-%
-% \footnote{The order \hl{between} type variables $\alpha$ and $\beta$
-%     \hl{can be} arbitrary. Our choice is aligned with the literature.
+expressions, has two type variables $\alpha$ and $\beta$ corresponding%
+% \footnote{The order between type variables $\alpha$ and $\beta$
+%     can be arbitrary. Our choice is aligned with the literature.
 % For instance, $\mathrm{CCS}(h,k)$ is the CCS subcalculus that can use at most $h$ constants
@@
 % having the corresponding cardinalities $h$ and $k$.}
-to  %$\mathscr{X}$ (
-the set of agent variables %) 
-and %$\mathscr{L}$ (
-the
-set of names % used for labels), 
+to the set of agent variables
+and the set of names
 respectively (indeed the CCS syntax in Section~\ref{ss:ccs} is parametric
@@
 %
-The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha},
-  \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' \hl{is defined
-  inductively by the  HOL \texttt{Datatype} package}
+The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' is defined inductively by the HOL \texttt{Datatype} package
 (here ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling
-  functions;   \hl{we have also formalised relabeling, though it is not
- discussed below}):
+  functions; we have also formalised relabeling, though it is not
+  discussed below):
 \begin{lstlisting}
@@
 \HOLinline{\HOLConst{TRANS}} by HOL \texttt{HOL_reln} function 
-(\hl{see}~\citep[p.~219]{holdesc} for more details).
+(see~\citep[p.~219]{holdesc} for more details).
 A successful invocation of the definitional principle returns three
@@
 for ``\HOLinline{\HOLConst{CCS_Subst}\;\;\HOLFreeVar{E}\;\;\ensuremath{(}\HOLConst{rec}\;\;\HOLFreeVar{X}\;\;\HOLFreeVar{E}\ensuremath{)}\;\;\HOLFreeVar{X}}'', where \HOLinline{\HOLConst{CCS_Subst}} is a
-recursive function substituting all appearences of a free variable \hl{with} another CCS term.
+recursive function substituting all appearences of a free variable with another CCS term.
 For most CCS operators \HOLinline{\HOLConst{CCS_Subst}} just recursively goes into a deeper
@@
 A useful facility exploiting the interplay
-between HOL4 and Standard ML (that follows an idea \hl{of} Nesi~\cite{Nesi:1992ve})
- is a \hl{recursive} ML function \hl{that takes} a CCS process and \hl{returns} a theorem indicating all
-  direct transitions of the process \hl{(if the input process is
- infinitely branching, the function will not terminate).}
+between HOL4 and Standard ML (that follows an idea of Nesi~\cite{Nesi:1992ve})
+ is a recursive ML function that takes a CCS process and returns a theorem indicating all
+  direct transitions of the process (if the input process is
+ infinitely branching, the function will not terminate).
 For instance, we know that the process $(a.\nil | \bar{a}.\nil)$ has three
-possible \hl{(one-step)} transitions: $(a.\nil | \bar{a}.\nil) \overset{a}{\longrightarrow}
+possible (one-step) transitions: $(a.\nil | \bar{a}.\nil) \overset{a}{\longrightarrow}
 (\nil | \bar{a}.\nil)$, $(a.\nil | \bar{a}.\nil)
@@
 \overset{\tau}{\longrightarrow} (\nil | \nil)$.
-To completely describe all possible transitions of \hl{the} process manually, the
+To completely describe all possible transitions of the process manually, the
 following two facts should be proved: (1) there are indeed the three
-  transitions mentioned above; (2) there \hl{is} no other
-  \hl{transition}. For large CCS processes it is surprisingly tedious to manually derive
+  transitions mentioned above; (2) there is no other
+  transition. For large CCS processes it is surprisingly tedious to manually derive
 all the possible transitions and prove the non-existence of other transitions.
@@
 \texttt{CCS\_TRANS\_CONV} that is designed to automate the whole process.
-For instance, \hl{taking the input} $(a.\nil | \bar{a}.\nil)$ the function returns the
-following theorem which describes all \hl{its one-step} transitions:
+For instance, taking the input $(a.\nil | \bar{a}.\nil)$ the function returns the
+following theorem which describes all its one-step transitions:
 \begin{alltt}

### 2019-11-27 ic-journal/conclusions.tex
Clean up reviewed highlights; fixed some bibitems

@@
 method);
-\item constructing a `bisimulation up-to'; 
+\item constructing a ``bisimulation up-to''; 
 \item employing algebraic laws;
@@
  MIUR-PRIN project `Analysis of
-Program Analyses' (ASPRA, ID 201784YSZ5$\_$004), and by the 
+Program Analyses' (ASPRA, ID: \texttt{201784YSZ5\_004}), and by the 
 European Research

### 2019-11-27 ic-journal/formal.tex
Clean up reviewed highlights; fixed some bibitems

@@
 further defined as $\lambda$-functions: 
-% (one rarely needs to care
-% things at this level, however.)
 \begin{equation*}
 \begin{array}{l}
-\turn \T       =  ((\lquant{x_{\ty{bool}}}x) =
+\turn \T \HOLTokenDefEquality ((\lquant{x_{\ty{bool}}}x) =
                (\lquant{x_{\ty{bool}}}x))    \\
-\turn \forall  =  \lquant{P_{\alpha\fun\ty{bool}}} P =
+\turn \forall \HOLTokenDefEquality \lquant{P_{\alpha\fun\ty{bool}}} P =
                     (\lquant{x}\T ) \\
-\turn \exists  =  \lquant{P_{\alpha\fun\ty{bool}}} P({\hilbert}\, P) \\
-\turn \F  =  \uquant{b_{\ty{bool}}} b  \\
-\turn \neg    =  \lquant{b} b \imp \F \\
-\turn {\wedge}  =  \lquant{b_1\ b_2}\uquant{b} (b_1\imp (b_2 \imp b)) \imp b \\
-\turn {\vee}  =  \lquant{b_1\ b_2}\uquant{b} (b_1 \imp b)\imp ((b_2 \imp b) \imp b) \\
-\turn \OneOne  =  \lquant{f_{\alpha \fun\beta}}\uquant{x_1\ x_2}
+\turn \exists \HOLTokenDefEquality \lquant{P_{\alpha\fun\ty{bool}}} P({\hilbert}\, P) \\
+\turn \F \HOLTokenDefEquality \uquant{b_{\ty{bool}}} b  \\
+\turn \neg \HOLTokenDefEquality \lquant{b} b \imp \F \\
+\turn {\wedge}  \HOLTokenDefEquality  \lquant{b_1\ b_2}\uquant{b} (b_1\imp (b_2 \imp b)) \imp b \\
+\turn {\vee} \HOLTokenDefEquality \lquant{b_1\ b_2}\uquant{b} (b_1 \imp b)\imp ((b_2 \imp b) \imp b) \\
+\turn \OneOne \HOLTokenDefEquality \lquant{f_{\alpha \fun\beta}}\uquant{x_1\ x_2}
                     (f\ x_1 = f\ x_2)  \imp (x_1 = x_2) \\
-\turn \Onto  =  \lquant{f_{\alpha\fun\beta}}
+\turn \Onto \HOLTokenDefEquality \lquant{f_{\alpha\fun\beta}}
                   \uquant{y}\equant{x} y = f\ x \\
-\turn \TyDef  =  \lambda P_{\alpha\fun\ty{bool}}\
+\turn \TyDef \HOLTokenDefEquality \lambda P_{\alpha\fun\ty{bool}}\
                   rep_{\beta\fun\alpha}.\;
@@
 Usually the above four axioms are the only axioms allowed
-in conventional formalisation projects in HOL: adding new axioms
-manually, may break logical consistency.
+in conventional formalisation projects in HOL4: adding new axioms
+manually may break logical consistency.
 

### 2019-11-27 ic-journal/intro.tex
Clean up reviewed highlights; fixed some bibitems

@@
 proofs about various forms of enhancements of the bisimulation proof
-method (the `up-to' techniques).
+method (the ``up-to'' techniques).
 %

### 2019-11-27 ic-journal/related.tex
Clean up reviewed highlights; fixed some bibitems

@@
 However, the differences are substantial, especially in the way of defining
-bisimilarities. We greatly benefited from \hl{new} features and standard
+bisimilarities. We greatly benefited from new features and standard
 libraries in recent versions of HOL4, and our formalisation has
@@
 he has formalized basic properties for strong/weak equivalence (congruence, basic
- algebraic laws); \hl{the CCS syntax does not have constants
-or recursion, using instead replication.}
+ algebraic laws); the CCS syntax does not have constants
+or recursion, using instead replication.
 % The formalisation effort has then been continued 
@@
 and Chaudhuri et al.\;\cite{chaudhuri2015lightweight} in Abella, the latter
-focuses on `bisimulation up-to' techniques (for strong bisimilarity)
+focuses on ``bisimulation up-to'' techniques (for strong bisimilarity)
 for CCS and $\pi$-calculus.

### 2019-11-27 ic-journal/unique.tex
Clean up reviewed highlights; fixed some bibitems

@@
 show that $\R$ is a bisimulation. Suppose $(R, S) \in \R$ via a context
-$C$. For any $R'$ such that $R \arr{\mu} R'$, we have to find \hl{an} $S'$ with $S \Arcap{\mu}
+$C$. For any $R'$ such that $R \arr{\mu} R'$, we have to find an $S'$ with $S \Arcap{\mu}
 S'$ and $(R', S') \in \R$. From $R \wb C[{\til P}]$, we derive $C[{\til P}]
@@
 relation $\mcontrBIS$.
-Furthermore, we needed to show that the  definition \hl{found} 
-does indeed yields the coarsest precongruence
-contains in $\mcontrBIS$; the proof is similar \hl{to}
+Furthermore, we needed to show that the definition \hl{being found}
+indeed yields the coarsest precongruence
+\hl{contained} in $\mcontrBIS$. The proof is similar with
 the analogous result for $\rapprox$. See Section~\ref{s:coarsest} for

### 2019-12-05 ic-journal/ccs.tex
Revised Section 1 and 2

@@
 
-Here we recall the core theory of CCS.
+%Here we recall the core theory of CCS.
 We assume a possibly infinite set of \emph{names} $\mathscr{L} = \{a, b,
-\ldots\}$ yielding \emph{input} and \emph{output labels} (or \emph{actions}), plus a special invisible
+\ldots\}$ yielding \emph{input} and \emph{output labels} (or
+\emph{actions}), a special \emph{invisible}
 action $\tau \notin \mathscr{L}$, and another possibly infinite
@@
 In our presentation of CCS, the restriction operator takes a set of labels $L
-  \subseteq \mathscr{L}$, rather than a single one.  
+  \subseteq \mathscr{L}$ rather than a single one.  
 The relabeling operator takes a relabeling function
@@
 We sometimes omit a trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil$.
-A CCS process $P$ may evolve to another one, say $P'$, under
+A CCS process $P$ may evolve to another one \hl{(i.e. having a \emph{transition})}, say $P'$, under
   an action $\mu$, written by $P \arr{\mu} P'$.
@@
 Semantics (SOS) rules shown in Fig.~\ref{f:LTSCCS}.
-(The symmetric versions of the SOS rules for
-parallel composition and binary choice are omitted.)
-A CCS processes uses only \emph{guarded sums} if all occurrences of
-sums are in the form $a.P + b.Q$. 
+A CCS \hl{process is said to use} only \emph{guarded sums} if all occurrences of
+\hl{summation} are in the form $a.P + b.Q$.
 The \emph{immediate derivatives} of a
-process $P$ are elements of the set $\{P' \st P \arr\mu P' \mbox{for some $\mu$}\}$.
+process $P$ are \hl{the} elements of the set $\{P' \st P \arr\mu P'
+\mbox{ for some $\mu$}\}$.
 We use $\ell$ to range over visible actions (i.e.~inputs or outputs, excluding $\tau$)
-and $\alpha, \mu$  to range over all actions.
+and $\mu$ to range over all actions.
 \begin{figure*}[t]
@@
 \end{center}
-\caption{Structural Operational Semantics of CCS}
+\caption{Structural Operational Semantics of CCS. (The symmetric rules for
+$+$ and $|$ are omitted.)}
 \label{f:LTSCCS}

### 2019-12-05 ic-journal/intro.tex
Revised Section 1 and 2

@@
 the equations must be both \emph{guarded} and \emph{sequential}. That is,
-the variables of the equations can only occur underneath visible prefixes and summations.
-One way to overcome such limitations is to replace the equations
+the variables of the equations can only occur underneath visible prefixes and \hl{summation}.
+One way to overcome \hl{these} limitations is to replace the equations
 with special inequations called
-\emph{contractions}~\cite{sangiorgi2015equations,sangiorgi2017equations}. Contraction is a
+\emph{contractions}~\cite{sangiorgi2015equations,sangiorgi2017equations}. \hl{The
+contraction relation} is a
 preorder that, roughly, places some efficiency constraints on processes.
@@
 in the case of contractions the solution is evaluated with respect to
-the contraction preorder, rather than bisimilarity. 
+the contraction preorder rather than bisimilarity. 
 With contractions, most syntactic limitations of the unique-solution theorem are
@@
 in~\cite{sangiorgi2017equations}
-(where the issue is bypassed using a more
+(where the issue is bypassed \hl{by} using a more
 restrictive CCS syntax)
-is the occurrences of sums (e.g.~$P + Q$) due to
+is the occurrences of \hl{\emph{unprefixed}} sums (e.g.~$P + Q$) due to
 the non-substitutivity of the contraction preorder in this case.
@@
 the unique-solution theorems rely on a large number of fundamental results.
-Indeed the formalisation encompasses all basic properties of strong and weak
-bisimilarities (e.g.~the fixed-point and substitutivity properties), the
-basic properties of rooted bisimilarity and their algebraic laws.
+Indeed the formalisation encompasses all basic properties of strong,
+\hl{weak and rooted}
+bisimilarities (e.g.~the fixed-point and substitutivity properties), \hl{and} their algebraic laws.
 Further extensions include several versions of ``bisimulation up to''
-techniques, the expansion and contraction preorder.
+techniques, \hl{and properties of the expansion and contraction preorders}.
 Concerning rooted bisimilarity, the formalisation
-includes Hennessy's Lemma and Deng's Lemma,
+includes Hennessy's Lemma, Deng's Lemma,
  and two theorems saying that rooted bisimilarity is the coarsest (largest)
@@
 without such hypothesis, essentially \hl{formalising} van Glabbeek's proof~\cite{van2005characterisation}.
-Similar results are also proved for the rooted contraction preorder.
-In this respect, the work is also an extensive experiment using the HOL theorem prover with its
+\hl{With} this respect, the work is also an extensive experiment using the HOL theorem prover with its
 recent developments, including its coinduction package.
 
-From the point of view of the CCS theory, this formalisation has offered us the possibility of
+This formalisation has offered us the possibility of
 further refining the theory of unique solutions of contractions.
-In particular,  existing results~\cite{sangiorgi2017equations} have limitations on the body of the contractions due to the
+In particular,  existing results~\cite{sangiorgi2017equations} have
+limitations on the body of the contractions due to the
 substitutivity problems of weak bisimilarity and other behavioural relations with respect
@@
 refined by moving from the contraction preorder to
-\emph{rooted contraction}, that is, the coarsest precongruence contained in the contraction
-preorder. The resulting unique-solution theorem is now valid for
+\emph{rooted contraction}, \hl{which is shown to be} the coarsest
+precongruence contained in the contraction preorder.
+The resulting unique-solution theorem is now valid for
 \emph{rooted bisimilarity} (hence also for bisimilarity itself), and places no 
-constraints on the use the sum operator.
+constraints on \hl{summation}.
 
@@
 for weak bisimilarity that use the contraction preorder as an
-auxiliary relation, and other unique solution results (e.g. the one
+auxiliary relation, and other \hl{unique-solution theorems} (e.g. the one
 for rooted bisimilarity 
@@
 %
-In these cases, when moving between proofs there are only a few places in
-which the HOL proof scripts have to be modified.
+In these cases, when moving between proofs there are only a few places \hl{in}
+the HOL proof scripts \hl{that has} to be modified.
 Then the successful termination of a proof gives us the
- guarantee that the proof is
-sound and complete, eliminating the risks 
+ guarantee that the proof is \hl{correct}, eliminating the risks 
 of overlooking or missing details as in \emph{paper-and-pencil} proofs.
 
-We first consider the case of a single equation (or contraction)
-that we call the \emph{\univariate case}. \hl{Then we} consider
-the \emph{\multivariate case}, where more than one equation
-  (or contraction) with multiple equation variables is considered.
-The \univariate versions \hl{of the} unique-solution theorems use
-$\lambda$-functions to present CCS equations,
-while the \multivariate versions require a
-more careful and delicate treatment of CCS
+\hl{Concerning the formalisation of unique-solution theorems,}
+we first consider the case of a single equation (or contraction), the
+\emph{\univariate case}.
+\hl{Then we turn to} the \emph{\multivariate case} where more equations
+  (or contractions) with multiple equation variables \hl{are involved}.
+  The \univariate versions \hl{of the} unique-solution theorems
+  \hl{can directly use}
+$\lambda$-functions to \hl{represent} CCS equations,
+while the \multivariate versions \hl{require}
+more careful and delicate \hl{treatments} of CCS
 expressions, with multiple variables and substitutions acting on them.
-
+% should be in the same paragraph, still talking about multivariable equations.
 In contrast to literature such as~\cite{Gorrieri:2015jt},
@@
 in CCS terms are treated as  (free) equation variables, and a CCS
-\emph{process} is a CCS term without equation variables. 
+process is a CCS \hl{expression} without equation variables.  % don't use "term"
 This allows us a smoother move from the \univariate case to the \multivariate
-one. See Section~\ref{sec:multivariate} for  details.
+one. (See Section~\ref{sec:multivariate} for more details.)
 
@@
 
-Section~\ref{ss:ccs} presents basic background materials on CCS,
+In Section~\ref{ss:ccs} \hl{we recall the core theory} of CCS,
 including its syntax, operational semantics, bisimilarity and rooted
 bisimilarity.
-Section~\ref{s:eq} discusses equations and contractions.
+\hl{Then,} Section~\ref{s:eq} discusses equations and contractions, and in particular,
 Section~\ref{ss:new} presents rooted contraction and the related
 unique-solution result for rooted bisimilarity.
-Section~\ref{s:for} highlights our formalisation in HOL4 for the \univariate case.
-Section~\ref{sec:multivariate} describes the \hl{extension} to the \multivariate case.
-Finally,  Section~\ref{s:rel} and \ref{s:concl} discuss related work,
+In Section~\ref{s:for} we highlight the CCS formalisation in HOL4, with
+the unique-solution theorems in the \univariate case.
+Section~\ref{sec:multivariate} describes the extension to the \multivariate case.
+Finally, in Section~\ref{s:rel} and \ref{s:concl} \hl{we discuss} the related work,
 conclusions, and a few directions for future work.

### 2019-12-07 ic-journal/ccs.tex
Up to Section 3.1

@@
 The \emph{immediate derivatives} of a
-process $P$ are \hl{the} elements of the set $\{P' \st P \arr\mu P'
+process $P$ are \hl{the} elements of $\{P' \st P \arr\mu P'
 \mbox{ for some $\mu$}\}$.
@@
 \paragraph{Further notations}
-We let $\R$, $\S$ range over binary relations, sometimes using 
+\hl{Let} $\R$, $\S$ range over binary relations, sometimes using 
  infix notation for them, \hl{e.g.} $P \,\R\, Q$ means $(P,Q) \in \R$.

### 2019-12-07 ic-journal/equa.tex
Clean up reviewed highlights; fixed some bibitems
Up to Section 3.1

@@
  in $a.X + \recu X (b.X)$.
-A \hl{term} without free variables is  a \emph{process}.
+A term without free variables is  a \emph{process}.
 % This setting does not cause any ambiguity, but sometimes leads to more
@@
 variables also as \emph{equation variables}. This eliminates the need of
-another type for  equations, and we can reuse the existing
+\hl{an additional} type for \hl{CCS} equations, and we can reuse the existing
 variable substitution operation (cf.~the SOS rule for the Recursion in
-Fig.~\ref{f:LTSCCS}) for the substitution of equation variables.
-For example, the result of substituting variable $X$ with $\nil$ in $a.X +
-\recu X (b.X)$,  written $(a.X + \recu X (b.X)) \sub {\nil} X$, is
-$a.\nil + \recu X (b.X)$ (with the part $\recu X (b.X)$
-untouched). \Multivariate substitutions are written in the same syntax,
+Fig.~\ref{f:LTSCCS}) for \hl{substitutions} of equation variables.
+For example, the result of substituting \hl{the} variable $X$ with $\nil$ in $a.X +
+\recu X (b.X)$,  written \hl{as} $(a.X + \recu X (b.X)) \sub {\nil} X$, is
+$a.\nil + \recu X (b.X)$ with $\recu X (b.X)$
+untouched. \Multivariate substitutions are written in the same syntax,
 e.g. $E \sub {\til P} {\til X}$. Whenever $\til X$ is clear from the
@@
 \label{ss:SysEq}
-When discussing equations it is standard to talk about `context'. This is a 
+When discussing equations it is standard to talk about ``contexts''. This is
 a CCS expression possibly containing free variables that, however, may not occur within
@@
 say that, if a context $C$
-%  \hl{(i.e., a CCS expression with possibly
-% free variables)}\footnote{\hl{Rigorously speaking, under our setting
+%  (i.e., a CCS expression with possibly
+% free variables)\footnote{Rigorously speaking, under our setting
 % (i.e.~reusing free agent variables as equation variables) not all
@@
 % equations/contractions'' theorems do not hold if equation variables
-% are allowed to occur inside any recursion operator.}} 
+% are allowed to occur inside any recursion operator.}
 obeys certain conditions,
@@
  a countable indexing set $I$, we have variables $X_i$, and expressions
-$E_i$ possibly containing such variables $\cup_i \{ X_i\}$. Then 
+$E_i$ possibly containing such variables $\bigcup_i \{ X_i\}$. Then 
 $\{ X_i = E_i\}_{i\in I}$ is 
@@
 
-\begin{definition}[solutions and unique solutions]
+\begin{definition}[solutions and the unique solution]
   \label{def:solution}
@@
 (or for $\rapprox$) can be obtained by replacing all occurrences of $\wb$
-in above definition with $\sim$ and $\rapprox$, respectively.
+in \hl{the} above definition with $\sim$ and $\rapprox$, respectively.
 
-For instance, the solution of the equation $X = a. X$ 
+For instance, the solution of the equation $X \wb a. X$ 
 is the process
@@
 In contrast, the equation 
- $X = a|  X$ has solutions that may be quite different, for instance,
+ $X \wb a|  X$ has solutions that may be quite different, for instance,
  $K$ and $K | b$, for $K \DSdefi \recu K {\, (a. K)}$. (Actually any process capable of
-continuously performing $a$--actions is a solution of $X = a|  X$.)
-
-%
-% The unique solution of the system (1), modulo $\wb$,  is the constant $K \Defi a
-% . K$:  for any other solution $P$ we have $P \wb K$.
-% The unique solution of (2), modulo $\wb$, are the constants $K_1 , K_2$
-% with $K_1 \Defi a . K_2$ and $K_2 \Defi b. K_1$; again, for any other
-% pair of solutions $P_1,P_2$ we have $K_1 \wb P_1$ and $K_2 \wb P_2$.
+continuously performing $a$--actions is a solution of $X \wb a|  X$.)
 %
@@
 \label{t:Mil89}
-Let $E_i$ be guarded and sequential with free
-variables in $\til X$, and let ${\til P} \wb {\til E}\{\til P /\til X\}$,
-  ${\til Q} \wb {\til E}\{\til Q /\til X\}$. Then ${\til P} \wb {\til Q}$.
+Let $E_i$ be guarded and sequential \hl{(with only guarded sums)}, and with free
+variables in $\til X$. Let ${\til P} \wb {\til E}\{\til P /\til X\}$,
+  ${\til Q} \wb {\til E}\{\til Q /\til X\}$, then ${\til P} \wb {\til Q}$.
 \end{theorem}
 
-The proof of the theorem above exploits an invariance
+The proof of the last two theorems above exploits an invariance
 property on immediate derivatives
 of guarded and sequential expressions, and then extracts a bisimulation
-(up to bisimilarity) out
-of the solutions of the system.
+(up to bisimilarity) out of the solutions of the system.
 To see the need of the sequentiality condition, consider
- the equation (from \cite{Mil89}) $X = \res a (a. X | \outC a)$
+ the equation (from~\cite{Mil89}) $X \wb \res a (a. X | \outC a)$
 where $X$ is guarded but not sequential. Any process that does not use
-$a$ is a solution, e.g. $\nil$ and $b.\nil$.
+$a$\hl{--action} is a solution, e.g. $\nil$ and $b.\nil$.
 
-For more details of above three theorems, see Section~\ref{ss:part2}
-for the \univariate case and
-Section~\ref{sec:multivariate} for the \multivariate case.
+For more details \hl{on the formalisation of the} above three theorems, see Section~\ref{ss:part2}
+for the \univariate case and Section~\ref{sec:multivariate} for the \multivariate case.
 

### 2019-12-09 ic-journal/contraction.tex
Up to Section 4.0

@@
 brings a new proof technique for proving (weak) bisimilarities. However, it has
- limitations: the equations must be guarded and sequential (moreover
-all sums where equation variables appear must be guarded sums).
+ limitations: the equations must be guarded and sequential. (\hl{Moreover,}
+all sums where equation variables appear must be guarded sums.)
 This limits the usefulness of the technique, since
-the occurrences of other operators above the variables, such as parallel
-composition and restriction, in general cannot be removed.
-The constraints of Theorem~\ref{t:Mil89}, however, can be 
+the occurrences of other operators \hl{using equation} variables, such as parallel
+composition and restriction,
+in general cannot be \hl{eliminated}. % without changing the meaning of equations
+The constraints \hl{in} Theorem~\ref{t:Mil89}, however, can be
 weakened if we move from equations to a special kind of inequations called
@@
 Intuitively, the bisimilarity contraction $\mcontrBIS$ is a preorder
-where $P \mcontrBIS Q$ holds if $P \wb Q$ and, in addition, 
-$Q$ \emph{has the possibility of being at least as efficient as $P$} (as far as
+\hl{that} $P \mcontrBIS Q$ holds if $P \wb Q$ and, in addition, 
+\emph{$Q$ has the possibility of being at least as efficient as $P$} (as far as
 $\tau$-actions are performed).
-Process $Q$, however, may be non-deterministic and may have other ways
-of doing the same work, and these could be slow (i.e., involving
+The process $Q$, however, may be nondeterministic and may have other ways
+\hl{to do} the same work, \hl{ways} which could be \hl{slower} (i.e., involving
 more $\tau$-actions than those performed by $P$).
@@
 A process relation ${\R}$ 
- is a \emph{(bisimulation) contraction} if, whenever
- $P\RR Q$, %for all $\mu$
+ is a \emph{(bisimulation) contraction} if, whenever $P\RR Q$,
 
 \begin{enumerate}
-\item   $P \arr\mu P'$ implies there is $Q'$ such that $Q \arcap \mu
+\item $P \arr\mu P'$ implies \hl{that} there is $Q'$ \hl{with} $Q \arcap \mu
   Q'$ and $P' \RR Q'$;
-\item $Q \arr\mu Q'$   implies there is $P'$ such that $P \Arcap \mu
- P'$ and $P' \wb Q'$\enspace.
+\item $Q \arr\mu Q'$ implies \hl{that} there is $P'$ \hl{with} $P \Arcap \mu
+ P'$ and $P' \wb Q'$.
 \end{enumerate}
 Two processes $P$ and $Q$ are in the \emph{bisimilarity
-contraction}, written as $P \mcontrBIS Q$ ($P$ \emph{contracts to} $Q$),
+contraction}, written as $P \mcontrBIS Q$,
 if $P\ \R\ Q$ for some contraction $\R$.
@@
 \end{definition}
-
-In the first clause $Q$ is required to match $P$'s challenge
-transition with at most one transition.
+In clause (1) \hl{of the above definition}, $Q$ is required to match the challenge
+transition \hl{of $P$} with at most one transition.
 This makes sure that $Q$ is capable of mimicking % verb: mimic
 $P$'s work at least as efficiently as $P$. 
-In contrast, the second clause of Definition~\ref{d:BisCon}, on the
-challenges from $Q$, entirely ignores efficiency: it is the same
-clause of  weak bisimulation~--- the final derivatives are indeed required
-to be related  by $\wb$, rather than by $\R$.
+In contrast, \hl{clause (2) entirely ignores efficiency on the challenges from $Q$:}
+the final derivatives are required to be related by $\wb$, rather than by $\R$.
 
-Bisimilarity contraction is coarser than 
-the \emph{expansion relation}
-$\expa$~\cite{arun1992efficiency,sangiorgi2015equations}:
+Bisimilarity contraction is coarser than bisimilarity expansion
+$\expa$~\cite{arun1992efficiency,sangiorgi2015equations}, \hl{one of the
+most useful auxiliary relations in up-to techniques}:
 \begin{definition}[expansion]
@@
 A process relation ${\R}$
-  is an \emph{expansion} if, whenever
-we have $P\RR Q$, for all $\mu$
+  is an \emph{expansion} if, whenever $P\RR Q$,
  \begin{enumerate}
@@
 Two processes $P$ and $Q$ are in the \emph{bisimilarity
-  expansion}, written as $P \expa Q$ ($P$ \emph{expands} $Q$),
- if $P \RR Q$ for some expansion $\R$.
+  expansion}, written as $P \expa Q$, if $P \RR Q$ for some expansion $\R$.
  \end{definition}
-The expansion preorder is widely used in proof techniques for bisimilarity and
-intuitively refines bisimilarity by 
+\hl{Bisimilarity expansion} is widely used in proof techniques for bisimilarity.
+\hl{It} intuitively refines bisimilarity by 
 formalising the idea of ``efficiency'' between processes.
-Clause (1) is the same in the both preorders, while in clause (2) expansion uses 
-$P \Arr \mu P'$, rather than $P \Arcap \mu P'$; 
-moreover in clause (2) of Def.~\ref{d:BisCon} the final derivatives
+Clause (1) is the same in the both preorders, while in clause (2) expansion \hl{requires}
+$P \Arr \mu P'$, rather than $P \Arcap \mu P'$.
+\hl{Moreover,} in clause (2) of Def.~\ref{d:BisCon} the final derivatives
 are simply required to be bisimilar ($P' \wb Q'$).
@@
 
-In the same way as bisimilarity, both the expansion and the
+\hl{Bisimilarity expansion and bisimilarity contraction are both
+preorders. (Thus we can also call them the \emph{expansion or contraction
+preorder}, respectively.)}
+Similarily with (weak) bisimilarity, both the expansion and the
 contraction preorders are preserved by all CCS operators except the
-summation. The proofs are similar, see e.g.~\cite{sangiorgi2017equations}.
+summation. The proofs are similar \hl{with the case of bisimilarity},
+see, e.g.~\cite{sangiorgi2017equations} \hl{for details.}
 

### 2019-12-09 ic-journal/formal.tex
Up to Section 4.0

@@
 
-We highlight here a formalisation of CCS in the HOL theorem prover
+We highlight here a \hl{comprehensive} formalisation of CCS in the HOL theorem prover
 (HOL4)~\cite{Melham:1993vl,slind2008brief}, with a focus towards the
@@
 Higher Order Logic (HOL)~\cite{hollogic} traces
-its roots back to LCF
-\cite{gordon1979edinburgh,milner1972logic} by Robin Milner and others
+its roots back to the
+\emph{Logic of Computable Functions
+  (LCF)}~\cite{gordon1979edinburgh,milner1972logic}
+by Robin Milner and others
 since 1972. It is a variant of
@@
 HOL4 has implemented the original HOL, 
-while some other theorem provers in the HOL family (e.g. Isabelle/HOL) have
+while some other theorem provers in the HOL family (e.g.~Isabelle/HOL) have
 certain extensions.
@@
 % inconsistent). 
-Indeed HOL has considerably simpler logical
-foundations than most other theorem provers. %, e.g. Coq. 
+Indeed, HOL has considerably simpler logical
+foundations than most other theorem provers.
 As a consequence, theories and proofs verified in HOL are easier to understand
- to people who are not familar with more advanced
-dependent type theories.
+ \hl{for} people who are not familar with more advanced
+dependent type theories, \hl{e.g.~those implemented by Coq.}
 

### 2019-12-09 ic-journal/unique.tex
Up to Section 4.0

@@
 A \emph{system of contractions} is defined as a system of equations,
-except that the contraction symbol $\mcontr$ is used in the place of
+except that the contraction symbol $\mcontrBIS$ is used in the place of
 $=$ in Def.~\ref{def:equation}. Thus a system of contractions is a set 
-$\{  X_i \mcontr E_i\}_{i\in I}$ where $I$ is an indexing set and each
+$\{  X_i \mcontrBIS E_i\}_{i\in I}$ where $I$ is an indexing set and each
 $E_i$  contains variables in $\til X$.
@@
 \label{l:uptocon}
-Suppose $\til P$ and $\til Q$ are solutions for $\mcontrBIS$
- of a system of weakly-guarded contractions that uses 
-guarded sums.
+Suppose $\til P$ and $\til Q$ are solutions (for $\mcontrBIS$)
+ of a system of weakly guarded contractions that uses guarded sums.
 For any context $\qct$  that uses guarded sums,
@@
 \begin{proof}{(sketch from~\cite{sangiorgi2017equations})}
-  Let $n$ be the length (the number of one-step transitions) of
+  Let $n$ be the length (i.e., the number of one-step transitions) of
 a transition $\ct{\til P}\Arr\mu R$, and
 let $\ctpp {\til P}$ and $\ctpp {\til Q}$  be the processes obtained
-from  $\ct {\til P}$ and $\ct {\til Q}$ by unfolding the definitions
-of the contractions $n$ times. Thus in $\qctpp$ each hole is
-underneath at least $n$ prefixes, and cannot contribute to an action
-in the first $n$ transitions; moreover all the contexts use guarded sums.
+from  $\ct {\til P}$ and $\ct {\til Q}$ by unfolding the \hl{definition
+of $\mcontrBIS$ for} $n$ times. Thus in $\qctpp$ each hole is
+underneath at least $n$ prefixes, and \hl{therefore} cannot contribute to an action
+in the first $n$ transitions. \hl{Moreover}, all \hl{involved} contexts use guarded sums.
 
-We have $\ct{\til P} \mcontrBIS \ctpp{\til P}$, and 
-$\ct{\til Q} \mcontrBIS \ctpp{\til Q}$, 
+We have $\ct{\til P} \mcontrBIS \ctpp{\til P}$ and 
+$\ct{\til Q} \mcontrBIS \ctpp{\til Q}$
  from the precongruence property of $\mcontrBIS$ (we exploit here
@@
  prefixes, applying the definition
- of $ \mcontrBIS$ on the transition 
+ of $\mcontrBIS$ on the transition 
  $\ct{\til P}\Arr{\mu}  R$, we infer the existence
@@
 However, comparing with Milner's Theorem~\ref{t:Mil89s1}, there remains
-a constraint: the involved CCS expression may only
+\hl{one limitation}: the involved CCS expression \hl{can} only
 use guarded sums. This is mainly due to the fact that $\wb$ is not a
@@
 The above definition was found with the help of interactive theorem proving.
-The following two principles were adopted when searching
+The following two principles were adopted when \hl{manually} searching
 for a possible definition: (1) the definition should not be coinductive,
@@
 relation $\mcontrBIS$.
-Furthermore, we needed to show that the definition \hl{being found}
+Furthermore, we needed to \hl{prove} that the definition \hl{being found}
 indeed yields the coarsest precongruence
@@
 Theorem~\ref{t:contraBisimulationU} can now be stated without
-constraints on the sum operator.
+constraints on \hl{summation}.
 The schema of the proofs is almost identical, because all 
 properties of $\rcontr$ needed in this proof is its precongruence, which is
-indeed true on unrestricted contexts including direct sums:
+indeed true for \hl{all weakly guarded contexts:} % removed "direct sums"
 \begin{lemma}
 \label{l:ruptocon}
-Suppose $\til P$ and $\til Q$ are solutions  for $\rcontr$ 
- of a system of weakly-guarded contractions.
+Let $\til P$ and $\til Q$ be solutions (for $\rcontr$)
+ of a system of weakly guarded contractions.
 For any context $\qct$, 
@@
 
-\begin{theorem}[Unique solution of rooted contractions]
+\begin{theorem}[unique solution of rooted contractions]
 \label{t:rcontraBisimulationU}
-Let $E_i$ be weakly guarded with free variables in $\til X$,
+Let $E_i$ be weakly guarded with free variables \hl{up to} $\til X$,
 and let $\til P \rcontr \til E\{\til P/\til X\}$,

### 2019-12-11 ic-journal/expansion.tex
Up to Section 4.0
Up to Section 4.2

@@
  $P_1 + P_2 \wb Q_1 + Q_2$.
-For this, Milner introduced the concept of \emph{observational congruence}, also called \emph{rooted
+For this \hl{reason}, Milner introduced the concept of
+\emph{observational congruence}, also called \emph{rooted
   bisimilarity}~\cite{Gorrieri:2015jt,Sangiorgi:2011ut}:
@@
 important role in proving some key results in this paper:
-\begin{lemma}[Rooted bisimilarity by bisimulation]
+\begin{lemma}[rooted bisimilarity by bisimulation]
 \label{l:obsCongrByWeakBisim}

### 2019-12-11 ic-journal/formal.tex
Up to Section 4.2

@@
 As a consequence, theories and proofs verified in HOL are easier to understand
- \hl{for} people who are not familar with more advanced
-dependent type theories, \hl{e.g.~those implemented by Coq.}
+ \hl{for} people who are not familar with more advanced dependent type
+ theories, \hl{e.g. the Calculus of Constructions implemented in Coq.}
 
@@
 plays three different roles:
-\begin{enumerate}
+\begin{itemize}
 \item The underlying implementation language for the core HOL engine;
@@
 \item The interface language of the HOL proof scripts and interactive shell.
-\end{enumerate}
+\end{itemize}
 Moreover, using the same language HOL4 users can write complex automatic
@@
 grammar. In HOL, the standard atomic types \emph{bool} and \emph{ind}
- denote, respectively, the distinguished two-element set 2 and the
-distinguished infinite set $I$.
+ denote, respectively, the distinguished two-element set $\mathbf{2}$ and the
+distinguished infinite set $\mathbf{I}$.
 
@@
 
-The terms of the HOL logic represent elements of the
-sets denoted by the types. There are four kinds of terms in the HOL
-logic. They can be described (in simplified forms) by the BNF grammar in
-Fig.~\ref{fig:hol-terms}; see~\cite{hollogic} for a complete description.
+\hl{HOL terms} represent elements of the
+sets denoted by \hl{their} types. There are four kinds of \hl{HOL terms,
+which} can be described (in simplified forms) by the BNF grammar in
+Fig.~\ref{fig:hol-terms}. (See~\cite{hollogic} for a complete
+description of HOL, \hl{including the primitive derivative rules to be
+mentioned below.})
 
@@
 The deductive system of HOL is specified by eight primitive
-derivative rules~\cite{hollogic}:
+derivative rules:
 \begin{enumerate}

### 2019-12-11 ic-journal/sos.tex
Up to Section 4.2

@@
 
-\subsection{CCS: the formal theory}
+\subsection{The CCS formalisation}
 \label{ss:formalCCS}
@@
 for all labels (i.e. visible actions), where the type variable $\beta$ corresponds
-to $\mathscr{L}$ (the set of names for labels) used at the beginning
-of Section~\ref{ss:ccs}. The
-cardinality and the exact elements of this type depend on the type variable $\beta$
-instantiated by the end user.
+to $\mathscr{L}$ (the set of names for labels) \hl{mentioned} at the beginning
+of Section~\ref{ss:ccs}. (Thus the
+cardinality of ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' depend on \hl{its type variable:
+\mbox{when $\beta$ is finite or countable, ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is countable.}})
 All labels are divided into input and output ones.
@@
 \end{lstlisting}
-Intuitively, with reference to the CCS terminology reported in
-Section~\ref{ss:ccs}, $\beta$ represents the set of \emph{names}, and
-\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}} turns names into
-\emph{input and output actions}.
+Intuitively, ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' turns names in $\mathscr{L}$ into \emph{input and output labels}.
 For instance, if the type $\beta$ is instantiated to \texttt{string}
-(the type of all strings), then the HOL terms \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
-\HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input action $a$ and output
-action $\overline{b}$, respectively.
+(the type of all ASCII strings), then the HOL terms \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
+\HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input \emph{label} $a$ and output
+\emph{label} $\overline{b}$, respectively.
 The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
-union of all visible actions, plus the invisible action $\tau$
-(\texttt{tau}). For instace, the input action $a$ and output
-action $\overline{b}$ of type ``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''
+union of \hl{all visible actions (input and output labels) and the invisible action} $\tau$
+(\texttt{tau}). For instace, the input \emph{action} $a$ and output
+\emph{action} $\overline{b}$ of the type ``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''
 are denoted by \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLStringLit{a}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLStringLit{b}\ensuremath{)}}, respectively.
+\hl{On the
+other hand,} \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLNumLit{1}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLNumLit{2}\ensuremath{)}} could be actions of the type ``\HOLinline{\HOLTyOp{num} \HOLTyOp{Action}}'', where
+\HOLinline{\HOLTyOp{num}} is the type of natural numbers in HOL.
 
-The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'', accounting for the CCS
-expressions, has two type variables $\alpha$ and $\beta$ corresponding%
-% \footnote{The order between type variables $\alpha$ and $\beta$
-%     can be arbitrary. Our choice is aligned with the literature.
-% For instance, $\mathrm{CCS}(h,k)$ is the CCS subcalculus that can use at most $h$ constants
-% and $k$ actions~\cite{gorrieri2017ccs}. To formalize theorems on
-%  $\mathrm{CCS}(h,k)$, the required CCS type can be retrieved by instantiating the type
-% variables $\alpha$ and $\beta$ in ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' with types
-% having the corresponding cardinalities $h$ and $k$.}
-to the set of agent variables
-and the set of names
-respectively (indeed the CCS syntax in Section~\ref{ss:ccs} is parametric
-with respect to the choice of these two sets).
+The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'', accounting for all CCS terms,
+has two type variables $\alpha$ and $\beta$ corresponding
+to the set of agent variables $\mathscr{X}$
+and the set of names $\mathscr{L}$,
+respectively. (Indeed the CCS syntax in Section~\ref{ss:ccs} is parametric
+w.r.t. the choice of these two sets.)
 %
-The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' is defined inductively by the HOL \texttt{Datatype} package
+The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' is defined inductively by the
+\texttt{Datatype} package
 (here ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}'' is the type of all relabeling
@@
 \end{lstlisting}
-The above definitions allow us to use terms like \texttt{nil} and
-\texttt{sum P Q} in HOL. Their correspondences with conventional CCS notations
+The above \hl{definition allows us to write} terms like \texttt{nil} and
+\texttt{sum P Q} in HOL4. Their correspondences with conventional CCS notations
 in the literature are given in Table~\ref{tab:ccsoperator}, where
-most CCS operators have also the more readable abbreviation forms,
-either for end user or for \TeX{} outputs. (All
+most CCS operators have also more readable \hl{abbreviated} forms,
+either for end users or for \TeX{} outputs. (All
   formal theorems and definitions in this paper
   are generated from HOL4. Also, by default, all theorems are fully
-  specialised, removing outermost universal quantifiers.)
+  specialised with outermost universal quantifiers \hl{removed.})
 
@@
 The transition semantics of CCS processes strictly follows the SOS rules given
-in Fig.~\ref{f:LTSCCS}. However, they are not axioms, but the
-consequence of an \emph{inductive relation} definition of
-\HOLinline{\HOLConst{TRANS}} by HOL \texttt{HOL_reln} function 
+in Fig.~\ref{f:LTSCCS}. However, they are not axioms but
+consequences of an \emph{inductive relation} definition of
+\HOLinline{\HOLConst{TRANS}} by the \texttt{HOL_reln} function of HOL4
 (see~\citep[p.~219]{holdesc} for more details).
@@
 \item \emph{cases} is the so-called `cases' or `inversion' theorem for
-  the relations, and is used to decompose an element in the relation into the possible ways of
-  obtaining it by the rules. For instance, it leads to the following
-  theorem:
+  the relation, and is used to decompose an element in the relation into the possible ways of
+  obtaining it by the rules:
+\begin{alltt}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}.
+       \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenEquiv{}}
+       \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenDisj{}} \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \HOLBoundVar{l} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+            \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}}
+            \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLBoundVar{l}\ensuremath{)}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{l} \HOLBoundVar{L}.
+            \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+            \ensuremath{(}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLBoundVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{rf}.
+            \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{=}} \HOLConst{relabel} \HOLBoundVar{rf} \HOLBoundVar{u} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \HOLConst{relab} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{rf} \HOLSymConst{\HOLTokenConj{}}
+            \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \HOLBoundVar{X}.
+\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \ensuremath{[}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}
+\end{alltt}  
+For instance, \hl{the following proposition
+can only be proven by using the above \emph{cases} theorem}:
 \begin{alltt}
@@
 
-The last SOS rule \texttt{REC} (Recursion)
- says that if we substitute all occurrences of the variable $A$ in $P$ to
+\hl{In particular,} the SOS rule \texttt{REC} (Recursion)
+ says that, if we substitute all occurrences of the variable $A$ in $P$ to
 $(\recu A P)$ and the resulting process has a transition to $P'$
-with action $u$, then $(\recu A P)$ has the same
-transition. Here, ``\HOLinline{\ensuremath{[}\HOLConst{rec}\;\;\HOLFreeVar{X}\;\;\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\;\;\HOLFreeVar{E}}'' is an abbreviation
+with an action $u$, then $(\recu A P)$ has the same
+transition. Here ``\HOLinline{\ensuremath{[}\HOLConst{rec}\;\;\HOLFreeVar{X}\;\;\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\;\;\HOLFreeVar{E}}'' is an abbreviation
 for ``\HOLinline{\HOLConst{CCS_Subst}\;\;\HOLFreeVar{E}\;\;\ensuremath{(}\HOLConst{rec}\;\;\HOLFreeVar{X}\;\;\HOLFreeVar{E}\ensuremath{)}\;\;\HOLFreeVar{X}}'', where \HOLinline{\HOLConst{CCS_Subst}} is a
-recursive function substituting all appearences of a free variable with another CCS term.
+recursive function substituting all \hl{occurrences} of a free variable with a CCS term.
 For most CCS operators \HOLinline{\HOLConst{CCS_Subst}} just recursively goes into a deeper
@@
 \end{alltt}
-The variable substitutions only affects free
-variables: the variable $Y$ in ``\HOLinline{\HOLConst{rec}\!\;\HOLFreeVar{Y}\!\;\HOLFreeVar{E}}'' is
+Notice that, variable substitutions only affect free
+variables. For instance, the variable $Y$ in ``\HOLinline{\HOLConst{rec}\!\;\HOLFreeVar{Y}\!\;\HOLFreeVar{E}}'' is
 bound and therefore the substitution ignores it.
-% The actual substitution happens in case of
-% ``\HOLinline{\HOLConst{var} \HOLFreeVar{Y}}'' if $Y$ is being
-% substituted (and if \HOLinline{\HOLConst{CCS_Subst}} can actually reach it).
 
 A useful facility exploiting the interplay
-between HOL4 and Standard ML (that follows an idea of Nesi~\cite{Nesi:1992ve})
+between HOL4 and Standard ML (\hl{which} follows an idea of Nesi~\cite{Nesi:1992ve})
  is a recursive ML function that takes a CCS process and returns a theorem indicating all
-  direct transitions of the process (if the input process is
- infinitely branching, the function will not terminate).
+  direct transitions of the process. (If the input process is
+ infinitely branching, the function will not terminate, however.)
 For instance, we know that the process $(a.\nil | \bar{a}.\nil)$ has three
-possible (one-step) transitions: $(a.\nil | \bar{a}.\nil) \overset{a}{\longrightarrow}
+\hl{immediate derivatives given by the following transitions}:
+$(a.\nil | \bar{a}.\nil) \overset{a}{\longrightarrow}
 (\nil | \bar{a}.\nil)$, $(a.\nil | \bar{a}.\nil)
@@
 \overset{\tau}{\longrightarrow} (\nil | \nil)$.
-To completely describe all possible transitions of the process manually, the
-following two facts should be proved: (1) there are indeed the three
+To completely describe all possible transitions of the process, the
+following two facts must be proved: (1) there are indeed the three
   transitions mentioned above; (2) there is no other

### 2019-12-12 ic-journal/coarsest.tex
Up to Section 4.7

@@
 congruence contained in $\wb$. 
-The formalisation of this theorem presents some 
-delicate aspects; for instance, 
-with our CCS syntax (\hl{which has} only binary sums)
-we have to add an hypothesis about
- the involved processes not using all available labels.
-The general form of the theorem is thus~\cite{van2005characterisation,Gorrieri:2015jt,Mil89}:
+The general form of this theorem is the \hl{following}
+one~\cite{van2005characterisation,Gorrieri:2015jt,Mil89}:
 \begin{proposition}
@@
 From left to right (\ref{eq:coarsest}) trivially holds, due to the substitutivity of
-$\rapprox$ for summation and the fact that $\rapprox$ implies $\wb$:
+$\rapprox$ for summation and the fact that $\rapprox$ implies $\wb$: (Thus we are only interested in (\ref{eq:coarsest}) from right to left.)
 \begin{alltt}
@@
 \end{alltt}
-Thus we are only interested in (\ref{eq:coarsest}) from right to left.
+
+The formalisation of this theorem presents some 
+delicate aspects. For instance, 
+\hl{within} our CCS syntax \hl{which supports} only binary sums,
+one way to prove Proposition~\ref{prop:coarsest} is
+to add \hl{an additional} hypothesis \hl{that}
+ the involved processes \hl{do not use up} all available labels.
+ Indeed, this is the standard argument by Milner~\citep[p.~153]{Mil89}.
 %
-The standard argument~\cite{Mil89} requires that $p$
-and $q$ do not use all available labels (i.e.~visible actions).
-Formalising this result, however, requires a detailed treatment of free and bound names of CCS
-processes (with the restriction operator acting as a binder).
-In our formalisation, in contrast,
-we assume \hl{a} weaker condition that all immediate \emph{weak} derivatives of
- $p$ and $q$ do not use all available labels. We call this
- the \emph{free action} property:
+ Formalising this result, however, requires a detailed treatment of
+ free and bound names \hl{(of labels)} of CCS
+processes, with the restriction operator acting as a binder.
+In our actual formalisation, instead,
+we assume \hl{a} weaker hypothesis that all \emph{immediate weak} derivatives of
+$p$ and $q$ do not \hl{use up} all available labels.
+We \hl{may call it} the \emph{free action} property:
 \begin{alltt}
@@
 
-Below we show how Proposition~\ref{prop:coarsest} is connected with
-the statement in Theorem~\ref{t:rapproxCongruence}, and prove it under
+Now we show how (\ref{eq:coarsest}) is connected with
+the statement of Proposition~\ref{prop:coarsest}, and prove it under
 the free action assumptions.
@@
 contained in (weak) bisimilarity, namely \emph{bisimilarity
-  congruence}, is
+  congruence} (\texttt{WEAK_CONGR} in HOL), is
 the \emph{composition closure} (\texttt{CC}) of (weak) bisimilarity:
@@
 on CCS processes, the composition closure of $R$ is always at least as
-fine as $R$ ($\subseteq_r$ stands for \emph{relational subset}):
+fine as $R$ (here $\subseteq_r$ stands for \emph{relational subset}):
 \begin{alltt}
@@
 is contained in the composition closure of $R$
-(hence the composition closure is the coarsest one):
+(hence the composition closure is \hl{indeed} the coarsest one):
 \begin{alltt}
@@
 
-% it doesn't satisfy substitutivity on direct sums (but if the CCS syntax
-% is non-standard, i.e.~has only prefixed sums, $\approx$ is indeed a
-% congruence). The purpose is to find a coarsest congruence contained in
-% weak bisimilarity. (``coarsest'' means, any other congruence finer than it must be contained in it)
-% There're two ways to build a congruence from weak bisimilarity, one
-% way is the standard definition for observational congruence (rooted
-% weak bisimilarity) $\rapprox$ in CCS textbooks, but even it's proven to be a
-% congruence we don't know if it's coarsest one.  The other way is to
-% build a (pre)congruence closure (Def ??) directly upon
-% the original weak bisimilarity relation, we call the resulting
-% relation ``Weak bisimilarity congruence'' ($[\approx]$):
-% \begin{alltt}
-% \HOLConst{WEAK_CONGR} \HOLTokenDefEquality{} \HOLConst{CC} \HOLConst{WEAK_EQUIV}
-% \end{alltt}
-% It can be shown that any such (pre)congruence closure is automatically coarsest.
-%
-% Now it remains to prove that, the congruence relation built by above
-% two quite different approaches actually coincide. To achieve this goal,
-% we first noticed that, all other operators beside sums used in
-% semantic context doesn't matter, because they're already substitutable
-% for weak bisimilarity. The only important operator is the sum
-% operator. To focus on this important operator, we can temporally
-% introduce another concept called \emph{sum equivalence}:
-% \begin{alltt}
-% \HOLConst{SUM_EQUIV} \HOLTokenDefEquality{} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}.
-\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}.
-\HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)}
-% \end{alltt}
 Rooted bisimilarity $\rapprox$ (as a congruence contained in
@@
 in Fig.~\ref{fig:relationship}. Thus, to prove Proposition~\ref{prop:coarsest},
-the crux is to prove that \texttt{SUM_EQUIV} implies
-rooted bisimilarity ($\rapprox$), making all three relations
+the crux is to prove that \texttt{SUM_EQUIV} is contained in
+$\rapprox$,
+making all three relations
 ($\rapprox$, \texttt{WEAK_CONGR} and \texttt{SUM_EQUIV}) coincide:
@@
 
-The formalisation of (\ref{equa:pq}) says:
+Here is the formalisation of (\ref{equa:pq}) under free action hypothesis:
 \begin{theorem}[\texttt{COARSEST_CONGR_RL}]
-  Under the free actions assumption, $\rapprox$ is coarsest congruence contained in $\wb$.
+  \label{thm:coarsestR}
+  Under the free action hypothesis, $\rapprox$ is coarsest congruence contained in $\wb$.
 \begin{alltt}
@@
 \begin{theorem}[\texttt{COARSEST_PRECONGR_RL}]
-  Under the free actions assumption, $\mcontrBIS$ is the coarsest precongruence contained in $\contr$.
+  \label{thm:coarsestPre}
+  Under the free action hypothesis, $\mcontrBIS$ is the coarsest precongruence contained in $\contr$.
 \begin{alltt}
@@
 
-The formal proofs  of the above two results follow Milner's proof~\cite{Mil89}.
-The assumption in Milner's result 
-requires $\mathrm{fn}(p) \cup
-\mathrm{fn}(q) \neq \mathscr{L}$ (where $\mathrm{fn}$ stands for \emph{free
-  names}), and is therefore strictly stronger than the assumption in
-our result above. Indeed, in our result we only look at immediate weak
-derivatives for $p$ and $q$, and only requires that there is an input
-or output action
-that never appears as a label. Furthermore, such an action need
-not to be the same for $p$ and for $q$,
-and an action $a$ and its complementary $\outC a$ are
-considered different actions.
+The formal proofs of Theorem~\ref{thm:coarsestR} and
+\ref{thm:coarsestPre} precisely follow Milner~\citep[p.~153--154]{Mil89}.
+Although Milner requires a stronger hypothesis: $\mathrm{fn}(p) \cup
+\mathrm{fn}(q) \neq \mathscr{L}$ (here $\mathrm{fn}$ stands for \emph{free
+  names}), the actual proof essentially requires only the above
+free action property.
+\hl{Indeed, in the proof one only looks at the immediate weak
+derivatives of $p$ and $q$, and only requires that there is an input
+or output label that never occurs as a label of the involved weak transitions.
+Furthermore, an label $a$ and its complementary $\outC a$ are
+considered different: even the involved processes have used up all
+available names, including, say, $a$, the whole proof can still complete as
+long as $\outC a$ never occurs in the immediate weak
+derivatives.}
 
@@
 
-In this section, we give another more complex proof of the second part
-of Theorem~\ref{t:rapproxCongruence}, but only for finite-state CCS.
+\hl{Since the type} ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' is \hl{parameterized with two
+type variables $\alpha$ and $\beta$, if the type of all label
+names $\beta$ has a relatively small cardinality (or just a singleton in the
+extreme case), it is quite possible that the involved processes in}
+Proposition~\ref{prop:coarsest} used up all available labels, and thus the free
+action hypothesis does not hold. In this case, it is still possible to prove
+Proposition~\ref{prop:coarsest}, \hl{but due to some
+limitations of HOL itself we have to assume that the involved
+processes are \emph{finite-state}, i.e. the set of all derivatives is
+finite.} The original proof, due to van
+Glabbeek~\cite{van2005characterisation}, does not require finite-state CCS.
+Below is the main theorem:
 \begin{theorem}[\texttt{COARSEST_CONGR_FINITE}]
     \label{thm:coarsestfiniteState}
-    For finite-state CCS, $\wb$ is the coarsest congruence contained in $\approx$:
+    For finite-state CCS, $\rapprox$ is the coarsest congruence contained in $\wb$:
 \begin{alltt}
@@
 
-The formal proof follows van
-Glabbeek~\cite{van2005characterisation}.
-The core lemma says that for
+The precise definition of \texttt{finite_state} used in above theorem
+will be given later. We start with a core lemma saying that, for
 any two processes $p$ and $q$, if there exists a \emph{stable} (i.e.~$\tau$-free)
@@
  $q$, then \texttt{SUM_EQUIV} indeed implies rooted bisimilarity
- ($\rapprox$) (see~\cite{Tian:2017wrba} for more details of the proof):
+ ($\rapprox$) (see~\cite{van2005characterisation,Tian:2017wrba} for its proof):
 \begin{alltt}

### 2019-12-12 ic-journal/coarsest.tex
Up to page 23

@@
 \hl{Since the type} ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' is \hl{parameterized with two
-type variables $\alpha$ and $\beta$, if the type of all label
+type variables, if the type of all label
 names $\beta$ has a relatively small cardinality (or just a singleton in the
@@
 Glabbeek~\cite{van2005characterisation}, does not require finite-state CCS.
-Below is the main theorem:
+Here is the main theorem:
 \begin{theorem}[\texttt{COARSEST_CONGR_FINITE}]
@@
 The precise definition of \texttt{finite_state} used in above theorem
-will be given later. We start with a core lemma saying that, for
-any two processes $p$ and $q$, if there exists a \emph{stable} (i.e.~$\tau$-free)
- process $k$ which is not bisimilar with any derivative of $p$ and
+will be given later. We start with a core lemma (\texttt{PROP3_COMMON}) saying that, for
+any two processes $p$ and $q$, if there exists a \emph{stable}
+(i.e.~\hl{all immediate derivatives} are $\tau$-free)
+ process $k$ which is not bisimilar with any \hl{weak} derivative of $p$ and
  $q$, then \texttt{SUM_EQUIV} indeed implies rooted bisimilarity
- ($\rapprox$) (see~\cite{van2005characterisation,Tian:2017wrba} for its proof):
+ ($\rapprox$) (see~\cite{van2005characterisation,Tian:2017wrba} for
+ its proof, both informal and formal versions):
 \begin{alltt}
@@
 
-To actually construct this process $k$,
- the proof relies on arbitrary infinite sums of 
-processes and uses transfinite induction to obtain
-an arbitrary large sequence of processes (firstly introduced by Jan
-Willem Klop \cite{van2005characterisation})
- that are all pairwise non-bisimilar.
+To prove Theorem~\ref{thm:coarsestfiniteState}, \hl{it only remains to construct this stable
+process $k$ for any two finite-state processes $p$ and $q$.}
+\hl{For arbitrary CCS processes, this construction} relies on
+arbitrary infinite sums of processes (not within our CCS syntax) and
+transfinite induction to obtain
+an arbitrary large sequence of processes that are all pairwise
+non-bisimilar,
+which was firstly introduced by Jan
+Willem Klop~(see \cite{van2005characterisation} for some historical notes).
 We have only partially formalised
-this proof (Theorem~\ref{thm:coarsestfiniteState} in next section),
-because
-the typed logic
+van Glabbeek's proof, mostly because our CCS syntax does not allow infinite
+summation (and it is not easy to extend it with this support).
+Another more important reason is that, the typed logic
 implemented in various HOL systems (including Isabelle/HOL) is not
 strong enough to define a type for all possible
-ordinals~\cite{norrish2013ordinals}.
-As a consequence, the final result is only for finite-state
-CCS.\footnote{van Glabbeek's
-  original proof applies to all CCS processes; however,  it
-  requires the CCS syntax to support arbitrary large summations based
-  on ordinals, and relies on the existence  of an
-  ordinal larger than the cardinality of any given set. This is beyond
-  the possibilities of HOL.}
+ordinals~\cite{norrish2013ordinals} which is required in van
+Glabbeek's proof. As the consequence, the formalisation
+(Theorem~\ref{thm:coarsestfiniteState})
+can only apply to finite-state CCS.
 
-The assumption in \texttt{PROP3_COMMON} requires the
+The above core lemma (\texttt{PROP3_COMMON}) requires the
 existence of a special CCS process, which is not weakly bisimilar to
-any sub-process emanating from the two root processes by weak
+any \hl{subprocess emanated} from the two root processes by weak
 transitions.
-There could be infinitely many such sub-processes, even on finitely
+There could be infinitely many such subprocesses, even on finitely
 branching processes.
@@
 modulo weak bisimilarity.
-If there are infinitely many of such classes, 
+If there are infinitely many such classes, 
 then it will be 
 possible to choose one that is distinct from all the (finitely many) states in the
-graphs of the two given processes.  
-This can be done following Klop's contruction \cite{van2005characterisation}.
+\hl{transition} graphs of the two given processes.
+This can be done by following Klop's contruction.
  We call the processes in this construction the ``Klop processes'':
@@
 
-Following the inductive structure of the definition of Klop processes,
+Following the inductive structure of the above definition,
   and using the SOS rules
-  ($\mathrm{Sum}_1$) and ($\mathrm{Sum}_2$), we have proved
+  ($\mathrm{Sum}_1$) and ($\mathrm{Sum}_2$), we can prove
 the following properties of Klop functions:
@@
 \end{proposition}
-Having
- a recursive function  on all natural numbers,
-  we can map these into a set containing  all Klop processes. 
-We can therefore 
-choose a number that is mapped onto a Klop process
-that is distinct (i.e., not bisimilar)  from 
-any  of the derivatives of two  given 
+
+For any ``\HOLinline{\HOLConst{label}\;\HOLFreeVar{a}}'', having a function ``\HOLinline{\HOLConst{KLOP}\;\HOLFreeVar{a}}'' (of the type ``\HOLinline{\HOLTyOp{num} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
+\hl{defined on all natural numbers, we can get a set of processes
+containing all Klop processes built by the same label.
+Since the number of all Klop processes in this set is (countably) infinite, and
+since they are all pairwise non-bisimiar,
+we can always
+choose a number that is mapped to a Klop process
+that is non-bisimilar with} any derivative of two given 
  finite-state CCS processes $p$ and $q$
 (by definition, the number of such derivatives is finite).
-This is done by 
-appealing to a basic set-theory result.
+This property is captured by appealing to the following set-theoreric lamma.
 
-% (processes 
-% all states coming from
-% two finite-state CCS processes $p$ and $q$ is finite. Choosing from an
-% infinite set for an element distinct with any subprocess leading from
-% $p$ and $q$, is always possible.  This result is purely mathematical,
-% completely falling into basic set theory:
 \begin{lemma}

### 2019-12-12 ic-journal/coarsest.tex
Up to Section 4.8 (page 22)

@@
 For any ``\HOLinline{\HOLConst{label}\;\HOLFreeVar{a}}'', having a function ``\HOLinline{\HOLConst{KLOP}\;\HOLFreeVar{a}}'' (of the type ``\HOLinline{\HOLTyOp{num} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
-\hl{defined on all natural numbers, we can get a set of processes
+\hl{defined on all natural numbers, we can get a countable set of processes
 containing all Klop processes built by the same label.
@@
  finite-state CCS processes $p$ and $q$
-(by definition, the number of such derivatives is finite).
-This property is captured by appealing to the following set-theoreric lamma.
-
+(by definition, the number of such derivatives is finite), \emph{even}
+if $a$ is the only element of type $\beta$ (i.e. the only label name
+in $\mathscr{L}$).
+This property is captured by appealing to the following set-theoreric
+lamma (see~\cite{Tian:2017wrba} for its proof):
 \begin{lemma}
@@
 of ``finite-state'':
-\begin{definition}{(Definitions related to finite-state CCS)}
+\begin{definition}[finite-state CCS]
 \begin{enumerate}
-\item Define \emph{reachable} as the RTC (reflexive and transitive
-  closure) of a relation, which
-  indicates the existence of a transition between two processes:
+\item A binary relation \texttt{Reach} is the RTC (reflexive and transitive
+  closure) of a relation indicating the existence of a transition between two processes:
 \begin{alltt}
@@
 \end{alltt}
-\item The ``nodes'' of a process is the set of all processes reachable
-  from it:
+\item The set of all derivatives (\texttt{NODES}) of a process is the
+  set of all processes reachable from it:
 \begin{alltt}
@@
 \end{alltt}
-\item A process is finite-state if the set of nodes is finite:
+\item A process is \texttt{finite-state} if the set of all derivatives is finite:
 \begin{alltt}
@@
 \begin{proposition}
-If $p$ has a weak transition onto $q$, then $q$ must be in the node set of $p$:
+If $p$ has a weak transition to $q$, then $q$ must be \hl{one of the derivatives} of $p$:
 \begin{alltt}
@@
 
-Using all the above results, now we can prove the following finite
+Using all the above results, now we can prove the following \hl{finite-state}
 version of ``Klop lemma'':
-\begin{lemma}{(Klop lemma,  finite version)}
+\begin{lemma}[Klop lemma for finite-state CCS]
 \label{lem:klop-lemma-finite}
@@
 $k$, which is not weakly bisimilar 
-with
- any weak derivative  of $p$
-and $q$ (i.e., any process reachable from $p $ or $q$ by means of transitions):
+with any weak derivative  of $p$
+and $q$ (i.e., any process reachable from $p$ or $q$ by means of transitions):
 \begin{alltt}
@@
 \end{lemma}
-
-Combining the above lemma with \texttt{PROP3_COMMON} and \texttt{COARSEST_CONGR_RL},
-we can prove the theorem \texttt{COARSEST_CONGR_FINITE}.
+\hl{Then, }combining the above lemma with \texttt{PROP3_COMMON} and \texttt{COARSEST_CONGR_RL},
+\hl{we finally proved Theorem}~\ref{thm:coarsestfiniteState}
+(\texttt{COARSEST_CONGR_FINITE}). \hl{(In the future, we seek a method to
+completely eliminate the finite-state hypothesis for our CCS syntax
+with binary summation.)}
 

### 2019-12-12 ic-journal/coarsest.tex
Up to Section 4.9 (page 24)

@@
 To reason about finite-state CCS, we also need to define the concept
-of ``finite-state'':
+of ``finite-state CCS'' as a predicate on CCS processes:
 \begin{definition}[finite-state CCS]
+  \hl{Let $p$ be an arbitrary CCS process:}
 \begin{enumerate}
@@
 \end{lemma}
-\hl{Then, }combining the above lemma with \texttt{PROP3_COMMON} and \texttt{COARSEST_CONGR_RL},
-\hl{we finally proved Theorem}~\ref{thm:coarsestfiniteState}
-(\texttt{COARSEST_CONGR_FINITE}). \hl{(In the future, we seek a method to
+\hl{Then,} combining the above lemma with the core lemma
+(\texttt{PROP3_COMMON}) and Theorem~\ref{thm:coarsestR} (\texttt{COARSEST_CONGR_RL}),
+\hl{finally we proved Theorem}~\ref{thm:coarsestfiniteState}
+(\texttt{COARSEST_CONGR_FINITE}). The same proof idea also works for
+the contraction and the rooted contration. \hl{(In the future, we seek a method to
 completely eliminate the finite-state hypothesis for our CCS syntax

### 2019-12-12 ic-journal/context.tex
Up to Section 4.9 (page 24)

@@
 % context. There're multiple ways. Here 
-
-We have chosen to use $\lambda$-expressions (with the type
-``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
-to represent \emph{multi-hole contexts}.
+\hl{CCS contexts are needed in defining (pre)congruence.
+To prevent doing variable substititions, the easiest way is}
+to use \univariate $\lambda$-expressions (of the type
+``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'') as \emph{multi-hole CCS contexts}.
 %
 This choice has a significant advantage over \emph{one-hole
-contexts}, as each hole corresponds to one
-appearance of the \emph{same} variable in single-variable
-expressions (or equations). Thus \emph{contexts} can be directly used in
-formulating the unique solution of equations theorems in
-single-variable cases. The precise definition is given inductively:
+contexts}, as each hole corresponds to one occurrence of the (same)
+variable in \univariate CCS expressions or equations.
+\hl{Thus \emph{contexts} can be used both in (pre)congruence definitions
+and in formulating the unique solution of equations theorems in}
+the \univariate case. The precise definition of CCS contexts is inductive:
 \begin{alltt}
@@
 \end{alltt}
-In above inductive definitions, for any CCS term $p$,
-\HOLinline{\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{p}} is a valid context with no hole.
+\hl{Notice that, in the above definition (actually generated by
+\texttt{HOL_reln}), for any process $p$,} (\HOLinline{\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{p}}) is a
+valid context with no hole \hl{(like an equation without variable).}
 
-A context is \emph{weakly guarded} (\HOLinline{\HOLConst{WG}}) if each hole is
-underneath a prefix:
+\hl{Now comes the formal version of Def.}~\ref{def:guardness}.
+A context is \emph{weakly guarded} (\HOLinline{\HOLConst{WG}}) if each hole \hl{of
+  it} is underneath a prefix:
 \begin{alltt}
@@
 \end{alltt}
-(Notice the differences between a weakly guarded context and an
-ordinary
-context: $\lambda t. t$ is not weakly guarded as the variable is directly
-exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
-guarded as long as $e[\cdot]$ is a context, not necessary weakly guarded.)
+Notice the differences between a weakly guarded context and an
+ordinary context: $(\lambda t. t)$ is not weakly guarded as the
+variable $t$ is directly
+exposed without any prefixed action, while $(\lambda t. a.e[t])$ is weakly
+guarded as long as $e[\cdot]$ is a context, which is not necessary weakly guarded.
 
-A context is \emph{guarded} (\HOLinline{\HOLConst{SG}}) if each hole is underneath a \emph{visible} prefix:
+A context is \emph{\hl{(strongly)}  guarded} (\HOLinline{\HOLConst{SG}}) if each hole
+\hl{of it} is underneath a \emph{visible} prefix:
 \begin{alltt}
@@
 a hole, apart from the hole itself, is in forms of prefixes or sums:
-(See Def.~\ref{def:guardness} and \citep[p.~101, 157]{Mil89} for
-the informal definitions.)
  \begin{alltt}
@@
 In the same manner, we can also define variants of contexts (\HOLinline{\HOLConst{GCONTEXT}}) and weakly guarded
-contexts (\HOLinline{\HOLConst{WGS}}) in which only guarded sums are allowed (i.e.~arbitrary sums are forbidden):
+contexts (\HOLinline{\HOLConst{WGS}}) in which only guarded sums are allowed \hl{to occur}:
 \begin{alltt}
@@
 Although weak bisimilarity ($\approx$) is \emph{not} a congruence
-  with respect to~\HOLinline{\HOLConst{CONTEXT}}, it is indeed substitutive
-  with respect to~\HOLinline{\HOLConst{GCONTEXT}} 
-% (or if the CCS syntax were defined with
-%   only guarded sum operator \cite{sangiorgi2015equations}) 
-as $\approx$ is indeed preserved by guarded sums.
+  w.r.t~\HOLinline{\HOLConst{CONTEXT}}, it is indeed substitutive w.r.t.~\HOLinline{\HOLConst{GCONTEXT}} 
+as $\approx$ is indeed preserved by guarded sums. \hl{Similarily,
+contraction ($\mcontrBIS$) is also substitutive w.r.t.}~\HOLinline{\HOLConst{GCONTEXT}}.
 %
-Rooted contraction, on the other hand, is a precongruence:
+Rooted contraction ($\rcontr$, or \HOLinline{\HOLConst{OBS_contracts}} in HOL), on
+the other hand, is indeed a precongruence:
 \begin{alltt}

### 2019-12-12 ic-journal/part2.tex
Up to Section 4.10

@@
 
-\subsubsection{The case of strong bisimilarity}
+\hl{In this section we describe the formalisation of Milner's
+``unique solution of equations'' theorems, limited to} \univariate equations. (The
+\multivariate extension is described in Section~\ref{sec:multivariate}.)
 
-Based on results about ``bisimulation up to $\sim$'', we have first proved the following
- lemma. It states  that if $X$ is weakly guarded
+\subsubsection{The version for strong bisimilarity}
+
+\hl{Using ``bisimulation up to $\sim$'' technique}, we first proved the following
+key lemma, which states that, if $X$ is weakly guarded
 in $E$, then the ``first move'' of $E$ is independent of the agent
 substituted for $X$:
-\begin{lemma}[\texttt{STRONG_UNIQUE_SOLUTION_LEMMA} (Lemma 3.13 of~\cite{Mil89}, \univariate version)]
+\begin{lemma}[\texttt{STRONG_UNIQUE_SOLUTION_LEMMA}, Lemma 3.13
+  of~\cite{Mil89}, \univariate version]
 \label{lem:313}
@@
 
-Then, by a structural induction on weakly-guarded context
-(\texttt{WG}), we have proved Milner's strong unique-solution theorem
-in the \univariate case (cf.~Section~\ref{sec:multivariate} for the
-\multivariate case). The formal proof basically follows the outline of its
-informal version. It is tedious due to large amounts of case analyses
-on each CCS operator.
-
-\begin{theorem}[\texttt{STRONG_UNIQUE_SOLUTION} (Proposition 3.14 of~\cite{Mil89})]
+Then, by structural induction on weakly guarded contexts
+(\texttt{WG}), we have proved Theorem~\ref{t:Mil89s1}
+in the \univariate case. The formal proof basically follows the outline of its
+informal version~\citep[p.~102--103]{Mil89}, which is tedious due to
+large amounts of case analyses on each CCS operator.
+\begin{theorem}[\texttt{STRONG_UNIQUE_SOLUTION}, Proposition 3.14
+  of~\cite{Mil89}, \univariate version]
 Suppose the expression $E$ contains at most the variable $X$, and let $X$ be weakly
@@
 
-\subsubsection{The case of rooted bisimilarity}
+\subsubsection{The version for rooted bisimilarity}
 
-For the ``unique solutions of
-equations'' theorem of rooted bisimilarity, we use a different
-technique, represented by the
-following lemma.   It is   assertion 
- \texttt{OBS_CONGR_BY_WEAK_BISIM} mentioned in
- Section~\ref{ss:bb}, and corresponds to
- Lemma~\ref{l:obsCongrByWeakBisim}; we only report the text for  \texttt{OBS_CONGR_BY_WEAK_BISIM}.
-
-\begin{lemma}[\texttt{OBS_CONGR_BY_WEAK_BISIM}]
-% To prove two processes $E$ and $E'$  observationally congruent, it is
-% sufficient enough to construct a bisimulation with additional observational
-% transition properties:
+For the proof of Theorem~\ref{t:Mil89s3}, we have used a different
+technique based on Lemma~\ref{l:obsCongrByWeakBisim}, whose formal
+version is the following one:
 \begin{alltt}
@@
 \HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \ensuremath{\HOLBoundVar{E}\sp{\prime}}
+       \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\hfill{[OBS_CONGR_BY_WEAK_BISIM]}
 \end{alltt}
-\end{lemma}
-
-This lemma plays a key role in the
-corresponding `unique solutions' theorem, in connection with the
-following result. 
-In this part, we have not 
-used 
- ``bisimulation up-to'' techniques. Using
- the  above \texttt{OBS_CONGR_BY_WEAK_BISIM},
- we  directly construct the appropriate bisimulation relations.
+In this proof, we did not use any ``bisimulation up-to'' technique.
+With the above lemma, the next results can be proved by directly
+constructing the required bisimulation:
 \begin{lemma}[\texttt{OBS_UNIQUE_SOLUTION_LEMMA}]
@@
 
-\subsubsection{The case of weak bisimilarity}
+\subsubsection{The version for weak bisimilarity}
 
@@
 rooted bisimilarity.   There is, however, another
-version for weak bisimilarity that shares a large portion of proof
+version for weak bisimilarity (Theorem~\ref{t:Mil89}) that shares a large portion of proof
 steps with the proof for \hl{rooted bisimilarity.}
-As weak bisimilarity is not a congruence, we have to be more restrictive
-on the syntax of the equation, using strong guardedness.
+\hl{Since} weak bisimilarity is not a congruence, we have to be more restrictive
+on the syntax of the equation, \hl{with only guarded sums.}
+The related formal proofs are tedious but closely follow the informal
+proof~\citep[p.~158--159]{Mil89}, \hl{except for the uses of} ``bisimulation up
+to with weak arrows'' (Def.~\ref{def:doubleweak}) instead of the
+original version (Def.~\ref{def:singleweak}).
 
 \begin{lemma}[\texttt{WEAK_UNIQUE_SOLUTION_LEMMA}]
-If the variable $X$ is guarded and sequential in $G$, and
+If the variable $X$ is guarded and sequential (with only guarded sums) in $G$, and
 $G\{P/X\}\overset{\alpha}{\rightarrow} P'$, then $P'$ takes the form
@@
 
-We can then derive the target theorem:
 \begin{theorem}[\texttt{WEAK_UNIQUE_SOLUTION}]

### 2019-12-13 ic-journal/coarsest.tex
Up to Section 4.11

@@
  process $k$ which is not bisimilar with any \hl{weak} derivative of $p$ and
- $q$, then \texttt{SUM_EQUIV} indeed implies rooted bisimilarity
+ $q$, then \HOLinline{\HOLConst{SUM_EQUIV}} indeed implies rooted bisimilarity
  ($\rapprox$) (see~\cite{van2005characterisation,Tian:2017wrba} for

### 2019-12-13 ic-journal/part2.tex
Up to Section 4.11

@@
 large amounts of case analyses on each CCS operator.
-\begin{theorem}[\texttt{STRONG_UNIQUE_SOLUTION}, Proposition 3.14
-  of~\cite{Mil89}, \univariate version]
+\begin{theorem}[\texttt{STRONG_UNIQUE_SOLUTION}, \univariate version
+  of Theorem~\ref{t:Mil89s1}]
 Suppose the expression $E$ contains at most the variable $X$, and let $X$ be weakly
@@
 
-For the proof of Theorem~\ref{t:Mil89s3}, we have used a different
+For the proof of Theorem~\ref{t:Mil89s3}, we did not use any
+``bisimulation up-to'' technique.
+\hl{Instead,} we have used a different
 technique based on Lemma~\ref{l:obsCongrByWeakBisim}, whose formal
-version is the following one:
+version is the following one (\texttt{OBS_CONGR_BY_WEAK_BISIM}):
 \begin{alltt}
@@
 \HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\hfill{[OBS_CONGR_BY_WEAK_BISIM]}
+       \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \ensuremath{\HOLBoundVar{E}\sp{\prime}}
 \end{alltt}
-In this proof, we did not use any ``bisimulation up-to'' technique.
-With the above lemma, the next results can be proved by directly
-constructing the required bisimulation:
+\hl{By using Lemma}~\ref{l:obsCongrByWeakBisim}, \hl{the next two results} can be proved by 
+directly constructing the required bisimulation:
+(see~\cite{Tian:2017wrba} for more details)
 \begin{lemma}[\texttt{OBS_UNIQUE_SOLUTION_LEMMA}]
@@
 
-\begin{theorem}[\texttt{OBS_UNIQUE_SOLUTION}]
+\begin{theorem}[\texttt{OBS_UNIQUE_SOLUTION}, \univariate version of Theorem~\ref{t:Mil89s3}]
 Let $E$ be guarded and sequential expressions, and let $P \rapprox
@@
 steps with the proof for \hl{rooted bisimilarity.}
-\hl{Since} weak bisimilarity is not a congruence, we have to be more restrictive
+As weak bisimilarity is not a congruence, we have to be more restrictive
 on the syntax of the equation, \hl{with only guarded sums.}
@@
 
-\begin{theorem}[\texttt{WEAK_UNIQUE_SOLUTION}]
+\begin{theorem}[\texttt{WEAK_UNIQUE_SOLUTION}, \univariate version of Theorem~\ref{t:Mil89}]
 Let $E$ be guarded and sequential expressions, and let $P \wb
@@
 A delicate point in the formalisation of the results about unique solution of
-contractions are the proof of Lemma~\ref{l:ruptocon} and lemmas alike;
-in particular, there is
- an induction on the length of weak transitions. 
-For this, rather than 
- introducing a refined form of weak transition relation
-enriched with its length, 
-we found it more elegant  to  work with traces
-(a further motivation is to set the ground for extensions of this
-formalisation work to trace equivalence in place of bisimilarity).
+contractions \hl{is} the proof of Lemma~\ref{l:ruptocon} and lemmas alike.
+\hl{In particular, we have do} induction on the length of weak transitions.
+For this, rather than introducing a refined form of weak transition relation
+enriched with its length, we found it more elegant to work with
+\emph{traces}, \hl{i.e. weak transitions with all intermediate actions.}
+(A further motivation is to set the ground for future extensions of this
+formalisation work to \emph{trace equivalence} in place of bisimilarity.)
 
-% but such a non-standard relation finds no
-% other uses beside proving our target theorem. Another way is to use 
-% traces instead, as it shows more clearly all passing actions inside a
-% trace, making formal reasoning easier.
-
-% We represent a trace by the initial process, the final derivative, and
-% the list of actions performed. 
-% To formalise this, 
-% we first introduce 
-% the Reflexive Transitive Closure with a
-% List (LRTC);
-
-A trace is represented by the initial and final processes, plus
+A trace is formally represented by the initial and final processes, plus
 a list of actions so performed.
-For this, we first 
- define the concept of label-accumulated reflexive transitive closure
- (\texttt{LRTC}).
-Given a labeled transition relation \texttt{R} on CCS, \texttt{LRTC R} is
-a label-accumulated relation representing the trace of transitions:
+For this, we first define the concept of \emph{label-accumulated reflexive transitive closure}
+ (\HOLinline{\HOLConst{LRTC}}).
+\hl{Then,} given any labeled transition relation \HOLinline{\HOLFreeVar{R}} (of the type
+``\HOLinline{\ensuremath{\alpha} \HOLTokenTransEnd \ensuremath{\beta} \HOLTokenTransEnd \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}''), \HOLinline{\HOLConst{LRTC} \HOLFreeVar{R}} is
+a relation representing \hl{traces} (of the type
+``\HOLinline{\ensuremath{\alpha} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{list} \HOLTokenTransEnd \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}''):
 \begin{alltt}
@@
 \end{alltt}
-The trace relation for CCS can be then obtained
- by calling \texttt{LRTC} on the (strong, or single-step) labeled transition
- relation \texttt{TRANS} ($\overset{\mu}{\rightarrow}$) defined by SOS rules:
+The trace relation for CCS, \HOLinline{\HOLConst{TRACE}} (of the
+type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTyOp{list} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}''),
+can be then obtained
+ by \hl{combining} \texttt{LRTC} and the \texttt{TRANS}
+ ($\overset{\mu}{\rightarrow}$) relation inductively defined by SOS rules:
 \begin{alltt}
@@
 
-If the list of actions is empty, there is no transition and hence,
-if there is at most one visible action (i.e., a label) in the list of actions,
-then the trace is also a weak transition. Here
-we have to distinguish between two cases: no label and unique label (in
+\hl{Let the trace be $P\overset{acts}{\longrightarrow}Q$.}
+If the list of actions $acts$ is empty, then there is no transition
+actually: the initial and final processes are the same, i.e. $P = Q$.
+\hl{On the other hand, if there is at most one visible action (i.e. a
+label) $\mu$ in $acts$ (all other actions are $\tau$, if they exist),}
+then the trace is actually a weak transition: $P \Arr{\mu} Q$.
+Here we have to distinguish between two cases: no label and unique label (in
 the list of actions). The definition of ``no
-label'' in an action list is easy (here \texttt{MEM} tests if a given element is a member of a list):
+label'' in an action list is easy (here \texttt{MEM} tests if \hl{an} element is a member of a list):
 \begin{alltt}
@@
 The definition of ``unique label'' can be done in many ways. The
-following definition (a suggestion from Robert Beers)
-avoids any counting or filtering in the list.
+following definition (due to a suggestion from Robert Beers)
+avoids any \hl{kind} of counting or filtering in the list.
 It says that a label is unique in a list of actions if and only if there is no
-label in the rest of list:
+label in the rest of list (here $\HOLTokenDoublePlus$ \hl{denotes the concatenation
+of lists}):
 \begin{alltt}
@@
 
-The final relationship between traces and weak transitions is stated
-and proved in the following theorem
-(where the  variable $acts$ stands for
-a list of actions); 
-it says that a weak transition $P\overset{u}{\Rightarrow}P'$ is also a
+\hl{Finally, the connection} between traces and weak transitions is stated
+and proved in the following theorem, \hl{which} says that a weak transition $P \Arr{u} P'$ is also a
 trace $P\overset{acts}{\longrightarrow}P'$ with a
@@
 $u$ is the unique label (for $u \neq \tau$):
-%\begin{lemma}
-% A weak transition $P\overset{u}{\Rightarrow}P'$ is a just trace with non
-% empty action list: 1) without any visible label, if $u = \tau$, or 2)
-% $u$ is the unique label in the list, if $u \neq \tau$.
 \begin{alltt}
@@
 \end{alltt}
-%\end{lemma}
 
@@
 \end{alltt}
-which roughly says that for any context $C$ and weakly-guarded context
-$E$, if $C [\, E^n[P]\,] \overset{xs}{\Longrightarrow} P'$ and the length
-of actions $xs \leqslant n$, then $P'$ has the form of $C'[P]$.
+which roughly says that, for any context $C$ and weakly guarded context
+$E$, if $C [\, E^n[P]\,] \overset{xs}{\longrightarrow} P'$ and the length
+of actions $xs \leqslant n$, then $P'$ has the form $C'[P]$.
 Traces are used in reasoning about the number of intermediate actions in weak

### 2019-12-13 ic-journal/part2.tex
Up to Section 4 (4.12)

@@
   of Theorem~\ref{t:Mil89s1}]
+  \label{thm:Mil89s1f}
 Suppose the expression $E$ contains at most the variable $X$, and let $X$ be weakly
@@
 
-\begin{theorem}[\texttt{OBS_UNIQUE_SOLUTION}, \univariate version of Theorem~\ref{t:Mil89s3}]
+\begin{theorem}[\texttt{OBS_UNIQUE_SOLUTION}, \univariate version of
+  Theorem~\ref{t:Mil89s3}]
+  \label{thm:Mil89s3f}
 Let $E$ be guarded and sequential expressions, and let $P \rapprox
@@
 
-\begin{theorem}[\texttt{WEAK_UNIQUE_SOLUTION}, \univariate version of Theorem~\ref{t:Mil89}]
+\begin{theorem}[\texttt{WEAK_UNIQUE_SOLUTION}, \univariate version of
+  Theorem~\ref{t:Mil89}]
+  \label{thm:Mil89f}
 Let $E$ be guarded and sequential expressions, and let $P \wb
@@
 The formal proof of ``unique solution of rooted contractions theorem''
-(Theorem~\ref{t:rcontraBisimulationU}) has the
-same initial proof steps as Theorem~\ref{t:contraBisimulationU}; 
-it then requires a
+(Theorem~\ref{t:rcontraBisimulationU}, \univariate version) shares the
+same initial proof steps as Theorem~\ref{t:contraBisimulationU}.
+It then requires a
 few more steps to handle rooted bisimilarity in the conclusion. 
-Overall  the
-two proofs are very similar, mostly because the only property we need
-from (rooted) contraction is its precongruence. 
- Below is the formally verified version of
-Theorem~\ref{t:rcontraBisimulationU}
-(having proved
-the precongruence of rooted contraction, 
-we can use  weakly-guarded expressions,   without constraints on  sums;
-that is, \texttt{WG} in place of \texttt{WGS}):
+Overall \hl{speaking}, the two proofs are very similar, mostly because
+the only property \hl{one needed} from (rooted) contraction is the precongruence.
+Below is the formal version of Theorem~\ref{t:rcontraBisimulationU}
+(\texttt{UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS}):
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Q}\hfill{[UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS]}
+\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Q}
 \end{alltt}
 
-Having removed the  constraints on sums, the result is
- similar to Milner's original `unique solution of
-equations' theorem for \emph{strong} bisimilarity ($\sim$)~--- 
-the same weakly guarded context (\texttt{WG}) is required.
+Having proved the precongruence property of rooted contraction ($\rcontr$), 
+now we can use weakly guarded expressions in the above theorem,
+which has no more constraints on summation, that is, having
+\texttt{WG} in place of \texttt{WGS} (cf.~Theorem~\ref{thm:Mil89f}, \texttt{WEAK_UNIQUE_SOLUTION}).
+
+On the other hand, having removed the constraints on \hl{summation}, now
+this result is very similar to Milner's original `unique solution of
+equations' theorem for \emph{strong} bisimilarity ($\sim$) (Theorem~\ref{t:Mil89s1})~--- 
+the same weakly guarded context (\texttt{WG}) is required
+(cf.~Theorem~\ref{thm:Mil89s1f}, \texttt{STRONG_UNIQUE_SOLUTION}).
 In contrast, Milner's ``unique solution of
-equations'' theorem for rooted bisimilarity ($\rapprox$)
-has more rigid constraints, as the variables must be both guarded and sequential.
-%  Theorem~\ref{t:rcontraBisimulationU} can also be seen as a more
-% applicable version of Milner's ``unique solution of
-% equations'' theorem for rooted bisimilarity ($\rapprox$), which has more
-% restrictions on equations.
-% next file: related.tex
+equations'' theorem for rooted bisimilarity ($\rapprox$) (Theorem~\ref{t:Mil89s3}),
+has more rigid constraints, as the \emph{equations} must be both guarded and
+sequential (cf.~Theorem~\ref{thm:Mil89s3f}, \texttt{OBS_UNIQUE_SOLUTION}).
+
+% next file: multivariate.tex

### 2019-12-13 ic-journal/multivariate.tex
Up to Section 5.0

@@
 %%%% -*- Mode: LaTeX -*-
+%%
+%% This is the draft of the 3rd part of IC journal, co-authored by
+%% Prof. Davide Sangiorgi and Chun Tian.
 
@@
 
-In this section,  we discuss the formalisation of the \multivariate
+In this section,  we describe the formalisation of the \multivariate
 cases of Milner's ``unique solution of equations (for $\sim$)''
@@
 contractions'' (Theorem~\ref{t:rcontraBisimulationU}).
+%
 This formalisation supports finitely many
   equations/contractions and equation variables.\footnote{The original theorems
-hold for even  infinitely-many equations and equation variables.}
-We chose these two theorems because of their relevance and 
-because they well illustrate the effort needed for the \multivariate case.
-% Both theorems depend on the same
-% concept of ``weakly guarded contexts'', and Lemma~\ref{lem:milner313}.
-The work is an extension of the \univariate case %~\cite{EPTCS276.10}
- in the sense that neither the CCS datatype nor
-the SOS rules need to be changed.
+hold for even infinitely many equations and equation variables.}
+We chose the two theorems because \hl{they both require the same
+weakly guarded contexts (with minimized efforts)}, and 
+because they well illustrate the \hl{efforts} needed for the \multivariate case.
+The work is a \hl{natural} extension of the \univariate case, as
+\hl{no new algebraic type (e.g. the type for CCS processes) has to be defined,}
+and neither the CCS syntax nor the SOS rules \hl{needs} to be changed.
 
 The central problem of the \multivariate formalisation is the
-representation of CCS equations (expressions, contexts).
-In the \univariate formalisation, $\lambda$-functions (of type
-$CCS\rightarrow CCS$) are used to represent \univariate CCS
+representation of \multivariate CCS equations (expressions and contexts).
+In the \univariate case, $\lambda$-functions
+are used for representing \univariate CCS
 equations, and variable substitutions are simply 
-calls to $\lambda$-functions on the target CCS terms.
-This idea cannot be extended to the \multivariate case, as
-we do not have a fixed number of variables to deal with.
+\hl{applications of} $\lambda$-functions to CCS terms \hl{as substitutions}.
+This idea (i.e. \multivariate $\lambda$-functions), however,
+cannot be extended to \hl{support} the \multivariate case of
+unique-solution theorems, as we do not have a fixed number of variables to deal with.
 
-In the  literature the variables  $X_i$ of
+In the literature (\citep[p.~102]{Gorrieri:2015jt}, e.g.), the variables $X_i$ of
 a system of equations $\{X_i = E_i\}_{i\in I}$ are usually considered as
-equation variables
-\emph{outside} of the CCS syntax; then an equation body  $E_i$  is an \emph{open} expression
-built with CCS operators plus the equation variables.
-For a formal point of view, this means we either need to define a
+\hl{separate} \emph{process variables} outside the CCS syntax.
+Then, an equation body  $E_i$  is an \emph{open} expression
+built with CCS operators plus these equation variables.
+For a formal point of view, this means \hl{that} we either need to define a
 whole new datatype (with extra equation variables) in which each CCS
 operator must be duplicated, or we have to add equation variables as a
-new primitive (e.g.~\texttt{Var X}) to the existing CCS type (besides
-the agent variables such as  \texttt{var X}).
- Then the substitution of equation
-variables in $E_i\{\til P/\til X\}$ would be the \emph{syntactic substitution} of
-each occurrence of $X_i$ in $E_i$ with the corresponding $P_i$.
+new primitive (e.g.~\texttt{Var X}) to the existing CCS type in addition
+to the agent variables such as \texttt{var X}.
+(Then the substitution of equation
+variables in $E_i\{\til P/\til X\}$ would become the \emph{syntactic substitution} of
+each occurrence of $X_i$ in $E_i$ with the corresponding $P_i$.)
 In either cases the \emph{disjointness} between equation variables and
@@
 guaranteed. Both solutions are rather combersome, and require a non-trivial modification
-of the formalisation of the \univariate case.
+of the existing \univariate formalisation.
 
-In this project, we have followed Milner~\cite{Mil89}, using the
-same alphabet for both agent variables and equation variables.
-This has allowed a large reuse of the \univariate formalisation.
-For instance, the variable
-substitution function used in SOS rules \texttt{REC} can be also
-used for substituting equation variables.
+In this project, we have followed Milner's original
+approach~\cite{milner1990operational}, using the
+\emph{same} alphabet for both agent variables and equation variables.
+This \hl{approach allows} a large reuse of the \univariate formalisation.
+For instance, the variable substitution \hl{occurred in SOS rule}
+\texttt{REC} can be reused for substituting equation variables.
 However, a lot of care is needed in the proofs of many
 fundamental lemmas, mostly due to the variable capture issues between
-equation variables and agent variables.
-
-% which is also the most elegant way: reusing \emph{free} agent variables
-% (i.e. undefined constants) as equation variables, then the variable
-% substitution function used in SOS rules [\texttt{REC}] can be also
-% used for substituting eqaution variables.
-% However, this approach brings us great difficulities in proving many
-% fundamental lemmas, mostly due to the variable capture issues between
-% equation variables and agent variables.
+equation variables \hl{(free)} and agent variables \hl{(bound)}.
 
@@
 As mentioned at the beginning of Section~\ref{s:eq},
- an agent variable may occur outside the recursion in which it is bound;
-i.e., a variable can appear both \emph{bound} and \emph{free} in a term.
-
+within our CCS syntax an agent variable may occur outside the recursion in which it is bound.
+\hl{Thus the same} variable can appear both \emph{bound} and \emph{free} in
+a CCS term.
+%
 We denote the set of bound variables of a

### 2019-12-13 ic-journal/part2.tex
Up to Section 5.0

@@
 the only property \hl{one needed} from (rooted) contraction is the precongruence.
-Below is the formal version of Theorem~\ref{t:rcontraBisimulationU}
-(\texttt{UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS}):
+Below is the formal version of Theorem~\ref{t:rcontraBisimulationU}:
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Q}
+\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Q}\hfill{[UNIQUE_SOLUTION_OF_ROOTED_CONTRACTIONS]}
 \end{alltt}
@@
 which has no more constraints on summation, that is, having
-\texttt{WG} in place of \texttt{WGS} (cf.~Theorem~\ref{thm:Mil89f}, \texttt{WEAK_UNIQUE_SOLUTION}).
+\texttt{WG} in place of \texttt{WGS} (cf.~\texttt{UNIQUE_SOLUTION_OF_CONTRACTIONS}).
 

### 2019-12-13 ic-journal/multivariate.tex
Up to Section 5.1

@@
 
-In this section,  we describe the formalisation of the \multivariate
-cases of Milner's ``unique solution of equations (for $\sim$)''
+\hl{Our goal in this last part of the CCS formalisation are two formally
+verified theorems, which dwarf all previous results in this project:}
+the general (\multivariate) cases of
+Milner's ``unique solution of equations (for $\sim$)''
 (Theorem~\ref{t:Mil89s1}) and our ``unique solution of rooted
@@
 because they well illustrate the \hl{efforts} needed for the \multivariate case.
-The work is a \hl{natural} extension of the \univariate case, as
+The work is a \hl{natural} extension of the existing work, for
 \hl{no new algebraic type (e.g. the type for CCS processes) has to be defined,}
@@
 within our CCS syntax an agent variable may occur outside the recursion in which it is bound.
-\hl{Thus the same} variable can appear both \emph{bound} and \emph{free} in
-a CCS term.
+\hl{Thus the same} variable can appear both \emph{free} and \emph{bound} in a CCS term.
 %
@@
 type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}'', i.e.
-functions taking CCS terms and returning sets of
-variables (of type \HOLinline{\ensuremath{\alpha}}).
+functions taking CCS terms and returning
+\hl{(finite)} sets of variables (of the type \HOLinline{\ensuremath{\alpha}}).
 % Milner didn't give their definitions explicitly. However, one can
@@
 
-The set of free and bound
-variables of a term need not be disjoint, e.g.~in $X + \recu X E$.
+The set of free and \hl{the set of} bound
+variables of a term need not \hl{to} be disjoint, e.g.~in $X + \recu X E$.
 More importantly, when going
@@
 $\fv{\mu.X} = \{X\}$. This property of $\fv{\cdot}$ brings some
-difficulities when doing proofs about CCS transitions. As an evidence,
-we prove the following fundamental result about $\fv{\cdot}$\hl{\mbox{~\citep[p.~1209]{milner1990operational}}}:
-
+difficulities when doing \hl{transition inductions}. As an evidence,
+we prove the following fundamental property of
+$\fv{\cdot}$~\citep[p.~1209]{milner1990operational}:
+%
 \begin{proposition}
@@
 \begin{proof}
-We actually prove a stronger result, asserting that the set of free
-variables in a CCS process may decrease through its derivatives:
+We actually proved a stronger result, asserting that the set of free
+variables in a CCS process \hl{\emph{never increases}} through its derivatives:
 \begin{alltt}
@@
 
-In textbooks such as~\cite{Mil89}, the proof of the above property is 
-commented as  ``an easy action induction''.
-\hl{The actual proof in HOL is not that trivial}:
+In~\cite{milner1990operational}, the proof of the above property is 
+commented by  ``an easy action induction''.
+\hl{However, the actual proof (in HOL) is not that trivial}:
  ``action induction'' (or \emph{transition induction}) becomes a form of higher-order application
-of the following \emph{induction principle}, generated together with the SOS
-rules (and that essentially says that \HOLinline{\HOLConst{TRANS}} is the smallest relation
-satisfying the SOS rules):
+of the following \emph{induction principle} (generated together with the SOS
+rules), which essentially says that \HOLinline{\HOLConst{TRANS}} is the smallest relation
+satisfying the SOS rules:
 \begin{alltt}
@@
 \end{alltt}
-The above long theorem has the form \HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLBoundVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}} (with $a_0, a_1, a_2$ renamed), where the
+The above long theorem has the form \HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLBoundVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}} (with $a_0, a_1, a_2$ renamed), \hl{where} the
 outermost universal quantifier $P$ is a higher-order
-proposition (about $E$, $\mu$ and $E'$), and $X$ is another higher-order
-proposition about $P$.
-What we are trying to prove is actually in the form of
+proposition (\hl{taking} $E$, $\mu$ and $E'$), while $X$ is another higher-order
+proposition \hl{containing} $P$.
+\hl{Our proof goal} is actually in the form of
 \HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLFreeVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}}, where
@@
 Proposition~\ref{prop:transFV} is essential in the proofs of the
-  multivariable versions of all unique-solution
-  theorems.
-In comparison with the above proof, the proof of the analogous
-result for bound variables is easier:
+  \multivariate versions of all unique-solution theorems.
+On the other hand, the analogous
+result for bound variables is indeed just an easy transition
+induction. (The easy proof is omitted.)
 \begin{proposition}
@@
 \end{proposition}
-\begin{proof}
-Following the proof of Proposition~\ref{prop:transFV}, we do action
-induction on $E \arr{\mu} E'$ and simplify all subgoals by set-theoretic
-facts. The only subgoal left is:
-\begin{alltt}
-        \HOLinline{\HOLConst{BV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLFreeVar{X} \HOLConst{INSERT} \HOLConst{BV} \HOLFreeVar{E}}
-   ------------------------------------
-    0.
+% \begin{proof}
+% Following the proof of Proposition~\ref{prop:transFV}, we do action
+% induction on $E \arr{\mu} E'$ and simplify all subgoals by set-theoretic
+% facts. The only subgoal left is:
+% \begin{alltt}
+%         \HOLinline{\HOLConst{BV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLFreeVar{X} \HOLConst{INSERT} \HOLConst{BV} \HOLFreeVar{E}}
+%    ------------------------------------
+%     0.
 \HOLinline{\HOLConst{BV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
-\end{alltt}
-Note the difference with the proof of Proposition~\ref{prop:transFV}: now
-we have \texttt{INSERT} in place of \texttt{DELETE}. Then, we directly
-use the assumption and the transitivity of $\subseteq$ and try to
-prove the following goal instead:
-\begin{alltt}
-        \HOLinline{\HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLFreeVar{X} \HOLConst{INSERT} \HOLConst{BV} \HOLFreeVar{E}}
-   ------------------------------------
-    0.
+% \end{alltt}
+% Note the difference with the proof of Proposition~\ref{prop:transFV}: now
+% we have \texttt{INSERT} in place of \texttt{DELETE}. Then, we directly
+% use the assumption and the transitivity of $\subseteq$ and try to
+% prove the following goal instead:
+% \begin{alltt}
+%         \HOLinline{\HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLFreeVar{X} \HOLConst{INSERT} \HOLConst{BV} \HOLFreeVar{E}}
+%    ------------------------------------
+%     0.
 \HOLinline{\HOLConst{BV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
-\end{alltt}
-This is an easy goal, due to the following lemma which is
- proved by \hl{doing} induction on $E$:
-\begin{alltt}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+% \end{alltt}
+% This is an easy goal, due to the following lemma which is
+%  proved by \hl{doing} induction on $E$:
+% \begin{alltt}
+% \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
 \HOLConst{BV} \ensuremath{(}\ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\hfill{[BV_SUBSET]}
-\end{alltt}
-Taking $E ' = \recu X E$ in the above lemma, we have
-    \HOLinline{\HOLConst{BV}\\\;\ensuremath{(}\ensuremath{[}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\HOLSymConst{\HOLTokenSubset{}}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}\\\;\HOLConst{BV}\\\;\ensuremath{(}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{)}},
-    the right side equals to \HOLinline{\HOLConst{BV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}\\\;\ensuremath{(}\HOLFreeVar{X}\\\;\HOLConst{INSERT}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}} $=$
-    \HOLinline{\HOLFreeVar{X}\\\;\HOLConst{INSERT}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}}.
-This completes the proof.
-\end{proof}
+% \end{alltt}
+% Taking $E ' = \recu X E$ in the above lemma, we have
+%     \HOLinline{\HOLConst{BV}\\\;\ensuremath{(}\ensuremath{[}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\HOLSymConst{\HOLTokenSubset{}}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}\\\;\HOLConst{BV}\\\;\ensuremath{(}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{)}},
+%     the right side equals to \HOLinline{\HOLConst{BV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}\\\;\ensuremath{(}\HOLFreeVar{X}\\\;\HOLConst{INSERT}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}} $=$
+%     \HOLinline{\HOLFreeVar{X}\\\;\HOLConst{INSERT}\\\;\HOLConst{BV}\\\;\HOLFreeVar{E}}.
+% This completes the proof.
+% \end{proof}
 

### 2019-12-13 ic-journal/part2.tex
Up to Section 5.1

@@
 Overall \hl{speaking}, the two proofs are very similar, mostly because
-the only property \hl{one needed} from (rooted) contraction is the precongruence.
+the only property needed from \hl{contraction and rooted contraction is their} precongruence.
 Below is the formal version of Theorem~\ref{t:rcontraBisimulationU}:

### 2019-12-13 ic-journal/multivariate.tex
Up to Section 5.2

@@
 is completed.
-Now, the goal can be reduced to several conjunct
+Now the goal can be reduced to several conjunct
 subgoals, each corresponding to one SOS rule. For instance, in
@@
 
-There are two ways to represent the \multivariate
-substitution $E\{\til P/\til X\}$, that replaces each \hl{free
-occurrence} of variables $X_i$ in $E$ with the corresponding
+There are two (obvious) ways to \hl{do} % not "represent" but actually "do"
+the \multivariate substitution $E\{\til P/\til X\}$, \hl{which} replaces each \hl{free
+occurrence} of the variables $X_i$ in $E$ with the corresponding
 $P_i$: (1) iterately applying the existing \univariate
 \HOLinline{\HOLConst{CCS_Subst}}; (2) defining a new \multivariate substitution
-function.
-% In any case, we (reasonably) assume that all $X_i$ are
-%distinct with each other. 
+function which substitutes all variables $\til X$ in parallel.
 Note that there is the
@@
 different orders of iterated substitutions may lead to different results.
-% In fact, there are all kinds of issues with
-% substitutions and applying them to term-like structures. 
-To obtain the
-maximal flexibility with a reduced effort, we defined
+To obtain the maximal flexibility with reduced efforts, we defined
 a \multivariate version of \HOLinline{\HOLConst{CCS_Subst}}
-called \HOLinline{\HOLConst{CCS_SUBST}} based HOL's \texttt{finite\_map} theory~\cite{holdesc}.
+called \HOLinline{\HOLConst{CCS_SUBST}}, based \hl{on} HOL
+\texttt{finite\_map} theory~\cite{holdesc}.
 
-A finite map of type \HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{\beta}} is like a function of type
-\HOLinline{\ensuremath{\alpha} \HOLTokenTransEnd \ensuremath{\beta}} having only finitely many elements in its
+A finite map (of the type \HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{\beta}}) is like a function (of the type
+\HOLinline{\ensuremath{\alpha} \HOLTokenTransEnd \ensuremath{\beta}}) having only finitely many elements in its
 domain. In HOL, an empty finite map is denoted as \HOLinline{\HOLConst{FEMPTY}}.
@@
 The function \HOLinline{\HOLConst{CCS_SUBST}} takes a finite
-map \HOLinline{\HOLFreeVar{fm}} of type \HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}} and a CCS expression,
+map \HOLinline{\HOLFreeVar{fm}} (of the type \HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}) and a CCS expression,
 and returns another CCS expression in which
-all occurrences of variables in \HOLinline{\HOLFreeVar{fm}} domain are substituted with
-the corresponding value in \HOLinline{\HOLFreeVar{fm}}. Such a finite map can be built from
-the list of variables \HOLinline{\HOLFreeVar{Xs}} and the corresponding targets
-\HOLinline{\HOLFreeVar{Ps}} by a helper function \HOLinline{\HOLConst{fromList}} (whose details are
-omitted here), while
-\HOLinline{\HOLConst{CCS_SUBST}\\\;\ensuremath{(}\HOLConst{fromList}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Ps}\ensuremath{)}\\\;\HOLFreeVar{E}} is
+all occurrences of variables in \hl{the finite domain of} \HOLinline{\HOLFreeVar{fm}} are substituted with
+the corresponding value in \HOLinline{\HOLFreeVar{fm}}. \hl{Initially,} such a finite map can be built from
+a list of variables \HOLinline{\HOLFreeVar{Xs}} and the corresponding substituted terms
+\HOLinline{\HOLFreeVar{Ps}} by a helper function \HOLinline{\HOLConst{fromList}} (\hl{defined by us, and} whose details are
+omitted here).
+\HOLinline{\HOLConst{CCS_SUBST}\\\;\ensuremath{(}\HOLConst{fromList}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Ps}\ensuremath{)}\\\;\HOLFreeVar{E}} is usually
 abbreviated as \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}.
-The substitution mechanism is order-independent. For most CCS operators it
-just recursively calls itself on subterms. The only
+The substitution mechanism is order-independent, \hl{as there is no
+ordering in finite maps.} For most CCS operators it
+just recursively calls itself on subterms, \hl{while the} only
 interesting cases are at agent variables and recursion:
@@
 Variable substitution only occurs on free
-variables. In the case of $\recu X E$: if $X$ (a bound variable) is in
+variables. When the term $E$ of ``\HOLinline{\HOLConst{CCS_SUBST}\\\;\HOLFreeVar{fm}\\\;\HOLFreeVar{E}}''
+is in the form of $\recu X E'$, if $X$ (a bound variable) is in
 the domain of \HOLinline{\HOLFreeVar{fm}}, \HOLinline{\HOLConst{CCS_SUBST}} must continue the
-substitution on $E$ using a reduced map~--- without $X$~--- so that all
-occurences of $X$ in $E$ are correctly bypassed.
+substitution on $E'$ using a reduced map~--- without $X$~--- so that all
+occurences of $X$ in $E'$ are correctly bypassed.
 Since \HOLinline{\HOLConst{CCS_SUBST}} only runs
@@
  substituted.
-% Thus the process is indeed
-% order-independent. 
+
 Below we present some key lemmas about
@@
 
-In the above lemmas, the condition
+In \hl{some of} the above lemmas, the condition
 \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}} (the bound
 variables of $E$ and the free substitution variables are disjoint) is
-not necessary but makes some proofs easier. 
-As these lemmas are
-used in the rest work, such disjointness conditions 
-are propagated everywhere. 
-% (We believe that they can be
-% all eliminated in the future.)
+added to ease the related proofs. This disjointness requirement
+is not necessary \hl{and (in theory) can be all eliminated with more efforts.}
+\hl{As many of these lemmas are used in proving other theorems, eventually}
+the disjointness condition are propagated everywhere.
 
@@
 guarded companions are defined as predicates over $\lambda$-expressions
-of type $CCS\rightarrow CCS$. These predicates, such as
+of the type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}''.
+These predicates, such as
 \HOLinline{\HOLConst{CONTEXT}}

### 2019-12-13 ic-journal/multivariate.tex
Up to Section 5.3

@@
 \HOLinline{\HOLConst{CONTEXT}}
-(contexts/expressions), \HOLinline{\HOLConst{WG}} (weak guarded contexts),
+(\hl{multi-hole} contexts), \HOLinline{\HOLConst{WG}} (weak guarded contexts),
 \HOLinline{\HOLConst{SG}} (guarded contexts) and \HOLinline{\HOLConst{SEQ}} (sequential
-contexts), are defined inductively, i.e.~they are built from some ``holes''
-in a bottom-up way.
+contexts), are \hl{all} defined inductively, i.e.~they are built from some ``holes''
+in a bottom-up \hl{manner}.
 For instance, \HOLinline{\HOLConst{WG}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\\\;\HOLSymConst{\ensuremath{\mid}}\\\;\HOLFreeVar{P}\ensuremath{)}}
@@
 
-It is possible to inductively assert \multivariate contexts and their
-guarded variants, but care is needed as  we need to exclude the cases where
-free variables occur inside a recusion operator. A more elegant
- solution is to define \multivariate contexts (and variants) upon the
-existing \univariate definitions, which is the approach we have followed.
+\hl{In theory}, it is possible to inductively assert \multivariate contexts and their
+guarded variants, but care is needed as we \hl{have} to exclude the cases where
+free variables occur \hl{within recusion}.  \hl{Here we choose} a more elegant
+ solution, which defines \multivariate contexts (and variants) upon the
+ existing \univariate definitions.
+\hl{The core idea is that, whenever we replace a variable by a hole and view
+the other variables as constants, this is a single variable context
+that can be asserted by predicates like} \HOLinline{\HOLConst{CONTEXT}}.
 For example, to see the weak guardedness of $a.X + b.X + c.Y$, it is
@@
 allows us to formalise the concepts of contexts and guardedness
-independently of \HOLinline{\HOLConst{FV}}.
-Then \HOLinline{\HOLConst{weakly_guarded}\\\;\ensuremath{(}\HOLConst{SET_TO_LIST}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\ensuremath{)}\\\;\HOLFreeVar{E}} can
-be used assert that $E$ is weakly guarded w.r.t.~all its free
+independently of the free variables of \HOLinline{\HOLFreeVar{E}}.
+Then a logical term ``\HOLinline{\HOLConst{weakly_guarded}\\\;\ensuremath{(}\HOLConst{SET_TO_LIST}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\ensuremath{)}\\\;\HOLFreeVar{E}}'' can
+be used \hl{to} assert the weak guardedness of $E$ w.r.t.~all its free
 variables.\footnote{Here \HOLinline{\HOLConst{SET_TO_LIST}} converts a finite set
@@
   \HOLinline{\HOLFreeVar{Xs}}.}
-(Guardedness and sequentiality can also be defined similarily, using
-their \univariate companions \HOLinline{\HOLConst{SG}} and \HOLinline{\HOLConst{SEQ}}.)
+(The \multivariate guardedness and sequentiality can also be defined similarily, using
+their \univariate companions \HOLinline{\HOLConst{SG}} and \HOLinline{\HOLConst{SEQ}}, \hl{but so far
+they are not defined.})
 
-The most important property of contexts are that, strong bisimilarity
-and other (pre)congruence relations are preserved by contexts, e.g.
+The most important property of \multivariate contexts is that, strong bisimilarity
+and other (pre)congruence relations are preserved by them, for instance:
 \begin{lemma}[\texttt{STRONG_EQUIV_subst_context}]
@@
 The similar properties also hold if $\sim$ is replaced with rooted
-bisimilarity ($\rapprox$) or rooted contraction ($\rcontr$). (It does
-not hold for weak bisimilarity $\wb$ and the contraction preorder $\mcontrBIS$.)
+bisimilarity ($\rapprox$) \hl{and} rooted contraction ($\rcontr$). It does
+not hold, however, for weak bisimilarity ($\wb$) and the contraction
+preorder ($\mcontrBIS$), \hl{as they are not (pre)congruence
+w.r.t.}~\HOLinline{\HOLConst{context}}.
 
 Another important property of contexts is their composability: if we
-substitute some free variables in a context for some other contexts, the
-resulting term is still a context (w.r.t.~the same set of variables):
+substitute some free variables in a context \hl{to} some other contexts, the
+resulting term is still a \hl{valid} context (w.r.t.~the same set of variables):
 \begin{alltt}
@@
 
-Not every expression from the CCS syntax is a context, as 
-context variable may not within a recusion. Trivially,
- if the set of free variables of an expression
-is disjoint from a list of variables, then the expression is a context:
+On the other hand, not every term within the CCS syntax is a context, as 
+\hl{context (or equation) variables are not allowed to occur within recursion. The converse
+holds however:} if the set of free variables of an CCS term
+is disjoint from a list of variables, then the term is indeed a context
+w.r.t. the same list of variables:
 \begin{alltt}
@@
 On the other hand, for any context (w.r.t.~$\til X$) of the form $\recu Y E$,
-the set of free variables of $E$ excluding $Y$ is
-disjoint from $\til X$, i.e.
+the set of free variables of $E$ excluding $Y$ is disjoint with $\til X$:
 \begin{alltt}
@@
 \end{alltt}
-In the above result we cannot
+Note that, in the above lemma we cannot
 conclude \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}}, because $Y$ as a bound
@@
 also cannot conclude \HOLinline{\HOLConst{context}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{E}}, because in $\recu Y E$
-it is possible that the bound variable $Y$ occurs inside another
-recursion operator, and then it is a free variable for $E$ (as in $\recu Y
+it is possible that the bound variable $Y$ occurs with another \hl{nested}
+recursion, and then it is free in $E$ (as in $\recu Y
 (\recu Z (a.Y + b.Z) + c.Y)$).
 
-For weakly-guarded contexts (which are also normal contexts), beside
+For weakly guarded contexts (which are also normal contexts), beside
 their regular properties (i.e. weak
@@
 their composability w.r.t.~\multivariate contexts: if we
-substitute some free variables in a context $C$ for some weakly-guarded
-contexts the resulting term is weakly-guarded (w.r.t.~the same set of variables):
+substitute some free variables in a context $C$ to some weakly guarded
+contexts, the resulting \hl{context becomes} weakly guarded (w.r.t.~the same set of variables):
 \begin{alltt}
@@
 With the formal definitions of \multivariate substitution and
-\multivariate (weakly-guarded) contexts, now we are ready to formally
+\multivariate (weakly guarded) contexts, now we are ready to formally
 define \multivariate CCS equations/contractions and their (unique)

### 2019-12-13 ic-journal/multivariate.tex
Done, it remains to shorten the proof of TRANS_FV

@@
 holds however:} if the set of free variables of an CCS term
-is disjoint from a list of variables, then the term is indeed a context
+is disjoint with a list of variables, then the term is indeed a context
 w.r.t. the same list of variables:
@@
 \end{itemize}
-Obviously the two lists must have the same length. 
-% The all
-% distinctness of $\til X$ is not really necessary but is very
-% reasonable. 
-Furthermore, we should assume that $\til E$ does not contain
- free variables not in $\til X$.
-% , as Milner's unique-solution
-% theorems also require the same condition.
-% \footnote{One may think that,
-%   if all other (i.e.~not in $\til X$) free variables in $\til E$ have
-%   the same functionalities as $\nil$ as they are not to be
-%   substituted, then all versions of unique-solution
-%   theorems should still hold. However this is not the case for at
-%   least Milner's Theorem~\ref{t:Mil89s1} as we shall explain.}
-The only optional condition we have added is that, for each
-$E_i$, the set of its bound variables must be \emph{disjoint} from $\til X$.
-% This restriction is actually aligned with literature based on
-% process constants as one should never use the same name for equation
-% variables and constants. However, we believe this restriction can be
-% removed in the future.~
-\footnote{Essentially, this condition is due
-  to  some early lemmas about \multivariate
-  substitutions where \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}}
- appears in the antecedents. Removing this would require 
-  more complex proofs.
-% (We have succeeded in
-%   fixing many such lemmas.) Once all these lemmas are
-% fixed, the final unique-solution theorems also do not need this
-% disjointness restriction.
-} 
-Putting all together, below is the fomal
+Obviously the two lists $\til X$ and $\til E$ must have the same
+length, and in practice the variables in $\til X$ should be all distinct.
+Furthermore, we assume that $\til E$ does not contain
+ free variables that are not in $\til X$, i.e. each $E_i$ contains
+ variables up to $\til X$.
+\hl{Finally, the only extraordinary hypothesis} is that, for each
+$E_i$, the set of its bound variables must be \emph{disjoint} with
+$\til X$. \hl{(In practice, however, one can always
+rename all recursion binders in the equations to satisfy this
+requirement without changing the semantics of equations.)}
+Putting all requirements together, below is the fomal
 definition of \multivariate CCS equation:
@@
 all, the definition should be parametrized on a binary CCS
-relation $\R$ such as $\sim$ and $\rcontr$, so that the single definition
-could be used for the solution of all kinds of CCS
-equations/contractions. Then, of course ${\til P} \ \R\  {\til E}\{\til
-P/\til X\}$ must hold, i.e.
+relation $\R$ such as $\sim$ and $\rcontr$, so that a single definition
+can be used to represent solutions of all kinds of CCS
+\hl{equations and inequations.} Then, of course ${\til P} \ \R\  {\til E}\{\til
+P/\til X\}$ must hold:
 \begin{equation*}
@@
 \end{equation*}
-Furthermore, each $P_i$ should be a pure process, i.e. having no free
+Furthermore, each $P_i$ should be a pure process, i.e.~having no free
 variable.
@@
 the set of bound variables %(i.e. process constants) 
-must be disjoint from
+must be disjoint with
 $\til X$ (this disjointness requirement is optional but makes many proofs
@@
 \end{alltt}
-Note that, in HOL, \HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}\\\;\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenEquiv{}}\\\;\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenIn{}}\\\;\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}.
-The form in the right-hand side suggests that,
-\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}} is actually a set containing all
-solutions (of \HOLinline{\HOLConst{CCS_equation}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}). Then the unique-solution
-theorems can be understood thus: any two (syntactically different) elements
+Note that, in HOL, the two logical terms ``\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}\\\;\HOLFreeVar{Ps}}'' and ``\HOLinline{\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenIn{}}\\\;\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}'' have the same meaning
+(w.r.t.~\texttt{pred_set} theory). The latter form suggests that,
+``\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}'' is actually a set containing all
+solutions (of ``\HOLinline{\HOLConst{CCS_equation}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}''). Then the unique-solution
+theorems can be understood in this way: any two (syntactically different) elements
 in the set are bisimilar.
@@
 
-With the above machinery about \multivariate contexts and substitutions,
-the \multivariate case of Lemma~\ref{lem:milner313} is formalised
-below:
+With all above machineries of \multivariate contexts and substitutions,
+the \multivariate case of Lemma~\ref{lem:milner313} is formalised below:
 \begin{alltt}
@@
 
-And the \multivariate version of Theorem~\ref{t:rcontraBisimulationU}:
+\hl{So is} the \multivariate version of Theorem~\ref{t:rcontraBisimulationU}:
 \begin{alltt}
@@
 step related to \multivariate substitutions is more difficult than
-the \univariate case, the entire proofs still follow the same outline,
-and many proof scripts can be directly copied from their \univariate version.
+the \univariate case, the entire proofs still follow the same \hl{outlines}.
+and many proof \hl{steps} can even be copied from their \univariate \hl{companions}.

### 2019-12-13 ic-journal/response-letter2.tex
Up to Section 5.3
Processed the rest questions from the reviewer. Giving up shortening TRANS_FV

@@
   \Mark 
-We have reformulated, trying to highlight its (possible) interest.
-% Milner said it can be proven by ``an easy action induction''.
-%              It is actually not that easy, and we take this chance to
-%              illustrate how to apply ``action induction'' in HOL.
-%              (TODO) 
-The proof has also been now shortened, according to the
-             latest updates in the HOL formalisation.
+We have reformulated, trying to highlight its (possible)
+interests. The (easy) proof of the other proposition (5.2), has been removed.
 
@@
 \end{quote}
-  \Mark
+  \Mark We consider the (informal) explanation as statements of the
+  lemma, and the formal code a more rigorous representation. This
+  convention has been used across the whole paper. It's only on this
+  page that we put too many (small) lemmas together.
 
@@
 \end{quote}
-  \Mark
+  \Mark We have put this sentence into the paper. Thanks.
 
-  \item \begin{quote}
-1165: "used *to* assert"
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 1165: "used *to* assert"
+% \end{quote}
+%   \Mark
 
-  \item \begin{quote}
-1169 add colon after e.g.
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 1169 add colon after e.g.
+% \end{quote}
+%   \Mark
 
-  \item \begin{quote}
-1171 add "then" after the comma 
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 1171 add "then" after the comma 
+% \end{quote}
+%   \Mark
 
-  \item \begin{quote}
-1175 "The similar properties" => "Similar properties"
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 1175 "The similar properties" => "Similar properties"
+% \end{quote}
+%   \Mark Fixed.
 
-  \item \begin{quote}
-1182 "Not every expression fit with CCS syntax " ?
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 1182 "Not every expression fit with CCS syntax " ?
+% \end{quote}
+%   \Mark
 
-  \item \begin{quote}
-1210 "optional restriction" ?
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 1210 "optional restriction" ?
+% \end{quote}
+%   \Mark
 
-  \item \begin{quote}
-1219 "that, the set" remove comma; also "must be disjoint" => "is disjoint"
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 1219 "that, the set" remove comma; also "must be disjoint" => "is disjoint"
+% \end{quote}
+%   \Mark
 
-  \item \begin{quote}
-1241 "while Milner did not pointed out explicitly," grammar
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 1241 "while Milner did not pointed out explicitly," grammar
+% \end{quote}
+%   \Mark
 
-  \item \begin{quote}
-1293 " for people who can read them" sounds a bit strange; also the last sentence of the paragraph suggest most people could
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 1293 " for people who can read them" sounds a bit strange; also the last sentence of the paragraph suggest most people could
+% \end{quote}
+%   \Mark
 
-  \item \begin{quote}
-1293-1294 "For some other textbook proofs (..) formalisation work." perhaps give a pointer to an instance where this was the case?
-\end{quote}
-  \Mark
+%   \item \begin{quote}
+% 1293-1294 "For some other textbook proofs (..) formalisation work." perhaps give a pointer to an instance where this was the case?
+% \end{quote}
+%   \Mark
 

### 2019-12-13 ic-journal/conclusions.tex
Processed the rest questions from the reviewer. Giving up shortening TRANS_FV

@@
 
-The formalisation has focused on the theory of
-unique solution of equations and contractions, both in the \univariate and
-in the \multivariate cases. It
- has allowed us to further develop the theory,
+The formalisation has focused on the theory of unique solution of
+equations and contractions, both in the \univariate and in the
+\multivariate cases. It has allowed us to further develop the theory,
 notably the basic properties of rooted contraction, and the unique
-solution theorem for it with respect to rooted bisimilarity. 
-The formalisation brings up and exploits similarities between results
-and proofs for different equivalences and preorders. Indeed we have
-considered several ``unique-solution'' results (for various equivalences
-and preorders); they share many parts of the proofs, but present a few
-delicate and subtle differences in a few points. In a paper-pencil
-proof, checking all details would be long and error-prone,
-especially in cases where the proofs are similar to each other or
-  when there are long case analyses to be carried out.
-% \hl{Some of the textbook proofs were even wrong and the correct version is
-% known but not available in the literature. This is the case of Milner's
-% proof of the unique-solution theorem for $wb$}
-% (Theorem~\ref{t:Mil89s3}). \hl{Now we have fully verified formal proofs for
-% people who can read them.}
-% For some other textbook proofs, even they are correct, sometimes they actually
-% do not need all information from the antecedents, which can be further
-% weakened. This kind of improvements can be easily found during the
-% formalisation work.
-%For our CCS formalisation, 
-We believe that the formalisation of  all definitions and
-theorems are easy to read and
-to understand, as they are close to their original statement in
-textbooks.
+solution theorem for it with respect to rooted bisimilarity.  The
+formalisation brings up and exploits similarities between results and
+proofs for different equivalences and preorders. Indeed we have
+considered several ``unique-solution'' results (for various
+equivalences and preorders); they share many parts of the proofs, but
+present a few delicate and subtle differences in a few points. In a
+paper-pencil proof, checking all details would be long and
+error-prone, especially in cases where the proofs are similar to each
+other or when there are long case analyses to be carried out.  We
+believe that the formalisation of all definitions and theorems are
+easy to read and to understand, as they are close to their original
+statement in textbooks.
 
-For future work, formalising other equivalences and preorders could also be considered,
-notably trace-based equivalences, as well as more refined process
-calculi such as value-passing CCS.
+For some future work, formalising other equivalences and preorders
+could also be considered, notably trace-based equivalences, as well as
+more refined process calculi such as value-passing CCS.
 %
@@
 %
-The paper was written in memory of Michael J.~C.~Gordon, the creator of the HOL theorem prover.
+The paper was written in memory of Michael J.~C.~Gordon (1948--2017),
+the creator of the HOL theorem prover.

### 2019-12-13 ic-journal/multivariate.tex
Processed the rest questions from the reviewer. Giving up shortening TRANS_FV

@@
  existing \univariate definitions.
-\hl{The core idea is that, whenever we replace a variable by a hole and view
+\hl{The idea is that, whenever we replace a variable by a hole and view
 the other variables as constants, this is a single variable context
@@
   means that two lists of CCS processes are componentwise
-  (strongly) bisimilar.}, then
-for any context $E$
-% with the possible occurrences of variables $\til X$
-% (same length as $\til P$ and $\til Q$),
-also $E\{\til P/\til X\}$ and
+  bisimilar ($P_i \sim Q_i$).}, then
+for any context $E$, $E\{\til P/\til X\}$ and
 $E\{\til Q/\til X\}$ are strongly bisimilar:
@@
 \end{lemma}
-The similar properties also hold if $\sim$ is replaced with rooted
+%
+Similar properties also hold if $\sim$ is replaced with rooted
 bisimilarity ($\rapprox$) \hl{and} rooted contraction ($\rcontr$). It does
@@
 also cannot conclude \HOLinline{\HOLConst{context}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{E}}, because in $\recu Y E$
-it is possible that the bound variable $Y$ occurs with another \hl{nested}
-recursion, and then it is free in $E$ (as in $\recu Y
-(\recu Z (a.Y + b.Z) + c.Y)$).
+the bound variable $Y$ \hl{may occur \emph{freely} within another nested}
+recursion, and then it is free in $E$. \hl{For instance,} $\recu Y E = \recu Y
+(\recu Z (a.Y + b.Z) + c.Y)$, $Y$ is free in $E = \recu Z (a.Y + b.Z) + c.Y$.
 
@@
 Furthermore, each $P_i$ should be a pure process, i.e.~having no free
-variable.
-% This is usually implicitly assumed in the literature but is
-% actually a \emph{must} to complete some unique-solution proofs.
-Finally, 
-%like the case of CCS equations, we must assume that, 
-the set of bound variables %(i.e. process constants) 
-must be disjoint with
-$\til X$ (this disjointness requirement is optional but makes many proofs
-easier). Putting all together,
+variable. Finally, the set of bound variables is disjoint with
+$\til X$. (This disjointness requirement is optional but makes many proofs
+easier.) Putting all together,
 below is the formal definition of a solution of \multivariate CCS
@@
 \end{alltt}
-Note that, in HOL, the two logical terms ``\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}\\\;\HOLFreeVar{Ps}}'' and ``\HOLinline{\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenIn{}}\\\;\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}'' have the same meaning
-(w.r.t.~\texttt{pred_set} theory). The latter form suggests that,
+Note that the two logical terms ``\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}\\\;\HOLFreeVar{Ps}}'' and ``\HOLinline{\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenIn{}}\\\;\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}'' in
+HOL have the same meaning. The latter form suggests that,
 ``\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}'' is actually a set containing all
-solutions (of ``\HOLinline{\HOLConst{CCS_equation}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}''). Then the unique-solution
-theorems can be understood in this way: any two (syntactically different) elements
-in the set are bisimilar.
+solutions of ``\HOLinline{\HOLConst{CCS_equation}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}''. Then the unique-solution
+theorems can be understood thus: any two (syntactically different) elements
+in the solution set are bisimilar.
 
@@
 \end{alltt}
-
-Compared with their formal proofs in the \univariate case, although each
+\hl{In comparison} with the formal proofs in the \univariate cases, although each
 step related to \multivariate substitutions is more difficult than

### 2019-12-14 ic-journal/response-letter2.tex
text

@@
 grammatical problems we found, and also trying to improve the
-presentation in a number of sentences.
+presentation in several places.
 
@@
   \Mark
-  This was a (embarassing) typo; we have corrected it. 
+  This was a (embarassing) typo; we have corrected it (it was in fact correct in the HOL
+  code -- otherwise the script would not have reported success!). 
 %  when we were trying to make the paper
@@
 We have reformulated, trying to highlight its (possible)
-interests. The (easy) proof of the other proposition (5.2), has been removed.
+interests. The (simple) proof of the other proposition (5.2) has been removed.
 
@@
 \end{quote}
-  \Mark We consider the (informal) explanation as statements of the
-  lemma, and the formal code a more rigorous representation. This
-  convention has been used across the whole paper. It's only on this
-  page that we put too many (small) lemmas together.
+  \Mark We consider the (informal) explanation both  a statement 
+and  as a support (easier to read) for the formal code. 
+We have followed this schema throughout the paper, here it might appear 
+heavy because there is a sequence of (small) lemmas. 
+Still, here we prefer to be homogeneous wrt the rest of the paper.
 
@@
 \end{quote}
-  \Mark We have put this sentence into the paper. Thanks.
+  \Mark We have add the sentence (thanks).
 

### 2019-12-14 ic-journal/ccs.tex
text

@@
 Semantics (SOS) rules shown in Fig.~\ref{f:LTSCCS}.
-A CCS \hl{process is said to use} only \emph{guarded sums} if all occurrences of
+A CCS \hlD{process has or uses}  \emph{guarded sums} if all occurrences of
 \hl{summation} are in the form $a.P + b.Q$.
@@
 \paragraph{Further notations}
-\hl{Let} $\R$, $\S$ range over binary relations, sometimes using 
+\hlD{We let} $\R$, $\S$ range over binary relations, sometimes using 
  infix notation for them, \hl{e.g.} $P \,\R\, Q$ means $(P,Q) \in \R$.
@@
 e.g., $\til P \,\R\, \til Q$ means $P_i \,\R\, Q_i$ for each index $i$ of the tuples $\til P$ and $\til Q$.
-We use $\DSdefi$ to \hl{define} abbreviations. For instance, $P \DSdefi G $, where
+We use $\DSdefi$ for \hl{abbreviations}. For instance, $P \DSdefi G $, where
 $G$ is some expression, means that $P$ stands for the expression $G$.

### 2019-12-14 ic-journal/contraction.tex
text

@@
 Intuitively, the bisimilarity contraction $\mcontrBIS$ is a preorder
-\hl{that} $P \mcontrBIS Q$ holds if $P \wb Q$ and, in addition, 
+\hlD{in which} $P \mcontrBIS Q$ holds if $P \wb Q$ and, in addition, 
 \emph{$Q$ has the possibility of being at least as efficient as $P$} (as far as
@@
 
-\hl{Bisimilarity expansion and bisimilarity contraction are both
-preorders. (Thus we can also call them the \emph{expansion or contraction
-preorder}, respectively.)}
+\hlD{Bisimilarity expansion and bisimilarity contraction are both
+preorders.}
 Similarily with (weak) bisimilarity, both the expansion and the
 contraction preorders are preserved by all CCS operators except the
-summation. The proofs are similar \hl{with the case of bisimilarity},
+summation. The proofs are similar \hlD{to those for bisimilarity},
 see, e.g.~\cite{sangiorgi2017equations} \hl{for details.}

### 2019-12-14 ic-journal/equa.tex
Up to Section 4.11
text

@@
 Fig.~\ref{f:LTSCCS}) for \hl{substitutions} of equation variables.
-For example, the result of substituting \hl{the} variable $X$ with $\nil$ in $a.X +
+For example, the result of substituting  variable $X$ with $\nil$ in $a.X +
 \recu X (b.X)$,  written \hl{as} $(a.X + \recu X (b.X)) \sub {\nil} X$, is
@@
 \label{t:Mil89}
-Let $E_i$ be guarded and sequential \hl{(with only guarded sums)}, and with free
+Let $E_i$   \hl{(with only guarded sums)}  be guarded and sequential,
+and  with free
 variables in $\til X$. Let ${\til P} \wb {\til E}\{\til P /\til X\}$,
@@
  the equation (from~\cite{Mil89}) $X \wb \res a (a. X | \outC a)$
-where $X$ is guarded but not sequential. Any process that does not use
+where $X$ is guarded but not sequential. Any process that does not perform
 $a$\hl{--action} is a solution, e.g. $\nil$ and $b.\nil$.

### 2019-12-14 ic-journal/intro.tex
text

@@
 restrictive CCS syntax)
-is the occurrences of \hl{\emph{unprefixed}} sums (e.g.~$P + Q$) due to
+is the occurrences of \hlD{{arbitrary}} sums (e.g.~$P + Q$) due to
 the non-substitutivity of the contraction preorder in this case.
@@
 In these cases, when moving between proofs there are only a few places \hl{in}
-the HOL proof scripts \hl{that has} to be modified.
+the HOL proof scripts \hlD{that have} to be modified.
 Then the successful termination of a proof gives us the

### 2019-12-14 ic-journal/unique.tex
Up to Section 4.2
text

@@
 \label{t:contraBisimulationU} % was: Thm 3.10
-Let $E_i$ be weakly guarded (and with guarded sums only) with free
+Let $E_i$ (and with guarded sums only) be weakly guarded,   with free
 variables in $\til X$, and let $\til P \mcontrBIS \til E\{\til P/\til X\}$,
@@
 in addition to $\wb$).
-However, comparing with Milner's Theorem~\ref{t:Mil89s1}, there remains
-\hl{one limitation}: the involved CCS expression \hl{can} only
-use guarded sums. This is mainly due to the fact that $\wb$ is not a
+However, compared with Milner's Theorem~\ref{t:Mil89s1}, there remains
+\hlD{the limitation on the need of 
+guarded sums}. This is mainly due to the fact that $\wb$ is not a
  congruence and also $\mcontrBIS$ is not a precongruence.
@@
 \label{t:rcontraBisimulationU}
-Let $E_i$ be weakly guarded with free variables \hl{up to} $\til X$,
+Let $E_i$ be weakly guarded with free variables \hlD{in} $\til X$,
 and let $\til P \rcontr \til E\{\til P/\til X\}$,

### 2019-12-15 ic-journal/coarsest.tex
text

--- 2019-12-12 ic-journal/coarsest.tex
@@
 one way to prove Proposition~\ref{prop:coarsest} is
-to add \hl{an additional} hypothesis \hl{that}
- the involved processes \hl{do not use up} all available labels.
+to add \hlD{an} hypothesis \hl{that}
+ the involved processes \hlD{do not use} all available labels.
  Indeed, this is the standard argument by Milner~\citep[p.~153]{Mil89}.
@@
 In our actual formalisation, instead,
-we assume \hl{a} weaker hypothesis that all \emph{immediate weak} derivatives of
-$p$ and $q$ do not \hl{use up} all available labels.
-We \hl{may call it} the \emph{free action} property:
+we assume \hlD{the} weaker hypothesis that all \emph{immediate weak} derivatives of
+$p$ and $q$ do not \hlD{use} all available labels.
+We \hlD{call this} the \emph{free action} property:
 \begin{alltt}
@@
 derivatives of $p$ and $q$, and only requires that there is an input
-or output label that never occurs as a label of the involved weak transitions.
-Furthermore, an label $a$ and its complementary $\outC a$ are
-considered different: even the involved processes have used up all
-available names, including, say, $a$, the whole proof can still complete as
-long as $\outC a$ never occurs in the immediate weak
-derivatives.}
+or output label that never occurs as a label of the involved transitions.
+% Furthermore, an label $a$ and its complementary $\outC a$ are
+% considered different: even the involved processes have used up all
+% available names, including, say, $a$, the whole proof can still complete as
+% long as $\outC a$ never occurs in the immediate weak
+% derivatives.
+}
 
@@
 
-\hl{Since the type} ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' is \hl{parameterized with two
+\hlD{As the type} ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' is \hl{parameterized on two
 type variables, if the type of all label
-names $\beta$ has a relatively small cardinality (or just a singleton in the
-extreme case), it is quite possible that the involved processes in}
-Proposition~\ref{prop:coarsest} used up all available labels, and thus the free
+names $\beta$ has a  small cardinality (a singleton in the
+extreme case), it is  possible that the processes of}
+Proposition~\ref{prop:coarsest} use all available labels, and thus the free
 action hypothesis does not hold. In this case, it is still possible to prove
-Proposition~\ref{prop:coarsest}, \hl{but due to some
-limitations of HOL itself we have to assume that the involved
-processes are \emph{finite-state}, i.e. the set of all derivatives is
+Proposition~\ref{prop:coarsest};  \hlD{however,  due to some
+limitations of HOL itself we have to assume that the
+processes are \emph{finite-state}, i.e. the set of all their derivatives is
 finite.} The original proof, due to van
@@
 any two processes $p$ and $q$, if there exists a \emph{stable}
-(i.e.~\hl{all immediate derivatives} are $\tau$-free)
- process $k$ which is not bisimilar with any \hl{weak} derivative of $p$ and
- $q$, then \texttt{SUM_EQUIV} indeed implies rooted bisimilarity
- ($\rapprox$) (see~\cite{van2005characterisation,Tian:2017wrba} for
- its proof, both informal and formal versions):
+(i.e.~\hl{without  $\tau$ transitions})
+ process which is not bisimilar with any \hl{weak} derivative of $p$ and
+ $q$, then \HOLinline{\HOLConst{SUM_EQUIV}} indeed implies rooted bisimilarity
+ ($\rapprox$)~\cite{van2005characterisation,Tian:2017wrba}:
 \begin{alltt}
@@
 
-To prove Theorem~\ref{thm:coarsestfiniteState}, \hl{it only remains to construct this stable
+To prove Theorem~\ref{thm:coarsestfiniteState}, \hl{it only remains to construct such stable
 process $k$ for any two finite-state processes $p$ and $q$.}
@@
 existence of a special CCS process, which is not weakly bisimilar to
-any \hl{subprocess emanated} from the two root processes by weak
-transitions.
+any \hlD{weak derivative} of the two root processes.
 There could be infinitely many such subprocesses, even on finitely
@@
 
-For any ``\HOLinline{\HOLConst{label}\;\HOLFreeVar{a}}'', having a function ``\HOLinline{\HOLConst{KLOP}\;\HOLFreeVar{a}}'' (of the type ``\HOLinline{\HOLTyOp{num} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
-\hl{defined on all natural numbers, we can get a countable set of processes
-containing all Klop processes built by the same label.
+For any ``\HOLinline{\HOLConst{label}\;\HOLFreeVar{a}}'', having a function ``\HOLinline{\HOLConst{KLOP}\;\HOLFreeVar{a}}'' (of  type ``\HOLinline{\HOLTyOp{num} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
+\hlD{defined on the natural numbers, we obtain a countable set of processes
+with all Klop processes built from the same label.
 Since the number of all Klop processes in this set is (countably) infinite, and
@@
 that is non-bisimilar with} any derivative of two given 
- finite-state CCS processes $p$ and $q$
-(by definition, the number of such derivatives is finite), \emph{even}
-if $a$ is the only element of type $\beta$ (i.e. the only label name
+ (finite-state) processes $p$ and $q$,
+%(by definition, the number of such derivatives is finite), 
+({even}
+when $a$ is the only element of type $\beta$, i.e. the only label name
 in $\mathscr{L}$).
@@
 \begin{definition}[finite-state CCS]
-  \hl{Let $p$ be an arbitrary CCS process:}
+%  \hl{Let $p$ be an arbitrary CCS process:}
 \begin{enumerate}
@@
 \begin{proposition}
-If $p$ has a weak transition to $q$, then $q$ must be \hl{one of the derivatives} of $p$:
+If $p$ has a weak transition to $q$, then $q$ is among \hlD{the derivatives} of $p$:
 \begin{alltt}
@@
 \end{lemma}
-\hl{Then,} combining the above lemma with the core lemma
+Combining the above lemma with the core lemma
 (\texttt{PROP3_COMMON}) and Theorem~\ref{thm:coarsestR} (\texttt{COARSEST_CONGR_RL}),
-\hl{finally we proved Theorem}~\ref{thm:coarsestfiniteState}
-(\texttt{COARSEST_CONGR_FINITE}). The same proof idea also works for
-the contraction and the rooted contration. \hl{(In the future, we seek a method to
-completely eliminate the finite-state hypothesis for our CCS syntax
-with binary summation.)}
+\hlD{yields the proof of Theorem}~\ref{thm:coarsestfiniteState}
+(\texttt{COARSEST_CONGR_FINITE}). The same proof idea can also be used with
+ contraction and rooted contration.
+%  \hl{(In the future, we seek a method to
+% completely eliminate the finite-state hypothesis for our CCS syntax
+% with binary summation.)}
 

### 2019-12-15 ic-journal/context.tex
text

@@
 % context. There're multiple ways. Here 
-\hl{CCS contexts are needed in defining (pre)congruence.
-To prevent doing variable substititions, the easiest way is}
-to use \univariate $\lambda$-expressions (of the type
+\hlD{CCS contexts are needed in defining (pre)congruence.
+To prevent doing variable substititions, one can take}
+ \univariate $\lambda$-expressions (of  type
 ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'') as \emph{multi-hole CCS contexts}.
@@
 \end{alltt}
-\hl{Notice that, in the above definition (actually generated by
+\hlD{In the above definition (actually generated by
 \texttt{HOL_reln}), for any process $p$,} (\HOLinline{\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{p}}) is a
-valid context with no hole \hl{(like an equation without variable).}
+valid context with no hole \hlD{(similarly to an equation without variables).}
 
-\hl{Now comes the formal version of Def.}~\ref{def:guardness}.
-A context is \emph{weakly guarded} (\HOLinline{\HOLConst{WG}}) if each hole \hl{of
-  it} is underneath a prefix:
+\hlD{Below is the formalisation  of Def.}~\ref{def:guardness}.
+A context is \emph{weakly guarded} (\HOLinline{\HOLConst{WG}}) if each hole  is underneath a prefix:
 \begin{alltt}
@@
 A context is \emph{\hl{(strongly)}  guarded} (\HOLinline{\HOLConst{SG}}) if each hole
-\hl{of it} is underneath a \emph{visible} prefix:
+ is underneath a \emph{visible} prefix:
 \begin{alltt}
@@
 In the same manner, we can also define variants of contexts (\HOLinline{\HOLConst{GCONTEXT}}) and weakly guarded
-contexts (\HOLinline{\HOLConst{WGS}}) in which only guarded sums are allowed \hl{to occur}:
+contexts (\HOLinline{\HOLConst{WGS}}) in which only guarded sums are allowed:
 \begin{alltt}
@@
 \HOLinline{\HOLConst{SEQ}}, etc.) \hl{are needed for capturing} properties about
- the relationships among these kinds of contexts and their
+ the relationships among these kinds of contexts and about their
  compositions. These proofs are usually tedious and long,  due to multiple levels of
@@
 Although weak bisimilarity ($\approx$) is \emph{not} a congruence
-  w.r.t~\HOLinline{\HOLConst{CONTEXT}}, it is indeed substitutive w.r.t.~\HOLinline{\HOLConst{GCONTEXT}} 
-as $\approx$ is indeed preserved by guarded sums. \hl{Similarily,
-contraction ($\mcontrBIS$) is also substitutive w.r.t.}~\HOLinline{\HOLConst{GCONTEXT}}.
+  w.r.t~\HOLinline{\HOLConst{CONTEXT}}, it is  substitutive w.r.t.~\HOLinline{\HOLConst{GCONTEXT}} 
+as $\approx$ is  preserved by guarded sums. \hl{Similarily,
+contraction ($\mcontrBIS$) is  substitutive w.r.t.}~\HOLinline{\HOLConst{GCONTEXT}}.
 %

### 2019-12-15 ic-journal/intro.tex
text

@@
 restrictive CCS syntax)
-is the occurrences of \hlD{{arbitrary}} sums (e.g.~$P + Q$) due to
+is the occurrences of \hlD{arbitrary} sums (e.g.~$P + Q$) due to
 the non-substitutivity of the contraction preorder in this case.

### 2019-12-15 ic-journal/multivariate.tex
text

@@
 
-\hl{Our goal in this last part of the CCS formalisation are two formally
-verified theorems, which dwarf all previous results in this project:}
-the general (\multivariate) cases of
+\hl{In this section we attack the case of 
+  multiple equations (the ``\multivariate''  case), for two major theorems earlier discussed:}
 Milner's ``unique solution of equations (for $\sim$)''
-(Theorem~\ref{t:Mil89s1}) and our ``unique solution of rooted
+(Theorem~\ref{t:Mil89s1}) and  the  ``unique solution of rooted
 contractions'' (Theorem~\ref{t:rcontraBisimulationU}).
 %
-This formalisation supports finitely many
+The formalisation supports finitely many
   equations/contractions and equation variables.\footnote{The original theorems
 hold for even infinitely many equations and equation variables.}
-We chose the two theorems because \hl{they both require the same
-weakly guarded contexts (with minimized efforts)}, and 
-because they well illustrate the \hl{efforts} needed for the \multivariate case.
-The work is a \hl{natural} extension of the existing work, for
-\hl{no new algebraic type (e.g. the type for CCS processes) has to be defined,}
-and neither the CCS syntax nor the SOS rules \hl{needs} to be changed.
+We chose these two theorems because \hlD{of their relevance}, and 
+because they well illustrate the \hlD{effort} needed in the \multivariate case.
+% The work is a \hl{natural} extension of the existing work, for
+% \hl{no new algebraic type (e.g. the type for CCS processes) has to be defined,}
+% and neither the CCS syntax nor the SOS rules \hl{needs} to be changed.
 
@@
 equations, and variable substitutions are simply 
-\hl{applications of} $\lambda$-functions to CCS terms \hl{as substitutions}.
-This idea (i.e. \multivariate $\lambda$-functions), however,
-cannot be extended to \hl{support} the \multivariate case of
-unique-solution theorems, as we do not have a fixed number of variables to deal with.
+\hl{applications of} $\lambda$-functions to CCS terms.
+This idea, however,
+cannot be extended to  the \multivariate case, as we do not have a fixed number of variables to deal with.
 
@@
 a system of equations $\{X_i = E_i\}_{i\in I}$ are usually considered as
-\hl{separate} \emph{process variables} outside the CCS syntax.
+ \emph{process variables} outside the CCS syntax.
 Then, an equation body  $E_i$  is an \emph{open} expression
 built with CCS operators plus these equation variables.
-For a formal point of view, this means \hl{that} we either need to define a
-whole new datatype (with extra equation variables) in which each CCS
-operator must be duplicated, or we have to add equation variables as a
-new primitive (e.g.~\texttt{Var X}) to the existing CCS type in addition
-to the agent variables such as \texttt{var X}.
-(Then the substitution of equation
-variables in $E_i\{\til P/\til X\}$ would become the \emph{syntactic substitution} of
-each occurrence of $X_i$ in $E_i$ with the corresponding $P_i$.)
+In a  formalisation, this means either  defining a
+whole new datatype (with extra equation variables), in which each CCS
+operator must be duplicated, or adding equation variables as a
+new primitive (e.g.~\texttt{Var X}) to the existing CCS type (besides
+ agent variables such as \texttt{var X}).
+% (Then the substitution of equation
+% variables in $E_i\{\til P/\til X\}$ would become the \emph{syntactic substitution} of
+% each occurrence of $X_i$ in $E_i$ with the corresponding $P_i$.)
 In either cases the \emph{disjointness} between equation variables and
@@
 
-In this project, we have followed Milner's original
+In our work, we have followed Milner's original
 approach~\cite{milner1990operational}, using the
@@
 This \hl{approach allows} a large reuse of the \univariate formalisation.
-For instance, the variable substitution \hl{occurred in SOS rule}
+For instance, the variable substitution \hlD{in the  SOS rule}
 \texttt{REC} can be reused for substituting equation variables.
-However, a lot of care is needed in the proofs of many
-fundamental lemmas, mostly due to the variable capture issues between
-equation variables \hl{(free)} and agent variables \hl{(bound)}.
+However,  care is needed in the proofs of many
+fundamental lemmas, mostly due to  variable capture issues between
+free equation variables and bound agent variables.
 
@@
 
-The set of free and \hl{the set of} bound
-variables of a term need not \hl{to} be disjoint, e.g.~in $X + \recu X E$.
+The set of free and bound
+variables of a term need not be disjoint, e.g.~in $X + \recu X E$.
 More importantly, when going
@@
 $\fv{\mu.X} = \{X\}$. This property of $\fv{\cdot}$ brings some
-difficulities when doing \hl{transition inductions}. As an evidence,
+difficulities in \hl{transition inductions}. As an evidence,
 we prove the following fundamental property of
@@
 \begin{proof}
-We actually proved a stronger result, asserting that the set of free
-variables in a CCS process \hl{\emph{never increases}} through its derivatives:
+We  prove a stronger result, asserting that the set of free
+variables in a CCS process \hlD{does not increase} in its derivatives:
 \begin{alltt}
@@
 In~\cite{milner1990operational}, the proof of the above property is 
-commented by  ``an easy action induction''.
-\hl{However, the actual proof (in HOL) is not that trivial}:
- ``action induction'' (or \emph{transition induction}) becomes a form of higher-order application
+commented as  ``an easy action induction''.
+\hlD{As a matter of fact, in the  HOL proof}
+ ``action induction'' %(or \emph{transition induction}) 
+becomes a form of higher-order application
 of the following \emph{induction principle} (generated together with the SOS
@@
 \end{alltt}
-The above long theorem has the form \HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLBoundVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}} (with $a_0, a_1, a_2$ renamed), \hl{where} the
+The above long theorem is of the form \HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLBoundVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}} (with $a_0, a_1, a_2$ renamed), \hl{where} the
 outermost universal quantifier $P$ is a higher-order
-proposition (\hl{taking} $E$, $\mu$ and $E'$), while $X$ is another higher-order
-proposition \hl{containing} $P$.
-\hl{Our proof goal} is actually in the form of
+proposition (\hl{taking} $E$, $\mu$ and $E'$), and $X$ is another higher-order
+proposition.
+\hl{The proof goal} is actually in the form of
 \HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLFreeVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}}, where
@@
 
-There are two (obvious) ways to \hl{do} % not "represent" but actually "do"
+There are two natural ways to \hlD{implement} % not "represent" but actually "do"
 the \multivariate substitution $E\{\til P/\til X\}$, \hl{which} replaces each \hl{free
@@
 a list of variables \HOLinline{\HOLFreeVar{Xs}} and the corresponding substituted terms
-\HOLinline{\HOLFreeVar{Ps}} by a helper function \HOLinline{\HOLConst{fromList}} (\hl{defined by us, and} whose details are
+\HOLinline{\HOLFreeVar{Ps}} by a helper function \HOLinline{\HOLConst{fromList}} (whose details are
 omitted here).
@@
 abbreviated as \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}.
-The substitution mechanism is order-independent, \hl{as there is no
-ordering in finite maps.} For most CCS operators it
-just recursively calls itself on subterms, \hl{while the} only
+The substitution mechanism is order-independent, \hlD{as based
+ maps.} For most CCS operators it
+just recursively calls itself on subterms.  \hlD{The} most
 interesting cases are at agent variables and recursion:
@@
 \HOLinline{\HOLConst{ALL_DISTINCT}} says that
-the elements of a list are all distinct; \HOLinline{\HOLConst{MAP}} is
+the elements of a list are  distinct; \HOLinline{\HOLConst{MAP}} is
 the mapping function from one list to another; \HOLinline{\HOLConst{EVERY}} means
@@
 variables of $E$ and the free substitution variables are disjoint) is
-added to ease the related proofs. This disjointness requirement
-is not necessary \hl{and (in theory) can be all eliminated with more efforts.}
-\hl{As many of these lemmas are used in proving other theorems, eventually}
-the disjointness condition are propagated everywhere.
+added to ease the proofs. The 
+condition
+is not necessary and could be  eliminated, at the price of some extra effort.
+% \hl{As many of these lemmas are used in proving other theorems, eventually}
+% the disjointness condition are propagated everywhere.
 
@@
 
-\hl{In theory}, it is possible to inductively assert \multivariate contexts and their
-guarded variants, but care is needed as we \hl{have} to exclude the cases where
-free variables occur \hl{within recusion}.  \hl{Here we choose} a more elegant
- solution, which defines \multivariate contexts (and variants) upon the
+It could be possible to inductively define \multivariate contexts and their
+guarded variants, but care is needed
+for 
+ variables that occur \hl{within a  recusion}.  \hl{We have preferred a different
+   solution,} in which the definitions of 
+ \multivariate contexts  is based on the
  existing \univariate definitions.
-\hl{The idea is that, whenever we replace a variable by a hole and view
-the other variables as constants, this is a single variable context
-that can be asserted by predicates like} \HOLinline{\HOLConst{CONTEXT}}.
-For example, to see the weak guardedness of $a.X + b.X + c.Y$, it is
-natural to focus on each (free) variable: if we substitute each
-occurrence of just one variable, say $X$, with a ``hole'' and see the
+\hlD{For this, intuitively,  we replace a single variable with a hole and (viewing
+the other variables as constants) so to obtain a  single-variable context
+on which predicates like} \HOLinline{\HOLConst{CONTEXT}} can be used.
+For example, to see the weak guardedness of $a.X + b.X + c.Y$, 
+we focus on each (free) variable: if we substitute each
+occurrence of a variable, say $X$, with a ``hole'' and see the
 resulting term as a $\lambda$-function, then all such $\lambda$-functions
@@
 (The \multivariate guardedness and sequentiality can also be defined similarily, using
-their \univariate companions \HOLinline{\HOLConst{SG}} and \HOLinline{\HOLConst{SEQ}}, \hl{but so far
-they are not defined.})
+their \univariate companions \HOLinline{\HOLConst{SG}} and \HOLinline{\HOLConst{SEQ}}.)
 
@@
 bisimilarity ($\rapprox$) \hl{and} rooted contraction ($\rcontr$). It does
-not hold, however, for weak bisimilarity ($\wb$) and the contraction
-preorder ($\mcontrBIS$), \hl{as they are not (pre)congruence
-w.r.t.}~\HOLinline{\HOLConst{context}}.
+not hold for weak bisimilarity ($\wb$) and the contraction
+preorder ($\mcontrBIS$), \hl{as they are not (pre)congruence relations}.
 
 Another important property of contexts is their composability: if we
-substitute some free variables in a context \hl{to} some other contexts, the
+substitute some free variables in a context \hl{with} some other contexts, the
 resulting term is still a \hl{valid} context (w.r.t.~the same set of variables):
@@
 \hl{context (or equation) variables are not allowed to occur within recursion. The converse
-holds however:} if the set of free variables of an CCS term
-is disjoint with a list of variables, then the term is indeed a context
-w.r.t. the same list of variables:
+holds however:} if the set of free variables of a CCS term
+is disjoint from a list of variables, then the term is indeed a context
+w.r.t. such list of variables:
 \begin{alltt}
@@
 Note that, in the above lemma we cannot
-conclude \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}}, because $Y$ as a bound
-variable of $\recu Y E$ may also be a free variable in $\til X$. We
+conclude
+\HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}},
+because $Y$ may appear in both sets.
+%, as a bound
+%variable of $\recu Y E$, may also be a free variable in $\til X$.
+ We
 also cannot conclude \HOLinline{\HOLConst{context}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{E}}, because in $\recu Y E$
-the bound variable $Y$ \hl{may occur \emph{freely} within another nested}
-recursion, and then it is free in $E$. \hl{For instance,} $\recu Y E = \recu Y
-(\recu Z (a.Y + b.Z) + c.Y)$, $Y$ is free in $E = \recu Z (a.Y + b.Z) + c.Y$.
+the bound variable $Y$ \hlD{may occur {freely} within another nested}
+recursion. \hl{For instance,} variable $Y$ is free   
+in $\recu Y E $ , for 
+ $E = \recu Z (a.Y + b.Z) + c.Y$.
 
@@
 their composability w.r.t.~\multivariate contexts: if we
-substitute some free variables in a context $C$ to some weakly guarded
-contexts, the resulting \hl{context becomes} weakly guarded (w.r.t.~the same set of variables):
+substitute some free variables in a context $C$ with some weakly guarded
+contexts, the resulting \hlD{context is} weakly guarded (w.r.t.~the same set of variables):
 \begin{alltt}
@@
 \end{itemize}
-Obviously the two lists $\til X$ and $\til E$ must have the same
-length, and in practice the variables in $\til X$ should be all distinct.
-Furthermore, we assume that $\til E$ does not contain
- free variables that are not in $\til X$, i.e. each $E_i$ contains
- variables up to $\til X$.
-\hl{Finally, the only extraordinary hypothesis} is that, for each
-$E_i$, the set of its bound variables must be \emph{disjoint} with
-$\til X$. \hl{(In practice, however, one can always
-rename all recursion binders in the equations to satisfy this
-requirement without changing the semantics of equations.)}
-Putting all requirements together, below is the fomal
+The two lists $\til X$ and $\til E$ must have the same
+length, and  the variables in $\til X$ should  be distinct.
+Furthermore,  $\til E$ does not contain
+ free variables that are not in $\til X$.
+\hlD{Finally, } for each
+$E_i$, the set of its bound variables must be \emph{disjoint} from
+$\til X$. 
+% \hl{(In practice, however, one can always
+% rename all recursion binders in the equations to satisfy this
+% requirement without changing the semantics of equations.)}
+These requirements yield the fomal
 definition of \multivariate CCS equation:
@@
 
-\hl{So is} the \multivariate version of Theorem~\ref{t:rcontraBisimulationU}:
+\hlD{Now} the \multivariate version of Theorem~\ref{t:rcontraBisimulationU}:
 \begin{alltt}
@@
 \end{alltt}
-\hl{In comparison} with the formal proofs in the \univariate cases, although each
+In summary, while  each
 step related to \multivariate substitutions is more difficult than
-the \univariate case, the entire proofs still follow the same \hl{outlines}.
-and many proof \hl{steps} can even be copied from their \univariate \hl{companions}.
+that for the \univariate case, the structure of the 
+ the overall proofs is the same;  
+various proof \hl{steps} can even be copied from the \univariate \hl{case}.

### 2019-12-15 ic-journal/part2.tex
text

--- 2019-12-13 ic-journal/part2.tex
@@
 
-\hl{Using ``bisimulation up to $\sim$'' technique}, we first proved the following
+\hl{Using ``bisimulation up to $\sim$'' technique}, we obtain the following
 key lemma, which states that, if $X$ is weakly guarded
@@
 Then, by structural induction on weakly guarded contexts
-(\texttt{WG}), we have proved Theorem~\ref{t:Mil89s1}
+(\texttt{WG}), we prove Theorem~\ref{t:Mil89s1}
 in the \univariate case. The formal proof basically follows the outline of its
@@
 \end{alltt}
-\hl{By using Lemma}~\ref{l:obsCongrByWeakBisim}, \hl{the next two results} can be proved by 
+\hlD{Using Lemma}~\ref{l:obsCongrByWeakBisim}, \hl{the next two results} are proved by 
 directly constructing the required bisimulation:
@@
 As weak bisimilarity is not a congruence, we have to be more restrictive
-on the syntax of the equation, \hl{with only guarded sums.}
+on the syntax of the equation, \hlD{using only guarded sums.}
 The related formal proofs are tedious but closely follow the informal
-proof~\citep[p.~158--159]{Mil89}, \hl{except for the uses of} ``bisimulation up
-to with weak arrows'' (Def.~\ref{def:doubleweak}) instead of the
-original version (Def.~\ref{def:singleweak}).
+proof~\citep[p.~158--159]{Mil89}, \hlD{with the exception of the use  of} ``bisimulation up
+to with weak arrows'' (Def.~\ref{def:doubleweak}, instead of Def.~\ref{def:singleweak}).
 
@@
 contractions \hl{is} the proof of Lemma~\ref{l:ruptocon} and lemmas alike.
-\hl{In particular, we have do} induction on the length of weak transitions.
+\hlD{In particular, we use} induction on the length of weak transitions.
 For this, rather than introducing a refined form of weak transition relation
 enriched with its length, we found it more elegant to work with
-\emph{traces}, \hl{i.e. weak transitions with all intermediate actions.}
+\emph{traces}, \hlD {sequences of transitions.}
 (A further motivation is to set the ground for future extensions of this
@@
  (\HOLinline{\HOLConst{LRTC}}).
-\hl{Then,} given any labeled transition relation \HOLinline{\HOLFreeVar{R}} (of the type
+\hl{Then,} given any labeled transition relation \HOLinline{\HOLFreeVar{R}} (of  type
 ``\HOLinline{\ensuremath{\alpha} \HOLTokenTransEnd \ensuremath{\beta} \HOLTokenTransEnd \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}''), \HOLinline{\HOLConst{LRTC} \HOLFreeVar{R}} is
-a relation representing \hl{traces} (of the type
+a relation representing \hl{traces over} \HOLinline{\HOLFreeVar{R}}  (of type
 ``\HOLinline{\ensuremath{\alpha} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{list} \HOLTokenTransEnd \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}''):
@@
 type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTyOp{list} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}''),
-can be then obtained
+is then obtained
  by \hl{combining} \texttt{LRTC} and the \texttt{TRANS}
- ($\overset{\mu}{\rightarrow}$) relation inductively defined by SOS rules:
+ ($\overset{\mu}{\rightarrow}$) relation defining the SOS rules:
 \begin{alltt}
@@
 
-\hl{Let the trace be $P\overset{acts}{\longrightarrow}Q$.}
-If the list of actions $acts$ is empty, then there is no transition
-actually: the initial and final processes are the same, i.e. $P = Q$.
-\hl{On the other hand, if there is at most one visible action (i.e. a
-label) $\mu$ in $acts$ (all other actions are $\tau$, if they exist),}
-then the trace is actually a weak transition: $P \Arr{\mu} Q$.
-Here we have to distinguish between two cases: no label and unique label (in
-the list of actions). The definition of ``no
-label'' in an action list is easy (here \texttt{MEM} tests if \hl{an} element is a member of a list):
+\hlD{In a  trace  $P\overset{acts}{\longrightarrow}Q$,}
+ the list of actions $acts$ may be  empty, in which case there is no transition, and 
+ the initial and final processes are the same, i.e. $P = Q$.
+\hlD{If there is at most one visible action $\mu$  in $acts$, and all other actions are $\tau$'s,}
+then the trace represents  a weak transition $P \Arr{\mu} Q$.
+For this,  we have to distinguish two cases in
+the list of actions: no label and unique label. The definition of ``no
+label'' for a list of  actions is as follows, where \texttt{MEM} tests if \hl{an} element is a member of a list:
 \begin{alltt}
@@
 following definition (due to a suggestion from Robert Beers)
-avoids any \hl{kind} of counting or filtering in the list.
-It says that a label is unique in a list of actions if and only if there is no
-label in the rest of list (here $\HOLTokenDoublePlus$ \hl{denotes the concatenation
+avoids any  counting or filtering in the list.
+It says that a label is unique in a list of actions if there is no
+label in the rest of list (here $\HOLTokenDoublePlus$ \hlD{is the concatenation
 of lists}):
@@
 
-\hl{Finally, the connection} between traces and weak transitions is stated
-and proved in the following theorem, \hl{which} says that a weak transition $P \Arr{u} P'$ is also a
+\hlD{Finally, the  relationship} between traces and weak transitions is stated
+and proved in the following theorem.  \hl{It} says that a weak transition $P \Arr{u} P'$ is also a
 trace $P\overset{acts}{\longrightarrow}P'$ with a
@@
 few more steps to handle rooted bisimilarity in the conclusion. 
-Overall \hl{speaking}, the two proofs are very similar, mostly because
-the only property \hl{one needed} from (rooted) contraction is the precongruence.
+The two proofs are similar, mostly because
+the main property needed from \hlD{contraction and rooted contraction is} precongruence.
 Below is the formal version of Theorem~\ref{t:rcontraBisimulationU}:
@@
 now we can use weakly guarded expressions in the above theorem,
-which has no more constraints on summation, that is, having
-\texttt{WG} in place of \texttt{WGS} (cf.~\texttt{UNIQUE_SOLUTION_OF_CONTRACTIONS}).
+which has no more constraints on summation (as shown by the appearance of
+\texttt{WG} rather than \texttt{WGS}).
+% (cf.~\texttt{UNIQUE_SOLUTION_OF_CONTRACTIONS}).
 
-On the other hand, having removed the constraints on \hl{summation}, now
-this result is very similar to Milner's original `unique solution of
-equations' theorem for \emph{strong} bisimilarity ($\sim$) (Theorem~\ref{t:Mil89s1})~--- 
-the same weakly guarded context (\texttt{WG}) is required
-(cf.~Theorem~\ref{thm:Mil89s1f}, \texttt{STRONG_UNIQUE_SOLUTION}).
+Having removed the constraints on \hl{summation}, 
+this result is close to Milner's original `unique solution of
+equations' theorem for \emph{strong} bisimilarity  (Theorem~\ref{t:Mil89s1})~--- 
+the same weakly guarded context (\texttt{WG}) is required.
+%(cf.~Theorem~\ref{thm:Mil89s1f}, \texttt{STRONG_UNIQUE_SOLUTION}).
 In contrast, Milner's ``unique solution of
@@
 has more rigid constraints, as the \emph{equations} must be both guarded and
-sequential (cf.~Theorem~\ref{thm:Mil89s3f}, \texttt{OBS_UNIQUE_SOLUTION}).
+sequential. % (cf.~Theorem~\ref{thm:Mil89s3f}, \texttt{OBS_UNIQUE_SOLUTION}).
 

### 2019-12-15 ic-journal/sos.tex
text

@@
 of Section~\ref{ss:ccs}. (Thus the
-cardinality of ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' depend on \hl{its type variable:
+cardinality of ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}''  \hlD{depends on its type variable:
 \mbox{when $\beta$ is finite or countable, ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is countable.}})
@@
 \begin{itemize}
-  \item \emph{rules} is a conjunction of implications that will be the
-    same as the input term. In fact, the following formal versions of SOS rules are
+  \item
+\emph{rules} is a conjunction of implications (each
+    corresponding to a SOS rule) that will be the
+    same as the input term.
+% \emph{rules} is a conjunction of implications that will be the
+%    same as the input term. 
+In fact, the following formal versions of SOS rules are
     extracted from the \emph{rules} theorem:
@@
 \end{alltt}  
-For instance, \hl{the following proposition
-can only be proven by using the above \emph{cases} theorem}:
+For instance, \hlD{the following proposition
+need the above \emph{cases} theorem}:
 \begin{alltt}

### 2019-12-15 ic-journal/multivariate.tex
text

@@
 \hl{In this section we attack the case of 
-  multiple equations (the ``\multivariate''  case), for two major theorems earlier discussed:}
+  multiple equations (the `\multivariate'  case), for two major theorems earlier discussed:}
 Milner's ``unique solution of equations (for $\sim$)''
@@
 We chose these two theorems because \hlD{of their relevance}, and 
-because they well illustrate the \hlD{effort} needed in the \multivariate case.
+because they well illustrate the \hlD{work} needed in the \multivariate case.
 % The work is a \hl{natural} extension of the existing work, for
@@
 abbreviated as \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}.
-The substitution mechanism is order-independent, \hlD{as based
- maps.} For most CCS operators it
-just recursively calls itself on subterms.  \hlD{The} most
+Using maps, the substitution mechanism is order-independent. For most CCS operators,
+\HOLinline{\HOLConst{CCS_SUBST}}
+ recursively calls itself on subterms.  \hlD{The} most
 interesting cases are at agent variables and recursion:
@@
  existing \univariate definitions.
-\hlD{For this, intuitively,  we replace a single variable with a hole and (viewing
-the other variables as constants) so to obtain a  single-variable context
+\hlD{For this, intuitively,  we replace a single variable with a hole  (viewing
+the other variables as constants), so to obtain a  single-variable context
 on which predicates like} \HOLinline{\HOLConst{CONTEXT}} can be used.
 For example, to see the weak guardedness of $a.X + b.X + c.Y$, 
-we focus on each (free) variable: if we substitute each
+we focus on each (free) variable, we substitute each
 occurrence of a variable, say $X$, with a ``hole'' and see the
-resulting term as a $\lambda$-function, then all such $\lambda$-functions
-must satisfy \HOLinline{\HOLConst{WG}}, i.e.~the following results hold:
+resulting term as a $\lambda$-function; then all such $\lambda$-functions
+should satisfy \HOLinline{\HOLConst{WG}}, i.e.~the following results hold:
 \begin{alltt}
@@
 
-For weakly guarded contexts (which are also normal contexts), beside
-their regular properties (i.e. weak
-guardedness) as in the \univariate case (\HOLinline{\HOLConst{WG}}), we also need
+For weakly guarded contexts, % (which are also normal contexts), 
+besides
+their usual properties  as in the \univariate case (i.e., weak
+guardedness,
+\HOLinline{\HOLConst{WG}}), we also need
 their composability w.r.t.~\multivariate contexts: if we
@@
 can be used to represent solutions of all kinds of CCS
-\hl{equations and inequations.} Then, of course ${\til P} \ \R\  {\til E}\{\til
+\hlD{equations.} Then,  ${\til P} \ \R\  {\til E}\{\til
 P/\til X\}$ must hold:
@@
   \HOLinline{\HOLConst{LIST_REL}\\\;\HOLFreeVar{R}} is the same binary relation but for lists of
-  CCS processes. Furthermore, \HOLinline{\HOLConst{LIST_REL}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{A}\\\;\HOLFreeVar{B}} implicitly
-  implies that the two lists $A$ and $B$ have the same length.}
+  CCS processes with the same length.
+ % Furthermore,  \HOLinline{\HOLConst{LIST_REL}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{A}\\\;\HOLFreeVar{B}}
+  implicitly   implies that the two lists $A$ and $B$ have the same length.
+}
 \begin{alltt}

### 2019-12-15 ic-journal/multivariate.tex
text

@@
 \end{itemize}
-The two lists $\til X$ and $\til E$ must have the same
+The two lists $\til X$ and $\til E$ should have the same
 length, and  the variables in $\til X$ should  be distinct.
@@
 \hlD{Finally, } for each
-$E_i$, the set of its bound variables must be \emph{disjoint} from
+$E_i$, the set of its bound variables should be \emph{disjoint} from
 $\til X$. 
@@
 \hlD{equations.} Then,  ${\til P} \ \R\  {\til E}\{\til
-P/\til X\}$ must hold:
+P/\til X\}$  should hold:
 \begin{equation*}

### 2019-12-15 ic-journal/sos.tex
text

@@
 To completely describe all possible transitions of the process, the
-following two facts must be proved: (1) there are indeed the three
+following two facts have to be proved: (1) there are indeed the three
   transitions mentioned above; (2) there is no other

### 2019-12-15 ic-journal/ccs.tex
Synchronized all changes from .tex to .htex; clean up all reviewed highlights (adding 3 new)

@@
 
-%Here we recall the core theory of CCS.
 We assume a possibly infinite set of \emph{names} $\mathscr{L} = \{a, b,
@@
 action $\tau \notin \mathscr{L}$, and another possibly infinite
-set of \emph{agent variables} \hl{$\mathscr{X} = \{X, Y, \ldots\}$}.
-The class of  CCS \hl{terms} is then inductively
+set of \emph{agent variables} $\mathscr{X} = \{X, Y, \ldots\}$.
+The class of CCS terms is then inductively
 defined from $\nil$ (the terminated process) and agent variables by the operators
@@
 We sometimes omit a trailing $\nil$, e.g., writing $a|b$ for $a.\nil |b .\nil$.
-A CCS process $P$ may evolve to another one \hl{(i.e. having a \emph{transition})}, say $P'$, under
+A CCS process $P$ may evolve to another one (i.e. having a \emph{transition}), say $P'$, under
   an action $\mu$, written by $P \arr{\mu} P'$.
@@
 Semantics (SOS) rules shown in Fig.~\ref{f:LTSCCS}.
-A CCS \hlD{process has or uses}  \emph{guarded sums} if all occurrences of
-\hl{summation} are in the form $a.P + b.Q$.
+A CCS process has or uses \emph{guarded sums} if all occurrences of
+summation are in the form $a.P + b.Q$.
 The \emph{immediate derivatives} of a
-process $P$ are \hl{the} elements of $\{P' \st P \arr\mu P'
+process $P$ are the elements of $\{P' \st P \arr\mu P'
 \mbox{ for some $\mu$}\}$.
@@
 \paragraph{Further notations}
-\hlD{We let} $\R$, $\S$ range over binary relations, sometimes using 
- infix notation for them, \hl{e.g.} $P \,\R\, Q$ means $(P,Q) \in \R$.
+We let $\R$, $\S$ range over binary relations, sometimes using 
+ infix notation for them, e.g. $P \,\R\, Q$ means $(P,Q) \in \R$.
 We use a tilde, as in  $\til P$, to denote (finite) tuples of elements. 
-% We use a tilde, as in  $\til P$, to denote tuples of processes with
-% countably many \hl{elements.}
-All \hl{relation} notations can be extended to tuples componentwise,
+All relation notations can be extended to tuples componentwise,
 e.g., $\til P \,\R\, \til Q$ means $P_i \,\R\, Q_i$ for each index $i$ of the tuples $\til P$ and $\til Q$.
-We use $\DSdefi$ for \hl{abbreviations}. For instance, $P \DSdefi G $, where
+We use $\DSdefi$ for abbreviations. For instance, $P \DSdefi G $, where
 $G$ is some expression, means that $P$ stands for the expression $G$.
-If $\leq$ is a preorder, then  $\geq$  is its inverse (and
-conversely).
+If $\leq$ is a preorder, then  $\geq$  is its inverse (and conversely).
 

### 2019-12-15 ic-journal/coarsest.tex
Synchronized all changes from .tex to .htex; clean up all reviewed highlights (adding 3 new)

@@
 congruence contained in $\wb$. 
-The general form of this theorem is the \hl{following}
+The general form of this theorem is the following
 one~\cite{van2005characterisation,Gorrieri:2015jt,Mil89}:
@@
 delicate aspects. For instance, 
-\hl{within} our CCS syntax \hl{which supports} only binary sums,
+within our CCS syntax which supports only binary sums,
 one way to prove Proposition~\ref{prop:coarsest} is
-to add \hlD{an} hypothesis \hl{that}
- the involved processes \hlD{do not use} all available labels.
+to add an hypothesis that
+ the involved processes do not use all available labels.
  Indeed, this is the standard argument by Milner~\citep[p.~153]{Mil89}.
@@
  Formalising this result, however, requires a detailed treatment of
- free and bound names \hl{(of labels)} of CCS
+ free and bound names (of labels) of CCS
 processes, with the restriction operator acting as a binder.
 In our actual formalisation, instead,
-we assume \hlD{the} weaker hypothesis that all \emph{immediate weak} derivatives of
-$p$ and $q$ do not \hlD{use} all available labels.
-We \hlD{call this} the \emph{free action} property:
+we assume the weaker hypothesis that all \emph{immediate weak} derivatives of
+$p$ and $q$ do not use all available labels.
+We call this the \emph{free action} property:
 \begin{alltt}
@@
 is contained in the composition closure of $R$
-(hence the composition closure is \hl{indeed} the coarsest one):
+(hence the composition closure is indeed the coarsest one):
 \begin{alltt}
@@
 free action property.
-\hl{Indeed, in the proof one only looks at the immediate weak
+Indeed, in the proof one only looks at the immediate weak
 derivatives of $p$ and $q$, and only requires that there is an input
 or output label that never occurs as a label of the involved transitions.
-% Furthermore, an label $a$ and its complementary $\outC a$ are
-% considered different: even the involved processes have used up all
-% available names, including, say, $a$, the whole proof can still complete as
-% long as $\outC a$ never occurs in the immediate weak
-% derivatives.
-}
 
@@
 
-\hlD{As the type} ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' is \hl{parameterized on two
+As the type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'' is parameterized with two
 type variables, if the type of all label
 names $\beta$ has a  small cardinality (a singleton in the
-extreme case), it is  possible that the processes of}
+extreme case), it is possible that the processes of
 Proposition~\ref{prop:coarsest} use all available labels, and thus the free
 action hypothesis does not hold. In this case, it is still possible to prove
-Proposition~\ref{prop:coarsest};  \hlD{however,  due to some
+Proposition~\ref{prop:coarsest}; however, due to some
 limitations of HOL itself we have to assume that the
 processes are \emph{finite-state}, i.e. the set of all their derivatives is
-finite.} The original proof, due to van
+finite. The original proof, due to van
 Glabbeek~\cite{van2005characterisation}, does not require finite-state CCS.
@@
 any two processes $p$ and $q$, if there exists a \emph{stable}
-(i.e.~\hl{without  $\tau$ transitions})
- process which is not bisimilar with any \hl{weak} derivative of $p$ and
+(i.e.~without $\tau$ transitions)
+ process which is not bisimilar with any weak derivative of $p$ and
  $q$, then \HOLinline{\HOLConst{SUM_EQUIV}} indeed implies rooted bisimilarity
@@
 
-To prove Theorem~\ref{thm:coarsestfiniteState}, \hl{it only remains to construct such stable
-process $k$ for any two finite-state processes $p$ and $q$.}
-\hl{For arbitrary CCS processes, this construction} relies on
+To prove Theorem~\ref{thm:coarsestfiniteState}, it only remains to construct such stable
+process $k$ for any two finite-state processes $p$ and $q$.
+For arbitrary CCS processes, this construction relies on
 arbitrary infinite sums of processes (not within our CCS syntax) and
@@
 existence of a special CCS process, which is not weakly bisimilar to
-any \hlD{weak derivative} of the two root processes.
+any weak derivative of the two root processes.
 There could be infinitely many such subprocesses, even on finitely
@@
 possible to choose one that is distinct from all the (finitely many) states in the
-\hl{transition} graphs of the two given processes.
+transition graphs of the two given processes.
 This can be done by following Klop's contruction.
@@
 
-For any ``\HOLinline{\HOLConst{label}\;\HOLFreeVar{a}}'', having a function ``\HOLinline{\HOLConst{KLOP}\;\HOLFreeVar{a}}'' (of  type ``\HOLinline{\HOLTyOp{num} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
-\hlD{defined on the natural numbers, we obtain a countable set of processes
+For any ``\HOLinline{\HOLConst{label}\;\HOLFreeVar{a}}'', having a function ``\HOLinline{\HOLConst{KLOP}\;\HOLFreeVar{a}}'' (of the type ``\HOLinline{\HOLTyOp{num} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
+defined on the natural numbers, we obtain a countable set of processes
 with all Klop processes built from the same label.
@@
 choose a number that is mapped to a Klop process
-that is non-bisimilar with} any derivative of two given 
+that is non-bisimilar with any derivative of two given 
  (finite-state) processes $p$ and $q$,
-%(by definition, the number of such derivatives is finite), 
-({even}
-when $a$ is the only element of type $\beta$, i.e. the only label name
-in $\mathscr{L}$).
+even when $a$ is the only element of type $\beta$, i.e. the only label name
+in $\mathscr{L}$.
 This property is captured by appealing to the following set-theoreric
@@
 \begin{definition}[finite-state CCS]
-%  \hl{Let $p$ be an arbitrary CCS process:}
+  \mbox{}
 \begin{enumerate}
@@
 \begin{proposition}
-If $p$ has a weak transition to $q$, then $q$ is among \hlD{the derivatives} of $p$:
+If $p$ has a weak transition to $q$, then $q$ is among the derivatives of $p$:
 \begin{alltt}
@@
 
-Using all the above results, now we can prove the following \hl{finite-state}
+Using all the above results, now we can prove the following finite-state
 version of ``Klop lemma'':
@@
 (\texttt{PROP3_COMMON}) and Theorem~\ref{thm:coarsestR} (\texttt{COARSEST_CONGR_RL}),
-\hlD{yields the proof of Theorem}~\ref{thm:coarsestfiniteState}
+yields the proof of Theorem~\ref{thm:coarsestfiniteState}
 (\texttt{COARSEST_CONGR_FINITE}). The same proof idea can also be used with
  contraction and rooted contration.
-%  \hl{(In the future, we seek a method to
-% completely eliminate the finite-state hypothesis for our CCS syntax
-% with binary summation.)}
 

### 2019-12-15 ic-journal/context.tex
Synchronized all changes from .tex to .htex; clean up all reviewed highlights (adding 3 new)

@@
 
-% We need to find a suitable formal definition of 
-% context. There're multiple ways. Here 
-\hlD{CCS contexts are needed in defining (pre)congruence.
-To prevent doing variable substititions, one can take}
+CCS contexts are needed in defining (pre)congruence.
+To prevent doing variable substititions, one can take
  \univariate $\lambda$-expressions (of type
@@
 variable in \univariate CCS expressions or equations.
-\hl{Thus \emph{contexts} can be used both in (pre)congruence definitions
-and in formulating the unique solution of equations theorems in}
+Thus \emph{contexts} can be used both in (pre)congruence definitions
+and in formulating the unique solution of equations theorems in
 the \univariate case. The precise definition of CCS contexts is inductive:
@@
 \end{alltt}
-\hlD{In the above definition (actually generated by
-\texttt{HOL_reln}), for any process $p$,} (\HOLinline{\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{p}}) is a
-valid context with no hole \hlD{(similarly to an equation without variables).}
+In the above definition (actually generated by
+\texttt{HOL_reln}), for any process $p$, (\HOLinline{\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{p}}) is a
+valid context with no hole (similarly to an equation without variables).
 
-\hlD{Below is the formalisation  of Def.}~\ref{def:guardness}.
+Below is the formalisation  of Def.~\ref{def:guardness}.
 A context is \emph{weakly guarded} (\HOLinline{\HOLConst{WG}}) if each hole is underneath a prefix:
@@
 
-A context is \emph{\hl{(strongly)}  guarded} (\HOLinline{\HOLConst{SG}}) if each hole
+A context is \emph{(strongly)} guarded (\HOLinline{\HOLConst{SG}}) if each hole
 is underneath a \emph{visible} prefix:
@@
 
-\hl{Several}
+Several
 lemmas about the above concepts (\HOLinline{\HOLConst{CONTEXT}}, \HOLinline{\HOLConst{WG}},
-\HOLinline{\HOLConst{SEQ}}, etc.) \hl{are needed for capturing} properties about
+\HOLinline{\HOLConst{SEQ}}, etc.) are needed for capturing properties about
  the relationships among these kinds of contexts and about their
@@
   w.r.t~\HOLinline{\HOLConst{CONTEXT}}, it is substitutive w.r.t.~\HOLinline{\HOLConst{GCONTEXT}}
-as $\approx$ is  preserved by guarded sums. \hl{Similarily,
-contraction ($\mcontrBIS$) is  substitutive w.r.t.}~\HOLinline{\HOLConst{GCONTEXT}}.
+as $\approx$ is preserved by guarded sums. Similarily,
+contraction ($\mcontrBIS$) is substitutive w.r.t.~\HOLinline{\HOLConst{GCONTEXT}}.
 %

### 2019-12-15 ic-journal/contraction.tex
Synchronized all changes from .tex to .htex; clean up all reviewed highlights (adding 3 new)

@@
 brings a new proof technique for proving (weak) bisimilarities. However, it has
- limitations: the equations must be guarded and sequential. (\hl{Moreover,}
+ limitations: the equations must be guarded and sequential. (Moreover,
 all sums where equation variables appear must be guarded sums.)
 This limits the usefulness of the technique, since
-the occurrences of other operators \hl{using equation} variables, such as parallel
+the occurrences of other operators using equation variables, such as parallel
 composition and restriction,
-in general cannot be \hl{eliminated}. % without changing the meaning of equations
-The constraints \hl{in} Theorem~\ref{t:Mil89}, however, can be
+in general cannot be eliminated. % without changing the meaning of equations
+The constraints in Theorem~\ref{t:Mil89}, however, can be
 weakened if we move from equations to a special kind of inequations called
@@
 Intuitively, the bisimilarity contraction $\mcontrBIS$ is a preorder
-\hlD{in which} $P \mcontrBIS Q$ holds if $P \wb Q$ and, in addition, 
+in which $P \mcontrBIS Q$ holds if $P \wb Q$ and, in addition, 
 \emph{$Q$ has the possibility of being at least as efficient as $P$} (as far as
@@
 The process $Q$, however, may be nondeterministic and may have other ways
-\hl{to do} the same work, \hl{ways} which could be \hl{slower} (i.e., involving
+to do the same work, ways which could be slower (i.e., involving
 more $\tau$-actions than those performed by $P$).
@@
 \begin{enumerate}
-\item $P \arr\mu P'$ implies \hl{that} there is $Q'$ \hl{with} $Q \arcap \mu
+\item $P \arr\mu P'$ implies that there is $Q'$ with $Q \arcap \mu
   Q'$ and $P' \RR Q'$;
-\item $Q \arr\mu Q'$ implies \hl{that} there is $P'$ \hl{with} $P \Arcap \mu
+\item $Q \arr\mu Q'$ implies that there is $P'$ with $P \Arcap \mu
  P'$ and $P' \wb Q'$.
@@
 \end{definition}
-In clause (1) \hl{of the above definition}, $Q$ is required to match the challenge
-transition \hl{of $P$} with at most one transition.
+In clause (1) of the above definition, $Q$ is required to match the challenge
+transition of $P$ with at most one transition.
 This makes sure that $Q$ is capable of mimicking % verb: mimic
 $P$'s work at least as efficiently as $P$. 
-In contrast, \hl{clause (2) entirely ignores efficiency on the challenges from $Q$:}
+In contrast, clause (2) entirely ignores efficiency on the challenges from $Q$:
 the final derivatives are required to be related by $\wb$, rather than by $\R$.
@@
 Bisimilarity contraction is coarser than bisimilarity expansion
-$\expa$~\cite{arun1992efficiency,sangiorgi2015equations}, \hl{one of the
-most useful auxiliary relations in up-to techniques}:
+$\expa$~\cite{arun1992efficiency,sangiorgi2015equations}, one of the
+most useful auxiliary relations in up-to techniques:
 \begin{definition}[expansion]
@@
  \end{definition}
-\hl{Bisimilarity expansion} is widely used in proof techniques for bisimilarity.
-\hl{It} intuitively refines bisimilarity by 
+Bisimilarity expansion is widely used in proof techniques for bisimilarity.
+It intuitively refines bisimilarity by 
 formalising the idea of ``efficiency'' between processes.
-Clause (1) is the same in the both preorders, while in clause (2) expansion \hl{requires}
+Clause (1) is the same in the both preorders, while in clause (2) expansion requires
 $P \Arr \mu P'$, rather than $P \Arcap \mu P'$.
-\hl{Moreover,} in clause (2) of Def.~\ref{d:BisCon} the final derivatives
+Moreover, in clause (2) of Def.~\ref{d:BisCon} the final derivatives
 are simply required to be bisimilar ($P' \wb Q'$).
@@
 
-\hlD{Bisimilarity expansion and bisimilarity contraction are both
-preorders.}
+Bisimilarity expansion and bisimilarity contraction are both preorders.
 Similarily with (weak) bisimilarity, both the expansion and the
 contraction preorders are preserved by all CCS operators except the
-summation. The proofs are similar \hlD{to those for bisimilarity},
-see, e.g.~\cite{sangiorgi2017equations} \hl{for details.}
+summation. The proofs are similar to those for bisimilarity,
+see, e.g.~\cite{sangiorgi2017equations} for details.
 

### 2019-12-15 ic-journal/equa.tex
Synchronized all changes from .tex to .htex; clean up all reviewed highlights (adding 3 new)

@@
 variables also as \emph{equation variables}. This eliminates the need of
-\hl{an additional} type for \hl{CCS} equations, and we can reuse the existing
+an additional type for CCS equations, and we can reuse the existing
 variable substitution operation (cf.~the SOS rule for the Recursion in
-Fig.~\ref{f:LTSCCS}) for \hl{substitutions} of equation variables.
+Fig.~\ref{f:LTSCCS}) for substitutions of equation variables.
 For example, the result of substituting  variable $X$ with $\nil$ in $a.X +
-\recu X (b.X)$,  written \hl{as} $(a.X + \recu X (b.X)) \sub {\nil} X$, is
+\recu X (b.X)$,  written as $(a.X + \recu X (b.X)) \sub {\nil} X$, is
 $a.\nil + \recu X (b.X)$ with $\recu X (b.X)$
@@
 (or for $\rapprox$) can be obtained by replacing all occurrences of $\wb$
-in \hl{the} above definition with $\sim$ and $\rapprox$, respectively.
+in the above definition with $\sim$ and $\rapprox$, respectively.
 
@@
 \label{t:Mil89}
-Let $E_i$   \hl{(with only guarded sums)}  be guarded and sequential,
+Let $E_i$ (with only guarded sums) be guarded and sequential,
 and  with free
@@
 where $X$ is guarded but not sequential. Any process that does not perform
-$a$\hl{--action} is a solution, e.g. $\nil$ and $b.\nil$.
+$a$--action is a solution, e.g. $\nil$ and $b.\nil$.
 
-For more details \hl{on the formalisation of the} above three theorems, see Section~\ref{ss:part2}
+For more details on the formalisation of the above three theorems, see Section~\ref{ss:part2}
 for the \univariate case and Section~\ref{sec:multivariate} for the \multivariate case.

### 2019-12-15 ic-journal/expansion.tex
Synchronized all changes from .tex to .htex; clean up all reviewed highlights (adding 3 new)

@@
 Weak bisimilarity is not preserved by the sum operator (except for
-guarded sums), i.e.~$P_1 \wb Q_1$ and $P_2 \wb Q_2$  \hl{do} not imply
+guarded sums), i.e.~$P_1 \wb Q_1$ and $P_2 \wb Q_2$ do not imply
  $P_1 + P_2 \wb Q_1 + Q_2$.
-For this \hl{reason}, Milner introduced the concept of
+For this reason, Milner introduced the concept of
 \emph{observational congruence}, also called \emph{rooted
@@
 Relation $\rapprox$ is indeed preserved by the sum operator.
-% \hl{It can be proved that $P_1 \rapprox Q_1 \wedge P_2 \rapprox Q_2 \Longrightarrow
-% P_1 + P_2 \rapprox Q_1 + Q_2$.}
 The above definition also brings up a proof technique for proving rooted
@@
 indeed it is  the coarsest congruence contained in bisimilarity
-(see Section~\ref{s:coarsest} and \hl{\mbox{Section~\ref{ss:context}}} for more details):
+(see Section~\ref{s:coarsest} and Section~\ref{ss:context} for more details):
 \begin{theorem}

### 2019-12-15 ic-journal/formal.tex
Synchronized all changes from .tex to .htex; clean up all reviewed highlights (adding 3 new)

@@
 
-We highlight here a \hl{comprehensive} formalisation of CCS in the HOL theorem prover
+We highlight here a comprehensive formalisation of CCS in the HOL theorem prover
 (HOL4)~\cite{Melham:1993vl,slind2008brief}, with a focus towards the
@@
 As a consequence, theories and proofs verified in HOL are easier to understand
- \hl{for} people who are not familar with more advanced dependent type
- theories, \hl{e.g. the Calculus of Constructions implemented in Coq.}
+ for people who are not familar with more advanced dependent type
+ theories, e.g. the Calculus of Constructions implemented in Coq.
 
@@
 
-\hl{HOL terms} represent elements of the
-sets denoted by \hl{their} types. There are four kinds of \hl{HOL terms,
-which} can be described (in simplified forms) by the BNF grammar in
+HOL terms represent elements of the
+sets denoted by their types. There are four kinds of HOL terms,
+which can be described (in simplified forms) by the BNF grammar in
 Fig.~\ref{fig:hol-terms}. (See~\cite{hollogic} for a complete
-description of HOL, \hl{including the primitive derivative rules to be
-mentioned below.})
+description of HOL, including the primitive derivative rules to be
+mentioned below.)
 

### 2019-12-15 ic-journal/intro.tex
Synchronized all changes from .tex to .htex; clean up all reviewed highlights (adding 3 new)

@@
 the equations must be both \emph{guarded} and \emph{sequential}. That is,
-the variables of the equations can only occur underneath visible prefixes and \hl{summation}.
-One way to overcome \hl{these} limitations is to replace the equations
+the variables of the equations can only occur underneath visible prefixes and summation.
+One way to overcome these limitations is to replace the equations
 with special inequations called
-\emph{contractions}~\cite{sangiorgi2015equations,sangiorgi2017equations}. \hl{The
-contraction relation} is a
+\emph{contractions}~\cite{sangiorgi2015equations,sangiorgi2017equations}. The
+contraction relation is a
 preorder that, roughly, places some efficiency constraints on processes.
@@
 in~\cite{sangiorgi2017equations}
-(where the issue is bypassed \hl{by} using a more
+(where the issue is bypassed by using a more
 restrictive CCS syntax)
-is the occurrences of \hlD{arbitrary} sums (e.g.~$P + Q$) due to
+is the occurrences of arbitrary sums (e.g.~$P + Q$) due to
 the non-substitutivity of the contraction preorder in this case.
@@
 Indeed the formalisation encompasses all basic properties of strong,
-\hl{weak and rooted}
-bisimilarities (e.g.~the fixed-point and substitutivity properties), \hl{and} their algebraic laws.
+weak and rooted
+bisimilarities (e.g.~the fixed-point and substitutivity properties), and their algebraic laws.
 Further extensions include several versions of ``bisimulation up to''
-techniques, \hl{and properties of the expansion and contraction preorders}.
+techniques, and properties of the expansion and contraction preorders.
 Concerning rooted bisimilarity, the formalisation
@@
 the other one is 
-without such hypothesis, essentially \hl{formalising} van Glabbeek's proof~\cite{van2005characterisation}.
-\hl{With} this respect, the work is also an extensive experiment using the HOL theorem prover with its
+without such hypothesis, essentially formalising van Glabbeek's proof~\cite{van2005characterisation}.
+With this respect, the work is also an extensive experiment using the HOL theorem prover with its
 recent developments, including its coinduction package.
@@
 refined by moving from the contraction preorder to
-\emph{rooted contraction}, \hl{which is shown to be} the coarsest
+\emph{rooted contraction}, which is shown to be the coarsest
 precongruence contained in the contraction preorder.
@@
 \emph{rooted bisimilarity} (hence also for bisimilarity itself), and places no 
-constraints on \hl{summation}.
+constraints on summation.
 
@@
 for weak bisimilarity that use the contraction preorder as an
-auxiliary relation, and other \hl{unique-solution theorems} (e.g. the one
+auxiliary relation, and other unique-solution theorems (e.g. the one
 for rooted bisimilarity 
@@
 %
-In these cases, when moving between proofs there are only a few places \hl{in}
-the HOL proof scripts \hlD{that have} to be modified.
+In these cases, when moving between proofs there are only a few places in
+the HOL proof scripts that have to be modified.
 Then the successful termination of a proof gives us the
- guarantee that the proof is \hl{correct}, eliminating the risks 
+ guarantee that the proof is correct, eliminating the risks 
 of overlooking or missing details as in \emph{paper-and-pencil} proofs.
 
-\hl{Concerning the formalisation of unique-solution theorems,}
+Concerning the formalisation of unique-solution theorems,
 we first consider the case of a single equation (or contraction), the
 \emph{\univariate case}.
-\hl{Then we turn to} the \emph{\multivariate case} where more equations
-  (or contractions) with multiple equation variables \hl{are involved}.
-  The \univariate versions \hl{of the} unique-solution theorems
-  \hl{can directly use}
-$\lambda$-functions to \hl{represent} CCS equations,
-while the \multivariate versions \hl{require}
-more careful and delicate \hl{treatments} of CCS
+Then we turn to the \emph{\multivariate case} where more equations
+  (or contractions) with multiple equation variables are involved.
+  The \univariate versions of the unique-solution theorems
+  can directly use
+$\lambda$-functions to represent CCS equations,
+while the \multivariate versions require
+more careful and delicate treatments of CCS
 expressions, with multiple variables and substitutions acting on them.
@@
 in CCS terms are treated as  (free) equation variables, and a CCS
-process is a CCS \hl{expression} without equation variables.  % don't use "term"
+process is a CCS expression without equation variables.  % don't use "term"
 This allows us a smoother move from the \univariate case to the \multivariate
@@
 
-In Section~\ref{ss:ccs} \hl{we recall the core theory} of CCS,
+In Section~\ref{ss:ccs} we recall the core theory of CCS,
 including its syntax, operational semantics, bisimilarity and rooted
 bisimilarity.
-\hl{Then,} Section~\ref{s:eq} discusses equations and contractions, and in particular,
+Then, Section~\ref{s:eq} discusses equations and contractions, and in particular,
 Section~\ref{ss:new} presents rooted contraction and the related
@@
 Section~\ref{sec:multivariate} describes the extension to the \multivariate case.
-Finally, in Section~\ref{s:rel} and \ref{s:concl} \hl{we discuss} the related work,
+Finally, in Section~\ref{s:rel} and \ref{s:concl} we discuss the related work,
 conclusions, and a few directions for future work.

### 2019-12-15 ic-journal/multivariate.tex
Synchronized all changes from .tex to .htex; clean up all reviewed highlights (adding 3 new)

@@
 
-\hl{In this section we attack the case of 
-  multiple equations (the `\multivariate'  case), for two major theorems earlier discussed:}
+In this section we attack the case of
+  multiple equations (the `\multivariate' case), for two major theorems earlier discussed:
 Milner's ``unique solution of equations (for $\sim$)''
@@
 hold for even infinitely many equations and equation variables.}
-We chose these two theorems because \hlD{of their relevance}, and 
-because they well illustrate the \hlD{work} needed in the \multivariate case.
-% The work is a \hl{natural} extension of the existing work, for
-% \hl{no new algebraic type (e.g. the type for CCS processes) has to be defined,}
-% and neither the CCS syntax nor the SOS rules \hl{needs} to be changed.
+We chose these two theorems because of their relevance, and
+because they well illustrate the work needed in the \multivariate case.
 
@@
 equations, and variable substitutions are simply
-\hl{applications of} $\lambda$-functions to CCS terms.
+applications of $\lambda$-functions to CCS terms.
 This idea, however,
@@
  agent variables such as \texttt{var X}).
-% (Then the substitution of equation
-% variables in $E_i\{\til P/\til X\}$ would become the \emph{syntactic substitution} of
-% each occurrence of $X_i$ in $E_i$ with the corresponding $P_i$.)
 In either cases the \emph{disjointness} between equation variables and
@@
 \emph{same} alphabet for both agent variables and equation variables.
-This \hl{approach allows} a large reuse of the \univariate formalisation.
-For instance, the variable substitution \hlD{in the  SOS rule}
+This approach allows a large reuse of the \univariate formalisation.
+For instance, the variable substitution in the  SOS rule
 \texttt{REC} can be reused for substituting equation variables.
@@
 within our CCS syntax an agent variable may occur outside the recursion in which it is bound.
-\hl{Thus the same} variable can appear both \emph{free} and \emph{bound} in a CCS term.
+Thus the same variable can appear both \emph{free} and \emph{bound} in a CCS term.
 %
@@
 functions taking CCS terms and returning
-\hl{(finite)} sets of variables (of the type \HOLinline{\ensuremath{\alpha}}).
+(finite) sets of variables (of the type \HOLinline{\ensuremath{\alpha}}).
 % Milner didn't give their definitions explicitly. However, one can
@@
 $\fv{\mu.X} = \{X\}$. This property of $\fv{\cdot}$ brings some
-difficulities in \hl{transition inductions}. As an evidence,
+difficulities in transition inductions. As an evidence,
 we prove the following fundamental property of
@@
 We prove a stronger result, asserting that the set of free
-variables in a CCS process \hlD{does not increase} in its derivatives:
+variables in a CCS process does not increase in its derivatives:
 \begin{alltt}
@@
 commented as ``an easy action induction''.
-\hlD{As a matter of fact, in the  HOL proof}
- ``action induction'' %(or \emph{transition induction}) 
+As a matter of fact, in the HOL proof ``action induction''
 becomes a form of higher-order application
@@
 \end{alltt}
-The above long theorem is of the form \HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLBoundVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}} (with $a_0, a_1, a_2$ renamed), \hl{where} the
+The above long theorem is of the form \HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLBoundVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}} (with $a_0, a_1, a_2$ renamed), where the
 outermost universal quantifier $P$ is a higher-order
-proposition (\hl{taking} $E$, $\mu$ and $E'$), and $X$ is another higher-order
+proposition (taking $E$, $\mu$ and $E'$), and $X$ is another higher-order
 proposition.
-\hl{The proof goal} is actually in the form of
+The proof goal is actually in the form of
 \HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLFreeVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}}, where
@@
 % This is an easy goal, due to the following lemma which is
-%  proved by \hl{doing} induction on $E$:
+%  proved by doing induction on $E$:
 % \begin{alltt}
@@
 
-There are two natural ways to \hlD{implement} % not "represent" but actually "do"
-the \multivariate substitution $E\{\til P/\til X\}$, \hl{which} replaces each \hl{free
-occurrence} of the variables $X_i$ in $E$ with the corresponding
+There are two natural ways to implement
+the \multivariate substitution $E\{\til P/\til X\}$, which replaces each free
+occurrence of the variables $X_i$ in $E$ with the corresponding
 $P_i$: (1) iterately applying the existing \univariate
@@
 a \multivariate version of \HOLinline{\HOLConst{CCS_Subst}}
-called \HOLinline{\HOLConst{CCS_SUBST}}, based \hl{on} HOL
+called \HOLinline{\HOLConst{CCS_SUBST}}, based on HOL
 \texttt{finite\_map} theory~\cite{holdesc}.
@@
 and returns another CCS expression in which
-all occurrences of variables in \hl{the finite domain of} \HOLinline{\HOLFreeVar{fm}} are substituted with
-the corresponding value in \HOLinline{\HOLFreeVar{fm}}. \hl{Initially,} such a finite map can be built from
+all occurrences of variables in the finite domain of \HOLinline{\HOLFreeVar{fm}} are substituted with
+the corresponding value in \HOLinline{\HOLFreeVar{fm}}. Initially, such a finite map can be built from
 a list of variables \HOLinline{\HOLFreeVar{Xs}} and the corresponding substituted terms
@@
 abbreviated as \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}.
-Using maps, the substitution mechanism is order-independent. For most CCS operators,
+Using \hl{finite} maps, the substitution mechanism is order-independent. For most CCS operators,
 \HOLinline{\HOLConst{CCS_SUBST}}
- recursively calls itself on subterms.  \hlD{The} most
+ recursively calls itself on subterms. The most
 interesting cases are at agent variables and recursion:
@@
 
-In \hl{some of} the above lemmas, the condition
+In some of the above lemmas, the condition
 \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}} (the bound
 variables of $E$ and the free substitution variables are disjoint) is
-added to ease the proofs. The 
-condition
+added to ease the proofs. The condition
 is not necessary and could be eliminated, at the price of some extra effort.
-% \hl{As many of these lemmas are used in proving other theorems, eventually}
-% the disjointness condition are propagated everywhere.
 
@@
 \HOLinline{\HOLConst{CONTEXT}}
-(\hl{multi-hole} contexts), \HOLinline{\HOLConst{WG}} (weak guarded contexts),
+(multi-hole contexts), \HOLinline{\HOLConst{WG}} (weak guarded contexts),
 \HOLinline{\HOLConst{SG}} (guarded contexts) and \HOLinline{\HOLConst{SEQ}} (sequential
-contexts), are \hl{all} defined inductively, i.e.~they are built from some ``holes''
-in a bottom-up \hl{manner}.
+contexts), are all defined inductively, i.e.~they are built from some ``holes''
+in a bottom-up manner.
 For instance, \HOLinline{\HOLConst{WG}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\\\;\HOLSymConst{\ensuremath{\mid}}\\\;\HOLFreeVar{P}\ensuremath{)}}
@@
 It could be possible to inductively define \multivariate contexts and their
-guarded variants, but care is needed
-for 
- variables that occur \hl{within a  recusion}.  \hl{We have preferred a different
-   solution,} in which the definitions of 
- \multivariate contexts  is based on the
+guarded variants, but care is needed for
+variables that occur within a recusion. We have preferred a different
+solution, in which the definitions of \multivariate contexts  is based on the
 existing \univariate definitions.
-\hlD{For this, intuitively,  we replace a single variable with a hole  (viewing
+For this, intuitively, we replace a single variable with a hole (viewing
 the other variables as constants), so to obtain a  single-variable context
-on which predicates like} \HOLinline{\HOLConst{CONTEXT}} can be used.
+on which predicates like \HOLinline{\HOLConst{CONTEXT}} can be used.
 For example, to see the weak guardedness of $a.X + b.X + c.Y$,
@@
 Then a logical term ``\HOLinline{\HOLConst{weakly_guarded}\\\;\ensuremath{(}\HOLConst{SET_TO_LIST}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\ensuremath{)}\\\;\HOLFreeVar{E}}'' can
-be used \hl{to} assert the weak guardedness of $E$ w.r.t.~all its free
+be used to assert the weak guardedness of $E$ w.r.t.~all its free
 variables.\footnote{Here \HOLinline{\HOLConst{SET_TO_LIST}} converts a finite set
@@
 Similar properties also hold if $\sim$ is replaced with rooted
-bisimilarity ($\rapprox$) \hl{and} rooted contraction ($\rcontr$). It does
+bisimilarity ($\rapprox$) and rooted contraction ($\rcontr$). It does
 not hold for weak bisimilarity ($\wb$) and the contraction
-preorder ($\mcontrBIS$), \hl{as they are not (pre)congruence relations}.
+preorder ($\mcontrBIS$), as they are not (pre)congruence relations.
 
 Another important property of contexts is their composability: if we
-substitute some free variables in a context \hl{with} some other contexts, the
-resulting term is still a \hl{valid} context (w.r.t.~the same set of variables):
+substitute some free variables in a context with some other contexts, the
+resulting term is still a valid context (w.r.t.~the same set of variables):
 \begin{alltt}
@@
 On the other hand, not every term within the CCS syntax is a context, as
-\hl{context (or equation) variables are not allowed to occur within recursion. The converse
-holds however:} if the set of free variables of a CCS term
+context (or equation) variables are not allowed to occur within recursion. The converse
+holds however: if the set of free variables of a CCS term
 is disjoint from a list of variables, then the term is indeed a context
@@
 Note that, in the above lemma we cannot
-conclude
-\HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}},
+conclude \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}},
 because $Y$ may appear in both sets.
-%, as a bound
-%variable of $\recu Y E$, may also be a free variable in $\til X$.
- We
-also cannot conclude \HOLinline{\HOLConst{context}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{E}}, because in $\recu Y E$
-the bound variable $Y$ \hlD{may occur {freely} within another nested}
-recursion. \hl{For instance,} variable $Y$ is free   
-in $\recu Y E $ , for 
- $E = \recu Z (a.Y + b.Z) + c.Y$.
+We also cannot conclude \HOLinline{\HOLConst{context}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{E}}, because in $\recu Y E$
+the bound variable $Y$ may occur freely within another nested
+recursion. For instance, variable $Y$ is free
+in $\recu Y E$ , for $E = \recu Z (a.Y + b.Z) + c.Y$.
 
 For weakly guarded contexts, % (which are also normal contexts),
-besides
-their usual properties  as in the \univariate case (i.e., weak
-guardedness,
-\HOLinline{\HOLConst{WG}}), we also need
+besides their usual properties as in the \univariate case (i.e., weak
+guardedness, \HOLinline{\HOLConst{WG}}), we also need
 their composability w.r.t.~\multivariate contexts: if we
 substitute some free variables in a context $C$ with some weakly guarded
-contexts, the resulting \hlD{context is} weakly guarded (w.r.t.~the same set of variables):
+contexts, the resulting context is weakly guarded (w.r.t.~the same set of variables):
 \begin{alltt}
@@
 length, and  the variables in $\til X$ should  be distinct.
-Furthermore,  $\til E$ does not contain
- free variables that are not in $\til X$.
-\hlD{Finally, } for each
-$E_i$, the set of its bound variables should be \emph{disjoint} from
-$\til X$. 
-% \hl{(In practice, however, one can always
-% rename all recursion binders in the equations to satisfy this
-% requirement without changing the semantics of equations.)}
+Furthermore, $\til E$ does not contain free variables that are not in $\til X$.
+Finally, for each
+$E_i$, the set of its bound variables should be \emph{disjoint} from $\til X$.
 These requirements yield the fomal
@@
 can be used to represent solutions of all kinds of CCS
-\hlD{equations.} Then,  ${\til P} \ \R\  {\til E}\{\til
-P/\til X\}$  should hold:
+equations. Then, ${\til P} \ \R\  {\til E}\{\til P/\til X\}$ should hold:
 \begin{equation*}
@@
   CCS processes with the same length.
- % Furthermore,  \HOLinline{\HOLConst{LIST_REL}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{A}\\\;\HOLFreeVar{B}}
-  implicitly   implies that the two lists $A$ and $B$ have the same length.
-}
+  implicitly implies that the two lists $A$ and $B$ have the same length.}
 \begin{alltt}
@@
 
-\hlD{Now} the \multivariate version of Theorem~\ref{t:rcontraBisimulationU}:
+Now the \multivariate version of Theorem~\ref{t:rcontraBisimulationU}:
 \begin{alltt}
@@
  the overall proofs is the same;  
-various proof \hl{steps} can even be copied from the \univariate \hl{case}.
+various proof steps can even be copied from the \univariate case.
+
+% next file: related.tex

### 2019-12-15 ic-journal/part2.tex
Synchronized all changes from .tex to .htex; clean up all reviewed highlights (adding 3 new)

@@
 
-\hl{In this section we describe the formalisation of Milner's
-``unique solution of equations'' theorems, limited to} \univariate equations. (The
+In this section we describe the formalisation of Milner's
+``unique solution of equations'' theorems, limited to \univariate equations. (The
 \multivariate extension is described in Section~\ref{sec:multivariate}.)
@@
 
-\hl{Using ``bisimulation up to $\sim$'' technique}, we obtain the following
+Using ``bisimulation up to $\sim$'' technique, we obtain the following
 key lemma, which states that, if $X$ is weakly guarded
@@
 ``bisimulation up-to'' technique.
-\hl{Instead,} we have used a different
+Instead, we have used a different
 technique based on Lemma~\ref{l:obsCongrByWeakBisim}, whose formal
@@
 \end{alltt}
-\hlD{Using Lemma}~\ref{l:obsCongrByWeakBisim}, \hl{the next two results} are proved by 
+Using Lemma~\ref{l:obsCongrByWeakBisim}, the next two results are proved by 
 directly constructing the required bisimulation:
@@
 version for weak bisimilarity (Theorem~\ref{t:Mil89}) that shares a large portion of proof
-steps with the proof for \hl{rooted bisimilarity.}
+steps with the proof for rooted bisimilarity.
 As weak bisimilarity is not a congruence, we have to be more restrictive
-on the syntax of the equation, \hlD{using only guarded sums.}
+on the syntax of the equation, using only guarded sums.
 The related formal proofs are tedious but closely follow the informal
-proof~\citep[p.~158--159]{Mil89}, \hlD{with the exception of the use  of} ``bisimulation up
+proof~\citep[p.~158--159]{Mil89}, with the exception of the use of ``bisimulation up
 to with weak arrows'' (Def.~\ref{def:doubleweak}, instead of Def.~\ref{def:singleweak}).
@@
 A delicate point in the formalisation of the results about unique solution of
-contractions \hl{is} the proof of Lemma~\ref{l:ruptocon} and lemmas alike.
-\hlD{In particular, we use} induction on the length of weak transitions.
+contractions is the proof of Lemma~\ref{l:ruptocon} and lemmas alike.
+In particular, we use induction on the length of weak transitions.
 For this, rather than introducing a refined form of weak transition relation
 enriched with its length, we found it more elegant to work with
-\emph{traces}, \hlD {sequences of transitions.}
+\emph{traces}, sequences of transitions.
 (A further motivation is to set the ground for future extensions of this
@@
  (\HOLinline{\HOLConst{LRTC}}).
-\hl{Then,} given any labeled transition relation \HOLinline{\HOLFreeVar{R}} (of  type
+Then, given any labeled transition relation \HOLinline{\HOLFreeVar{R}} (of type
 ``\HOLinline{\ensuremath{\alpha} \HOLTokenTransEnd \ensuremath{\beta} \HOLTokenTransEnd \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}''), \HOLinline{\HOLConst{LRTC} \HOLFreeVar{R}} is
-a relation representing \hl{traces over} \HOLinline{\HOLFreeVar{R}}  (of type
+a relation representing traces over \HOLinline{\HOLFreeVar{R}} (of type
 ``\HOLinline{\ensuremath{\alpha} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{list} \HOLTokenTransEnd \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}''):
@@
 is then obtained
- by \hl{combining} \texttt{LRTC} and the \texttt{TRANS}
+ by combining \texttt{LRTC} and the \texttt{TRANS}
  ($\overset{\mu}{\rightarrow}$) relation defining the SOS rules:
@@
 
-\hlD{In a  trace  $P\overset{acts}{\longrightarrow}Q$,}
+In a trace  $P\overset{acts}{\longrightarrow}Q$,
  the list of actions $acts$ may be  empty, in which case there is no transition, and 
  the initial and final processes are the same, i.e. $P = Q$.
-\hlD{If there is at most one visible action $\mu$  in $acts$, and all other actions are $\tau$'s,}
+If there is at most one visible action $\mu$  in $acts$, and all other actions are $\tau$'s,
 then the trace represents a weak transition $P \Arr{\mu} Q$.
@@
 the list of actions: no label and unique label. The definition of ``no
-label'' for a list of  actions is as follows, where \texttt{MEM} tests if \hl{an} element is a member of a list:
+label'' for a list of  actions is as follows, where \texttt{MEM} tests if an element is a member of a list:
 \begin{alltt}
@@
 It says that a label is unique in a list of actions if there is no
-label in the rest of list (here $\HOLTokenDoublePlus$ \hlD{is the concatenation
-of lists}):
+label in the rest of list (here $\HOLTokenDoublePlus$ is the concatenation
+of lists):
 \begin{alltt}
@@
 
-\hlD{Finally, the  relationship} between traces and weak transitions is stated
-and proved in the following theorem.  \hl{It} says that a weak transition $P \Arr{u} P'$ is also a
+Finally, the relationship between traces and weak transitions is stated
+and proved in the following theorem. It says that a weak transition $P \Arr{u} P'$ is also a
 trace $P\overset{acts}{\longrightarrow}P'$ with a
@@
 The two proofs are similar, mostly because
-the main property needed from \hlD{contraction and rooted contraction is} precongruence.
+the main property needed from contraction and rooted contraction is precongruence.
 Below is the formal version of Theorem~\ref{t:rcontraBisimulationU}:
@@
 which has no more constraints on summation (as shown by the appearance of
-\texttt{WG} rather than \texttt{WGS}).
+\HOLinline{\HOLConst{WG}} rather than \HOLinline{\HOLConst{WGS}}).
 % (cf.~\texttt{UNIQUE_SOLUTION_OF_CONTRACTIONS}).
 
-Having removed the constraints on \hl{summation}, 
+Having removed the constraints on summation,
 this result is close to Milner's original `unique solution of
 equations' theorem for \emph{strong} bisimilarity  (Theorem~\ref{t:Mil89s1})~--- 
-the same weakly guarded context (\texttt{WG}) is required.
+the same weakly guarded context (\HOLinline{\HOLConst{WG}}) is required.
 %(cf.~Theorem~\ref{thm:Mil89s1f}, \texttt{STRONG_UNIQUE_SOLUTION}).

### 2019-12-15 ic-journal/sos.tex
Synchronized all changes from .tex to .htex; clean up all reviewed highlights (adding 3 new)

@@
 for all labels (i.e. visible actions), where the type variable $\beta$ corresponds
-to $\mathscr{L}$ (the set of names for labels) \hl{mentioned} at the beginning
+to $\mathscr{L}$ (the set of names for labels) mentioned at the beginning
 of Section~\ref{ss:ccs}. (Thus the
-cardinality of ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}''  \hlD{depends on its type variable:
-\mbox{when $\beta$ is finite or countable, ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is countable.}})
+cardinality of ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' depends on its type variable:
+when $\beta$ is finite or countable, ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is countable.)
 All labels are divided into input and output ones.
@@
 The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
-union of \hl{all visible actions (input and output labels) and the invisible action} $\tau$
+union of all visible actions (input and output labels) and the invisible action $\tau$
 (\texttt{tau}). For instace, the input \emph{action} $a$ and output
@@
 are denoted by \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLStringLit{a}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLStringLit{b}\ensuremath{)}}, respectively.
-\hl{On the
-other hand,} \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLNumLit{1}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLNumLit{2}\ensuremath{)}} could be actions of the type ``\HOLinline{\HOLTyOp{num} \HOLTyOp{Action}}'', where
+On the
+other hand, \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLNumLit{1}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLNumLit{2}\ensuremath{)}} could be actions of the type ``\HOLinline{\HOLTyOp{num} \HOLTyOp{Action}}'', where
 \HOLinline{\HOLTyOp{num}} is the type of natural numbers in HOL.
@@
 \end{lstlisting}
-The above \hl{definition allows us to write} terms like \texttt{nil} and
+The above definition allows us to write terms like \texttt{nil} and
 \texttt{sum P Q} in HOL4. Their correspondences with conventional CCS notations
 in the literature are given in Table~\ref{tab:ccsoperator}, where
-most CCS operators have also more readable \hl{abbreviated} forms,
+most CCS operators have also more readable abbreviated forms,
 either for end users or for \TeX{} outputs. (All
@@
   are generated from HOL4. Also, by default, all theorems are fully
-  specialised with outermost universal quantifiers \hl{removed.})
+  specialised with outermost universal quantifiers removed.)
 
@@
 \begin{itemize}
-  \item
-\emph{rules} is a conjunction of implications (each
+  \item \emph{rules} is a conjunction of implications (each
     corresponding to a SOS rule) that will be the
     same as the input term.
-% \emph{rules} is a conjunction of implications that will be the
-%    same as the input term. 
     In fact, the following formal versions of SOS rules are
@@
 \end{alltt}  
-For instance, \hlD{the following proposition
-need the above \emph{cases} theorem}:
+For instance, the following proposition \hl{needs} the above \emph{cases} theorem:
 \begin{alltt}
@@
 
-\hl{In particular,} the SOS rule \texttt{REC} (Recursion)
+In particular, the SOS rule \texttt{REC} (Recursion)
  says that, if we substitute all occurrences of the variable $A$ in $P$ to
@@
 for ``\HOLinline{\HOLConst{CCS_Subst}\;\;\HOLFreeVar{E}\;\;\ensuremath{(}\HOLConst{rec}\;\;\HOLFreeVar{X}\;\;\HOLFreeVar{E}\ensuremath{)}\;\;\HOLFreeVar{X}}'', where \HOLinline{\HOLConst{CCS_Subst}} is a
-recursive function substituting all \hl{occurrences} of a free variable with a CCS term.
+recursive function substituting all occurrences of a free variable with a CCS term.
 For most CCS operators \HOLinline{\HOLConst{CCS_Subst}} just recursively goes into a deeper
@@
 A useful facility exploiting the interplay
-between HOL4 and Standard ML (\hl{which} follows an idea of Nesi~\cite{Nesi:1992ve})
+between HOL4 and Standard ML (which follows an idea of Nesi~\cite{Nesi:1992ve})
  is a recursive ML function that takes a CCS process and returns a theorem indicating all
@@
 For instance, we know that the process $(a.\nil | \bar{a}.\nil)$ has three
-\hl{immediate derivatives given by the following transitions}:
+immediate derivatives given by the following transitions:
 $(a.\nil | \bar{a}.\nil) \overset{a}{\longrightarrow}

### 2019-12-15 ic-journal/unique.tex
Synchronized all changes from .tex to .htex; clean up all reviewed highlights (adding 3 new)

@@
 let $\ctpp {\til P}$ and $\ctpp {\til Q}$  be the processes obtained
-from  $\ct {\til P}$ and $\ct {\til Q}$ by unfolding the \hl{definition
-of $\mcontrBIS$ for} $n$ times. Thus in $\qctpp$ each hole is
-underneath at least $n$ prefixes, and \hl{therefore} cannot contribute to an action
-in the first $n$ transitions. \hl{Moreover}, all \hl{involved} contexts use guarded sums.
+from  $\ct {\til P}$ and $\ct {\til Q}$ by unfolding the definition
+of $\mcontrBIS$ for $n$ times. Thus in $\qctpp$ each hole is
+underneath at least $n$ prefixes, and therefore cannot contribute to an action
+in the first $n$ transitions. Moreover, all involved contexts use guarded sums.
 
@@
 However, compared with Milner's Theorem~\ref{t:Mil89s1}, there remains
-\hlD{the limitation on the need of 
-guarded sums}. This is mainly due to the fact that $\wb$ is not a
+the limitation on the need of 
+guarded sums. This is mainly due to the fact that $\wb$ is not a
  congruence and also $\mcontrBIS$ is not a precongruence.
@@
 The above definition was found with the help of interactive theorem proving.
-The following two principles were adopted when \hl{manually} searching
+The following two principles were adopted when manually searching
 for a possible definition: (1) the definition should not be coinductive,
@@
 relation $\mcontrBIS$.
-Furthermore, we needed to \hl{prove} that the definition \hl{being found}
+Furthermore, we needed to prove that the definition being found
 indeed yields the coarsest precongruence
-\hl{contained} in $\mcontrBIS$. The proof is similar with
+contained in $\mcontrBIS$. The proof is similar with
 the analogous result for $\rapprox$. See Section~\ref{s:coarsest} for
@@
 Theorem~\ref{t:contraBisimulationU} can now be stated without
-constraints on \hl{summation}.
+constraints on summation.
 The schema of the proofs is almost identical, because all 
 properties of $\rcontr$ needed in this proof is its precongruence, which is
-indeed true for \hl{all weakly guarded contexts:} % removed "direct sums"
+indeed true for all weakly guarded contexts: % removed "direct sums"
 \begin{lemma}
@@
 \label{t:rcontraBisimulationU}
-Let $E_i$ be weakly guarded with free variables \hlD{in} $\til X$,
+Let $E_i$ be weakly guarded with free variables in $\til X$,
 and let $\til P \rcontr \til E\{\til P/\til X\}$,

### 2019-12-16 ic-journal/coarsest.tex
Fixed other small issues per email discussions.

@@
 summation (and it is not easy to extend it with this support).
-Another more important reason is that, the typed logic
+Another more important reason is that the typed logic
 implemented in various HOL systems (including Isabelle/HOL) is not

### 2019-12-16 ic-journal/multivariate.tex
Fixed other small issues per email discussions.

@@
 In a  formalisation, this means either defining a
-whole new datatype (with extra equation variables), in which each CCS
+whole new datatype (with the new equation variables), in which each CCS
 operator must be duplicated, or adding equation variables as a
-new primitive (e.g.~\texttt{Var X}) to the existing CCS type (besides
- agent variables such as \texttt{var X}).
+new primitive to the existing CCS type.
 In either cases the \emph{disjointness} between equation variables and
@@
 (finite) sets of variables (of the type \HOLinline{\ensuremath{\alpha}}).
-% Milner didn't give their definitions explicitly. However, one can
-% imagine that, for most CCS operators they just pass into
-% subterms without collecting anything (and $\nil$ gives $\emptyset$).
 For their definition the interesting cases are those of
@@
 $\fv{\mu.X} = \{X\}$. This property of $\fv{\cdot}$ brings some
+%% "transition induction" (1/2)
 difficulities in transition inductions. As an evidence,
@@
 commented as ``an easy action induction''.
-As a matter of fact, in the HOL proof ``action induction''
+As a matter of fact, in the HOL proof ``action induction'' (also
+known as \emph{transition induction})
 becomes a form of higher-order application
@@
 \end{alltt}
-Note that \HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLConst{DELETE}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{=}}\\\;\HOLConst{FV}\\\;\ensuremath{(}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{)}}, so
-this is indeed the consequence of action induction on the Recursion.
+Note that \HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLConst{DELETE}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{=}}\\\;\HOLConst{FV}\\\;\ensuremath{(}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{)}}, thus
+the current proof goal is indeed the consequence of action induction on the
+recursion operator.
 Here the problem is that we know nothing about
@@
 On the other hand, the analogous
-result for bound variables is indeed just an easy transition
-induction. (The easy proof is omitted.)
+result for bound variables is indeed just a simple
+%% transition induction
+transition induction. (The easy proof is omitted.)
 \begin{proposition}
@@
 different orders of iterated substitutions may lead to different results.
-To obtain the maximal flexibility with reduced efforts, we defined
-a \multivariate version of \HOLinline{\HOLConst{CCS_Subst}}
+We thus prefer to define a \multivariate version of \HOLinline{\HOLConst{CCS_Subst}}
 called \HOLinline{\HOLConst{CCS_SUBST}}, based on HOL
@@
 abbreviated as \HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}.
-Using \hl{finite} maps, the substitution mechanism is order-independent. For most CCS operators,
+Using finite maps, the substitution mechanism is order-independent. For most CCS operators,
 \HOLinline{\HOLConst{CCS_SUBST}}
@@
 For example, to see the weak guardedness of $a.X + b.X + c.Y$,
-we focus on each (free) variable, we substitute each
-occurrence of a variable, say $X$, with a ``hole'' and see the
-resulting term as a $\lambda$-function; then all such $\lambda$-functions
+we substitute each occurrence of a variable with a ``hole'' and consider the
+resulting term as a multi-hole context (i.e., a $\lambda$-function); then all such multi-hole contexts
 should satisfy \HOLinline{\HOLConst{WG}}, i.e.~the following results hold:
@@
 variables.\footnote{Here \HOLinline{\HOLConst{SET_TO_LIST}} converts a finite set
-  to a list of the same elements. It turns out that, we never need this, because
+  to a list of the same elements. It turns out that we never need this, because
   in all unique-solution theorems a list of variables \HOLinline{\HOLFreeVar{Xs}} is fixed and
@@
 
-The most important property of \multivariate contexts is that, strong bisimilarity
+The most important property of \multivariate contexts is that strong bisimilarity
 and other (pre)congruence relations are preserved by them, for instance:
@@
 
-On the other hand, not every term within the CCS syntax is a context, as
+Not every term within the CCS syntax is a context, as
 context (or equation) variables are not allowed to occur within recursion. The converse
@@
 \end{alltt}
-Note that, in the above lemma we cannot
+In the above lemma we cannot
 conclude \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}},
@@
 Note that the two logical terms ``\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}\\\;\HOLFreeVar{Ps}}'' and ``\HOLinline{\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenIn{}}\\\;\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}'' in
-HOL have the same meaning. The latter form suggests that,
+HOL have the same meaning. The latter form suggests that
 ``\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}'' is actually a set containing all
@@
 \end{alltt}
-% Notice that, while Milner did not pointed out explicitly, the involved
-% weakly guarded context $E$ must contain free variables up to $\til
-% X$~--- the same requirement as in Theorem~\ref{t:Mil89s1}, which
-% otherwise does not complete. Besides, we further required that, the
-% bound variables of $E$ must be disjoint with $\til X$.
 

### 2019-12-16 ic-journal/part2.tex
Fixed other small issues per email discussions.

@@
 
-Milner~\cite{Mil89} \emph{only mentioned} two ``unique solution of
+Milner~\cite{Mil89} only mentioned two ``unique solution of
 equations'' theorems, one for strong equivalence, the other for
@@
 enriched with its length, we found it more elegant to work with
-\emph{traces}, sequences of transitions.
+\emph{traces}, i.e., sequences of transitions.
 (A further motivation is to set the ground for future extensions of this

### 2019-12-16 ic-journal/sos.tex
Fixed other small issues per email discussions.

@@
 \end{alltt}  
-For instance, the following proposition \hl{needs} the above \emph{cases} theorem:
+For instance, the following proposition needs the above \emph{cases} theorem:
 \begin{alltt}
@@
 For most CCS operators \HOLinline{\HOLConst{CCS_Subst}} just recursively goes into a deeper
-level without changing anything, e.g.
+level without changing anything, e.g.:
 \begin{alltt}
@@
 \end{alltt}
-Notice that, variable substitutions only affect free
+Notice that variable substitutions only affect free
 variables. For instance, the variable $Y$ in ``\HOLinline{\HOLConst{rec}\!\;\HOLFreeVar{Y}\!\;\HOLFreeVar{E}}'' is

### 2019-12-16 ic-journal/multivariate.tex
Fixed generated definitions for CCS_solution_def and CCS_equation_def (they were wrongly generated as theorems)

@@
 \begin{alltt}
-   \HOLTokenTurnstile{} \HOLConst{CCS_equation} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenEquiv{}}
+   \HOLConst{CCS_equation} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLTokenDefEquality{}
      \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}}
      \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
-\HOLConst{FV} \HOLBoundVar{e} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
-      \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
+\HOLConst{FV} \HOLBoundVar{e} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
 \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Es}\hfill{[CCS_equation_def]}
@@
 \begin{alltt}
-   \HOLTokenTurnstile{} \HOLConst{CCS_solution} \HOLFreeVar{R} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenEquiv{}}
+   \HOLConst{CCS_solution} \HOLFreeVar{R} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLFreeVar{Ps} \HOLTokenDefEquality{}
      \HOLConst{ALL_PROC} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
@@
 With all above machineries of \multivariate contexts and substitutions,
-the \multivariate case of Lemma~\ref{lem:milner313} is formalised below:
+the \multivariate case of Lemma~\ref{lem:milner313} is formalised
+below (\texttt{strong_unique_solution_lemma}):
 \begin{alltt}

### 2019-12-16 ic-journal/multivariate.tex
Removed the unnecessary definition names (CCS_eqaution_def and CCS_solution_def) for lacking spaces

@@
 \HOLConst{FV} \HOLBoundVar{e} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
-\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Es}\hfill{[CCS_equation_def]}
+\HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Es}
 \end{alltt}
@@
 \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-     \HOLConst{LIST_REL} \HOLFreeVar{R} \HOLFreeVar{Ps} \ensuremath{(}\HOLConst{MAP} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{Es}\ensuremath{)}\hfill{[CCS_solution_def]}
+     \HOLConst{LIST_REL} \HOLFreeVar{R} \HOLFreeVar{Ps} \ensuremath{(}\HOLConst{MAP} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{Es}\ensuremath{)}
 \end{alltt}

### 2019-12-16 ic-journal/multivariate.tex
Fixed a double "the" (the the) ignored due to line breaks in latex source.

@@
 step related to \multivariate substitutions is more difficult than
-that for the \univariate case, the structure of the 
- the overall proofs is the same;  
+that for the \univariate case, the structure of the overall proofs is the same;  
 various proof steps can even be copied from the \univariate case.

### 2019-12-16 ic-journal/conclusions.tex
paper-pencil -> paper-and-pencil (appeared once in intro.tex)

@@
 present a few delicate and subtle differences in a few points. In a
-paper-pencil proof, checking all details would be long and
+paper-and-pencil proof, checking all details would be long and
 error-prone, especially in cases where the proofs are similar to each

### 2019-12-17 ic-journal/sos.tex

@@
 A successful invocation of the definitional principle returns three
-important theorems (\emph{rules}, \emph{ind} and \emph{cases}):
+important theorems (\texttt{TRANS_rules}, \texttt{TRANS_ind} and \texttt{TRANS_cases}):
 \begin{itemize}
-  \item \emph{rules} is a conjunction of implications (each
+  \item \texttt{TRANS_rules} is a conjunction of implications (each
     corresponding to a SOS rule) that will be the
-    same as the input term.
-    In fact, the following formal versions of SOS rules are
+    same as the input term. In fact, the following formal versions of SOS rules are
     extracted from the \emph{rules} theorem:
@@
 \end{equation*}
-\item \emph{ind} is the induction principle for the relation
-  (see Section~\ref{sec:multivariate} for the exact form and its application).
-\item \emph{cases} is the so-called `cases' or `inversion' theorem for
+\item \texttt{TRANS_ind} is the induction principle for the relation
+  (see Section~\ref{sec:multivariate} for its exact statement and an
+  application in the proof of Proposition~\ref{prop:transFV}).
+\item \texttt{TRANS_cases} is the so-called `cases' or `inversion' theorem for
   the relation, and is used to decompose an element in the relation into the possible ways of
@@
 \end{alltt}  
-For instance, the following proposition needs the above \emph{cases} theorem:
+For instance, the following proposition requires \texttt{TRANS_cases}:
 \begin{alltt}

### 2019-12-17 ic-journal/multivariate.tex
proof would be complete -> proof would complete
any two (syntactically different) elements in the solution set -> any two elements in the solution set

@@
        \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}.
-\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\hfill{[TRANS_IND]}
+\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\hfill{[TRANS_ind]}
 \end{alltt}
@@
 \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}, no matter if \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E}} or not, and the proof
-would be complete. Thus it remains to show that
+would complete. Thus it remains to show that
 \begin{alltt}
@@
 Note that the two logical terms ``\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}\\\;\HOLFreeVar{Ps}}'' and ``\HOLinline{\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenIn{}}\\\;\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}'' in
-HOL have the same meaning. The latter form suggests that
+HOL have the same meaning (they are equivalent). The latter form suggests that
 ``\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}'' is actually a set containing all
 solutions of ``\HOLinline{\HOLConst{CCS_equation}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}''. Then the unique-solution
-theorems can be understood thus: any two (syntactically different) elements
+theorems can be understood thus: any two elements
 in the solution set are bisimilar.

### 2019-12-17 ic-journal/coarsest.tex
Changed most "w.r.t." to "with respect to"; removed "the" from (of the type ...) following other papers.

@@
  summation, we also consider the relation closure of bisimilarity
- w.r.t. summation, called \emph{equivalence compatible with summation}
+ \hl{with respect to} summation, called \emph{equivalence compatible with summation}
 (\texttt{SUM_EQUIV}): %%, denoted by $\approx^+$: (not used this symbol)
@@
 
-For any ``\HOLinline{\HOLConst{label}\;\HOLFreeVar{a}}'', having a function ``\HOLinline{\HOLConst{KLOP}\;\HOLFreeVar{a}}'' (of the type ``\HOLinline{\HOLTyOp{num} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
+For any ``\HOLinline{\HOLConst{label}\;\HOLFreeVar{a}}'', having a function ``\HOLinline{\HOLConst{KLOP}\;\HOLFreeVar{a}}'' (\hl{of type} ``\HOLinline{\HOLTyOp{num} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
 defined on the natural numbers, we obtain a countable set of processes

### 2019-12-17 ic-journal/context.tex
Changed most "w.r.t." to "with respect to"; removed "the" from (of the type ...) following other papers.

@@
 Although weak bisimilarity ($\approx$) is \emph{not} a congruence
-  w.r.t~\HOLinline{\HOLConst{CONTEXT}}, it is substitutive w.r.t.~\HOLinline{\HOLConst{GCONTEXT}}
+\hl{with respect to}~\HOLinline{\HOLConst{CONTEXT}}, it is substitutive
+\hl{with respect to}~\HOLinline{\HOLConst{GCONTEXT}}
 as $\approx$ is preserved by guarded sums. Similarily,
-contraction ($\mcontrBIS$) is substitutive w.r.t.~\HOLinline{\HOLConst{GCONTEXT}}.
+contraction ($\mcontrBIS$) is substitutive \hl{with respect to} \HOLinline{\HOLConst{GCONTEXT}}.
 %

### 2019-12-17 ic-journal/multivariate.tex
Changed most "w.r.t." to "with respect to"; removed "the" from (of the type ...) following other papers.

@@
 functions taking CCS terms and returning
-(finite) sets of variables (of the type \HOLinline{\ensuremath{\alpha}}).
+(finite) sets of variables (\hl{of type} \HOLinline{\ensuremath{\alpha}}).
 For their definition the interesting cases are those of
@@
 
-A finite map (of the type \HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{\beta}}) is like a function (of the type
-\HOLinline{\ensuremath{\alpha} \HOLTokenTransEnd \ensuremath{\beta}}) having only finitely many elements in its
+A finite map (\hl{of type} \HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{\beta}}) is like a function
+(\hl{of type} \HOLinline{\ensuremath{\alpha} \HOLTokenTransEnd \ensuremath{\beta}}) having only finitely many elements in its
 domain. In HOL, an empty finite map is denoted as \HOLinline{\HOLConst{FEMPTY}}.
@@
 The function \HOLinline{\HOLConst{CCS_SUBST}} takes a finite
-map \HOLinline{\HOLFreeVar{fm}} (of the type \HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}) and a CCS expression,
+map \HOLinline{\HOLFreeVar{fm}} (\hl{of type} \HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}) and a CCS expression,
 and returns another CCS expression in which
@@
 The next three lemmas show the relative correctness of \texttt{CCS\_SUBST}
-w.r.t.~\texttt{CCS\_Subst}:
+\hl{with respect to}~\texttt{CCS\_Subst}:
 \begin{lemma}[\texttt{CCS_SUBST_sing}]
@@
 guarded companions are defined as predicates over $\lambda$-expressions
-of the type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}''.
+\hl{of type} ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}''.
 These predicates, such as
@@
 Then a logical term ``\HOLinline{\HOLConst{weakly_guarded}\\\;\ensuremath{(}\HOLConst{SET_TO_LIST}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\ensuremath{)}\\\;\HOLFreeVar{E}}'' can
-be used to assert the weak guardedness of $E$ w.r.t.~all its free
+be used to assert the weak guardedness of $E$ \hl{with respect to} all its free
 variables.\footnote{Here \HOLinline{\HOLConst{SET_TO_LIST}} converts a finite set
@@
 is disjoint from a list of variables, then the term is indeed a context
-w.r.t. such list of variables:
+\hl{with respect to} such list of variables:
 \begin{alltt}
@@
 guardedness, \HOLinline{\HOLConst{WG}}), we also need
-their composability w.r.t.~\multivariate contexts: if we
+their composability \hl{with respect to}~\multivariate contexts: if we
 substitute some free variables in a context $C$ with some weakly guarded
@@
 Note that the two logical terms ``\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}\\\;\HOLFreeVar{Ps}}'' and ``\HOLinline{\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenIn{}}\\\;\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}'' in
-HOL have the same meaning (they are equivalent). The latter form suggests that
+HOL have the same meaning \hl{(they are equivalent)}. The latter form suggests that
 ``\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}'' is actually a set containing all
 solutions of ``\HOLinline{\HOLConst{CCS_equation}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}''. Then the unique-solution
-theorems can be understood thus: any two elements
+theorems can be understood thus: any two elements\hl{\ \ }%
 in the solution set are bisimilar.

### 2019-12-17 ic-journal/sos.tex
Changed most "w.r.t." to "with respect to"; removed "the" from (of the type ...) following other papers.

@@
 (\texttt{tau}). For instace, the input \emph{action} $a$ and output
-\emph{action} $\overline{b}$ of the type ``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''
+\emph{action} $\overline{b}$ \hl{of type} ``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''
 are denoted by \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLStringLit{a}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLStringLit{b}\ensuremath{)}}, respectively.
 On the
-other hand, \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLNumLit{1}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLNumLit{2}\ensuremath{)}} could be actions of the type ``\HOLinline{\HOLTyOp{num} \HOLTyOp{Action}}'', where
+other hand, \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLNumLit{1}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLNumLit{2}\ensuremath{)}} could be actions \hl{of type} ``\HOLinline{\HOLTyOp{num} \HOLTyOp{Action}}'', where
 \HOLinline{\HOLTyOp{num}} is the type of natural numbers in HOL.
@@
 respectively. (Indeed the CCS syntax in Section~\ref{ss:ccs} is parametric
-w.r.t. the choice of these two sets.)
+\hl{with respect to} the choice of these two sets.)
 %
@@
 (see~\citep[p.~219]{holdesc} for more details).
-A successful invocation of the definitional principle returns three
-important theorems (\texttt{TRANS_rules}, \texttt{TRANS_ind} and \texttt{TRANS_cases}):
+\hl{The} successful invocation of the definitional principle returns three
+important theorems \hl{(\texttt{TRANS_rules}, \texttt{TRANS_ind} and \texttt{TRANS_cases})}:
 \begin{itemize}
-  \item \texttt{TRANS_rules} is a conjunction of implications (each
+  \item \hl{\texttt{TRANS_rules}} is a conjunction of implications (each
     corresponding to a SOS rule) that will be the
     same as the input term. In fact, the following formal versions of SOS rules are
-    extracted from the \emph{rules} theorem:
+    extracted from \hl{\texttt{TRANS_rules}}:
 \begin{alltt}
@@
 \end{equation*}
-\item \texttt{TRANS_ind} is the induction principle for the relation
+\item \hl{\texttt{TRANS_ind}} is the induction principle for the relation
   (see Section~\ref{sec:multivariate} for its exact statement and an
   application in the proof of Proposition~\ref{prop:transFV}).
-\item \texttt{TRANS_cases} is the so-called `cases' or `inversion' theorem for
+\item \hl{\texttt{TRANS_cases}} is the so-called `cases' or `inversion' theorem for
   the relation, and is used to decompose an element in the relation into the possible ways of

### 2019-12-17 ic-journal/multivariate.tex
Expanded the rest three "w.r.t."

@@
 substitute some free variables in a context with some other contexts, the
-resulting term is still a valid context (w.r.t.~the same set of variables):
+resulting term is still a valid context (\hl{with respect to} the same set of variables):
 \begin{alltt}
@@
 \end{alltt}
-On the other hand, for any context (w.r.t.~$\til X$) of the form $\recu Y E$,
+On the other hand, for any context (\hl{with respect to} $\til X$) of the form $\recu Y E$,
 the set of free variables of $E$ excluding $Y$ is disjoint with $\til X$:
@@
 substitute some free variables in a context $C$ with some weakly guarded
-contexts, the resulting context is weakly guarded (w.r.t.~the same set of variables):
+contexts, the resulting context is weakly guarded (\hl{with respect to} the same set of variables):
 \begin{alltt}

### 2019-12-18 ic-journal/coarsest.tex
Clean up all highlights on "w.r.t." and "of type"

--- 2019-12-16 ic-journal/coarsest.tex
@@
  summation, we also consider the relation closure of bisimilarity
- w.r.t. summation, called \emph{equivalence compatible with summation}
+ with respect to summation, called \emph{equivalence compatible with summation}
 (\texttt{SUM_EQUIV}): %%, denoted by $\approx^+$: (not used this symbol)
@@
 
-For any ``\HOLinline{\HOLConst{label}\;\HOLFreeVar{a}}'', having a function ``\HOLinline{\HOLConst{KLOP}\;\HOLFreeVar{a}}'' (of the type ``\HOLinline{\HOLTyOp{num} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
+For any ``\HOLinline{\HOLConst{label}\;\HOLFreeVar{a}}'', having a function ``\HOLinline{\HOLConst{KLOP}\;\HOLFreeVar{a}}'' (of type ``\HOLinline{\HOLTyOp{num} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
 defined on the natural numbers, we obtain a countable set of processes

### 2019-12-18 ic-journal/context.tex
Clean up all highlights on "w.r.t." and "of type"

--- 2019-12-15 ic-journal/context.tex
@@
 Although weak bisimilarity ($\approx$) is \emph{not} a congruence
-  w.r.t~\HOLinline{\HOLConst{CONTEXT}}, it is substitutive w.r.t.~\HOLinline{\HOLConst{GCONTEXT}}
+with respect to~\HOLinline{\HOLConst{CONTEXT}}, it is substitutive
+with respect to~\HOLinline{\HOLConst{GCONTEXT}}
 as $\approx$ is preserved by guarded sums. Similarily,
-contraction ($\mcontrBIS$) is substitutive w.r.t.~\HOLinline{\HOLConst{GCONTEXT}}.
+contraction ($\mcontrBIS$) is substitutive with respect to \HOLinline{\HOLConst{GCONTEXT}}.
 %

### 2019-12-18 ic-journal/multivariate.tex
Clean up all highlights on "w.r.t." and "of type"

--- 2019-12-17 ic-journal/multivariate.tex
@@
 functions taking CCS terms and returning
-(finite) sets of variables (of the type \HOLinline{\ensuremath{\alpha}}).
+(finite) sets of variables (of type \HOLinline{\ensuremath{\alpha}}).
 For their definition the interesting cases are those of
@@
 
-A finite map (of the type \HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{\beta}}) is like a function (of the type
-\HOLinline{\ensuremath{\alpha} \HOLTokenTransEnd \ensuremath{\beta}}) having only finitely many elements in its
+A finite map (of type \HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{\beta}}) is like a function
+(of type \HOLinline{\ensuremath{\alpha} \HOLTokenTransEnd \ensuremath{\beta}}) having only finitely many elements in its
 domain. In HOL, an empty finite map is denoted as \HOLinline{\HOLConst{FEMPTY}}.
@@
 The function \HOLinline{\HOLConst{CCS_SUBST}} takes a finite
-map \HOLinline{\HOLFreeVar{fm}} (of the type \HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}) and a CCS expression,
+map \HOLinline{\HOLFreeVar{fm}} (of type \HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}) and a CCS expression,
 and returns another CCS expression in which
@@
 The next three lemmas show the relative correctness of \texttt{CCS\_SUBST}
-w.r.t.~\texttt{CCS\_Subst}:
+with respect to~\texttt{CCS\_Subst}:
 \begin{lemma}[\texttt{CCS_SUBST_sing}]
@@
 guarded companions are defined as predicates over $\lambda$-expressions
-of the type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}''.
+of type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}''.
 These predicates, such as
@@
 Then a logical term ``\HOLinline{\HOLConst{weakly_guarded}\\\;\ensuremath{(}\HOLConst{SET_TO_LIST}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\ensuremath{)}\\\;\HOLFreeVar{E}}'' can
-be used to assert the weak guardedness of $E$ w.r.t.~all its free
+be used to assert the weak guardedness of $E$ with respect to all its free
 variables.\footnote{Here \HOLinline{\HOLConst{SET_TO_LIST}} converts a finite set
@@
 substitute some free variables in a context with some other contexts, the
-resulting term is still a valid context (w.r.t.~the same set of variables):
+resulting term is still a valid context (with respect to the same set of variables):
 \begin{alltt}
@@
 is disjoint from a list of variables, then the term is indeed a context
-w.r.t. such list of variables:
+with respect to such list of variables:
 \begin{alltt}
@@
 \end{alltt}
-On the other hand, for any context (w.r.t.~$\til X$) of the form $\recu Y E$,
+On the other hand, for any context (with respect to $\til X$) of the form $\recu Y E$,
 the set of free variables of $E$ excluding $Y$ is disjoint with $\til X$:
@@
 guardedness, \HOLinline{\HOLConst{WG}}), we also need
-their composability w.r.t.~\multivariate contexts: if we
+their composability with respect to~\multivariate contexts: if we
 substitute some free variables in a context $C$ with some weakly guarded
-contexts, the resulting context is weakly guarded (w.r.t.~the same set of variables):
+contexts, the resulting context is weakly guarded (with respect to the same set of variables):
 \begin{alltt}

### 2019-12-18 ic-journal/sos.tex
Clean up all highlights on "w.r.t." and "of type"

@@
 (\texttt{tau}). For instace, the input \emph{action} $a$ and output
-\emph{action} $\overline{b}$ \hl{of type} ``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''
+\emph{action} $\overline{b}$ of type ``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''
 are denoted by \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLStringLit{a}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLStringLit{b}\ensuremath{)}}, respectively.
 On the
-other hand, \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLNumLit{1}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLNumLit{2}\ensuremath{)}} could be actions \hl{of type} ``\HOLinline{\HOLTyOp{num} \HOLTyOp{Action}}'', where
+other hand, \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLNumLit{1}\ensuremath{)}} and \HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLNumLit{2}\ensuremath{)}} could be actions of type ``\HOLinline{\HOLTyOp{num} \HOLTyOp{Action}}'', where
 \HOLinline{\HOLTyOp{num}} is the type of natural numbers in HOL.
@@
 respectively. (Indeed the CCS syntax in Section~\ref{ss:ccs} is parametric
-\hl{with respect to} the choice of these two sets.)
+with respect to the choice of these two sets.)
 %

### 2019-12-18 ic-journal/sos.tex
text

@@
 (the type of all ASCII strings), then the HOL terms \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
-\HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input \emph{label} $a$ and output
-\emph{label} $\overline{b}$, respectively.
+\HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input {label} $a$ and output
+{label} $\overline{b}$, respectively.
 The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
@@
 In particular, the SOS rule \texttt{REC} (Recursion)
- says that, if we substitute all occurrences of the variable $A$ in $P$ to
+ says that if we substitute all occurrences of the variable $A$ in $P$ to
 $(\recu A P)$ and the resulting process has a transition to $P'$

### 2019-12-18 ic-journal/sos.tex
Synchronized all changes from .tex files; removed URL in one bibitem; cleaned up all highlights.

@@
 (the type of all ASCII strings), then the HOL terms \HOLinline{\HOLConst{name} \HOLStringLit{a}} and
-\HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input {label} $a$ and output
-{label} $\overline{b}$, respectively.
+\HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input label $a$ and output
+label $\overline{b}$, respectively.
 The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}'' is the
@@
 (see~\citep[p.~219]{holdesc} for more details).
-\hl{The} successful invocation of the definitional principle returns three
-important theorems \hl{(\texttt{TRANS_rules}, \texttt{TRANS_ind} and \texttt{TRANS_cases})}:
+The successful invocation of the definitional principle returns three
+important theorems (\texttt{TRANS_rules}, \texttt{TRANS_ind} and \texttt{TRANS_cases}):
 \begin{itemize}
-  \item \hl{\texttt{TRANS_rules}} is a conjunction of implications (each
+  \item \texttt{TRANS_rules} is a conjunction of implications (each
     corresponding to a SOS rule) that will be the
     same as the input term. In fact, the following formal versions of SOS rules are
-    extracted from \hl{\texttt{TRANS_rules}}:
+    extracted from \texttt{TRANS_rules}:
 \begin{alltt}
@@
 \end{equation*}
-\item \hl{\texttt{TRANS_ind}} is the induction principle for the relation
+\item \texttt{TRANS_ind} is the induction principle for the relation
   (see Section~\ref{sec:multivariate} for its exact statement and an
   application in the proof of Proposition~\ref{prop:transFV}).
-\item \hl{\texttt{TRANS_cases}} is the so-called `cases' or `inversion' theorem for
+\item \texttt{TRANS_cases} is the so-called `cases' or `inversion' theorem for
   the relation, and is used to decompose an element in the relation into the possible ways of

### 2019-12-19 ic-journal/coarsest.tex
Fixed a buggy sentence in Section 4.9, related to Klop processes

@@
 
-For any ``\HOLinline{\HOLConst{label}\;\HOLFreeVar{a}}'', having a function ``\HOLinline{\HOLConst{KLOP}\;\HOLFreeVar{a}}'' (of type ``\HOLinline{\HOLTyOp{num} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
-defined on the natural numbers, we obtain a countable set of processes
-with all Klop processes built from the same label.
-Since the number of all Klop processes in this set is (countably) infinite, and
-since they are all pairwise non-bisimiar,
-we can always
-choose a number that is mapped to a Klop process
+For any \HOLinline{\HOLConst{label}\;\HOLFreeVar{a}}, having the function ``\HOLinline{\HOLConst{KLOP}\;\HOLFreeVar{a}}'' (of type ``\HOLinline{\HOLTyOp{num} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
+defined on the natural numbers, we obtain a countable set of Klop processes built from the same label.
+As the number of all Klop processes in this set is (countably) infinite, and
+as they are all pairwise non-bisimiar,
+we can always choose a number, corresponding to a Klop process,
 that is non-bisimilar with any derivative of two given 

### 2019-12-20 ic-journal/coarsest.tex
Prepare PDF for submission (version 3)

@@
 As the number of all Klop processes in this set is (countably) infinite, and
-as they are all pairwise non-bisimiar,
+they are all pairwise non-bisimiar,
 we can always choose a number, corresponding to a Klop process,

### 2020-06-21 ic-journal/multivariate.tex
Updated translations due to HOL updates (the only visible change is at BIGUNION)

@@
 \HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-   \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{BV} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
+   \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{\HOLTokenBigUnion{}} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{BV} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
 \end{alltt}
@@
 \HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-   \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DIFF} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{FV} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
+   \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DIFF} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{\HOLTokenBigUnion{}} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{FV} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
 \end{alltt}

### 2020-06-21 paper/HOLMultivariate.tex
Updated code generations
Updated translations due to HOL updates (the only visible change is at BIGUNION)

@@
-\newcommand{\HOLMultivariateDate}{19 Novembre 2019}
-\newcommand{\HOLMultivariateTime}{10:23}
+\newcommand{\HOLMultivariateDate}{21 June 2020}
+\newcommand{\HOLMultivariateTime}{18:11}
 \begin{SaveVerbatim}{HOLMultivariateDefinitionsCCSXXequationXXdef}
@@
        \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{BV} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}
+       \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{\HOLTokenBigUnion{}} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{BV} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}
 \end{SaveVerbatim}
@@
        \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{FV} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}
+       \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{\HOLTokenBigUnion{}} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{FV} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}
 \end{SaveVerbatim}
@@
        \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLConst{\HOLTokenSubset{}}
-       \HOLConst{FV} \HOLBoundVar{E} \HOLConst{DIFF} \HOLConst{set} \HOLBoundVar{Xs} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{FV} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}
+       \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E} \HOLConst{DIFF} \HOLConst{set} \HOLBoundVar{Xs} \HOLConst{\HOLTokenUnion{}} \HOLConst{\HOLTokenBigUnion{}} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{FV} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}
 \end{SaveVerbatim}

### 2020-07-31 ic-journal/editor-proof.tex
Editorial changes to LaTeX sources

%BeginFileInfo
%%Publisher=ESCH
%%Project=YINCO
%%Manuscript=YINCO104606
%%MS position=
%%Stage=204
%%TID=lgiriuniene
%%Pages=4,32
%%Format=2019
%%Distribution=vtex
%%Destination=DVI
%%PDF type=
%%DVI.Maker=luadvi
%%PS.Maker=luaps
%%Spelled=Dictionary: British, Computer: 1GSRED593, 2020.07.30 10:52
%%History1=2020.07.24 12:25
%EndFileInfo
%
%Spelling_date
% Opcijos: [secthm,seceqn,secfloat,xxtheorem,noappeqn]
%%
\RequirePackage{styledata}
\documentclass[GCNS]{yincog}
\usepackage[left]{vmkcol}\usepackage{multirow}
%\usepackage[hidebg]{tmultirow}
\usepackage{tabcols} %%% [debug]
\usepackage[v5.6.0]{jadtd}
\usepackage{mathrsfs}
\usepackage{stmaryrd}
%\usepackage{holindex}
\usepackage{listings}
%\usepackage{soul}
\usepackage{xyfix}
\usepackage[all,dvips]{xy}%,dvips
\usepackage{alltt}
\usepackage{proof}
\usepackage{holtenbasic}
%\usepackage{DSarrow}
%%\usepackage[show]{elscon}
\usepackage{xspace}
\PROOF
%\preCRC
%\psdraft
%\psprintphoto
\articlenumber{104606}% Updated by PTS2LaTeX.exe, 24.07.2020 12:25
\aid{104606}% Updated by PTS2LaTeX.exe, 24.07.2020 12:25
\PII{S0890-5401(20)30094-8}% Updated by PTS2LaTeX.exe, 24.07.2020 12:28
\doi{10.1016/j.ic.2020.104606}% Updated by PTS2LaTeX.exe, 24.07.2020 12:28
\docsubty{FLA}
\volume{00}
%\issue{00}
%\supplement{}
\pubyear{2020}
%\pagenumbering{roman}%Roman,alph,Alph
\firstpage{1}
\lastpage{32}
\TID{Loreta}
%
\crossmark{0}% Updated by PTS2LaTeX.exe, 24.07.2020 12:25
%
% APIBREZIMAI:
%
\startlocaldefs
\begin{nonSGML}
\DeclareRobustCommand\setData[4][]{%
  \expandafter\gdef\csname#2:\detokenize{#3}\endcsname{#4}%
  \@for\curr@option:={#1}\do{%
    \expandafter\split@@eq\curr@option\split@@end
    \expandafter\xdef\csname#2:\detokenize{#3}.\split@@eq@one\endcsname{\split@@eq@two}%
    }%
  }
\end{nonSGML}
\renewcommand{\ttdefault}{cmtt}
\begin{nonSGML}
\renewcommand{\HOLinline}[1]{\mbox{\textup{\texttt{#1}}}}
\renewcommand{\HOLTokenDoublePlus}{\ensuremath{\mathbin{+\mkern -10mu+}}}
\end{nonSGML}
\renewcommand{\HOLConst}[1]{\texttt{#1}}
\renewcommand{\HOLNumLit}[1]{\ensuremath{#1}}
\renewcommand{\HOLStringLit}[1]{\textrm{``#1''}}
\renewcommand{\HOLTyOp}[1]{\texttt{#1}}
\renewcommand{\HOLBoundVar}[1]{\ensuremath{\mathit{#1}}}
\renewcommand{\HOLFreeVar}[1]{\ensuremath{\mathit{#1}}}
\renewcommand{\HOLKeyword}[1]{{\textbf{\textsf{#1}}}}
\renewcommand{\HOLSymConst}[1]{#1}
\renewcommand{\HOLTokenConj}{\ensuremath{\wedge}}
\renewcommand{\HOLTokenEmpty}{\ensuremath{\emptyset}}

\renewcommand{\HOLTokenIn}{\ensuremath{\in}}
\renewcommand{\HOLTokenLeftbrace}{\ensuremath{\left \{\right .}}
\renewcommand{\HOLTokenRightbrace}{\ensuremath{\left .\right \}}}
\renewcommand{\HOLTokenLeq}{\ensuremath{\leq}}
\renewcommand{\HOLTokenLt}{\ensuremath{<}}
\renewcommand{\HOLTokenMapto}{\ensuremath{\mapsto}}
\renewcommand{\HOLTokenNeg}{\ensuremath{\neg}}
\renewcommand{\HOLTokenNotEqual}{\ensuremath{\neq}}
\renewcommand{\HOLTokenRCompose}{\ensuremath{\circ _r}}
\renewcommand{\HOLTokenRSubset}{\ensuremath{\subseteq _r}}
\renewcommand{\HOLTokenSubset}{\ensuremath{\subseteq}}
\renewcommand{\HOLTokenUnion}{\ensuremath{\cup}}

\begin{nonSGML}
\lstset{tabsize=8,language=ML,basicstyle=\small \ttfamily \bfseries,
keywordstyle=\ttfamily,
stringstyle=\color{red}\ttfamily,
commentstyle=\color{green}\ttfamily,
morecomment=[l][\color{magenta}]{\#}}

\def \rightarrowfill{$\m@th\mathord{\smash-}\mkern-6mu%
  \cleaders\hbox{$\mkern-2mu\mathord{\smash-}\mkern-2mu$}\hfill
  \mkern-6mu\mathord\rightarrow$}

\def \rightarrowfillWEAK{$\m@th\mathord{\smash=}\mkern-6mu%
  \cleaders\hbox{$\mkern-2mu\mathord{\smash=}\mkern-2mu$}\hfill
  \mkern-6mu\mathord\Rightarrow$}
%\renewcommand{\HOLTokenDefEquality}{\ensuremath{\mathrel{\overset{\makebox [0pt]{\mbox{\normalfont \tiny \textsf{def}}}}{=}}}}
\renewcommand{\HOLTokenDefEquality}{\ensuremath{\mathrel{\overset{\makebox [0pt]{\text{\tiny \textsf{def}}}}{=}}}}

%\renewcommand{\HOLTokenEquiv}{\ensuremath{\iff}}

\renewcommand{\HOLTokenEquiv}{\ensuremath{\Longleftrightarrow}}

\end{nonSGML}
\renewcommand{\HOLTokenExists}{\ensuremath{\exists \,}}
\renewcommand{\HOLTokenForall}{\ensuremath{\forall \,}}
\renewcommand{\HOLTokenLambda}{\ensuremath{\lambda \,}}
\renewcommand{\HOLTokenNotIn}{\ensuremath{\notin}}
\renewcommand{\HOLTokenSupStar}{\ensuremath{{}^{*}}}
\renewcommand{\HOLTokenTurnstile}{\ensuremath{\:\:\vdash}}

\renewcommand{\HOLTokenDisj}{\ensuremath{\vee}}
\renewcommand{\HOLTokenBar}{\texttt{|}}
\renewcommand{\HOLTokenBigUnion}{\ensuremath{\bigcup}}
\renewcommand{\HOLTokenCompose}{\ensuremath{\circ}}

\theoremstyle{remark}
\newtheorem{definition}{Definition}[section]
\theoremstyle{theorem}

\newtheorem{lemma}[definition]{Lemma}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{corollary}[definition]{Corollary}
\newtheorem{proposition}[definition]{Proposition}
\theoremstyle{remark}
\newtheorem{remark}[definition]{Remark}
\newtheorem{example}[definition]{Example}
\newcommand{\HOLTokenStrongEQ}{$\sim$}
\newcommand{\HOLTokenWeakEQ}{$\approx$}
\newcommand{\HOLTokenObsCongr}{$\approx^{\mathrm{c}}\!$}
\newcommand{\HOLTokenEPS}{$\overset{\epsilon}{\Longrightarrow}$}
\newcommand{\HOLTokenTransBegin}{$-$}
\newcommand{\HOLTokenTransEnd}{$\rightarrow$\xspace}
\newcommand{\HOLTokenWeakTransBegin}{$=$}
\newcommand{\HOLTokenWeakTransEnd}{$\Rightarrow$\xspace}
\newcommand{\HOLTokenExpands}{$\succeq_{\mathrm{e}}\!$}
\newcommand{\HOLTokenContracts}{$\succeq_{\mathrm{bis}}\!$}
\newcommand{\HOLTokenObsContracts}{$\succeq^{\mathrm{c}}_{\mathrm{bis}}\!$}
\newcommand{\HOLTokenInputAct}{$\mathrm{in}$}
\newcommand{\HOLTokenOutputAct}{$\overline{\mathrm{out}}$}

\renewcommand{\HOLTokenImp}{\ensuremath{\Longrightarrow}}

\newcommand{\univariate}{univariable\xspace}
\newcommand{\multivariate}{multivariable\xspace}
\newcommand{\Multivariate}{Multivariable\xspace}

\def\fvvtex#1{\rmsf{fv}(#1)}
\def\bvvtex#1{\rmsf{bv}(#1)}

\def\nil{{\boldsymbol 0}}
\def\res#1{{\boldsymbol \nu} #1\:}
\mathcode `\!="4021 \mathcode `\.="602E \mathcode `\|="326A

\newcommand{\outC}[1]{\overline{#1}}

\begin{nonSGML}
\def\sub#1#2{\{\raisebox{.5ex}{\small$#1$}\! / \!\mbox{\small$#2$}\}}
\end{nonSGML}
\newcommand{\arr}[1]{\mathrel{\stackrel{{\;\;#1\;\;}}{\mbox{\rightarrowfill}}}}

\newcommand{\Arr}[1]{\mathrel{\stackrel{{\;\;#1\;\;}}{\mbox{\rightarrowfillWEAK}}}}

\newcommand{\arcap}[1]{\mathrel{\stackrel{{\;\; {\widehat{#1}} \;\;}}{\mbox{\rightarrowfill}}}}
\newcommand{\Arcap}[1]{\mathrel{\stackrel{{\;\;{\widehat{#1}}\;\;}}{\mbox{\rightarrowfillWEAK}}}}

\newcommand{\ctvtex}[1]{ C \brac{#1} }
\newcommand{\qct}{ C }
\newcommand{\brac}[1]{[#1] }

\newcommand{\rmsf}[1]{{\mathsf{{#1}}}}

\def\Rvtex{\mathcal{R}}
\def\RRvtex{\mathrel{\mathcal{R}}}
\def\Svtex{\mathcal{S}}

\def\midd{\; \; \mbox{\Large{$\mid$}}\;\;}

\def\stvtex{\; \mid \;}
\def\DSdefi{\stackrel{\text{def}}{=}}

\renewcommand{\tilde}{\widetilde}

\newcommand{\recu}[2]{\mathtt{rec}\: #1 . #2}

\newcommand{\rapprox}{\mathrel{\approx^{\mathrm{c}}}}

\newcommand{\hbvtex}{\hspace{0.5cm}}

\newcommand{\wbvtex}{\approx}
\newcommand{\contr}{\mathrel{\succeq_{\mathrm{bis}}}}
\newcommand{\expa}{\mathrel{\succeq_{\mathrm{e}}}}

\newcommand{\mcontrBIS}{\mathrel{\succeq_{\mathrm{bis}}}}
\newcommand{\mexpaBIS}{\mathrel{\preceq_{\mathrm{bis}}}}

\newcommand{\rcontr}{\mathrel{\succeq^{\mathrm{c}}_{\mathrm{bis}}}}

\newcommand{\til}{\tilde}

\newcommand{\ctp}[1]{ C' \brac{#1} }
\newcommand{\qctp}{ C' }
\newcommand{\ctpp}[1]{ C'' \brac{#1} }

\newcommand{\qctpp}{ C'' }

\newcommand{\hkvtex}{\hspace{0.2cm}}

\newcommand{\Tvtex}{\mathcal{T}}
\newcommand\fun{{\to}}
\newcommand{\tyvtex}[1]{\textsl{#1}}
\newcommand\conj{\ \wedge\ }
\newcommand\imp{ \Rightarrow }
\newcommand\turn{\ \vdash\ }
\newcommand\hilbert{\varepsilon}
\newcommand{\uquant}[1]{\forall #1.\ }
\newcommand{\equant}[1]{\exists #1.\ }
\newcommand{\lquant}[1]{\lambda #1.\ }
\newcommand{\con}[1]{\mathrm{#1}}

\newcommand\ind{\tyvtex{ind}}

\renewcommand{\Tvtex}{\con{T}}
\newcommand\Fvtex{\con{F}}
\newcommand\OneOne{\con{One\_One}}
\newcommand\Onto{\con{Onto}}
\newcommand\TyDef{\con{Type\_Definition}}

\newlength{\ttX}
\settowidth{\ttX}{\texttt{X}}
\newcommand{\tyvar}{\setlength{\unitlength}{\ttX}\begin{picture}(1,6)
\put(.5,0){\makebox(0,0)[b]{\footnotesize type variables}}
\put(0,1.5){\vector(0,1){4.5}}
\end{picture}}
\newcommand{\tyatom}{\setlength{\unitlength}{\ttX}\begin{picture}(1,6)
\put(.5,2.3){\makebox(0,0)[b]{\footnotesize atomic types}}
\put(.5,3.3){\vector(0,1){2.6}}
\end{picture}}
\newcommand{\funty}{\setlength{\unitlength}{\ttX}\begin{picture}(1,6)
\put(.5,1.5){\makebox(0,0)[b]{\footnotesize function types}}
\put(.5,0){\makebox(0,0)[b]{\footnotesize (domain $\sigma_1$, codomain $\sigma_2$)}}
\put(1,2.5){\vector(0,1){3.5}}
\end{picture}}
\newcommand{\cmpty}{\setlength{\unitlength}{\ttX}\begin{picture}(1,6)
\put(2,3.3){\makebox(0,0)[b]{\footnotesize compound types}}
\put(1.9,4.5){\vector(0,1){1.5}}
\end{picture}}

\settowidth{\ttX}{\texttt{X}}
\newcommand{\var}{\setlength{\unitlength}{\ttX}\begin{picture}(1,6)
\put(.5,0){\makebox(0,0)[b]{\footnotesize variables}}
\put(0,1.5){\vector(0,1){4.5}}
\end{picture}}
\newcommand{\const}{\setlength{\unitlength}{\ttX}\begin{picture}(1,6)
\put(.5,2.3){\makebox(0,0)[b]{\footnotesize constants}}
\put(.5,3.5){\vector(0,1){2.4}}
\end{picture}}
\newcommand{\app}{\setlength{\unitlength}{\ttX}\begin{picture}(1,6)
\put(.5,1.5){\makebox(0,0)[b]{\footnotesize function applications}}
\put(.5,0){\makebox(0,0)[b]{\footnotesize (function $t$, argument $t'$)}}
\put(0.5,2.5){\vector(0,1){3.5}}
\end{picture}}
\newcommand{\abs}{\setlength{\unitlength}{\ttX}\begin{picture}(1,6)
\put(1,3.3){\makebox(0,0)[b]{\footnotesize $\lambda$-abstractions}}
\put(0.7,4.5){\vector(0,1){1.5}}
\end{picture}}

\endlocaldefs
%
\begin{copyrightinfo}[type=standard]% Updated by PTS2LaTeX.exe, 24.07.2020 12:25
\cpcopyrightNotice{\textCopyright\ 2020 Elsevier Inc. All rights reserved.}% Updated by PTS2LaTeX.exe, 24.07.2020 12:28
%\cplicenseLine{}
%\oauserLicense{}
\cpcopyrightYear{2020}% Updated by PTS2LaTeX.exe, 24.07.2020 12:25
\cpcopyrightHolderDisplayName{Elsevier Inc.}% Updated by PTS2LaTeX.exe, 24.07.2020 12:28
\cpxmlCopyrightType{full-transfer}% Updated by PTS2LaTeX.exe, 24.07.2020 12:28
\copyrt{2020}
\CopyrightStatus{001}
\end{copyrightinfo}
%
\begin{document}
\begin{frontmatter}
%% REFERSTO
%\dochead{}
\title{Unique solutions of contractions, CCS, and their HOL
formalisation\thanksref{ATL1}}
% \title{}
%\artthanks[]{}
\artthanks[ATL1]{This is an extended and refined
version of the paper with the same title published in EXPRESS/SOS 2018~\cite{EPTCS276.10}.}
%\begin{aug}
%\runauthor{}
%\author[A]{\inits{}\fnm{} \snm{}}
%\corthanks[cor]{Corresponding author.}
%\address[A]{}
%\end{aug}
\begin{aug}
\author[a,b]{\inits{C.}\fnm{Chun}~\snm{Tian}\ead{chun.tian@unitn.it}\thanksref{THNKS2}},
\thanks[THNKS2]{Part of this work was carried out when the first
author was studying at the University of Bologna, Italy.}
\author[c,d]{\inits{D.}\fnm{Davide}~\snm{Sangiorgi}\ead{davide.sangiorgi@unibo.it}}
\address[a]{\orgname{University of Trento}, \cny{Italy}%
   \adrsource{University of Trento, Italy}}
\address[b]{\orgname{Fondazione Bruno Kessler},
   \cny{Italy}%
   \adrsource{Fondazione Bruno Kessler, Italy}}
\address[c]{\orgname{University of Bologna},
   \cny{Italy}%
   \adrsource{University of Bologna, Italy}}
\address[d]{\orgname{INRIA},
   \cny{France}%
   \adrsource{INRIA, France}}
\end{aug}
%
% HISTORY:
\received{\sday{22} \smonth{6} \syear{2020}}% Updated by PTS2LaTeX.exe, 24.07.2020 12:28
%\revised{\sday{} \smonth{} \syear{}}% Updated by PTS2LaTeX.exe, 24.07.2020 12:28
\accepted{\sday{29} \smonth{6} \syear{2020}}% Updated by PTS2LaTeX.exe, 24.07.2020 12:28
%\pubonline{\sday{} \smonth{} \syear{}}
%
%\dataset[]{}
%
%\dedicated{}
%
%\begin{abstract}    %%% Visada FLA tipui (<=150 zodziu)
%\end{abstract}
%
%\begin{abstract}[class=graphical]  %%% Jei yra
%\begin{figure} \includegraphics{<aid>fab} \end{figure} \abstext{}
%\end{abstract}
%
%\begin{abstract}[class=author-highlights,title=Highlights] %%% Jei yra
%\begin{itemize} %\item
%\end{itemize}
%\end{abstract}
\begin{abstract}
The unique solution of contractions is a proof technique for (weak) bisimilarity
that overcomes certain syntactic limitations of Milner's ``unique solution
of equations'' theorem. This paper presents an overview of a comprehensive
formalisation of Milner's Calculus of Communicating Systems (CCS) in the
HOL theorem prover (HOL4), with a focus towards the theory of unique solutions
of equations and contractions. The formalisation consists of about 24,000
lines (1MB) of code in total. Some refinements of the ``unique solution
of contractions'' theory itself are obtained. In particular we remove the
constraints on summation, which must be guarded, by moving from contraction
to \emph{rooted contraction}. We prove the ``unique solution of rooted contractions''
theorem and show that rooted contraction is the coarsest precongruence
contained in the contraction preorder.
\end{abstract}
%
% Opcijos: [class=KWD]
%\begin{keyword}             %%% Jei yra FLA tipui
%\kwd{}\kwd{}
%\end{keyword}
\begin{keyword}
\kwd{Process calculi}
\kwd{Theorem proving}
\kwd{Coinduction}
\kwd{Unique solution of equations}
\kwd{Congruence}
\end{keyword}
\end{frontmatter}
%spell_from    *************** Text entry area ******************%

%s1 #&#
\section{Introduction}
 \label{sec1}

A prominent proof method for bisimulation, put forward by Robin Milner
and widely used in his landmark CCS book~\cite{Mil89}, is the
\emph{unique solution of equations}, whereby two tuples of processes are
componentwise bisimilar if they are solutions of the same system of equations.
This method is important in verification techniques and tools based on
algebraic reasoning~\cite{BaeBOOK,theoryAndPractice,RosUnder10}.

Milner's unique-solution theorem for weak bisimilarity, however, has severe
syntactic limitations: the equations must be both \emph{guarded} and
\emph{sequential}. That is, the variables of the equations can only occur
underneath visible prefixes and summation. One way to overcome these limitations
is to replace the equations with special inequations called
\emph{contractions}~\cite{sangiorgi2015equations,sangiorgi2017equations}.
The contraction relation is a preorder that, roughly, places some efficiency
constraints on processes. The unique solution of contractions is defined
as with equations: any two solutions must be componentwise bisimilar. The
difference from equations is in the meaning of a solution: in the case
of contractions the solution is evaluated with respect to the contraction
preorder rather than bisimilarity. With contractions, most syntactic limitations
of the unique-solution theorem are eliminated. One constraint that still
remains in~\cite{sangiorgi2017equations} (where the issue is bypassed by
using a more restrictive CCS syntax) is the occurrences of arbitrary sums
(e.g.~$P + Q$) due to the non-substitutivity of the contraction preorder
in this case.

This paper presents a comprehensive formalisation of Milner's Calculus
of Communicating Systems (CCS) in the HOL theorem prover (HOL4), with a
focus towards the theory of unique solutions of equations and contractions.
Many results in Milner's CCS book~\cite{Mil89} are covered, since the unique-solution
theorems rely on a large number of fundamental results. Indeed the formalisation
encompasses all basic properties of strong, weak and rooted bisimilarities
(e.g.~the fixed-point and substitutivity properties), and their algebraic
laws. Further extensions include several versions of ``bisimulation up
to'' techniques, and properties of the expansion and contraction preorders.
Concerning rooted bisimilarity, the formalisation includes Hennessy's Lemma,
Deng's Lemma, and two theorems saying that rooted bisimilarity is the coarsest
(largest) congruence contained in weak bisimilarity ($\wbvtex $): one is
classical with the hypothesis that no process uses up all labels; the other
one is without such hypothesis, essentially formalising van Glabbeek's
proof~\cite{van2005characterisation}. With this respect, the work is also
an extensive experiment using the HOL theorem prover with its recent developments,
including its coinduction package.

This formalisation has offered us the possibility of further refining the
theory of unique solutions of contractions. In particular, existing results~\cite{sangiorgi2017equations}
have limitations on the body of the contractions due to the substitutivity
problems of weak bisimilarity and other behavioural relations with respect
to the sum operator. In this paper, the contraction-based proof technique
is further refined by moving from the contraction preorder to
\emph{rooted contraction}, which is shown to be the coarsest precongruence
contained in the contraction preorder. The resulting unique-solution theorem
is now valid for \emph{rooted bisimilarity} (hence also for bisimilarity
itself), and places no constraints on summation.

Another benefit of the formalisation is that we can take advantage of results
about different equivalences and preorders that share similar proof structures.
Such structural \xch{similarities}{simililarities} can be found, for instance, in the following
cases: the proofs that rooted bisimilarity and rooted contraction are,
respectively, the coarsest congruence contained in weak bisimilarity and
the coarsest precongruence contained in the contraction preorder; the proofs
about unique solution(s) of equations for weak bisimilarity that use the
contraction preorder as an auxiliary relation, and other unique-solution
theorems (e.g. the one for rooted bisimilarity in which the auxiliary relation
is rooted contraction); the proofs about various forms of enhancements
of the bisimulation proof method (the ``up-to'' techniques). In these cases,
when moving between proofs there are only a few places in the HOL proof
scripts that have to be modified. Then the successful termination of a
proof gives us the guarantee that the proof is correct, eliminating the
risks of overlooking or missing details as in \emph{paper-and-pencil} proofs.

Concerning the formalisation of unique-solution theorems, we first consider
the case of a single equation (or contraction), the
\emph{\univariate case}. Then we turn to the \emph{\multivariate case} where
more equations (or contractions) with multiple equation variables are involved.
The \univariate versions of the unique-solution theorems can directly use
$\lambda $-functions to represent CCS equations, while the
\multivariate versions require more careful and delicate treatments of
CCS expressions, with multiple variables and substitutions acting on them.
In contrast to literature such as~\cite{Gorrieri:2015jt}, we have followed
Milner's original approach~\cite{milner1990operational} and adopted the
same type for both CCS equations and processes: those undefined constants
in CCS terms are treated as (free) equation variables, and a CCS process
is a CCS expression without equation variables. This allows us a smoother
move from the \univariate case to the \multivariate one. (See Section~\ref{sec:multivariate}
for more details.)

%p1 #&#
\bigskip\noindent\textit{Structure of the paper}.
In Section~\ref{ss:ccs} we recall the core theory of CCS, including its
syntax, operational semantics, bisimilarity and rooted bisimilarity. Then,
Section~\ref{s:eq} discusses equations and contractions, and in particular,
Section~\ref{ss:new} presents rooted contraction and the related unique-solution
result for rooted bisimilarity. In Section~\ref{s:for} we highlight the
CCS formalisation in HOL4, with the unique-solution theorems in the
\univariate case. Section~\ref{sec:multivariate} describes the extension
to the \multivariate case. Finally, in \xch{Sections}{Section}~\ref{s:rel} and \ref{s:concl} we discuss the related work, conclusions, and a few directions
for future work.

%s2 #&#
\section{Calculus of communicating systems (CCS)}
%%LEAP%%%\label{sec2}
 \label{ss:ccs}

We assume a possibly infinite set of \emph{names}
$\mathscr{L} = \{a, b, \ldots \}$ yielding \emph{input} and
\emph{output labels} (or \emph{actions}), a special \emph{invisible} action
$\tau \notin \mathscr{L}$, and another possibly infinite set of
\emph{agent variables} $\mathscr{X} = \{X, Y, \ldots \}$. The class of CCS
terms is then inductively defined from $\nil $ (the terminated process)
and agent variables by the operators of \emph{prefixing} (.),
\emph{parallel composition} ($|$), \emph{summation} (or
\emph{binary choice}, $+$), \emph{restriction} ($\nu $),
\emph{relabeling} ($[\cdot ]$) and \emph{recursion} ($\texttt{rec}$):
%
\begin{equation*}
%
\begin{array}{cccl}
\mu & := & \tau \!\!\!\! & \midd \; a \; \midd \; \outC a
\\
P & := & \nil \!\!\!\! & \midd \; \mu . P \; \midd \; P_1 | P_2 \;
\midd \; P_1 + P_2 \; \midd (\res L)\, P \; \midd \; P\; [\mathit{rf}]
\; \midd \; X \; \midd \; \recu X P
\end{array}
%
\end{equation*}
%
In our presentation of CCS, the restriction operator takes a set of labels
$L \subseteq \mathscr{L}$ rather than a single one. The relabeling operator
takes a relabeling function
$\mathit{rf} \colon \mathscr{L} \cup \overline{\mathscr{L}} \cup \{
\tau \} \rightarrow \mathscr{L} \cup \overline{\mathscr{L}} \cup \{
\tau \}$, that can handle multiple actions including $\tau $. A valid relabeling
function $\mathit{rf}$ must however satisfy
$\mathit{rf}(\tau ) = \tau $ and
$\forall l\in \mathscr{L} \cup \overline{\mathscr{L}}.\, \mathit{rf}(
\overline{l}) = \overline{\mathit{rf}(l)}$ (with $\bar{\bar l} = l$ for
all $l \in \mathscr{L}$). We sometimes omit a trailing $\nil $, e.g., writing
$a|b$ for $a.\nil |b .\nil $. A CCS process $P$ may evolve to another one
(i.e. having a \emph{transition}), say $P'$, under an action $\mu $, written
by $P \arr{\mu} P'$. The transition semantics of CCS processes is given
by means of a Labeled Transition System (LTS) expressed in Structural Operational
Semantics (SOS) rules shown in \reftext{Fig.~\ref{f:LTSCCS}}. A CCS process has or
uses \emph{guarded sums} if all occurrences of summation are in the form
$a.P + b.Q$. The \emph{immediate derivatives} of a process $P$ are the elements
of $\{P' \stvtex P \arr\mu P' \mbox{ for some $\mu $}\}$. We use
$\ell $ to range over visible actions (i.e.~inputs or outputs, excluding
$\tau $) and $\mu $ to range over all actions.
%
%f1 #&#
\begin{figure*}%[t]
%
\begin{sgmlfig}
\begin{center}\normalsize
\vskip .1cm $\displaystyle{ \over \mu . P \arr\mu P } $ $ \hbvtex $
\hskip .5cm $\displaystyle{ P \arr\mu P' \over P + Q \arr\mu P' } $
$ \hbvtex $
\hskip .5cm
$\displaystyle{ P \arr\mu P' \over P | Q \arr\mu P' | Q } $
$ \hbvtex $
\hskip .3cm $\; \;$
$\displaystyle{ P \arr{ a}P' \hkvtex \hkvtex Q \arr{\outC a }Q'
\over P| Q \arr{ \tau} P' | Q' }$
\\
\vspace{.2cm}
$\displaystyle{ P \arr{\mu}P' \over (\res L\!)\, P \arr{\mu} (\res L
\!)\, P'} $ $ \mu , \outC\mu \notin L$ $ \hbvtex $
$\displaystyle{ P \sub {\recu X P} X \arr{\mu}P' \over \recu X P
\arr{\mu} P'} $
\hskip .5cm
$\displaystyle{ P \arr{\mu} P' \over P \;[r\!f] \arr{r\!f(\mu )} P'
\;[r\!f]} $ $ \hbvtex $
\end{center}
\end{sgmlfig}
%
\caption{Structural Operational Semantics of CCS. (The symmetric rules for $+$
and $|$ are omitted.)}
 \label{f:LTSCCS}
\end{figure*}

Some standard notations for transitions: $\Arr\epsilon $ is the reflexive
and transitive closure of $\arr\tau $, and $\Arr \mu $ is
$\Arr\epsilon \arr\mu \Arr\epsilon $ (the composition of the three relations).
Moreover, $P \arcap \mu P'$ holds if $P \arr\mu P'$ or
$\mu =\tau \wedge P = P'$; similarly $P \Arcap \mu P'$ holds if ($P
\Arr\mu P'$ or $\mu =\tau \wedge P = P'$). We write
$P \:(\arr\mu )^{n} P'$ if $P$ can become $P'$ after performing $n$
$\mu $-transitions. Finally, $P \arr\mu $ holds if there is $P'$ with
$P \arr\mu P'$, and similarly for other forms of transitions.

%p2 #&#
\bigskip\noindent\textit{Further notations}. We let $\Rvtex $, $\Svtex $ range over binary
relations, sometimes using infix notation for them, e.g.
$P \,\Rvtex \, Q$ means $(P,Q) \in \Rvtex $. We use a tilde, as in
$\til P$, to denote (finite) tuples of elements. All relation notations
can be extended to tuples componentwise, e.g.,
$\til P \,\Rvtex \, \til Q$ means $P_i \,\Rvtex \, Q_i$ for each index
$i$ of the tuples $\til P$ and $\til Q$. We use $\DSdefi $ for abbreviations.
For instance, $P \DSdefi G $, where $G$ is some expression, means that
$P$ stands for the expression $G$. If $\leq $ is a preorder, then
$\geq $ is its inverse (and conversely).

%s2.1 #&#
\subsection{Bisimilarity and rooted bisimilarity}
%%LEAP%%%\label{sec2.1}
 \label{ss:BiEx}

The equivalences we consider here are mainly \emph{weak} ones, in that they
abstract from the number of internal steps being performed:
%
%d2.1 #&#
\begin{definition}%
 \label{d:wb}
A process relation ${\Rvtex}$ is a (weak) \emph{bisimulation} if, whenever
$P\RRvtex Q$,
%
\begin{enumerate}
%
\item $P \arr\mu P'$ implies that there is $Q'$ such that
$Q \Arcap \mu Q'$ and $P' \RRvtex Q'$;
%
\item $Q \arr\mu Q'$, implies that there is $P'$ such that
$P \Arcap \mu P'$ and $P' \RRvtex Q'$;
%
\end{enumerate}
%
$P$ and $Q$ are (weakly) \emph{bisimilar}, written as $P \wbvtex Q$, if
$P \RRvtex Q$ for some bisimulation $\Rvtex $.
\end{definition}

\emph{Strong} bisimulation and strong bisimilarity ($\sim $) can be obtained
by replacing the weak transition $Q\Arcap\mu Q'$ in clause (1) with the
transition $Q \arr \mu Q'$ (and similarly for the other clause). Weak bisimilarity
is not preserved by the sum operator (except for guarded sums), i.e.~$P_1
\wbvtex Q_1$ and $P_2 \wbvtex Q_2$ do not imply
$P_1 + P_2 \wbvtex Q_1 + Q_2$. For this reason, Milner introduced the concept
of \emph{observational congruence}, also called
\emph{rooted bisimilarity}~\cite{Gorrieri:2015jt,Sangiorgi:2011ut}:
%
%d2.2 #&#
\begin{definition}%
 \label{d:rootedBisimilarity}
Two processes $P$ and $Q$ are \emph{rooted bisimilar}, written as
$P \rapprox Q$, if
%
\begin{enumerate}
%
\item $P \arr\mu P'$ implies that there is $Q'$ such that
$Q \Arr\mu Q'$ and $P' \wbvtex Q'$;
%
\item $Q \arr\mu Q'$ implies that there is $P'$ such that
$P \Arr\mu P'$ and $P' \wbvtex Q'$.
%
\end{enumerate}
%
\end{definition}
%
Relation $\rapprox $ is indeed preserved by the sum operator. The above
definition also brings up a proof technique for proving rooted bisimilarity
from a given bisimulation. The next lemma plays an important role in proving
some key results in this paper:
%
%l2.3 #&#
\begin{lemma}[rooted bisimilarity by bisimulation]
 \label{lobsCongrByWeakBisim}
Given a (weak) bisimulation $\RRvtex $, suppose two processes $P$ and
$Q$ satisfy the following properties:
%
\begin{enumerate}
%
\item $P \arr\mu P'$ implies that there is $Q'$ such that
$Q \Arr\mu Q'$ and $P' \RRvtex Q'$;
%
\item $Q \arr\mu Q'$ implies that there is $P'$ such that
$P \Arr\mu P'$ and $P' \RRvtex Q'$.
%
\end{enumerate}
%
Then $P$ and $Q$ are rooted bisimilar, i.e.~$P \approx ^{c} Q$.
\end{lemma}

One basic property of rooted \xch{bisimilarity}{bisimiarity} is congruence, indeed it is the
coarsest congruence contained in bisimilarity (see Section~\ref{s:coarsest}
and Section~\ref{sscontext} for more details):
%
%t2.4 #&#
\begin{theorem}
 \label{t:rapproxCongruence}
$\rapprox $ is a congruence in CCS, and it is the coarsest congruence contained
in $\wbvtex $.
\end{theorem}

%s3 #&#
\section{Equations and contractions}
%%LEAP%%%\label{sec3}
 \label{s:eq}

In the CCS syntax, a recursion $\recu A P$ acts as a binder for $A$ in
the body $P$. This gives rise, in the expected manner, to the notions of
\emph{free} and \emph{bound} recursion variables in a CCS expression. For
instance, $X$ is free in $a.X + \recu Y (b.Y)$ while $Y$ is bound; whereas
$X$ is both free and bound in $a.X + \recu X (b.X)$. A term without free
variables is a \emph{process}.

In this paper (and the formalisation work), we use the agent variables
also as \emph{equation variables}. This eliminates the need of an additional
type for CCS equations, and we can reuse the existing variable substitution
operation (cf.~the SOS rule for the Recursion in \reftext{Fig.~\ref{f:LTSCCS}}) for
substitutions of equation variables. For example, the result of substituting
variable $X$ with $\nil $ in $a.X + \recu X (b.X)$, written as
$(a.X + \recu X (b.X)) \sub {\nil} X$, is $a.\nil + \recu X (b.X)$ with
$\recu X (b.X)$ untouched. \Multivariate substitutions are written in the
same syntax, e.g. $E \sub {\til P} {\til X}$. Whenever $\til X$ is clear
from the context, we may also write $E[\til P]$ instead of
$E \sub {\til P} {\til X}$ (and $E[P]$ for $E \sub {P} X$ if there is a single
equation variable $X$).

%s3.1 #&#
\subsection{Systems of equations}
%%LEAP%%%\label{sec3.1}
 \label{ss:SysEq}

When discussing equations it is standard to talk about ``contexts''. This
is a CCS expression possibly containing free variables that, however, may
not occur within the body of recursive definitions. Milner's ``unique solution
of equations'' theorems~\cite{Mil89} intuitively say that, if a context
$C$ obeys certain conditions, then all processes $P$ that satisfy the equation
$P \wbvtex \ctvtex P$ are bisimilar with each other.

%d3.1 #&#
\begin{definition}[equations]
 \label{def:equation}
Assume that, for each $i$ of a countable indexing set $I$, we have variables
$X_i$, and expressions $E_i$ possibly containing such variables
$\bigcup _i \{ X_i\}$. Then $\{ X_i = E_i\}_{i\in I}$ is a
\emph{system of equations}. (There is one equation $E_i$ for each variable
$X_i$.)
\end{definition}

The components of $\til P$ need not be different from each other, as it
must be for the variables $\til X$.

%d3.2 #&#
\begin{definition}[solutions and the unique solution]
 \label{def:solution}
Suppose $\{ X_i = E_i\}_{i\in I}$ is a system of equations:
%
\begin{itemize}
%
\item $\til P$ is a
\emph{solution of the system of equations (for $\wbvtex $)} if for each
$i$ it holds that $P_i \wbvtex E_i [\til P]$;
%
\item The system has \emph{a unique solution for $\wbvtex $} if whenever
$\til P$ and $\til Q$ are both solutions then
$\til P \wbvtex \til Q$.
%
\end{itemize}
%
\end{definition}
%
\xch{Similarly}{Similarily}, the
\emph{(unique) solution of a system of equations for $\sim $} (or for
$\rapprox $) can be obtained by replacing all occurrences of
$\wbvtex $ in the above definition with $\sim $ and $\rapprox $, respectively.

For instance, the solution of the equation $X \wbvtex a. X$ is the process
$R \DSdefi \recu A {\, (a. A)}$, and for any other solution $P$ we have
$P \wbvtex R$. In contrast, the equation $X \wbvtex a| X$ has solutions
that may be quite different, for instance, $K$ and $K | b$, for
$K \DSdefi \recu K {\, (a. K)}$. (Actually any process capable of continuously
performing $a$--actions is a solution of $X \wbvtex a| X$.) Examples of
systems that do not have unique solutions are: $X = X$,
$X = \tau . X$ and $X = a | X$.

%d3.3 #&#
\begin{definition}[guardedness of equations]
 \label{def:guardness}
A system of equations $\{ X_i = E_i\}_{i\in I}$ is
%
\begin{itemize}
%
\item \emph{weakly guarded} if, in each $E_i$, each occurrence of each
$X_i$ is underneath a prefix;
%
\item \emph{guarded} if, in each $E_i$, each occurrence of each $X_i$ is
underneath a \emph{visible} prefix;
%
\item \emph{sequential} if, in each $E_i$, each occurrence of each
$X_i$ is only underneath prefixes and sums.
%
\end{itemize}
%
\end{definition}

In other words, if a system of equations is sequential, then for each
$E_i$, any subexpression of $E_i$ in which $X_j $ appears, apart from
$X_j$ itself, is a sum of prefixed expressions. For instance,
%
\begin{itemize}
%
\item $X = \tau . X + \mu . \nil $ is sequential but not guarded, because
the guarding prefix for the variable is not visible;
%
\item $X = \ell . X | P$ is guarded but not sequential;
%
\item $X = \ell . X + \tau . \res a (a .\outC b | a.\nil )$, as well as
$X = \tau . (a. X + \tau . b .X + \tau )$ are both guarded and sequential.
%
\end{itemize}

Milner has three versions of ``unique solution of equations'' theorems,
for $\sim $, $\wbvtex $ and $\rapprox $, respectively, though only the
following two versions are explicitly mentioned in~\citep[p.~103, 158]{Mil89}:
%
%t3.4 #&#
\begin{theorem}[unique solution of equations for $\sim $]
 \label{t:Mil89s1}
Let $E_i$ be weakly guarded with free variables in $\til X$, and let
${\til P} \sim {\til E}\{\til P /\til X\}$,
${\til Q} \sim {\til E}\{\til Q /\til X\}$. Then
${\til P} \sim {\til Q}$.
\end{theorem}

%t3.5 #&#
\begin{theorem}[unique solution of equations for $\rapprox $]
 \label{t:Mil89s3}
Let $E_i$ be guarded and sequential with free variables in $\til X$, and
let ${\til P} \rapprox {\til E}\{\til P /\til X\}$,
${\til Q} \rapprox {\til E}\{\til Q /\til X\}$. Then
${\til P} \rapprox {\til Q}$.
\end{theorem}

The version of Milner's unique-solution theorem for $\wbvtex $ further
requires that all sums are guarded:
%
%t3.6 #&#
\begin{theorem}[unique solution of equations for $\wbvtex $]
 \label{t:Mil89}
Let $E_i$ (with only guarded sums) be guarded and sequential, and with
free variables in $\til X$. Let
${\til P} \wbvtex {\til E}\{\til P /\til X\}$,
${\til Q} \wbvtex {\til E}\{\til Q /\til X\}$, then
${\til P} \wbvtex {\til Q}$.
\end{theorem}

The proof of the last two theorems above exploits an invariance property
on immediate derivatives of guarded and sequential expressions, and then
extracts a bisimulation (up to bisimilarity) out of the solutions of the
system. To see the need of the sequentiality condition, consider the equation
(from~\cite{Mil89}) $X \wbvtex \res a (a. X | \outC a)$ where $X$ is guarded
but not sequential. Any process that does not perform $a$--action is a
solution, e.g. $\nil $ and $b.\nil $.

For more details on the formalisation of the above three theorems, see
Section~\ref{ss:part2} for the \univariate case and Section~\ref{sec:multivariate}
for the \multivariate case.

%s3.2 #&#
\subsection{Expansions and contractions}
%%LEAP%%%\label{sec3.2}
 \label{s:mcontr}

Milner's ``unique solution of equations'' theorem for $\wbvtex $ (\reftext{Theorem~\ref{t:Mil89}})
brings a new proof technique for proving (weak) bisimilarities. However,
it has limitations: the equations must be guarded and sequential. (Moreover,
all sums where equation variables appear must be guarded sums.) This limits
the usefulness of the technique, since the occurrences of other operators
using equation variables, such as parallel composition and restriction,
in general cannot be eliminated. The constraints in \reftext{Theorem~\ref{t:Mil89}},
however, can be weakened if we move from equations to a special kind of
inequations called \emph{contractions}.

Intuitively, the bisimilarity contraction $\mcontrBIS $ is a preorder in
which $P \mcontrBIS Q$ holds if $P \wbvtex Q$ and, in addition,
\emph{$Q$ has the possibility of being at least as efficient as $P$} (as
far as $\tau $-actions are performed). The process $Q$, however, may be
nondeterministic and may have other ways to do the same work, ways which
could be slower (i.e., involving more $\tau $-actions than those performed
by $P$).

%d3.7 #&#
\begin{definition}[contraction]
 \label{d:BisCon}
A process relation ${\Rvtex}$ is a \emph{(bisimulation) contraction} if,
whenever $P\RRvtex Q$,
%
\begin{enumerate}
%
\item $P \arr\mu P'$ implies that there is $Q'$ with
$Q \arcap \mu Q'$ and $P' \RRvtex Q'$;
%
\item $Q \arr\mu Q'$ implies that there is $P'$ with
$P \Arcap \mu P'$ and $P' \wbvtex Q'$.
%
\end{enumerate}
%
Two processes $P$ and $Q$ are in the \emph{bisimilarity contraction}, written
as $P \mcontrBIS Q$, if $P\ \Rvtex \ Q$ for some contraction
$\Rvtex $. Sometimes we write $\mexpaBIS $ for the inverse of
$\mcontrBIS $.
\end{definition}
%
In clause (1) of the above definition, $Q$ is required to match the challenge
transition of $P$ with at most one transition. This makes sure that
$Q$ is capable of mimicking $P$'s work at least as efficiently as
$P$. In contrast, clause (2) entirely ignores efficiency on the challenges
from $Q$: the final derivatives are required to be related by
$\wbvtex $, rather than by $\Rvtex $.

Bisimilarity contraction is coarser than bisimilarity expansion
$\expa $~\cite{arun1992efficiency,sangiorgi2015equations}, one of the most
useful auxiliary relations in up-to techniques:
%
%d3.8 #&#
\begin{definition}[expansion]
 \label{d:expa}
A process relation ${\Rvtex}$ is an \emph{expansion} if, whenever
$P\RRvtex Q$,
%
\begin{enumerate}
%
\item $P \arr\mu P'$ implies that there is $Q'$ with
$Q \arcap \mu Q'$ and $P' \RRvtex Q'$;
%
\item $Q \arr\mu Q'$ implies that there is $P'$ with $P \Arr \mu P'$ and
$P' \RRvtex Q'$.
%
\end{enumerate}
%
Two processes $P$ and $Q$ are in the \emph{bisimilarity expansion}, written
as $P \expa Q$, if $P \RRvtex Q$ for some expansion $\Rvtex $.
\end{definition}
%
Bisimilarity expansion is widely used in proof techniques for bisimilarity.
It intuitively refines bisimilarity by formalising the idea of ``efficiency''
between processes. Clause (1) is the same as for contraction, while in
clause (2) expansion requires $P \Arr \mu P'$, rather than
$P \Arcap \mu P'$. Moreover, in clause (2) of \reftext{Definition~\ref{d:BisCon}} the final
derivatives are simply required to be bisimilar ($P' \wbvtex Q'$). Intuitively,
$P \expa Q$ holds if $P\wbvtex Q$ and, in addition,
\emph{$Q$ is always at least as efficient as $P$}.

%e3.9 #&#
\begin{example}
 \label{exa:contr}
We have $ a \not \mcontrBIS \tau . a$. However,
$a+ \tau . a \mcontrBIS a$, as well as its converse,
$ a \mcontrBIS a + \tau . a $. Indeed, if $P \wbvtex Q$ then
$ P \mcontrBIS P +Q$. The last two relations do not hold with
$\expa $, which explains the strictness of the inclusion
${\expa} \subset {\mcontrBIS}$.
\end{example}

Bisimilarity expansion and bisimilarity contraction are both preorders.
Similarily with (weak) bisimilarity, both the expansion and the contraction
preorders are preserved by all CCS operators except the summation. The
proofs are similar to those for bisimilarity, see, e.g.~\cite{sangiorgi2017equations}
for details.

%s3.3 #&#
\subsection{Systems of contractions}
%%LEAP%%%\label{sec3.3}
 \label{ss:SysContr}

A \emph{system of contractions} is defined as a system of equations, except
that the contraction symbol $\mcontrBIS $ is used in the place of
$=$ in \reftext{Definition~\ref{def:equation}}. Thus a system of contractions is a set
$\{ X_i \mcontrBIS E_i\}_{i\in I}$ where $I$ is an indexing set and each
$E_i$ contains variables in $\til X$.

Now we recall the ``unique solution of contractions'' theorem~\cite{sangiorgi2017equations},
which weakens the requirements of Milner's result (\reftext{Theorem~\ref{t:Mil89}}).

%l3.10 #&#
\begin{lemma}
 \label{l:uptocon}
Suppose $\til P$ and $\til Q$ are solutions (for $\mcontrBIS $) of a system
of weakly guarded contractions that uses guarded sums. For any context
$\qct $ that uses guarded sums, if $\ctvtex{\til P}\Arr{\mu} R$, then there
is a context $\qctp $ that uses guarded sums such that
$R \mcontrBIS \ctp{\til P}$ and
$\ctvtex{\til Q} \Arcap{\mu} R' \wbvtex \ctp{\til Q}$ for some $R'$.
\end{lemma}

\begin{proof}%
{(sketch from~\cite{sangiorgi2017equations})} Let $n$ be the length (i.e.,
the number of one-step transitions) of a transition
$\ctvtex{\til P}\Arr\mu R$, and let $\ctpp {\til P}$ and
$\ctpp {\til Q}$ be the processes obtained from $\ctvtex {\til P}$ and
$\ctvtex {\til Q}$ by unfolding the definition of $\mcontrBIS $ for
$n$ times. Thus in $\qctpp $ each hole is underneath at least $n$ prefixes,
and therefore cannot contribute to an action in the first $n$ transitions.
Moreover, all involved contexts use guarded sums.

We have $\ctvtex{\til P} \mcontrBIS \ctpp{\til P}$ and
$\ctvtex{\til Q} \mcontrBIS \ctpp{\til Q}$ from the precongruence property
of $\mcontrBIS $ (we exploit here the syntactic constraints on sums). Moreover,
since each hole of the context $\qctpp $ is underneath at least $n$ prefixes,
applying the definition of $\mcontrBIS $ on the transition
$\ctvtex{\til P}\Arr{\mu} R$, we infer the existence of $\qctp $ such that
$\ctpp{\til P}\Arcap{\mu} \ctp{\til P} \mexpaBIS R$ and
$\ctpp{\til Q}\Arcap{\mu} \ctp{\til Q}$. Finally, again applying the definition
of $\mcontrBIS $ on $\ctvtex{\til Q} \mcontrBIS \ctpp{\til Q}$, we derive
$\ctvtex{\til Q}\Arcap{\mu} R' \wbvtex \ctp{\til Q}$ for some $R'$.
\end{proof}

%t3.11 #&#
\begin{theorem}[unique solution of contractions~\cite{sangiorgi2017equations}]
 \label{t:contraBisimulationU}
Let $E_i$ (and with guarded sums only) be weakly guarded, with free variables
in $\til X$, and let $\til P \mcontrBIS \til E\{\til P/\til X\}$,
$\til Q \mcontrBIS \til E\{\til Q/\til X\}$. Then
$\til P \wbvtex \til Q$.
\end{theorem}

\begin{proof}
We prove $P_i \wbvtex Q_i$ (for each $i \in I$) by considering the following
relation
%
\begin{equation*}
\Rvtex \DSdefi \{(R,S) \stvtex R \wbvtex \ctvtex{\til P}, S \wbvtex
\ctvtex{\til Q}
\mbox{~for some context $\qct $ (with only guarded sums)} \} .
\end{equation*}

Obviously we have $(P_i,Q_i) \in \Rvtex $ (by taking $C = E_i$, and the
fact that $\mcontrBIS $ implies $\wbvtex $). It remains to show that
$\Rvtex $ is a bisimulation. Suppose $(R, S) \in \Rvtex $ via a context
$C$. For any $R'$ such that $R \arr{\mu} R'$, we have to find an
$S'$ with $S \Arcap{\mu} S'$ and $(R', S') \in \Rvtex $. From
$R \wbvtex C[{\til P}]$, we derive
$C[{\til P}] \Arcap{\mu} R'' \wbvtex R'$ for some $R''$. Then by \reftext{Lemma~\ref{l:uptocon}},
there exists $C'$ with $R'' \mcontrBIS C'[{\til P}]$ and
$C[{\til Q}] \Arcap{\mu} S'' \wbvtex C'[{\til Q}]$ for some $S''$. From
$S \wbvtex C[{\til Q}]$ and $C[{\til Q}] \Arcap{\mu} S''$, by induction
and definition of $\wbvtex $, we find $S'$ with $S \Arcap{\mu} S'$. This
completes the proof, as we have $R' \wbvtex C'[{\til P}]$ and
$S' \wbvtex C'[{\til Q}]$ by transitivity of $\wbvtex $ and the fact that
$\mcontrBIS $ implies $\wbvtex $. (The other side from $S$ follows in the
same manner.) See \reftext{Fig.~\ref{fig:310}} for a visual illustration.
\end{proof}

%f2 #&#
\begin{figure}%[ht]
\vspace{-12pt}
%d3.3 #&#
\begin{sgmlfig}\normalsize
%
$$
\xymatrix{
{C[{\til P}]} \ar@{.}[r]^{\wbvtex} \ar@{=>}[d]^{\widehat{\mu}} & {R} \ar@{-}[r]
\ar@{->}[d]^{\mu} & {\Rvtex} \ar@{-}[r] & {S} \ar@{.}[r]^{\wbvtex}
\ar@{=>}[d]^{\widehat{\mu}} & {C[{\til Q}]} \ar@{=>}[d]^{\widehat{\mu}} \\
{R''} \ar@{.}[d]_{\mcontrBIS} \ar@{.}[r]^{\wbvtex} & {R'} \ar@{-}[r]
\ar@{.}[ld]^{\wbvtex} & {\Rvtex} \ar@{-}[r] & {S'} \ar@{.}[r]^{\wbvtex} \ar@{.}[rd]_{\wbvtex}
& {S''} \ar@{.}[d]^{\wbvtex} \\
{C'[{\til P}]} & {} & {} & {} & {C'[{\til Q}]}
}
%
$$\vspace{-12pt}
\end{sgmlfig}
%
\caption{Proof illustration of \reftext{Theorem~\ref{t:contraBisimulationU}} (showing
$\Rvtex $ is a bisimulation).}
 \label{fig:310}
\end{figure}

%s3.4 #&#
\subsection{Rooted contraction}
%%LEAP%%%\label{sec3.4}
 \label{ss:new}

\reftext{Theorem~\ref{t:contraBisimulationU}} brings a new proof technique for bisimilarity,
which is less restrictive than Milner's \reftext{Theorem~\ref{t:Mil89}} (but with
the additional costs of checking $\mcontrBIS $ in addition to
$\wbvtex $). However, compared with Milner's \reftext{Theorem~\ref{t:Mil89s1}}, there
remains the limitation on the need of guarded sums. This is mainly due
to the fact that $\wbvtex $ is not a congruence and also
$\mcontrBIS $ is not a precongruence. Inspired by rooted bisimilarity,
to eliminate the restriction on guarded sums we refine the idea of contractions
by moving to \emph{rooted contractions}:

%d3.12 #&#
\begin{definition}
 \label{d:rcontra}
Two processes $P$ and $Q$ are in \emph{rooted contraction}, written as
$P\rcontr Q$, if
%
\begin{enumerate}
%
\item $P \arr\mu P'$ implies that there is $Q'$ with $Q \arr \mu Q'$ and
$P'\mcontrBIS Q'$;
%
\item $Q \arr\mu Q'$ implies that there is $P'$ with $P \Arr \mu P'$ and
$P' \wbvtex Q'$.
%
\end{enumerate}
%
\end{definition}

The above definition was found with the help of interactive theorem proving.
The following two principles were adopted when manually searching for a
possible definition: (1) the definition should not be coinductive, along
the lines of rooted bisimilarity $\rapprox $ (\reftext{Definition~\ref{d:rootedBisimilarity}});
(2) the definition should be built on top of the existing
\emph{contraction} relation $\mcontrBIS $. Furthermore, we needed to prove
that the definition being found indeed yields the coarsest precongruence
contained in $\mcontrBIS $. The proof is similar with the analogous result
for $\rapprox $. See Section~\ref{s:coarsest} for more details.

%t3.13 #&#
\begin{theorem}
 \label{t:rcontrPrecongruence}
$\rcontr $ is a precongruence in CCS, and it is the coarsest precongruence
contained in $\mcontrBIS $.
\end{theorem}

For this new relation, the analogous of \reftext{Lemma~\ref{l:uptocon}} and of \reftext{Theorem~\ref{t:contraBisimulationU}}
can now be stated without constraints on summation. The schema of the proofs
is almost identical, because \xch{the only property}{all properties} of $\rcontr $ needed in this
proof is its precongruence, which is indeed true for all weakly guarded
contexts:
%
%l3.14 #&#
\begin{lemma}
 \label{l:ruptocon}
Let $\til P$ and $\til Q$ be solutions (for $\rcontr $) of a system of
weakly guarded contractions. For any context $\qct $, if
$\ctvtex{\til P}\Arr{\mu} R$, then there is a context $\qctp $ such that
$R \mcontrBIS \ctp{\til P}$ and
$\ctvtex{\til Q} \Arr{\mu} R' \wbvtex \ctp{\til Q}$ for some $R'$.
\end{lemma}

The next lemma is actually Lemma 3.13 of~\citep[p.~102]{Mil89}, and is
needed to prove Milner's ``unique solution of equations for $\sim $'' (\reftext{Theorem~\ref{t:Mil89s1}}):
%
%l3.15 #&#
\begin{lemma}
 \label{lem:milner313}
If the variables ${\til X}$ are weakly guarded in $E$, and
$E\{\til P/\til X\} \arr{\alpha} P'$, then $P'$ takes the form
$E'\{\til P/\til X\}$ (for some expression $E'$), and moreover, for any
${\til Q}$, $E\{\til Q/\til X\} \arr{\alpha} E'\{\til Q/\til X\}$.
\end{lemma}

%t3.16 #&#
\begin{theorem}[unique solution of rooted contractions]
 \label{t:rcontraBisimulationU}
Let $E_i$ be weakly guarded with free variables in $\til X$, and let
$\til P \rcontr \til E\{\til P/\til X\}$,
$\til Q \rcontr \til E\{\til Q/\til X\}$. Then
$\til P \rapprox \til Q$.
\end{theorem}

\begin{proof}
We prove $P_i \rapprox Q_i$ (for each $i \in I$) by considering the following
relation
%
\begin{equation*}
\Rvtex \DSdefi \{(R,S) \stvtex R \wbvtex \ctvtex{\til P}, S \wbvtex
\ctvtex{\til Q} \mbox{~for some context $\qct $} \} .
\end{equation*}

Following the same steps in the proof of \reftext{Theorem~\ref{t:contraBisimulationU}}
(using \reftext{Lemma~\ref{l:ruptocon}} in place of \reftext{Lemma~\ref{l:uptocon}}), we can
prove that $(P_i, Q_i) \in \Rvtex $ and $\Rvtex $ is indeed a bisimulation.
But this only shows $P_i \wbvtex Q_i$. To further show
$P_i \rapprox Q_i$, we appeal to \reftext{Lemma~\ref{lobsCongrByWeakBisim}}: for
any $P'$ such that $P_i \arr{\mu} P'$, we have to find a $Q'$ with
$Q_i \Arr{\mu} Q'$ and $(R',S') \in \Rvtex $. From
$P_i \rcontr E_i[{\til P}]$, by definition of $\rcontr $ we derive
$E_i[{\til P}] \arr{\mu} P''$ for some $P''$. Then by \reftext{Lemma~\ref{lem:milner313}}
there exists a context $E'$ with $P'' = E'[{\til P}]$ and
$E_i[{\til Q}] \arr{\mu} E'[{\til Q}]$. From
$Q_i \rcontr E_i[{\til Q}]$ and
$E_i[{\til Q}] \arr{\mu} E'[{\til Q}]$, by definition of $\rcontr $ we
have $Q_i \Arr{\mu} Q'$ for some $Q'$ and $Q' \wbvtex E'[{\til Q}]$. This
completes the proof, as we have $P' \wbvtex C[{\til P}]$ (by the fact that
$\mcontrBIS $ implies $\wbvtex $) and $Q' \wbvtex C[{\til Q}]$. (The other
side from $Q_i$ follows in the same manner.) See \reftext{Fig.~\ref{fig:314}} for
a visual illustration.
\end{proof}

%f3 #&#
\begin{figure}%[ht]
\vspace{-12pt}%
%d3.4 #&#
\begin{sgmlfig}\normalsize
%
$$
\xymatrix{
{E_i[{\til P}]} \ar@{.}[r]^{\preceq ^{\mathrm{c}}_{\mathrm{bis}}} \ar@{->}[d]^{\mu} & {P_i} \ar@{-}[r]
\ar@{->}[d]^{\mu} & {\Rvtex} \ar@{-}[r] & {Q_i} \ar@{.}[r]^{\rcontr}
\ar@{=>}[d]^{\mu} & {E_i[{\til Q}]} \ar@{->}[d]^{\mu} \\
{P'' = E'[{\til P}]} \ar@{.}[r]^{\qquad \preceq _{\mathrm{bis}}} & {P'} \ar@{-}[r] & {\Rvtex} \ar@{-}[r] & {Q'} \ar@{.}[r]^{\wbvtex}
& {E'[{\til Q}]} \\
}
%
$$\vspace{-12pt}
\end{sgmlfig}
%
\caption{Proof illustration of \reftext{Theorem~\ref{t:rcontraBisimulationU}} (showing
$P_i \rapprox Q_i$).}
 \label{fig:314}
\end{figure}

%s4 #&#
\section{The formalisation}
%%LEAP%%%\label{sec4}
 \label{s:for}

We highlight here a comprehensive formalisation of CCS in the HOL theorem
prover (HOL4)~\cite{Melham:1993vl,slind2008brief}, with a focus towards
the theory (and formal proofs) of the unique solution of equations/contractions
theorems mentioned in Section~\ref{s:eq} and \ref{s:mcontr}. All proof
scripts are available as part of HOL's official examples.\footnote{\url{https://github.com/HOL-Theorem-Prover/HOL/tree/master/examples/CCS}.}
The work so far consists of about 24,000 lines (1MB) of code in total,
in which about 5,000 lines were derived from the early work of Monica Nesi~\cite{Nesi:1992ve}
on HOL88, with major modifications.

Higher Order Logic (HOL)~\cite{hollogic} traces its roots back to the
\emph{Logic of Computable Functions (LCF)}~\cite{gordon1979edinburgh,milner1972logic}
by Robin Milner and others since 1972. It is a variant of Church's Simple
Theory of Types (STT)~\cite{church1940formulation}, plus a higher order
version of Hilbert's choice operator $\varepsilon $, Axiom of Infinity,
and Rank-1 (prenex) polymorphism. HOL4 has implemented the original HOL,
while some other theorem provers in the HOL family (e.g.~Isabelle/HOL)
have certain extensions. Indeed, HOL has considerably simpler logical foundations
than most other theorem provers. As a consequence, theories and proofs
verified in HOL are easier to understand for people who are not \xch{familiar}{familar}
with more advanced dependent type theories, e.g. the Calculus of Constructions
implemented in Coq.

HOL4 is implemented in Standard ML, and the same programming language plays
three different roles:
%
\begin{itemize}
%
\item The underlying implementation language for the core HOL engine;
%
\item The language in which proof tactics are implemented;
%
\item The interface language of the HOL proof scripts and interactive shell.
%
\end{itemize}
%
Moreover, using the same language HOL4 users can write complex automatic
verification tools by calling HOL's theorem proving facilities. The formal
proofs of the CCS theorems that we have carried out are mostly done in
a manner that closely follows their paper proofs, with minimal automatic
proof searching.

%s4.1 #&#
\subsection{Higher order logic (HOL)}
 \label{sec4.1}

HOL is a formal system of typed logical terms. The types are expressions
that denote sets (in the universe $\mathcal{U}$). HOL type system is much
simpler than those based on dependent types and other type theories. There
are four kinds of types in the HOL logic, as illustrated in \reftext{Fig.~\ref{fig:hol-types}} for its BNF grammar. In HOL, the standard atomic types
\emph{bool} and \emph{ind} denote, respectively, the distinguished two-element
set $\mathbf{2}$ and the distinguished infinite set $\mathbf{I}$.

%f4 #&#
\begin{figure}%[h]
\vspace{-12pt}%
\begin{sgmlfig}\normalsize
%
$$
\sigma \quad ::=\quad {\mathord{\mathop{\alpha}\limits _{\tyvar}}}
\quad \mid \quad{\mathord{\mathop{c}\limits _{\tyatom}}} \quad \mid
\quad \underbrace{(\sigma _1, \ldots , \sigma _n){op}}_{\cmpty}
\quad \mid \quad \underbrace{\sigma _1\fun \sigma _2}_{\funty}
%
$$\vspace{-12pt}
\end{sgmlfig}
%
\caption{HOL's type grammar.}
 \label{fig:hol-types}
\end{figure}

HOL terms represent elements of the sets denoted by their types. There
are four kinds of HOL terms, which can be described (in simplified forms)
by the BNF grammar in \reftext{Fig.~\ref{fig:hol-terms}}. (See~\cite{hollogic} for
a complete description of HOL, including the primitive derivative rules
to be mentioned below.)

%f5 #&#
\begin{figure}%[h]
\vspace{-12pt}%
\begin{sgmlfig}\normalsize
%
$$
t \quad ::=\quad {\mathord{\mathop{x}\limits _{\var}}} \quad \mid
\quad{\mathord{\mathop{c}\limits _{\const}}} \quad \mid \quad
\underbrace{t\ t'}_{\app} \quad \mid \quad
\underbrace{\lambda x .\ t}_{\abs}
%
$$\vspace{-12pt}
\end{sgmlfig}
%
\caption{HOL's term grammar.}
 \label{fig:hol-terms}
\end{figure}

The deductive system of HOL is specified by eight primitive derivative
rules:
%
\begin{enumerate}
%
\item Assumption introduction (\texttt{ASSUME});
%
\item Reflexivity (\texttt{REFL});
%
\item $\beta $-conversion (\texttt{BETA\_CONV});
%
\item Substitution (\texttt{SUBST});
%
\item Abstraction (\texttt{ABS});
%
\item Type instantiation (\texttt{INST\_TYPE});
%
\item Discharging an assumption (\texttt{DISCH});
%
\item Modus Ponens (\texttt{MP}).
%
\end{enumerate}
%
All proofs are eventually reduced to applications of the above rules, which
also give the semantics of two \xch{fundamental}{foundamental} logical connectives, equality
($=$) and implication ($\Rightarrow $). The remaining logical connectives
and first-order quantifiers, including the logical true (\HOLinline{\HOLConst{T}})
and false (\HOLinline{\HOLConst{F}}), are further defined as
$\lambda $-functions:
%
\begin{equation*}
%
\begin{array}{l}
\turn \Tvtex \HOLTokenDefEquality ((\lquant{x_{\tyvtex{bool}}}x) = (
\lquant{x_{\tyvtex{bool}}}x))
\\
\turn \forall \HOLTokenDefEquality
\lquant{P_{\alpha \fun \tyvtex{bool}}} P = (\lquant{x}\Tvtex )
\\
\turn \exists \HOLTokenDefEquality
\lquant{P_{\alpha \fun \tyvtex{bool}}} P({\hilbert}\, P)
\\
\turn \Fvtex \HOLTokenDefEquality \uquant{b_{\tyvtex{bool}}} b
\\
\turn \neg \HOLTokenDefEquality \lquant{b} b \imp \Fvtex
\\
\turn {\wedge} \HOLTokenDefEquality \lquant{b_1\ b_2}\uquant{b} (b_1
\imp (b_2 \imp b)) \imp b
\\
\turn {\vee} \HOLTokenDefEquality \lquant{b_1\ b_2}\uquant{b} (b_1
\imp b)\imp ((b_2 \imp b) \imp b)
\\
\turn \OneOne \HOLTokenDefEquality \lquant{f_{\alpha \fun \beta}}
\uquant{x_1\ x_2} (f\ x_1 = f\ x_2) \imp (x_1 = x_2)
\\
\turn \Onto \HOLTokenDefEquality \lquant{f_{\alpha \fun \beta}}
\uquant{y}\equant{x} y = f\ x
\\
\turn \TyDef \HOLTokenDefEquality \lambda P_{\alpha \fun
\tyvtex{bool}}\
 rep_{\beta \fun \alpha}.\; \OneOne \ rep \ \wedge{}\  (\uquant{x}P x =
(\equant{y} x = rep\ y))
\end{array}
%
\end{equation*}
%
The last logical constant, $\TyDef $, can be used to define new HOL types
as bijections of subsets of existing types~\cite{Melham:1989dk}. HOL
\texttt{Datatype} package~\cite{Melham:1991,holdesc} automates this tedious
process, and can be used for defining the types needed for CCS. Finally,
the whole HOL \emph{standard} theory is based on the following four axioms\footnote{HOL
is strictly weaker than ZFC (the Zermelo-Frankel set theory with the Axiom
of Choice), thus not all theorems valid in ZFC can be formalised in HOL.
(See~\cite{hollogic} for more details.)}:
%
\begin{equation*}
%
\begin{array}{@{}l@{\qquad}l}
\mbox{\texttt{BOOL\_CASES\_AX}} &\vdash \uquant{b} (b = \Tvtex )\
\vee \ (b = \Fvtex )
\\
\mbox{\texttt{ETA\_AX}} & \vdash \uquant{f_{\alpha \fun \beta}}(
\lquant{x}f\ x) = f
\\
\mbox{\texttt{SELECT\_AX}} & \vdash
\uquant{P_{\alpha \fun \tyvtex{bool}}\ x} P\ x \imp P({\hilbert}\ P)
\\
\mbox{\texttt{INFINITY\_AX}}& \vdash \equant{f_{\ind \fun \ind}}
\OneOne \ f \conj \neg (\Onto \ f)
\\
\end{array}
%
\end{equation*}

Usually the above four axioms are the only axioms allowed in conventional
formalisation projects in HOL4: adding new axioms manually may break logical
consistency.

%s4.2 #&#
\subsection{The CCS formalisation}
%%LEAP%%%\label{sec4.2}
 \label{ss:formalCCS}

The CCS formalisation starts with type definitions for action, relabeling
and then the processes. We use the type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}''
for all labels (i.e. visible actions), where the type variable
$\beta $ corresponds to $\mathscr{L}$ (the set of names for labels) mentioned
at the beginning of Section~\ref{ss:ccs}. (Thus the cardinality of ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}''
depends on its type variable: when $\beta $ is finite or countable, ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}''
is countable.) All labels are divided into input and output ones. The type
``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}'' is defined by HOL's
\texttt{Datatype} package in the following syntax:
%
\begin{lstlisting}
Datatype: Label = name 'b | coname 'b
End
\end{lstlisting} Intuitively, ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Label}}''
turns names in $\mathscr{L}$ into \emph{input and output labels}. For instance,
if the type $\beta $ is instantiated to \texttt{string} (the type of all
ASCII strings), then the HOL terms
\HOLinline{\HOLConst{name} \HOLStringLit{a}} and
\HOLinline{\HOLConst{coname} \HOLStringLit{b}} denote the input label
$a$ and output label $\overline{b}$, respectively. The type ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Action}}''
is the union of all visible actions (input and output labels) and the invisible
action $\tau $ (\texttt{tau}). For \xch{instance}{instace}, the input \emph{action}
$a$ and output \emph{action} $\overline{b}$ of type ``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''
are denoted by
\HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLStringLit{a}\ensuremath{)}}
and
\HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLStringLit{b}\ensuremath{)}},
respectively. On the other hand,
\HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{name} \HOLNumLit{1}\ensuremath{)}}
and
\HOLinline{\HOLConst{label} \ensuremath{(}\HOLConst{coname} \HOLNumLit{2}\ensuremath{)}}
could be actions of type ``\HOLinline{\HOLTyOp{num} \HOLTyOp{Action}}'',
where \HOLinline{\HOLTyOp{num}} is the type of natural numbers in HOL.

The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'',
accounting for all CCS terms, has two type variables $\alpha $ and
$\beta $ corresponding to the set of agent variables $\mathscr{X}$ and
the set of names $\mathscr{L}$, respectively. (Indeed the CCS syntax in
Section~\ref{ss:ccs} is parametric with respect to the choice of these
two sets.) The type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}''
is defined inductively by the \texttt{Datatype} package (here ``\HOLinline{\ensuremath{\beta} \HOLTyOp{Relabeling}}''
is the type of all relabeling functions; we have also formalised relabeling,
though it is not discussed below):\looseness=-1
%
\begin{lstlisting}
Datatype: CCS = nil
              | var 'a
              | prefix ('b Action) CCS
              | sum CCS CCS
              | par CCS CCS
              | restr (('b Label) set) CCS
              | relab CCS ('b Relabeling)
              | rec 'a CCS
End
\end{lstlisting} The above definition allows us to write terms like
\texttt{nil} and \texttt{sum P Q} in HOL4. Their correspondences with conventional
CCS notations in the literature are given in \reftext{Table~\ref{tab:ccsoperator}},
where most CCS operators have also more readable abbreviated forms, either
for end users or for \TeX{} outputs. (All formal theorems and definitions
in this paper are generated from HOL4. Also, by default, all theorems are
fully specialised with outermost universal quantifiers removed.)

%t1 #&#
\begin{table}
%\tablewidth=
\caption{Syntax of some CCS concepts in HOL.}
 \label{tab:ccsoperator}
%
%
\begin{tabular*}{\tablewidth}{lllll}
\hline
CCS concept & Notation & HOL term &
                                             HOL abbrev. & \TeX{} outputs \\
\hline
nil & $\textbf{0}$ & \texttt{nil} & \texttt{nil} & \HOLinline{\HOLConst{\ensuremath{\mathbf{0}}}} \\
prefix & $\mu .P$ & \texttt{prefix u P} & \texttt{u..P}
& \HOLinline{\HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{P}} \\
summation & $P + Q$ & \texttt{sum P Q} & \texttt{P + Q}
& \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{Q}} \\
parallel composition & $P \,\mid \, Q$ & \texttt{par P Q} & \texttt{P || Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{Q}} \\
restriction & $(\nu{}L)\;P$ & \texttt{restr L P} & \texttt{(nu L) P} & \HOLinline{\ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{P}}  \\
recursion & $\recu A P$ & \texttt{rec A P} & \texttt{rec A P} & \HOLinline{\HOLConst{rec} \HOLFreeVar{A} \HOLFreeVar{P}}  \\
relabeling & $P\;[r\!f]$ & \texttt{relab P rf} &\texttt{relab P rf} & \HOLinline{\HOLConst{relab} \HOLFreeVar{P} \HOLFreeVar{rf}}  \\
constant/variable & $A$ & \texttt{var A} &\texttt{var A} & \HOLinline{\HOLConst{var} \HOLFreeVar{A}} \\
[\tvspace{6pt}]
invisible action & $\tau $ & \texttt{tau} & \texttt{tau} & \HOLinline{\HOLSymConst{\ensuremath{\tau}}} \\
input action & $a$ & \texttt{label (name a)} &\texttt{In(a)} & \HOLinline{\HOLConst{\HOLTokenInputAct} \HOLFreeVar{a}} \\
output action & $\outC a$ & \texttt{label (coname a)} & \texttt{Out(a)} & \HOLinline{\HOLConst{\HOLTokenOutputAct} \HOLFreeVar{a}} \\
[\tvspace{6pt}]
variable substitution & $E\{E'/X\}$ & \texttt{CCS\_Subst E E' X} &
                                           \texttt{[E'/X]  E} & \HOLinline{\ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}} \\
transition & $P\overset{\mu}{\longrightarrow}Q$
                       & \texttt{TRANS P u Q} & \texttt{P ---u-> Q} & \HOLinline{\HOLFreeVar{P} \HOLTokenTransBegin \HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{Q}} \\
weak transition & $P\overset{\mu}{\Longrightarrow}Q$
                       & \texttt{WEAK\_TRANS P u Q} & \texttt{P ==u=> Q} & \HOLinline{\HOLFreeVar{P} \HOLTokenWeakTransBegin \HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{Q}} \\
$\epsilon $--transition & $P\overset{\epsilon}{\Longrightarrow}Q$
                       & \texttt{EPS P Q} & \texttt{EPS P Q} & \HOLinline{\HOLFreeVar{P} \HOLSymConst{\HOLTokenEPS} \HOLFreeVar{Q}} \\
\hline
\end{tabular*}
%
%
\end{table}

The transition semantics of CCS processes strictly follows the SOS rules
given in \reftext{Fig.~\ref{f:LTSCCS}}. However, they are not axioms but consequences
of an \emph{inductive relation} definition of
\HOLinline{\HOLConst{TRANS}} by the \texttt{HOL\_reln} function of HOL4
(see~\citep[p.~219]{holdesc} for more details). The successful invocation
of the definitional principle returns three important theorems (\texttt{TRANS\_rules},
\texttt{TRANS\_ind} and \texttt{TRANS\_cases}):
%
\begin{itemize}
%
\item \texttt{TRANS\_rules} is a conjunction of implications (each corresponding
to a SOS rule) that will be the same as the input term. In fact, the following
formal versions of SOS rules are extracted from \texttt{TRANS\_rules}:
%
%a4.2 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E}\hfill\texttt{[PREFIX]}
\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}\hfill\texttt{[SUM1]}
\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}\hfill\texttt{[SUM2]}
\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sp{\prime}}\hfill\texttt{[PAR1]}
\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}\hfill\texttt{[PAR2]}
\end{alltt}
%
\begin{equation*}
\infer[\HOLRuleName{PAR3}]{\HOLinline{\HOLFreeVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin \HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin \HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}}&\HOLinline{\ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin \HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLFreeVar{l}\ensuremath{)}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}}}
\end{equation*}
%
\begin{equation*}
\infer[\HOLRuleName{RESTR}]{\HOLinline{\ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E} \HOLTokenTransBegin \HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \ensuremath{\HOLFreeVar{E}\sp{\prime}}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin \HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime}}}&\HOLinline{\HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLFreeVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}}}
\end{equation*}
%
\begin{equation*}
\infer[\HOLRuleName{RELABELING}]{\HOLinline{\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin \HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLFreeVar{rf}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin \HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime}}}}
\end{equation*}
%
\begin{equation*}
\infer[\HOLRuleName{REC}]{\HOLinline{\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E} \HOLTokenTransBegin \HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}}}{\HOLinline{\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin \HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}}}
\end{equation*}
%
\item \texttt{TRANS\_ind} is the induction principle for the relation (see
Section~\ref{sec:multivariate} for its exact statement and an application
in the proof of \reftext{Proposition~\ref{prop:transFV}}).
%
\item \texttt{TRANS\_cases} is the so-called `cases' or `inversion' theorem
for the relation, and is used to decompose an element in the relation into
the possible ways of obtaining it by the rules:
%
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}.
       \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenEquiv{}}
       \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenDisj{}} \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}. \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}. \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}. \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}. \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \HOLBoundVar{l} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
            \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}}
            \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLBoundVar{l}\ensuremath{)}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{l} \HOLBoundVar{L}.
            \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
            \ensuremath{(}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLBoundVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{rf}.
            \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{=}} \HOLConst{relabel} \HOLBoundVar{rf} \HOLBoundVar{u} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \HOLConst{relab} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{rf} \HOLSymConst{\HOLTokenConj{}}
            \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \HOLBoundVar{X}. \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \ensuremath{[}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}
\end{alltt}
%
For instance, the following proposition requires \texttt{TRANS\_cases}:
%
%a4.2 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\Prime}} \HOLSymConst{\HOLTokenEquiv{}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\Prime}} \HOLSymConst{\HOLTokenDisj{}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\Prime}}\hfill{[TRANS\_SUM\_EQ]}
\end{alltt}
%
\end{itemize}

In particular, the SOS rule \texttt{REC} (Recursion) says that if we substitute
all occurrences of the variable $A$ in $P$ to $(\recu A P)$ and the resulting
process has a transition to $P'$ with an action $u$, then
$(\recu A P)$ has the same transition. Here ``\HOLinline{\ensuremath{[}\HOLConst{rec}\;\;\HOLFreeVar{X}\;\;\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\;\;\HOLFreeVar{E}}''
is an abbreviation for ``\HOLinline{\HOLConst{CCS\_Subst}\;\;\HOLFreeVar{E}\;\;\ensuremath{(}\HOLConst{rec}\;\;\HOLFreeVar{X}\;\;\HOLFreeVar{E}\ensuremath{)}\;\;\HOLFreeVar{X}}'',
where \HOLinline{\HOLConst{CCS\_Subst}} is a recursive function substituting
all occurrences of a free variable with a CCS term. For most CCS operators
\HOLinline{\HOLConst{CCS\_Subst}} just recursively goes into a deeper level
without changing anything, e.g.:
%
%a4.2 #&#
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}\hfill{[CCS\_Subst\_sum]}
\end{alltt}
%
The only two \xch{interesting}{insteresting} cases are those for agent variables and recursion:
%
%a4.2 #&#
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{var} \HOLFreeVar{Y}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}\hfill{[CCS\_Subst\_var]}
\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} \ensuremath{(}\ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\hfill{[CCS\_Subst\_rec]}
\end{alltt}
%
Notice that variable substitutions only affect free variables. For instance,
the variable $Y$ in ``\HOLinline{\HOLConst{rec}\!\;\HOLFreeVar{Y}\!\;\HOLFreeVar{E}}''
is bound and therefore the substitution ignores it.

A useful facility exploiting the interplay between HOL4 and Standard ML
(which follows an idea of Nesi~\cite{Nesi:1992ve}) is a recursive ML function
that takes a CCS process and returns a theorem indicating all direct transitions
of the process. (If the input process is infinitely branching, the function
will not terminate, however.) For instance, we know that the process
$(a.\nil | \bar{a}.\nil )$ has three immediate derivatives given by the
following transitions:
$(a.\nil | \bar{a}.\nil ) \overset{a}{\longrightarrow} (\nil |
\bar{a}.\nil )$,
$(a.\nil | \bar{a}.\nil ) \overset{\bar{a}}{\longrightarrow} (a.\nil |
\nil )$ and
$(a.\nil | \bar{a}.\nil ) \overset{\tau}{\longrightarrow} (\nil |
\nil )$. To completely describe all possible transitions of the process,
the following two facts have to be proved: (1) there are indeed the three
transitions mentioned above; (2) there is no other transition. For large
CCS processes it is surprisingly tedious to manually derive all the possible
transitions and prove the non-existence of other transitions. This shows
the usefulness of appealing to an ML function
\texttt{CCS\_TRANS\_CONV} that is designed to automate the whole process.
For instance, taking the input $(a.\nil | \bar{a}.\nil )$ the function
returns the following theorem which describes all its one-step transitions:
%
%a4.2 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}}
   \ensuremath{(}\HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenOutputAct} \HOLStringLit{a} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\HOLTokenInputAct} \HOLStringLit{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
   \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{\ensuremath{\mathbf{0}}}
\end{alltt}

%s4.3 #&#
\subsection{Bisimulation and bisimilarity}
%%LEAP%%%\label{sec4.3}
 \label{ss:bb}

A highlight of this CCS formalisation is the simplified definitions of
bisimilarities using the new coinduction package of HOL4. Without this
package, \xch{bisimilarities}{bisimilaries} can still be defined in HOL, but proving their properties
would be more tedious and complicated~\citep[p.~91]{Mil89}. Below we briefly
describe how weak bisimulation and weak bisimilarity are defined in HOL.
Strong bisimulation and strong bisimilarity, as well as other concepts
such as expansion and contraction, can be defined in the same manner.

To define (weak) bisimilarity, first we need to define weak transitions
of CCS processes. A (possibly empty) sequence of $\tau $-transitions between
two processes is defined as a new binary relation
\HOLinline{\HOLConst{EPS}} ($\overset{\epsilon}{\Longrightarrow}$), which
is the reflexive and transitive closure (RTC, denoted by a superscript
$^{*}$) of ordinary $\tau $-transitions of CCS processes:
%
%a4.3 #&#
\begin{alltt}
   \HOLConst{EPS} \HOLTokenDefEquality{} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}. \HOLBoundVar{E} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)}\HOLSymConst{\HOLTokenSupStar{}}\hfill{[EPS\_def]}
\end{alltt}
%
Then we can define a weak transition as an ordinary transition wrapped
by two $\epsilon $-transitions:
%
%a4.3 #&#
\begin{alltt}
   \HOLFreeVar{E} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenDefEquality{} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \HOLFreeVar{E} \HOLSymConst{\HOLTokenEPS} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenEPS} \ensuremath{\HOLFreeVar{E}\sp{\prime}}\hfill{[WEAK\_TRANS]}
\end{alltt}
%
The definition of weak bisimulation is then based on weak and
$\epsilon $--transitions:
%
%a4.3 #&#
\begin{alltt}
   \HOLConst{WEAK\_BISIM} \HOLFreeVar{Wbsm} \HOLTokenDefEquality{}
     \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
         \HOLFreeVar{Wbsm} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l}.
              \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
              \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenEPS} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
         \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLSymConst{\HOLTokenEPS} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\hfill{[WEAK\_BISIM]}
\end{alltt}

We can prove, for example, that the identity relation (\HOLinline{\HOLTokenLambda{}\HOLBoundVar{x}\;\!\HOLBoundVar{y}.\;\!\HOLBoundVar{x}\;\!\HOLSymConst{\ensuremath{=}}\;\!\HOLBoundVar{y}})
is indeed a bisimulation, and that bisimulation is preserved by inversion,
composition, and union operations. Weak bisimilarity can be then defined
in HOL4 by the following code:
%
\begin{lstlisting}
CoInductive WEAK_EQUIV :
    !(E :('a, 'b) CCS) (E' :('a, 'b) CCS).
       (!l.
         (!E1. TRANS E  (label l) E1 ==>
               (?E2. WEAK_TRANS E' (label l) E2 /\ WEAK_EQUIV E1 E2)) /\
         (!E2. TRANS E' (label l) E2 ==>
               (?E1. WEAK_TRANS E  (label l) E1 /\ WEAK_EQUIV E1 E2))) /\
       (!E1. TRANS E  tau E1 ==> (?E2. EPS E' E2 /\ WEAK_EQUIV E1 E2)) /\
       (!E2. TRANS E' tau E2 ==> (?E1. EPS E  E1 /\ WEAK_EQUIV E1 E2))
      ==> WEAK_EQUIV E E'
End
\end{lstlisting} Like the case of \HOLinline{\HOLConst{TRANS}}, the successful
invocation of the coinductive definitional principle returns three theorems
(\texttt{WEAK\_EQUIV\_rules}, \texttt{WEAK\_EQUIV\_coind} and
\texttt{WEAK\_EQUIV\_cases}):
%
\begin{itemize}
%
\item \texttt{WEAK\_EQUIV\_rules} is the same as the input term, which now
becomes a theorem:
%
%a4.2 #&#
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l}.
        \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLFreeVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLFreeVar{E} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLFreeVar{E} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenEPS} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLFreeVar{E} \HOLSymConst{\HOLTokenEPS} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLFreeVar{E} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLFreeVar{E}\sp{\prime}}
\end{alltt}
%
\item \texttt{WEAK\_EQUIV\_coind} is the coinduction principle for
\HOLinline{\HOLConst{WEAK\_EQUIV}} ($\wbvtex $):
%
%a4.2 #&#
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}.
        \ensuremath{\HOLFreeVar{WEAK\HOLTokenUnderscore{}EQUIV}\sp{\prime}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}}
        \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l}.
             \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}.
                  \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}}
                  \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLFreeVar{WEAK\HOLTokenUnderscore{}EQUIV}\sp{\prime}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
             \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
                 \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLFreeVar{WEAK\HOLTokenUnderscore{}EQUIV}\sp{\prime}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenEPS} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLFreeVar{WEAK\HOLTokenUnderscore{}EQUIV}\sp{\prime}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\HOLTokenEPS} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLFreeVar{WEAK\HOLTokenUnderscore{}EQUIV}\sp{\prime}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}. \ensuremath{\HOLFreeVar{WEAK\HOLTokenUnderscore{}EQUIV}\sp{\prime}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}
\end{alltt}
%
\item \texttt{WEAK\_EQUIV\_cases} is the so-called `cases' or `inversion'
theorem for the relations, and is used to decompose an element in the relation
into the possible ways of obtaining it by the rules:
%
%a4.2 #&#
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{\HOLFreeVar{a}\sb{\mathrm{0}}} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLFreeVar{a}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenEquiv{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l}.
        \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \ensuremath{\HOLFreeVar{a}\sb{\mathrm{0}}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLFreeVar{a}\sb{\mathrm{1}}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLFreeVar{a}\sb{\mathrm{1}}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \ensuremath{\HOLFreeVar{a}\sb{\mathrm{0}}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \ensuremath{\HOLFreeVar{a}\sb{\mathrm{0}}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLFreeVar{a}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenEPS} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLFreeVar{a}\sb{\mathrm{1}}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \ensuremath{\HOLFreeVar{a}\sb{\mathrm{0}}} \HOLSymConst{\HOLTokenEPS} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
\end{alltt}
%
\end{itemize}

The coinduction principle \texttt{WEAK\_EQUIV\_coind} says that any bisimulation
is contained in the resulting relation. The purpose of
\texttt{WEAK\_EQUIV\_cases} is to further assert that such resulting relation
is indeed a fixed point. Thus \texttt{WEAK\_EQUIV\_coind} and
\texttt{WEAK\_EQUIV\_cases} together make sure that bisimilarity is the greatest
fixed point.

The original definition of \texttt{WEAK\_EQUIV} now becomes a theorem:
%
%a4.2 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{Wbsm}. \HOLBoundVar{Wbsm} \HOLFreeVar{E} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WEAK\_BISIM} \HOLBoundVar{Wbsm}\hfill{[WEAK\_EQUIV]}
\end{alltt}

The formal definition of rooted bisimilarity ($\rapprox $,
\texttt{OBS\_CONGR}) is not recursive and follows \reftext{Definition~\ref{d:rootedBisimilarity}}:
%
%a4.2 #&#
\begin{alltt}
   \HOLFreeVar{E} \HOLSymConst{\HOLTokenObsCongr} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenDefEquality{}
     \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u}.
         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
         \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLFreeVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\hfill{[OBS\_CONGR]}
\end{alltt}
%
Below is the formal version of \reftext{Lemma~\ref{lobsCongrByWeakBisim}} (\texttt{OBS\_CONGR\_BY\_WEAK\_BISIM}),
which is needed later, in the proof of \reftext{Theorem~\ref{t:rcontraBisimulationU}}:
%
%a4.2 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{WEAK\_BISIM} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u}.
            \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
            \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \ensuremath{\HOLBoundVar{E}\sp{\prime}}
\end{alltt}

Finally, on the relationship between (weak) bisimilarity and rooted bisimilarity,
we have proved Deng's Lemma and Hennessy's Lemma (Lemma 4.1 and 4.2 of~\citep[p.~176,~178]{Gorrieri:2015jt}):
%
%a4.2 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}.
       \HOLBoundVar{p} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\HOLTokenImp{}}
       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{p}\sp{\prime}}. \HOLBoundVar{p} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{p}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{p}\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}} \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{q}\sp{\prime}}. \HOLBoundVar{q} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{q}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{p} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLBoundVar{q}\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}} \HOLBoundVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{q}\hfill{[DENG\_LEMMA]}
\end{alltt}

\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}. \HOLBoundVar{p} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLBoundVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{q} \HOLSymConst{\HOLTokenDisj{}} \HOLBoundVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLSymConst{\ensuremath{\tau}}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{q} \HOLSymConst{\HOLTokenDisj{}} \HOLSymConst{\ensuremath{\tau}}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{q}\hfill{[HENNESSY\_LEMMA]}
\end{alltt}
%
These are useful results in the theory of CCS (though we will not need
them in the remainder of the paper).

%s4.4 #&#
\subsection{Algebraic laws}
%%LEAP%%%\label{sec4.4}
 \label{ss:alaws}

Having formalised the definitions of strong bisimulation and strong bisimilarity,
we can derive \emph{algebraic laws} for the bisimilarities. We only report
a few algebraic laws on summation:
%
%a4.4 #&#
\begin{alltt}
STRONG\_SUM\_IDEMP:          \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E}
STRONG\_SUM\_COMM:           \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenStrongEQ} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E}
STRONG\_SUM\_IDENT\_L:        \HOLTokenTurnstile{} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E}
STRONG\_SUM\_IDENT\_R:        \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E}
STRONG\_SUM\_ASSOC\_R:        \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\Prime}} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{(}\ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\Prime}}\ensuremath{)}
STRONG\_SUM\_ASSOC\_L:        \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{(}\ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\Prime}}\ensuremath{)} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\Prime}}
STRONG\_SUM\_MID\_IDEMP:      \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E} \HOLSymConst{\HOLTokenStrongEQ} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E}
STRONG\_LEFT\_SUM\_MID\_IDEMP: \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\Prime}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\Prime}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\prime}}
\end{alltt}

The first five of them are proven by constructing appropriate bisimulations,
and their formal proofs are written in a goal-directed manner~\citep[Chapter 4]{holdesc}.
In \xch{contrast}{constrast}, the last three algebraic laws are derived in a forward manner
by applications of previous proven laws (without directly using the SOS
inference rules and the definition of bisimulation). These algebraic laws
also hold for weak bisimilarity and rooted bisimilarity, as these are coarser
than strong bisimilarity. For weak bisimilarity and rooted bisimilarity,
the following algebraic laws, called $\tau $-laws, hold:
%
%a4.4 #&#
\begin{alltt}
TAU1:      \HOLTokenTurnstile{} \HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLSymConst{\ensuremath{\tau}}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{E} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{E}
TAU2:      \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \HOLSymConst{\ensuremath{\tau}}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{E} \HOLSymConst{\HOLTokenObsCongr} \HOLSymConst{\ensuremath{\tau}}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{E}
TAU3:      \HOLTokenTurnstile{} \HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{(}\HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \HOLSymConst{\ensuremath{\tau}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{)} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{(}\HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \HOLSymConst{\ensuremath{\tau}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{)}
TAU\_STRAT: \HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \HOLSymConst{\ensuremath{\tau}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{(}\ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenObsCongr} \HOLSymConst{\ensuremath{\tau}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{(}\ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E}\ensuremath{)}
TAU\_WEAK:  \HOLTokenTurnstile{} \HOLSymConst{\ensuremath{\tau}}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{E} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E}
\end{alltt}

%s4.5 #&#
\subsection{Expansion, contraction and rooted contraction}
 \label{sec4.5}

We formalise and contraction along the lines of strong and weak bisimilarity:
%
%a4.5 #&#
\begin{alltt}
   \HOLConst{EXPANSION} \HOLFreeVar{Exp} \HOLTokenDefEquality{}
     \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
         \HOLFreeVar{Exp} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l}.
              \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Exp} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
              \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Exp} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{Exp} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenDisj{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Exp} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
         \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Exp} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\hfill{[EXPANSION]}
\end{alltt}

\begin{alltt}
\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLSymConst{\HOLTokenExpands{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{Exp}. \HOLBoundVar{Exp} \HOLFreeVar{P} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EXPANSION} \HOLBoundVar{Exp}\hfill{[expands\_thm]}
\end{alltt}

\begin{alltt}
   \HOLConst{CONTRACTION} \HOLFreeVar{Con} \HOLTokenDefEquality{}
     \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
         \HOLFreeVar{Con} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l}.
              \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Con} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
              \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{Con} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenDisj{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Con} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
         \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLSymConst{\HOLTokenEPS} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\hfill{[CONTRACTION]}
\end{alltt}

\begin{alltt}
\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{Con}. \HOLBoundVar{Con} \HOLFreeVar{P} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTRACTION} \HOLBoundVar{Con}\hfill{[contracts\_thm]}
\end{alltt}

The contraction preorder ($\mcontrBIS $) contains the expansion preorder
($\expa $), and they are both contained in weak bisimilarity ($
\wbvtex $):
%
%p4.1 #&#
\begin{proposition}%
{(Relationships between contraction preorder, expansion preorder and weak
bisimilarity)}
%
\begin{enumerate}
%
\item (Expansion preorder implies contraction preorder)
%
%a1 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}. \HOLBoundVar{P} \HOLSymConst{\HOLTokenExpands{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{Q}\hfill[expands\_IMP\_contracts]
\end{alltt}
%
\item (Contraction preorder implies weak bisimilarity)
%
%a2 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{Q}. \HOLBoundVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{Q}\hfill[contracts\_IMP\_WEAK\_EQUIV]
\end{alltt}
%
\end{enumerate}
%
\end{proposition}

The proofs of properties for contraction are generally harder than those
for expansion. This is mostly due to the fact that, although the contraction
preorder ($\mcontrBIS $) is contained in bisimilarity ($\wbvtex $), a contraction
need not be a bisimulation. In another words, the following proposition
does not hold:
%
%a4.5 #&#
\begin{alltt}
   \HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Con}. \HOLConst{CONTRACTION} \HOLBoundVar{Con} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WEAK\_BISIM} \HOLBoundVar{Con}}
\end{alltt}
%
However it does hold that, if $\Rvtex $ is a contraction, then
$\Rvtex \;\cup \wbvtex $ is a bisimulation. For instance, we can prove
\texttt{contracts\_IMP\_WEAK\_EQUIV} by constructing a bisimulation
\HOLinline{\HOLFreeVar{Wbsm}} containing two processes $P$ and $Q$, given
that they are in $Con$ (a contraction):
%
%a4.5 #&#
\begin{alltt}
        \HOLinline{\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{Wbsm}. \HOLBoundVar{Wbsm} \HOLFreeVar{P} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WEAK\_BISIM} \HOLBoundVar{Wbsm}}
   ------------------------------------
    0.  \HOLinline{\HOLFreeVar{Con} \HOLFreeVar{P} \HOLFreeVar{Q}}
    1.  \HOLinline{\HOLConst{CONTRACTION} \HOLFreeVar{Con}}
\end{alltt}
%
To complete the proof, one cannot choose $Con$ for $Wbsm$ and show that
$Con$ itself is a bisimulation, but rather that
$Con\;\cup \!\wbvtex $ is a bisimulation. In contrast, in the corresponding
lemma for expansion one can just take $Con$. Finally, the rooted contraction
($\rcontr $) is formalised as follows:
%
%a4.5 #&#
\begin{alltt}
   \HOLFreeVar{E} \HOLSymConst{\HOLTokenObsContracts} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenDefEquality{}
     \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u}.
         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenContracts{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
         \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLFreeVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenWeakEQ} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\hfill{[OBS\_contracts]}
\end{alltt}

%s4.6 #&#
\subsection{The formalisation of ``bisimulation up to''}
 \label{sec4.6}

``Bisimulation up to'' is a family of powerful proof techniques for reducing
the sizes of relations needed for defining bisimulations~\cite{PousS19}.
By definition, two processes are bisimilar iff there exists a bisimulation
relation containing them. However, in practice this definition is sometimes
hard to apply. Instead, to reduce the sizes of the exhibited relations,
one prefers to define relations which are bisimulations only when closed
up under some specific and privileged relation, so to relieve the needed
proof work. These techniques are usually called
\emph{``up-to'' techniques}.

Recall that we often write $P \;\Rvtex \; Q$ to denote
$(P, Q) \in \Rvtex $ for any binary relation $\Rvtex $. Moreover,
$\sim \mathcal{S} \sim $ is the composition of three binary relations:
$\sim $, $\Svtex $ and $\sim $. Hence $P \sim \Svtex \sim Q$ means that
there exist $P'$ and $Q'$ such that $P \sim P'$, $P' \;\Svtex \; Q'$ and
$Q' \sim Q$.
%
%d4.2 #&#
\begin{definition}%
 \label{def:bisimUptoSim}
$\Svtex $ is a ``bisimulation up to $\sim $'' if $P\ \Svtex \ Q$ implies,
for all $\mu $,
%
\begin{enumerate}
%
\item Whenever $P \overset{\mu}{\rightarrow} P'$ then, for some $Q'$,
$Q \overset{\mu}{\rightarrow} Q'$ and $P' \sim \Svtex \sim Q'$,
%
\item Whenever $Q \overset{\mu}{\rightarrow} Q'$ then, for some $P'$,
$P \overset{\mu}{\rightarrow} P'$ and $P' \sim \Svtex \sim Q'$.
%
\end{enumerate}
%
\end{definition}

%t4.3 #&#
\begin{theorem}
If $\mathcal{S}$ is a ``bisimulation up to $\sim $'', then
$\mathcal{S} \subseteq \;\sim $:
%
%a4.3 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{STRONG\_BISIM\_UPTO} \HOLFreeVar{Bsm} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Bsm} \HOLFreeVar{P} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{Q}\hfill{[STRONG\_EQUIV\_BY\_BISIM\_UPTO]}
\end{alltt}
%
\end{theorem}
%
Hence, to prove $P \sim Q$, one only needs to find a bisimulation up to
$\sim $ that contains $(P, Q)$. For weak bisimilarity, the naive weak bisimulation
up to weak bisimilarity is unsound: if one simply replaces all occurrences
of $\sim $ in \reftext{Definition~\ref{def:bisimUptoSim}} with $\wbvtex $, the resulting
``weak bisimulation up to'' relation need not be contained in weak bisimilarity
($\wbvtex $)~\cite{PoSa2019}. There are a few ways to fix this problem,
and one is the following:
%
%d4.4 #&#
\begin{definition}%
 \label{def:singleweak}
$\Svtex $ is a ``bisimulation up to $\approx $'' if $P\ \Svtex \ Q$ implies,
for all $\mu $,
%
\begin{enumerate}
%
\item Whenever $P \arr{\mu} P'$ then, for some $Q'$,
$Q \Arcap{\mu} Q'$ and $P' \sim \Svtex \approx Q'$,
%
\item Whenever $Q \arr{\mu} Q'$ then, for some $P'$,
$P \Arcap{\mu} P'$ and $P' \approx \Svtex \sim Q'$.
%
\end{enumerate}
%
Formally:
%
%a4.4 #&#
\begin{alltt}
   \HOLConst{WEAK\_BISIM\_UPTO} \HOLFreeVar{Wbsm} \HOLTokenDefEquality{}
     \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
         \HOLFreeVar{Wbsm} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l}.
              \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}.
                   \HOLBoundVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}}
                   \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
                       \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}}
                       \ensuremath{(}\HOLConst{WEAK\_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{STRONG\_EQUIV}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
              \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
                  \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
                  \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}.
                      \HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}}
                      \ensuremath{(}\HOLConst{STRONG\_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{WEAK\_EQUIV}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}.
              \HOLBoundVar{E} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}}
              \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenEPS} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{WEAK\_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{STRONG\_EQUIV}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
         \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
             \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
             \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLSymConst{\HOLTokenEPS} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{STRONG\_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{WEAK\_EQUIV}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
\end{alltt}
%
\end{definition}
%
Note that the HOL term corresponding to $\sim \Rvtex \wbvtex $ is ``\HOLinline{\HOLConst{WEAK\_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLFreeVar{R} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{STRONG\_EQUIV}}''
where the order of $\sim $ and $\approx $ seems reverted. This is because,
in HOL notation, the rightmost relation (\HOLinline{\HOLConst{STRONG\_EQUIV}}
or $\sim $) in the relational composition is applied first.

%t4.5 #&#
\begin{theorem}
If $\mathcal{S}$ is a bisimulation up to $\approx $, then
$\mathcal{S} \subseteq \;\approx $:
%
%a4.5 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{WEAK\_BISIM\_UPTO} \HOLFreeVar{Bsm} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Bsm} \HOLFreeVar{P} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{Q}\hfill{[WEAK\_EQUIV\_BY\_BISIM\_UPTO]}
\end{alltt}
%
\end{theorem}

The above version of ``bisimulation up to $\wbvtex $'' is not powerful
enough for Milner's ``unique solution of equations'' theorem for
$\wbvtex $ (\reftext{Theorem~\ref{t:Mil89}}, see~\cite{sangiorgi1992problem} for
more details). The following version, with weak arrows, is used in the
proof of \reftext{Theorem~\ref{t:Mil89}}:
%
%d4.6 #&#
\begin{definition}%
 \label{def:doubleweak}
$\mathcal{S}$ is a ``bisimulation up to $\approx $ with weak arrows'' if
$P \; \mathcal{S} \; Q$ implies, for all $\mu $,
%
\begin{enumerate}
%
\item Whenever $P \Arr{\mu} P'$ then, for some $Q'$,
$Q \Arcap{\mu} Q'$ and $P' \wbvtex \Svtex \wbvtex Q'$,
%
\item Whenever $Q \Arr{\mu} Q'$ then, for some $P'$,
$P \Arcap{\mu} P'$ and $P' \wbvtex \Svtex \wbvtex Q'$.
%
\end{enumerate}
%
Formally:
%
%a4.6 #&#
\begin{alltt}
   \HOLConst{WEAK\_BISIM\_UPTO\_ALT} \HOLFreeVar{Wbsm} \HOLTokenDefEquality{}
     \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
         \HOLFreeVar{Wbsm} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l}.
              \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}.
                   \HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}}
                   \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
                       \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}}
                       \ensuremath{(}\HOLConst{WEAK\_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{WEAK\_EQUIV}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
              \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
                  \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
                  \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}.
                      \HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}}
                      \ensuremath{(}\HOLConst{WEAK\_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{WEAK\_EQUIV}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}.
              \HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}}
              \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenEPS} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{WEAK\_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{WEAK\_EQUIV}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
         \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
             \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenWeakTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
             \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLSymConst{\HOLTokenEPS} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{WEAK\_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{WEAK\_EQUIV}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
\end{alltt}
%
\end{definition}

%t4.7 #&#
\begin{theorem}
If $\mathcal{S}$ is a bisimulation up to $\approx $ with weak arrows, then
$\mathcal{S} \subseteq \;\approx $:
%
%a4.7 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{WEAK\_BISIM\_UPTO\_ALT} \HOLFreeVar{Bsm} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Bsm} \HOLFreeVar{P} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{Q}\hfill{[WEAK\_EQUIV\_BY\_BISIM\_UPTO\_ALT]}
\end{alltt}
%
\end{theorem}

%s4.7 #&#
\subsection{Context, guardedness and (pre)congruence}
%%LEAP%%%\label{sec4.7}
 \label{sscontext}

CCS contexts are needed in defining (pre)congruence. To prevent doing variable
\xch{substitutions}{substititions}, one can take \univariate $\lambda $-expressions (of type
``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
as \emph{multi-hole CCS contexts}. This choice has a significant advantage
over \emph{one-hole contexts}, as each hole corresponds to one occurrence
of the (same) variable in \univariate CCS expressions or equations. Thus
\emph{contexts} can be used both in (pre)congruence definitions and in formulating
the unique solution of equations theorems in the \univariate case. The
precise definition of CCS contexts is inductive:
%
%a4.7 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{CONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{CONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)}\hfill{[CONTEXT\_rules]}
\end{alltt}
%
In the above definition (actually generated by \texttt{HOL\_reln}), for
any process $p$, (\HOLinline{\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{p}})
is a valid context with no hole (similarly to an equation without variables).

Below is the formalisation of \reftext{Definition~\ref{def:guardness}}. A context is
\emph{weakly guarded} (\HOLinline{\HOLConst{WG}}) if each hole is underneath
a prefix:
%
%a4.7 #&#
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{WG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{WG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}. \HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}. \HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)}\hfill{[WG\_rules]}
\end{alltt}
%
Notice the differences between a weakly guarded context and an ordinary
context: $(\lambda t. t)$ is not weakly guarded as the variable $t$ is
directly exposed without any prefixed action, while
$(\lambda t. a.e[t])$ is weakly guarded as long as $e[\cdot ]$ is a context,
which is not necessary weakly guarded.

A context is \emph{(strongly)} guarded (\HOLinline{\HOLConst{SG}}) if each
hole is underneath a \emph{visible} prefix:
%
%a4.7 #&#
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{label} \HOLBoundVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}. \HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{SG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{SG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}. \HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}. \HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)}\hfill{[SG\_rules]}
\end{alltt}

A context is \emph{sequential} (\HOLinline{\HOLConst{SEQ}}) if each of its
\emph{subcontexts} with a hole, apart from the hole itself, is in forms
of prefixes or sums:
%
%a4.7 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}. \HOLConst{SEQ} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{SEQ} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\hfill{[SEQ\_rules]}
\end{alltt}

In the same manner, we can also define variants of contexts (\HOLinline{\HOLConst{GCONTEXT}})
and weakly guarded contexts (\HOLinline{\HOLConst{WGS}}) in which only
guarded sums are allowed:
%
%a4.7 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}. \HOLConst{GCONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}.
        \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}. \HOLConst{GCONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}. \HOLConst{GCONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)}\hfill{[GCONTEXT\_rules]}
\end{alltt}
%
%a4.7 #&#
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{WGS} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}. \HOLConst{GCONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{WGS} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}. \HOLConst{WGS} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}. \HOLConst{WGS} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WGS} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)}\hfill{[WGS\_rules]}
\end{alltt}

Several lemmas about the above concepts (\HOLinline{\HOLConst{CONTEXT}},
\HOLinline{\HOLConst{WG}}, \HOLinline{\HOLConst{SEQ}}, etc.) are needed
for capturing properties about the relationships among these kinds of contexts
and about their compositions. These proofs are usually tedious and long,
due to multiple levels of inductions on the structure of the contexts.

A (pre)congruence is a relation on CCS processes defined on top of
\HOLinline{\HOLConst{CONTEXT}}. The only difference between congruence
and precongruence is that the former is an equivalence, while the latter
can just be a preorder:
%
%a4.7 #&#
\begin{alltt}
   \HOLConst{congruence} \HOLFreeVar{R} \HOLTokenDefEquality{}
     \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}. \HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \ensuremath{(}\HOLBoundVar{ctx} \HOLBoundVar{x}\ensuremath{)} \ensuremath{(}\HOLBoundVar{ctx} \HOLBoundVar{y}\ensuremath{)}\hfill{[congruence]}
\end{alltt}

\begin{alltt}
   \HOLConst{precongruence} \HOLFreeVar{R} \HOLTokenDefEquality{}
     \HOLConst{PreOrder} \HOLFreeVar{R} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y} \HOLBoundVar{ctx}. \HOLConst{CONTEXT} \HOLBoundVar{ctx} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \ensuremath{(}\HOLBoundVar{ctx} \HOLBoundVar{x}\ensuremath{)} \ensuremath{(}\HOLBoundVar{ctx} \HOLBoundVar{y}\ensuremath{)}\hfill{[precongruence]}
\end{alltt}

Both strong bisimilarity ($\sim $) and rooted bisimilarity ($\approx ^{c}$)
are congruence relations:
%
%a4.7 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{congruence} \HOLConst{STRONG\_EQUIV}\hfill{[STRONG\_EQUIV\_congruence]}
\HOLTokenTurnstile{} \HOLConst{congruence} \HOLConst{OBS\_CONGR}\hfill{[OBS\_CONGR\_congruence]}
\end{alltt}

Although weak bisimilarity ($\approx $) is \emph{not} a congruence with
respect to~\HOLinline{\HOLConst{CONTEXT}}, it is substitutive with respect
to~\HOLinline{\HOLConst{GCONTEXT}} as $\approx $ is preserved by guarded
sums. Similarily, contraction ($\mcontrBIS $) is substitutive with respect
to \HOLinline{\HOLConst{GCONTEXT}}. Rooted contraction ($\rcontr $, or
\HOLinline{\HOLConst{OBS\_contracts}} in HOL), on the other hand, is indeed
a precongruence:
%
%a4.7 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{precongruence} \HOLConst{OBS\_contracts}\hfill{[OBS\_contracts\_precongruence]}
\end{alltt}

%s4.8 #&#
\subsection{Coarsest (pre)congruence contained in $\approx $ ($\succeq _{\mathrm{bis}}$)}
%%LEAP%%%\label{sec4.8}
 \label{s:coarsest}

In this section we give a proof of the second part of \reftext{Theorem~\ref{t:rapproxCongruence}},
i.e. $\rapprox $ is the coarsest congruence contained in $\wbvtex $. The
general form of this theorem is the following one~\cite{van2005characterisation,Gorrieri:2015jt,Mil89}:
%
%p4.8 #&#
\begin{proposition}
 \label{prop:coarsest}
Rooted bisimilarity ($\rapprox $) is the coarsest congruence contained
in weak bisimilarity ($\wbvtex $):
%
%e1 #&#
\begin{equation}
 \label{eq:coarsest}
\forall p\ \ q.\ p\ \rapprox \ \! q\ \Longleftrightarrow \ ( \forall r.
\ p\ +\
r\ \approx \ q\ +\ r ).
\end{equation}
%
\end{proposition}
%
From left to right \reftext{(\ref{eq:coarsest})} trivially holds, due to the substitutivity
of $\rapprox $ for summation and the fact that $\rapprox $ implies
$\wbvtex $: (Thus we are only interested in \reftext{(\ref{eq:coarsest})} from right
to left.)
%
%a4.8 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}. \HOLBoundVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{q} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\hfill{[COARSEST\_CONGR\_LR]}
\end{alltt}

The formalisation of this theorem presents some delicate aspects. For instance,
within our CCS syntax which supports only binary sums, one way to prove
\reftext{Proposition~\ref{prop:coarsest}} is to add an hypothesis that the involved
processes do not use all available labels. Indeed, this is the standard
argument by Milner~\citep[p.~153]{Mil89}. Formalising this result, however,
requires a detailed treatment of free and bound names (of labels) of CCS
processes, with the restriction operator acting as a binder. In our actual
formalisation, instead, we assume the weaker hypothesis that all
\emph{immediate weak} derivatives of $p$ and $q$ do not use all available
labels. We call this the \emph{free action} property:
%
%a4.8 #&#
\begin{alltt}
   \HOLConst{free\_action} \HOLFreeVar{p} \HOLTokenDefEquality{} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{a}. \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{p}\sp{\prime}}. \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{a}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{p}\sp{\prime}}\ensuremath{)}\hfill{[free\_action\_def]}
\end{alltt}

Now we show how \reftext{(\ref{eq:coarsest})} is connected with the statement of
\reftext{Proposition~\ref{prop:coarsest}}, and prove it under the free action assumptions.
The coarsest congruence contained in (weak) bisimilarity, namely
\emph{bisimilarity congruence} (\texttt{WEAK\_CONGR} in HOL), is the
\emph{composition closure} (\texttt{CC}) of (weak) bisimilarity:
%
%a4.8 #&#
\begin{alltt}
   \HOLConst{CC} \HOLFreeVar{R} \HOLTokenDefEquality{} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}. \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}. \HOLConst{CONTEXT} \HOLBoundVar{c} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \ensuremath{(}\HOLBoundVar{c} \HOLBoundVar{g}\ensuremath{)} \ensuremath{(}\HOLBoundVar{c} \HOLBoundVar{h}\ensuremath{)}\ensuremath{)}\hfill{[CC\_def]}
   \HOLConst{WEAK\_CONGR} \HOLTokenDefEquality{} \HOLConst{CC} \HOLConst{WEAK\_EQUIV}\hfill{[WEAK\_CONGR]}
\end{alltt}
%
We do not need to put $R\ g\ h$ into the antecedents of
\texttt{CC\_def}, as this is anyhow obtained from the trivial context
$(\lambda x.\,x)$. The next result shows that, for any binary relation
$R$ on CCS processes, the composition closure of $R$ is always at least
as fine as $R$ (here $\subseteq _r$ stands for
\emph{relational subset}):
%
%a4.8 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}. \HOLConst{CC} \HOLBoundVar{R} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R}\hfill{[CC\_is\_finer]}
\end{alltt}
%
Furthermore, we prove that any (pre)congruence contained in $R$, that itself
needs not to be a (pre)congruence, is contained in the composition closure
of $R$ (hence the composition closure is indeed the coarsest one):
%
%a4.8 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R} \ensuremath{\HOLBoundVar{R}\sp{\prime}}. \HOLConst{congruence} \ensuremath{\HOLBoundVar{R}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{R}\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \ensuremath{\HOLBoundVar{R}\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLConst{CC} \HOLBoundVar{R}\hfill{[CC\_is\_coarsest]}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R} \ensuremath{\HOLBoundVar{R}\sp{\prime}}. \HOLConst{precongruence} \ensuremath{\HOLBoundVar{R}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{R}\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \ensuremath{\HOLBoundVar{R}\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLConst{CC} \HOLBoundVar{R}\hfill{[PCC\_is\_coarsest]}
\end{alltt}

Given the central role of summation, we also consider the relation closure
of bisimilarity with respect to summation, called
\emph{equivalence compatible with summation} (\texttt{SUM\_EQUIV}):
%
%a4.8 #&#
\begin{alltt}
   \HOLConst{SUM\_EQUIV} \HOLTokenDefEquality{} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}. \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)}\hfill{[SUM\_EQUIV]}
\end{alltt}

Rooted bisimilarity $\rapprox $ (as a congruence contained in
$\wbvtex $) is now contained in \texttt{WEAK\_CONGR}, which in turn is trivially
contained in \texttt{SUM\_EQUIV}, as shown in \reftext{Fig.~\ref{fig:relationship}}.
Thus, to prove \reftext{Proposition~\ref{prop:coarsest}}, the crux is to prove that
\texttt{SUM\_EQUIV} is contained in $\rapprox $, making all three relations
($\rapprox $, \texttt{WEAK\_CONGR} and \texttt{SUM\_EQUIV}) coincide:
%
%f6 #&#
\begin{figure}%[ht]
%
%d4.8 #&#
\begin{sgmlfig}\normalsize
%
$$\xymatrix{
{\textrm{Weak bisimilarity } (\approx )} & {\textrm{Equiv.
compatible with summation (\texttt{SUM\_EQUIV})}}
\ar@/^3ex/[ldd]^{\supseteq \; ?}\\
{\textrm{Bisimilarity congruence (\texttt{WEAK\_CONGR})}}
\ar[u]^{\subseteq} \ar[ru]^{\subseteq} \\
{\textrm{Rooted bisimilarity } (\rapprox )} \ar[u]^{\subseteq}
}$$
\end{sgmlfig}
%
\caption{Relationships between several equivalences and $\wbvtex $.}
 \label{fig:relationship}
\end{figure}\vspace{-3pt}
%e2 #&#
\begin{equation}
 \label{equa:pq}
\forall p\ \ q.\ ( \forall r.\ p\ +\ r \;\approx \; q\ +\ r ) \
\Longrightarrow \ p\ \rapprox \ \! q.
\end{equation}

Here is the formalisation of \reftext{(\ref{equa:pq})} under free action hypothesis:\vspace{-3pt}
%
%t4.9 #&#
\begin{theorem}[\texttt{COARSEST\_CONGR\_RL}]
 \label{thm:coarsestR}
Under the free action hypothesis, $\rapprox $ is coarsest congruence contained
in $\wbvtex $.\vspace{-3pt}
%
%a4.9 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}. \HOLConst{free\_action} \HOLBoundVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free\_action} \HOLBoundVar{q} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{q}
\end{alltt}
%
\end{theorem}

With an almost identical proof, rooted contraction ($\rcontr $) is also
the coarsest precongruence contained in the bisimilarity contraction ($
\mcontrBIS $):
%
%t4.10 #&#
\begin{theorem}[\texttt{COARSEST\_PRECONGR\_RL}]
 \label{thm:coarsestPre}
Under the free action hypothesis, $\mcontrBIS $ is the coarsest precongruence
contained in $\contr $.
%
%a4.10 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}. \HOLConst{free\_action} \HOLBoundVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{free\_action} \HOLBoundVar{q} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{p} \HOLSymConst{\HOLTokenObsContracts} \HOLBoundVar{q}
\end{alltt}
%
\end{theorem}

The formal proofs of \reftext{\xch{Theorems}{Theorem}~\ref{thm:coarsestR} and \ref{thm:coarsestPre}} precisely follow Milner~\citep[p.~153--154]{Mil89}.
Although Milner requires a stronger hypothesis:
$\mathrm{fn}(p) \cup \mathrm{fn}(q) \neq \mathscr{L}$ (here
$\mathrm{fn}$ stands for \emph{free names}), the actual proof essentially
requires only the above free action property. Indeed, in the proof one
only looks at the immediate weak derivatives of $p$ and $q$, and only requires
that there is an input or output label that never occurs as a label of
the involved transitions.

%s4.9 #&#
\subsection{Arbitrarily many non-bisimilar processes}
%%LEAP%%%\label{sec4.9}
 \label{ss:arbitrarily}

As the type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}''
is parameterized with two type variables, if the type of all label names
$\beta $ has a small cardinality (a singleton in the extreme case), it
is possible that the processes of \reftext{Proposition~\ref{prop:coarsest}} use all
available labels, and thus the free action hypothesis does not hold. In
this case, it is still possible to prove \reftext{Proposition~\ref{prop:coarsest}};
however, due to some limitations of HOL itself we have to assume that the
processes are \emph{finite-state}, i.e. the set of all their derivatives
is finite. The original proof, due to van Glabbeek~\cite{van2005characterisation},
does not require finite-state CCS. Here is the main theorem:
%
%t4.11 #&#
\begin{theorem}[\texttt{COARSEST\_CONGR\_FINITE}]
 \label{thm:coarsestfiniteState}
For finite-state CCS, $\rapprox $ is the coarsest congruence contained
in $\wbvtex $:
%
%a4.11 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}. \HOLConst{finite\_state} \HOLBoundVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite\_state} \HOLBoundVar{q} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLBoundVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)}
\end{alltt}
%
\end{theorem}

The precise definition of \texttt{finite\_state} used in above theorem will
be given later. We start with a core lemma (\texttt{PROP3\_COMMON}) saying
that, for any two processes $p$ and $q$, if there exists a
\emph{stable} (i.e.~without $\tau $ transitions) process which is not bisimilar
with any weak derivative of $p$ and $q$, then
\HOLinline{\HOLConst{SUM\_EQUIV}} indeed implies rooted bisimilarity ($
\rapprox $)~\cite{van2005characterisation,Tian:2017wrba}:
%
%a4.9 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}.
       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
            \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{p}\sp{\prime}} \HOLBoundVar{u}. \HOLBoundVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{p}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\ensuremath{\HOLBoundVar{p}\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
            \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{q}\sp{\prime}} \HOLBoundVar{u}. \HOLBoundVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{q}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\ensuremath{\HOLBoundVar{q}\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \HOLBoundVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLBoundVar{q}\hfill{[PROP3\_COMMON]}
\end{alltt}
%
%a4.9 #&#
\begin{alltt}
   \HOLConst{STABLE} \HOLFreeVar{p} \HOLTokenDefEquality{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \ensuremath{\HOLBoundVar{p}\sp{\prime}}. \HOLFreeVar{p} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{p}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{u} \HOLSymConst{\HOLTokenNotEqual{}} \HOLSymConst{\ensuremath{\tau}}\hfill{[STABLE]}
\end{alltt}

To prove \reftext{Theorem~\ref{thm:coarsestfiniteState}}, it only remains to construct
such stable process $k$ for any two finite-state processes $p$ and
$q$. For arbitrary CCS processes, this construction relies on arbitrary
infinite sums of processes (not within our CCS syntax) and transfinite
induction to obtain an arbitrary large sequence of processes that are all
pairwise non-bisimilar, which was firstly introduced by Jan Willem Klop~(see
\cite{van2005characterisation} for some historical notes). We have only
partially formalised van Glabbeek's proof, mostly because our CCS syntax
does not allow infinite summation (and it is not easy to extend it with
this support). Another more important reason is that the typed logic implemented
in various HOL systems (including Isabelle/HOL) is not strong enough to
define a type for all possible ordinals~\cite{norrish2013ordinals} which
is required in van Glabbeek's proof. As the consequence, the formalisation
(\reftext{Theorem~\ref{thm:coarsestfiniteState}}) can only apply to finite-state
CCS.

The above core lemma (\texttt{PROP3\_COMMON}) requires the existence of
a special CCS process, which is not weakly bisimilar to any weak derivative
of the two root processes. There could be infinitely many such subprocesses,
even on finitely branching processes. We can, however, consider the equivalence
classes of CCS processes modulo weak bisimilarity. If there are infinitely
many such classes, then it will be possible to choose one that is distinct
from all the (finitely many) states in the transition graphs of the two
given processes. This can be done by following Klop's \xch{construction}{contruction}. We call
the processes in this construction the ``Klop processes'':
%
%d4.12 #&#
\begin{definition}[Klop processes]
For each ordinal $\lambda $, and an arbitrary chosen action
$a \neq \tau $, define a CCS process $k_\lambda $ as follows:
%
\begin{itemize}
%
\item $k_0 = 0$,
%
\item $k_{\lambda +1} = k_\lambda + a.k_\lambda $ and
%
\item for $\lambda $ a limit ordinal,
$k_\lambda = \sum _{\mu < \lambda} k_\mu $ (meaning that
$k_\lambda $ is constructed from all graphs $k_\mu $ for
$\mu < \lambda $ by identifying their root).
%
\end{itemize}
%
\end{definition}
%
When processes are finite-state, that is, the number of states in which
a process may evolve by performing transitions is finite, we can use the
following subset of Klop processes, defined as a recursive function (on
natural numbers) in HOL4:
%
%d4.13 #&#
\begin{definition}%
{(Klop processes as recursive function on natural numbers)}
%
%a4.13 #&#
\begin{alltt}
   \HOLConst{KLOP} \HOLFreeVar{a} \HOLNumLit{0} \HOLTokenDefEquality{} \HOLConst{\ensuremath{\mathbf{0}}}
   \HOLConst{KLOP} \HOLFreeVar{a} \ensuremath{(}\HOLConst{SUC} \HOLFreeVar{n}\ensuremath{)} \HOLTokenDefEquality{} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLSymConst{\ensuremath{+}} \HOLConst{label} \HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\hfill{[KLOP\_def]}
\end{alltt}
%
\end{definition}

Following the inductive structure of the above definition, and using the
SOS rules ($\mathrm{Sum}_1$) and ($\mathrm{Sum}_2$), we can prove the following
properties of Klop functions:
%
%p4.14 #&#
\begin{proposition}%
{(Properties of Klop functions and processes)}
%
\begin{enumerate}
%
\item (All Klop processes are stable)
%
%a1 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{STABLE} \ensuremath{(}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\ensuremath{)}\hfill[KLOP\_PROP0]
\end{alltt}

%
\item (Any transition from a Klop process leads to a smaller Klop process,
and conversely)
%
%a2 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{a}\HOLTokenTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{m}. \HOLBoundVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{KLOP} \HOLFreeVar{a} \HOLBoundVar{m}\hfill{[KLOP\_PROP1]}
\end{alltt}
%
\item (The weak version of the previous property)
%
%a3 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n} \HOLTokenWeakTransBegin\HOLConst{label} \HOLFreeVar{a}\HOLTokenWeakTransEnd \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{m}. \HOLBoundVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{KLOP} \HOLFreeVar{a} \HOLBoundVar{m}\hfill{[KLOP\_PROP1']}
\end{alltt}
%
\item (All Klop processes are distinct according to strong bisimilarity)
%
%a4 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLFreeVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{m} \HOLSymConst{\HOLTokenStrongEQ} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\ensuremath{)}\hfill{[KLOP\_PROP2]}
\end{alltt}
%
\item (All Klop processes are distinct according to weak bisimilarity)
%
%a5 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLFreeVar{m} \HOLSymConst{\HOLTokenLt{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{m} \HOLSymConst{\HOLTokenWeakEQ} \HOLConst{KLOP} \HOLFreeVar{a} \HOLFreeVar{n}\ensuremath{)}\hfill{[KLOP\_PROP2']}
\end{alltt}
%
\item (Klop functions are one-one)
%
%a6 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ONE\_ONE} \ensuremath{(}\HOLConst{KLOP} \HOLFreeVar{a}\ensuremath{)}\hfill{[KLOP\_ONE\_ONE]}
\end{alltt}
%
\end{enumerate}
%
\end{proposition}

For any \HOLinline{\HOLConst{label}\;\HOLFreeVar{a}}, having the function
``\HOLinline{\HOLConst{KLOP}\;\HOLFreeVar{a}}'' (of type ``\HOLinline{\HOLTyOp{num} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
defined on the natural numbers, we obtain a countable set of Klop processes
built from the same label. As the number of all Klop processes in this
set is (countably) infinite, and they are all pairwise non-\xch{bisimilar}{bisimiar}, we
can always choose a number, corresponding to a Klop process, that is non-bisimilar
with any derivative of two given (finite-state) processes $p$ and
$q$, even when $a$ is the only element of type $\beta $, i.e. the only
label name in $\mathscr{L}$. This property is captured by appealing to
the following set-\xch{theoretic}{theoreric} \xch{lemma}{lamma} (see~\cite{Tian:2017wrba} for its proof):
%
%l4.15 #&#
\begin{lemma}
Given an equivalence relation $R$ defined on a type, and two sets
$A, B$ of elements in this type, if $A$ is finite, $B$ is infinite, and
all elements in $B$ belong to distinct equivalence classes, then there
exists an element $k$ in $B$ which is not equivalent to any element in
$A$:
%
%a4.15 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{equivalence} \HOLFreeVar{R} \HOLSymConst{\HOLTokenImp{}}
   \HOLConst{FINITE} \HOLFreeVar{A} \HOLSymConst{\HOLTokenConj{}} \HOLConst{INFINITE} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{y}. \HOLBoundVar{x} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{x} \HOLSymConst{\HOLTokenNotEqual{}} \HOLBoundVar{y} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{y}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}. \HOLBoundVar{k} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{B} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n}. \HOLBoundVar{n} \HOLSymConst{\HOLTokenIn{}} \HOLFreeVar{A} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\HOLFreeVar{R} \HOLBoundVar{n} \HOLBoundVar{k}\hfill[INFINITE\_EXISTS\_LEMMA]
\end{alltt}
%
\end{lemma}

To reason about finite-state CCS, we also need to define the concept of
``finite-state CCS'' as a predicate on CCS processes:
%
%d4.16 #&#
\begin{definition}[finite-state CCS]
\mbox{}
%
\begin{enumerate}
%
\item A binary relation \texttt{Reach} is the RTC (reflexive and transitive
closure) of a relation indicating the existence of a transition between
two processes:
%
%a1 #&#
\begin{alltt}
\HOLConst{Reach} \HOLTokenDefEquality{} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}. \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{u}. \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)}\HOLSymConst{\HOLTokenSupStar{}}\hfill[Reach\_def]
\end{alltt}
%
\item The set of all derivatives (\texttt{NODES}) of a process is the set
of all processes reachable from it:
%
%a2 #&#
\begin{alltt}
\HOLConst{NODES} \HOLFreeVar{p} \HOLTokenDefEquality{} \HOLTokenLeftbrace{}\HOLBoundVar{q} \HOLTokenBar{} \HOLConst{Reach} \HOLFreeVar{p} \HOLBoundVar{q}\HOLTokenRightbrace{}\hfill[NODES\_def]
\end{alltt}
%
\item A process is \texttt{finite-state} if the set of all derivatives
is finite:
%
%a3 #&#
\begin{alltt}
\HOLConst{finite\_state} \HOLFreeVar{p} \HOLTokenDefEquality{} \HOLConst{FINITE} \ensuremath{(}\HOLConst{NODES} \HOLFreeVar{p}\ensuremath{)}\hfill[finite\_state\_def]
\end{alltt}
%
\end{enumerate}
%
\end{definition}
%
We rely on various properties of the above definitions, such as the following
one:
%
%p4.17 #&#
\begin{proposition}
If $p$ has a weak transition to $q$, then $q$ is among the derivatives
of $p$:
%
%a4.17 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{q} \HOLSymConst{\HOLTokenIn{}} \HOLConst{NODES} \HOLFreeVar{p}\hfill[WEAK\_TRANS\_IN\_NODES]
\end{alltt}
%
\end{proposition}

Using all the above results, now we can prove the following finite-state
version of ``Klop lemma'':
%
%l4.18 #&#
\begin{lemma}[Klop lemma for finite-state CCS]
 \label{lem:klop-lemma-finite}
For any two finite-state CCS $p$ and $q$, there is another process
$k$, which is not weakly bisimilar with any weak derivative of $p$ and
$q$ (i.e., any process reachable from $p$ or $q$ by means of transitions):
%
%a4.18 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p} \HOLBoundVar{q}.
       \HOLConst{finite\_state} \HOLBoundVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite\_state} \HOLBoundVar{q} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
           \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{p}\sp{\prime}} \HOLBoundVar{u}. \HOLBoundVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{p}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\ensuremath{\HOLBoundVar{p}\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
           \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{q}\sp{\prime}} \HOLBoundVar{u}. \HOLBoundVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{q}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\ensuremath{\HOLBoundVar{q}\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\hfill{[KLOP\_LEMMA\_FINITE]}
\end{alltt}
%
\end{lemma}
%
Combining the above lemma with the core lemma (\texttt{PROP3\_COMMON}) and
\reftext{Theorem~\ref{thm:coarsestR}} (\texttt{COARSEST\_CONGR\_RL}), yields the proof
of \reftext{Theorem~\ref{thm:coarsestfiniteState}} (\texttt{COARSEST\_CONGR\_FINITE}).
The same proof idea can also be used with contraction and rooted \xch{contraction}{contration}.

%s4.10 #&#
\subsection{Unique solution of equations}
%%LEAP%%%\label{sec4.10}
 \label{ss:part2}

In this section we describe the formalisation of Milner's ``unique solution
of equations'' theorems, limited to \univariate equations. (The
\multivariate extension is described in Section~\ref{sec:multivariate}.)

%s4.10.1 #&#
\subsubsection{The version for strong bisimilarity}
 \label{sec4.10.1}

Using ``bisimulation up to $\sim $'' technique, we obtain the following
key lemma, which states that, if $X$ is weakly guarded in $E$, then the
``first move'' of $E$ is independent of the agent substituted for
$X$:
%
%l4.19 #&#
\begin{lemma}[\texttt{STRONG\_UNIQUE\_SOLUTION\_LEMMA}, Lemma 3.13
of~\cite{Mil89}, \univariate version]
 \label{lem:313}
If the variable $X$ is weakly guarded in $E$, and
$E\{P/X\}\overset{\alpha}{\rightarrow} P'$, then $P'$ takes the form
$E'\{P/X\}$ (for some expression $E'$), and moreover, for any $Q$,
$E\{Q/X\}\overset{\alpha}{\rightarrow} E'\{Q/X\}$:
%
%a4.19 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \ensuremath{\HOLBoundVar{P}\sp{\prime}}. \HOLFreeVar{E} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sp{\prime}}. \HOLConst{CONTEXT} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}. \HOLFreeVar{E} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{Q}
\end{alltt}
%
\end{lemma}

Then, by structural induction on weakly guarded contexts (\texttt{WG}),
we prove \reftext{Theorem~\ref{t:Mil89s1}} in the \univariate case. The formal proof
basically follows the outline of its informal version~\citep[p.~102--103]{Mil89},
which is tedious due to large amounts of case analyses on each CCS operator.
%
%t4.20 #&#
\begin{theorem}[\texttt{STRONG\_UNIQUE\_SOLUTION}, \univariate version
of \reftext{Theorem~\ref{t:Mil89s1}}]
 \label{thm:Mil89s1f}
Suppose the expression $E$ contains at most the variable $X$, and let
$X$ be weakly guarded in $E$.
%
%e3 #&#
\begin{equation}
\text{If } P \sim E\{P/X\} \text{ and } Q \sim E\{Q/X\} \text{ then } P
\sim Q.
\end{equation}
%
%a4.20 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{Q}
\end{alltt}
%
\end{theorem}

%s4.10.2 #&#
\subsubsection{The version for rooted bisimilarity}
 \label{sec4.10.2}

For the proof of \reftext{Theorem~\ref{t:Mil89s3}}, we did not use any ``bisimulation
up-to'' technique. Instead, we have used a different technique based on
\reftext{Lemma~\ref{lobsCongrByWeakBisim}}, whose formal version is the following
one (\texttt{OBS\_CONGR\_BY\_WEAK\_BISIM}):
%
%a4.10.2 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{WEAK\_BISIM} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u}.
            \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
            \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \ensuremath{\HOLBoundVar{E}\sp{\prime}}
\end{alltt}
%
Using \reftext{Lemma~\ref{lobsCongrByWeakBisim}}, the next two results are proved
by directly constructing the required bisimulation: (see~\cite{Tian:2017wrba}
for more details)
%
%l4.21 #&#
\begin{lemma}[\texttt{OBS\_UNIQUE\_SOLUTION\_LEMMA}]
If the variable $X$ is guarded and sequential in $G$, and
$G\{P/X\}\overset{\alpha}{\rightarrow} P'$, then $P'$ takes the form
$H\{P/X\}$, for some $H$, and for any $Q$, we also have
$G\{Q/X\}\overset{\alpha}{\rightarrow} H\{Q/X\}$. Moreover $H$ is sequential,
and if $\alpha = \tau $, then $H$ is also guarded.
%
%a4.21 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{G} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{G} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
       \HOLFreeVar{G} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}. \HOLConst{SEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}. \HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}
\end{alltt}
%
\end{lemma}

%t4.22 #&#
\begin{theorem}[\texttt{OBS\_UNIQUE\_SOLUTION}, \univariate version of
\reftext{Theorem~\ref{t:Mil89s3}}]
 \label{thm:Mil89s3f}
Let $E$ be guarded and sequential expressions, and let
$P \rapprox E\{P/X\}$, $Q \rapprox E\{Q/X\}$. Then $P \rapprox Q$.
%
%a4.22 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Q}
\end{alltt}
%
\end{theorem}

%s4.10.3 #&#
\subsubsection{The version for weak bisimilarity}
 \label{sec4.10.3}

Milner~\cite{Mil89} only mentioned two ``unique solution of equations''
theorems, one for strong equivalence, the other for rooted bisimilarity.
There is, however, another version for weak bisimilarity (\reftext{Theorem~\ref{t:Mil89}})
that shares a large portion of proof steps with the proof for rooted bisimilarity.
As weak bisimilarity is not a congruence, we have to be more restrictive
on the syntax of the equation, using only guarded sums. The related formal
proofs are tedious but closely follow the informal proof~\citep[p.~158--159]{Mil89},
with the exception of the use of ``bisimulation up to with weak arrows''
(\reftext{Definition~\ref{def:doubleweak}}, instead of \reftext{Definition~\ref{def:singleweak}}).

%l4.23 #&#
\begin{lemma}[\texttt{WEAK\_UNIQUE\_SOLUTION\_LEMMA}]
If the variable $X$ is guarded and sequential (with only guarded sums)
in $G$, and $G\{P/X\}\overset{\alpha}{\rightarrow} P'$, then $P'$ takes
the form $H\{P/X\}$, for some expression $H$, and for any $Q$, we have
$G\{Q/X\}\overset{\alpha}{\rightarrow} H\{Q/X\}$. Moreover $H$ is sequential,
and if $\alpha = \tau $ then $H$ is also guarded.
%
%a4.23 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{G} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{G} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
       \HOLFreeVar{G} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}. \HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}. \HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}
\end{alltt}
%
\end{lemma}

%t4.24 #&#
\begin{theorem}[\texttt{WEAK\_UNIQUE\_SOLUTION}, \univariate version of
\reftext{Theorem~\ref{t:Mil89}}]
 \label{thm:Mil89f}
Let $E$ be guarded and sequential expressions, and let
$P \wbvtex E\{P/X\}$, $Q \wbvtex E\{Q/X\}$. Then $P \wbvtex Q$.
%
%a4.24 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{Q}
\end{alltt}
%
\end{theorem}

%s4.11 #&#
\subsection{Unique solution of contractions}
 \label{sec4.11}

A delicate point in the formalisation of the results about unique solution
of contractions is the proof of \reftext{Lemma~\ref{l:ruptocon}} and lemmas alike.
In particular, we use induction on the length of weak transitions. For
this, rather than introducing a refined form of weak transition relation
enriched with its length, we found it more elegant to work with
\emph{traces}, i.e., sequences of transitions. (A further motivation is
to set the ground for future extensions of this formalisation work to
\emph{trace equivalence} in place of bisimilarity.)

A trace is formally represented by the initial and final processes, plus
a list of actions so performed. For this, we first define the concept of
\emph{label-accumulated reflexive transitive closure} (\HOLinline{\HOLConst{LRTC}}).
Then, given any labeled transition relation
\HOLinline{\HOLFreeVar{R}} (of type ``\HOLinline{\ensuremath{\alpha} \HOLTokenTransEnd \ensuremath{\beta} \HOLTokenTransEnd \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}''),
\HOLinline{\HOLConst{LRTC} \HOLFreeVar{R}} is a relation representing traces
over \HOLinline{\HOLFreeVar{R}} (of type ``\HOLinline{\ensuremath{\alpha} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{list} \HOLTokenTransEnd \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}''):
%
%a4.11 #&#
\begin{alltt}
   \HOLConst{LRTC} \HOLFreeVar{R} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b} \HOLTokenDefEquality{}
     \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.
         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x}. \HOLBoundVar{P} \HOLBoundVar{x} \ensuremath{[}\ensuremath{]} \HOLBoundVar{x}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z}. \HOLFreeVar{R} \HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \HOLBoundVar{x} \ensuremath{(}\HOLBoundVar{h}\HOLSymConst{::}\HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{z}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
         \HOLBoundVar{P} \HOLFreeVar{a} \HOLFreeVar{l} \HOLFreeVar{b}\hfill{[LRTC\_DEF]}
\end{alltt}
%
The trace relation for CCS, \HOLinline{\HOLConst{TRACE}} (of the type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTyOp{list} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}''),
is then obtained by combining \texttt{LRTC} and the \texttt{TRANS} ($
\overset{\mu}{\rightarrow}$) relation defining the SOS rules:
%
%a4.11 #&#
\begin{alltt}
   \HOLConst{TRACE} \HOLTokenDefEquality{} \HOLConst{LRTC} \HOLConst{TRANS}\hfill{[TRACE\_def]}
\end{alltt}

In a trace $P\overset{acts}{\longrightarrow}Q$, the list of actions
$acts$ may be empty, in which case there is no transition, and the initial
and final processes are the same, i.e. $P = Q$. If there is at most one
visible action $\mu $ in $acts$, and all other actions are $\tau $'s, then
the trace represents a weak transition $P \Arr{\mu} Q$. For this, we have
to distinguish two cases in the list of actions: no label and unique label.
The definition of ``no label'' for a list of actions is as follows, where
\texttt{MEM} tests if an element is a member of a list:
%
%a4.11 #&#
\begin{alltt}
   \HOLConst{NO\_LABEL} \HOLFreeVar{L} \HOLTokenDefEquality{} \HOLSymConst{\HOLTokenNeg{}}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{l}. \HOLConst{MEM} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \HOLFreeVar{L}\hfill{[NO\_LABEL\_def]}
\end{alltt}

The definition of ``unique label'' can be done in many ways. The following
definition (due to a suggestion from Robert Beers) avoids any counting
or filtering in the list. It says that a label is unique in a list of actions
if there is no label in the rest of list (here
$\HOLTokenDoublePlus $ is the concatenation of lists):
%
%a4.11 #&#
\begin{alltt}
   \HOLConst{UNIQUE\_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLTokenDefEquality{}
     \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{L}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{L}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{L}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} \ensuremath{[}\HOLFreeVar{u}\ensuremath{]} \HOLSymConst{\HOLTokenDoublePlus} \ensuremath{\HOLBoundVar{L}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO\_LABEL} \ensuremath{\HOLBoundVar{L}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO\_LABEL} \ensuremath{\HOLBoundVar{L}\sb{\mathrm{2}}}\hfill{[UNIQUE\_LABEL\_def]}
\end{alltt}

Finally, the relationship between traces and weak transitions is stated
and proved in the following theorem. It says that a weak transition
$P \Arr{u} P'$ is also a trace $P\overset{acts}{\longrightarrow}P'$ with
a non-empty action list $acts$, in which either there is no label (for
$u = \tau $), or $u$ is the unique label (for $u \neq \tau $):
%
%a4.11 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLFreeVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}}
   \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{acts}.
       \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{acts} \ensuremath{\HOLFreeVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{NULL} \HOLBoundVar{acts} \HOLSymConst{\HOLTokenConj{}}
       \HOLKeyword{if} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLKeyword{then} \HOLConst{NO\_LABEL} \HOLBoundVar{acts} \HOLKeyword{else} \HOLConst{UNIQUE\_LABEL} \HOLFreeVar{u} \HOLBoundVar{acts}\hfill{[WEAK\_TRANS\_AND\_TRACE]}
\end{alltt}

Now the formal version of \reftext{Lemma~\ref{l:uptocon}} (\texttt{UNIQUE\_SOLUTION\_OF\_CONTRACTIONS\_LEMMA}):
%
%a4.11 #&#
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E}. \HOLConst{WGS} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{E} \HOLFreeVar{Q}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{C}.
       \HOLConst{GCONTEXT} \HOLBoundVar{C} \HOLSymConst{\HOLTokenImp{}}
       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{R}.
            \HOLBoundVar{C} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
            \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}.
                \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenContracts{}} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}}
                \ensuremath{(}\HOLConst{WEAK\_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}. \HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{y}\ensuremath{)}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C} \HOLFreeVar{Q}\ensuremath{)} \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLFreeVar{Q}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}.
           \HOLBoundVar{C} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
           \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}. \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenContracts{}} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{WEAK\_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{EPS}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C} \HOLFreeVar{Q}\ensuremath{)} \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLFreeVar{Q}\ensuremath{)}
\end{alltt}

Traces are actually used in the proof of above lemma via the following
lemma (\texttt{unfolding\_lemma4}):
%
%a4.11 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{GCONTEXT} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}\ensuremath{)} \HOLFreeVar{P}\ensuremath{)} \HOLFreeVar{xs} \ensuremath{\HOLFreeVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{xs} \HOLSymConst{\HOLTokenLeq{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}. \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLFreeVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}. \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}\ensuremath{)} \HOLBoundVar{Q}\ensuremath{)} \HOLFreeVar{xs} \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLBoundVar{Q}\ensuremath{)}
\end{alltt}
%
which roughly says that, for any context $C$ and weakly guarded context
$E$, if $C [\, E^{n}[P]\,] \overset{xs}{\longrightarrow} P'$ and the length
of actions $xs \leqslant n$, then $P'$ has the form $C'[P]$. Traces are
used in reasoning about the number of intermediate actions in weak transitions.
For instance, from \reftext{Definition~\ref{d:BisCon}}, it is easy to see that a weak transition
either becomes shorter or remains the same when moving between
$\mcontrBIS $-related processes. This property is essential in the proof
of \reftext{Lemma~\ref{l:uptocon}}. We show only one such lemma, for the case of
visible weak transitions:
%
%a4.11 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{xs} \HOLBoundVar{l} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
       \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{xs} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{UNIQUE\_LABEL} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{xs}\sp{\prime}} \ensuremath{\HOLBoundVar{Q}\sp{\prime}}.
           \HOLConst{TRACE} \HOLFreeVar{Q} \ensuremath{\HOLBoundVar{xs}\sp{\prime}} \ensuremath{\HOLBoundVar{Q}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \ensuremath{\HOLBoundVar{xs}\sp{\prime}} \HOLSymConst{\HOLTokenLeq{}} \HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenConj{}}
           \HOLConst{UNIQUE\_LABEL} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \ensuremath{\HOLBoundVar{xs}\sp{\prime}}\hfill{[contracts\_AND\_TRACE\_label]}
\end{alltt}

With all above lemmas, we can thus finally prove \reftext{Theorem~\ref{t:contraBisimulationU}}:
%
%a4.11 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{Q}\hfill{[UNIQUE\_SOLUTION\_OF\_CONTRACTIONS]}
\end{alltt}

%s4.12 #&#
\subsection{Unique solution of rooted contractions}
 \label{sec4.12}

The formal proof of ``unique solution of rooted contractions theorem''
(\reftext{Theorem~\ref{t:rcontraBisimulationU}}, \univariate version) shares the
same initial proof steps as \reftext{Theorem~\ref{t:contraBisimulationU}}. It then
requires a few more steps to handle rooted bisimilarity in the conclusion.
The two proofs are similar, mostly because the main property needed from
contraction and rooted contraction is precongruence. Below is the formal
version of \reftext{Theorem~\ref{t:rcontraBisimulationU}}:
%
%a4.12 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenObsContracts} \HOLFreeVar{E} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Q}\hfill{[UNIQUE\_SOLUTION\_OF\_ROOTED\_CONTRACTIONS]}
\end{alltt}

Having proved the precongruence property of rooted contraction ($
\rcontr $), now we can use weakly guarded expressions in the above theorem,
which has no more constraints on summation (as shown by the appearance
of \HOLinline{\HOLConst{WG}} rather than \HOLinline{\HOLConst{WGS}}).

Having removed the constraints on summation, this result is close to Milner's
original `unique solution of equations' theorem for \emph{strong} bisimilarity
(\reftext{Theorem~\ref{t:Mil89s1}})~--- the same weakly guarded context (\HOLinline{\HOLConst{WG}})
is required. In contrast, Milner's ``unique solution of equations'' theorem
for rooted bisimilarity ($\rapprox $) (\reftext{Theorem~\ref{t:Mil89s3}}), has more
rigid constraints, as the \emph{equations} must be both guarded and sequential.

%s5 #&#
\section{The \multivariate formalisation}
%%LEAP%%%\label{sec5}
 \label{sec:multivariate}

In this section we attack the case of multiple equations (the `\multivariate '
case), for two major theorems earlier discussed: Milner's ``unique solution
of equations (for $\sim $)'' (\reftext{Theorem~\ref{t:Mil89s1}}) and the ``unique
solution of rooted contractions'' (\reftext{Theorem~\ref{t:rcontraBisimulationU}}).
The formalisation supports finitely many equations/contractions and equation
variables.\footnote{The original theorems hold for even infinitely many
equations and equation variables.} We chose these two theorems because
of their relevance, and because they well illustrate the work needed in
the \multivariate case.

The central problem of the \multivariate formalisation is the representation
of \multivariate CCS equations (expressions and contexts). In the
\univariate case, $\lambda $-functions are used for representing
\univariate CCS equations, and variable substitutions are simply applications
of $\lambda $-functions to CCS terms. This idea, however, cannot be extended
to the \multivariate case, as we do not have a fixed number of variables
to deal with.

In the literature (\citep[p.~102]{Gorrieri:2015jt}, e.g.), the variables
$X_i$ of a system of equations $\{X_i = E_i\}_{i\in I}$ are usually considered
as \emph{process variables} outside the CCS syntax. Then, an equation body
$E_i$ is an \emph{open} expression built with CCS operators plus these equation
variables. In a formalisation, this means either defining a whole new datatype
(with the new equation variables), in which each CCS operator must be duplicated,
or adding equation variables as a new primitive to the existing CCS type.
In either cases the \emph{disjointness} between equation variables and agent
variables is syntactically guaranteed. Both solutions are rather combersome,
and require a non-trivial modification of the existing \univariate formalisation.

In our work, we have followed Milner's original approach~\cite{milner1990operational},
using the \emph{same} alphabet for both agent variables and equation variables.
This approach allows a large reuse of the \univariate formalisation. For
instance, the variable substitution in the SOS rule \texttt{REC} can be
reused for substituting equation variables. However, care is needed in
the proofs of many fundamental lemmas, mostly due to variable capture issues
between free equation variables and bound agent variables.

%s5.1 #&#
\subsection{Free and bound variables}
 \label{sec5.1}

As mentioned at the beginning of Section~\ref{s:eq}, within our CCS syntax
an agent variable may occur outside the recursion in which it is bound.
Thus the same variable can appear both \emph{free} and \emph{bound} in a
CCS term. We denote the set of bound variables of a given CCS term
$E$ (the variables that are bound in a recursion subexpression of
$E$) as $\bvvtex{E}$ (or \HOLinline{\HOLConst{BV}\\\;\HOLFreeVar{E}} in
HOL), and the set of free variables as $\fvvtex{E}$ (or
\HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}} in HOL). Both
\HOLinline{\HOLConst{BV}} and \HOLinline{\HOLConst{FV}} have the type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\alpha} \HOLTokenTransEnd \HOLTyOp{bool}}'',
i.e. functions taking CCS terms and returning (finite) sets of variables
(of type \HOLinline{\ensuremath{\alpha}}). For their definition the interesting
cases are those of recursion and agent variables, shown below (here
\texttt{DELETE} and \texttt{INSERT} are set-theoretic operators of HOL's
\texttt{pred\_set} theory):
%
\begin{center}
%
\begin{tabular}{ll}
\hline
\HOLConst{FV} \ensuremath{(}\HOLConst{var} \HOLFreeVar{X}\ensuremath{)} \HOLTokenDefEquality{} \HOLTokenLeftbrace{}\HOLFreeVar{X}\HOLTokenRightbrace{} & \HOLConst{FV} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{p}\ensuremath{)} \HOLTokenDefEquality{} \HOLConst{FV} \HOLFreeVar{p} \HOLConst{DELETE} \HOLFreeVar{X} \\
\HOLConst{BV} \ensuremath{(}\HOLConst{var} \HOLFreeVar{X}\ensuremath{)} \HOLTokenDefEquality{} \HOLSymConst{\HOLTokenEmpty{}} & \HOLConst{BV} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{p}\ensuremath{)} \HOLTokenDefEquality{} \HOLFreeVar{X} \HOLConst{INSERT} \HOLConst{BV} \HOLFreeVar{p} \\
\hline
\end{tabular}
%
\end{center}
%
Furthermore, $E$ is a process, written
\HOLinline{\HOLConst{IS\_PROC} \HOLFreeVar{E}}, if it does not contain any
free variable, i.e. $\fvvtex{E} = \emptyset $:
%
%a5.1 #&#
\begin{alltt}
   \HOLConst{IS\_PROC} \HOLFreeVar{E} \HOLTokenDefEquality{} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\HOLTokenEmpty{}}\hfill{[IS\_PROC\_def]}
\end{alltt}
%
And a list of CCS processes can be asserted by
\HOLinline{\HOLConst{ALL\_PROC}} defined upon
\HOLinline{\HOLConst{IS\_PROC}}:
%
%a5.1 #&#
\begin{alltt}
   \HOLConst{ALL\_PROC} \HOLFreeVar{Es} \HOLTokenDefEquality{} \HOLConst{EVERY} \HOLConst{IS\_PROC} \HOLFreeVar{Es}\hfill{[ALL\_PROC\_def]}
\end{alltt}

The set of free and bound variables of a term need not be disjoint, e.g.~in
$X + \recu X E$. More importantly, when going from a CCS expression to
its sub-expressions, the set of free variables may increase, while the
set of bound variables either remains the same or decreases. For instance,
$\fvvtex{\recu X (\mu .X)} = \emptyset $, while
$\fvvtex{\mu .X} = \{X\}$. This property of $\fvvtex{\cdot}$ brings some
\xch{difficulties}{difficulities} in transition inductions. As an evidence, we prove the following
fundamental property of $\fvvtex{\cdot}$~\citep[p.~1209]{milner1990operational}:
%
%p5.1 #&#
\begin{proposition}
 \label{prop:transFV}
The derivatives of a process are themselves processes, i.e. if
$E \arr{\mu} E'$ and $\fvvtex{E} = \emptyset $, then
$\fvvtex{E'} = \emptyset $. Formally:
%
%a5.1 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}}. \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{IS\_PROC} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{IS\_PROC} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\hfill{[TRANS\_PROC]}
\end{alltt}
%
\end{proposition}

\begin{proof}
We prove a stronger result, asserting that the set of free variables in
a CCS process does not increase in its derivatives:
%
%a5.1 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}}. \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E}\hfill{[TRANS\_FV]}
\end{alltt}

In~\cite{milner1990operational}, the proof of the above property is commented
as ``an easy action induction''. As a matter of fact, in the HOL proof
``action induction'' (also known as \emph{transition induction}) becomes
a form of higher-order application of the following
\emph{induction principle} (generated together with the SOS rules), which
essentially says that \HOLinline{\HOLConst{TRANS}} is the smallest relation
satisfying the SOS rules:
%
%a5.1 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.
       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u}. \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}. \HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}. \HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}. \HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}. \HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{l} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
            \HOLBoundVar{P} \HOLBoundVar{E} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \ensuremath{(}\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLBoundVar{l}\ensuremath{)}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
            \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \HOLSymConst{\ensuremath{\tau}} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{l} \HOLBoundVar{L}.
            \HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLBoundVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
            \HOLBoundVar{P} \ensuremath{(}\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{rf}. \HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)} \ensuremath{(}\HOLConst{relabel} \HOLBoundVar{rf} \HOLBoundVar{u}\ensuremath{)} \ensuremath{(}\HOLConst{relab} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{rf}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{X} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}. \HOLBoundVar{P} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}. \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\hfill{[TRANS\_ind]}
\end{alltt}
%
The above long theorem is of the form
\HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin \HOLBoundVar{u}\HOLTokenTransEnd \\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLBoundVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}}
(with $a_0, a_1, a_2$ renamed), where the outermost universal quantifier
$P$ is a higher-order proposition (taking $E$, $\mu $ and $E'$), and
$X$ is another higher-order proposition. The proof goal is actually in
the form of
\HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin \HOLBoundVar{u}\HOLTokenTransEnd \\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLFreeVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}},
where
\HOLinline{\HOLFreeVar{P}\\\;\HOLSymConst{\ensuremath{=}}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLConst{FV}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenSubset{}}\\\;\HOLConst{FV}\\\;\HOLBoundVar{E}\ensuremath{)}}.
Thus, if we can prove $X$ under this specific $P$, by Modus Ponens (MP)
the original proof is completed. Now the goal can be reduced to several
conjunct subgoals, each corresponding to one SOS rule. For instance, in
the subgoal for \texttt{SUM1} we need to prove
$\fvvtex{E_1} \subseteq \fvvtex{E} \Longrightarrow \fvvtex{E_1}
\subseteq \fvvtex{E + E'}$, which holds as
$\fvvtex{E} \subseteq \fvvtex{E + E'} = \fvvtex{E} \cup \fvvtex{E'}$. Eventually
we have only the following goal left (the term above the dash line is the
goal, those below the line are assumptions):
%
%a5.1 #&#
\begin{alltt}
        \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}
   ------------------------------------
    0.  \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
\end{alltt}
%
Note that
\HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLConst{DELETE}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{=}}\\\;\HOLConst{FV}\\\;\ensuremath{(}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{)}},
thus the current proof goal is indeed the consequence of action induction
on the recursion operator. Here the problem is that we know nothing about
\HOLinline{\HOLConst{FV}\\\;\ensuremath{(}\ensuremath{[}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\HOLFreeVar{E}\ensuremath{)}}.
To further proceed, we need to prove some other (easier) lemmas. First,
the next lemma can be proven by induction on $E$ and a few basic set-theoretic
facts:
%
%a5.1 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}. \HOLConst{FV} \ensuremath{(}\ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\hfill{[FV\_SUBSET]}
\end{alltt}
%
Now, if we take $E' = \recu X E$ in the above lemma, we get
\HOLinline{\HOLConst{FV}\\\;\ensuremath{(}\ensuremath{[}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\HOLSymConst{\HOLTokenSubset{}}\\\;\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}\\\;\HOLConst{FV}\\\;\ensuremath{(}\HOLConst{rec}\\\;\HOLFreeVar{X}\\\;\HOLFreeVar{E}\ensuremath{)}}
$=$
\HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLSymConst{\HOLTokenUnion{}}}\break
\HOLinline{\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\\\;\HOLConst{DELETE}\\\;\HOLFreeVar{X}\ensuremath{)}}
$=$ \HOLinline{\HOLConst{FV}\\\;\HOLFreeVar{E}}, i.e. the following lemma:
%
%a5.1 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E}. \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E}\hfill{[FV\_SUBSET\_REC]}
\end{alltt}
%
Thus we can enrich the assumptions of the current proof goal with above
lemma, and obtain
\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
by the transitivity of $\subseteq $:
%
%a5.1 #&#
\begin{alltt}
        \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}
   ------------------------------------
    0.  \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
    1.  \HOLinline{\HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
    2.  \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
\end{alltt}
%
Knowing
\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
we cannot prove
\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}.
However, if we knew
\HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}}},
then
\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLConst{DELETE}}\break \HOLinline{\HOLFreeVar{X} \HOLSymConst{\ensuremath{=}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}}},
and then
\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}},
no matter if
\HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E}}
or not, and the proof would complete. Thus it remains to show that
%
%a5.1 #&#
\begin{alltt}
        \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}}}
   ------------------------------------
    0.  \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
    1.  \HOLinline{\HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
    2.  \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
\end{alltt}
%
Now we try the proof by contradiction (\emph{reductio ad absurdum}): if
the goal does not hold, i.e.
\HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}}},
then by assumption 0 we have
\HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}:
%
%a5.1 #&#
\begin{alltt}
        F
   ------------------------------------
    0.  \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
    1.  \HOLinline{\HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
    2.  \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
    3.  \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}}}
    4.  \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
\end{alltt}
%
But this is impossible, because all free occurrences of $X$ in $E$ now
become bound in the form of $\recu X E$. In fact, the following lemma can
be proven by induction on $E$:
%
%a5.1 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}. \HOLBoundVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLBoundVar{X} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\hfill{[NOTIN\_FV\_lemma]}
\end{alltt}
%
Adding the above lemma (taking $E' = E$) into the assumption list immediately
causes a contradiction with assumption 4, and the proof finally completes.
\end{proof}

\reftext{Proposition~\ref{prop:transFV}} is essential in the proofs of the
\multivariate versions of all unique-solution theorems. On the other hand,
the analogous result for bound variables is indeed just a simple transition
induction. (The easy proof is omitted.)
%
%p5.2 #&#
\begin{proposition}
 \label{prop:transBV}
if $E \arr{\mu} E'$ then $\bvvtex{E'} \subseteq \bvvtex{E}$, or formally:
%
%a5.2 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}}. \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E}\hfill{[TRANS\_BV]}
\end{alltt}
%
\end{proposition}

%s5.2 #&#
\subsection{\Multivariate substitutions}
 \label{sec5.2}

There are two natural ways to implement the \multivariate substitution
$E\{\til P/\til X\}$, which replaces each free occurrence of the variables
$X_i$ in $E$ with the corresponding $P_i$: (1) iterately applying the existing
\univariate \HOLinline{\HOLConst{CCS\_Subst}}; (2) defining a new
\multivariate substitution function which substitutes all variables
$\til X$ in parallel. Note that there is the possibility that
$\til P$ syntactically again contains variables from $\til X$, thus different
orders of iterated substitutions may lead to different results. We thus
prefer to define a \multivariate version of
\HOLinline{\HOLConst{CCS\_Subst}} called
\HOLinline{\HOLConst{CCS\_SUBST}}, based on HOL \texttt{finite\_map} theory~\cite{holdesc}.

A finite map (of type
\HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{\beta}}) is
like a function (of type
\HOLinline{\ensuremath{\alpha} \HOLTokenTransEnd \ensuremath{\beta}}) having
only finitely many elements in its domain. In HOL, an empty finite map
is denoted as \HOLinline{\HOLConst{FEMPTY}}. If
\HOLinline{\HOLFreeVar{fm}} is a finite map, its domain (as a set of keys)
is denoted as \HOLinline{\HOLConst{FDOM} \HOLFreeVar{fm}}. Applying
\HOLinline{\HOLFreeVar{fm}} on a certain key, say $k$, is denoted by
\HOLinline{\HOLFreeVar{fm} \HOLConst{'} \HOLFreeVar{k}}.

The function \HOLinline{\HOLConst{CCS\_SUBST}} takes a finite map
\HOLinline{\HOLFreeVar{fm}} (of type
\HOLinline{\ensuremath{\alpha} \HOLTokenMapto{} \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}})
and a CCS expression, and returns another CCS expression in which all occurrences
of variables in the finite domain of \HOLinline{\HOLFreeVar{fm}} are substituted
with the corresponding value in \HOLinline{\HOLFreeVar{fm}}. Initially,
such a finite map can be built from a list of variables
\HOLinline{\HOLFreeVar{Xs}} and the corresponding substituted terms
\HOLinline{\HOLFreeVar{Ps}} by a helper function
\HOLinline{\HOLConst{fromList}} (whose details are omitted here).
\HOLinline{\HOLConst{CCS\_SUBST}\\\;\ensuremath{(}\HOLConst{fromList}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Ps}\ensuremath{)}\\\;\HOLFreeVar{E}}
is usually abbreviated as
\HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}.
Using finite maps, the substitution mechanism is order-independent. For
most CCS operators, \HOLinline{\HOLConst{CCS\_SUBST}} recursively calls
itself on subterms. The most interesting cases are at agent variables and
recursion:
%
%a5.2 #&#
\begin{alltt}
   \HOLConst{CCS\_SUBST} \HOLFreeVar{fm} \ensuremath{(}\HOLConst{var} \HOLFreeVar{X}\ensuremath{)} \HOLTokenDefEquality{} \HOLKeyword{if} \HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLFreeVar{fm} \HOLKeyword{then} \HOLFreeVar{fm} \HOLConst{'} \HOLFreeVar{X} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{X}\hfill{[CCS\_SUBST\_var]}
\end{alltt}

\begin{alltt}
   \HOLConst{CCS\_SUBST} \HOLFreeVar{fm} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{)} \HOLTokenDefEquality{}
     \HOLKeyword{if} \HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLFreeVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{X} \ensuremath{(}\HOLConst{CCS\_SUBST} \ensuremath{(}\HOLFreeVar{fm} \HOLSymConst{\ensuremath{\setminus}} \HOLFreeVar{X}\ensuremath{)} \HOLFreeVar{E}\ensuremath{)}
     \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{X} \ensuremath{(}\HOLConst{CCS\_SUBST} \HOLFreeVar{fm} \HOLFreeVar{E}\ensuremath{)}\hfill{[CCS\_SUBST\_rec]}
\end{alltt}
%
Variable substitution only occurs on free variables. When the term
$E$ of ``\HOLinline{\HOLConst{CCS\_SUBST}\\\;\HOLFreeVar{fm}\\\;\HOLFreeVar{E}}''
is in the form of $\recu X E'$, if $X$ (a bound variable) is in the domain
of \HOLinline{\HOLFreeVar{fm}}, \HOLinline{\HOLConst{CCS\_SUBST}} must continue
the substitution on $E'$ using a reduced map~--- without $X$~--- so that
all \xch{occurrences}{occurences} of $X$ in $E'$ are correctly bypassed. Since
\HOLinline{\HOLConst{CCS\_SUBST}} only runs once on each subterm, the possible
free variables in \HOLinline{\HOLFreeVar{Ps}} are never substituted.

Below we present some key lemmas about
\HOLinline{\HOLConst{CCS\_SUBST}}, omitting the proofs\footnote{Hereafter,
some new logical constants from HOL's \texttt{pred\_set} and
\texttt{list} theories are used (see~\cite{holdesc} for more details.):
\HOLinline{\HOLConst{DISJOINT}} denotes set disjointness; ``\HOLinline{\HOLConst{set}\\\;\HOLFreeVar{Xs}}''
is the set converted from the list \HOLinline{\HOLFreeVar{Xs}};
\HOLinline{\HOLConst{ALL\_DISTINCT}} says that the elements of a list are
distinct; \HOLinline{\HOLConst{MAP}} is the mapping function from one list
to another; \HOLinline{\HOLConst{EVERY}} means each element of a list satisfies
a predicate; \HOLinline{\HOLConst{ZIP}} creates a new list from two lists
of the same length, and each element of the new list is a pair of elements
from the given lists.}:

%l5.3 #&#
\begin{lemma}[\texttt{CCS\_SUBST\_elim}]
If the free variables of $E$ \xch{are}{is} disjoint with
\HOLinline{\HOLFreeVar{Xs}}, a substitution of
\HOLinline{\HOLFreeVar{Xs}} in $E$ does not change $E$:
%
%a5.3 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{E}
\end{alltt}
%
\end{lemma}

%l5.4 #&#
\begin{lemma}[\texttt{CCS\_SUBST\_self}]
Substituting each free variable $X$ in $E$ with
\HOLinline{\HOLConst{var}\\\;\HOLFreeVar{X}} (itself) does not change
$E$:
%
%a5.4 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ALL\_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLConst{MAP} \HOLConst{var} \HOLFreeVar{Xs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{E}
\end{alltt}
%
\end{lemma}

The next lemma plays an important role. It essentially swaps the order
of two substitutions:
%
%l5.5 #&#
\begin{lemma}[\texttt{CCS\_SUBST\_nested}]
Under certain conditions (to get rid of substitution orders), two nested
substitutions can be converted into a single substitution where the targets
are substituted first:
%
%a5.5 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ALL\_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}}
   \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{C}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLConst{MAP} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}
\end{alltt}
%
\end{lemma}

The next three lemmas show the relative correctness of
\texttt{CCS\_SUBST} with respect to~\texttt{CCS\_Subst}:
%
%l5.6 #&#
\begin{lemma}[\texttt{CCS\_SUBST\_sing}]
If there is only one single variable $X$ in the map (with the target expression
$E'$), then \HOLinline{\HOLConst{CCS\_SUBST}} behaves exactly the same as
(the \univariate ) \HOLinline{\HOLConst{CCS\_Subst}}:
%
%a5.6 #&#
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{]}\ensuremath{/}\ensuremath{[}\HOLFreeVar{X}\ensuremath{]}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}
\end{alltt}
%
\end{lemma}

%l5.7 #&#
\begin{lemma}[\texttt{CCS\_SUBST\_reduce}]
Under certain conditions (to get rid of substitution orders), a
\multivariate substitution of variables
\HOLinline{\HOLFreeVar{X}\HOLSymConst{::}\HOLFreeVar{Xs}} can be reduced
to a \multivariate substitution of variables
\HOLinline{\HOLFreeVar{Xs}} and an \univariate substitution of $X$:
%
%a5.7 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLFreeVar{X} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL\_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}}
   \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \HOLBoundVar{e}\ensuremath{)} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}. \ensuremath{[}\HOLFreeVar{P}\HOLSymConst{::}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{X}\HOLSymConst{::}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLFreeVar{P}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}
\end{alltt}
%
\end{lemma}

%l5.8 #&#
\begin{lemma}[\texttt{CCS\_SUBST\_FOLDR}]
Under certain conditions (to get rid of substitution orders), a
\multivariate substitution can be reduced to repeated applications of
\univariate substitutions of each variable:
%
%a5.8 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ALL\_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}}
   \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{p}\ensuremath{)}. \HOLConst{FV} \HOLBoundVar{p} \HOLSymConst{\HOLTokenSubset{}} \HOLTokenLeftbrace{}\HOLBoundVar{x}\HOLTokenRightbrace{}\ensuremath{)} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLFreeVar{Xs}\HOLSymConst{,}\HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{FOLDR} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}\ensuremath{)} \HOLBoundVar{e}. \ensuremath{[}\HOLBoundVar{y}\ensuremath{/}\HOLBoundVar{x}\ensuremath{]} \HOLBoundVar{e}\ensuremath{)} \HOLFreeVar{E} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLFreeVar{Xs}\HOLSymConst{,}\HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
\end{alltt}
%
\end{lemma}

Finally, the following two lemmas precisely estimate the free and bound
variables of a substituted term:
%
%l5.9 #&#
\begin{lemma}[\texttt{BV\_SUBSET\_BIGUNION}]
The bound variables of
\HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}
are contained in the union of the bound variables in $E$ and
\HOLinline{\HOLFreeVar{Ps}}.
%
%a5.9 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ALL\_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{\HOLTokenBigUnion{}} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{BV} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
\end{alltt}
%
\end{lemma}

%l5.10 #&#
\begin{lemma}[\texttt{FV\_SUBSET\_BIGUNION\_PRO}]
The free variables of
\HOLinline{\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]}\\\;\HOLFreeVar{E}}
are contained in the union of the free variables in $E$ and
\HOLinline{\HOLFreeVar{Ps}}, excluding \HOLinline{\HOLFreeVar{Xs}}.
%
%a5.10 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ALL\_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DIFF} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{\HOLTokenBigUnion{}} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{FV} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Ps}\ensuremath{)}\ensuremath{)}
\end{alltt}
%
\end{lemma}

In some of the above lemmas, the condition
\HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}}
(the bound variables of $E$ and the free substitution variables are disjoint)
is added to ease the proofs. The condition is not necessary and could be
eliminated, at the price of some extra effort.

%s5.3 #&#
\subsection{\Multivariate (weakly guarded) contexts}
 \label{sec5.3}

As mentioned in Section~\ref{sscontext}, \univariate contexts and their
guarded companions are defined as predicates over $\lambda $-expressions
of type ``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}''.
These predicates, such as \HOLinline{\HOLConst{CONTEXT}} (multi-hole contexts),
\HOLinline{\HOLConst{WG}} (weak guarded contexts),
\HOLinline{\HOLConst{SG}} (guarded contexts) and
\HOLinline{\HOLConst{SEQ}} (sequential contexts), are all defined inductively,
i.e.~they are built from some ``holes'' in a bottom-up manner. For instance,
\HOLinline{\HOLConst{WG}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\\\;\HOLSymConst{\ensuremath{\mid}}\\\;\HOLFreeVar{P}\ensuremath{)}}
holds because
\HOLinline{\HOLConst{WG}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\ensuremath{)}}
holds as a base case of the inductive definition of
\HOLinline{\HOLConst{WG}}:
%
%a5.3 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a}. \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\ensuremath{)}\hfill{[WG1]}
\end{alltt}
%
For any agent variable $X$, we have by $\beta $-reduction:
\HOLinline{\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{P}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{var}\\\;\HOLFreeVar{X}\ensuremath{)}\\\;\HOLSymConst{\ensuremath{=}}\\\;\HOLFreeVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{P}}
(or ``$l.X + P$'' in textbook notation), and the expression is weakly guarded
(\reftext{Definition~\ref{def:guardness}}).

It could be possible to inductively define \multivariate contexts and their
guarded variants, but care is needed for variables that occur within a
\xch{recursion}{recusion}.
We \xch{prefer}{have preferred} a different solution, in which the definitions
of \multivariate contexts \xch{are}{is} based on the existing \univariate definitions.
For this, intuitively, we replace a single variable with a hole (viewing
the other variables as constants), so to obtain a single-variable context
on which predicates like \HOLinline{\HOLConst{CONTEXT}} can be used. For
example, to see the weak guardedness of $a.X + b.X + c.Y$, we substitute
each occurrence of a variable with a ``hole'' and consider the resulting
term as a multi-hole context (i.e., a $\lambda $-function); then all such
multi-hole contexts should satisfy \HOLinline{\HOLConst{WG}}, i.e.~the
following results hold:
%
%a5.3 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var} \HOLFreeVar{Y}\ensuremath{)}
\HOLTokenTurnstile{} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var} \HOLFreeVar{X} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var} \HOLFreeVar{X} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{t}\ensuremath{)}
\end{alltt}
%
Note that
\HOLinline{\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{t}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{Y}\\\;\HOLSymConst{\ensuremath{=}}\\\;\ensuremath{[}\HOLFreeVar{t}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]}\\\;\ensuremath{(}\HOLFreeVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{b}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\ensuremath{+}}\\\;\HOLFreeVar{c}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{var}\\\;\HOLFreeVar{Y}\ensuremath{)}}
can be expressed as a \univariate substitution of the original term. This
idea leads to the following definitions:
%
%a5.3 #&#
\begin{alltt}
   \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLTokenDefEquality{} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Xs}\hfill{[context\_def]}
\end{alltt}

\begin{alltt}
   \HOLConst{weakly\_guarded} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLTokenDefEquality{} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Xs}\hfill{[weakly\_guarded\_def]}
\end{alltt}
%
The above definitions take an extra list of variables
\HOLinline{\HOLFreeVar{Xs}} and assert the CCS expression
\HOLinline{\HOLFreeVar{E}} with respect to this list. This allows us to
formalise the concepts of contexts and guardedness independently of the
free variables of \HOLinline{\HOLFreeVar{E}}. Then a logical term ``\HOLinline{\HOLConst{weakly\_guarded}\\\;\ensuremath{(}\HOLConst{SET\_TO\_LIST}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\ensuremath{)}\\\;\HOLFreeVar{E}}''
can be used to assert the weak guardedness of $E$ with respect to all its
free variables.\footnote{Here \HOLinline{\HOLConst{SET\_TO\_LIST}} converts
a finite set to a list of the same elements. It turns out that we never
need this, because in all unique-solution theorems a list of variables
\HOLinline{\HOLFreeVar{Xs}} is fixed and then all equations are required
to contain free variables in \HOLinline{\HOLFreeVar{Xs}}.} (The
\multivariate guardedness and sequentiality can also be defined \xch{similarly}{similarily},
using their \univariate companions \HOLinline{\HOLConst{SG}} and
\HOLinline{\HOLConst{SEQ}}.)

The most important property of \multivariate contexts is that strong bisimilarity
and other (pre)congruence relations are preserved by them, for instance:
%
%l5.11 #&#
\begin{lemma}[\texttt{STRONG\_EQUIV\_subst\_context}]
If two tuples of processes $\til P$ and $\til Q$ are strongly bisimilar,\footnote{A
HOL term like
\HOLinline{\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenStrongEQ}\\\;\HOLFreeVar{Qs}}
means that two lists of CCS processes are componentwise bisimilar ($P_i
\sim Q_i$).} then for any context $E$, $E\{\til P/\til X\}$ and
$E\{\til Q/\til X\}$ are strongly bisimilar:
%
%a5.11 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ALL\_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{Qs} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}. \HOLConst{context} \HOLFreeVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\HOLTokenStrongEQ} \ensuremath{[}\HOLFreeVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLBoundVar{E}
\end{alltt}
%
\end{lemma}
%
Similar properties also hold if $\sim $ is replaced with rooted bisimilarity
($\rapprox $) and rooted contraction ($\rcontr $). It does not hold for
weak bisimilarity ($\wbvtex $) and the contraction preorder ($
\mcontrBIS $), as they are not (pre)congruence relations.

Another important property of contexts is their composability: if we substitute
some free variables in a context with some other contexts, the resulting
term is still a valid context (with respect to the same set of variables):
%
%a5.3 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ALL\_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLConst{context} \HOLFreeVar{Xs}\ensuremath{)} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
   \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)}\hfill{[context\_combin]}
\end{alltt}

Not every term within the CCS syntax is a context, as context (or equation)
variables are not allowed to occur within recursion. The converse holds
however: if the set of free variables of a CCS term is disjoint from a
list of variables, then the term is indeed a context with respect to such
list of variables:
%
%a5.3 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{E}\hfill{[disjoint\_imp\_context]}
\end{alltt}
%
On the other hand, for any context (with respect to $\til X$) of the form
$\recu Y E$, the set of free variables of $E$ excluding $Y$ is disjoint
with $\til X$:
%
%a5.3 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{Y}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\hfill{[context\_rec]}
\end{alltt}
%
In the above lemma we cannot conclude
\HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}},
because $Y$ may appear in both sets. We also cannot conclude
\HOLinline{\HOLConst{context}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{E}}, because
in $\recu Y E$ the bound variable $Y$ may occur freely within another nested
recursion. For instance, variable $Y$ is free in $\recu Y E$, for
$E = \recu Z (a.Y + b.Z) + c.Y$.

For weakly guarded contexts, besides their usual properties as in the
\univariate case (i.e., weak guardedness, \HOLinline{\HOLConst{WG}}), we
also need their composability with respect to~\multivariate contexts: if
we substitute some free variables in a context $C$ with some weakly guarded
contexts, the resulting context is weakly guarded (with respect to the
same set of variables):
%
%a5.3 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ALL\_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly\_guarded} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
   \HOLConst{weakly\_guarded} \HOLFreeVar{Xs} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)}\hfill{[weakly\_guarded\_combin]}
\end{alltt}

%s5.4 #&#
\subsection{\Multivariate equations and solutions}
 \label{sec5.4}

With the formal definitions of \multivariate substitution and
\multivariate (weakly guarded) contexts, now we are ready to formally define
\multivariate CCS equations/contractions and their (unique) solutions.
Consider a system of equation $\{X_i = E_i\}_{i\in I}$ (\reftext{Definition~\ref{def:equation}}),
or its expanded form (here we suppose $I = [1,n] \in \mathbb{N}$, i.e.~a
finite list):
%
\begin{equation*}
%
\begin{cases}
&X_1 = E_1[\til X]
\\
&X_2 = E_2[\til X]
\\
& \cdots
\\
&X_n = E_n[\til X]
\end{cases}
%
\end{equation*}
%
Consider its two essential ingredients:
%
\begin{itemize}
%
\item $\til X = (X_1, X_2, \ldots , X_n)$: a list of equation variables;
%
\item $\til E = (E_1, E_2, \ldots , E_n)$: a list of CCS contexts with
possible occurrences of free variables in $\til X$.
%
\end{itemize}
%
The two lists $\til X$ and $\til E$ should have the same length, and the
variables in $\til X$ should be distinct. Furthermore, $\til E$ does not
contain free variables that are not in $\til X$. Finally, for each
$E_i$, the set of its bound variables should be \emph{disjoint} from
$\til X$. These requirements yield the \xch{formal}{fomal} definition of
\multivariate CCS equation:
%
%a5.4 #&#
\begin{alltt}
   \HOLConst{CCS\_equation} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLTokenDefEquality{}
     \HOLConst{ALL\_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}}
     \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{FV} \HOLBoundVar{e} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Es}
\end{alltt}

Now consider (formally) what is a solution $\til P$ of CCS equations. First
of all, the definition should be
\xch{parameterized}{parametrized} on a binary CCS relation
$\Rvtex $ such as $\sim $ and $\rcontr $, so that a single definition can
be used to represent solutions of all kinds of CCS equations. Then,
${\til P} \ \Rvtex \  {\til E}\{\til P/\til X\}$ should hold:
%
\begin{equation*}
%
\begin{cases}
&P_1 \ \Rvtex \ E_1\{\til P/\til X\}
\\
&P_2 \ \Rvtex \ E_2\{\til P/\til X\}
\\
& \cdots
\\
&P_n \ \Rvtex \ E_n\{\til P/\til X\}
\end{cases}
%
\end{equation*}
%
Furthermore, each $P_i$ should be a pure process, i.e.~having no free variable.
Finally, the set of bound variables is disjoint with $\til X$. (This disjointness
requirement is optional but makes many proofs easier.) Putting all together,
below is the formal definition of a solution of \multivariate CCS equations\footnote{If
$R$ is a binary relation of CCS processes,
\HOLinline{\HOLConst{LIST\_REL}\\\;\HOLFreeVar{R}} is the same binary relation
but for lists of CCS processes with the same length. Implicitly implies
that the two lists $A$ and $B$ have the same length.}:
%
%a5.4 #&#
\begin{alltt}
   \HOLConst{CCS\_solution} \HOLFreeVar{R} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLFreeVar{Ps} \HOLTokenDefEquality{}
     \HOLConst{ALL\_PROC} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenConj{}}
     \HOLConst{LIST\_REL} \HOLFreeVar{R} \HOLFreeVar{Ps} \ensuremath{(}\HOLConst{MAP} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{Es}\ensuremath{)}
\end{alltt}
%
Note that the two logical terms ``\HOLinline{\HOLConst{CCS\_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}\\\;\HOLFreeVar{Ps}}''
and ``\HOLinline{\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenIn{}}\\\;\HOLConst{CCS\_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}''
in HOL have the same meaning (they are equivalent). The latter form suggests
that ``\HOLinline{\HOLConst{CCS\_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}''
is actually a set containing all solutions of ``\HOLinline{\HOLConst{CCS\_equation}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}''.
Then the unique-solution theorems can be understood thus: any two elements
in the solution set are bisimilar.

%s5.5 #&#
\subsection{Unique solution of equations/contractions (the \multivariate version)}
 \label{sec5.5}

With all above machineries of \multivariate contexts and substitutions,
the \multivariate case of \reftext{Lemma~\ref{lem:milner313}} is formalised below
(\texttt{strong\_unique\_solution\_lemma}):
%
%a5.5 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{weakly\_guarded} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps}.
       \HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
           \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
           \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sp{\prime}}.
               \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
               \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
               \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}. \HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime}}
\end{alltt}

The \multivariate version of \reftext{Theorem~\ref{t:Mil89s1}} is formalised thus:
%
%a5.5 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{CCS\_equation} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly\_guarded} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenIn{}} \HOLConst{CCS\_solution} \HOLConst{STRONG\_EQUIV} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLFreeVar{Qs} \HOLSymConst{\HOLTokenIn{}} \HOLConst{CCS\_solution} \HOLConst{STRONG\_EQUIV} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenImp{}}
   \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenStrongEQ} \HOLFreeVar{Qs}\hfill{[strong\_unique\_solution\_thm]}
\end{alltt}

Now the \multivariate version of \reftext{Theorem~\ref{t:rcontraBisimulationU}}:
%
%a5.5 #&#
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{CCS\_equation} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly\_guarded} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenIn{}} \HOLConst{CCS\_solution} \HOLConst{OBS\_contracts} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLFreeVar{Qs} \HOLSymConst{\HOLTokenIn{}} \HOLConst{CCS\_solution} \HOLConst{OBS\_contracts} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenImp{}}
   \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Qs}\hfill{[unique\_solution\_of\_rooted\_contractions]}
\end{alltt}
%
In summary, while each step related to \multivariate substitutions is more
difficult than that for the \univariate case, the structure of the overall
proofs is the same; various proof steps can even be copied from the
\univariate case.

%s6 #&#
\section{Related work on formalisation}
%%LEAP%%%\label{sec6}
 \label{s:rel}

Monica Nesi did the first CCS formalisations for both pure and value-passing
CCS \cite{Nesi:1992ve,Nesi:2017wo} using early versions of the HOL theorem
prover.\footnote{Part of this work can now be found at
\url{https://github.com/binghe/HOL-CCS/tree/master/CCS-Nesi}.} Her main
focus was on implementing decision procedures (as a ML program, e.g.~\cite{cleaveland1993concurrency})
for automatically proving bisimilarities of CCS processes. Her work has
been a basis for ours~\cite{Tian:2017wrba}. However, the differences are
substantial, especially in the way of defining bisimilarities. We greatly
benefited from new features and standard libraries in recent versions of
HOL4, and our formalisation has covered a larger spectrum of the (pure)
CCS theory.

Bengtson, Parrow and Weber did a substantial formalisation work on CCS,
$\pi $-calculi and $\psi $-calculi using Isabelle/HOL and its nominal logic,
with the main focus on the handling of name binders
\cite{bengtson2007completeness,parrow2009formalising}. More details can
be found in Bengtson's PhD thesis~\cite{bengtson2010formalising}. For CCS,
he has \xch{formalised}{formalized} basic properties for strong/weak equivalence (congruence,
basic algebraic laws); the CCS syntax does not have constants or recursion,
using instead replication. Other formalisations in this area include the
early work of T.F.~Melham \cite{melham1994mechanized} and O.A.~Mohamed
\cite{mohamed1995mechanizing} in HOL, Compton
\cite{compton2005embedding} in Isabelle/HOL, Solange\footnote{\url{https://github.com/coq-contribs/ccs}.}
in Coq and Chaudhuri et al.\;\cite{chaudhuri2015lightweight} in Abella,
the latter focuses on ``bisimulation up-to'' techniques (for strong bisimilarity)
for CCS and $\pi $-calculus. Damien Pous \cite{pous2007new} also formalised
up-to techniques and some CCS examples in Coq. Formalisations less related
to ours include Kahsai and Miculan \cite{kahsai2008implementing} for the
spi calculus in Isabelle/HOL, and Hirschkoff
\cite{hirschkoff1997full} for the $\pi $-calculus in Coq.

%s7 #&#
\section{Conclusions and future work}
%%LEAP%%%\label{sec7}
 \label{s:concl}

In this paper, besides introducing rooted contraction and its unique solution
theorems, we have carried out a comprehensive formalisation of the theory
of CCS in the HOL4 theorem prover. In particular, the formalisation supports
four methods for establishing (strong and weak) bisimilarities:
%
\begin{enumerate}
%
\item constructing a bisimulation (the standard bisimulation proof method);
%
\item constructing a ``bisimulation up-to'';
%
\item employing algebraic laws;
%
\item constructing a system of equations or contractions (i.e., the `unique-solution'
method)
%
\end{enumerate}

The formalisation has focused on the theory of unique solution of equations
and contractions, both in the \univariate and in the \multivariate cases.
It has allowed us to further develop the theory, notably the basic properties
of rooted contraction, and the unique solution theorem for it with respect
to rooted bisimilarity. The formalisation brings up and exploits similarities
between results and proofs for different equivalences and preorders. Indeed
we have considered several ``unique-solution'' results (for various equivalences
and preorders); they share many parts of the proofs, but present a few
delicate and subtle differences in a few points. In a paper-and-pencil
proof, checking all details would be long and error-prone, especially in
cases where the proofs are similar to each other or when there are long
case analyses to be carried out. We believe that \xch{our}{the} formalisation of all
definitions and theorems \xch{is}{are} easy to read and to understand, as they are
close to their original statement in textbooks.

For some future work, formalising other equivalences and preorders could
also be considered, notably trace-based equivalences, as well as more refined
process calculi such as value-passing CCS. A different and possibly challenging
research line is the formalisation of a different approach~\cite{DurierHS17,DurierHS18}
to unique solutions, in which the use of contraction is replaced by semantic
conditions on process transitions such as divergence.

%%% PASTABA: Pagal zurnalo ypatumus, reikalinga
%%%          zemiau esanti aplinka {conflict}.
%%%          S5 etapui koduoti NEREIKIA.

\begin{conflict}
The authors declare that they have no known competing financial interests or personal
relationships that could have appeared to influence the work reported in this paper.
\end{conflict}

\begin{acks}
We have benefitted from suggestions and comments from the anonymous reviewers
and several people from the HOL community, including (in alphabetical order)
Robert Beers, Jeremy Dawson, Ramana Kumar, Michael Norrish, Konrad Slind,
and Thomas T\"{u}rk. Sangiorgi has been supported by \gsponsor[id=GS4]{MIUR-PRIN} project
`Analysis of Program Analyses' (ASPRA, ID: \texttt{\gnumber[refid=GS4]{201784YSZ5\_004}}), and
by the \gsponsor[id=GS2,sponsor-id=501100000781,country=European Union]{European Research Council} (ERC) Grant \gnumber[refid=GS2]{DLV-818616 DIAPASoN}. The paper
was written in memory of Michael J.~C.~Gordon (1948--2017), the creator
of the HOL theorem prover.
\end{acks}

%\begin{appm}
%\def\the...{}
%\reset{}{}
%\appendix{}
%\appendix*{}
%\end{appm}%
%spell_to        ********** End of text entry *****************
%
%
\begin{backmatter}%
% structpyb loaded by lgiriuniene, 2020-07-27 15:55:25
\begin{thebibliography}{}
% pybtex-2.60. Style name=elsv1, version=1.53, label_style=original, sorting_style=none, cfg=None, language=None.

%b1 ###
\bibitem{EPTCS276.10}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{C.} \snm{Tian}}
\bauthor{\fnm{D.} \snm{Sangiorgi}}
\btitle{Unique solutions of contractions, CCS, and their HOL formalisation}
\end{bcontribution}
\begin{bhost}
\begin{beditedbook}
\beditors{%
\beditor{\fnm{J.A.} \snm{P\'{e}rez}}
\beditor{\fnm{S.} \snm{Tini}}}
\btitle{Proceedings Combined 25th International Workshop on Expressiveness
in Concurrency {and 15th Workshop on} Structural Operational Semantics}
\bconference{Beijing, China, September 3, 2018}
\bbookseries{
\bseries{\btitle{Electronic Proceedings in Theoretical Computer Science}\bvolumeno{276}}}
\bdate{2018}
\bpublisher{\bname{Open Publishing Association}}
\end{beditedbook}
\bpages{\bfirstpage{122}\blastpage{139}}
\bdoi{10.4204/EPTCS.276.10}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
C.~Tian, D.~Sangiorgi, {Unique Solutions of Contractions, CCS, and their
HOL Formalisation}, in: J.~A. P\'erez, S.~Tini (Eds.), \textrm{Proceedings
Combined 25th International Workshop on} Expressiveness in Concurrency
\textrm{and 15th Workshop on} Structural Operational Semantics, \textrm{Beijing,
China, September 3, 2018}, Vol. 276 of Electronic Proceedings in Theoretical
Computer Science, Open Publishing Association, 2018, pp. 122--139.
10.4204/EPTCS.276.10.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b2 ###
\bibitem{Mil89}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{R.} \snm{Milner}}
\btitle{Communication and Concurrency}
\end{bcontribution}
\begin{bhost}
\begin{bbook}
\bbookseries{
\bseries{\btitle{{PHI} Series in Computer Science}}}
\bdate{1989}
\bpublisher{\bname{Prentice-Hall}}
\end{bbook}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
R.~Milner, Communication and concurrency, {PHI} Series in computer science,
Prentice-Hall, 1989.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b3 ###
\bibitem{BaeBOOK}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{J.C.M.} \snm{Baeten}}
\bauthor{\fnm{T.} \snm{Basten}}
\bauthor{\fnm{M.A.} \snm{Reniers}}
\btitle{Process Algebra: Equational Theories of Communicating Processes}
\end{bcontribution}
\begin{bhost}
\begin{bbook}
\bdate{2010}
\bpublisher{\bname{Cambridge University Press}}
\end{bbook}
\bdoi{10.1017/CBO9781139195003}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
J.~C.~M. Baeten, T.~Basten, M.~A. Reniers, Process Algebra: Equational
Theories of Communicating Processes, Cambridge University Press, 2010.
10.1017/CBO9781139195003.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b4 ###
\bibitem{theoryAndPractice}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{A.W.} \snm{Roscoe}}
\btitle{The Theory and Practice of Concurrency}
\end{bcontribution}
\begin{bhost}
\begin{bbook}%%[class=report]
\bdate{1998}
\bpublisher{\bname{Prentice Hall}}
\end{bbook}
\end{bhost}
\begin{bhost}
\begin{behost}
\binterref[locator-type=url]{http://www.cs.ox.ac.uk/people/bill.roscoe/publications/68b.pdf}
\end{behost}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
A.~W. Roscoe,
{The
theory and practice of concurrency}, {Prentice Hall}, 1998.
\url{http://www.cs.ox.ac.uk/people/bill.roscoe/publications/68b.pdf}
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b5 ###
\bibitem{RosUnder10}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{A.W.} \snm{Roscoe}}
\btitle{Understanding Concurrent Systems}
\end{bcontribution}
\begin{bhost}
\begin{bbook}
\bdate{2010}
\bpublisher{\bname{Springer}}
\end{bbook}
\bdoi{10.1007/978-1-84882-258-0}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
A.~W. Roscoe, Understanding Concurrent Systems, Springer, 2010.
10.1007/978-1-84882-258-0.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b6 ###
\bibitem{sangiorgi2015equations}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{D.} \snm{Sangiorgi}}
\btitle{Equations, contractions, and unique solutions}
\end{bcontribution}
\begin{bhost}
\begin{bissue}
\bseries{\btitle{SIGPLAN Not.} \bvolumeno{50}}
\bissueno{1}
\bdate{2015}
\end{bissue}
\bpages{\bfirstpage{421}\blastpage{432}}
\bdoi{10.1145/2775051.2676965}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
D.~Sangiorgi, Equations, contractions, and unique solutions, SIGPLAN Not.
50~(1) (2015) 421--432. 10.1145/2775051.2676965.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b7 ###
\bibitem{sangiorgi2017equations}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{D.} \snm{Sangiorgi}}
\btitle{Equations, contractions, and unique solutions}
\end{bcontribution}
\begin{bhost}
\begin{bissue}
\bseries{\btitle{ACM Trans. Comput. Log.} \bvolumeno{18}}
\bissueno{1}
\bdate{2017}
\end{bissue}
\bpages{\bfirstpage{4:1}\blastpage{4:30}}
\bdoi{10.1145/2971339}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
D.~Sangiorgi, Equations, contractions, and unique solutions, ACM Trans.
Comput. Logic 18~(1) (2017) 4:1--4:30. 10.1145/2971339.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b8 ###
\bibitem{van2005characterisation}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{R.J.} \snm{van Glabbeek}}
\btitle{A characterisation of weak bisimulation congruence}
\end{bcontribution}
\begin{bhost}
\begin{beditedbook}
\btitle{Processes, Terms and Cycles: Steps on the Road to Infinity}
\bdate{2005}
\bpublisher{\bname{Springer}}
\end{beditedbook}
\bpages{\bfirstpage{26}\blastpage{39}}
\bdoi{10.1007/11601548\_4}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
R.~J. van Glabbeek, A characterisation of weak bisimulation congruence,
in: Processes, Terms and Cycles: Steps on the Road to Infinity, Springer,
2005, pp. 26--39. 10.1007/11601548\_4.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b9 ###
\bibitem{Gorrieri:2015jt}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{R.} \snm{Gorrieri}}
\bauthor{\fnm{C.} \snm{Versari}}
\btitle{Introduction to Concurrency Theory}
\end{bcontribution}
\begin{bhost}
\begin{bbook}
\bbookseries{\bseries{\btitle{Transition Systems and CCS}}}
\bdate{2015}
\bpublisher{\bname{Springer}\blocation{Cham}}
\end{bbook}
\bdoi{10.1007/978-3-319-21491-7}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
R.~Gorrieri, C.~Versari, {Introduction to Concurrency Theory}, Transition
Systems and CCS, Springer, Cham, 2015. 10.1007/978-3-319-21491-7.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b10 ###
\bibitem{milner1990operational}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{R.} \snm{Milner}}
\btitle{Operational and algebraic semantics of concurrent processes}
\end{bcontribution}
\begin{bhost}
\begin{beditedbook}
\btitle{Handbook of Theoretical Comput. Sci.}
\bdate{1990}
\end{beditedbook}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
R.~Milner, Operational and algebraic semantics of concurrent processes,
Handbook of Theoretical Comput. Sci. (1990).
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b11 ###
\bibitem{Sangiorgi:2011ut}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{D.} \snm{Sangiorgi}}
\btitle{Introduction to Bisimulation and Coinduction}
\end{bcontribution}
\begin{bhost}
\begin{bbook}
\bdate{2011}
\bpublisher{\bname{Cambridge University Press}}
\end{bbook}
\bdoi{10.1017/CBO9780511777110}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
D.~Sangiorgi, Introduction to Bisimulation and Coinduction, Cambridge University
Press, 2011. 10.1017/CBO9780511777110.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b12 ###
\bibitem{arun1992efficiency}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{S.} \snm{Arun-Kumar}}
\bauthor{\fnm{M.} \snm{Hennessy}}
\btitle{An efficiency preorder for processes}
\end{bcontribution}
\begin{bhost}
\begin{bissue}
\bseries{\btitle{Acta Inform.} \bvolumeno{29}}
\bissueno{8}
\bdate{1992}
\end{bissue}
\bpages{\bfirstpage{737}\blastpage{760}}
\bdoi{10.1007/BF01191894}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
S.~Arun-Kumar, M.~Hennessy, An efficiency preorder for processes, Acta
Informatica 29~(8) (1992) 737--760. 10.1007/BF01191894.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b13 ###
\bibitem{Melham:1993vl}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{M.J.C.} \snm{Gordon}}
\bauthor{\fnm{T.F.} \snm{Melham}}
\btitle{Introduction to {HOL}: A Theorem Proving Environment for Higher Order Logic}
\end{bcontribution}
\begin{bhost}
\begin{bbook}
\bdate{1993}
\bpublisher{\bname{Cambrige University Press}\blocation{New York, NY}}
\end{bbook}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
M.~J.~C. Gordon, T.~F. Melham, Introduction to {HOL}: A Theorem Proving
Environment for Higher Order Logic, Cambrige University Press, New York,
NY, 1993.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b14 ###
\bibitem{slind2008brief}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{K.} \snm{Slind}}
\bauthor{\fnm{M.} \snm{Norrish}}
\btitle{A brief overview of {HOL4}}
\end{bcontribution}
\begin{bhost}
\begin{beditedbook}
\btitle{International Conference on Theorem Proving in Higher Order Logics}
\bdate{2008}
\bpublisher{\bname{Springer}}
\end{beditedbook}
\bpages{\bfirstpage{28}\blastpage{32}}
\bdoi{10.1007/978-3-540-71067-7\_6}
\end{bhost}
\begin{bhost}
\begin{behost}
\binterref[locator-type=url]{http://ts.data61.csiro.au/publications/nicta\_full\_text/1482.pdf}
\end{behost}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
K.~Slind, M.~Norrish,
{A
brief overview of {HOL4}}, in: International Conference on Theorem Proving
in Higher Order Logics, Springer, 2008, pp. 28--32. 10.1007/978-3-540-71067-7\_6.
\url{http://ts.data61.csiro.au/publications/nicta\_full\_text/1482.pdf}
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b15 ###
\bibitem{Nesi:1992ve}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{M.} \snm{Nesi}}
\btitle{A formalization of the process algebra CCS in high order logic}
\end{bcontribution}
\bcomment{Tech. Rep. UCAM-CL-TR-278}\prnsep{,\ }
\begin{bhost}
\begin{bbook}[class=report]
\bdate{1992}
\bpublisher{\bname{University of Cambridge, Computer Laboratory}}
\end{bbook}
\end{bhost}
\begin{bhost}
\begin{behost}
\binterref[locator-type=url]{http://www.cl.cam.ac.uk/techreports/UCAM-CL-TR-278.pdf}
\end{behost}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
M.~Nesi,
{{A
formalization of the process algebra CCS in high order logic}}, Tech. Rep.
UCAM-CL-TR-278, University of Cambridge, Computer Laboratory (1992).
\url{http://www.cl.cam.ac.uk/techreports/UCAM-CL-TR-278.pdf}
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b16 ###
\bibitem{hollogic}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\snm{HOL4 contributors}}
\btitle{The HOL System LOGIC (Kananaskis-13 Release)}
\end{bcontribution}
\begin{bhost}
\begin{bbook}%%[class=report]
\bdate{Aug. 2019}
\end{bbook}
\end{bhost}
\begin{bhost}
\begin{behost}
\binterref[locator-type=url]{http://sourceforge.net/projects/hol/files/hol/kananaskis-13/kananaskis-13-logic.pdf}
\end{behost}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
{HOL4 contributors},
{{The
HOL System LOGIC (Kananaskis-13 release)}} (Aug. 2019).
\url{http://sourceforge.net/projects/hol/files/hol/kananaskis-13/kananaskis-13-logic.pdf}
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b17 ###
\bibitem{gordon1979edinburgh}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{M.J.C.} \snm{Gordon}}
\bauthor{\fnm{A.J.} \snm{Milner}}
\bauthor{\fnm{C.P.} \snm{Wadsworth}}
\btitle{Edinburgh {LCF}: A Mechanised Logic of Computation}
\end{bcontribution}
\begin{bhost}
\begin{bbook}
\bbookseries{
\bseries{\btitle{Lecture Notes in Computer Science}\bvolumeno{78}}}
\bdate{1979}
\bpublisher{\bname{Springer}\blocation{Berlin, Heidelberg}}
\end{bbook}
\bdoi{10.1007/3-540-09724-4}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
M.~J.~C. Gordon, A.~J. Milner, C.~P. Wadsworth, Edinburgh {LCF}: A Mechanised
Logic of Computation, Vol.~78 of Lecture Notes in Computer Science, Springer,
Berlin Heidelberg, 1979. 10.1007/3-540-09724-4.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b18 ###
\bibitem{milner1972logic}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{R.} \snm{Milner}}
\btitle{Logic for computable functions: description of a machine implementation}
\end{bcontribution}
\bcomment{Tech. Rep}\prnsep{,\ }
\begin{bhost}
\begin{bbook}[class=report]
\bdate{1972}
\bpublisher{\bname{Stanford Univ., Dept. of Computer Science}}
\end{bbook}
\end{bhost}
\begin{bhost}
\begin{behost}
\binterref[locator-type=url]{http://www.dtic.mil/dtic/tr/fulltext/u2/785072.pdf}
\end{behost}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
R.~Milner,
{Logic for
computable functions: description of a machine implementation}, Tech. rep.,
Stanford Univ., Dept. of Computer Science (1972).
 \url{http://www.dtic.mil/dtic/tr/fulltext/u2/785072.pdf}
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b19 ###
\bibitem{church1940formulation}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{A.} \snm{Church}}
\btitle{A formulation of the simple theory of types}
\end{bcontribution}
\begin{bhost}
\begin{bissue}
\bseries{\btitle{J. Symb. Log.} \bvolumeno{5}}
\bissueno{2}
\bdate{1940}
\end{bissue}
\bpages{\bfirstpage{56}\blastpage{68}}
\bdoi{10.2307/2266170}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
A.~Church, A formulation of the simple theory of types, The journal of
symbolic logic 5~(2) (1940) 56--68. 10.2307/2266170.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b20 ###
\bibitem{Melham:1989dk}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{T.F.} \snm{Melham}}
\btitle{Automating recursive type definitions in higher order logic}
\end{bcontribution}
\begin{bhost}
\begin{beditedbook}
\btitle{Current Trends in Hardware Verification and Automated Theorem Proving}
\bdate{1989}
\bpublisher{\bname{Springer}\blocation{New York, NY}}
\end{beditedbook}
\bpages{\bfirstpage{341}\blastpage{386}}
\bdoi{10.1007/978-1-4612-3658-0\_9}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
T.~F. Melham, {Automating Recursive Type Definitions in Higher Order Logic},
in: Current Trends in Hardware Verification and Automated Theorem Proving,
Springer, New York, NY, 1989, pp. 341--386. 10.1007/978-1-4612-3658-0\_9.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b21 ###
\bibitem{Melham:1991}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{T.F.} \snm{Melham}}
\btitle{A package for inductive relation definitions in HOL}
\end{bcontribution}
\begin{bhost}
\begin{beditedbook}
\btitle{1991, International Workshop on the HOL Theorem Proving System and Its Applications}
\bdate{1991}
\bpublisher{\bname{IEEE Computer Society Press}\blocation{Davis, CA, USA}}
\end{beditedbook}
\bpages{\bfirstpage{350}\blastpage{357}}
\bdoi{10.1109/HOL.1991.596299}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
T.~F. Melham, {A Package For Inductive Relation Definitions In HOL}, in:
1991., International Workshop on the HOL Theorem Proving System and Its
Applications, IEEE Computer Society Press, Davis, CA, USA, 1991, pp. 350--357.
10.1109/HOL.1991.596299.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b22 ###
\bibitem{holdesc}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\snm{HOL4 contributors}}
\btitle{The HOL System DESCRIPTION (Kananaskis-13 Release)}
\end{bcontribution}
\begin{bhost}
\begin{bbook}%%[class=report]
\bdate{Aug. 2019}
\end{bbook}
\end{bhost}
\begin{bhost}
\begin{behost}
\binterref[locator-type=url]{http://sourceforge.net/projects/hol/files/hol/kananaskis-13/kananaskis-13-description.pdf}
\end{behost}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
{HOL4 contributors},
{{The
HOL System DESCRIPTION (Kananaskis-13 release)}} (Aug. 2019).
\url{http://sourceforge.net/projects/hol/files/hol/kananaskis-13/kananaskis-13-description.pdf}
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b23 ###
\bibitem{PousS19}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{D.} \snm{Pous}}
\bauthor{\fnm{D.} \snm{Sangiorgi}}
\btitle{Bisimulation and coinduction enhancements: a historical perspective}
\end{bcontribution}
\begin{bhost}
\begin{bissue}
\bseries{\btitle{Form. Asp. Comput.} \bvolumeno{31}}
\bissueno{6}
\bdate{2019}
\end{bissue}
\bpages{\bfirstpage{733}\blastpage{749}}
\bdoi{10.1007/s00165-019-00497-w}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
D.~Pous, D.~Sangiorgi, Bisimulation and coinduction enhancements: {A} historical
perspective, Formal Asp. Comput. 31~(6) (2019) 733--749. 10.1007/s00165-019-00497-w.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b24 ###
\bibitem{PoSa2019}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{D.} \snm{Pous}}
\bauthor{\fnm{D.} \snm{Sangiorgi}}
\btitle{Bisimulation and coinduction enhancements: a historical perspective}
\end{bcontribution}
\begin{bhost}
\begin{bissue}
\bseries{\btitle{Form. Asp. Comput.}}
\bdate{2019}
\end{bissue}
\bdoi{10.1007/s00165-019-00497-w}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
D.~Pous, D.~Sangiorgi, Bisimulation and coinduction enhancements: A historical
perspective, Formal Aspects of Computing (2019). 10.1007/s00165-019-00497-w.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b25 ###
\bibitem{sangiorgi1992problem}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{D.} \snm{Sangiorgi}}
\bauthor{\fnm{R.} \snm{Milner}}
\btitle{The problem of ``weak bisimulation up to''}
\end{bcontribution}
\begin{bhost}
\begin{beditedbook}
\btitle{LNCS 630 - CONCUR '92 - Concurrency Theory}
\bdate{1992}
\bpublisher{\bname{Springer}}
\end{beditedbook}
\bpages{\bfirstpage{32}\blastpage{46}}
\bdoi{10.1007/BFb0084781}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
D.~Sangiorgi, R.~Milner, {The problem of ``Weak Bisimulation up to''},
in: LNCS 630 - CONCUR '92 - Concurrency Theory, Springer, 1992, pp. 32--46.
10.1007/BFb0084781.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b26 ###
\bibitem{Tian:2017wrba}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{C.} \snm{Tian}}
\btitle{A Formalization of Unique Solutions of Equations in Process
Algebra}
\end{bcontribution}
\bcomment{Master's thesis}\prnsep{,\ }
\begin{bhost}
\begin{bbook}%%[class=report]
\bdate{Dec. 2017}
\bpublisher{\bname{AlmaDigital} \blocation{Bologna}}
\end{bbook}
\end{bhost}
\begin{bhost}
\begin{behost}
\binterref[locator-type=url]{http://amslaurea.unibo.it/14798/}
\end{behost}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
C.~Tian,
{{A Formalization of Unique
Solutions of Equations in Process Algebra}}, Master's thesis, AlmaDigital,
Bologna (Dec. 2017).
 \url{http://amslaurea.unibo.it/14798/}
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b27 ###
\bibitem{norrish2013ordinals}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{M.} \snm{Norrish}}
\bauthor{\fnm{B.} \snm{Huffman}}
\btitle{Ordinals in HOL: transfinite arithmetic up to (and beyond) $\omega _1$}
\end{bcontribution}
\begin{bhost}
\begin{beditedbook}
\btitle{International Conference on Interactive Theorem Proving}
\bdate{2013}
\bpublisher{\bname{Springer}}
\end{beditedbook}
\bpages{\bfirstpage{133}\blastpage{146}}
\bdoi{10.1007/978-3-642-39634-2\_12}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
M.~Norrish, B.~Huffman, {Ordinals in HOL: Transfinite arithmetic up to
(and beyond) $\omega _1$}, in: International Conference on Interactive
Theorem Proving, Springer, 2013, pp. 133--146. 10.1007/978-3-642-39634-2\_12.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b28 ###
\bibitem{Nesi:2017wo}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{M.} \snm{Nesi}}
\btitle{Formalising a value-passing calculus in HOL}
\end{bcontribution}
\begin{bhost}
\begin{bissue}
\bseries{\btitle{Form. Asp. Comput.} \bvolumeno{11}}
\bissueno{2}
\bdate{1999}
\end{bissue}
\bpages{\bfirstpage{160}\blastpage{199}}
\bdoi{10.1007/s001650050046}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
M.~Nesi, {Formalising a Value-Passing Calculus in HOL}, Formal Aspects
of Computing 11~(2) (1999) 160--199. 10.1007/s001650050046.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b29 ###
\bibitem{cleaveland1993concurrency}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{R.} \snm{Cleaveland}}
\bauthor{\fnm{J.} \snm{Parrow}}
\bauthor{\fnm{B.} \snm{Steffen}}
\btitle{The concurrency workbench: a semantics-based tool for the verification
of concurrent systems}
\end{bcontribution}
\begin{bhost}
\begin{bissue}
\bseries{\btitle{ACM Trans. Program. Lang. Syst.} \bvolumeno{15}}
\bissueno{1}
\bdate{1993}
\end{bissue}
\bpages{\bfirstpage{36}\blastpage{72}}
\bdoi{10.1145/151646.151648}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
R.~Cleaveland, J.~Parrow, B.~Steffen, The concurrency workbench: A semantics-based
tool for the verification of concurrent systems, ACM Transactions on Programming
Languages and Systems (TOPLAS) 15~(1) (1993) 36--72. 10.1145/151646.151648.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b30 ###
\bibitem{bengtson2007completeness}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{J.} \snm{Bengtson}}
\bauthor{\fnm{J.} \snm{Parrow}}
\btitle{A completeness proof for bisimulation in the pi-calculus using isabelle}
\end{bcontribution}
\begin{bhost}
\begin{bissue}
\bseries{\btitle{Electron. Notes Theor. Comput. Sci.} \bvolumeno{192}}
\bissueno{1}
\bdate{2007}
\end{bissue}
\bpages{\bfirstpage{61}\blastpage{75}}
\bdoi{10.1016/j.entcs.2007.08.017}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
J.~Bengtson, J.~Parrow, A completeness proof for bisimulation in the pi-calculus
using isabelle, Electronic Notes in Theoretical Computer Science 192~(1)
(2007) 61--75. 10.1016/j.entcs.2007.08.017.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b31 ###
\bibitem{parrow2009formalising}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{J.} \snm{Parrow}}
\bauthor{\fnm{J.} \snm{Bengtson}}
\btitle{Formalising the pi-calculus using nominal logic}
\end{bcontribution}
\begin{bhost}
\begin{bissue}
\bseries{\btitle{Log. Methods Comput. Sci.} \bvolumeno{5}}
\bdate{2009}
\end{bissue}
\bdoi{10.2168/LMCS-5(2:16)2009}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
J.~Parrow, J.~Bengtson, Formalising the pi-calculus using nominal logic,
Logical Methods in Computer Science 5 (2009). 10.2168/LMCS-5(2:16)2009.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b32 ###
\bibitem{bengtson2010formalising}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{J.} \snm{Bengtson}}
\btitle{Formalising process calculi}
\end{bcontribution}
\bcomment{Ph.D. thesis}\prnsep{,\ }
\begin{bhost}
\begin{bbook}[class=report]
\bdate{2010}
\bpublisher{\bname{Acta Universitatis Upsaliensis}}
\end{bbook}
\end{bhost}
\begin{bhost}
\begin{behost}
\binterref[locator-type=url]{http://uu.diva-portal.org/smash/record.jsf?pid=diva2\%3A311032}
\end{behost}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
J.~Bengtson,
{Formalising
process calculi}, Ph.D. thesis, Acta Universitatis Upsaliensis (2010).
\url{http://uu.diva-portal.org/smash/record.jsf?pid=diva2\%3A311032}
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b33 ###
\bibitem{melham1994mechanized}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{T.F.} \snm{Melham}}
\btitle{A mechanized theory of the pi-calculus in HOL}
\end{bcontribution}
\begin{bhost}
\begin{bissue}
\bseries{\btitle{Nord. J. Comput.} \bvolumeno{1}}
\bissueno{1}
\bdate{1994}
\end{bissue}
\bpages{\bfirstpage{50}\blastpage{76}}
\end{bhost}
\begin{bhost}
\begin{behost}
\binterref[locator-type=url]{http://core.ac.uk/download/pdf/22878407.pdf}
\end{behost}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
T.~F. Melham,
{{A Mechanized
Theory of the Pi-Calculus in HOL}}, Nord. J. Comput. 1~(1) (1994) 50--76.
 \url{http://core.ac.uk/download/pdf/22878407.pdf}
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b34 ###
\bibitem{mohamed1995mechanizing}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{O.} \snm{A\"{\i}t Mohamed}}
\btitle{Mechanizing a $\pi $-calculus equivalence in HOL}
\end{bcontribution}
\begin{bhost}
\begin{beditedbook}
\beditors{%
\beditor{\fnm{E.} \snm{Thomas Schubert}}
\beditor{\fnm{P.J.} \snm{Windley}}
\beditor{\fnm{J.} \snm{Alves-Foss}}}
\btitle{Higher Order Logic Theorem Proving and Its Applications}
\bdate{1995}
\bpublisher{\bname{Springer}\blocation{Berlin, Heidelberg}}
\end{beditedbook}
\bpages{\bfirstpage{1}\blastpage{16}}
\bdoi{10.1007/3-540-60275-5\_53}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
O.~A{\"i}t~Mohamed, {{Mechanizing a $\pi $-calculus equivalence in HOL}},
in: E.~Thomas~Schubert, P.~J. Windley, J.~Alves-Foss (Eds.), Higher Order
Logic Theorem Proving and Its Applications, Springer Berlin Heidelberg,
Berlin, Heidelberg, 1995, pp. 1--16. 10.1007/3-540-60275-5\_53.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b35 ###
\bibitem{compton2005embedding}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{M.} \snm{Compton}}
\btitle{Embedding a fair CCS in Isabelle/HOL}
\end{bcontribution}
\begin{bhost}
\begin{beditedbook}
\btitle{Theorem Proving in Higher Order Logics: Emerging Trends Proceedings}
\bdate{2005}
\end{beditedbook}
\bpages{\bfirstpage{30}}
%\bdoi{10.1.1.105.834}
\end{bhost}
\begin{bhost}
\begin{behost}
\binterref[locator-type=url]{https://web.comlab.ox.ac.uk/techreports/oucl/RR-05-02.pdf\#page=36}
\end{behost}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
M.~Compton,
{{Embedding
a fair CCS in Isabelle/HOL}}, in: Theorem Proving in Higher Order Logics:
Emerging Trends Proceedings, 2005, p.~30. \href {https://doi.org/10.1.1.105.834} 10.1.1.105.834.
\url{https://web.comlab.ox.ac.uk/techreports/oucl/RR-05-02.pdf\#page=36}
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b36 ###
\bibitem{chaudhuri2015lightweight}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{K.} \snm{Chaudhuri}}
\bauthor{\fnm{M.} \snm{Cimini}}
\bauthor{\fnm{D.} \snm{Miller}}
\btitle{A lightweight formalization of the metatheory of bisimulation-up-to}
\end{bcontribution}
\begin{bhost}
\begin{beditedbook}
\btitle{Proceedings of the 2015 Conference on Certified Programs and Proofs}
\bdate{2015}
\bpublisher{\bname{ACM}}
\end{beditedbook}
\bpages{\bfirstpage{157}\blastpage{166}}
\bdoi{10.1145/2676724.2693170}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
K.~Chaudhuri, M.~Cimini, D.~Miller, A lightweight formalization of the
metatheory of bisimulation-up-to, in: Proceedings of the 2015 Conference
on Certified Programs and Proofs, ACM, 2015, pp. 157--166. 10.1145/2676724.2693170.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b37 ###
\bibitem{pous2007new}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{D.} \snm{Pous}}
\btitle{New up-to techniques for weak bisimulation}
\end{bcontribution}
\begin{bhost}
\begin{bissue}
\bseries{\btitle{Theor. Comput. Sci.} \bvolumeno{380}}
\bdate{2007}
\end{bissue}
\bpages{\bfirstpage{164}\blastpage{180}}
\bdoi{10.1016/j.tcs.2007.02.060}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
D.~Pous, New up-to techniques for weak bisimulation, Theoretical Computer
Science 380 (2007) 164--180. 10.1016/j.tcs.2007.02.060.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b38 ###
\bibitem{kahsai2008implementing}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{T.} \snm{Kahsai}}
\bauthor{\fnm{M.} \snm{Miculan}}
\btitle{Implementing spi calculus using nominal techniques}
\end{bcontribution}
\begin{bhost}
\begin{beditedbook}
\btitle{Conference on Computability in Europe}
\bdate{2008}
\bpublisher{\bname{Springer}}
\end{beditedbook}
\bpages{\bfirstpage{294}\blastpage{305}}
\bdoi{10.1007/978-3-540-69407-6\_33}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
T.~Kahsai, M.~Miculan, Implementing spi calculus using nominal techniques,
in: Conference on Computability in Europe, Springer, 2008, pp. 294--305.
10.1007/978-3-540-69407-6\_33.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b39 ###
\bibitem{hirschkoff1997full}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{D.} \snm{Hirschkoff}}
\btitle{A full formalisation of $\pi $-calculus theory in the calculus of constructions}
\end{bcontribution}
\begin{bhost}
\begin{beditedbook}
\btitle{International Conference on Theorem Proving in Higher Order Logics}
\bdate{1997}
\bpublisher{\bname{Springer}}
\end{beditedbook}
\bpages{\bfirstpage{153}\blastpage{169}}
\bdoi{10.1007/BFb0028392}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
D.~Hirschkoff, A full formalisation of $\pi $-calculus theory in the calculus
of constructions, in: International Conference on Theorem Proving in Higher
Order Logics, Springer, 1997, pp. 153--169. 10.1007/BFb0028392.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b40 ###
\bibitem{DurierHS17}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{A.} \snm{Durier}}
\bauthor{\fnm{D.} \snm{Hirschkoff}}
\bauthor{\fnm{D.} \snm{Sangiorgi}}
\btitle{Divergence and unique solution of equations}
\end{bcontribution}
\begin{bhost}
\begin{beditedbook}
\beditors{%
\beditor{\fnm{R.} \snm{Meyer}}
\beditor{\fnm{U.} \snm{Nestmann}}}
\btitle{28th International Conference on Concurrency Theory (CONCUR 2017)}
\bbookseries{
\bseries{\btitle{Leibniz International Proceedings in Informatics (LIPIcs)}\bvolumeno{85}}}
\bdate{2017}
\bpublisher{\bname{Schloss
Dagstuhl--Leibniz-Zentrum fuer Informatik}\blocation{Dagstuhl, Germany}}
\end{beditedbook}
\bpages{\bfirstpage{11:1}\blastpage{11:16}}
\bdoi{10.4230/LIPIcs.CONCUR.2017.11}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
A.~Durier, D.~Hirschkoff, D.~Sangiorgi, Divergence and unique solution
of equations, in: R.~Meyer, U.~Nestmann (Eds.), 28th International Conference
on Concurrency Theory (CONCUR 2017), Vol.~85 of Leibniz International Proceedings
in Informatics (LIPIcs), Schloss Dagstuhl--Leibniz-Zentrum fuer Informatik,
Dagstuhl, Germany, 2017, pp. 11:1--11:16. 10.4230/LIPIcs.CONCUR.2017.11.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

%b41 ###
\bibitem{DurierHS18}
\begin{bsubitem}
\begin{bcontribution}%[language=fr]%de,it,pl,ru
\bauthor{\fnm{A.} \snm{Durier}}
\bauthor{\fnm{D.} \snm{Hirschkoff}}
\bauthor{\fnm{D.} \snm{Sangiorgi}}
\btitle{Eager functions as processes}
\end{bcontribution}
\begin{bhost}
\begin{beditedbook}
\btitle{\xch{33rd Annual}{33nd Annual} {ACM/IEEE} Symposium on Logic in Computer Science, {LICS} 2018}
\bdate{2018}
\bpublisher{\bname{{IEEE} Computer Society}}
\end{beditedbook}
\bpages{\bfirstpage{364}\blastpage{373}}
\bdoi{10.1145/3209108.3209152}
\end{bhost}
\end{bsubitem}
%
\OrigBibText
A.~Durier, D.~Hirschkoff, D.~Sangiorgi, Eager functions as processes, in:
33nd Annual {ACM/IEEE} Symposium on Logic in Computer Science, {LICS} 2018,
{IEEE} Computer Society, 2018, pp. 364--373. 10.1145/3209108.3209152.
\endOrigBibText
\bptok{structpyb}%
\endbibitem

\end{thebibliography}

\end{backmatter}
\end{document}

### 2020-07-31 ic-journal/equa.tex
Editorial changes to LaTeX sources

@@
  \end{definition}
-Similarily, the \emph{(unique) solution of a system of equations for $\sim$}
+ Similarly, % I&C editor issue 4
+the \emph{(unique) solution of a system of equations for $\sim$}
 (or for $\rapprox$) can be obtained by replacing all occurrences of $\wb$

### 2020-07-31 ic-journal/expansion.tex
Editorial changes to LaTeX sources

@@
 
-One basic property of rooted bisimiarity is congruence,
+One basic property of rooted bisimilarity is congruence, % editorial
 indeed it is  the coarsest congruence contained in bisimilarity

### 2020-07-31 ic-journal/intro.tex
Editorial changes to LaTeX sources

@@
 equivalences and preorders that share similar proof structures.
-Such structural simililarities can be found, for instance, in the
+Such structural similarities can be found, for instance, in the % editorial changes
 following cases: the proofs that rooted bisimilarity and rooted
@@
 Section~\ref{sec:multivariate} describes the extension to the \multivariate case.
-Finally, in Section~\ref{s:rel} and \ref{s:concl} we discuss the related work,
+Finally, in Sections~\ref{s:rel} and \ref{s:concl} we discuss the related work, % editorial
 conclusions, and a few directions for future work.

### 2020-07-31 ic-journal/related.tex
Editorial changes to LaTeX sources

@@
 More details can be found in Bengtson's PhD thesis~\cite{bengtson2010formalising}. For CCS, 
-he has formalized basic properties for strong/weak equivalence (congruence, basic
+he has formalised basic properties for strong/weak equivalence (congruence, basic % editorial
  algebraic laws); the CCS syntax does not have constants

### 2020-07-31 ic-journal/unique.tex
Editorial changes to LaTeX sources

@@
 constraints on summation.
-The schema of the proofs is almost identical, because all 
-properties of $\rcontr$ needed in this proof is its precongruence, which is
+The schema of the proofs is almost identical, because
+the only property % I&C editor issue 5
+of $\rcontr$ needed in this proof is its precongruence, which is
 indeed true for all weakly guarded contexts: % removed "direct sums"

### 2020-07-31 ic-journal/coarsest.tex
Updated generated LaTeX sources

@@
 
-The formal proofs of Theorem~\ref{thm:coarsestR} and
+The formal proofs of Theorems~\ref{thm:coarsestR} and % editorial
 \ref{thm:coarsestPre} precisely follow Milner~\citep[p.~153--154]{Mil89}.
@@
 transition graphs of the two given processes.
-This can be done by following Klop's contruction.
+This can be done by following Klop's construction. % editorial
  We call the processes in this construction the ``Klop processes'':
@@
 As the number of all Klop processes in this set is (countably) infinite, and
-they are all pairwise non-bisimiar,
+they are all pairwise non-bisimilar, % editorial changes
 we can always choose a number, corresponding to a Klop process,
@@
 in $\mathscr{L}$.
-This property is captured by appealing to the following set-theoreric
-lamma (see~\cite{Tian:2017wrba} for its proof):
+This property is captured by appealing to the following set-theoretic % editorial changes
+lemma (see~\cite{Tian:2017wrba} for its proof): % editorial changes
 \begin{lemma}
@@
 (\texttt{COARSEST_CONGR_FINITE}). The same proof idea can also be used with
- contraction and rooted contration.
+ contraction and rooted contraction. % editorial changes
 

### 2020-07-31 ic-journal/formal.tex
Updated generated LaTeX sources

@@
 As a consequence, theories and proofs verified in HOL are easier to understand
- for people who are not familar with more advanced dependent type
+ for people who are not familiar with more advanced dependent type % editorial
  theories, e.g. the Calculus of Constructions implemented in Coq.
@@
 All proofs are eventually reduced to applications of the above rules,
-which also give the semantics of two foundamental
+which also give the semantics of two fundamental % editorial
 logical connectives, equality ($=$) and implication

### 2020-07-31 ic-journal/multivariate.tex
Updated generated LaTeX sources

@@
 %% "transition induction" (1/2)
-difficulities in transition inductions. As an evidence,
+difficulties in transition inductions. As an evidence, % editorial changes
 we prove the following fundamental property of
@@
 substitution on $E'$ using a reduced map~--- without $X$~--- so that all
-occurences of $X$ in $E'$ are correctly bypassed.
+occurrences of $X$ in $E'$ are correctly bypassed. % editorial changes
 Since \HOLinline{\HOLConst{CCS_SUBST}} only runs
@@
 \begin{lemma}[\texttt{CCS_SUBST_elim}]
-If the free variables of $E$ is disjoint with \HOLinline{\HOLFreeVar{Xs}}, a
+If the free variables of $E$ are % I&C editor issue 8
+disjoint with \HOLinline{\HOLFreeVar{Xs}}, a
 substitution of \HOLinline{\HOLFreeVar{Xs}} in $E$ does not change $E$:
@@
 guarded variants, but care is needed for
-variables that occur within a recusion. We have preferred a different
-solution, in which the definitions of \multivariate contexts  is based on the
-existing \univariate definitions.
+variables that occur within a recursion. % I&C editor issue 9
+We prefer % I&C editor issue 10
+a different solution, in which the definitions of \multivariate contexts are % I&C editor issue 10
+based on the existing \univariate definitions.
 For this, intuitively, we replace a single variable with a hole (viewing
@@
   \HOLinline{\HOLFreeVar{Xs}}.}
-(The \multivariate guardedness and sequentiality can also be defined similarily, using
+(The \multivariate guardedness and sequentiality can also be defined similarly, using % editorial
 their \univariate companions \HOLinline{\HOLConst{SG}} and \HOLinline{\HOLConst{SEQ}}.)
@@
 $E_i$, the set of its bound variables should be \emph{disjoint} from $\til X$.
-These requirements yield the fomal
+These requirements yield the formal % editorial
 definition of \multivariate CCS equation:

### 2020-07-31 ic-journal/sos.tex
Updated generated LaTeX sources

@@
 union of all visible actions (input and output labels) and the invisible action $\tau$
-(\texttt{tau}). For instace, the input \emph{action} $a$ and output
+(\texttt{tau}). For instance, the input \emph{action} $a$ and output % editorial
 \emph{action} $\overline{b}$ of type ``\HOLinline{\HOLTyOp{string} \HOLTyOp{Action}}''
@@
 \end{alltt}
-The only two insteresting cases are those for agent variables and recursion:
+The only two interesting cases are those for agent variables and recursion: % editorial
 \begin{alltt}

### 2021-10-27 ic-journal/multivariate.tex
Updated HOL scripts from HOL4 official; rebuilt paper PDF without line numbers
Signed-off-by: Chun Tian (binghe) <binghe.lisp@gmail.com>

@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{IS_PROC} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{IS_PROC} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\hfill{[TRANS_PROC]}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{IS_PROC} \HOLBoundVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{IS_PROC} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\hfill{[TRANS_PROC]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E}\hfill{[TRANS_FV]}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E}\hfill{[TRANS_FV]}
 \end{alltt}
@@
 \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u}.
-\HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{l} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
-            \HOLBoundVar{P} \HOLBoundVar{E} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \ensuremath{(}\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLBoundVar{l}\ensuremath{)}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
-            \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \HOLSymConst{\ensuremath{\tau}} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{l} \HOLBoundVar{L}.
-            \HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLBoundVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-            \HOLBoundVar{P} \ensuremath{(}\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{rf}.
-\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)} \ensuremath{(}\HOLConst{relabel} \HOLBoundVar{rf} \HOLBoundVar{u}\ensuremath{)} \ensuremath{(}\HOLConst{relab} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{rf}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+\HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\ensuremath{)} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{l} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+          \HOLBoundVar{P} \HOLBoundVar{E} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{P} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \ensuremath{(}\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLBoundVar{l}\ensuremath{)}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}}
+          \HOLBoundVar{P} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\ensuremath{)} \HOLSymConst{\ensuremath{\tau}} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLBoundVar{l} \HOLBoundVar{L}.
+          \HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLBoundVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLBoundVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
+          \HOLBoundVar{P} \ensuremath{(}\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{u} \ensuremath{(}\ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLBoundVar{rf}.
+\HOLBoundVar{P} \HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{P} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)} \ensuremath{(}\HOLConst{relabel} \HOLBoundVar{rf} \HOLBoundVar{u}\ensuremath{)} \ensuremath{(}\HOLConst{relab} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLBoundVar{rf}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \HOLBoundVar{X} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}.
@@
 \end{alltt}
-The above long theorem is of the form \HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLBoundVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}} (with $a_0, a_1, a_2$ renamed), where the
+The above long theorem is of the form \HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.\\\;\HOLFreeVar{X}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLBoundVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}} (with $a_0, a_1, a_2$ renamed), where the
 outermost universal quantifier $P$ is a higher-order
@@
 The proof goal is actually in the form of
-\HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLFreeVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}}, where
-\HOLinline{\HOLFreeVar{P}\\\;\HOLSymConst{\ensuremath{=}}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}.\\\;\HOLConst{FV}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime}}\\\;\HOLSymConst{\HOLTokenSubset{}}\\\;\HOLConst{FV}\\\;\HOLBoundVar{E}\ensuremath{)}}.
+\HOLinline{\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.\\\;\HOLBoundVar{E}\\\;\HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\\\;\HOLSymConst{\HOLTokenImp{}}\\\;\HOLFreeVar{P}\\\;\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}}, where
+\HOLinline{\HOLFreeVar{P}\\\;\HOLSymConst{\ensuremath{=}}\\\;\ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}\\\;\HOLBoundVar{u}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.\\\;\HOLConst{FV}\\\;\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\\\;\HOLSymConst{\HOLTokenSubset{}}\\\;\HOLConst{FV}\\\;\HOLBoundVar{E}\ensuremath{)}}.
 Thus, if we can prove
@@
 \begin{alltt}
-        \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}
+        \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}
    ------------------------------------
     0.
-\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\HOLConst{FV} \ensuremath{(}\ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\hfill{[FV_SUBSET]}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\HOLConst{FV} \ensuremath{(}\ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLBoundVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\hfill{[FV_SUBSET]}
 \end{alltt}
@@
 Thus we can enrich the assumptions of the current proof goal with above
-lemma, and obtain \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} by the transitivity of $\subseteq$:
+lemma, and obtain \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} by the transitivity of $\subseteq$:
 \begin{alltt}
-        \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}
+        \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}
    ------------------------------------
     0.
-\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
     1.
 \HOLinline{\HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
-    2.  \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
+    2.  \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
 \end{alltt}
-Knowing \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} we cannot prove \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}.
-However, if we knew \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}}}, then \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\ensuremath{=}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}}}, and then
-\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}, no matter if \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E}} or not, and the proof
+Knowing \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}} we cannot prove \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}.
+However, if we knew \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}}}, then \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\ensuremath{=}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}}}, and then
+\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLConst{DELETE} \HOLFreeVar{X} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{X}}, no matter if \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E}} or not, and the proof
 would complete. Thus it remains to show that
 \begin{alltt}
-        \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}}}
+        \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}}}
    ------------------------------------
     0.
-\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
     1.
 \HOLinline{\HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
-    2.  \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
+    2.  \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
 \end{alltt}
@@
 the goal does not hold, i.e.
-\HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}}}, then by assumption 0 we have \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}:
+\HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}}}, then by assumption 0 we have \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}:
 \begin{alltt}
@@
     0.
-\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+\HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
     1.
 \HOLinline{\HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
-    2.  \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
-    3.  \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime}}}
+    2.  \HOLinline{\HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{FV} \HOLFreeVar{E}}
+    3.  \HOLinline{\HOLFreeVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}}}
     4.
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\HOLBoundVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLBoundVar{X} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\hfill{[NOTIN_FV_lemma]}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\HOLBoundVar{X} \HOLSymConst{\HOLTokenNotIn{}} \HOLConst{FV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLBoundVar{X} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\hfill{[NOTIN_FV_lemma]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E}\hfill{[TRANS_BV]}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E}\hfill{[TRANS_BV]}
 \end{alltt}
@@
 % \begin{alltt}
-%         \HOLinline{\HOLConst{BV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLFreeVar{X} \HOLConst{INSERT} \HOLConst{BV} \HOLFreeVar{E}}
+%         \HOLinline{\HOLConst{BV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLFreeVar{X} \HOLConst{INSERT} \HOLConst{BV} \HOLFreeVar{E}}
 %    ------------------------------------
 %     0.
-\HOLinline{\HOLConst{BV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+\HOLinline{\HOLConst{BV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
 % \end{alltt}
@@
 %     0.
-\HOLinline{\HOLConst{BV} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
+\HOLinline{\HOLConst{BV} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLConst{rec} \HOLFreeVar{X} \HOLFreeVar{E}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}}
 % \end{alltt}
@@
 % \begin{alltt}
-% \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\HOLConst{BV} \ensuremath{(}\ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\hfill{[BV_SUBSET]}
+% \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\HOLConst{BV} \ensuremath{(}\ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E} \HOLSymConst{\HOLTokenUnion{}} \HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\hfill{[BV_SUBSET]}
 % \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{]}\ensuremath{/}\ensuremath{[}\HOLFreeVar{X}\ensuremath{]}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}
+\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime{}}}\ensuremath{]}\ensuremath{/}\ensuremath{[}\HOLFreeVar{X}\ensuremath{]}\ensuremath{]} \HOLFreeVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime{}}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}
 \end{alltt}
@@
      \HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
-           \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-           \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-               \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-               \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+     \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \ensuremath{\HOLBoundVar{P}\sp{\prime{}}}.
+       \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+         \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+         \ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}}
          \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
-\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime}}
+\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}
 \end{alltt}

### 2021-10-27 ic-journal/part2.tex
Updated HOL scripts from HOL4 official; rebuilt paper PDF without line numbers
Signed-off-by: Chun Tian (binghe) <binghe.lisp@gmail.com>

@@
 \HOLTokenTurnstile{} \HOLConst{WG} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
-\HOLFreeVar{E} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\HOLConst{CONTEXT} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
-\HOLFreeVar{E} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{Q}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \ensuremath{\HOLBoundVar{P}\sp{\prime{}}}.
+\HOLFreeVar{E} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\HOLConst{CONTEXT} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLFreeVar{E} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLBoundVar{Q}
 \end{alltt}
@@
 \HOLTokenTurnstile{} \HOLConst{WEAK_BISIM} \HOLFreeVar{Wbsm} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
      \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u}.
@@
 \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
-\ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+\ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
           \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
-\ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}.
+\ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}.
 \HOLBoundVar{E} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Wbsm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \ensuremath{\HOLBoundVar{E}\sp{\prime}}
+     \HOLBoundVar{E} \HOLSymConst{\HOLTokenObsCongr} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}
 \end{alltt}
@@
 \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{G} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLFreeVar{G} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
-       \HOLFreeVar{G} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}.
-\HOLConst{SEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \ensuremath{\HOLBoundVar{P}\sp{\prime{}}}.
+     \HOLFreeVar{G} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}.
+\HOLConst{SEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
 \HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}
@@
 \HOLTokenTurnstile{} \HOLConst{SG} \HOLFreeVar{G} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GSEQ} \HOLFreeVar{G} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
-       \HOLFreeVar{G} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}.
-\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P} \HOLBoundVar{a} \ensuremath{\HOLBoundVar{P}\sp{\prime{}}}.
+     \HOLFreeVar{G} \HOLBoundVar{P} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{H}.
+\HOLConst{GSEQ} \HOLBoundVar{H} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{a} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \HOLBoundVar{H}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{H} \HOLBoundVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
 \HOLFreeVar{G} \HOLBoundVar{Q} \HOLTokenTransBegin\HOLBoundVar{a}\HOLTokenTransEnd \HOLBoundVar{H} \HOLBoundVar{Q}
@@
      \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{P}.
-         \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x}. \HOLBoundVar{P} \HOLBoundVar{x} \ensuremath{[}\ensuremath{]} \HOLBoundVar{x}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+\ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x}.
+\HOLBoundVar{P} \HOLBoundVar{x} \ensuremath{[}\ensuremath{]} \HOLBoundVar{x}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
          \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{h} \HOLBoundVar{y} \HOLBoundVar{t} \HOLBoundVar{z}.
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLFreeVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenEquiv{}}
+\HOLTokenTurnstile{} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLFreeVar{u}\HOLTokenWeakTransEnd \ensuremath{\HOLFreeVar{P}\sp{\prime{}}} \HOLSymConst{\HOLTokenEquiv{}}
    \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{acts}.
-       \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{acts} \ensuremath{\HOLFreeVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{NULL} \HOLBoundVar{acts} \HOLSymConst{\HOLTokenConj{}}
+     \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{acts} \ensuremath{\HOLFreeVar{P}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{NULL} \HOLBoundVar{acts} \HOLSymConst{\HOLTokenConj{}}
      \HOLKeyword{if} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLKeyword{then} \HOLConst{NO_LABEL} \HOLBoundVar{acts} \HOLKeyword{else} \HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLBoundVar{acts}\hfill{[WEAK_TRANS_AND_TRACE]}
@@
 \HOLConst{WGS} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{E} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenContracts{}} \HOLBoundVar{E} \HOLFreeVar{Q}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{C}.
-       \HOLConst{GCONTEXT} \HOLBoundVar{C} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{C}. \HOLConst{GCONTEXT} \HOLBoundVar{C} \HOLSymConst{\HOLTokenImp{}}
        \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{R}.
           \HOLBoundVar{C} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
-            \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}.
-                \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenContracts{}} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}}
+          \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime{}}}.
+            \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenContracts{}} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}}
             \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}.
-\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{y}\ensuremath{)}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C} \HOLFreeVar{Q}\ensuremath{)} \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLFreeVar{Q}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{y}\ensuremath{)}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C} \HOLFreeVar{Q}\ensuremath{)} \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sp{\prime{}}} \HOLFreeVar{Q}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}.
 \HOLBoundVar{C} \HOLFreeVar{P} \HOLTokenWeakTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
-           \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}.
-\HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenContracts{}} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{EPS}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C} \HOLFreeVar{Q}\ensuremath{)} \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLFreeVar{Q}\ensuremath{)}
+           \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime{}}}.
+\HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenContracts{}} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLSymConst{\HOLTokenRCompose{}} \HOLConst{EPS}\ensuremath{)} \ensuremath{(}\HOLBoundVar{C} \HOLFreeVar{Q}\ensuremath{)} \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sp{\prime{}}} \HOLFreeVar{Q}\ensuremath{)}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLConst{GCONTEXT} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}\ensuremath{)} \HOLFreeVar{P}\ensuremath{)} \HOLFreeVar{xs} \ensuremath{\HOLFreeVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{xs} \HOLSymConst{\HOLTokenLeq{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}.
-\HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLFreeVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
-\HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}\ensuremath{)} \HOLBoundVar{Q}\ensuremath{)} \HOLFreeVar{xs} \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLBoundVar{Q}\ensuremath{)}
+\HOLTokenTurnstile{} \HOLConst{GCONTEXT} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WGS} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}\ensuremath{)} \HOLFreeVar{P}\ensuremath{)} \HOLFreeVar{xs} \ensuremath{\HOLFreeVar{P}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{xs} \HOLSymConst{\HOLTokenLeq{}} \HOLFreeVar{n} \HOLSymConst{\HOLTokenImp{}}
+   \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime{}}}.
+\HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLFreeVar{P}\sp{\prime{}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Q}.
+\HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\HOLFreeVar{C} \HOLSymConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLFreeVar{E} \HOLFreeVar{n}\ensuremath{)} \HOLBoundVar{Q}\ensuremath{)} \HOLFreeVar{xs} \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sp{\prime{}}} \HOLBoundVar{Q}\ensuremath{)}
 \end{alltt}
@@
 \HOLTokenTurnstile{} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenImp{}}
-   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{xs} \HOLBoundVar{l} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
-       \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{xs} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{UNIQUE_LABEL} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{xs}\sp{\prime}} \ensuremath{\HOLBoundVar{Q}\sp{\prime}}.
-           \HOLConst{TRACE} \HOLFreeVar{Q} \ensuremath{\HOLBoundVar{xs}\sp{\prime}} \ensuremath{\HOLBoundVar{Q}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \ensuremath{\HOLBoundVar{xs}\sp{\prime}} \HOLSymConst{\HOLTokenLeq{}} \HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenConj{}}
-           \HOLConst{UNIQUE_LABEL} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \ensuremath{\HOLBoundVar{xs}\sp{\prime}}\hfill{[contracts_AND_TRACE_label]}
+   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{xs} \HOLBoundVar{l} \ensuremath{\HOLBoundVar{P}\sp{\prime{}}}.
+     \HOLConst{TRACE} \HOLFreeVar{P} \HOLBoundVar{xs} \ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{UNIQUE_LABEL} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenImp{}}
+     \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{xs}\sp{\prime{}}} \ensuremath{\HOLBoundVar{Q}\sp{\prime{}}}.
+       \HOLConst{TRACE} \HOLFreeVar{Q} \ensuremath{\HOLBoundVar{xs}\sp{\prime{}}} \ensuremath{\HOLBoundVar{Q}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{P} \HOLSymConst{\HOLTokenContracts{}} \HOLFreeVar{Q} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \ensuremath{\HOLBoundVar{xs}\sp{\prime{}}} \HOLSymConst{\HOLTokenLeq{}} \HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{UNIQUE_LABEL} \ensuremath{(}\HOLConst{label} \HOLBoundVar{l}\ensuremath{)} \ensuremath{\HOLBoundVar{xs}\sp{\prime{}}}\hfill{[contracts_AND_TRACE_label]}
 \end{alltt}

### 2021-10-27 ic-journal/sos.tex
Updated HOL scripts from HOL4 official; rebuilt paper PDF without line numbers
Signed-off-by: Chun Tian (binghe) <binghe.lisp@gmail.com>

@@
 variable substitution & $E\{E'/X\}$ & \texttt{CCS_Subst E E' X} &
-                                           \texttt{[E'/X]  E} & \HOLinline{\ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}} \\
+                                           \texttt{[E'/X]  E} & \HOLinline{\ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime{}}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}} \\
 transition & $P\overset{\mu}{\longrightarrow}Q$
@@
 \HOLTokenTurnstile{} \HOLFreeVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \HOLFreeVar{E}\hfill\texttt{[PREFIX]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}\hfill\texttt{[SUM1]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}\hfill\texttt{[SUM2]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sp{\prime}}\hfill\texttt{[PAR1]}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}\hfill\texttt{[PAR2]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}\hfill\texttt{[SUM1]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}\hfill\texttt{[SUM2]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}}\hfill\texttt{[PAR1]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenImp{}} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\ensuremath{\mid}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}\hfill\texttt{[PAR2]}
 \end{alltt}
 \begin{equation*}
-\infer[\HOLRuleName{PAR3}]{\HOLinline{\HOLFreeVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}}&\HOLinline{\ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLFreeVar{l}\ensuremath{)}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}}}
+\infer[\HOLRuleName{PAR3}]{\HOLinline{\HOLFreeVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLTokenTransBegin\HOLSymConst{\ensuremath{\tau}}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLFreeVar{l}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}}}&\HOLinline{\ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLTokenTransBegin\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLFreeVar{l}\ensuremath{)}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}}}
 \end{equation*}
 \begin{equation*}
-\infer[\HOLRuleName{RESTR}]{\HOLinline{\ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \ensuremath{\HOLFreeVar{E}\sp{\prime}}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime}}}&\HOLinline{\HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLFreeVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}}}
+\infer[\HOLRuleName{RESTR}]{\HOLinline{\ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{(\nu}\HOLFreeVar{L}\ensuremath{)} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime{}}}}&\HOLinline{\HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \HOLFreeVar{u} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLFreeVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLFreeVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLFreeVar{L}}}
 \end{equation*}
 \begin{equation*}
-\infer[\HOLRuleName{RELABELING}]{\HOLinline{\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLFreeVar{rf}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime}}}}
+\infer[\HOLRuleName{RELABELING}]{\HOLinline{\HOLConst{relab} \HOLFreeVar{E} \HOLFreeVar{rf} \HOLTokenTransBegin\HOLConst{relabel} \HOLFreeVar{rf} \HOLFreeVar{u}\HOLTokenTransEnd \HOLConst{relab} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLFreeVar{rf}}}{\HOLinline{\HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime{}}}}}
 \end{equation*}
@@
      \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenEquiv{}}
-       \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenDisj{}} \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \HOLBoundVar{l} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
-            \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}}
-            \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLBoundVar{l}\ensuremath{)}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{l} \HOLBoundVar{L}.
-            \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+     \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenDisj{}} \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
+     \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
+     \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
+     \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
+     \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \HOLBoundVar{l} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
+        \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}}
+        \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLTokenTransBegin\HOLConst{label} \ensuremath{(}\HOLConst{COMPL} \HOLBoundVar{l}\ensuremath{)}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
+     \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLBoundVar{l} \HOLBoundVar{L}.
+        \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}}
         \ensuremath{(}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{=}} \HOLSymConst{\ensuremath{\tau}} \HOLSymConst{\HOLTokenDisj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{=}} \HOLConst{label} \HOLBoundVar{l} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L} \HOLSymConst{\HOLTokenConj{}} \HOLConst{COMPL} \HOLBoundVar{l} \HOLSymConst{\HOLTokenNotIn{}} \HOLBoundVar{L}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
-       \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{rf}.
-            \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{=}} \HOLConst{relabel} \HOLBoundVar{rf} \HOLBoundVar{u} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \HOLConst{relab} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLBoundVar{rf} \HOLSymConst{\HOLTokenConj{}}
-            \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}} \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \HOLBoundVar{X}.
+     \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLBoundVar{rf}.
+        \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{=}} \HOLConst{relabel} \HOLBoundVar{rf} \HOLBoundVar{u} \HOLSymConst{\HOLTokenConj{}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \HOLSymConst{\ensuremath{=}} \HOLConst{relab} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLBoundVar{rf} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\ensuremath{)} \HOLSymConst{\HOLTokenDisj{}}
+     \HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{E} \HOLBoundVar{X}.
 \ensuremath{\HOLBoundVar{a}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \ensuremath{[}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime\prime}} \HOLSymConst{\HOLTokenEquiv{}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime\prime}} \HOLSymConst{\HOLTokenDisj{}} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime\prime}}\hfill{[TRANS_SUM_EQ]}
+\HOLTokenTurnstile{} \HOLFreeVar{E} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime{}\prime{}}} \HOLSymConst{\HOLTokenEquiv{}} \HOLFreeVar{E} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime{}\prime{}}} \HOLSymConst{\HOLTokenDisj{}} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLTokenTransBegin\HOLFreeVar{u}\HOLTokenTransEnd \ensuremath{\HOLFreeVar{E}\sp{\prime{}\prime{}}}\hfill{[TRANS_SUM_EQ]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}\hfill{[CCS_Subst_sum]}
+\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime{}}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime{}}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime{}}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{\HOLFreeVar{E}\sb{\mathrm{2}}}\hfill{[CCS_Subst_sum]}
 \end{alltt}
@@
 \begin{alltt}
-\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{var} \HOLFreeVar{Y}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \ensuremath{\HOLFreeVar{E}\sp{\prime}} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}\hfill{[CCS_Subst_var]}
-\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} \ensuremath{(}\ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\hfill{[CCS_Subst_rec]}
+\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime{}}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{var} \HOLFreeVar{Y}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \ensuremath{\HOLFreeVar{E}\sp{\prime{}}} \HOLKeyword{else} \HOLConst{var} \HOLFreeVar{Y}\hfill{[CCS_Subst_var]}
+\HOLTokenTurnstile{} \ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime{}}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLKeyword{if} \HOLFreeVar{Y} \HOLSymConst{\ensuremath{=}} \HOLFreeVar{X} \HOLKeyword{then} \HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E} \HOLKeyword{else} \HOLConst{rec} \HOLFreeVar{Y} \ensuremath{(}\ensuremath{[}\ensuremath{\HOLFreeVar{E}\sp{\prime{}}}\ensuremath{/}\HOLFreeVar{X}\ensuremath{]} \HOLFreeVar{E}\ensuremath{)}\hfill{[CCS_Subst_rec]}
 \end{alltt}

### 2021-10-27 paper/HOLMultivariate.tex
Updated HOL scripts from HOL4 official; rebuilt paper PDF without line numbers
Signed-off-by: Chun Tian (binghe) <binghe.lisp@gmail.com>

@@
-\newcommand{\HOLMultivariateDate}{21 June 2020}
-\newcommand{\HOLMultivariateTime}{18:11}
+\newcommand{\HOLMultivariateDate}{27 October 2021}
+\newcommand{\HOLMultivariateTime}{11:42}
 \begin{SaveVerbatim}{HOLMultivariateDefinitionsCCSXXequationXXdef}
@@
    \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
-        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
-        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+      \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
-        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
-        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+      \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
    \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{L} \HOLBoundVar{E}.
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
+     \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXsing}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\ensuremath{[}\ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{]}\ensuremath{/}\ensuremath{[}\HOLBoundVar{X}\ensuremath{]}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\ensuremath{[}\ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\ensuremath{]}\ensuremath{/}\ensuremath{[}\HOLBoundVar{X}\ensuremath{]}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \begin{SaveVerbatim}{HOLMultivariateTheoremsCCSXXSUBSTXXSING}
-\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-\HOLConst{CCS_SUBST} \ensuremath{(}\HOLConst{FEMPTY} \HOLSymConst{|+} \ensuremath{(}\HOLBoundVar{X}\HOLSymConst{,}\ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}
+\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+\HOLConst{CCS_SUBST} \ensuremath{(}\HOLConst{FEMPTY} \HOLSymConst{|+} \ensuremath{(}\HOLBoundVar{X}\HOLSymConst{,}\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\ensuremath{)}\ensuremath{)} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}.
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
-       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
+     \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{\HOLBoundVar{E}\sb{\mathrm{2}}}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps}.
-       \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \ensuremath{(}\HOLConst{FDOM} \ensuremath{(}\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
+     \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLConst{FDOM} \ensuremath{(}\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLBoundVar{Qs}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{OBS_CONGR} \HOLBoundVar{Ps} \HOLBoundVar{Qs} \HOLSymConst{\HOLTokenImp{}}
+     \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{OBS_CONGR} \HOLBoundVar{Ps} \HOLBoundVar{Qs} \HOLSymConst{\HOLTokenImp{}}
      \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}.
@@
        \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
-               \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-               \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sp{\prime}}.
-                   \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}}
-                   \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-                   \ensuremath{(}\ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \ensuremath{\HOLBoundVar{P}\sp{\prime{}}}.
+         \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\HOLTokenImp{}}
+         \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sp{\prime{}}}.
+           \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}}
+           \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
            \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
-                       \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-                       \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime}}
+             \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime{}}}
 \end{SaveVerbatim}
@@
             \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
-                \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}.
-                    \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{C}\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-                    \HOLBoundVar{R} \HOLConst{contracts} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
+            \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime{}}}.
+              \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+              \HOLBoundVar{R} \HOLConst{contracts} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}}
               \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLConst{O} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}.
-\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{y}\ensuremath{)}\ensuremath{)}
-                      \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+\HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{y}\ensuremath{)}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)}
+                \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
          \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}.
 \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}
-               \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}.
-                   \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{C}\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-                   \HOLBoundVar{R} \HOLConst{contracts} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
-                   \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLConst{O} \HOLConst{EPS}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime}}\ensuremath{)}
+             \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime{}}}.
+               \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+               \HOLBoundVar{R} \HOLConst{contracts} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}}
+               \ensuremath{(}\HOLConst{WEAK_EQUIV} \HOLConst{O} \HOLConst{EPS}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}}\ensuremath{)}
 \end{SaveVerbatim}
@@
 \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-           \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
+         \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{u} \ensuremath{\HOLBoundVar{P}\sp{\prime{}}}.
            \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
@@
 \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-               \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-               \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}.
-                   \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{C}\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-                   \ensuremath{(}\ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+           \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\HOLTokenImp{}}
+           \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime{}}}.
+             \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+             \ensuremath{(}\ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
              \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
                \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-                       \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime}}
+               \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{C} \HOLBoundVar{E}.
-       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
+     \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+     \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
      \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}.
@@
 \HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{x} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
+     \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{x} \ensuremath{\HOLBoundVar{P}\sp{\prime{}}}.
        \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
@@
 \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-           \ensuremath{[}\HOLBoundVar{E} \HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
-           \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime}}.
-               \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{C}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{C}\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-               \ensuremath{(}\ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \ensuremath{[}\HOLBoundVar{E} \HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime{}}}.
+         \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+         \ensuremath{(}\ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
          \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
-                   \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-                   \ensuremath{[}\HOLBoundVar{E} \HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime}}
+           \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLBoundVar{E} \HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C} \HOLTokenTransBegin\HOLBoundVar{x}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime{}}}
 \end{SaveVerbatim}
@@
 \HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{C} \HOLBoundVar{E} \ensuremath{\HOLBoundVar{C}\sb{\mathrm{0}}}.
-       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
-       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-       \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
-\HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
+     \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{C} \HOLSymConst{\HOLTokenConj{}}
+     \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
+\HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+     \ensuremath{(}\ensuremath{\HOLBoundVar{C}\sb{\mathrm{0}}} \HOLSymConst{\ensuremath{=}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{Ys}.
 \ensuremath{[}\HOLBoundVar{Ys}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n} \HOLBoundVar{xs} \HOLBoundVar{Ps} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
+     \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{n} \HOLBoundVar{xs} \HOLBoundVar{Ps} \ensuremath{\HOLBoundVar{P}\sp{\prime{}}}.
        \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
@@
 \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
-           \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\ensuremath{\HOLBoundVar{C}\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}\ensuremath{)} \HOLBoundVar{Ps}\ensuremath{)} \HOLBoundVar{xs} \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenLeq{}} \HOLBoundVar{n} \HOLSymConst{\HOLTokenImp{}}
-           \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime\prime}}.
-               \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{C}\sp{\prime\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{C}\sp{\prime\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
-               \ensuremath{(}\ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+       \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\ensuremath{\HOLBoundVar{C}\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}\ensuremath{)} \HOLBoundVar{Ps}\ensuremath{)} \HOLBoundVar{xs} \ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenLeq{}} \HOLBoundVar{n} \HOLSymConst{\HOLTokenImp{}}
+       \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{C}\sp{\prime{}\prime{}}}.
+         \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{\HOLBoundVar{C}\sp{\prime{}\prime{}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{C}\sp{\prime{}\prime{}}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
+         \ensuremath{(}\ensuremath{\HOLBoundVar{P}\sp{\prime{}}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime{}\prime{}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
          \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}.
            \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
-                   \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\ensuremath{\HOLBoundVar{C}\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}\ensuremath{)} \HOLBoundVar{Qs}\ensuremath{)} \HOLBoundVar{xs} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime\prime}}\ensuremath{)}
+           \HOLConst{TRACE} \ensuremath{(}\ensuremath{(}\ensuremath{\HOLBoundVar{C}\sb{\mathrm{0}}} \HOLConst{\HOLTokenCompose} \HOLConst{FUNPOW} \HOLBoundVar{E} \HOLBoundVar{n}\ensuremath{)} \HOLBoundVar{Qs}\ensuremath{)} \HOLBoundVar{xs} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{C}\sp{\prime{}\prime{}}}\ensuremath{)}
 \end{SaveVerbatim}
